### 2015-11-02 paper/sigplanconf-template.tex
Adding paper template

%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
%               sigplanconf-guide.pdf
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------

\documentclass{sigplanconf}

% The following \documentclass options may be useful:

% preprint      Remove this option only once the paper is in final form.
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% authoryear    To obtain author/year citation style instead of numeric.

\usepackage{amsmath}

\begin{document}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
\copyrightyear{20yy} 
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
\doi{nnnnnnn.nnnnnnn}

% Uncomment one of the following two, if you are not going for the 
% traditional copyright transfer agreement.

%\exclusivelicense                % ACM gets exclusive license to publish, 
                                  % you retain copyright

%\permissiontopublish             % ACM gets nonexclusive license to publish
                                  % (paid open-access papers, 
                                  % short abstracts)

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Title Text}
\subtitle{Subtitle Text, if any}

\authorinfo{Name1}
           {Affiliation1}
           {Email1}
\authorinfo{Name2\and Name3}
           {Affiliation2/3}
           {Email2/3}

\maketitle

\begin{abstract}
This is the text of the abstract.
\end{abstract}

\category{CR-number}{subcategory}{third-level}

% general terms are not compulsory anymore, 
% you may leave them out
\terms
term1, term2

\keywords
keyword1, keyword2

\section{Introduction}

%% Word vommit
\begin{itemize}
	\item Network configuration is hard ...
	\item Configs are local and distributed
	\item Difficult to express intent directly
	\item Often achieve intent through indirect means (i.e., backups through aggregation)
	\item Distributed, asynchronous, environment unknown, failures ... means difficult to consider all scenarios	
	\item Problems are compounded in inter-domain routing where other factors like peering agreements are important
	\item Wide variety of considerations: Have preferences for certain routes over others, failure resistance, backups etc
	\item On the other hand, BGP is the only widely used, policy-rich routing language
	\item Often used for intra-domain routing as well
	\item We present a new language that allows operators to directly express intent for inter and intra-domain routing policies 
		  from a centralized point of view.
	\item The language provides the operator with the abstraction that they can control all end-to-end routes that transit their 
		  network, even if the routes start and/or end outside of their network.
	\item The language consists of regular expression constraints on the set of allowed routes along with a flexible preference operator
		  that allows ranking sets of paths to enable both inter-domain routing preferences and intra-domain backup paths.
	\item A compiler takes a routing policy written in this language and synthesizes concrete, per-device configurations running BGP. 
	\item The resulting configurations are guaranteed to correctly implement the policy using the standard, distributed path vector protocol, 
		  and remain correct under all possible network failure scenarios.
	\item To enable a wider spectrum of implementable policies, we model common environment assumptions (e.g., semantics of BGP community values)
		  As sets of allowed/disallowed paths provided by a neighbor using the same regular path framework.
	\item Although we choose to target BGP for both inter and intra domain routing due to its expressiveness, our language is agnostic to any particular 
		  routing protocol. It describes only routes and their relative preferences. As such, an alternative routing protocol, such as OSPF, could 
		  be used internally. This would change the set of implementable policies.
	\item To allow for more fine-grained control over control-plane details, our language permits additional constraints on the control protocol
		  (e.g., maximum number of allowed routes, whether to use multipath etc)
	\item Advantages: Centralized configuration (no copy paste error, more concise), Synthesis (no need for gory details, e.g., community values),
		  Expressiveness (backup routing, preferences, waypointing, directly say things like no transit), 
		  Correctness: (Guaranteed to implement the policy, even under failure scenarios),
		  Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
\end{itemize}

\section{Overview}

\begin{itemize}
	\item Introduce language with examples...
	\item Maybe, start with a typical AS, and show how simple it would be to implement a typical policy
	\item Another good example, would be something that combined internal backup routing with preference based 
		  entrance into the network using aggregation.
	\item Could probably show an example of the resulting config, and how it is tagging using communities, 
		  or alternatively show that it doesn't compile due to a particular failure scenario.
\end{itemize}

\section{Language}

\subsection{Syntax}
Define the grammar of the language.
Need to distinguish whether the preference operator 
appears only at the top level or not.

\subsection{Semantics} 
Give the semantics in terms of ranked paths.
Should be straightforward extension of regular expression semantics with the 
additional constraint that we take only valid topology paths and that their are no paths with 
repeated locations in the path. If preferences appear only at the top level, then it is easy to rank the paths.
One tricky point is that we care about paths starting or ending at locations that are connected to end-hosts in some way.
And we want the length of the path to be a secondary tie-breaker .
Additional assumption here should be that the prefixes are disjoint.

\subsection{Theory}
What are the properties of this language? Ideally, a proof here about its expressiveness. We can perhaps do everything 
BGP can do? We can't do shortest paths routing with BGP, but we could with OSPF though? Clearly we can only describe 
policies that are stable under all possible failure scenarios (at least internally stable, could still cause) routing 
loops with interactions with neighbors.

\section{Compilation}

\begin{itemize}
	\item Separate prefixes so they are disjoint (assumption) for semantics)
		  probably using BDDs where each bit is a variable is the easiest way to do this.
	\item For each prefix, build a DFA from each of the regular path constraints 
		  We do this using character classes and regular expression derivatives.
		  The accepting states are labeled with the particular preference.
	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or 
		  more of the regular path constraints. We accept if we are in at least one of the accepting states 
		  for one or more of the DFAs. We take the max of the preferences for the accepting preference.
		  Add a new start and end node as well.
	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution. 
		  This is sound. Removing these makes it easier to check if things are implementable using BGP (see next point).
		  There are two ways to do this: a sound heuristic for removing edges and nodes, and a complete, but slow method for 
		  removing everything not needed.
	\item Since our policy language is richer than BGP, we need to check if it is implementable with BGP.
		  First show some examples of what the problem is: why BGP cannot make a decision.
		  We check: preference consistency (doesn't regret a choice based on which preference accepting state it might reach)
		  and topology consistency (no failure scenario will result in an advertisement reaching a router from a more preferred neighbor 
		  but then not get to an accepting state, when another, less preferred route was available).
	\item We can check for topology consistency using a sufficient condition (that works often and is very fast), 
		  and by enumerating failure scenarios using a necessary and sufficient condition (that always works but is slooooow)

	\item Finally, if we know BGP can make decision locally, then we can directly translate to local BGP configurations using 
		  information about the state machines from the neighbors. In particular, we tag (and test on) community values for the
		  corresponding state and set preferences accordingly (example will be needed)
	\item Running example will be helpful here.	
\end{itemize}

\section{Evaluation}

\begin{itemize}
	\item Expressiveness of the policy language (maybe a proof earlier for this)
	\item Compactness of the policy language (how verbose? likely pretty concise)
	\item Intuitiveness of the policy language (how easy is it to understand? probably make the earlier examples clear)
	\item Speed of compilation (does it take forever?)
	\item Understandability of the resulting configurations (Can humans understand them?)
	\item Some measure of the size of the resulting configurations (is this actually an issue in BGP??)
\end{itemize}

\section{Related Work}

\begin{itemize}
	\item Regular path queries
	\item Lots of background on BGP
	\item Feamster rcc stuff
	\item Logic programming BGP configs
\end{itemize}

\section{Conclusions}

TODO

\appendix
\section{Appendix Title}

This is the text of the appendix, if you need one.

\acks

Acknowledgments, if needed.

% We recommend abbrvnat bibliography style.

\bibliographystyle{abbrvnat}

% The bibliography should be embedded for final submission.

\begin{thebibliography}{}
\softraggedright

\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
P. Q. Smith, and X. Y. Jones. ...reference text...

\end{thebibliography}

\end{document}

%                       Revision History
%                       -------- -------
%  Date         Person  Ver.    Change
%  ----         ------  ----    ------

%  2013.06.29   TU      0.1--4  comments on permission/copyright notices

### 2015-11-12 paper/sigplanconf-template.tex
Adding front-end parser

@@
 		  Add a new start and end node as well.
+
 	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution. 
@@
 		  removing everything not needed.
-	\item Since our policy language is richer than BGP, we need to check if it is implementable with BGP.
+
+	\item Since our policy language can express things not implementable in BGP, we need a few checks.
 		  First show some examples of what the problem is: why BGP cannot make a decision. 
-		  We check: preference consistency (doesn't regret a choice based on which preference accepting state it might reach)
-		  and topology consistency (no failure scenario will result in an advertisement reaching a router from a more preferred neighbor 
-		  but then not get to an accepting state, when another, less preferred route was available).
+		  The reasons this can happen are: 
+		  (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
+		  (2) Failures - Have to make a decision without knowing what failures have occurred. Must be the case that
+
 	\item We can check for topology consistency using a sufficient condition (that works often and is very fast), 
@@
 	\item Running example will be helpful here.	
+\end{itemize}
+
+\subsection{Optimizations}
+
+\begin{itemize}
+	\item Compress communities by reusing communities across routers.
+	      That is, we can reuse the same community value since we know who the next hop is 
+	      (e.g., if there are 4 Y nodes, then use communities 0-4 for Y)
+
+	\item If we have the same match across all starting locations, then match only on community.
+		  If we have the same match across all communities (per peer) for a location, then omit checking 
+		  the community (similarly avoid tagging the community from the other point of view)
+		  These mainly just make things much easier to read for a human (more natural policy).
 \end{itemize}

### 2015-12-19 paper/paper.tex
Added macro expansion combinators to the policy language.

--- 2015-11-12 paper/sigplanconf-template.tex
@@
 
-\documentclass{sigplanconf}
+\documentclass{paper}
 
@@
 \begin{abstract}
-This is the text of the abstract.
+TODO
 \end{abstract}
@@
 %% Word vommit
+Why network configuration is hard:
 \begin{itemize}
-	\item Network configuration is hard ...
-	\item Configs are local and distributed
-	\item Difficult to express intent directly
-	\item Often achieve intent through indirect means (i.e., backups through aggregation)
-	\item Distributed, asynchronous, environment unknown, failures ... means difficult to consider all scenarios	
-	\item Problems are compounded in inter-domain routing where other factors like peering agreements are important
 	\item Wide variety of considerations: Have preferences for certain routes over others, failure resistance, backups etc
-	\item On the other hand, BGP is the only widely used, policy-rich routing language
-	\item Often used for intra-domain routing as well
-	\item We present a new language that allows operators to directly express intent for inter and intra-domain routing policies 
-		  from a centralized point of view.
-	\item The language provides the operator with the abstraction that they can control all end-to-end routes that transit their 
-		  network, even if the routes start and/or end outside of their network.
-	\item The language consists of regular expression constraints on the set of allowed routes along with a flexible preference operator
-		  that allows ranking sets of paths to enable both inter-domain routing preferences and intra-domain backup paths.
-	\item A compiler takes a routing policy written in this language and synthesizes concrete, per-device configurations running BGP. 
-	\item The resulting configurations are guaranteed to correctly implement the policy using the standard, distributed path vector protocol, 
-		  and remain correct under all possible network failure scenarios.
-	\item To enable a wider spectrum of implementable policies, we model common environment assumptions (e.g., semantics of BGP community values)
-		  As sets of allowed/disallowed paths provided by a neighbor using the same regular path framework.
-	\item Although we choose to target BGP for both inter and intra domain routing due to its expressiveness, our language is agnostic to any particular 
-		  routing protocol. It describes only routes and their relative preferences. As such, an alternative routing protocol, such as OSPF, could 
-		  be used internally. This would change the set of implementable policies.
-	\item To allow for more fine-grained control over control-plane details, our language permits additional constraints on the control protocol
-		  (e.g., maximum number of allowed routes, whether to use multipath etc)
-	\item Advantages: Centralized configuration (no copy paste error, more concise), Synthesis (no need for gory details, e.g., community values),
-		  Expressiveness (backup routing, preferences, waypointing, directly say things like no transit), 
-		  Correctness: (Guaranteed to implement the policy, even under failure scenarios),
-		  Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
+	\item Configurations are implemented locally and in a distributed fashion even though network intent is global
+	\item Often achieve intent through indirect means (i.e., backups through aggregation, preferences through MED, AS PATH length, local-pref values, filtering through communities)
+	\item Networks are distributed, asynchronous systems where the environment can be unknown, failures can occur ... which makes it difficult to consider all scenarios
+	\item Problems are compounded in inter-domain setting where factors like peering agreements and bad peer behavior need to be taken into account.
+	\item Protocol-specific issues such as lack of convergence in BGP
 \end{itemize}
+
+We present a new language that allows operators to directly express and compile high-level routing policies (both inter and intra-domain) from a centralized point of view.
+
+The language provides the operator with the abstraction that they can control the routes that all traffic through their network can take, even if the routes start and/or end in a different autonomous system.
+
+The core language consists of regular expression constraints on the set of allowed routes along with a preference operator between routes, which is used to specify both routing preferences and backup paths.
+On top of the core language, we provide a higher-level macro language to talk only about constraints on routes without specifying any particular route details.
+
+A compiler takes a routing policy written in our language and synthesizes concrete, per-device configurations running BGP.
+Although the language is independent of any particular routing protocol, we target BGP due to its expressiveness, scalability, and use for both inter-domain and intra-domain routing.
+The compiler either guarantees that the resulting configurations correctly implement the policy and remain correct under all possible network failure scenarios, or it returns a counterexample.
+(Similar to SDN, you get centralized control, yet a distributed implementation that uses an existing, scalable, fault-tolerant protocol.)
+
+To allow for more fine-grained control over control-plane details, our language permits additional constraints on control protocol details (e.g., maximum number of allowed routes, whether to use multipath etc).
+
+Summary: 
+	 (1) Centralized: (simpler reasoning, no copy paste error, more concise), 
+	 (2) Synthesis: (no need for gory details, e.g., community values, local-pref, MED, ...),
+	 (3) Expressive: (backup routing, preferences, waypointing, directly say things like no transit or cold-potato routing), 
+	 (4) Correct: (implement the policy, even under all failure scenarios)
 
@@
 
+Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention). 
+Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
+
 \begin{itemize}
-	\item Introduce language with examples...
-	\item Maybe, start with a typical AS, and show how simple it would be to implement a typical policy
-	\item Another good example, would be something that combined internal backup routing with preference based 
-		  entrance into the network using aggregation.
-	\item Could probably show an example of the resulting config, and how it is tagging using communities, 
-		  or alternatively show that it doesn't compile due to a particular failure scenario.
+	\item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
+	\item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
+	\item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
+	\item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
+	\item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
+\end{itemize}
+
+Possible Examples:
+\begin{itemize}
+	\item Basic datacenter with spine preference
+	\item Simple AS that prefers customers over peers over providers
+	\item Combined internal backup routing with preference based entrance into the network using aggregation.
+	\item Something like cold potato routing
 \end{itemize}
@@
 \subsection{Syntax}
-Define the grammar of the language.
-Need to distinguish whether the preference operator 
-appears only at the top level or not.
+Define the grammar of each of the languages - regular language, the macro language on top of it, and maybe the IR language.
 
@@
 Give the semantics in terms of ranked paths.
-Should be straightforward extension of regular expression semantics with the 
+Extension of regular expression semantics with the 
 additional constraint that we take only valid topology paths and that their are no paths with 
-repeated locations in the path. If preferences appear only at the top level, then it is easy to rank the paths.
-One tricky point is that we care about paths starting or ending at locations that are connected to end-hosts in some way.
-And we want the length of the path to be a secondary tie-breaker .
-Additional assumption here should be that the prefixes are disjoint.
+repeated locations in the path. One tricky point is that we care about paths starting or ending at locations that are 
+connected to end-hosts in some way. And we want the length of the path to be a secondary tie-breaker.
 
@@
 \begin{itemize}
-	\item Separate prefixes so they are disjoint (assumption) for semantics)
-		  probably using BDDs where each bit is a variable is the easiest way to do this.
+	\item Separate prefixes so they are disjoint
+
 	\item For each prefix, build a DFA from each of the regular path constraints 
@@
 		  The accepting states are labeled with the particular preference.
+
 	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or 
 		  more of the regular path constraints. We accept if we are in at least one of the accepting states 
-		  for one or more of the DFAs. We take the max of the preferences for the accepting preference.
-		  Add a new start and end node as well.
+		  for one or more of the DFAs. Add a new start and end node as well.
 
 	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution. 
-		  This is sound. Removing these makes it easier to check if things are implementable using BGP (see next point).
-		  There are two ways to do this: a sound heuristic for removing edges and nodes, and a complete, but slow method for 
-		  removing everything not needed.
+		  Required for soundness. Removing these makes it easier to check if things are implementable using BGP (see next point).
+		  We use several heuristics to make this faster (e.g., removing edges for dominated nodes)
 
@@
 		  (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
-		  (2) Failures - Have to make a decision without knowing what failures have occurred. Must be the case that
+		  (2) Failures - Have to make a decision without knowing what failures have occurred. Never want to prefer one peer over another and then not get a path when one was available
 
-	\item We can check for topology consistency using a sufficient condition (that works often and is very fast), 
-		  and by enumerating failure scenarios using a necessary and sufficient condition (that always works but is slooooow)
+	\item We can check for these with a sufficient condition (that works often and is very fast),
+
+	\item For each router, build a preference pre-order, that defines the constraints between preferences.
 
@@
 		  corresponding state and set preferences accordingly (example will be needed)
+
 	\item Running example will be helpful here.	
@@
 \begin{itemize}
-	\item Compress communities by reusing communities across routers.
-	      That is, we can reuse the same community value since we know who the next hop is 
-	      (e.g., if there are 4 Y nodes, then use communities 0-4 for Y)
-
-	\item If we have the same match across all starting locations, then match only on community.
-		  If we have the same match across all communities (per peer) for a location, then omit checking 
-		  the community (similarly avoid tagging the community from the other point of view)
-		  These mainly just make things much easier to read for a human (more natural policy).
+	\item For performance, the main bottleneck will probably be the minimization step. We use a number of heuristics here to make this faster.
+	\item For config readability and number of route maps/communities, we avoid community tagging/matching whenever possible with a number of tricks.
 \end{itemize}
@@
 
+\begin{enumerate}
+	\item Expressiveness of the policy language / BGP safe part of the language (maybe a proof earlier for this)
+	\item Compactness of the policy language (how verbose/concise, maybe in loc)
+	\item Intuitiveness of the policy language (how easy is it to understand? Not really a good way to evaluate this other than demonstrate earlier by example)
+	\item Speed of compilation (does it take forever? what are the bottlenecks)
+	\item Understandability of the resulting configurations (Can humans understand them?)
+	\item Some measure of the size of the resulting configurations (e.g., the number of route maps. Is this actually ever an issue in BGP?)
+\end{enumerate}
+
+\section{Future Work}
+
 \begin{itemize}
-	\item Expressiveness of the policy language (maybe a proof earlier for this)
-	\item Compactness of the policy language (how verbose? likely pretty concise)
-	\item Intuitiveness of the policy language (how easy is it to understand? probably make the earlier examples clear)
-	\item Speed of compilation (does it take forever?)
-	\item Understandability of the resulting configurations (Can humans understand them?)
-	\item Some measure of the size of the resulting configurations (is this actually an issue in BGP??)
+	\item Environments: Model environments using the same framework. (e.g., no-export allows certain paths that weren't before
+	\item Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
+	\item OSPF: language isn't inherently tied to BGP, and could use iBGP with OSPF or some other protocol. This would require different kinds of checks though.
 \end{itemize}

### 2016-01-08 paper/paper.tex
added motivation

@@
 	 (4) Correct: (implement the policy, even under all failure scenarios)
+
+\section{Motivation}
+\label{sec:motivation}
+
+We motivate our work by describing the current practice in network configuration and its shortcomings.
+In traditional networks with distributed control planes, the operators’ goal is to generate the configuration of individual devices.
+Based on its configuration, the device exchanges information with other (e.g., links costs or best known paths) devices, filters and ranks incoming information, and decides how to forward packets to various destinations.
+
+Device configuration languages are low-level and indirect.
+For instance, instead of allowing operators to express directly the paths they want through the network, they require operators to specify link costs that result in those paths; instead of allowing operators to express directly the types of traffic to not carry through the network, they require operators to select and program an appropriate filtering mechanism (e.g., route maps, null routing,  access control lists) and instantiate it on topologically appropriate devices; instead of allowing operators to directly specify that they prefer to send traffic via customer, peer, and provider networks, in that order, they require operators to program BGP local preferences at each router and ensure that the preferences are consistent across routers.
+
+In many networks today, device configurations are generated manually by operators, without the support of many automated tools.
+It is easy to see the problems with this approach, for instance, typos, inconsistency across devices, and no guarantees of policy compliance.
+
+To reduce such problems, some networks use a template-based approach.
+Configuration templates abstract certain constants into variables (e.g., instead of concrete interface IP address, they may contain a variable \$$Router1\_Interface1\_IP$) and may be device-vendor-neutral in their syntax.
+Operators manually generate the templates, and then use tools to translate them into device configuration, by replacing variables with appropriate constants using a database of network information and replacing vendor-neutral constructs with their vendor-specific counterparts.
+
+%In practice, most networks use a hybrid of templates and manual generation of device configuration.
+Templates are used for standardized and common configuration elements across devices and the result is manually tweaked to obtain the exact desired network behavior.
+
+Template-based configuration helps avoid some of the pitfalls of the fully manual approach, it is still far from ideal.
+The fundamental issue is the semantic mismatch between desirable policies and the level of abstraction that templates offer.
+While desirable policies are network-wide (e.g., prefer customer networks or link $A$ server as backup for link $B$), templates are specified at the level of individual devices (e.g., BGP local preferences or link costs to use).
+Operators must still manually decompose network-wide policies into device-level policies that can produce the desired network-wide behavior.
+
+This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures. FOR EXAMPLE:
 

### 2016-01-08 paper/paper.tex
added motivation

@@
 
-Template-based configuration helps avoid some of the pitfalls of the fully manual approach, it is still far from ideal.
+While template-based configuration avoids some of the pitfalls of the fully manual approach, it is still far from ideal.
 The fundamental issue is the semantic mismatch between desirable policies and the level of abstraction that templates offer.
-While desirable policies are network-wide (e.g., prefer customer networks or link $A$ server as backup for link $B$), templates are specified at the level of individual devices (e.g., BGP local preferences or link costs to use).
+While desirable policies are network-wide (e.g., prefer customer networks, or link $A$ should serve as backup for link $B$), templates are device-level (e.g., BGP local preferences or link costs to use).
 Operators must still manually decompose network-wide policies into device-level policies that can produce the desired network-wide behavior.

### 2016-01-14 paper/compilation.tex
splitting the paper across files

--- 2015-12-19 paper/paper.tex
@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-%
-% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
-%               sigplanconf-guide.pdf
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
-
-\documentclass{paper}
-
-% The following \documentclass options may be useful:
-
-% preprint      Remove this option only once the paper is in final form.
-% 10pt          To set in 10-point type instead of 9-point.
-% 11pt          To set in 11-point type instead of 9-point.
-% authoryear    To obtain author/year citation style instead of numeric.
-
-\usepackage{amsmath}
-
-\begin{document}
-
-\special{papersize=8.5in,11in}
-\setlength{\pdfpageheight}{\paperheight}
-\setlength{\pdfpagewidth}{\paperwidth}
-
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
-\copyrightyear{20yy} 
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
-\doi{nnnnnnn.nnnnnnn}
-
-% Uncomment one of the following two, if you are not going for the 
-% traditional copyright transfer agreement.
-
-%\exclusivelicense                % ACM gets exclusive license to publish, 
-                                  % you retain copyright
-
-%\permissiontopublish             % ACM gets nonexclusive license to publish
-                                  % (paid open-access papers, 
-                                  % short abstracts)
-
-\titlebanner{banner above paper title}        % These are ignored unless
-\preprintfooter{short description of paper}   % 'preprint' option specified.
-
-\title{Title Text}
-\subtitle{Subtitle Text, if any}
-
-\authorinfo{Name1}
-           {Affiliation1}
-           {Email1}
-\authorinfo{Name2\and Name3}
-           {Affiliation2/3}
-           {Email2/3}
-
-\maketitle
-
-\begin{abstract}
-TODO
-\end{abstract}
-
-\category{CR-number}{subcategory}{third-level}
-
-% general terms are not compulsory anymore, 
-% you may leave them out
-\terms
-term1, term2
-
-\keywords
-keyword1, keyword2
-
-\section{Introduction}
-
-%% Word vommit
-Why network configuration is hard:
-\begin{itemize}
-	\item Wide variety of considerations: Have preferences for certain routes over others, failure resistance, backups etc
-	\item Configurations are implemented locally and in a distributed fashion even though network intent is global
-	\item Often achieve intent through indirect means (i.e., backups through aggregation, preferences through MED, AS PATH length, local-pref values, filtering through communities)
-	\item Networks are distributed, asynchronous systems where the environment can be unknown, failures can occur ... which makes it difficult to consider all scenarios
-	\item Problems are compounded in inter-domain setting where factors like peering agreements and bad peer behavior need to be taken into account.
-	\item Protocol-specific issues such as lack of convergence in BGP
-\end{itemize}
-
-We present a new language that allows operators to directly express and compile high-level routing policies (both inter and intra-domain) from a centralized point of view.
-
-The language provides the operator with the abstraction that they can control the routes that all traffic through their network can take, even if the routes start and/or end in a different autonomous system.
-
-The core language consists of regular expression constraints on the set of allowed routes along with a preference operator between routes, which is used to specify both routing preferences and backup paths.
-On top of the core language, we provide a higher-level macro language to talk only about constraints on routes without specifying any particular route details.
-
-A compiler takes a routing policy written in our language and synthesizes concrete, per-device configurations running BGP.
-Although the language is independent of any particular routing protocol, we target BGP due to its expressiveness, scalability, and use for both inter-domain and intra-domain routing.
-The compiler either guarantees that the resulting configurations correctly implement the policy and remain correct under all possible network failure scenarios, or it returns a counterexample.
-(Similar to SDN, you get centralized control, yet a distributed implementation that uses an existing, scalable, fault-tolerant protocol.)
-
-To allow for more fine-grained control over control-plane details, our language permits additional constraints on control protocol details (e.g., maximum number of allowed routes, whether to use multipath etc).
-
-Summary: 
-	 (1) Centralized: (simpler reasoning, no copy paste error, more concise), 
-	 (2) Synthesis: (no need for gory details, e.g., community values, local-pref, MED, ...),
-	 (3) Expressive: (backup routing, preferences, waypointing, directly say things like no transit or cold-potato routing), 
-	 (4) Correct: (implement the policy, even under all failure scenarios)
-
-\section{Overview}
-
-Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention). 
-Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
-
-\begin{itemize}
-	\item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
-	\item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
-	\item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
-	\item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
-	\item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
-\end{itemize}
-
-Possible Examples:
-\begin{itemize}
-	\item Basic datacenter with spine preference
-	\item Simple AS that prefers customers over peers over providers
-	\item Combined internal backup routing with preference based entrance into the network using aggregation.
-	\item Something like cold potato routing
-\end{itemize}
-
-\section{Language}
-
-\subsection{Syntax}
-Define the grammar of each of the languages - regular language, the macro language on top of it, and maybe the IR language.
-
-\subsection{Semantics} 
-Give the semantics in terms of ranked paths.
-Extension of regular expression semantics with the 
-additional constraint that we take only valid topology paths and that their are no paths with 
-repeated locations in the path. One tricky point is that we care about paths starting or ending at locations that are 
-connected to end-hosts in some way. And we want the length of the path to be a secondary tie-breaker.
-
-\subsection{Theory}
-What are the properties of this language? Ideally, a proof here about its expressiveness. We can perhaps do everything 
-BGP can do? We can't do shortest paths routing with BGP, but we could with OSPF though? Clearly we can only describe 
-policies that are stable under all possible failure scenarios (at least internally stable, could still cause) routing 
-loops with interactions with neighbors.
-
 \section{Compilation}
+\label{sec:compilation}
 
@@
 \end{itemize}
-
-\section{Evaluation}
-
-\begin{enumerate}
-	\item Expressiveness of the policy language / BGP safe part of the language (maybe a proof earlier for this)
-	\item Compactness of the policy language (how verbose/concise, maybe in loc)
-	\item Intuitiveness of the policy language (how easy is it to understand? Not really a good way to evaluate this other than demonstrate earlier by example)
-	\item Speed of compilation (does it take forever? what are the bottlenecks)
-	\item Understandability of the resulting configurations (Can humans understand them?)
-	\item Some measure of the size of the resulting configurations (e.g., the number of route maps. Is this actually ever an issue in BGP?)
-\end{enumerate}
-
-\section{Future Work}
-
-\begin{itemize}
-	\item Environments: Model environments using the same framework. (e.g., no-export allows certain paths that weren't before
-	\item Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
-	\item OSPF: language isn't inherently tied to BGP, and could use iBGP with OSPF or some other protocol. This would require different kinds of checks though.
-\end{itemize}
-
-\section{Related Work}
-
-\begin{itemize}
-	\item Regular path queries
-	\item Lots of background on BGP
-	\item Feamster rcc stuff
-	\item Logic programming BGP configs
-\end{itemize}
-
-\section{Conclusions}
-
-TODO
-
-\appendix
-\section{Appendix Title}
-
-This is the text of the appendix, if you need one.
-
-\acks
-
-Acknowledgments, if needed.
-
-% We recommend abbrvnat bibliography style.
-
-\bibliographystyle{abbrvnat}
-
-% The bibliography should be embedded for final submission.
-
-\begin{thebibliography}{}
-\softraggedright
-
-\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
-P. Q. Smith, and X. Y. Jones. ...reference text...
-
-\end{thebibliography}
-
-\end{document}
-
-%                       Revision History
-%                       -------- -------
-%  Date         Person  Ver.    Change
-%  ----         ------  ----    ------
-
-%  2013.06.29   TU      0.1--4  comments on permission/copyright notices

### 2016-01-14 paper/conclusions.tex
splitting the paper across files

--- 2015-12-19 paper/paper.tex
@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-%
-% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
-%               sigplanconf-guide.pdf
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
-
-\documentclass{paper}
-
-% The following \documentclass options may be useful:
-
-% preprint      Remove this option only once the paper is in final form.
-% 10pt          To set in 10-point type instead of 9-point.
-% 11pt          To set in 11-point type instead of 9-point.
-% authoryear    To obtain author/year citation style instead of numeric.
-
-\usepackage{amsmath}
-
-\begin{document}
-
-\special{papersize=8.5in,11in}
-\setlength{\pdfpageheight}{\paperheight}
-\setlength{\pdfpagewidth}{\paperwidth}
-
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
-\copyrightyear{20yy} 
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
-\doi{nnnnnnn.nnnnnnn}
-
-% Uncomment one of the following two, if you are not going for the 
-% traditional copyright transfer agreement.
-
-%\exclusivelicense                % ACM gets exclusive license to publish, 
-                                  % you retain copyright
-
-%\permissiontopublish             % ACM gets nonexclusive license to publish
-                                  % (paid open-access papers, 
-                                  % short abstracts)
-
-\titlebanner{banner above paper title}        % These are ignored unless
-\preprintfooter{short description of paper}   % 'preprint' option specified.
-
-\title{Title Text}
-\subtitle{Subtitle Text, if any}
-
-\authorinfo{Name1}
-           {Affiliation1}
-           {Email1}
-\authorinfo{Name2\and Name3}
-           {Affiliation2/3}
-           {Email2/3}
-
-\maketitle
-
-\begin{abstract}
-TODO
-\end{abstract}
-
-\category{CR-number}{subcategory}{third-level}
-
-% general terms are not compulsory anymore, 
-% you may leave them out
-\terms
-term1, term2
-
-\keywords
-keyword1, keyword2
-
-\section{Introduction}
-
-%% Word vommit
-Why network configuration is hard:
-\begin{itemize}
-	\item Wide variety of considerations: Have preferences for certain routes over others, failure resistance, backups etc
-	\item Configurations are implemented locally and in a distributed fashion even though network intent is global
-	\item Often achieve intent through indirect means (i.e., backups through aggregation, preferences through MED, AS PATH length, local-pref values, filtering through communities)
-	\item Networks are distributed, asynchronous systems where the environment can be unknown, failures can occur ... which makes it difficult to consider all scenarios
-	\item Problems are compounded in inter-domain setting where factors like peering agreements and bad peer behavior need to be taken into account.
-	\item Protocol-specific issues such as lack of convergence in BGP
-\end{itemize}
-
-We present a new language that allows operators to directly express and compile high-level routing policies (both inter and intra-domain) from a centralized point of view.
-
-The language provides the operator with the abstraction that they can control the routes that all traffic through their network can take, even if the routes start and/or end in a different autonomous system.
-
-The core language consists of regular expression constraints on the set of allowed routes along with a preference operator between routes, which is used to specify both routing preferences and backup paths.
-On top of the core language, we provide a higher-level macro language to talk only about constraints on routes without specifying any particular route details.
-
-A compiler takes a routing policy written in our language and synthesizes concrete, per-device configurations running BGP.
-Although the language is independent of any particular routing protocol, we target BGP due to its expressiveness, scalability, and use for both inter-domain and intra-domain routing.
-The compiler either guarantees that the resulting configurations correctly implement the policy and remain correct under all possible network failure scenarios, or it returns a counterexample.
-(Similar to SDN, you get centralized control, yet a distributed implementation that uses an existing, scalable, fault-tolerant protocol.)
-
-To allow for more fine-grained control over control-plane details, our language permits additional constraints on control protocol details (e.g., maximum number of allowed routes, whether to use multipath etc).
-
-Summary: 
-	 (1) Centralized: (simpler reasoning, no copy paste error, more concise), 
-	 (2) Synthesis: (no need for gory details, e.g., community values, local-pref, MED, ...),
-	 (3) Expressive: (backup routing, preferences, waypointing, directly say things like no transit or cold-potato routing), 
-	 (4) Correct: (implement the policy, even under all failure scenarios)
-
-\section{Overview}
-
-Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention). 
-Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
-
-\begin{itemize}
-	\item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
-	\item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
-	\item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
-	\item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
-	\item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
-\end{itemize}
-
-Possible Examples:
-\begin{itemize}
-	\item Basic datacenter with spine preference
-	\item Simple AS that prefers customers over peers over providers
-	\item Combined internal backup routing with preference based entrance into the network using aggregation.
-	\item Something like cold potato routing
-\end{itemize}
-
-\section{Language}
-
-\subsection{Syntax}
-Define the grammar of each of the languages - regular language, the macro language on top of it, and maybe the IR language.
-
-\subsection{Semantics} 
-Give the semantics in terms of ranked paths.
-Extension of regular expression semantics with the 
-additional constraint that we take only valid topology paths and that their are no paths with 
-repeated locations in the path. One tricky point is that we care about paths starting or ending at locations that are 
-connected to end-hosts in some way. And we want the length of the path to be a secondary tie-breaker.
-
-\subsection{Theory}
-What are the properties of this language? Ideally, a proof here about its expressiveness. We can perhaps do everything 
-BGP can do? We can't do shortest paths routing with BGP, but we could with OSPF though? Clearly we can only describe 
-policies that are stable under all possible failure scenarios (at least internally stable, could still cause) routing 
-loops with interactions with neighbors.
-
-\section{Compilation}
-
-\begin{itemize}
-	\item Separate prefixes so they are disjoint
-
-	\item For each prefix, build a DFA from each of the regular path constraints 
-		  We do this using character classes and regular expression derivatives.
-		  The accepting states are labeled with the particular preference.
-
-	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or 
-		  more of the regular path constraints. We accept if we are in at least one of the accepting states 
-		  for one or more of the DFAs. Add a new start and end node as well.
-
-	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution. 
-		  Required for soundness. Removing these makes it easier to check if things are implementable using BGP (see next point).
-		  We use several heuristics to make this faster (e.g., removing edges for dominated nodes)
-
-	\item Since our policy language can express things not implementable in BGP, we need a few checks.
-		  First show some examples of what the problem is: why BGP cannot make a decision. 
-		  The reasons this can happen are: 
-		  (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
-		  (2) Failures - Have to make a decision without knowing what failures have occurred. Never want to prefer one peer over another and then not get a path when one was available
-
-	\item We can check for these with a sufficient condition (that works often and is very fast),
-
-	\item For each router, build a preference pre-order, that defines the constraints between preferences.
-
-	\item Finally, if we know BGP can make decision locally, then we can directly translate to local BGP configurations using 
-		  information about the state machines from the neighbors. In particular, we tag (and test on) community values for the
-		  corresponding state and set preferences accordingly (example will be needed)
-
-	\item Running example will be helpful here.	
-\end{itemize}
-
-\subsection{Optimizations}
-
-\begin{itemize}
-	\item For performance, the main bottleneck will probably be the minimization step. We use a number of heuristics here to make this faster.
-	\item For config readability and number of route maps/communities, we avoid community tagging/matching whenever possible with a number of tricks.
-\end{itemize}
-
-\section{Evaluation}
-
-\begin{enumerate}
-	\item Expressiveness of the policy language / BGP safe part of the language (maybe a proof earlier for this)
-	\item Compactness of the policy language (how verbose/concise, maybe in loc)
-	\item Intuitiveness of the policy language (how easy is it to understand? Not really a good way to evaluate this other than demonstrate earlier by example)
-	\item Speed of compilation (does it take forever? what are the bottlenecks)
-	\item Understandability of the resulting configurations (Can humans understand them?)
-	\item Some measure of the size of the resulting configurations (e.g., the number of route maps. Is this actually ever an issue in BGP?)
-\end{enumerate}
-
-\section{Future Work}
-
-\begin{itemize}
-	\item Environments: Model environments using the same framework. (e.g., no-export allows certain paths that weren't before
-	\item Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
-	\item OSPF: language isn't inherently tied to BGP, and could use iBGP with OSPF or some other protocol. This would require different kinds of checks though.
-\end{itemize}
-
-\section{Related Work}
-
-\begin{itemize}
-	\item Regular path queries
-	\item Lots of background on BGP
-	\item Feamster rcc stuff
-	\item Logic programming BGP configs
-\end{itemize}
-
 \section{Conclusions}
+\label{sec:conclusions}
 
 TODO
-
-\appendix
-\section{Appendix Title}
-
-This is the text of the appendix, if you need one.
-
-\acks
-
-Acknowledgments, if needed.
-
-% We recommend abbrvnat bibliography style.
-
-\bibliographystyle{abbrvnat}
-
-% The bibliography should be embedded for final submission.
-
-\begin{thebibliography}{}
-\softraggedright
-
-\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
-P. Q. Smith, and X. Y. Jones. ...reference text...
-
-\end{thebibliography}
-
-\end{document}
-
-%                       Revision History
-%                       -------- -------
-%  Date         Person  Ver.    Change
-%  ----         ------  ----    ------
-
-%  2013.06.29   TU      0.1--4  comments on permission/copyright notices

### 2016-01-14 paper/evaluation.tex
splitting the paper across files

--- 2015-12-19 paper/paper.tex
@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-%
-% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
-%               sigplanconf-guide.pdf
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
-
-\documentclass{paper}
-
-% The following \documentclass options may be useful:
-
-% preprint      Remove this option only once the paper is in final form.
-% 10pt          To set in 10-point type instead of 9-point.
-% 11pt          To set in 11-point type instead of 9-point.
-% authoryear    To obtain author/year citation style instead of numeric.
-
-\usepackage{amsmath}
-
-\begin{document}
-
-\special{papersize=8.5in,11in}
-\setlength{\pdfpageheight}{\paperheight}
-\setlength{\pdfpagewidth}{\paperwidth}
-
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
-\copyrightyear{20yy} 
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
-\doi{nnnnnnn.nnnnnnn}
-
-% Uncomment one of the following two, if you are not going for the 
-% traditional copyright transfer agreement.
-
-%\exclusivelicense                % ACM gets exclusive license to publish, 
-                                  % you retain copyright
-
-%\permissiontopublish             % ACM gets nonexclusive license to publish
-                                  % (paid open-access papers, 
-                                  % short abstracts)
-
-\titlebanner{banner above paper title}        % These are ignored unless
-\preprintfooter{short description of paper}   % 'preprint' option specified.
-
-\title{Title Text}
-\subtitle{Subtitle Text, if any}
-
-\authorinfo{Name1}
-           {Affiliation1}
-           {Email1}
-\authorinfo{Name2\and Name3}
-           {Affiliation2/3}
-           {Email2/3}
-
-\maketitle
-
-\begin{abstract}
-TODO
-\end{abstract}
-
-\category{CR-number}{subcategory}{third-level}
-
-% general terms are not compulsory anymore, 
-% you may leave them out
-\terms
-term1, term2
-
-\keywords
-keyword1, keyword2
-
-\section{Introduction}
-
-%% Word vommit
-Why network configuration is hard:
-\begin{itemize}
-	\item Wide variety of considerations: Have preferences for certain routes over others, failure resistance, backups etc
-	\item Configurations are implemented locally and in a distributed fashion even though network intent is global
-	\item Often achieve intent through indirect means (i.e., backups through aggregation, preferences through MED, AS PATH length, local-pref values, filtering through communities)
-	\item Networks are distributed, asynchronous systems where the environment can be unknown, failures can occur ... which makes it difficult to consider all scenarios
-	\item Problems are compounded in inter-domain setting where factors like peering agreements and bad peer behavior need to be taken into account.
-	\item Protocol-specific issues such as lack of convergence in BGP
-\end{itemize}
-
-We present a new language that allows operators to directly express and compile high-level routing policies (both inter and intra-domain) from a centralized point of view.
-
-The language provides the operator with the abstraction that they can control the routes that all traffic through their network can take, even if the routes start and/or end in a different autonomous system.
-
-The core language consists of regular expression constraints on the set of allowed routes along with a preference operator between routes, which is used to specify both routing preferences and backup paths.
-On top of the core language, we provide a higher-level macro language to talk only about constraints on routes without specifying any particular route details.
-
-A compiler takes a routing policy written in our language and synthesizes concrete, per-device configurations running BGP.
-Although the language is independent of any particular routing protocol, we target BGP due to its expressiveness, scalability, and use for both inter-domain and intra-domain routing.
-The compiler either guarantees that the resulting configurations correctly implement the policy and remain correct under all possible network failure scenarios, or it returns a counterexample.
-(Similar to SDN, you get centralized control, yet a distributed implementation that uses an existing, scalable, fault-tolerant protocol.)
-
-To allow for more fine-grained control over control-plane details, our language permits additional constraints on control protocol details (e.g., maximum number of allowed routes, whether to use multipath etc).
-
-Summary: 
-	 (1) Centralized: (simpler reasoning, no copy paste error, more concise), 
-	 (2) Synthesis: (no need for gory details, e.g., community values, local-pref, MED, ...),
-	 (3) Expressive: (backup routing, preferences, waypointing, directly say things like no transit or cold-potato routing), 
-	 (4) Correct: (implement the policy, even under all failure scenarios)
-
-\section{Overview}
-
-Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention). 
-Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
-
-\begin{itemize}
-	\item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
-	\item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
-	\item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
-	\item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
-	\item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
-\end{itemize}
-
-Possible Examples:
-\begin{itemize}
-	\item Basic datacenter with spine preference
-	\item Simple AS that prefers customers over peers over providers
-	\item Combined internal backup routing with preference based entrance into the network using aggregation.
-	\item Something like cold potato routing
-\end{itemize}
-
-\section{Language}
-
-\subsection{Syntax}
-Define the grammar of each of the languages - regular language, the macro language on top of it, and maybe the IR language.
-
-\subsection{Semantics} 
-Give the semantics in terms of ranked paths.
-Extension of regular expression semantics with the 
-additional constraint that we take only valid topology paths and that their are no paths with 
-repeated locations in the path. One tricky point is that we care about paths starting or ending at locations that are 
-connected to end-hosts in some way. And we want the length of the path to be a secondary tie-breaker.
-
-\subsection{Theory}
-What are the properties of this language? Ideally, a proof here about its expressiveness. We can perhaps do everything 
-BGP can do? We can't do shortest paths routing with BGP, but we could with OSPF though? Clearly we can only describe 
-policies that are stable under all possible failure scenarios (at least internally stable, could still cause) routing 
-loops with interactions with neighbors.
-
-\section{Compilation}
-
-\begin{itemize}
-	\item Separate prefixes so they are disjoint
-
-	\item For each prefix, build a DFA from each of the regular path constraints 
-		  We do this using character classes and regular expression derivatives.
-		  The accepting states are labeled with the particular preference.
-
-	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or 
-		  more of the regular path constraints. We accept if we are in at least one of the accepting states 
-		  for one or more of the DFAs. Add a new start and end node as well.
-
-	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution. 
-		  Required for soundness. Removing these makes it easier to check if things are implementable using BGP (see next point).
-		  We use several heuristics to make this faster (e.g., removing edges for dominated nodes)
-
-	\item Since our policy language can express things not implementable in BGP, we need a few checks.
-		  First show some examples of what the problem is: why BGP cannot make a decision. 
-		  The reasons this can happen are: 
-		  (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
-		  (2) Failures - Have to make a decision without knowing what failures have occurred. Never want to prefer one peer over another and then not get a path when one was available
-
-	\item We can check for these with a sufficient condition (that works often and is very fast),
-
-	\item For each router, build a preference pre-order, that defines the constraints between preferences.
-
-	\item Finally, if we know BGP can make decision locally, then we can directly translate to local BGP configurations using 
-		  information about the state machines from the neighbors. In particular, we tag (and test on) community values for the
-		  corresponding state and set preferences accordingly (example will be needed)
-
-	\item Running example will be helpful here.	
-\end{itemize}
-
-\subsection{Optimizations}
-
-\begin{itemize}
-	\item For performance, the main bottleneck will probably be the minimization step. We use a number of heuristics here to make this faster.
-	\item For config readability and number of route maps/communities, we avoid community tagging/matching whenever possible with a number of tricks.
-\end{itemize}
-
 \section{Evaluation}
@@
 \end{enumerate}
-
-\section{Future Work}
-
-\begin{itemize}
-	\item Environments: Model environments using the same framework. (e.g., no-export allows certain paths that weren't before
-	\item Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
-	\item OSPF: language isn't inherently tied to BGP, and could use iBGP with OSPF or some other protocol. This would require different kinds of checks though.
-\end{itemize}
-
-\section{Related Work}
-
-\begin{itemize}
-	\item Regular path queries
-	\item Lots of background on BGP
-	\item Feamster rcc stuff
-	\item Logic programming BGP configs
-\end{itemize}
-
-\section{Conclusions}
-
-TODO
-
-\appendix
-\section{Appendix Title}
-
-This is the text of the appendix, if you need one.
-
-\acks
-
-Acknowledgments, if needed.
-
-% We recommend abbrvnat bibliography style.
-
-\bibliographystyle{abbrvnat}
-
-% The bibliography should be embedded for final submission.
-
-\begin{thebibliography}{}
-\softraggedright
-
-\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
-P. Q. Smith, and X. Y. Jones. ...reference text...
-
-\end{thebibliography}
-
-\end{document}
-
-%                       Revision History
-%                       -------- -------
-%  Date         Person  Ver.    Change
-%  ----         ------  ----    ------
-
-%  2013.06.29   TU      0.1--4  comments on permission/copyright notices

### 2016-01-14 paper/introduction.tex
splitting the paper across files

--- 2015-12-19 paper/paper.tex
@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-%
-% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
-%               sigplanconf-guide.pdf
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
-
-\documentclass{paper}
-
-% The following \documentclass options may be useful:
-
-% preprint      Remove this option only once the paper is in final form.
-% 10pt          To set in 10-point type instead of 9-point.
-% 11pt          To set in 11-point type instead of 9-point.
-% authoryear    To obtain author/year citation style instead of numeric.
-
-\usepackage{amsmath}
-
-\begin{document}
-
-\special{papersize=8.5in,11in}
-\setlength{\pdfpageheight}{\paperheight}
-\setlength{\pdfpagewidth}{\paperwidth}
-
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
-\copyrightyear{20yy} 
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
-\doi{nnnnnnn.nnnnnnn}
-
-% Uncomment one of the following two, if you are not going for the 
-% traditional copyright transfer agreement.
-
-%\exclusivelicense                % ACM gets exclusive license to publish, 
-                                  % you retain copyright
-
-%\permissiontopublish             % ACM gets nonexclusive license to publish
-                                  % (paid open-access papers, 
-                                  % short abstracts)
-
-\titlebanner{banner above paper title}        % These are ignored unless
-\preprintfooter{short description of paper}   % 'preprint' option specified.
-
-\title{Title Text}
-\subtitle{Subtitle Text, if any}
-
-\authorinfo{Name1}
-           {Affiliation1}
-           {Email1}
-\authorinfo{Name2\and Name3}
-           {Affiliation2/3}
-           {Email2/3}
-
-\maketitle
-
-\begin{abstract}
-TODO
-\end{abstract}
-
-\category{CR-number}{subcategory}{third-level}
-
-% general terms are not compulsory anymore, 
-% you may leave them out
-\terms
-term1, term2
-
-\keywords
-keyword1, keyword2
-
 \section{Introduction}
+\label{sec:introduction}
 
@@
 	 (4) Correct: (implement the policy, even under all failure scenarios)
-
-\section{Overview}
-
-Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention). 
-Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
-
-\begin{itemize}
-	\item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
-	\item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
-	\item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
-	\item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
-	\item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
-\end{itemize}
-
-Possible Examples:
-\begin{itemize}
-	\item Basic datacenter with spine preference
-	\item Simple AS that prefers customers over peers over providers
-	\item Combined internal backup routing with preference based entrance into the network using aggregation.
-	\item Something like cold potato routing
-\end{itemize}
-
-\section{Language}
-
-\subsection{Syntax}
-Define the grammar of each of the languages - regular language, the macro language on top of it, and maybe the IR language.
-
-\subsection{Semantics} 
-Give the semantics in terms of ranked paths.
-Extension of regular expression semantics with the 
-additional constraint that we take only valid topology paths and that their are no paths with 
-repeated locations in the path. One tricky point is that we care about paths starting or ending at locations that are 
-connected to end-hosts in some way. And we want the length of the path to be a secondary tie-breaker.
-
-\subsection{Theory}
-What are the properties of this language? Ideally, a proof here about its expressiveness. We can perhaps do everything 
-BGP can do? We can't do shortest paths routing with BGP, but we could with OSPF though? Clearly we can only describe 
-policies that are stable under all possible failure scenarios (at least internally stable, could still cause) routing 
-loops with interactions with neighbors.
-
-\section{Compilation}
-
-\begin{itemize}
-	\item Separate prefixes so they are disjoint
-
-	\item For each prefix, build a DFA from each of the regular path constraints 
-		  We do this using character classes and regular expression derivatives.
-		  The accepting states are labeled with the particular preference.
-
-	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or 
-		  more of the regular path constraints. We accept if we are in at least one of the accepting states 
-		  for one or more of the DFAs. Add a new start and end node as well.
-
-	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution. 
-		  Required for soundness. Removing these makes it easier to check if things are implementable using BGP (see next point).
-		  We use several heuristics to make this faster (e.g., removing edges for dominated nodes)
-
-	\item Since our policy language can express things not implementable in BGP, we need a few checks.
-		  First show some examples of what the problem is: why BGP cannot make a decision. 
-		  The reasons this can happen are: 
-		  (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
-		  (2) Failures - Have to make a decision without knowing what failures have occurred. Never want to prefer one peer over another and then not get a path when one was available
-
-	\item We can check for these with a sufficient condition (that works often and is very fast),
-
-	\item For each router, build a preference pre-order, that defines the constraints between preferences.
-
-	\item Finally, if we know BGP can make decision locally, then we can directly translate to local BGP configurations using 
-		  information about the state machines from the neighbors. In particular, we tag (and test on) community values for the
-		  corresponding state and set preferences accordingly (example will be needed)
-
-	\item Running example will be helpful here.	
-\end{itemize}
-
-\subsection{Optimizations}
-
-\begin{itemize}
-	\item For performance, the main bottleneck will probably be the minimization step. We use a number of heuristics here to make this faster.
-	\item For config readability and number of route maps/communities, we avoid community tagging/matching whenever possible with a number of tricks.
-\end{itemize}
-
-\section{Evaluation}
-
-\begin{enumerate}
-	\item Expressiveness of the policy language / BGP safe part of the language (maybe a proof earlier for this)
-	\item Compactness of the policy language (how verbose/concise, maybe in loc)
-	\item Intuitiveness of the policy language (how easy is it to understand? Not really a good way to evaluate this other than demonstrate earlier by example)
-	\item Speed of compilation (does it take forever? what are the bottlenecks)
-	\item Understandability of the resulting configurations (Can humans understand them?)
-	\item Some measure of the size of the resulting configurations (e.g., the number of route maps. Is this actually ever an issue in BGP?)
-\end{enumerate}
-
-\section{Future Work}
-
-\begin{itemize}
-	\item Environments: Model environments using the same framework. (e.g., no-export allows certain paths that weren't before
-	\item Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
-	\item OSPF: language isn't inherently tied to BGP, and could use iBGP with OSPF or some other protocol. This would require different kinds of checks though.
-\end{itemize}
-
-\section{Related Work}
-
-\begin{itemize}
-	\item Regular path queries
-	\item Lots of background on BGP
-	\item Feamster rcc stuff
-	\item Logic programming BGP configs
-\end{itemize}
-
-\section{Conclusions}
-
-TODO
-
-\appendix
-\section{Appendix Title}
-
-This is the text of the appendix, if you need one.
-
-\acks
-
-Acknowledgments, if needed.
-
-% We recommend abbrvnat bibliography style.
-
-\bibliographystyle{abbrvnat}
-
-% The bibliography should be embedded for final submission.
-
-\begin{thebibliography}{}
-\softraggedright
-
-\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
-P. Q. Smith, and X. Y. Jones. ...reference text...
-
-\end{thebibliography}
-
-\end{document}
-
-%                       Revision History
-%                       -------- -------
-%  Date         Person  Ver.    Change
-%  ----         ------  ----    ------
-
-%  2013.06.29   TU      0.1--4  comments on permission/copyright notices

### 2016-01-14 paper/language.tex
splitting the paper across files

--- 2015-12-19 paper/paper.tex
@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-%
-% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
-%               sigplanconf-guide.pdf
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
-
-\documentclass{paper}
-
-% The following \documentclass options may be useful:
-
-% preprint      Remove this option only once the paper is in final form.
-% 10pt          To set in 10-point type instead of 9-point.
-% 11pt          To set in 11-point type instead of 9-point.
-% authoryear    To obtain author/year citation style instead of numeric.
-
-\usepackage{amsmath}
-
-\begin{document}
-
-\special{papersize=8.5in,11in}
-\setlength{\pdfpageheight}{\paperheight}
-\setlength{\pdfpagewidth}{\paperwidth}
-
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
-\copyrightyear{20yy} 
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
-\doi{nnnnnnn.nnnnnnn}
-
-% Uncomment one of the following two, if you are not going for the 
-% traditional copyright transfer agreement.
-
-%\exclusivelicense                % ACM gets exclusive license to publish, 
-                                  % you retain copyright
-
-%\permissiontopublish             % ACM gets nonexclusive license to publish
-                                  % (paid open-access papers, 
-                                  % short abstracts)
-
-\titlebanner{banner above paper title}        % These are ignored unless
-\preprintfooter{short description of paper}   % 'preprint' option specified.
-
-\title{Title Text}
-\subtitle{Subtitle Text, if any}
-
-\authorinfo{Name1}
-           {Affiliation1}
-           {Email1}
-\authorinfo{Name2\and Name3}
-           {Affiliation2/3}
-           {Email2/3}
-
-\maketitle
-
-\begin{abstract}
-TODO
-\end{abstract}
-
-\category{CR-number}{subcategory}{third-level}
-
-% general terms are not compulsory anymore, 
-% you may leave them out
-\terms
-term1, term2
-
-\keywords
-keyword1, keyword2
-
-\section{Introduction}
-
-%% Word vommit
-Why network configuration is hard:
-\begin{itemize}
-	\item Wide variety of considerations: Have preferences for certain routes over others, failure resistance, backups etc
-	\item Configurations are implemented locally and in a distributed fashion even though network intent is global
-	\item Often achieve intent through indirect means (i.e., backups through aggregation, preferences through MED, AS PATH length, local-pref values, filtering through communities)
-	\item Networks are distributed, asynchronous systems where the environment can be unknown, failures can occur ... which makes it difficult to consider all scenarios
-	\item Problems are compounded in inter-domain setting where factors like peering agreements and bad peer behavior need to be taken into account.
-	\item Protocol-specific issues such as lack of convergence in BGP
-\end{itemize}
-
-We present a new language that allows operators to directly express and compile high-level routing policies (both inter and intra-domain) from a centralized point of view.
-
-The language provides the operator with the abstraction that they can control the routes that all traffic through their network can take, even if the routes start and/or end in a different autonomous system.
-
-The core language consists of regular expression constraints on the set of allowed routes along with a preference operator between routes, which is used to specify both routing preferences and backup paths.
-On top of the core language, we provide a higher-level macro language to talk only about constraints on routes without specifying any particular route details.
-
-A compiler takes a routing policy written in our language and synthesizes concrete, per-device configurations running BGP.
-Although the language is independent of any particular routing protocol, we target BGP due to its expressiveness, scalability, and use for both inter-domain and intra-domain routing.
-The compiler either guarantees that the resulting configurations correctly implement the policy and remain correct under all possible network failure scenarios, or it returns a counterexample.
-(Similar to SDN, you get centralized control, yet a distributed implementation that uses an existing, scalable, fault-tolerant protocol.)
-
-To allow for more fine-grained control over control-plane details, our language permits additional constraints on control protocol details (e.g., maximum number of allowed routes, whether to use multipath etc).
-
-Summary: 
-	 (1) Centralized: (simpler reasoning, no copy paste error, more concise), 
-	 (2) Synthesis: (no need for gory details, e.g., community values, local-pref, MED, ...),
-	 (3) Expressive: (backup routing, preferences, waypointing, directly say things like no transit or cold-potato routing), 
-	 (4) Correct: (implement the policy, even under all failure scenarios)
-
-\section{Overview}
-
-Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention). 
-Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
-
-\begin{itemize}
-	\item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
-	\item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
-	\item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
-	\item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
-	\item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
-\end{itemize}
-
-Possible Examples:
-\begin{itemize}
-	\item Basic datacenter with spine preference
-	\item Simple AS that prefers customers over peers over providers
-	\item Combined internal backup routing with preference based entrance into the network using aggregation.
-	\item Something like cold potato routing
-\end{itemize}
-
 \section{Language}
+\label{sec:language}
 
@@
 loops with interactions with neighbors.
-
-\section{Compilation}
-
-\begin{itemize}
-	\item Separate prefixes so they are disjoint
-
-	\item For each prefix, build a DFA from each of the regular path constraints 
-		  We do this using character classes and regular expression derivatives.
-		  The accepting states are labeled with the particular preference.
-
-	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or 
-		  more of the regular path constraints. We accept if we are in at least one of the accepting states 
-		  for one or more of the DFAs. Add a new start and end node as well.
-
-	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution. 
-		  Required for soundness. Removing these makes it easier to check if things are implementable using BGP (see next point).
-		  We use several heuristics to make this faster (e.g., removing edges for dominated nodes)
-
-	\item Since our policy language can express things not implementable in BGP, we need a few checks.
-		  First show some examples of what the problem is: why BGP cannot make a decision. 
-		  The reasons this can happen are: 
-		  (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
-		  (2) Failures - Have to make a decision without knowing what failures have occurred. Never want to prefer one peer over another and then not get a path when one was available
-
-	\item We can check for these with a sufficient condition (that works often and is very fast),
-
-	\item For each router, build a preference pre-order, that defines the constraints between preferences.
-
-	\item Finally, if we know BGP can make decision locally, then we can directly translate to local BGP configurations using 
-		  information about the state machines from the neighbors. In particular, we tag (and test on) community values for the
-		  corresponding state and set preferences accordingly (example will be needed)
-
-	\item Running example will be helpful here.	
-\end{itemize}
-
-\subsection{Optimizations}
-
-\begin{itemize}
-	\item For performance, the main bottleneck will probably be the minimization step. We use a number of heuristics here to make this faster.
-	\item For config readability and number of route maps/communities, we avoid community tagging/matching whenever possible with a number of tricks.
-\end{itemize}
-
-\section{Evaluation}
-
-\begin{enumerate}
-	\item Expressiveness of the policy language / BGP safe part of the language (maybe a proof earlier for this)
-	\item Compactness of the policy language (how verbose/concise, maybe in loc)
-	\item Intuitiveness of the policy language (how easy is it to understand? Not really a good way to evaluate this other than demonstrate earlier by example)
-	\item Speed of compilation (does it take forever? what are the bottlenecks)
-	\item Understandability of the resulting configurations (Can humans understand them?)
-	\item Some measure of the size of the resulting configurations (e.g., the number of route maps. Is this actually ever an issue in BGP?)
-\end{enumerate}
-
-\section{Future Work}
-
-\begin{itemize}
-	\item Environments: Model environments using the same framework. (e.g., no-export allows certain paths that weren't before
-	\item Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
-	\item OSPF: language isn't inherently tied to BGP, and could use iBGP with OSPF or some other protocol. This would require different kinds of checks though.
-\end{itemize}
-
-\section{Related Work}
-
-\begin{itemize}
-	\item Regular path queries
-	\item Lots of background on BGP
-	\item Feamster rcc stuff
-	\item Logic programming BGP configs
-\end{itemize}
-
-\section{Conclusions}
-
-TODO
-
-\appendix
-\section{Appendix Title}
-
-This is the text of the appendix, if you need one.
-
-\acks
-
-Acknowledgments, if needed.
-
-% We recommend abbrvnat bibliography style.
-
-\bibliographystyle{abbrvnat}
-
-% The bibliography should be embedded for final submission.
-
-\begin{thebibliography}{}
-\softraggedright
-
-\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
-P. Q. Smith, and X. Y. Jones. ...reference text...
-
-\end{thebibliography}
-
-\end{document}
-
-%                       Revision History
-%                       -------- -------
-%  Date         Person  Ver.    Change
-%  ----         ------  ----    ------
-
-%  2013.06.29   TU      0.1--4  comments on permission/copyright notices

### 2016-01-14 paper/motivation.tex
splitting the paper across files

--- 2016-01-08 paper/paper.tex
@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-%
-% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
-%               sigplanconf-guide.pdf
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
-
-\documentclass{paper}
-
-% The following \documentclass options may be useful:
-
-% preprint      Remove this option only once the paper is in final form.
-% 10pt          To set in 10-point type instead of 9-point.
-% 11pt          To set in 11-point type instead of 9-point.
-% authoryear    To obtain author/year citation style instead of numeric.
-
-\usepackage{amsmath}
-
-\begin{document}
-
-\special{papersize=8.5in,11in}
-\setlength{\pdfpageheight}{\paperheight}
-\setlength{\pdfpagewidth}{\paperwidth}
-
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country}
-\copyrightyear{20yy}
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
-\doi{nnnnnnn.nnnnnnn}
-
-% Uncomment one of the following two, if you are not going for the
-% traditional copyright transfer agreement.
-
-%\exclusivelicense                % ACM gets exclusive license to publish,
-                                  % you retain copyright
-
-%\permissiontopublish             % ACM gets nonexclusive license to publish
-                                  % (paid open-access papers,
-                                  % short abstracts)
-
-\titlebanner{banner above paper title}        % These are ignored unless
-\preprintfooter{short description of paper}   % 'preprint' option specified.
-
-\title{Title Text}
-\subtitle{Subtitle Text, if any}
-
-\authorinfo{Name1}
-           {Affiliation1}
-           {Email1}
-\authorinfo{Name2\and Name3}
-           {Affiliation2/3}
-           {Email2/3}
-
-\maketitle
-
-\begin{abstract}
-TODO
-\end{abstract}
-
-\category{CR-number}{subcategory}{third-level}
-
-% general terms are not compulsory anymore,
-% you may leave them out
-\terms
-term1, term2
-
-\keywords
-keyword1, keyword2
-
-\section{Introduction}
-
-%% Word vommit
-Why network configuration is hard:
-\begin{itemize}
-	\item Wide variety of considerations: Have preferences for certain routes over others, failure resistance, backups etc
-	\item Configurations are implemented locally and in a distributed fashion even though network intent is global
-	\item Often achieve intent through indirect means (i.e., backups through aggregation, preferences through MED, AS PATH length, local-pref values, filtering through communities)
-	\item Networks are distributed, asynchronous systems where the environment can be unknown, failures can occur ... which makes it difficult to consider all scenarios
-	\item Problems are compounded in inter-domain setting where factors like peering agreements and bad peer behavior need to be taken into account.
-	\item Protocol-specific issues such as lack of convergence in BGP
-\end{itemize}
-
-We present a new language that allows operators to directly express and compile high-level routing policies (both inter and intra-domain) from a centralized point of view.
-
-The language provides the operator with the abstraction that they can control the routes that all traffic through their network can take, even if the routes start and/or end in a different autonomous system.
-
-The core language consists of regular expression constraints on the set of allowed routes along with a preference operator between routes, which is used to specify both routing preferences and backup paths.
-On top of the core language, we provide a higher-level macro language to talk only about constraints on routes without specifying any particular route details.
-
-A compiler takes a routing policy written in our language and synthesizes concrete, per-device configurations running BGP.
-Although the language is independent of any particular routing protocol, we target BGP due to its expressiveness, scalability, and use for both inter-domain and intra-domain routing.
-The compiler either guarantees that the resulting configurations correctly implement the policy and remain correct under all possible network failure scenarios, or it returns a counterexample.
-(Similar to SDN, you get centralized control, yet a distributed implementation that uses an existing, scalable, fault-tolerant protocol.)
-
-To allow for more fine-grained control over control-plane details, our language permits additional constraints on control protocol details (e.g., maximum number of allowed routes, whether to use multipath etc).
-
-Summary:
-	 (1) Centralized: (simpler reasoning, no copy paste error, more concise),
-	 (2) Synthesis: (no need for gory details, e.g., community values, local-pref, MED, ...),
-	 (3) Expressive: (backup routing, preferences, waypointing, directly say things like no transit or cold-potato routing),
-	 (4) Correct: (implement the policy, even under all failure scenarios)
-
 \section{Motivation}
@@
 In many networks today, device configurations are generated manually by operators, without the support of many automated tools.
-It is easy to see the problems with this approach, for instance, typos, inconsistency across devices, and no guarantees of policy compliance.
+It is easy to see the problems with this approach, such as typos, inconsistency across devices, and no guarantees of policy compliance.
 
 To reduce such problems, some networks use a template-based approach.
-Configuration templates abstract certain constants into variables (e.g., instead of concrete interface IP address, they may contain a variable \$$Router1\_Interface1\_IP$) and may be device-vendor-neutral in their syntax.
-Operators manually generate the templates, and then use tools to translate them into device configuration, by replacing variables with appropriate constants using a database of network information and replacing vendor-neutral constructs with their vendor-specific counterparts.
+Configuration templates abstract certain constants into variables (e.g., instead of concrete interface IP address, they may contain a variable {\small \sf{\$$Rtr1\_Int1\_IP$)}} and may use a device vendor-neutral syntax.
+Operators manually generate the templates, and then use tools to translate them into device configuration, by replacing variables with appropriate constants using a database of network information.
+
+ %and replacing vendor-neutral constructs with their vendor-specific counterparts.
 
@@
 
-While template-based configuration avoids some of the pitfalls of the fully manual approach, it is still far from ideal.
+While templates avoids some pitfalls of the fully manual approach, they too are far from ideal.
 The fundamental issue is the semantic mismatch between desirable policies and the level of abstraction that templates offer.
@@
 
-This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures. FOR EXAMPLE:
+This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures.
+We illustrate this point using two examples, based on policies that we have seen in practice.
 
-\section{Overview}
+\subsection{OLD -- Overview}
+\todo{this subsection can be deleted once we have captured everything in it}
 
@@
 \end{itemize}
-
-\section{Language}
-
-\subsection{Syntax}
-Define the grammar of each of the languages - regular language, the macro language on top of it, and maybe the IR language.
-
-\subsection{Semantics}
-Give the semantics in terms of ranked paths.
-Extension of regular expression semantics with the
-additional constraint that we take only valid topology paths and that their are no paths with
-repeated locations in the path. One tricky point is that we care about paths starting or ending at locations that are
-connected to end-hosts in some way. And we want the length of the path to be a secondary tie-breaker.
-
-\subsection{Theory}
-What are the properties of this language? Ideally, a proof here about its expressiveness. We can perhaps do everything
-BGP can do? We can't do shortest paths routing with BGP, but we could with OSPF though? Clearly we can only describe
-policies that are stable under all possible failure scenarios (at least internally stable, could still cause) routing
-loops with interactions with neighbors.
-
-\section{Compilation}
-
-\begin{itemize}
-	\item Separate prefixes so they are disjoint
-
-	\item For each prefix, build a DFA from each of the regular path constraints
-		  We do this using character classes and regular expression derivatives.
-		  The accepting states are labeled with the particular preference.
-
-	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or
-		  more of the regular path constraints. We accept if we are in at least one of the accepting states
-		  for one or more of the DFAs. Add a new start and end node as well.
-
-	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution.
-		  Required for soundness. Removing these makes it easier to check if things are implementable using BGP (see next point).
-		  We use several heuristics to make this faster (e.g., removing edges for dominated nodes)
-
-	\item Since our policy language can express things not implementable in BGP, we need a few checks.
-		  First show some examples of what the problem is: why BGP cannot make a decision.
-		  The reasons this can happen are:
-		  (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
-		  (2) Failures - Have to make a decision without knowing what failures have occurred. Never want to prefer one peer over another and then not get a path when one was available
-
-	\item We can check for these with a sufficient condition (that works often and is very fast),
-
-	\item For each router, build a preference pre-order, that defines the constraints between preferences.
-
-	\item Finally, if we know BGP can make decision locally, then we can directly translate to local BGP configurations using
-		  information about the state machines from the neighbors. In particular, we tag (and test on) community values for the
-		  corresponding state and set preferences accordingly (example will be needed)
-
-	\item Running example will be helpful here.	
-\end{itemize}
-
-\subsection{Optimizations}
-
-\begin{itemize}
-	\item For performance, the main bottleneck will probably be the minimization step. We use a number of heuristics here to make this faster.
-	\item For config readability and number of route maps/communities, we avoid community tagging/matching whenever possible with a number of tricks.
-\end{itemize}
-
-\section{Evaluation}
-
-\begin{enumerate}
-	\item Expressiveness of the policy language / BGP safe part of the language (maybe a proof earlier for this)
-	\item Compactness of the policy language (how verbose/concise, maybe in loc)
-	\item Intuitiveness of the policy language (how easy is it to understand? Not really a good way to evaluate this other than demonstrate earlier by example)
-	\item Speed of compilation (does it take forever? what are the bottlenecks)
-	\item Understandability of the resulting configurations (Can humans understand them?)
-	\item Some measure of the size of the resulting configurations (e.g., the number of route maps. Is this actually ever an issue in BGP?)
-\end{enumerate}
-
-\section{Future Work}
-
-\begin{itemize}
-	\item Environments: Model environments using the same framework. (e.g., no-export allows certain paths that weren't before
-	\item Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
-	\item OSPF: language isn't inherently tied to BGP, and could use iBGP with OSPF or some other protocol. This would require different kinds of checks though.
-\end{itemize}
-
-\section{Related Work}
-
-\begin{itemize}
-	\item Regular path queries
-	\item Lots of background on BGP
-	\item Feamster rcc stuff
-	\item Logic programming BGP configs
-\end{itemize}
-
-\section{Conclusions}
-
-TODO
-
-\appendix
-\section{Appendix Title}
-
-This is the text of the appendix, if you need one.
-
-\acks
-
-Acknowledgments, if needed.
-
-% We recommend abbrvnat bibliography style.
-
-\bibliographystyle{abbrvnat}
-
-% The bibliography should be embedded for final submission.
-
-\begin{thebibliography}{}
-\softraggedright
-
-\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
-P. Q. Smith, and X. Y. Jones. ...reference text...
-
-\end{thebibliography}
-
-\end{document}
-
-%                       Revision History
-%                       -------- -------
-%  Date         Person  Ver.    Change
-%  ----         ------  ----    ------
-
-%  2013.06.29   TU      0.1--4  comments on permission/copyright notices

### 2016-01-14 paper/paper.tex
splitting the paper across files

--- 2015-12-19 paper/paper.tex
@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-%
-% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
-%               sigplanconf-guide.pdf
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
-
-\documentclass{paper}
-
-% The following \documentclass options may be useful:
-
-% preprint      Remove this option only once the paper is in final form.
-% 10pt          To set in 10-point type instead of 9-point.
-% 11pt          To set in 11-point type instead of 9-point.
-% authoryear    To obtain author/year citation style instead of numeric.
+\documentclass{sig-alternate-10pt}
 
 \usepackage{amsmath}
+\usepackage{xcolor}
+\usepackage{times}
+
+%\definecolor{red}{rgb}{0.8,0,0}
+%\definecolor{green}{rgb}{0,0.33,0}
+%\definecolor{blue}{rgb}{0.8,0,0}
+
+\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
+\newcommand{\ratul}[1]{\textcolor{blue}{[ratul: #1]}}
+\newcommand{\ryan}[1]{\textcolor{green}{[ryan: #1]}}
 
@@
 
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
-\copyrightyear{20yy} 
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
-\doi{nnnnnnn.nnnnnnn}
-
-% Uncomment one of the following two, if you are not going for the 
-% traditional copyright transfer agreement.
-
-%\exclusivelicense                % ACM gets exclusive license to publish, 
-                                  % you retain copyright
-
-%\permissiontopublish             % ACM gets nonexclusive license to publish
-                                  % (paid open-access papers, 
-                                  % short abstracts)
-
-\titlebanner{banner above paper title}        % These are ignored unless
-\preprintfooter{short description of paper}   % 'preprint' option specified.
-
-\title{Title Text}
-\subtitle{Subtitle Text, if any}
-
-\authorinfo{Name1}
-           {Affiliation1}
-           {Email1}
-\authorinfo{Name2\and Name3}
-           {Affiliation2/3}
-           {Email2/3}
+\title{Programming Distributed Control Planes}
+\author{Paper \#XXX}
 
@@
 
-\begin{abstract}
-TODO
-\end{abstract}
+%\category{CR-number}{subcategory}{third-level}
+%% general terms are not compulsory anymore,
+%% you may leave them out
+%\terms
+%term1, term2
+%\keywords
+%keyword1, keyword2
 
-\category{CR-number}{subcategory}{third-level}
+\input{introduction}
+\input{motivation}
+\input{language}
+\input{compilation}
+\input{evaluation}
+\input{discussion}
+\input{related}
+\input{conclusions}
 
-% general terms are not compulsory anymore, 
-% you may leave them out
-\terms
-term1, term2
-
-\keywords
-keyword1, keyword2
-
-\section{Introduction}
-
-%% Word vommit
-Why network configuration is hard:
-\begin{itemize}
-	\item Wide variety of considerations: Have preferences for certain routes over others, failure resistance, backups etc
-	\item Configurations are implemented locally and in a distributed fashion even though network intent is global
-	\item Often achieve intent through indirect means (i.e., backups through aggregation, preferences through MED, AS PATH length, local-pref values, filtering through communities)
-	\item Networks are distributed, asynchronous systems where the environment can be unknown, failures can occur ... which makes it difficult to consider all scenarios
-	\item Problems are compounded in inter-domain setting where factors like peering agreements and bad peer behavior need to be taken into account.
-	\item Protocol-specific issues such as lack of convergence in BGP
-\end{itemize}
-
-We present a new language that allows operators to directly express and compile high-level routing policies (both inter and intra-domain) from a centralized point of view.
-
-The language provides the operator with the abstraction that they can control the routes that all traffic through their network can take, even if the routes start and/or end in a different autonomous system.
-
-The core language consists of regular expression constraints on the set of allowed routes along with a preference operator between routes, which is used to specify both routing preferences and backup paths.
-On top of the core language, we provide a higher-level macro language to talk only about constraints on routes without specifying any particular route details.
-
-A compiler takes a routing policy written in our language and synthesizes concrete, per-device configurations running BGP.
-Although the language is independent of any particular routing protocol, we target BGP due to its expressiveness, scalability, and use for both inter-domain and intra-domain routing.
-The compiler either guarantees that the resulting configurations correctly implement the policy and remain correct under all possible network failure scenarios, or it returns a counterexample.
-(Similar to SDN, you get centralized control, yet a distributed implementation that uses an existing, scalable, fault-tolerant protocol.)
-
-To allow for more fine-grained control over control-plane details, our language permits additional constraints on control protocol details (e.g., maximum number of allowed routes, whether to use multipath etc).
-
-Summary: 
-	 (1) Centralized: (simpler reasoning, no copy paste error, more concise), 
-	 (2) Synthesis: (no need for gory details, e.g., community values, local-pref, MED, ...),
-	 (3) Expressive: (backup routing, preferences, waypointing, directly say things like no transit or cold-potato routing), 
-	 (4) Correct: (implement the policy, even under all failure scenarios)
-
-\section{Overview}
-
-Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention). 
-Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
-
-\begin{itemize}
-	\item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
-	\item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
-	\item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
-	\item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
-	\item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
-\end{itemize}
-
-Possible Examples:
-\begin{itemize}
-	\item Basic datacenter with spine preference
-	\item Simple AS that prefers customers over peers over providers
-	\item Combined internal backup routing with preference based entrance into the network using aggregation.
-	\item Something like cold potato routing
-\end{itemize}
-
-\section{Language}
-
-\subsection{Syntax}
-Define the grammar of each of the languages - regular language, the macro language on top of it, and maybe the IR language.
-
-\subsection{Semantics} 
-Give the semantics in terms of ranked paths.
-Extension of regular expression semantics with the 
-additional constraint that we take only valid topology paths and that their are no paths with 
-repeated locations in the path. One tricky point is that we care about paths starting or ending at locations that are 
-connected to end-hosts in some way. And we want the length of the path to be a secondary tie-breaker.
-
-\subsection{Theory}
-What are the properties of this language? Ideally, a proof here about its expressiveness. We can perhaps do everything 
-BGP can do? We can't do shortest paths routing with BGP, but we could with OSPF though? Clearly we can only describe 
-policies that are stable under all possible failure scenarios (at least internally stable, could still cause) routing 
-loops with interactions with neighbors.
-
-\section{Compilation}
-
-\begin{itemize}
-	\item Separate prefixes so they are disjoint
-
-	\item For each prefix, build a DFA from each of the regular path constraints 
-		  We do this using character classes and regular expression derivatives.
-		  The accepting states are labeled with the particular preference.
-
-	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or 
-		  more of the regular path constraints. We accept if we are in at least one of the accepting states 
-		  for one or more of the DFAs. Add a new start and end node as well.
-
-	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution. 
-		  Required for soundness. Removing these makes it easier to check if things are implementable using BGP (see next point).
-		  We use several heuristics to make this faster (e.g., removing edges for dominated nodes)
-
-	\item Since our policy language can express things not implementable in BGP, we need a few checks.
-		  First show some examples of what the problem is: why BGP cannot make a decision. 
-		  The reasons this can happen are: 
-		  (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
-		  (2) Failures - Have to make a decision without knowing what failures have occurred. Never want to prefer one peer over another and then not get a path when one was available
-
-	\item We can check for these with a sufficient condition (that works often and is very fast),
-
-	\item For each router, build a preference pre-order, that defines the constraints between preferences.
-
-	\item Finally, if we know BGP can make decision locally, then we can directly translate to local BGP configurations using 
-		  information about the state machines from the neighbors. In particular, we tag (and test on) community values for the
-		  corresponding state and set preferences accordingly (example will be needed)
-
-	\item Running example will be helpful here.	
-\end{itemize}
-
-\subsection{Optimizations}
-
-\begin{itemize}
-	\item For performance, the main bottleneck will probably be the minimization step. We use a number of heuristics here to make this faster.
-	\item For config readability and number of route maps/communities, we avoid community tagging/matching whenever possible with a number of tricks.
-\end{itemize}
-
-\section{Evaluation}
-
-\begin{enumerate}
-	\item Expressiveness of the policy language / BGP safe part of the language (maybe a proof earlier for this)
-	\item Compactness of the policy language (how verbose/concise, maybe in loc)
-	\item Intuitiveness of the policy language (how easy is it to understand? Not really a good way to evaluate this other than demonstrate earlier by example)
-	\item Speed of compilation (does it take forever? what are the bottlenecks)
-	\item Understandability of the resulting configurations (Can humans understand them?)
-	\item Some measure of the size of the resulting configurations (e.g., the number of route maps. Is this actually ever an issue in BGP?)
-\end{enumerate}
-
-\section{Future Work}
-
-\begin{itemize}
-	\item Environments: Model environments using the same framework. (e.g., no-export allows certain paths that weren't before
-	\item Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
-	\item OSPF: language isn't inherently tied to BGP, and could use iBGP with OSPF or some other protocol. This would require different kinds of checks though.
-\end{itemize}
-
-\section{Related Work}
-
-\begin{itemize}
-	\item Regular path queries
-	\item Lots of background on BGP
-	\item Feamster rcc stuff
-	\item Logic programming BGP configs
-\end{itemize}
-
-\section{Conclusions}
-
-TODO
-
-\appendix
-\section{Appendix Title}
-
-This is the text of the appendix, if you need one.
-
-\acks
-
-Acknowledgments, if needed.
-
-% We recommend abbrvnat bibliography style.
-
-\bibliographystyle{abbrvnat}
+\bibliographystyle{abbrv}
+\bibliography{references}
 
@@
 
-\begin{thebibliography}{}
-\softraggedright
-
-\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
-P. Q. Smith, and X. Y. Jones. ...reference text...
-
-\end{thebibliography}
-
 \end{document}
-
-%                       Revision History
-%                       -------- -------
-%  Date         Person  Ver.    Change
-%  ----         ------  ----    ------
-
-%  2013.06.29   TU      0.1--4  comments on permission/copyright notices

### 2016-01-14 paper/related.tex
splitting the paper across files

--- 2015-11-02 paper/sigplanconf-template.tex
@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-%
-% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
-%               sigplanconf-guide.pdf
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
-
-\documentclass{sigplanconf}
-
-% The following \documentclass options may be useful:
-
-% preprint      Remove this option only once the paper is in final form.
-% 10pt          To set in 10-point type instead of 9-point.
-% 11pt          To set in 11-point type instead of 9-point.
-% authoryear    To obtain author/year citation style instead of numeric.
-
-\usepackage{amsmath}
-
-\begin{document}
-
-\special{papersize=8.5in,11in}
-\setlength{\pdfpageheight}{\paperheight}
-\setlength{\pdfpagewidth}{\paperwidth}
-
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
-\copyrightyear{20yy} 
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
-\doi{nnnnnnn.nnnnnnn}
-
-% Uncomment one of the following two, if you are not going for the 
-% traditional copyright transfer agreement.
-
-%\exclusivelicense                % ACM gets exclusive license to publish, 
-                                  % you retain copyright
-
-%\permissiontopublish             % ACM gets nonexclusive license to publish
-                                  % (paid open-access papers, 
-                                  % short abstracts)
-
-\titlebanner{banner above paper title}        % These are ignored unless
-\preprintfooter{short description of paper}   % 'preprint' option specified.
-
-\title{Title Text}
-\subtitle{Subtitle Text, if any}
-
-\authorinfo{Name1}
-           {Affiliation1}
-           {Email1}
-\authorinfo{Name2\and Name3}
-           {Affiliation2/3}
-           {Email2/3}
-
-\maketitle
-
-\begin{abstract}
-This is the text of the abstract.
-\end{abstract}
-
-\category{CR-number}{subcategory}{third-level}
-
-% general terms are not compulsory anymore, 
-% you may leave them out
-\terms
-term1, term2
-
-\keywords
-keyword1, keyword2
-
-\section{Introduction}
-
-%% Word vommit
-\begin{itemize}
-	\item Network configuration is hard ...
-	\item Configs are local and distributed
-	\item Difficult to express intent directly
-	\item Often achieve intent through indirect means (i.e., backups through aggregation)
-	\item Distributed, asynchronous, environment unknown, failures ... means difficult to consider all scenarios	
-	\item Problems are compounded in inter-domain routing where other factors like peering agreements are important
-	\item Wide variety of considerations: Have preferences for certain routes over others, failure resistance, backups etc
-	\item On the other hand, BGP is the only widely used, policy-rich routing language
-	\item Often used for intra-domain routing as well
-	\item We present a new language that allows operators to directly express intent for inter and intra-domain routing policies 
-		  from a centralized point of view.
-	\item The language provides the operator with the abstraction that they can control all end-to-end routes that transit their 
-		  network, even if the routes start and/or end outside of their network.
-	\item The language consists of regular expression constraints on the set of allowed routes along with a flexible preference operator
-		  that allows ranking sets of paths to enable both inter-domain routing preferences and intra-domain backup paths.
-	\item A compiler takes a routing policy written in this language and synthesizes concrete, per-device configurations running BGP. 
-	\item The resulting configurations are guaranteed to correctly implement the policy using the standard, distributed path vector protocol, 
-		  and remain correct under all possible network failure scenarios.
-	\item To enable a wider spectrum of implementable policies, we model common environment assumptions (e.g., semantics of BGP community values)
-		  As sets of allowed/disallowed paths provided by a neighbor using the same regular path framework.
-	\item Although we choose to target BGP for both inter and intra domain routing due to its expressiveness, our language is agnostic to any particular 
-		  routing protocol. It describes only routes and their relative preferences. As such, an alternative routing protocol, such as OSPF, could 
-		  be used internally. This would change the set of implementable policies.
-	\item To allow for more fine-grained control over control-plane details, our language permits additional constraints on the control protocol
-		  (e.g., maximum number of allowed routes, whether to use multipath etc)
-	\item Advantages: Centralized configuration (no copy paste error, more concise), Synthesis (no need for gory details, e.g., community values),
-		  Expressiveness (backup routing, preferences, waypointing, directly say things like no transit), 
-		  Correctness: (Guaranteed to implement the policy, even under failure scenarios),
-		  Verification: (Language serves as a high-level abstraction of the low-level details, so we can perform verification directly on the high-level policies)
-\end{itemize}
-
-\section{Overview}
-
-\begin{itemize}
-	\item Introduce language with examples...
-	\item Maybe, start with a typical AS, and show how simple it would be to implement a typical policy
-	\item Another good example, would be something that combined internal backup routing with preference based 
-		  entrance into the network using aggregation.
-	\item Could probably show an example of the resulting config, and how it is tagging using communities, 
-		  or alternatively show that it doesn't compile due to a particular failure scenario.
-\end{itemize}
-
-\section{Language}
-
-\subsection{Syntax}
-Define the grammar of the language.
-Need to distinguish whether the preference operator 
-appears only at the top level or not.
-
-\subsection{Semantics} 
-Give the semantics in terms of ranked paths.
-Should be straightforward extension of regular expression semantics with the 
-additional constraint that we take only valid topology paths and that their are no paths with 
-repeated locations in the path. If preferences appear only at the top level, then it is easy to rank the paths.
-One tricky point is that we care about paths starting or ending at locations that are connected to end-hosts in some way.
-And we want the length of the path to be a secondary tie-breaker .
-Additional assumption here should be that the prefixes are disjoint.
-
-\subsection{Theory}
-What are the properties of this language? Ideally, a proof here about its expressiveness. We can perhaps do everything 
-BGP can do? We can't do shortest paths routing with BGP, but we could with OSPF though? Clearly we can only describe 
-policies that are stable under all possible failure scenarios (at least internally stable, could still cause) routing 
-loops with interactions with neighbors.
-
-\section{Compilation}
-
-\begin{itemize}
-	\item Separate prefixes so they are disjoint (assumption) for semantics)
-		  probably using BDDs where each bit is a variable is the easiest way to do this.
-	\item For each prefix, build a DFA from each of the regular path constraints 
-		  We do this using character classes and regular expression derivatives.
-		  The accepting states are labeled with the particular preference.
-	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or 
-		  more of the regular path constraints. We accept if we are in at least one of the accepting states 
-		  for one or more of the DFAs. We take the max of the preferences for the accepting preference.
-		  Add a new start and end node as well.
-	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution. 
-		  This is sound. Removing these makes it easier to check if things are implementable using BGP (see next point).
-		  There are two ways to do this: a sound heuristic for removing edges and nodes, and a complete, but slow method for 
-		  removing everything not needed.
-	\item Since our policy language is richer than BGP, we need to check if it is implementable with BGP.
-		  First show some examples of what the problem is: why BGP cannot make a decision.
-		  We check: preference consistency (doesn't regret a choice based on which preference accepting state it might reach)
-		  and topology consistency (no failure scenario will result in an advertisement reaching a router from a more preferred neighbor 
-		  but then not get to an accepting state, when another, less preferred route was available).
-	\item We can check for topology consistency using a sufficient condition (that works often and is very fast), 
-		  and by enumerating failure scenarios using a necessary and sufficient condition (that always works but is slooooow)
-
-	\item Finally, if we know BGP can make decision locally, then we can directly translate to local BGP configurations using 
-		  information about the state machines from the neighbors. In particular, we tag (and test on) community values for the
-		  corresponding state and set preferences accordingly (example will be needed)
-	\item Running example will be helpful here.	
-\end{itemize}
-
-\section{Evaluation}
-
-\begin{itemize}
-	\item Expressiveness of the policy language (maybe a proof earlier for this)
-	\item Compactness of the policy language (how verbose? likely pretty concise)
-	\item Intuitiveness of the policy language (how easy is it to understand? probably make the earlier examples clear)
-	\item Speed of compilation (does it take forever?)
-	\item Understandability of the resulting configurations (Can humans understand them?)
-	\item Some measure of the size of the resulting configurations (is this actually an issue in BGP??)
-\end{itemize}
-
 \section{Related Work}
@@
 \end{itemize}
-
-\section{Conclusions}
-
-TODO
-
-\appendix
-\section{Appendix Title}
-
-This is the text of the appendix, if you need one.
-
-\acks
-
-Acknowledgments, if needed.
-
-% We recommend abbrvnat bibliography style.
-
-\bibliographystyle{abbrvnat}
-
-% The bibliography should be embedded for final submission.
-
-\begin{thebibliography}{}
-\softraggedright
-
-\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
-P. Q. Smith, and X. Y. Jones. ...reference text...
-
-\end{thebibliography}
-
-\end{document}
-
-%                       Revision History
-%                       -------- -------
-%  Date         Person  Ver.    Change
-%  ----         ------  ----    ------
-
-%  2013.06.29   TU      0.1--4  comments on permission/copyright notices

### 2016-01-15 paper/background.tex
editing 2 and 3

\section{Background on BGP}
\label{sec:background}

We focus on BGP as it is the most common and flexible way to implement distributed control planes today. Before delving into the details of our work, we provide here relevant background on BGP.

BGP is a path vector protocol that connects autonomous systems (ASes). An AS has one or more routers controlled by the same administrative entity. ASes exchange routing announcements with their neighbors. Each announcement has a destination IP prefix and some attributes (see below), and it indicates that the sending AS is willing to carry traffic to that prefix from the receiving AS. (Traffic flows in the opposite direction, from announcement receivers to senders.)

When an AS receives an announcement from a neighbor, it is processed by import filters that may drop the announcement or modify some attributes. If multiple announcements for the same prefix survive import filters, the router selects the best one based on local policy, expressed in terms of route attributes. This route is then used to send traffic to the destination. It is also advertised to the neighbors, after passing them through neighbor-specific export filters that may stop the announcement or modify some attributes.

A few route attributes are notable. The AS-path attribute accompanies all announcements and it has the ordered list of ASes that the announcement has traversed thus far. While AS-path attribute has a global meaning, some attributes are meaningful only within an AS or between neighboring ASes.  Two such attributes are communities and multi-exit discriminator (MED). Communities are opaque, string attributes that ASes use to color incoming routes on different criteria (e.g., ``entered on West Coast"). They can also be used to signal to neighbors about how the announcement should be handled (e.g., do not export it further). MEDs are used when an AS has more than one link to a neighboring AS. They are numeric values that signal to the receiving AS which link the sender prefers to receive traffic on.

The route selection process assigns a {\em local preference} to each route that survives the import filters. Routes with higher local preference are preferred. For routes with equal preference, other factors such as AS path length, MEDs, internal routing cost, are considered in order. Because they are considered first in the selection process, they This preference can be based on any route attribute. It can also be based on the sending neighbor, which is a common practice.

 , or other existing attributes.  Local preference is an internal attribute that is not carried beteeen the first criterion in selecting the best route and higher numbers are assigned to preferred routes. BGP conside

aggregation

### 2016-01-15 paper/motivation.tex
editing 2 and 3

@@
 Device configuration languages are low-level and indirect.
-For instance, instead of allowing operators to express directly the paths they want through the network, they require operators to specify link costs that result in those paths; instead of allowing operators to express directly the types of traffic to not carry through the network, they require operators to select and program an appropriate filtering mechanism (e.g., route maps, null routing,  access control lists) and instantiate it on topologically appropriate devices; instead of allowing operators to directly specify that they prefer to send traffic via customer, peer, and provider networks, in that order, they require operators to program BGP local preferences at each router and ensure that the preferences are consistent across routers.
+For instance, instead of allowing operators to express directly the paths they want through the network, they require operators to specify link costs that result in those paths; instead of allowing operators to express directly the types of traffic to not carry through the network, they require operators to select and program an appropriate filtering mechanism (e.g., route maps, null routing,  access control lists) and instantiate it on topologically appropriate devices; instead of allowing operators to directly specify that they prefer BGP neighbors in a certain order, they require operators to program BGP local preferences and multi-exit discriminators (MED) at each router and ensure that the numbers are consistent across routers.
 
@@
 This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures.
-We illustrate this point using two examples, based on policies that we have seen in practice.
+We illustrate this point using two examples based on policies that we have seen in practice.
 
-\subsection{OLD -- Overview}
-\todo{this subsection can be deleted once we have captured everything in it}
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{figures/example1}
+\caption{Creating router-level policies is difficult.}
+\label{fig:example1}
+\end{figure}
 
-Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention).
-Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
+Consider the backbone network in Figure~\ref{fig:example1}, with three neighbors, a customer $Cust$ , a peer $Peer$, and a provider $Prov$.
+The policy of this network is shown on the right.
+Due to the nature of commercial relationships, it prefers the neighbors in a certain order ($P1$) and does not want to act as a transit between Peer and Prov ($P2$).
+It prefers to exchange traffic with Cust over $R1$ rather than $R2$ because $R2$ is more expensive or lower-capacity link ($P3$).
+To guard against another network (known as autonomous system or AS in BGP terminology) "hijacking" prefixes owned by Cust, it only sends traffic to those prefixes if Cust is on the AS path ($P4$).
+To guard against Cust accidentally becoming a transit for Prov, it does not use Cust for traffic with Prov (and possibly other large networks) in the AS path ($P5$).
 
-\begin{itemize}
-	\item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
-	\item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
-	\item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
-	\item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
-	\item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
-\end{itemize}
+To correctly implement this network's policy, the operators must compute and assign router local preferences such that those at Cust-facing interfaces $>$ Peer-facing interfaces $>$ Peer-facing interfaces.
+At the same time, the preference at $R2$'s Cust-facing interface should be lower than that at $R1$ (but higher than that at Prov-facing interface).
+To fully realize $P2$, MEDs will have to be appropriately configured as well.
+To implement $P3$ and $P4$, the operators may assign communities that indicate where a certain routing announcement entered the network.
+Then, R4 must not announce to Peer routes that have communities that correspond to the R2-prov link but must announce communities for the $R2$-Cust and $R1$-Cust links.
+Finally, to implement $P4$ and $P5$, the operators will have to compute and configure appropriate prefix-based and AS-path-based filters at each router.
 
-Possible Examples:
-\begin{itemize}
-	\item Basic datacenter with spine preference
-	\item Simple AS that prefers customers over peers over providers
-	\item Combined internal backup routing with preference based entrance into the network using aggregation.
-	\item Something like cold potato routing
-\end{itemize}
+It should be straightforward to see how difficult such policy configuration can be in practice, where the network will have many neighbors across multiple classes of commercial relationships, differing numbers of links per neighbor, along with several region-, neighbor- or prefix-based exceptions to the general policy.
+Templates only help to certain extent, e.g., keeping preference and community values consistent across routers.
+The operators must still do much of the work manually, in coming up with the templates themselves.
+We show later how \sysname enables a direct expression of the policies of such networks and compiles them automatically to individual router configurations.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{figures/example2}
+\caption{Policy-compliance under failures is difficult.}
+\label{fig:example2}
+\end{figure}
+
+If configuring network policies is difficult, doing so in a way that ensures policy compliance in the face of failures is even more difficult.
+Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running eBGP with each other.\footnote{To scale and to simplify policy implementation, data center networks increasingly use BGP, with a private ASN per router~\cite{bgp-in-dc-rfc}.} The network has two clusters, one that hosts services that should be reachable globally and one that hosts that should be accessible only internally.
+This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally.
+In addition, instead of announcing individual prefixes in this global space, the space is aggregated as one less specific prefix $P_G$.
+
+The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ {\em not export} externally what they hear from routers G and H since these routers border the cluster with local services; and $ii)$ announce what they hear from routers C and D and aggregate to $P_G$ if an announcement is subset of $P_G$.
+The appeal of this implementation is that X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be added to local services without updating router configurations).
+
+However, the implementation above is not correct in the face of failures.
+Suppose links X--G and X--H fail.
+Then, X will hear announcements for $P_{l*}$ from C and D, having traversed from G and H to Y to C and D.
+Per policy implementation, X will start "leaking" these prefixes externally.
+Depending on the reason to have local services, this leak could impact security (e.g., if the services were sensitive) or availability (e.g., if the $P_{l*}$ prefixes are used for other services outside of the data center).
+This problem does not happen without failures (and thus in operators' initial testing) because without failures X prefers paths to $P_{l*}$ through G and H since they are shorter.
+A similar problem will happen if links Y--G and Y--H fail.\footnote{On the other hand, depending on the exact implementation, if links X--C and X--D (or Y--C and Y--D) fail, the network will run into a problem where X (Y) may stop announcing the global prefixes because they would be heard through G and H.}  Link failures in data centers are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.
+
+\todo{keep this para only if we discuss aggregation stuff in the design}
+To avoid this problem, the operator may decide to disallow paths with "valleys," that is, those that go up, down, and back up again.
+This can be implemented by $X$ and $Y$ rejecting paths through the other.
+However, that creates a different problem, aggregation-related blackhole~\cite{xx}, in the face of failures.
+Suppose links D--A and X--C fail.
+Now, X will hear announcements for $P_{g2}$ from D and will thus announce the $P_G$ externally.
+This announcement will bring to X traffic for $P_{g1}$ as well, but because of valley-free filtering, X does not have a valid route for $P_{g1}$ and will thus drop all traffic to it.
+
+Given high-level policy specification, \sysname implements them in a way that guarantees compliance under all failures if that is possible.
+Otherwise, it generates a compiler error that informs the operator that their specification cannot be met.
+For features like aggregation, it will also provide a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
+
+%\subsection{OLD -- Overview}
+%\todo{this subsection can be deleted once we have captured everything in it}
+%
+%Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention).
+%Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
+%
+%\begin{itemize}
+%	\item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
+%	\item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
+%	\item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
+%	\item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
+%	\item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
+%\end{itemize}
+%
+%
+%Possible Examples:
+%\begin{itemize}
+%	\item Basic datacenter with spine preference
+%	\item Simple AS that prefers customers over peers over providers
+%	\item Combined internal backup routing with preference based entrance into the network using aggregation.
+%	\item Something like cold potato routing
+%\end{itemize}

### 2016-01-15 paper/background.tex
a pass

@@
 
-We focus on BGP as it is the most common and flexible way to implement distributed control planes today. Before delving into the details of our work, we provide here relevant background on BGP.
+Our work focuses on BGP as it is the most common and flexible way to implement distributed control planes today. In this section, we provide relevant background on BGP.
 
-BGP is a path vector protocol that connects autonomous systems (ASes).
-An AS has one or more routers controlled by the same administrative entity.
-ASes exchange routing announcements with their neighbors.
+BGP is a path-vector routing protocol that connects autonomous systems (ASes).
+An AS has one or more routers managed by the same administrative entity.
+ASes exchange routing announcements with their neighboring ASes.
 Each announcement has a destination IP prefix and some attributes (see below), and it indicates that the sending AS is willing to carry traffic to that prefix from the receiving AS.
-(Traffic flows in the opposite direction, from announcement receivers to senders.)
+Traffic flows in the opposite direction, from announcement receivers to senders.
 
-When an AS receives an announcement from a neighbor, it is processed by import filters that may drop the announcement or modify some attributes.
-If multiple announcements for the same prefix survive import filters, the router selects the best one based on local policy, expressed in terms of route attributes.
+When a route announcement is received by an AS, it is processed by custom import filters that may drop the announcement or modify some attributes.
+If multiple announcements for the same prefix survive import filters, the router selects the best one based on local policy (see below).
 This route is then used to send traffic to the destination.
-It is also advertised to the neighbors, after passing them through neighbor-specific export filters that may stop the announcement or modify some attributes.
+It is also advertised to the neighbors, after processing through neighbor-specific export filters that may stop the announcement or modify some attributes.
 
-A few route attributes are notable.
-The AS-path attribute accompanies all announcements and it has the ordered list of ASes that the announcement has traversed thus far.
-While AS-path attribute has a global meaning, some attributes are meaningful only within an AS or between neighboring ASes.
-Two such attributes are communities and multi-exit discriminator (MED).
-Communities are opaque, string attributes that ASes use to color incoming routes on different criteria (e.g., ``entered on West Coast").
-They can also be used to signal to neighbors about how the announcement should be handled (e.g., do not export it further).
-MEDs are used when an AS has more than one link to a neighboring AS.
-They are numeric values that signal to the receiving AS which link the sender prefers to receive traffic on.
+All routing announcements are accompanied by an AS-path attribute that reflects the sequence of ASes that the announcement has traversed thus far.
+While the AS-path attribute has a global meaning, some attributes are meaningful only within an AS or between neighboring ASes.
+One such attribute is a list of community strings.
+ASes use such strings to color routes on different criteria (e.g., ``entered on West Coast") and then use the color later in the routing process.
+Communities are also used to signal to neighbors how they should handle an announcement (e.g., do not export it further).
+Another non-global attribute is the multi-exit discriminator (MED).
+It is used when an AS has more than one router-level link to a neighboring AS.
+Its (numeric) values signal to the neighbor how this AS prefers to receive traffic among those links.
 
@@
 Routes with higher local preference are preferred.
-For routes with equal preference, other factors such as AS path length, MEDs, internal routing cost, are considered in order.
-Because they are considered first in the selection process, they This preference can be based on any route attribute.
-It can also be based on the sending neighbor, which is a common practice.
+Among routes with the same local preference, other factors such as AS path length, MEDs, internal routing cost, are considered in order.
+Because it is considered first during route selection, local preference is highly influential, and ASes may assign this preference based on any aspect of the route.
+A common practice is to assign it based on the commercial relationship with the neighbor.
+For instance, an AS may prefer in order customer ASes (which pay money), peer ASes (with free exchange of traffic), and provider ASes (which charge money for traffic).
 
- , or other existing attributes.
-Local preference is an internal attribute that is not carried beteeen the first criterion in selecting the best route and higher numbers are assigned to preferred routes.
-BGP conside
-
-aggregation
+The combination of arbitrary import and export filters and route selection policies at individual routers make BGP a highly flexible routing protocol.
+That flexibility, however, comes at the cost of it being difficult to configure correctly, as we explain next.

### 2016-01-15 paper/motivation.tex
a pass

--- 2016-01-14 paper/motivation.tex
@@
 
-We motivate our work by describing the current practice in network configuration and its shortcomings.
-In traditional networks with distributed control planes, the operators’ goal is to generate the configuration of individual devices.
-Based on its configuration, the device exchanges information with other (e.g., links costs or best known paths) devices, filters and ranks incoming information, and decides how to forward packets to various destinations.
+We motivate our work by describing the current practice in network configuration.
+In traditional networks with distributed control planes, the operators' goal is to generate the configuration of individual devices based on their desired policy.
+This configuration dictates the behavior of a device, how it exchanges routing information with neighbors and how it filters and ranks that information.
+The collective behavior of the devices should implement the desired policy.
 
 Device configuration languages are low-level and indirect.
-For instance, instead of allowing operators to express directly the paths they want through the network, they require operators to specify link costs that result in those paths; instead of allowing operators to express directly the types of traffic to not carry through the network, they require operators to select and program an appropriate filtering mechanism (e.g., route maps, null routing,  access control lists) and instantiate it on topologically appropriate devices; instead of allowing operators to directly specify that they prefer to send traffic via customer, peer, and provider networks, in that order, they require operators to program BGP local preferences at each router and ensure that the preferences are consistent across routers.
+For instance, instead of allowing operators to express directly the paths they want through the network, they require operators to specify metrics that result in those paths; instead of allowing operators to express directly the types of traffic to not carry through the network, they require operators to select and program an appropriate filtering mechanism (e.g., BGP import or export filters, null routing,  access control lists) and instantiate it on topologically appropriate devices; instead of allowing operators to directly specify that they prefer BGP neighbors in a certain order, they require operators to program local preferences and multi-exit discriminators (MED) at each router and ensure that the numbers are consistent across routers.
 
@@
 To reduce such problems, some networks use a template-based approach.
-Configuration templates abstract certain constants into variables (e.g., instead of concrete interface IP address, they may contain a variable {\small \sf{\$$Rtr1\_Int1\_IP$)}} and may use a device vendor-neutral syntax.
-Operators manually generate the templates, and then use tools to translate them into device configuration, by replacing variables with appropriate constants using a database of network information.
+Configuration templates abstract certain constants into variables (e.g., instead of concrete community value, they may contain a variable {\small \sf{\$$BadNeighbor$)}} and may use a device vendor-neutral syntax.
+Operators manually generate the templates and use tools to translate them into device configuration, by replacing variables with appropriate constants using a database of network information.
 
@@
 While templates avoids some pitfalls of the fully manual approach, they too are far from ideal.
-The fundamental issue is the semantic mismatch between desirable policies and the level of abstraction that templates offer.
-While desirable policies are network-wide (e.g., prefer customer networks, or link $A$ should serve as backup for link $B$), templates are device-level (e.g., BGP local preferences or link costs to use).
+The fundamental issue is the semantic mismatch between desired policies and the level of abstraction of templates.
+While many policies are network-wide (e.g., prefer customer networks, or never announce a route to a certain prefix to external neighbors), templates are device-level.
 Operators must still manually decompose network-wide policies into device-level policies that can produce the desired network-wide behavior.
+This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures.
+We illustrate this point using two examples based on policies that we have seen in practice.
 
-This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures.
-We illustrate this point using two examples, based on policies that we have seen in practice.
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{figures/example1}
+\caption{Creating router-level policies is difficult.}
+\label{fig:example1}
+\end{figure}
 
-\subsection{OLD -- Overview}
-\todo{this subsection can be deleted once we have captured everything in it}
+Consider the backbone network in Figure~\ref{fig:example1}.
+It has three neighbors, a customer $Cust$ , a peer $Peer$, and a provider $Prov$.
+The policy of this network is shown on the right.
+Per commercial relationships, it prefers the neighbors in a certain order ($P1$) and does not want to act as a transit between Peer and Prov ($P2$).
+It prefers to exchange traffic with Cust over $R1$ rather than $R2$ because $R2$ is a more expensive link ($P3$).
+To guard against another AS "hijacking" prefixes owned by Cust, it only sends traffic to those prefixes if Cust is on the AS path ($P4$).
+Finally, to guard against Cust accidentally becoming a transit for Prov, it does not use Cust for traffic that will later traverse Prov ($P5$).
 
-Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention).
-Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
+To correctly implement this network's policy, the operators must compute and assign local preferences such that preferences at Cust-facing interfaces $>$ Peer-facing interfaces $>$ Prov-facing interfaces.
+At the same time, the preference at $R2$'s Cust-facing interface should be lower than that at $R1$, but higher than that at Prov-facing interface.
+To fully realize $P2$, MEDs will have to be appropriately configured as well.
+To implement $P3$ and $P4$, the operators may assign communities that indicate where a certain routing announcement entered the network.
+Then, R4 must not announce to $Peer$ routes that have communities that correspond to the R2-prov link but must announce communities for the $R2$-Cust and $R1$-Cust links.
+Finally, to implement $P4$ and $P5$, the operators will have to compute and configure appropriate prefix- and AS-path-based filters at each router.
 
-\begin{itemize}
-	\item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
-	\item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
-	\item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
-	\item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
-	\item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
-\end{itemize}
+We can now see that devising correct configuration for real, larger networks will quickly become a nightmare.
+These networks will have many neighbors across multiple classes of commercial relationships, differing numbers of links per neighbor, along with several region-, neighbor- or prefix-based exceptions to the default policy.
+Templates only help to certain extent, e.g., by keeping preference and community values consistent across routers.
+The operators must still do much of the conceptually difficult work manually, in coming up with the templates themselves.
+\sysname enables a direct expression of the policies of such networks and compiles them automatically to individual router configurations.
 
-Possible Examples:
-\begin{itemize}
-	\item Basic datacenter with spine preference
-	\item Simple AS that prefers customers over peers over providers
-	\item Combined internal backup routing with preference based entrance into the network using aggregation.
-	\item Something like cold potato routing
-\end{itemize}
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{figures/example2}
+\caption{Policy-compliance under failures is difficult.}
+\label{fig:example2}
+\end{figure}
+
+If configuring policies for a fully functional network is difficult, doing so in a way that ensures policy compliance in the face of failures can be almost impossible.
+Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{To scale and to simplify policy implementation, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc-rfc}.} The network has two clusters, one that hosts services that should be reachable globally and one that hosts that should be accessible only internally.
+This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally.
+In addition, to reduce the number of prefixes that are announced externally, the global space is aggregated into one larger, less-specific prefix $P_G$.
+The semantics of aggregation in BGP is that the aggregate prefix is announced as long as the router has a path to even one sub-prefix.
+
+The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from routers G and H since these routers border the cluster with local services; and $ii)$ announce what they hear from routers C and D and aggregate to $P_G$ if an announcement is subset of $P_G$.
+The appeal of this implementation is that X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be added to local services without updating router configurations).
+
+However, this implementation is incorrect because it does not have the right behavior in the face of failures.
+Suppose links X--G and X--H fail.
+Then, X will hear announcements for $P_{l*}$ from C and D, having traversed from G and H to Y to C and D.
+Per policy implementation, X will start "leaking" these prefixes externally.
+Depending on the rationale for local services, this leak could impact security (e.g., if the services were sensitive) or availability (e.g., if the $P_{l*}$ prefixes are used for other services outside of the data center).
+This problem does not manifest without failures because then X has and prefers paths to $P_{l*}$ through G and H since they are shorter.
+A similar problem will happen if links Y--G and Y--H fail.
+%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}  
+Link failures in data centers are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.
+
+\todo{remove if we do not discuss aggregation in the design}
+To avoid this problem, the operator may decide to disallow paths with "valleys," i.e., those that go up, down, and back up again.
+This safeguard can be implemented by $X$ and $Y$ rejecting paths through the other.
+However, that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{xx}.
+Suppose links D--A and X--C fail.
+Now, X will hear announcements for $P_{g2}$ from D and will thus announce the $P_G$ externally.
+This announcement will bring to X traffic for $P_{g1}$ as well, but because of valley-free filtering, X does not have a valid route for $P_{g1}$ and will thus drop all traffic to it.
+
+Thus, we see that devising configuration that ensures policy compliance in the face of failures is complex and error-prone.
+\sysname helps operators by implementing their high-level policy specification in a way that guarantees compliance under all failures if that is possible.
+Otherwise, it generates a compile-time error that informs them that the specification cannot be met.
+For aggregation, it will also provide a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
+
+%\subsection{OLD -- Overview}
+%\todo{this subsection can be deleted once we have captured everything in it}
+%
+%Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention).
+%Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
+%
+%\begin{itemize}
+%	\item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
+%	\item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
+%	\item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
+%	\item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
+%	\item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
+%\end{itemize}
+%
+%
+%Possible Examples:
+%\begin{itemize}
+%	\item Basic datacenter with spine preference
+%	\item Simple AS that prefers customers over peers over providers
+%	\item Combined internal backup routing with preference based entrance into the network using aggregation.
+%	\item Something like cold potato routing
+%\end{itemize}

### 2016-01-17 paper/language.tex
added syntax figure to paper

@@
 Define the grammar of each of the languages - regular language, the macro language on top of it, and maybe the IR language.
+
+% grammar
+\newcommand{\BNFALT}{\;\;|\;\;}
+\newcommand{\hdr}[2]{\flushleft \chdr{#1}{#2}}
+\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}
+
+\begin{figure*}
+  \begin{minipage}[t]{.42\linewidth}
+  \hdr{\large Syntax}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rclr}
+    \hline
+     pol &::=& c_1, \dots, c_n & \textit{constraints} \\
+     c   &::=& p \Rightarrow r_1 \gg \dots \gg r_m & \textit{preferences} \\
+     p   &::=& true & \textit{true} \\
+      &\BNFALT& \neg p & \textit{negation} \\
+      &\BNFALT& p_1 \vee p_2 & \textit{disjunction} \\
+      &\BNFALT& p_1 \wedge p_2 & \textit{conjunction} \\
+      &\BNFALT& prefix = x & \textit{prefix test} \\
+      &\BNFALT& comm = t & \textit{community test} \\
+     r   &::=& n & \textit{AS number} \\
+      &\BNFALT& in & \textit{internal loc} \\
+      &\BNFALT& out & \textit{external loc} \\
+      &\BNFALT& r_1 \cup r_2 & \textit{union} \\
+      &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
+      &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
+      &\BNFALT& !(r) & \textit{path negation} \\
+      &\BNFALT& r^* & \textit{repetition} \\
+  \end{array} \]
+
+  \end{minipage}
+  %
+  ~~
+  \vrule
+  ~~
+  %
+  \begin{minipage}[t]{.5\linewidth}
+  \hdr{\large Propane Macros}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rcl}
+    \hline
+    only(X)       & = & X^* \\
+    never(X)      & = & (!X)^* \\
+    through(X)    & = & out^* \cdot in^* \cdot X \cdot in^* \cdot out^* \\
+    upstream(X)   & = & out^* \cdot (X \cap out) \cdot out^* \cdot in^+ \cdot out^* \\
+    downstream(X) & = & out^* \cdot in^+ \cdot out^* \cdot (X \cap out) \cdot out^* \\
+    end(X)        & = & (out^* \cdot in^* \cdot (X \cap in)) \cup \\
+                  & = & (out^* \cdot in^+ \cdot out^* \cdot (X \cap out)) \\
+    start(X)      & = & ((X \cap in) \cdot in^* \cdot out^*) \cup \\
+                  & = & ((X \cap out) \cdot out^* \cdot in^+ \cdot out^*) \\
+    exit(X)       & = & (out^* \cdot in^* \cdot (X \cap in) \cdot out \cdot out^*) \cup \\
+                  &        & (out^* \cdot in^+ \cdot (X \cap out) \cdot out^*) \\
+    enter(X)      & = & (out^* \cdot out \cdot (X \cap in) \cdot in^* \cdot out^*) \cup \\
+                  &        & (out^* \cdot (X \cap out) \cdot in^+ \cdot out^*) \\
+    link(X,Y)     & = & (out^* \cdot in^* \cdot X \cdot Y \cdot in^* \cdot out^*) \cup \\
+                  & = & (out^* \cdot (X \cap out) \cdot (Y \cap in) \cdot in^* \cdot out^*) \cup \\
+                  & = & (out^* \cdot in^* \cdot (X \cap in) \cdot (Y \cap out) \cdot out^*) \\
+  \end{array} \]
+
+  \end{minipage}
+
+  \hrulefill
+
+  \caption{Regular Intemediate Language (RIL) syntax (left), and 
+           Propane language expansions (right).}
+  \label{fig:semantics}
+\end{figure*}
 

### 2016-01-18 paper/language.tex
finishing figure for language

--- 2016-01-14 paper/language.tex
@@
 Define the grammar of each of the languages - regular language, the macro language on top of it, and maybe the IR language.
+
+% grammar
+\newcommand{\BNFALT}{\;\;|\;\;}
+\newcommand{\hdr}[2]{\flushleft \chdr{#1}{#2}}
+\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}
+
+\begin{figure*}
+  \begin{minipage}[t]{.45\linewidth}
+  \hdr{\large Syntax}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rclr}
+    \hline
+
+     pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
+     p       &::=& p \Rightarrow r_1 \gg \dots \gg r_m & \textit{preferences} \\
+     t       &::=& & \textit{test} \\
+         &\BNFALT& true & \textit{true} \\
+         &\BNFALT& \neg t & \textit{negation} \\
+         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
+         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
+         &\BNFALT& prefix = x & \textit{prefix test} \\
+         &\BNFALT& comm = c & \textit{community test} \\
+     r       &::=& & \textit{regular paths} \\ 
+         &\BNFALT& n & \textit{AS number} \\
+         &\BNFALT& in & \textit{internal loc} \\
+         &\BNFALT& out & \textit{external loc} \\
+         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
+         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
+         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
+         &\BNFALT& !(r) & \textit{path negation} \\
+         &\BNFALT& r^* & \textit{repetition} \\
+     l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
+     cc     &::=& agg(x, l) \BNFALT tag(c, t, l) & \textit{control constraints} \\
+  \end{array} \]
+
+  \end{minipage}
+  %
+  ~~
+  \vrule
+  ~~
+  %
+  \begin{minipage}[t]{.5\linewidth}
+  \hdr{\large Propane Expansions}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rcl}
+    \hline
+    any           & = & out^* \cdot in^+ \cdot out^* \\
+    internal      & = & in^+ \\
+    external      & = & out^+ \\
+    only(X)       & = & any \cap X^* \\
+    never(X)      & = & any \cap (!X)^* \\
+    through(X)    & = & out^* \cdot in^* \cdot X \cdot in^* \cdot out^* \\
+    after(X)      & = & out^* \cdot (X \cap out) \cdot out^* \cdot in^+ \cdot out^* \\
+    before(X)     & = & out^* \cdot in^+ \cdot out^* \cdot (X \cap out) \cdot out^* \\
+    end(X)        & = & any \cap (\Sigma^* \cdot X) \\
+    start(X)      & = & any \cap (X \cdot \Sigma^*) \\
+    exit(X)       & = & (out^* \cdot in^* \cdot (X \cap in) \cdot out \cdot out^*) \cup \\
+                  &        & (out^* \cdot in^+ \cdot (X \cap out) \cdot out^*) \\
+    enter(X)      & = & (out^* \cdot out \cdot (X \cap in) \cdot in^* \cdot out^*) \cup \\
+                  &        & (out^* \cdot (X \cap out) \cdot in^+ \cdot out^*) \\
+    link(X,Y)     & = & any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
+    path(\vec{X}) & = & any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
+    novalley(\vec{X}) & = & any ~ \cap \\
+                  &   & !path(X_2,X_1,X_2) ~ \cap \dots \cap \\ 
+                  &   & !path(X_n,X_{n-1},X_n) \\
+  \end{array} \]
+
+  \end{minipage}
+
+  \hrulefill
+
+  \caption{Regular Intemediate Language (RIL) syntax (left), and 
+           Propane language expansions (right).}
+  \label{fig:semantics}
+\end{figure*}
 

### 2016-01-18 paper/language.tex
finishing figure for language

@@
      pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
-     p       &::=& p \Rightarrow r_1 \gg \dots \gg r_m & \textit{preferences} \\
+     p       &::=& p \leadsto r_1 \gg \dots \gg r_m & \textit{preferences} \\
      t       &::=& & \textit{test} \\

### 2016-01-18 paper/propane.tex

\section{Propane}
\label{sec:propane}

Show how to solve examples from the previous section.

### 2016-01-18 paper/regularir.tex

--- 2016-01-18 paper/language.tex
@@
-\section{Language}
-\label{sec:language}
+\section{Regular IR}
+\label{sec:rir}
 
@@
      pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
-     p       &::=& p \leadsto r_1 \gg \dots \gg r_m & \textit{preferences} \\
+     p       &::=& t \text{ with } r_1 \gg \dots \gg r_m & \textit{preferences} \\
      t       &::=& & \textit{test} \\

### 2016-01-18 paper/propane.tex
adding propane example 2 to paper.

@@
 
-Show how to solve examples from the previous section.
+\sysname simplifies network configuration by automatically generating low-level BGP configurations from a high-level specification of the network's routing policy. 
+%
+The operator configures the network with the abstraction that he or she has centralized control over routing and uses a set of high-level constraints to describe the different routes traffic may (or may not) take and their relative preferences.
+%
+The \sysname compiler generates BGP configurations for each device in the network that operate in a completely distributed fashion and are correct by construction -- automatically synthesizing import/export filters, local preference and MED attributes, and community tags to ensure policy compliance under all possible failure scenarios.
+%
+We now demonstrate \sysname by showing how to configure the networks from the previous examples.
+
+\example{1}
+
+\example{2}
+
+Consider again the datacenter from Section~\ref{sec:motivation}.
+In this example, there are primarily three main concerns: (1) traffic for the prefix block allocated to each top-of-rack router can reach that router, (2) local services do not leak outside the datacenter, and (3) aggregation is performed on global prefixes to reduce churn in the network.
+
+\sysname allows us to decompose and specify each of these constraints in a modular fashion.
+The first constraint is about prefix ownership -- namely, that we only want traffic for certain prefixes to end up at a particular locations.
+The following definition in propane captures this intent:
+
+\begin{lstlisting}[mathescape=true]
+define Ownership = {
+    $\path{p_{g1}}{end(A)}$
+    $\path{p_{g2}}{end(B)}$
+    $\path{p_{l1}}{end(E)}$
+    $\path{p_{l2}}{end(F)}$
+}
+\end{lstlisting}
+
+The constraints in the ownership task are read in a top-down fashion.
+Traffic for prefix $p_{g1}$ is only allowed to to follow paths that end at router A.
+Similarly, traffic not matching $p_{g1}$, but which matches $p_{g2}$ must end at router B and so on.
+%
+To capture the second constraint, we can define another task for the core routing policy:
+
+\begin{lstlisting}[mathescape=true]
+define Routing = {
+    $\path{p_{g*}}{any}$
+    $\path{p_{l*}}{\neg enter(out)}$
+    $\path{true}{exit(out)}$
+}
+\end{lstlisting}
+
+The first line states that there is no restriction on how traffic must traverse the network for global prefixes.
+This means traffic for $p_{g*}$ may be sent either from other routers in the datacenter, or from external ASes.
+The second line ensures that traffic for local prefixes never enters the network from an outside location.
+This  guarantees that the services remain reachable only to locations internal to the data center.
+
+Finally, we can combine these constraints logically to specify the network-wide policy.
+
+\begin{lstlisting}[mathescape=true]
+Ownership $\wedge$ Routing $\wedge$ agg($p_{agg}$, $in \rightarrow out$)
+\end{lstlisting}
+
+In addition to constraints on the shape of paths, \sysname allows the operator to specify constraints on the BGP control plane.
+Above, a constraint on aggregation is included to ensure that an aggregation for $p_{agg}$ is performed from locations inside the network to locations outside the network.
+
+% correct by construction
+% mention centralized
+% mention attributes

### 2016-01-19 paper/propane.tex
Example 2 in paper. Better rule compression for memory reduction.

@@
 
-\example{1}
+\para{Example 1}
 
-\example{2}
+We now show how to write the routing policy for the backbone network in Section~\ref{sec:motivation}.
+
+\para{Example 2}
 
@@
 
-Finally, we can combine these constraints logically to specify the network-wide policy.
+Finally, we can combine these constraints logically to specify the network-wide policy:
 
@@
 
-% correct by construction
-% mention centralized
-% mention attributes
+Once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. Similarly, it can check for aggregate-induced black holes up to $k$ failures.

### 2016-01-19 paper/propane.tex
Finish draft of section 4.

@@
 We now show how to write the routing policy for the backbone network in Section~\ref{sec:motivation}.
+\sysname allows to address each of the requirements in turn.
+First we address requirements (P1), (P3), and (P4) that customers are preferred over peers over providers, and that a customer appear on the path for its prefix.
+The following \sysname code accomplishes these two objectives:
+
+\begin{lstlisting}[mathescape=true]
+define ExitCust = $exit(R_1 \gg R_2)$
+
+define Routing = {
+    $\path{C_{pfx}}{ExitCust \gg end(Cust) }$
+    $\path{I_{pfx}}{end(in)}$
+    $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
+}
+\end{lstlisting}
+
+The first definition defines paths that exit our network to the customer.
+The statement $exit(R_1 \gg R_2)$ restricts us to paths that leave our network through either router $R_1$ or $R_2$, with a preference for $R_1$.
+The first line of the \textsf{Routing} policy ensures that traffic destined for customer prefixes ($C_{pfx}$) either leaves the network directly to the customer (with a preference for leaving through $R_1$), or simply ends at the customer.
+Not leaving directly to the customer by going through \textit{Peer} or \textit{Prov} is less preferred than leaving directly, and thus serves as a backup route in a direct route is not available.
+
+The second line state that traffic for internal prefixes $I_{pfx}$ must end in our network, and is otherwise unconstrained.
+The last line applies to any other traffic, and allows for any routes that leave through a peer with a preference for customers over peers over providers.
+While this still allows transit traffic (e.g., traffic can enter from \textit{Peer} and leave through \textit{Prov}), we can restrict this behavior separately as follows:
+
+\begin{lstlisting}[mathescape=true]
+define PP = Peer or Prov
+define PPTransit = $enter(PP) \wedge exit(PP)$
+define CustTransit = $later(Cust) \wedge later(Prov)$
+
+define NoTransit = {
+    $\path{true}{\neg PPTransit \wedge \neg CustTransit}$
+}
+\end{lstlisting}
+
+The \textsf{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied.
+In particular, it says that, for any prefix, traffice should never both enter and exit the network from \textit{Peer} or \textit{Prov}.
+Similarly it prevents traffic from ever following paths that leave our network and later go through both \textit{Prov} and \textit{Cust}.
+
+\begin{lstlisting}[mathescape=true]
+Routing $\wedge$  NoTransit
+\end{lstlisting}
+
+The final policy is simply the conjunction of the routing and no transit constraints.
+\sysname will generate per-device import and export filters, local preferences and MED attributes, and community tags to ensure that the policy is met under all failure scenarios.
 

### 2016-01-20 paper/compilation1.tex
Add compilation overview. Add to regular IR section.

\section{Compilation}
\label{sec:compilation}

\subsection{Overview}

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/pipeline}
\caption{Compilation pipeline stages for Propane.}
\label{fig:pipeline}
\end{figure}

In this section we briefly describe our compilation strategy for \sysname. Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate user-level \sysname policies into vendor-specific, device-local BGP policies. The first stage of the pipeline involves simple rewriting rules and substitutions from the user-level languae into the core Regular Intermediate Representation (RIR). Policies in RIR are checked for well-formedness (e.g., never constraining traffic that does not enter the network), before being combined with topological information to obtain Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the control flow of all BGP advertisements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance, guarantee failure safety, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines the PGIR for the policy is safe, the compiler uses a simple translation to an abstract BGP (ABGP) representation. To make configurations more readable for human operators, and to reduce the size of the resulting configurations, the \sysname compiler makes several passes over ABGP form. Finally, vendor-specific adaptors can be added to \sysname to translate from ABGP to actual concrete configurations that go on the network devices.

\subsection{Regular IR (RIR)} 
\label{sec:rir}

The high-level language presented in Section~\ref{sec:propane} is just a thin layer on top of a core, regular-expression-based language for describing preference-based path constraints. Regular expressions are an expressive formalism that have been studied extensively for their ability usefulness in describing paths through graphs~\cite{bib:todo}. We prese

\para{Syntax}
Define the grammar of each of the languages - regular language, the macro language on top of it, and maybe the IR language.

% grammar
\newcommand{\BNFALT}{\;\;|\;\;}
\newcommand{\hdr}[2]{\flushleft \chdr{#1}{#2}}
\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}

\begin{figure*}
  \begin{minipage}[t]{.45\linewidth}
  \hdr{\large Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
    \hline

     pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
     p       &::=& t \mapsto r_1 \gg \dots \gg r_m & \textit{preferences} \\
     t       &::=& & \textit{test} \\
         &\BNFALT& true & \textit{true} \\
         &\BNFALT& \neg t & \textit{negation} \\
         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
         &\BNFALT& prefix = x & \textit{prefix test} \\
         &\BNFALT& comm = c & \textit{community test} \\
     r       &::=& & \textit{regular paths} \\ 
         &\BNFALT& n & \textit{AS number} \\
         &\BNFALT& in & \textit{internal loc} \\
         &\BNFALT& out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& !(r) & \textit{path negation} \\
         &\BNFALT& r^* & \textit{repetition} \\
     l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
     cc     &::=& agg(x, l) \BNFALT tag(c, t, l) & \textit{control constraints} \\
  \end{array} \]

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{\large Propane Expansions}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rcl}
    \hline
    any           & = & out^* \cdot in^+ \cdot out^* \\
    internal      & = & in^+ \\
    external      & = & out^+ \\
    only(X)       & = & any \cap X^* \\
    never(X)      & = & any \cap (!X)^* \\
    through(X)    & = & out^* \cdot in^* \cdot X \cdot in^* \cdot out^* \\
    after(X)      & = & out^* \cdot (X \cap out) \cdot out^* \cdot in^+ \cdot out^* \\
    before(X)     & = & out^* \cdot in^+ \cdot out^* \cdot (X \cap out) \cdot out^* \\
    end(X)        & = & any \cap (\Sigma^* \cdot X) \\
    start(X)      & = & any \cap (X \cdot \Sigma^*) \\
    exit(X)       & = & (out^* \cdot in^* \cdot (X \cap in) \cdot out \cdot out^*) \cup \\
                  &        & (out^* \cdot in^+ \cdot (X \cap out) \cdot out^*) \\
    enter(X)      & = & (out^* \cdot out \cdot (X \cap in) \cdot in^* \cdot out^*) \cup \\
                  &        & (out^* \cdot (X \cap out) \cdot in^+ \cdot out^*) \\
    link(X,Y)     & = & any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
    path(\vec{X}) & = & any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
    novalley(\vec{X}) & = & any ~ \cap \\
                  &   & !path(X_2,X_1,X_2) ~ \cap \dots \cap \\ 
                  &   & !path(X_n,X_{n-1},X_n) \\
  \end{array} \]

  \end{minipage}

  \hrulefill

  \caption{Regular Intemediate Language (RIL) syntax (left), and 
           Propane language expansions (right).}
  \label{fig:semantics}
\end{figure*}

\para{Semantics}
Give the semantics in terms of ranked paths.
Extension of regular expression semantics with the
additional constraint that we take only valid topology paths and that their are no paths with
repeated locations in the path. One tricky point is that we care about paths starting or ending at locations that are
connected to end-hosts in some way. And we want the length of the path to be a secondary tie-breaker.

\para{Propane to RIR}

TODO

\subsection{Theory}
What are the properties of this language? Ideally, a proof here about its expressiveness. We can perhaps do everything
BGP can do? We can't do shortest paths routing with BGP, but we could with OSPF though? Clearly we can only describe
policies that are stable under all possible failure scenarios (at least internally stable, could still cause) routing
loops with interactions with neighbors.

\begin{itemize}
	\item Separate prefixes so they are disjoint

	\item For each prefix, build a DFA from each of the regular path constraints
		  We do this using character classes and regular expression derivatives.
		  The accepting states are labeled with the particular preference.

	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or
		  more of the regular path constraints. We accept if we are in at least one of the accepting states
		  for one or more of the DFAs. Add a new start and end node as well.

	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution.
		  Required for soundness. Removing these makes it easier to check if things are implementable using BGP (see next point).
		  We use several heuristics to make this faster (e.g., removing edges for dominated nodes)

	\item Since our policy language can express things not implementable in BGP, we need a few checks.
		  First show some examples of what the problem is: why BGP cannot make a decision.
		  The reasons this can happen are:
		  (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
		  (2) Failures - Have to make a decision without knowing what failures have occurred. Never want to prefer one peer over another and then not get a path when one was available

	\item We can check for these with a sufficient condition (that works often and is very fast),

	\item For each router, build a preference pre-order, that defines the constraints between preferences.

	\item Finally, if we know BGP can make decision locally, then we can directly translate to local BGP configurations using
		  information about the state machines from the neighbors. In particular, we tag (and test on) community values for the
		  corresponding state and set preferences accordingly (example will be needed)

	\item Running example will be helpful here.	
\end{itemize}

\subsection{Optimizations}

\begin{itemize}
	\item For performance, the main bottleneck will probably be the minimization step. We use a number of heuristics here to make this faster.
	\item For config readability and number of route maps/communities, we avoid community tagging/matching whenever possible with a number of tricks.
\end{itemize}

### 2016-01-20 paper/compilation.tex
Finished syntax and semantics for RIR.

@@
 \label{sec:compilation}
+
+\subsection{Overview}
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{figures/pipeline}
+\caption{Compilation pipeline stages for Propane.}
+\label{fig:pipeline}
+\end{figure}
+
+In this section we briefly describe our compilation strategy for \sysname.
+Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate user-level \sysname policies into vendor-specific, device-local BGP policies.
+The first stage of the pipeline involves simple rewriting rules and substitutions from the user-level languae into the core Regular Intermediate Representation (RIR).
+Policies in RIR are checked for well-formedness (e.g., never constraining traffic that does not enter the network), before being combined with topological information to obtain Product Graph Intermediate Representation (PGIR).
+The PGIR is a data representation that compactly captures the control flow of all BGP advertisements subject to the policy and topology restrictions.
+We develop efficient algorithms that operate over the PGIR to ensure policy compliance, guarantee failure safety, avoid BGP instability, and prevent aggregation-induced black holes.
+Once the compiler determines the PGIR for the policy is safe, the compiler uses a simple translation to an abstract BGP (ABGP) representation.
+To make configurations more readable for human operators, and to reduce the size of the resulting configurations, the \sysname compiler makes several passes over ABGP form.
+Finally, vendor-specific adaptors can be added to \sysname to translate from ABGP to actual concrete configurations that go on the network devices.
+
+\subsection{Regular IR (RIR)} 
+\label{sec:rir}
+
+The high-level language presented in Section~\ref{sec:propane} is just a thin layer on top of a core, regular-expression-based language for describing preference-based path constraints.
+Regular expressions are an expressive formalism that have been studied extensively for their ability utility in describing paths through graphs~\cite{bib:todo}, and applications to networks~\cite{bib:todo}.
+We present our core Regular language in the below.
+
+% grammar
+\newcommand{\BNFALT}{\;\;|\;\;}
+\newcommand{\hdr}[2]{\flushleft \chdr{#1}{#2}}
+\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}
+
+\begin{figure*}
+  \begin{minipage}[t]{.45\linewidth}
+  \hdr{\large Syntax}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rclr}
+    \hline
+
+     pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
+     p       &::=& t \mapsto r_1 \gg \dots \gg r_m & \textit{preferences} \\
+     t       &::=& & \textit{test} \\
+         &\BNFALT& true & \textit{true} \\
+         &\BNFALT& \neg t & \textit{negation} \\
+         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
+         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
+         &\BNFALT& prefix = x & \textit{prefix test} \\
+         &\BNFALT& comm = c & \textit{community test} \\
+     r       &::=& & \textit{regular paths} \\ 
+         &\BNFALT& n & \textit{AS number} \\
+         &\BNFALT& in & \textit{internal loc} \\
+         &\BNFALT& out & \textit{external loc} \\
+         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
+         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
+         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
+         &\BNFALT& !(r) & \textit{path negation} \\
+         &\BNFALT& r^* & \textit{repetition} \\
+     l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
+     cc     &::=& agg(x, l) \BNFALT tag(c, t, l) & \textit{control constraints} \\
+  \end{array} \]
+
+  \end{minipage}
+  %
+  ~~
+  \vrule
+  ~~
+  %
+  \begin{minipage}[t]{.5\linewidth}
+  \hdr{\large Propane Expansions}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rcl}
+    \hline
+    any           & = & out^* \cdot in^+ \cdot out^* \\
+    internal      & = & in^+ \\
+    external      & = & out^+ \\
+    only(X)       & = & any \cap X^* \\
+    never(X)      & = & any \cap (!X)^* \\
+    through(X)    & = & out^* \cdot in^* \cdot X \cdot in^* \cdot out^* \\
+    after(X)      & = & out^* \cdot (X \cap out) \cdot out^* \cdot in^+ \cdot out^* \\
+    before(X)     & = & out^* \cdot in^+ \cdot out^* \cdot (X \cap out) \cdot out^* \\
+    end(X)        & = & any \cap (\Sigma^* \cdot X) \\
+    start(X)      & = & any \cap (X \cdot \Sigma^*) \\
+    exit(X)       & = & (out^* \cdot in^* \cdot (X \cap in) \cdot out \cdot out^*) \cup \\
+                  &        & (out^* \cdot in^+ \cdot (X \cap out) \cdot out^*) \\
+    enter(X)      & = & (out^* \cdot out \cdot (X \cap in) \cdot in^* \cdot out^*) \cup \\
+                  &        & (out^* \cdot (X \cap out) \cdot in^+ \cdot out^*) \\
+    link(X,Y)     & = & any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
+    path(\vec{X}) & = & any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
+    novalley(\vec{X}) & = & any ~ \cap \\
+                  &   & !path(X_2,X_1,X_2) ~ \cap \dots \cap \\ 
+                  &   & !path(X_n,X_{n-1},X_n) \\
+  \end{array} \]
+
+  \end{minipage}
+
+  \hrulefill
+
+  \caption{Regular Intemediate Language (RIL) syntax (left), and 
+           Propane language expansions (right).}
+  \label{fig:rir-syntax}
+\end{figure*}
+
+\para{Syntax}
+
+The syntax for the RIR is shown in Figure~\ref{fig:rir-syntax}.
+A policy consists of one or more constraints, each of which consists of a test on the type of route, and a corresponding set of preferred regular paths.
+Regular paths are simply regular expressions where the base locations are AS numbers.
+Special \textit{in} and \textit{out} symbols are used to refer to any internal or external location respectively.
+For example, the constraint 
+$$prefix=74.125.28.0/24 \mapsto (200 \cdot in \cdot in^*) \gg (100 \cdot in \cdot in^*)$$
+describes a more-preferred set of paths for traffic announced by a prefixes no less specific than $74.125.28.0/24$, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same.
+Tests over route types are allowed to be used with standard boolean connectives, and they can refer to both prefixes and community values (which are often important when interoperating with existing ASes).
+
+\sysname also supports constraints purely on the control-plane behavior of the BGP routing protocol.
+Thing like prefix aggregation, which should not affect routing behavior, is an important optimization to reduce routing table size and churn.
+Aggregation, for example from internal locations and external locations, is specified using the same regular syntax as before:
+$$agg(128.17.0.0/16, in \rightarrow out)$$
+where the expression $in \rightarrow out$ refers to control messages flowing from any internal location to any external location.
+
+We list the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, however our implementation also supports other constraints such as limiting the maximum number of routes, or enabling BGP multipath.
+
+\para{Semantics}
+
+The semantics of RIR can be thought of in terms of ranked paths.
+Each preference-based regular path constraint (of the form $r_1 \gg \dots \gg r_j$) maps to a set of concrete paths in the network that match one of $r_i$.
+We denote a network path as a string of ASes of the form: $n_1 n_2 \dots n_k$, and we say regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$ and $p$ is a topologically-valid path.
+We denote the length of a path $p$ as $\abs{p}$.
+A path $p$ will have a rank:
+$$(\min_i \set{ p \in \mathcal{L}(r_i) }, \abs{p})$$
+where the rank is lexicographically ordered according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the length of the path.
+A lower rank indicates a \emph{more} preferred path.
+The desired semantics is to allow traffic to be sent along any of the most preferred paths for any pair of starting and ending locations that appear in some valid path.
+
+The set of ranked paths depends on which paths are valid given the topology, and thus when failures occur, so do the most preferred routes.
+It is the job of the \sysname compiler to ensure that generated configurations for a policy always achieve the most preferred path possible given the failures in the topology, and it must do so using purely distributed mechanisms.
+
+\para{Propane to RIR}
+
+TODO
+
+\subsection{Theory}
+What are the properties of this language? Ideally, a proof here about its expressiveness. We can perhaps do everything
+BGP can do? We can't do shortest paths routing with BGP, but we could with OSPF though? Clearly we can only describe
+policies that are stable under all possible failure scenarios (at least internally stable, could still cause) routing
+loops with interactions with neighbors.
 

### 2016-01-21 paper/compilation.tex
Adding compilation example to paper / implementation tests.

@@
 
-TODO
+The main differences between \sysname the regular language are: (1) \sysname allows the programmer to specify constraints separately, and combine them together modularly, (2) \sysname provides high-level names that abstract sets of routes, and (3) \sysname allows the preference operator to appear in more locations.
+The translation from \sysname to RIR is based on a set of simple rewriting rules.
 
-\subsection{Theory}
-What are the properties of this language? Ideally, a proof here about its expressiveness. We can perhaps do everything
-BGP can do? We can't do shortest paths routing with BGP, but we could with OSPF though? Clearly we can only describe
-policies that are stable under all possible failure scenarios (at least internally stable, could still cause) routing
-loops with interactions with neighbors.
+One of the main constraints when translating to RIR is to ensure that all specified routes are well-formed.
+In particular, each regular path constraint $r$ must satisfy $r \subseteq out^* \cdot in^+ \cdot out^*$.
+This ensures that one can only ever talk about controlling traffic that goes through the user's network at some point.
+
+The first step is to merge separate constraints.
+This is accomplished by simply taking the cross product of per-prefix constraints, where logical conjunction ($a \wedge b$) is replaced by intersection on regular constraints ($a \cap b$), logical disjunction is replaced by union, and logical negation ($\neg a$) is replaced by ($any \cap !(a)$).
+%
+For example, in the data center configuration from Section~\ref{sec:propane}, combining the \textit{Routing} and \textit{Ownership} constraints would result in the following RIR configuration:
+
+\begin{lstlisting}[mathescape=true]
+$\path{p_{g1}}{any \cap end(A)}$
+$\path{p_{g2}}{any \cap end(B)}$
+$\path{p_{l1}}{\neg enter(out) \cap end(E)}$
+$\path{p_{l2}}{\neg enter(out) \cap end(F)}$
+$\path{true}{exit(out)}$
+\end{lstlisting}
+
+The next step is to rewrite the high-level constraints such as \textit{enter} and \textit{exit} according to the equivalences listed in Figure~\ref{fig:rir-syntax}.
+Since preferences can only occur at the top level for RIR, the final step is to lift the preferences that occur in the regular expression.
+For example, the regular expression $a \cdot (b \gg c) \cdot d$ is lifted to $(a \cdot b \cdot d) \gg (a \cdot c \cdot d)$.
+In general, we employ the follwing:
+%
+$$x \odot (y_1 \gg \dots \gg y_n) = x \odot y_1 \gg \dots \gg x \odot y_n$$
+%
+where $\odot$ stands for an arbitrary regular binary operator. Preferences nested under a unary operator, \textit{star} or \textit{negation}, are invalid policies.
+
+\subsection{Product Graph IR}
+
+\newcommand{\state}[4]{\node[state,#3](#1)[#4]{#2};}
+\newcommand{\transition}[4]{\path[->] (#1) edge [#4] node {#3} (#2);}
+
+\begin{figure*}
+  \begin{minipage}[t]{.5\linewidth}
+  \hdr{\large Topology}{}
+  \vspace*{-1\baselineskip}
+
+  \includegraphics[width=.8\columnwidth]{figures/topology}
+
+  \hdr{\large Policy Automata}{}
+  \vspace*{1\baselineskip}
+
+  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.6cm]
+    \state{0}{$0$}{              }{}
+    \state{1}{$1$}{right of=0}{}
+    \state{2}{$2$}{right of=1}{}
+    \state{3}{$3$}{right of=2}{}
+    \state{4}{$4$}{right of=3}{}
+    \state{5}{$5$}{right of=4}{accepting}
+    \transition{0}{1}{out}{}
+    \transition{1}{2}{D}{}
+    \transition{2}{3}{C}{}
+    \transition{3}{4}{A}{}
+    \transition{4}{5}{W}{}
+  \end{tikzpicture}
+
+  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.6cm]
+    \state{0}{$0$}{              }{}
+    \state{1}{$1$}{right of=0}{}
+    \state{2}{$2$}{right of=1}{}
+    \state{3}{$3$}{right of=2}{}
+    \state{4}{$5$}{right of=3}{accepting}
+    \transition{0}{1}{out}{}
+    \transition{1}{2}{in}{}
+    \transition{2}{2}{ACDE}{loop above}
+    \transition{2}{3}{B}{}
+    \transition{3}{3}{B}{loop above}
+    \transition{3}{2}{ACDE}{bend left}
+    \transition{3}{4}{W}{}
+  \end{tikzpicture}
+
+  \end{minipage}
+  %
+  ~~
+  ~~
+  %
+  \begin{minipage}[t]{.5\linewidth}
+  \hdr{\large Product Graph}{}
+  \vspace*{-1\baselineskip}
+  %
+
+  \includegraphics[width=.8\columnwidth]{figures/productgraph}
+
+  \end{minipage}
+
+  \hrulefill
+
+  \caption{Example Product Graph construction.}
+  \label{fig:example-compilation}
+\end{figure*}
+
+Now that the user policy exists in a simplified form, we must take the topology into consideration.
+In particular, we are interested in a compact representation that describes all the possible ways BGP route advertisements can flow through the network subject to the policy and topology constraints.
+To this end, we use a Product Graph Intermediate Representation (PGIR) to capture these dependencies.
+The Product graph can be thought of as the intersection of each of the regular automata corresponding to the RIR path preferences, and the topology.
+Finding paths through a graph subject to regular constraints has been studied extensively in the database literature~\ref{bib:todo}, and has been applied to networks in the past~\ref{bib:todo}.
+
+\para{Formal definition}
+
+The translated user policy into RIR is of the form $r_1 \gg \dots \gg r_j$.
+While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., router advertisements flowing in the opposite direction).
+To capture this idea, for each regular expression $r_i$, we construct a deterministic finite state machine on the reversed regular expression.
+Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
+The alphabet $\Sigma$ consists of all internal and external ASes, $Q_i$ is a set of states, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ the state transition function.
+
+The topology is modelled as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon 2^{V \times V}$.
+
+\todo{use different symbols here}
+
+The combined product graph is a tuple: ($V'$, $E'$, $s$, $A$) with 
+vertices $V' \colon V \times 2^{Q_1 \times \dots \times Q_j}$, 
+edges $E' \colon 2^{V' \times V'}$, 
+a unique starting vertex $s$, 
+and an preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the graph to the set preferences for which the corresponding automata are accepting in state $Q_i$
+
+\para{Construction}
+
+Intuitively product graph tracks which states of each automaton the policy is in as traffic moves between different topology locations.
+
+\todo{work out the exact details here}
 

### 2016-01-21 paper/compilation.tex
Adding to compilation section.

@@
     \state{3}{$3$}{right of=2}{}
-    \state{4}{$5$}{right of=3}{accepting}
+    \state{4}{$4$}{right of=3}{accepting}
     \transition{0}{1}{out}{}
@@
 
-\para{Construction}
+\para{Example}
 
@@
 
-\todo{work out the exact details here}
+Consider the topology shown in Figure~\ref{fig:example-compilation}.
+Suppose we want to set up a primary route from W that enters the network from $A$, and utilizes the A -- C and C -- D links.
+We also would like a backup route that utilizes enters from node $B$, and utilizes the B -- C link, but is otherwise unconstrained.
+For the sake of simplicity, we will assume that the route can end in either $X$, $Y$, or $Z$.
+The RIR for the policy is:
+%
+$$(W \cdot A \cdot C \cdot D \cdot out) \gg (W \cdot B \cdot in^* \cdot out)$$
+%
+Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference.
+Since we are interested in the flow of control messages, the automata match backwards.
+Figure~\ref{fig:example-compilation} shows the product graph obtained from intersecting the topology and policy automata.
+Every path in the product graph corresponds to a concrete path in the topology.
+In particular, every path through the product graph that ends at a node with an accepting preference is a valid topological path that satisfies the policy constraints and results in a particular preferenced path.
+%
+For example, the path $X D C A W$ is a valid path in the topology that BGP route advertisements might take, which would lead to obtaining the most prefered preference.
+BGP control messages can start from peer X, which would match the $out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
+This is reflected in the product graph by the node with state $(1,1) X$.
+From here, if X were to advertise this route to D, it would result in the path $D X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
+Since node $(5,-) W$ is in an accepting state for the first automata, it indicates this path has preference 1.
+
+\todo{explain drop states}
+\todo{preferences are reversed in picture}
+
+\para{Minimization}
+
+TODO
 

### 2016-01-21 paper/compilation.tex
more edits

@@
 
-TODO
+Although every path through the product graph is a valid path in the topology, we typically do not want to consider loops when configuring a network.
+In particular, BGP's loop prevention mechanism (where an AS rejects any route for which it is already in the AS path), means that loops should never occur \footnote{Misconfigured aggregation can still lead to loops in some cases}.
+When analyzing the user policy for correctness and failure safety, it is often useful to avoid considering possibilities that cannot
 

### 2016-01-21 paper/compilation.tex
added minimization subsection

--- 2016-01-21 paper/compilation.tex
@@
   %
-
   \includegraphics[width=.8\columnwidth]{figures/productgraph}
-
   \end{minipage}
@@
 
-\para{Example}
+\para{From RIR To PGIR}
 
@@
 
-TODO
+Although every path through the product graph is a valid path in the topology, we do not want to consider loops when configuring the network.
+In particular, BGP's loop prevention mechanism (where an AS rejects any route for which it is already in the AS path), means that loops should never occur.\footnote{Misconfigured aggregation can still lead to loops in BGP}
+%
+However, the product graph may contain many paths that form loops in the topology.
+For example, in Figure~\ref{fig:example-compilation}, the path $W A C B W$ is a valid path that BGP route advertisements might take through the topology, leading to a path that satisfies the preference 1 policy, but which contains a loop.
+%
+Since we are primarily concerned with guaranteeing user policy correctness and safety with respect to network failures, it is useful to avoid considering possibilities that are not possible due to loops.
+For example, if we can safely remove an edge from the product graph, then we don't have to consider the case that the edge has failed.
+
+We can safely remove any node or edge from the product graph so long as it never appears on any \emph{simple} path from the \textit{start} node to some node with an accepting preference.
+For example, node $(1,1) W$ in Figure~\ref{fig:example-compilation} is never on a simple path to an accepting preference since both end at location $W$.
+%
+Although fully minimizing the product graph is an NP-complete problem, we find that a simple and efficient algorithm based on graph dominators achieves largely the same effect, without preventing compilation of most policies in practice.
+
+A node $x$ dominates node $y$ if $x$ appears on every path leading to $y$ from the $start$ node.
+Many algorithms for finding graph dominators efficiently exist~\ref{bib:todo}.
+To minimize the product graph, we compute the dominator set for each node in both the product graph $G$, and the reversed product graph $G^R$ (with a source node attached to each accepting state).
+The following rules us to efficiently simplify the product graph.
+
+\begin{itemize}
+  \item Remove nodes that never reach an accepting state
+  \item Remove nodes not reachable from the $start$ node
+  \item Remove any node $x$ such that $x$ is dominated by $y$ in $G$ or $G^R$, and $loc(x) = loc(y)$
+  \item Remove any edge from $x$ to $y$ in $G$ or $G^R$ if there is some $z$ dominated by $y$ such that $loc(x) = loc(z)$
+\end{itemize}
+
+Repeated application of the 4 above rules leads to removing the colored nodes and dashed lines in Figure~\ref{fig:example-compilation}.
+
+\para{Failure Safety}
 

### 2016-01-21 paper/introduction.tex
starting intro; not done yet

@@
 \label{sec:introduction}
+
+It is well-known that network configuration is hard and error prone~\cite{x,y,z}; many studies of network incidents point to configuration errors as the leading cause.
+%
+One reason is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.
+%
+
+Another, more fundamental reason is the semantic mismatch between intended policies and configuring individual devices.
+%
+Many policies are network-wide (e.g., such as prefer certain external neighbors over others, never announce certain destination prefixes externally, use a certain path only if another fails), but configurations describe the behavior of individual devices.
+%
+Operators must manually decompose network-wide policy into device-level behaviors, such that their interactions produce the desired policy.
+%
+This decomposition is not always straightforward and ensuring policy-compliance is hard, especially in the face of failures.
+Certain decompositions that work correctly in the absence of failures, violate policies when failures occur.
+%
+As a result, many configuration errors manifest only during failures~\cite{batfish}.
+
+To simplify network configuration, the practitioner community is adopting a template-based approach~\cite{x,y}.
+While templates help with the low-level nature of configuration languages, they too suffer from the semantic mismatch between network policies and device-level configuration (\S\ref{sec:motivation}).
+
+Software-defined networking (SDN) was, in part, the research community's response to the difficulty of maintaining policy compliance in the face of this semantic mismatch~\cite{xx}.
+It completely eliminates distributed control planes.
+Instead of devices computing their forwarding behavior by interacting with each other, they are told by a centralized controller exactly how to forward packets.
+The controller is responsible for ensuring policy compliance at all times, including when failures occur.
+To program centralized control planes, researchers have developed increasingly sophisticated languages that let operators directly express network policies~\cite{x,y,z}.
+
+However, SDN does not help the vast majority of networks in the world, which  still operate a distributed control plane.
+Many of these networks will continue to operate a distributed control plane for the foreseeable future, due to the difficulty of migration, scaling challenges of centralized control, or the inherent robustness to failures of distributed control planes.
+Centralized control planes need careful design to be robust to failures---one must ensure that devices can communicate with the controller at all times, even under arbitrary combinations of failure.
+
+In this paper, we ask if distributed control planes can be centrally programmed.
+Operators should be able to directly express network-wide policies, which are automatically decomposed into individual device configurations in a way that ensures policy-compliance under all possible failures.
+If successful, this approach would combine the ease of programming of centralized control planes and robustness to failures of distributed control planes.
+
+\todo{new intro is not complete}
+
+\todo{OLD TEXT IS BELOW}
 

### 2016-01-21 paper/compilation.tex

@@
 
+To implement backups in routing, BGP uses local preferences on a per-device basis.
+However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult, particularly in the presence of failures.
+For example, imagine an extremely simple policy for the topology in Figure~\ref{fig:example-compilation}, which says to prefer $WACD$ over $WBCE$:
+%
+$$(W \cdot A \cdot C \cdot D) \gg (W \cdot B \cdot C \cdot E)$$
+%
+How could such a policy be implemented in BGP?
+Suppose we simply set the local preference at router $C$ to prefer $D$ over $E$.
+However, now if the A -- C link fails, then suddenly $C$ has made the wrong decision and can not get either the primary or backup route specified, despite the fact that $W \cdot B \cdot C \cdot E$ route is available.
+
+In particular, any time a router must make a decision locally between several route options, there is the possibility that it might choose incorrectly and regret its decision.
+The product graph representation captures this notion of choice precisely.
+For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the product graph, possible receiving route advertisements from $Y$ or $X$.
+However, regardless of where
+
+\para{Notes}
+
 \begin{itemize}

### 2016-01-21 paper/introduction.tex
minor tweaks; technical work content missing

--- 2016-01-14 paper/introduction.tex
@@
 \label{sec:introduction}
+
+It is well-known that network configuration is hard and error prone~\cite{x,y,z}; many studies of network incidents point to configuration errors as the leading cause.
+%
+One reason is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.
+%
+
+Another, more fundamental reason is the semantic mismatch between intended policies and configuring individual devices.
+%
+Many policies are network-wide (e.g., such as prefer certain external neighbors over others, never announce certain destination prefixes externally, use a certain path only if another fails), but configurations describe the behavior of individual devices.
+%
+Operators must manually decompose network-wide policy into device-level behaviors, such that their interactions produce the desired policy.
+%
+Ensuring policy-compliance through this manual decomposition is hard and error-prone, especially in the face of failures.
+Certain decompositions that work correctly otherwise, violate policies when failures occur.
+%
+As a result, many configuration errors manifest only during failures~\cite{batfish}.
+
+To reduce configuration errors, the practitioner community is adopting a template-based approach~\cite{x,y}, in which common configuration constructs are captured as parameterized templates.
+ While templates help with the low-level nature of configuration languages, they do not bridge the semantic divide between network policies and device-level configuration (\S\ref{sec:motivation}).
+
+Software-defined networking (SDN) was, in part, the research community's response to the difficulty of maintaining policy compliance through distributed interaction of individual devices~\cite{xx}.
+It eliminates distributed control planes altogether.
+Instead of devices computing  forwarding tables through mutual interactions, they are told by a centralized controller exactly how to forward packets.
+The controller is responsible for ensuring policy compliance at all times.
+To program centralized control planes, researchers have developed increasingly sophisticated languages that let operators directly express network policies~\cite{x,y,z} that are then translated to forwarding tables at runtime.
+
+However, SDN does not help the vast majority of networks in the world, which  still operate a distributed control plane.
+For the foreseeable future, many of these networks will continue to operate a distributed control plane, due to the difficulty of migration or the challenges that centralized control planes face in terms of scaling and failure robustness.
+%, scaling challenges of centralized control, or the inherent robustness of distributed control planes to failures.
+%It is difficult to scale centralized control planes both 
+Centralized control planes need careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure~\cite{x,y,z}.\footnote{For this challenge, researchers are exploring multi-controller networks, with interacting controllers, thus bringing back distributed control planes~\cite{x,y,z} and their current programming difficulties.}
+
+In this paper, we ask if it is possible to centrally program distributed control planes.
+Operators should be able to directly express network-wide policies, which are automatically decomposed into individual device configurations.
+The resulting forwarding behavior, which emerges through device interactions, must be policy-compliant even under failures.
+If successful, this approach would combine easy programmability of centralized control planes and failure robustness of distributed control planes.
+
+Through our system, called \sysname, we demonstrate the feasibility of centrally programming distributed control planes.
+We focus on BGP because it is a common and highly flexible way to implement such control planes.
+
+\todo{new intro is not complete}
+
+\todo{OLD TEXT IS BELOW}
 

### 2016-01-21 paper/introduction.tex
tweaks to the leading paras

@@
 
-However, SDN does not help the vast majority of networks in the world, which  still operate a distributed control plane.
-For the foreseeable future, many of these networks will continue to operate a distributed control plane, due to the difficulty of migration or the challenges that centralized control planes face in terms of scaling and failure robustness.
-%, scaling challenges of centralized control, or the inherent robustness of distributed control planes to failures.
-%It is difficult to scale centralized control planes both 
-Centralized control planes need careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure~\cite{x,y,z}.\footnote{For this challenge, researchers are exploring multi-controller networks, with interacting controllers, thus bringing back distributed control planes~\cite{x,y,z} and their current programming difficulties.}
+Centralized control planes, however, are not a panacea. 
+%They face significant challenges related to scaling and failure robustness. 
+They require careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure~\cite{x,y,z}.
+For this challenge, researchers are exploring multi-controller networks, with interacting controllers, thus bringing back distributed control planes~\cite{x,y,z} and their current programming difficulties.
 
@@
 Operators should be able to directly express network-wide policies, which are automatically decomposed into individual device configurations.
-The resulting forwarding behavior, which emerges through device interactions, must be policy-compliant even under failures.
+The resulting forwarding behavior, which emerges through device interactions, must be policy-compliant under all possible failures.
 If successful, this approach would combine easy programmability of centralized control planes and failure robustness of distributed control planes. 
+%
+More pragmatically, it would help many networks that, for the foreseeable future, will continue to use a distributed control plane, due to the difficulty of migrating to SDN or the inherent scalability and failure-robustness of distributed control.
 

### 2016-01-22 paper/introduction.tex

@@
 Through our system, called \sysname, we demonstrate the feasibility of centrally programming distributed control planes.
-We focus on BGP because it is a common and highly flexible way to implement such control planes.
+We focus on BGP, a common and highly flexible way to implement distributed control planes, and show how to automatically generate router BGP configurations from a program that directly expresses network policies.
 

### 2016-01-22 paper/compilation.tex
Adding more to failures section.

@@
 Suppose we simply set the local preference at router $C$ to prefer $D$ over $E$.
-However, now if the A -- C link fails, then suddenly $C$ has made the wrong decision and can not get either the primary or backup route specified, despite the fact that $W \cdot B \cdot C \cdot E$ route is available.
+However, now if the A -- C link fails, then suddenly $C$ has made the wrong decision and can not get either the primary or backup route specified, despite the fact that the $W \cdot B \cdot C \cdot E$ path is available.
 
-In particular, any time a router must make a decision locally between several route options, there is the possibility that it might choose incorrectly and regret its decision.
+At a first cut, any time a router must make a decision locally between several route options, there is the possibility that it might choose incorrectly.
 The product graph representation captures this notion of choice precisely.
-For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the product graph, possible receiving route advertisements from $Y$ or $X$.
-However, regardless of where
+For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the product graph, possibly receiving route advertisements from $Y$ or $X$.
+However, regardless of whether $D$ chooses a route from $X$ or $Y$, the set of paths allowed by the policy after going through $D$ will be the same in either case.
+This remains true despite any failures that might have occurred in the network.
+Thus $D$ can safely prefer $X$ and $Y$ equally.
+
+The more challenging case is when a topology location occurs in mutliple contexts in the product graph.
+For example, the topology node $C$ can receive an advertisement from $E$ and later achieve the backup path, or it can receive an advertisement from its neighbor $D$ and later achieve either the primary or backup path.
+Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $C$?
+The important observation is that, if $C$ prefers $D$, then it will always achieve at least as good a path as if it had choosen $E$.
+For example, suppose $C$ chooses a route from $D$, but cannot achieve its primary path because the $A$ -- $W$ link has failed.
+In this case, the advertisement from $C$ will still be sent along towards the ultimate backup location $W$.
+Since the $(-,2) C$ and $(3,2) C$ nodes in the product graph share the same next hops in either case, no possible failure will prevent a route advertisment from reaching $(-,4) W$ that wouldn't have otherwise prevented it if $C$ had choosen $E$.
+
+In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard.
+A simple enumeration of failures is intractable.
+Instead, we adopt a conservative analysis based on the product graph representation, and the previous observations, which runs efficiently in practice.
+The high-level idea is to order each node in the product graph according to an \textit{can prefer} relation.
+For example, node $(3,2) C$ can be preferred to node $(-,2) C$, but not the other way around.
+Intuitively, a node $N_1$ can be preferred to another node $N_2$ when, for each preference $N_2$ might achieve, there is a better preference that $N_1$ will achieve regardless of failures.
+Formally this means that $N_1$ can be preferred to $N_2$ when:
+%
+$$\forall i, \exists j, j \leq i \wedge protect(G_j, N_1, G_i, N_2)$$
+%
+The algorithm listed in Figure~\ref{fig:algorithm} defines what it means for one node to \textit{protect} against the failures of another.
+Intuitively, the algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
+Thus $N_1$ any paths leading from $N_2$ will have an equivalent path from $N_1$.
+
+\makeatletter
+\def\BState{\State\hskip-\ALG@thistlm}
+\makeatother
+
+\begin{algorithm}
+\caption{Failure Protection}\label{euclid}
+\begin{algorithmic}[1]
+\Procedure{Protect($G_1$, $N_1$, $G_2$, $N_2$)}{}
+\If {$N_1.loc \neq N_2.loc$} \Return false
+\EndIf
+\State $q \gets Queue()$
+\State $q.Push (N_1, N_2)$
+\While {\textit{not} $q.Empty()$}
+\State TODO
+\State TODO
+\EndWhile
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
+TODO: how simple paths factor in
+
+TODO:
 

### 2016-01-22 paper/compilation.tex
more edits

@@
 The product graph representation captures this notion of choice precisely.
-For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the product graph, possibly receiving route advertisements from $Y$ or $X$.
+For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the product graph, possibly receiving route advertisements from $X$ or $Y$.
 However, regardless of whether $D$ chooses a route from $X$ or $Y$, the set of paths allowed by the policy after going through $D$ will be the same in either case.
@@
 For example, the topology node $C$ can receive an advertisement from $E$ and later achieve the backup path, or it can receive an advertisement from its neighbor $D$ and later achieve either the primary or backup path.
-Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $C$?
+Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $E$?
 The important observation is that, if $C$ prefers $D$, then it will always achieve at least as good a path as if it had choosen $E$.
@@
 In this case, the advertisement from $C$ will still be sent along towards the ultimate backup location $W$.
-Since the $(-,2) C$ and $(3,2) C$ nodes in the product graph share the same next hops in either case, no possible failure will prevent a route advertisment from reaching $(-,4) W$ that wouldn't have otherwise prevented it if $C$ had choosen $E$.
+Since the $(3,2) C$ node has the same one-step and two-step next hops as node $(-,2) C$ in the product graph, no possible failure will prevent a route advertisment from reaching $(-,4) W$ that wouldn't have otherwise prevented it if $C$ had choosen $E$.
 
@@
 A simple enumeration of failures is intractable.
-Instead, we adopt a conservative analysis based on the product graph representation, and the previous observations, which runs efficiently in practice.
-The high-level idea is to order each node in the product graph according to an \textit{can prefer} relation.
+Instead, we adopt a conservative analysis based on the product graph representation and the previous observations, which runs efficiently in practice.
+The high-level idea is to order each node in the product graph according to a \textit{can prefer} relation.
 For example, node $(3,2) C$ can be preferred to node $(-,2) C$, but not the other way around.
@@
 %
-The algorithm listed in Figure~\ref{fig:algorithm} defines what it means for one node to \textit{protect} against the failures of another.
+where the \textit{protect} predicate means that, from $N_1$ on the product graph restricted to preferences $j$ or better, there are at least as many paths as from $N_2$ restricted to $G_i$
+
+The algorithm listed in Figure~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another.
 Intuitively, the algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
@@
 
-\makeatletter
-\def\BState{\State\hskip-\ALG@thistlm}
-\makeatother
-
-\begin{algorithm}
-\caption{Failure Protection}\label{euclid}
+\begin{algorithm}[t!]
+\caption{Failure Protection}
+\label{alg:failures}
 \begin{algorithmic}[1]
@@
   \State $q \gets Queue()$
-\State $q.Push (N_1, N_2)$
-\While {\textit{not} $q.Empty()$}
-\State TODO
-\State TODO
+  \State $q.Enqueue (N_1, N_2)$
+  \While {$!q.Empty()$}
+    \State $(n_1,n_2) \gets q.Dequeue()$
+    \For {$x$ in $adj(G_2, n_2)$}
+      \If {exists a $y$ where $y$ shadows $x$} 
+        \If {$(x,y)$ not marked}
+          \State {mark $(x,y)$ as seen}
+          \State $q.Enqueue(x,y)$
+        \EndIf
+      \Else { \Return $false$}
+      \EndIf
+    \EndFor
   \EndWhile
+  \Return true
   \EndProcedure
@@
 \end{algorithm}
-
-TODO: how simple paths factor in
-
-TODO:
 

### 2016-01-22 paper/compilation.tex
starting eval, expressiveness, aggregation parts

@@
 
-The algorithm listed in Figure~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another.
-Intuitively, the algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
-Thus $N_1$ any paths leading from $N_2$ will have an equivalent path from $N_1$.
-
 \begin{algorithm}[t!]
@@
 
-\para{Notes}
+The algorithm listed in Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another.
+Intuitively, the algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
+Thus $N_1$ any paths leading from $N_2$ will have an equivalent path from $N_1$.
+Algorithm~\ref{alg:failures} works because each node in the product graph can have at most one outgoing neighbor with the same topological location, so the next hop neighbors can be checked without backtracking.
+The algorithm terminates since the number of related states $(x,y)$ that can be expolored is finite.
 
-\begin{itemize}
-	\item Separate prefixes so they are disjoint
+Local preferences are obtained by, for each router in the topology, sorting the corresponding nodes in the product graph according to \textit{can prefer} relation.
+If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
 
-	\item For each prefix, build a DFA from each of the regular path constraints
-		  We do this using character classes and regular expression derivatives.
-		  The accepting states are labeled with the particular preference.
+\para{Avoiding Simple Paths}
 
-	\item Build the constraint graph, which gives us valid paths through the network that satisfy one or
-		  more of the regular path constraints. We accept if we are in at least one of the accepting states
-		  for one or more of the DFAs. Add a new start and end node as well.
+The checks for failure safety described previously overlook one critical point: even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$.
+To avoid this situation, we simply conservatively check that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the product graph (i.e., nodes reachable from $x$ in $G_j^R$).
+It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
 
-	\item Minimize the constraint graph by removing nodes and edges that never contribute to a solution.
-		  Required for soundness. Removing these makes it easier to check if things are implementable using BGP (see next point).
-		  We use several heuristics to make this faster (e.g., removing edges for dominated nodes)
+\para{Aggregation-Induced Black Holes}
 
-	\item Since our policy language can express things not implementable in BGP, we need a few checks.
-		  First show some examples of what the problem is: why BGP cannot make a decision.
-		  The reasons this can happen are:
-		  (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
-		  (2) Failures - Have to make a decision without knowing what failures have occurred. Never want to prefer one peer over another and then not get a path when one was available
+As was demonstrated in Example 2 of Section~\ref{sec:motivation}, the use of aggregation in BGP can lead to black-holing traffic when failures occur.
+Deciding whether this can happen required knowledge of the routing policy and not just the topology.
+For example, a policy might require all traffic for a particular prefix going through a router where an aggregate is advertised to go over a single link, even if there are several available in the toplogy.
+However, the PGIR captures the both the policy and the topology information together.
 
-	\item We can check for these with a sufficient condition (that works often and is very fast),
+We can frame the aggregation problem as a problem of connectivity in the PGIR.
+More specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures that would disconnect the prefix from its more specific aggregate.
 
-	\item For each router, build a preference pre-order, that defines the constraints between preferences.
+\todo{explain in detail}
 
-	\item Finally, if we know BGP can make decision locally, then we can directly translate to local BGP configurations using
-		  information about the state machines from the neighbors. In particular, we tag (and test on) community values for the
-		  corresponding state and set preferences accordingly (example will be needed)
+\subsection{Abstract BGP}
 
-	\item Running example will be helpful here.	
-\end{itemize}
+The final stages of compilation consist in translating policies from PGIR to a simple, vendor-neutral abstraction of BGP (ABGP), and then translating from ABGP to actual device configurations.
 
-\subsection{Optimizations}
+Having found a total ordering on node preferences in the product graph from the failure safety analysis, the translation to ABGP becomes very simple.
+The idea is to encode the state of the automaton using BGP community values.
+Each router will match based on its peer and a community value corresponding to the state of the product graph, and then update the state before exporting to the neighbors permitted according to the product graph.
+For example, router $A$ from the example in Figure~\ref{fig:example-compilation} will allow an advertisement from its peer $C$ with a community value for state $(3,2)$ (and deny anything else).
+If it sees such an advertisement, it will remove the old community value, and add a new community value for state $(4,2)$ before exporting the route to its neighbor $W$.
 
-\begin{itemize}
-	\item For performance, the main bottleneck will probably be the minimization step. We use a number of heuristics here to make this faster.
-	\item For config readability and number of route maps/communities, we avoid community tagging/matching whenever possible with a number of tricks.
-\end{itemize}
+To ensure preferred paths are always obtained, for each router $r$, the compiler will simply set a higher local preference for neighbors of a more-preferred node for $r$ in the product graph.
+For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
+
+Since the compiler is only able to control community tagging for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
+Instead, it simply translates matches from external ASes into a BGP regular expression filter.
+For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$ and prefer them equally.
+In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
+
+Finally, in our example, the external AS $W$ would need to prefer our internal router $A$ over $B$.
+In general, it is not possible to control traffic entering the network beyond certain special cases.
+In this example however, the BGP MED attribute can influence $W$ to prefer $A$ over $B$ since the preference is for a single external peer, and the BGP no-export community can ensure that no other AS beyond $W$ can send us traffic.
+The compiler can perform a simple analysis to determine when it can utilize various BGP special attributes to ensure traffic enters the network in a particular way.
+Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
+Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., by having a more general aggregate on a backup preference).

### 2016-01-22 paper/evaluation.tex
starting eval, expressiveness, aggregation parts

@@
 \section{Evaluation}
+
+We have written a prototype compiler for \sysname that is implemented in roughly 5000 lines of F\# code.
+The compiler includes command-line flags for enabling or disabling the use of BGP MED, AS path prepending, the commonly used no-export community, as well as for ensuring k-failure safety for user-sepcified aggregates.
+The compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct automata for large alphabets efficiently.
+The compiler uses the algorithm for computing graph dominators described in~\ref{bib:todo}.
+When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the ``can prefer'' relation.
+\todo{this needs work}
+
+We have evaluated our compiler by translating and compiling real-world network configurations for data centers and a core backbone network into \sysname.
+We evaluate our compiler by measuring compilation times for these policies across topologies of different sizes.
+
+\para{Notes}
+
+\begin{itemize}
+
+  \item Since our policy language can express things not implementable in BGP, we need a few checks.
+      First show some examples of what the problem is: why BGP cannot make a decision.
+      The reasons this can happen are:
+      (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
+      (2) Failures - Have to make a decision without knowing what failures have occurred. Never want to prefer one peer over another and then not get a path when one was available
+\end{itemize}
+
+\subsection{Optimizations}
+
+\begin{itemize}
+  \item For config readability and number of route maps/communities, we avoid community tagging/matching whenever possible with a number of tricks.
+\end{itemize}
 

### 2016-01-22 paper/compilation.tex
Adding abstract.

@@
 We can frame the aggregation problem as a problem of connectivity in the PGIR.
-More specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures that would disconnect the prefix from its more specific aggregate.
+More specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures that would disconnect where the prefix originates from where its more specific aggregate is located.
+The difficulty lies in the fact that the same links in the topology can appear in multiples places in the PGIR.
+We adopt the following simple strategy to lower bound the number of failures:
 
-\todo{explain in detail}
+\begin{enumerate}
+	\item Pick a random path through the product graph from start to end.
+	\item Remove all edges in the product graph corresponding to the set of topological edges choosen.
+	\item Repeat until no path exists.
+\end{enumerate}
+
+Since each path through the PGIR will result in a new edge-disjoint path through the topology (since we have removed all already used edges), and since the number of edge-disjoint paths through the topology is no more than the min-cut.
+\todo{clarify this}
 

### 2016-01-22 paper/expressiveness.tex
Adding abstract.

\para{Expressiveness}

\todo{Do we need all of this}

### 2016-01-22 paper/compilation.tex
Adding compiled policy figures.

@@
 
-\para{Aggregation-Induced Black Holes}
+\subsection{Abstract BGP}
 
-As was demonstrated in Example 2 of Section~\ref{sec:motivation}, the use of aggregation in BGP can lead to black-holing traffic when failures occur.
-Deciding whether this can happen required knowledge of the routing policy and not just the topology.
-For example, a policy might require all traffic for a particular prefix going through a router where an aggregate is advertised to go over a single link, even if there are several available in the toplogy.
-However, the PGIR captures the both the policy and the topology information together.
+%\begin{figure}[t!]
+%\centering
+%\includegraphics[width=.9\columnwidth]{figures/config}
+%\caption{Abstract BGP configuration.}
+%\label{fig:abgp-config}
+%\end{figure}
 
-We can frame the aggregation problem as a problem of connectivity in the PGIR.
-More specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures that would disconnect where the prefix originates from where its more specific aggregate is located.
-The difficulty lies in the fact that the same links in the topology can appear in multiples places in the PGIR.
-We adopt the following simple strategy to lower bound the number of failures:
+\newcommand{\Router}[1]{ \textbf{Router #1:} }
+\newcommand{\REGEX}[1]{ \text{regex}(#1) }
+\newcommand{\PEER}{ \text{peer} }
+\newcommand{\COMM} {\text{comm}}
+\newcommand{\MED} {\text{MED}}
 
-\begin{enumerate}
-	\item Pick a random path through the product graph from start to end.
-	\item Remove all edges in the product graph corresponding to the set of topological edges choosen.
-	\item Repeat until no path exists.
-\end{enumerate}
+\begin{figure}[t!]
+\begin{lstlisting}[frame=single, mathescape=true] 
+$\Router{A}$
+  Match $\PEER=C, \COMM=(3,2)$
+    Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
+$\Router{B}$
+  Match $\PEER = C, \COMM = (-,2)$
+    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$ 
+           $\MED \leftarrow 81, \PEER \leftarrow W$
+  Match $\PEER = C, \COMM = (3,2)$
+    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$ 
+           $\MED \leftarrow 81, \PEER \leftarrow W$
+$\Router{C}$
+  Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
+    Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
+  Match $\PEER = D, \COMM = (2,2)$
+    Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
+$\Router{D}$
+  Match $\REGEX{X + Y}$
+    Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
+$\Router{E}$
+  Match $\REGEX{Z}$
+    Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
+\end{lstlisting}
+\label{fig:config}
+\caption{Abstract BGP router configurations.}
+\end{figure}
 
-Since each path through the PGIR will result in a new edge-disjoint path through the topology (since we have removed all already used edges), and since the number of edge-disjoint paths through the topology is no more than the min-cut.
-\todo{clarify this}
-
-\subsection{Abstract BGP}
+\begin{figure}[t!]
+\begin{lstlisting}[frame=single, mathescape=true] 
+$\Router{A}$
+  Match $\PEER=C$
+    Export $\MED \leftarrow 80, \PEER \leftarrow W$
+$\Router{B}$
+  Match $\PEER = C$
+    Export $\COMM \leftarrow \text{noexport}, \MED \leftarrow 81, \PEER \leftarrow W$
+$\Router{C}$
+  Match$[LP=99]$ $\PEER = E $
+    Export $\PEER \leftarrow B$
+  Match $\PEER = D$
+    Export $\PEER \leftarrow A,B$
+$\Router{D}$
+  Match $\REGEX{X + Y}$
+    Export $\PEER \leftarrow C$
+$\Router{E}$
+  Match $\REGEX{Z}$
+    Export $\PEER \leftarrow C$
+\end{lstlisting}
+\label{fig:config-min}
+\caption{Abstract BGP minimized configurations}
+\end{figure}
 
@@
 Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., by having a more general aggregate on a backup preference).
+
+\subsection{Aggregation-Induced Black Holes}
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{figures/aggregation}
+\caption{Aggregation Safety.}
+\label{fig:aggregation-safety}
+\end{figure}
+
+As was demonstrated in Example 2 of Section~\ref{sec:motivation}, the use of aggregation in BGP can lead to black-holing traffic when failures occur.
+Deciding whether this can happen required knowledge of the routing policy and not just the topology.
+For example, a policy might require all traffic for a particular prefix going through a router where an aggregate is advertised to go over a single link, even if there are several available in the toplogy.
+However, the PGIR captures the both the policy and the topology information together.
+
+We can frame the aggregation problem as a problem of connectivity in the PGIR.
+More specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures that would disconnect where the prefix originates from where its more specific aggregate is located.
+The difficulty lies in the fact that the same links in the topology can appear in multiples places in the PGIR.
+We adopt the following simple strategy to lower bound the number of failures:
+
+\begin{enumerate}
+	\item Pick a random path through the product graph from start to end.
+	\item Remove all edges in the product graph corresponding to the set of topological edges choosen.
+	\item Repeat until no path exists.
+\end{enumerate}
+
+Since each path through the PGIR will result in a new edge-disjoint path through the topology (since we have removed all already used edges), and since the number of edge-disjoint paths through the topology is no more than the min-cut.
+\todo{clarify this}
+
+For example, imagine we use the earlier data center example from Section~\ref{sec:motivation}, with the policy: $p_{g1} \mapsto end(A)$, where $p_{g1}$ falls under the $p_{g^*}$ aggregate.
+The data center topology and a simplification of the corresponding product graph are shown in Figure~\ref{fig:aggregation-safety}.
+Since the compiler knows an aggregate will be placed at $X$, and it knows that for prefix $p_{g1}$, the route will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$ in the product graph.
+In this case, we could remove the $A$ -- $D$ -- $X$ path first.
+We would then need to remove any other $A$ -- $D$ or $D$ -- $X$ links from the product graph, although in this case there are none.
+Next, we could remove the links along the $A$ -- $C$ -- $X$ path, repeating the process.
+Afterwards, $A$ is disconnected from $X$, so the compiler knowns that 2 is a lower bound from aggregation safety for prefix $p_{g1}$.
+This process is then repeated for other aggregation locations, in this case router $Y$.

### 2016-01-22 paper/expressiveness.tex
Adding compiled policy figures.

@@
-\para{Expressiveness}
+\section{Expressiveness}
+
+In this section we investigate correctness and expressiveness properties of \sysname.
+We are mainly concerned with the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures?
+(2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?
+
+In this section, we compare the expressiveness of the \sysname language to that of BGP.
 

### 2016-01-22 paper/expressiveness.tex
saving changes to theory.

@@
-\section{Expressiveness}
+\section{Theory}
 
-In this section we investigate correctness and expressiveness properties of \sysname.
+\newtheorem{defn}{Proposition}[section]
+
+In this section we investigate the correctness and expressiveness properties of \sysname.
 We are mainly concerned with the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures?
 (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?
+
+\subsection{Correctness}
+
+We argue that, if \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario.
+We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges.
+We argue that \sysname is correct by breaking down the claim into two distinct parts:
+
+\begin{defn}
+A distributed BGP configuration is \textit{Sound} with respect to a \sysname policy, if the only routes that that traffic ever takes in the network, are those that are specified in the policy.
+\end{defn}
+
+The Soundness claim follows directly from compilation of the product graph.
+Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations will be Sound.
+
+\begin{defn}
+A distributed BGP configuration is \textit{Complete} with respect to a \sysname policy, if the distributed implementation always obtains a most preferred route between two nodes if the corresponding path exists in the network.
+\end{defn}
+
+The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.
+This means there is a valid path in the product graph corresponding to this path, and which is available in the network.
+Assume we are unable to achieve this route in the network.
+To not achieve this path means that some router along advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead.
+This implies that that router that makes the ``wrong'' choice appears as a separate node in the product graph.
+However, from our failure safety check, we know that the other, more-preferred node must have a superset of the paths to accepting states as the less preferred node has for at least as good of a final preference.
+However, this implies that a route advertisement will still reach $X$, resulting in a path with a preference between $X$ and $Y$ that is just as good.
+
+The combination of Soundness and Completeness ensures that the distributed implementation will always achieve the best routes possible, yet will never also achieve unwanted routes.
+
+\begin{defn}
+The internal routers in a distributed BGP configuration produced by \sysname will be stable. 
+\end{defn}
+
+The argument for stability comes from the path suffix condition.
+
+\para{Expressiveness}
 

### 2016-01-22 paper/expressiveness.tex
Added future work section

@@
 
-The argument for stability comes from the path suffix condition.
+The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}.
+If a set of BGP configurations do not have a dispute wheel, then they will converge to their best routes.
+Any BGP policy with a dispute wheel will not satisfy the failure safety condition in Section~\ref{sec:compilation}.
+Assume that there is a dispute wheel.
+Then that means each node $u_i$ in the dispute wheel prefers to go through
 

### 2016-01-23 paper/conclusions.tex
conclusion.

@@
 
-TODO
+In this paper, we introduced \sysname, a language and compiler for implementing centralized network policies using a distributed set of devices running the Border Gateway Protocol.
+Propane allows operators to describe network-wide intent directly through high-level constraints, built on top of a regular-expression-based language for describing desired paths through the network and their relative preferences.
+When Propane compiles a policy, then the resulting BGP configurations are correct-by-construction, faithfully implementing the centralized policy in a distributed fashion, regardless of network failures.
+When \sysname can not implement the policy, it notifies the user during the compilation stage rather than after deployment.

### 2016-01-23 paper/evaluation.tex
conclusion.

@@
 We evaluate our compiler by measuring compilation times for these policies across topologies of different sizes.
-
-\para{Notes}
-
-\begin{itemize}
-
-  \item Since our policy language can express things not implementable in BGP, we need a few checks.
-      First show some examples of what the problem is: why BGP cannot make a decision.
-      The reasons this can happen are:
-      (1) Single best path per router - no subset of paths specified is consistent (if A goes through B and C goes through A, then C goes through B).
-      (2) Failures - Have to make a decision without knowing what failures have occurred. Never want to prefer one peer over another and then not get a path when one was available
-\end{itemize}
-
-\subsection{Optimizations}
-
-\begin{itemize}
-  \item For config readability and number of route maps/communities, we avoid community tagging/matching whenever possible with a number of tricks.
-\end{itemize}
-
-\begin{enumerate}
-	\item Expressiveness of the policy language / BGP safe part of the language (maybe a proof earlier for this)
-	\item Compactness of the policy language (how verbose/concise, maybe in loc)
-	\item Intuitiveness of the policy language (how easy is it to understand? Not really a good way to evaluate this other than demonstrate earlier by example)
-	\item Speed of compilation (does it take forever? what are the bottlenecks)
-	\item Understandability of the resulting configurations (Can humans understand them?)
-	\item Some measure of the size of the resulting configurations (e.g., the number of route maps. Is this actually ever an issue in BGP?)
-\end{enumerate}

### 2016-01-23 paper/expressiveness.tex
quasi-proof of stability.

@@
 
+\begin{figure}[t!]
+\includegraphics[width=\columnwidth]{figures/dispute-wheel}
+\label{fig:dispute-wheel}
+\caption{Product graph for a dispute wheel.}
+\end{figure}
+
 The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}.
@@
 Any BGP policy with a dispute wheel will not satisfy the failure safety condition in Section~\ref{sec:compilation}.
-Assume that there is a dispute wheel.
-Then that means each node $u_i$ in the dispute wheel prefers to go through
+Assume that the preferences in the policy describe a dispute wheel, and we will show that our failure check will reject the policy.
+Informally, a dispute wheel occurs when there are some number of nodes $u_1, \dots, u_n$ attempting to get a path to a destination node $d$.
+Each node $u_i$ prefers to go through its neighbor $u_{i+1}$ over route $R_i$ than directly to $d$ with route $Q_i$.
+Thus the nodes form a wheel of preferences.
+The product graph for a policy that contains a dispute wheel will look like Figure~\ref{fig:dispute-wheel}, which shows a dispute wheel of size 3.
+In order to pass the failure safety check for the compiler, the more-preferred node for $u_2$ will need to have a superset of the paths starting from the less-preferred node for $u_2$.
+In turn, this means that the maximum length path after visiting the more preferred $u_2$ will be $max(Z) = 1 + max(Y)$, similarly, if we look at $u_1$, we will determine that $max(Y) = 1 + max(X)$, and so on.
+The resulting equations define a system of unsatisfiable equations.
+Therefore, it is not possible for \sysname to compile a BGP policy that contains a dispute wheel.
+Since no-dispute-wheel is a sufficient condition for BGP stability, any compiled \sysname policy will be stable.
 

### 2016-01-23 paper/expressiveness.tex
Cleaning up bullet points, starting expressiveness.

@@
 (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?
+
+\subsection{Expressiveness}
+
+Models for BGP are traditionally given over per-device ranked paths 
+In this section, we describe the expressiveness of \sysname.
+
+\begin{defn}
+
+\end{defn}
 
@@
 
-\para{Expressiveness}
-
-In this section, we compare the expressiveness of the \sysname language to that of BGP.
-
-\todo{Do we need all of this}
+An important distinction is that BGP might still be instable with respect to other external ASes, since \sysname has no way of configuring their routing policy and can only rely on AS path filters to see what advertisements are observed.

### 2016-01-23 paper/introduction.tex
Cleaning up bullet points, starting expressiveness.

@@
 \todo{new intro is not complete}
-
-\todo{OLD TEXT IS BELOW}
-
-%% Word vommit
-Why network configuration is hard:
-\begin{itemize}
-	\item Wide variety of considerations: Have preferences for certain routes over others, failure resistance, backups etc
-	\item Configurations are implemented locally and in a distributed fashion even though network intent is global
-	\item Often achieve intent through indirect means (i.e., backups through aggregation, preferences through MED, AS PATH length, local-pref values, filtering through communities)
-	\item Networks are distributed, asynchronous systems where the environment can be unknown, failures can occur ... which makes it difficult to consider all scenarios
-	\item Problems are compounded in inter-domain setting where factors like peering agreements and bad peer behavior need to be taken into account.
-	\item Protocol-specific issues such as lack of convergence in BGP
-\end{itemize}
-
-We present a new language that allows operators to directly express and compile high-level routing policies (both inter and intra-domain) from a centralized point of view.
-
-The language provides the operator with the abstraction that they can control the routes that all traffic through their network can take, even if the routes start and/or end in a different autonomous system.
-
-The core language consists of regular expression constraints on the set of allowed routes along with a preference operator between routes, which is used to specify both routing preferences and backup paths.
-On top of the core language, we provide a higher-level macro language to talk only about constraints on routes without specifying any particular route details.
-
-A compiler takes a routing policy written in our language and synthesizes concrete, per-device configurations running BGP.
-Although the language is independent of any particular routing protocol, we target BGP due to its expressiveness, scalability, and use for both inter-domain and intra-domain routing.
-The compiler either guarantees that the resulting configurations correctly implement the policy and remain correct under all possible network failure scenarios, or it returns a counterexample.
-(Similar to SDN, you get centralized control, yet a distributed implementation that uses an existing, scalable, fault-tolerant protocol.)
-
-To allow for more fine-grained control over control-plane details, our language permits additional constraints on control protocol details (e.g., maximum number of allowed routes, whether to use multipath etc).
-
-Summary:
-	 (1) Centralized: (simpler reasoning, no copy paste error, more concise),
-	 (2) Synthesis: (no need for gory details, e.g., community values, local-pref, MED, ...),
-	 (3) Expressive: (backup routing, preferences, waypointing, directly say things like no transit or cold-potato routing),
-	 (4) Correct: (implement the policy, even under all failure scenarios)

### 2016-01-23 paper/compilation.tex
edited paper.

@@
 In this section we briefly describe our compilation strategy for \sysname.
-Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate user-level \sysname policies into vendor-specific, device-local BGP policies.
+Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate user-level \sysname policies into device-local BGP policies.
 The first stage of the pipeline involves simple rewriting rules and substitutions from the user-level languae into the core Regular Intermediate Representation (RIR).
@@
 The PGIR is a data representation that compactly captures the control flow of all BGP advertisements subject to the policy and topology restrictions.
-We develop efficient algorithms that operate over the PGIR to ensure policy compliance, guarantee failure safety, avoid BGP instability, and prevent aggregation-induced black holes.
+We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes.
 Once the compiler determines the PGIR for the policy is safe, the compiler uses a simple translation to an abstract BGP (ABGP) representation.
-To make configurations more readable for human operators, and to reduce the size of the resulting configurations, the \sysname compiler makes several passes over ABGP form.
+To make configurations more readable for human operators, and to reduce the size of the resulting configurations, the \sysname compiler makes several passes over the ABGP form.
 Finally, vendor-specific adaptors can be added to \sysname to translate from ABGP to actual concrete configurations that go on the network devices.
@@
 The high-level language presented in Section~\ref{sec:propane} is just a thin layer on top of a core, regular-expression-based language for describing preference-based path constraints.
-Regular expressions are an expressive formalism that have been studied extensively for their ability utility in describing paths through graphs~\cite{bib:todo}, and applications to networks~\cite{bib:todo}.
-We present our core Regular language in the below.
+Regular expressions are an expressive formalism that have been studied extensively for their utility in describing paths through graphs~\cite{bib:todo}, and applications to networks~\cite{bib:todo}.
+Our regular expression language differs from others by allowing operators to describe preferences between paths.
 
@@
 A policy consists of one or more constraints, each of which consists of a test on the type of route, and a corresponding set of preferred regular paths.
-Regular paths are simply regular expressions where the base locations are AS numbers.
+Regular paths are simply regular expressions where the base characters are AS numbers.
 Special \textit{in} and \textit{out} symbols are used to refer to any internal or external location respectively.
@@
 describes a more-preferred set of paths for traffic announced by a prefixes no less specific than $74.125.28.0/24$, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same.
-Tests over route types are allowed to be used with standard boolean connectives, and they can refer to both prefixes and community values (which are often important when interoperating with existing ASes).
+Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.
 
@@
 A lower rank indicates a \emph{more} preferred path.
-The desired semantics is to allow traffic to be sent along any of the most preferred paths for any pair of starting and ending locations that appear in some valid path.
+The desired semantics is to allow traffic to be sent along any of the most preferred paths for each pair of starting and ending locations that appear in some valid specified path.
 
 The set of ranked paths depends on which paths are valid given the topology, and thus when failures occur, so do the most preferred routes.
-It is the job of the \sysname compiler to ensure that generated configurations for a policy always achieve the most preferred path possible given the failures in the topology, and it must do so using purely distributed mechanisms.
+It is the job of the \sysname compiler to ensure that generated configurations for a policy always achieve the most preferred path possible given the failures in the topology, using only distributed mechanisms.
 
@@
 
-The main differences between \sysname the regular language are: (1) \sysname allows the programmer to specify constraints separately, and combine them together modularly, (2) \sysname provides high-level names that abstract sets of routes, and (3) \sysname allows the preference operator to appear in more locations.
-The translation from \sysname to RIR is based on a set of simple rewriting rules.
+The main differences between \sysname the regular language are: (1) \sysname allows the programmer to specify constraints separately, and combine them together modularly, (2) \sysname provides high-level names that abstract sets of routes, and (3) \sysname allows the preference operator to be used locally.
 
@@
 
+The translation from \sysname to RIR is based on a set of simple rewriting rules.
 The first step is to merge separate constraints.
-This is accomplished by simply taking the cross product of per-prefix constraints, where logical conjunction ($a \wedge b$) is replaced by intersection on regular constraints ($a \cap b$), logical disjunction is replaced by union, and logical negation ($\neg a$) is replaced by ($any \cap !(a)$).
+This is accomplished by simply taking the cross product of per-prefix constraints, where logical conjunction ($a \wedge b$) is replaced by intersection on regular constraints ($a \cap b$), logical disjunction is replaced by union, and logical negation ($\neg a$) is replaced by ($any \cap !(a)$), where $any$ ensures the routes are well-formed.
 %
@@
 Since preferences can only occur at the top level for RIR, the final step is to lift the preferences that occur in the regular expression.
-For example, the regular expression $a \cdot (b \gg c) \cdot d$ is lifted to $(a \cdot b \cdot d) \gg (a \cdot c \cdot d)$.
-In general, we employ the follwing:
+For example, the regular expression $a \cdot (b \gg c) \cdot d$ is lifted to $(a \cdot b \cdot d) \gg (a \cdot c \cdot d)$ by distributing the preference over the sequence operator.
+In general, we employ the follwing equivalence:
 %
@@
 %
-where $\odot$ stands for an arbitrary regular binary operator. Preferences nested under a unary operator, \textit{star} or \textit{negation}, are invalid policies.
+where $\odot$ stands for an arbitrary regular binary operator. Preferences nested under a unary operator, \textit{star} or \textit{negation}, are flagged by the compiler as invalid policies.
 
@@
     \transition{1}{2}{in}{}
-    \transition{2}{2}{ACDE}{loop above}
+    \transition{2}{2}{A,C,D,E}{loop above}
     \transition{2}{3}{B}{}
     \transition{3}{3}{B}{loop above}
-    \transition{3}{2}{ACDE}{bend left}
+    \transition{3}{2}{A,C,D,E}{bend left}
     \transition{3}{4}{W}{}
@@
 
-  \caption{Example Product Graph construction.}
+  \caption{Example Product graph construction.}
   \label{fig:example-compilation}
@@
 The Product graph can be thought of as the intersection of each of the regular automata corresponding to the RIR path preferences, and the topology.
+Paths through the product graph will correspond to real paths through the topology that satisfy the user constraints.
 Finding paths through a graph subject to regular constraints has been studied extensively in the database literature~\ref{bib:todo}, and has been applied to networks in the past~\ref{bib:todo}.
@@
 
+% Formally define automata
 The translated user policy into RIR is of the form $r_1 \gg \dots \gg r_j$.
@@
 Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ consists of all internal and external ASes, $Q_i$ is a set of states, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ the state transition function.
-
-The topology is modelled as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon 2^{V \times V}$.
-
-\todo{use different symbols here}
-
-The combined product graph is a tuple: ($V'$, $E'$, $s$, $A$) with 
-vertices $V' \colon V \times 2^{Q_1 \times \dots \times Q_j}$, 
+The alphabet $\Sigma$ consists of all internal and external ASes, $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+%
+% Formally define topology
+The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon 2^{V \times V}$.
+%
+% Formally define product graph
+The combined product graph is a tuple: ($V'$, $E'$, $s$, $e$, $A$) with 
+vertices $V' \colon V \times Q_1 \times \dots \times Q_j$, 
 edges $E' \colon 2^{V' \times V'}$, 
 a unique starting vertex $s$, 
-and an preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the graph to the set preferences for which the corresponding automata are accepting in state $Q_i$
+a unique ending vertex $e$,
+and an preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to the sets of preferences. 
+For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. We say a node $x$ shadows node $y$ in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$.
+
+% Formal product construction
+Let $a_i$ and $b_i$ stand for states in the policy automata.
+The product graph is constructed by adding an edge from $v_1 = (x, a_1, \dots, a_m)$ to $v_2 = (y, b_1, \dots, b_m)$ whenever $\sigma_i(a_i, y) = b_i$ for each $i$ and $(x,y) \in E$ is a valid topology link.
+Additionally, we add edges from the start node $s$ to any $v = (x, a_1, \dots, a_m)$ when $\sigma_i(q_{0_i}, x) = a_i$ for each $i$.
+The preference function $P$ for node $v = (x, a_1, \dots, a_m)$ is defined as $P(v) = \set{i \vert a_i \in F_i} $.
+That is, it records which preferences are achieved for the policy automata for each node in the product construction.
+Finally, there is an edge from each node in the product graph such that $P(v) \neq \emptyset$ to the special end node $e$.
 
@@
 
-Intuitively product graph tracks which states of each automaton the policy is in as traffic moves between different topology locations.
+Intuitively the product graph tracks which states of each automaton the policy is in as route advertisements move between routers in the topology.
 
@@
 Suppose we want to set up a primary route from W that enters the network from $A$, and utilizes the A -- C and C -- D links.
-We also would like a backup route that utilizes enters from node $B$, and utilizes the B -- C link, but is otherwise unconstrained.
+We also would like a backup route that enters from node $B$, and utilizes the B -- C link, but is otherwise unconstrained.
 For the sake of simplicity, we will assume that the route can end in either $X$, $Y$, or $Z$.
@@
 %
-Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference.
-Since we are interested in the flow of control messages, the automata match backwards.
+Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards. 
+%
 Figure~\ref{fig:example-compilation} shows the product graph obtained from intersecting the topology and policy automata.
 Every path in the product graph corresponds to a concrete path in the topology.
-In particular, every path through the product graph that ends at a node with an accepting preference is a valid topological path that satisfies the policy constraints and results in a particular preferenced path.
+In particular, every path through the product graph that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
 %
-For example, the path $X D C A W$ is a valid path in the topology that BGP route advertisements might take, which would lead to obtaining the most prefered preference.
+For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route advertisements might take, which would lead to obtaining the most prefered preference $1$.
 BGP control messages can start from peer X, which would match the $out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
@@
 Since node $(5,-) W$ is in an accepting state for the first automata, it indicates this path has preference 1.
-
-\todo{explain drop states}
-\todo{preferences are reversed in picture}
 
@@
 However, the product graph may contain many paths that form loops in the topology.
-For example, in Figure~\ref{fig:example-compilation}, the path $W A C B W$ is a valid path that BGP route advertisements might take through the topology, leading to a path that satisfies the preference 1 policy, but which contains a loop.
+For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid path that BGP route advertisements might take through the topology, leading to a path that satisfies the preference 1 policy, but which contains a loop.
 %
 Since we are primarily concerned with guaranteeing user policy correctness and safety with respect to network failures, it is useful to avoid considering possibilities that are not possible due to loops.
-For example, if we can safely remove an edge from the product graph, then we don't have to consider the case that the edge has failed.
+For example, if we can safely remove an edge from the product graph, then we don't have to consider what happens when the edge has failed.
 
-We can safely remove any node or edge from the product graph so long as it never appears on any \emph{simple} path from the \textit{start} node to some node with an accepting preference.
-For example, node $(1,1) W$ in Figure~\ref{fig:example-compilation} is never on a simple path to an accepting preference since both end at location $W$.
+We can safely remove any node or edge from the product graph so long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node.
+For example, node $(1,1) W$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it most go through another $W$ in either case.
 %
-Although fully minimizing the product graph is an NP-complete problem, we find that a simple and efficient algorithm based on graph dominators achieves largely the same effect, without preventing compilation of most policies in practice.
+Although fully minimizing the product graph is an NP-complete problem, we find that a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.
 
-A node $x$ dominates node $y$ if $x$ appears on every path leading to $y$ from the $start$ node.
+A node $x$ dominates node $y$ if $x$ appears on every path leading to $y$ from a source node.
 Many algorithms for finding graph dominators efficiently exist~\ref{bib:todo}.
-To minimize the product graph, we compute the dominator set for each node in both the product graph $G$, and the reversed product graph $G^R$ (with a source node attached to each accepting state).
-The following rules us to efficiently simplify the product graph.
-
+For minimization, we compute the dominator set for each node in both the product graph $G$ with respect to the start node, and in the reversed product graph $G^R$ with respect to the end node.
+The following rules enable a cheap simplification of the product graph.
+%
 \begin{itemize}
-  \item Remove nodes that never reach an accepting state
+  \item Remove nodes that never reach the end node
   \item Remove nodes not reachable from the $start$ node
   \item Remove any node $x$ such that $x$ is dominated by $y$ in $G$ or $G^R$, and $loc(x) = loc(y)$
-  \item Remove any edge from $x$ to $y$ in $G$ or $G^R$ if there is some $z$ dominated by $y$ such that $loc(x) = loc(z)$
+  \item Remove any edge from $x$ to $y$ in $G$ or $G^R$ if there is some node $z$ dominated by $y$ such that $loc(x) = loc(z)$
 \end{itemize}
-
-Repeated application of the 4 above rules leads to removing the colored nodes and dashed lines in Figure~\ref{fig:example-compilation}.
+%
+Repeated application of the above rules leads to removing the colored nodes and dashed lines in Figure~\ref{fig:example-compilation}.
 
@@
 However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult, particularly in the presence of failures.
-For example, imagine an extremely simple policy for the topology in Figure~\ref{fig:example-compilation}, which says to prefer $WACD$ over $WBCE$:
+For example, imagine an extremely simple policy for the topology in Figure~\ref{fig:example-compilation}, which says to prefer one route over another:
 %
@@
 Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $E$?
-The important observation is that, if $C$ prefers $D$, then it will always achieve at least as good a path as if it had choosen $E$.
+The important observation is that, if $C$ prefers $D$, then it is never worse off -- it will always achieve at least as good a path as if it had choosen $E$.
 For example, suppose $C$ chooses a route from $D$, but cannot achieve its primary path because the $A$ -- $W$ link has failed.
@@
 
-In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard.
-A simple enumeration of failures is intractable.
-Instead, we adopt a conservative analysis based on the product graph representation and the previous observations, which runs efficiently in practice.
+In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and a simple enumeration of failures is intractable.
+Instead, we adopt a conservative analysis based on the product graph representation and the previous observations.
 The high-level idea is to order each node in the product graph according to a \textit{can prefer} relation.
@@
 %
-where the \textit{protect} predicate means that, from $N_1$ on the product graph restricted to preferences $j$ or better, there are at least as many paths as from $N_2$ restricted to $G_i$
+where the \textit{protect} predicate means that, from $N_1$ on the product graph restricted nodes that achieve preference $j$ or better, there are at least as the same paths as from $N_2$ restricted to $G_i$
 
@@
 \Procedure{Protect($G_1$, $N_1$, $G_2$, $N_2$)}{}
-  \If {$N_1.loc \neq N_2.loc$} \Return false
+  \If {$loc(N_1) \neq loc(N_2)$} \Return false
   \EndIf
@@
     \For {$x$ in $adj(G_2, n_2)$}
-      \If {exists a $y$ where $y$ shadows $x$} 
+      \If {some $y$ in $adj(G_1,n_1)$ shadows $x$} 
         \If {$(x,y)$ not marked}
@@
 Intuitively, the algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
-Thus $N_1$ any paths leading from $N_2$ will have an equivalent path from $N_1$.
+Thus any paths leading from $N_2$ will have an equivalent path over the same topology locations from $N_1$.
 Algorithm~\ref{alg:failures} works because each node in the product graph can have at most one outgoing neighbor with the same topological location, so the next hop neighbors can be checked without backtracking.
@@
 
-Local preferences are obtained by, for each router in the topology, sorting the corresponding nodes in the product graph according to \textit{can prefer} relation.
+Local preferences are now obtained by, for each router in the topology, sorting the corresponding nodes in the product graph according to \textit{can prefer} relation.
 If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
@@
 The checks for failure safety described previously overlook one critical point: even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$.
-To avoid this situation, we simply conservatively check that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the product graph (i.e., nodes reachable from $x$ in $G_j^R$).
+To avoid this situation, the compiler simply conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the product graph (i.e., nodes reachable from $x$ in $G_j^R$).
 It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
@@
 
-Having found a total ordering on node preferences in the product graph from the failure safety analysis, the translation to ABGP becomes very simple.
+\para{From PGIR to ABGP}
+
+Having found a total ordering on node preferences in the product graph from the failure safety analysis, the translation to ABGP becomes straightforward.
 The idea is to encode the state of the automaton using BGP community values.
@@
 
-To ensure preferred paths are always obtained, for each router $r$, the compiler will simply set a higher local preference for neighbors of a more-preferred node for $r$ in the product graph.
+To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler will simply set a higher local preference for neighbors of a more-preferred node for $r$ in the product graph.
 For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
 
-Since the compiler is only able to control community tagging for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
+Since the compiler is only able to control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
 Instead, it simply translates matches from external ASes into a BGP regular expression filter.
@@
 In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
+In practice, we model the unknown AS topology as a special node in the product graph that generates a filter to match any sequence of ASes.
 
@@
 In general, it is not possible to control traffic entering the network beyond certain special cases.
-In this example however, the BGP MED attribute can influence $W$ to prefer $A$ over $B$ since the preference is for a single external peer, and the BGP no-export community can ensure that no other AS beyond $W$ can send us traffic.
-The compiler can perform a simple analysis to determine when it can utilize various BGP special attributes to ensure traffic enters the network in a particular way.
+In this example however, the BGP MED attribute can influence $W$ to prefer $A$ over $B$ since the preference is for a single external peer.
+Additionally, the compiler can use the BGP no-export community can ensure that no other AS beyond $W$ can send us traffic.
+The compiler can perform a simple analysis to determine when it can utilize various BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
 Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
-Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., by having a more general aggregate on a backup preference).
+Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
+
+Figure~\ref{fig:config} shows the full configuration from the compilation example.
+To make configurations more compact and readable, the \sysname compiler will rewrite configurations in ABGP - for example removing community tagging and matching when there is no ambiguity.
+Figure~\ref{config-min} shows the minimized router configurations.
 
@@
 \includegraphics[width=\columnwidth]{figures/aggregation}
-\caption{Aggregation Safety.}
+\caption{Aggregation safety.}
 \label{fig:aggregation-safety}
@@
 
-As was demonstrated in Example 2 of Section~\ref{sec:motivation}, the use of aggregation in BGP can lead to black-holing traffic when failures occur.
-Deciding whether this can happen required knowledge of the routing policy and not just the topology.
-For example, a policy might require all traffic for a particular prefix going through a router where an aggregate is advertised to go over a single link, even if there are several available in the toplogy.
-However, the PGIR captures the both the policy and the topology information together.
+As was demonstrated in Example 2 of Section~\ref{sec:motivation}, the use of aggregation in BGP can lead to subtle black-holing traffic when failures occur.
+Deciding when this can happen requires knowledge of the routing policy and not just the topology.
+For instance, a policy might require all traffic for a particular prefix going through a router where an aggregate is advertised to go over a single link, even if there are several available in the toplogy.
+If the single link fails, then a black hole might be introduced.
+Fortunately, the PGIR captures this information precisely, describing the how information meeting the policy flows over the topology.
 
@@
 More specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures that would disconnect where the prefix originates from where its more specific aggregate is located.
-The difficulty lies in the fact that the same links in the topology can appear in multiples places in the PGIR.
+The difficulty lies in the fact that the same links in the topology can appear in multiple places in the PGIR.
 We adopt the following simple strategy to lower bound the number of failures:
-
 \begin{enumerate}
@@
 \end{enumerate}
-
 Since each path through the PGIR will result in a new edge-disjoint path through the topology (since we have removed all already used edges), and since the number of edge-disjoint paths through the topology is no more than the min-cut.
@@
 The data center topology and a simplification of the corresponding product graph are shown in Figure~\ref{fig:aggregation-safety}.
-Since the compiler knows an aggregate will be placed at $X$, and it knows that for prefix $p_{g1}$, the route will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$ in the product graph.
+Since the compiler knows an aggregate will be placed at $X$, and it knows that, for prefix $p_{g1}$ the route will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$ in the product graph.
 In this case, we could remove the $A$ -- $D$ -- $X$ path first.
-We would then need to remove any other $A$ -- $D$ or $D$ -- $X$ links from the product graph, although in this case there are none.
+We would then need to remove any other $A$ -- $D$ or $D$ -- $X$ links from the product graph, though in this case there are none.
 Next, we could remove the links along the $A$ -- $C$ -- $X$ path, repeating the process.
-Afterwards, $A$ is disconnected from $X$, so the compiler knowns that 2 is a lower bound from aggregation safety for prefix $p_{g1}$.
-This process is then repeated for other aggregation locations, in this case router $Y$.
+Because afterwards $A$ is disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix $p_{g1}$.
+This process is then repeated for other aggregation locations (e.g., $Y$).

### 2016-01-23 paper/related.tex
related work

@@
 \end{itemize}
+
+\dpw{We could also consider citing Boon's stuff on declarative routing.}
+
+\paragraph*{SDN Programming Languages}
+The design of \sysname{} was heavily influenced by recent SDN programming
+languages such as Merlin~\cite{foster:merlin}, FatTire~\cite{fattire},
+NetKAT~\cite{netkat}, as well as Narayana's path queries~\cite{queries}.
+Each of these languages is oriented around regular expressions, which
+describe paths through a network, and predicates, which classify packets.
+In particular, FatTire allows programmers to define sets of paths together
+with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
+and the compiler will generate
+OpenFlow 1.3 rules that satisfy the policy.  \sysname is somewhat more
+expressive than FatTire as it allows users to specify preferences among
+routes and it automatically generates distributed
+implementations that will tolerate
+any number of faults.  Because FatTire generates data plane rules up front,
+before faults occur, specifying higher levels of fault tolerance comes 
+at the cost of generating additional rules, which must fit in switch
+memory.  In contrast, \sysname uses traditional distributed
+control plane mechanisms to react to faults as they occur and to the
+extent that they occur without imposing up front costs that may
+necessitate overprovisioning.
+Because of the differences in the underlying technology, the analyses
+and compilation algorithms used in \sysname are quite different from
+previous work on SDN.  Finally, in addition to using path-based abstractions
+for intra-domain routing, \sysname uses them for inter-domain routing as
+well, unlike any existing SDN language.
+
+\paragraph*{Configuration Analysis}  The notion that
+configuring network devices is difficult and error-prone is not new.  Past 
+researchers have
+tried to tackle this problem by analyzing existing 
+firewall configurations~\cite{fang,lumeta,margrave} and
+BGP configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe} and reporting errors or
+inconsistencies when they are detected. 
+Our research is complementary to these analysis
+efforts.  Propane hopes to eliminate bugs by using higher-level
+languages and a ``correct-by-construction''
+methodology.  By proposing network administrators write configurations
+at a high-level of abstraction, a whole host of low-level errors can be 
+avoided.  We also believe the high-level, centralized nature of propane policies
+has the benefit of making configurations
+easier to understand and maintain.
+
+\paragraph*{Configuration Synthesis}  
+ConfigAssure~\cite{narain:lisa05,narain+:configassure} 
+is another system designed to
+help users define and debug low-level router
+configurations.  Inputs to
+ConfigAssure include a \emph{configuration database}, which contains a
+collection of tuples over constants and configuration variables, and a
+\emph{requirement}, which is a set of constraints.  For instance, the
+tuple \texttt{hsrp(rexa,rA1,int(1),int(2))} states that interface
+\texttt{rA1} on device \texttt{rexa} belongs to the HSRP group defined
+by configuration variable \texttt{int(1)} with virtual IP address
+defined by configuration variable \texttt{int(2)}.  The constraint
+\texttt{hsrp\_subnet([rexa-rA1,rexb-rB1])} states that a database
+contains tuples defining HSRP group identifiers and virtual IPs for
+interfaces \texttt{rA1} and \texttt{rB1} on devices \texttt{rexa} and
+\texttt{rexb}.  The authors use a combination of logic programming and
+SAT solving to find concrete values for configuration variables such
+as \texttt{int(1)}.  ConfigAssure has very broad scope, handling
+configuration for a wide range of different protocols and many
+different concerns.  In contrast, the scope of \sysname is much
+narrower.  In return, \sysname offers compact, higher-level
+abstractions customized for our domain, such as regular paths, as well
+as domain-specific analyses customized to those abstractions, such as
+our failure safety analysis.  The implementation technology is also
+entirely different, as we define algorithms over automata and graphs
+as opposed to using logic programming and SAT-based model-finding.

### 2016-01-23 data/graph.py
adding preliminary graph for dc

@@ -1,0 +1,75 @@
+import csv
+import os.path
+import numpy as np
+import matplotlib.pyplot as plt
+
+# collect stats from csv
+num_pods = []
+tpp_total_mean = []
+tpp_build_mean = []
+tpp_minimize_mean = []
+tpp_order_mean = []
+tpp_gen_mean = []
+tpp_compress_mean = []
+
+# read values from csv file
+direct = os.path.dirname(os.path.realpath(__file__))
+with open(direct + os.path.sep + 'stats.csv') as f:
+  r = csv.reader(f)
+  for row in r:
+    num_pods.append(row[0])
+    tpp_total_mean.append(row[10])
+    tpp_build_mean.append(row[13])
+    tpp_minimize_mean.append(row[16])
+    tpp_order_mean.append(row[19])
+    tpp_gen_mean.append(row[22])
+    tpp_compress_mean.append(row[25])
+
+# remove first row, and convert type
+num_pods = map(int, num_pods[2:])
+tpp_total_mean = map(float, tpp_total_mean[2:])
+tpp_build_mean = map(float, tpp_build_mean[2:])
+tpp_minimize_mean = map(float, tpp_minimize_mean[2:])
+tpp_order_mean = map(float, tpp_order_mean[2:])
+tpp_gen_mean = map(float, tpp_gen_mean[2:])
+tpp_compress_mean = map(float, tpp_compress_mean[2:])
+
+# stack data lowest -> highest (build, minimize, order, gen, compress)
+data = (tpp_build_mean, tpp_minimize_mean, tpp_order_mean, tpp_gen_mean, tpp_compress_mean)
+foo = np.row_stack( data )
+y_stack = np.cumsum(foo, axis=0)
+
+# plot colors
+color1 = "#FFC09F"
+color2 = "#FFEE93"
+color3 = "#FCF5C7"
+color4 = "#A0CED9"
+color5 = "#ADF7B6"
+
+fig = plt.figure()
+plt.grid()
+ax1 = fig.add_subplot(111)
+ax1.fill_between(num_pods, 0, y_stack[0,:], facecolor=color1, alpha=.7)
+ax1.fill_between(num_pods, y_stack[0,:], y_stack[1,:], facecolor=color2, alpha=.7)
[…]

### 2016-01-23 data/graph.py
simplifying overview picture

@@ -46,6 +46,7 @@ color3 = "#FCF5C7"
 color4 = "#A0CED9"
 color5 = "#ADF7B6"
 
+# stacked plot showing different running times
 fig = plt.figure()
 plt.grid()
 ax1 = fig.add_subplot(111)
@@ -54,22 +55,23 @@ ax1.fill_between(num_pods, y_stack[0,:], y_stack[1,:], facecolor=color2, alpha=.
 ax1.fill_between(num_pods, y_stack[1,:], y_stack[2,:], facecolor=color3)
 ax1.fill_between(num_pods, y_stack[2,:], y_stack[3,:], facecolor=color4)
 ax1.fill_between(num_pods, y_stack[3,:], y_stack[4,:], facecolor=color5)
-ax1.set_xlabel('Fattree pods')
+ax1.set_xlabel('Fattree pod size')
 ax1.set_ylabel('Time (sec)')
-
+# custom legend for stack color
 p1 = plt.Rectangle((0, 0), 1, 1, fc=color1, alpha=.7)
 p2 = plt.Rectangle((0, 0), 1, 1, fc=color2, alpha=.7)
 p3 = plt.Rectangle((0, 0), 1, 1, fc=color3, alpha=.7)
 p4 = plt.Rectangle((0, 0), 1, 1, fc=color4, alpha=.7)
 p5 = plt.Rectangle((0, 0), 1, 1, fc=color5, alpha=.7)
+leg_boxes = [p1, p2, p3, p4, p5]
 descrs = ["Construct PG", "Minimize PG", "Find Preferences", "Generate ABGP", "Minimize ABGP"]
-ax1.legend([p1, p2, p3, p4, p5], descrs, loc=2)
+ax1.legend(leg_boxes, descrs, loc=2)
 fig.savefig('compilation-time-stacked.png')
 
 # plot figures 
 fig = plt.figure()
 plt.plot(num_pods, tpp_total_mean, label='Total')
-plt.xlabel('Fattree pods')
+plt.xlabel('Fattree pod size')
 plt.ylabel('Time (sec)')
 plt.legend(loc=2)
 fig.savefig('compilation-time.png')

### 2016-01-24 data/graph.py
added preliminary config compression results for dc

@@ -5,6 +5,9 @@ import matplotlib.pyplot as plt
 
 # collect stats from csv
 num_pods = []
+num_nodes = []
+sizes_raw = []
+sizes_compressed = []
 tpp_total_mean = []
 tpp_build_mean = []
 tpp_minimize_mean = []
@@ -14,10 +17,13 @@ tpp_compress_mean = []
 
 # read values from csv file
 direct = os.path.dirname(os.path.realpath(__file__))
-with open(direct + os.path.sep + 'stats.csv') as f:
+with open(direct + os.path.sep + 'stats-dc.csv') as f:
   r = csv.reader(f)
   for row in r:
     num_pods.append(row[0])
+    num_nodes.append(row[1])
+    sizes_raw.append(row[4])
+    sizes_compressed.append(row[5])
     tpp_total_mean.append(row[10])
     tpp_build_mean.append(row[13])
     tpp_minimize_mean.append(row[16])
@@ -25,8 +31,11 @@ with open(direct + os.path.sep + 'stats.csv') as f:
     tpp_gen_mean.append(row[22])
     tpp_compress_mean.append(row[25])
 
-# remove first row, and convert type
+# remove header info, and convert type
 num_pods = map(int, num_pods[2:])
+num_nodes = map(int, num_nodes[2:])
+sizes_raw = map(int, sizes_raw[2:])
+sizes_compressed = map(int, sizes_compressed[2:])
 tpp_total_mean = map(float, tpp_total_mean[2:])
 tpp_build_mean = map(float, tpp_build_mean[2:])
 tpp_minimize_mean = map(float, tpp_minimize_mean[2:])
@@ -34,17 +43,31 @@ tpp_order_mean = map(float, tpp_order_mean[2:])
 tpp_gen_mean = map(float, tpp_gen_mean[2:])
 tpp_compress_mean = map(float, tpp_compress_mean[2:])
 
+#====================================================
+# 
+# Stack plot of compilation times broken down by task
+#
+#====================================================
+
 # stack data lowest -> highest (build, minimize, order, gen, compress)
 data = (tpp_build_mean, tpp_minimize_mean, tpp_order_mean, tpp_gen_mean, tpp_compress_mean)
 foo = np.row_stack( data )
[…]

### 2016-01-24 paper/compilation.tex
adding preliminary graph for dc
Adding minor edits from feedback.

@@
 For example, the constraint 
-$$prefix=74.125.28.0/24 \mapsto (200 \cdot in \cdot in^*) \gg (100 \cdot in \cdot in^*)$$
+$$prefix=74.125.28.0/24 \mapsto (AS200 \cdot in \cdot in^*) \gg (AS100 \cdot in \cdot in^*)$$
 describes a more-preferred set of paths for traffic announced by a prefixes no less specific than $74.125.28.0/24$, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same.
@@
 Each preference-based regular path constraint (of the form $r_1 \gg \dots \gg r_j$) maps to a set of concrete paths in the network that match one of $r_i$.
-We denote a network path as a string of ASes of the form: $n_1 n_2 \dots n_k$, and we say regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$ and $p$ is a topologically-valid path.
+We denote a network path as a string of abstraction locations (routers or external ASes) of the form: $n_1 n_2 \dots n_k$, and we say regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$ and $p$ is a topologically-valid path.
 We denote the length of a path $p$ as $\abs{p}$.
@@
 
-\para{Propane to RIR}
+\para{Propane front-end to RIR}
 
@@
 
-To implement backups in routing, BGP uses local preferences on a per-device basis.
+To implement path preferences in routing, BGP uses local preferences on a per-device basis.
 However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult, particularly in the presence of failures.

### 2016-01-24 paper/background.tex

@@
 Another non-global attribute is the multi-exit discriminator (MED).
-It is used when an AS has more than one router-level link to a neighboring AS.
+It is used when an AS has multiple links to a neighboring AS.
 Its (numeric) values signal to the neighbor how this AS prefers to receive traffic among those links.
@@
 
+In implementing their policy, each network assumes that neighboring ASes correctly implement BGP and honor contracts related to MEDs and communities.
+While deriving configurations, \sysname makes a similar assumption.
+
 The combination of arbitrary import and export filters and route selection policies at individual routers make BGP a highly flexible routing protocol.

### 2016-01-24 data/graph.py
edits

@@ -73,12 +73,12 @@ color5 = "#DCB8CB"
 fig = plt.figure()
 plt.grid()
 ax1 = fig.add_subplot(111)
-ax1.fill_between(num_pods, 0, y_stack[0,:], facecolor=color1, alpha=.7)
-ax1.fill_between(num_pods, y_stack[0,:], y_stack[1,:], facecolor=color2, alpha=.7)
-ax1.fill_between(num_pods, y_stack[1,:], y_stack[2,:], facecolor=color3)
-ax1.fill_between(num_pods, y_stack[2,:], y_stack[3,:], facecolor=color4)
-ax1.fill_between(num_pods, y_stack[3,:], y_stack[4,:], facecolor=color5)
-ax1.set_xlabel('Fattree pod size')
+ax1.fill_between(num_nodes, 0, y_stack[0,:], facecolor=color1, alpha=.7)
+ax1.fill_between(num_nodes, y_stack[0,:], y_stack[1,:], facecolor=color2, alpha=.7)
+ax1.fill_between(num_nodes, y_stack[1,:], y_stack[2,:], facecolor=color3)
+ax1.fill_between(num_nodes, y_stack[2,:], y_stack[3,:], facecolor=color4)
+ax1.fill_between(num_nodes, y_stack[3,:], y_stack[4,:], facecolor=color5)
+ax1.set_xlabel('Data center size (routers)')
 ax1.set_ylabel('Time (sec)')
 # custom legend for stack color
 p1 = plt.Rectangle((0, 0), 1, 1, fc=color1, alpha=.7)
@@ -106,16 +106,16 @@ fig.savefig('compilation-time.png')
 #
 #====================================================
 
-num_pods1 = num_pods 
-num_pods2 = map(lambda x: x, num_pods)
+num_nodes1 = num_pods 
+num_nodes2 = map(lambda x: x, num_nodes)
 sizes_raw_per = map(lambda (size,n): size/n, zip(sizes_raw, num_nodes))
 sizes_compressed_per = map(lambda (size,n): size/n, zip(sizes_compressed, num_nodes))
 
 fig = plt.figure()
 ax1 = fig.add_subplot(111)
-ax1.bar(num_pods1, sizes_raw_per, width=.5, color=color1, alpha=1, align='center') # use log=true
-ax1.bar(num_pods2, sizes_compressed_per, width=.5, color=color3, alpha=1, align='center')
-ax1.set_xlabel('Fattree pod size')
[…]

### 2016-01-24 paper/motivation.tex
adding propane example 2 to paper.
Example 2 in paper. Better rule compression for memory reduction.
edits
draft merging of sec 3 and 4

@@
 
-We motivate our work by describing the current practice in network configuration.
+We motivate our work by describing the current practice in network 
+configuration.
 In traditional networks with distributed control planes, the operators' goal is to generate the configuration of individual devices based on their desired policy.
@@
 This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures.
-We illustrate this point using two examples based on policies that we have seen in practice.
+We illustrate this point using two examples based on policies that we have seen in practice and we demonstrate the ease with which the
+examples are described using our new language \sysname.
 
@@
 \end{figure}
+
+\subsection{Example 1:  The Backbone}
 
@@
 The operators must still do much of the conceptually difficult work manually, in coming up with the templates themselves.
-\sysname enables a direct expression of the policies of such networks and compiles them automatically to individual router configurations.
 
@@
 \end{figure}
+
+\para{The Backbone in \sysname}
+\sysname simplifies network configuration by allowing users to
+specify end-to-end forwarding paths and associating such paths with
+the appropriate prefixes.  The \sysname compiler handles the task of 
+generating low-level BGP configurations consistent with the user's
+end-to-end specifications.  It automatically synthesizes 
+import/export filters, local preference, MED attributes, and community tags 
+to ensure policy compliance under all possible failure scenarios.
+
+In general, \sysname specifications are written modularly via a series
+of user declarations.  
+%These definitions allow users to express the three
+%major elements of any \sysname specification:  \emph{prefixes}, 
+%\emph{paths} and \emph{policies}.  
+For example, to begin specification of the backbone
+network, we first express the idea that for routes leading to our customer,
+we prefer using $R_1$ over $R_2$ (Policy P3 from Figure~\ref{fig:example1}):
+\begin{lstlisting}[mathescape=true]
+define ExitCust = $exit(R_1 \gg R_2)$
+\end{lstlisting}
+The above statement defines a set of \emph{ranked paths}.
+Included in the set are all paths (and only those paths) that \cd{exit} 
+our network
+through either router $R_1$ or $R_2$.  The paths that exit through $R_1$
+are preferred ($\gg$) to the paths that exit through $R_2$.
+
+To associate ranked paths with
+one or more prefixes, we must define a \sysname \emph{policy}.  
+Within a policy, statements with the form $\path{x}{p}$
+associate the prefixes defined by the predicate $x$ with the set of 
+ranked paths defined by the path expression $p$.
+For instance, in the following code, ranked paths are associated with
+the customer prefixes ($C_{pfx}$), the internal prefixes ($I_{pfx}$),
+and all other prefixes (\cd{true}).\footnote{Policy statements are processed in
+order with earlier policy statements taking precedence over later
+policy statements.  Hence, when the prefix predicate \cd{true} follows
+statements involving $C_{pfx}$ and $I_{pfx}$, it is interpreted as
+$\cd{true} \AND \NOT C_{pfx} \AND \NOT I_{pfx}$.}
+
+\begin{lstlisting}[mathescape=true]
+define Routing = {
+    $\path{C_{pfx}}{ExitCust \gg end(Cust)}$
+    $\path{I_{pfx}}{end(in)}$
+    $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
+}
+\end{lstlisting}
+
+Line 2 of the policy above
+defines the paths that exit our network to customer prefixes ---
+\cd{ExitCust} defines paths through $R_1$ and $R_2$ and in the event
+that connections to the customer through both of those routers fail,
+a backup route ($end(Cust)$) is defined that admits traffic to go through
+any path that ends at the customer.  
+Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \cd{in} represents any location
+inside the user's network whereas the keyword \cd{out} represents any location
+outside the user's network.
+Line 4 applies to any other traffic, and allows for any routes that leave through a peer with a preference for customers over peers over providers.
+To summarize our progress so far, the \cd{Routing} policy
+implements (P1), (P3) and (P4) from Figure~\ref{fig:example1}
+
+Since, routing still allows transit traffic (e.g., traffic can enter from \textit{Peer} and leave through \textit{Prov}), we can define a new policy that
+implements this restriction separately.
+
+\begin{lstlisting}[mathescape=true]
+define PP = Peer or Prov
+define PPTransit = $enter(PP) \AND exit(PP)$
+define CustTransit = $later(Cust) \AND later(Prov)$
+
+define NoTransit = {
+    $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
+}
+\end{lstlisting}
+
+The \textsf{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied.
+In particular, it says that for any prefix, traffic should never both enter and exit the network from \textit{Peer} or \textit{Prov}.
+Similarly it prevents traffic from ever following paths that leave our network and later passing through both \textit{Prov} and \textit{Cust}.
+To implement both \cd{Routing}
+and \cd{NoTransit} simultaneously, we simply conjoin them:
+
+\begin{lstlisting}[mathescape=true]
+Routing $\AND$  NoTransit
+\end{lstlisting}
+
+\sysname will generate per-device import and export filters, local preferences, 
+MED attributes, and community tags to ensure that the policy is 
+implemented correctly under all failure scenarios.
+
+\subsection{Example 2:  The Data Center}
 
@@
 
-Thus, we see that devising configuration that ensures policy compliance in the face of failures is complex and error-prone.
+Thus, we see that devising a configuration that ensures policy compliance in the face of failures is complex and error-prone.
 \sysname helps operators by implementing their high-level policy specification in a way that guarantees compliance under all failures if that is possible.
@@
 For aggregation, it will also provide a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
+
+\para{The Data Center in \sysname}
+In our data center example, 
+there are primarily three main concerns: 
+(1) traffic for the prefix block allocated to each top-of-rack router must be able to reach that router, 
+(2) local services must not leak outside the datacenter, and 
+(3) aggregation must be performed on global prefixes to reduce churn 
+in the network.
+
+\sysname allows us to decompose and specify each of these constraints in a modular fashion.
+The first constraint is about prefix ownership -- namely, that we only want traffic for certain prefixes to end up at a particular locations.
+The following definition captures this intent.
+
+\begin{lstlisting}[mathescape=true]
+define Ownership = {
+    $\path{p_{g1}}{end(A)}$
+    $\path{p_{g2}}{end(B)}$
+    $\path{p_{l1}}{end(E)}$
+    $\path{p_{l2}}{end(F)}$
+}
+\end{lstlisting}
+
+In English: traffic for prefix $p_{g1}$ is only allowed to follow paths that 
+end at router A; traffic not matching $p_{g1}$, but which matches $p_{g2}$ must 
+end at router B; and so on.
+
+To capture the second constraint, we can define another task for the core 
+routing policy:
+
+\begin{lstlisting}[mathescape=true]
+define Routing = {
+    $\path{p_{g*}}{any}$
+    $\path{p_{l*}}{\NOT enter(out)}$
+    $\path{true}{exit(out)}$
+}
+\end{lstlisting}
+
+The first line states that there is no restriction (\cd{any})
+on how traffic must
+traverse the network for global prefixes, aside from the default restriction
+that traffic must not pass through the user's network and then loop
+back on itself. This means traffic for
+$p_{g*}$ may be sent either from other routers in the datacenter, or
+from external ASes. The second line ensures that traffic for local
+prefixes never enters the network from an outside location. This constraint
+guarantees that the services remain reachable only to locations
+internal to the data center.
+
+As in the backbone example, we can combine these constraints 
+logically to specify the network-wide policy.
+However, in addition to constraints on the shape of paths, 
+\sysname allows the operator to specify constraints on the BGP control plane. 
+For instance, a constraint on aggregation is included to ensure that 
+aggregation for $p_{agg}$ is performed from locations inside the network 
+to locations outside the network. \todo{Say more about aggregation here.
+What prefixes are aggregated in to what blocks?  How is this defined?}
+
+\begin{lstlisting}[mathescape=true]
+Ownership $\wedge$ Routing $\wedge$ agg($p_{agg}$, $in \rightarrow out$)
+\end{lstlisting}
+
+As before, once \sysname compiles the policy, it is guaranteed to hold under 
+all possible failure scenarios. In addition, the system can check for 
+aggregate-induced black holes in the presence of up to $k$ failures. 
+\todo{Note:  Another comment about failure checking for black holes, which may
+not be implemented yet.}
 

### 2016-01-24 paper/evaluation.tex
adding preliminary graph for dc
added preliminary config compression results for dc
checking in changes

@@
 \section{Evaluation}
-
-We have written a prototype compiler for \sysname that is implemented in roughly 5000 lines of F\# code.
-The compiler includes command-line flags for enabling or disabling the use of BGP MED, AS path prepending, the commonly used no-export community, as well as for ensuring k-failure safety for user-sepcified aggregates.
-The compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct automata for large alphabets efficiently.
-The compiler uses the algorithm for computing graph dominators described in~\ref{bib:todo}.
-When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the ``can prefer'' relation.
-\todo{this needs work}
 
@@
 We evaluate our compiler by measuring compilation times for these policies across topologies of different sizes.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{figures/compilation-times-dc.png}
+\label{fig:compilation-times-dc}
+\caption{Data center compilation times.}
+\end{figure}
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{figures/config-compression-dc.png}
+\label{fig:compilation-compression-dc}
+\caption{Data center config minimization.}
+\end{figure}

### 2016-01-24 paper/implementation.tex
starting implementation section
checking in changes

--- 2016-01-23 paper/evaluation.tex
@@
-\section{Evaluation}
+\section{Implementation}
 
-We have written a prototype compiler for \sysname that is implemented in roughly 5000 lines of F\# code.
-The compiler includes command-line flags for enabling or disabling the use of BGP MED, AS path prepending, the commonly used no-export community, as well as for ensuring k-failure safety for user-sepcified aggregates.
-The compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct automata for large alphabets efficiently.
-The compiler uses the algorithm for computing graph dominators described in~\ref{bib:todo}.
-When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the ``can prefer'' relation.
-\todo{this needs work}
+We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code.
+The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-sepcified aggregates.
+Users see only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}.
+
+\para{PG construction}
+
+Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\ref{bib:todo}.
+Our \sysname compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently.
+Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy.
+Similarly, to model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.
+
+Rather than construct the product graph in full, our implementation prevents exploring parts of the graph when no accepting state is reachable in any of the corresponding regular automata during construction.
+
+\para{PG Minimization}
+
+Our compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\ref{bib:todo}.
+
+When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the ``can prefer'' relation. \todo{this needs work}
 

### 2016-01-24 paper/theory.tex
checking in changes

--- 2016-01-23 paper/expressiveness.tex
@@
 In this section we investigate the correctness and expressiveness properties of \sysname.
-We are mainly concerned with the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures?
+We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures?
 (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?
 
-\subsection{Expressiveness}
+%\subsection{Expressiveness}
+%
+%Models for BGP are traditionally given as per-device ranked paths where the configuration of each device is known ahead of time.
+For example router $r_1$ might have a first preference of $r_1 \cdot r_2 \cdot d$ and a second preference of $r_1 \cdot d$.
+Similarly, $r_2$ might have a first preference of $r_2 \cdot d$, and no other preference.
+Against this model of BGP we have the following.
+%
+%\begin{defn}
+%Any policy expressible in BGP is expressible in \sysname.
+%\end{defn}
+%
+%The proof of this is straightforward.
+Simply take the union of each router's rank 1 path, and make that the new most-prefered route in \sysname, and so on.
+For example, the above preferences would be encoded as:
+%$$(r_1 \cdot r_2 \cdot d) \cup (r_2 \cdot d) \gg (r_1 \cdot d) $$
+%Since the semantics of \sysname is such that each unique starting-ending locations should get their most-preferred path.
 
-Models for BGP are traditionally given over per-device ranked paths 
-In this section, we describe the expressiveness of \sysname.
-
-\begin{defn}
-
-\end{defn}
+%\todo{I'm not sure if this is true}.
 
@@
 \begin{defn}
-A distributed BGP configuration is \textit{Sound} with respect to a \sysname policy, if the only routes that that traffic ever takes in the network, are those that are specified in the policy.
+A distributed BGP configuration is \textit{Sound} with respect to a \sysname policy, if the any route traffic takes in the network, is a valid route specified in the policy.
 \end{defn}
@@
 The Soundness claim follows directly from compilation of the product graph.
-Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations will be Sound.
+Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations are Sound.
 
 \begin{defn}
-A distributed BGP configuration is \textit{Complete} with respect to a \sysname policy, if the distributed implementation always obtains a most preferred route between two nodes if the corresponding path exists in the network.
+A distributed BGP configuration is \textit{Complete} with respect to a \sysname policy, if the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
 \end{defn}
@@
 Assume we are unable to achieve this route in the network.
-To not achieve this path means that some router along advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead.
-This implies that that router that makes the ``wrong'' choice appears as a separate node in the product graph.
-However, from our failure safety check, we know that the other, more-preferred node must have a superset of the paths to accepting states as the less preferred node has for at least as good of a final preference.
-However, this implies that a route advertisement will still reach $X$, resulting in a path with a preference between $X$ and $Y$ that is just as good.
+To not achieve this path means that some router along the advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead.
+This implies that router that makes the ``wrong'' choice appears as a separate node in the product graph.
+However, from our failure safety check, we know that the other, more-preferred node must have a superset of the paths to accepting states as the less preferred node (from which it stole the route) for at least as good of a final preference.
+The argument then proceeds by induction on the path length - there are only a finite number of such stealings that can occur, each of which will ultimately still result in a route advertisement reaching $X$ along a most preferred path.
 
-The combination of Soundness and Completeness ensures that the distributed implementation will always achieve the best routes possible, yet will never also achieve unwanted routes.
+The combination of Soundness and Completeness ensures that the distributed implementation will always achieve the best routes possible, yet will never also use any unwanted routes.
 

### 2016-01-24 paper/implementation.tex
added basic implementation section

@@
 Our compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\ref{bib:todo}.
+More complex algorithms with better theoretical complexity exist~\ref{bib:todo} and may be better for large enough examples.
+However, we have not found minimization to be a bottleneck in our implementation.
+Minimization steps are ordered from cheapest to most expensive.
+All minimization steps are repeated until no more progress can be made.
 
-When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the ``can prefer'' relation. \todo{this needs work}
+\para{Failure Safety}
 
-We have evaluated our compiler by translating and compiling real-world network configurations for data centers and a core backbone network into \sysname.
-We evaluate our compiler by measuring compilation times for these policies across topologies of different sizes.
+When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the ``can prefer'' relation.
+That is, whenever for two states $n_1$ and $n_2$ we compute $protect(G_j, n_1, G_i, n_2)$, if the function evaluates to $true$, then each of the intermediate related states $x$ and $y$ must also satisfy $protect(G_j, x, G_i, y)$.
+Memoizing these states significantly cuts down the amount of work that needs to be in the common case.
 
-\begin{figure}[t!]
-\centering
-\includegraphics[width=\columnwidth]{figures/compilation-times-dc.png}
-\label{fig:compilation-times-dc}
-\caption{Data center compilation times.}
-\end{figure}
+\para{Configuration generation}
 
-\begin{figure}[t!]
-\centering
-\includegraphics[width=\columnwidth]{figures/config-compression-dc.png}
-\label{fig:compilation-compression-dc}
-\caption{Data center config minimization.}
-\end{figure}
+The naive code generation algorithm described in Section~\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair in the product graph before minimization.
+Our implementation performs partial minimization during generation by recognizing cases where there is no restriction on exporting or importing from neighbors to avoid enumerating such cases.

### 2016-01-25 paper/compilation.tex
fixing bug with MEDs on external ASes

@@
 
+\newcommand{\highlight}[1]{%
+  \colorbox{red!50}{$\displaystyle#1$}}
 \newcommand{\Router}[1]{ \textbf{Router #1:} }
@@
            $\MED \leftarrow 81, \PEER \leftarrow W$
-$\Router{C}$
+$\Router{C}$-
   Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $

### 2016-01-25 data/graph.py

@@ -106,15 +106,15 @@ fig.savefig('compilation-time.png')
 #
 #====================================================
 
-num_nodes1 = num_pods 
-num_nodes2 = map(lambda x: x, num_nodes)
+num_nodes1 = num_nodes 
+num_nodes2 = map(lambda x: x-20, num_nodes)
 sizes_raw_per = map(lambda (size,n): size/n, zip(sizes_raw, num_nodes))
 sizes_compressed_per = map(lambda (size,n): size/n, zip(sizes_compressed, num_nodes))
 
 fig = plt.figure()
 ax1 = fig.add_subplot(111)
-ax1.bar(num_nodes1, sizes_raw_per, width=.5, color=color1, alpha=1, align='center') # use log=true
-ax1.bar(num_nodes2, sizes_compressed_per, width=.5, color=color3, alpha=1, align='center')
+ax1.bar(num_nodes1, sizes_raw_per, width=20, color=color1, alpha=1, align='center') # use log=true
+ax1.bar(num_nodes2, sizes_compressed_per, width=20, color=color3, alpha=1, align='center')
 ax1.set_xlabel('Data center size (routers)')
 ax1.set_ylabel('Config Size (lines of ABGP per router)')
 leg_boxes = [p1, p3]

### 2016-01-25 paper/background.tex
shortened motivation

@@
 
-Our work focuses on BGP as it is the most common and flexible way to implement distributed control planes today. In this section, we provide relevant background on BGP.
+%Our work focuses on BGP as it is the most common and flexible way to implement distributed control planes today. In this section, we provide relevant background on BGP.
 
@@
 An AS has one or more routers managed by the same administrative entity.
-ASes exchange routing announcements with their neighboring ASes.
-Each announcement has a destination IP prefix and some attributes (see below), and it indicates that the sending AS is willing to carry traffic to that prefix from the receiving AS.
+ASes exchange routing announcements with their neighbors.
+Each announcement has a destination IP prefix and some attributes (see below), and it indicates that the sending AS is willing to carry traffic destined to that prefix from the receiving AS.
 Traffic flows in the opposite direction, from announcement receivers to senders.

### 2016-01-25 paper/motivation.tex
shortened motivation

@@
-\section{Motivation}
+\section{Motivation and Propane overview}
 \label{sec:motivation}
 
-We motivate our work by describing the current practice in network 
-configuration.
+%We motivate our work by describing the current practice in network
+%configuration.
 In traditional networks with distributed control planes, the operators' goal is to generate the configuration of individual devices based on their desired policy.
@@
 The collective behavior of the devices should implement the desired policy.
-
-Device configuration languages are low-level and indirect.
+%
+%Device configuration languages are low-level and indirect.
 For instance, instead of allowing operators to express directly the paths they want through the network, they require operators to specify metrics that result in those paths; instead of allowing operators to express directly the types of traffic to not carry through the network, they require operators to select and program an appropriate filtering mechanism (e.g., BGP import or export filters, null routing,  access control lists) and instantiate it on topologically appropriate devices; instead of allowing operators to directly specify that they prefer BGP neighbors in a certain order, they require operators to program local preferences and multi-exit discriminators (MED) at each router and ensure that the numbers are consistent across routers.
-
-In many networks today, device configurations are generated manually by operators, without the support of many automated tools.
+%
+%In many networks today, device configurations are generated manually by operators, without the support of many automated tools.
 It is easy to see the problems with this approach, such as typos, inconsistency across devices, and no guarantees of policy compliance.
-
-To reduce such problems, some networks use a template-based approach.
+%
+%To reduce such problems, some networks use a template-based approach.
 Configuration templates abstract certain constants into variables (e.g., instead of concrete community value, they may contain a variable {\small \sf{\$$BadNeighbor$)}} and may use a device vendor-neutral syntax.
 Operators manually generate the templates and use tools to translate them into device configuration, by replacing variables with appropriate constants using a database of network information.
-
- %and replacing vendor-neutral constructs with their vendor-specific counterparts.
-
-%In practice, most networks use a hybrid of templates and manual generation of device configuration.
+%
+% %and replacing vendor-neutral constructs with their vendor-specific counterparts.
+%
+%%In practice, most networks use a hybrid of templates and manual generation of device configuration.
 Templates are used for standardized and common configuration elements across devices and the result is manually tweaked to obtain the exact desired network behavior.
-
-While templates avoids some pitfalls of the fully manual approach, they too are far from ideal.
+%
+%While templates avoids some pitfalls of the fully manual approach, they too are far from ideal.
 The fundamental issue is the semantic mismatch between desired policies and the level of abstraction of templates.
@@
 Operators must still manually decompose network-wide policies into device-level policies that can produce the desired network-wide behavior.
+%This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures.
+We illustrate this point using two examples based on policies that we have seen in practice and we demonstrate the ease with which the
+%examples are described using our new language \sysname.
+
+In networks with distributed control planes, the operators today generate the configuration of individual devices based on intended policy.
+Whether this task is done fully manually or with the aid of templates, the challenge is to decompose network-wide policies
+%(e.g., prefer customer networks, or never announce a route to a certain prefix to external neighbors), 
+into device-level policies that collectively produce the intended behavior.
 This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures.
-We illustrate this point using two examples based on policies that we have seen in practice and we demonstrate the ease with which the
-examples are described using our new language \sysname.
+We illustrate this point using two examples based on policies that we have seen in practice.
+We also demonstrate the ease with which the
+policies can be specified using our new language \sysname. The next section describes how to automatically compile this specification to device-level policies.
 
@@
 The policy of this network is shown on the right.
-Per commercial relationships, it prefers the neighbors in a certain order ($P1$) and does not want to act as a transit between Peer and Prov ($P2$).
-It prefers to exchange traffic with Cust over $R1$ rather than $R2$ because $R2$ is a more expensive link ($P3$).
-To guard against another AS "hijacking" prefixes owned by Cust, it only sends traffic to those prefixes if Cust is on the AS path ($P4$).
+It prefers the neighbors in a certain order ($P1$) and does not want to act as a transit between Peer and Prov ($P2$).
+It prefers to exchange traffic with Cust over $R1$ rather than $R2$ because $R1$ is a cheaper ($P3$).
+To guard against another AS "hijacking" prefixes owned by Cust, it only sends traffic to them if Cust is on the AS path ($P4$).
 Finally, to guard against Cust accidentally becoming a transit for Prov, it does not use Cust for traffic that will later traverse Prov ($P5$).
 
-To correctly implement this network's policy, the operators must compute and assign local preferences such that preferences at Cust-facing interfaces $>$ Peer-facing interfaces $>$ Prov-facing interfaces.
+To correctly implement this policy, the operators must compute and assign local preferences such that preferences at Cust-facing interfaces $>$ Peer-facing interfaces $>$ Prov-facing interfaces.
 At the same time, the preference at $R2$'s Cust-facing interface should be lower than that at $R1$, but higher than that at Prov-facing interface.
@@
 
-We can now see that devising correct configuration for real, larger networks will quickly become a nightmare.
-These networks will have many neighbors across multiple classes of commercial relationships, differing numbers of links per neighbor, along with several region-, neighbor- or prefix-based exceptions to the default policy.
-Templates only help to certain extent, e.g., by keeping preference and community values consistent across routers.
-The operators must still do much of the conceptually difficult work manually, in coming up with the templates themselves.
+We can now see how devising correct configuration for real, larger networks will quickly become a nightmare.
+The networks will have many neighbors across multiple classes of commercial relationships, differing numbers of links per neighbor, along with several region-, neighbor- or prefix-based exceptions to the default behavior.
+Templates help by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually.
+%, in coming up with the templates themselves.
 
@@
 \sysname simplifies network configuration by allowing users to
-specify end-to-end forwarding paths and associating such paths with
-the appropriate prefixes.  The \sysname compiler handles the task of 
+specify end-to-end forwarding paths and associating them with
+appropriate prefixes.  The \sysname compiler handles the task of
 generating low-level BGP configurations consistent with the user's
-end-to-end specifications.  It automatically synthesizes 
-import/export filters, local preference, MED attributes, and community tags 
+specifications.  It automatically synthesizes
+import-export filters, local preferences, MED attributes, and community tags
 to ensure policy compliance under all possible failure scenarios.
@@
 \end{lstlisting}
-The above statement defines a set of \emph{ranked paths}.
-Included in the set are all paths (and only those paths) that \cd{exit} 
+The  statement above defines a set of \emph{ranked paths}, which includes
+all paths (and only those paths) that \cd{exit}
 our network
@@
 
-\todo{remove if we do not discuss aggregation in the design}
 To avoid this problem, the operator may decide to disallow paths with "valleys," i.e., those that go up, down, and back up again.

### 2016-01-25 paper/motivation.tex
shortened motivation
divorcing motivation and propane

@@
-\section{Motivation and Propane overview}
+\section{Motivation}
 \label{sec:motivation}
@@
 
-In networks with distributed control planes, the operators today generate the configuration of individual devices based on intended policy.
+Operators today generate the BGP configuration of individual devices based on intended policy.
 Whether this task is done fully manually or with the aid of templates, the challenge is to decompose network-wide policies
@@
 We illustrate this point using two examples based on policies that we have seen in practice.
-We also demonstrate the ease with which the
-policies can be specified using our new language \sysname. The next section describes how to automatically compile this specification to device-level policies.
+%In the next section, we demonstrate the ease with which the
+%policies can be specified using our new language \sysname.
+%The next section describes how to automatically compile this specification to device-level policies.
 
@@
 
-We can now see how devising correct configuration for real, larger networks will quickly become a nightmare.
-The networks will have many neighbors across multiple classes of commercial relationships, differing numbers of links per neighbor, along with several region-, neighbor- or prefix-based exceptions to the default behavior.
+We can now see how devising correct configurations for real, larger networks can be a nightmare.
+Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several geography-, neighbor- or prefix-based exceptions to the default behavior.
 Templates help by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually.
-%, in coming up with the templates themselves.
+\sysname lets operator express such policies easily and intuitively.
+It them automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.
 
@@
 \end{figure}
-
-\para{The Backbone in \sysname}
-\sysname simplifies network configuration by allowing users to
-specify end-to-end forwarding paths and associating them with
-appropriate prefixes.  The \sysname compiler handles the task of
-generating low-level BGP configurations consistent with the user's
-specifications.  It automatically synthesizes
-import-export filters, local preferences, MED attributes, and community tags
-to ensure policy compliance under all possible failure scenarios.
-
-In general, \sysname specifications are written modularly via a series
-of user declarations.
-%These definitions allow users to express the three
-%major elements of any \sysname specification:  \emph{prefixes},
-%\emph{paths} and \emph{policies}.
-For example, to begin specification of the backbone
-network, we first express the idea that for routes leading to our customer,
-we prefer using $R_1$ over $R_2$ (Policy P3 from Figure~\ref{fig:example1}):
-\begin{lstlisting}[mathescape=true]
-define ExitCust = $exit(R_1 \gg R_2)$
-\end{lstlisting}
-The  statement above defines a set of \emph{ranked paths}, which includes
-all paths (and only those paths) that \cd{exit}
-our network
-through either router $R_1$ or $R_2$.  The paths that exit through $R_1$
-are preferred ($\gg$) to the paths that exit through $R_2$.
-
-To associate ranked paths with
-one or more prefixes, we must define a \sysname \emph{policy}.
-Within a policy, statements with the form $\path{x}{p}$
-associate the prefixes defined by the predicate $x$ with the set of
-ranked paths defined by the path expression $p$.
-For instance, in the following code, ranked paths are associated with
-the customer prefixes ($C_{pfx}$), the internal prefixes ($I_{pfx}$),
-and all other prefixes (\cd{true}).\footnote{Policy statements are processed in
-order with earlier policy statements taking precedence over later
-policy statements.  Hence, when the prefix predicate \cd{true} follows
-statements involving $C_{pfx}$ and $I_{pfx}$, it is interpreted as
-$\cd{true} \AND \NOT C_{pfx} \AND \NOT I_{pfx}$.}
-
-\begin{lstlisting}[mathescape=true]
-define Routing = {
-    $\path{C_{pfx}}{ExitCust \gg end(Cust)}$
-    $\path{I_{pfx}}{end(in)}$
-    $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
-}
-\end{lstlisting}
-
-Line 2 of the policy above
-defines the paths that exit our network to customer prefixes ---
-\cd{ExitCust} defines paths through $R_1$ and $R_2$ and in the event
-that connections to the customer through both of those routers fail,
-a backup route ($end(Cust)$) is defined that admits traffic to go through
-any path that ends at the customer.
-Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \cd{in} represents any location
-inside the user's network whereas the keyword \cd{out} represents any location
-outside the user's network.
-Line 4 applies to any other traffic, and allows for any routes that leave through a peer with a preference for customers over peers over providers.
-To summarize our progress so far, the \cd{Routing} policy
-implements (P1), (P3) and (P4) from Figure~\ref{fig:example1}
-
-Since, routing still allows transit traffic (e.g., traffic can enter from \textit{Peer} and leave through \textit{Prov}), we can define a new policy that
-implements this restriction separately.
-
-\begin{lstlisting}[mathescape=true]
-define PP = Peer or Prov
-define PPTransit = $enter(PP) \AND exit(PP)$
-define CustTransit = $later(Cust) \AND later(Prov)$
-
-define NoTransit = {
-    $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
-}
-\end{lstlisting}
-
-The \textsf{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied.
-In particular, it says that for any prefix, traffic should never both enter and exit the network from \textit{Peer} or \textit{Prov}.
-Similarly it prevents traffic from ever following paths that leave our network and later passing through both \textit{Prov} and \textit{Cust}.
-To implement both \cd{Routing}
-and \cd{NoTransit} simultaneously, we simply conjoin them:
-
-\begin{lstlisting}[mathescape=true]
-Routing $\AND$  NoTransit
-\end{lstlisting}
-
-\sysname will generate per-device import and export filters, local preferences,
-MED attributes, and community tags to ensure that the policy is
-implemented correctly under all failure scenarios.
 
@@
 \sysname helps operators by implementing their high-level policy specification in a way that guarantees compliance under all failures if that is possible.
-Otherwise, it generates a compile-time error that informs them that the specification cannot be met.
-For aggregation, it will also provide a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
-
-\para{The Data Center in \sysname}
-In our data center example,
-there are primarily three main concerns:
-(1) traffic for the prefix block allocated to each top-of-rack router must be able to reach that router,
-(2) local services must not leak outside the datacenter, and
-(3) aggregation must be performed on global prefixes to reduce churn
-in the network.
-
-\sysname allows us to decompose and specify each of these constraints in a modular fashion.
-The first constraint is about prefix ownership -- namely, that we only want traffic for certain prefixes to end up at a particular locations.
-The following definition captures this intent.
-
-\begin{lstlisting}[mathescape=true]
-define Ownership = {
-    $\path{p_{g1}}{end(A)}$
-    $\path{p_{g2}}{end(B)}$
-    $\path{p_{l1}}{end(E)}$
-    $\path{p_{l2}}{end(F)}$
-}
-\end{lstlisting}
-
-In English: traffic for prefix $p_{g1}$ is only allowed to follow paths that
-end at router A; traffic not matching $p_{g1}$, but which matches $p_{g2}$ must
-end at router B; and so on.
-
-To capture the second constraint, we can define another task for the core
-routing policy:
-
-\begin{lstlisting}[mathescape=true]
-define Routing = {
-    $\path{p_{g*}}{any}$
-    $\path{p_{l*}}{\NOT enter(out)}$
-    $\path{true}{exit(out)}$
-}
-\end{lstlisting}
-
-The first line states that there is no restriction (\cd{any})
-on how traffic must
-traverse the network for global prefixes, aside from the default restriction
-that traffic must not pass through the user's network and then loop
-back on itself. This means traffic for
-$p_{g*}$ may be sent either from other routers in the datacenter, or
-from external ASes. The second line ensures that traffic for local
-prefixes never enters the network from an outside location. This constraint
-guarantees that the services remain reachable only to locations
-internal to the data center.
-
-As in the backbone example, we can combine these constraints
-logically to specify the network-wide policy.
-However, in addition to constraints on the shape of paths,
-\sysname allows the operator to specify constraints on the BGP control plane.
-For instance, a constraint on aggregation is included to ensure that
-aggregation for $p_{agg}$ is performed from locations inside the network
-to locations outside the network. \todo{Say more about aggregation here.
-What prefixes are aggregated in to what blocks?  How is this defined?}
-
-\begin{lstlisting}[mathescape=true]
-Ownership $\wedge$ Routing $\wedge$ agg($p_{agg}$, $in \rightarrow out$)
-\end{lstlisting}
-
-As before, once \sysname compiles the policy, it is guaranteed to hold under
-all possible failure scenarios. In addition, the system can check for
-aggregate-induced black holes in the presence of up to $k$ failures.
-\todo{Note:  Another comment about failure checking for black holes, which may
-not be implemented yet.}
+(Otherwise, it generates a compile-time error that informs them that the specification cannot be met.) For aggregation, it will also provide a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
 

### 2016-01-25 paper/propane.tex
divorcing motivation and propane

--- 2016-01-18 paper/propane.tex
@@
-\section{Propane}
+\section{Propane overview}
 \label{sec:propane}
 
-\sysname simplifies network configuration by automatically generating low-level BGP configurations from a high-level specification of the network's routing policy. 
+\sysname simplifies network configuration by automatically generating low-level BGP configurations from a high-level specification of routing policy.
 %
+%
+We introduce \sysname by expressing the policies for the two examples above.
+%
+The next section describes how we compile such policies to BGP.
+
+\subsection{Example 1: The Backbone}
+
+%\sysname simplifies network configuration by allowing users to
+%specify end-to-end forwarding paths and associating them with
+%appropriate prefixes.  The \sysname compiler handles the task of
+%generating low-level BGP configurations consistent with the user's
+%specifications.  It automatically synthesizes
+%import-export filters, local preferences, MED attributes, and community tags
+%to ensure policy compliance under all possible failure scenarios.
+
 The operator configures the network with the abstraction that he or she has centralized control over routing and uses a set of high-level constraints to describe the different routes traffic may (or may not) take and their relative preferences.
-%
-The \sysname compiler generates BGP configurations for each device in the network that operate in a completely distributed fashion and are correct by construction -- automatically synthesizing import/export filters, local preference and MED attributes, and community tags to ensure policy compliance under all possible failure scenarios.
-%
-We now demonstrate \sysname by showing how to configure the networks from the previous examples.
+In general, \sysname specifications are written modularly via a series
+of user declarations.
+%These definitions allow users to express the three
+%major elements of any \sysname specification:  \emph{prefixes},
+%\emph{paths} and \emph{policies}.
+For example, to begin specification of the backbone
+network, we first express the idea that for routes leading to our customer,
+we prefer using $R_1$ over $R_2$ (Policy P3 from Figure~\ref{fig:example1}):
+\begin{lstlisting}[mathescape=true]
+define ExitCust = $exit(R_1 \gg R_2)$
+\end{lstlisting}
+The  statement above defines a set of \emph{ranked paths}, which includes
+all paths (and only those paths) that \cd{exit}
+our network
+through either router $R_1$ or $R_2$.  The paths that exit through $R_1$
+are preferred ($\gg$) to the paths that exit through $R_2$.
 
-\example{1}
+To associate ranked paths with
+one or more prefixes, we must define a \sysname \emph{policy}.
+Within a policy, statements with the form $\path{x}{p}$
+associate the prefixes defined by the predicate $x$ with the set of
+ranked paths defined by the path expression $p$.
+For instance, in the following code, ranked paths are associated with
+the customer prefixes ($C_{pfx}$), the internal prefixes ($I_{pfx}$),
+and all other prefixes (\cd{true}).\footnote{Policy statements are processed in
+order with earlier policy statements taking precedence over later
+policy statements.  Hence, when the prefix predicate \cd{true} follows
+statements involving $C_{pfx}$ and $I_{pfx}$, it is interpreted as
+$\cd{true} \AND \NOT C_{pfx} \AND \NOT I_{pfx}$.}
 
-\example{2}
+\begin{lstlisting}[mathescape=true]
+define Routing = {
+    $\path{C_{pfx}}{ExitCust \gg end(Cust)}$
+    $\path{I_{pfx}}{end(in)}$
+    $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
+}
+\end{lstlisting}
 
-Consider again the datacenter from Section~\ref{sec:motivation}.
-In this example, there are primarily three main concerns: (1) traffic for the prefix block allocated to each top-of-rack router can reach that router, (2) local services do not leak outside the datacenter, and (3) aggregation is performed on global prefixes to reduce churn in the network.
+Line 2 of the policy above
+defines the paths that exit our network to customer prefixes ---
+\cd{ExitCust} defines paths through $R_1$ and $R_2$ and in the event
+that connections to the customer through both of those routers fail,
+a backup route ($end(Cust)$) is defined that admits traffic to go through
+any path that ends at the customer.
+Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \cd{in} represents any location
+inside the user's network whereas the keyword \cd{out} represents any location
+outside the user's network.
+Line 4 applies to any other traffic, and allows for any routes that leave through a peer with a preference for customers over peers over providers.
+To summarize our progress so far, the \cd{Routing} policy
+implements (P1), (P3) and (P4) from Figure~\ref{fig:example1}
+
+Since, routing still allows transit traffic (e.g., traffic can enter from \textit{Peer} and leave through \textit{Prov}), we can define a new policy that
+implements this restriction separately.
+
+\begin{lstlisting}[mathescape=true]
+define PP = Peer or Prov
+define PPTransit = $enter(PP) \AND exit(PP)$
+define CustTransit = $later(Cust) \AND later(Prov)$
+
+define NoTransit = {
+    $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
+}
+\end{lstlisting}
+
+The \textsf{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied.
+In particular, it says that for any prefix, traffic should never both enter and exit the network from \textit{Peer} or \textit{Prov}.
+Similarly it prevents traffic from ever following paths that leave our network and later passing through both \textit{Prov} and \textit{Cust}.
+To implement both \cd{Routing}
+and \cd{NoTransit} simultaneously, we simply conjoin them:
+
+\begin{lstlisting}[mathescape=true]
+Routing $\AND$  NoTransit
+\end{lstlisting}
+
+The lines above capture the entire policy. From it, \sysname will generate per-device import and export filters, local preferences,
+MED attributes, and community tags to ensure that the policy is
+implemented correctly under all failure cases.
+
+\subsection{Example 2: The Data Center}
+
+In our data center example,
+there are primarily three main concerns:
+(1) traffic for the prefix block allocated to each top-of-rack router must be able to reach that router,
+(2) local services must not leak outside the datacenter, and
+(3) aggregation must be performed on global prefixes to reduce churn
+in the network.
 
@@
 The first constraint is about prefix ownership -- namely, that we only want traffic for certain prefixes to end up at a particular locations.
-The following definition in propane captures this intent:
+The following definition captures this intent.
 
@@
 
-The constraints in the ownership task are read in a top-down fashion.
-Traffic for prefix $p_{g1}$ is only allowed to to follow paths that end at router A.
-Similarly, traffic not matching $p_{g1}$, but which matches $p_{g2}$ must end at router B and so on.
-%
-To capture the second constraint, we can define another task for the core routing policy:
+In English: traffic for prefix $p_{g1}$ is only allowed to follow paths that
+end at router A; traffic not matching $p_{g1}$, but which matches $p_{g2}$ must
+end at router B; and so on.
+
+To capture the second constraint, we can define another task for the core
+routing policy:
 
@@
     $\path{p_{g*}}{any}$
-    $\path{p_{l*}}{\neg enter(out)}$
+    $\path{p_{l*}}{\NOT enter(out)}$
     $\path{true}{exit(out)}$
@@
 
-The first line states that there is no restriction on how traffic must traverse the network for global prefixes.
-This means traffic for $p_{g*}$ may be sent either from other routers in the datacenter, or from external ASes.
-The second line ensures that traffic for local prefixes never enters the network from an outside location.
-This  guarantees that the services remain reachable only to locations internal to the data center.
+The first line states that there is no restriction (\cd{any})
+on how traffic must
+traverse the network for global prefixes, aside from the default restriction
+that traffic must not pass through the user's network and then loop
+back on itself. This means traffic for
+$p_{g*}$ may be sent either from other routers in the datacenter, or
+from external ASes. The second line ensures that traffic for local
+prefixes never enters the network from an outside location. This constraint
+guarantees that the services remain reachable only to locations
+internal to the data center.
 
-Finally, we can combine these constraints logically to specify the network-wide policy.
+As in the backbone example, we can combine these constraints
+logically to specify the network-wide policy.
+However, in addition to constraints on the shape of paths,
+\sysname allows the operator to specify constraints on the BGP control plane.
+For instance, a constraint on aggregation is included to ensure that
+aggregation for $p_{agg}$ is performed from locations inside the network
+to locations outside the network. \todo{Say more about aggregation here.
+What prefixes are aggregated in to what blocks?  How is this defined?}
 
@@
 
-In addition to constraints on the shape of paths, \sysname allows the operator to specify constraints on the BGP control plane.
+As before, once \sysname compiles the policy, it is guaranteed to hold under
+all possible failure scenarios. In addition, the system can check for
+aggregate-induced black holes in the presence of up to $k$ failures.
+\todo{Note:  Another comment about failure checking for black holes, which may
+not be implemented yet.}
+
+%%%%OLD TEXT BELOW
+%
+%\section{Propane}
+%\label{sec:propane}
+%
+%\sysname simplifies network configuration by automatically generating low-level BGP configurations from a high-level specification of the network's routing policy.
+%%
+%The operator configures the network with the abstraction that he or she has centralized control over routing and uses a set of high-level constraints to describe the different routes traffic may (or may not) take and their relative preferences.
+%%
+%The \sysname compiler generates BGP configurations for each device in the network that operate in a completely distributed fashion and are correct by construction -- automatically synthesizing import/export filters, local preference and MED attributes, and community tags to ensure policy compliance under all possible failure scenarios.
+%%
+%We now demonstrate \sysname by showing how to configure the networks from the previous examples.
+%
+%\para{Example 1}
+%
+%We now show how to write the routing policy for the backbone network in Section~\ref{sec:motivation}.
+\sysname allows to address each of the requirements in turn.
+First we address requirements (P1), (P3), and (P4) that customers are preferred over peers over providers, and that a customer appear on the path for its prefix.
+The following \sysname code accomplishes these two objectives:
+%
+%\begin{lstlisting}[mathescape=true]
+%define ExitCust = $exit(R_1 \gg R_2)$
+%
+%define Routing = {
+%    $\path{C_{pfx}}{ExitCust \gg end(Cust) }$
+%    $\path{I_{pfx}}{end(in)}$
+%    $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
+%}
+%\end{lstlisting}
+%
+%The first definition defines paths that exit our network to the customer.
+The statement $exit(R_1 \gg R_2)$ restricts us to paths that leave our network through either router $R_1$ or $R_2$, with a preference for $R_1$.
+%The first line of the \textsf{Routing} policy ensures that traffic destined for customer prefixes ($C_{pfx}$) either leaves the network directly to the customer (with a preference for leaving through $R_1$), or simply ends at the customer.
+Not leaving directly to the customer by going through \textit{Peer} or \textit{Prov} is less preferred than leaving directly, and thus serves as a backup route in a direct route is not available.
+%
+%The second line state that traffic for internal prefixes $I_{pfx}$ must end in our network, and is otherwise unconstrained.
+The last line applies to any other traffic, and allows for any routes that leave through a peer with a preference for customers over peers over providers.
+While this still allows transit traffic (e.g., traffic can enter from \textit{Peer} and leave through \textit{Prov}), we can restrict this behavior separately as follows:
+%
+%\begin{lstlisting}[mathescape=true]
+%define PP = Peer or Prov
+%define PPTransit = $enter(PP) \wedge exit(PP)$
+%define CustTransit = $later(Cust) \wedge later(Prov)$
+%
+%define NoTransit = {
+%    $\path{true}{\neg PPTransit \wedge \neg CustTransit}$
+%}
+%\end{lstlisting}
+%
+%The \textsf{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied.
+In particular, it says that, for any prefix, traffice should never both enter and exit the network from \textit{Peer} or \textit{Prov}.
+Similarly it prevents traffic from ever following paths that leave our network and later go through both \textit{Prov} and \textit{Cust}.
+%
+%\begin{lstlisting}[mathescape=true]
+%Routing $\wedge$  NoTransit
+%\end{lstlisting}
+%
+%The final policy is simply the conjunction of the routing and no transit constraints.
+\sysname will generate per-device import and export filters, local preferences and MED attributes, and community tags to ensure that the policy is met under all failure scenarios.
+%
+%
+%\para{Example 2}
+%
+%Consider again the datacenter from Section~\ref{sec:motivation}.
+In this example, there are primarily three main concerns: (1) traffic for the prefix block allocated to each top-of-rack router can reach that router, (2) local services do not leak outside the datacenter, and (3) aggregation is performed on global prefixes to reduce churn in the network.
+%
+%\sysname allows us to decompose and specify each of these constraints in a modular fashion.
+The first constraint is about prefix ownership -- namely, that we only want traffic for certain prefixes to end up at a particular locations.
+The following definition in propane captures this intent:
+%
+%\begin{lstlisting}[mathescape=true]
+%define Ownership = {
+%    $\path{p_{g1}}{end(A)}$
+%    $\path{p_{g2}}{end(B)}$
+%    $\path{p_{l1}}{end(E)}$
+%    $\path{p_{l2}}{end(F)}$
+%}
+%\end{lstlisting}
+%
+%The constraints in the ownership task are read in a top-down fashion.
+Traffic for prefix $p_{g1}$ is only allowed to to follow paths that end at router A.
+Similarly, traffic not matching $p_{g1}$, but which matches $p_{g2}$ must end at router B and so on.
+%%
+%To capture the second constraint, we can define another task for the core routing policy:
+%
+%\begin{lstlisting}[mathescape=true]
+%define Routing = {
+%    $\path{p_{g*}}{any}$
+%    $\path{p_{l*}}{\neg enter(out)}$
+%    $\path{true}{exit(out)}$
+%}
+%\end{lstlisting}
+%
+%The first line states that there is no restriction on how traffic must traverse the network for global prefixes.
+This means traffic for $p_{g*}$ may be sent either from other routers in the datacenter, or from external ASes.
+The second line ensures that traffic for local prefixes never enters the network from an outside location.
+This  guarantees that the services remain reachable only to locations internal to the data center.
+%
+%Finally, we can combine these constraints logically to specify the network-wide policy:
+%
+%\begin{lstlisting}[mathescape=true]
+%Ownership $\wedge$ Routing $\wedge$ agg($p_{agg}$, $in \rightarrow out$)
+%\end{lstlisting}
+%
+%
+%In addition to constraints on the shape of paths, \sysname allows the operator to specify constraints on the BGP control plane.
 Above, a constraint on aggregation is included to ensure that an aggregation for $p_{agg}$ is performed from locations inside the network to locations outside the network.
-
-% correct by construction
-% mention centralized
-% mention attributes
+%
+%Once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. Similarly, it can check for aggregate-induced black holes up to $k$ failures.
+%
+%
+%
+%

### 2016-01-25 paper/motivation.tex
minor changes to motivation

@@
 
-If configuring policies for a fully functional network is difficult, doing so in a way that ensures policy compliance in the face of failures can be almost impossible.
-Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{To scale and to simplify policy implementation, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc-rfc}.} The network has two clusters, one that hosts services that should be reachable globally and one that hosts that should be accessible only internally.
+ While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible.
+Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc-rfc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally.
 This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally.
-In addition, to reduce the number of prefixes that are announced externally, the global space is aggregated into one larger, less-specific prefix $P_G$.
-The semantics of aggregation in BGP is that the aggregate prefix is announced as long as the router has a path to even one sub-prefix.
+Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix $P_G$.
+The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.
 
-The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from routers G and H since these routers border the cluster with local services; and $ii)$ announce what they hear from routers C and D and aggregate to $P_G$ if an announcement is subset of $P_G$.
-The appeal of this implementation is that X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be added to local services without updating router configurations).
+The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ announce what they hear from routers C and D and aggregate to $P_G$ if an announcement is subset of $P_G$.
+This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be assigned to local services without updating router configurations).
 
-However, this implementation is incorrect because it does not have the right behavior in the face of failures.
+However, this implementation does not have the right behavior in the face of failures.
 Suppose links X--G and X--H fail.
@@
 
-To avoid this problem, the operator may decide to disallow paths with "valleys," i.e., those that go up, down, and back up again.
-This safeguard can be implemented by $X$ and $Y$ rejecting paths through the other.
-However, that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{xx}.
-Suppose links D--A and X--C fail.
-Now, X will hear announcements for $P_{g2}$ from D and will thus announce the $P_G$ externally.
+To avoid this problem, the operator may decide to disallow "valleys" paths, i.e., those that go up, down, and back up again.
+This guard can be implemented by $X$ and $Y$ rejecting paths through the other.
+But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{xx}.
+If links D--A and X--C fail, X will hear announcements for $P_{g2}$ from D and will thus announce the $P_G$ externally.
 This announcement will bring to X traffic for $P_{g1}$ as well, but because of valley-free filtering, X does not have a valid route for $P_{g1}$ and will thus drop all traffic to it.
@@
 Thus, we see that devising a configuration that ensures policy compliance in the face of failures is complex and error-prone.
-\sysname helps operators by implementing their high-level policy specification in a way that guarantees compliance under all failures if that is possible.
-(Otherwise, it generates a compile-time error that informs them that the specification cannot be met.) For aggregation, it will also provide a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
+\sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures (if that is possible; otherwise, it generates a compile-time error).
+For aggregation, it will also provide a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
 

### 2016-01-25 paper/evaluation.tex
filling out the head of eval

@@
 
-We have evaluated our compiler by translating and compiling real-world network configurations for data centers and a core backbone network into \sysname.
-We evaluate our compiler by measuring compilation times for these policies across topologies of different sizes.
+We apply \sysname on real policies for backbone and data center networks.
+Our goal is to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
+
+\subsection{Networks studied}
+
+We obtain routing policy for the backbone network and for the data centers of a large cloud provider.
+Multiple data centers share this policy.
+The backbone network connects to the data centers and also has many external BGP neighbors.
+The policies are written in English and serve as a guide for operators when generating configuration templates for the data center routers or actual configurations for the backbone network (where templates are not used because of less regular structure).
+
+The networks have the type of policies that we outline earlier (\S\ref{sec:motivation}).
+The backbone network classifies external neighbors into several different categories and prefers paths through them in order.
+It does not want to provide transit among certain types of neighbors.
+For some neighbors, it prefers some links over the others.
+It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA).
+Finally, it has filters to prevent bogons (private address space) from external neighbors, accept customer prefixes only from customers, and prevent customers from providing transit to other large networks.
+
+All routers in the datacenter network run BGP using a private AS number and peer with each other and with the backbone network over eBGP.
+The routers aggregate prefixes when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region.
+They also have policies by which some prefixes should not be announced beyond a certain level in the data center hierarchy.
+
+\subsection{Expressiveness}
+
+We found that we could translate all network policies to \sysname.
+We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname.
+The data center operator said that he found the language intuitive.
+The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{x}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to compute the various local preferences, import-export filters, and MEDs.} We found that the data center policies were correctly translated.
+For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.
+
+Not counting the lines for various definitions like prefix and customer groups, which we cannot reveal because of confidentiality concerns, the \sysname policies were \todo{x} lines for the backbone network and \todo{y} lines for the data center networks.
+
+\subsection{Compilation time}
+
+We now study the compilation of time for both policies as a function of network size.
+Even though the networks we study have a fixed topology and size, we can explore the impact of size because our converted policies are network-wide and the compiler takes topology itself as an input.
+For the data center network, we build and provide as input fat tree topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy.
+We take this approach to smoothly explore different sizes; there is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete data center topologies.
+For a given size, our reported results match those for the concrete topologies.
+
+For the backbone network, the internal topology does not matter since all routers connect in a full iBGP mesh. We explore different mesh sizes and randomly map neighboring networks to routers.
+
+\todo{Talk about results now}
 
@@
 \label{fig:compilation-times-dc}
-\caption{Data center compilation times.}
+\caption{Data center compilation times. \todo{change pod size to number of routers}}
 \end{figure}

### 2016-01-25 paper/motivation.tex
filling out the head of eval

@@
  While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible.
-Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc-rfc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally.
+Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally.
 This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally.

### 2016-01-25 paper/propane.tex
whats new and what is hard

@@
 %
+\ratul{Does this capture the differences correctly?}
+Policies for (distributed) control planes differ from data plane policies~\cite{x,y,z} in two ways.
+First, they must account for all failures at specification time; there is no controller at runtime, the routers must handle failures by themselves in a compliant manner.
 %
+In \sysname, we enable such specifications through path preferences, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable.
+%
+Second, paths may be under-specified (e.g., "prefer customer" does not indicate a concrete path).
+The \sysname compiler treats such under-specifications as constraints on the set of paths and automatically compute valid sets based on topology.
+
 We introduce \sysname by expressing the policies for the two examples above.

### 2016-01-26 paper/propane.tex
make prettier code

@@
 we prefer using $R_1$ over $R_2$ (Policy P3 from Figure~\ref{fig:example1}):
-\begin{lstlisting}[mathescape=true]
-define ExitCust = $exit(R_1 \gg R_2)$
-\end{lstlisting}
+%\begin{lstlisting}[mathescape=true]
+%define ExitCust = $exit(R_1 \gg R_2)$
+%\end{lstlisting}
+\begin{code}
+\Define ExitCust = \Exit(R1 \Prefer R2)
+\end{code}
 The  statement above defines a set of \emph{ranked paths}, which includes
-all paths (and only those paths) that \cd{exit}
+all paths (and only those paths) that exit
 our network
-through either router $R_1$ or $R_2$.  The paths that exit through $R_1$
-are preferred ($\gg$) to the paths that exit through $R_2$.
+through either router \CD{R1} or \CD{R2}.  The paths that exit through \CD{R1}
+are preferred (\Prefer) to the paths that exit through $R_2$.
+
+% DAVE CONVERSIONS
+% C_{pfx} ===> PCust
+% I_{pfx} ===> PInternal
 
@@
 one or more prefixes, we must define a \sysname \emph{policy}.
-Within a policy, statements with the form $\path{x}{p}$
+Within a policy, statements with the form $x$\Path$p$
 associate the prefixes defined by the predicate $x$ with the set of
@@
 For instance, in the following code, ranked paths are associated with
-the customer prefixes ($C_{pfx}$), the internal prefixes ($I_{pfx}$),
-and all other prefixes (\cd{true}).\footnote{Policy statements are processed in
+the customer prefixes (\CD{PCust}), the internal prefixes (\CD{PInt}),
+and all other prefixes (\CD{true}).\footnote{Policy statements are processed in
 order with earlier policy statements taking precedence over later
-policy statements.  Hence, when the prefix predicate \cd{true} follows
-statements involving $C_{pfx}$ and $I_{pfx}$, it is interpreted as
-$\cd{true} \AND \NOT C_{pfx} \AND \NOT I_{pfx}$.}
+policy statements.  Hence, when the prefix predicate \True follows
+statements involving \CD{PCust} and \CD{PInt}, it is interpreted as
+\CD{\True{} \AND{} \NOT{}PCust \AND{} \NOT{}PInt}.}
 
-\begin{lstlisting}[mathescape=true]
-define Routing = {
-    $\path{C_{pfx}}{ExitCust \gg end(Cust)}$
-    $\path{I_{pfx}}{end(in)}$
-    $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
-}
-\end{lstlisting}
+%% \begin{lstlisting}[mathescape=true]
+%% define Routing = {
+%%     $\path{C_{pfx}}{ExitCust \gg end(Cust)}$
+%%     $\path{I_{pfx}}{end(in)}$
+%%     $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
+%% }
+%% \end{lstlisting}
 
+\begin{code}
+\Define Routing = \{
+     PCust \Path ExitCust \Prefer \End(Cust)
+     PInt  \Path \End(in)
+     \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)
+\}
+\end{code}
+\noindent
 Line 2 of the policy above
 defines the paths that exit our network to customer prefixes ---
-\cd{ExitCust} defines paths through $R_1$ and $R_2$ and in the event
+\CD{ExitCust} defines paths through \CD{R1} and \CD{R2} and in the event
 that connections to the customer through both of those routers fail,
-a backup route ($end(Cust)$) is defined that admits traffic to go through
+a backup route (\CD{\End(Cust)}) is defined that admits traffic to go through
 any path that ends at the customer.
-Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \cd{in} represents any location
-inside the user's network whereas the keyword \cd{out} represents any location
+Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \In{} represents any location
+inside the user's network whereas the keyword \Out{} represents any location
 outside the user's network.
 Line 4 applies to any other traffic, and allows for any routes that leave through a peer with a preference for customers over peers over providers.
-To summarize our progress so far, the \cd{Routing} policy
-implements (P1), (P3) and (P4) from Figure~\ref{fig:example1}
+To summarize our progress so far, the \CD{Routing} policy
+implements (P1), (P3) and (P4) from Figure~\ref{fig:example1}.
 
-Since, routing still allows transit traffic (e.g., traffic can enter from \textit{Peer} and leave through \textit{Prov}), we can define a new policy that
+Since routing allows transit traffic (\emph{i.e.}, traffic can enter from 
+\CD{Peer} and leave through \CD{Prov}), we should define a new policy that
 implements this restriction separately.
 
-\begin{lstlisting}[mathescape=true]
-define PP = Peer or Prov
-define PPTransit = $enter(PP) \AND exit(PP)$
-define CustTransit = $later(Cust) \AND later(Prov)$
+%% \begin{lstlisting}[mathescape=true]
+%% define PP = Peer or Prov
+%% define PPTransit = $enter(PP) \AND exit(PP)$
+%% define CustTransit = $later(Cust) \AND later(Prov)$
 
-define NoTransit = {
-    $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
-}
-\end{lstlisting}
+%% define NoTransit = {
+%%     $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
+%% }
+%% \end{lstlisting}
+\begin{code}
+\Define PP = Peer \OR Prov
+\Define PPTransit   = \Enter(PP) \AND \Exit(PP)
+\Define CustTransit = \Later(Cust) \AND \Later(Prov)
+\Define NoTransit   = \{
+    \True \Path \NOT{}PPTransit \AND \NOT{}CustTransit
+\}
+\end{code}
+\noindent
+The \CD{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied.
+In particular, it says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}.
+Similarly it prevents traffic from ever following paths that leave our network and later passing through both \CD{Prov} and \CD{Cust}.
+To implement both \CD{Routing}
+and \CD{NoTransit} simultaneously, we simply conjoin them:
 
-The \textsf{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied.
-In particular, it says that for any prefix, traffic should never both enter and exit the network from \textit{Peer} or \textit{Prov}.
-Similarly it prevents traffic from ever following paths that leave our network and later passing through both \textit{Prov} and \textit{Cust}.
-To implement both \cd{Routing}
-and \cd{NoTransit} simultaneously, we simply conjoin them:
+%% \begin{lstlisting}[mathescape=true]
+%% Routing $\AND$  NoTransit
+%% \end{lstlisting}
 
-\begin{lstlisting}[mathescape=true]
-Routing $\AND$  NoTransit
-\end{lstlisting}
+\begin{code}
+Routing \AND{} NoTransit
+\end{code}
 
+\noindent
 The lines above capture the entire policy. From it, \sysname will generate per-device import and export filters, local preferences,
@@
 
-In our data center example,
-there are primarily three main concerns:
+In our data center,
+there are three main concerns:
 (1) traffic for the prefix block allocated to each top-of-rack router must be able to reach that router,
@@
 
-\begin{lstlisting}[mathescape=true]
-define Ownership = {
-    $\path{p_{g1}}{end(A)}$
-    $\path{p_{g2}}{end(B)}$
-    $\path{p_{l1}}{end(E)}$
-    $\path{p_{l2}}{end(F)}$
-}
-\end{lstlisting}
+%% \begin{lstlisting}[mathescape=true]
+%% define Ownership = {
+%%     $\path{p_{g1}}{end(A)}$
+%%     $\path{p_{g2}}{end(B)}$
+%%     $\path{p_{l1}}{end(E)}$
+%%     $\path{p_{l2}}{end(F)}$
+%% }
+%% \end{lstlisting}
 
-In English: traffic for prefix $p_{g1}$ is only allowed to follow paths that
-end at router A; traffic not matching $p_{g1}$, but which matches $p_{g2}$ must
-end at router B; and so on.
+\begin{code}
+\Define Ownership = \{
+    PG1 \Path \End(A)
+    PG2 \Path \End(B)
+    PL1 \Path \End(E)
+    PL2 \Path \End(F)
+\}
+\end{code}
+\noindent
+In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
+end at router \CD{A}; traffic not matching \CD{PG1}, 
+but which matches \CD{PG2} must
+end at router \CD{B}; and so on.
 
@@
 
-\begin{lstlisting}[mathescape=true]
-define Routing = {
-    $\path{p_{g*}}{any}$
-    $\path{p_{l*}}{\NOT enter(out)}$
-    $\path{true}{exit(out)}$
-}
-\end{lstlisting}
+%% \begin{lstlisting}[mathescape=true]
+%% define Routing = {
+%%     $\path{p_{g*}}{any}$
+%%     $\path{p_{l*}}{\NOT enter(out)}$
+%%     $\path{true}{exit(out)}$
+%% }
+%% \end{lstlisting}
+\begin{code}
+\Define Routing = \{
+    PG1 \OR PG2 \Path \Any 
+    PL1 \OR PL2 \Path \NOT{}\Enter(\Out)
+    \True      \Path \Exit(\Out)
+\}
+\end{code}
 
-The first line states that there is no restriction (\cd{any})
+\dpw{Note that I did not use an asterix above but used disjunction.}
+The first line states that there is no restriction (\Any)
 on how traffic must
@@
 back on itself. This means traffic for
-$p_{g*}$ may be sent either from other routers in the datacenter, or
+\CD{PG*} may be sent either from other routers in the datacenter, or
 from external ASes. The second line ensures that traffic for local
@@
 For instance, a constraint on aggregation is included to ensure that
-aggregation for $p_{agg}$ is performed from locations inside the network
+aggregation for the prefixes in the set \CD{AGG} is performed from 
+locations inside the network
 to locations outside the network. \todo{Say more about aggregation here.
@@
 
-\begin{lstlisting}[mathescape=true]
-Ownership $\wedge$ Routing $\wedge$ agg($p_{agg}$, $in \rightarrow out$)
-\end{lstlisting}
+\begin{code}
+Ownership \AND{} Routing \AND{} \Agg(AGG, \In \Link \Out)
+\end{code}
 

### 2016-01-26 paper/compilation.tex
typo

@@
 \label{sec:compilation}
+
+The front-end language of \sysname is designed to simplify operators' task of describing preferred paths.
+That simplicity, however, comes at the cost of compilation complexity.
+The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, compute which ones can be honored under a given failure scenario, and ensure policy compliance under all possible failure cases.
+We handle this challenge by breaking down the compilation task into multiple stages and developing efficient algorithms for each.
 
@@
 
-In this section we briefly describe our compilation strategy for \sysname.
+%In this section we briefly describe our compilation strategy for \sysname.
+
 Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate user-level \sysname policies into device-local BGP policies.
@@
 
-The high-level language presented in Section~\ref{sec:propane} is just a thin layer on top of a core, regular-expression-based language for describing preference-based path constraints.
+The high-level language of \S\ref{sec:propane} is just a thin layer on top of a core, regular-expression-based language for describing preference-based path constraints.
 Regular expressions are an expressive formalism that have been studied extensively for their utility in describing paths through graphs~\cite{bib:todo}, and applications to networks~\cite{bib:todo}.
@@
 
-  \caption{Regular Intemediate Language (RIL) syntax (left), and 
+  \caption{Regular Intermediate Language (RIL) syntax (left), and
            Propane language expansions (right).}

### 2016-01-26 data/graph.py
updating figures

@@ -50,7 +50,7 @@ tpp_compress_mean = map(float, tpp_compress_mean[2:])
 #====================================================
 
 # stack data lowest -> highest (build, minimize, order, gen, compress)
-data = (tpp_build_mean, tpp_minimize_mean, tpp_order_mean, tpp_gen_mean, tpp_compress_mean)
+data = (tpp_build_mean, tpp_minimize_mean, tpp_order_mean, tpp_gen_mean)
 foo = np.row_stack( data )
 y_stack = np.cumsum(foo, axis=0)
 
@@ -66,7 +66,7 @@ color1 = "#828A95"
 color2 = "#CEEAF7"
 color3 = "#CCD7E4"
 color4 = "#D5C9DF"
-color5 = "#DCB8CB"
+# color5 = "#DCB8CB"
 
 
 # stacked plot showing different running times
@@ -77,32 +77,34 @@ ax1.fill_between(num_nodes, 0, y_stack[0,:], facecolor=color1, alpha=.7)
 ax1.fill_between(num_nodes, y_stack[0,:], y_stack[1,:], facecolor=color2, alpha=.7)
 ax1.fill_between(num_nodes, y_stack[1,:], y_stack[2,:], facecolor=color3)
 ax1.fill_between(num_nodes, y_stack[2,:], y_stack[3,:], facecolor=color4)
-ax1.fill_between(num_nodes, y_stack[3,:], y_stack[4,:], facecolor=color5)
+#ax1.fill_between(num_nodes, y_stack[3,:], y_stack[4,:], facecolor=color5)
 ax1.set_xlabel('Data center size (routers)')
-ax1.set_ylabel('Time (sec)')
+ax1.set_ylabel('Mean time per prefix (sec)')
+ax1.set_xlim([0,1600])
+ax1.set_ylim([0,20])
 # custom legend for stack color
 p1 = plt.Rectangle((0, 0), 1, 1, fc=color1, alpha=.7)
 p2 = plt.Rectangle((0, 0), 1, 1, fc=color2, alpha=.7)
 p3 = plt.Rectangle((0, 0), 1, 1, fc=color3, alpha=.7)
 p4 = plt.Rectangle((0, 0), 1, 1, fc=color4, alpha=.7)
-p5 = plt.Rectangle((0, 0), 1, 1, fc=color5, alpha=.7)
-leg_boxes = [p5, p4, p3, p2, p1]
[…]

### 2016-01-26 paper/introduction.tex

@@
 It eliminates distributed control planes altogether.
-Instead of devices computing  forwarding tables through mutual interactions, they are told by a centralized controller exactly how to forward packets.
-The controller is responsible for ensuring policy compliance at all times.
-To program centralized control planes, researchers have developed increasingly sophisticated languages that let operators directly express network policies~\cite{x,y,z} that are then translated to forwarding tables at runtime.
+Instead of devices computing  forwarding tables through mutual interactions, they are told by a centralized controller how to forward packets.
+The controller is responsible for ensuring that the paths taken are compliant with operator specifications.
+Researchers have developed increasingly sophisticated languages that let operators specify desirable network paths~\cite{x,y,z} which are then translated to forwarding tables at runtime.
 
-Centralized control planes, however, are not a panacea. 
-%They face significant challenges related to scaling and failure robustness. 
+Centralized control planes of SDN, however, are not a panacea.
+%
 They require careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure~\cite{x,y,z}.
@@
 
-In this paper, we ask if it is possible to centrally program distributed control planes.
+In this paper, we ask if it is possible to program distributed control planes using network-wide policies.
 Operators should be able to directly express network-wide policies, which are automatically decomposed into individual device configurations.
@@
 
-Through our system, called \sysname, we demonstrate the feasibility of centrally programming distributed control planes.
-We focus on BGP, a common and highly flexible way to implement distributed control planes, and show how to automatically generate router BGP configurations from a program that directly expresses network policies.
+Through \sysname, our system that includes a language and a compiler, we demonstrate the feasibility of programming distributed control planes.
+We focus on BGP, a common and highly flexible way to implement distributed control planes, and show how to automatically generate router BGP configurations from network-wide policies.
+
+We face two challenges in designing \sysname that differ from designing a system for programming data planes~\cite{x,y,z}.
+The first is policy specification itself---specifying network {\em policies} is different from specifying network {\em paths}.
+%
+The specification must compactly capture behavior under all possible failures.
+Since there is no controller at runtime, the routers must be programmed ahead of time, based on the specification, to handle failures.
+%
+Further, many policies naturally under-specify paths (e.g., "prefer paying neighbors" is not a concrete path). 
+%
+\sysname addresses this specification challenge by allowing operators to express {\em path preferences}, where preference describes a set of valid paths and less-preferred options are taken only when a higher-preference options are unavailable.
+
+The direct nature of \sysname specifications brings up the second challenge, of compiling them to router configurations.
+We must compute the sets of paths represented by the intersection of multiple preferences and topology, compute which ones can be honored under a given failure scenario, and ensure policy compliance under all possible failure cases.
+We handle this challenge by compactly capturing policy and topology in a {\em product graph} and developing efficient algorithms that operate on this graph.
+
+We evaluate \sysname by using it to encode policies of real backbone and data center networks.
 

### 2016-01-26 paper/compilation.tex
making edit pass

@@
 Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate user-level \sysname policies into device-local BGP policies.
-The first stage of the pipeline involves simple rewriting rules and substitutions from the user-level languae into the core Regular Intermediate Representation (RIR).
-Policies in RIR are checked for well-formedness (e.g., never constraining traffic that does not enter the network), before being combined with topological information to obtain Product Graph Intermediate Representation (PGIR).
+The first stage of the pipeline involves simple rewriting rules and substitutions from the user-level language into the core Regular Intermediate Representation (RIR).
+Policies in RIR are checked for well-formedness (e.g., never constraining traffic that does not enter the network), before being combined with topological information to obtain the Product Graph Intermediate Representation (PGIR).
 The PGIR is a data representation that compactly captures the control flow of all BGP advertisements subject to the policy and topology restrictions.
 We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes.
-Once the compiler determines the PGIR for the policy is safe, the compiler uses a simple translation to an abstract BGP (ABGP) representation.
+Once the compiler determines the PGIR for the policy is safe, it uses a simple translation to an abstract BGP (ABGP) representation.
 To make configurations more readable for human operators, and to reduce the size of the resulting configurations, the \sysname compiler makes several passes over the ABGP form.
@@
 The high-level language of \S\ref{sec:propane} is just a thin layer on top of a core, regular-expression-based language for describing preference-based path constraints.
-Regular expressions are an expressive formalism that have been studied extensively for their utility in describing paths through graphs~\cite{bib:todo}, and applications to networks~\cite{bib:todo}.
+Regular expressions are an expressive formalism that have been studied extensively for their utility in describing paths through graphs~\cite{bib:todo}, with applications to networks~\cite{bib:todo}.
 Our regular expression language differs from others by allowing operators to describe preferences between paths.
@@
 A policy consists of one or more constraints, each of which consists of a test on the type of route, and a corresponding set of preferred regular paths.
-Regular paths are simply regular expressions where the base characters are AS numbers.
+Regular paths are simply regular expressions where the base characters are abstract locations - either a router or an Autonomous System (AS) number.
 Special \textit{in} and \textit{out} symbols are used to refer to any internal or external location respectively.
 For example, the constraint
-$$prefix=74.125.28.0/24 \mapsto (AS200 \cdot in \cdot in^*) \gg (AS100 \cdot in \cdot in^*)$$
+$$prefix=74.125.28.0/24 \mapsto (AS200 \cdot in^+) \gg (AS100 \cdot in^+)$$
 describes a more-preferred set of paths for traffic announced by a prefixes no less specific than $74.125.28.0/24$, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same.
+The plus operator $in^+$ stands for $in \cdot in^*$ in the usual way.
 Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.
@@
 \sysname also supports constraints purely on the control-plane behavior of the BGP routing protocol.
-Thing like prefix aggregation, which should not affect routing behavior, is an important optimization to reduce routing table size and churn.
+Thing like prefix aggregation, which should not affect routing behavior, is an important optimization to reduce routing table size and churn in practice.
 Aggregation, for example from internal locations and external locations, is specified using the same regular syntax as before:
@@
 
-We list the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, however our implementation also supports other constraints such as limiting the maximum number of routes, or enabling BGP multipath.
+We list the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, however our implementation also supports other constraints such as limiting the maximum number of routes allowed between ASes, or enabling BGP multipath.
 
@@
 
-The main differences between \sysname the regular language are: (1) \sysname allows the programmer to specify constraints separately, and combine them together modularly, (2) \sysname provides high-level names that abstract sets of routes, and (3) \sysname allows the preference operator to be used locally.
+The main differences between the \sysname front-end language and the RIR are: (1) \sysname allows the programmer to specify constraints separately, and combine them together modularly, (2) \sysname provides high-level names that abstract sets of routes, and (3) \sysname allows the preference operator to be used locally.
 
@@
 The next step is to rewrite the high-level constraints such as \textit{enter} and \textit{exit} according to the equivalences listed in Figure~\ref{fig:rir-syntax}.
-Since preferences can only occur at the top level for RIR, the final step is to lift the preferences that occur in the regular expression.
+Since preferences can only occur at the outermost level for an RIR expression, the final step is to lift occurences of the preference operator that occur in the regular expression.
 For example, the regular expression $a \cdot (b \gg c) \cdot d$ is lifted to $(a \cdot b \cdot d) \gg (a \cdot c \cdot d)$ by distributing the preference over the sequence operator.
@@
 % Formally define product graph
-The combined product graph is a tuple: ($V'$, $E'$, $s$, $e$, $A$) with
+The combined product graph is a tuple: ($V'$, $E'$, $s$, $e$, $P$) with
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
@@
 a unique ending vertex $e$,
-and an preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to the sets of preferences.
-For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. We say a node $x$ shadows node $y$ in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$.
-
-% Formal product construction
-Let $a_i$ and $b_i$ stand for states in the policy automata.
-The product graph is constructed by adding an edge from $v_1 = (x, a_1, \dots, a_m)$ to $v_2 = (y, b_1, \dots, b_m)$ whenever $\sigma_i(a_i, y) = b_i$ for each $i$ and $(x,y) \in E$ is a valid topology link.
-Additionally, we add edges from the start node $s$ to any $v = (x, a_1, \dots, a_m)$ when $\sigma_i(q_{0_i}, x) = a_i$ for each $i$.
-The preference function $P$ for node $v = (x, a_1, \dots, a_m)$ is defined as $P(v) = \set{i \vert a_i \in F_i} $.
-That is, it records which preferences are achieved for the policy automata for each node in the product construction.
-Finally, there is an edge from each node in the product graph such that $P(v) \neq \emptyset$ to the special end node $e$.
+and a preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
+For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$.
+We say a node $x$ shadows node $y$ in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$.
+That is, $x$ shadows $y$ when they are different nodes in the PGIR that represent the same topology location.
 
@@
 
+% Formal product construction
+Let $a_i$ and $b_i$ stand for states in the regular policy automata.
+The product graph is constructed by adding an edge from $v_1 = (x, a_1, \dots, a_m)$ to $v_2 = (y, b_1, \dots, b_m)$ whenever $\sigma_i(a_i, y) = b_i$ for each $i$ and $(x,y) \in E$ is a valid topology link.
+%
+Additionally, we add edges from the start node $s$ to any $v = (x, a_1, \dots, a_m)$ when $\sigma_i(q_{0_i}, x) = a_i$ for each $i$.
+%
+The preference function $P$ for node $v = (x, a_1, \dots, a_m)$ is defined as $P(v) = \set{i~\vert~a_i \in F_i} $.
+That is, it records which preferences are achieved for the policy automata for each node in the product construction.
+%
+Finally, there is an edge from each node in the product graph such that $P(v) \neq \emptyset$ to the special end node $e$.
+
 Intuitively the product graph tracks which states of each automaton the policy is in as route advertisements move between routers in the topology.
-
+%
 Consider the topology shown in Figure~\ref{fig:example-compilation}.
@@
 From here, if X were to advertise this route to D, it would result in the path $D X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
+The $-$ state indicates it is dropped from the corresponding automaton.
 Since node $(5,-) W$ is in an accepting state for the first automata, it indicates this path has preference 1.
@@
 Although every path through the product graph is a valid path in the topology, we do not want to consider loops when configuring the network.
-In particular, BGP's loop prevention mechanism (where an AS rejects any route for which it is already in the AS path), means that loops should never occur.\footnote{Misconfigured aggregation can still lead to loops in BGP}
+In particular, BGP's loop prevention mechanism (where an AS rejects any route for which it is already in the AS path), means that loops should never occur.\footnote{Note: misconfigured aggregation can still lead to loops in BGP}
 %
@@
 %
-Since we are primarily concerned with guaranteeing user policy correctness and safety with respect to network failures, it is useful to avoid considering possibilities that are not possible due to loops.
+Since we are primarily concerned with guaranteeing user policy correctness and safety with respect to network failures, it is useful to avoid considering cases that are not possible due to loops.
 For example, if we can safely remove an edge from the product graph, then we don't have to consider what happens when the edge has failed.
@@
 For minimization, we compute the dominator set for each node in both the product graph $G$ with respect to the start node, and in the reversed product graph $G^R$ with respect to the end node.
-The following rules enable a cheap simplification of the product graph.
+The following rules enable efficient minimization of the product graph.
 %
@@
 The more challenging case is when a topology location occurs in mutliple contexts in the product graph.
-For example, the topology node $C$ can receive an advertisement from $E$ and later achieve the backup path, or it can receive an advertisement from its neighbor $D$ and later achieve either the primary or backup path.
+For example, in the compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ and later achieve the backup path, or it can receive an advertisement from its neighbor $D$ and later achieve either the primary or backup path.
 Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $E$?
@@
 %
-where the \textit{protect} predicate means that, from $N_1$ on the product graph restricted nodes that achieve preference $j$ or better, there are at least as the same paths as from $N_2$ restricted to $G_i$
+where the \textit{protect} predicate means that, from $N_1$ on the product graph restricted nodes that can potentially achieve preference $j$ or better, there are at least as many paths as from $N_2$ restricted to $G_i$
 
@@
 The algorithm listed in Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another.
-Intuitively, the algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
+The algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
 Thus any paths leading from $N_2$ will have an equivalent path over the same topology locations from $N_1$.
@@
 The algorithm terminates since the number of related states $(x,y)$ that can be expolored is finite.
+\ryan{Add the new part that goes up to a dominating predecessor when no other option}
 
@@
 If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
+\ryan{We are checking if the preorder forms a partial order by satisfying asymmetry}
 
@@
 The checks for failure safety described previously overlook one critical point: even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$.
-To avoid this situation, the compiler simply conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the product graph (i.e., nodes reachable from $x$ in $G_j^R$).
+To avoid this situation, the compiler conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the product graph (i.e., nodes reachable from $x$ in $G_j^R$).
 It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
+\ryan{rework this}
 

### 2016-01-26 paper/implementation.tex
making edit pass

@@
 The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-sepcified aggregates.
-Users see only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}.
+Users only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}.
 
@@
 Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\ref{bib:todo}.
-Our \sysname compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently.
+The \sysname compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently.
 Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy.
@@
 
-Our compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\ref{bib:todo}.
-More complex algorithms with better theoretical complexity exist~\ref{bib:todo} and may be better for large enough examples.
+The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\ref{bib:todo}.
+More complex algorithms with better theoretical complexity exist~\ref{bib:todo} and may be better suited for large enough topologies.
 However, we have not found minimization to be a bottleneck in our implementation.
@@
 
-The naive code generation algorithm described in Section~\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair in the product graph before minimization.
-Our implementation performs partial minimization during generation by recognizing cases where there is no restriction on exporting or importing from neighbors to avoid enumerating such cases.
+The naive code generation algorithm described in Section~\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair for every node in the product graph before minimization.
+Our implementation performs partial minimization during generation by recognizing common cases where there is no restriction on exporting or importing from neighbors.

### 2016-01-26 paper/evaluation.tex
a new section to comment on the types of configs we generate
Add comparison for propane generated configs.

@@
 \end{figure}
+
+\subsection{Propane-generated configurations}
+
+Finally, we comment briefly on how the configurations generated by \sysname differ from those generated by operators today.
+In some cases, \sysname-generated configurations are implemented as one would expect.
+For example, preferences among neighboring ASes are implemented with a compiler-generated community value to tag incoming routes according to preference, which is then observed at other border routers to influence decisions.
+In other cases, the \sysname configurations are different, often relying on a different BGP mechanism to achieve the same result.
+For example, in one instance operators would use the no-export community to prevent routes from leaking beyond a certain tier of the data center, whereas \sysname would selectively import the route only below a certain tier.
+\sysname could use a similar implementation mechanism in the future as an optimization.
+In another instance, operators made assumptions about a neighboring AS to cut down on the propogation of route advertisements.

### 2016-01-26 paper/evaluation.tex
Writeup compilation times for DC, use nodes not pods.

@@
 
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{figures/compilation-times-dc.png}
+\label{fig:compilation-times-dc}
+\caption{Data center compilation times.}
+\end{figure}
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{figures/config-compression-dc.png}
+\label{fig:compilation-compression-dc}
+\caption{Data center config minimization.}
+\end{figure}
+
 We now study the compilation of time for both policies as a function of network size.
@@
 
-\todo{Talk about results now}
+All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7. 
+%
+For the data center policy, we measure the mean compilation time per-prefix since the \sysname compiler can compile for each prefix independently, and in parallel.
+Figure~\ref{fig:compilation-times-dc} shows the compilation times for data centers of different sizes, broken down by compilation phase.
+No individual compilation phase dominates the running time of the compiler, with construction and minimization of the product graph taking the most time.
+\sysname compiles each data center in under 15 seconds per-prefix on average.
+Total compilation time for the largest data center with (>1600) routers takes less than 9 minutes total.
+\todo{Core compilation times here}
 
-\begin{figure}[t!]
-\centering
-\includegraphics[width=\columnwidth]{figures/compilation-times-dc.png}
-\label{fig:compilation-times-dc}
-\caption{Data center compilation times. \todo{change pod size to number of routers}}
-\end{figure}
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=\columnwidth]{figures/config-compression-dc.png}
-\label{fig:compilation-compression-dc}
-\caption{Data center config minimization.}
-\end{figure}
+\ryan{Do we want to include this?}
+The naive compilation algorithm from \S\ref{sec:compilation} generates extremely large ABGP policies.
+To offset this, the compiler performs configuration minimization both during and after configuration generation.
+Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
+Figure~\ref{fig:compilation-compress-dc} shows the effect of minimization for the data center policy.
+Minimization significantly reduces the size of the naive configurations.
 

### 2016-01-26 paper/evaluation.tex
add loc count to eval section.

@@
 
-Not counting the lines for various definitions like prefix and customer groups, which we cannot reveal because of confidentiality concerns, the \sysname policies were \todo{x} lines for the backbone network and \todo{y} lines for the data center networks.
+Not counting the lines for various definitions like prefix and customer groups or for ownership constraints that define where routes originate, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.
 

### 2016-01-27 paper/introduction.tex
intro checkpoint

@@
 
-It is well-known that network configuration is hard and error prone~\cite{x,y,z}; many studies of network incidents point to configuration errors as the leading cause.
+It is well-known that network configuration is highly error 
+prone and that such errors can lead to costly network 
+downtime~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish}.  
+For instance, in the context of BGP, Mahajan~~\cite{mahajan+:bgp-misconfiguration} 
+estimated that 200-1200 prefixes suffered from
+misconfiguration each day and that close to 3 in 4 of all
+new prefix advertisements were the result of misconfiguration.
+Moreover, these misconfigurations sometimes cause significant network downtime for
+individual networks~\cite{time-warner} or even broader internet connectivity problems~\cite{routing-instability,mahajan+:bgp-misconfiguration}.
+\dpw{Note that \cite{time-warner} and I am not sure about the specifics of the problem there
+or what exactly was misconfigured.  It is also unclear if our language really helps with the
+``broader internet connectivity problems'' however, I thought that adding some specific examples
+would help make the intro more compelling.  Feel free to rewrite.}
+
+One reason is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.
+Another, more fundamental reason is the semantic mismatch between the intended high-level
+policies and the low-level device-by-device configurations.  In particular,
+many policies involve network-wide properties---prefer a certain neighbor,
+never announce a particular destination externally, 
+use a particular path only if another fails---but configurations describe the behavior of 
+individual devices.
 %
-One reason is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.
+Operators must manually decompose network-wide policy into device-level behaviors, such that their interactions satisfy the given high-level objectives.
 %
+Ensuring policy-compliance through this manual decomposition is challenging under normal
+circumstances and even more so in the face of failures. Some decompositions that work correctly 
+in failure-free environments, violate key constraints when failures occur.
+%
+As a result, many network configuration problems are only revealed after failures~\cite{batfish},
+sometimes making a bad situation worse.
 
-Another, more fundamental reason is the semantic mismatch between intended policies and configuring individual devices.
-%
-Many policies are network-wide (e.g., such as prefer certain external neighbors over others, never announce certain destination prefixes externally, use a certain path only if another fails), but configurations describe the behavior of individual devices.
-%
-Operators must manually decompose network-wide policy into device-level behaviors, such that their interactions produce the desired policy.
-%
-Ensuring policy-compliance through this manual decomposition is hard and error-prone, especially in the face of failures.
-Certain decompositions that work correctly otherwise, violate policies when failures occur.
-%
-As a result, many configuration errors manifest only during failures~\cite{batfish}.
+To reduce configuration errors, many practitioners have a adopted a template-based 
+approach~\cite{x,y}, in which common configuration patterns are captured as parameterized templates.
+ While templates help ensure certain kinds of consistency across several devices, they do not 
+bridge the 
+semantic divide between network policies and device-level configuration (\S\ref{sec:motivation}):
+These templates do not provide new reasoning principles or fundamentally different abstractions 
+from existing configuration languages.
 
-To reduce configuration errors, the practitioner community is adopting a template-based approach~\cite{x,y}, in which common configuration constructs are captured as parameterized templates.
- While templates help with the low-level nature of configuration languages, they do not bridge the semantic divide between network policies and device-level configuration (\S\ref{sec:motivation}).
+Software-defined networking (SDN) and the abstractions
+that support it are, in part, the research
+community's response to the difficulty of maintaining policy
+compliance through distributed interaction of individual
+devices~\cite{sdn-languages}. Indeed, instead of organizing networks
+around a distributed collection of devices that compute forwarding tables through
+mutual interactions, the devices are told how to
+forward packets by a centralized controller. The controller is responsible for ensuring that the
+paths taken are compliant with operator specifications. 
+%Researchers
+%have developed increasingly sophisticated languages that let operators
+%specify desirable network paths~\cite{x,y,z} which are then translated
+%to forwarding tables at runtime.
 
-Software-defined networking (SDN) was, in part, the research community's response to the difficulty of maintaining policy compliance through distributed interaction of individual devices~\cite{xx}.
-It eliminates distributed control planes altogether.
-Instead of devices computing  forwarding tables through mutual interactions, they are told by a centralized controller how to forward packets.
-The controller is responsible for ensuring that the paths taken are compliant with operator specifications.
-Researchers have developed increasingly sophisticated languages that let operators specify desirable network paths~\cite{x,y,z} which are then translated to forwarding tables at runtime.
-
-Centralized control planes of SDN, however, are not a panacea.
+The centralized control planes of SDN, however, are not a panacea.
 %
 They require careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure~\cite{x,y,z}.
-For this challenge, researchers are exploring multi-controller networks, with interacting controllers, thus bringing back distributed control planes~\cite{x,y,z} and their current programming difficulties.
+To address this challenge, many researchers are beginning to explore
+multi-controller networks, with interacting controllers, thus bringing back distributed 
+control planes~\cite{x,y,z} and their current programming difficulties.  However, academic
+language design and implementation efforts have not kept pace.  For instance, work on
+experimental SDN languages
+such as Frenetic~\cite{frenetic}, Flowlog~\cite{flowlog}, Vericon~\cite{vericon}, Merlin~\cite{merlin}, NetKAT~\cite{netkat}, and Kinetic~\cite{kinetic}, to 
+name a few, has not yet shown how to implement fault tolerant 
+multi-controller systems that support their abstractions efficiently.
 

### 2016-01-27 paper/compilation.tex
Remove some unimportant figures + text

@@
 
-\begin{figure}[t!]
-\begin{lstlisting}[frame=single, mathescape=true]
-$\Router{A}$
-  Match $\PEER=C$
-    Export $\MED \leftarrow 80, \PEER \leftarrow W$
-$\Router{B}$
-  Match $\PEER = C$
-    Export $\COMM \leftarrow \text{noexport}, \MED \leftarrow 81, \PEER \leftarrow W$
-$\Router{C}$
-  Match$[LP=99]$ $\PEER = E $
-    Export $\PEER \leftarrow B$
-  Match $\PEER = D$
-    Export $\PEER \leftarrow A,B$
-$\Router{D}$
-  Match $\REGEX{X + Y}$
-    Export $\PEER \leftarrow C$
-$\Router{E}$
-  Match $\REGEX{Z}$
-    Export $\PEER \leftarrow C$
-\end{lstlisting}
-\label{fig:config-min}
-\caption{Abstract BGP minimized configurations}
-\end{figure}
+%\begin{figure}[t!]
+%\begin{lstlisting}[frame=single, mathescape=true]
+%$\Router{A}$
+%  Match $\PEER=C$
+%    Export $\MED \leftarrow 80, \PEER \leftarrow W$
+%$\Router{B}$
+%  Match $\PEER = C$
+%    Export $\COMM \leftarrow \text{noexport}, \MED \leftarrow 81, \PEER \leftarrow W$
+%$\Router{C}$
+%  Match$[LP=99]$ $\PEER = E $
+%    Export $\PEER \leftarrow B$
+%  Match $\PEER = D$
+%    Export $\PEER \leftarrow A,B$
+%$\Router{D}$
+%  Match $\REGEX{X + Y}$
+%    Export $\PEER \leftarrow C$
+%$\Router{E}$
+%  Match $\REGEX{Z}$
+%    Export $\PEER \leftarrow C$
+%\end{lstlisting}
+%\label{fig:config-min}
+%\caption{Abstract BGP minimized configurations}
+%\end{figure}
 

### 2016-01-27 paper/theory.tex
Remove some unimportant figures + text

@@
 
-\newtheorem{defn}{Proposition}[section]
+\newtheorem{prop}{Proposition}[section]
 
-In this section we investigate the correctness and expressiveness properties of \sysname.
+Here we investigate the correctness and expressiveness properties of \sysname.
 We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures?
@@
 
-%\subsection{Expressiveness}
-%
-%Models for BGP are traditionally given as per-device ranked paths where the configuration of each device is known ahead of time.
-For example router $r_1$ might have a first preference of $r_1 \cdot r_2 \cdot d$ and a second preference of $r_1 \cdot d$.
-Similarly, $r_2$ might have a first preference of $r_2 \cdot d$, and no other preference.
-Against this model of BGP we have the following.
-%
-%\begin{defn}
-%Any policy expressible in BGP is expressible in \sysname.
-%\end{defn}
-%
-%The proof of this is straightforward.
-Simply take the union of each router's rank 1 path, and make that the new most-prefered route in \sysname, and so on.
-For example, the above preferences would be encoded as:
-%$$(r_1 \cdot r_2 \cdot d) \cup (r_2 \cdot d) \gg (r_1 \cdot d) $$
-%Since the semantics of \sysname is such that each unique starting-ending locations should get their most-preferred path.
-
-%\todo{I'm not sure if this is true}.
-
-\subsection{Correctness}
-
-We argue that, if \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario.
+If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario.
 We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges.
@@
 
-\begin{defn}
+\begin{prop}
 A distributed BGP configuration is \textit{Sound} with respect to a \sysname policy, if the any route traffic takes in the network, is a valid route specified in the policy.
-\end{defn}
+\end{prop}
 
@@
 
-\begin{defn}
+\begin{prop}
 A distributed BGP configuration is \textit{Complete} with respect to a \sysname policy, if the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
-\end{defn}
+\end{prop}
 
-The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.
+%The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.
 This means there is a valid path in the product graph corresponding to this path, and which is available in the network.
-Assume we are unable to achieve this route in the network.
+%Assume we are unable to achieve this route in the network.
 To not achieve this path means that some router along the advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead.
@@
 
+Any \sysname-compiled policy will be \textit{Complete} as a result of the failure safety check.
+%
 The combination of Soundness and Completeness ensures that the distributed implementation will always achieve the best routes possible, yet will never also use any unwanted routes.
 
-\begin{defn}
+\begin{prop}
 The internal routers in a distributed BGP configuration produced by \sysname will be stable. 
-\end{defn}
+\end{prop}
 
-\begin{figure}[t!]
-\includegraphics[width=\columnwidth]{figures/dispute-wheel}
-\label{fig:dispute-wheel}
-\caption{Product graph for a dispute wheel.}
-\end{figure}
+The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo} for stable BGP.
+In particular, any policy with a dispute wheel will not pass the stronger failure safety check by \sysname.
 
-The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}.
+%\begin{figure}[t!]
+%\includegraphics[width=\columnwidth]{figures/dispute-wheel}
+%\label{fig:dispute-wheel}
+%\caption{Product graph for a dispute wheel.}
+%\end{figure}
+
+%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}.
 If a set of BGP configurations do not have a dispute wheel, then they will converge to their best routes.

### 2016-01-27 paper/introduction.tex
some tweaks

@@
 downtime~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish}.
-For instance, in the context of BGP, Mahajan~~\cite{mahajan+:bgp-misconfiguration} 
-estimated that 200-1200 prefixes suffered from
-misconfiguration each day and that close to 3 in 4 of all
-new prefix advertisements were the result of misconfiguration.
-Moreover, these misconfigurations sometimes cause significant network downtime for
-individual networks~\cite{time-warner} or even broader internet connectivity problems~\cite{routing-instability,mahajan+:bgp-misconfiguration}.
-\dpw{Note that \cite{time-warner} and I am not sure about the specifics of the problem there
-or what exactly was misconfigured.  It is also unclear if our language really helps with the
-``broader internet connectivity problems'' however, I thought that adding some specific examples
-would help make the intro more compelling.  Feel free to rewrite.}
+For instance, a recent misconfiguration led to an hour-long, nation-wide outage for Time Warner's backbone network~\cite{time-warner}; and a major BGP-related incident makes international news every few months~\cite{bgpmon}.
 
-One reason is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.
+%For instance, in the context of BGP, Mahajan~~\cite{mahajan+:bgp-misconfiguration}
+%estimated that 200-1200 prefixes suffered from
+%misconfiguration each day and that close to 3 in 4 of all
+%new prefix advertisements were the result of misconfiguration.
+%Moreover, these misconfigurations sometimes cause significant network downtime for
+%individual networks~\cite{time-warner} or even broader internet connectivity problems~\cite{routing-instability,mahajan+:bgp-misconfiguration}.
+%\dpw{Note that \cite{time-warner} and I am not sure about the specifics of the problem there
+%or what exactly was misconfigured.  It is also unclear if our language really helps with the
+%``broader internet connectivity problems'' however, I thought that adding some specific examples
+%would help make the intro more compelling.  Feel free to rewrite.}
+
+One reason for network configuration being onerous is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.
+
 Another, more fundamental reason is the semantic mismatch between the intended high-level
@@
 %
-Operators must manually decompose network-wide policy into device-level behaviors, such that their interactions satisfy the given high-level objectives.
+Operators must manually decompose network-wide policy into device-level behaviors, such that their interactions satisfy the high-level objectives.
 %
@@
 To reduce configuration errors, many practitioners have a adopted a template-based
-approach~\cite{x,y}, in which common configuration patterns are captured as parameterized templates.
- While templates help ensure certain kinds of consistency across several devices, they do not 
+approach~\cite{hatch,thwack}, in which common configuration patterns are captured as parameterized templates.
+ While templates help ensure certain kinds of consistency across devices, they do not
 bridge the
-semantic divide between network policies and device-level configuration (\S\ref{sec:motivation}):
-These templates do not provide new reasoning principles or fundamentally different abstractions 
+semantic divide between network policies and device-level configuration.
+They do not provide fundamentally different abstractions
 from existing configuration languages.
 
-Software-defined networking (SDN) and the abstractions
-that support it are, in part, the research
+Software-defined networking (SDN) and its abstractions 
+are, in part, the research
 community's response to the difficulty of maintaining policy

### 2016-01-27 paper/compilation.tex
stashing changes
a few edits

@@
      p       &::=& t \mapsto r_1 \gg \dots \gg r_m & \textit{preferences} \\
-     t       &::=& & \textit{test} \\
-         &\BNFALT& true & \textit{true} \\
+     t       &::=& true & \textit{true} \\
          &\BNFALT& \neg t & \textit{negation} \\
@@
          &\BNFALT& comm = c & \textit{community test} \\
-     r       &::=& & \textit{regular paths} \\
-         &\BNFALT& n & \textit{AS number} \\
+     r       &::=& n & \textit{AS number} \\
          &\BNFALT& in & \textit{internal loc} \\
@@
     internal      & = & in^+ \\
-    external      & = & out^+ \\
     only(X)       & = & any \cap X^* \\

### 2016-01-27 paper/theory.tex
a few edits

@@
 
-Here we investigate the correctness and expressiveness properties of \sysname.
+%Here we investigate the correctness and expressiveness properties of \sysname.
 We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures?

### 2016-01-27 paper/related.tex
a few edits
edits to related work

@@
 
-\begin{itemize}
-	\item Regular path queries
-	\item Lots of background on BGP
-	\item Feamster rcc stuff
-	\item Logic programming BGP configs
-\end{itemize}
+%\begin{itemize}
+%	\item Regular path queries
+%	\item Lots of background on BGP
+%	\item Feamster rcc stuff
+%	\item Logic programming BGP configs
+%\end{itemize}
 
@@
 
+Our work builds on three themes of prior work.
+
 \paragraph*{SDN Programming Languages}
-The design of \sysname{} was heavily influenced by recent SDN programming
+\sysname{} was heavily influenced by recent SDN programming
 languages such as Merlin~\cite{foster:merlin}, FatTire~\cite{fattire},
-NetKAT~\cite{netkat}, as well as Narayana's path queries~\cite{queries}.
+NetKAT~\cite{netkat}, as well as path queries~\cite{queries}.
 Each of these languages is oriented around regular expressions, which
@@
 with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
-and the compiler will generate
-OpenFlow 1.3 rules that satisfy the policy.  \sysname is somewhat more
-expressive than FatTire as it allows users to specify preferences among
-routes and it automatically generates distributed
-implementations that will tolerate
+and the compiler will generate appropriate
+OpenFlow rules.  \sysname is more
+expressive as it allows users to specify preferences among
+paths and it automatically generates distributed
+implementations that tolerate
 any number of faults.  Because FatTire generates data plane rules up front,
 before faults occur, specifying higher levels of fault tolerance comes
-at the cost of generating additional rules, which must fit in switch
+at the cost of generating additional rules that tax switch
 memory.  In contrast, \sysname uses traditional distributed
-control plane mechanisms to react to faults as they occur and to the
-extent that they occur without imposing up front costs that may
-necessitate overprovisioning.
+control plane mechanisms to react to faults, which do not impose 
+additional memory cost.
 Because of the differences in the underlying technology, the analyses
@@
 well, unlike any existing SDN language.
-
-\paragraph*{Configuration Analysis}  The notion that
-configuring network devices is difficult and error-prone is not new.  Past 
-researchers have
-tried to tackle this problem by analyzing existing 
-firewall configurations~\cite{fang,lumeta,margrave} and
-BGP configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe} and reporting errors or
-inconsistencies when they are detected. 
-Our research is complementary to these analysis
-efforts.  Propane hopes to eliminate bugs by using higher-level
-languages and a ``correct-by-construction''
-methodology.  By proposing network administrators write configurations
-at a high-level of abstraction, a whole host of low-level errors can be 
-avoided.  We also believe the high-level, centralized nature of propane policies
-has the benefit of making configurations
-easier to understand and maintain.
 
@@
 SAT solving to find concrete values for configuration variables such
-as \texttt{int(1)}.  ConfigAssure has very broad scope, handling
-configuration for a wide range of different protocols and many
+as \texttt{int(1)}.  ConfigAssure handles
+configuration for a wide range of protocols and many
 different concerns.  In contrast, the scope of \sysname is much
@@
 as opposed to using logic programming and SAT-based model-finding.
+
+\paragraph*{Configuration Analysis}  The notion that
+configuring network devices is difficult and error-prone is not new.  Past
+researchers have
+tried to tackle this problem by analyzing existing
+firewall configurations~\cite{fang,lumeta,margrave} and
+BGP configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe} and reporting errors or
+inconsistencies when they are detected.
+Our research is complementary to these analysis
+efforts.  We hope to eliminate bugs by using higher-level
+languages and a ``correct-by-construction''
+methodology.  By proposing network administrators write configurations
+at a high-level of abstraction, a whole host of low-level errors can be
+avoided.
+
+%We also believe the high-level, centralized nature of \sysname policies
+%has the benefit of making configurations
+%easier to understand and maintain.

### 2016-01-27 paper/motivation.tex
minor to motivation

@@
 
-Operators today generate the BGP configuration of individual devices based on intended policy.
-Whether this task is done fully manually or with the aid of templates, the challenge is to decompose network-wide policies
-%(e.g., prefer customer networks, or never announce a route to a certain prefix to external neighbors),
-into device-level policies that collectively produce the intended behavior.
-This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures.
+%Operators today generate the BGP configuration of individual devices based on intended policy. 
+When generating BGP configurations, whether fully manually or aided by templates, the operators face the challenge of decomposing network-wide policies
+into appropriate device-level policies.
+This decomposition is not always straightforward and ensuring policy-compliance is tricky, especially in the face of failures.
 We illustrate this point using two examples based on policies that we have seen in practice.
-%In the next section, we demonstrate the ease with which the
+The next section shows how \sysname allows operators to directly express these policies.
+%the ease with which the
 %policies can be specified using our new language \sysname.

### 2016-01-27 paper/compilation.tex
editting sections 3-5

@@
 \centering
-\includegraphics[width=\columnwidth]{figures/pipeline}
+\includegraphics[width=.9\columnwidth]{figures/pipeline}
 \caption{Compilation pipeline stages for Propane.}
@@
 
-The high-level language of \S\ref{sec:propane} is just a thin layer on top of a core, regular-expression-based language for describing preference-based path constraints.
+The high-level language of \S\ref{sec:propane} is just a thin layer on top of a core, regular-expression language for describing preference-based path constraints.
 Regular expressions are an expressive formalism that have been studied extensively for their utility in describing paths through graphs~\cite{bib:todo}, with applications to networks~\cite{bib:todo}.
@@
     through(X)    & = & out^* \cdot in^* \cdot X \cdot in^* \cdot out^* \\
-    after(X)      & = & out^* \cdot (X \cap out) \cdot out^* \cdot in^+ \cdot out^* \\
+    later(X)      & = & out^* \cdot (X \cap out) \cdot out^* \cdot in^+ \cdot out^* \\
     before(X)     & = & out^* \cdot in^+ \cdot out^* \cdot (X \cap out) \cdot out^* \\
@@
 For example, the constraint
-$$prefix=74.125.28.0/24 \mapsto (AS200 \cdot in^+) \gg (AS100 \cdot in^+)$$
-describes a more-preferred set of paths for traffic announced by a prefixes no less specific than $74.125.28.0/24$, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same.
-The plus operator $in^+$ stands for $in \cdot in^*$ in the usual way.
+$$prefix=74.3.28.0/24 \mapsto (as200 \cdot in^+) \gg (as100 \cdot in^+)$$
+describes a more-preferred set of paths for traffic announced by a prefix no less specific than $74.125.28.0/24$, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same.
+The plus operator $in^+$ stands for $in \cdot in^*$, at least one internal hop.
 Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.
@@
 \sysname also supports constraints purely on the control-plane behavior of the BGP routing protocol.
-Thing like prefix aggregation, which should not affect routing behavior, is an important optimization to reduce routing table size and churn in practice.
+For example, prefix aggregation, which should not affect routing behavior, is an important optimization to reduce routing table size and churn in practice.
 Aggregation, for example from internal locations and external locations, is specified using the same regular syntax as before:
@@
 Each preference-based regular path constraint (of the form $r_1 \gg \dots \gg r_j$) maps to a set of concrete paths in the network that match one of $r_i$.
-We denote a network path as a string of abstraction locations (routers or external ASes) of the form: $n_1 n_2 \dots n_k$, and we say regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$ and $p$ is a topologically-valid path.
+We denote a network path as a string of abstract locations (routers or external ASes) of the form: $n_1 n_2 \dots n_k$.
+A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$ and $p$ is a topologically-valid path.
 We denote the length of a path $p$ as $\abs{p}$.
@@
 The next step is to rewrite the high-level constraints such as \textit{enter} and \textit{exit} according to the equivalences listed in Figure~\ref{fig:rir-syntax}.
-Since preferences can only occur at the outermost level for an RIR expression, the final step is to lift occurences of the preference operator that occur in the regular expression.
+Since preferences can only occur at the outermost level for an RIR expression, the final step is to lift occurences of the preference operator in each regular expression.
 For example, the regular expression $a \cdot (b \gg c) \cdot d$ is lifted to $(a \cdot b \cdot d) \gg (a \cdot c \cdot d)$ by distributing the preference over the sequence operator.

### 2016-01-27 paper/motivation.tex
editting sections 3-5

@@
 It prefers the neighbors in a certain order ($P1$) and does not want to act as a transit between Peer and Prov ($P2$).
-It prefers to exchange traffic with Cust over $R1$ rather than $R2$ because $R1$ is a cheaper ($P3$).
+It prefers to exchange traffic with Cust over $R1$ rather than $R2$ because $R1$ is cheaper ($P3$).
 To guard against another AS "hijacking" prefixes owned by Cust, it only sends traffic to them if Cust is on the AS path ($P4$).
@@
 Templates help by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually.
-\sysname lets operator express such policies easily and intuitively.
-It them automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.
+\sysname lets operators express such policies easily and intuitively.
+It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.
 

### 2016-01-27 paper/propane.tex
editting sections 3-5

@@
 
-\sysname simplifies network configuration by automatically generating low-level BGP configurations from a high-level specification of routing policy.
-%
-\ratul{Does this capture the differences correctly?}
 Policies for (distributed) control planes differ from data plane policies~\cite{x,y,z} in two ways.
@@
 %
-In \sysname, we enable such specifications through path preferences, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable.
+In \sysname, we enable such specifications through path preferences, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
 %
 Second, paths may be under-specified (e.g., "prefer customer" does not indicate a concrete path).
-The \sysname compiler treats such under-specifications as constraints on the set of paths and automatically compute valid sets based on topology.
+The \sysname compiler treats such under-specifications as constraints on the set of paths and automatically computes valid sets based on topology.
 
@@
 
-The operator configures the network with the abstraction that he or she has centralized control over routing and uses a set of high-level constraints to describe the different routes traffic may (or may not) take and their relative preferences.
+\sysname allows the operator to configure the network with the abstraction that he or she has centralized control over routing and uses a set of high-level constraints to describe the different routes traffic may (or may not) take and their relative preferences.
 In general, \sysname specifications are written modularly via a series
@@
 The  statement above defines a set of \emph{ranked paths}, which includes
-all paths (and only those paths) that exit
-our network
+all paths (and only those paths) for which traffic exits our network
 through either router \CD{R1} or \CD{R2}.  The paths that exit through \CD{R1}
@@
 
-\dpw{Note that I did not use an asterix above but used disjunction.}
 The first line states that there is no restriction (\Any)
@@
 For instance, a constraint on aggregation is included to ensure that
-aggregation for the prefixes in the set \CD{AGG} is performed from 
-locations inside the network
-to locations outside the network. \todo{Say more about aggregation here.
+aggregation for global prefixes (with aggregate \CD{PG}) is performed from 
+locations inside the network to locations outside the network. In this case, both \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG} when advertised outside the datacenter.
+\todo{Say more about aggregation here.
 What prefixes are aggregated in to what blocks?  How is this defined?}
@@
 \begin{code}
-Ownership \AND{} Routing \AND{} \Agg(AGG, \In \Link \Out)
+Ownership \AND{} Routing \AND{} \Agg(P_G, \In \Link \Out)
 \end{code}
@@
 As before, once \sysname compiles the policy, it is guaranteed to hold under
-all possible failure scenarios. In addition, the system can check for
-aggregate-induced black holes in the presence of up to $k$ failures.
-\todo{Note:  Another comment about failure checking for black holes, which may
-not be implemented yet.}
+all possible failure scenarios.
+\sysname also checks for failure safety against aggregation-induced black holes due to the presence of aggregation constraints.
+It can efficiently determine a lower bound on the number of failures necessary to black hole traffic given the user's policy, topology, and placement of specific aggregates.
 

### 2016-01-27 paper/compilation.tex
edits to 4 and 5

@@
 
-The front-end language of \sysname is designed to simplify operators' task of describing preferred paths.
+The front-end (FE) of \sysname simplifies operators' task of describing preferred paths.
 That simplicity, however, comes at the cost of compilation complexity.
-The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, compute which ones can be honored under a given failure scenario, and ensure policy compliance under all possible failure cases.
-We handle this challenge by breaking down the compilation task into multiple stages and developing efficient algorithms for each.
+The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, compute which ones can be honored under failures, and ensure policy compliance under all possible failure cases.
 
-\subsection{Overview}
+%\subsection{Overview}
 
@@
 \centering
-\includegraphics[width=.9\columnwidth]{figures/pipeline}
+\includegraphics[width=.75\columnwidth]{figures/pipeline}
 \caption{Compilation pipeline stages for Propane.}
@@
 
-Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate user-level \sysname policies into device-local BGP policies.
-The first stage of the pipeline involves simple rewriting rules and substitutions from the user-level language into the core Regular Intermediate Representation (RIR).
-Policies in RIR are checked for well-formedness (e.g., never constraining traffic that does not enter the network), before being combined with topological information to obtain the Product Graph Intermediate Representation (PGIR).
-The PGIR is a data representation that compactly captures the control flow of all BGP advertisements subject to the policy and topology restrictions.
+We handle this challenge by breaking compilation into multiple stages and developing efficient algorithms for each.
+Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate \sysname FE policies to device-local BGP policies.
+The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR).
+Policies in RIR are checked for well-formedness (e.g., never constraining traffic that does not enter the network), before being combined with topology to obtain the Product Graph Intermediate Representation (PGIR).
+The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions.
 We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes.
-Once the compiler determines the PGIR for the policy is safe, it uses a simple translation to an abstract BGP (ABGP) representation.
+Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation.
 To make configurations more readable for human operators, and to reduce the size of the resulting configurations, the \sysname compiler makes several passes over the ABGP form.
-Finally, vendor-specific adaptors can be added to \sysname to translate from ABGP to actual concrete configurations that go on the network devices.
+Finally, vendor-specific adaptors can translate from ABGP to concrete device configurations.
 
@@
 
-The high-level language of \S\ref{sec:propane} is just a thin layer on top of a core, regular-expression language for describing preference-based path constraints.
-Regular expressions are an expressive formalism that have been studied extensively for their utility in describing paths through graphs~\cite{bib:todo}, with applications to networks~\cite{bib:todo}.
+The \sysname FE is just a thin layer atop a core, regular-expression language for describing preference-based path constraints.
+Regular expressions are an expressive formalism that have been used extensively for describing paths through graphs~\cite{bib:todo}, with applications to networks~\cite{bib:todo}.
 Our regular expression language differs from others by allowing operators to describe preferences between paths.
@@
 
-The syntax for the RIR is shown in Figure~\ref{fig:rir-syntax}.
+Figure~\ref{fig:rir-syntax} shows the RIR syntax.
 A policy consists of one or more constraints, each of which consists of a test on the type of route, and a corresponding set of preferred regular paths.
-Regular paths are simply regular expressions where the base characters are abstract locations - either a router or an Autonomous System (AS) number.
-Special \textit{in} and \textit{out} symbols are used to refer to any internal or external location respectively.
+Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS.
+Special \textit{in} and \textit{out} symbols refer to any internal or external location respectively.
 For example, the constraint
@@
 
-\sysname also supports constraints purely on the control-plane behavior of the BGP routing protocol.
+\sysname also supports constraints purely on the control-plane behavior of BGP.
 For example, prefix aggregation, which should not affect routing behavior, is an important optimization to reduce routing table size and churn in practice.
-Aggregation, for example from internal locations and external locations, is specified using the same regular syntax as before:
+Aggregation, for example, from internal to external locations, is specified using the same regular syntax as before:
 $$agg(128.17.0.0/16, in \rightarrow out)$$
-where the expression $in \rightarrow out$ refers to control messages flowing from any internal location to any external location.
+where the expression $in \rightarrow out$ refers to control messages flowing from any internal to any external location.
 
-We list the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, however our implementation also supports other constraints such as limiting the maximum number of routes allowed between ASes, or enabling BGP multipath.
+We list only the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, but we also support other constraints such as limiting the maximum number of routes allowed between ASes, or enabling BGP multipath.
 
@@
 
-The semantics of RIR can be thought of in terms of ranked paths.
+The semantics of RIR is in terms of ranked paths.
 Each preference-based regular path constraint (of the form $r_1 \gg \dots \gg r_j$) maps to a set of concrete paths in the network that match one of $r_i$.
@@
 where the rank is lexicographically ordered according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the length of the path.
-A lower rank indicates a \emph{more} preferred path.
-The desired semantics is to allow traffic to be sent along any of the most preferred paths for each pair of starting and ending locations that appear in some valid specified path.
+Lower ranks indicate \emph{more} preferred paths.
+The semantics is to allow traffic to be sent along any of the most preferred paths for each pair of starting and ending locations that appear in some valid specified path.
 
-The set of ranked paths depends on which paths are valid given the topology, and thus when failures occur, so do the most preferred routes.
-It is the job of the \sysname compiler to ensure that generated configurations for a policy always achieve the most preferred path possible given the failures in the topology, using only distributed mechanisms.
+The set of ranked paths depends on which paths are valid in the topology, and thus when failures occur, the most preferred routes change.
+The \sysname compiler ensures that generated configurations for a policy always achieve the most preferred path possible given the failures in the topology, using only distributed mechanisms.
 
-\para{Propane front-end to RIR}
+\para{Propane FE to RIR}
 
-The main differences between the \sysname front-end language and the RIR are: (1) \sysname allows the programmer to specify constraints separately, and combine them together modularly, (2) \sysname provides high-level names that abstract sets of routes, and (3) \sysname allows the preference operator to be used locally.
+The main differences between the \sysname FE and the RIR are: (1) FE allows the programmer to specify constraints separately, and combine them  modularly, (2) FE provides high-level names that abstract sets of routes, and (3) FE allows the preference operator to be used locally.
 
-One of the main constraints when translating to RIR is to ensure that all specified routes are well-formed.
+A key constraint when translating FE to RIR is to ensure that all specified routes are well-formed.
 In particular, each regular path constraint $r$ must satisfy $r \subseteq out^* \cdot in^+ \cdot out^*$.
-This ensures that one can only ever talk about controlling traffic that goes through the user's network at some point.
+This ensures that one can only talk about controlling traffic that goes through the user's network at some point.
 
-The translation from \sysname to RIR is based on a set of simple rewriting rules.
-The first step is to merge separate constraints.
-This is accomplished by simply taking the cross product of per-prefix constraints, where logical conjunction ($a \wedge b$) is replaced by intersection on regular constraints ($a \cap b$), logical disjunction is replaced by union, and logical negation ($\neg a$) is replaced by ($any \cap !(a)$), where $any$ ensures the routes are well-formed.
+The translation from \sysname to RIR is based on a set of rewriting rules.
+The first step merges separate constraints.
+It takes the cross product of per-prefix constraints, where logical conjunction ($a \wedge b$) is replaced by intersection on regular constraints ($a \cap b$), logical disjunction is replaced by union, and logical negation ($\neg a$) is replaced by ($any \cap !(a)$), where $any$ ensures the routes are well-formed.
 %
-For example, in the data center configuration from Section~\ref{sec:propane}, combining the \textit{Routing} and \textit{Ownership} constraints would result in the following RIR configuration:
+For example, in the data center configuration from \S\ref{sec:propane}, combining the \textit{Routing} and \textit{Ownership} policies results in the following RIR:
 
@@
 
-The next step is to rewrite the high-level constraints such as \textit{enter} and \textit{exit} according to the equivalences listed in Figure~\ref{fig:rir-syntax}.
-Since preferences can only occur at the outermost level for an RIR expression, the final step is to lift occurences of the preference operator in each regular expression.
+The next step rewrites the high-level constraints such as \textit{enter} according to the equivalences in Figure~\ref{fig:rir-syntax}.
+Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression.
 For example, the regular expression $a \cdot (b \gg c) \cdot d$ is lifted to $(a \cdot b \cdot d) \gg (a \cdot c \cdot d)$ by distributing the preference over the sequence operator.

### 2016-01-27 paper/propane.tex
edits to 4 and 5

@@
 
-Policies for (distributed) control planes differ from data plane policies~\cite{x,y,z} in two ways.
-First, they must account for all failures at specification time; there is no controller at runtime, the routers must handle failures by themselves in a compliant manner.
+Policies for (distributed) control planes differ from data plane policies~\cite{x,y,z}.
+First, they must account for all failures at specification time; there is no controller at runtime, the routers must be configured in advance to handle failures in a compliant manner.
 %
@@
 \sysname allows the operator to configure the network with the abstraction that he or she has centralized control over routing and uses a set of high-level constraints to describe the different routes traffic may (or may not) take and their relative preferences.
-In general, \sysname specifications are written modularly via a series
-of user declarations.
+\sysname specifications are written modularly via a series
+of declarations.
 %These definitions allow users to express the three
@@
 \end{code}
-The  statement above defines a set of \emph{ranked paths}, which includes
+This  statement defines a set of \emph{ranked paths}, which includes
 all paths (and only those paths) for which traffic exits our network
 through either router \CD{R1} or \CD{R2}.  The paths that exit through \CD{R1}
-are preferred (\Prefer) to the paths that exit through $R_2$.
+are preferred (\Prefer) to those that exit through $R_2$.
 
@@
 To associate ranked paths with
-one or more prefixes, we must define a \sysname \emph{policy}.
+one or more prefixes, we define a \sysname \emph{policy}.
 Within a policy, statements with the form $x$\Path$p$
@@
 \noindent
-Line 2 of the policy above
-defines the paths that exit our network to customer prefixes ---
-\CD{ExitCust} defines paths through \CD{R1} and \CD{R2} and in the event
+Line 2 of this policy 
+defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2} and in the event
 that connections to the customer through both of those routers fail,
@@
 outside the user's network.
-Line 4 applies to any other traffic, and allows for any routes that leave through a peer with a preference for customers over peers over providers.
+Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers.
 To summarize our progress so far, the \CD{Routing} policy
@@
 The \CD{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied.
-In particular, it says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}.
+It says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}.
 Similarly it prevents traffic from ever following paths that leave our network and later passing through both \CD{Prov} and \CD{Cust}.
@@
 
-\sysname allows us to decompose and specify each of these constraints in a modular fashion.
-The first constraint is about prefix ownership -- namely, that we only want traffic for certain prefixes to end up at a particular locations.
+\sysname allows us to specify each of these constraints modularly.
+The first constraint is about prefix ownership---namely, we only want traffic for certain prefixes to end up at a particular locations.
 The following definition captures this intent.
@@
 \Define Ownership = \{
-    PG1 \Path \End(A)
-    PG2 \Path \End(B)
-    PL1 \Path \End(E)
-    PL2 \Path \End(F)
+    Pg1 \Path \End(A)
+    Pg2 \Path \End(B)
+    Pl1 \Path \End(E)
+    Pl2 \Path \End(F)
 \}
@@
 \noindent
-In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
-end at router \CD{A}; traffic not matching \CD{PG1}, 
-but which matches \CD{PG2} must
+In English: traffic for prefix \CD{Pg1} is only allowed to follow paths that
+end at router \CD{A}; traffic matching \CD{Pg2},
+but not \CD{Pg1}, must
 end at router \CD{B}; and so on.
 
-To capture the second constraint, we can define another task for the core
-routing policy:
+For the second constraint, we can define another policy:
 
@@
 \end{code}
-
+\noindent
 The first line states that there is no restriction (\Any)
@@
 back on itself. This means traffic for
-\CD{PG*} may be sent either from other routers in the datacenter, or
+\CD{Pg*} may be sent either from other routers in the datacenter, or
 from external ASes. The second line ensures that traffic for local
@@
 aggregation for global prefixes (with aggregate \CD{PG}) is performed from
-locations inside the network to locations outside the network. In this case, both \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG} when advertised outside the datacenter.
+locations inside the network to locations outside. In this case, \CD{Pg1} and \CD{Pg2} will use the aggregate \CD{PG} when advertised outside the datacenter.
 \todo{Say more about aggregation here.
@@
 \begin{code}
-Ownership \AND{} Routing \AND{} \Agg(P_G, \In \Link \Out)
+Ownership \AND{} Routing \AND{} \Agg(PG, \In \Link \Out)
 \end{code}
 
-As before, once \sysname compiles the policy, it is guaranteed to hold under
-all possible failure scenarios.
-\sysname also checks for failure safety against aggregation-induced black holes due to the presence of aggregation constraints.
-It can efficiently determine a lower bound on the number of failures necessary to black hole traffic given the user's policy, topology, and placement of specific aggregates.
+As before, once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. \sysname also checks for safety against aggregation-induced black holes.
+%It can efficiently determine a lower bound on the number of failures necessary to black hole traffic given the user's policy, topology, and placement of specific aggregates.
 

### 2016-01-27 paper/compilation.tex
edits to 5

@@
 
-Now that the user policy exists in a simplified form, we must take the topology into consideration.
-In particular, we are interested in a compact representation that describes all the possible ways BGP route advertisements can flow through the network subject to the policy and topology constraints.
-To this end, we use a Product Graph Intermediate Representation (PGIR) to capture these dependencies.
-The Product graph can be thought of as the intersection of each of the regular automata corresponding to the RIR path preferences, and the topology.
-Paths through the product graph will correspond to real paths through the topology that satisfy the user constraints.
-Finding paths through a graph subject to regular constraints has been studied extensively in the database literature~\ref{bib:todo}, and has been applied to networks in the past~\ref{bib:todo}.
+Now that the user policy exists in a simplified form, we must consider topology.
+In particular, we want a compact representation that describes all the possible ways BGP route announcements can flow through the network subject to the policy and topology constraints.
+Our PGIR captures these dependencies by ``intersecting" each of the regular automata corresponding to the RIR path preferences, and the topology.
+Paths through the PGIR correspond to real paths through the topology that satisfy the user constraints.
+
+%Finding paths through a graph subject to regular constraints has been studied extensively in the database literature~\ref{bib:todo}, and has been applied to networks in the past~\ref{bib:todo}.
 
@@
 % Formally define automata
-The translated user policy into RIR is of the form $r_1 \gg \dots \gg r_j$.
-While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., router advertisements flowing in the opposite direction).
+The RIR policy is of the form $r_1 \gg \dots \gg r_j$.
+While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., route announcements flowing in the opposite direction).
 To capture this idea, for each regular expression $r_i$, we construct a deterministic finite state machine on the reversed regular expression.
 Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ consists of all internal and external ASes, $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+The alphabet $\Sigma$ consists of all internal and external ASes, \ratul{ASes or locations?} $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
 %
@@
 % Formally define product graph
-The combined product graph is a tuple: ($V'$, $E'$, $s$, $e$, $P$) with
+The combined PGIR is a tuple: ($V'$, $E'$, $s$, $e$, $P$) with
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
@@
 % Formal product construction
-Let $a_i$ and $b_i$ stand for states in the regular policy automata.
-The product graph is constructed by adding an edge from $v_1 = (x, a_1, \dots, a_m)$ to $v_2 = (y, b_1, \dots, b_m)$ whenever $\sigma_i(a_i, y) = b_i$ for each $i$ and $(x,y) \in E$ is a valid topology link.
+Let $a_i$ and $b_i$ denote states in the regular policy automata.
+The PGIR is constructed by adding an edge from $v_1 = (x, a_1, \dots, a_m)$ to $v_2 = (y, b_1, \dots, b_m)$ whenever $\sigma_i(a_i, y) = b_i$ for each $i$ and $(x,y) \in E$ is a valid topology link.
 %
@@
 %
-Finally, there is an edge from each node in the product graph such that $P(v) \neq \emptyset$ to the special end node $e$.
+Finally, there is an edge from each node in the PGIR such that $P(v) \neq \emptyset$ to the special end node $e$.
 
-Intuitively the product graph tracks which states of each automaton the policy is in as route advertisements move between routers in the topology.
+Intuitively, PGIR tracks which states of each automaton the policy is in as route announcements move between routers.
 %
-Consider the topology shown in Figure~\ref{fig:example-compilation}.
-Suppose we want to set up a primary route from W that enters the network from $A$, and utilizes the A -- C and C -- D links.
-We also would like a backup route that enters from node $B$, and utilizes the B -- C link, but is otherwise unconstrained.
-For the sake of simplicity, we will assume that the route can end in either $X$, $Y$, or $Z$.
+Consider the topology in Figure~\ref{fig:example-compilation}.
+Suppose we want a primary route from W that enters the network from $A$, and utilizes the A--C and C--D links.
+We also want a backup route that enters from $B$, and utilizes the B--C link, but is otherwise unconstrained.
+For simplicity, we assume that the route can end in either $X$, $Y$, or $Z$.
 The RIR for the policy is:
@@
 %
-Figure~\ref{fig:example-compilation} shows the product graph obtained from intersecting the topology and policy automata.
-Every path in the product graph corresponds to a concrete path in the topology.
-In particular, every path through the product graph that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
+The figure also shows the PGIR after intersecting the topology and policy automata.
+Every path in it corresponds to a concrete path in the topology.
+In particular, every path through the PGIR that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
 %
-For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route advertisements might take, which would lead to obtaining the most prefered preference $1$.
+For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining the most prefered preference $1$.
 BGP control messages can start from peer X, which would match the $out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
@@
 From here, if X were to advertise this route to D, it would result in the path $D X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
-The $-$ state indicates it is dropped from the corresponding automaton.
-Since node $(5,-) W$ is in an accepting state for the first automata, it indicates this path has preference 1.
+%
+The ``--" state indicates it is dropped from the corresponding automaton. Since node $(5,-) W$ is in an accepting state for the first automata, it indicates this path has preference 1.
 
 \para{Minimization}
+\ratul{This minimization section can probably go entirely, shrunken, or moved to the implementation}
+Before checking if policies captured by the PGIR are safe, we minimize the PGIR to better scale our failure safety checks.
+The minimization is based on the observation that although every path in the PGIR is a valid path in the topology, we do not want to consider loops when configuring the network.
+In particular, BGP's loop prevention mechanism, by which an AS rejects any route for which it is already in the AS path, means that loops should never occur.\footnote{ Misconfigured aggregation can still lead to loops in BGP.}
+%
+However, the PGIR may contain many paths that form loops in the topology.
+For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path that BGP announcements might take, leading to a path that satisfies the preference 1 policy, but which contains a loop.
+%
+Since we are primarily concerned with guaranteeing user policy correctness and safety with respect to network failures, it is useful to eliminate cases that are not possible due to loops.
+For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
 
-Although every path through the product graph is a valid path in the topology, we do not want to consider loops when configuring the network.
-In particular, BGP's loop prevention mechanism (where an AS rejects any route for which it is already in the AS path), means that loops should never occur.\footnote{Note: misconfigured aggregation can still lead to loops in BGP}
-%
-However, the product graph may contain many paths that form loops in the topology.
-For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid path that BGP route advertisements might take through the topology, leading to a path that satisfies the preference 1 policy, but which contains a loop.
-%
-Since we are primarily concerned with guaranteeing user policy correctness and safety with respect to network failures, it is useful to avoid considering cases that are not possible due to loops.
-For example, if we can safely remove an edge from the product graph, then we don't have to consider what happens when the edge has failed.
-
-We can safely remove any node or edge from the product graph so long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node.
+We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node.
 For example, node $(1,1) W$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it most go through another $W$ in either case.
 %
-Although fully minimizing the product graph is an NP-complete problem, we find that a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.
+Although fully minimizing this graph is an NP-complete problem,  a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.
 
-A node $x$ dominates node $y$ if $x$ appears on every path leading to $y$ from a source node.
-Many algorithms for finding graph dominators efficiently exist~\ref{bib:todo}.
+A node $x$ dominates $y$ if $x$ appears on every path leading to $y$ from a source node.
+Many efficient algorithms exist for finding graph dominators~\ref{bib:todo}.
 For minimization, we compute the dominator set for each node in both the product graph $G$ with respect to the start node, and in the reversed product graph $G^R$ with respect to the end node.
@@
 At a first cut, any time a router must make a decision locally between several route options, there is the possibility that it might choose incorrectly.
-The product graph representation captures this notion of choice precisely.
-For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the product graph, possibly receiving route advertisements from $X$ or $Y$.
+PGIR captures this notion of choice precisely.
+For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the PGIR, possibly receiving announcements from $X$ or $Y$.
 However, regardless of whether $D$ chooses a route from $X$ or $Y$, the set of paths allowed by the policy after going through $D$ will be the same in either case.
@@
 
-The more challenging case is when a topology location occurs in mutliple contexts in the product graph.
-For example, in the compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ and later achieve the backup path, or it can receive an advertisement from its neighbor $D$ and later achieve either the primary or backup path.
+The more challenging case is when a topology location occurs in mutliple contexts in the PGIR.
+For example, in the compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an announcement from $E$ and later achieve the backup path, or it can receive an announcement from its neighbor $D$ and later achieve either the primary or backup path.
 Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $E$?
-The important observation is that, if $C$ prefers $D$, then it is never worse off -- it will always achieve at least as good a path as if it had choosen $E$.
+The important observation is that, if $C$ prefers $D$, then it is never worse off---it will always achieve at least as good a path as if it had choosen $E$.
 For example, suppose $C$ chooses a route from $D$, but cannot achieve its primary path because the $A$ -- $W$ link has failed.
@@
 
-In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and a simple enumeration of failures is intractable.
-Instead, we adopt a conservative analysis based on the product graph representation and the previous observations.
-The high-level idea is to order each node in the product graph according to a \textit{can prefer} relation.
+In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and enumerating all failures is intractable.
+We thus adopt a conservative analysis based on the observations above.
+The high-level idea is to order each PGIR node according to a \textit{can prefer} relation.
 For example, node $(3,2) C$ can be preferred to node $(-,2) C$, but not the other way around.
@@
 %
-where the \textit{protect} predicate means that, from $N_1$ on the product graph restricted nodes that can potentially achieve preference $j$ or better, there are at least as many paths as from $N_2$ restricted to $G_i$
+where \textit{protect} means that, from $N_1$ on the PGIR restricted nodes that can potentially achieve preference $j$ or better, there are at least as many paths as from $N_2$ restricted to $G_i$
 
@@
 
-The algorithm listed in Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another.
-The algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
+Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another.
+It walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
 Thus any paths leading from $N_2$ will have an equivalent path over the same topology locations from $N_1$.
-Algorithm~\ref{alg:failures} works because each node in the product graph can have at most one outgoing neighbor with the same topological location, so the next hop neighbors can be checked without backtracking.
+Algorithm~\ref{alg:failures} works because each PGIR node can have at most one outgoing neighbor with the same topological location, so the next hop neighbors can be checked without backtracking.
 The algorithm terminates since the number of related states $(x,y)$ that can be expolored is finite.
@@
 
-Local preferences are now obtained by, for each router in the topology, sorting the corresponding nodes in the product graph according to \textit{can prefer} relation.
+Local preferences are now obtained by, for each router in the topology, sorting the corresponding PGIR nodes according to \textit{can prefer} relation.
 If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
@@
 
-The checks for failure safety described previously overlook one critical point: even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$.
-To avoid this situation, the compiler conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the product graph (i.e., nodes reachable from $x$ in $G_j^R$).
+The checks for failure safety described above overlook a critical point: even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$.
+To avoid this situation, the compiler conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the PGIR (i.e., nodes reachable from $x$ in $G_j^R$).
 It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.

### 2016-01-27 paper/compilation.tex
edits to 5

@@
   \hdr{\large Topology}{}
-  \vspace*{-1\baselineskip}
+  \vspace*{-2\baselineskip}
 
-  \includegraphics[width=.8\columnwidth]{figures/topology}
+  \includegraphics[width=.6\columnwidth]{figures/topology}
 
   \hdr{\large Policy Automata}{}
-  \vspace*{1\baselineskip}
+  \vspace*{-0.5\baselineskip}
 
-  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.6cm]
+  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.4cm,minimum size=1cm]
     \state{0}{$0$}{              }{}
@@
   \begin{minipage}[t]{.5\linewidth}
-  \hdr{\large Product Graph}{}
+  \hdr{\large Product Graph IR}{}
   \vspace*{-1\baselineskip}
   %
-  \includegraphics[width=.8\columnwidth]{figures/productgraph}
+  \includegraphics[width=.65\columnwidth]{figures/productgraph}
   \end{minipage}
@@
 
-  \caption{Example Product graph construction.}
+  \caption{Example Product Graph IR construction.}
   \label{fig:example-compilation}
@@
 
-The final stages of compilation consist in translating policies from PGIR to a simple, vendor-neutral abstraction of BGP (ABGP), and then translating from ABGP to actual device configurations.
+The final stages of compilation translate policies from PGIR to a  vendor-neutral abstraction of BGP (ABGP) and then from ABGP to actual device configurations.
 
@@
 
-Having found a total ordering on node preferences in the product graph from the failure safety analysis, the translation to ABGP becomes straightforward.
+Once we have the total ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
 The idea is to encode the state of the automaton using BGP community values.
-Each router will match based on its peer and a community value corresponding to the state of the product graph, and then update the state before exporting to the neighbors permitted according to the product graph.
-For example, router $A$ from the example in Figure~\ref{fig:example-compilation} will allow an advertisement from its peer $C$ with a community value for state $(3,2)$ (and deny anything else).
-If it sees such an advertisement, it will remove the old community value, and add a new community value for state $(4,2)$ before exporting the route to its neighbor $W$.
+Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR.
+For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else).
+If it sees such an announcement, it will remove the old community value, and add a new one for state $(4,2)$ before exporting it to $W$.
 
-To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler will simply set a higher local preference for neighbors of a more-preferred node for $r$ in the product graph.
+To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR.
 For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
@@
 Since the compiler is only able to control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
-Instead, it simply translates matches from external ASes into a BGP regular expression filter.
+Instead, it translates matches from external ASes into a BGP regular expression filter.
 For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$ and prefer them equally.
@@
 
-Finally, in our example, the external AS $W$ would need to prefer our internal router $A$ over $B$.
-In general, it is not possible to control traffic entering the network beyond certain special cases.
-In this example however, the BGP MED attribute can influence $W$ to prefer $A$ over $B$ since the preference is for a single external peer.
-Additionally, the compiler can use the BGP no-export community can ensure that no other AS beyond $W$ can send us traffic.
+Finally, in our example, the external AS $W$ should prefer our internal router $A$ over $B$.
+In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
+In this example, however, assuming our network and$W$ have an agreement to honor MEDs, the BGP MED attribute can influence $W$ to prefer $A$ over $B$.
+Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
 The compiler can perform a simple analysis to determine when it can utilize various BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
@@
 Figure~\ref{fig:config} shows the full configuration from the compilation example.
-To make configurations more compact and readable, the \sysname compiler will rewrite configurations in ABGP - for example removing community tagging and matching when there is no ambiguity.
-Figure~\ref{config-min} shows the minimized router configurations.
+To make configurations more compact and readable, the \sysname compiler rewrites configurations in ABGP, e.g., removing community tagging and matching when there is no ambiguity.
+Figure~\ref{config-min} shows minimized router configurations.
+\todo{figure was removed?}
 
@@
 
-As was demonstrated in Example 2 of Section~\ref{sec:motivation}, the use of aggregation in BGP can lead to subtle black-holing traffic when failures occur.
+As demonstrated with Example 2 in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing traffic when failures occur.
 Deciding when this can happen requires knowledge of the routing policy and not just the topology.
 For instance, a policy might require all traffic for a particular prefix going through a router where an aggregate is advertised to go over a single link, even if there are several available in the toplogy.
-If the single link fails, then a black hole might be introduced.
-Fortunately, the PGIR captures this information precisely, describing the how information meeting the policy flows over the topology.
+If that link fails, a black hole might be introduced.
+Fortunately, the PGIR captures this information precisely.
+%, describing the how information meeting the policy flows over the topology.
 
-We can frame the aggregation problem as a problem of connectivity in the PGIR.
-More specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures that would disconnect where the prefix originates from where its more specific aggregate is located.
-The difficulty lies in the fact that the same links in the topology can appear in multiple places in the PGIR.
+We frame the aggregation problem as a problem of connectivity in the PGIR.
+Specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures that would disconnect where the prefix originates from where its more specific aggregate is located.
+The difficulty is that the same links in the topology can appear in multiple places in the PGIR.
 We adopt the following simple strategy to lower bound the number of failures:
 \begin{enumerate}
-	\item Pick a random path through the product graph from start to end.
-	\item Remove all edges in the product graph corresponding to the set of topological edges choosen.
+	\item Pick a random start-to-end path in PGIR.
+	\item Remove all edges in the PGIR for the set of topological edges chosen.
 	\item Repeat until no path exists.
 \end{enumerate}
-Since each path through the PGIR will result in a new edge-disjoint path through the topology (since we have removed all already used edges), and since the number of edge-disjoint paths through the topology is no more than the min-cut.
+The number of PGIR paths that we are able to remove is a lower bound on the number of failures.
+Since each PGIR path results in a new edge-disjoint path through the topology (because of Step 2), and since the number of edge-disjoint paths through the topology is no more than the min-cut.
 \todo{clarify this}
 
-For example, imagine we use the earlier data center example from Section~\ref{sec:motivation}, with the policy: $p_{g1} \mapsto end(A)$, where $p_{g1}$ falls under the $p_{g^*}$ aggregate.
-The data center topology and a simplification of the corresponding product graph are shown in Figure~\ref{fig:aggregation-safety}.
-Since the compiler knows an aggregate will be placed at $X$, and it knows that, for prefix $p_{g1}$ the route will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$ in the product graph.
-In this case, we could remove the $A$ -- $D$ -- $X$ path first.
-We would then need to remove any other $A$ -- $D$ or $D$ -- $X$ links from the product graph, though in this case there are none.
-Next, we could remove the links along the $A$ -- $C$ -- $X$ path, repeating the process.
-Because afterwards $A$ is disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix $p_{g1}$.
-This process is then repeated for other aggregation locations (e.g., $Y$).
+For example, imagine we use the data center example from \S\ref{sec:motivation}, with the policy: $p_{g1} \mapsto end(A)$, where $p_{g1}$ falls under the $p_{g^*}$ aggregate.
+Figure~\ref{fig:aggregation-safety} shows the network topology and a simplified PGIR.
+Since the compiler knows an aggregate will be placed at $X$, and it knows that, the route for $p_{g1}$ will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
+We could remove the $A$--$D$--$X$ path first.
+We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR, though in this case there are none.
+Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
+Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix $p_{g1}$.
+This process is repeated for other aggregation locations (e.g., $Y$).

### 2016-01-27 paper/evaluation.tex
adding initial performance numbers of backbone

@@
 \centering
+\includegraphics[width=\columnwidth]{figures/compilation-times-backbone.png}
+\label{fig:compilation-times-dc}
+\caption{Data center compilation times.}
+\end{figure}
+
+\begin{figure}[t!]
+\centering
 \includegraphics[width=\columnwidth]{figures/config-compression-dc.png}
@@
 
-\subsection{Propane-generated configurations}
+\subsection{Propane vs. operator configurations}
 
-Finally, we comment briefly on how the configurations generated by \sysname differ from those generated by operators today.
-In some cases, \sysname-generated configurations are implemented as one would expect.
+Finally, we comment briefly on how \sysname-generated configurations differ from those generated by operators today. 
+%
+In some cases, \sysname configurations are implemented as one would expect.
 For example, preferences among neighboring ASes are implemented with a compiler-generated community value to tag incoming routes according to preference, which is then observed at other border routers to influence decisions.
-In other cases, the \sysname configurations are different, often relying on a different BGP mechanism to achieve the same result.
-For example, in one instance operators would use the no-export community to prevent routes from leaking beyond a certain tier of the data center, whereas \sysname would selectively import the route only below a certain tier.
-\sysname could use a similar implementation mechanism in the future as an optimization.
-In another instance, operators made assumptions about a neighboring AS to cut down on the propogation of route advertisements.
+In other cases, the \sysname configurations are different, relying on a different BGP mechanism to achieve the same result.
+Some key differences that we observed were:
+%
+$i)$ operators used the no-export community to prevent routes from leaking beyond a certain tier of the data center, whereas \sysname selectively imported the route only below a certain tier; 
+%\sysname could use a similar implementation mechanism in the future as an optimization.
+%
+$ii)$ operators prevented unneeded propagation of more-specific route advertisements from a neighboring AS based on their out-of-band knowledge about topology, whereas \sysname propagated these advertisements; and
+%
+$iii)$ operators used a layer of indirection using community groups and re-writing to implement certain policies in a more maintainable way, where \sysname uses flat communities.
+We are currently investigating if such differences matter to operators (e.g., if they want to read \sysname configurations) and, if necessary, how to reduce them.

### 2016-01-27 paper/introduction.tex

@@
 %
-They require careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure~\cite{x,y,z}.
-To address this challenge, many researchers are beginning to explore
+They require careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure.
+Even ignoring failures, it is necessary for controller systems to
+scale to meet the demands of larger networks and to react sufficiently quickly
+to a changing environment. To address this challenge, some researchers are beginning to 
+explore
 multi-controller networks, with interacting controllers, thus bringing back distributed
-control planes~\cite{x,y,z} and their current programming difficulties.  However, academic
+control planes~\cite{mccauley2013extending,onos} and their current programming difficulties.  However, academic
 language design and implementation efforts have not kept pace.  For instance, work on
@@
 name a few, has not yet shown how to implement fault tolerant
-multi-controller systems that support their abstractions efficiently.
+multi-controller systems that support their high-level abstractions efficiently.
 
-In this paper, we ask if it is possible to program distributed control planes using network-wide policies.
-Operators should be able to directly express network-wide policies, which are automatically decomposed into individual device configurations.
-The resulting forwarding behavior, which emerges through device interactions, must be policy-compliant under all possible failures.
-If successful, this approach would combine easy programmability of centralized control planes and failure robustness of distributed control planes.
+In this paper, we ask if it is possible to program 
+distributed control planes using network-wide policies.  In particular,
+operators should be able to directly express \emph{end-to-end}, 
+\emph{network-wide} policies directly; it is the job of a compiler
+to decompose such policies into individual device configurations. 
+In addition, the resulting forwarding behavior, which emerges through device interactions, must be policy-compliant under all possible failures.
+If successful, this approach would combine easy programmability of centralized control planes with the failure robustness and scalability of distributed control planes.
 %

### 2016-01-27 paper/compilation.tex
editing pass over compilation section.

@@
   \begin{minipage}[t]{.5\linewidth}
+
   \hdr{\large Topology}{}
@@
 
-  \caption{Example Product Graph IR construction.}
+  \caption{Example Product Graph IR construction for policy: $(W \cdot A \cdot C \cdot D \cdot out) \gg (W \cdot B \cdot in^* \cdot out)$.}
   \label{fig:example-compilation}
@@
 % Formally define automata
-The RIR policy is of the form $r_1 \gg \dots \gg r_j$.
+The RIR policy is an ordered sequence of regular expressions $r_1 \gg \dots \gg r_j$.
 While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., route announcements flowing in the opposite direction).
@@
 Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ consists of all internal and external ASes, \ratul{ASes or locations?} $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+The alphabet $\Sigma$ consists of all all abstraction locations (routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
 %
@@
 For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. 
-We say a node $x$ shadows node $y$ in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$.
+A node $x$ shadows node $y$ in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$.
 That is, $x$ shadows $y$ when they are different nodes in the PGIR that represent the same topology location.
@@
 The preference function $P$ for node $v = (x, a_1, \dots, a_m)$ is defined as $P(v) = \set{i~\vert~a_i \in F_i} $.
-That is, it records which preferences are achieved for the policy automata for each node in the product construction.
+That is, it records which preferences are achieved from each policy automaton for every node in the product construction.
 %
@@
 Since we are primarily concerned with guaranteeing user policy correctness and safety with respect to network failures, it is useful to eliminate cases that are not possible due to loops. 
-For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
+%For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
+We use graph dominators~\ref{bib:todo} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any simple path between the start and end nodes.
+A node $x$ dominates $y$ if $x$ appears on every path leading to $y$ from a source node. Many efficient algorithms exist for finding graph dominators in practice~\ref{bib:todo}.
+%We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
+For example, node $(1,1) W$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it most go through another $W$ in either case.
+Colored nodes and dashed edges are removed after minimization since they are irrelvant to the BGP decision process.
+%
+%Although fully minimizing this graph is an NP-complete problem,  a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.
 
-We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node.
-For example, node $(1,1) W$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it most go through another $W$ in either case.
-%
-Although fully minimizing this graph is an NP-complete problem,  a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.
-
-A node $x$ dominates $y$ if $x$ appears on every path leading to $y$ from a source node.
+%A node $x$ dominates $y$ if $x$ appears on every path leading to $y$ from a source node.
 Many efficient algorithms exist for finding graph dominators~\ref{bib:todo}.
@@
 %
-\begin{itemize}
-  \item Remove nodes that never reach the end node
-  \item Remove nodes not reachable from the $start$ node
-  \item Remove any node $x$ such that $x$ is dominated by $y$ in $G$ or $G^R$, and $loc(x) = loc(y)$
-  \item Remove any edge from $x$ to $y$ in $G$ or $G^R$ if there is some node $z$ dominated by $y$ such that $loc(x) = loc(z)$
-\end{itemize}
+%\begin{itemize}
+%  \item Remove nodes that never reach the end node
+%  \item Remove nodes not reachable from the $start$ node
+%  \item Remove any node $x$ such that $x$ is dominated by $y$ in $G$ or $G^R$, and $loc(x) = loc(y)$
+%  \item Remove any edge from $x$ to $y$ in $G$ or $G^R$ if there is some node $z$ dominated by $y$ such that $loc(x) = loc(z)$
+%\end{itemize}
 %
-Repeated application of the above rules leads to removing the colored nodes and dashed lines in Figure~\ref{fig:example-compilation}.
+%Repeated application of the above rules leads to removing the colored nodes and dashed lines in Figure~\ref{fig:example-compilation}.
 
@@
 Instead, it translates matches from external ASes into a BGP regular expression filter.
-For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$ and prefer them equally.
+For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$.
 In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
-In practice, we model the unknown AS topology as a special node in the product graph that generates a filter to match any sequence of ASes.
+Any unknown AS topology is modelled as a special node in the product graph that generates a filter to match any sequence of ASes.
 
@@
 In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
-In this example, however, assuming our network and$W$ have an agreement to honor MEDs, the BGP MED attribute can influence $W$ to prefer $A$ over $B$.
+In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the BGP MED attribute can influence $W$ to prefer $A$ over $B$.
 Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
 The compiler can perform a simple analysis to determine when it can utilize various BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
-Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
+%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
 Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
+Figure~\ref{fig:config} shows the full configuration from the compilation example.
 
-Figure~\ref{fig:config} shows the full configuration from the compilation example.
-To make configurations more compact and readable, the \sysname compiler rewrites configurations in ABGP, e.g., removing community tagging and matching when there is no ambiguity.
-Figure~\ref{config-min} shows minimized router configurations.
-\todo{figure was removed?}
+To make configurations more compact and readable, the \sysname compiler makes several passes over the ABGP policy, removing community tagging and matching when possible, combining filters, removing dead filters, and so on.
+In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from.
+After removing the communities, the two rules at router $B$ are merged into a single rule.
 
@@
 
-As demonstrated with Example 2 in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing traffic when failures occur.
+As demonstrated with Example 2 in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur.
 Deciding when this can happen requires knowledge of the routing policy and not just the topology.
-For instance, a policy might require all traffic for a particular prefix going through a router where an aggregate is advertised to go over a single link, even if there are several available in the toplogy.
+For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated, even if there are several available in the toplogy.
 If that link fails, a black hole might be introduced.
-Fortunately, the PGIR captures this information precisely.
+Fortunately, the PGIR captures the information about both the policy and topology precisely.
 %, describing the how information meeting the policy flows over the topology.
@@
 The difficulty is that the same links in the topology can appear in multiple places in the PGIR.
-We adopt the following simple strategy to lower bound the number of failures:
-\begin{enumerate}
-	\item Pick a random start-to-end path in PGIR.
-	\item Remove all edges in the PGIR for the set of topological edges chosen.
-	\item Repeat until no path exists.
-\end{enumerate}
-The number of PGIR paths that we are able to remove is a lower bound on the number of failures.
-Since each PGIR path results in a new edge-disjoint path through the topology (because of Step 2), and since the number of edge-disjoint paths through the topology is no more than the min-cut.
+We adopt the following simple strategy to lower bound the number of failures: $i)$ Pick a random start-to-end path in PGIR, $ii)$ remove all edges in the PGIR for the set of topological edges chosen, and $iii)$ repeat until no such path exists.
+The number of PGIR paths that we are able to remove is a lower bound on the number of failures required to disconnect the prefix from its aggregate. 
+%Since each PGIR path results in a new edge-disjoint path through the topology (because of Step 2), and since the number of edge-disjoint paths through the topology is no more than the min-cut.
 \todo{clarify this}

### 2016-01-27 paper/introduction.tex

@@
 To reduce configuration errors, many practitioners have a adopted a template-based
-approach~\cite{hatch,thwack}, in which common configuration patterns are captured as parameterized templates.
- While templates help ensure certain kinds of consistency across devices, they do not
-bridge the
-semantic divide between network policies and device-level configuration.
-They do not provide fundamentally different abstractions
-from existing configuration languages.
+approach~\cite{hatch,thwack}, in which common configuration patterns are captured as parameterized templates.  More powerful still are systems like
+ConfigAssure~\cite{narain:lisa05,narain+:configassure}, which use SAT solving
+and model finding tools to fill in parameters in configurations while
+ensuring key correctness constraints are satisfied.  However,
+ while templates help ensure certain kinds of consistency across devices, 
+they do not bridge the
+semantic divide between network policies and device-level configuration,
+nor do they do not provide fundamentally different abstractions
+from existing configuration languages or new, higher-level reasoning 
+principles.
 
@@
 Even ignoring failures, it is necessary for controller systems to
-scale to meet the demands of larger networks and to react sufficiently quickly
+scale to meet the demands of larger, geographically distributed networks, 
+and to react sufficiently quickly
 to a changing environment. To address this challenge, some researchers are beginning to 
@@
 multi-controller networks, with interacting controllers, thus bringing back distributed
-control planes~\cite{mccauley2013extending,onos} and their current programming difficulties.  However, academic
-language design and implementation efforts have not kept pace.  For instance, work on
-experimental SDN languages
-such as Frenetic~\cite{frenetic}, Flowlog~\cite{flowlog}, Vericon~\cite{vericon}, Merlin~\cite{merlin}, NetKAT~\cite{netkat}, and Kinetic~\cite{kinetic}, to
-name a few, has not yet shown how to implement fault tolerant
-multi-controller systems that support their high-level abstractions efficiently.
+control planes~\cite{mccauley2013extending,onos} and their current programming difficulties.  
+%However, academic
+%language design and implementation efforts have not kept pace.  For instance, work on many
+%experimental SDN languages~\cite{frenetic,flowlog,vericon,merlin,netkat,kinetic,pga} has not yet shown how to implement fault tolerant
+%multi-controller systems that support their high-level abstractions efficiently.
+A second problem with existing SDN frameworks, and the languages used to
+program them, is that while they provide many 
+effective \emph{intra}-domain routing
+abstractions, they fail to provide a \emph{coherent} means to enable 
+\emph{inter}-domain communication of available routes.
 
-In this paper, we ask if it is possible to program 
-distributed control planes using network-wide policies.  In particular,
-operators should be able to directly express \emph{end-to-end}, 
-\emph{network-wide} policies directly; it is the job of a compiler
-to decompose such policies into individual device configurations. 
-In addition, the resulting forwarding behavior, which emerges through device interactions, must be policy-compliant under all possible failures.
-If successful, this approach would combine easy programmability of centralized control planes with the failure robustness and scalability of distributed control planes.
-%
-More pragmatically, it would help many networks that, for the foreseeable future, will continue to use a distributed control plane, due to the difficulty of migrating to SDN or the inherent scalability and failure-robustness of distributed control.
+Hence, in this paper, we have two central goals:
+\begin{enumerate}
+\item Design a new, high-level, declarative language with abstractions 
+suitable for simultaneously expressing intra-domain routing, inter-domain 
+routing and alternatives in case of failures.
+\item Define algorithms for compiling these specifications in to 
+configurations for off-the-shelf devices running standard
+distributed control plane algorithms, while ensuring correct behavior
+independent of the number of faults.
+\end{enumerate}
 
-Through \sysname, our system that includes a language and a compiler, we demonstrate the feasibility of programming distributed control planes.
+To achieve the first goal, we borrowed heavily from the design of
+recent high-level SDN languages based around specification of 
+paths via regular expressions such as FatTire~\cite{fattire}, 
+Merlin~\cite{foster:merlin}, and
+NetKAT~\cite{netkat}.  However, one of the key differences is that
+we incorporate expression of user preferences in to the algebra
+of regular expressions and provide a semantics to our language
+in terms of sets of ranked paths.  The preferences indicate possible
+fail-over routes:  If too many faults occur, the network may be
+disconnected, but as long as any path the user has expressed is
+still available, the system guarantees the highest available ranked
+path will be taken.  We also support network operators by defining a
+set of common abbreviations for entering, leaving, and traversing
+the user network.  Operators use familiar logical operations
+to build routes in a modular and compositional manner from these 
+primitives.  All abbreviations are translated in to our regular-expression-based
+intermediate representation and compiled from there.
+
+To achieve the second goal, we define program analysis and compilation
+algorithms that translate the regular policies in to a graph-based
+intermediate language and from there in to BGP.  During the
+compilation process, our compiler automatically synthesizes per-device
+import and export filters, local preferences, MED attributes, and 
+community tags.  We chose BGP for pragmatic reasons:  it is an industry
+standard and many data centers use it internally as well as externally.
+Indeed, despite the presence of SDN, many networks will continue to
+use BGP for the foreseeable future due to investments they have already
+made in the infrastructure, the difficulty of transitioning to SDN,
+and the scalability and fault-tolerance advantages of a distributed
+control plane.  However, using BGP as a back end is not without its 
+challenges: not all high-level specifications can be implemented correctly in
+the presence of arbitrary failures.  Consequently, we define new
+program analysis algorithms to detect specifications that cannot be implemented
+and report our findings to the user, so he or she may fix the specification
+early rather than waiting until configurations have been deployed.  
+These algorithms differ from
+standard BGP analysis algorithms~\cite{feamster:rcc,batfish} because they operate on representations of
+our high-level specifications (which has the pleasant effect of simplifying our 
+task) rather than directly on arbitrary BGP configurations.
+
+To evaluate language and system, we have experimented with specifying policy
+for several realistic data center and backbone networks. We have also
+measured the performance of our compiler, demonstrating that our compilation
+algorithms scale to topologies with several thousand routers.
+
+In the remainder of the paper, we review BGP~\ref{sec:background} (readers
+familiar with BGP may skip this section),
+further motivate the need for new languages 
+for programming distributed control planes (Section \ref{sec:motivation}),
+introduce \sysname{} by example (Section \ref{sec:propane}), 
+explain our compiler algorithms (Section \ref{sec:compilation}),
+present several lemmas justifying the correctness of our techniques (Section \ref{sec:theory}), describe our implementation (Section \ref{sec:implementation}
+and discuss related work (Section \ref{sec:related}).
+
+%% In this paper, we ask if it is possible to program 
+%% fully distributed control planes using 
+%% \emph{end-to-end}, 
+%% \emph{network-wide} policies, while handing the job of compiling
+%% such policy.  In particular,
+%% operators should be able to directly express \emph{end-to-end}, 
+%% \emph{network-wide} policies directly; it is the job of a compiler
+%% to decompose such policies into individual device configurations. 
+%% In addition, the resulting forwarding behavior, which emerges through device interactions, must be policy-compliant under all possible failures.
+%% If successful, this approach would combine easy programmability of centralized control planes with the failure robustness and scalability of distributed control planes.
+%% %
+%% More pragmatically, it would help many networks that, for the foreseeable future, will continue to use a distributed control plane, due to the difficulty of migrating to SDN or the inherent scalability and failure-robustness of distributed control.
+
+%% Through \sysname, our system that includes a language and a compiler, we demonstrate the feasibility of programming distributed control planes.
 We focus on BGP, a common and highly flexible way to implement distributed control planes, and show how to automatically generate router BGP configurations from network-wide policies.
 
-We face two challenges in designing \sysname that differ from designing a system for programming data planes~\cite{x,y,z}.
+%% We face two challenges in designing \sysname that differ from designing a system for programming data planes~\cite{x,y,z}.
 The first is policy specification itself---specifying network {\em policies} is different from specifying network {\em paths}.
-%
-The specification must compactly capture behavior under all possible failures.
+%% %
+%% The specification must compactly capture behavior under all possible failures.
 Since there is no controller at runtime, the routers must be programmed ahead of time, based on the specification, to handle failures.
-%
-Further, many policies naturally under-specify paths (e.g., "prefer paying neighbors" is not a concrete path).
-%
-\sysname addresses this specification challenge by allowing operators to express {\em path preferences}, where preference describes a set of valid paths and less-preferred options are taken only when a higher-preference options are unavailable.
+%% %
+%% Further, many policies naturally under-specify paths (e.g., "prefer paying neighbors" is not a concrete path).
+%% %
+%% \sysname addresses this specification challenge by allowing operators to express {\em path preferences}, where preference describes a set of valid paths and less-preferred options are taken only when a higher-preference options are unavailable.
 
-The direct nature of \sysname specifications brings up the second challenge, of compiling them to router configurations.
+%% The direct nature of \sysname specifications brings up the second challenge, of compiling them to router configurations.
 We must compute the sets of paths represented by the intersection of multiple preferences and topology, compute which ones can be honored under a given failure scenario, and ensure policy compliance under all possible failure cases.
@@
 
-We evaluate \sysname by using it to encode policies of real backbone and data center networks.
+%% We evaluate \sysname by using it to encode policies of real backbone and data center networks.
 
-\todo{new intro is not complete}
+%% \todo{new intro is not complete}

### 2016-01-27 paper/introduction.tex
intro rewrites

@@
 The centralized control planes of SDN, however, are not a panacea.
-%
-They require careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure.
+First, while many SDN systems provide effective \emph{intra}-domain routing
+abstractions, allowing users to specify paths within their own network,
+they fail to provide a coherent means to enable specification of preferred
+\emph{inter}-domain routes.  Second, centralized control planes
+require careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure.
 Even ignoring failures, it is necessary for controller systems to
@@
 %multi-controller systems that support their high-level abstractions efficiently.
-A second problem with existing SDN frameworks, and the languages used to
-program them, is that while they provide many 
-effective \emph{intra}-domain routing
-abstractions, they fail to provide a \emph{coherent} means to enable 
-\emph{inter}-domain communication of available routes.
 
@@
 \begin{enumerate}
-\item Design a new, high-level, declarative language with abstractions 
-suitable for simultaneously expressing intra-domain routing, inter-domain 
-routing and alternatives in case of failures.
+\item Design a new, high-leve language with abstractions 
+for expressing intra-domain routing, inter-domain 
+routing and routing alternatives in case of failures.
 \item Define algorithms for compiling these specifications in to 
-configurations for off-the-shelf devices running standard
+configurations for devices running standard
 distributed control plane algorithms, while ensuring correct behavior
@@
 To achieve the first goal, we borrowed heavily from the design of
-recent high-level SDN languages based around specification of 
-paths via regular expressions such as FatTire~\cite{fattire}, 
+recent high-level SDN languages such as FatTire~\cite{fattire}, 
 Merlin~\cite{foster:merlin}, and
-NetKAT~\cite{netkat}.  However, one of the key differences is that
+NetKAT~\cite{netkat} by using regular expressions to specify paths
+through networks.  However, our design also contains several key
+differences from existing languages.  The most important difference is semantic:  the paths specified
+by programmers can extend from outside the operator's network to inside
+the network, across several devices internally, and then out again.  This design
+choice allows users to specify preferences about both external and internal 
+routes in the same uniform notation.  No SDN programming language provides
+similar facilities.  In addition,
 we incorporate expression of user preferences in to the algebra
 of regular expressions and provide a semantics to our language
-in terms of sets of ranked paths.  The preferences indicate possible
+in terms of sets of ranked paths.  These preferences indicate possible
 fail-over routes:  If too many faults occur, the network may be
 disconnected, but as long as any path the user has expressed is
-still available, the system guarantees the highest available ranked
+still available, the system guarantees the highest-ranked, available
 path will be taken.  We also support network operators by defining a
 set of common abbreviations for entering, leaving, and traversing
-the user network.  Operators use familiar logical operations
+the user network and we provide abstractions for managing common features of
+control plane algorithms such as route aggregation.  Operators use familiar logical operations
 to build routes in a modular and compositional manner from these 
-primitives.  All abbreviations are translated in to our regular-expression-based
+primitives.  Our abbreviations are translated in to our regular-expression-based
 intermediate representation and compiled from there.
@@
 and report our findings to the user, so he or she may fix the specification
-early rather than waiting until configurations have been deployed.  
+early rather than waiting until configurations have been deployed.  We also
+analyze route aggregation to detect the possibility of failure-induced black-holes.
 These algorithms differ from
-standard BGP analysis algorithms~\cite{feamster:rcc,batfish} because they operate on representations of
-our high-level specifications (which has the pleasant effect of simplifying our 
-task) rather than directly on arbitrary BGP configurations.
+standard BGP analysis algorithms~\cite{feamster:rcc,batfish} because they operate on 
+our graph-based intermediate representation, which operates at a higher level
+of abstraction than raw BGP configurations (and which has the pleasant effect of simplifying our 
+task).
 
-To evaluate language and system, we have experimented with specifying policy
-for several realistic data center and backbone networks. We have also
+To evaluate the \sysname{} language and system, we have experimented with specifying policy
+for several realistic data center and backbone networks and compared these specifications
+with existing operating specifications. We have also
 measured the performance of our compiler, demonstrating that our compilation

### 2016-01-27 paper/implementation.tex
trimming implementation, cutting future work and conclusion.

@@
 \section{Implementation}
+\label{sec:implementation}
 
@@
 Similarly, to model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.
-
+%
 Rather than construct the product graph in full, our implementation prevents exploring parts of the graph when no accepting state is reachable in any of the corresponding regular automata during construction.
@@
 More complex algorithms with better theoretical complexity exist~\ref{bib:todo} and may be better suited for large enough topologies.
-However, we have not found minimization to be a bottleneck in our implementation.
-Minimization steps are ordered from cheapest to most expensive.
 All minimization steps are repeated until no more progress can be made.
@@
 
-When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the ``can prefer'' relation.
+When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the \textit{protect} function.
 That is, whenever for two states $n_1$ and $n_2$ we compute $protect(G_j, n_1, G_i, n_2)$, if the function evaluates to $true$, then each of the intermediate related states $x$ and $y$ must also satisfy $protect(G_j, x, G_i, y)$.
@@
 The naive code generation algorithm described in Section~\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair for every node in the product graph before minimization.
-Our implementation performs partial minimization during generation by recognizing common cases where there is no restriction on exporting or importing from neighbors.
+Our implementation performs partial minimization during generation by recognizing common cases where there is no restriction on exporting to or importing from neighbors.

### 2016-01-27 paper/introduction.tex
intro edits

@@
 
-In the remainder of the paper, we review BGP~\ref{sec:background} (readers
+\dpw{The following could be cut for space.}
+In the remainder of the paper, we review BGP (Section~\ref{sec:background}---readers
 familiar with BGP may skip this section),
@@
 explain our compiler algorithms (Section \ref{sec:compilation}),
-present several lemmas justifying the correctness of our techniques (Section \ref{sec:theory}), describe our implementation (Section \ref{sec:implementation}
-and discuss related work (Section \ref{sec:related}).
+present several lemmas justifying the correctness of our techniques (Section \ref{sec:theory}), describe our implementation (Section \ref{sec:implementation})
+evaluate our work  (Section \ref{sec:evaluation}) and discuss related work (Section \ref{sec:related}).
 

### 2016-01-27 paper/introduction.tex
stuff

@@
 for several realistic data center and backbone networks and compared these specifications
-with existing operating specifications. We have also
+with existing configurations. We have also
 measured the performance of our compiler, demonstrating that our compilation

### 2016-01-27 paper/compilation.tex
more edits.

@@
 \para{Minimization}
-\ratul{This minimization section can probably go entirely, shrunken, or moved to the implementation}
-Before checking if policies captured by the PGIR are safe, we minimize the PGIR to better scale our failure safety checks.
-The minimization is based on the observation that although every path in the PGIR is a valid path in the topology, we do not want to consider loops when configuring the network.
-In particular, BGP's loop prevention mechanism, by which an AS rejects any route for which it is already in the AS path, means that loops should never occur.\footnote{ Misconfigured aggregation can still lead to loops in BGP.}
+
+Before checking if policies captured by the PGIR are safe, we minimize the PGIR to improve our safety analysis. 
+The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops.
+In particular, BGP's loop prevention mechanism forces an AS to reject any route for which it is already in the AS path.
 %
-However, the PGIR may contain many paths that form loops in the topology.
-For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path that BGP announcements might take, leading to a path that satisfies the preference 1 policy, but which contains a loop.
+For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path, leading to a path that satisfies the preference 1 policy, but which contains a loop.
 %
-Since we are primarily concerned with guaranteeing user policy correctness and safety with respect to network failures, it is useful to eliminate cases that are not possible due to loops. 
+It often simplifies the failure-safety analysis to eliminate cases that are not possible due to loops. 
 %For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
-We use graph dominators~\ref{bib:todo} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any simple path between the start and end nodes.
-A node $x$ dominates $y$ if $x$ appears on every path leading to $y$ from a source node. Many efficient algorithms exist for finding graph dominators in practice~\ref{bib:todo}.
+We use graph dominators~\ref{bib:todo} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
+In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading to $y$ from the start node. Many efficient algorithms exist for finding graph dominators in practice~\ref{bib:todo}.
 %We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
@@
 Suppose we simply set the local preference at router $C$ to prefer $D$ over $E$.
-However, now if the A -- C link fails, then suddenly $C$ has made the wrong decision and can not get either the primary or backup route specified, despite the fact that the $W \cdot B \cdot C \cdot E$ path is available.
+However, now if the A -- C link fails, then suddenly $C$ has made the wrong decision and can not get either the primary or backup route specified, despite the fact that the $W \cdot B \cdot C \cdot E$ path is available in the network.
 
 At a first cut, any time a router must make a decision locally between several route options, there is the possibility that it might choose incorrectly.
-PGIR captures this notion of choice precisely.
+The PGIR captures this notion of choice precisely.
 For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the PGIR, possibly receiving announcements from $X$ or $Y$.
@@
 %
-where \textit{protect} means that, from $N_1$ on the PGIR restricted nodes that can potentially achieve preference $j$ or better, there are at least as many paths as from $N_2$ restricted to $G_i$
+where \textit{protect} means that, from $N_1$ on the product graph restricted to nodes that can potentially achieve preference $j$ or better, 
+there is always a path to each each ending location whenever this is a path from $N_2$ restricted to $G_i$.
 
@@
     \State $(n_1,n_2) \gets q.Dequeue()$
-    \For {$x$ in $adj(G_2, n_2)$}
-      \If {some $y$ in $adj(G_1,n_1)$ shadows $x$}
+    \For {$x$ in adj($G_2$, $n_2$)}
+      \If {\big($\exists y \in$ adj($G_1$,$n_1$), shadows $x$\big) \textbf{or} \\  
+            \hspace{5.2em} \big($\exists y \in$ $G_1$, dominates $n_1$, shadows $x$\big)}
         \If {$(x,y)$ not marked}
@@
 It walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
-Thus any paths leading from $N_2$ will have an equivalent path over the same topology locations from $N_1$.
-Algorithm~\ref{alg:failures} works because each PGIR node can have at most one outgoing neighbor with the same topological location, so the next hop neighbors can be checked without backtracking.
+When there is no equivalent step, the algorithm checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) that can protect against failures instead.
+Thus any time $N_2$ can get to a final location for preference $i$, $N_1$ can get to at least the same final locations for a better preference $j$.
 The algorithm terminates since the number of related states $(x,y)$ that can be expolored is finite.
-\ryan{Add the new part that goes up to a dominating predecessor when no other option}
 
@@
 If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
-\ryan{We are checking if the preorder forms a partial order by satisfying asymmetry}
 
@@
 
-The checks for failure safety described above overlook a critical point: even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$.
+The checks for failure safety described above overlook one critical point: Paths for a higher preference might not actually exist due to loops.
+To avoid this situation, the compiler conservatively checks that, when node $x$ protects against failures for node $y$, its does so without using any nodes that shadow another node that appears ``above'' $x$ in the PGIR.
+%It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
+%even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$.
 To avoid this situation, the compiler conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the PGIR (i.e., nodes reachable from $x$ in $G_j^R$).
 It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
-\ryan{rework this}
 
@@
 
-Once we have the total ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
+Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
 The idea is to encode the state of the automaton using BGP community values.
@@
 In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from.
-After removing the communities, the two rules at router $B$ are merged into a single rule.
+Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
 

### 2016-01-27 paper/compilation.tex
Moving theory to compilation.

@@
 The number of PGIR paths that we are able to remove is a lower bound on the number of failures required to disconnect the prefix from its aggregate.
-%Since each PGIR path results in a new edge-disjoint path through the topology (because of Step 2), and since the number of edge-disjoint paths through the topology is no more than the min-cut.
-\todo{clarify this}
 
@@
 This process is repeated for other aggregation locations (e.g., $Y$).
+
+\subsection{Formal Properties}
+
+\newtheorem{prop}{Proposition}[section]
+
+%Here we investigate the correctness and expressiveness properties of \sysname.
+We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures?
+(2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?
+
+If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario.
+We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges.
+We argue that \sysname is correct by breaking down the claim into two distinct parts:
+
+\begin{prop}
+A distributed BGP configuration is \textit{Sound} with respect to a \sysname policy, if the any route traffic takes in the network, is a valid route specified in the policy.
+\end{prop}
+
+The Soundness claim follows directly from compilation of the product graph.
+Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations are Sound.
+
+\begin{prop}
+A distributed BGP configuration is \textit{Complete} with respect to a \sysname policy, if the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
+\end{prop}
+
+%The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.
+This means there is a valid path in the product graph corresponding to this path, and which is available in the network.
+%Assume we are unable to achieve this route in the network.
+To not achieve this path means that some router along the advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead.
+This implies that router that makes the ``wrong'' choice appears as a separate node in the product graph.
+However, from our failure safety check, we know that the other, more-preferred node must have a superset of the paths to accepting states as the less preferred node (from which it stole the route) for at least as good of a final preference.
+The argument then proceeds by induction on the path length - there are only a finite number of such stealings that can occur, each of which will ultimately still result in a route advertisement reaching $X$ along a most preferred path.
+
+Any \sysname-compiled policy will be \textit{Complete} as a result of the failure safety check.
+%
+The combination of Soundness and Completeness ensures that the distributed implementation will always achieve the best routes possible, yet will never also use any unwanted routes.
+
+\begin{prop}
+The internal routers in a distributed BGP configuration produced by \sysname will be stable. 
+\end{prop}
+
+The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo} for stable BGP.
+In particular, any policy with a dispute wheel will not pass the stronger failure safety check by \sysname.
+
+%\begin{figure}[t!]
+%\includegraphics[width=\columnwidth]{figures/dispute-wheel}
+%\label{fig:dispute-wheel}
+%\caption{Product graph for a dispute wheel.}
+%\end{figure}
+
+%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}.
+If a set of BGP configurations do not have a dispute wheel, then they will converge to their best routes.
+Any BGP policy with a dispute wheel will not satisfy the failure safety condition in Section~\ref{sec:compilation}.
+Assume that the preferences in the policy describe a dispute wheel, and we will show that our failure check will reject the policy.
+Informally, a dispute wheel occurs when there are some number of nodes $u_1, \dots, u_n$ attempting to get a path to a destination node $d$.
+Each node $u_i$ prefers to go through its neighbor $u_{i+1}$ over route $R_i$ than directly to $d$ with route $Q_i$.
+Thus the nodes form a wheel of preferences.
+The product graph for a policy that contains a dispute wheel will look like Figure~\ref{fig:dispute-wheel}, which shows a dispute wheel of size 3.
+In order to pass the failure safety check for the compiler, the more-preferred node for $u_2$ will need to have a superset of the paths starting from the less-preferred node for $u_2$.
+In turn, this means that the maximum length path after visiting the more preferred $u_2$ will be $max(Z) = 1 + max(Y)$, similarly, if we look at $u_1$, we will determine that $max(Y) = 1 + max(X)$, and so on.
+The resulting equations define a system of unsatisfiable equations.
+Therefore, it is not possible for \sysname to compile a BGP policy that contains a dispute wheel.
+Since no-dispute-wheel is a sufficient condition for BGP stability, any compiled \sysname policy will be stable.
+
+An important distinction is that BGP might still be instable with respect to other external ASes, since \sysname has no way of configuring their routing policy and can only rely on AS path filters to see what advertisements are observed.

### 2016-01-27 paper/compilation.tex
trim formal properties section.

@@
 We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges.
-We argue that \sysname is correct by breaking down the claim into two distinct parts:
+We argue that \sysname is correct by breaking down the claim:
 
 \begin{prop}
-A distributed BGP configuration is \textit{Sound} with respect to a \sysname policy, if the any route traffic takes in the network, is a valid route specified in the policy.
+A distributed BGP configuration produced by \sysname is \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.
 \end{prop}
-
-The Soundness claim follows directly from compilation of the product graph.
+%
+%The Soundness claim follows directly from compilation of the product graph.
 Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations are Sound.
-
+%
 \begin{prop}
-A distributed BGP configuration is \textit{Complete} with respect to a \sysname policy, if the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
+A distributed BGP configuration produced by \sysname is \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
 \end{prop}
-
+%
 %The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.
@@
 The argument then proceeds by induction on the path length - there are only a finite number of such stealings that can occur, each of which will ultimately still result in a route advertisement reaching $X$ along a most preferred path.
-
-Any \sysname-compiled policy will be \textit{Complete} as a result of the failure safety check.
 %
-The combination of Soundness and Completeness ensures that the distributed implementation will always achieve the best routes possible, yet will never also use any unwanted routes.
-
+%Any \sysname-compiled policy will be \textit{Complete} as a result of the failure safety check.
+%
+The combination of Soundness and Completeness ensures that the distributed implementation will always send traffic along the best paths possible, yet will also never also use any undesired paths.
+These properties rely on the fact that \sysname produces stable BGP configurations:
+%
 \begin{prop}
@@
 
-The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo} for stable BGP.
+%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo} for stable BGP.
 In particular, any policy with a dispute wheel will not pass the stronger failure safety check by \sysname.

### 2016-01-27 paper/compilation.tex
minor fix in ABGP policy.

@@
            $\MED \leftarrow 81, \PEER \leftarrow W$
-$\Router{C}$-
+$\Router{C}$
   Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $

### 2016-01-28 paper/evaluation.tex
Adding description to evaluation.

@@
 \section{Evaluation}
+\label{sec:evaluation}
 
@@
 %
-For the data center policy, we measure the mean compilation time per-prefix since the \sysname compiler can compile for each prefix independently, and in parallel.
+For the data center policy, we measure the mean compilation time per prefix since the \sysname compiler can compile for each prefix independently, and in parallel.
 Figure~\ref{fig:compilation-times-dc} shows the compilation times for data centers of different sizes, broken down by compilation phase.
@@
 Total compilation time for the largest data center with (>1600) routers takes less than 9 minutes total.
-\todo{Core compilation times here}
+%
+For the backbone policy, the \sysname compiler scales hundreds of routers, in a little over a minute per-prefix.
+However, unlike the data center policy, the number of prefixes for the backbone policy stays relatively fixed.
+Total compilation time for the largest backbone topology tested, with 200 routers, takes less than 3 minutes total.
+The presence of more preferences in the backbone policy increases the size of the product graph, and means minimization becomes a more expensive step in compilation.
 
-\ryan{Do we want to include this?}
 The naive compilation algorithm from \S\ref{sec:compilation} generates extremely large ABGP policies.
@@
 Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
-Figure~\ref{fig:compilation-compress-dc} shows the effect of minimization for the data center policy.
-Minimization significantly reduces the size of the naive configurations.
+Figure~\ref{fig:compilation-compress-dc} shows the effect of minimization for the data center and backbone policies.
+In all cases, minimized policies are only a small fraction of the size of their non-minimized counterparts.
 

### 2016-01-28 data/backbone.py
update scripts to make graphs more legible

@@ -4,6 +4,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 
 # collect stats from csv
+num_pods = []
 num_nodes = []
 sizes_raw = []
 sizes_compressed = []
@@ -19,6 +20,7 @@ direct = os.path.dirname(os.path.realpath(__file__))
 with open(direct + os.path.sep + 'stats-backbone.csv') as f:
   r = csv.reader(f)
   for row in r:
+    num_pods.append(row[0])
     num_nodes.append(row[1])
     sizes_raw.append(row[4])
     sizes_compressed.append(row[5])
@@ -30,15 +32,16 @@ with open(direct + os.path.sep + 'stats-backbone.csv') as f:
     tpp_compress_mean.append(row[25])
 
 # remove header info, and convert type
-num_nodes = map(int, num_nodes[1:])
-sizes_raw = map(int, sizes_raw[1:])
-sizes_compressed = map(int, sizes_compressed[1:])
-tpp_total_mean = map(float, tpp_total_mean[1:])
-tpp_build_mean = map(float, tpp_build_mean[1:])
-tpp_minimize_mean = map(float, tpp_minimize_mean[1:])
-tpp_order_mean = map(float, tpp_order_mean[1:])
-tpp_gen_mean = map(float, tpp_gen_mean[1:])
-tpp_compress_mean = map(float, tpp_compress_mean[1:])
+num_pods = map(int, num_pods[2:])
+num_nodes = map(int, num_nodes[2:])
+sizes_raw = map(int, sizes_raw[2:])
+sizes_compressed = map(int, sizes_compressed[2:])
+tpp_total_mean = map(float, tpp_total_mean[2:])
+tpp_build_mean = map(float, tpp_build_mean[2:])
+tpp_minimize_mean = map(float, tpp_minimize_mean[2:])
+tpp_order_mean = map(float, tpp_order_mean[2:])
+tpp_gen_mean = map(float, tpp_gen_mean[2:])
+tpp_compress_mean = map(float, tpp_compress_mean[2:])
 
 #====================================================
 # 
@@ -75,9 +78,11 @@ ax1.fill_between(num_nodes, y_stack[0,:], y_stack[1,:], facecolor=color2, alpha=
 ax1.fill_between(num_nodes, y_stack[1,:], y_stack[2,:], facecolor=color3)
 ax1.fill_between(num_nodes, y_stack[2,:], y_stack[3,:], facecolor=color4)
[…]

### 2016-01-28 data/datacenter.py

@@ -78,9 +78,11 @@ ax1.fill_between(num_nodes, y_stack[0,:], y_stack[1,:], facecolor=color2, alpha=
 ax1.fill_between(num_nodes, y_stack[1,:], y_stack[2,:], facecolor=color3)
 ax1.fill_between(num_nodes, y_stack[2,:], y_stack[3,:], facecolor=color4)
 #ax1.fill_between(num_nodes, y_stack[3,:], y_stack[4,:], facecolor=color5)
-ax1.set_xlabel('Data center size (routers)')
-ax1.set_ylabel('Mean time per prefix (sec)')
-ax1.set_xlim([0,1600])
+ax1.set_xlabel('Data center size (routers)', fontsize=20)
+ax1.set_ylabel('Mean time per prefix (sec)', fontsize=20)
+ax1.tick_params(axis='both', which='major', labelsize=18)
+ax1.tick_params(axis='both', which='minor', labelsize=18)
+ax1.set_xlim([0,1400])
 ax1.set_ylim([0,20])
 # custom legend for stack color
 p1 = plt.Rectangle((0, 0), 1, 1, fc=color1, alpha=.7)
@@ -109,16 +111,20 @@ fig.savefig('compilation-time.png')
 #====================================================
 
 num_nodes1 = num_nodes 
-num_nodes2 = map(lambda x: x-20, num_nodes)
+num_nodes2 = map(lambda x: x, num_nodes)
 sizes_raw_per = map(lambda (size,n): size/n, zip(sizes_raw, num_nodes))
 sizes_compressed_per = map(lambda (size,n): size/n, zip(sizes_compressed, num_nodes))
 
 fig = plt.figure()
 ax1 = fig.add_subplot(111)
-ax1.bar(num_nodes1, sizes_raw_per, width=20, color=color1, alpha=1, align='center') # use log=true
-ax1.bar(num_nodes2, sizes_compressed_per, width=20, color=color3, alpha=1, align='center')
-ax1.set_xlabel('Data center size (routers)')
-ax1.set_ylabel('Config Size (lines of ABGP per router)')
+ax1.bar(num_nodes1, sizes_raw_per, width=25, color=color1, alpha=1, align='center', log=True) # use log=true
+ax1.bar(num_nodes2, sizes_compressed_per, width=20, color=color3, alpha=1, align='center',log=True)
+ax1.set_xlabel('Data center size (routers)', fontsize=20)
[…]

### 2016-01-28 data/backbone.py
updated stats

@@ -128,7 +128,7 @@ ax1.tick_params(axis='both', which='minor', labelsize=18)
 leg_boxes = [p1, p3]
 descrs = ["Raw Config", "Minimized Config"]
 ax1.legend(leg_boxes, descrs, loc=2)
-fig.savefig('config-compression-dc.png')
+fig.savefig('config-compression-backbone.png')
 
 #====================================================
 # 

### 2016-01-28 data/backbone.py
updating experiments

@@ -32,16 +32,16 @@ with open(direct + os.path.sep + 'stats-backbone.csv') as f:
     tpp_compress_mean.append(row[25])
 
 # remove header info, and convert type
-num_pods = map(int, num_pods[2:])
-num_nodes = map(int, num_nodes[2:])
-sizes_raw = map(int, sizes_raw[2:])
-sizes_compressed = map(int, sizes_compressed[2:])
-tpp_total_mean = map(float, tpp_total_mean[2:])
-tpp_build_mean = map(float, tpp_build_mean[2:])
-tpp_minimize_mean = map(float, tpp_minimize_mean[2:])
-tpp_order_mean = map(float, tpp_order_mean[2:])
-tpp_gen_mean = map(float, tpp_gen_mean[2:])
-tpp_compress_mean = map(float, tpp_compress_mean[2:])
+num_pods = map(int, num_pods[1:])
+num_nodes = map(int, num_nodes[1:])
+sizes_raw = map(int, sizes_raw[1:])
+sizes_compressed = map(int, sizes_compressed[1:])
+tpp_total_mean = map(float, tpp_total_mean[1:])
+tpp_build_mean = map(float, tpp_build_mean[1:])
+tpp_minimize_mean = map(float, tpp_minimize_mean[1:])
+tpp_order_mean = map(float, tpp_order_mean[1:])
+tpp_gen_mean = map(float, tpp_gen_mean[1:])
+tpp_compress_mean = map(float, tpp_compress_mean[1:])
 
 #====================================================
 # 
@@ -77,11 +77,12 @@ ax1.fill_between(num_nodes, 0, y_stack[0,:], facecolor=color1, alpha=.7)
 ax1.fill_between(num_nodes, y_stack[0,:], y_stack[1,:], facecolor=color2, alpha=.7)
 ax1.fill_between(num_nodes, y_stack[1,:], y_stack[2,:], facecolor=color3)
 ax1.fill_between(num_nodes, y_stack[2,:], y_stack[3,:], facecolor=color4)
-#ax1.fill_between(num_nodes, y_stack[3,:], y_stack[4,:], facecolor=color5)
-ax1.set_xlabel('Backbone size (routers)', fontsize=20)
-ax1.set_ylabel('Mean time per prefix (sec)', fontsize=20)
-ax1.tick_params(axis='both', which='major', labelsize=18)
-ax1.tick_params(axis='both', which='minor', labelsize=18)
[…]

### 2016-01-28 data/datacenter.py

@@ -78,31 +78,23 @@ ax1.fill_between(num_nodes, y_stack[0,:], y_stack[1,:], facecolor=color2, alpha=
 ax1.fill_between(num_nodes, y_stack[1,:], y_stack[2,:], facecolor=color3)
 ax1.fill_between(num_nodes, y_stack[2,:], y_stack[3,:], facecolor=color4)
 #ax1.fill_between(num_nodes, y_stack[3,:], y_stack[4,:], facecolor=color5)
-ax1.set_xlabel('Data center size (routers)', fontsize=20)
-ax1.set_ylabel('Mean time per prefix (sec)', fontsize=20)
-ax1.tick_params(axis='both', which='major', labelsize=18)
-ax1.tick_params(axis='both', which='minor', labelsize=18)
+ax1.set_xlabel('Routers', fontsize=35)
+ax1.set_ylabel('Avg. Time / Prefix (s)', fontsize=35)
+ax1.tick_params(axis='both', which='major', labelsize=35)
+ax1.tick_params(axis='both', which='minor', labelsize=35)
 ax1.set_xlim([0,1400])
-ax1.set_ylim([0,20])
+ax1.set_ylim([0,15])
+ax1.xaxis.set_ticks([200,600,1000,1400])
+ax1.yaxis.set_ticks([0,5,10,15])
 # custom legend for stack color
 p1 = plt.Rectangle((0, 0), 1, 1, fc=color1, alpha=.7)
 p2 = plt.Rectangle((0, 0), 1, 1, fc=color2, alpha=.7)
 p3 = plt.Rectangle((0, 0), 1, 1, fc=color3, alpha=.7)
 p4 = plt.Rectangle((0, 0), 1, 1, fc=color4, alpha=.7)
-#p5 = plt.Rectangle((0, 0), 1, 1, fc=color5, alpha=.7)
 leg_boxes = [p4, p3, p2, p1]
-descrs = ["Generate/Minimize ABGP", "Find Preferences", "Minimize PG", "Construct PG"]
-ax1.legend(leg_boxes, descrs, loc=2)
-fig.savefig('compilation-time-stacked.png')
-
-# plot figures 
-fig = plt.figure()
-plt.grid()
-plt.plot(num_nodes, tpp_total_mean, label='Total')
-plt.xlabel('Data center size (routers)')
-plt.ylabel('Mean time per prefix (sec)')
-plt.legend(loc=2)
[…]

### 2016-01-28 paper/evaluation.tex
updating experiments
shrinking images

@@
   \centering
-\includegraphics[width=\columnwidth]{figures/compilation-times-dc.png}
-\label{fig:compilation-times-dc}
-\caption{Data center compilation times.}
+  \begin{minipage}[b]{0.45\linewidth}
+    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-dc.png}
+  \end{minipage}
+  \quad
+  \begin{minipage}[b]{0.45\linewidth}
+    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-backbone.png}
+  \end{minipage}
+  \caption{Compilation times.}
+  \label{fig:compilation-times}
 \end{figure}
@@
   \centering
-\includegraphics[width=\columnwidth]{figures/compilation-times-backbone.png}
-\label{fig:compilation-times-dc}
-\caption{Data center compilation times.}
-\end{figure}
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=\columnwidth]{figures/config-compression-dc.png}
-\label{fig:compilation-compression-dc}
-\caption{Data center config minimization.}
+  \begin{minipage}[b]{0.45\linewidth}
+    \includegraphics[width=1.1\columnwidth]{figures/config-compression-dc.png}
+  \end{minipage}
+  \quad
+  \begin{minipage}[b]{0.45\linewidth}
+    \includegraphics[width=1.1\columnwidth]{figures/config-compression-backbone.png}
+  \end{minipage}
+  \caption{Configuration minimization.}
+  \label{fig:minipage2}
 \end{figure}

### 2016-01-28 data/backbone.py

@@ -81,7 +81,7 @@ ax1.set_xlabel('Routers', fontsize=35)
 ax1.set_ylabel('Avg. Time / Prefix (s)', fontsize=35)
 ax1.tick_params(axis='both', which='major', labelsize=35)
 ax1.tick_params(axis='both', which='minor', labelsize=35)
-ax1.xaxis.set_ticks([40,80,120,160,200])
+ax1.xaxis.set_ticks([0,40,80,120,160,200])
 ax1.yaxis.set_ticks([5,15,25,35,45])
 #ax1.set_xlim([0,1400])
 #ax1.set_ylim([0,20])
@@ -92,8 +92,8 @@ p3 = plt.Rectangle((0, 0), 1, 1, fc=color3, alpha=.7)
 p4 = plt.Rectangle((0, 0), 1, 1, fc=color4, alpha=.7)
 leg_boxes = [p4, p3, p2, p1]
 descrs = ["Gen/Min ABGP", "Find Preferences", "Minimize PG", "Construct PG"]
-ax1.legend(leg_boxes, descrs, loc=2, fontsize=20)
-fig.savefig('compilation-time-backbone.png', bbox_inches='tight')
+ax1.legend(leg_boxes, descrs, loc=2, fontsize=24)
+fig.savefig('compilation-times-backbone.png', bbox_inches='tight')
 
 
 #====================================================
@@ -109,14 +109,15 @@ sizes_compressed_per = map(lambda (size,n): size/n, zip(sizes_compressed, num_no
 
 fig = plt.figure()
 ax1 = fig.add_subplot(111)
-ax1.bar(num_nodes1, sizes_raw_per, width=4, color=color1, alpha=1, align='center', log=True)
-ax1.bar(num_nodes2, sizes_compressed_per, width=4, color=color3, alpha=1, align='center',log=True)
+ax1.bar(num_nodes1, sizes_raw_per, width=3.2, color=color1, alpha=1, align='center', log=True)
+ax1.bar(num_nodes2, sizes_compressed_per, width=3.2, color=color3, alpha=1, align='center',log=True)
 ax1.set_xlabel('Routers', fontsize=35)
 ax1.set_ylabel('ABGP Lines/Router', fontsize=35)
 ax1.tick_params(axis='both', which='major', labelsize=35)
 ax1.tick_params(axis='both', which='minor', labelsize=35)
 ax1.set_xlim([0,220])
[…]

### 2016-01-28 data/datacenter.py

@@ -93,8 +93,8 @@ p3 = plt.Rectangle((0, 0), 1, 1, fc=color3, alpha=.7)
 p4 = plt.Rectangle((0, 0), 1, 1, fc=color4, alpha=.7)
 leg_boxes = [p4, p3, p2, p1]
 descrs = ["Gen/Min ABGP", "Find Preferences", "Minimize PG", "Construct PG"]
-ax1.legend(leg_boxes, descrs, loc=2, fontsize=20)
-fig.savefig('compilation-time-dc.png', bbox_inches='tight')
+ax1.legend(leg_boxes, descrs, loc=2, fontsize=24)
+fig.savefig('compilation-times-dc.png', bbox_inches='tight')
 
 #====================================================
 # 
@@ -118,8 +118,9 @@ ax1.tick_params(axis='both', which='minor', labelsize=35)
 
 ax1.xaxis.set_ticks([200,600,1000,1400])
 #ax1.set_xlim([0,1400])
-#ax1.set_ylim([0,20])
+ax1.set_ylim([0,10*10*10*10*10*10*10])
+
 leg_boxes = [p1, p3]
 descrs = ["Raw Config", "Minimized Config"]
-ax1.legend(leg_boxes, descrs, loc=2)
+ax1.legend(leg_boxes, descrs, loc=2, fontsize=24)
 fig.savefig('config-compression-dc.png', bbox_inches='tight')

### 2016-01-28 paper/introduction.tex
updates to intro

--- 2016-01-27 paper/introduction.tex
@@
 
-One reason for network configuration being onerous is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.
+%One reason for network configuration being onerous is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.
 
-Another, more fundamental reason is the semantic mismatch between the intended high-level
+Besides the languages being low-level, a fundamental reason for configuration being onerous is the semantic mismatch between the intended high-level
 policies and the low-level device-by-device configurations.  In particular,
@@
 To reduce configuration errors, many practitioners have a adopted a template-based
-approach~\cite{hatch,thwack}, in which common configuration patterns are captured as parameterized templates.  More powerful still are systems like
-ConfigAssure~\cite{narain:lisa05,narain+:configassure}, which use SAT solving
-and model finding tools to fill in parameters in configurations while
-ensuring key correctness constraints are satisfied.  However,
+approach~\cite{hatch,thwack}, in which common tasks are captured as parameterized templates.
+%
+%More powerful still are systems like
+%ConfigAssure~\cite{narain:lisa05,narain+:configassure}, which use SAT solving
+%and model finding tools to fill in parameters in configurations while
+%ensuring key correctness constraints are satisfied.
+One step further, systems like
+ConfigAssure~\cite{narain:lisa05,narain+:configassure} use SAT solving
+and model finding tools to correctly and consistently fill in some parameters.
+%
+However,
  while templates help ensure certain kinds of consistency across devices,
 they do not bridge the
-semantic divide between network policies and device-level configuration,
-nor do they do not provide fundamentally different abstractions
+semantic divide between network policies and device-level configuration.
+They do not provide fundamentally different abstractions
 from existing configuration languages or new, higher-level reasoning
@@
 compliance through distributed interaction of individual
-devices~\cite{sdn-languages}. Indeed, instead of organizing networks
+devices~\cite{ethane}. Indeed, instead of organizing networks
 around a distributed collection of devices that compute forwarding tables through
@@
 First, while many SDN systems provide effective \emph{intra}-domain routing
-abstractions, allowing users to specify paths within their own network,
-they fail to provide a coherent means to enable specification of preferred
+abstractions, letting users specify paths within their network,
+they fail to provide a coherent means to specify preferred
 \emph{inter}-domain routes.  Second, centralized control planes
-require careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure.
+require careful design and engineering to be robust to failures---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure.
 Even ignoring failures, it is necessary for controller systems to
-scale to meet the demands of larger, geographically distributed networks, 
-and to react sufficiently quickly
-to a changing environment. To address this challenge, some researchers are beginning to 
-explore
-multi-controller networks, with interacting controllers, thus bringing back distributed
+scale to meet the demands of large, geographically distributed networks,
+and to react quickly
+to a changing environment. To address this challenge, researchers are exploring
+multi-controller systems with interacting controllers, thus bringing back distributed
 control planes~\cite{mccauley2013extending,onos} and their current programming difficulties.
@@
 
-To achieve the first goal, we borrowed heavily from the design of
+To achieve the first goal, we borrowed heavily from 
 recent high-level SDN languages such as FatTire~\cite{fattire},
 Merlin~\cite{foster:merlin}, and
-NetKAT~\cite{netkat} by using regular expressions to specify paths
-through networks.  However, our design also contains several key
-differences from existing languages.  The most important difference is semantic:  the paths specified
+NetKAT~\cite{netkat} by using regular expressions to specify network paths.  However, our design also contains several key
+departures from existing languages.  The most important difference is semantic:  the paths specified
 by programmers can extend from outside the operator's network to inside
@@
 choice allows users to specify preferences about both external and internal
-routes in the same uniform notation.  No SDN programming language provides
-similar facilities.  In addition,
-we incorporate expression of user preferences in to the algebra
-of regular expressions and provide a semantics to our language
-in terms of sets of ranked paths.  These preferences indicate possible
-fail-over routes:  If too many faults occur, the network may be
-disconnected, but as long as any path the user has expressed is
-still available, the system guarantees the highest-ranked, available
-path will be taken.  We also support network operators by defining a
-set of common abbreviations for entering, leaving, and traversing
-the user network and we provide abstractions for managing common features of
-control plane algorithms such as route aggregation.  Operators use familiar logical operations
-to build routes in a modular and compositional manner from these 
-primitives.  Our abbreviations are translated in to our regular-expression-based
-intermediate representation and compiled from there.
+routes in the same notation.  
+%No SDN programming language provides similar facilities.  
+In addition,
+we incorporate user preferences in to the algebra
+of regular expressions and provide a semantics in terms of sets of ranked paths.  The preferences indicate fail-over behaviors:  among all specified paths that are still available,
+the system guarantees that the highest-ranked one will be taken.  
+%We also support network operators by defining a
+%set of common abbreviations for entering, leaving, and traversing
+%the user network and we provide abstractions for managing common features %of
+%control plane algorithms such as route aggregation.  Operators use familiar logical operations
+%to build routes in a modular and compositional manner from these
+%primitives.  Our abbreviations are translated in to our regular-expression-based
+%intermediate representation and compiled from there.
 
-To achieve the second goal, we define program analysis and compilation
-algorithms that translate the regular policies in to a graph-based
-intermediate language and from there in to BGP.  During the
-compilation process, our compiler automatically synthesizes per-device
-import and export filters, local preferences, MED attributes, and 
-community tags.  We chose BGP for pragmatic reasons:  it is an industry
-standard and many data centers use it internally as well as externally.
-Indeed, despite the presence of SDN, many networks will continue to
-use BGP for the foreseeable future due to investments they have already
-made in the infrastructure, the difficulty of transitioning to SDN,
+To achieve the second goal, we develop program analysis and compilation
+algorithms that translate the regular policies to a graph-based
+intermediate language and from there to BGP configurations.  
+We target BGP for pragmatic reasons:  it is an industry
+standard and many networks use it internally as well as externally. Despite the advent of SDN, many networks will continue to
+use BGP for the foreseeable future due to existing infrastructure investments, the difficulty of transitioning to SDN,
 and the scalability and fault-tolerance advantages of a distributed
-control plane.  However, using BGP as a back end is not without its 
-challenges: not all high-level specifications can be implemented correctly in
-the presence of arbitrary failures.  Consequently, we define new
-program analysis algorithms to detect specifications that cannot be implemented
-and report our findings to the user, so he or she may fix the specification
-early rather than waiting until configurations have been deployed.  We also
-analyze route aggregation to detect the possibility of failure-induced black-holes.
-These algorithms differ from
-standard BGP analysis algorithms~\cite{feamster:rcc,batfish} because they operate on 
-our graph-based intermediate representation, which operates at a higher level
-of abstraction than raw BGP configurations (and which has the pleasant effect of simplifying our 
-task).
+control plane.
 
-To evaluate the \sysname{} language and system, we have experimented with specifying policy
-for several realistic data center and backbone networks and compared these specifications
-with existing operating specifications. We have also
-measured the performance of our compiler, demonstrating that our compilation
-algorithms scale to topologies with several thousand routers.
+However, using BGP as a vehicle for implementing high-level policies is
+challenging because not all policies can be implemented correctly in
+the presence of arbitrary failures.  We develop new
+algorithms to detect policies that cannot be implemented
+and report our findings to the operators, so they may fix the specification at compile time rather than experience undesirable behavior after configurations are deployed.
+%We also analyze route aggregation to detect the possibility of failure-induced black-holes.
+If the policies are implementable, our compiler automatically synthesizes per-device import and export filters, local preferences, MED attributes, and community tags.
 
-In the remainder of the paper, we review BGP~\ref{sec:background} (readers
-familiar with BGP may skip this section),
-further motivate the need for new languages 
-for programming distributed control planes (Section \ref{sec:motivation}),
-introduce \sysname{} by example (Section \ref{sec:propane}), 
-explain our compiler algorithms (Section \ref{sec:compilation}),
-present several lemmas justifying the correctness of our techniques (Section \ref{sec:theory}), describe our implementation (Section \ref{sec:implementation}
-and discuss related work (Section \ref{sec:related}).
+%These algorithms differ from
+%standard BGP analysis algorithms~\cite{feamster:rcc,batfish} because they operate on
+%our graph-based intermediate representation, which operates at a higher level
+%of abstraction than raw BGP configurations (and which has the pleasant effect of simplifying our
+%task).
+
+We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies of data center and backbone networks.
+% and compared these specifications with existing configurations. 
+We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds of routers.
+
+%measured the performance of our compiler, demonstrating that our compilation
+%algorithms scale to topologies with several thousand routers.
+%
+%\dpw{The following could be cut for space.}
+%In the remainder of the paper, we review BGP (Section~\ref{sec:background}---readers
+%familiar with BGP may skip this section),
+%further motivate the need for new languages
+%for programming distributed control planes (Section \ref{sec:motivation}),
+%introduce \sysname{} by example (Section \ref{sec:propane}),
+%explain our compiler algorithms (Section \ref{sec:compilation}),
+%present several lemmas justifying the correctness of our techniques (Section \ref{sec:theory}), describe our implementation (Section \ref{sec:implementation})
+%evaluate our work  (Section \ref{sec:evaluation}) and discuss related work (Section \ref{sec:related}).
 

### 2016-01-28 paper/propane.tex
more edits.
fonts

@@
 network, we first express the idea that for routes leading to our customer,
-we prefer using $R_1$ over $R_2$ (Policy P3 from Figure~\ref{fig:example1}):
+we prefer using \CD{R1} over \CD{R2} (Policy P3 from Figure~\ref{fig:example1}):
 %\begin{lstlisting}[mathescape=true]
@@
 through either router \CD{R1} or \CD{R2}.  The paths that exit through \CD{R1}
-are preferred (\Prefer) to those that exit through $R_2$.
+are preferred (\Prefer) to those that exit through \CD{R2}.
 
@@
 \noindent
-In English: traffic for prefix \CD{Pg1} is only allowed to follow paths that
-end at router \CD{A}; traffic matching \CD{Pg2},
-but not \CD{Pg1}, must
+In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
+end at router \CD{A}; traffic matching \CD{PG2},
+but not \CD{PG1}, must
 end at router \CD{B}; and so on.
@@
 back on itself. This means traffic for
-\CD{Pg*} may be sent either from other routers in the datacenter, or
+\CD{PG*} may be sent either from other routers in the datacenter, or
 from external ASes. The second line ensures that traffic for local
@@
 aggregation for global prefixes (with aggregate \CD{PG}) is performed from
-locations inside the network to locations outside. In this case, \CD{Pg1} and \CD{Pg2} will use the aggregate \CD{PG} when advertised outside the datacenter.
-\todo{Say more about aggregation here.
-What prefixes are aggregated in to what blocks?  How is this defined?}
+locations inside the network to locations outside. In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG} when advertised outside the datacenter.
 

### 2016-01-28 paper/compilation.tex
adding figure

@@
 %
+\begin{prop}
+The internal routers in a distributed BGP configuration produced by \sysname will be stable. 
+\end{prop}
+%
 The combination of Soundness and Completeness ensures that the distributed implementation will always send traffic along the best paths possible, yet will also never also use any undesired paths.
@@
 %
-\begin{prop}
-The internal routers in a distributed BGP configuration produced by \sysname will be stable. 
-\end{prop}
-
 %The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo} for stable BGP.
 In particular, any policy with a dispute wheel will not pass the stronger failure safety check by \sysname.
-
+%
 %\begin{figure}[t!]
@@
 %\end{figure}
-
+%
 %The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}.
@@
 Since no-dispute-wheel is a sufficient condition for BGP stability, any compiled \sysname policy will be stable.
-
+%
 An important distinction is that BGP might still be instable with respect to other external ASes, since \sysname has no way of configuring their routing policy and can only rely on AS path filters to see what advertisements are observed.

### 2016-01-28 data/backbone.py
making bar graphs wider

@@ -107,10 +107,15 @@ num_nodes2 = map(lambda x: x, num_nodes)
 sizes_raw_per = map(lambda (size,n): size/n, zip(sizes_raw, num_nodes))
 sizes_compressed_per = map(lambda (size,n): size/n, zip(sizes_compressed, num_nodes))
 
+num_nodes1 = num_nodes1[2::3]
+num_nodes2 = num_nodes2[2::3]
+sizes_raw_per = sizes_raw_per[2::3]
+sizes_compressed_per = sizes_compressed_per[2::3]
+
 fig = plt.figure()
 ax1 = fig.add_subplot(111)
-ax1.bar(num_nodes1, sizes_raw_per, width=3.2, color=color1, alpha=1, align='center', log=True)
-ax1.bar(num_nodes2, sizes_compressed_per, width=3.2, color=color3, alpha=1, align='center',log=True)
+ax1.bar(num_nodes1, sizes_raw_per, width=5.2, color=color1, alpha=1, align='center', log=True)
+ax1.bar(num_nodes2, sizes_compressed_per, width=5.2, color=color3, alpha=1, align='center',log=True)
 ax1.set_xlabel('Routers', fontsize=35)
 ax1.set_ylabel('ABGP Lines/Router', fontsize=35)
 ax1.tick_params(axis='both', which='major', labelsize=35)

### 2016-01-28 data/datacenter.py

@@ -102,15 +102,20 @@ fig.savefig('compilation-times-dc.png', bbox_inches='tight')
 #
 #====================================================
 
-num_nodes1 = num_nodes 
+num_nodes1 = num_nodes
 num_nodes2 = map(lambda x: x, num_nodes)
 sizes_raw_per = map(lambda (size,n): size/n, zip(sizes_raw, num_nodes))
 sizes_compressed_per = map(lambda (size,n): size/n, zip(sizes_compressed, num_nodes))
 
+num_nodes1 = num_nodes1[1:]
+num_nodes2 = num_nodes2[1:]
+sizes_raw_per = sizes_raw_per[1:]
+sizes_compressed_per = sizes_compressed_per[1:]
+
 fig = plt.figure()
 ax1 = fig.add_subplot(111)
-ax1.bar(num_nodes1, sizes_raw_per, width=25, color=color1, alpha=1, align='center', log=True) # use log=true
-ax1.bar(num_nodes2, sizes_compressed_per, width=25, color=color3, alpha=1, align='center',log=True)
+ax1.bar(num_nodes1, sizes_raw_per, width=40, color=color1, alpha=1, align='center', log=True) # use log=true
+ax1.bar(num_nodes2, sizes_compressed_per, width=40, color=color3, alpha=1, align='center',log=True)
 ax1.set_xlabel('Routers', fontsize=35)
 ax1.set_ylabel('ABGP Lines/Router', fontsize=35)
 ax1.tick_params(axis='both', which='major', labelsize=35)
@@ -118,7 +123,7 @@ ax1.tick_params(axis='both', which='minor', labelsize=35)
 
 ax1.xaxis.set_ticks([200,600,1000,1400])
 #ax1.set_xlim([0,1400])
-ax1.set_ylim([0,10*10*10*10*10*10*10])
+ax1.set_ylim([-10, 10*10*10*10*10*10*10])
 
 leg_boxes = [p1, p3]
 descrs = ["Raw Config", "Minimized Config"]

### 2016-01-28 paper/compilation.tex
fontifying

@@
 
-We handle this challenge by breaking compilation into multiple stages and developing efficient algorithms for each.
-Figure~\ref{fig:pipeline} shows the 5 stage compilation pipeline to translate \sysname FE policies to device-local BGP policies.
+We handle these challenges by breaking compilation into multiple stages and developing efficient algorithms for each (See Figure~\ref{fig:pipeline}).
 The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR).
-Policies in RIR are checked for well-formedness (e.g., never constraining traffic that does not enter the network), before being combined with topology to obtain the Product Graph Intermediate Representation (PGIR).
+Policies in RIR are checked for well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR).
 The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions.
@@
 
-The \sysname FE is just a thin layer atop a core, regular-expression language for describing preference-based path constraints.
-Regular expressions are an expressive formalism that have been used extensively for describing paths through graphs~\cite{bib:todo}, with applications to networks~\cite{bib:todo}.
+%Regular expressions are an expressive formalism that have been used extensively for describing paths through graphs~\cite{bib:todo}, with applications to networks~\cite{bib:todo}.
 Our regular expression language differs from others by allowing operators to describe preferences between paths.
@@
 \newcommand{\BNFALT}{\;\;|\;\;}
-\newcommand{\hdr}[2]{\flushleft \chdr{#1}{#2}}
+\newcommand{\hdr}[2]{\flushleft \chdr{\hspace{5mm}#1}{#2}}
 \newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}
 
-\begin{figure*}
+\begin{figure*}\small
   \begin{minipage}[t]{.45\linewidth}
@@
      pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
-     p       &::=& t \mapsto r_1 \gg \dots \gg r_m & \textit{preferences} \\
-     t       &::=& true & \textit{true} \\
-         &\BNFALT& \neg t & \textit{negation} \\
-         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
-         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
-         &\BNFALT& prefix = x & \textit{prefix test} \\
-         &\BNFALT& comm = c & \textit{community test} \\
+     p       &::=& t \mapsto r_1 \Prefer \dots \Prefer r_m & \textit{preferences} \\
+     x       &::=& a.b.c.d/n & \textit{prefix} \\
+     c       &::=& \cdots & \textit{community value} \\
+     t       &::=& \True & \textit{true} \\
+         &\BNFALT& \NOT t & \textit{negation} \\
+         &\BNFALT& t_1 \OR{} t_2 & \textit{disjunction} \\
+         &\BNFALT& t_1 \AND{} t_2 & \textit{conjunction} \\
+         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
+         &\BNFALT& \textit{comm} = c & \textit{community test} \\
      r       &::=& n & \textit{AS number} \\
-         &\BNFALT& in & \textit{internal loc} \\
-         &\BNFALT& out & \textit{external loc} \\
+         &\BNFALT& \In & \textit{internal loc} \\
+         &\BNFALT& \Out & \textit{external loc} \\
          &\BNFALT& r_1 \cup r_2 & \textit{union} \\
@@
          &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
-         &\BNFALT& !(r) & \textit{path negation} \\
+         &\BNFALT& \NOT(r) & \textit{path negation} \\
          &\BNFALT& r^* & \textit{repetition} \\
@@
   %
-  \begin{minipage}[t]{.5\linewidth}
+  \begin{minipage}[t]{.5\linewidth}\small
   \hdr{\large Propane Expansions}{}
@@
   %
-  \[ \begin{array}{rcl}
+  \[\begin{array}{rcl}
     \hline
-    any           & = & out^* \cdot in^+ \cdot out^* \\
-    internal      & = & in^+ \\
-    only(X)       & = & any \cap X^* \\
-    never(X)      & = & any \cap (!X)^* \\
-    through(X)    & = & out^* \cdot in^* \cdot X \cdot in^* \cdot out^* \\
-    later(X)      & = & out^* \cdot (X \cap out) \cdot out^* \cdot in^+ \cdot out^* \\
-    before(X)     & = & out^* \cdot in^+ \cdot out^* \cdot (X \cap out) \cdot out^* \\
-    end(X)        & = & any \cap (\Sigma^* \cdot X) \\
-    start(X)      & = & any \cap (X \cdot \Sigma^*) \\
-    exit(X)       & = & (out^* \cdot in^* \cdot (X \cap in) \cdot out \cdot out^*) \cup \\
-                  &        & (out^* \cdot in^+ \cdot (X \cap out) \cdot out^*) \\
-    enter(X)      & = & (out^* \cdot out \cdot (X \cap in) \cdot in^* \cdot out^*) \cup \\
-                  &        & (out^* \cdot (X \cap out) \cdot in^+ \cdot out^*) \\
-    link(X,Y)     & = & any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
-    path(\vec{X}) & = & any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
-    novalley(\vec{X}) & = & any ~ \cap \\
-                  &   & !path(X_2,X_1,X_2) ~ \cap \dots \cap \\
-                  &   & !path(X_n,X_{n-1},X_n) \\
+    \Any           & = & \Out^* \cdot \In^+ \cdot \Out^* \\
+    \Internal      & = & \In^+ \\
+    \Only(X)       & = & \Any \cap X^* \\
+    \Never(X)      & = & \Any \cap (!X)^* \\
+    \Through(X)    & = & \Out^* \cdot \In^* \cdot X \cdot \In^* \cdot \Out^* \\
+    \Later(X)      & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
+    \Before(X)     & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
+    \End(X)        & = & \Any \cap (\Sigma^* \cdot X) \\
+    \Start(X)      & = & \Any \cap (X \cdot \Sigma^*) \\
+    \Exit(X)       & = & (\Out^* \cdot \In^* \cdot (X \cap \In) \cdot \Out \cdot \Out^*) \cup \\
+                  &        & (\Out^* \cdot \In^+ \cdot (X \cap \Out) \cdot \Out^*) \\
+    \Enter(X)      & = & (\Out^* \cdot \Out \cdot (X \cap \In) \cdot \In^* \cdot \Out^*) \cup \\
+                  &        & (\Out^* \cdot (X \cap \Out) \cdot \In^+ \cdot \Out^*) \\
+    \LinkKW(X,Y)     & = & \Any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
+    \PathKW(\vec{X}) & = & \Any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
+    \Novalley(\vec{X}) & = & \Any ~ \cap \\
+                  &   & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
+                  &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
   \end{array} \]
@@
 \para{Syntax}
-
+The \sysname FE is just a thin layer atop a core, regular-expression language for describing preference-based path constraints. 
 Figure~\ref{fig:rir-syntax} shows the RIR syntax.
@@
 Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS.
-Special \textit{in} and \textit{out} symbols refer to any internal or external location respectively.
-For example, the constraint
-$$prefix=74.3.28.0/24 \mapsto (as200 \cdot in^+) \gg (as100 \cdot in^+)$$
-describes a more-preferred set of paths for traffic announced by a prefix no less specific than $74.125.28.0/24$, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same.
-The plus operator $in^+$ stands for $in \cdot in^*$, at least one internal hop.
+Special \In{} and \Out{} symbols refer to any internal or external location respectively.
+In addition, $\Sigma$ refers to any symbol, and hence $\Sigma^*$ is
+any sequence of symbols.  We also use other standard abbreviations
+for regular expressions such as $r^+$, a sequence of one or more occurrences
+of $r$, when appropriate.
+%% For example, the constraint
+%% \[(\textit{prefix}=74.3.28.0/24) \Link \\
+%% (as200 \cdot \In^+) \Prefer (as100 \cdot \In^+)
+%% \]
+%% describes a more-preferred set of paths for traffic announced by a prefix no less specific than \CD{74.125.28.0/24}, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same.
+The plus operator $\In^+$ stands for $\In \cdot \In^*$, at least one internal hop.
 Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.
@@
 For example, prefix aggregation, which should not affect routing behavior, is an important optimization to reduce routing table size and churn in practice.
-Aggregation, for example, from internal to external locations, is specified using the same regular syntax as before:
-$$agg(128.17.0.0/16, in \rightarrow out)$$
-where the expression $in \rightarrow out$ refers to control messages flowing from any internal to any external location.
-
+%% Aggregation, for example, from internal to external locations, is specified using the same regular syntax as before:
+%% $$\Agg(128.17.0.0/16, \In \Link \Out)$$
+%% where the expression $\In \Link Out$ refers to control messages flowing from any internal to any external location.
 We list only the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, but we also support other constraints such as limiting the maximum number of routes allowed between ASes, or enabling BGP multipath.
@@
 The semantics of RIR is in terms of ranked paths.
-Each preference-based regular path constraint (of the form $r_1 \gg \dots \gg r_j$) maps to a set of concrete paths in the network that match one of $r_i$.
+Each preference-based regular path constraint (of the form $r_1 \Prefer \dots \Prefer r_j$) maps to a set of concrete paths in the network that match one of $r_i$.
 We denote a network path as a string of abstract locations (routers or external ASes) of the form: $n_1 n_2 \dots n_k$.
@@
 Lower ranks indicate \emph{more} preferred paths.
-The semantics is to allow traffic to be sent along any of the most preferred paths for each pair of starting and ending locations that appear in some valid specified path.
+Traffic may be sent along any of the most preferred paths for each pair of starting and ending locations that appear in some valid specified path.
 
@@
 
-The main differences between the \sysname FE and the RIR are: (1) FE allows the programmer to specify constraints separately, and combine them  modularly, (2) FE provides high-level names that abstract sets of routes, and (3) FE allows the preference operator to be used locally.
+The main differences between the FE and RIR are: (1) FE allows the programmer to specify constraints using a series of (modular) definitions, and combine them later, (2) FE provides high-level names that abstract sets of routes, and (3) FE allows the preference operator to be used locally.
 
 A key constraint when translating FE to RIR is to ensure that all specified routes are well-formed.
-In particular, each regular path constraint $r$ must satisfy $r \subseteq out^* \cdot in^+ \cdot out^*$.
-This ensures that one can only talk about controlling traffic that goes through the user's network at some point.
+In particular, each regular path constraint $r$ must satisfy $r \subseteq \Out^* \cdot \In^+ \cdot \Out^*$.
+This ensures that one can only talk about controlling traffic that goes through the user's network at some point,
+and that such traffic does not loop back multiple times to the user network.
 
@@
 The first step merges separate constraints.
-It takes the cross product of per-prefix constraints, where logical conjunction ($a \wedge b$) is replaced by intersection on regular constraints ($a \cap b$), logical disjunction is replaced by union, and logical negation ($\neg a$) is replaced by ($any \cap !(a)$), where $any$ ensures the routes are well-formed.
+It takes the cross product of per-prefix constraints, where logical conjunction ($a \AND b$) is replaced by intersection on regular constraints ($a \Intersect b$), logical disjunction is replaced by union, and logical negation ($\NOT a$) is replaced by ($\Any \cap \NOT(a)$), where $\Any$ ensures the routes are well-formed.
 %
-For example, in the data center configuration from \S\ref{sec:propane}, combining the \textit{Routing} and \textit{Ownership} policies results in the following RIR:
+For example, in the data center configuration from \S\ref{sec:propane}, combining the \CD{Routing} and \CD{Ownership} policies results in the following RIR:
 
-\begin{lstlisting}[mathescape=true]
-$\path{p_{g1}}{any \cap end(A)}$
-$\path{p_{g2}}{any \cap end(B)}$
-$\path{p_{l1}}{\neg enter(out) \cap end(E)}$
-$\path{p_{l2}}{\neg enter(out) \cap end(F)}$
-$\path{true}{exit(out)}$
-\end{lstlisting}
+%% \begin{lstlisting}[mathescape=true]
+%% $\path{p_{g1}}{any \cap end(A)}$
+%% $\path{p_{g2}}{any \cap end(B)}$
+%% $\path{p_{l1}}{\neg enter(out) \cap end(E)}$
+%% $\path{p_{l2}}{\neg enter(out) \cap end(F)}$
+%% $\path{true}{exit(out)}$
+%% \end{lstlisting}
+
+\begin{code}
+PG1 \Path \Any \Intersect \End(A)
+PG2 \Path \Any \Intersect \End(B)
+PL1 \Path \NOT\Enter(\Out) \Intersect \End(E)
+PL2 \Path \NOT\Enter(\Out) \Intersect \End(F)
+\True \Path \Exit(\Out)
+\end{code}
 
@@
 Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression.
-For example, the regular expression $a \cdot (b \gg c) \cdot d$ is lifted to $(a \cdot b \cdot d) \gg (a \cdot c \cdot d)$ by distributing the preference over the sequence operator.
+For example, the regular expression $a \cdot (b \Prefer c) \cdot d$ is lifted to $(a \cdot b \cdot d) \Prefer (a \cdot c \cdot d)$ by distributing the preference over the sequence operator.
 In general, we employ the follwing equivalence:
 %
-$$x \odot (y_1 \gg \dots \gg y_n) = x \odot y_1 \gg \dots \gg x \odot y_n$$
+$$x \odot (y_1 \Prefer \dots \Prefer y_n) = (x \odot y_1) \Prefer \dots \Prefer (x \odot y_n)$$
 %
@@
 
-  \caption{Example Product Graph IR construction for policy: $(W \cdot A \cdot C \cdot D \cdot out) \gg (W \cdot B \cdot in^* \cdot out)$.}
+  \caption{Example Product Graph IR construction for policy: $(W \cdot A \cdot C \cdot D \cdot out) \Prefer (W \cdot B \cdot in^* \cdot out)$.}
   \label{fig:example-compilation}
@@
 % Formally define automata
-The RIR policy is an ordered sequence of regular expressions $r_1 \gg \dots \gg r_j$.
+The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$.
 While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., route announcements flowing in the opposite direction).
@@
 %
-$$(W \cdot A \cdot C \cdot D \cdot out) \gg (W \cdot B \cdot in^* \cdot out)$$
+$$(W \cdot A \cdot C \cdot D \cdot \Out) \Prefer (W \cdot B \cdot in^* \cdot \Out)$$
 %
@@
 For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining the most prefered preference $1$.
-BGP control messages can start from peer X, which would match the $out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
+BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
 This is reflected in the product graph by the node with state $(1,1) X$.
@@
 %
-$$(W \cdot A \cdot C \cdot D) \gg (W \cdot B \cdot C \cdot E)$$
+$$(W \cdot A \cdot C \cdot D) \Prefer (W \cdot B \cdot C \cdot E)$$
 %
@@
   \colorbox{red!50}{$\displaystyle#1$}}
-\newcommand{\Router}[1]{ \textbf{Router #1:} }
-\newcommand{\REGEX}[1]{ \text{regex}(#1) }
-\newcommand{\PEER}{ \text{peer} }
-\newcommand{\COMM} {\text{comm}}
-\newcommand{\MED} {\text{MED}}
+\newcommand{\Router}[1]{\KW{Router} #1:}
+\newcommand{\REGEX}[1]{\texttt{regex}(#1)}
+\newcommand{\PEER}{\texttt{peer}}
+\newcommand{\COMM}{\texttt{comm}}
+\newcommand{\MED}{\texttt{MED}}
+\newcommand{\Arrow}{\ensuremath{\leftarrow}}
 
 \begin{figure}[t!]
-\begin{lstlisting}[frame=single, mathescape=true]
-$\Router{A}$
-  Match $\PEER=C, \COMM=(3,2)$
-    Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
-$\Router{B}$
-  Match $\PEER = C, \COMM = (-,2)$
-    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
-           $\MED \leftarrow 81, \PEER \leftarrow W$
-  Match $\PEER = C, \COMM = (3,2)$
-    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
-           $\MED \leftarrow 81, \PEER \leftarrow W$
-$\Router{C}$
-  Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
-    Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
-  Match $\PEER = D, \COMM = (2,2)$
-    Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
-$\Router{D}$
-  Match $\REGEX{X + Y}$
-    Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
-$\Router{E}$
-  Match $\REGEX{Z}$
-    Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
-\end{lstlisting}
+%% \begin{lstlisting}[frame=single, mathescape=true]
+%% $\Router{A}$
+%%   Match $\PEER=C, \COMM=(3,2)$
+%%     Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
+%% $\Router{B}$
+%%   Match $\PEER = C, \COMM = (-,2)$
+%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
+%%            $\MED \leftarrow 81, \PEER \leftarrow W$
+%%   Match $\PEER = C, \COMM = (3,2)$
+%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
+%%            $\MED \leftarrow 81, \PEER \leftarrow W$
+%% $\Router{C}$
+%%   Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
+%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
+%%   Match $\PEER = D, \COMM = (2,2)$
+%%     Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
+%% $\Router{D}$
+%%   Match $\REGEX{X + Y}$
+%%     Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
+%% $\Router{E}$
+%%   Match $\REGEX{Z}$
+%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
+%% \end{lstlisting}
+\begin{code}
+\Router{A}
+  Match \PEER=C, \COMM=(3,2)
+    Export \COMM \Arrow (4,2), \MED \Arrow 80, \PEER \Arrow W
+\Router{B}
+  Match \PEER = C, \COMM = (-,2)
+    Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
+           \MED \Arrow 81, \PEER \Arrow W
+  Match \PEER = C, \COMM = (3,2)
+    Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
+           \MED \Arrow 81, \PEER \Arrow W
+\Router{C}
+  Match[LP=99] \PEER = E, \COMM = (-,2) 
+    Export \COMM \Arrow (-,2), \PEER \Arrow B
+  Match \PEER = D, \COMM = (2,2)
+    Export \COMM \Arrow (3,2), \PEER \Arrow A,B
+\Router{D}
+  Match \REGEX{X + Y}
+    Export \COMM \Arrow (2,2), \PEER \Arrow C
+\Router{E}
+  Match \REGEX{Z}
+    Export \COMM \Arrow (-,2), \PEER \Arrow C
+\end{code}\vspace{-1cm}
 \label{fig:config}

### 2016-01-28 paper/propane.tex
fontifying

@@
 The \sysname compiler treats such under-specifications as constraints on the set of paths and automatically computes valid sets based on topology.
-
-We introduce \sysname by expressing the policies for the two examples above.
 %
-The next section describes how we compile such policies to BGP.
+To illustrate \sysname in action, we define policies for the two 
+examples described in the previous section.
+%
+The following section describes how we compile such policies to BGP.
 
@@
 one or more prefixes, we define a \sysname \emph{policy}.
-Within a policy, statements with the form $x$\Path$p$
-associate the prefixes defined by the predicate $x$ with the set of
-ranked paths defined by the path expression $p$.
-For instance, in the following code, ranked paths are associated with
-the customer prefixes (\CD{PCust}), the internal prefixes (\CD{PInt}),
+Within a policy, statements with the form $t$\Path$p$
+associate the prefixes defined by the predicate $t$ with the set of
+ranked paths defined by the path expression $p$.  In general,
+prefix predicates can be defined by arbitrary boolean combinations
+(and, or, not) of concrete prefixes and community tags.  Here,
+we assume we have already defined predicates \CD{PCust} for the
+customer prefixes and \CD{PInt} for our internal prefixes.
+In the following code, ranked paths are associated with
+customer prefixes, internal prefixes,
 and all other prefixes (\CD{true}).\footnote{Policy statements are processed in
 order with earlier policy statements taking precedence over later
-policy statements.  Hence, when the prefix predicate \True follows
+policy statements.  Hence, when the prefix predicate \True{} follows
 statements involving \CD{PCust} and \CD{PInt}, it is interpreted as
@@
      PCust \Path ExitCust \Prefer \End(Cust)
-     PInt  \Path \End(in)
+     PInt  \Path \End(\In)
      \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)
@@
 that connections to the customer through both of those routers fail,
-a backup route (\CD{\End(Cust)}) is defined that admits traffic to go through
-any path that ends at the customer.
+a backup route (\CD{\End(Cust)}) is defined that admits traffic along
+any path (including those through other networks) that ends at the customer.
 Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \In{} represents any location
@@
 
-Since routing allows transit traffic (\emph{i.e.}, traffic can enter from
+Since routing allows transit traffic (\IE, traffic can enter from
 \CD{Peer} and leave through \CD{Prov}), we should define a new policy that
-implements this restriction separately.
-
+implements this restriction separately.  We do so by using conjunction (\AND),
+disjunction (\OR) and negation (\NOT) of constraints. 
+%union (\Union), intersection (\Intersect), and negation (\NOT) to
+%specify the appropriate sets of paths.
+%
 %% \begin{lstlisting}[mathescape=true]
@@
 \Define PP = Peer \OR Prov
-\Define PPTransit   = \Enter(PP) \AND \Exit(PP)
-\Define CustTransit = \Later(Cust) \AND \Later(Prov)
-\Define NoTransit   = \{
-    \True \Path \NOT{}PPTransit \AND \NOT{}CustTransit
-\}
+\Define PPTrans   = \Enter(PP) \OR \Exit(PP)
+\Define CustTrans = \Later(Cust) \AND \Later(Prov)
+\Define NoTrans   = \True \Path \NOT{}PPTrans \AND \NOT{}CustTrans
 \end{code}
 \noindent
-The \CD{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied.
+The \CD{NoTrans} constraint above ensures that requirements (P2) and (P5) are satisfied.
 It says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}.
@@
 To implement both \CD{Routing}
-and \CD{NoTransit} simultaneously, we simply conjoin them:
-
+and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
+%
 %% \begin{lstlisting}[mathescape=true]
@@
 %% \end{lstlisting}
-
-\begin{code}
-Routing \AND{} NoTransit
-\end{code}
-
-\noindent
-The lines above capture the entire policy. From it, \sysname will generate per-device import and export filters, local preferences,
+%
+These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
 MED attributes, and community tags to ensure that the policy is
@@
 \sysname allows us to specify each of these constraints modularly.
-The first constraint is about prefix ownership---namely, we only want traffic for certain prefixes to end up at a particular locations.
+The first constraint is about prefix ownership---namely, we only want traffic for certain prefixes to end up at a particular location.
 The following definition captures this intent.
@@
 \Define Ownership = \{
-    Pg1 \Path \End(A)
-    Pg2 \Path \End(B)
-    Pl1 \Path \End(E)
-    Pl2 \Path \End(F)
+    PG1 \Path \End(A)
+    PG2 \Path \End(B)
+    PL1 \Path \End(E)
+    PL2 \Path \End(F)
 \}
@@
 end at router \CD{B}; and so on.
-
 For the second constraint, we can define another policy:
@@
 For instance, a constraint on aggregation is included to ensure that
-aggregation for global prefixes (with aggregate \CD{PG}) is performed from
-locations inside the network to locations outside. In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG} when advertised outside the datacenter.
+aggregation for global prefixes is performed from
+locations inside (\In) the network to locations outside (\Out). 
+In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG} 
+(which we assume is defined earlier using an appropriate prefix such 
+as \CD{74.3.28.0/24})
+when advertised outside the datacenter.
 

### 2016-01-28 paper/evaluation.tex
edits

@@
 The backbone network connects to the data centers and also has many external BGP neighbors.
-The policies are written in English and serve as a guide for operators when generating configuration templates for the data center routers or actual configurations for the backbone network (where templates are not used because of less regular structure).
+The policies are written in English and guide operators when writing configuration templates for data center routers or actual configurations for the backbone network (where templates are not used because of less regular structure).
 
@@
 It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA).
-Finally, it has filters to prevent bogons (private address space) from external neighbors, accept customer prefixes only from customers, and prevent customers from providing transit to other large networks.
+Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent using peers to go through a provider, etc.
 
@@
 
-Not counting the lines for various definitions like prefix and customer groups or for ownership constraints that define where routes originate, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.
+Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.
 
@@
   \caption{Configuration minimization.}
-  \label{fig:minipage2}
+  \label{fig:config-minimization}
 \end{figure}
@@
 For the data center network, we build and provide as input fat tree topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy.
-We take this approach to smoothly explore different sizes; there is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete data center topologies.
+We take this approach to smoothly explore different sizes.
+%there is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete data center topologies.
 For a given size, our reported results match those for the concrete topologies.
@@
 %
-For the data center policy, we measure the mean compilation time per prefix since the \sysname compiler can compile for each prefix independently, and in parallel.
-Figure~\ref{fig:compilation-times-dc} shows the compilation times for data centers of different sizes, broken down by compilation phase.
-No individual compilation phase dominates the running time of the compiler, with construction and minimization of the product graph taking the most time.
-\sysname compiles each data center in under 15 seconds per-prefix on average.
-Total compilation time for the largest data center with (>1600) routers takes less than 9 minutes total.
-%
-For the backbone policy, the \sysname compiler scales hundreds of routers, in a little over a minute per-prefix.
-However, unlike the data center policy, the number of prefixes for the backbone policy stays relatively fixed.
-Total compilation time for the largest backbone topology tested, with 200 routers, takes less than 3 minutes total.
-The presence of more preferences in the backbone policy increases the size of the product graph, and means minimization becomes a more expensive step in compilation.
+For both policies, we measure the mean compilation time per prefix since the \sysname compiler can compile for each prefix independently, and in parallel.
+Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes, broken down by compilation phase.
+No single compilation phase dominates the running time of the compiler, however construction and minimization of the product graph take the most time.
+Total compilation for the largest data center takes less than 9 minutes total.
+Unlike the data center policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases.
+Compilation for the largest backbone network, takes less than 3 minutes total.
+The inclusion of more preferences in the backbone policy increases the size of the PGIR, which leads to PGIR construction and minimization taking proportionally more time.
+
+\subsection{Configuration size}
 
@@
 To offset this, the compiler performs configuration minimization both during and after configuration generation.
-Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
-Figure~\ref{fig:compilation-compress-dc} shows the effect of minimization for the data center and backbone policies.
+%Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
+Figure~\ref{fig:config-minimization} shows the effect of minimization for the data center and backbone policies.
 In all cases, minimized policies are only a small fraction of the size of their non-minimized counterparts.

### 2016-01-28 paper/evaluation.tex
more edits. bring back conclusion
label images, and change image placement for space

@@
 
+\begin{figure}
+  \subcaptionbox{Data center}
+    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-dc.png}}
+  \subcaptionbox{Backbone network}
+    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
+  \label{fig:compilation-times}
+  \caption{Compilation time.}
+\end{figure}
+
 \subsection{Expressiveness}
@@
 
-\begin{figure}[t!]
-  \centering
-  \begin{minipage}[b]{0.45\linewidth}
-    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-dc.png}
-  \end{minipage}
-  \quad
-  \begin{minipage}[b]{0.45\linewidth}
-    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-backbone.png}
-  \end{minipage}
-  \caption{Compilation times.}
-  \label{fig:compilation-times}
-\end{figure}
+%\begin{figure}[t!]
+%  \centering
+%  \begin{minipage}[b]{0.45\linewidth}
+%    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-dc.png}
+%  \end{minipage}
+%  \quad
+%  \begin{minipage}[b]{0.45\linewidth}
+%    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-backbone.png}
+%  \end{minipage}
+%  \caption{Compilation times.}
+%  \label{fig:compilation-times}
+%\end{figure}
 
-\begin{figure}[t!]
-  \centering
-  \begin{minipage}[b]{0.45\linewidth}
-    \includegraphics[width=1.1\columnwidth]{figures/config-compression-dc.png}
-  \end{minipage}
-  \quad
-  \begin{minipage}[b]{0.45\linewidth}
-    \includegraphics[width=1.1\columnwidth]{figures/config-compression-backbone.png}
-  \end{minipage}
-  \caption{Configuration minimization.}
-  \label{fig:config-minimization}
-\end{figure}
+%\begin{figure}[t!]
+%  \centering
+%  \begin{minipage}[b]{0.45\linewidth}
+%    \includegraphics[width=1.1\columnwidth]{figures/config-compression-dc.png}
+%  \end{minipage}
+%  \quad
+%  \begin{minipage}[b]{0.45\linewidth}
+%    \includegraphics[width=1.1\columnwidth]{figures/config-compression-backbone.png}
+%  \end{minipage}
+%  \caption{Configuration minimization.}
+%  \label{fig:config-minimization}
+%\end{figure}
 
@@
 
-For the backbone network, the internal topology does not matter since all routers connect in a full iBGP mesh. We explore different mesh sizes and randomly map neighboring networks to routers.
+For the backbone network, the internal topology does not matter since all routers connect in a full iBGP mesh.
+We explore different mesh sizes and randomly map neighboring networks to routers.
+Even though each border router connects to many external peers, we count only the internal topology size.
 
@@
 
+\begin{figure}
+  \subcaptionbox{Data center}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
+  \subcaptionbox{Backbone network}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
+  \label{fig:config-min}
+  \caption{Configuration minimization.}
+\end{figure}
+
 \subsection{Configuration size}
@@
 %Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
-Figure~\ref{fig:config-minimization} shows the effect of minimization for the data center and backbone policies.
+Figure~\ref{fig:config-min} shows the effect of minimization for the data center and backbone policies.
 In all cases, minimized policies are only a small fraction of the size of their non-minimized counterparts.

### 2016-01-28 paper/compilation.tex
space savings

@@
 
-At a first cut, any time a router must make a decision locally between several route options, there is the possibility that it might choose incorrectly.
+At a first cut, any time a router must make a decision locally between several route options, there is the possibility it might choose incorrectly.
 The PGIR captures this notion of choice precisely.
@@
     Export \COMM \Arrow (-,2), \PEER \Arrow C
-\end{code}\vspace{-1cm}
-\label{fig:config}
+\end{code}\vspace{-.5cm}
+\label{fig:abgp-config}
 \caption{Abstract BGP router configurations.}
@@
 In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
-Any unknown AS topology is modelled as a special node in the product graph that generates a filter to match any sequence of ASes.
+The unknown AS topology is modelled as a special node in the PGIR that generates a filter to match any sequence of ASes.
 
@@
 Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
-Figure~\ref{fig:config} shows the full configuration from the compilation example.
+Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.
 
@@
 \begin{prop}
-A distributed BGP configuration produced by \sysname is \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.
+BGP configurations produced by \sysname are \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.
 \end{prop}
@@
 \begin{prop}
-A distributed BGP configuration produced by \sysname is \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
+BGP configurations produced by \sysname are \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
 \end{prop}
@@
 \begin{prop}
-The internal routers in a distributed BGP configuration produced by \sysname will be stable. 
+BGP configurations for internal routers produced by \sysname will be stable. 
 \end{prop}

### 2016-01-28 data/backbone.py
finished experiments with finer granularity

@@ -107,10 +107,10 @@ num_nodes2 = map(lambda x: x, num_nodes)
 sizes_raw_per = map(lambda (size,n): size/n, zip(sizes_raw, num_nodes))
 sizes_compressed_per = map(lambda (size,n): size/n, zip(sizes_compressed, num_nodes))
 
-num_nodes1 = num_nodes1[2::3]
-num_nodes2 = num_nodes2[2::3]
-sizes_raw_per = sizes_raw_per[2::3]
-sizes_compressed_per = sizes_compressed_per[2::3]
+num_nodes1 = num_nodes1[2::5]
+num_nodes2 = num_nodes2[2::5]
+sizes_raw_per = sizes_raw_per[2::5]
+sizes_compressed_per = sizes_compressed_per[2::5]
 
 fig = plt.figure()
 ax1 = fig.add_subplot(111)

### 2016-01-28 paper/introduction.tex
tweaks to abstract and intro

@@
 
-It is well-known that network configuration is highly error
+It is well known that network configuration is highly error
 prone and that such errors can lead to costly network
@@
 
-Besides the languages being low-level, a fundamental reason for configuration being onerous is the semantic mismatch between the intended high-level
-policies and the low-level device-by-device configurations.  In particular,
+A fundamental reason for the prevalence of misconfigurations is the
+semantic mismatch between the intended high-level
+policies and the low-level configurations.  In particular,
 many policies involve network-wide properties---prefer a certain neighbor,
@@
 %
-Operators must manually decompose network-wide policy into device-level behaviors, such that their interactions satisfy the high-level objectives.
+Operators therefore must manually decompose network-wide policy into
+device-level behaviors, such that the distributed interactions among
+these devices satisfy the high-level objectives.
 %
-Ensuring policy-compliance through this manual decomposition is challenging under normal
-circumstances and even more so in the face of failures. Some decompositions that work correctly
-in failure-free environments, violate key constraints when failures occur.
-%
-As a result, many network configuration problems are only revealed after failures~\cite{batfish},
-sometimes making a bad situation worse.
+Further, policy-compliance must be ensured not only under normal network
+circumstances but also in the face of failures.  The need to reason
+about possible failures exacerbates an already considerable challenge
+for network operators.  As a result, configurations that work
+correctly in failure-free environments have nonetheless been found to violate key
+network-wide properties when failures occur~\cite{batfish}.
 
@@
 %
-However,
- while templates help ensure certain kinds of consistency across devices,
+While templates help ensure certain kinds of consistency across devices,
 they do not bridge the
-semantic divide between network policies and device-level configuration.
+semantic divide between network-wide policies and device-level configuration.
 They do not provide fundamentally different abstractions
-from existing configuration languages or new, higher-level reasoning
-principles.
+from existing configuration languages and so still require operators to
+manually decompose policies into per-device behaviors.
 
@@
 they fail to provide a coherent means to specify preferred
-\emph{inter}-domain routes.  Second, centralized control planes
+\emph{inter}-domain routes.  \todd{What is the impact of these
+  languages not supporting inter-domain routing?  How are those
+  policies expressed instead in an SDN context?  A sentence on the
+  impact would help.}  Second, centralized control planes
 require careful design and engineering to be robust to failures---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure.
@@
 \begin{enumerate}
-\item Design a new, high-leve language with abstractions
+\item Design a new, high-level language with natural abstractions
 for expressing intra-domain routing, inter-domain
 routing and routing alternatives in case of failures.
-\item Define algorithms for compiling these specifications in to
+\item Define algorithms for compiling these specifications into
 configurations for devices running standard
@@
 
-To achieve the first goal, we borrowed heavily from 
+To achieve the first goal, we borrow the idea of using regular
+expressions to specify network paths from 
 recent high-level SDN languages such as FatTire~\cite{fattire},
 Merlin~\cite{foster:merlin}, and
-NetKAT~\cite{netkat} by using regular expressions to specify network paths.  However, our design also contains several key
+NetKAT~\cite{netkat}.  However, our design also contains several key
 departures from existing languages.  The most important difference is semantic:  the paths specified
@@
 choice allows users to specify preferences about both external and internal
-routes in the same notation.  
+routes in the exact same way.
 %No SDN programming language provides similar facilities.  
-In addition,
-we incorporate user preferences in to the algebra
-of regular expressions and provide a semantics in terms of sets of ranked paths.  The preferences indicate fail-over behaviors:  among all specified paths that are still available,
+In addition, we augment the algebra
+of regular expressions to directly support a notion of {\em preferences} and provide a semantics in terms of sets of ranked paths.
+The preferences indicate fail-over behaviors:  among all specified paths that are still available,
 the system guarantees that the highest-ranked one will be taken.  
@@
 algorithms that translate the regular policies to a graph-based
-intermediate language and from there to BGP configurations.  
+intermediate language and from there to BGP configurations, including
+per-device import and export filters, local preferences, MED attributes, and community tags.
 We target BGP for pragmatic reasons:  it is an industry
@@
 
-However, using BGP as a vehicle for implementing high-level policies is
-challenging because not all policies can be implemented correctly in
+The BGP configurations produced by our compiler are
+guaranteed to satisfy the given policy specification in the face of
+{\em arbitrary} failures.  In this way, we provide network operators
+with a strong guarantee that is otherwise impossible to achieve
+today. 
+However, some policies simply cannot be implemented correctly in BGP in 
  the presence of arbitrary failures.  We develop new
-algorithms to detect policies that cannot be implemented
-and report our findings to the operators, so they may fix the specification at compile time rather than experience undesirable behavior after configurations are deployed.
+algorithms to detect such policies
+and report our findings to the operators, so they may fix the policy
+specification at compile time rather than experience undesirable
+behavior after the configurations are deployed.
 %We also analyze route aggregation to detect the possibility of failure-induced black-holes.
-If the policies are implementable, our compiler automatically synthesizes per-device import and export filters, local preferences, MED attributes, and community tags.
 

### 2016-01-28 paper/conclusions.tex

--- 2016-01-14 paper/conclusions.tex
@@
 
-TODO
+In this paper, we introduced \sysname, a language and compiler for implementing centralized network policies using a distributed set of devices running BGP.
+Propane allows operators to describe network-wide intent directly through high-level constraints on the shape and relative preferences of paths for different types of traffic.
+When \sysname compiles a policy, then the resulting BGP configurations are correct-by-construction, faithfully implementing the centralized policy in a distributed fashion, regardless of failures.
+When \sysname can not implement the policy, it notifies the user during the compilation stage rather than after deployment.

### 2016-01-28 paper/motivation.tex
updating figures to match code more closely

@@
 
-We can now see how devising correct configurations for real, larger networks can be a nightmare.
+We can now see how devising correct configurations for real, larger networks can quickly become a nightmare.
 Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several geography-, neighbor- or prefix-based exceptions to the default behavior.
-Templates help by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually.
-\sysname lets operators express such policies easily and intuitively.
+For example, a large AS with many peers in different geographic locations, may be faced with complex challenges like keeping traffic within national boundaries.
+Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually. 
+%\sysname lets operators express such policies easily and intuitively.
 It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.

### 2016-01-28 paper/compilation.tex
fix label reference issue
more edits

@@
 
-\sysname also supports constraints purely on the control-plane behavior of BGP.
-For example, prefix aggregation, which should not affect routing behavior, is an important optimization to reduce routing table size and churn in practice.
+\sysname also supports constraints purely on the control-plane behavior of BGP. For example, prefix aggregation is an important optimization to reduce routing table size and churn in practice. 
 %% Aggregation, for example, from internal to external locations, is specified using the same regular syntax as before:
@@
 We denote a network path as a string of abstract locations (routers or external ASes) of the form: $n_1 n_2 \dots n_k$.
-A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$ and $p$ is a topologically-valid path.
+A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$, that is the path is in the language of the regular expression, and $p$ is a topologically-valid path.
 We denote the length of a path $p$ as $\abs{p}$.
@@
 
-The main differences between the FE and RIR are: (1) FE allows the programmer to specify constraints using a series of (modular) definitions, and combine them later, (2) FE provides high-level names that abstract sets of routes, and (3) FE allows the preference operator to be used locally.
+The main differences between the FE and RIR are: $i)$ FE allows the programmer to specify constraints using a series of (modular) definitions, and combine them later, $ii)$ FE provides high-level names that abstract sets of routes and groups of prefixes/neighbors, and $iii)$ FE allows the preference operator to be used more flexibly.
 
@@
 In particular, each regular path constraint $r$ must satisfy $r \subseteq \Out^* \cdot \In^+ \cdot \Out^*$.
-This ensures that one can only talk about controlling traffic that goes through the user's network at some point,
-and that such traffic does not loop back multiple times to the user network.
+This ensures that the user only control traffic that goes through the user's network at some point, and that such traffic does not loop back multiple times to the user network.
 
@@
 For example, the regular expression $a \cdot (b \Prefer c) \cdot d$ is lifted to $(a \cdot b \cdot d) \Prefer (a \cdot c \cdot d)$ by distributing the preference over the sequence operator.
-In general, we employ the follwing equivalence:
+In general, we employ the follwing distributivity equivalences:
 %
-$$x \odot (y_1 \Prefer \dots \Prefer y_n) = (x \odot y_1) \Prefer \dots \Prefer (x \odot y_n)$$
+\[ 
+\begin{array}{c}
+  x \odot (y_1 \Prefer \dots \Prefer y_n) = (x \odot y_1) \Prefer \dots \Prefer (x \odot y_n) \\
+  (y_1 \Prefer \dots \Prefer y_n) \odot x = (y_1 \odot x) \Prefer \dots \Prefer (y_n \odot x)
+\end{array}
+\]
 %
@@
   \end{tikzpicture}
-
   \end{minipage}
@@
   \hrulefill
+  \vspace*{.4em}
 
@@
 %We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
-For example, node $(1,1) W$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it most go through another $W$ in either case.
+For example, node $(1,1) W$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it must go through another $W$ in either case.
 Colored nodes and dashed edges are removed after minimization since they are irrelvant to the BGP decision process.
@@
 
-\para{Avoiding Simple Paths}
+\para{Avoiding Loops}
 
@@
 \end{code}\vspace{-.5cm}
-\label{fig:abgp-config}
-\caption{Abstract BGP router configurations.}
+\caption{Abstract BGP router configurations. \label{fig:abgp-config}}
 \end{figure}

### 2016-01-28 paper/compilation.tex
more edits

@@
 That simplicity, however, comes at the cost of compilation complexity.
-The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, compute which ones can be honored under failures, and ensure policy compliance under all possible failure cases.
-
-%\subsection{Overview}
+The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, determine which ones can be honored under failures, and ensure policy compliance under all possible failure cases.
 
@@
 \end{figure}
-
-%In this section we briefly describe our compilation strategy for \sysname.
 
@@
 \para{Syntax}
-The \sysname FE is just a thin layer atop a core, regular-expression language for describing preference-based path constraints. 
+The \sysname FE is just a thin layer atop a core, regular-expression language (RIR) for describing preference-based path constraints. 
 Figure~\ref{fig:rir-syntax} shows the RIR syntax.

### 2016-01-28 paper/motivation.tex
more edits

@@
 This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally.
-Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix $P_G$.
+Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}.
 The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.
 
-The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ announce what they hear from routers C and D and aggregate to $P_G$ if an announcement is subset of $P_G$.
+The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ announce what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}.
 This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be assigned to local services without updating router configurations).
@@
 Suppose links X--G and X--H fail.
-Then, X will hear announcements for $P_{l*}$ from C and D, having traversed from G and H to Y to C and D.
+Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D.
 Per policy implementation, X will start "leaking" these prefixes externally.
-Depending on the rationale for local services, this leak could impact security (e.g., if the services were sensitive) or availability (e.g., if the $P_{l*}$ prefixes are used for other services outside of the data center).
-This problem does not manifest without failures because then X has and prefers paths to $P_{l*}$ through G and H since they are shorter.
+Depending on the rationale for local services, this leak could impact security (e.g., if the services were sensitive) or availability (e.g., if the \CD{PL*} prefixes are used for other services outside of the data center).
+This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter.
 A similar problem will happen if links Y--G and Y--H fail.
@@
 But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{xx}.
-If links D--A and X--C fail, X will hear announcements for $P_{g2}$ from D and will thus announce the $P_G$ externally.
-This announcement will bring to X traffic for $P_{g1}$ as well, but because of valley-free filtering, X does not have a valid route for $P_{g1}$ and will thus drop all traffic to it.
+If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce the \CD{PG} externally.
+This announcement will bring to X traffic for \CD{PG1} as well, but because of valley-free filtering, X does not have a valid route for \CD{PG1} and will thus drop all traffic to it.
 

### 2016-01-28 paper/propane.tex
more edits

@@
 Line 2 of this policy 
-defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2} and in the event
-that connections to the customer through both of those routers fail,
+defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
+that connections to the customer through both routers fail,
 a backup route (\CD{\End(Cust)}) is defined that admits traffic along
@@
 Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \In{} represents any location
-inside the user's network whereas the keyword \Out{} represents any location
+inside the user's network and the keyword \Out{} represents any location
 outside the user's network.
-Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers.
-To summarize our progress so far, the \CD{Routing} policy
+Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers. To summarize our progress, the \CD{Routing} policy
 implements (P1), (P3) and (P4) from Figure~\ref{fig:example1}.
 
-Since routing allows transit traffic (\IE, traffic can enter from
-\CD{Peer} and leave through \CD{Prov}), we should define a new policy that
-implements this restriction separately.  We do so by using conjunction (\AND),
+Since routing allows transit traffic (\EG, traffic entering from
+\CD{Peer} and leaving through \CD{Prov}), we define a new policy to implement this restriction separately, using conjunction (\AND),
 disjunction (\OR) and negation (\NOT) of constraints. 
@@
 \Define PP = Peer \OR Prov
-\Define PPTrans   = \Enter(PP) \OR \Exit(PP)
+\Define PPTrans   = \Enter(PP) \AND \Exit(PP)
 \Define CustTrans = \Later(Cust) \AND \Later(Prov)
-\Define NoTrans   = \True \Path \NOT{}PPTrans \AND \NOT{}CustTrans
+\Define NoTrans   = \{\True \Path \NOT{}PPTrans \AND \NOT{}CustTrans\}
 \end{code}

### 2016-01-28 paper/compilation.tex
changing product graph to match formal description

@@
 BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
-This is reflected in the product graph by the node with state $(1,1) X$.
+This is reflected in the product graph by the node with state $(X,1,1)$.
 From here, if X were to advertise this route to D, it would result in the path $D X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
 %
-The ``--" state indicates it is dropped from the corresponding automaton. Since node $(5,-) W$ is in an accepting state for the first automata, it indicates this path has preference 1.
+The ``--" state indicates it is dropped from the corresponding automaton. Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates this path has preference 1.
 
@@
 %We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
-For example, node $(1,1) W$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it must go through another $W$ in either case.
+For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it must go through another $W$ in either case.
 Colored nodes and dashed edges are removed after minimization since they are irrelvant to the BGP decision process.
@@
 In this case, the advertisement from $C$ will still be sent along towards the ultimate backup location $W$.
-Since the $(3,2) C$ node has the same one-step and two-step next hops as node $(-,2) C$ in the product graph, no possible failure will prevent a route advertisment from reaching $(-,4) W$ that wouldn't have otherwise prevented it if $C$ had choosen $E$.
+Since the $(C,3,2)$ node has the same one-step and two-step next hops as node $(C,-,2)$ in the product graph, no possible failure will prevent a route advertisment from reaching $(W,-,4)$ that wouldn't have otherwise prevented it if $C$ had choosen $E$.
 
@@
 The high-level idea is to order each PGIR node according to a \textit{can prefer} relation.
-For example, node $(3,2) C$ can be preferred to node $(-,2) C$, but not the other way around.
+For example, node $(C,3,2)$ can be preferred to node $(C,-,2)$, but not the other way around.
 Intuitively, a node $N_1$ can be preferred to another node $N_2$ when, for each preference $N_2$ might achieve, there is a better preference that $N_1$ will achieve regardless of failures.
@@
 
-For example, imagine we use the data center example from \S\ref{sec:motivation}, with the policy: $p_{g1} \mapsto end(A)$, where $p_{g1}$ falls under the $p_{g^*}$ aggregate.
+For example, imagine we use the data center example from \S\ref{sec:motivation}, with the policy: 
+$\CD{PG1} \mapsto \End(A)$, where \CD{PG1} falls under the \CD{PG} aggregate.
 Figure~\ref{fig:aggregation-safety} shows the network topology and a simplified PGIR.
-Since the compiler knows an aggregate will be placed at $X$, and it knows that, the route for $p_{g1}$ will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
+Since the compiler knows an aggregate will be placed at $X$, and it knows that, the route for \CD{PG1} will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
 We could remove the $A$--$D$--$X$ path first.
@@
 Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
-Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix $p_{g1}$.
+Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}.
 This process is repeated for other aggregation locations (e.g., $Y$).

### 2016-01-28 paper/compilation.tex
unify syntax across paper

@@
      pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
-     p       &::=& t \mapsto r_1 \Prefer \dots \Prefer r_m & \textit{preferences} \\
+     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{preferences} \\
      x       &::=& a.b.c.d/n & \textit{prefix} \\
@@
 
-  \caption{Example Product Graph IR construction for policy: $(W \cdot A \cdot C \cdot D \cdot out) \Prefer (W \cdot B \cdot in^* \cdot out)$.}
+  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^* \cdot \Out)$.}
   \label{fig:example-compilation}
@@
 %
-$$(W \cdot A \cdot C \cdot D \cdot \Out) \Prefer (W \cdot B \cdot in^* \cdot \Out)$$
+$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^* \cdot \Out)$$
 %
@@
 %
-$$(W \cdot A \cdot C \cdot D) \Prefer (W \cdot B \cdot C \cdot E)$$
+$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D}) \Prefer (\CD{W} \cdot \CD{B} \cdot \CD{C} \cdot \CD{E})$.
 %
+
 How could such a policy be implemented in BGP?
@@
 For example, imagine we use the data center example from \S\ref{sec:motivation}, with the policy: 
-$\CD{PG1} \mapsto \End(A)$, where \CD{PG1} falls under the \CD{PG} aggregate.
+\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
 Figure~\ref{fig:aggregation-safety} shows the network topology and a simplified PGIR.

### 2016-01-28 paper/compilation.tex
adding some references

@@
 %For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
-We use graph dominators~\ref{bib:todo} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
-In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading to $y$ from the start node. Many efficient algorithms exist for finding graph dominators in practice~\ref{bib:todo}.
+We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
+In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading to $y$ from the start node.
+Many efficient algorithms exist for finding graph dominators in practice~\cite{linear-dominance, fast-dominance, tarjan-dominance}.
 %We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 

### 2016-01-28 paper/implementation.tex
adding some references

@@
 Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\ref{bib:todo}.
-The \sysname compiler uses regular expressions derivatives~\ref{bib:todo} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently.
+The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently.
 Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy.
@@
 
-The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\ref{bib:todo}.
-More complex algorithms with better theoretical complexity exist~\ref{bib:todo} and may be better suited for large enough topologies.
+The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\cite{fast-dominance}.
+More complex algorithms with better theoretical complexity exist~\cite{linear-dominance, tarjan-dominance} and may be better suited for large enough topologies.
 All minimization steps are repeated until no more progress can be made.

### 2016-01-28 paper/background.tex
tweaks to background

@@
 One such attribute is a list of community strings.
-ASes use such strings to color routes on different criteria (e.g., ``entered on West Coast") and then use the color later in the routing process.
+ASes use such strings to color routes on different criteria (e.g., ``entered on West Coast'') and then use the color later in the routing process.
 Communities are also used to signal to neighbors how they should handle an announcement (e.g., do not export it further).
@@
 
-The route selection process assigns a {\em local preference} to each route that survives the import filters.
-Routes with higher local preference are preferred.
-Among routes with the same local preference, other factors such as AS path length, MEDs, internal routing cost, are considered in order.
+The route selection process assigns a {\em local preference} to each
+route that survives the import filters. Routes with higher local
+preference are preferred. Among routes with the same local preference,
+other factors such as AS path length, MEDs, and internal routing cost, are considered in order.
 Because it is considered first during route selection, local preference is highly influential, and ASes may assign this preference based on any aspect of the route.
@@
 
-In implementing their policy, each network assumes that neighboring ASes correctly implement BGP and honor contracts related to MEDs and communities.
-While deriving configurations, \sysname makes a similar assumption.
+In implementing their policy, each network operator assumes that
+neighboring ASes correctly implement BGP and honor contracts related
+to MEDs and communities. \sysname makes the same assumption when
+deriving BGP configurations for a network.
 

### 2016-01-28 paper/implementation.tex
a few more citations

@@
 
-Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\ref{bib:todo}.
+Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\cite{regex-complexity}.
 The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently.

### 2016-01-28 paper/evaluation.tex
space savings
more edits
pass over eval

@@
 We apply \sysname on real policies for backbone and data center networks.
-Our goal is to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
+Our mains goals are to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
 
@@
 The backbone network connects to the data centers and also has many external BGP neighbors.
-The policies are written in English and guide operators when writing configuration templates for data center routers or actual configurations for the backbone network (where templates are not used because of less regular structure).
+The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for data center routers or actual configurations for the backbone network (where templates are not used because the network has less regular structure).
 
@@
 It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA).
-Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent using peers to go through a provider, etc.
+Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, etc.
 
@@
 The routers aggregate prefixes when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region.
-They also have policies by which some prefixes should not be announced beyond a certain level in the data center hierarchy.
+They also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
 
@@
     {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
-  \label{fig:compilation-times}
-  \caption{Compilation time.}
+  \caption{Compilation time. \label{fig:compilation-times}}
 \end{figure}
@@
 The data center operator said that he found the language intuitive.
-The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{x}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to compute the various local preferences, import-export filters, and MEDs.} We found that the data center policies were correctly translated.
+The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{x}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We found that the data center policies were correctly translated.
 For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.
@@
 Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.
+
+\begin{figure}
+  \subcaptionbox{Data center}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
+  \subcaptionbox{Backbone network}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
+  \caption{Configuration minimization. \label{fig:config-min}}
+\end{figure}
 
@@
 
-We now study the compilation of time for both policies as a function of network size.
+We study the compilation of time for both policies as a function of network size.
 Even though the networks we study have a fixed topology and size, we can explore the impact of size because our converted policies are network-wide and the compiler takes topology itself as an input.
-For the data center network, we build and provide as input fat tree topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy.
+For the data center network, we build and provide as input fat tree~\cite{fattree} topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy.
 We take this approach to smoothly explore different sizes.
-%there is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete data center topologies.
+%There is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete data center topologies.
 For a given size, our reported results match those for the concrete topologies.
@@
 We explore different mesh sizes and randomly map neighboring networks to routers.
-Even though each border router connects to many external peers, we count only the internal topology size.
+Even though each border router connects to many external peers, we count only the mesh size.
 
@@
 %
+Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes.
 For both policies, we measure the mean compilation time per prefix since the \sysname compiler can compile for each prefix independently, and in parallel.
-Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes, broken down by compilation phase.
-No single compilation phase dominates the running time of the compiler, however construction and minimization of the product graph take the most time.
-Total compilation for the largest data center takes less than 9 minutes total.
+At their largest sizes, the per-prefix compilation time is roughly 10 seconds for the data center network and 45 seconds for the backbone network.
+
+From the break down of the time by compilation phase, we see that no single compilation phase dominates the running time of the compiler.
+However, construction and minimization of the product graph take the most time.
+
+Total compilation for the largest data center is less than 9 minutes total.
 Unlike the data center policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases.
@@
 
-\begin{figure}
-  \subcaptionbox{Data center}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
-  \subcaptionbox{Backbone network}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
-  \label{fig:config-min}
-  \caption{Configuration minimization.}
-\end{figure}
+%
 
@@
 
-The naive compilation algorithm from \S\ref{sec:compilation} generates extremely large ABGP policies.
+Figure~\ref{fig:config-min} shows the size of the configuration generated by \sysname, again as a function of network size.
+The naive translation of PGIR to ABGP generates extremely large ABGP policies.
 To offset this, the compiler performs configuration minimization both during and after configuration generation.
 %Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
-Figure~\ref{fig:config-min} shows the effect of minimization for the data center and backbone policies.
+The figure shows the minimization is highly effective for the data center and backbone policies.
 In all cases, minimized policies are only a small fraction of the size of their non-minimized counterparts.
+
+%for i in *.set; do grep bgp $i | wc; done
+However, even minimized configurations are hundreds or thousands of lines per router.
+For the backbone network, the size of \sysname configurations is roughly similar to the BGP components of actual router configurations, though qualitative differences exist (see below).
+We did not have actual configurations for the data center network; they are dynamically generated from templates.
 
@@
 
-Finally, we comment briefly on how \sysname-generated configurations differ from those generated by operators today. 
+Finally, we comment briefly on how \sysname-generated configurations differ from configurations or templates generated by operators.
 %
-In some cases, \sysname configurations are implemented as one would expect.
-For example, preferences among neighboring ASes are implemented with a compiler-generated community value to tag incoming routes according to preference, which is then observed at other border routers to influence decisions.
-In other cases, the \sysname configurations are different, relying on a different BGP mechanism to achieve the same result.
-Some key differences that we observed were:
-%
-$i)$ operators used the no-export community to prevent routes from leaking beyond a certain tier of the data center, whereas \sysname selectively imported the route only below a certain tier; 
+In some cases, \sysname configurations are similar.
+For example, preferences among neighboring ASes are implemented with a community value to tag incoming routes according to preference, which is then used at other border routers to influence decisions.
+
+In other cases, the \sysname configurations are different, relying on a different BGP mechanism to achieve the same result. Some key differences that we observed were:
+
+$i)$ operators used the no-export community to prevent routes from leaking beyond a certain tier of the datacenter topology, whereas \sysname selectively imported the route only below a certain tier;
 %\sysname could use a similar implementation mechanism in the future as an optimization.
-%
-$ii)$ operators prevented unneeded propagation of more-specific route advertisements from a neighboring AS based on their out-of-band knowledge about topology, whereas \sysname propagated these advertisements; and
-%
-$iii)$ operators used a layer of indirection using community groups and re-writing to implement certain policies in a more maintainable way, where \sysname uses flat communities.
+
+$ii)$ operators prevented unneeded propagation of more-specific route announcements from a neighboring AS based on their out-of-band knowledge about topology, whereas \sysname propagated these advertisements; and
+
+$iii)$ operators used a layer of indirection for community values, using community groups and re-writing values, to implement certain policies in a more maintainable manner, where \sysname uses flat communities.
+
 We are currently investigating if such differences matter to operators (e.g., if they want to read \sysname configurations) and, if necessary, how to reduce them.

### 2016-01-28 paper/motivation.tex
small updates to motivation

@@
 
-Consider the backbone network in Figure~\ref{fig:example1}.
-It has three neighbors, a customer $Cust$ , a peer $Peer$, and a provider $Prov$.
+Consider the backbone network in Figure~\ref{fig:example1}. It has
+three neighbors, a customer \CD{Cust}, a peer \CD{Peer}, and a provider \CD{Prov}.
 The policy of this network is shown on the right.
-It prefers the neighbors in a certain order ($P1$) and does not want to act as a transit between Peer and Prov ($P2$).
-It prefers to exchange traffic with Cust over $R1$ rather than $R2$ because $R1$ is cheaper ($P3$).
-To guard against another AS "hijacking" prefixes owned by Cust, it only sends traffic to them if Cust is on the AS path ($P4$).
-Finally, to guard against Cust accidentally becoming a transit for Prov, it does not use Cust for traffic that will later traverse Prov ($P5$).
+It prefers the neighbors in a certain order (P1) and does not want to act as a transit between \CD{Peer} and \CD{Prov} (P2).
+It prefers to exchange traffic with \CD{Cust} over \CD{R1} rather than \CD{R2} because \CD{R1} is cheaper (P3).
+To guard against another AS "hijacking" prefixes owned by \CD{Cust}, it only sends traffic to them if \CD{Cust} is on the AS path (P4).
+Finally, to guard against \CD{Cust} accidentally becoming a transit for \CD{Prov}, it does not use \CD{Cust} for traffic that will later traverse \CD{Prov} (P5).
 
-To correctly implement this policy, the operators must compute and assign local preferences such that preferences at Cust-facing interfaces $>$ Peer-facing interfaces $>$ Prov-facing interfaces.
-At the same time, the preference at $R2$'s Cust-facing interface should be lower than that at $R1$, but higher than that at Prov-facing interface.
-To fully realize $P2$, MEDs will have to be appropriately configured as well.
-To implement $P3$ and $P4$, the operators may assign communities that indicate where a certain routing announcement entered the network.
-Then, R4 must not announce to $Peer$ routes that have communities that correspond to the R2-prov link but must announce communities for the $R2$-Cust and $R1$-Cust links.
-Finally, to implement $P4$ and $P5$, the operators will have to compute and configure appropriate prefix- and AS-path-based filters at each router.
+To implement P1 of the policy, the operators must compute and assign
+local preferences such that preferences at \CD{Cust}-facing interfaces
+$>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
+the same time, to satisfy P3 the preference at \CD{R2}'s
+\CD{Cust}-facing interface should be lower than that at
+\CD{R1}. % Implementing P2 properly will require MEDs to be
+% appropriately configured. 
+\todd{I commented out the sentence about MEDs for P2, because the next
+  two sentences seem to be about P2 instead of P3 and P4, which it
+  originally said.  Please check}  To implement P2, the operators can assign communities that
+indicate where a certain routing announcement entered the
+network. Then, \CD{R4} must be configured to not announce to
+$\CD{Peer}$ routes that have communities that correspond to the
+\CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links.
+Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based filters at each router.
 
-We can now see how devising correct configurations for real, larger networks can quickly become a nightmare.
-Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several geography-, neighbor- or prefix-based exceptions to the default behavior.
-For example, a large AS with many peers in different geographic locations, may be faced with complex challenges like keeping traffic within national boundaries.
+Clearly it is no simple task to properly configure even this
+small example network manually; devising correct configurations for real networks can quickly become a nightmare.
+Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several neighbor- or prefix-based exceptions to the default behavior.
+For example, a large AS with many peers in different geographic locations may be faced with complex challenges like keeping traffic within national boundaries.
 Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually. 
@@
 Per policy implementation, X will start "leaking" these prefixes externally.
-Depending on the rationale for local services, this leak could impact security (e.g., if the services were sensitive) or availability (e.g., if the \CD{PL*} prefixes are used for other services outside of the data center).
+Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are used for other services outside of the data center).
 This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter.
@@
 
-To avoid this problem, the operator may decide to disallow "valleys" paths, i.e., those that go up, down, and back up again.
+To avoid this problem, the operator may decide to disallow "valley" paths, i.e., those that go up, down, and back up again.
 This guard can be implemented by $X$ and $Y$ rejecting paths through the other.
@@
 \sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures (if that is possible; otherwise, it generates a compile-time error).
-For aggregation, it will also provide a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
+For aggregation, it also provides a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
 

### 2016-01-29 paper/introduction.tex
pass over introduction

@@
 %ensuring key correctness constraints are satisfied.
-One step further, systems like
-ConfigAssure~\cite{narain:lisa05,narain+:configassure} use SAT solving
-and model finding tools to correctly and consistently fill in some parameters.
+%One step further, systems like
+%ConfigAssure~\cite{narain:lisa05,narain+:configassure} use SAT solving
+%and model finding tools to correctly and consistently fill in some parameters.
 %
@@
 from existing configuration languages and so still require operators to
-manually decompose policies into per-device behaviors.
+manually decompose policies into device-level behaviors.
 
@@
 they fail to provide a coherent means to specify preferred
-\emph{inter}-domain routes.  \todd{What is the impact of these
+\emph{inter}-domain routes. 
+This means that existing inter-domain routing protocols and their associated configuration difficulties will be around for the forseeable future.
+\ryan{I added this. Is it true? what about SDX?}
+\todd{What is the impact of these
   languages not supporting inter-domain routing?  How are those
   policies expressed instead in an SDN context?  A sentence on the
-  impact would help.}  Second, centralized control planes
+  impact would help.}  
+Second, centralized control planes
 require careful design and engineering to be robust to failures---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure.
@@
 The preferences indicate fail-over behaviors:  among all specified paths that are still available,
-the system guarantees that the highest-ranked one will be taken.  
+the system guarantees that the distributed implementation will always use the highest-ranked ones.  
 %We also support network operators by defining a
@@
 We target BGP for pragmatic reasons: it is an industry
-standard and many networks use it internally as well as externally. Despite the advent of SDN, many networks will continue to
+standard, and many networks use it internally as well as externally. Despite the advent of SDN, many networks will continue to
 use BGP for the foreseeable future due to existing infrastructure investments, the difficulty of transitioning to SDN,
@@
 The BGP configurations produced by our compiler are
-guaranteed to satisfy the given policy specification in the face of
+guaranteed to be policy compliant in the face of
 {\em arbitrary} failures.  In this way, we provide network operators

### 2016-01-29 paper/propane.tex
small tweaks to sec 4

@@
 
-Policies for (distributed) control planes differ from data plane policies~\cite{x,y,z}.
-First, they must account for all failures at specification time; there is no controller at runtime, the routers must be configured in advance to handle failures in a compliant manner.
+Policies for (distributed) control planes differ from data-plane
+policies~\cite{x,y,z} in a few important ways. First, control-plane
+policies must account for all failures at specification time; there is
+no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
 %
-In \sysname, we enable such specifications through path preferences, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
+In \sysname, we enable such specifications through a notion of {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
 %
-Second, paths may be under-specified (e.g., "prefer customer" does not indicate a concrete path).
-The \sysname compiler treats such under-specifications as constraints on the set of paths and automatically computes valid sets based on topology.
+Second, paths in a control-plane policy may be under-specified (e.g.,
+"prefer customer" does not indicate a concrete path). The \sysname
+compiler treats such under-specifications as constraints on the set of
+allowed paths and automatically computes valid sets based on topology.
 %
-To illustrate \sysname in action, we define policies for the two 
-examples described in the previous section.
-%
-The following section describes how we compile such policies to BGP.
+
+In the rest of this section, we define \sysname policies for the two 
+examples described in the previous section, introducing key aspects of
+the \sysname language along the way.  The complete syntax of the
+language as well as our strategy for compiling \sysname policies to
+BGP is defined in the next section.
 
@@
 
-\sysname allows the operator to configure the network with the abstraction that he or she has centralized control over routing and uses a set of high-level constraints to describe the different routes traffic may (or may not) take and their relative preferences.
+\sysname allows the operator to configure the network with the
+abstraction that he or she has centralized control over routing.
+Specifically, the operator simply provides a set of high-level constraints
+that describe the 
+different routes traffic may (or may not) take and their relative preferences.
 \sysname specifications are written modularly via a series
@@
 For example, to begin specification of the backbone
-network, we first express the idea that for routes leading to our customer,
+network from the previous section, we first express the idea that for routes leading to our customer,
 we prefer using \CD{R1} over \CD{R2} (Policy P3 from Figure~\ref{fig:example1}):
@@
 Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers. To summarize our progress, the \CD{Routing} policy
-implements (P1), (P3) and (P4) from Figure~\ref{fig:example1}.
+implements P1, P3, and P4 from Figure~\ref{fig:example1}.
 
@@
 \noindent
-The \CD{NoTrans} constraint above ensures that requirements (P2) and (P5) are satisfied.
+The \CD{NoTrans} constraint above ensures that requirements P2 and P5 are satisfied.
 It says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}.
@@
 (1) traffic for the prefix block allocated to each top-of-rack router must be able to reach that router,
-(2) local services must not leak outside the datacenter, and
+(2) local services must not leak outside the data center, and
 (3) aggregation must be performed on global prefixes to reduce churn
@@
 back on itself. This means traffic for
-\CD{PG*} may be sent either from other routers in the datacenter, or
+\CD{PG*} may be sent either from other routers in the data center, or
 from external ASes. The second line ensures that traffic for local

### 2016-01-29 paper/compilation.tex
moving extra sections to appendix

@@
 Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
-
-\subsection{Aggregation-Induced Black Holes}
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=\columnwidth]{figures/aggregation}
-\caption{Aggregation safety.}
-\label{fig:aggregation-safety}
-\end{figure}
-
-As demonstrated with Example 2 in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur.
-Deciding when this can happen requires knowledge of the routing policy and not just the topology.
-For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated, even if there are several available in the toplogy.
-If that link fails, a black hole might be introduced.
-Fortunately, the PGIR captures the information about both the policy and topology precisely.
-%, describing the how information meeting the policy flows over the topology.
-
-We frame the aggregation problem as a problem of connectivity in the PGIR.
-Specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures that would disconnect where the prefix originates from where its more specific aggregate is located.
-The difficulty is that the same links in the topology can appear in multiple places in the PGIR.
-We adopt the following simple strategy to lower bound the number of failures: $i)$ Pick a random start-to-end path in PGIR, $ii)$ remove all edges in the PGIR for the set of topological edges chosen, and $iii)$ repeat until no such path exists.
-The number of PGIR paths that we are able to remove is a lower bound on the number of failures required to disconnect the prefix from its aggregate.
-
-For example, imagine we use the data center example from \S\ref{sec:motivation}, with the policy: 
-\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
-Figure~\ref{fig:aggregation-safety} shows the network topology and a simplified PGIR.
-Since the compiler knows an aggregate will be placed at $X$, and it knows that, the route for \CD{PG1} will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
-We could remove the $A$--$D$--$X$ path first.
-We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR, though in this case there are none.
-Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
-Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}.
-This process is repeated for other aggregation locations (e.g., $Y$).
-
-\subsection{Formal Properties}
-
-\newtheorem{prop}{Proposition}[section]
-
-%Here we investigate the correctness and expressiveness properties of \sysname.
-We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures?
-(2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?
-
-If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario.
-We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges.
-We argue that \sysname is correct by breaking down the claim:
-
-\begin{prop}
-BGP configurations produced by \sysname are \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.
-\end{prop}
-%
-%The Soundness claim follows directly from compilation of the product graph.
-Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations are Sound.
-%
-\begin{prop}
-BGP configurations produced by \sysname are \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
-\end{prop}
-%
-%The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.
-This means there is a valid path in the product graph corresponding to this path, and which is available in the network.
-%Assume we are unable to achieve this route in the network.
-To not achieve this path means that some router along the advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead.
-This implies that router that makes the ``wrong'' choice appears as a separate node in the product graph.
-However, from our failure safety check, we know that the other, more-preferred node must have a superset of the paths to accepting states as the less preferred node (from which it stole the route) for at least as good of a final preference.
-The argument then proceeds by induction on the path length - there are only a finite number of such stealings that can occur, each of which will ultimately still result in a route advertisement reaching $X$ along a most preferred path.
-%
-%Any \sysname-compiled policy will be \textit{Complete} as a result of the failure safety check.
-%
-\begin{prop}
-BGP configurations for internal routers produced by \sysname will be stable. 
-\end{prop}
-%
-The combination of Soundness and Completeness ensures that the distributed implementation will always send traffic along the best paths possible, yet will also never also use any undesired paths.
-These properties rely on the fact that \sysname produces stable BGP configurations:
-%
-%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo} for stable BGP.
-In particular, any policy with a dispute wheel will not pass the stronger failure safety check by \sysname.
-%
-%\begin{figure}[t!]
-%\includegraphics[width=\columnwidth]{figures/dispute-wheel}
-%\label{fig:dispute-wheel}
-%\caption{Product graph for a dispute wheel.}
-%\end{figure}
-%
-%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}.
-If a set of BGP configurations do not have a dispute wheel, then they will converge to their best routes.
-Any BGP policy with a dispute wheel will not satisfy the failure safety condition in Section~\ref{sec:compilation}.
-Assume that the preferences in the policy describe a dispute wheel, and we will show that our failure check will reject the policy.
-Informally, a dispute wheel occurs when there are some number of nodes $u_1, \dots, u_n$ attempting to get a path to a destination node $d$.
-Each node $u_i$ prefers to go through its neighbor $u_{i+1}$ over route $R_i$ than directly to $d$ with route $Q_i$.
-Thus the nodes form a wheel of preferences.
-The product graph for a policy that contains a dispute wheel will look like Figure~\ref{fig:dispute-wheel}, which shows a dispute wheel of size 3.
-In order to pass the failure safety check for the compiler, the more-preferred node for $u_2$ will need to have a superset of the paths starting from the less-preferred node for $u_2$.
-In turn, this means that the maximum length path after visiting the more preferred $u_2$ will be $max(Z) = 1 + max(Y)$, similarly, if we look at $u_1$, we will determine that $max(Y) = 1 + max(X)$, and so on.
-The resulting equations define a system of unsatisfiable equations.
-Therefore, it is not possible for \sysname to compile a BGP policy that contains a dispute wheel.
-Since no-dispute-wheel is a sufficient condition for BGP stability, any compiled \sysname policy will be stable.
-%
-An important distinction is that BGP might still be instable with respect to other external ASes, since \sysname has no way of configuring their routing policy and can only rely on AS path filters to see what advertisements are observed.

### 2016-01-29 paper/introduction.tex
moving extra sections to appendix

@@
 \emph{inter}-domain routes.  
-This means that existing inter-domain routing protocols and their associated configuration difficulties will be around for the forseeable future.
-\ryan{I added this. Is it true? what about SDX?}
-\todd{What is the impact of these
-  languages not supporting inter-domain routing?  How are those
-  policies expressed instead in an SDN context?  A sentence on the
-  impact would help.}  
 Second, centralized control planes

### 2016-01-29 paper/appendix.tex
adding appendix

--- 2016-01-27 paper/theory.tex
@@
-\section{Theory}
+\section*{Appendix}
+\label{sec:appendix}
+
+\renewcommand\thesubsection{\Alph{subsection}}
+
+\subsection{Aggregation-Induced Black Holes}
+\label{sec:black-holes}
+
+As demonstrated with Example 2 in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur.
+Deciding when this can happen requires knowledge of the routing policy and not just the topology.
+For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated, even if there are several available in the toplogy.
+If that link fails, a black hole might be introduced.
+Fortunately, the PGIR captures the information about both the policy and topology precisely.
+%, describing the how information meeting the policy flows over the topology.
+
+We frame the aggregation problem as a problem of connectivity in the PGIR.
+Specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures that would disconnect where the prefix originates from where its more specific aggregate is located.
+The difficulty is that the same links in the topology can appear in multiple places in the PGIR.
+We adopt the following simple strategy to lower bound the number of failures: $i)$ Pick a random start-to-end path in PGIR, $ii)$ remove all edges in the PGIR for the set of topological edges chosen, and $iii)$ repeat until no such path exists.
+The number of PGIR paths that we are able to remove is a lower bound on the number of failures required to disconnect the prefix from its aggregate.
+
+For example, imagine we use the data center example from \S\ref{sec:motivation}, with the policy: 
+\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
+Figure~\ref{fig:aggregation-safety} shows the network topology and a simplified PGIR.
+Since the compiler knows an aggregate will be placed at $X$, and it knows that, the route for \CD{PG1} will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
+We could remove the $A$--$D$--$X$ path first.
+We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR, though in this case there are none.
+Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
+Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}.
+This process is repeated for other aggregation locations (e.g., $Y$).
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=\columnwidth]{figures/aggregation}
+\caption{Aggregation safety.}
+\label{fig:aggregation-safety}
+\end{figure}
+
+\subsection{Propane Properties}
 
@@
 We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges.
-We argue that \sysname is correct by breaking down the claim into two distinct parts:
+We argue that \sysname is correct by breaking down the claim:
 
 \begin{prop}
-A distributed BGP configuration is \textit{Sound} with respect to a \sysname policy, if the any route traffic takes in the network, is a valid route specified in the policy.
+BGP configurations produced by \sysname are \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.
 \end{prop}
-
-The Soundness claim follows directly from compilation of the product graph.
+%
+%The Soundness claim follows directly from compilation of the product graph.
 Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations are Sound.
-
+%
 \begin{prop}
-A distributed BGP configuration is \textit{Complete} with respect to a \sysname policy, if the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
+BGP configurations produced by \sysname are \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
 \end{prop}
-
+%
 %The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.
@@
 The argument then proceeds by induction on the path length - there are only a finite number of such stealings that can occur, each of which will ultimately still result in a route advertisement reaching $X$ along a most preferred path.
-
-Any \sysname-compiled policy will be \textit{Complete} as a result of the failure safety check.
 %
-The combination of Soundness and Completeness ensures that the distributed implementation will always achieve the best routes possible, yet will never also use any unwanted routes.
-
+%Any \sysname-compiled policy will be \textit{Complete} as a result of the failure safety check.
+%
 \begin{prop}
-The internal routers in a distributed BGP configuration produced by \sysname will be stable. 
+BGP configurations for internal routers produced by \sysname will be stable. 
 \end{prop}
-
-The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo} for stable BGP.
+%
+The combination of Soundness and Completeness ensures that the distributed implementation will always send traffic along the best paths possible, yet will also never also use any undesired paths.
+These properties rely on the fact that \sysname produces stable BGP configurations:
+%
+%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo} for stable BGP.
 In particular, any policy with a dispute wheel will not pass the stronger failure safety check by \sysname.
-
+%
 %\begin{figure}[t!]

### 2016-01-29 paper/compilation.tex
adding appendix

@@
 
+\para{Aggregation Failures}
+Because the \sysname compiler has the complete user policy and topology, it is also able to efficiently ensure that user-specified aggregates do not black hole traffic for up to $k$ failures, where $k$ is specified by the user.
+The algorithm for aggregation failure safety is detailed in Section~\ref{sec:black-holes} of the appendix.
 \subsection{Abstract BGP}

### 2016-01-29 paper/implementation.tex
adding appendix

@@
 We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code.
-The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-sepcified aggregates.
+The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates.
 Users only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}.

### 2016-01-29 paper/compilation.tex
shrinking space after images
more space savings

--- 2016-01-29 paper/compilation.tex
@@
   \label{fig:pipeline}
+  \vspace{-1em}
 \end{figure}
@@
   \label{fig:rir-syntax}
+  \vspace{-1em}
 \end{figure*}
@@
   \label{fig:example-compilation}
+  \vspace{-1em}
 \end{figure*}
@@
 
-The checks for failure safety described above overlook one critical point: Paths for a higher preference might not actually exist due to loops.
-To avoid this situation, the compiler conservatively checks that, when node $x$ protects against failures for node $y$, its does so without using any nodes that shadow another node that appears ``above'' $x$ in the PGIR.
+The checks for failure safety described above overlook one critical point: Paths for a higher preference might not exist due to loops.
+To avoid this situation, the compiler checks that, when node $x$ protects against failures for node $y$, its does so without using any nodes that shadow another node that appears ``above'' $x$ in the PGIR.
 %It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
@@
 
+\para{Aggregation-Induced Black Holes}
+Because the \sysname compiler has the complete user policy and topology, it is also able to efficiently check that user-specified aggregates do not black hole traffic for up to $k$ failures, where $k$ is specified by the user.
+The algorithm for aggregation failure safety is detailed in Section~\ref{sec:black-holes} of the appendix.
 \subsection{Abstract BGP}
@@
       Export \COMM \Arrow (-,2), \PEER \Arrow C
-\end{code}\vspace{-.5cm}
+  \end{code}
+  \vspace{-2em} 
   \caption{Abstract BGP router configurations. \label{fig:abgp-config}}
+  \vspace{-1em}
 \end{figure}

### 2016-01-29 paper/evaluation.tex
adding appendix
shrinking space after images
more space savings

@@
 Our mains goals are to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
+
+\begin{figure}
+  \subcaptionbox{Data center}
+    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-dc.png}}
+  \subcaptionbox{Backbone network}
+    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
+  \caption{Compilation time. \label{fig:compilation-times}}
+  \vspace{-1em}
+\end{figure}
 
@@
 
-\begin{figure}
-  \subcaptionbox{Data center}
-    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-dc.png}}
-  \subcaptionbox{Backbone network}
-    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
-  \caption{Compilation time. \label{fig:compilation-times}}
-\end{figure}
-
 \subsection{Expressiveness}
@@
   \caption{Configuration minimization. \label{fig:config-min}}
+  \vspace{-1em}
 \end{figure}
@@
 Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes.
-For both policies, we measure the mean compilation time per prefix since the \sysname compiler can compile for each prefix independently, and in parallel.
+For both policies, we measure the mean compilation time per prefix since the compiler operates on each prefix in parallel.
 At their largest sizes, the per-prefix compilation time is roughly 10 seconds for the data center network and 45 seconds for the backbone network.
@@
 
-$i)$ operators used the no-export community to prevent routes from leaking beyond a certain tier of the datacenter topology, whereas \sysname selectively imported the route only below a certain tier;
+$i)$ operators used the no-export community to prevent routes from leaking beyond a certain tier of the datacenter, while \sysname selectively imported the route only below the tier;
 %\sysname could use a similar implementation mechanism in the future as an optimization.

### 2016-01-29 paper/motivation.tex
shrinking space after images
more space savings

@@
   \label{fig:example1}
+  \vspace{-1em}
 \end{figure}
@@
 \CD{Cust}-facing interface should be lower than that at
-\CD{R1}. % Implementing P2 properly will require MEDs to be
-% appropriately configured. 
-\todd{I commented out the sentence about MEDs for P2, because the next
-  two sentences seem to be about P2 instead of P3 and P4, which it
-  originally said.  Please check}  To implement P2, the operators can assign communities that
+\CD{R1}. Implementing P3 properly will require MEDs to be appropriately configured. 
+To implement P2, the operators can assign communities that
 indicate where a certain routing announcement entered the
@@
   \label{fig:example2}
+  \vspace{-1em}
 \end{figure}

### 2016-01-29 paper/evaluation.tex
more space savings

@@
 Figure~\ref{fig:config-min} shows the size of the configuration generated by \sysname, again as a function of network size.
-The naive translation of PGIR to ABGP generates extremely large ABGP policies.
+The naive translation of PGIR to ABGP generates large ABGP policies.
 To offset this, the compiler performs configuration minimization both during and after configuration generation.
 %Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
-The figure shows the minimization is highly effective for the data center and backbone policies.
-In all cases, minimized policies are only a small fraction of the size of their non-minimized counterparts.
+The figure shows that minimization is highly effective for both the data center and backbone policies.
+In all cases, minimized policies are a small fraction of the size of their non-minimized counterparts.
 

### 2016-01-29 paper/appendix.tex
shrinking space after images
more space savings

@@
   \label{fig:aggregation-safety}
+  \vspace{-1em}
 \end{figure}
@@
 %
-The combination of Soundness and Completeness ensures that the distributed implementation will always send traffic along the best paths possible, yet will also never also use any undesired paths.
+
+%The combination of Soundness and Completeness ensures that the distributed implementation will always send traffic along the best paths possible, yet will also never also use any undesired paths.
 These properties rely on the fact that \sysname produces stable BGP configurations:
+
 %
@@
 %
-An important distinction is that BGP might still be instable with respect to other external ASes, since \sysname has no way of configuring their routing policy and can only rely on AS path filters to see what advertisements are observed.
+
+%An important distinction is that BGP might still be instable with respect to other external ASes, since \sysname has no way of configuring their routing policy and can only rely on AS path filters to see what advertisements are observed.

### 2016-01-29 paper/compilation.tex
more space savings

@@
 \para{Aggregation-Induced Black Holes}
-Because the \sysname compiler has the complete user policy and topology, it is also able to efficiently check that user-specified aggregates do not black hole traffic for up to $k$ failures, where $k$ is specified by the user.
+Because the \sysname compiler has the complete user policy and topology, it is also able to efficiently check that aggregates do not black hole traffic for up to $k$ failures.
 The algorithm for aggregation failure safety is detailed in Section~\ref{sec:black-holes} of the appendix.

### 2016-01-29 paper/evaluation.tex
more space savings

@@
 
-Figure~\ref{fig:config-min} shows the size of the configuration generated by \sysname, again as a function of network size.
+Figure~\ref{fig:config-min} shows the size of the compiled ABGP policies as a function of network size.
 The naive translation of PGIR to ABGP generates large ABGP policies.
-To offset this, the compiler performs configuration minimization both during and after configuration generation.
+To offset this, the compiler performs configuration minimization both both during and after the PGIR to ABGP translation.
 %Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
-The figure shows that minimization is highly effective for both the data center and backbone policies.
-In all cases, minimized policies are a small fraction of the size of their non-minimized counterparts.
+Minimization is highly effective for both the data center and backbone policies. In all cases, minimized policies are a small fraction of the size of their non-minimized counterparts.
 

### 2016-01-29 paper/implementation.tex
more space savings

@@
 We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code.
+Users of \sysname only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}.
 The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates.
-Users only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}.
+Since each prefix is specified separately, the \sysname compiler is able to operate over each per-prefix routing policy in parallel.
 

### 2016-01-29 paper/appendix.tex
adding small part in intro about verification

@@
 
-If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario.
+%If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario.
 We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges.

### 2016-01-29 paper/introduction.tex
adding small part in intro about verification

@@
 manually decompose policies into device-level behaviors.
+
+Verification tools for network configurations~\cite{batfish} have been developed as a complimentary approach for reducing misconfigurations by checking that the low-level configurations match high-level operator intent.
+However, existing verification tools have their drawbacks: like templates, they do not help operators come up with the configuration in the first place, and moreover, they can only check correctness under concrete environment and failure scenarios, rather than under all possible environments and failure scenarios.
 

### 2016-01-29 paper/evaluation.tex
more ediiiiiiiitsssss

@@
 
-\subsection{Expressiveness}
-
-We found that we could translate all network policies to \sysname.
-We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname.
-The data center operator said that he found the language intuitive.
-The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{x}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We found that the data center policies were correctly translated.
-For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.
-
-Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.
-
 \begin{figure}
@@
 \end{figure}
+
+\subsection{Expressiveness}
+
+We found that we could translate all network policies to \sysname.
+We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname.
+The data center operator said that he found the language intuitive.
+The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We found that the data center policies were correctly translated.
+For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.
+
+Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.
 

### 2016-01-29 paper/propane.tex
more space savings
more ediiiiiiiitsssss

@@
 Policies for (distributed) control planes differ from data-plane
-policies~\cite{x,y,z} in a few important ways. First, control-plane
-policies must account for all failures at specification time; there is
+policies in a few important ways. First, control-plane
+policies must account for all failures at compile time; there is
 no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
@@
 In the rest of this section, we define \sysname policies for the two 
-examples described in the previous section, introducing key aspects of
+examples from the previous section, introducing key aspects of
 the \sysname language along the way. The complete syntax of the
@@
 \begin{code}
-\Define Routing = \{
-     PCust \Path ExitCust \Prefer \End(Cust)
+\Define Routing = 
+    \{PCust \Path ExitCust \Prefer \End(Cust)
      PInt  \Path \End(\In)
-     \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)
-\}
+     \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)\}
 \end{code}
@@
 \begin{code}
-\Define Ownership = \{
-    PG1 \Path \End(A)
+\Define Ownership = 
+    \{PG1 \Path \End(A)
      PG2 \Path \End(B)
      PL1 \Path \End(E)
-    PL2 \Path \End(F)
-\}
+     PL2 \Path \End(F)\}
 \end{code}
@@
 \begin{code}
-\Define Routing = \{
-    PG1 \OR PG2 \Path \Any
+\Define Routing = 
+    \{PG1 \OR PG2 \Path \Any
      PL1 \OR PL2 \Path \NOT{}\Enter(\Out)
-    \True      \Path \Exit(\Out)
-\}
+     \True      \Path \Exit(\Out)\}
 \end{code}

### 2016-01-29 paper/evaluation.tex
force page size

@@
 
-$ii)$ operators prevented unneeded propagation of more-specific route announcements from a neighboring AS based on their out-of-band knowledge about topology, whereas \sysname propagated these advertisements; and
+$ii)$ operators prevented unneeded propagation of more-specific route announcements from a neighboring AS based on their out-of-band knowledge about the topology, whereas \sysname propagated these advertisements; and
 

### 2016-01-29 paper/related.tex
intro and labels to sections
more edits. bring back conclusion
more ediiiiiiiitsssss
force page size

@@
 \section{Related Work}
+\label{sec:related}
 
-%\begin{itemize}
-%	\item Regular path queries
-%	\item Lots of background on BGP
-%	\item Feamster rcc stuff
-%	\item Logic programming BGP configs
-%\end{itemize}
-
-\dpw{We could also consider citing Boon's stuff on declarative routing.}
-
-Our work builds on three themes of prior work.
-
-\paragraph*{SDN Programming Languages}
+\paragraph*{SDN Languages}
 \sysname{} was heavily influenced by recent SDN programming
-languages such as Merlin~\cite{foster:merlin}, FatTire~\cite{fattire},
-NetKAT~\cite{netkat}, as well as path queries~\cite{queries}.
+languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire}, 
+as well as path queries~\cite{queries}.
 Each of these languages is oriented around regular expressions, which

### 2016-01-29 paper/introduction.tex
typo fix

@@
 
-Verification tools for network configurations~\cite{batfish} have been developed as a complimentary approach for reducing misconfigurations by checking that the low-level configurations match high-level operator intent.
+Verification tools for network configurations~\cite{batfish} have been developed as a complementary approach for reducing misconfigurations by checking that the low-level configurations match high-level operator intent.
 However, existing verification tools have their drawbacks: like templates, they do not help operators come up with the configuration in the first place, and moreover, they can only check correctness under concrete environment and failure scenarios, rather than under all possible environments and failure scenarios.

### 2016-01-29 paper/compilation.tex
minor changes ... ryan, see my email

@@
 Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ consists of all all abstraction locations (routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+The alphabet $\Sigma$ consists of all abstraction locations (routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
 %
@@
 a unique ending vertex $e$,
-and a preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
+and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
 For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. 
@@
 %
-Finally, there is an edge from each node in the PGIR such that $P(v) \neq \emptyset$ to the special end node $e$.
+Finally, there is an edge from each node in the PGIR such that $P(v) \neq \emptyset$ to the special end node $e$.  This product construction is a variation on
+the construction used in Merlin~\cite{foster:merlin}, extended to manage
+preferences.
 

### 2016-01-29 paper/compilation.tex
minor fixes.

--- 2016-01-29 paper/compilation.tex
@@
 
-  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^* \cdot \Out)$.}
+  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
   \label{fig:example-compilation}
@@
 For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. 
-A node $x$ shadows node $y$ in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$.
-That is, $x$ shadows $y$ when they are different nodes in the PGIR that represent the same topology location.
+Two nodes $x$ and $y$ \emph{shadow} each other in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$.
+That is, $x$ and $y$ shadow each other when they are different nodes in the PGIR that represent the same topology location.
 
@@
 %
-$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^* \cdot \Out)$$
+$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$$
 %
@@
 %
-The ``--" state indicates it is dropped from the corresponding automaton. Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates this path has preference 1.
+The ``--" state indicates the corresponding automaton can not accept the current path or any extension of it.
+Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates this path has preference 1.
 

### 2016-01-29 paper/compilation.tex
change failure safety wording.

--- 2016-01-29 paper/compilation.tex
@@
 %
-It often simplifies the failure-safety analysis to eliminate cases that are not possible due to loops. 
+It often improves the precision of the failure-safety analysis to eliminate cases that are not possible due to loops. 
 %For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
@@
 In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading to $y$ from the start node.
-Many efficient algorithms exist for finding graph dominators in practice~\cite{linear-dominance, fast-dominance, tarjan-dominance}.
 %We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 

### 2016-01-29 paper/related.tex
shorten configassure related work

@@
 with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
-and the compiler will generate appropriate
-OpenFlow rules.  \sysname is more
-expressive as it allows users to specify preferences among
-paths and it automatically generates distributed
-implementations that tolerate
-any number of faults.  Because FatTire generates data plane rules up front,
-before faults occur, specifying higher levels of fault tolerance comes
-at the cost of generating additional rules that tax switch
-memory.  In contrast, \sysname uses traditional distributed
-control plane mechanisms to react to faults, which do not impose
-additional memory cost.
+and the compiler will generate appropriate OpenFlow rules.
+\sysname is more expressive as it allows users to specify preferences among
+paths and it generates distributed implementations that tolerate any number of faults. 
+Because FatTire generates data plane rules up front, 
+specifying higher levels of fault tolerance comes
+at the cost of generating additional rules that tax switch memory.  
+In contrast, \sysname uses traditional distributed
+control plane mechanisms to react to faults, which do not impose additional memory cost.
 Because of the differences in the underlying technology, the analyses
@@
 well, unlike any existing SDN language.
+
+\paragraph{}
 
@@
 collection of tuples over constants and configuration variables, and a
-\emph{requirement}, which is a set of constraints.  For instance, the
-tuple \texttt{hsrp(rexa,rA1,int(1),int(2))} states that interface
-\texttt{rA1} on device \texttt{rexa} belongs to the HSRP group defined
-by configuration variable \texttt{int(1)} with virtual IP address
-defined by configuration variable \texttt{int(2)}.  The constraint
-\texttt{hsrp\_subnet([rexa-rA1,rexb-rB1])} states that a database
-contains tuples defining HSRP group identifiers and virtual IPs for
-interfaces \texttt{rA1} and \texttt{rB1} on devices \texttt{rexa} and
-\texttt{rexb}.  The authors use a combination of logic programming and
-SAT solving to find concrete values for configuration variables such
-as \texttt{int(1)}.  ConfigAssure handles
-configuration for a wide range of protocols and many
+\emph{requirement}, which is a set of constraints.  
+%For instance, the tuple \texttt{hsrp(rexa,rA1,int(1),int(2))} states that interface
+%\texttt{rA1} on device \texttt{rexa} belongs to the HSRP group defined
+%by configuration variable \texttt{int(1)} with virtual IP address
+%defined by configuration variable \texttt{int(2)}.  The constraint
+%\texttt{hsrp\_subnet([rexa-rA1,rexb-rB1])} states that a database
+%contains tuples defining HSRP group identifiers and virtual IPs for
+%interfaces \texttt{rA1} and \texttt{rB1} on devices \texttt{rexa} and
+%\texttt{rexb}.  
+The authors use a combination of logic programming and
+SAT solving to find concrete values for configuration variables.
+%such as \texttt{int(1)}.  
+ConfigAssure handles configuration for a wide range of protocols and many
 different concerns.  In contrast, the scope of \sysname is much
@@
 firewall configurations~\cite{fang,lumeta,margrave} and
-BGP configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe} and reporting errors or
-inconsistencies when they are detected.
+BGP configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe} and reporting errors or inconsistencies when they are detected.
 Our research is complementary to these analysis

### 2016-01-29 paper/introduction.tex
pass over abstract/intro

--- 2016-01-29 paper/introduction.tex
@@
 
-It is well known that network configuration is highly error
-prone and that such errors can lead to costly network
-downtime~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish}.
+It is well known that configuring networks is error
+prone and such errors can lead to disruptive network
+downtimes~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
 For instance, a recent misconfiguration led to an hour-long, nation-wide outage for Time Warner's backbone network~\cite{time-warner}; and a major BGP-related incident makes international news every few months~\cite{bgpmon}.
@@
 semantic mismatch between the intended high-level
-policies and the low-level configurations.  In particular,
-many policies involve network-wide properties---prefer a certain neighbor,
+policies and the low-level configurations.  
+Many policies involve network-wide properties---prefer a certain neighbor,
 never announce a particular destination externally,
@@
 Operators therefore must manually decompose network-wide policy into
-device-level behaviors, such that the distributed interactions among
-these devices satisfy the high-level objectives.
+device behaviors, such that policy-compliant behavior results from the distributed interactions of
+these devices.
 %
-Further, policy-compliance must be ensured not only under normal network
-circumstances but also in the face of failures.  The need to reason
-about possible failures exacerbates an already considerable challenge
+Policy-compliance must be ensured not only under normal 
+circumstances but also during failures.  The need to reason
+about possible failures exacerbates the challenge
 for network operators.  As a result, configurations that work
@@
 While templates help ensure certain kinds of consistency across devices,
-they do not bridge the
-semantic divide between network-wide policies and device-level configuration.
-They do not provide fundamentally different abstractions
-from existing configuration languages and so still require operators to
-manually decompose policies into device-level behaviors.
+they do not provide fundamentally different abstractions from existing configuration languages 
+or bridge the semantic divide between network-wide policies and device-level configuration. 
+%They do not provide fundamentally different abstractions
+%from existing configuration languages and 
+Thus, they still require operators to
+manually decompose policies into device behaviors.
+
+Configuration analysis tools~\cite{batfish,feamster+:rcc} have been developed as a complementary approach for reducing misconfigurations by checking that the low-level configurations match high-level operator intent.
+However, such tools cannot help operators come up with the configuration in the first place.
+Further, today's tools can only check correctness under concrete failure scenarios, rather than under all possible failures.
 
@@
 community's response to the difficulty of maintaining policy
-compliance through distributed interaction of individual
-devices~\cite{ethane}. Indeed, instead of organizing networks
+compliance through distributed device interactions~\cite{ethane}. Indeed, instead of organizing networks
 around a distributed collection of devices that compute forwarding tables through
@@
 The centralized control planes of SDN, however, are not a panacea.
-First, while many SDN systems provide effective \emph{intra}-domain routing
+First, while many SDN programming systems~\cite{sdn-languages} provide effective \emph{intra}-domain routing
 abstractions, letting users specify paths within their network,
-they fail to provide a coherent means to specify preferred
-\emph{inter}-domain routes.  
+they fail to provide a coherent means to specify \emph{inter}-domain routes.
 Second, centralized control planes
-require careful design and engineering to be robust to failures---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure.
-Even ignoring failures, it is necessary for controller systems to
-scale to meet the demands of large, geographically distributed networks,
+require careful design and engineering to be robust to failures---one must ensure that all devices can communicate with the controller at all times, even under arbitrary failure combinations.
+Even ignoring failures, it is necessary for the control system to
+scale to meet the demands of large or geographically-distributed networks,
 and to react quickly
-to a changing environment. To address this challenge, researchers are exploring
+to environmental changes. For this challenge, researchers are exploring
 multi-controller systems with interacting controllers, thus bringing back distributed
@@
 NetKAT~\cite{netkat}.  However, our design also contains several key
-departures from existing languages.  The most important difference is semantic:  the paths specified
+departures from existing languages.  The most important one is semantic:  the paths specified
 by programmers can extend from outside the operator's network to inside
@@
 algorithms that translate the regular policies to a graph-based
-intermediate language and from there to BGP configurations, including
-per-device import and export filters, local preferences, MED attributes, and community tags.
+intermediate language and from there to per-device BGP configurations, which include various filters and preferences that govern BGP behavior.
+%import and export filters, local preferences, MED attributes, and community tags.
 We target BGP for pragmatic reasons: it is an industry

### 2016-01-29 paper/related.tex
added to related work

@@
 
-\paragraph{}
+\paragraph*{Configuration Automation}
+Many practitioners use configuration templates~\cite{hatch,thwack}, to ensure certain kinds of consistency across similar devices.
+In addition, configuration languages such as RPSL~\cite{RFC2622}, Yang~\cite{RFC6020}, and Netconf~\cite{RFC6241} allow operators to express routing policy in a vendor-neutral way.
+However, all of these solutions remain low-level, for example, requiring operators to specify exact local preferences.
+Unlike \sysname, there is no guarantee that these low-level configurations satisfy the original, high-level intent.
+
+\paragraph*{Configuration Analysis}  
+The notion that configuring network devices is difficult and error-prone is not new.  
+Past researchers have tried to tackle this problem by analyzing existing
+firewall configurations~\cite{fang,lumeta,margrave} and
+BGP configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe} and reporting errors or inconsistencies when they are detected.
+Our research is complementary to these analysis
+efforts.  We hope to eliminate bugs by using higher-level
+languages and a ``correct-by-construction''
+methodology.  By proposing network administrators write configurations
+at a high-level of abstraction, a whole host of low-level errors can be avoided.
 
@@
 
-\paragraph*{Configuration Analysis}  The notion that
-configuring network devices is difficult and error-prone is not new.  Past
-researchers have
-tried to tackle this problem by analyzing existing
-firewall configurations~\cite{fang,lumeta,margrave} and
-BGP configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe} and reporting errors or inconsistencies when they are detected.
-Our research is complementary to these analysis
-efforts.  We hope to eliminate bugs by using higher-level
-languages and a ``correct-by-construction''
-methodology.  By proposing network administrators write configurations
-at a high-level of abstraction, a whole host of low-level errors can be
-avoided.
-
 %We also believe the high-level, centralized nature of \sysname policies

### 2016-01-29 paper/compilation.tex
clarifying failure example

@@
 How could such a policy be implemented in BGP?
-Suppose we simply set the local preference at router $C$ to prefer $D$ over $E$.
-However, now if the A -- C link fails, then suddenly $C$ has made the wrong decision and can not get either the primary or backup route specified, despite the fact that the $W \cdot B \cdot C \cdot E$ path is available in the network.
+Suppose we set the local preference at router $C$ to prefer $D$ over $E$, and use the BGP MED attribute to influence $W$ to prefer $A$ over $B$.
+This might work as expected under normal conditions, however, if the A -- C link fails, then suddenly $C$ has made the wrong decision.
+Traffic will now follow the
+$W \cdot B \cdot C \cdot D$ path, even though this was path was not specified by the policy.
+This is a violation of \emph{Soundness}: The distributed implementation has used a route not specified by the policy.
+To make matters worse, the second preference $W \cdot B \cdot C \cdot E$ is available in the network but not being used.
+This is a violation of \emph{Completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
+We could solve the first problem by placing a filter at router $B$ to prevent using a path that goes through $D$, but we can not help with the second problem: $C$ has made the wrong choice.
+
+%and can not get either the primary or backup route specified, despite the fact that the $W \cdot B \cdot C \cdot E$ path is available in the network.
 

### 2016-01-29 paper/compilation.tex
typo

@@
 Traffic will now follow the
-$W \cdot B \cdot C \cdot D$ path, even though this was path was not specified by the policy.
-This is a violation of \emph{Soundness}: The distributed implementation has used a route not specified by the policy.
+$W \cdot B \cdot C \cdot D$ path, even though this path was not specified by the policy.
+This is a violation of \emph{soundness}: The distributed implementation has used a route not specified by the policy.
 To make matters worse, the second preference $W \cdot B \cdot C \cdot E$ is available in the network but not being used.
-This is a violation of \emph{Completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
-We could solve the first problem by placing a filter at router $B$ to prevent using a path that goes through $D$, but we can not help with the second problem: $C$ has made the wrong choice.
+This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
+We could solve the first problem by placing routes that go through $D$ at $B$, however, we can not fix the second problem---$C$ has made the wrong choice.
+In fact, this policy can not be implemented in BGP in a way that is policy compliant under all failures.
 
@@
 where \textit{protect} means that, from $N_1$ on the product graph restricted to nodes that can potentially achieve preference $j$ or better, 
-there is always a path to each each ending location whenever this is a path from $N_2$ restricted to $G_i$.
+there is always a path to each ending location whenever this is a path from $N_2$ restricted to $G_i$.
 

### 2016-01-29 paper/compilation.tex
changes to failure description

@@
 where \textit{protect} means that, from $N_1$ on the product graph restricted to nodes that can potentially achieve preference $j$ or better, 
-there is always a path to each ending location whenever this is a path from $N_2$ restricted to $G_i$.
+there is always a path to each each ending location whenever this is a path from $N_2$ restricted to $G_i$.
 

### 2016-01-29 paper/compilation.tex
edits

--- 2016-01-29 paper/compilation.tex
@@
 
-Local preferences are now obtained by, for each router in the topology, sorting the corresponding PGIR nodes according to \textit{can prefer} relation.
-If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
+For each router in the topology, local preferences are now obtained by  sorting the corresponding PGIR nodes according to the \textit{can prefer} relation.
+If two nodes are incomparable, the compiler rejects the policy as unimplementable.
 

### 2016-01-29 paper/introduction.tex
clarify under all failures in intro

@@
 %import and export filters, local preferences, MED attributes, and community tags.
-We target BGP for pragmatic reasons: it is an industry
-standard, and many networks use it internally as well as externally. Despite the advent of SDN, many networks will continue to
-use BGP for the foreseeable future due to existing infrastructure investments, the difficulty of transitioning to SDN,
-and the scalability and fault-tolerance advantages of a distributed
+We target BGP for pragmatic reasons: 
+it is a highly flexible routing protocol, 
+it is an industry standard, 
+and many networks use it internally as well as externally. 
+Despite the advent of SDN, many networks will continue to
+use BGP for the foreseeable future due to existing infrastructure investments, the difficulty of transitioning to SDN, and the scalability and fault-tolerance advantages of a distributed
 control plane.
@@
 The BGP configurations produced by our compiler are
-guaranteed to be policy compliant in the face of
-{\em arbitrary} failures.  In this way, we provide network operators
+guaranteed to be policy-compliant in the face of
+{\em arbitrary} failures. This does not mean that the implementation is always 
+able to send traffic to its ultimate destination 
+(\EG in the case of a network partition), but rather that always respects the 
+centralized policy, which may include dropping traffic when there is no route.
+%
+In this way, we provide network operators
 with a strong guarantee that is otherwise impossible to achieve
@@
 % and compared these specifications with existing configurations.
-We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds of routers.
+We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds of routers, compiling in under 9 minutes in all cases.
 

### 2016-01-29 paper/implementation.tex
more ediiiiiiiitsssss
more edits

@@
 The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates.
-Since each prefix is specified separately, the \sysname compiler is able to operate over each per-prefix routing policy in parallel.
+Finally, since each prefix has a separate routing policy, the \sysname compiler is able to compile each routing policy in parallel.
 
@@
 
-\para{PG Minimization}
+%\para{PG Minimization}
 
-The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\cite{fast-dominance}.
+%The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\cite{fast-dominance}.
 More complex algorithms with better theoretical complexity exist~\cite{linear-dominance, tarjan-dominance} and may be better suited for large enough topologies.

### 2016-01-29 paper/introduction.tex
more edits

@@
 able to send traffic to its ultimate destination 
-(\EG in the case of a network partition), but rather that always respects the 
+(\EG in the case of a network partition), but rather that it always respects the 
 centralized policy, which may include dropping traffic when there is no route.

### 2016-01-29 paper/motivation.tex
more space savings
added aggregation black hole reference
trimming

@@
 
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=\columnwidth]{figures/example1}
-  \caption{Creating router-level policies is difficult.}
-  \label{fig:example1}
-  \vspace{-1em}
-\end{figure}
-
 \subsection{Example 1:  The Backbone}
@@
 Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several neighbor- or prefix-based exceptions to the default behavior.
-For example, a large AS with many peers in different geographic locations may be faced with complex challenges like keeping traffic within national boundaries.
+A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
 Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually. 
@@
   \centering
-  \includegraphics[width=\columnwidth]{figures/example2}
-  \caption{Policy-compliance under failures is difficult.}
-  \label{fig:example2}
+  \includegraphics[width=\columnwidth]{figures/example1}
+  \caption{Creating router-level policies is difficult.}
+  \label{fig:example1}
   \vspace{-1em}
@@
 
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=\columnwidth]{figures/example2}
+  \caption{Policy-compliance under failures is difficult.}
+  \label{fig:example2}
+  \vspace{-1em}
+\end{figure}
+
 However, this implementation does not have the right behavior in the face of failures.
@@
 This guard can be implemented by $X$ and $Y$ rejecting paths through the other.
-But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{xx}.
+But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{route-aggregation}.
 If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce the \CD{PG} externally.

### 2016-01-29 paper/propane.tex
small changes to sec 4

@@
 network from the previous section, we first express the idea that for routes leading to our customer,
-we prefer using \CD{R1} over \CD{R2} (Policy P3 from Figure~\ref{fig:example1}):
+we prefer using \CD{R1} over \CD{R2} (policy P3 from Figure~\ref{fig:example1}):
 %\begin{lstlisting}[mathescape=true]
@@
 through either router \CD{R1} or \CD{R2}.  The paths that exit through \CD{R1}
-are preferred (\Prefer) to those that exit through \CD{R2}.
+are preferred (\Prefer) to those that exit through \CD{R2}.  As we
+describe in the next section, the \Exit\ predicate, as well as other
+path predicates used later in this section, is simply a shorthand for 
+a particular regular expression over paths that is expressible in our policy
+language.
 
@@
 
-Since routing allows transit traffic (\EG, traffic entering from
-\CD{Peer} and leaving through \CD{Prov}), we define a new policy to implement this restriction separately, using conjunction (\AND),
+Since by default routing allows transit traffic (\EG, traffic entering from
+\CD{Peer} and leaving through \CD{Prov}), we separately define a
+policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
 disjunction (\OR) and negation (\NOT) of constraints. 
@@
 \noindent
-The \CD{NoTrans} constraint above ensures that requirements P2 and P5 are satisfied.
-It says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}.
+The \CD{NoTrans} constraint above says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}.
 Similarly it prevents traffic from ever following paths that leave our network and later passing through both \CD{Prov} and \CD{Cust}.
@@
 
-As in the backbone example, we can combine these constraints
-logically to specify the network-wide policy.
+As in the backbone example, we can logically conjoin these constraints
+to specify the network-wide policy.
 However, in addition to constraints on the shape of paths,
@@
 
-As before, once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. \sysname also checks for safety against aggregation-induced black holes.
+As before, once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. \sysname also ensures safety against aggregation-induced black holes.
 %It can efficiently determine a lower bound on the number of failures necessary to black hole traffic given the user's policy, topology, and placement of specific aggregates.

### 2016-01-29 paper/evaluation.tex
typo

@@
 
-We obtain routing policy for the backbone network and for the data centers of a large cloud provider.
+We obtained routing policy for the backbone network and for the data centers of a large cloud provider.
 Multiple data centers share this policy.
@@
 
-From the break down of the time by compilation phase, we see that no single compilation phase dominates the running time of the compiler.
+%From the break down of the time by compilation phase, we see that no single compilation phase dominates the running time of the compiler.
 However, construction and minimization of the product graph take the most time.

### 2016-01-29 paper/compilation.tex
edit to 5.3 intro to cut mention of vendor specific config translation
clarify about our implementation

@@
 Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation.
-To make configurations more readable for human operators, and to reduce the size of the resulting configurations, the \sysname compiler makes several passes over the ABGP form.
-Finally, vendor-specific adaptors can translate from ABGP to concrete device configurations.
+Our current \sysname compiler produces ABGP configurations, however vendor-specific adaptors to translate from ABGP to concrete device configurations could easily be added.
 
@@
 
-The final stages of compilation translate policies from PGIR to a  vendor-neutral abstraction of BGP (ABGP) and then from ABGP to actual device configurations.
+The final stage of our compiler translates policies from PGIR to a vendor-neutral abstraction of BGP (ABGP).
+% and then from ABGP to actual device configurations.
 

### 2016-01-29 paper/compilation.tex
final edits from Jitu

@@
 
-To make configurations more compact and readable, the \sysname compiler makes several passes over the ABGP policy, removing community tagging and matching when possible, combining filters, removing dead filters, and so on.
+After configuration generation, the compiler further processes the ABGP policy to minimize it, removing community tagging and matching when possible, combining filters, removing dead filters, and so on.
 In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from.

### 2016-01-29 paper/propane.tex
final edits from Jitu

@@
 
-\sysname allows the operator to configure the network with the
-abstraction that he or she has centralized control over routing.
+\sysname allows operators to configure the network with the
+abstraction that they have centralized control over routing.
 Specifically, the operator simply provides a set of high-level constraints
@@
 The first line states that there is no restriction (\Any)
-on how traffic must
-traverse the network for global prefixes, aside from the default restriction
-that traffic must not pass through the user's network and then loop
-back on itself. This means traffic for
-\CD{PG*} may be sent either from other routers in the data center, or
+on how traffic must traverse the network for global prefixes.
+%aside from the default restriction
+%that traffic must not pass through the user's network and then loop
+%back on itself. 
+This means traffic for
+\CD{PG*} may be sent either from other data center routers or
 from external ASes. The second line ensures that traffic for local
@@
 guarantees that the services remain reachable only to locations
-internal to the data center.
+inside the data center.
 

### 2016-01-29 paper/evaluation.tex
making things look nicer

@@
 
-Figure~\ref{fig:config-min} shows the size of the compiled ABGP policies as a function of network size.
-The naive translation of PGIR to ABGP generates large ABGP policies.
-To offset this, the compiler performs configuration minimization both both during and after the PGIR to ABGP translation.
+Figure~\ref{fig:config-min} shows the size of the compiled ABGP policies as a function of the topology size.
+The naive translation of PGIR to ABGP outlined in \S\ref{sec:compilation} generates extremely large ABGP policies by default.
+To offset this, the compiler performs ABGP configuration minimization both during and after the PGIR to ABGP translation phase.
 %Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.

### 2016-01-29 paper/compilation.tex
adding information about us only compiling to ABGP to implementation

@@
 Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation.
-Our current \sysname compiler produces ABGP configurations, however vendor-specific adaptors to translate from ABGP to concrete device configurations could easily be added.
+Vendor-specific adaptors to translate from ABGP to concrete device configurations are easily added to generate concrete configurations.
 

### 2016-01-29 paper/implementation.tex
adding information about us only compiling to ABGP to implementation

@@
 We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code.
-Users of \sysname only ever see the high-level constraint-based language presented in Section~\ref{sec:motivation}.
-The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the commonly used no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates.
-Finally, since each prefix has a separate routing policy, the \sysname compiler is able to compile each routing policy in parallel.
+The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates.
+Since each prefix has a separate routing policy, the \sysname compiler is able to compile each routing policy in parallel.
+The current compiler produces only ABGP policies, which can be incorporated into an existing template-based system, for example by mixing the \sysname configuration with other configuration components, or by generating vendor-specific configurations.
 

### 2016-01-30 paper/compilation.tex
final edits

@@
      r       &::=& n & \textit{AS number} \\
+         &\BNFALT& \emptyset & \textit{empty set} \\
          &\BNFALT& \In & \textit{internal loc} \\
@@
     \Any           & = & \Out^* \cdot \In^+ \cdot \Out^* \\
+    \None          & = & \emptyset \\
     \Internal      & = & \In^+ \\
@@
 Figure~\ref{fig:rir-syntax} shows the RIR syntax.
-A policy consists of one or more constraints, each of which consists of a test on the type of route, and a corresponding set of preferred regular paths.
+A policy consists of one or more constraints, each of which have a test on the type of route, and a corresponding set of preferred regular paths.
 Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS.
 Special \In{} and \Out{} symbols refer to any internal or external location respectively.
-In addition, $\Sigma$ refers to any symbol, and hence $\Sigma^*$ is
-any sequence of symbols.  We also use other standard abbreviations
+In addition, $\Sigma$ refers to any symbol.
+We also use other standard abbreviations
 for regular expressions such as $r^+$, a sequence of one or more occurrences
@@
 $$(\min_i \set{ p \in \mathcal{L}(r_i) }, \abs{p})$$
-where the rank is lexicographically ordered according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the length of the path.
+where the rank is lexicographically ordered according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the path length.
 Lower ranks indicate \emph{more} preferred paths.
-Traffic may be sent along any of the most preferred paths for each pair of starting and ending locations that appear in some valid specified path.
+Traffic may be sent on any of the most preferred paths for each pair of starting and ending locations that appear in some specified path.
+There is an implicit lowest preference to drop traffic: $\emptyset$ when no other route is possible.
 
@@
 This is reflected in the product graph by the node with state $(X,1,1)$.
-From here, if X were to advertise this route to D, it would result in the path $D X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
+From here, if X were to advertise this route to D, it would result in the path $D \cdot X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
 %
@@
 
-Finally, in our example, the external AS $W$ should prefer our internal router $A$ over $B$.
+Finally, the external AS $W$ should prefer our internal router $A$ over $B$.
 In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
-In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the BGP MED attribute can influence $W$ to prefer $A$ over $B$.
+In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$.
 Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
-The compiler can perform a simple analysis to determine when it can utilize various BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
+The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
 %Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
@@
 
-After configuration generation, the compiler further processes the ABGP policy to minimize it, removing community tagging and matching when possible, combining filters, removing dead filters, and so on.
+After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
 In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from.

### 2016-01-30 paper/introduction.tex
final edits

@@
 departures from existing languages.  The most important one is semantic:  the paths specified 
-by programmers can extend from outside the operator's network to inside
+can extend from outside the operator's network to inside
 the network, across several devices internally, and then out again. This design
@@
 routes in the exact same way.
-%No SDN programming language provides similar facilities.
 In addition, we augment the algebra
@@
 the system guarantees that the distributed implementation will always use the highest-ranked ones.
+Although we target a distributed implementation, the language is more general and could potentially be used in an SDN context.
+
 %We also support network operators by defining a

### 2016-01-30 paper/introduction.tex
footnote

@@
 guaranteed to be policy-compliant in the face of
-{\em arbitrary} failures. This does not mean that the implementation is always 
+{\em arbitrary} failures.\footnote{The control plane of a network may use more than one routing protocol, e.g., an IGP in addition to BGP.
+We assume that these other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This does not mean that the implementation is always
 able to send traffic to its ultimate destination

### 2016-02-08 paper/introduction.tex

--- 2016-01-30 paper/introduction.tex
@@
 guaranteed to be policy-compliant in the face of
-{\em arbitrary} failures. This does not mean that the implementation is always 
+{\em arbitrary} failures.\footnote{In this paper we assume that BGP is the only control plane protocol running in the network or the other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This does not mean that the implementation is always
 able to send traffic to its ultimate destination

### 2016-04-03 paper/propane.tex
final edits
implemented export policy translation for quagga

@@
      PL1 \Path \End(E)
-     PL2 \Path \End(F)\}
+     PL2 \Path \End(F)
+     \True \Path \End(\Out)\}
 \end{code}
@@
 end at router \CD{B}; and so on.
+Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location.
 For the second constraint, we can define another policy:
@@
 \begin{code}
-\Define Routing = 
-    \{PG1 \OR PG2 \Path \Any
-     PL1 \OR PL2 \Path \NOT{}\Enter(\Out)
-     \True      \Path \Exit(\Out)\}
+\Define Locality = 
+    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
 \end{code}
 \noindent
-The first line states that there is no restriction (\Any)
-on how traffic must traverse the network for global prefixes.
+%The first line states that there is no restriction (\Any)
+%on how traffic must traverse the network for global prefixes.
 %aside from the default restriction
@@
 %back on itself. 
-This means traffic for
-\CD{PG*} may be sent either from other data center routers or
-from external ASes. The second line ensures that traffic for local
-prefixes never enters the network from an outside location. This constraint
-guarantees that the services remain reachable only to locations
+%This means traffic for
+%\CD{PG*} may be sent either from other data center routers or
+%from external ASes. 
+The locality constraint ensures that traffic for local
+prefixes only ever follows paths that are internal to the network at each hop. 
+This constraint guarantees that the services remain reachable only to locations
 inside the data center.
@@
 to specify the network-wide policy.
-However, in addition to constraints on the shape of paths,
+In addition to constraints on the shape of paths,
 \sysname allows the operator to specify constraints on the BGP control plane.
@@
 \begin{code}
-Ownership \AND{} Routing \AND{} \Agg(PG, \In \Link \Out)
+Ownership \AND{} Locality \AND{} \Agg(PG, \In \Link \Out)
 \end{code}

### 2016-06-07 paper/v1/compilation.tex
adding revisions to paper

--- 2016-01-30 paper/compilation.tex
@@
 %
-For example, in the data center configuration from \S\ref{sec:propane}, combining the \CD{Routing} and \CD{Ownership} policies results in the following RIR:
+For example, in the data center configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:
 
@@
 \begin{code}
-PG1 \Path \Any \Intersect \End(A)
-PG2 \Path \Any \Intersect \End(B)
-PL1 \Path \NOT\Enter(\Out) \Intersect \End(E)
-PL2 \Path \NOT\Enter(\Out) \Intersect \End(F)
+PG1 \Path \End(A)
+PG2 \Path \End(B)
+PL1 \Path \textbf{only}(\In) \Intersect \End(E)
+PL2 \Path \textbf{only}(\In) \Intersect \End(F)
 \True \Path \Exit(\Out)
@@
 This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
-We could solve the first problem by placing routes that go through $D$ at $B$, however, we can not fix the second problem---$C$ has made the wrong choice.
+We could solve the first problem by filtering routes that go through $D$ at $B$, however, we can not fix the second problem---$C$ has made the wrong choice.
 In fact, this policy can not be implemented in BGP in a way that is policy compliant under all failures.
@@
 
-\begin{figure}[t!]
-%% \begin{lstlisting}[frame=single, mathescape=true]
-%% $\Router{A}$
-%%   Match $\PEER=C, \COMM=(3,2)$
-%%     Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
-%% $\Router{B}$
-%%   Match $\PEER = C, \COMM = (-,2)$
-%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
-%%            $\MED \leftarrow 81, \PEER \leftarrow W$
-%%   Match $\PEER = C, \COMM = (3,2)$
-%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
-%%            $\MED \leftarrow 81, \PEER \leftarrow W$
-%% $\Router{C}$
-%%   Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
-%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
-%%   Match $\PEER = D, \COMM = (2,2)$
-%%     Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
-%% $\Router{D}$
-%%   Match $\REGEX{X + Y}$
-%%     Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
-%% $\Router{E}$
-%%   Match $\REGEX{Z}$
-%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
-%% \end{lstlisting}
-\begin{code}
-  \Router{A}
-    Match \PEER=C, \COMM=(3,2)
-      Export \COMM \Arrow (4,2), \MED \Arrow 80, \PEER \Arrow W
-  \Router{B}
-    Match \PEER = C, \COMM = (-,2)
-      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
-             \MED \Arrow 81, \PEER \Arrow W
-    Match \PEER = C, \COMM = (3,2)
-      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
-             \MED \Arrow 81, \PEER \Arrow W
-  \Router{C}
-    Match[LP=99] \PEER = E, \COMM = (-,2) 
-      Export \COMM \Arrow (-,2), \PEER \Arrow B
-    Match \PEER = D, \COMM = (2,2)
-      Export \COMM \Arrow (3,2), \PEER \Arrow A,B
-  \Router{D}
-    Match \REGEX{X + Y}
-      Export \COMM \Arrow (2,2), \PEER \Arrow C
-  \Router{E}
-    Match \REGEX{Z}
-      Export \COMM \Arrow (-,2), \PEER \Arrow C
-  \end{code}
-  \vspace{-2em} 
-  \caption{Abstract BGP router configurations. \label{fig:abgp-config}}
-  \vspace{-1em}
-\end{figure}
-
 %\begin{figure}[t!]
@@
 Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
+
+\begin{figure}[t!]
+%% \begin{lstlisting}[frame=single, mathescape=true]
+%% $\Router{A}$
+%%   Match $\PEER=C, \COMM=(3,2)$
+%%     Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
+%% $\Router{B}$
+%%   Match $\PEER = C, \COMM = (-,2)$
+%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
+%%            $\MED \leftarrow 81, \PEER \leftarrow W$
+%%   Match $\PEER = C, \COMM = (3,2)$
+%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
+%%            $\MED \leftarrow 81, \PEER \leftarrow W$
+%% $\Router{C}$
+%%   Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
+%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
+%%   Match $\PEER = D, \COMM = (2,2)$
+%%     Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
+%% $\Router{D}$
+%%   Match $\REGEX{X + Y}$
+%%     Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
+%% $\Router{E}$
+%%   Match $\REGEX{Z}$
+%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
+%% \end{lstlisting}
+\begin{code}
+  \Router{A}
+    Match \PEER=C, \COMM=(3,2)
+      Export \COMM \Arrow (4,2), \MED \Arrow 80, \PEER \Arrow W
+  \Router{B}
+    Match \PEER = C, \COMM = (-,2)
+      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
+             \MED \Arrow 81, \PEER \Arrow W
+    Match \PEER = C, \COMM = (3,2)
+      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
+             \MED \Arrow 81, \PEER \Arrow W
+  \Router{C}
+    Match[LP=99] \PEER = E, \COMM = (-,2) 
+      Export \COMM \Arrow (-,2), \PEER \Arrow B
+    Match \PEER = D, \COMM = (2,2)
+      Export \COMM \Arrow (3,2), \PEER \Arrow A,B
+  \Router{D}
+    Match \REGEX{X + Y}
+      Export \COMM \Arrow (2,2), \PEER \Arrow C
+  \Router{E}
+    Match \REGEX{Z}
+      Export \COMM \Arrow (-,2), \PEER \Arrow C
+  \end{code}
+  \vspace{-2em} 
+  \caption{Abstract BGP router configurations. \label{fig:abgp-config}}
+  \vspace{-1em}
+\end{figure}

### 2016-06-07 paper/v1/discussion.tex
adding revisions to paper

\section{Future Work}

There are a number of possible directions for future work in programming distributed control planes. One option would be to integrate a model of the environment into the compiler. For example, many ASes make use of informal peering agreements (e.g., tagging routes with certain communities) to enable a wider range of policies. A compiler with this information, could automatically derive routes conforming to these agreements. 
%
Another direction would be to perform policy verification at the level of centralized language. There has been great deal of work on verification of the data plane, but much less so on control plane verification. The \sysname language provides a high-level abstraction of the control plane, which could be amenable to verification or checking equivalence of policies. For example, an operator could check if adding aggregation at various points in the network as an optimization ever changes routing behavior. The automata-based representation of the product graph may lend itself well to this kinds of analysis.
%
While we target BGP in this paper as a distributed backend for \sysname due to its expressiveness, scalability, and uniformity, it should be possible to use other protocols to achieve different types of routing policies (e.g., OSPF). In particular, one could potentially combine different distributed routing protocols through route redistribution to achieve a larger variety of policies.
%
Another possible future direction is automate AS-wide load balancing for BGP. Load-balancing with BGP across external ASes is difficult since there are few mechanisms at the operators disposal. However BGP policies can artificially prepend to the AS path to increases its length, and influence peer decisions. The product graph representation describes, not only which neighbors routers should prefer, but also which neighbors it is indifferent towards. Thus the compiler knowns when it can safely perform load-balancing across different neighbors.

### 2016-06-07 paper/v1/motivation.tex
adding revisions to paper

--- 2016-01-29 paper/motivation.tex
@@
 
-Clearly it is no simple task to properly configure even this
+Clearly it is difficult to properly configure even this
 small example network manually; devising correct configurations for real networks can quickly become a nightmare.

### 2016-06-07 paper/v2/paper-edited.tex
adding revisions to paper

\documentclass{sig-alternate-10pt}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{url}
\usepackage{times}
\usepackage{xspace}
\usepackage{listings}
\usepackage{code}  
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning}
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{subcaption}
%\usepackage{geometry}

\usepackage{balance}

\definecolor{princetonorange}{RGB}{255,143,0}
\definecolor{tmlblue}{RGB}{0,58,120}  % tmlblue == Toronto Maple Leafs Blue!

\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\newcommand{\ratul}[1]{\textcolor{blue}{[ratul: #1]}}
\newcommand{\ryan}[1]{\textcolor{green}{[ryan: #1]}}
\newcommand{\dpw}[1]{\textcolor{tmlblue}{[dpw: #1]}}
\newcommand{\todd}[1]{\textcolor{princetonorange}{[todd: #1]}}

\newcommand{\EG}{\emph{e.g.}} 
\newcommand{\IE}{\emph{i.e.}} 
\newcommand{\ETC}{\emph{etc.}} 
\newcommand{\ETAL}{\emph{et al.}}

\newcommand{\sysname}{{\small \sf Propane}\xspace}

\newcommand{\para}[1]{\paragraph*{\textbf{#1}}}

\newcommand{\set}[1]{\ensuremath{\{ #1 \} }}
\newcommand{\abs}[1]{\ensuremath{ \lvert #1 \rvert }}

\newcommand{\CD}[1]{\texttt{\small #1}}  % code font
\newcommand{\KW}[1]{\texttt{\small\bfseries{#1}}}
%\newcommand{\KW}[1]{\texttt{#1}}
\newcommand{\True}{\CD{true}}
\newcommand{\Define}{\KW{define}}
\newcommand{\Prefer}{\texttt{>>}}
\newcommand{\Path}{\texttt{=>}}
\newcommand{\Link}{\texttt{->}}
\newcommand{\Agg}{\KW{agg}}
\newcommand{\Any}{\KW{any}}
\newcommand{\None}{\KW{none}}
\newcommand{\In}{\KW{in}}
\newcommand{\Out}{\KW{out}}
\newcommand{\AND}{\texttt{\&}}
\newcommand{\OR}{\texttt{|}}
\newcommand{\NOT}{\texttt{!}}
\newcommand{\Intersect}{\ensuremath{\cap}}
\newcommand{\Union}{\ensuremath{\cup}}

\newcommand{\Exit}{\KW{exit}}
\newcommand{\End}{\KW{end}}
\newcommand{\Start}{\KW{start}}
\newcommand{\Enter}{\KW{enter}}
\newcommand{\Later}{\KW{later}}
\newcommand{\Before}{\KW{before}}
\newcommand{\Internal}{\KW{internal}}
\newcommand{\Never}{\KW{never}}
\newcommand{\Only}{\KW{only}}
\newcommand{\Through}{\KW{through}}
\newcommand{\LinkKW}{\KW{link}}
\newcommand{\PathKW}{\KW{path}}
\newcommand{\Novalley}{\KW{novalley}}

%\let\Url\url
%\renewcommand*{\LaTeX}{\oldLaTeX\space}
\renewcommand{\path}[2]{ #1 \mapsto \ensuremath{#2} }

\begin{document}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\title{Don't Mind the Gap:  Bridging Network-wide Objectives and Device-level Configurations}

%\author{Paper \#324, 14 pages}

\author{%
Ryan Beckett\\
  \affaddr{Princeton University}\\
  \email{rbeckett@princeton.edu}
\and
Ratul Mahajan\\
  \affaddr{Microsoft Research}\\
  \email{ratul@microsoft.com}
\and
Todd Millstein\\
  \affaddr{University of California, Los Angeles}\\
  \email{todd@cs.ucla.edu}
\and
Jitu Padhye\\
  \affaddr{Microsoft Research}\\
  \email{padhye@microsoft.com}
\and
David Walker\\
  \affaddr{Princeton University}\\
  \email{dpw@princeton.edu}
}

\maketitle

%\category{CR-number}{subcategory}{third-level}
%% general terms are not compulsory anymore,
%% you may leave them out
%\terms
%term1, term2
%\keywords
%keyword1, keyword2

%=====================================================
%
%
%  **Abstract**
%
%
%=====================================================

%\textbf{Abstract---}
%% Networks are notoriously difficult to configure correctly.
%% Operators typically rely on local configuration of individual devices running
%% distributed control plane protocols to achieve network-wide objectives.
%% Managing implicit dependencies between device configurations and properly accounting for failures makes
%% a network operator's work particularly difficult.
%% %
%% %The recent move towards software-defined networking has been motivated, in part,
%% %by the simplicity of the centralized model, where a controller directly manages
%% %individual devices rather than letting them manage themselves. However distributed
%% %protocols have many important advantages in scalability,
%% %latency and fault tolerance over the completely centralized approach.
%% %
%% In this paper, we describe a new system -- \sysname, which allows an operator to specify a high-level,
%% centralized routing policy declaratively, but then to compile it to a purely distributed
%% implementation, which uses the BGP routing protocol to run on existing, commodity hardware.
%% %
%% Propane allows operators to describe the types of paths traffic may (or may not) take
%% through the network, as well as relative preferences (or backups) between paths.
%% %
%% Network policies compiled with \sysname are guaranteed to implement the correct routing policy regardless of the number of failures, if possible.  If this is not possible, the compiler notifies the user at compile time rather than as the network is in
%% operation.
%% %
%% %\sysname also takes the centralized model one step further by unifying inter and intra-domain routing. Operators can specify routing policy for an autonomous system by programming against the abstraction that they can control any route in the wider internet.
%% %
%% We have implemented a compiler for \sysname and evaluated it against several real-world configurations for data centers and core backbone networks. We demonstrate the \sysname compiler can scale to
%% topologies with thousands of routers.
%
%\begin{abstract}
%Traditional network operators have a difficult job: They are charged
%with achieving network-wide objectives, but they must do so by
%managing many individual, separate devices, each of which is running a
%complex distributed control plane protocol.  Bridging the gap between
%high-level objectives and low-level mechanisms manually is a challenging and
%error-prone task.
%%
%In this paper, we describe our preliminary efforts to design and
%implement a new language called Propane, which simplifies the task of
%network management by allowing operators to specify their objectives
%using end-to-end forwarding paths rather than device-by-device
%configurations.  A compiler rather than a human bridges the gap
%between high-level goals and the low-level mechanisms.  More
%specifically, Propane allows operators to describe and rank the sets
%of paths that traffic may follow.  Such paths stretch from external
%ASes, through the user's network, and possibly onward again to other
%ASes.  The Propane compiler analyzes these user specifications and
%then compiles them to a collection of BGP configurations, so they may
%exploit existing distributed fault tolerance mechanisms and
%execute on existing commodity hardware.  During the compilation
%process, it automatically synthesizes per-device import and export
%filters, local preferences, MED attributes, and community tags.  An
%important feature of the language is that whenever possible, compiled
%configurations are guaranteed to implement the correct routing policy,
%regardless of the number of failures.  If correct compilation is
%impossible, the compiler notifies the user at compile time rather than
%waiting until the system is in operation and failures have occurred.
%To date, we have used the language and compiler to experiment with
%several real-world configurations for data centers and core backbone
%networks.  We demonstrate our prototype compiler can scale to
%topologies with thousands of routers.
%\end{abstract}

\textbf{Abstract---}
We develop a system called \sysname to help network operators with a challenging and error prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex distributed protocols.
%
\sysname allows operators to specify their objectives naturally, describing high-level constraints and preferences on the types of paths that traffic should take through their network or other networks.
%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
%
Our compiler automatically translates these specifications to a collection of BGP router configurations.
% that can execute on existing commodity hardware.
%
We introduce data structures and algorithms that guarantee that the compiled, distributed configurations correctly implement the routing policy under all possible combinations of failures.
%
We use \sysname to specify and compile the configurations of real
data center and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds to thousands of routers.

%=====================================================
%
%
%  **Introduction**
%
%
%=====================================================

\section{Introduction}
\label{sec:introduction}

It is well known that configuring networks is error
prone and such errors can lead to disruptive network
downtimes~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
For instance, a recent misconfiguration led to an hour-long, nation-wide outage for Time Warner's backbone network~\cite{time-warner}; and a major BGP-related incident makes international news every few months~\cite{bgpmon}.

%For instance, in the context of BGP, Mahajan~~\cite{mahajan+:bgp-misconfiguration}
%estimated that 200-1200 prefixes suffered from
%misconfiguration each day and that close to 3 in 4 of all
%new prefix advertisements were the result of misconfiguration.
%Moreover, these misconfigurations sometimes cause significant network downtime for
%individual networks~\cite{time-warner} or even broader internet connectivity problems~\cite{routing-instability,mahajan+:bgp-misconfiguration}.
%\dpw{Note that \cite{time-warner} and I am not sure about the specifics of the problem there
%or what exactly was misconfigured.  It is also unclear if our language really helps with the
%``broader internet connectivity problems'' however, I thought that adding some specific examples
%would help make the intro more compelling.  Feel free to rewrite.}

%One reason for network configuration being onerous is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.

A fundamental reason for the prevalence of misconfigurations is the
semantic mismatch between the intended high-level
policies and the low-level configurations.
Many policies involve network-wide properties---prefer a certain neighbor,
never announce a particular destination externally,
use a particular path only if another fails---but configurations describe the behavior of
individual devices.
%
Operators therefore must manually decompose network-wide policy into
device behaviors, such that policy-compliant behavior results from the distributed interactions of
these devices.
%
Policy-compliance must be ensured not only under normal
circumstances but also during failures.  The need to reason
about possible failures exacerbates the challenge
for network operators.  As a result, configurations that work
correctly in failure-free environments have nonetheless been found to violate key
network-wide properties when failures occur~\cite{batfish}.

To reduce configuration errors, many practitioners have a adopted a template-based
approach~\cite{hatch,thwack}, in which common tasks are captured as parameterized templates.
%
%More powerful still are systems like
%ConfigAssure~\cite{narain:lisa05,narain+:configassure}, which use SAT solving
%and model finding tools to fill in parameters in configurations while
%ensuring key correctness constraints are satisfied.
%One step further, systems like
%ConfigAssure~\cite{narain:lisa05,narain+:configassure} use SAT solving
%and model finding tools to correctly and consistently fill in some parameters.
%
While templates help ensure certain kinds of consistency across devices,
they do not provide fundamentally different abstractions from existing configuration languages
or bridge the semantic divide between network-wide policies and device-level configuration.
%They do not provide fundamentally different abstractions
%from existing configuration languages and
Thus, they still require operators to
manually decompose policies into device behaviors.

Configuration analysis tools~\cite{batfish,feamster+:rcc} have been developed as a complementary approach for reducing misconfigurations by checking that the low-level configurations match high-level operator intent. However, such tools cannot help operators come up with the configuration in the first place. Further, today's tools can only check correctness under concrete failure scenarios, rather than under all possible failures.

Software-defined networking (SDN) and its abstractions
are, in part, the research
community's response to the difficulty of maintaining policy
compliance through distributed device interactions~\cite{ethane}. 
Instead of organizing networks around a distributed 
collection of devices that compute forwarding tables through
mutual interactions, the devices are told how to
forward packets by a centralized controller. The controller is responsible for ensuring that the
paths taken are compliant with operator specifications.
%Researchers
%have developed increasingly sophisticated languages that let operators
%specify desirable network paths~\cite{x,y,z} which are then translated
%to forwarding tables at runtime.

The centralized control planes of SDN, however, are not a panacea.
First, while many SDN programming systems~\cite{sdn-languages} provide effective \emph{intra}-domain routing
abstractions, letting users specify paths within their network,
they fail to provide a coherent means to specify \emph{inter}-domain routes.
Second, centralized control planes
require careful design and engineering to be robust to failures---one must ensure that all devices can communicate with the controller at all times, even under arbitrary failure combinations. Even ignoring failures, it is necessary for the control system to
scale to meet the demands of large or geographically-distributed networks,
and to react quickly
to environmental changes. For this challenge, researchers are exploring
multi-controller systems with interacting controllers, thus bringing back distributed
control planes~\cite{mccauley2013extending,onos} and their current programming difficulties.
%However, academic
%language design and implementation efforts have not kept pace.  For instance, work on many
%experimental SDN languages~\cite{frenetic,flowlog,vericon,merlin,netkat,kinetic,pga} has not yet shown how to implement fault tolerant
%multi-controller systems that support their high-level abstractions efficiently.

Hence, in this paper, we have two central goals:
\begin{enumerate}
\item Design a new, high-level language with natural abstractions
for expressing intra-domain routing, inter-domain
routing and routing alternatives in case of failures.
\item Define algorithms for compiling these specifications into
configurations for devices running standard
distributed control plane algorithms, while ensuring correct behavior
independent of the number of faults.
\end{enumerate}

To achieve the first goal, we borrow the idea of using regular
expressions to specify network paths from
recent high-level SDN languages such as FatTire~\cite{fattire},
Merlin~\cite{foster:merlin}, and
NetKAT~\cite{netkat}.  However, our design also contains several key
departures from existing languages.  The most important one is semantic:  the paths specified
can extend from outside the operator's network to inside
the network, across several devices internally, and then out again. This design
choice allows users to specify preferences about both external and internal
routes in the exact same way.
In addition, we augment the algebra
of regular expressions to directly support a notion of {\em preferences} and provide a semantics in terms of sets of ranked paths. The preferences indicate fail-over behaviors:  among all specified paths that are still available,
the system guarantees that the distributed implementation will always use the highest-ranked ones.
Although we target a distributed implementation, the language is more general and could potentially be used in an SDN context.

%We also support network operators by defining a
%set of common abbreviations for entering, leaving, and traversing
%the user network and we provide abstractions for managing common features %of
%control plane algorithms such as route aggregation.  Operators use familiar logical operations
%to build routes in a modular and compositional manner from these
%primitives.  Our abbreviations are translated in to our regular-expression-based
%intermediate representation and compiled from there.

To achieve the second goal, we develop program analysis and compilation
algorithms that translate the regular policies to a graph-based
intermediate representation and from there to per-device BGP configurations, which include various filters and preferences that govern BGP behavior.
%import and export filters, local preferences, MED attributes, and community tags.
We target BGP for pragmatic reasons:
it is a highly flexible routing protocol,
it is an industry standard,
and many networks use it internally as well as externally.
Despite the advent of SDN, many networks will continue to
use BGP for the foreseeable future due to existing infrastructure investments, the difficulty of transitioning to SDN, and the scalability and fault-tolerance advantages of a distributed
control plane.

The BGP configurations produced by our compiler are
guaranteed to be policy-compliant in the face of
{\em arbitrary} failures.\footnote{In this paper we assume that BGP is the only control plane protocol running in the network or the other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This does not mean that the implementation is always
able to send traffic to its ultimate destination
(\EG in the case of a network partition), but rather that it always respects the
centralized policy, which may include dropping traffic when there is no route.
%
In this way, we provide network operators
with a strong guarantee that is otherwise impossible to achieve
today.
However, some policies simply cannot be implemented correctly in BGP in
 the presence of arbitrary failures.  We develop new
algorithms to detect such policies
and report our findings to the operators, so they may fix the policy
specification at compile time rather than experience undesirable
behavior after the configurations are deployed.
%We also analyze route aggregation to detect the possibility of failure-induced black-holes.

%These algorithms differ from
%standard BGP analysis algorithms~\cite{feamster:rcc,batfish} because they operate on
%our graph-based intermediate representation, which operates at a higher level
%of abstraction than raw BGP configurations (and which has the pleasant effect of simplifying our
%task).

We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies of data center and backbone networks.
% and compared these specifications with existing configurations.
We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds of routers, compiling in under 9 minutes in all cases.

%measured the performance of our compiler, demonstrating that our compilation
%algorithms scale to topologies with several thousand routers.
%
%\dpw{The following could be cut for space.}
%In the remainder of the paper, we review BGP (Section~\ref{sec:background}---readers
%familiar with BGP may skip this section),
%further motivate the need for new languages
%for programming distributed control planes (Section \ref{sec:motivation}),
%introduce \sysname{} by example (Section \ref{sec:propane}),
%explain our compiler algorithms (Section \ref{sec:compilation}),
%present several lemmas justifying the correctness of our techniques (Section \ref{sec:theory}), describe our implementation (Section \ref{sec:implementation})
%evaluate our work  (Section \ref{sec:evaluation}) and discuss related work (Section \ref{sec:related}).

%% In this paper, we ask if it is possible to program
%% fully distributed control planes using
%% \emph{end-to-end},
%% \emph{network-wide} policies, while handing the job of compiling
%% such policy.  In particular,
%% operators should be able to directly express \emph{end-to-end},
%% \emph{network-wide} policies directly; it is the job of a compiler
%% to decompose such policies into individual device configurations.
%% In addition, the resulting forwarding behavior, which emerges through device interactions, must be policy-compliant under all possible failures.
%% If successful, this approach would combine easy programmability of centralized control planes with the failure robustness and scalability of distributed control planes.
%% %
%% More pragmatically, it would help many networks that, for the foreseeable future, will continue to use a distributed control plane, due to the difficulty of migrating to SDN or the inherent scalability and failure-robustness of distributed control.

%% Through \sysname, our system that includes a language and a compiler, we demonstrate the feasibility of programming distributed control planes. We focus on BGP, a common and highly flexible way to implement distributed control planes, and show how to automatically generate router BGP configurations from network-wide policies.

%% We face two challenges in designing \sysname that differ from designing a system for programming data planes~\cite{x,y,z}. The first is policy specification itself---specifying network {\em policies} is different from specifying network {\em paths}.
%% %
%% The specification must compactly capture behavior under all possible failures. Since there is no controller at runtime, the routers must be programmed ahead of time, based on the specification, to handle failures.
%% %
%% Further, many policies naturally under-specify paths (e.g., "prefer paying neighbors" is not a concrete path).
%% %
%% \sysname addresses this specification challenge by allowing operators to express {\em path preferences}, where preference describes a set of valid paths and less-preferred options are taken only when a higher-preference options are unavailable.

%% The direct nature of \sysname specifications brings up the second challenge, of compiling them to router configurations.  We must compute the sets of paths represented by the intersection of multiple preferences and topology, compute which ones can be honored under a given failure scenario, and ensure policy compliance under all possible failure cases. We handle this challenge by compactly capturing policy and topology in a {\em product graph} and developing efficient algorithms that operate on this graph.

%% We evaluate \sysname by using it to encode policies of real backbone and data center networks.

%% \todo{new intro is not complete}

%=====================================================
%
%
%  **Background**
%
%
%=====================================================

\section{Background on BGP}
\label{sec:background}

%Our work focuses on BGP as it is the most common and flexible way to implement distributed control planes today. In this section, we provide relevant background on BGP.

BGP is a path-vector routing protocol that connects autonomous systems (ASes). An AS has one or more routers managed by the same administrative entity. ASes exchange routing announcements with their neighbors. Each announcement has a destination IP prefix and some attributes (see below), and it indicates that the sending AS is willing to carry traffic destined to that prefix from the receiving AS. Traffic flows in the opposite direction, from announcement receivers to senders.

When a route announcement is received by an AS, it is processed by custom import filters that may drop the announcement or modify some attributes. If multiple announcements for the same prefix survive import filters, the router selects the best one based on local policy (see below). This route is then used to send traffic to the destination. It is also advertised to the neighbors, after processing through neighbor-specific export filters that may stop the announcement or modify some attributes.

All routing announcements are accompanied by an AS-path attribute that reflects the sequence of ASes that the announcement has traversed thus far. While the AS-path attribute has a global meaning, some attributes are meaningful only within an AS or between neighboring ASes.  One such attribute is a list of community strings. ASes use such strings to color routes on different criteria (e.g., ``entered on West Coast'') and then use the color later in the routing process.  Communities are also used to signal to neighbors how they should handle an announcement (e.g., do not export it further). Another non-global attribute is the multi-exit discriminator (MED). It is used when an AS has multiple links to a neighboring AS.  Its (numeric) values signal to the neighbor how this AS prefers to receive traffic among those links.

The route selection process assigns a {\em local preference} to each
route that survives the import filters. Routes with higher local
preference are preferred. Among routes with the same local preference,
other factors such as AS path length, MEDs, and internal routing cost, are considered in order. Because it is considered first during route selection, local preference is highly influential, and ASes may assign this preference based on any aspect of the route. A common practice is to assign it based on the commercial relationship with the neighbor. For instance, an AS may prefer in order customer ASes (which pay money), peer ASes (with free exchange of traffic), and provider ASes (which charge money for traffic).

In implementing their policy, each network operator assumes that
neighboring ASes correctly implement BGP and honor contracts related
to MEDs and communities. \sysname makes the same assumption when
deriving BGP configurations for a network.

The combination of arbitrary import and export filters and route selection policies at individual routers make BGP a highly flexible routing protocol. That flexibility, however, comes at the cost of it being difficult to configure correctly.

%=====================================================
%
%
%  **Motivation**
%
%
%=====================================================

\section{Motivation}
\label{sec:motivation}

%We motivate our work by describing the current practice in network
%configuration. In traditional networks with distributed control planes, the operators' goal is to generate the configuration of individual devices based on their desired policy. This configuration dictates the behavior of a device, how it exchanges routing information with neighbors and how it filters and ranks that information. The collective behavior of the devices should implement the desired policy.
%
%Device configuration languages are low-level and indirect. For instance, instead of allowing operators to express directly the paths they want through the network, they require operators to specify metrics that result in those paths; instead of allowing operators to express directly the types of traffic to not carry through the network, they require operators to select and program an appropriate filtering mechanism (e.g., BGP import or export filters, null routing,  access control lists) and instantiate it on topologically appropriate devices; instead of allowing operators to directly specify that they prefer BGP neighbors in a certain order, they require operators to program local preferences and multi-exit discriminators (MED) at each router and ensure that the numbers are consistent across routers.
%
%In many networks today, device configurations are generated manually by operators, without the support of many automated tools. It is easy to see the problems with this approach, such as typos, inconsistency across devices, and no guarantees of policy compliance.
%
%To reduce such problems, some networks use a template-based approach. Configuration templates abstract certain constants into variables (e.g., instead of concrete community value, they may contain a variable {\small \sf{\$$BadNeighbor$)}} and may use a device vendor-neutral syntax. Operators manually generate the templates and use tools to translate them into device configuration, by replacing variables with appropriate constants using a database of network information.
%
% %and replacing vendor-neutral constructs with their vendor-specific counterparts.
%
%%In practice, most networks use a hybrid of templates and manual generation of device configuration. Templates are used for standardized and common configuration elements across devices and the result is manually tweaked to obtain the exact desired network behavior.
%
%While templates avoids some pitfalls of the fully manual approach, they too are far from ideal. The fundamental issue is the semantic mismatch between desired policies and the level of abstraction of templates. While many policies are network-wide (e.g., prefer customer networks, or never announce a route to a certain prefix to external neighbors), templates are device-level. Operators must still manually decompose network-wide policies into device-level policies that can produce the desired network-wide behavior.
%This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures. We illustrate this point using two examples based on policies that we have seen in practice and we demonstrate the ease with which the
%examples are described using our new language \sysname.

%Operators today generate the BGP configuration of individual devices based on intended policy. 
When generating BGP configurations, whether fully manually or aided by templates, the operators face the challenge of decomposing network-wide policies
into appropriate device-level policies.
This decomposition is not always straightforward and ensuring policy-compliance is tricky, especially in the face of failures. We illustrate this point using two examples based on policies that we have seen in practice. The next section shows how \sysname allows operators to directly express these policies. 
%the ease with which the
%policies can be specified using our new language \sysname.
%The next section describes how to automatically compile this specification to device-level policies.

\subsection{Example 1:  The Backbone}

Consider the backbone network in Figure~\ref{fig:example1}. It has
three neighbors, a customer \CD{Cust}, a peer \CD{Peer}, and a provider \CD{Prov}. The policy of this network is shown on the right. It prefers the neighbors in a certain order (P1) and does not want to act as a transit between \CD{Peer} and \CD{Prov} (P2). It prefers to exchange traffic with \CD{Cust} over \CD{R1} rather than \CD{R2} because \CD{R1} is cheaper (P3). To guard against another AS "hijacking" prefixes owned by \CD{Cust}, the network only sends traffic to a neighbor if \CD{Cust} is on the AS path (P4). Finally, to guard against \CD{Cust} accidentally becoming a transit for \CD{Prov}, it does not use \CD{Cust} for traffic that will later traverse \CD{Prov} (P5).

To implement P1 of the policy, the operators must compute and assign
local preferences such that preferences at \CD{Cust}-facing interfaces
$>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
the same time, to satisfy P3 the preference at \CD{R2}'s
\CD{Cust}-facing interface should be lower than that at
\CD{R1}. Implementing P3 properly will require MEDs to be appropriately configured on \CD{R1} and \CD{R2}. 
To implement P2, the operators can assign communities that
indicate where a certain routing announcement entered the
network. Then, \CD{R4} must be configured to not announce to
$\CD{Peer}$ routes that have communities that correspond to the
\CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links. Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based import and export filters at each router.

Clearly it is difficult to properly configure even this
small example network manually; devising correct configurations for real networks can quickly become a nightmare. Such networks have many neighbors spanning multiple commercial-relationship classes, differing numbers of links to each neighbor, along with several neighbor- or prefix-based exceptions to the default behavior. A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually. 
%\sysname lets operators express such policies easily and intuitively. It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/example1}
  \caption{Creating router-level policies is difficult.}
  \label{fig:example1}
  \vspace{-1em}
\end{figure}

\subsection{Example 2:  The Data Center}

 While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible. Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally. This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally. Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}. The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.

The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ announce what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}. This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be assigned to local services without updating router configurations).

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/example2}
  \caption{Policy-compliance under failures is difficult.}
  \label{fig:example2}
  \vspace{-1em}
\end{figure}

However, this implementation does not have the right behavior in the face of failures. Suppose links X--G and X--H fail. Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D. Per policy implementation, X will start "leaking" these prefixes externally. Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are used for other services outside of the data center). This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter. A similar problem will happen if links Y--G and Y--H fail.
%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
Link failures in data centers are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.

To avoid this problem, the operator may decide to disallow "valley" paths, i.e., those that go up, down, and back up again. This guard can be implemented by $X$ and $Y$ rejecting paths through the other. But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{route-aggregation}. If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce \CD{PG} externally. This announcement will bring to X traffic for \CD{PG1} as well, but because of valley-free filtering, X does not have a valid route for \CD{PG1} and will thus drop all traffic to it.

Thus, we see that devising a configuration that ensures policy compliance in the face of failures is complex and error-prone. \sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures (if that is possible; otherwise, it generates a compile-time error). For aggregation, it also provides a lower bound to operators on the number of failures under which aggregation will not result in blackholes.

%\subsection{OLD -- Overview}
%\todo{this subsection can be deleted once we have captured everything in it}
%
%Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention).
%Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
%
%\begin{itemize}
% \item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
% \item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
% \item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
% \item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
% \item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
%\end{itemize}
%
%
%Possible Examples:
%\begin{itemize}
% \item Basic datacenter with spine preference
% \item Simple AS that prefers customers over peers over providers
% \item Combined internal backup routing with preference based entrance into the network using aggregation.
% \item Something like cold potato routing
%\end{itemize}

%=====================================================
%
%
%  **Propane Language**
%
%
%=====================================================

\section{Propane overview}
\label{sec:propane}

Policies for (distributed) control planes differ from data-plane
policies in a few important ways. First, control-plane
policies must account for all failures at compile time; there is
no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
%
In \sysname, we enable such specifications through a notion of {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
%
Second, paths in a control-plane policy may be under-specified (e.g.,
"prefer customer" does not indicate a concrete path). The \sysname
compiler treats such under-specifications as constraints on the set of
allowed paths and automatically computes valid sets based on the topology.
%

In the rest of this section, we define \sysname policies for the two 
examples from the previous section, introducing key aspects of
the \sysname language along the way. The complete syntax of the
language as well as our strategy for compiling \sysname policies to
BGP is defined in \S\ref{sec:compilation}.

\subsection{Example 1: The Backbone}

%\sysname simplifies network configuration by allowing users to
%specify end-to-end forwarding paths and associating them with
%appropriate prefixes.  The \sysname compiler handles the task of
%generating low-level BGP configurations consistent with the user's
%specifications.  It automatically synthesizes
%import-export filters, local preferences, MED attributes, and community tags
%to ensure policy compliance under all possible failure scenarios.

\sysname allows operators to configure the network with the
abstraction that they have centralized control over routing.
Specifically, the operator simply provides a set of high-level constraints
that describe the 
different routes traffic may (or may not) take and their relative preferences.
\sysname specifications are written modularly via a series
of declarations.
%These definitions allow users to express the three
%major elements of any \sysname specification:  \emph{prefixes},
%\emph{paths} and \emph{policies}.
For example, to begin specification of the backbone
network from the previous section, we first express the idea that for routes leading to our customer,
we prefer using \CD{R1} over \CD{R2} (policy P3 from Figure~\ref{fig:example1}):
%\begin{lstlisting}[mathescape=true]
%define ExitCust = $exit(R_1 \gg R_2)$
%\end{lstlisting}
\begin{code}
\Define Prefs = \Exit(R1 \Prefer R2 \Prefer Peer \Prefer Prov)
\end{code}
This  statement defines a set of \emph{ranked paths}, which includes
all paths (and only those paths) for which traffic exits our network
through either router \CD{R1}, router \CD{R2}, \CD{Peer}, or \CD{Prov}.  
The paths that exit through \CD{R1}
are preferred (\Prefer) to those that exit through \CD{R2}, which are preferred to those that 
leave through \CD{Peer} and so then \CD{Prov}.  As we
describe in the next section, the \Exit\ predicate, as well as other
path predicates used later in this section, is simply a shorthand for 
a particular regular expression over paths that is expressible in our policy
language.

% DAVE CONVERSIONS
% C_{pfx} ===> PCust
% I_{pfx} ===> PInternal

To associate ranked paths with
one or more prefixes, we define a \sysname \emph{policy}.
Within a policy, statements with the form $t$\Path$p$
associate the prefixes defined by the predicate $t$ with the set of
ranked paths defined by the path expression $p$.  In general,
prefix predicates can be defined by arbitrary boolean combinations
(and, or, not) of concrete prefixes and community tags.  Here,
we assume we have already defined predicates \CD{PCust} for the
customer prefixes.
%and \CD{PInt} for our internal prefixes.
In the following code, ranked paths are associated with
customer prefixes,
and all other prefixes (\CD{true}).\footnote{Policy statements are processed in
order with earlier policy statements taking precedence over later
policy statements.  Hence, when the prefix predicate \True{} follows
the statement involving \CD{PCust}, it is interpreted as
\CD{\True{} \AND{} \NOT{}PCust}.}

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{C_{pfx}}{ExitCust \gg end(Cust)}$
%%     $\path{I_{pfx}}{end(in)}$
%%     $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
%% }
%% \end{lstlisting}

\begin{code}
\Define Routing = 
    \{PCust \Path Prefs \AND \End(Cust)
     \True  \Path Prefs \}
\end{code}
\noindent

Line 2 of this policy 
restricts traffic destined to known customer prefixes (\CD{PCust}) to only follow paths that end at the customer. In addition, it enforces the network-wide preference that traffic leaves through \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
%defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
%that connections to the customer through both routers fail,
%a backup route (\CD{\End(Cust)}) is defined that admits traffic along
%any path (including those through other networks) that ends at the customer.
%Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.
Line 3 applies to any other traffic, and allows the traffic to leave through any direct neighbor with the usual preferences of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}. To summarize our progress, the \CD{Routing} policy
implements P1, P3, and P4 from Figure~\ref{fig:example1}.

Since by default routing allows transit traffic (\EG, traffic entering from
\CD{Peer} and leaving through \CD{Prov}), we separately define a
policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
disjunction (\OR) and negation (\NOT) of constraints. 
First, we create reusable abstractions for describing traffic that transits our network. In \sysname, this is done by creating a new parameterized definition.
\begin{code}
\Define transit(X,Y) = \Enter(X \OR Y) \AND \Exit(X \OR Y)
\Define cust-transit(X,Y) = \Later(X) \AND \Later(Y)
\end{code}
\noindent
Here we define transit traffic between $X$ and $Y$ as traffic that enters the network through $X$ or $Y$ and then leaves the network through $X$ or $Y$. Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network. Using these two new abstractions, we can now implement policies P2 and P5 with the following constraint.

\begin{code}
\Define NoTrans = 
  \{\True \Path \NOT{}transit(Peer,Prov) \AND 
           \NOT{}cust-transit(Cust,Prov)\}
\end{code}
\noindent
The \CD{NoTrans} constraint above requires that all traffic not follow a path that transits the network between \CD{Peer} and \CD{Prov}. Additionally, it prevents traffic from ever following paths that leave our network and later pass through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
%
%% \begin{lstlisting}[mathescape=true]
%% Routing $\AND$  NoTransit
%% \end{lstlisting}
%
These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
MED attributes, and community tags to ensure that the policy is
implemented correctly under all failure cases.

\subsection{Example 2: The Data Center}

In our data center,
there are three main concerns:
(1) traffic for the prefix block allocated to each top-of-rack router must be able to reach that router,
(2) local services must not leak outside the data center, and
(3) aggregation must be performed on global prefixes to reduce churn
in the network.

\sysname allows us to specify each of these constraints modularly. The first constraint is about prefix ownership---namely, we only want traffic for certain prefixes to end up at a particular location. The following definition captures this intent.

%% \begin{lstlisting}[mathescape=true]
%% define Ownership = {
%%     $\path{p_{g1}}{end(A)}$
%%     $\path{p_{g2}}{end(B)}$
%%     $\path{p_{l1}}{end(E)}$
%%     $\path{p_{l2}}{end(F)}$
%% }
%% \end{lstlisting}

\begin{code}
\Define Ownership = 
    \{PG1 \Path \End(A)
     PG2 \Path \End(B)
     PL1 \Path \End(E)
     PL2 \Path \End(F)
     \True \Path \End(\Out)\}
\end{code}
\noindent
In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
end at router \CD{A}; traffic matching \CD{PG2},
but not \CD{PG1}, must
end at router \CD{B}; and so on.
Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location.
The special keyword \Out{} represents any location outside the user's network, and the keyword \In{} represents any location inside the network.
For the second constraint, we can define another policy:

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{p_{g*}}{any}$
%%     $\path{p_{l*}}{\NOT enter(out)}$
%%     $\path{true}{exit(out)}$
%% }
%% \end{lstlisting}
\begin{code}
\Define Locality = 
    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
\end{code}
\noindent
%The first line states that there is no restriction (\Any)
%on how traffic must traverse the network for global prefixes.
%aside from the default restriction
%that traffic must not pass through the user's network and then loop
%back on itself. 
%This means traffic for
%\CD{PG*} may be sent either from other data center routers or
%from external ASes. 
The locality constraint ensures that traffic for local
prefixes only ever follows paths that are internal to the network at each hop. 
This constraint guarantees that the services remain reachable only to locations
inside the data center.

As in the backbone example, we can logically conjoin these constraints
to specify the network-wide policy.
In addition to constraints on the shape of paths,
\sysname allows the operator to specify constraints on the BGP control plane.
For instance, a constraint on aggregation is included to ensure that
aggregation for global prefixes is performed from
locations inside (\In) the network to locations outside (\Out). 
In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG} 
(which we assume is defined earlier using an appropriate prefix such 
as \CD{74.3.28.0/24})
when advertised outside the datacenter.

\begin{code}
Ownership \AND{} Locality \AND{} \Agg(PG, \In \Link \Out)
\end{code}

As before, once \sysname compiles the policy, it is guaranteed to be policy-compliant under all possible failure scenarios. In addition, \sysname will efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.
%It can efficiently determine a lower bound on the number of failures necessary to black hole traffic given the user's policy, topology, and placement of specific aggregates.

%%%%OLD TEXT BELOW
%
%\section{Propane}
%\label{sec:propane}
%
%\sysname simplifies network configuration by automatically generating low-level BGP configurations from a high-level specification of the network's routing policy.
%%
%The operator configures the network with the abstraction that he or she has centralized control over routing and uses a set of high-level constraints to describe the different routes traffic may (or may not) take and their relative preferences.
%%
%The \sysname compiler generates BGP configurations for each device in the network that operate in a completely distributed fashion and are correct by construction -- automatically synthesizing import/export filters, local preference and MED attributes, and community tags to ensure policy compliance under all possible failure scenarios.
%%
%We now demonstrate \sysname by showing how to configure the networks from the previous examples.
%
%\para{Example 1}
%
%We now show how to write the routing policy for the backbone network in Section~\ref{sec:motivation}. \sysname allows to address each of the requirements in turn. First we address requirements (P1), (P3), and (P4) that customers are preferred over peers over providers, and that a customer appear on the path for its prefix. The following \sysname code accomplishes these two objectives:
%
%\begin{lstlisting}[mathescape=true]
%define ExitCust = $exit(R_1 \gg R_2)$
%
%define Routing = {
%    $\path{C_{pfx}}{ExitCust \gg end(Cust) }$
%    $\path{I_{pfx}}{end(in)}$
%    $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
%}
%\end{lstlisting}
%
%The first definition defines paths that exit our network to the customer. The statement $exit(R_1 \gg R_2)$ restricts us to paths that leave our network through either router $R_1$ or $R_2$, with a preference for $R_1$.
%The first line of the \textsf{Routing} policy ensures that traffic destined for customer prefixes ($C_{pfx}$) either leaves the network directly to the customer (with a preference for leaving through $R_1$), or simply ends at the customer. Not leaving directly to the customer by going through \textit{Peer} or \textit{Prov} is less preferred than leaving directly, and thus serves as a backup route in a direct route is not available.
%
%The second line state that traffic for internal prefixes $I_{pfx}$ must end in our network, and is otherwise unconstrained. The last line applies to any other traffic, and allows for any routes that leave through a peer with a preference for customers over peers over providers. While this still allows transit traffic (e.g., traffic can enter from \textit{Peer} and leave through \textit{Prov}), we can restrict this behavior separately as follows:
%
%\begin{lstlisting}[mathescape=true]
%define PP = Peer or Prov
%define PPTransit = $enter(PP) \wedge exit(PP)$
%define CustTransit = $later(Cust) \wedge later(Prov)$
%
%define NoTransit = {
%    $\path{true}{\neg PPTransit \wedge \neg CustTransit}$
%}
%\end{lstlisting}
%
%The \textsf{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied. In particular, it says that, for any prefix, traffice should never both enter and exit the network from \textit{Peer} or \textit{Prov}. Similarly it prevents traffic from ever following paths that leave our network and later go through both \textit{Prov} and \textit{Cust}.
%
%\begin{lstlisting}[mathescape=true]
%Routing $\wedge$  NoTransit
%\end{lstlisting}
%
%The final policy is simply the conjunction of the routing and no transit constraints. \sysname will generate per-device import and export filters, local preferences and MED attributes, and community tags to ensure that the policy is met under all failure scenarios.
%
%
%\para{Example 2}
%
%Consider again the datacenter from Section~\ref{sec:motivation}. In this example, there are primarily three main concerns: (1) traffic for the prefix block allocated to each top-of-rack router can reach that router, (2) local services do not leak outside the datacenter, and (3) aggregation is performed on global prefixes to reduce churn in the network.
%
%\sysname allows us to decompose and specify each of these constraints in a modular fashion. The first constraint is about prefix ownership -- namely, that we only want traffic for certain prefixes to end up at a particular locations. The following definition in propane captures this intent:
%
%\begin{lstlisting}[mathescape=true]
%define Ownership = {
%    $\path{p_{g1}}{end(A)}$
%    $\path{p_{g2}}{end(B)}$
%    $\path{p_{l1}}{end(E)}$
%    $\path{p_{l2}}{end(F)}$
%}
%\end{lstlisting}
%
%The constraints in the ownership task are read in a top-down fashion. Traffic for prefix $p_{g1}$ is only allowed to to follow paths that end at router A. Similarly, traffic not matching $p_{g1}$, but which matches $p_{g2}$ must end at router B and so on.
%%
%To capture the second constraint, we can define another task for the core routing policy:
%
%\begin{lstlisting}[mathescape=true]
%define Routing = {
%    $\path{p_{g*}}{any}$
%    $\path{p_{l*}}{\neg enter(out)}$
%    $\path{true}{exit(out)}$
%}
%\end{lstlisting}
%
%The first line states that there is no restriction on how traffic must traverse the network for global prefixes. This means traffic for $p_{g*}$ may be sent either from other routers in the datacenter, or from external ASes. The second line ensures that traffic for local prefixes never enters the network from an outside location. This  guarantees that the services remain reachable only to locations internal to the data center.
%
%Finally, we can combine these constraints logically to specify the network-wide policy:
%
%\begin{lstlisting}[mathescape=true]
%Ownership $\wedge$ Routing $\wedge$ agg($p_{agg}$, $in \rightarrow out$)
%\end{lstlisting}
%
%
%In addition to constraints on the shape of paths, \sysname allows the operator to specify constraints on the BGP control plane. Above, a constraint on aggregation is included to ensure that an aggregation for $p_{agg}$ is performed from locations inside the network to locations outside the network.
%
%Once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. Similarly, it can check for aggregate-induced black holes up to $k$ failures.
%

%=====================================================
%
%
%  **Compilation**
%
%
%=====================================================

\section{Compilation}
\label{sec:compilation}

The front-end (FE) of \sysname simplifies operators' task of describing preferred paths. That simplicity, however, comes at the cost of compilation complexity. The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, determine which ones can be honored under failures, and ensure policy compliance under all possible failure cases.

\begin{figure}[t!]
  \centering
  \includegraphics[width=.75\columnwidth]{figures/pipeline}
  \caption{Compilation pipeline stages for Propane.}
  \label{fig:pipeline}
  \vspace{-1em}
\end{figure}

We handle these challenges by breaking compilation into multiple stages and developing efficient algorithms for each (See Figure~\ref{fig:pipeline}). The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR). Policies in RIR are checked for well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation. Vendor-specific adaptors to translate from ABGP to concrete device configurations or to integrate with an existing template-based system are easily added. The \sysname compiler currently generates Quagga configurations by default.

\subsection{Regular IR (RIR)}
\label{sec:rir}

%Regular expressions are an expressive formalism that have been used extensively for describing paths through graphs~\cite{bib:todo}, with applications to networks~\cite{bib:todo}. Our regular expression language differs from others by allowing operators to describe preferences between paths.

% grammar
\newcommand{\BNFALT}{\;\;|\;\;}
\newcommand{\hdr}[2]{\flushleft \chdr{\hspace{5mm}#1}{#2}}
\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}

\begin{figure*}\small
  \begin{minipage}[t]{.45\linewidth}
  \hdr{\large Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
    \hline

     pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{preferences} \\
     x       &::=& a.b.c.d/n & \textit{prefix} \\
     c       &::=& \cdots & \textit{community value} \\
     t       &::=& \True & \textit{true} \\
         &\BNFALT& \NOT t & \textit{negation} \\
         &\BNFALT& t_1 \OR{} t_2 & \textit{disjunction} \\
         &\BNFALT& t_1 \AND{} t_2 & \textit{conjunction} \\
         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
         &\BNFALT& \textit{comm} = c & \textit{community test} \\
     r       &::=& n & \textit{AS number} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT(r) & \textit{path negation} \\
         &\BNFALT& r^* & \textit{repetition} \\
     l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
     cc     &::=& agg(x, l) \BNFALT tag(c, t, l) & \textit{control constraints} \\
  \end{array} \]

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}\small
  \hdr{\large Propane Expansions}{}
  \vspace*{-1\baselineskip}
  %
  \[\begin{array}{rcl}
    \hline
    \Any           & = & \Out^* \cdot \In^+ \cdot \Out^* \\
    \None          & = & \emptyset \\
    \Internal      & = & \In^+ \\
    \Only(X)       & = & \Any \cap X^* \\
    \Never(X)      & = & \Any \cap (!X)^* \\
    \Through(X)    & = & \Out^* \cdot \In^* \cdot X \cdot \In^* \cdot \Out^* \\
    \Later(X)      & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
    \Before(X)     & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
    \End(X)        & = & \Any \cap (\Sigma^* \cdot X) \\
    \Start(X)      & = & \Any \cap (X \cdot \Sigma^*) \\
    \Exit(X)       & = & (\Out^* \cdot \In^* \cdot (X \cap \In) \cdot \Out \cdot \Out^*) \cup \\
                  &        & (\Out^* \cdot \In^+ \cdot (X \cap \Out) \cdot \Out^*) \\
    \Enter(X)      & = & (\Out^* \cdot \Out \cdot (X \cap \In) \cdot \In^* \cdot \Out^*) \cup \\
                  &        & (\Out^* \cdot (X \cap \Out) \cdot \In^+ \cdot \Out^*) \\
    \LinkKW(X,Y)     & = & \Any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
    \PathKW(\vec{X}) & = & \Any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
    \Novalley(\vec{X}) & = & \Any ~ \cap \\
                  &   & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
                  &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
  \end{array} \]

  \end{minipage}

  \hrulefill

  \caption{Regular Intermediate Language (RIL) syntax (left), and
           Propane language expansions (right).}
  \label{fig:rir-syntax}
  \vspace{-1em}
\end{figure*}

\para{Syntax}
The \sysname FE is just a thin layer atop a core, regular-expression language (RIR) for describing preference-based path constraints. 
Figure~\ref{fig:rir-syntax} shows the RIR syntax. A policy consists of one or more constraints, each of which have a test on the type of route, and a corresponding set of preferred regular paths. Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS. Special \In{} and \Out{} symbols refer to any internal or external location respectively. In addition, $\Sigma$ refers to any symbol. We also use other standard abbreviations
for regular expressions such as $r^+$, which is simply syntactic sugar for $r \cdot r^*$, a sequence of one or more occurrences of $r$, when appropriate.
%% For example, the constraint
%% \[(\textit{prefix}=74.3.28.0/24) \Link \\
%% (as200 \cdot \In^+) \Prefer (as100 \cdot \In^+)
%% \]
%% describes a more-preferred set of paths for traffic announced by a prefix no less specific than \CD{74.125.28.0/24}, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same. The plus operator $\In^+$ stands for $\In \cdot \In^*$, at least one internal hop. Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.

\sysname also supports constraints purely on the control-plane behavior of BGP. For example, prefix aggregation is an important optimization to reduce routing table size and churn in practice. 
%% Aggregation, for example, from internal to external locations, is specified using the same regular syntax as before:
%% $$\Agg(128.17.0.0/16, \In \Link \Out)$$
%% where the expression $\In \Link Out$ refers to control messages flowing from any internal to any external location.
We list only the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, but we also support other constraints such as limiting the maximum number of routes allowed between ASes, or enabling BGP multipath.

\para{Semantics}

The semantics of RIR is in terms of ranked paths. Each preference-based regular path constraint (of the form $r_1 \Prefer \dots \Prefer r_j$) maps to a set of concrete paths in the network that match one of $r_i$. We denote a network path as a string of abstract locations (routers or external ASes) of the form: $n_1 n_2 \dots n_k$. A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$, that is the path is in the language of the regular expression, and $p$ is a topologically-valid path. We denote the length of a path $p$ as $\abs{p}$. A path $p$ will have a rank:
$$(\min_i \set{ p \in \mathcal{L}(r_i) }, \abs{p})$$
where the rank is lexicographically ordered according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the path length. Lower ranks indicate \emph{more} preferred paths. Traffic may be sent on any of the most preferred paths for each pair of starting and ending locations that appear in some specified path. There is an implicit lowest preference to drop traffic: $\emptyset$ when no other route is possible.

The set of ranked paths depends on which paths are valid in the topology, and thus when failures occur, the most preferred routes change. The \sysname compiler ensures that generated configurations for a policy always achieve the most preferred path possible given the failures in the topology, using only distributed mechanisms.

\para{Propane FE to RIR}

The main differences between the FE and RIR are: $i)$ FE allows the programmer to specify constraints using a series of (modular) definitions, and combine them later, $ii)$ FE provides high-level names that abstract sets of routes and groups of prefixes/neighbors, and $iii)$ FE allows the preference operator to be used more flexibly.

A key constraint when translating FE to RIR is to ensure that all specified routes are well-formed. In particular, each regular path constraint $r$ must satisfy $r \subseteq \Out^* \cdot \In^+ \cdot \Out^*$. This ensures that the user only control traffic that goes through the user's network at some point, and that such traffic does not loop back multiple times to the user network.

The translation from \sysname to RIR is based on a set of rewriting rules.
The first step merges separate constraints. It takes the cross product of per-prefix constraints, where logical conjunction ($a \AND b$) is replaced by intersection on regular constraints ($a \Intersect b$), logical disjunction is replaced by union, and logical negation ($\NOT a$) is replaced by ($\Any \cap \NOT(a)$), where $\Any$ ensures the routes are well-formed.
%
For example, in the data center configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:

%% \begin{lstlisting}[mathescape=true]
%% $\path{p_{g1}}{any \cap end(A)}$
%% $\path{p_{g2}}{any \cap end(B)}$
%% $\path{p_{l1}}{\neg enter(out) \cap end(E)}$
%% $\path{p_{l2}}{\neg enter(out) \cap end(F)}$
%% $\path{true}{exit(out)}$
%% \end{lstlisting}

\begin{code}
PG1 \Path \End(A)
PG2 \Path \End(B)
PL1 \Path \textbf{only}(\In) \Intersect \End(E)
PL2 \Path \textbf{only}(\In) \Intersect \End(F)
\True \Path \Exit(\Out)
\end{code}

The next step rewrites the high-level constraints such as \textit{enter} according to the equivalences in Figure~\ref{fig:rir-syntax}. Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression. For example, the regular expression $a \cdot (b \Prefer c) \cdot d$ is lifted to $(a \cdot b \cdot d) \Prefer (a \cdot c \cdot d)$ by distributing the preference over the sequence operator. In general, we employ the follwing distributivity equivalences:
%
\[ 
\begin{array}{c}
  x \odot (y_1 \Prefer \dots \Prefer y_n) = (x \odot y_1) \Prefer \dots \Prefer (x \odot y_n) \\
  (y_1 \Prefer \dots \Prefer y_n) \odot x = (y_1 \odot x) \Prefer \dots \Prefer (y_n \odot x)
\end{array}
\]
%
where $\odot$ stands for an arbitrary regular binary operator. Preferences nested under a unary operator, \textit{star} or \textit{negation}, are flagged by the compiler as invalid policies.

\subsection{Product Graph IR}

\newcommand{\state}[4]{\node[state,#3](#1)[#4]{#2};}
\newcommand{\transition}[4]{\path[->] (#1) edge [#4] node {#3} (#2);}

\begin{figure*}
  \begin{minipage}[t]{.5\linewidth}

  \hdr{\large Topology}{}
  \vspace*{-2\baselineskip}

  \includegraphics[width=.6\columnwidth]{figures/topology}

  \hdr{\large Policy Automata}{}
  \vspace*{-0.5\baselineskip}

  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.4cm,minimum size=1cm]
    \state{0}{$0$}{              }{}
    \state{1}{$1$}{right of=0}{}
    \state{2}{$2$}{right of=1}{}
    \state{3}{$3$}{right of=2}{}
    \state{4}{$4$}{right of=3}{}
    \state{5}{$5$}{right of=4}{accepting}
    \transition{0}{1}{out}{}
    \transition{1}{2}{D}{}
    \transition{2}{3}{C}{}
    \transition{3}{4}{A}{}
    \transition{4}{5}{W}{}
  \end{tikzpicture}

  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.6cm]
    \state{0}{$0$}{              }{}
    \state{1}{$1$}{right of=0}{}
    \state{2}{$2$}{right of=1}{}
    \state{3}{$3$}{right of=2}{}
    \state{4}{$4$}{right of=3}{accepting}
    \transition{0}{1}{out}{}
    \transition{1}{2}{in}{}
    \transition{2}{2}{A,C,D,E}{loop above}
    \transition{2}{3}{B}{}
    \transition{3}{3}{B}{loop above}
    \transition{3}{2}{A,C,D,E}{bend left}
    \transition{3}{4}{W}{}
  \end{tikzpicture}
  \end{minipage}
  %
  ~~
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{\large Product Graph IR}{}
  \vspace*{-1\baselineskip}
  %
  \includegraphics[width=.65\columnwidth]{figures/productgraph}
  \end{minipage}

  \hrulefill
  \vspace*{.4em}

  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
  \label{fig:example-compilation}
  \vspace{-1em}
\end{figure*}

Now that the user policy exists in a simplified form, we must consider topology. In particular, we want a compact representation that describes all the possible ways BGP route announcements can flow through the network subject to the policy and topology constraints. Our PGIR captures these dependencies by ``intersecting" each of the regular automata corresponding to the RIR path preferences, and the topology. Paths through the PGIR correspond to real paths through the topology that satisfy the user constraints.

%Finding paths through a graph subject to regular constraints has been studied extensively in the database literature~\ref{bib:todo}, and has been applied to networks in the past~\ref{bib:todo}.

\para{Formal definition}

% Formally define automata
The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$. While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., route announcements flowing in the opposite direction). To capture this idea, for each regular expression $r_i$, we construct a deterministic finite state machine on the reversed regular expression. Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$). The alphabet $\Sigma$ consists of all all abstraction locations (routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
%
% Formally define topology
The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon 2^{V \times V}$.
%
% Formally define product graph
The combined PGIR is a tuple: ($V'$, $E'$, $s$, $e$, $P$) with
vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
edges $E' \colon 2^{V' \times V'}$,
a unique starting vertex $s$,
a unique ending vertex $e$,
and a preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. 
Two nodes $x$ and $y$ \emph{shadow} each other in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$. That is, $x$ and $y$ shadow each other when they are different nodes in the PGIR that represent the same topology location.

\para{From RIR To PGIR}

% Formal product construction
Let $a_i$ and $b_i$ denote states in the regular policy automata.
The PGIR is constructed by adding an edge from $v_1 = (x, a_1, \dots, a_m)$ to $v_2 = (y, b_1, \dots, b_m)$ whenever $\sigma_i(a_i, y) = b_i$ for each $i$ and $(x,y) \in E$ is a valid topology link.
%
Additionally, we add edges from the start node $s$ to any $v = (x, a_1, \dots, a_m)$ when $\sigma_i(q_{0_i}, x) = a_i$ for each $i$.
%
The preference function $P$ for node $v = (x, a_1, \dots, a_m)$ is defined as $P(v) = \set{i~\vert~a_i \in F_i} $. That is, it records which preferences are achieved from each policy automaton for every node in the product construction.
%
Finally, there is an edge from each node in the PGIR such that $P(v) \neq \emptyset$ to the special end node $e$.

Intuitively, PGIR tracks which states of each automaton the policy is in as route announcements move between routers.
%
Consider the topology in Figure~\ref{fig:example-compilation}. Suppose we want a primary route from W that enters the network from $A$, and utilizes the A--C and C--D links. We also want a backup route that enters from $B$, and utilizes the B--C link, but is otherwise unconstrained. For simplicity, we assume that the route can end in either $X$, $Y$, or $Z$. The RIR for the policy is:
%
$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$$
%
Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
%
The figure also shows the PGIR after intersecting the topology and policy automata. Every path in it corresponds to a concrete path in the topology. In particular, every path through the PGIR that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
%
For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining the most prefered preference $1$.
BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton. This is reflected in the product graph by the node with state $(X,1,1)$. From here, if X were to advertise this route to D, it would result in the path $D \cdot X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
%
The ``--" state indicates the corresponding automaton can not accept the current path or any extension of it. Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates this path has preference 1.

\para{Minimization}

Before checking if policies captured by the PGIR are safe, we minimize the PGIR to improve our safety analysis. 
The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops. In particular, BGP's loop prevention mechanism forces an AS to reject any route for which it is already in the AS path.
%
For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path, leading to a path that satisfies the preference 1 policy, but which contains a loop.
%
It often improves the precision of the failure-safety analysis to eliminate cases that are not possible due to loops. 
%For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading to $y$ from the start node.
%We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it must go through another $W$ in either case.
Colored nodes and dashed edges are removed after minimization since they are irrelvant to the BGP decision process.
%
%Although fully minimizing this graph is an NP-complete problem,  a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.

%A node $x$ dominates $y$ if $x$ appears on every path leading to $y$ from a source node. Many efficient algorithms exist for finding graph dominators~\ref{bib:todo}. For minimization, we compute the dominator set for each node in both the product graph $G$ with respect to the start node, and in the reversed product graph $G^R$ with respect to the end node. The following rules enable efficient minimization of the product graph.
%
%\begin{itemize}
%  \item Remove nodes that never reach the end node
%  \item Remove nodes not reachable from the $start$ node
%  \item Remove any node $x$ such that $x$ is dominated by $y$ in $G$ or $G^R$, and $loc(x) = loc(y)$
%  \item Remove any edge from $x$ to $y$ in $G$ or $G^R$ if there is some node $z$ dominated by $y$ such that $loc(x) = loc(z)$
%\end{itemize}
%
%Repeated application of the above rules leads to removing the colored nodes and dashed lines in Figure~\ref{fig:example-compilation}.

\para{Failure Safety}

To implement path preferences in routing, BGP uses local preferences on a per-device basis. However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult, particularly in the presence of failures. For example, imagine an extremely simple policy for the topology in Figure~\ref{fig:example-compilation}, which says to prefer one route over another:
%
$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D}) \Prefer (\CD{W} \cdot \CD{B} \cdot \CD{C} \cdot \CD{E})$.
%

How could such a policy be implemented in BGP? Suppose we set the local preference at router $C$ to prefer $D$ over $E$, and use the BGP MED attribute to influence $W$ to prefer $A$ over $B$. This might work as expected under normal conditions, however, if the A -- C link fails, then suddenly $C$ has made the wrong decision. Traffic will now follow the
$W \cdot B \cdot C \cdot D$ path, even though this path was not specified by the policy. This is a violation of \emph{soundness}: The distributed implementation has used a route not specified by the policy. To make matters worse, the second preference $W \cdot B \cdot C \cdot E$ is available in the network but not being used. This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
We could solve the first problem by filtering routes that go through $D$ at $B$, however, we can not fix the second problem---$C$ has made the wrong choice. In fact, this policy can not be implemented in BGP in a way that is policy compliant under all failures.

%and can not get either the primary or backup route specified, despite the fact that the $W \cdot B \cdot C \cdot E$ path is available in the network.

At a first cut, any time a router must make a decision locally between several route options, there is the possibility it might choose incorrectly. The PGIR captures this notion of choice precisely. For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the PGIR, possibly receiving announcements from $X$ or $Y$. However, regardless of whether $D$ chooses a route from $X$ or $Y$, the set of paths allowed by the policy after going through $D$ will be the same in either case. This remains true despite any failures that might have occurred in the network. Thus $D$ can safely prefer $X$ and $Y$ equally.

The more challenging case is when a topology location occurs in mutliple contexts in the PGIR. For example, in the compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an announcement from $E$ and later achieve the backup path, or it can receive an announcement from its neighbor $D$ and later achieve either the primary or backup path. Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $E$? The important observation is that, if $C$ prefers $D$, then it is never worse off---it will always achieve at least as good a path as if it had choosen $E$.
For example, suppose $C$ chooses a route from $D$, but cannot achieve its primary path because the $A$ -- $W$ link has failed. In this case, the advertisement from $C$ will still be sent along towards the ultimate backup location $W$. Since the $(C,3,2)$ node has the same one-step and two-step next hops as node $(C,-,2)$ in the product graph, no possible failure will prevent a route advertisment from reaching $(W,-,4)$ that wouldn't have otherwise prevented it if $C$ had choosen $E$.

In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and enumerating all failures is intractable. We thus adopt a conservative analysis based on the observations above. The high-level idea is to order each PGIR node according to a \textit{can prefer} relation. For example, node $(C,3,2)$ can be preferred to node $(C,-,2)$, but not the other way around. Intuitively, a node $N_1$ can be preferred to another node $N_2$ when, for each preference $N_2$ might achieve, there is a better preference that $N_1$ will achieve regardless of failures. Formally this means that $N_1$ can be preferred to $N_2$ when:
%
$$\forall i, \exists j, j \leq i \wedge protect(G_j, N_1, G_i, N_2)$$
%
where \textit{protect} means that, from $N_1$ on the product graph restricted to nodes that can potentially achieve preference $j$ or better, 
there is always a path to each ending location whenever this is a path from $N_2$ restricted to $G_i$.

\begin{algorithm}[t!]
\caption{Failure Protection}
\label{alg:failures}
\begin{algorithmic}[1]
\Procedure{Protect($G_1$, $N_1$, $G_2$, $N_2$)}{}
  \If {$loc(N_1) \neq loc(N_2)$} \Return false
  \EndIf
  \State $q \gets Queue()$
  \State $q.Enqueue (N_1, N_2)$
  \While {$!q.Empty()$}
    \State $(n_1,n_2) \gets q.Dequeue()$
    \For {$x$ in adj($G_2$, $n_2$)}
      \If {\big($\exists y \in$ adj($G_1$,$n_1$), shadows $x$\big) \textbf{or} \\  
            \hspace{5.2em} \big($\exists y \in$ $G_1$, dominates $n_1$, shadows $x$\big)}
        \If {$(x,y)$ not marked}
          \State {mark $(x,y)$ as seen}
          \State $q.Enqueue(x,y)$
        \EndIf
      \Else { \Return $false$}
      \EndIf
    \EndFor
  \EndWhile
  \Return true
  \EndProcedure
\end{algorithmic}
\end{algorithm}

Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another. It walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step. 
When there is no equivalent step, the algorithm checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) that can protect against failures instead.
Thus any time $N_2$ can get to a final location for preference $i$, $N_1$ can get to at least the same final locations for a better preference $j$. The algorithm terminates since the number of related states $(x,y)$ that can be expolored is finite.

For each router in the topology, local preferences are now obtained by  sorting the corresponding PGIR nodes according to the \textit{can prefer} relation. If two nodes are incomparable, the compiler rejects the policy as unimplementable.

\para{Avoiding Loops}

The checks for failure safety described above overlook one critical point: Paths for a higher preference might not exist due to loops. To avoid this situation, the compiler checks that, when node $x$ protects against failures for node $y$, its does so without using any nodes that shadow another node that appears ``above'' $x$ in the PGIR. 
%It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
%even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$. To avoid this situation, the compiler conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the PGIR (i.e., nodes reachable from $x$ in $G_j^R$). It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.

\para{Aggregation-Induced Black Holes}
Because the \sysname compiler has the complete user policy and topology, it is also able to efficiently check that aggregates do not black hole traffic for up to $k$ failures. The algorithm for aggregation failure safety is detailed in Section~\ref{sec:black-holes} of the appendix.
\subsection{Abstract BGP}

%\begin{figure}[t!]
%\centering
%\includegraphics[width=.9\columnwidth]{figures/config}
%\caption{Abstract BGP configuration.}
%\label{fig:abgp-config}
%\end{figure}

\newcommand{\highlight}[1]{%
  \colorbox{red!50}{$\displaystyle#1$}}
\newcommand{\Router}[1]{\KW{Router} #1:}
\newcommand{\REGEX}[1]{\texttt{regex}(#1)}
\newcommand{\PEER}{\texttt{peer}}
\newcommand{\COMM}{\texttt{comm}}
\newcommand{\MED}{\texttt{MED}}
\newcommand{\Arrow}{\ensuremath{\leftarrow}}

%\begin{figure}[t!]
%\begin{lstlisting}[frame=single, mathescape=true]
%$\Router{A}$
%  Match $\PEER=C$
%    Export $\MED \leftarrow 80, \PEER \leftarrow W$
%$\Router{B}$
%  Match $\PEER = C$
%    Export $\COMM \leftarrow \text{noexport}, \MED \leftarrow 81, \PEER \leftarrow W$
%$\Router{C}$
%  Match$[LP=99]$ $\PEER = E $
%    Export $\PEER \leftarrow B$
%  Match $\PEER = D$
%    Export $\PEER \leftarrow A,B$
%$\Router{D}$
%  Match $\REGEX{X + Y}$
%    Export $\PEER \leftarrow C$
%$\Router{E}$
%  Match $\REGEX{Z}$
%    Export $\PEER \leftarrow C$
%\end{lstlisting}
%\label{fig:config-min}
%\caption{Abstract BGP minimized configurations}
%\end{figure}

The final stage of our compiler translates policies from PGIR to a vendor-neutral abstraction of BGP (ABGP).
% and then from ABGP to actual device configurations.

\para{From PGIR to ABGP}

Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward. The idea is to encode the state of the automaton using BGP community values. Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR. For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else). If it sees such an announcement, it will remove the old community value, and add a new one for state $(4,2)$ before exporting it to $W$.

To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR. For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.

Since the compiler is only able to control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes. Instead, it translates matches from external ASes into a BGP regular expression filter. For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$. In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters. The unknown AS topology is modelled as a special node in the PGIR that generates a filter to match any sequence of ASes.

Finally, the external AS $W$ should prefer our internal router $A$ over $B$. In general, it is not possible to reliably control traffic entering the network beyond certain special cases. In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$. Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic. The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology. 
%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default. Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.

After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on. In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from. Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.

\begin{figure}[t!]
%% \begin{lstlisting}[frame=single, mathescape=true]
%% $\Router{A}$
%%   Match $\PEER=C, \COMM=(3,2)$
%%     Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
%% $\Router{B}$
%%   Match $\PEER = C, \COMM = (-,2)$
%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
%%            $\MED \leftarrow 81, \PEER \leftarrow W$
%%   Match $\PEER = C, \COMM = (3,2)$
%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
%%            $\MED \leftarrow 81, \PEER \leftarrow W$
%% $\Router{C}$
%%   Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
%%   Match $\PEER = D, \COMM = (2,2)$
%%     Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
%% $\Router{D}$
%%   Match $\REGEX{X + Y}$
%%     Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
%% $\Router{E}$
%%   Match $\REGEX{Z}$
%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
%% \end{lstlisting}
\begin{code}
  \Router{A}
    Match \PEER=C, \COMM=(3,2)
      Export \COMM \Arrow (4,2), \MED \Arrow 80, \PEER \Arrow W
  \Router{B}
    Match \PEER = C, \COMM = (-,2)
      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
             \MED \Arrow 81, \PEER \Arrow W
    Match \PEER = C, \COMM = (3,2)
      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
             \MED \Arrow 81, \PEER \Arrow W
  \Router{C}
    Match[LP=99] \PEER = E, \COMM = (-,2) 
      Export \COMM \Arrow (-,2), \PEER \Arrow B
    Match \PEER = D, \COMM = (2,2)
      Export \COMM \Arrow (3,2), \PEER \Arrow A,B
  \Router{D}
    Match \REGEX{X + Y}
      Export \COMM \Arrow (2,2), \PEER \Arrow C
  \Router{E}
    Match \REGEX{Z}
      Export \COMM \Arrow (-,2), \PEER \Arrow C
  \end{code}
  \vspace{-2em} 
  \caption{Abstract BGP router configurations. \label{fig:abgp-config}}
  \vspace{-1em}
\end{figure}

%=====================================================
%
%
%  **Implementation**
%
%
%=====================================================

\section{Implementation}
\label{sec:implementation}

We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code. The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates. Since each prefix has a separate routing policy, the \sysname compiler is able to compile each routing policy in parallel. The current compiler produces only ABGP policies, which can be incorporated into an existing template-based system, for example by mixing the \sysname configuration with other configuration components, or by generating vendor-specific configurations.

\para{PG construction}

Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\cite{regex-complexity}. The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently. Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy. Similarly, to model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.
%
Rather than construct the product graph in full, our implementation prevents exploring parts of the graph when no accepting state is reachable in any of the corresponding regular automata during construction.

%\para{PG Minimization}

%The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\cite{fast-dominance}. More complex algorithms with better theoretical complexity exist~\cite{linear-dominance, tarjan-dominance} and may be better suited for large enough topologies. All minimization steps are repeated until no more progress can be made.

\para{Failure Safety}

When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the \textit{protect} function. That is, whenever for two states $n_1$ and $n_2$ we compute $protect(G_j, n_1, G_i, n_2)$, if the function evaluates to $true$, then each of the intermediate related states $x$ and $y$ must also satisfy $protect(G_j, x, G_i, y)$. Memoizing these states significantly cuts down the amount of work that needs to be in the common case.

\para{Configuration generation}

The naive code generation algorithm described in Section~\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair for every node in the product graph before minimization. Our implementation performs partial minimization during generation by recognizing common cases where there is no restriction on exporting to or importing from neighbors.

%=====================================================
%
%
%  **Evaluation**
%
%
%=====================================================

\begin{figure}
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-dc.png}}
  \subcaptionbox{Backbone network}
    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
  \caption{Compilation time. \label{fig:compilation-times}}
  \vspace{-1em}
\end{figure}

\section{Evaluation}
\label{sec:evaluation}

We apply \sysname on real policies for backbone and data center networks. Our mains goals are to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.

\subsection{Networks studied}

We obtained routing policy for the backbone network and for the data centers of a large cloud provider. Multiple data centers share this policy. The backbone network connects to the data centers and also has many external BGP neighbors. The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for data center routers or actual configurations for the backbone network (where templates are not used because the network has less regular structure).

The networks have the type of policies that we outline earlier (\S\ref{sec:motivation}). The backbone network classifies external neighbors into several different categories and prefers paths through them in order. It does not want to provide transit among certain types of neighbors. For some neighbors, it prefers some links over the others. It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA). Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, etc.

All routers in the datacenter network run BGP using a private AS number and peer with each other and with the backbone network over eBGP. The routers aggregate prefixes when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region. They also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.

\begin{figure}
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
  \subcaptionbox{Backbone network}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
  \caption{Configuration minimization. \label{fig:config-min}}
  \vspace{-1em}
\end{figure}

\subsection{Expressiveness}

We found that we could translate all network policies to \sysname. We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname. The data center operator said that he found the language intuitive. The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We found that the data center policies were correctly translated. For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.

Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.

\subsection{Compilation time}

%\begin{figure}[t!]
%  \centering
%  \begin{minipage}[b]{0.45\linewidth}
%    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-dc.png}
%  \end{minipage}
%  \quad
%  \begin{minipage}[b]{0.45\linewidth}
%    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-backbone.png}
%  \end{minipage}
%  \caption{Compilation times.}
%  \label{fig:compilation-times}
%\end{figure}

%\begin{figure}[t!]
%  \centering
%  \begin{minipage}[b]{0.45\linewidth}
%    \includegraphics[width=1.1\columnwidth]{figures/config-compression-dc.png}
%  \end{minipage}
%  \quad
%  \begin{minipage}[b]{0.45\linewidth}
%    \includegraphics[width=1.1\columnwidth]{figures/config-compression-backbone.png}
%  \end{minipage}
%  \caption{Configuration minimization.}
%  \label{fig:config-minimization}
%\end{figure}

We study the compilation of time for both policies as a function of network size. Even though the networks we study have a fixed topology and size, we can explore the impact of size because our converted policies are network-wide and the compiler takes topology itself as an input. For the data center network, we build and provide as input fat tree~\cite{fattree} topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy. We take this approach to smoothly explore different sizes. 
%There is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete data center topologies. For a given size, our reported results match those for the concrete topologies.

For the backbone network, the internal topology does not matter since all routers connect in a full iBGP mesh. We explore different mesh sizes and randomly map neighboring networks to routers. Even though each border router connects to many external peers, we count only the mesh size.

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes. For both policies, we measure the mean compilation time per prefix since the compiler operates on each prefix in parallel. At their largest sizes, the per-prefix compilation time is roughly 10 seconds for the data center network and 45 seconds for the backbone network.

%From the break down of the time by compilation phase, we see that no single compilation phase dominates the running time of the compiler. However, construction and minimization of the product graph take the most time.

Total compilation for the largest data center is less than 9 minutes total. Unlike the data center policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases. Compilation for the largest backbone network, takes less than 3 minutes total. The inclusion of more preferences in the backbone policy increases the size of the PGIR, which leads to PGIR construction and minimization taking proportionally more time.

%

\subsection{Configuration size}

Figure~\ref{fig:config-min} shows the size of the compiled ABGP policies as a function of the topology size. The naive translation of PGIR to ABGP outlined in \S\ref{sec:compilation} generates extremely large ABGP policies by default. To offset this, the compiler performs ABGP configuration minimization both during and after the PGIR to ABGP translation phase.
%Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
Minimization is highly effective for both the data center and backbone policies. In all cases, minimized policies are a small fraction of the size of their non-minimized counterparts.

%for i in *.set; do grep bgp $i | wc; done
However, even minimized configurations are hundreds or thousands of lines per router. For the backbone network, the size of \sysname configurations is roughly similar to the BGP components of actual router configurations, though qualitative differences exist (see below). We did not have actual configurations for the data center network; they are dynamically generated from templates.

\subsection{Propane vs. operator configurations}

Finally, we comment briefly on how \sysname-generated configurations differ from configurations or templates generated by operators.
%
In some cases, \sysname configurations are similar. For example, preferences among neighboring ASes are implemented with a community value to tag incoming routes according to preference, which is then used at other border routers to influence decisions.

In other cases, the \sysname configurations are different, relying on a different BGP mechanism to achieve the same result. Some key differences that we observed were:

$i)$ operators used the no-export community to prevent routes from leaking beyond a certain tier of the datacenter, while \sysname selectively imported the route only below the tier;
%\sysname could use a similar implementation mechanism in the future as an optimization.

$ii)$ operators prevented unneeded propagation of more-specific route announcements from a neighboring AS based on their out-of-band knowledge about the topology, whereas \sysname propagated these advertisements; and

$iii)$ operators used a layer of indirection for community values, using community groups and re-writing values, to implement certain policies in a more maintainable manner, where \sysname uses flat communities.

We are currently investigating if such differences matter to operators (e.g., if they want to read \sysname configurations) and, if necessary, how to reduce them.

%=====================================================
%
%
%  **Related Work**
%
%
%=====================================================

\section{Related Work}
\label{sec:related}

\paragraph*{SDN Languages}
\sysname{} was heavily influenced by recent SDN programming
languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire}, 
as well as path queries~\cite{queries}.
Each of these languages is oriented around regular expressions, which
describe paths through a network, and predicates, which classify packets.
In particular, FatTire allows programmers to define sets of paths together
with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
and the compiler will generate appropriate OpenFlow rules.
\sysname is more expressive as it allows users to specify preferences among
paths and it generates distributed implementations that tolerate any number of faults. 
Because FatTire generates data plane rules up front, 
specifying higher levels of fault tolerance comes
at the cost of generating additional rules that tax switch memory.  
In contrast, \sysname uses traditional distributed
control plane mechanisms to react to faults, which do not impose additional memory cost.
Because of the differences in the underlying technology, the analyses
and compilation algorithms used in \sysname are quite different from
previous work on SDN. 
Finally, in addition to using path-based abstractions
for intra-domain routing, \sysname uses them for inter-domain routing as
well, unlike any existing SDN language.

\paragraph*{Configuration Automation}
Many practitioners use configuration templates~\cite{hatch,thwack}, to ensure certain kinds of consistency across similar devices. In addition, configuration languages such as RPSL~\cite{RFC2622}, Yang~\cite{RFC6020}, and Netconf~\cite{RFC6241} allow operators to express routing policy in a vendor-neutral way. 
However, all of these solutions remain low-level, for example, requiring operators to specify exact local preferences. Unlike \sysname, there is no guarantee that these low-level configurations satisfy the original, high-level intent.

\paragraph*{Configuration Analysis}  
The notion that configuring network devices is difficult and error-prone is not new.  
Past researchers have tried to tackle this problem by analyzing existing
firewall configurations~\cite{fang,lumeta,margrave} and
BGP configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe} and reporting errors or inconsistencies when they are detected.
Our research is complementary to these analysis
efforts.  We hope to eliminate bugs by using higher-level
languages and a ``correct-by-construction''
methodology.  By proposing network administrators write configurations
at a high-level of abstraction, a whole host of low-level errors can be avoided.

\paragraph*{Configuration Synthesis}
ConfigAssure~\cite{narain:lisa05,narain+:configassure}
is another system designed to
help users define and debug low-level router
configurations.  Inputs to
ConfigAssure include a \emph{configuration database}, which contains a
collection of tuples over constants and configuration variables, and a
\emph{requirement}, which is a set of constraints.  
%For instance, the tuple \texttt{hsrp(rexa,rA1,int(1),int(2))} states that interface
%\texttt{rA1} on device \texttt{rexa} belongs to the HSRP group defined
%by configuration variable \texttt{int(1)} with virtual IP address
%defined by configuration variable \texttt{int(2)}.  The constraint
%\texttt{hsrp\_subnet([rexa-rA1,rexb-rB1])} states that a database
%contains tuples defining HSRP group identifiers and virtual IPs for
%interfaces \texttt{rA1} and \texttt{rB1} on devices \texttt{rexa} and
%\texttt{rexb}.  
The authors use a combination of logic programming and
SAT solving to find concrete values for configuration variables.
%such as \texttt{int(1)}.  
ConfigAssure handles configuration for a wide range of protocols and many
different concerns.  In contrast, the scope of \sysname is much
narrower.  In return, \sysname offers compact, higher-level
abstractions customized for our domain, such as regular paths, as well
as domain-specific analyses customized to those abstractions, such as
our failure safety analysis.  The implementation technology is also
entirely different, as we define algorithms over automata and graphs
as opposed to using logic programming and SAT-based model-finding.

%We also believe the high-level, centralized nature of \sysname policies
%has the benefit of making configurations
%easier to understand and maintain.

%=====================================================
%
%
%  **Future Work**
%
%
%=====================================================

\section{Future Work}

There are a number of possible directions for future work in programming distributed control planes. One option would be to integrate a model of the environment into the compiler. For example, many ASes make use of informal peering agreements (e.g., tagging routes with certain communities) to enable a wider range of policies. A compiler with this information, could automatically derive routes conforming to these agreements. 
%
Another direction would be to perform policy verification at the level of centralized language. There has been great deal of work on verification of the data plane, but much less so on control plane verification. The \sysname language provides a high-level abstraction of the control plane, which could be amenable to verification or checking equivalence of policies. For example, an operator could check if adding aggregation at various points in the network as an optimization ever changes routing behavior. The automata-based representation of the product graph may lend itself well to this kinds of analysis.
%
While we target BGP in this paper as a distributed backend for \sysname due to its expressiveness, scalability, and uniformity, it should be possible to use other protocols to achieve different types of routing policies (e.g., OSPF). In particular, one could potentially combine different distributed routing protocols through route redistribution to achieve a larger variety of policies.
%
Another possible future direction is automate AS-wide load balancing for BGP. Load-balancing with BGP across external ASes is difficult since there are few mechanisms at the operators disposal. However BGP policies can artificially prepend to the AS path to increases its length, and influence peer decisions. The product graph representation describes, not only which neighbors routers should prefer, but also which neighbors it is indifferent towards. Thus the compiler knowns when it can safely perform load-balancing across different neighbors.

%=====================================================
%
%
%  **Conclusions**
%
%
%=====================================================

\section{Conclusions}
\label{sec:conclusions}

In this paper, we introduced \sysname, a language and compiler for implementing centralized network policies using a distributed set of devices running BGP. Propane allows operators to describe network-wide intent directly through high-level constraints on the shape and relative preferences of paths for different types of traffic. When \sysname compiles a policy, then the resulting BGP configurations are correct-by-construction, faithfully implementing the centralized policy in a distributed fashion, regardless of failures.

%=====================================================
%
%
%  **Appendix**
%
%
%=====================================================

\section*{Appendix}
\label{sec:appendix}

\renewcommand\thesubsection{\Alph{subsection}}

\subsection{Aggregation-Induced Black Holes}
\label{sec:black-holes}

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/aggregation}
  \caption{Aggregation safety.}
  \label{fig:aggregation-safety}
  \vspace{-1em}
\end{figure}

As demonstrated with Example 2 in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur. Deciding when this can happen requires knowledge of the routing policy and not just the topology. For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated, even if there are several available in the toplogy. If that link fails, a black hole might be introduced. Fortunately, the PGIR captures the information about both the policy and topology precisely.
%, describing the how information meeting the policy flows over the topology.

We frame the aggregation problem as a problem of connectivity in the PGIR. Specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures that would disconnect where the prefix originates from where its more specific aggregate is located. The difficulty is that the same links in the topology can appear in multiple places in the PGIR. We adopt the following simple strategy to lower bound the number of failures: $i)$ Pick a random start-to-end path in PGIR, $ii)$ remove all edges in the PGIR for the set of topological edges chosen, and $iii)$ repeat until no such path exists.
The number of PGIR paths that we are able to remove is a lower bound on the number of failures required to disconnect the prefix from its aggregate.

For example, imagine we use the data center example from \S\ref{sec:motivation}, with the policy: 
\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the network topology and a simplified PGIR. Since the compiler knows an aggregate will be placed at $X$, and it knows that, the route for \CD{PG1} will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first. We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR, though in this case there are none. Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}. This process is repeated for other aggregation locations (e.g., $Y$).

\subsection{Propane Properties}

\newtheorem{prop}{Proposition}[section]

%Here we investigate the correctness and expressiveness properties of \sysname. We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures? (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?

%If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario. We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges. We argue that \sysname is correct by breaking down the claim:

\begin{prop}
BGP configurations for internal routers produced by \sysname will be stable. 
\end{prop}

\begin{prop}
BGP configurations produced by \sysname are \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.
\end{prop}
%
%The Soundness claim follows directly from compilation of the product graph. Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations are Sound. 
%
\begin{prop}
BGP configurations produced by \sysname are \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
\end{prop}
%
%The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.  This means there is a valid path in the product graph corresponding to this path, and which is available in the network. 
%Assume we are unable to achieve this route in the network. To not achieve this path means that some router along the advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead. This implies that router that makes the ``wrong'' choice appears as a separate node in the product graph. However, from our failure safety check, we know that the other, more-preferred node must have a superset of the paths to accepting states as the less preferred node (from which it stole the route) for at least as good of a final preference. The argument then proceeds by induction on the path length - there are only a finite number of such stealings that can occur, each of which will ultimately still result in a route advertisement reaching $X$ along a most preferred path.
%
%Any \sysname-compiled policy will be \textit{Complete} as a result of the failure safety check.
%

%

%The combination of Soundness and Completeness ensures that the distributed implementation will always send traffic along the best paths possible, yet will also never also use any undesired paths. These properties rely on the fact that \sysname produces stable BGP configurations:

%
%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo} for stable BGP. In particular, any policy with a dispute wheel will not pass the stronger failure safety check by \sysname.
%
%\begin{figure}[t!]
%\includegraphics[width=\columnwidth]{figures/dispute-wheel}
%\label{fig:dispute-wheel}
%\caption{Product graph for a dispute wheel.}
%\end{figure}
%
%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}. If a set of BGP configurations do not have a dispute wheel, then they will converge to their best routes. Any BGP policy with a dispute wheel will not satisfy the failure safety condition in Section~\ref{sec:compilation}. Assume that the preferences in the policy describe a dispute wheel, and we will show that our failure check will reject the policy. Informally, a dispute wheel occurs when there are some number of nodes $u_1, \dots, u_n$ attempting to get a path to a destination node $d$. Each node $u_i$ prefers to go through its neighbor $u_{i+1}$ over route $R_i$ than directly to $d$ with route $Q_i$. Thus the nodes form a wheel of preferences. The product graph for a policy that contains a dispute wheel will look like Figure~\ref{fig:dispute-wheel}, which shows a dispute wheel of size 3. In order to pass the failure safety check for the compiler, the more-preferred node for $u_2$ will need to have a superset of the paths starting from the less-preferred node for $u_2$. In turn, this means that the maximum length path after visiting the more preferred $u_2$ will be $max(Z) = 1 + max(Y)$, similarly, if we look at $u_1$, we will determine that $max(Y) = 1 + max(X)$, and so on. The resulting equations define a system of unsatisfiable equations. Therefore, it is not possible for \sysname to compile a BGP policy that contains a dispute wheel. Since no-dispute-wheel is a sufficient condition for BGP stability, any compiled \sysname policy will be stable.
%

%An important distinction is that BGP might still be instable with respect to other external ASes, since \sysname has no way of configuring their routing policy and can only rely on AS path filters to see what advertisements are observed.

%=====================================================
%
%
%  **Bibliography**
%
%
%=====================================================

\bibliographystyle{abbrv}
\bibliography{references}

% The bibliography should be embedded for final submission.

\end{document}

### 2016-06-07 paper/v2/paper.tex
adding revisions to paper

--- 2016-06-07 paper/v2/paper-edited.tex
@@
 %\usepackage{geometry}
-
-\usepackage{balance}
 
@@
 We use \sysname to specify and compile the configurations of real
-data center and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds to thousands of routers.
+data center and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds of routers.
 
@@
 community's response to the difficulty of maintaining policy
-compliance through distributed device interactions~\cite{ethane}. 
-Instead of organizing networks around a distributed 
-collection of devices that compute forwarding tables through
+compliance through distributed device interactions~\cite{ethane}. Indeed, instead of organizing networks
+around a distributed collection of devices that compute forwarding tables through
 mutual interactions, the devices are told how to
@@
 algorithms that translate the regular policies to a graph-based
-intermediate representation and from there to per-device BGP configurations, which include various filters and preferences that govern BGP behavior.
+intermediate language and from there to per-device BGP configurations, which include various filters and preferences that govern BGP behavior.
 %import and export filters, local preferences, MED attributes, and community tags.
@@
 It prefers to exchange traffic with \CD{Cust} over \CD{R1} rather than \CD{R2} because \CD{R1} is cheaper (P3).
-To guard against another AS "hijacking" prefixes owned by \CD{Cust}, the network only sends traffic to a neighbor if \CD{Cust} is on the AS path (P4).
+To guard against another AS "hijacking" prefixes owned by \CD{Cust}, it only sends traffic to them if \CD{Cust} is on the AS path (P4).
 Finally, to guard against \CD{Cust} accidentally becoming a transit for \CD{Prov}, it does not use \CD{Cust} for traffic that will later traverse \CD{Prov} (P5).
@@
 \CD{Cust}-facing interface should be lower than that at
-\CD{R1}. Implementing P3 properly will require MEDs to be appropriately configured on \CD{R1} and \CD{R2}. 
+\CD{R1}. Implementing P3 properly will require MEDs to be appropriately configured. 
 To implement P2, the operators can assign communities that
@@
 \CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links.
-Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based import and export filters at each router.
+Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based filters at each router.
 
@@
 small example network manually; devising correct configurations for real networks can quickly become a nightmare.
-Such networks have many neighbors spanning multiple commercial-relationship classes, differing numbers of links to each neighbor, along with several neighbor- or prefix-based exceptions to the default behavior.
+Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several neighbor- or prefix-based exceptions to the default behavior.
 A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
@@
 But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{route-aggregation}.
-If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce \CD{PG} externally.
+If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce the \CD{PG} externally.
 This announcement will bring to X traffic for \CD{PG1} as well, but because of valley-free filtering, X does not have a valid route for \CD{PG1} and will thus drop all traffic to it.
@@
 compiler treats such under-specifications as constraints on the set of
-allowed paths and automatically computes valid sets based on the topology.
+allowed paths and automatically computes valid sets based on topology.
 %
@@
 language as well as our strategy for compiling \sysname policies to
-BGP is defined in \S\ref{sec:compilation}.
+BGP is defined in the next section.
 
@@
 \begin{code}
-\Define Prefs = \Exit(R1 \Prefer R2 \Prefer Peer \Prefer Prov)
+\Define ExitCust = \Exit(R1 \Prefer R2)
 \end{code}
@@
 all paths (and only those paths) for which traffic exits our network
-through either router \CD{R1}, router \CD{R2}, \CD{Peer}, or \CD{Prov}.  
-The paths that exit through \CD{R1}
-are preferred (\Prefer) to those that exit through \CD{R2}, which are preferred to those that 
-leave through \CD{Peer} and so then \CD{Prov}.  As we
+through either router \CD{R1} or \CD{R2}.  The paths that exit through \CD{R1}
+are preferred (\Prefer) to those that exit through \CD{R2}.  As we
 describe in the next section, the \Exit\ predicate, as well as other
@@
 we assume we have already defined predicates \CD{PCust} for the
-customer prefixes.
-%and \CD{PInt} for our internal prefixes.
+customer prefixes and \CD{PInt} for our internal prefixes.
 In the following code, ranked paths are associated with
-customer prefixes,
+customer prefixes, internal prefixes,
 and all other prefixes (\CD{true}).\footnote{Policy statements are processed in
@@
 policy statements.  Hence, when the prefix predicate \True{} follows
-the statement involving \CD{PCust}, it is interpreted as
-\CD{\True{} \AND{} \NOT{}PCust}.}
+statements involving \CD{PCust} and \CD{PInt}, it is interpreted as
+\CD{\True{} \AND{} \NOT{}PCust \AND{} \NOT{}PInt}.}
 
@@
 \Define Routing = 
-    \{PCust \Path Prefs \AND \End(Cust)
-     \True  \Path Prefs \}
+    \{PCust \Path ExitCust \Prefer \End(Cust)
+     PInt  \Path \End(\In)
+     \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)\}
 \end{code}
 \noindent
-
 Line 2 of this policy 
-restricts traffic destined to known customer prefixes (\CD{PCust}) to only follow paths that end at the customer.
-In addition, it enforces the network-wide preference that traffic leaves through \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
-%defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
-%that connections to the customer through both routers fail,
-%a backup route (\CD{\End(Cust)}) is defined that admits traffic along
-%any path (including those through other networks) that ends at the customer.
-%Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.
-Line 3 applies to any other traffic, and allows the traffic to leave through any direct neighbor with the usual preferences of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
-To summarize our progress, the \CD{Routing} policy
+defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
+that connections to the customer through both routers fail,
+a backup route (\CD{\End(Cust)}) is defined that admits traffic along
+any path (including those through other networks) that ends at the customer.
+Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \In{} represents any location
+inside the user's network and the keyword \Out{} represents any location
+outside the user's network.
+Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers. To summarize our progress, the \CD{Routing} policy
 implements P1, P3, and P4 from Figure~\ref{fig:example1}.
@@
 disjunction (\OR) and negation (\NOT) of constraints. 
-First, we create reusable abstractions for describing traffic that transits our network. In \sysname, this is done by creating a new parameterized definition.
+%union (\Union), intersection (\Intersect), and negation (\NOT) to
+%specify the appropriate sets of paths.
+%
+%% \begin{lstlisting}[mathescape=true]
+%% define PP = Peer or Prov
+%% define PPTransit = $enter(PP) \AND exit(PP)$
+%% define CustTransit = $later(Cust) \AND later(Prov)$
+
+%% define NoTransit = {
+%%     $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
+%% }
+%% \end{lstlisting}
 \begin{code}
-\Define transit(X,Y) = \Enter(X \OR Y) \AND \Exit(X \OR Y)
-\Define cust-transit(X,Y) = \Later(X) \AND \Later(Y)
+\Define PP = Peer \OR Prov
+\Define PPTrans   = \Enter(PP) \AND \Exit(PP)
+\Define CustTrans = \Later(Cust) \AND \Later(Prov)
+\Define NoTrans   = \{\True \Path \NOT{}PPTrans \AND \NOT{}CustTrans\}
 \end{code}
 \noindent
-Here we define transit traffic between $X$ and $Y$ as traffic that enters the network through $X$ or $Y$ and then leaves the network through $X$ or $Y$.
-Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network.
-Using these two new abstractions, we can now implement policies P2 and P5 with the following constraint.
-
-\begin{code}
-\Define NoTrans = 
-  \{\True \Path \NOT{}transit(Peer,Prov) \AND 
-           \NOT{}cust-transit(Cust,Prov)\}
-\end{code}
-\noindent
-The \CD{NoTrans} constraint above requires that all traffic not follow a path that transits the network between \CD{Peer} and \CD{Prov}.
-Additionally, it prevents traffic from ever following paths that leave our network and later pass through both \CD{Prov} and \CD{Cust}.
+The \CD{NoTrans} constraint above says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}.
+Similarly it prevents traffic from ever following paths that leave our network and later passing through both \CD{Prov} and \CD{Cust}.
 To implement both \CD{Routing}
@@
 Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location.
-The special keyword \Out{} represents any location outside the user's network, and the keyword \In{} represents any location inside the network.
 For the second constraint, we can define another policy:
@@
 
-As before, once \sysname compiles the policy, it is guaranteed to be policy-compliant under all possible failure scenarios.
-In addition, \sysname will efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.
+As before, once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. \sysname also ensures safety against aggregation-induced black holes.
 %It can efficiently determine a lower bound on the number of failures necessary to black hole traffic given the user's policy, topology, and placement of specific aggregates.
@@
 Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation.
-Vendor-specific adaptors to translate from ABGP to concrete device configurations or to integrate with an existing template-based system are easily added.
-The \sysname compiler currently generates Quagga configurations by default.
+Vendor-specific adaptors to translate from ABGP to concrete device configurations are easily added to generate concrete configurations.
 
@@
 We also use other standard abbreviations
-for regular expressions such as $r^+$, which is simply syntactic sugar for $r \cdot r^*$, a sequence of one or more occurrences of $r$, when appropriate.
+for regular expressions such as $r^+$, a sequence of one or more occurrences
+of $r$, when appropriate.
 %% For example, the constraint
@@
 %
-%  **Future Work**
-%
-%
-%=====================================================
-
-\section{Future Work}
-
-There are a number of possible directions for future work in programming distributed control planes.
-One option would be to integrate a model of the environment into the compiler.
-For example, many ASes make use of informal peering agreements (e.g., tagging routes with certain communities) to enable a wider range of policies.
-A compiler with this information, could automatically derive routes conforming to these agreements.
-%
-Another direction would be to perform policy verification at the level of centralized language.
-There has been great deal of work on verification of the data plane, but much less so on control plane verification.
-The \sysname language provides a high-level abstraction of the control plane, which could be amenable to verification or checking equivalence of policies.
-For example, an operator could check if adding aggregation at various points in the network as an optimization ever changes routing behavior.
-The automata-based representation of the product graph may lend itself well to this kinds of analysis.
-%
-While we target BGP in this paper as a distributed backend for \sysname due to its expressiveness, scalability, and uniformity, it should be possible to use other protocols to achieve different types of routing policies (e.g., OSPF).
-In particular, one could potentially combine different distributed routing protocols through route redistribution to achieve a larger variety of policies.
-%
-Another possible future direction is automate AS-wide load balancing for BGP.
-Load-balancing with BGP across external ASes is difficult since there are few mechanisms at the operators disposal.
-However BGP policies can artificially prepend to the AS path to increases its length, and influence peer decisions.
-The product graph representation describes, not only which neighbors routers should prefer, but also which neighbors it is indifferent towards.
-Thus the compiler knowns when it can safely perform load-balancing across different neighbors.
-
-%=====================================================
-%
-%
 %  **Conclusions**

### 2016-06-08 paper/v2/paper-edited.tex
more edits

@@
 For example, to begin specification of the backbone
-network from the previous section, we first express the idea that for routes leading to our customer,
-we prefer using \CD{R1} over \CD{R2} (policy P3 from Figure~\ref{fig:example1}):
+network from the previous section, we first express the idea that 
+we prefer that traffic leave the network through \CD{R1} over \CD{R2} (to \CD{Cust}) over \CD{Peer} over \CD{Prov} (policy P3 from Figure~\ref{fig:example1}):
 %\begin{lstlisting}[mathescape=true]
@@
 are preferred (\Prefer) to those that exit through \CD{R2}, which are preferred to those that 
-leave through \CD{Peer} and so then \CD{Prov}.  As we
+leave through \CD{Peer} and then \CD{Prov}.  As we
 describe in the next section, the \Exit\ predicate, as well as other
@@
 language.
-
-% DAVE CONVERSIONS
-% C_{pfx} ===> PCust
-% I_{pfx} ===> PInternal
+The preference operator (\Prefer) is flexible and can be used between constraints as well as among individual routers.
+For example, the above constraint could have been written equivalently as
+\Exit(\CD{R1}) \Prefer \ldots \Prefer ~\Exit(\CD{Prov})
 
@@
 customer prefixes,
-and all other prefixes (\CD{true}).\footnote{Policy statements are processed in
+and all other prefixes (\CD{true}). Policy statements are processed in
 order with earlier policy statements taking precedence over later
-policy statements.  Hence, when the prefix predicate \True{} follows
+policy statements. Hence, when the predicate \True{} follows
 the statement involving \CD{PCust}, it is interpreted as
-\CD{\True{} \AND{} \NOT{}PCust}.}
+\CD{\True{} \AND{} \NOT{}PCust}.
 
@@
 %Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.
-Line 3 applies to any other traffic, and allows the traffic to leave through any direct neighbor with the usual preferences of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
+Line 3 applies to any other traffic not matching \CD{PCust} and allows the traffic to leave through any direct neighbor with the usual preferences of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
 To summarize our progress, the \CD{Routing} policy
@@
 \noindent
-Here we define transit traffic between $X$ and $Y$ as traffic that enters the network through $X$ or $Y$ and then leaves the network through $X$ or $Y$.
+Here we define transit traffic between groups of neighbors $X$ and $Y$ as traffic that enters the network through some neighbor in $X$ or $Y$ and then leaves the network through some neighbor in either $X$ or $Y$.
 Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network.
@@
 The \CD{NoTrans} constraint above requires that all traffic not follow a path that transits the network between \CD{Peer} and \CD{Prov}.
-Additionally, it prevents traffic from ever following paths that leave our network and later pass through both \CD{Prov} and \CD{Cust}.
-To implement both \CD{Routing}
+Additionally, it prevents traffic from ever following paths that leave our network and later go through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
 and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
@@
 MED attributes, and community tags to ensure that the policy is
-implemented correctly under all failure cases.
+implemented correctly under all failures.
 
@@
 end at router \CD{B}; and so on.
-Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location.
-The special keyword \Out{} represents any location outside the user's network, and the keyword \In{} represents any location inside the network.
+Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location, which is otherwise unconstrained.
+The special keyword \Out{} here matches any location outside the user's network, while the keyword \In{} will match any location inside the network.
 For the second constraint, we can define another policy:
@@
 to specify the network-wide policy.
-In addition to constraints on the shape of paths,
-\sysname allows the operator to specify constraints on the BGP control plane.
+However, in addition to constraints on the shape of paths,
+\sysname allows the operator to specify constraints on the BGP control plane itself.
 For instance, a constraint on aggregation is included to ensure that
@@
 
-As before, once \sysname compiles the policy, it is guaranteed to be policy-compliant under all possible failure scenarios.
-In addition, \sysname will efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.
-%It can efficiently determine a lower bound on the number of failures necessary to black hole traffic given the user's policy, topology, and placement of specific aggregates.
+Once \sysname compiles the policy, it is guaranteed to be compliant under all possible failure scenarios, modulo aggregation black holes (which are unavoidable in general).
+In the presence of aggregation, the \sysname compiler will also efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.
 
@@
 Vendor-specific adaptors to translate from ABGP to concrete device configurations or to integrate with an existing template-based system are easily added.
-The \sysname compiler currently generates Quagga configurations by default.
+The \sysname compiler currently generates Quagga router configurations by default.
 
@@
      p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{preferences} \\
-     x       &::=& a.b.c.d/n & \textit{prefix} \\
-     c       &::=& \cdots & \textit{community value} \\
+     x       &::=& d.d.d.d/d & \textit{prefix} \\
      t       &::=& \True & \textit{true} \\
@@
          &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
-         &\BNFALT& \textit{comm} = c & \textit{community test} \\
+         &\BNFALT& \textit{comm} = d & \textit{community test} \\
      r       &::=& n & \textit{AS number} \\
@@
          &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
-         &\BNFALT& \NOT(r) & \textit{path negation} \\
-         &\BNFALT& r^* & \textit{repetition} \\
+         &\BNFALT& \NOT r & \textit{path negation} \\
+         &\BNFALT& r^* & \textit{iteration} \\
      l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
@@
 In addition, $\Sigma$ refers to any symbol.
-We also use other standard abbreviations
-for regular expressions such as $r^+$, which is simply syntactic sugar for $r \cdot r^*$, a sequence of one or more occurrences of $r$, when appropriate.
+We also use the standard regular expressions abbreviation $r^+$ to stand for $r \cdot r^*$, a sequence of one or more occurrences of $r$.
+Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisments with a particular community value (i.e., an integer value associated with a path).
 %% For example, the constraint
@@
 
-\sysname also supports constraints purely on the control-plane behavior of BGP. For example, prefix aggregation is an important optimization to reduce routing table size and churn in practice. 
+\sysname also supports constraints purely on the control-plane behavior of BGP.
+For example, prefix aggregation is an important optimization to reduce routing table size and churn in practice.
+A constraint of the form $agg(x,l)$ tells the compiler to perform aggregation for prefix $x$ across all links described by $l$.
+It is also often useful to be able to add community tags to exported routes in BGP (e.g., to communicate non-standard information to peers).
+A constraint of the form $tag(c,t,l)$ adds community tag $c$ for any prefixes matching $t$ across links $l$.
 %% Aggregation, for example, from internal to external locations, is specified using the same regular syntax as before:

### 2016-06-09 paper/v2/paper-edited.tex
update failure analysis section + code

@@
 \newcommand{\Any}{\KW{any}}
-\newcommand{\None}{\KW{none}}
+\newcommand{\None}{\KW{drop}}
 \newcommand{\In}{\KW{in}}
@@
 
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=\columnwidth]{figures/example1}
+  \caption{Creating router-level policies is difficult.}
+  \label{fig:example1}
+  \vspace{-1em}
+\end{figure}
+
 \subsection{Example 1:  The Backbone}
@@
 It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=\columnwidth]{figures/example1}
-  \caption{Creating router-level policies is difficult.}
-  \label{fig:example1}
-  \vspace{-1em}
-\end{figure}
 
@@
 
-Once \sysname compiles the policy, it is guaranteed to be compliant under all possible failure scenarios, modulo aggregation black holes (which are unavoidable in general).
+Once \sysname compiles the policy, it is guaranteed to remain compliant under all possible failure scenarios, modulo any aggregation-induced black holes.
 In the presence of aggregation, the \sysname compiler will also efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.
@@
 The \sysname compiler currently generates Quagga router configurations by default.
-
-\subsection{Regular IR (RIR)}
-\label{sec:rir}
-
-%Regular expressions are an expressive formalism that have been used extensively for describing paths through graphs~\cite{bib:todo}, with applications to networks~\cite{bib:todo}.
-Our regular expression language differs from others by allowing operators to describe preferences between paths.
 
@@
   \label{fig:rir-syntax}
-  \vspace{-1em}
+  %\vspace{-1em}
 \end{figure*}
+
+\subsection{Regular IR (RIR)}
+\label{sec:rir}
 
@@
 
+The first step in compilation is to reduce the \sysname front-end language (FE) to the simpler, regular intermediate representation (RIR) from Figure~\ref{fig:rir-syntax}.
 The main differences between the FE and RIR are: $i)$ FE allows the programmer to specify constraints using a series of (modular) definitions, and combine them later, $ii)$ FE provides high-level names that abstract sets of routes and groups of prefixes/neighbors, and $iii)$ FE allows the preference operator to be used more flexibly.
@@
 In particular, each regular path constraint $r$ must satisfy $r \subseteq \Out^* \cdot \In^+ \cdot \Out^*$.
-This ensures that the user only control traffic that goes through the user's network at some point, and that such traffic does not loop back multiple times to the user network.
-
-The translation from \sysname to RIR is based on a set of rewriting rules.
+This ensures that users only control traffic that goes through their network at some point, and that such traffic does not loop back multiple times through their network.
+
+The translation from \sysname FE to RIR is based on a set of rewriting rules.
 The first step merges separate constraints.
-It takes the cross product of per-prefix constraints, where logical conjunction ($a \AND b$) is replaced by intersection on regular constraints ($a \Intersect b$), logical disjunction is replaced by union, and logical negation ($\NOT a$) is replaced by ($\Any \cap \NOT(a)$), where $\Any$ ensures the routes are well-formed.
+It takes the cross product of per-prefix constraints, where logical conjunction ($a \AND b$) is replaced by intersection on regular constraints ($a \Intersect b$), logical disjunction is replaced by union, and logical negation ($\NOT a$) is replaced by path negation ($\Any \cap \NOT(a)$).
+The additional constraint $\Any$ ensures the routes are well-formed by restricting the paths to only those that go through the user's network.
 %
@@
 %
-where $\odot$ stands for an arbitrary regular binary operator. Preferences nested under a unary operator, \textit{star} or \textit{negation}, are flagged by the compiler as invalid policies.
-
-\subsection{Product Graph IR}
+where $\odot$ stands for an arbitrary regular binary operator, and $x$ is a policy with a single preference.
+Preferences nested under a unary operator (i.e., \textit{star} or \textit{negation}) are flagged by the compiler as invalid policies.
 
@@
   \label{fig:example-compilation}
-  \vspace{-1em}
+  %\vspace{-1em}
 \end{figure*}
 
-Now that the user policy exists in a simplified form, we must consider topology.
+\subsection{Product Graph IR}
+
+Now that the user policy exists in a simplified form, we must consider the topology.
 In particular, we want a compact representation that describes all the possible ways BGP route announcements can flow through the network subject to the policy and topology constraints.
@@
 To capture this idea, for each regular expression $r_i$, we construct a deterministic finite state machine on the reversed regular expression.
-Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ consists of all all abstraction locations (routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+Each automaton for the reversed regular expression of $r_i$ is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
+The alphabet $\Sigma$ consists of all abstraction locations (routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
 %
 % Formally define topology
-The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon 2^{V \times V}$.
+The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon V \times V$.
 %
@@
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
-edges $E' \colon 2^{V' \times V'}$,
+edges $E' \colon V' \times V'$,
 a unique starting vertex $s$,
 a unique ending vertex $e$,
-and a preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
-For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. 
-Two nodes $x$ and $y$ \emph{shadow} each other in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$.
-That is, $x$ and $y$ shadow each other when they are different nodes in the PGIR that represent the same topology location.
+and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
+For a PGIR vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$, which indicates that the corresponding topology location for $v'$ is $v$. 
+Two nodes $x$ and $y$ \emph{shadow} each other in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$.
 
@@
 Consider the topology in Figure~\ref{fig:example-compilation}.
-Suppose we want a primary route from W that enters the network from $A$, and utilizes the A--C and C--D links.
-We also want a backup route that enters from $B$, and utilizes the B--C link, but is otherwise unconstrained.
-For simplicity, we assume that the route can end in either $X$, $Y$, or $Z$.
-The RIR for the policy is:
+Suppose we want a primary route from neighbor W that allows traffic to enter the network at $A$, and utilize the C--D link before leaving the network (through $X$ or $Y$).
+As a backup, we also want to allow traffic to enter the network from $B$, in which case the traffic can also utilize the C--E link before leaving the network.
+For simplicity, we assume that the route ends in either $X$, $Y$, or $Z$.
+The RIR for the policy could be written as:
 %
@@
 The figure also shows the PGIR after intersecting the topology and policy automata.
-Every path in it corresponds to a concrete path in the topology.
+Every path in the PGIR corresponds to a concrete path in the topology.
 In particular, every path through the PGIR that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
 %
-For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining the most prefered preference $1$.
+For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining a path with the most prefered preference of $1$.
 BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
@@
 The ``--" state indicates the corresponding automaton can not accept the current path or any extension of it.
-Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates this path has preference 1.
+Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates that this path has preference 1.
 
@@
 We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
-In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading to $y$ from the start node.
+In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading from the start node to $y$.
+Similarly, a node $x$ post-dominates a node $y$ in the PGIR if $x$ appears on every path from $y$ to the end node.
+We can safely remove nodes and edges in the PGIR when any of the following conditions hold, where $x$, $x'$ and $y$, $y'$ refer to PGIR nodes that shadow each other:
+\begin{itemize}
+\setlength{\itemsep}{1pt}
+\setlength{\parskip}{0pt}
+\setlength{\parsep}{0pt}
+\item Remove $x$ if it is not reachable from the start node
+\item Remove $x$ if it can not reach the end node
+\item Remove $x$ if it is (post-)dominated by some $x'$
+\item Remove edge ($x$, $y$) if $y$ is post-dominated by some $x'$
+\item Remove edge ($x$, $y$) if $x$ is dominated by some $y'$
+\end{itemize}
 %We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
-For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it must go through another $W$ in either case.
-Colored nodes and dashed edges are removed after minimization since they are irrelvant to the BGP decision process.
+For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} can be removed since it is never on a simple path to the end node because it must always go through node $(W,-,4)$.
+That is, node $(W,-,4)$ post-dominates node $(W,1,1)$.
+We repeatly apply the above minimizations to the PGIR until no further minimization is possible.
+Colored nodes and dashed edges in Figure~\ref{fig:example-compilation} are removed after minimization since they are irrelvant to the BGP decision process.
 %
@@
 
-\para{Failure Safety}
+\subsection{Failure Analysis}
 
 To implement path preferences in routing, BGP uses local preferences on a per-device basis.
-However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult, particularly in the presence of failures.
-For example, imagine an extremely simple policy for the topology in Figure~\ref{fig:example-compilation}, which says to prefer one route over another:
-%
-$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D}) \Prefer (\CD{W} \cdot \CD{B} \cdot \CD{C} \cdot \CD{E})$.
-%
-
+However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult.
+This task becomes even more challenging in the presence of failures since routers running BGP lack a global view of the network and thus cannot make dynamic routing decisions based on the which network elements are up or down.
+
+\para{An illustrative example}
+
+To demonstrate the difficulty of generating device-local preferences, consider the simple policy for the topology in Figure~\ref{fig:unimplementable}, which says to prefer the top path over the bottom path:
+%
+$(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G})  \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$.
+%
 How could such a policy be implemented in BGP?
-Suppose we set the local preference at router $C$ to prefer $D$ over $E$, and use the BGP MED attribute to influence $W$ to prefer $A$ over $B$.
-This might work as expected under normal conditions, however, if the A -- C link fails, then suddenly $C$ has made the wrong decision.
+Suppose we set the local preferences to have $D$ prefer $E$ over $F$, and have $A$ prefer $B$ over $C$.
+This works as expected under normal conditions, however, if the B--D link fails, then suddenly $D$ has made the wrong decision by preferring $E$.
 Traffic will now follow the
-$W \cdot B \cdot C \cdot D$ path, even though this path was not specified by the policy.
+$A \cdot C \cdot D \cdot E \cdot G$ path, even though this path was not allowed by the policy.
 This is a violation of \emph{soundness}: The distributed implementation has used a route not specified by the policy.
-To make matters worse, the second preference $W \cdot B \cdot C \cdot E$ is available in the network but not being used.
+To make matters worse, the second preference $A \cdot C \cdot D \cdot F \cdot G$ is available in the network but not being used.
 This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
-We could solve the first problem by filtering routes that go through $D$ at $B$, however, we can not fix the second problem---$C$ has made the wrong choice.
+
+The soundness violation could be fixed by tagging and filtering route advertisements appropriately to have $C$ reject routes that went through $E$, however the completeness violation can not be fixed.
 In fact, this policy can not be implemented in BGP in a way that is policy compliant under all failures.
-
-%and can not get either the primary or backup route specified, despite the fact that the $W \cdot B \cdot C \cdot E$ path is available in the network.
-
-At a first cut, any time a router must make a decision locally between several route options, there is the possibility it might choose incorrectly.
-The PGIR captures this notion of choice precisely.
-For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the PGIR, possibly receiving announcements from $X$ or $Y$.
-However, regardless of whether $D$ chooses a route from $X$ or $Y$, the set of paths allowed by the policy after going through $D$ will be the same in either case.
-This remains true despite any failures that might have occurred in the network.
-Thus $D$ can safely prefer $X$ and $Y$ equally.
-
-The more challenging case is when a topology location occurs in mutliple contexts in the PGIR.
-For example, in the compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an announcement from $E$ and later achieve the backup path, or it can receive an announcement from its neighbor $D$ and later achieve either the primary or backup path.
+The problem is that $D$ might "regret" its choice depending on what failures have occurred downstream.
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=.8\columnwidth]{figures/unimplementable}
+  \caption{Example topology for which the \sysname policy: $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
+  \label{fig:unimplementable}
+  %\vspace{-1em}
+\end{figure}
+
+\para{Problem Formulation}
+
+The problem of deciding local preferences for each router is closely reflected in the structure of the PGIR.
+In particular, whenever a given router appears in multiple different contexts in the PGIR (i.e., as multiple PGIR nodes), then the compiler must decide which context to prefer.
+%
+For example, in our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in context $(C,-,2)$ or it can receive an advertisement from its neighbor $D$ in context $(C,3,2)$.
+%
+The compiler's task is to determine a \emph{total ordering} of contexts for each router in the topology, which reflects the relative preference of advertisements received in each context.
+For example, if the compiler determines that context $(C,3,2)$ is preferred to context $(C,-,2)$, written as $(C,3,2) < (C,-,2)$, then $C$ will prefer advertisements heard from $D$ over $E$.
+
+\para{Regret-free Preferences}
+
+How should the compiler determine a total ordering of PGIR contexts for each router in a way that is \emph{sound} and \emph{complete} under all possible failures?
+To this end, we introduce \emph{regret-free} preferences, a sufficient condition for correctness motivated by the observations from our previous example.
+Intuitively, preferences are \emph{regret-free} if, whevever some router $r$ prefers an advertisement $X$ over another $Y$, there is always some policy-compliant path to each final (advertisement) destination that is at least as good as any path if it had accepted $Y$ instead.
+
+We now explain this property more formally in terms of the structure of the PGIR. We use the notation $path(s,d)$ to say that there exists a path in the PGIR from $s$ to $d$. 
+%
+Preferences (for the PGIR) are \emph{regret-free} if, given (i) any combination of failed topology links\footnote{Note that a single failure in the topology may correspond to zero or more failed nodes/edges in the PGIR}, (ii) a fixed topology (advertisement) destination $d$, and (iii) two contexts $N_1 < N_2$, then whever there exists a $d'$ such that $loc(d') = d$ and $path(N_2,d')$, then there exists a $d''$ such that $loc(d'') = d$ and $path(N_1,d'')$ with $min ~ P(d'') \leq min ~ P(d')$.
+%
+The property simply states that if router $N$ prefers context $N_1$ to $N_2$, then any time there is a path from $N_2$ to some destination $d$, then there exists a better (higher ranked) path from $N_1$ to destination $d$.
+%
+For example, the compilation example in Figure~\ref{fig:example-compilation}, a choice for $C$ to prefer context $(C,3,2)$ to $(C,-,2)$ would be regret-free, since there is always at least as good a path to destination $W$ regardless of failures.
+
+\para{A Preference Inference Algorithm}
+
+%For example, in our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an announcement from $E$ and later achieve the backup path, or it can receive an announcement from its neighbor $D$ and later achieve either the primary or backup path.
 Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $E$?
 The important observation is that, if $C$ prefers $D$, then it is never worse off---it will always achieve at least as good a path as if it had choosen $E$.
-For example, suppose $C$ chooses a route from $D$, but cannot achieve its primary path because the $A$ -- $W$ link has failed.
+%For example, suppose $C$ chooses a route from $D$, but cannot achieve its primary path because the $A$ -- $W$ link has failed.
 In this case, the advertisement from $C$ will still be sent along towards the ultimate backup location $W$.
@@
 
-In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and enumerating all failures is intractable.
-We thus adopt a conservative analysis based on the observations above.
-The high-level idea is to order each PGIR node according to a \textit{can prefer} relation.
-For example, node $(C,3,2)$ can be preferred to node $(C,-,2)$, but not the other way around.
-Intuitively, a node $N_1$ can be preferred to another node $N_2$ when, for each preference $N_2$ might achieve, there is a better preference that $N_1$ will achieve regardless of failures.
-Formally this means that $N_1$ can be preferred to $N_2$ when:
-%
-$$\forall i, \exists j, j \leq i \wedge protect(G_j, N_1, G_i, N_2)$$
-%
-where \textit{protect} means that, from $N_1$ on the product graph restricted to nodes that can potentially achieve preference $j$ or better, 
-there is always a path to each ending location whenever this is a path from $N_2$ restricted to $G_i$.
+Clearly searching for \emph{regret-free} preferences by enumerating all possible combinations of failures and preference orderings is intractable.
+We thus adopt a conservative analysis that we found to be highly-effective in practice.
+The idea is to search for regret-free preferences while also refining the search when possible by taking into account information about where advertisements must have already traversed.
+
+The analysis determines that context $N_1 < N_2$ if the following condition holds:
+%
+$$\forall i, ~\exists j, ~j \leq i ~\wedge~ protect(G_j, N_1, G_i, N_2)$$
+%
+where \textit{protect} checks if, from $N_1$ in the product graph restricted to nodes that can potentially achieve a path with preference $j$ or better, there is always a path to each final location whenever there is a path from $N_2$ restricted to $G_i$ to the same final location.
 
@@
 Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another.
-It walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
-When there is no equivalent step, the algorithm checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) that can protect against failures instead.
-Thus any time $N_2$ can get to a final location for preference $i$, $N_1$ can get to at least the same final locations for a better preference $j$.
-The algorithm terminates since the number of related states $(x,y)$ that can be expolored is finite.
-
-For each router in the topology, local preferences are now obtained by  sorting the corresponding PGIR nodes according to the \textit{can prefer} relation.
-If two nodes are incomparable, the compiler rejects the policy as unimplementable.
+The algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
+%
+When there is no equivalent step, the algorithm relaxes the regret-free property to take into account where the advertisement came from before reaching $N_1$.
+In particular, it checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) that can protect against failures instead.
+Thus any time $N_2$ has a path to a final location for preference $i$, $N_1$ can get to at least the same final locations for a preference $j$, which is at least as good.
+The algorithm terminates since the number of related states $(x,y)$ that can be explored is finite.
+
+For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR contexts according to the $(<)$ relation.
+If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
 
@@
 
-\para{PG construction}
+\para{PGIR construction}
 
@@
 %=====================================================
+
+\section{Evaluation}
+\label{sec:evaluation}
 
@@
 
-\section{Evaluation}
-\label{sec:evaluation}
-
 We apply \sysname on real policies for backbone and data center networks.
@@
 They also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
-
-\begin{figure}
-  \subcaptionbox{Data center}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
-  \subcaptionbox{Backbone network}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
-  \caption{Configuration minimization. \label{fig:config-min}}
-  \vspace{-1em}
-\end{figure}
 
@@
 %
+
+\begin{figure}[t!]
+  \subcaptionbox{Data center}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
+  \subcaptionbox{Backbone network}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
+  \caption{Configuration minimization. \label{fig:config-min}}
+  \vspace{-1em}
+\end{figure}
 
@@
 
-\subsection{Propane Properties}
-
-\newtheorem{prop}{Proposition}[section]
-
+%\subsection{Propane Properties}
+%
+%\newtheorem{prop}{Proposition}[section]
+%
 %Here we investigate the correctness and expressiveness properties of \sysname.
@@
 (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?
-
+%
 %If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario.
@@
 We argue that \sysname is correct by breaking down the claim:
-
-\begin{prop}
-BGP configurations for internal routers produced by \sysname will be stable. 
-\end{prop}
-
-\begin{prop}
-BGP configurations produced by \sysname are \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.
-\end{prop}
+%
+%\begin{prop}
+%BGP configurations for internal routers produced by \sysname will be stable. 
+%\end{prop}
+%
+%\begin{prop}
+%BGP configurations produced by \sysname are \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.
+%\end{prop}
 %
@@
 %
-\begin{prop}
-BGP configurations produced by \sysname are \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
-\end{prop}
+%\begin{prop}
+%BGP configurations produced by \sysname are \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
+%\end{prop}
 %

### 2016-06-09 paper/v2/paper-edited.tex
update implementation section

@@
 Finally, there is an edge from each node in the PGIR such that $P(v) \neq \emptyset$ to the special end node $e$.
+We use the notation $x \leq_{rank} y$ as a shorthand for $min ~ P(x) \leq min ~ P(y)$, which simply states that paths that end at PGIR node $x$ are better than (lower rank) than paths that end at $y$.
 
@@
 %
-Preferences (for the PGIR) are \emph{regret-free} if, given (i) any combination of failed topology links\footnote{Note that a single failure in the topology may correspond to zero or more failed nodes/edges in the PGIR}, (ii) a fixed topology (advertisement) destination $d$, and (iii) two contexts $N_1 < N_2$, then whever there exists a $d'$ such that $loc(d') = d$ and $path(N_2,d')$, then there exists a $d''$ such that $loc(d'') = d$ and $path(N_1,d'')$ with $min ~ P(d'') \leq min ~ P(d')$.
-%
-The property simply states that if router $N$ prefers context $N_1$ to $N_2$, then any time there is a path from $N_2$ to some destination $d$, then there exists a better (higher ranked) path from $N_1$ to destination $d$.
+Preferences (for the PGIR) are \emph{regret-free} if, given (i) any combination of failed topology links\footnote{Note that a single failure in the topology may correspond to zero or more failed nodes/edges in the PGIR}, (ii) a fixed topology (advertisement) destination $d$, and (iii) two contexts $N_1 < N_2$, then whever there exists a $d'$ such that $loc(d') = d$ and $path(N_2,d')$, then there exists a $d''$ such that $loc(d'') = d$ and $path(N_1,d'')$ with $d'' \leq_{rank} d'$.
+%
+The property simply says that if router $N$ prefers context $N_1$ to $N_2$, then any time there is a path from $N_2$ to some destination $d$, then there exists a better (lower ranked) path from $N_1$ to destination $d$.
 %
@@
 
-The analysis determines that context $N_1 < N_2$ if the following condition holds:
-%
-$$\forall i, ~\exists j, ~j \leq i ~\wedge~ protect(G_j, N_1, G_i, N_2)$$
-%
-where \textit{protect} checks if, from $N_1$ in the product graph restricted to nodes that can potentially achieve a path with preference $j$ or better, there is always a path to each final location whenever there is a path from $N_2$ restricted to $G_i$ to the same final location.
-
 \begin{algorithm}[t!]
@@
 \begin{algorithmic}[1]
-\Procedure{Protect($G_1$, $N_1$, $G_2$, $N_2$)}{}
+\Procedure{Protect($G$, $N_1$, $N_2$)}{}
   \If {$loc(N_1) \neq loc(N_2)$} \Return false
@@
     \State $(n_1,n_2) \gets q.Dequeue()$
-    \For {$x$ in adj($G_2$, $n_2$)}
-      \If {\big($\exists y \in$ adj($G_1$,$n_1$), shadows $x$\big) \textbf{or} \\  
-            \hspace{5.2em} \big($\exists y \in$ $G_1$, dominates $n_1$, shadows $x$\big)}
-        \If {$(x,y)$ not marked}
+    \For {$x$ in adj($G$, $n_2$)}
+      \If {\big($\exists y \in$ adj($G$,$n_1$), shadows $x$\big) \textbf{or} \\  
+            \hspace{5.2em} \big($\exists y \in$ $G$, dominates $n_1$, shadows $x$\big)}
+        \If {$(x,y)$ not marked $\wedge$ $x \leq_{rank} y$}
           \State {mark $(x,y)$ as seen}
@@
 
+The analysis determines that context $N_1 < N_2$ if $N_1$ \textit{protects} against the failures of $N_2$.
+%
 Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another.
-The algorithm walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
-%
-When there is no equivalent step, the algorithm relaxes the regret-free property to take into account where the advertisement came from before reaching $N_1$.
+The algorithm walks from nodes $N_1$ and $N_2$ and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
+%
+When there is no equivalent step, the algorithm attempts to take into account where the advertisement must have already traversed to have arrived at $N_1$.
 In particular, it checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) that can protect against failures instead.
-Thus any time $N_2$ has a path to a final location for preference $i$, $N_1$ can get to at least the same final locations for a preference $j$, which is at least as good.
-The algorithm terminates since the number of related states $(x,y)$ that can be explored is finite.
+
+By repeating this process, we are ensured that any time $N$ receives an advertisement in both context $N_2$ and $N_1$, $N$ can safely prefer $N_1$, knowing that BGP will obtain end-to-end paths which are at least as good as it would have if $N$ had preferred $N_2$.
+Algorithm~\ref{alg:failures} terminates since the number of related states $(x,y)$ that can be explored is finite.
 
@@
 
-The checks for failure safety described above overlook one critical point: Paths for a higher preference might not exist due to loops.
-To avoid this situation, the compiler checks that, when node $x$ protects against failures for node $y$, its does so without using any nodes that shadow another node that appears ``above'' $x$ in the PGIR.
+The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available after some router $N$ due to loops.
+To avoid this situation, the compiler checks that, any time some context $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$.
+The idea is that anytime $N_2$ is not available to use because the advertisement already went through $N_1$, it ultimately does not matter since $N_1$ will result in strictly better end-to-end paths.
+
 %It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
@@
 
-We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code.
-The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates.
+We have written a prototype compiler for \sysname that is implemented in roughly 6700 lines of F\# code.
+The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, anycast, the no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates.
 Since each prefix has a separate routing policy, the \sysname compiler is able to compile each routing policy in parallel.
-The current compiler produces only ABGP policies, which can be incorporated into an existing template-based system, for example by mixing the \sysname configuration with other configuration components, or by generating vendor-specific configurations.
+Currently \sysname supports generating Quagga router configurations out of the box.
+Users can also easily add new vendor-specific adaptors to translate from ABGP to other router configurations, or to incorporate the compiler into an existing template-based system, for example by mixing the \sysname configuration with other configuration components.
 
@@
 When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the \textit{protect} function.
-That is, whenever for two states $n_1$ and $n_2$ we compute $protect(G_j, n_1, G_i, n_2)$, if the function evaluates to $true$, then each of the intermediate related states $x$ and $y$ must also satisfy $protect(G_j, x, G_i, y)$.
-Memoizing these states significantly cuts down the amount of work that needs to be in the common case.
+That is, whenever for two states $N_1$ and $N_2$ we compute $protect(G, N_1, N_2)$, if the function evaluates to $true$, then each of the intermediate related states $x$ and $y$ must also satisfy $protect(G, x, y)$.
+Memoizing these states dramatically reduces the amount of work performed to find preferences in the common case.
 
@@
 They also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
+
+\begin{figure}[t!]
+  \subcaptionbox{Data center}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
+  \subcaptionbox{Backbone network}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
+  \caption{Configuration minimization. \label{fig:config-min}}
+  \vspace{-1em}
+\end{figure}
 
@@
 %
-
-\begin{figure}[t!]
-  \subcaptionbox{Data center}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
-  \subcaptionbox{Backbone network}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
-  \caption{Configuration minimization. \label{fig:config-min}}
-  \vspace{-1em}
-\end{figure}
 
@@
 
-\section{Future Work}
-
-There are a number of possible directions for future work in programming distributed control planes.
+%\section{Future Work}
+%
+%There are a number of possible directions for future work in programming distributed control planes.
 One option would be to integrate a model of the environment into the compiler.
@@
 %
-Another direction would be to perform policy verification at the level of centralized language.
+%Another direction would be to perform policy verification at the level of centralized language.
 There has been great deal of work on verification of the data plane, but much less so on control plane verification.
@@
 %
-While we target BGP in this paper as a distributed backend for \sysname due to its expressiveness, scalability, and uniformity, it should be possible to use other protocols to achieve different types of routing policies (e.g., OSPF).
+%While we target BGP in this paper as a distributed backend for \sysname due to its expressiveness, scalability, and uniformity, it should be possible to use other protocols to achieve different types of routing policies (e.g., OSPF).
 In particular, one could potentially combine different distributed routing protocols through route redistribution to achieve a larger variety of policies.
 %
-Another possible future direction is automate AS-wide load balancing for BGP.
+%Another possible future direction is automate AS-wide load balancing for BGP.
 Load-balancing with BGP across external ASes is difficult since there are few mechanisms at the operators disposal.

### 2016-06-09 paper/v2/paper-edited.tex
added to evaluation section

@@
 Finally, there is an edge from each node in the PGIR such that $P(v) \neq \emptyset$ to the special end node $e$.
-We use the notation $x \leq_{rank} y$ as a shorthand for $min ~ P(x) \leq min ~ P(y)$, which simply states that paths that end at PGIR node $x$ are better than (lower rank) than paths that end at $y$.
+We say that $x \leq_{rank} y$ if either $P(x) = P(y) = \emptyset$ or $min ~ P(x) \leq min ~ P(y)$, which simply states that paths that end at PGIR node $x$ are better than (lower rank) than paths that end at $y$.
 
@@
     \State $(n_1,n_2) \gets q.Dequeue()$
+    \If {$n_1 \nleq_{rank} n_2$} 
+      \Return false
+    \EndIf
     \For {$x$ in adj($G$, $n_2$)}
@@
             \hspace{5.2em} \big($\exists y \in$ $G$, dominates $n_1$, shadows $x$\big)}
-        \If {$(x,y)$ not marked $\wedge$ $x \leq_{rank} y$}
+        \If {$(x,y)$ not marked}
           \State {mark $(x,y)$ as seen}
@@
 Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
-The idea is to encode the state of the automaton using BGP community values.
+The idea is to encode the state of the automata using BGP community values.
 Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR.
@@
 The naive code generation algorithm described in Section~\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair for every node in the product graph before minimization.
-Our implementation performs partial minimization during generation by recognizing common cases where there is no restriction on exporting to or importing from neighbors.
+Our implementation performs partial minimization during generation by recognizing common cases like when there is no restriction on exporting to or importing from neighbors.
 
@@
 We apply \sysname on real policies for backbone and data center networks.
-Our mains goals are to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
+Our main goals are to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
 
@@
 
-Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.
+Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the routing policies for \sysname were 43 lines for the backbone network and 31 lines for the data center networks.
 
@@
 Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes.
-For both policies, we measure the mean compilation time per prefix since the compiler operates on each prefix in parallel.
-At their largest sizes, the per-prefix compilation time is roughly 10 seconds for the data center network and 45 seconds for the backbone network.
+For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on each prefix predicate in parallel.
+Note that a single predicate can describe many prefixes, for example by matching on a disjunction of prefixes.
+At their largest sizes, the per-predicate compilation time is roughly 10 seconds for the data center network and 45 seconds for the backbone network.
 
@@
 The inclusion of more preferences in the backbone policy increases the size of the PGIR, which leads to PGIR construction and minimization taking proportionally more time.
+
+In both examples, we observe that our safety analysis algorithm for finding preferences is highly efficient, taking only a small fraction of the total running time.
+PGIR minimization is proportionally the most expensive compilation phase, however minimization can be capped after a certain number of iterations for larger networks if necessary.
+Both the backbone and data center networks policies we considered can be successfully compiled without minimization.
 

### 2016-06-10 paper/v2/paper-edited.tex
cleaned up failure section

@@
 \noindent
-The \CD{NoTrans} constraint above requires that all traffic not follow a path that transits the network between \CD{Peer} and \CD{Prov}.
+The \CD{NoTrans} constraint requires that all traffic not follow a path that transits the network between \CD{Peer} and \CD{Prov}.
 Additionally, it prevents traffic from ever following paths that leave our network and later go through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
@@
 Finally, there is an edge from each node in the PGIR such that $P(v) \neq \emptyset$ to the special end node $e$.
-We say that $x \leq_{rank} y$ if either $P(x) = P(y) = \emptyset$ or $min ~ P(x) \leq min ~ P(y)$, which simply states that paths that end at PGIR node $x$ are better than (lower rank) than paths that end at $y$.
+We write $(x \leq_{rank} y)$ if either $P(x) = P(y) = \emptyset$ or $min ~ P(x) \leq min ~ P(y)$, which means that paths ending at PGIR node $x$ are better than (lower rank) than paths that ending at $y$.
 
@@
 %
-For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining a path with the most prefered preference of $1$.
+For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining a path with the lowest (best) rank of $1$.
 BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
@@
 However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult.
-This task becomes even more challenging in the presence of failures since routers running BGP lack a global view of the network and thus cannot make dynamic routing decisions based on the which network elements are up or down.
+This task becomes even more challenging in the presence of failures since routers running BGP lack a global view of the network.
 
@@
 This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
-
-The soundness violation could be fixed by tagging and filtering route advertisements appropriately to have $C$ reject routes that went through $E$, however the completeness violation can not be fixed.
+%
+The soundness violation could be fixed by tagging and filtering route advertisements appropriately so that $C$ rejects routes that go through $E$, however the completeness violation can not be fixed.
 In fact, this policy can not be implemented in BGP in a way that is policy compliant under all failures.
-The problem is that $D$ might "regret" its choice depending on what failures have occurred downstream.
 
@@
 %
-For example, in our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in context $(C,-,2)$ or it can receive an advertisement from its neighbor $D$ in context $(C,3,2)$.
+In our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in context $(C,-,2)$ or it can receive an advertisement from its neighbor $D$ in context $(C,3,2)$.
 %
 The compiler's task is to determine a \emph{total ordering} of contexts for each router in the topology, which reflects the relative preference of advertisements received in each context.
-For example, if the compiler determines that context $(C,3,2)$ is preferred to context $(C,-,2)$, written as $(C,3,2) < (C,-,2)$, then $C$ will prefer advertisements heard from $D$ over $E$.
+For example, if the compiler determines that, for router $C$, context $(C,3,2)$ is preferred to context $(C,-,2)$, written as $(C,3,2) <_{pref} (C,-,2)$, then this means that $C$ will prefer advertisements heard from $D$ (with tag $(2,2)$) over $E$ (with tag $(-,2)$).
+Section~\ref{sec:abgp} discusses our encoding of preferences and filters in more detail.
 
@@
 
-How should the compiler determine a total ordering of PGIR contexts for each router in a way that is \emph{sound} and \emph{complete} under all possible failures?
-To this end, we introduce \emph{regret-free} preferences, a sufficient condition for correctness motivated by the observations from our previous example.
-Intuitively, preferences are \emph{regret-free} if, whevever some router $r$ prefers an advertisement $X$ over another $Y$, there is always some policy-compliant path to each final (advertisement) destination that is at least as good as any path if it had accepted $Y$ instead.
-
-We now explain this property more formally in terms of the structure of the PGIR. We use the notation $path(s,d)$ to say that there exists a path in the PGIR from $s$ to $d$. 
-%
-Preferences (for the PGIR) are \emph{regret-free} if, given (i) any combination of failed topology links\footnote{Note that a single failure in the topology may correspond to zero or more failed nodes/edges in the PGIR}, (ii) a fixed topology (advertisement) destination $d$, and (iii) two contexts $N_1 < N_2$, then whever there exists a $d'$ such that $loc(d') = d$ and $path(N_2,d')$, then there exists a $d''$ such that $loc(d'') = d$ and $path(N_1,d'')$ with $d'' \leq_{rank} d'$.
-%
-The property simply says that if router $N$ prefers context $N_1$ to $N_2$, then any time there is a path from $N_2$ to some destination $d$, then there exists a better (lower ranked) path from $N_1$ to destination $d$.
-%
-For example, the compilation example in Figure~\ref{fig:example-compilation}, a choice for $C$ to prefer context $(C,3,2)$ to $(C,-,2)$ would be regret-free, since there is always at least as good a path to destination $W$ regardless of failures.
+A natural question then is how the compiler should order PGIR contexts for each router in a way that is both \emph{sound} and \emph{complete} under all possible failures?
+To this end, we introduce the notion of \emph{regret-free} preferences, which is motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
+Preferences are \emph{regret-free} if, whevever some router $r$ prefers an advertisement $X$ over another $Y$, there is always some policy-compliant path to each final (advertisement) destination $d$ that is at least as good $(\leq_{rank})$ as any possible path to $d$ if it had accepted $Y$ instead.
+In other words, the preference of $X$ over $Y$ at $r$ is regret-free if we are never worse off by choosing $X$.
+%
+In the compilation example from Figure~\ref{fig:example-compilation}, the choice for $C$ to prefer context $(C,3,2)$ to $(C,-,2)$ is regret-free, since there will always be at least as good a path to destination $W$ regardless of any failures that might occur in the network.
+
+%We now explain this property more formally in terms of the structure of the PGIR. We use the notation $path(s,d)$ to say that there exists a path in the PGIR from $s$ to $d$. 
+%
+%Preferences (for the PGIR) are \emph{regret-free} if, given (i) any combination of failed topology links\footnote{Note that a single failure in the topology may correspond to zero or more failed nodes/edges in the PGIR}, (ii) a fixed topology (advertisement) destination $d$, and (iii) two contexts $N_1 < N_2$, then whever there exists a $d'$ such that $loc(d') = d$ and $path(N_2,d')$, then there exists a $d''$ such that $loc(d'') = d$ and $path(N_1,d'')$ with $d'' \leq_{rank} d'$.
+%
+%The property simply says that if router $N$ prefers context $N_1$ to $N_2$, then any time there is a path from $N_2$ to some destination $d$, then there exists a better (lower ranked) path from $N_1$ to destination $d$.
+%
 
@@
 
-Clearly searching for \emph{regret-free} preferences by enumerating all possible combinations of failures and preference orderings is intractable.
-We thus adopt a conservative analysis that we found to be highly-effective in practice.
-The idea is to search for regret-free preferences while also refining the search when possible by taking into account information about where advertisements must have already traversed.
+Searching for \emph{regret-free} preferences in general is hard, and clearly enumerating all possible combinations of failures and preference orderings is intractable.
+We thus adopt a conservative analysis that we found to be both effective and efficient in practice.
+The idea is to search for regret-free preferences by comparing the set of paths available after accepting advertisments in two different PGIR contexts $N_1$ and $N_2$ while refining the comparison when necessary by taking into account information about where advertisements must have already traversed the network before arriving at $N_1$ or $N_2$.
 
@@
 \begin{algorithmic}[1]
-\Procedure{Protect($G$, $N_1$, $N_2$)}{}
+\Procedure{Regret-free($G$, $N_1$, $N_2$)}{}
   \If {$loc(N_1) \neq loc(N_2)$} \Return false
@@
 
-The analysis determines that context $N_1 < N_2$ if $N_1$ \textit{protects} against the failures of $N_2$.
-%
-Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another.
-The algorithm walks from nodes $N_1$ and $N_2$ and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
-%
-When there is no equivalent step, the algorithm attempts to take into account where the advertisement must have already traversed to have arrived at $N_1$.
-In particular, it checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) that can protect against failures instead.
-
-By repeating this process, we are ensured that any time $N$ receives an advertisement in both context $N_2$ and $N_1$, $N$ can safely prefer $N_1$, knowing that BGP will obtain end-to-end paths which are at least as good as it would have if $N$ had preferred $N_2$.
+Algorithm~\ref{alg:failures} checks whether one context can be preferred to another ($N_1 <_{pref} N_2$).
+The algorithm walks from nodes $N_1$ and $N_2$ and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, also take a step to an equivalent topology location.
+When there is no such equivalent step, the algorithm attempts to take into account where the advertisement must have already traversed.
+In particular, it checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) and walks from this new node instead.
 Algorithm~\ref{alg:failures} terminates since the number of related states $(x,y)$ that can be explored is finite.
 
-For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR contexts according to the $(<)$ relation.
+For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR contexts according to the $(<_{pref})$ relation.
 If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
@@
 
-The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available after some router $N$ due to loops.
+The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available due to loops.
 To avoid this situation, the compiler checks that, any time some context $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$.
-The idea is that anytime $N_2$ is not available to use because the advertisement already went through $N_1$, it ultimately does not matter since $N_1$ will result in strictly better end-to-end paths.
+The idea is that anytime $N_2$ is not usable because the advertisement already went through $N_1$, it ultimately does not matter since $N$ has a regret-free preference for $N_1$ anyway.
 
@@
 The algorithm for aggregation failure safety is detailed in Section~\ref{sec:black-holes} of the appendix.
+
 \subsection{Abstract BGP}
+\label{sec:abgp}
 

### 2016-06-10 paper/v2/paper-edited.tex
first pass edits

@@
 % and compared these specifications with existing configurations.
-We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds of routers, compiling in under 9 minutes in all cases.
+We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds to thousands of routers, compiling in under 9 minutes in all cases.
 
@@
 (and, or, not) of concrete prefixes and community tags.  Here,
-we assume we have already defined predicates \CD{PCust} for the
+we assume we have already defined the predicate \CD{PCust} for the
 customer prefixes.
@@
 
-\subsection{Failure Analysis}
+\subsection{Failure Safety}
 
 To implement path preferences in routing, BGP uses local preferences on a per-device basis.
-However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult.
+However, the distributed nature of BGP makes setting preferences locally to achieve a network-wide routing policy difficult.
 This task becomes even more challenging in the presence of failures since routers running BGP lack a global view of the network.
@@
 
-The problem of deciding local preferences for each router is closely reflected in the structure of the PGIR.
+The problem of determining local preferences for each router is closely reflected in the structure of the PGIR.
 In particular, whenever a given router appears in multiple different contexts in the PGIR (i.e., as multiple PGIR nodes), then the compiler must decide which context to prefer.
@@
 In particular, it checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) and walks from this new node instead.
+At each step, it requires that current node reachable from $N_1$ has a path rank that is at least as good as that of the current node reachable from $N_2$ ($n_1 \leq_{rank} n_2$).
+The intuition here is that if $n_1 \nleq_{rank} n_2$, then we can likely fail every edge in the topology except for the path that leads to the current $n_1$ and $n_2$, thereby generating in a counter example.
 Algorithm~\ref{alg:failures} terminates since the number of related states $(x,y)$ that can be explored is finite.
@@
 
-The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available due to loops.
+The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available due to loops that are rejected by BGP.
 To avoid this situation, the compiler checks that, any time some context $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$.
@@
 
-\para{Aggregation-Induced Black Holes}
-Because the \sysname compiler has the complete user policy and topology, it is also able to efficiently check that aggregates do not black hole traffic for up to $k$ failures.
-The algorithm for aggregation failure safety is detailed in Section~\ref{sec:black-holes} of the appendix.
+\subsection{More Safety}
+
+\para{Aggregation Safety}
+\label{sec:agg-safety}
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=\columnwidth]{figures/aggregation}
+  \caption{Aggregation safety for a data center.}
+  \label{fig:aggregation-safety}
+  \vspace{-1em}
+\end{figure}
+
+As demonstrated with Example 2 in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur.
+Deciding when this can happen requires knowledge of the routing policy and not just the topology.
+For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated, even if there are several available in the toplogy.
+If that link fails, a black hole might be introduced.
+%
+Because the \sysname compiler has the complete user policy and topology encoded in the PGIR, it is able to efficiently check that aggregates do not black hole traffic for up to $k$ failures.
+
+We frame the aggregation problem as a problem of connectivity in the PGIR.
+Specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures required to  disconnect where the prefix originates from where it is aggregated.
+The difficulty is that the same links in the topology can appear in multiple places in the PGIR.
+%
+%
+We adopt the following simple strategy to lower bound the number of failures: $i)$ Pick a random start-to-end path in PGIR, $ii)$ remove all edges in the PGIR for the set of topological edges chosen, and $iii)$ repeat until no such path exists.
+The number of PGIR paths that we are able to remove is a lower bound on the number of failures required to disconnect the prefix from its aggregate.
+
+For example, recall the data center example from \S\ref{sec:motivation}, with the policy: 
+\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
+Figure~\ref{fig:aggregation-safety} shows the network topology simplified PGIR.
+Since the compiler knows aggregation will occur at $X$, and it knows that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
+We could remove the $A$--$D$--$X$ path first.
+We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none).
+Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
+Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}.
+This process is repeated for other aggregation locations (e.g., $Y$).
+
+\para{Policy Safety}
+
+Even when programming the network centrally, it is possible for operators to make mistakes and write incorrect policies.
+\sysname includes many additional safety analysis checks to try to catch common mistakes at compile time.
+These include: (i) preference analysis to determine when backup paths/preferences will never be used, (ii) reachability analysis to check if topology locations that should be reachable according to the operator policy are not reachable after combining both the topology and policy, (iii) anycast analysis to find instances where the operator accidentally anycasts a prefix, (iv) aggregate analysis to find when aggregates do not summarize any specific prefix, and others.
 
@@
 
-\para{From PGIR to ABGP}
-
-Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
-The idea is to encode the state of the automata using BGP community values.
-Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR.
-For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else).
-If it sees such an announcement, it will remove the old community value, and add a new one for state $(4,2)$ before exporting it to $W$.
-
-To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR.
-For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
-
-Since the compiler is only able to control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
-Instead, it translates matches from external ASes into a BGP regular expression filter.
-For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$.
-In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
-The unknown AS topology is modelled as a special node in the PGIR that generates a filter to match any sequence of ASes.
-
-Finally, the external AS $W$ should prefer our internal router $A$ over $B$.
-In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
-In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$.
-Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
-The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
-%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
-Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
-Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.
-
-After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
-In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from.
-Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
-
 \begin{figure}[t!]
-%% \begin{lstlisting}[frame=single, mathescape=true]
-%% $\Router{A}$
-%%   Match $\PEER=C, \COMM=(3,2)$
-%%     Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
-%% $\Router{B}$
-%%   Match $\PEER = C, \COMM = (-,2)$
-%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
-%%            $\MED \leftarrow 81, \PEER \leftarrow W$
-%%   Match $\PEER = C, \COMM = (3,2)$
-%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
-%%            $\MED \leftarrow 81, \PEER \leftarrow W$
-%% $\Router{C}$
-%%   Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
-%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
-%%   Match $\PEER = D, \COMM = (2,2)$
-%%     Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
-%% $\Router{D}$
-%%   Match $\REGEX{X + Y}$
-%%     Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
-%% $\Router{E}$
-%%   Match $\REGEX{Z}$
-%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
-%% \end{lstlisting}
 \begin{code}
@@
 
+\para{From PGIR to ABGP}
+
+Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
+The idea is to encode the state of the automata using BGP community values.
+Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR.
+For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else).
+If it sees such an announcement, it will remove the old community value, and add a new one for state $(4,2)$ before exporting it to $W$.
+
+To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR.
+For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
+
+Since the compiler is only able to control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
+Instead, it translates matches from external ASes into a BGP regular expression filter.
+For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$.
+In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
+The unknown AS topology is modelled as a special node in the PGIR that generates a filter to match any sequence of ASes.
+
+Finally, the external AS $W$ should prefer our internal router $A$ over $B$.
+In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
+In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$.
+Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
+The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
+%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
+Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
+Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.
+
+After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
+In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from.
+Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
+
 %=====================================================
@@
 
-We have written a prototype compiler for \sysname that is implemented in roughly 6700 lines of F\# code.
+We have written a compiler for \sysname that is implemented in roughly 6700 lines of F\# code.
 The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, anycast, the no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates.
@@
 \label{sec:evaluation}
+
+We apply \sysname on real policies for backbone and data center networks.
+Our main goals are to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
+
+\subsection{Networks studied}
+
+We obtained routing policy for the backbone network and for the data centers of a large cloud provider.
+Multiple data centers share this policy.
+The backbone network connects to the data centers and also has many external BGP neighbors.
+The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for data center routers or actual configurations for the backbone network (where templates are not used because the network has less regular structure).
+
+The networks have the type of policies that we outline earlier (\S\ref{sec:motivation}).
+The backbone network classifies external neighbors into several different categories and prefers paths through them in order.
+It does not want to provide transit among certain types of neighbors.
+For some neighbors, it prefers some links over the others.
+It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA).
+Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, etc.
+
+All routers in the datacenter network run BGP using a private AS number and peer with each other and with the backbone network over eBGP.
+The routers aggregate prefixes when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region.
+They also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
 
@@
   \caption{Compilation time. \label{fig:compilation-times}}
-  \vspace{-1em}
-\end{figure}
-
-We apply \sysname on real policies for backbone and data center networks.
-Our main goals are to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
-
-\subsection{Networks studied}
-
-We obtained routing policy for the backbone network and for the data centers of a large cloud provider.
-Multiple data centers share this policy.
-The backbone network connects to the data centers and also has many external BGP neighbors.
-The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for data center routers or actual configurations for the backbone network (where templates are not used because the network has less regular structure).
-
-The networks have the type of policies that we outline earlier (\S\ref{sec:motivation}).
-The backbone network classifies external neighbors into several different categories and prefers paths through them in order.
-It does not want to provide transit among certain types of neighbors.
-For some neighbors, it prefers some links over the others.
-It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA).
-Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, etc.
-
-All routers in the datacenter network run BGP using a private AS number and peer with each other and with the backbone network over eBGP.
-The routers aggregate prefixes when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region.
-They also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
-
-\begin{figure}[t!]
-  \subcaptionbox{Data center}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
-  \subcaptionbox{Backbone network}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
-  \caption{Configuration minimization. \label{fig:config-min}}
   \vspace{-1em}
@@
 Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes.
-For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on each prefix predicate in parallel.
+For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on each predicate in parallel.
 Note that a single predicate can describe many prefixes, for example by matching on a disjunction of prefixes.
@@
 
-$ii)$ operators prevented unneeded propagation of more-specific route announcements from a neighboring AS based on their out-of-band knowledge about the topology, whereas \sysname propagated these advertisements; and
-
-$iii)$ operators used a layer of indirection for community values, using community groups and re-writing values, to implement certain policies in a more maintainable manner, where \sysname uses flat communities.
+$ii)$ operators prevented unneeded propagation of more-specific route announcements from a neighboring AS based on their out-of-band knowledge about the topology, whereas \sysname propagated these advertisements;
+
+$iii)$ operators used a layer of indirection for community values, using community groups and re-writing values, to implement certain policies in a more maintainable manner, where \sysname uses flat communities; and
+
+$iv)$ operators used BGP regular expression filters to enforce certain invariants that are independent of any particular prefix, whereas \sysname enforced these invariants per prefix.
 
@@
 
-\section*{Appendix}
-\label{sec:appendix}
-
-\renewcommand\thesubsection{\Alph{subsection}}
-
-\subsection{Aggregation-Induced Black Holes}
-\label{sec:black-holes}
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=\columnwidth]{figures/aggregation}
-  \caption{Aggregation safety.}
-  \label{fig:aggregation-safety}
-  \vspace{-1em}
-\end{figure}
-
-As demonstrated with Example 2 in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur.
-Deciding when this can happen requires knowledge of the routing policy and not just the topology.
-For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated, even if there are several available in the toplogy.
-If that link fails, a black hole might be introduced.
-Fortunately, the PGIR captures the information about both the policy and topology precisely.
-%, describing the how information meeting the policy flows over the topology.
-
-We frame the aggregation problem as a problem of connectivity in the PGIR.
-Specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures that would disconnect where the prefix originates from where its more specific aggregate is located.
-The difficulty is that the same links in the topology can appear in multiple places in the PGIR.
-We adopt the following simple strategy to lower bound the number of failures: $i)$ Pick a random start-to-end path in PGIR, $ii)$ remove all edges in the PGIR for the set of topological edges chosen, and $iii)$ repeat until no such path exists.
-The number of PGIR paths that we are able to remove is a lower bound on the number of failures required to disconnect the prefix from its aggregate.
-
-For example, imagine we use the data center example from \S\ref{sec:motivation}, with the policy: 
-\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
-Figure~\ref{fig:aggregation-safety} shows the network topology and a simplified PGIR.
-Since the compiler knows an aggregate will be placed at $X$, and it knows that, the route for \CD{PG1} will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
-We could remove the $A$--$D$--$X$ path first.
-We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR, though in this case there are none.
-Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
-Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}.
-This process is repeated for other aggregation locations (e.g., $Y$).
-
 %\subsection{Propane Properties}

### 2016-06-10 paper/v2/paper.tex
small wording changes

@@
 
-To reduce configuration errors, many practitioners have a adopted a template-based
+To reduce configuration errors, many practitioners have adopted a template-based
 approach~\cite{hatch,thwack}, in which common tasks are captured as parameterized templates.
@@
 guaranteed to be policy-compliant in the face of
-{\em arbitrary} failures.\footnote{In this paper we assume that BGP is the only control plane protocol running in the network or the other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This does not mean that the implementation is always
+{\em arbitrary} failures.\footnote{In this paper we assume that either BGP is the only control plane protocol running in the network or the other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This does not mean that the implementation is always
 able to send traffic to its ultimate destination
@@
 Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally.
-This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally.
+This policy is enabled by using non-overlapping address spaces in the two clusters and ensuring that only the address space for the global services is announced externally.
 Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}.

### 2016-06-13 paper/v2/paper-edited.tex
some edits

@@
 In addition, we augment the algebra
-of regular expressions to directly support a notion of {\em preferences} and provide a semantics in terms of sets of ranked paths.
+of regular expressions to support a notion of {\em preferences} and provide a semantics in terms of sets of ranked paths.
 The preferences indicate fail-over behaviors:  among all specified paths that are still available,
@@
 We illustrate this point using two examples based on policies that we have seen in practice.
-The next section shows how \sysname allows operators to directly express these policies.
+The next section shows how \sysname allows operators to express these policies directly.
 %the ease with which the
@@
 $>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
-the same time, to satisfy P3 the preference at \CD{R2}'s
+the same time, to satisfy P3, the preference at \CD{R2}'s
 \CD{Cust}-facing interface should be lower than that at
@@
 one or more prefixes, we define a \sysname \emph{policy}.
-Within a policy, statements with the form $t$\Path$p$
+Within a policy, statements with the form $t\;$\Path$\;p$
 associate the prefixes defined by the predicate $t$ with the set of
@@
 
-Since by default routing allows transit traffic (\EG, traffic entering from
+Since, by default, routing allows transit traffic (\EG, traffic entering from
 \CD{Peer} and leaving through \CD{Prov}), we separately define a
@@
 
-We handle these challenges by breaking compilation into multiple stages and developing efficient algorithms for each (See Figure~\ref{fig:pipeline}).
+We handle these challenges by breaking compilation into multiple stages (see Figure~\ref{fig:pipeline}), and developing efficient algorithms for the translation between each stage.
 The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR).
@@
 Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation.
-Vendor-specific adaptors to translate from ABGP to concrete device configurations or to integrate with an existing template-based system are easily added.
-The \sysname compiler currently generates Quagga router configurations by default.
+ABGP can then be translated into various vendor-specific device
+configurations as needed. The \sysname compiler currently generates 
+Quagga router configurations from ABGP.
 
@@
 
-The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available due to loops that are rejected by BGP.
+The checks for failure safety described above overlooked one critical point: A better (lower rank) path might not be available due to loops that are rejected by BGP.
 To avoid this situation, the compiler checks that, any time some context $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$.
@@
 
-\subsection{More Safety}
+\subsection{Additional Safety Checks}
 
@@
 We frame the aggregation problem as a problem of connectivity in the PGIR.
-Specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures required to  disconnect where the prefix originates from where it is aggregated.
+Specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures required to disconnect the prefix origin from its aggregation point.
 The difficulty is that the same links in the topology can appear in multiple places in the PGIR.
@@
 %
-We adopt the following simple strategy to lower bound the number of failures: $i)$ Pick a random start-to-end path in PGIR, $ii)$ remove all edges in the PGIR for the set of topological edges chosen, and $iii)$ repeat until no such path exists.
+We adopt the following simple strategy to find a lower bound on 
+the number of failures: $i)$ Pick a random start-to-end path in PGIR, $ii)$ remove all edges in the PGIR for the set of topological edges chosen, and $iii)$ repeat until no such path exists.
 The number of PGIR paths that we are able to remove is a lower bound on the number of failures required to disconnect the prefix from its aggregate.
@@
 Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
-Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}.
+Because $A$ is then disconnected from $X$, the compiler knows that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}.
 This process is repeated for other aggregation locations (e.g., $Y$).

### 2016-06-13 paper/v2/paper-edited.tex
fix conflict

@@
 The policy of this network is shown on the right.
-It prefers the neighbors in a certain order (P1) and does not want to act as a transit between \CD{Peer} and \CD{Prov} (P2).
+It prefers that traffic leave the network through neighbors in a certain order (P1) and does not want to act as a transit between \CD{Peer} and \CD{Prov} (P2).
 It prefers to exchange traffic with \CD{Cust} over \CD{R1} rather than \CD{R2} because \CD{R1} is cheaper (P3).
@@
 \CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links.
+A similar policy must be configured for \CD{R2}.
 Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based import and export filters at each router.
@@
 To this end, we introduce the notion of \emph{regret-free} preferences, which is motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
-Preferences are \emph{regret-free} if, whevever some router $r$ prefers an advertisement $X$ over another $Y$, there is always some policy-compliant path to each final (advertisement) destination $d$ that is at least as good $(\leq_{rank})$ as any possible path to $d$ if it had accepted $Y$ instead.
-In other words, the preference of $X$ over $Y$ at $r$ is regret-free if we are never worse off by choosing $X$.
+Router $r$ has a \emph{regret-free} preference for a set of advertisements $X$ over $Y$ if, whevever $r$ selects an advertisement from $X$ over another from $Y$, there is always some policy-compliant path to each final (advertisement) destination $d$ that is at least as good $(\leq_{rank})$ as any possible path to $d$ if it had accepted an advertisement from $Y$ instead.
+In other words, the preference of $X$ over $Y$ at $r$ is regret-free if we are never worse off by choosing from $X$.
 %
@@
 \CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
-Figure~\ref{fig:aggregation-safety} shows the network topology simplified PGIR.
+Figure~\ref{fig:aggregation-safety} shows the simplified PGIR.
 Since the compiler knows aggregation will occur at $X$, and it knows that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
@@
 Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
-Because $A$ is then disconnected from $X$, the compiler knows that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}.
+Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}.
 This process is repeated for other aggregation locations (e.g., $Y$).
+>>>>>>> minor edits
 

### 2016-06-15 paper/v2/paper-edited.tex
fix
adding correct style
adding categories and terms

@@
-\documentclass{sig-alternate-10pt}
+%\documentclass{sig-alternate-10pt}
+\documentclass[10pt]{sigalternate052015}
 
@@
 \begin{document}
+
+\setcopyright{acmcopyright}
+\conferenceinfo{SIGCOMM '16}{August 22--26, 2016, Florianopolis, Brazil}
 
@@
 \maketitle
-
-%\category{CR-number}{subcategory}{third-level}
-%% general terms are not compulsory anymore,
-%% you may leave them out
-%\terms
-%term1, term2
-%\keywords
-%keyword1, keyword2
 
@@
 %
+%  **Keywords**
+%
+%
+%=====================================================
+
+%\category{CR-number}{subcategory}{third-level}
+
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10003033.10003068.10003073.10003075</concept_id>
+<concept_desc>Networks~Network control algorithms</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10011006.10011050.10011017</concept_id>
+<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[300]{Networks~Network control algorithms}
+\ccsdesc[300]{Software and its engineering~Domain specific languages}
+
+\printccsdesc
+
+\keywords{Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault tolerance}
+
+%% general terms are not compulsory anymore,
+%% you may leave them out
+%\terms Network Programming Language, Distributed Program Synthesis
+%\keywords Propane Language, BGP, Synthesis, Compilation
+
+%=====================================================
+%
+%
 %  **Introduction**
@@
 
-\subsection{Example 2:  The Data Center}
-
- While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible.
-Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally.
-This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally.
-Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}.
-The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.
-
-The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ announce what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}.
-This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be assigned to local services without updating router configurations).
-
 \begin{figure}[t!]
@@
 \end{figure}
+
+\subsection{Example 2:  The Data Center}
+
+ While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible.
+Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally.
+This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally.
+Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}.
+The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.
+
+The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ announce what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}.
+This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be assigned to local services without updating router configurations).
 
@@
 \begin{code}
-\Define transit(X,Y) = \Enter(X \OR Y) \AND \Exit(X \OR Y)
+\Define transit(X,Y) = \Enter(X{\OR}Y) \AND \Exit(X{\OR}Y)
 \Define cust-transit(X,Y) = \Later(X) \AND \Later(Y)
@@
 
-We handle these challenges by breaking compilation into multiple stages (see Figure~\ref{fig:pipeline}), and developing efficient algorithms for the translation between each stage.
-The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR).
-Policies in RIR are checked for well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR).
-The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions.
-We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes.
-Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation.
-ABGP can then be translated into various vendor-specific device
-configurations as needed. The \sysname compiler currently generates 
-Quagga router configurations from ABGP.
-
 % grammar
@@
 
-\begin{figure*}\small
+\begin{figure*}[t]\small
   \begin{minipage}[t]{.45\linewidth}
-  \hdr{\large Syntax}{}
+  \hdr{Syntax}{}
   \vspace*{-1\baselineskip}
@@
   \begin{minipage}[t]{.5\linewidth}\small
-  \hdr{\large Propane Expansions}{}
+  \hdr{Propane Expansions}{}
   \vspace*{-1\baselineskip}
@@
 
+We handle these challenges by breaking compilation into multiple stages (see Figure~\ref{fig:pipeline}), and developing efficient algorithms for the translation between each stage.
+The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR).
+Policies in RIR are checked for well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR).
+The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions.
+We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes.
+Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation.
+ABGP can then be translated into various vendor-specific device
+configurations as needed. The \sysname compiler currently generates 
+Quagga router configurations from ABGP.
+
 \para{Syntax}
@@
 
-  \hdr{\large Topology}{}
+  \hdr{Topology}{}
   \vspace*{-2\baselineskip}
@@
 
-  \hdr{\large Policy Automata}{}
+  \hdr{Policy Automata}{}
   \vspace*{-0.5\baselineskip}
@@
   \begin{minipage}[t]{.5\linewidth}
-  \hdr{\large Product Graph IR}{}
+  \hdr{Product Graph IR}{}
   \vspace*{-1\baselineskip}
@@
 This process is repeated for other aggregation locations (e.g., $Y$).
->>>>>>> minor edits
 
@@
     Match \PEER=C, \COMM=(3,2)
-      Export \COMM \Arrow (4,2), \MED \Arrow 80, \PEER \Arrow W
+      Export \COMM \Arrow (4,2), 
+             \MED \Arrow 80, \PEER \Arrow W
   \Router{B}

### 2016-06-15 paper/v2/paper-edited.tex
0,1,2

@@
 Ryan Beckett\\
-  \affaddr{Princeton University}\\
-  \email{rbeckett@princeton.edu}
+  \affaddr{Princeton University}
+  %\\
+  %\email{rbeckett@princeton.edu}
 \and
 Ratul Mahajan\\
-  \affaddr{Microsoft Research}\\
-  \email{ratul@microsoft.com}
+  \affaddr{Microsoft Research}
+  %\\
+  %\email{ratul@microsoft.com}
 \and
 Todd Millstein\\
-  \affaddr{University of California, Los Angeles}\\
-  \email{todd@cs.ucla.edu}
+  \affaddr{University of California, Los Angeles}
+  %\\
+  %\email{todd@cs.ucla.edu}
 \and
 Jitu Padhye\\
-  \affaddr{Microsoft Research}\\
-  \email{padhye@microsoft.com}
+  \affaddr{Microsoft Research}
+  %\\
+  %\email{padhye@microsoft.com}
 \and
 David Walker\\
-  \affaddr{Princeton University}\\
-  \email{dpw@princeton.edu}
+  \affaddr{Princeton University}
+  %\\
+  %\email{dpw@princeton.edu}
 }
@@
 
+%\textbf{Abstract---}
+%We develop a system called \sysname to help network operators with a challenging and error prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex distributed protocols.
+%%
+%\sysname allows operators to specify their objectives naturally, describing high-level constraints and preferences on the types of paths that traffic should take through their network or other networks.
+%%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
+%%
+%Our compiler automatically translates these specifications to a collection of BGP router configurations.
+%% that can execute on existing commodity hardware.
+%%
+%We introduce data structures and algorithms that guarantee that the compiled, distributed configurations correctly implement the routing policy under all possible combinations of failures.
+%%
+%We use \sysname to specify and compile the configurations of real
+%data center and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds to thousands of routers.
+
 \textbf{Abstract---}
-We develop a system called \sysname to help network operators with a challenging and error prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex distributed protocols.
-%
-\sysname allows operators to specify their objectives naturally, describing high-level constraints and preferences on the types of paths that traffic should take through their network or other networks.
+We develop \sysname, a language and a compiler to help network operators with a challenging, error-prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex, distributed protocols.
+%
+The language allows operators to specify their objectives naturally, using high-level constraints and ordered preferences on paths that traffic should take.
+%through their network or other networks.
 %using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
 %
-Our compiler automatically translates these specifications to a collection of BGP router configurations.
-% that can execute on existing commodity hardware.
-%
-We introduce data structures and algorithms that guarantee that the compiled, distributed configurations correctly implement the routing policy under all possible combinations of failures.
-%
-We use \sysname to specify and compile the configurations of real
-data center and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds to thousands of routers.
+The compiler automatically translates these specifications to router-level BGP configurations, using a novel data structure that compactly encodes the flow of routing information along policy-compliant paths.
+%It uses We introduce data structures and algorithms that
+It guarantees that the compiled configurations correctly implement the specified policy under all possible combinations of failures.
+%
+We use \sysname for data center and backbone networks of a large cloud provider.
+We find that our language can effectively express their policies and, despite its strong guarantees, our compiler scales to topologies with hundreds or thousands of routers.
 
@@
 It is well known that configuring networks is error
-prone and such errors can lead to disruptive network
+prone and such errors can lead to disruptive 
 downtimes~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
@@
 %
-Operators therefore must manually decompose network-wide policy into
+Operators must manually decompose network-wide policy into
 device behaviors, such that policy-compliant behavior results from the distributed interactions of
@@
 circumstances but also during failures.  The need to reason
-about possible failures exacerbates the challenge
+about all possible failures exacerbates the challenge
 for network operators.  As a result, configurations that work
@@
 
-To reduce configuration errors, many practitioners have a adopted a template-based
-approach~\cite{hatch,thwack}, in which common tasks are captured as parameterized templates.
+To reduce configuration errors, operators are increasingly adopting an 
+approach in which common tasks are captured as parameterized templates~\cite{hatch,thwack}.
 %
@@
 
-Configuration analysis tools~\cite{batfish,feamster+:rcc} have been developed as a complementary approach for reducing misconfigurations by checking that the low-level configurations match high-level operator intent.
-However, such tools cannot help operators come up with the configuration in the first place.
-Further, today's tools can only check correctness under concrete failure scenarios, rather than under all possible failures.
+As a complementary approach, configuration analysis tools can help reduce misconfigurations by checking if low-level configurations match high-level policy~\cite{batfish,feamster+:rcc}.
+However, such tools too cannot help operators with the challenging task of generating configurations in the first place.
+
+%Further, today's tools cannot verify correctness under concrete failure scenarios, rather than under all possible failures.
 
@@
 guaranteed to be policy-compliant in the face of
-{\em arbitrary} failures.\footnote{In this paper we assume that BGP is the only control plane protocol running in the network or the other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This does not mean that the implementation is always
+{\em arbitrary} failures.\footnote{We assume that BGP is the only routing protocol running in the network or the other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This guarantee does not mean that the implementation is always
 able to send traffic to its ultimate destination
-(\EG in the case of a network partition), but rather that it always respects the
+(\EG, in the case of a network partition), but rather that it always respects the
 centralized policy, which may include dropping traffic when there is no route.
@@
 
-In implementing their policy, each network operator assumes that
-neighboring ASes correctly implement BGP and honor contracts related
-to MEDs and communities. \sysname makes the same assumption when
-deriving BGP configurations for a network.
-
 The combination of arbitrary import and export filters and route selection policies at individual routers make BGP a highly flexible routing protocol.
 That flexibility, however, comes at the cost of it being difficult to configure correctly.
+When configuring BGP, network operators assume that
+neighboring ASes correctly implement BGP and honor contracts for MEDs and communities. \sysname makes the same assumption when
+deriving BGP configurations for a network.
 

### 2016-06-15 paper/v2/paper-edited.tex
3

@@
 %Operators today generate the BGP configuration of individual devices based on intended policy.
-When generating BGP configurations, whether fully manually or aided by templates, the operators face the challenge of decomposing network-wide policies
-into appropriate device-level policies.
+When generating BGP configurations, whether manually or aided by templates, the operators face the challenge of decomposing network-wide policies
+into correct device-level policies.
 This decomposition is not always straightforward and ensuring policy-compliance is tricky, especially in the face of failures.
-We illustrate this point using two examples based on policies that we have seen in practice.
-The next section shows how \sysname allows operators to express these policies directly.
+In this section, we illustrate this difficulty using two examples based on policies that we have seen in practice.
+The next section shows how \sysname allows operators to express these policies naturally.
 %the ease with which the
@@
 
-To implement P1 of the policy, the operators must compute and assign
+To implement policy P1, the operators must compute and assign
 local preferences such that preferences at \CD{Cust}-facing interfaces
@@
 \CD{Cust}-facing interface should be lower than that at
-\CD{R1}. Implementing P3 properly will require MEDs to be appropriately configured on \CD{R1} and \CD{R2}.
+\CD{R1}. Implementing P3 will also require MEDs to be appropriately configured on \CD{R1} and \CD{R2}.
 To implement P2, the operators can assign communities that
@@
 
-Clearly it is difficult to properly configure even this
-small example network manually; devising correct configurations for real networks can quickly become a nightmare.
-Such networks have many neighbors spanning multiple commercial-relationship classes, differing numbers of links to each neighbor, along with several neighbor- or prefix-based exceptions to the default behavior.
+Clearly, it is difficult to correctly configure even this
+small example network manually; correctly configuring real, larger networks can quickly become a nightmare.
+Such networks have hundreds of neighbors spanning multiple commercial-relationship classes, differing numbers of links to each neighbor, along with several neighbor- or prefix-based exceptions to the default behavior.
 A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
@@
 
-The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ announce what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}.
-This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be assigned to local services without updating router configurations).
-
-However, this implementation does not have the right behavior in the face of failures.
+The operator may implement the policy by having X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ export externally what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}.
+This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can occur independently, e.g., local services can be assigned new prefixes without updating those routers' configurations.
+
+However, this implementation has incorrect behavior in the face of failures.
 Suppose links X--G and X--H fail.
 Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D.
-Per policy implementation, X will start "leaking" these prefixes externally.
-Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are used for other services outside of the data center).
+Per its policy implementation, X will start "leaking" these prefixes externally.
+Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are reused for other services outside of the data center).
 This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter.
@@
 
-To avoid this problem, the operator may decide to disallow "valley" paths, i.e., those that go up, down, and back up again.
+To avoid this problem, the operator may disallow "valley" paths, i.e., those that go up, down, and back up again.
 This guard can be implemented by $X$ and $Y$ rejecting paths through the other.
@@
 If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce \CD{PG} externally.
-This announcement will bring to X traffic for \CD{PG1} as well, but because of valley-free filtering, X does not have a valid route for \CD{PG1} and will thus drop all traffic to it.
+This announcement will bring to X traffic for \CD{PG1} as well, but because valleys are disallowed, X does not have a valid route for \CD{PG1} and will drop all traffic to it.
 
 Thus, we see that devising a configuration that ensures policy compliance in the face of failures is complex and error-prone.
-\sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures (if that is possible; otherwise, it generates a compile-time error).
+\sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures if possible---otherwise, it generates a compile-time error.
 For aggregation, it also provides a lower bound to operators on the number of failures under which aggregation will not result in blackholes.

### 2016-06-15 paper/v2/paper-edited.tex
5

@@
 Policies for (distributed) control planes differ from data-plane
-policies in a few important ways. First, control-plane
-policies must account for all failures at compile time; there is
+policies in a few important ways. First, they must account for all failures at compile time; there is
 no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
 %
-In \sysname, we enable such specifications through a notion of {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
+In \sysname, we enable such specifications through {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
 %
@@
 
-In the rest of this section, we define \sysname policies for the two
-examples from the previous section, introducing key aspects of
-the \sysname language along the way. The complete syntax of the
-language as well as our strategy for compiling \sysname policies to
-BGP is defined in \S\ref{sec:compilation}.
+This section introduces the \sysname language using the 
+examples from the previous section.
+%, introducing key aspects of
+%the \sysname language along the way. 
+The next section describes the complete syntax of the
+language as well as our strategy for compiling it to
+BGP.
 
@@
 
-\sysname allows operators to configure the network with the
+\sysname lets operators configure the network with the
 abstraction that they have centralized control over routing.
@@
 that describe the
-different routes traffic may (or may not) take and their relative preferences.
+paths traffic should---or should not---take and their relative preferences.
 \sysname specifications are written modularly via a series
@@
 %
-These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
+
+Collectively, the constraints above capture the entire policy. From them, our compiler will generate per-device import and export filters, local preferences,
 MED attributes, and community tags to ensure that the policy is
@@
 
-In our data center,
-there are three main concerns:
-(1) traffic for the prefix block allocated to each top-of-rack router must be able to reach that router,
+Our data center example network has three main concerns:
+(1) traffic for the prefix allocated to each top-of-rack router must be able to reach that router,
 (2) local services must not leak outside the data center, and
@@
 
-\sysname allows us to specify each of these constraints modularly.
-The first constraint is about prefix ownership---namely, we only want traffic for certain prefixes to end up at a particular location.
+\sysname allows modular specification of each of these constraints.
+The first constraint is about prefix ownership---we want traffic only for certain prefixes to end up at a particular location.
 The following definition captures this intent.
@@
 \noindent
-In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
-end at router \CD{A}; traffic matching \CD{PG2},
+This definition says that traffic for prefix \CD{PG1} is allowed to follow only paths that
+end at router \CD{A}; traffic for \CD{PG2},
 but not \CD{PG1}, must
@@
 Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location, which is otherwise unconstrained.
-The special keyword \Out{} here matches any location outside the user's network, while the keyword \In{} will match any location inside the network.
-For the second constraint, we can define another policy:
+The special keyword \Out{} matches any location outside the data center network, while the keyword \In{} will match any location inside the network.
+
+For the second constraint, we define another policy:
 
@@
 %from external ASes.
-The locality constraint ensures that traffic for local
-prefixes only ever follows paths that are internal to the network at each hop.
+This definition says that traffic for local
+prefixes only follows paths that are internal to the network at each hop.
 This constraint guarantees that the services remain reachable only to locations
@@
 In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG}
-(which we assume is defined earlier using an appropriate prefix such
-as \CD{74.3.28.0/24})
+(which we assume is defined earlier)
 when advertised outside the datacenter.

### 2016-06-16 paper/v2/paper-edited.tex
5.1

@@
 
-The front-end (FE) of \sysname simplifies operators' task of describing preferred paths.
-That simplicity, however, comes at the cost of compilation complexity.
-The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, determine which ones can be honored under failures, and ensure policy compliance under all possible failure cases.
+The examples above use what we call the front end (FE) of \sysname.
+It simplifies operators' task of describing preferred paths, but that simplicity comes at the cost of compilation complexity.
+The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, determine which ones can be honored under failures, and ensure policy compliance under all failure cases.
 
@@
 
-  \caption{Regular Intermediate Language (RIL) syntax (left), and
+  \caption{Regular Intermediate Representation (RIR) syntax (left), and
            Propane language expansions (right).}
@@
 
-\subsection{Regular IR (RIR)}
-\label{sec:rir}
-
-We handle these challenges by breaking compilation into multiple stages (see Figure~\ref{fig:pipeline}), and developing efficient algorithms for the translation between each stage.
+To handle these challenges, we decompose compilation into multiple stages, shown in  Figure~\ref{fig:pipeline}, and develop efficient algorithms for the translation between stages.
 The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR).
@@
 We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes.
-Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation.
+Once the compiler determines safety, it translates the PGIR to an abstract BGP (ABGP) representation.
 ABGP can then be translated into various vendor-specific device
-configurations as needed. The \sysname compiler currently generates
-Quagga router configurations from ABGP.
-
-\para{Syntax}
-The \sysname FE is just a thin layer atop a core, regular-expression language (RIR) for describing preference-based path constraints.
+configurations as needed.
+%The \sysname compiler currently generates
+% Quagga router configurations from ABGP.
+
+\subsection{Regular IR (RIR)}
+\label{sec:rir}
+
+%\para{Syntax}
+The \sysname FE is just a thin layer atop the RIR for describing preference-based path constraints.
 Figure~\ref{fig:rir-syntax} shows the RIR syntax.
-A policy consists of one or more constraints, each of which have a test on the type of route, and a corresponding set of preferred regular paths.
+A policy has one or more constraints, each of which has a test on the type of route, and a corresponding set of preferred regular paths.
 Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS.
@@
 In addition, $\Sigma$ refers to any symbol.
-We also use the standard regular expressions abbreviation $r^+$ to stand for $r \cdot r^*$, a sequence of one or more occurrences of $r$.
+We also use the standard regular expressions abbreviation $r^+$ for $r \cdot r^*$, a sequence of one or more occurrences of $r$.
 Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisments with a particular community value (i.e., an integer value associated with a path).
@@
 The semantics of RIR is in terms of ranked paths.
-Each preference-based regular path constraint (of the form $r_1 \Prefer \dots \Prefer r_j$) maps to a set of concrete paths in the network that match one of $r_i$.
-We denote a network path as a string of abstract locations (routers or external ASes) of the form: $n_1 n_2 \dots n_k$.
-A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$, that is the path is in the language of the regular expression, and $p$ is a topologically-valid path.
-We denote the length of a path $p$ as $\abs{p}$.
-A path $p$ will have a rank:
+Each preference-based regular path constraint of the form $r_1 \Prefer \dots \Prefer r_j$ maps to a set of concrete paths in the network that match one of $r_i$.
+A network path is a string of abstract locations of the form $n_1 n_2 \dots n_k$.
+A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$, that is, the path is in the language of the regular expression and is topologically valid.
+%We denote the length of a path $p$ as $\abs{p}$.
+
+A path $p$ has rank:
 $$(\min_i \set{ p \in \mathcal{L}(r_i) }, \abs{p})$$
-where the rank is lexicographically ordered according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the path length.
+which is lexicographically ordered according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the path length $\abs{p}$.
 Lower ranks indicate \emph{more} preferred paths.
 Traffic may be sent on any of the most preferred paths for each pair of starting and ending locations that appear in some specified path.
-There is an implicit lowest preference to drop traffic: $\emptyset$ when no other route is possible.
+There is an implicit lowest preference $\emptyset$ to drop traffic when no other route is possible.
 
@@
 
-\para{Propane FE to RIR}
-
-The first step in compilation is to reduce the \sysname front-end language (FE) to the simpler, regular intermediate representation (RIR) from Figure~\ref{fig:rir-syntax}.
+\para{From FE to RIR}
+
+The first stage in \sysname compilation reduces the FE to the simpler RIR from Figure~\ref{fig:rir-syntax}.
 The main differences between the FE and RIR are: $i)$ FE allows the programmer to specify constraints using a series of (modular) definitions, and combine them later, $ii)$ FE provides high-level names that abstract sets of routes and groups of prefixes/neighbors, and $iii)$ FE allows the preference operator to be used more flexibly.
 
-A key constraint when translating FE to RIR is to ensure that all specified routes are well-formed.
+A key constraint when translating FE to RIR is ensuring that all specified routes are well-formed.
 In particular, each regular path constraint $r$ must satisfy $r \subseteq \Out^* \cdot \In^+ \cdot \Out^*$.
-This ensures that users only control traffic that goes through their network at some point, and that such traffic does not loop back multiple times through their network.
-
-The translation from \sysname FE to RIR is based on a set of rewriting rules.
+It ensures that users only control traffic that goes through their network at some point, and that such traffic does not loop back multiple times through their network.
+
+The translation from FE to RIR is based on a set of rewriting rules.
 The first step merges separate constraints.
@@
 
-The next step rewrites the high-level constraints such as \textit{enter} according to the equivalences in Figure~\ref{fig:rir-syntax}.
+The next step rewrites the high-level constraints such as $\Enter$ according to the equivalences in Figure~\ref{fig:rir-syntax}.
 Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression.
@@
 where $\odot$ stands for an arbitrary regular binary operator, and $x$ is a policy with a single preference.
-Preferences nested under a unary operator (i.e., \textit{star} or \textit{negation}) are flagged by the compiler as invalid policies.
+The compiler flags as invalid preferences nested under a unary operator (i.e., \textit{star} or \textit{negation}).
 

### 2016-06-16 paper/v2/paper-edited.tex
5.2

@@
 In particular, we want a compact representation that describes all the possible ways BGP route announcements can flow through the network subject to the policy and topology constraints.
-Our PGIR captures these dependencies by ``intersecting" each of the regular automata corresponding to the RIR path preferences, and the topology.
+The PGIR captures these constraints by ``intersecting" each of the regular automata corresponding to the RIR path preferences and the topology.
 Paths through the PGIR correspond to real paths through the topology that satisfy the user constraints.
@@
 % Formally define automata
-The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$.
-While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., route announcements flowing in the opposite direction).
-To capture this idea, for each regular expression $r_i$, we construct a deterministic finite state machine on the reversed regular expression.
-Each automaton for the reversed regular expression of $r_i$ is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ consists of all abstraction locations (routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+%The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$. 
+While paths in RIR policy describe the direction traffic flow through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated, i.e., route announcements flowing in the opposite direction.
+To capture this idea, for each regular expression $r_i$ in RIR policy, we construct a deterministic finite state machine on the reversed regular expression.
+Each automaton for the reversed regular expression of $r_i$ is a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
+The alphabet $\Sigma$ consists of all abstraction locations (i.e., routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
 %
@@
 % Formally define product graph
-The combined PGIR is a tuple: ($V'$, $E'$, $s$, $e$, $P$) with
+The combined PGIR is a tuple ($V'$, $E'$, $s$, $e$, $P$) with
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
@@
 
-Intuitively, PGIR tracks which states of each automaton the policy is in as route announcements move between routers.
+Intuitively, PGIR tracks which states of each automaton the policy is in as route announcements move between locations.
 %
@@
 BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
-This is reflected in the product graph by the node with state $(X,1,1)$.
+This possiblity is reflected in the product graph by the node with state $(X,1,1)$.
 From here, if X were to advertise this route to D, it would result in the path $D \cdot X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
@@
 \para{Minimization}
-
-Before checking if policies captured by the PGIR are safe, we minimize the PGIR to improve our safety analysis.
+After building the PGIR as desribed above, 
+we minimize it in order to improve the subsequent analysis that checks if the policies captured by it are safe under failures.
 The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops.
@@
 %
-It often improves the precision of the failure-safety analysis to eliminate cases that are not possible due to loops.
+The precision of the failure-safety analysis often increases when nodes and edges that are not possible due to loops are eliminated.
 %For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
+
 We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
@@
 That is, node $(W,-,4)$ post-dominates node $(W,1,1)$.
-We repeatly apply the above minimizations to the PGIR until no further minimization is possible.
-Colored nodes and dashed edges in Figure~\ref{fig:example-compilation} are removed after minimization since they are irrelvant to the BGP decision process.
+We repeatedly apply the minimizations above to the PGIR until no further minimization is possible.
+In the example of Figure~\ref{fig:example-compilation}, colored nodes and dashed edges are removed after minimization.
+ %since they are irrelvant to the BGP decision process.
 %

### 2016-06-16 paper/v2/paper-edited.tex
5, 6

@@
 
-\subsection{Failure Safety}
+\subsection{Failure-Safety Analysis}
 
@@
 The problem of determining local preferences for each router is closely reflected in the structure of the PGIR.
-In particular, whenever a given router appears in multiple different contexts in the PGIR (i.e., as multiple PGIR nodes), then the compiler must decide which context to prefer.
+In particular, whenever a given router appears in multiple different contexts in the PGIR (i.e., as multiple PGIR nodes that shadow each other), then the compiler must decide which context to prefer.
 %
@@
 A natural question then is how the compiler should order PGIR contexts for each router in a way that is both \emph{sound} and \emph{complete} under all possible failures?
-To this end, we introduce the notion of \emph{regret-free} preferences, which is motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
+To this end, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
 Router $r$ has a \emph{regret-free} preference for a set of advertisements $X$ over $Y$ if, whevever $r$ selects an advertisement from $X$ over another from $Y$, there is always some policy-compliant path to each final (advertisement) destination $d$ that is at least as good $(\leq_{rank})$ as any possible path to $d$ if it had accepted an advertisement from $Y$ instead.
@@
 
-Searching for \emph{regret-free} preferences in general is hard, and clearly enumerating all possible combinations of failures and preference orderings is intractable.
+Searching for \emph{regret-free} preferences in general is hard, and enumerating all possible combinations of failures and preference orderings is intractable.
 We thus adopt a conservative analysis that we found to be both effective and efficient in practice.
-The idea is to search for regret-free preferences by comparing the set of paths available after accepting advertisments in two different PGIR contexts $N_1$ and $N_2$ while refining the comparison when necessary by taking into account information about where advertisements must have already traversed the network before arriving at $N_1$ or $N_2$.
+The idea is to $i)$ search for regret-free preferences by comparing the set of paths available after accepting advertisments in two different PGIR contexts $N_1$ and $N_2$, and $ii)$ refine the comparison when necessary by considering where the announcements must have traversed before arriving at $N_1$ or $N_2$.
 
 \begin{algorithm}[t!]
-\caption{Failure Protection}
+\caption{Inferring regret-free preferences}
 \label{alg:failures}
@@
 
-\subsection{Additional Safety Checks}
-
-\para{Aggregation Safety}
+\subsection{Aggregation-Safety Analysis}
+
+%\para{Aggregation Safety}
 \label{sec:agg-safety}
@@
 
-As demonstrated with Example 2 in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur.
+As shown in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur.
 Deciding when this can happen requires knowledge of the routing policy and not just the topology.
@@
 %
-Because the \sysname compiler has the complete user policy and topology encoded in the PGIR, it is able to efficiently check that aggregates do not black hole traffic for up to $k$ failures.
+Because the PGIR encodes the complete user policy and topology,  \sysname can efficiently check that aggregates do not black hole traffic for up to $k$ failures.
 
@@
 %
-%
+
 We adopt the following simple strategy to find a lower bound on
-the number of failures: $i)$ Pick a random start-to-end path in PGIR, $ii)$ remove all edges in the PGIR for the set of topological edges chosen, and $iii)$ repeat until no such path exists.
+the number of failures: $i)$ pick a random start-to-end path in the PGIR, $ii)$ remove all edges in the PGIR for the set of topological edges chosen, and $iii)$ repeat until no such path exists.
 The number of PGIR paths that we are able to remove is a lower bound on the number of failures required to disconnect the prefix from its aggregate.
 
-For example, recall the data center example from \S\ref{sec:motivation}, with the policy:
+For example, recall the data center example from \S\ref{sec:motivation}, with the policy
 \CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
@@
 This process is repeated for other aggregation locations (e.g., $Y$).
-
-\para{Policy Safety}
-
-Even when programming the network centrally, it is possible for operators to make mistakes and write incorrect policies.
-\sysname includes many additional safety analysis checks to try to catch common mistakes at compile time.
-These include: (i) preference analysis to determine when backup paths/preferences will never be used, (ii) reachability analysis to check if topology locations that should be reachable according to the operator policy are not reachable after combining both the topology and policy, (iii) anycast analysis to find instances where the operator accidentally anycasts a prefix, (iv) aggregate analysis to find when aggregates do not summarize any specific prefix, and others.
 
@@
 
-Since the compiler is only able to control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
+Since the compiler can control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
 Instead, it translates matches from external ASes into a BGP regular expression filter.
@@
 
-We have written a compiler for \sysname that is implemented in roughly 6700 lines of F\# code.
-The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, anycast, the no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates.
-Since each prefix has a separate routing policy, the \sysname compiler is able to compile each routing policy in parallel.
-Currently \sysname supports generating Quagga router configurations out of the box.
-Users can also easily add new vendor-specific adaptors to translate from ABGP to other router configurations, or to incorporate the compiler into an existing template-based system, for example by mixing the \sysname configuration with other configuration components.
-
-\para{PGIR construction}
-
-Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\cite{regex-complexity}.
+Our \sysname compiler is implemented in roughly 6700 lines of F\# code.
+It includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the no-export community, as well as for ensuring at least k-failure safety for aggregate prefixes.
+Since each prefix has a separate routing policy, we compile each routing policy in parallel.
+Currently, \sysname supports generating Quagga router configurations out of the box.
+Users can add new vendor-specific adaptors to translate from ABGP to other router configuration languages, or incorporate the compiler into an existing template-based system, e.g., by mixing the \sysname-generated BGP configuration with other, non-BGP configuration elements.
+
+Our compiler includes the following features that improve its performance and usability.
+
+\para{Efficient PGIR construction}
+
+Constructing automata for extended regular expressions (i.e., those that include negation and intersection) are known to have high complexity~\cite{regex-complexity}.
 The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently.
@@
 
-\para{Failure Safety}
-
-When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the \textit{protect} function.
-That is, whenever for two states $N_1$ and $N_2$ we compute $protect(G, N_1, N_2)$, if the function evaluates to $true$, then each of the intermediate related states $x$ and $y$ must also satisfy $protect(G, x, y)$.
+\para{Fast failure-safety analysis}
+
+When computing local preferences and ensuring failure safety, as described in \S\ref{sec:compilation}, the compiler performs memoization of the \textit{Regret-Free} function.
+That is, whenever for two states $N_1$ and $N_2$ we compute $Regret-Free(G, N_1, N_2)$, if the function evaluates to $true$, then each of the intermediate related states $x$ and $y$ must also satisfy $protect(G, x, y)$.
 Memoizing these states dramatically reduces the amount of work performed to find preferences in the common case.
 
-\para{Configuration generation}
-
-The naive code generation algorithm described in Section~\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair for every node in the product graph before minimization.
-Our implementation performs partial minimization during generation by recognizing common cases like when there is no restriction on exporting to or importing from neighbors.
+\para{Efficient configuration generation}
+
+The naive code generation algorithm described in \S\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair for every node in the product graph before minimization.
+Our implementation performs partial minimization during generation by recognizing common cases such as when there is no restriction on exporting to or importing from neighbors.
+
+\para{Checking policy correctness}
+
+Even when programming the network centrally, it is possible for operators to make mistakes and write incorrect policies.
+\sysname includes many analyses to flag common mistakes at compile time.
+A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if topology locations that should be reachable according to the operator policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator accidentally anycasts a prefix (i.e., originates it from multiple locations), (iv) an aggregate analysis to find when aggregates do not summarize any specific prefix.
 

### 2016-06-16 paper/v2/paper-edited.tex
all

@@
 %% %
-%% We have implemented a compiler for \sysname and evaluated it against several real-world configurations for data centers and core backbone networks. We demonstrate the \sysname compiler can scale to
+%% We have implemented a compiler for \sysname and evaluated it against several real-world configurations for datacenters and core backbone networks. We demonstrate the \sysname compiler can scale to
 %% topologies with thousands of routers.
@@
 %To date, we have used the language and compiler to experiment with
-%several real-world configurations for data centers and core backbone
+%several real-world configurations for datacenters and core backbone
 %networks.  We demonstrate our prototype compiler can scale to
@@
 %We use \sysname to specify and compile the configurations of real
-%data center and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds to thousands of routers.
+%datacenter and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds to thousands of routers.
 
@@
 %
-We use \sysname for data center and backbone networks of a large cloud provider.
+We use \sysname for datacenter and backbone networks of a large cloud provider.
 We find that our language can effectively express their policies and, despite its strong guarantees, our compiler scales to topologies with hundreds or thousands of routers.
@@
 
-We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies of data center and backbone networks.
+We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies of datacenter and backbone networks.
 % and compared these specifications with existing configurations.
@@
 
-%% We evaluate \sysname by using it to encode policies of real backbone and data center networks.
+%% We evaluate \sysname by using it to encode policies of real backbone and datacenter networks.
 
@@
 
-\subsection{Example 1:  The Backbone}
+\subsection{Example 1:  The backbone}
 
@@
 
-\subsection{Example 2:  The Data Center}
+\subsection{Example 2:  The datacenter}
 
  While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible.
-Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally.
+Consider the datacenter network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, datacenter networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally.
 This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally.
@@
 Per its policy implementation, X will start "leaking" these prefixes externally.
-Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are reused for other services outside of the data center).
+Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are reused for other services outside of the datacenter).
 This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter.
@@
 %\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
-Link failures in data centers are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.
+Link failures in datacenters are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.
 
@@
 
-\subsection{Example 1: The Backbone}
+\subsection{Example 1: The backbone}
 
@@
 
-\subsection{Example 2: The Data Center}
-
-Our data center example network has three main concerns:
+\subsection{Example 2: The datacenter}
+
+Our datacenter example network has three main concerns:
 (1) traffic for the prefix allocated to each top-of-rack router must be able to reach that router,
-(2) local services must not leak outside the data center, and
+(2) local services must not leak outside the datacenter, and
 (3) aggregation must be performed on global prefixes to reduce churn
@@
 end at router \CD{B}; and so on.
-Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location, which is otherwise unconstrained.
-The special keyword \Out{} matches any location outside the data center network, while the keyword \In{} will match any location inside the network.
+Any traffic destined for a prefix that not a part of the datacenter should be allowed to leave the datacenter and end at some external location, which is otherwise unconstrained.
+The special keyword \Out{} matches any location outside the datacenter network, while the keyword \In{} will match any location inside the network.
 
@@
 %This means traffic for
-%\CD{PG*} may be sent either from other data center routers or
+%\CD{PG*} may be sent either from other datacenter routers or
 %from external ASes.
@@
 This constraint guarantees that the services remain reachable only to locations
-inside the data center.
+inside the datacenter.
 
@@
 The second line ensures that traffic for local prefixes never enters the network from an outside location.
-This  guarantees that the services remain reachable only to locations internal to the data center.
+This  guarantees that the services remain reachable only to locations internal to the datacenter.
 %
@@
 %
-For example, in the data center configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:
+For example, in the datacenter configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:
 
@@
 
-\subsection{Product Graph IR}
+\subsection{Product graph IR}
 
@@
 
-\subsection{Failure-Safety Analysis}
+\subsection{Failure-safety analysis}
 
@@
 
-\subsection{Aggregation-Safety Analysis}
+\subsection{Aggregation-safety analysis}
 
@@
   \includegraphics[width=\columnwidth]{figures/aggregation}
-  \caption{Aggregation safety for a data center.}
+  \caption{Aggregation safety for a datacenter.}
   \label{fig:aggregation-safety}
@@
 
-For example, recall the data center example from \S\ref{sec:motivation}, with the policy
+For example, recall the datacenter example from \S\ref{sec:motivation}, with the policy
 \CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
@@
 
-We apply \sysname on real policies for backbone and data center networks.
-Our main goals are to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
+We apply \sysname on real policies for backbone and datacenter networks.
+Our main goals are to evaluate if its language is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
 
@@
 
-We obtained routing policy for the backbone network and for the data centers of a large cloud provider.
-Multiple data centers share this policy.
-The backbone network connects to the data centers and also has many external BGP neighbors.
-The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for data center routers or actual configurations for the backbone network (where templates are not used because the network has less regular structure).
-
-The networks have the type of policies that we outline earlier (\S\ref{sec:motivation}).
+We obtained routing policy for the backbone network and for the datacenters of a large cloud provider.
+Multiple datacenters share this policy.
+The backbone network connects to the datacenters and also has many external BGP neighbors.
+The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for datacenter routers or actual configurations for the backbone network (where templates are not used because the network has less regular structure).
+
+The networks have the types of policies that we outlined earlier (\S\ref{sec:motivation}).
 The backbone network classifies external neighbors into several different categories and prefers paths through them in order.
@@
 
-All routers in the datacenter network run BGP using a private AS number and peer with each other and with the backbone network over eBGP.
-The routers aggregate prefixes when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region.
-They also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
+Routers in the datacenter network run BGP using private AS numbers and peer with each other and with the backbone network over eBGP.
+The routers aggregate some prefix blocks when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region.
+The datacenter networks also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
 
 \begin{figure}
-  \subcaptionbox{Data center}
+  \subcaptionbox{Datacenter}
     {\includegraphics[width=.49\columnwidth]{figures/compilation-times-dc.png}}
-  \subcaptionbox{Backbone network}
+  \subcaptionbox{Backbone}
     {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
@@
 We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname.
-The data center operator said that he found the language intuitive.
-The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We found that the data center policies were correctly translated.
+The datacenter operator said that he found the language intuitive.
+The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We found that the datacenter policies were correctly translated.
 For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.
 
-Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the routing policies for \sysname were 43 lines for the backbone network and 31 lines for the data center networks.
+Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the routing policies for \sysname were 43 lines for the backbone network and 31 lines for the datacenter networks.
 
@@
 We study the compilation of time for both policies as a function of network size.
-Even though the networks we study have a fixed topology and size, we can explore the impact of size because our converted policies are network-wide and the compiler takes topology itself as an input.
-For the data center network, we build and provide as input fat tree~\cite{fattree} topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy.
-We take this approach to smoothly explore different sizes.
-%There is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete data center topologies.
+Even though the networks we study have a fixed topology and size, we can explore the impact of size because the policies are network-wide and the compiler takes topology itself as an input.
+For the datacenter network, we build and provide as input fat tree~\cite{fattree} topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy.
+%We take this approach to smoothly explore different sizes.
+%There is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete datacenter topologies.
 For a given size, our reported results match those for the concrete topologies.
-
-For the backbone network, the internal topology does not matter since all routers connect in a full iBGP mesh.
-We explore different mesh sizes and randomly map neighboring networks to routers.
+For the backbone network, the internal topology does not matter since all routers connect to each other through iBGP.
+We explore different (full iBGP) mesh sizes and randomly map neighboring networks to routers.
 Even though each border router connects to many external peers, we count only the mesh size.
@@
 %
-Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes.
-For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on each predicate in parallel.
-Note that a single predicate can describe many prefixes, for example by matching on a disjunction of prefixes.
-At their largest sizes, the per-predicate compilation time is roughly 10 seconds for the data center network and 45 seconds for the backbone network.
+Figure~\ref{fig:compilation-times} shows the compilation times for datacenter and backbone networks of different sizes.
+For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on predicates in parallel.
+A single predicate can describe many prefixes, for example by matching on a disjunction of prefixes.
+At their largest sizes, the per-predicate compilation time is roughly 10 seconds for the datacenter network and 45 seconds for the backbone network.
 
@@
 
-Total compilation for the largest data center is less than 9 minutes total.
-Unlike the data center policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases.
+Total compilation for the largest datacenter is less than 9 minutes total.
+Unlike the datacenter policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases.
 Compilation for the largest backbone network, takes less than 3 minutes total.
@@
 
-In both examples, we observe that our safety analysis algorithm for finding preferences is highly efficient, taking only a small fraction of the total running time.
-PGIR minimization is proportionally the most expensive compilation phase, however minimization can be capped after a certain number of iterations for larger networks if necessary.
-Both the backbone and data center networks policies we considered can be successfully compiled without minimization.
+In both examples, we observe that our failure-safety analysis algorithm for finding preferences is highly efficient, taking only a small fraction of the total running time.
+PGIR minimization is the most expensive compilation phase.
+If needed, minimization can be capped after a certain number of iterations for large networks.
+Both the backbone and datacenter  policies we considered can be successfully compiled without minimization.
 
@@
 \begin{figure}[t!]
-  \subcaptionbox{Data center}
+  \subcaptionbox{Datacenter}
     {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
-  \subcaptionbox{Backbone network}
+  \subcaptionbox{Backbone}
     {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
@@
 %Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
-Minimization is highly effective for both the data center and backbone policies. In all cases, minimized policies are a small fraction of the size of their non-minimized counterparts.
+Minimization is highly effective for both the datacenter and backbone policies. In all cases, minimized policies are a small fraction of the size of their non-minimized counterparts.
 
@@
 For the backbone network, the size of \sysname configurations is roughly similar to the BGP components of actual router configurations, though qualitative differences exist (see below).
-We did not have actual configurations for the data center network; they are dynamically generated from templates.
+We did not have actual configurations for the datacenter network; they are dynamically generated from templates.
 
@@
 
-Finally, we comment briefly on how \sysname-generated configurations differ from configurations or templates generated by operators.
-%
-In some cases, \sysname configurations are similar.
+We comment briefly on how \sysname-generated configurations differ from configurations or templates generated by operators.
+%
+In some ways, \sysname configurations are similar.
 For example, preferences among neighboring ASes are implemented with a community value to tag incoming routes according to preference, which is then used at other border routers to influence decisions.
 
-In other cases, the \sysname configurations are different, relying on a different BGP mechanism to achieve the same result. Some key differences that we observed were:
+In other ways, the \sysname configurations are different, relying on a different BGP mechanism to achieve the same result. Some key differences that we observed were:
 
@@
 
-$ii)$ operators prevented unneeded propagation of more-specific route announcements from a neighboring AS based on their out-of-band knowledge about the topology, whereas \sysname propagated these advertisements;
+$ii)$ operators prevented unneeded propagation of more-specific route announcements from a less-preferred neighboring AS based on their out-of-band knowledge about the topology, whereas \sysname propagated these advertisements;
 
@@
 
-We are currently investigating if such differences matter to operators (e.g., if they want to read \sysname configurations) and, if necessary, how to reduce them.
+We are investigating if such differences matter to operators, e.g., if they want to read \sysname configurations, and, if necessary, how to reduce them.
 
@@
 
-\paragraph*{SDN Languages}
-\sysname{} was heavily influenced by recent SDN programming
+Our work draws on four threads of prior work.
+
+\para{SDN languages}
+\sysname{} was heavily influenced by SDN programming
 languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire},
@@
 with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
-and the compiler will generate appropriate OpenFlow rules.
+and the compiler generates appropriate OpenFlow rules.
 \sysname is more expressive as it allows users to specify preferences among
-paths and it generates distributed implementations that tolerate any number of faults.
+paths, and it generates distributed implementations that tolerate any number of faults.
 Because FatTire generates data plane rules up front,
@@
 at the cost of generating additional rules that tax switch memory.
-In contrast, \sysname uses traditional distributed
-control plane mechanisms to react to faults, which do not impose additional memory cost.
+In contrast, \sysname relies on distributed
+control plane mechanisms to react to faults, which do not have additional memory cost.
 Because of the differences in the underlying technology, the analyses
@@
 for intra-domain routing, \sysname uses them for inter-domain routing as
-well, unlike any existing SDN language.
-
-\paragraph*{Configuration Automation}
+well, unlike existing SDN languages.
+
+\para{Configuration automation}
 Many practitioners use configuration templates~\cite{hatch,thwack}, to ensure certain kinds of consistency across similar devices.
@@
 
-\paragraph*{Configuration Analysis}
+\para{Configuration analysis}
 The notion that configuring network devices is difficult and error-prone is not new.
-Past researchers have tried to tackle this problem by analyzing existing
+In the past, researchers have tried to tackle this problem by analyzing existing
 firewall configurations~\cite{fang,lumeta,margrave} and
-BGP configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe} and reporting errors or inconsistencies when they are detected.
+router configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe,arc} and reporting errors or inconsistencies when they are detected.
 Our research is complementary to these analysis
@@
 methodology.  By proposing network administrators write configurations
-at a high-level of abstraction, a whole host of low-level errors can be avoided.
-
-\paragraph*{Configuration Synthesis}
+at a high-level of abstraction, a whole host of low-level errors can be avoided and policy implementation can be simplified.
+
+\para{Configuration synthesis}
 ConfigAssure~\cite{narain:lisa05,narain+:configassure}
@@
 
-In this paper, we introduced \sysname, a language and compiler for implementing centralized network policies using a distributed set of devices running BGP.
-Propane allows operators to describe network-wide intent directly through high-level constraints on the shape and relative preferences of paths for different types of traffic.
-When \sysname compiles a policy, then the resulting BGP configurations are correct-by-construction, faithfully implementing the centralized policy in a distributed fashion, regardless of failures.
+We introduced \sysname, a language and compiler for implementing network-wide policies using a distributed set of devices running BGP.
+Propane allows operators to describe their policy naturally through high-level constraints on the shape and relative preferences of paths for different types of traffic.
+When \sysname compiles a policy, the resulting BGP configurations are correct-by-construction and faithfully implement the policy in a distributed fashion, regardless of the number and combinations of failures.
+Applying \sysname to real-world networks showed that its language is expressive and its compiler is scalable.
 

### 2016-06-17 paper/v2/paper-edited.tex
minor font fix

@@
 
-When computing local preferences and ensuring failure safety, as described in \S\ref{sec:compilation}, the compiler performs memoization of the \textit{Regret-Free} function.
-That is, whenever for two states $N_1$ and $N_2$ we compute $Regret-Free(G, N_1, N_2)$, if the function evaluates to $true$, then each of the intermediate related states $x$ and $y$ must also satisfy $protect(G, x, y)$.
+When computing local preferences and ensuring failure safety, as described in \S\ref{sec:compilation}, the compiler performs memoization of the \textup{Regret-Free} function.
+That is, whenever for two states $N_1$ and $N_2$ we compute $\textup{Regret-Free}(G, N_1, N_2)$, if the function evaluates to $true$, then each of the intermediate related states $x$ and $y$ must also satisfy $\textup{Regret-Free}(G, x, y)$.
 Memoizing these states dramatically reduces the amount of work performed to find preferences in the common case.

### 2016-06-17 paper/v2/paper-edited.tex
minor changes to abstract; cleaner title header

@@
 Ryan Beckett\\
-  \affaddr{Princeton University}
+  \affaddr{Princeton}
   %\\
@@
 Ratul Mahajan\\
-  \affaddr{Microsoft Research}
+  \affaddr{Microsoft}
   %\\
@@
 Todd Millstein\\
-  \affaddr{University of California, Los Angeles}
+  \affaddr{UCLA}
+  %\affaddr{University of California, Los Angeles}
   %\\
@@
 Jitu Padhye\\
-  \affaddr{Microsoft Research}
+  \affaddr{Microsoft}
   %\\
@@
 David Walker\\
-  \affaddr{Princeton University}
+  \affaddr{Princeton}
   %\\
@@
 \textbf{Abstract---}
-We develop \sysname, a language and a compiler to help network operators with a challenging, error-prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex, distributed protocols.
+We develop \sysname, a language and compiler to help network operators with a challenging, error-prone task---bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex, distributed protocols.
 %
@@
 %
-We use \sysname for datacenter and backbone networks of a large cloud provider.
-We find that our language can effectively express their policies and, despite its strong guarantees, our compiler scales to topologies with hundreds or thousands of routers.
+We show that \sysname can effectively express the policies of datacenter and backbone networks of a large cloud provider;  and despite its strong guarantees, our compiler scales to networks with hundreds or thousands of routers.
 

### 2016-06-17 paper/v2/paper-edited.tex
minor changes to 5

@@
 
-  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
+  \caption{Product graph construction for policy $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
   \label{fig:example-compilation}
@@
   \centering
-  \includegraphics[width=.8\columnwidth]{figures/unimplementable}
-  \caption{Example topology for which the \sysname policy: $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
+  \includegraphics[width=.5\columnwidth]{figures/unimplementable}
+  \caption{A network where the policy $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
   \label{fig:unimplementable}

### 2016-06-19 paper/v2/paper-edited.tex

@@
 <concept>
+<concept_id>10003033.10003083.10003095</concept_id>
+<concept_desc>Networks~Network reliability</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10003033.10003099.10003104</concept_id>
+<concept_desc>Networks~Network management</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10010940.10010992.10010998.10011000</concept_id>
+<concept_desc>Software and its engineering~Automated static analysis</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
 <concept_id>10011007.10011006.10011050.10011017</concept_id>
@@
 \ccsdesc[300]{Networks~Network control algorithms}
+\ccsdesc[300]{Networks~Network reliability}
+\ccsdesc[300]{Networks~Network management}
+\ccsdesc[300]{Software and its engineering~Automated static analysis}
 \ccsdesc[300]{Software and its engineering~Domain specific languages}
@@
 
-\keywords{Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault tolerance}
+\keywords{Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems}
 

### 2016-06-19 paper/v2/paper-edited.tex
Copy Edits
Corrections made to maintain grammatical word usage,  sentence
structure and clarity of meaning.

@@
 %
-The language allows operators to specify their objectives naturally, using high-level constraints and ordered preferences on paths that traffic should take.
+The language allows operators to specify their objectives naturally, using high-level constraints on and ordered preferences for paths that traffic should take.
 %through their network or other networks.
@@
 This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter.
-A similar problem will happen if links Y--G and Y--H fail.
+A similar problem will occur if links Y--G and Y--H fail.
 %\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
@@
 
-Since, by default, routing allows transit traffic (\EG, traffic entering from
+Since, routing allows transit traffic by default (\EG, traffic entering from
 \CD{Peer} and leaving through \CD{Prov}), we separately define a
@@
 prefixes only follows paths that are internal to the network at each hop.
-This constraint guarantees that the services remain reachable only to locations
+This constraint guarantees that the services remain accessible only to locations
 inside the datacenter.
@@
 The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR).
-Policies in RIR are checked for well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR).
+Policies in RIR are checked for being well-formed (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR).
 The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions.
@@
 
-Intuitively, PGIR tracks which states of each automaton the policy is in as route announcements move between locations.
+Intuitively, PGIR tracks the policy states of each automaton as route announcements move between locations.
 %
@@
 The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops.
-In particular, BGP's loop prevention mechanism forces an AS to reject any route for which it is already in the AS path.
+In particular, BGP's loop prevention mechanism forces an AS to reject any route that is already in the AS path.
 %
@@
 
-A natural question then is how the compiler should order PGIR contexts for each router in a way that is both \emph{sound} and \emph{complete} under all possible failures?
+A natural question then is, how should the compiler order PGIR contexts for each router in a way that is both \emph{sound} and \emph{complete} under all possible failures?
 To this end, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
@@
 After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
-In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from.
+In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neighbor from which the route is being imported.
 Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
@@
 The backbone network connects to the datacenters and also has many external BGP neighbors.
-The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for datacenter routers or actual configurations for the backbone network (where templates are not used because the network has less regular structure).
+The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for datacenter routers or actual configurations for the backbone network (where templates are not used because the network has a less regular structure).
 
@@
 The datacenter operator said that he found the language intuitive.
-The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We found that the datacenter policies were correctly translated.
+The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We further found that the datacenter policies were correctly translated.
 For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.

### 2016-06-19 paper/v2/paper-edited.tex
edits for sections 1-4

@@
 As a complementary approach, configuration analysis tools can help reduce misconfigurations by checking if low-level configurations match high-level policy~\cite{batfish,feamster+:rcc}.
-However, such tools too cannot help operators with the challenging task of generating configurations in the first place.
+However, such tools cannot help operators with the challenging task of generating configurations in the first place.
 
@@
 \CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links.
-A similar policy must be configured for \CD{R2}.
+A similar policy must be configured for \CD{R2} as well.
 Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based import and export filters at each router.
@@
 %\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
-Link failures in datacenters are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.
+Link failures in datacenters are frequent and it is not uncommon to have many failed links at a given time~\cite{dc-failure-study}.
 
@@
 But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{route-aggregation}.
-If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce \CD{PG} externally.
-This announcement will bring to X traffic for \CD{PG1} as well, but because valleys are disallowed, X does not have a valid route for \CD{PG1} and will drop all traffic to it.
+If links D--A and X--C fail, X will hear an announcement for \CD{PG2} from D and will thus announce \CD{PG} externally.
+This announcement will bring to X traffic for \CD{PG1} as well, but because valleys are disallowed, X does not have a valid route for \CD{PG1} and will drop all traffic for it despite the fact that a valid path exists through $Y$.
 
@@
 network from the previous section, we first express the idea that
-we prefer that traffic leave the network through \CD{R1} over \CD{R2} (to \CD{Cust}) over \CD{Peer} over \CD{Prov} (policy P3 from Figure~\ref{fig:example1}):
+we prefer that traffic leave the network through \CD{R1} over \CD{R2} (to \CD{Cust}) over \CD{Peer} over \CD{Prov} (policy P1 and P3 from Figure~\ref{fig:example1}):
 %\begin{lstlisting}[mathescape=true]
@@
 describe in the next section, the \Exit\ predicate, as well as other
-path predicates used later in this section, is simply a shorthand for
+path predicates used later in this section, are simply a shorthand for
 a particular regular expression over paths that is expressible in our policy
@@
 \noindent
-Here we define transit traffic between groups of neighbors $X$ and $Y$ as traffic that enters the network through some neighbor in $X$ or $Y$ and then leaves the network through some neighbor in either $X$ or $Y$.
+Here we define transit traffic between groups of neighbors $X$ and $Y$ as traffic that enters the network through some neighbor in $X$ or $Y$ and then also leaves the network through some neighbor in either $X$ or $Y$.
 Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network.
@@
 end at router \CD{B}; and so on.
-Any traffic destined for a prefix that not a part of the datacenter should be allowed to leave the datacenter and end at some external location, which is otherwise unconstrained.
+Any traffic destined for a prefix that is not a part of the datacenter should be allowed to leave the datacenter and end at some external location, which is otherwise unconstrained.
 The special keyword \Out{} matches any location outside the datacenter network, while the keyword \In{} will match any location inside the network.
@@
 In addition, $\Sigma$ refers to any symbol.
-We also use the standard regular expressions abbreviation $r^+$ for $r \cdot r^*$, a sequence of one or more occurrences of $r$.
+We also use the standard regular expression abbreviation $r^+$ for $r \cdot r^*$, a sequence of one or more occurrences of $r$.
 Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisments with a particular community value (i.e., an integer value associated with a path).
@@
 %
-For example, in the datacenter configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:
+For example, in the datacenter FE configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:
 
@@
 where $\odot$ stands for an arbitrary regular binary operator, and $x$ is a policy with a single preference.
-The compiler flags as invalid preferences nested under a unary operator (i.e., \textit{star} or \textit{negation}).
+The compiler flags preferences nested under a unary operator (i.e., \textit{star} or \textit{negation}) as invalid.
 
@@
 
-\begin{figure*}
+\begin{figure*}[t!]
   \begin{minipage}[t]{.5\linewidth}
@@
   \end{tikzpicture}
+
+  \vspace*{0.5em}
 
@@
   %
-  \includegraphics[width=.65\columnwidth]{figures/productgraph}
+  \includegraphics[width=.8\columnwidth]{figures/productgraph}
   \end{minipage}
@@
 and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
-For a PGIR vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$, which indicates that the corresponding topology location for $v'$ is $v$.
-Two nodes $x$ and $y$ \emph{shadow} each other in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$.
+For a PGIR vertex $v_1 = (v, \dots) \in V'$, we say $loc(v_1) = v$, which indicates that the corresponding topology location for $v_1$ is $v$.
+
+%
+We say that a PGIR node $x_1$ is a \emph{shadow} of topology location $x$ when $x_1 \in V'$ and $loc(x_1) = x$.
+%
+%Throughout the remainder of the paper, we will use metavariables without subscripts such as $x$ to represent topology locations, and we will use similar metavariables with subscripts such as $x_1$ or $x_2$ to represent shadows of $x$ (i.e., PGIR nodes for location $x$).
 
@@
 Finally, there is an edge from each node in the PGIR such that $P(v) \neq \emptyset$ to the special end node $e$.
-We write $(x \leq_{rank} y)$ if either $P(x) = P(y) = \emptyset$ or $min ~ P(x) \leq min ~ P(y)$, which means that paths ending at PGIR node $x$ are better than (lower rank) than paths that ending at $y$.
+We write $(x \leq_{rank} y)$ if either $P(x) = P(y) = \emptyset$ or $min ~ P(x) \leq min ~ P(y)$, which means that paths ending at PGIR node $x$ are better (lower rank) than paths ending at $y$.
 
@@
 Similarly, a node $x$ post-dominates a node $y$ in the PGIR if $x$ appears on every path from $y$ to the end node.
-We can safely remove nodes and edges in the PGIR when any of the following conditions hold, where $x$, $x'$ and $y$, $y'$ refer to PGIR nodes that shadow each other:
+We can safely remove nodes and edges in the PGIR when any of the following conditions hold, where $x$, $x'$ and $y$, $y'$ refer to PGIR nodes that are shadows of the same topology location.
 \begin{itemize}
@@
 \end{itemize}
-%We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node.
-For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} can be removed since it is never on a simple path to the end node because it must always go through node $(W,-,4)$.
-That is, node $(W,-,4)$ post-dominates node $(W,1,1)$.
-We repeatedly apply the minimizations above to the PGIR until no further minimization is possible.
+For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is removed since it is never on a simple path to the end node because the path must always go through node $(W,-,4)$.
+That is, node $(W,-,4)$ post-dominates node $(W,1,1)$ and both shadow topology location $W$.
+Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$ and shadows the same topology location $C$. 
+We repeatedly apply the minimizations above until no further minimization is possible.
 In the example of Figure~\ref{fig:example-compilation}, colored nodes and dashed edges are removed after minimization.
- %since they are irrelvant to the BGP decision process.
-%
-%Although fully minimizing this graph is an NP-complete problem,  a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.
-
-%A node $x$ dominates $y$ if $x$ appears on every path leading to $y$ from a source node.
-Many efficient algorithms exist for finding graph dominators~\ref{bib:todo}.
-For minimization, we compute the dominator set for each node in both the product graph $G$ with respect to the start node, and in the reversed product graph $G^R$ with respect to the end node.
-The following rules enable efficient minimization of the product graph.
-%
-%\begin{itemize}
-%  \item Remove nodes that never reach the end node
-%  \item Remove nodes not reachable from the $start$ node
-%  \item Remove any node $x$ such that $x$ is dominated by $y$ in $G$ or $G^R$, and $loc(x) = loc(y)$
-%  \item Remove any edge from $x$ to $y$ in $G$ or $G^R$ if there is some node $z$ dominated by $y$ such that $loc(x) = loc(z)$
-%\end{itemize}
-%
-%Repeated application of the above rules leads to removing the colored nodes and dashed lines in Figure~\ref{fig:example-compilation}.
 
@@
 
+\para{Problem Formulation}
+
+The problem of determining local preferences for each router is closely reflected in the structure of the PGIR.
+In particular, whenever a given router appears in multiple different contexts in the PGIR (i.e., as multiple PGIR nodes that shadow each other), then the compiler must decide which context to prefer.
+%
+In our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in context $(C,-,2)$ or it can receive an advertisement from its neighbor $D$ in context $(C,3,2)$.
+%
+The compiler's task is to determine a \emph{total ordering} of contexts for each router in the topology, which reflects the relative preference of advertisements received in each context.
+For example, if the compiler determines that, for router $C$, context $(C,3,2)$ is preferred to context $(C,-,2)$, written as $(C,3,2) <_{pref} (C,-,2)$, then this means that $C$ will prefer advertisements heard from $D$ (with tag $(2,2)$) over $E$ (with tag $(-,2)$).
+Section~\ref{sec:abgp} discusses our encoding of preferences and filters in more detail.
+
+\para{Regret-free Preferences}
+
+A natural question then is, how should the compiler order PGIR contexts for each router in a way that is both \emph{sound} and \emph{complete} under all possible failures?
+To this end, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
+Router $r$ has a \emph{regret-free} preference for a set of advertisements $X$ over $Y$ if, whevever $r$ selects an advertisement from $X$ over another from $Y$, there is always some policy-compliant path to each final (advertisement) destination $d$ that is at least as good $(\leq_{rank})$ as any possible path to $d$ if it had accepted an advertisement from $Y$ instead.
+In other words, the preference of $X$ over $Y$ at $r$ is regret-free if we are never worse off by choosing from $X$.
+%
+In the compilation example from Figure~\ref{fig:example-compilation}, the choice for $C$ to prefer context $(C,3,2)$ to $(C,-,2)$ is regret-free, since there will always be at least as good a path to destination $W$ regardless of any failures that might occur in the network.
+
+%We now explain this property more formally in terms of the structure of the PGIR. We use the notation $path(s,d)$ to say that there exists a path in the PGIR from $s$ to $d$.
+%
+%Preferences (for the PGIR) are \emph{regret-free} if, given (i) any combination of failed topology links\footnote{Note that a single failure in the topology may correspond to zero or more failed nodes/edges in the PGIR}, (ii) a fixed topology (advertisement) destination $d$, and (iii) two contexts $N_1 < N_2$, then whever there exists a $d'$ such that $loc(d') = d$ and $path(N_2,d')$, then there exists a $d''$ such that $loc(d'') = d$ and $path(N_1,d'')$ with $d'' \leq_{rank} d'$.
+%
+%The property simply says that if router $N$ prefers context $N_1$ to $N_2$, then any time there is a path from $N_2$ to some destination $d$, then there exists a better (lower ranked) path from $N_1$ to destination $d$.
+%
+
 \begin{figure}[t!]
@@
 \end{figure}
-
-\para{Problem Formulation}
-
-The problem of determining local preferences for each router is closely reflected in the structure of the PGIR.
-In particular, whenever a given router appears in multiple different contexts in the PGIR (i.e., as multiple PGIR nodes that shadow each other), then the compiler must decide which context to prefer.
-%
-In our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in context $(C,-,2)$ or it can receive an advertisement from its neighbor $D$ in context $(C,3,2)$.
-%
-The compiler's task is to determine a \emph{total ordering} of contexts for each router in the topology, which reflects the relative preference of advertisements received in each context.
-For example, if the compiler determines that, for router $C$, context $(C,3,2)$ is preferred to context $(C,-,2)$, written as $(C,3,2) <_{pref} (C,-,2)$, then this means that $C$ will prefer advertisements heard from $D$ (with tag $(2,2)$) over $E$ (with tag $(-,2)$).
-Section~\ref{sec:abgp} discusses our encoding of preferences and filters in more detail.
-
-\para{Regret-free Preferences}
-
-A natural question then is, how should the compiler order PGIR contexts for each router in a way that is both \emph{sound} and \emph{complete} under all possible failures?
-To this end, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
-Router $r$ has a \emph{regret-free} preference for a set of advertisements $X$ over $Y$ if, whevever $r$ selects an advertisement from $X$ over another from $Y$, there is always some policy-compliant path to each final (advertisement) destination $d$ that is at least as good $(\leq_{rank})$ as any possible path to $d$ if it had accepted an advertisement from $Y$ instead.
-In other words, the preference of $X$ over $Y$ at $r$ is regret-free if we are never worse off by choosing from $X$.
-%
-In the compilation example from Figure~\ref{fig:example-compilation}, the choice for $C$ to prefer context $(C,3,2)$ to $(C,-,2)$ is regret-free, since there will always be at least as good a path to destination $W$ regardless of any failures that might occur in the network.
-
-%We now explain this property more formally in terms of the structure of the PGIR. We use the notation $path(s,d)$ to say that there exists a path in the PGIR from $s$ to $d$.
-%
-%Preferences (for the PGIR) are \emph{regret-free} if, given (i) any combination of failed topology links\footnote{Note that a single failure in the topology may correspond to zero or more failed nodes/edges in the PGIR}, (ii) a fixed topology (advertisement) destination $d$, and (iii) two contexts $N_1 < N_2$, then whever there exists a $d'$ such that $loc(d') = d$ and $path(N_2,d')$, then there exists a $d''$ such that $loc(d'') = d$ and $path(N_1,d'')$ with $d'' \leq_{rank} d'$.
-%
-%The property simply says that if router $N$ prefers context $N_1$ to $N_2$, then any time there is a path from $N_2$ to some destination $d$, then there exists a better (lower ranked) path from $N_1$ to destination $d$.
-%
 
@@
 
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=\columnwidth]{figures/aggregation}
-  \caption{Aggregation safety for a datacenter.}
-  \label{fig:aggregation-safety}
-  \vspace{-1em}
-\end{figure}
-
 As shown in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur.
@@
 This process is repeated for other aggregation locations (e.g., $Y$).
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=\columnwidth]{figures/aggregation}
+  \caption{Aggregation safety for a datacenter.}
+  \label{fig:aggregation-safety}
+  \vspace{-1em}
+\end{figure}
 
@@
 % and then from ABGP to actual device configurations.
+
+\para{From PGIR to ABGP}
+
+Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
+The idea is to encode the state of the automata using BGP community values.
+Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR.
+For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else).
+If it sees such an announcement, it will remove the old community value, and add a new one for state $(4,2)$ before exporting it to $W$.
+
+To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR.
+For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
+
+Since the compiler can control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
+Instead, it translates matches from external ASes into a BGP regular expression filter.
+For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$.
+In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
+The unknown AS topology is modelled as a special node in the PGIR that generates a filter to match any sequence of ASes.
+
+Finally, the external AS $W$ should prefer our internal router $A$ over $B$.
+In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
+In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$.
+Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
+The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
+%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
+Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
+Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.
+
+After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
+In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from.
+Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
 
@@
 
-\para{From PGIR to ABGP}
-
-Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
-The idea is to encode the state of the automata using BGP community values.
-Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR.
-For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else).
-If it sees such an announcement, it will remove the old community value, and add a new one for state $(4,2)$ before exporting it to $W$.
-
-To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR.
-For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
-
-Since the compiler can control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
-Instead, it translates matches from external ASes into a BGP regular expression filter.
-For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$.
-In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
-The unknown AS topology is modelled as a special node in the PGIR that generates a filter to match any sequence of ASes.
-
-Finally, the external AS $W$ should prefer our internal router $A$ over $B$.
-In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
-In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$.
-Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
-The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
-%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
-Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
-Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.
-
-After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
-In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neighbor from which the route is being imported.
-Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
-
 %=====================================================
@@
 
-Constructing automata for extended regular expressions (i.e., those that include negation and intersection) are known to have high complexity~\cite{regex-complexity}.
+Constructing automata for extended regular expressions (i.e., regular expressions with negation and intersection operations) is known to have high complexity~\cite{regex-complexity}.
 The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently.
@@
 Our implementation performs partial minimization during generation by recognizing common cases such as when there is no restriction on exporting to or importing from neighbors.
-
-\para{Checking policy correctness}
-
-Even when programming the network centrally, it is possible for operators to make mistakes and write incorrect policies.
-\sysname includes many analyses to flag common mistakes at compile time.
-A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if topology locations that should be reachable according to the operator policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator accidentally anycasts a prefix (i.e., originates it from multiple locations), (iv) an aggregate analysis to find when aggregates do not summarize any specific prefix.
-
-%=====================================================
-%
-%
-%  **Evaluation**
-%
-%
-%=====================================================
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-We apply \sysname on real policies for backbone and datacenter networks.
-Our main goals are to evaluate if its language is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
-
-\subsection{Networks studied}
-
-We obtained routing policy for the backbone network and for the datacenters of a large cloud provider.
-Multiple datacenters share this policy.
-The backbone network connects to the datacenters and also has many external BGP neighbors.
-The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for datacenter routers or actual configurations for the backbone network (where templates are not used because the network has a less regular structure).
-
-The networks have the types of policies that we outlined earlier (\S\ref{sec:motivation}).
-The backbone network classifies external neighbors into several different categories and prefers paths through them in order.
-It does not want to provide transit among certain types of neighbors.
-For some neighbors, it prefers some links over the others.
-It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA).
-Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, etc.
-
-Routers in the datacenter network run BGP using private AS numbers and peer with each other and with the backbone network over eBGP.
-The routers aggregate some prefix blocks when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region.
-The datacenter networks also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
 
@@
 \end{figure}
+
+\para{Checking policy correctness}
+
+Even when programming the network centrally, it is possible for operators to make mistakes and write incorrect policies.
+\sysname includes many analyses to flag common mistakes at compile time.
+A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if topology locations that should be reachable according to the operator policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator accidentally anycasts a prefix (i.e., originates it from multiple locations), (iv) an aggregate analysis to find when aggregates do not summarize any specific prefix.
+
+%=====================================================
+%
+%
+%  **Evaluation**
+%
+%
+%=====================================================
+
+\begin{figure}[t!]
+  \subcaptionbox{Datacenter}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
+  \subcaptionbox{Backbone}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
+  \caption{Configuration minimization. \label{fig:config-min}}
+  \vspace{-1em}
+\end{figure}
+
+\section{Evaluation}
+\label{sec:evaluation}
+
+We apply \sysname on real policies for backbone and datacenter networks.
+Our main goals are to evaluate if its language is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
+
+\subsection{Networks studied}
+
+We obtained routing policy for the backbone network and for the datacenters of a large cloud provider.
+Multiple datacenters share this policy.
+The backbone network connects to the datacenters and also has many external BGP neighbors.
+The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for datacenter routers or actual configurations for the backbone network (where templates are not used because the network has a less regular structure).
+
+The networks have the types of policies that we outlined earlier (\S\ref{sec:motivation}).
+The backbone network classifies external neighbors into several different categories and prefers paths through them in order.
+It does not want to provide transit among certain types of neighbors.
+For some neighbors, it prefers some links over the others.
+It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA).
+Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, etc.
+
+Routers in the datacenter network run BGP using private AS numbers and peer with each other and with the backbone network over eBGP.
+The routers aggregate some prefix blocks when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region.
+The datacenter networks also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
 
@@
 %
-
-\begin{figure}[t!]
-  \subcaptionbox{Datacenter}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
-  \subcaptionbox{Backbone}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
-  \caption{Configuration minimization. \label{fig:config-min}}
-  \vspace{-1em}
-\end{figure}
 

### 2016-06-19 paper/v2/paper-edited.tex
edit section 5

@@
 and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
-For a PGIR vertex $v_1 = (v, \dots) \in V'$, we say $loc(v_1) = v$, which indicates that the corresponding topology location for $v_1$ is $v$.
+For a PGIR vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$ to indicate that the topology location for $v'$ is $v$.
 
@@
 We say that a PGIR node $x_1$ is a \emph{shadow} of topology location $x$ when $x_1 \in V'$ and $loc(x_1) = x$.
+As a shorthand, we write $x_1 \approx x_2$ when $x_1$ and $x_2$ are both shadows for the same topology location.
 %
@@
 For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is removed since it is never on a simple path to the end node because the path must always go through node $(W,-,4)$.
-That is, node $(W,-,4)$ post-dominates node $(W,1,1)$ and both shadow topology location $W$.
-Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$ and shadows the same topology location $C$. 
+That is, node $(W,-,4)$ post-dominates node $(W,1,1)$ and both are shadows of topology location $W$.
+Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$ and is a shadow of the same topology location $C$. 
 We repeatedly apply the minimizations above until no further minimization is possible.
-In the example of Figure~\ref{fig:example-compilation}, colored nodes and dashed edges are removed after minimization.
+In the example from Figure~\ref{fig:example-compilation}, colored nodes and dashed edges show edges and nodes removed after minimization.
 
@@
 The problem of determining local preferences for each router is closely reflected in the structure of the PGIR.
-In particular, whenever a given router appears in multiple different contexts in the PGIR (i.e., as multiple PGIR nodes that shadow each other), then the compiler must decide which context to prefer.
-%
-In our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in context $(C,-,2)$ or it can receive an advertisement from its neighbor $D$ in context $(C,3,2)$.
-%
-The compiler's task is to determine a \emph{total ordering} of contexts for each router in the topology, which reflects the relative preference of advertisements received in each context.
-For example, if the compiler determines that, for router $C$, context $(C,3,2)$ is preferred to context $(C,-,2)$, written as $(C,3,2) <_{pref} (C,-,2)$, then this means that $C$ will prefer advertisements heard from $D$ (with tag $(2,2)$) over $E$ (with tag $(-,2)$).
+In particular, whenever a given router appears in multiple different contexts in the PGIR (i.e., as multiple PGIR nodes that are shadows of the router), then the compiler must decide which shadow to prefer.
+%
+In our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in shadow $(C,-,2)$ or it can receive an advertisement from its neighbor $D$ in shadow $(C,3,2)$.
+%
+The compiler's task is to determine a \emph{total ordering} of shadow nodes for each router in the topology, which reflects the relative preference of advertisements received in each shadow.
+For example, if the compiler determines that, for router $C$, shadow $(C,3,2)$ can be locally preferred to shadow $(C,-,2)$, written as $(C,3,2) \leq_{lp} (C,-,2)$, then this means that $C$ will prefer advertisements heard from $D$ (with tag $(2,2)$) over $E$ (with tag $(-,2)$).
 Section~\ref{sec:abgp} discusses our encoding of preferences and filters in more detail.
@@
 
-A natural question then is, how should the compiler order PGIR contexts for each router in a way that is both \emph{sound} and \emph{complete} under all possible failures?
+A natural question then is, how should the compiler order PGIR shadows ($\leq_{lp}$) for each router in a way that is both \emph{sound} and \emph{complete} under all possible failures?
 To this end, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
-Router $r$ has a \emph{regret-free} preference for a set of advertisements $X$ over $Y$ if, whevever $r$ selects an advertisement from $X$ over another from $Y$, there is always some policy-compliant path to each final (advertisement) destination $d$ that is at least as good $(\leq_{rank})$ as any possible path to $d$ if it had accepted an advertisement from $Y$ instead.
-In other words, the preference of $X$ over $Y$ at $r$ is regret-free if we are never worse off by choosing from $X$.
-%
-In the compilation example from Figure~\ref{fig:example-compilation}, the choice for $C$ to prefer context $(C,3,2)$ to $(C,-,2)$ is regret-free, since there will always be at least as good a path to destination $W$ regardless of any failures that might occur in the network.
+We say a router $r$ has a \emph{regret-free} preference for a set of advertisements $X$ over $Y$ if, whevever $r$ selects an advertisement from $X$ over another from $Y$, there is always some policy-compliant path to each final (advertisement) destination $d$ that is at least as good $(\leq_{rank})$ as any possible path to $d$ if it had accepted an advertisement from $Y$ instead.
+In other words, the preference of $X$ over $Y$ at $r$ is regret-free if we are never worse off by choosing an advertisement from $X$ when available.
+The notion of regret-free preferences can be lifted to nodes in the PGIR by considering the set of advertisments available to each node.
+
+In the compilation example from Figure~\ref{fig:example-compilation}, the choice for $C$ to prefer shadow $(C,3,2)$ to $(C,-,2)$ is regret-free, since there will always be at least as good a path to destination $W$ regardless of any failures that might occur in the network.
+For example, if the $C$--$A$ link fails, then there is still a backup path from $(C,3,2)$ to $(W,-,4)$ that is just as good as any path from $(C,-,2)$.
+Likewise, any combination of failures to disconnect $(C,3,2)$ from $(W,-,4)$ would also disconnect $(C,-,2)$ from $(W,-,4)$.
 
@@
   \centering
-  \includegraphics[width=.5\columnwidth]{figures/unimplementable}
+  \includegraphics[width=.8\columnwidth]{figures/unimplementable}
   \caption{A network where the policy $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
@@
 
-Searching for \emph{regret-free} preferences in general is hard, and enumerating all possible combinations of failures and preference orderings is intractable.
+Searching precisely for \emph{regret-free} preferences in general is hard, and clearly enumerating all possible combinations of failures and preference orderings is intractable.
 We thus adopt a conservative analysis that we found to be both effective and efficient in practice.
-The idea is to $i)$ search for regret-free preferences by comparing the set of paths available after accepting advertisments in two different PGIR contexts $N_1$ and $N_2$, and $ii)$ refine the comparison when necessary by considering where the announcements must have traversed before arriving at $N_1$ or $N_2$.
+The idea is to $i)$ search for regret-free preferences by comparing the set of paths available after accepting advertisments in two different PGIR shadows $N_1$ and $N_2$ of topology location $N$, and $ii)$ refine the comparison when necessary by considering where the announcements must have traversed before arriving at $N_1$ or $N_2$.
 
@@
     \EndIf
-    \For {$x$ in adj($G$, $n_2$)}
-      \If {\big($\exists y \in$ adj($G$,$n_1$), shadows $x$\big) \textbf{or} \\
-            \hspace{5.2em} \big($\exists y \in$ $G$, dominates $n_1$, shadows $x$\big)}
+    \For {$n_2'$ in adj($G$, $n_2$)}
+      \If {\big($\exists n_1' \in \textup{adj}(G,n_1), n_1' \approx n_2'$\big) \textbf{or} \\
+            \hspace{5.2em} 
+            \big($\exists n_1' \in$ $G$, dominates $n_1$, $n_1' \approx n_1'$\big)}
         \If {$(x,y)$ not marked}
@@
 
-Algorithm~\ref{alg:failures} checks whether one context can be preferred to another ($N_1 <_{pref} N_2$).
-The algorithm walks from nodes $N_1$ and $N_2$ and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, also take a step to an equivalent topology location.
+Algorithm~\ref{alg:failures} checks whether one shadow can be preferred to another ($N_1 \leq_{lp} N_2$).
+The algorithm walks from nodes $N_1$ and $N_2$ and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, also take a step to an equivalent topology location $(\approx)$.
 When there is no such equivalent step, the algorithm attempts to take into account where the advertisement must have already traversed.
@@
 At each step, it requires that current node reachable from $N_1$ has a path rank that is at least as good as that of the current node reachable from $N_2$ ($n_1 \leq_{rank} n_2$).
-The intuition here is that if $n_1 \nleq_{rank} n_2$, then we can likely fail every edge in the topology except for the path that leads to the current $n_1$ and $n_2$, thereby generating in a counter example.
-Algorithm~\ref{alg:failures} terminates since the number of related states $(x,y)$ that can be explored is finite.
-
-For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR contexts according to the $(<_{pref})$ relation.
+The intuition here is that if $n_1 \nleq_{rank} n_2$, then we can very likely fail every edge in the topology except for the path that leads to the current $n_1$ and $n_2$, thereby generating in a counter example.
+Algorithm~\ref{alg:failures} terminates since the number of related states $(n_1,n_2)$ that can be explored is finite.
+
+For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR contexts according to the $(\leq_{lp})$ relation determined by the \textup{Regret-Free}.
 If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
@@
 The checks for failure safety described above overlooked one critical point: A better (lower rank) path might not be available due to loops that are rejected by BGP. 
-To avoid this situation, the compiler checks that, any time some context $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$.
+%
+For example, in Figure~\ref{fig:example-compilation}, suppose we did not remove node $(D,-,2)$ during minimization.
+In this case, $(C,3,2)$ might think that $(D,-,2)$ is available for use along a path to $W$ even though the advertisement might have already gone through $(D,2,2)$ prior to reaching $(C,3,2)$.
+Since BGP would reject any path using $D$ twice, the PGIR node $(D,-,2)$ may be unusable for $(C,3,2)$ despite the analysis not taking this information into account.
+
+To avoid this situation, the compiler checks that, any time we have two shadows $N_1$ and $N_2$ for some topology location $N$, where $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (that is, $N_1 <_{lp} N_2$).
 The idea is that anytime $N_2$ is not usable because the advertisement already went through $N_1$, it ultimately does not matter since $N$ has a regret-free preference for $N_1$ anyway.
+%
+For example, $(D,2,2)$ appears ``above'' $(D,-,2)$, so we require that $(D,2,2) <_{lp} (D,-,2)$.
+In this case, the compiler determines that this is safe according to Algorithm~\ref{alg:failures}, so router $D$ can simply prefer advertisements from $Y$ and $X$ over advertisements from $C$.
 
@@
 It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=\columnwidth]{figures/aggregation}
+  \caption{Aggregation safety for a datacenter.}
+  \label{fig:aggregation-safety}
+  \vspace{-1em}
+\end{figure}
 
@@
 
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=\columnwidth]{figures/aggregation}
-  \caption{Aggregation safety for a datacenter.}
-  \label{fig:aggregation-safety}
-  \vspace{-1em}
-\end{figure}
-
 \subsection{Abstract BGP}
@@
 \newcommand{\Arrow}{\ensuremath{\leftarrow}}
-
-%\begin{figure}[t!]
-%\begin{lstlisting}[frame=single, mathescape=true]
-%$\Router{A}$
-%  Match $\PEER=C$
-%    Export $\MED \leftarrow 80, \PEER \leftarrow W$
-%$\Router{B}$
-%  Match $\PEER = C$
-%    Export $\COMM \leftarrow \text{noexport}, \MED \leftarrow 81, \PEER \leftarrow W$
-%$\Router{C}$
-%  Match$[LP=99]$ $\PEER = E $
-%    Export $\PEER \leftarrow B$
-%  Match $\PEER = D$
-%    Export $\PEER \leftarrow A,B$
-%$\Router{D}$
-%  Match $\REGEX{X + Y}$
-%    Export $\PEER \leftarrow C$
-%$\Router{E}$
-%  Match $\REGEX{Z}$
-%    Export $\PEER \leftarrow C$
-%\end{lstlisting}
-%\label{fig:config-min}
-%\caption{Abstract BGP minimized configurations}
-%\end{figure}
-
-The final stage of our compiler translates policies from PGIR to a vendor-neutral abstraction of BGP (ABGP).
-% and then from ABGP to actual device configurations.
-
-\para{From PGIR to ABGP}
-
-Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
-The idea is to encode the state of the automata using BGP community values.
-Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR.
-For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else).
-If it sees such an announcement, it will remove the old community value, and add a new one for state $(4,2)$ before exporting it to $W$.
-
-To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR.
-For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
-
-Since the compiler can control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
-Instead, it translates matches from external ASes into a BGP regular expression filter.
-For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$.
-In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
-The unknown AS topology is modelled as a special node in the PGIR that generates a filter to match any sequence of ASes.
-
-Finally, the external AS $W$ should prefer our internal router $A$ over $B$.
-In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
-In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$.
-Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
-The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
-%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
-Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
-Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.
-
-After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
-In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from.
-Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
 
@@
 
+The final stage of our compiler translates policies from PGIR to a vendor-neutral abstraction of BGP (ABGP).
+% and then from ABGP to actual device configurations.
+
+\para{From PGIR to ABGP}
+
+Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
+The idea is to encode the state of the automata using BGP community values.
+Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR.
+For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else).
+If it sees such an announcement, it will remove the old community value, and add a new one for state $(4,2)$ before exporting it to $W$.
+
+To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR.
+For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
+
+Since the compiler can control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
+Instead, it translates matches from external ASes into a BGP regular expression filter.
+For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$.
+In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
+The unknown AS topology is modelled as a special node in the PGIR that generates a filter to match any sequence of ASes.
+
+Finally, the external AS $W$ should prefer our internal router $A$ over $B$.
+In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
+In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$.
+Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
+The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
+%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
+Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
+Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.
+
+After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
+In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from.
+Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
+
 %=====================================================
@@
 Our implementation performs partial minimization during generation by recognizing common cases such as when there is no restriction on exporting to or importing from neighbors.
+
+\para{Checking policy correctness}
+
+Even when programming the network centrally, it is possible for operators to make mistakes and write incorrect policies.
+\sysname includes many analyses to flag common mistakes at compile time.
+A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if topology locations that should be reachable according to the operator policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator accidentally anycasts a prefix (i.e., originates it from multiple locations), (iv) an aggregate analysis to find when aggregates do not summarize any specific prefix.
+
+%=====================================================
+%
+%
+%  **Evaluation**
+%
+%
+%=====================================================
+
+\section{Evaluation}
+\label{sec:evaluation}
+
+We apply \sysname on real policies for backbone and datacenter networks.
+Our main goals are to evaluate if its language is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
+
+\subsection{Networks studied}
+
+We obtained routing policy for the backbone network and for the datacenters of a large cloud provider.
+Multiple datacenters share this policy.
+The backbone network connects to the datacenters and also has many external BGP neighbors.
+The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for datacenter routers or actual configurations for the backbone network (where templates are not used because the network has a less regular structure).
+
+The networks have the types of policies that we outlined earlier (\S\ref{sec:motivation}).
+The backbone network classifies external neighbors into several different categories and prefers paths through them in order.
+It does not want to provide transit among certain types of neighbors.
+For some neighbors, it prefers some links over the others.
+It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA).
+Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, etc.
+
+Routers in the datacenter network run BGP using private AS numbers and peer with each other and with the backbone network over eBGP.
+The routers aggregate some prefix blocks when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region.
+The datacenter networks also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
+
+\subsection{Expressiveness}
+
+We found that we could translate all network policies to \sysname.
+We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname.
+The datacenter operator said that he found the language intuitive.
+The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We further found that the datacenter policies were correctly translated.
+For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.
+
+Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the routing policies for \sysname were 43 lines for the backbone network and 31 lines for the datacenter networks.
 
@@
 \end{figure}
-
-\para{Checking policy correctness}
-
-Even when programming the network centrally, it is possible for operators to make mistakes and write incorrect policies.
-\sysname includes many analyses to flag common mistakes at compile time.
-A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if topology locations that should be reachable according to the operator policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator accidentally anycasts a prefix (i.e., originates it from multiple locations), (iv) an aggregate analysis to find when aggregates do not summarize any specific prefix.
-
-%=====================================================
-%
-%
-%  **Evaluation**
-%
-%
-%=====================================================
-
-\begin{figure}[t!]
-  \subcaptionbox{Datacenter}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
-  \subcaptionbox{Backbone}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
-  \caption{Configuration minimization. \label{fig:config-min}}
-  \vspace{-1em}
-\end{figure}
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-We apply \sysname on real policies for backbone and datacenter networks.
-Our main goals are to evaluate if its language is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
-
-\subsection{Networks studied}
-
-We obtained routing policy for the backbone network and for the datacenters of a large cloud provider.
-Multiple datacenters share this policy.
-The backbone network connects to the datacenters and also has many external BGP neighbors.
-The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for datacenter routers or actual configurations for the backbone network (where templates are not used because the network has a less regular structure).
-
-The networks have the types of policies that we outlined earlier (\S\ref{sec:motivation}).
-The backbone network classifies external neighbors into several different categories and prefers paths through them in order.
-It does not want to provide transit among certain types of neighbors.
-For some neighbors, it prefers some links over the others.
-It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA).
-Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, etc.
-
-Routers in the datacenter network run BGP using private AS numbers and peer with each other and with the backbone network over eBGP.
-The routers aggregate some prefix blocks when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region.
-The datacenter networks also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
-
-\subsection{Expressiveness}
-
-We found that we could translate all network policies to \sysname.
-We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname.
-The datacenter operator said that he found the language intuitive.
-The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We further found that the datacenter policies were correctly translated.
-For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.
-
-Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the routing policies for \sysname were 43 lines for the backbone network and 31 lines for the datacenter networks.
 
@@
 %
+
+\begin{figure}[t!]
+  \subcaptionbox{Datacenter}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
+  \subcaptionbox{Backbone}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
+  \caption{Configuration minimization. \label{fig:config-min}}
+  \vspace{-1em}
+\end{figure}
 

### 2016-06-19 paper/v2/paper-edited.tex
balance last page
minor edit in section 6

@@
 Constructing automata for extended regular expressions (i.e., regular expressions with negation and intersection operations) is known to have high complexity~\cite{regex-complexity}.
-The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently.
+The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions efficiently.
 Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy.
-Similarly, to model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.
-%
-Rather than construct the product graph in full, our implementation prevents exploring parts of the graph when no accepting state is reachable in any of the corresponding regular automata during construction.
+To model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.
+%
+Rather than construct the product graph in full, our implementation prevents exploring parts of the graph during construction when no automata has a reachable accepting state.
 
@@
 
+\section*{Acknowledgement}
+
+\ryan{TODO: add acknowledgements}
+
 %=====================================================
@@
 
+\balance
+
 \bibliographystyle{abbrv}

### 2016-06-20 paper/v2/paper-edited.tex
small typo/wording fixes

@@
 describe in the next section, the \Exit\ predicate, as well as other
-path predicates used later in this section, are simply a shorthand for
+path predicates used later in this section, is simply a shorthand for
 a particular regular expression over paths that is expressible in our policy
@@
 Figure~\ref{fig:rir-syntax} shows the RIR syntax.
-A policy has one or more constraints, each of which has a test on the type of route, and a corresponding set of preferred regular paths.
+A policy has one or more constraints, each of which has a test on the type of route and a corresponding set of preferred regular paths.
 Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS.
@@
 The semantics of RIR is in terms of ranked paths.
-Each preference-based regular path constraint of the form $r_1 \Prefer \dots \Prefer r_j$ maps to a set of concrete paths in the network that match one of $r_i$.
+Each preference-based regular path constraint of the form $r_1 \Prefer \dots \Prefer r_j$ maps to a set of concrete paths in the network that match one of the $r_i$.
 A network path is a string of abstract locations of the form $n_1 n_2 \dots n_k$.
@@
 %The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$.
-While paths in RIR policy describe the direction traffic flow through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated, i.e., route announcements flowing in the opposite direction.
+While paths in an RIR policy describe the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated, i.e., route announcements flowing in the opposite direction.
 To capture this idea, for each regular expression $r_i$ in RIR policy, we construct a deterministic finite state machine on the reversed regular expression.
 Each automaton for the reversed regular expression of $r_i$ is a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ consists of all abstraction locations (i.e., routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+The alphabet $\Sigma$ consists of all abstract locations (i.e., routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
 %
 % Formally define topology
-The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon V \times V$.
+The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$.
 %
@@
 
-Intuitively, PGIR tracks the policy states of each automaton as route announcements move between locations.
+Intuitively, a PGIR tracks the policy states of each automaton as route announcements move between locations.
 %
 Consider the topology in Figure~\ref{fig:example-compilation}.
-Suppose we want a primary route from neighbor W that allows traffic to enter the network at $A$, and utilize the C--D link before leaving the network (through $X$ or $Y$).
+Suppose we want a primary route from neighbor W that allows traffic to enter the network at $A$ and utilize the C--D link before leaving the network (through $X$ or $Y$).
 As a backup, we also want to allow traffic to enter the network from $B$, in which case the traffic can also utilize the C--E link before leaving the network.
@@
 %
-The ``--" state indicates the corresponding automaton can not accept the current path or any extension of it.
-Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates that this path has preference 1.
+The ``--" state indicates the corresponding automaton cannot accept the current path or any extension of it. Since 
+node $(W,5,-)$ is in an accepting state for the first automaton, it indicates that this path has preference 1.
 
@@
 \end{itemize}
-For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is removed since it is never on a simple path to the end node because the path must always go through node $(W,-,4)$.
+For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is removed since it is never on a simple path to the end node, because the path must always go through node $(W,-,4)$.
 That is, node $(W,-,4)$ post-dominates node $(W,1,1)$ and both are shadows of topology location $W$.
@@
 %
-The soundness violation could be fixed by tagging and filtering route advertisements appropriately so that $C$ rejects routes that go through $E$, however the completeness violation can not be fixed.
-In fact, this policy can not be implemented in BGP in a way that is policy compliant under all failures.
+The soundness violation could be fixed by tagging and filtering route advertisements appropriately so that $C$ rejects routes that go through $E$, however the completeness violation cannot be fixed.
+In fact, this policy cannot be implemented in BGP in a way that is policy compliant under all failures.
 
@@
 In particular, it checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) and walks from this new node instead.
-At each step, it requires that current node reachable from $N_1$ has a path rank that is at least as good as that of the current node reachable from $N_2$ ($n_1 \leq_{rank} n_2$).
-The intuition here is that if $n_1 \nleq_{rank} n_2$, then we can very likely fail every edge in the topology except for the path that leads to the current $n_1$ and $n_2$, thereby generating in a counter example.
+At each step, it requires that the current node reachable from $N_1$ has a path rank that is at least as good as that of the current node reachable from $N_2$ ($n_1 \leq_{rank} n_2$).
+The intuition here is that if $n_1 \nleq_{rank} n_2$, then we can very likely fail every edge in the topology except for the path that leads to the current $n_1$ and $n_2$, thereby generating a counterexample.
 Algorithm~\ref{alg:failures} terminates since the number of related states $(n_1,n_2)$ that can be explored is finite.
 
-For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR contexts according to the $(\leq_{lp})$ relation determined by the \textup{Regret-Free}.
+For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR contexts according to the $(\leq_{lp})$ relation determined by the \textup{Regret-Free} algorithm.
 If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
@@
 To avoid this situation, the compiler checks that, any time we have two shadows $N_1$ and $N_2$ for some topology location $N$, where $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (that is, $N_1 <_{lp} N_2$).
-The idea is that anytime $N_2$ is not usable because the advertisement already went through $N_1$, it ultimately does not matter since $N$ has a regret-free preference for $N_1$ anyway.
+The idea is that any time $N_2$ is not usable because the advertisement already went through $N_1$, it ultimately does not matter since $N$ has a regret-free preference for $N_1$ anyway.
 %
@@
 For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else).
-If it sees such an announcement, it will remove the old community value, and add a new one for state $(4,2)$ before exporting it to $W$.
+If it sees such an announcement, it will remove the old community value and add a new one for state $(4,2)$ before exporting it to $W$.
 
@@
 After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
-In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from.
+In the compilation example all community tags can be removed, since there is never any ambiguity based on the router importing the route and the neigbor the route is being imported from.
 Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
@@
 
-The naive code generation algorithm described in \S\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair for every node in the product graph before minimization.
+The naive code generation algorithm described in \S\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in-edge/out-edge pair for every node in the product graph before minimization.
 Our implementation performs partial minimization during generation by recognizing common cases such as when there is no restriction on exporting to or importing from neighbors.
@@
 We study the compilation of time for both policies as a function of network size.
-Even though the networks we study have a fixed topology and size, we can explore the impact of size because the policies are network-wide and the compiler takes topology itself as an input.
+Even though the networks we study have a fixed topology and size, we can explore the impact of size because the policies are network-wide and the compiler takes the topology itself as an input.
 For the datacenter network, we build and provide as input fat tree~\cite{fattree} topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy.
@@
 languages and a ``correct-by-construction''
-methodology.  By proposing network administrators write configurations
+methodology.  By proposing that network administrators write configurations
 at a high-level of abstraction, a whole host of low-level errors can be avoided and policy implementation can be simplified.
@@
 \ryan{TODO: add acknowledgements}
+This work is supported in part by
+the National Science Foundation award CNS-1161595.
 

### 2016-06-21 paper/v2/paper-edited.tex
adding changes for Todd's comments

@@
 A policy has one or more constraints, each of which has a test on the type of route and a corresponding set of preferred regular paths.
-Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS.
+Regular paths are regular expressions where the base characters are AS numbers representing either a router or an external AS.
 Special \In{} and \Out{} symbols refer to any internal or external location respectively.
@@
 We say that a PGIR node $x_1$ is a \emph{shadow} of topology location $x$ when $x_1 \in V'$ and $loc(x_1) = x$.
-As a shorthand, we write $x_1 \approx x_2$ when $x_1$ and $x_2$ are both shadows for the same topology location.
+As a shorthand, we write $x_1 \approx x_2$ when $x_1$ and $x_2$ are both shadows of the same topology location (i.e., $loc(x_1) = loc(x_2)$).
 %
@@
 Suppose we set the local preferences to have $D$ prefer $E$ over $F$, and have $A$ prefer $B$ over $C$.
-This works as expected under normal conditions, however, if the B--D link fails, then suddenly $D$ has made the wrong decision by preferring $E$.
+This works as expected under normal conditions, however, if the A--B link fails, then suddenly $D$ has made the wrong decision by preferring $E$.
 Traffic will now follow the
@@
 The soundness violation could be fixed by tagging and filtering route advertisements appropriately so that $C$ rejects routes that go through $E$, however the completeness violation cannot be fixed.
-In fact, this policy cannot be implemented in BGP in a way that is policy compliant under all failures.
+In fact, this policy cannot be implemented in BGP in a way that is policy compliant under all failures since $D$ cannot safely choose between $E$ and $F$ without knowing whether the A--B link is available.
 
@@
 The problem of determining local preferences for each router is closely reflected in the structure of the PGIR.
-In particular, whenever a given router appears in multiple different contexts in the PGIR (i.e., as multiple PGIR nodes that are shadows of the router), then the compiler must decide which shadow to prefer.
+In particular, whenever a given router appears in multiple shadow nodes in the PGIR, then the compiler must decide which shadow to prefer.
 %
@@
 As shown in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur.
-Deciding when this can happen requires knowledge of the routing policy and not just the topology.
-For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated, even if there are several available in the toplogy.
-If that link fails, a black hole might be introduced.
+Determining when this can happen requires knowledge, not only of the topology, but also of the routing policy.
+For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated, even when there are several available in the toplogy.
+If that one link fails, a black hole might be introduced.
 %
@@
 
-We frame the aggregation problem as a problem of connectivity in the PGIR.
-Specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures required to disconnect the prefix origin from its aggregation point.
-The difficulty is that the same links in the topology can appear in multiple places in the PGIR.
-%
-
-We adopt the following simple strategy to find a lower bound on
-the number of failures: $i)$ pick a random start-to-end path in the PGIR, $ii)$ remove all edges in the PGIR for the set of topological edges chosen, and $iii)$ repeat until no such path exists.
-The number of PGIR paths that we are able to remove is a lower bound on the number of failures required to disconnect the prefix from its aggregate.
+We frame the aggregation problem as a variant of the min-cut problem in the PGIR.
+Specifically, for each prefix that falls under an aggregate, we are interested in finding a lower bound on the number of failures required to disconnect the prefix's origin from its aggregation point.
+The difficulty, however, is that links in the topology can appear in multiple places in the PGIR, thus preventing the direct application of a standard min-cut algorithm.
+%
+
+Instead, we adopt the following simple strategy: $i)$ pick a random origin-to-aggregation path in the PGIR, $ii)$ remove all similar edges in the PGIR for the topological edges chosen, and $iii)$ repeat until no such path exists.
+Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.
 
@@
 Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
-Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}.
+Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures required to potentially introduce an aggreagation black hole for prefix \CD{PG1}.
 This process is repeated for other aggregation locations (e.g., $Y$).
@@
 
-\section*{Acknowledgement}
+\section*{Acknowledgements}
 

### 2016-06-21 paper/v2/paper-edited.tex
more edits

@@
 
-As shown in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur.
-Determining when this can happen requires knowledge, not only of the topology, but also of the routing policy.
-For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated, even when there are several available in the toplogy.
+As shown in \S\ref{sec:motivation}, aggregation can lead to subtle black-holing of traffic when failures occur.
+Determining when this can happen requires knowledge, not only of the topology, but also of the policy.
+For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated.
 If that one link fails, a black hole might be introduced.
@@
 
-We frame the aggregation problem as a variant of the min-cut problem in the PGIR.
+We view the aggregation problem as a variant of the min-cut problem in the PGIR.
 Specifically, for each prefix that falls under an aggregate, we are interested in finding a lower bound on the number of failures required to disconnect the prefix's origin from its aggregation point.
-The difficulty, however, is that links in the topology can appear in multiple places in the PGIR, thus preventing the direct application of a standard min-cut algorithm.
+The difficulty, however, is that each link in the topology might appear as multiple links in the PGIR, thus preventing the direct application of standard min-cut algorithms.
 %
@@
 
-Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
+Once we have the total ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
 The idea is to encode the state of the automata using BGP community values.
@@
 \sysname includes many analyses to flag common mistakes at compile time.
-A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if topology locations that should be reachable according to the operator policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator accidentally anycasts a prefix (i.e., originates it from multiple locations), (iv) an aggregate analysis to find when aggregates do not summarize any specific prefix.
+A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if topology locations that should be reachable according to the operator policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator might accidentally anycast a prefix (i.e., originates the prefix from multiple locations), (iv) an aggregate analysis to find when aggregates do not summarize any specific prefix.
 
@@
 The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We further found that the datacenter policies were correctly translated.
-For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.
+For the backbone network, the operator mentioned an additional policy not present in the English document, which we added later.
 
@@
 
-In both examples, we observe that our failure-safety analysis algorithm for finding preferences is highly efficient, taking only a small fraction of the total running time.
+In both examples, we observe that Algorithm~\ref{alg:failures} for inferring \textup{Regret-Free} preferences is efficient, taking only a small fraction of the total running time.
 PGIR minimization is the most expensive compilation phase.
-If needed, minimization can be capped after a certain number of iterations for large networks.
-Both the backbone and datacenter  policies we considered can be successfully compiled without minimization.
+If needed, minimization can be limited to a fixed number of iterations for large networks.
+Both the backbone and datacenter policies could be successfully compiled without performing minimization.
 

### 2016-06-21 paper/v2/paper-edited.tex
more edits
another minor change

@@
 \Procedure{Regret-free($G$, $N_1$, $N_2$)}{}
-  \If {$loc(N_1) \neq loc(N_2)$} \Return false
+  \If {$N_1 \not\approx N_2$} \Return false
   \EndIf
@@
             \hspace{5.2em} 
-            \big($\exists n_1' \in$ $G$, dominates $n_1$, $n_1' \approx n_1'$\big)}
+            \big($\exists n_1' \in$ $G$, dominates $n_1$, $n_1' \approx n_1$\big)}
         \If {$(x,y)$ not marked}
@@
 
-To avoid this situation, the compiler checks that, any time we have two shadows $N_1$ and $N_2$ for some topology location $N$, where $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (that is, $N_1 <_{lp} N_2$).
-The idea is that any time $N_2$ is not usable because the advertisement already went through $N_1$, it ultimately does not matter since $N$ has a regret-free preference for $N_1$ anyway.
+To avoid this situation, the compiler checks that, any time there are two shadows $N_1$ and $N_2$ for topology location $N$, where $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (i.e., $N_1 <_{lp} N_2$).
+The idea is that any time shadow $N_2$ is not usable because the advertisement already went through $N_1$, it ultimately does not matter since $N$ has a regret-free preference for $N_1$ anyway and will only be better off.
 %

### 2016-06-21 paper/v2/paper-edited.tex
fix in algorithm
fix algorithm numbering bug. Edit conclusion

@@
             \big($\exists n_1' \in$ $G$, dominates $n_1$, $n_1' \approx n_1$\big)}
-        \If {$(x,y)$ not marked}
-          \State {mark $(x,y)$ as seen}
-          \State $q.Enqueue(x,y)$
+        \If {$(n_1',n_2')$ not marked}
+          \State {mark $(n_1',n_2')$ as seen}
+          \State $q.Enqueue(n_1',n_2')$
         \EndIf
@@
     \EndFor
-  \EndWhile
-  \Return true
+  \EndWhile \\
+  \hspace{\algorithmicindent} \Return true
 \EndProcedure
@@
 We introduced \sysname, a language and compiler for implementing network-wide policies using a distributed set of devices running BGP.
-Propane allows operators to describe their policy naturally through high-level constraints on the shape and relative preferences of paths for different types of traffic.
-When \sysname compiles a policy, the resulting BGP configurations are correct-by-construction and faithfully implement the policy in a distributed fashion, regardless of the number and combinations of failures.
+Propane allows operators to describe their policy through high-level constraints on the shape and relative preferences of paths for different types of traffic.
+When \sysname compiles a policy, the resulting BGP configurations are guaranteed to faithfully implement the policy in a distributed fashion, regardless of any number of network failures.
 Applying \sysname to real-world networks showed that its language is expressive and its compiler is scalable.

### 2016-06-21 paper/v2/paper-edited.tex
pass

@@
 
-The problem of determining local preferences for each router is closely reflected in the structure of the PGIR.
-In particular, whenever a given router appears in multiple shadow nodes in the PGIR, then the compiler must decide which shadow to prefer.
-%
-In our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in shadow $(C,-,2)$ or it can receive an advertisement from its neighbor $D$ in shadow $(C,3,2)$.
-%
-The compiler's task is to determine a \emph{total ordering} of shadow nodes for each router in the topology, which reflects the relative preference of advertisements received in each shadow.
-For example, if the compiler determines that, for router $C$, shadow $(C,3,2)$ can be locally preferred to shadow $(C,-,2)$, written as $(C,3,2) \leq_{lp} (C,-,2)$, then this means that $C$ will prefer advertisements heard from $D$ (with tag $(2,2)$) over $E$ (with tag $(-,2)$).
-Section~\ref{sec:abgp} discusses our encoding of preferences and filters in more detail.
+The problem of determining local preferences for each router is reflected in the structure of the PGIR.
+Whenever a given router appears as multiple shadow nodes in the PGIR, the compiler must decide which shadow to prefer.
+%
+In the example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in shadow $(C,-,2)$ or from $D$ in shadow $(C,3,2)$.
+%
+%
+The compiler must determine a \emph{total ordering} of shadow nodes for each router, which reflects the relative preference of advertisements received in each shadow and should be consistent with path ranks in routing policy.
+%
+For example, if $C$'s shadow $(C,3,2)$ is preferred to $(C,-,2)$, written as $(C,3,2) \leq_{lp} (C,-,2)$,  $C$ will prefer advertisements from $(D,2,2)$ over $(E,-,2)$.
+$D$ and $E$ tag their advertisements to let $C$ know which shadow sent the advertisement.
+\$\ref{sec:abgp} discusses tagging in detail.
 
 \para{Regret-free Preferences}
-
-A natural question then is, how should the compiler order PGIR shadows ($\leq_{lp}$) for each router in a way that is both \emph{sound} and \emph{complete} under all possible failures?
-To this end, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
-We say a router $r$ has a \emph{regret-free} preference for a set of advertisements $X$ over $Y$ if, whevever $r$ selects an advertisement from $X$ over another from $Y$, there is always some policy-compliant path to each final (advertisement) destination $d$ that is at least as good $(\leq_{rank})$ as any possible path to $d$ if it had accepted an advertisement from $Y$ instead.
-In other words, the preference of $X$ over $Y$ at $r$ is regret-free if we are never worse off by choosing an advertisement from $X$ when available.
-The notion of regret-free preferences can be lifted to nodes in the PGIR by considering the set of advertisments available to each node.
-
-In the compilation example from Figure~\ref{fig:example-compilation}, the choice for $C$ to prefer shadow $(C,3,2)$ to $(C,-,2)$ is regret-free, since there will always be at least as good a path to destination $W$ regardless of any failures that might occur in the network.
+To order PGIR shadows ($\leq_{lp}$) for each router in a way that is both sound and complete under all failures, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
+A router $r$ has a regret-free preference for a set of advertisements $X$ over $Y$ if, whenever $r$ selects an advertisement to destination $d$ from $X$ over another from $Y$, there is always some policy-compliant path to $d$ that is at least as good $(\leq_{rank})$ as any possible path to $d$ if $r$ had selected an advertisement from $Y$ instead.
+In other words, the preference of $X$ over $Y$ at $r$ is regret-free if $r$ is never (under any failure) worse-off by choosing an advertisement from $X$ when available.
+The notion of regret-free preferences can be lifted to PGIR nodes by considering the set of advertisements available to each node.
+
+In the example of Figure~\ref{fig:example-compilation}, the choice for $C$ to prefer shadow $(C,3,2)$ to $(C,-,2)$ is regret-free, since there will always be at least as good a path to destination $W$ regardless of any failures that might occur in the network.
 For example, if the $C$--$A$ link fails, then there is still a backup path from $(C,3,2)$ to $(W,-,4)$ that is just as good as any path from $(C,-,2)$.
@@
 
-Searching precisely for \emph{regret-free} preferences in general is hard, and clearly enumerating all possible combinations of failures and preference orderings is intractable.
-We thus adopt a conservative analysis that we found to be both effective and efficient in practice.
-The idea is to $i)$ search for regret-free preferences by comparing the set of paths available after accepting advertisments in two different PGIR shadows $N_1$ and $N_2$ of topology location $N$, and $ii)$ refine the comparison when necessary by considering where the announcements must have traversed before arriving at $N_1$ or $N_2$.
+Searching for precise regret-free preferences in general is hard, and clearly enumerating all possible combinations of failures and preference orderings is intractable.
+We thus adopt a conservative analysis that we found to be effective and efficient in practice.
+The idea is to $i)$ search for regret-free preferences by comparing the set of paths available after accepting advertisments in two different PGIR shadows $N_1$ and $N_2$ of topology node $N$, and $ii)$ refine the comparison when necessary by considering where the announcements must have traversed before arriving at $N_1$ or $N_2$.
 
@@
 Algorithm~\ref{alg:failures} checks whether one shadow can be preferred to another ($N_1 \leq_{lp} N_2$).
-The algorithm walks from nodes $N_1$ and $N_2$ and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, also take a step to an equivalent topology location $(\approx)$.
+It walks from nodes $N_1$ and $N_2$ and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, also take a step to an equivalent topology location $(\approx)$.
 When there is no such equivalent step, the algorithm attempts to take into account where the advertisement must have already traversed.
-In particular, it checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) and walks from this new node instead.
+In particular, it checks if there is an equivalent dominator (i.e., a topology location the advertisement must have passed through earlier) and walks from this new node instead.
 At each step, it requires that the current node reachable from $N_1$ has a path rank that is at least as good as that of the current node reachable from $N_2$ ($n_1 \leq_{rank} n_2$).
@@
 
-For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR contexts according to the $(\leq_{lp})$ relation determined by the \textup{Regret-Free} algorithm.
+For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR contexts according to the $(\leq_{lp})$ relation determined by Algorithm~\ref{alg:failures}.
 If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
@@
 \ryan{TODO: add acknowledgements}
+We thank R. Aditya, George Chen, and Lihua Yuan for feedback on this work and the SIGCOMM reviewers for comments on the paper.
 This work is supported in part by
-the National Science Foundation award CNS-1161595.
+the NSF award CNS-1161595.
 

### 2016-06-21 paper/v2/paper-edited.tex
correcting spelling mistakes

@@
 This guard can be implemented by $X$ and $Y$ rejecting paths through the other.
-But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{route-aggregation}.
+But that creates a different problem in the face of failures---an aggregation-induced black hole~\cite{route-aggregation}.
 If links D--A and X--C fail, X will hear an announcement for \CD{PG2} from D and will thus announce \CD{PG} externally.
@@
 \sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures if possible---otherwise, it generates a compile-time error.
-For aggregation, it also provides a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
+For aggregation, it also provides a lower bound to operators on the number of failures under which aggregation will not result in black holes.
 
@@
 We also use the standard regular expression abbreviation $r^+$ for $r \cdot r^*$, a sequence of one or more occurrences of $r$.
-Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisments with a particular community value (i.e., an integer value associated with a path).
+Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisements with a particular community value (i.e., an integer value associated with a path).
 %% For example, the constraint
@@
 For example, the regular expression $a \cdot (b \Prefer c) \cdot d$ is lifted to $(a \cdot b \cdot d) \Prefer (a \cdot c \cdot d)$ by distributing the preference over the sequence operator.
-In general, we employ the follwing distributivity equivalences:
+In general, we employ the following distributivity equivalences:
 %
@@
 BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
-This possiblity is reflected in the product graph by the node with state $(X,1,1)$.
+This possibility is reflected in the product graph by the node with state $(X,1,1)$.
 From here, if X were to advertise this route to D, it would result in the path $D \cdot X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
@@
 \para{Minimization}
-After building the PGIR as desribed above,
-we minimize it in order to improve the subsequent analysis that checks if the policies captured by it are safe under failures.
+After building the PGIR as described above,
+we minimize it in order to improve the precision of the subsequent analysis that checks if the policies captured by it are safe under failures.
 The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops.
@@
 %
-The precision of the failure-safety analysis often increases when nodes and edges that are not possible due to loops are eliminated.
+%The precision of the failure-safety analysis often increases when nodes and edges that are not possible due to loops are eliminated.
 %For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
@@
 Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$ and is a shadow of the same topology location $C$.
+
 We repeatedly apply the minimizations above until no further minimization is possible.
@@
 Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
-Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures required to potentially introduce an aggreagation black hole for prefix \CD{PG1}.
+Because $A$ is then disconnected from $X$, the compiler knows that 2 is a lower bound on the number of failures required to potentially introduce an aggregation black hole for prefix \CD{PG1}.
 This process is repeated for other aggregation locations (e.g., $Y$).
@@
 In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
-The unknown AS topology is modelled as a special node in the PGIR that generates a filter to match any sequence of ASes.
+The unknown AS topology is modeled as a special node in the PGIR that generates a filter to match any sequence of ASes.
 
@@
 After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
-In the compilation example all community tags can be removed, since there is never any ambiguity based on the router importing the route and the neigbor the route is being imported from.
+In the compilation example all community tags can be removed, since there is never any ambiguity based on the router importing the route and the neighbor the route is being imported from.
 Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
@@
 Currently, \sysname supports generating Quagga router configurations out of the box.
-Users can add new vendor-specific adaptors to translate from ABGP to other router configuration languages, or incorporate the compiler into an existing template-based system, e.g., by mixing the \sysname-generated BGP configuration with other, non-BGP configuration elements.
+Users can add new vendor-specific adapters to translate from ABGP to other router configuration languages, or incorporate the compiler into an existing template-based system, e.g., by mixing the \sysname-generated BGP configuration with other, non-BGP configuration elements.
 
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 
@@
 We thank R. Aditya, George Chen, and Lihua Yuan for feedback on this work and the SIGCOMM reviewers for comments on the paper.
-This work is supported in part by
-the NSF award CNS-1161595.
 

### 2016-06-21 paper/v2/paper-edited.tex
more spelling corrections + acknowledgment fix

@@
 \end{itemize}
-For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is removed since it is never on a simple path to the end node, because the path must always go through node $(W,-,4)$.
+For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is removed because every path to the end node must always go through node $(W,-,4)$.
 That is, node $(W,-,4)$ post-dominates node $(W,1,1)$ and both are shadows of topology location $W$.
-Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$ and is a shadow of the same topology location $C$.
+Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$ and is a shadow of $C$.
 
@@
 We thus adopt a conservative analysis that we found to be effective and efficient in practice.
-The idea is to $i)$ search for regret-free preferences by comparing the set of paths available after accepting advertisments in two different PGIR shadows $N_1$ and $N_2$ of topology node $N$, and $ii)$ refine the comparison when necessary by considering where the announcements must have traversed before arriving at $N_1$ or $N_2$.
+The idea is to $i)$ search for regret-free preferences by comparing the set of paths available after accepting advertisements in two different PGIR shadows $N_1$ and $N_2$ of topology node $N$, and $ii)$ refine the comparison when necessary by considering where the announcements must have traversed before arriving at $N_1$ or $N_2$.
 
@@
 
-Instead, we adopt the following simple strategy: $i)$ pick a random origin-to-aggregation path in the PGIR, $ii)$ remove all similar edges in the PGIR for the topological edges chosen, and $iii)$ repeat until no such path exists.
+Instead, we adopt the following simple strategy: $i)$ pick a random path in the PGIR between the prefix origin and aggregation point, $ii)$ remove all similar edges in the PGIR for each topological edges along the chosen path, and $iii)$ repeat until no such path exists.
 Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.
@@
 
-\ryan{TODO: add acknowledgements}
-We thank R. Aditya, George Chen, and Lihua Yuan for feedback on this work and the SIGCOMM reviewers for comments on the paper.
+We thank R.
+Aditya, George Chen, and Lihua Yuan for feedback on this work and the SIGCOMM reviewers for comments on the paper.
+This work is supported in part by the National Science Foundation award CNS-1161595.
 

### 2016-06-21 paper/v2/paper-edited.tex
edits

@@
          &\BNFALT& \textit{comm} = d & \textit{community test} \\
-     r       &::=& n & \textit{AS number} \\
+     r       &::=& l & \textit{location} \\
          &\BNFALT& \emptyset & \textit{empty set} \\
@@
 A policy has one or more constraints, each of which has a test on the type of route and a corresponding set of preferred regular paths.
-Regular paths are regular expressions where the base characters are AS numbers representing either a router or an external AS.
+Regular paths are regular expressions where the base characters are abstract locations representing either a router or an external AS.
 Special \In{} and \Out{} symbols refer to any internal or external location respectively.
@@
 
-For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR contexts according to the $(\leq_{lp})$ relation determined by Algorithm~\ref{alg:failures}.
+For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR shadows according to the $(\leq_{lp})$ relation determined by Algorithm~\ref{alg:failures}.
 If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
@@
 We introduced \sysname, a language and compiler for implementing network-wide policies using a distributed set of devices running BGP.
-Propane allows operators to describe their policy through high-level constraints on the shape and relative preferences of paths for different types of traffic.
-When \sysname compiles a policy, the resulting BGP configurations are guaranteed to faithfully implement the policy in a distributed fashion, regardless of any number of network failures.
+Propane allows operators to describe their policy naturally through high-level constraints on both the shape and relative preferences of paths for different types of traffic.
+When \sysname compiles a policy, the resulting BGP configurations are guaranteed to faithfully implement the centralized policy in a purely distributed fashion, regardless of any number of network failures.
 Applying \sysname to real-world networks showed that its language is expressive and its compiler is scalable.

### 2016-06-21 paper/v2/paper-edited.tex
simplify loop avoidance section

@@
          &\BNFALT& r^* & \textit{iteration} \\
-     l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
-     cc     &::=& agg(x, l) \BNFALT tag(c, t, l) & \textit{control constraints} \\
+     lp       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
+     cc     &::=& agg(x, lp) \BNFALT tag(c, t, lp) & \textit{control constraints} \\
   \end{array} \]
@@
 Each preference-based regular path constraint of the form $r_1 \Prefer \dots \Prefer r_j$ maps to a set of concrete paths in the network that match one of the $r_i$.
-A network path is a string of abstract locations of the form $n_1 n_2 \dots n_k$.
+A network path is a string of abstract locations of the form $l_1 l_2 \dots l_k$.
 A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$, that is, the path is in the language of the regular expression and is topologically valid.
@@
 The first step merges separate constraints.
-It takes the cross product of per-prefix constraints, where logical conjunction ($a \AND b$) is replaced by intersection on regular constraints ($a \Intersect b$), logical disjunction is replaced by union, and logical negation ($\NOT a$) is replaced by path negation ($\Any \cap \NOT(a)$).
+It takes the cross product of per-prefix constraints, where logical conjunction ($r_1 ~\AND~ r_2$) is replaced by intersection on regular constraints ($r_1 \Intersect r_2$), logical disjunction is replaced by union, and logical negation ($\NOT r$) is replaced by path negation ($\Any \cap \NOT(r)$).
 The additional constraint $\Any$ ensures the routes are well-formed by restricting the paths to only those that go through the user's network.
@@
 Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression.
-For example, the regular expression $a \cdot (b \Prefer c) \cdot d$ is lifted to $(a \cdot b \cdot d) \Prefer (a \cdot c \cdot d)$ by distributing the preference over the sequence operator.
+For example, the regular expression $r \cdot (s \Prefer t) \cdot u$ is lifted to $(r \cdot s \cdot u) \Prefer (r \cdot t \cdot u)$ by distributing the preference over the sequence operator.
 In general, we employ the following distributivity equivalences:
@@
 \begin{array}{c}
-  x \odot (y_1 \Prefer \dots \Prefer y_n) = (x \odot y_1) \Prefer \dots \Prefer (x \odot y_n) \\
-  (y_1 \Prefer \dots \Prefer y_n) \odot x = (y_1 \odot x) \Prefer \dots \Prefer (y_n \odot x)
+  r \odot (s_1 \Prefer \dots \Prefer s_n) = (r \odot s_1) \Prefer \dots \Prefer (r \odot s_n) \\
+  (s_1 \Prefer \dots \Prefer s_n) \odot r = (s_1 \odot r) \Prefer \dots \Prefer (s_n \odot r)
 \end{array}
@@
 %
-where $\odot$ stands for an arbitrary regular binary operator, and $x$ is a policy with a single preference.
+where $\odot$ stands for an arbitrary regular binary operator, and $r$ is a policy with a single preference.
 The compiler flags preferences nested under a unary operator (i.e., \textit{star} or \textit{negation}) as invalid.
@@
 and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
-For a PGIR vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$ to indicate that the topology location for $v'$ is $v$.
-
-%
-We say that a PGIR node $x_1$ is a \emph{shadow} of topology location $x$ when $x_1 \in V'$ and $loc(x_1) = x$.
-As a shorthand, we write $x_1 \approx x_2$ when $x_1$ and $x_2$ are both shadows of the same topology location (i.e., $loc(x_1) = loc(x_2)$).
-%
-%Throughout the remainder of the paper, we will use metavariables without subscripts such as $x$ to represent topology locations, and we will use similar metavariables with subscripts such as $x_1$ or $x_2$ to represent shadows of $x$ (i.e., PGIR nodes for location $x$).
+
+For a PGIR vertex $n = (l, \dots) \in V'$, we say that $n$ is a \emph{shadow} of topology location $l$, written as $\tilde{n} = l$, to indicate that the topology location for node $n$ is $l$.
+When two PGIR nodes $m$ and $n$ shadow the same topology location (i.e., $\tilde{m} = \tilde{n}$), we write $m \approx n$.
+
+Throughout the remainder of the paper, we will the convention that metavariables $m$ and $n$ stand for PGIR nodes and $l$ stands for a topology location.
+Captial letters like $X$, $Y$ refer to concrete topology locations, while capital letters with subscripts such as $X_1$ and $X_2$ refer to concrete PGIR nodes that share a topology location (i.e., $\tilde{X_1}$ = $\tilde{X_2} = X$).
 
@@
 Let $a_i$ and $b_i$ denote states in the regular policy automata.
-The PGIR is constructed by adding an edge from $v_1 = (x, a_1, \dots, a_m)$ to $v_2 = (y, b_1, \dots, b_m)$ whenever $\sigma_i(a_i, y) = b_i$ for each $i$ and $(x,y) \in E$ is a valid topology link.
-%
-Additionally, we add edges from the start node $s$ to any $v = (x, a_1, \dots, a_m)$ when $\sigma_i(q_{0_i}, x) = a_i$ for each $i$.
-%
-The preference function $P$ for node $v = (x, a_1, \dots, a_m)$ is defined as $P(v) = \set{i~\vert~a_i \in F_i} $.
+The PGIR is constructed by adding an edge from $m = (l_m, a_1, \dots, a_k)$ to $n = (l_n, b_1, \dots, b_k)$ whenever $\sigma_i(a_i, l_n) = b_i$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
+%
+Additionally, we add edges from the start node $s$ to any $n = (l, a_1, \dots, a_k)$ when $\sigma_i(q_{0_i}, l) = a_i$ for each $i$.
+%
+The preference function $P$ for node $n = (l, a_1, \dots, a_k)$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $.
 That is, it records which preferences are achieved from each policy automaton for every node in the product construction.
 %
-Finally, there is an edge from each node in the PGIR such that $P(v) \neq \emptyset$ to the special end node $e$.
-We write $(x \leq_{rank} y)$ if either $P(x) = P(y) = \emptyset$ or $min ~ P(x) \leq min ~ P(y)$, which means that paths ending at PGIR node $x$ are better (lower rank) than paths ending at $y$.
+Finally, there is an edge from each node in the PGIR such that $P(n) \neq \emptyset$ to the special end node $e$.
+We write $(m \leq_{rank} n)$ if either $P(m) = P(n) = \emptyset$ or $min ~ P(m) \leq min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.
 
@@
 Every path in the PGIR corresponds to a concrete path in the topology.
-In particular, every path through the PGIR that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
+In particular, every path through the PGIR that ends at a node $n$ such that the preference function $P(n) = \set{i_1, \dots, i_k}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_k$.
 %
@@
 We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
-In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading from the start node to $y$.
-Similarly, a node $x$ post-dominates a node $y$ in the PGIR if $x$ appears on every path from $y$ to the end node.
-We can safely remove nodes and edges in the PGIR when any of the following conditions hold, where $x$, $x'$ and $y$, $y'$ refer to PGIR nodes that are shadows of the same topology location.
+In the PGIR, a node $m$ dominates a node $n$ if $m$ appears on every path leading from the start node to $n$.
+Similarly, a node $m$ post-dominates a node $n$ in the PGIR if $m$ appears on every path from $n$ to the end node.
+We can safely remove nodes and edges in the PGIR when any of the following conditions hold, where we have $m$, $m'$ and $n$, $n'$ such that $\tilde{m} = \tilde{m}'$ and $\tilde{n} = \tilde{n}'$.
 \begin{itemize}
@@
 \setlength{\parsep}{0pt}
-\item Remove $x$ if it is not reachable from the start node
-\item Remove $x$ if it can not reach the end node
-\item Remove $x$ if it is (post-)dominated by some $x'$
-\item Remove edge ($x$, $y$) if $y$ is post-dominated by some $x'$
-\item Remove edge ($x$, $y$) if $x$ is dominated by some $y'$
+\item Remove $m$ if it is not reachable from the start node
+\item Remove $m$ if it can not reach the end node
+\item Remove $m$ if it is (post-)dominated by some $m'$
+\item Remove edge ($m$, $n$) if some $m'$ post-dominates $n$
+\item Remove edge ($m$, $n$) if some $n'$ dominates $m$
 \end{itemize}
 For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is removed because every path to the end node must always go through node $(W,-,4)$.
-That is, node $(W,-,4)$ post-dominates node $(W,1,1)$ and both are shadows of topology location $W$.
-Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$ and is a shadow of $C$.
+That is, node $(W,1,1$ is post-dominated by node $(W,-,4)$ and both are shadows of topology location $W$.
+Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$.
 
@@
 $A \cdot C \cdot D \cdot E \cdot G$ path, even though this path was not allowed by the policy.
-This is a violation of \emph{soundness}: The distributed implementation has used a route not specified by the policy.
-To make matters worse, the second preference $A \cdot C \cdot D \cdot F \cdot G$ is available in the network but not being used.
-This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
-%
-The soundness violation could be fixed by tagging and filtering route advertisements appropriately so that $C$ rejects routes that go through $E$, however the completeness violation cannot be fixed.
+Thus, the distributed implementation has used a route that is not allowed by the policy.
+To make matters worse, the second preference for the path $A \cdot C \cdot D \cdot F \cdot G$ is available in the network but not being used.
+Thus, a path for the best possible route available exists in the network but is not being used by the distributed implementation.
+%
+The first problem could be fixed by tagging and filtering route advertisements appropriately so that $C$ rejects routes that go through $E$, however the second problem cannot be fixed.
 In fact, this policy cannot be implemented in BGP in a way that is policy compliant under all failures since $D$ cannot safely choose between $E$ and $F$ without knowing whether the A--B link is available.
@@
 \$\ref{sec:abgp} discusses tagging in detail.
-
-\para{Regret-free Preferences}
-To order PGIR shadows ($\leq_{lp}$) for each router in a way that is both sound and complete under all failures, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
-A router $r$ has a regret-free preference for a set of advertisements $X$ over $Y$ if, whenever $r$ selects an advertisement to destination $d$ from $X$ over another from $Y$, there is always some policy-compliant path to $d$ that is at least as good $(\leq_{rank})$ as any possible path to $d$ if $r$ had selected an advertisement from $Y$ instead.
-In other words, the preference of $X$ over $Y$ at $r$ is regret-free if $r$ is never (under any failure) worse-off by choosing an advertisement from $X$ when available.
-The notion of regret-free preferences can be lifted to PGIR nodes by considering the set of advertisements available to each node.
-
-In the example of Figure~\ref{fig:example-compilation}, the choice for $C$ to prefer shadow $(C,3,2)$ to $(C,-,2)$ is regret-free, since there will always be at least as good a path to destination $W$ regardless of any failures that might occur in the network.
-For example, if the $C$--$A$ link fails, then there is still a backup path from $(C,3,2)$ to $(W,-,4)$ that is just as good as any path from $(C,-,2)$.
-Likewise, any combination of failures to disconnect $(C,3,2)$ from $(W,-,4)$ would also disconnect $(C,-,2)$ from $(W,-,4)$.
-
-%We now explain this property more formally in terms of the structure of the PGIR. We use the notation $path(s,d)$ to say that there exists a path in the PGIR from $s$ to $d$.
-%
-%Preferences (for the PGIR) are \emph{regret-free} if, given (i) any combination of failed topology links\footnote{Note that a single failure in the topology may correspond to zero or more failed nodes/edges in the PGIR}, (ii) a fixed topology (advertisement) destination $d$, and (iii) two contexts $N_1 < N_2$, then whever there exists a $d'$ such that $loc(d') = d$ and $path(N_2,d')$, then there exists a $d''$ such that $loc(d'') = d$ and $path(N_1,d'')$ with $d'' \leq_{rank} d'$.
-%
-%The property simply says that if router $N$ prefers context $N_1$ to $N_2$, then any time there is a path from $N_2$ to some destination $d$, then there exists a better (lower ranked) path from $N_1$ to destination $d$.
-%
 
@@
 \end{figure}
+
+\para{Regret-free Preferences}
+To order PGIR shadows ($\leq_{lp}$) for each router in a way that is both sound and complete under all failures, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
+A router (location) $l$ has a regret-free preference for a set of advertisements $A$ over $B$ if, whenever $l$ selects an advertisement to destination $d$ from $A$ over another from $B$, there is always some policy-compliant path to $d$ that is at least as good ($\leq_{rank}$ for the final node along the path) as any possible path (not necessily from $l$) to $d$ if $l$ had selected an advertisement from $B$ instead.
+In other words, the preference of $A$ over $B$ at $l$ is regret-free if $l$ is never (under any failure) worse-off by choosing an advertisement from $A$ when available.
+The notion of regret-free preferences can be lifted to PGIR nodes by considering the set of advertisements available to each node.
+
+In the example of Figure~\ref{fig:example-compilation}, the choice for $C$ to prefer shadow $(C,3,2)$ to $(C,-,2)$ is regret-free, since there will always be at least as good a path to destination $W$ regardless of any failures that might occur in the network.
+For example, if the $C$--$A$ link fails, then there is still a backup path from $(C,3,2)$ to $(W,-,4)$ that is just as good as any path from $(C,-,2)$.
+Likewise, any combination of failures to disconnect $(C,3,2)$ from $(W,-,4)$ would also disconnect $(C,-,2)$ from $(W,-,4)$.
+
+%We now explain this property more formally in terms of the structure of the PGIR. We use the notation $path(s,d)$ to say that there exists a path in the PGIR from $s$ to $d$.
+%
+%Preferences (for the PGIR) are \emph{regret-free} if, given (i) any combination of failed topology links\footnote{Note that a single failure in the topology may correspond to zero or more failed nodes/edges in the PGIR}, (ii) a fixed topology (advertisement) destination $d$, and (iii) two contexts $N_1 < N_2$, then whever there exists a $d'$ such that $loc(d') = d$ and $path(N_2,d')$, then there exists a $d''$ such that $loc(d'') = d$ and $path(N_1,d'')$ with $d'' \leq_{rank} d'$.
+%
+%The property simply says that if router $N$ prefers context $N_1$ to $N_2$, then any time there is a path from $N_2$ to some destination $d$, then there exists a better (lower ranked) path from $N_1$ to destination $d$.
+%
 
@@
   \While {$!q.Empty()$}
-    \State $(n_1,n_2) \gets q.Dequeue()$
-    \If {$n_1 \nleq_{rank} n_2$}
+    \State $(m,n) \gets q.Dequeue()$
+    \If {$m \nleq_{rank} n$}
       \Return false
     \EndIf
-    \For {$n_2'$ in adj($G$, $n_2$)}
-      \If {\big($\exists n_1' \in \textup{adj}(G,n_1), n_1' \approx n_2'$\big) \textbf{or} \\
+    \For {$n'$ in adj($G$, $n$)}
+      \If {\big($\exists m' \in \textup{adj}(G,m), m' \approx n'$\big) \textbf{or} \\
             \hspace{5.2em}
-            \big($\exists n_1' \in$ $G$, dominates $n_1$, $n_1' \approx n_1$\big)}
-        \If {$(n_1',n_2')$ not marked}
-          \State {mark $(n_1',n_2')$ as seen}
-          \State $q.Enqueue(n_1',n_2')$
+            \big($\exists m' \in$ $G$, dominates $m$, $m' \approx n'$\big)}
+        \If {$(m',n')$ not marked}
+          \State {mark $(m',n')$ as seen}
+          \State $q.Enqueue(m',n')$
         \EndIf
@@
 In particular, it checks if there is an equivalent dominator (i.e., a topology location the advertisement must have passed through earlier) and walks from this new node instead.
-At each step, it requires that the current node reachable from $N_1$ has a path rank that is at least as good as that of the current node reachable from $N_2$ ($n_1 \leq_{rank} n_2$).
-The intuition here is that if $n_1 \nleq_{rank} n_2$, then we can very likely fail every edge in the topology except for the path that leads to the current $n_1$ and $n_2$, thereby generating a counterexample.
-Algorithm~\ref{alg:failures} terminates since the number of related states $(n_1,n_2)$ that can be explored is finite.
+At each step, it requires that the current node reachable from $N_1$ has a path rank that is at least as good as that of the current node reachable from $N_2$ ($m \leq_{rank} n$).
+The intuition here is that if $m \nleq_{rank} n$, then we can very likely fail every edge in the topology except for the path that leads to the current $m$ and $n$, thereby generating a counterexample.
+Algorithm~\ref{alg:failures} terminates since the number of related states $(m,n)$ that can be explored is finite.
 
@@
 
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=.7\columnwidth]{figures/loops}
+  \caption{A Product Graph where preference inference is unsound before considering loops.}
+  \label{fig:avoiding-loops}
+  %\vspace{-1em}
+\end{figure}
+
 \para{Avoiding Loops}
 
-The checks for failure safety described above overlooked one critical point: A better (lower rank) path might not be available due to loops that are rejected by BGP.
-%
-For example, in Figure~\ref{fig:example-compilation}, suppose we did not remove node $(D,-,2)$ during minimization.
-In this case, $(C,3,2)$ might think that $(D,-,2)$ is available for use along a path to $W$ even though the advertisement might have already gone through $(D,2,2)$ prior to reaching $(C,3,2)$.
-Since BGP would reject any path using $D$ twice, the PGIR node $(D,-,2)$ may be unusable for $(C,3,2)$ despite the analysis not taking this information into account.
-
-To avoid this situation, the compiler checks that, any time there are two shadows $N_1$ and $N_2$ for topology location $N$, where $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (i.e., $N_1 <_{lp} N_2$).
-The idea is that any time shadow $N_2$ is not usable because the advertisement already went through $N_1$, it ultimately does not matter since $N$ has a regret-free preference for $N_1$ anyway and will only be better off.
-%
-For example, $(D,2,2)$ appears ``above'' $(D,-,2)$, so we require that $(D,2,2) <_{lp} (D,-,2)$.
-In this case, the compiler determines that this is safe according to Algorithm~\ref{alg:failures}, so router $D$ can simply prefer advertisements from $Y$ and $X$ over advertisements from $C$.
+The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available due to loops.
+BGP automatically rejects advertisements to a location where the locations is already contained in the AS path attribute.
+
+Consider the partial Product Graph shown in Figure~\ref{fig:avoiding-loops}.
+Our preference inference algorithm will determine that node $X_1$ should be locally preferred to node $X_2$ since this will result in a better (lower ranked) path to destination $A$.
+However, when applying Algorithm~\ref{alg:failures}, we failed to take into account the possibility of loops.
+In particular, node $A_2$ may be unusable for advertisements that go through $X_1$ since the advertisement may have already gone through $A_1$ previously.
+In this case, $X$ will have made the wrong choice since preferring $X_2$ would have resulted in a better path for the destination $A$ (a path of rank 3 instead of 4).
+
+On the other hand, this would not have been a problem if paths ending at $A_1$ had a lower rank than those ending at $A_2$ or $A_3$.
+For example, if paths ending at $A_1$ had rank 1, then any time $A_2$ is unusable due to a loop with $A_1$, it ultimately does not matter since $A_1$ is preferred anyway.
+%
+In fact, checking if we are never worse off using $A_1$ instead of $A_2$ corresponds exactly with determining if $A$ has a \textup{Regret-Free} preference for $A_1$ over $A_2$.
+%
+More specifically, the compiler checks that, any time there are two shadows $N_1$ and $N_2$ for the same topology location, where $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (i.e., $N_1 <_{lp} N_2$).
 
@@
 It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
+
+\subsection{Aggregation-safety analysis}
+
+%\para{Aggregation Safety}
+\label{sec:agg-safety}
+
+As shown in \S\ref{sec:motivation}, aggregation can lead to subtle black-holing of traffic when failures occur.
+Determining when this can happen requires knowledge, not only of the topology, but also of the policy.
+For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated.
+If that one link fails, a black hole might be introduced.
+%
+Because the PGIR encodes the complete user policy and topology, \sysname can efficiently check that aggregates do not black hole traffic for up to $k$ failures.
+
+We view the aggregation problem as a variant of the min-cut problem in the PGIR.
+Specifically, for each prefix that falls under an aggregate, we are interested in finding a lower bound on the number of failures required to disconnect the prefix's origin from its aggregation point.
+The difficulty, however, is that each link in the topology might appear as multiple links in the PGIR, thus preventing the direct application of standard min-cut algorithms.
+%
+
+Instead, we adopt the following simple strategy: $i)$ pick a random path in the PGIR between the prefix origin and aggregation point, $ii)$ remove all similar edges in the PGIR for each topological edges along the chosen path, and $iii)$ repeat until no such path exists.
+Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.
 
@@
 \end{figure}
-
-\subsection{Aggregation-safety analysis}
-
-%\para{Aggregation Safety}
-\label{sec:agg-safety}
-
-As shown in \S\ref{sec:motivation}, aggregation can lead to subtle black-holing of traffic when failures occur.
-Determining when this can happen requires knowledge, not only of the topology, but also of the policy.
-For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated.
-If that one link fails, a black hole might be introduced.
-%
-Because the PGIR encodes the complete user policy and topology, \sysname can efficiently check that aggregates do not black hole traffic for up to $k$ failures.
-
-We view the aggregation problem as a variant of the min-cut problem in the PGIR.
-Specifically, for each prefix that falls under an aggregate, we are interested in finding a lower bound on the number of failures required to disconnect the prefix's origin from its aggregation point.
-The difficulty, however, is that each link in the topology might appear as multiple links in the PGIR, thus preventing the direct application of standard min-cut algorithms.
-%
-
-Instead, we adopt the following simple strategy: $i)$ pick a random path in the PGIR between the prefix origin and aggregation point, $ii)$ remove all similar edges in the PGIR for each topological edges along the chosen path, and $iii)$ repeat until no such path exists.
-Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.
 
@@
 
-%\begin{figure}[t!]
-%\centering
-%\includegraphics[width=.9\columnwidth]{figures/config}
-%\caption{Abstract BGP configuration.}
-%\label{fig:abgp-config}
-%\end{figure}
+The final stage of our compiler translates policies from PGIR to a vendor-neutral abstraction of BGP (ABGP).
+% and then from ABGP to actual device configurations.
+
+\para{From PGIR to ABGP}
+
+Once we have the total ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
+The idea is to encode the state of the automata using BGP community values.
+Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR.
+For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else).
+If it sees such an announcement, it will remove the old community value and add a new one for state $(4,2)$ before exporting it to $W$.
+
+To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR.
+For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
+
+Since the compiler can control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
+Instead, it translates matches from external ASes into a BGP regular expression filter.
+For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$.
+In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
+The unknown AS topology is modeled as a special node in the PGIR that generates a filter to match any sequence of ASes.
+
+Finally, the external AS $W$ should prefer our internal router $A$ over $B$.
+In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
+In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$.
+Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
+The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
+%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
+Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
+Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.
+
+After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
+In the compilation example all community tags can be removed, since there is never any ambiguity based on the router importing the route and the neighbor the route is being imported from.
+Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
 
@@
 
-The final stage of our compiler translates policies from PGIR to a vendor-neutral abstraction of BGP (ABGP).
-% and then from ABGP to actual device configurations.
-
-\para{From PGIR to ABGP}
-
-Once we have the total ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
-The idea is to encode the state of the automata using BGP community values.
-Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR.
-For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else).
-If it sees such an announcement, it will remove the old community value and add a new one for state $(4,2)$ before exporting it to $W$.
-
-To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR.
-For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
-
-Since the compiler can control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
-Instead, it translates matches from external ASes into a BGP regular expression filter.
-For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$.
-In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
-The unknown AS topology is modeled as a special node in the PGIR that generates a filter to match any sequence of ASes.
-
-Finally, the external AS $W$ should prefer our internal router $A$ over $B$.
-In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
-In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$.
-Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
-The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
-%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
-Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
-Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.
-
-After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
-In the compilation example all community tags can be removed, since there is never any ambiguity based on the router importing the route and the neighbor the route is being imported from.
-Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
-
 %=====================================================
@@
 When computing local preferences and ensuring failure safety, as described in \S\ref{sec:compilation}, the compiler performs memoization of the \textup{Regret-Free} function.
-That is, whenever for two states $N_1$ and $N_2$ we compute $\textup{Regret-Free}(G, N_1, N_2)$, if the function evaluates to $true$, then each of the intermediate related states $x$ and $y$ must also satisfy $\textup{Regret-Free}(G, x, y)$.
+That is, whenever for two states $N_1$ and $N_2$ we compute $\textup{Regret-Free}(G, N_1, N_2)$, if the function evaluates to $true$, then each of the intermediate related states $m$ and $n$ must also satisfy $\textup{Regret-Free}(G, m, n)$.
 Memoizing these states dramatically reduces the amount of work performed to find preferences in the common case.
@@
 Even when programming the network centrally, it is possible for operators to make mistakes and write incorrect policies.
-\sysname includes many analyses to flag common mistakes at compile time.
-A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if topology locations that should be reachable according to the operator policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator might accidentally anycast a prefix (i.e., originates the prefix from multiple locations), (iv) an aggregate analysis to find when aggregates do not summarize any specific prefix.
+\sysname includes many analyses to identify common mistakes at compile time.
+A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if locations that should be reachable according to the policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator might accidentally anycast a prefix (i.e., originates the prefix from multiple locations), (iv) an aggregate analysis to find when aggregates do not summarize any specific prefix.
 
@@
 
-\subsection{Expressiveness}
-
-We found that we could translate all network policies to \sysname.
-We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname.
-The datacenter operator said that he found the language intuitive.
-The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We further found that the datacenter policies were correctly translated.
-For the backbone network, the operator mentioned an additional policy not present in the English document, which we added later.
-
-Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the routing policies for \sysname were 43 lines for the backbone network and 31 lines for the datacenter networks.
-
 \begin{figure}
@@
   \caption{Compilation time. \label{fig:compilation-times}}
+  \vspace{-1em}
+\end{figure}
+
+\subsection{Expressiveness}
+
+We found that we could translate all network policies to \sysname.
+We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname.
+The datacenter operator said that he found the language intuitive.
+The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We further found that the datacenter policies were correctly translated.
+For the backbone network, the operator mentioned an additional policy not present in the English document, which we added later.
+
+Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the routing policies for \sysname were 43 lines for the backbone network and 31 lines for the datacenter networks.
+
+\begin{figure}[t!]
+  \subcaptionbox{Datacenter}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
+  \subcaptionbox{Backbone}
+    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
+  \caption{Configuration minimization. \label{fig:config-min}}
   \vspace{-1em}

### 2016-06-21 paper/v2/paper-edited.tex
fixing image issue

@@
 When there is no such equivalent step, the algorithm attempts to take into account where the advertisement must have already traversed.
-In particular, it checks if there is an equivalent dominator (i.e., a topology location the advertisement must have passed through earlier) and walks from this new node instead.
+In particular, it checks if there is an equivalent dominator node and, if so, walks from this new node instead.
+%
+The idea is that, since the advertisement must have already passed through the dominator, we can check to see if we are guaranteed to find paths that are at least as good from this new node instead.
+%
 At each step, it requires that the current node reachable from $N_1$ has a path rank that is at least as good as that of the current node reachable from $N_2$ ($m \leq_{rank} n$).

### 2016-06-21 paper/v2/paper-edited.tex
clarify which cloud provider
italicize latin. change graph labels

@@
 %
-The language allows operators to specify their objectives naturally, using high-level constraints on and ordered preferences for paths that traffic should take.
-%through their network or other networks.
-%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
-%
-The compiler automatically translates these specifications to router-level BGP configurations, using a novel data structure that compactly encodes the flow of routing information along policy-compliant paths.
+The language allows operators to specify their objectives naturally, using 
+high-level constraints on both the shape and relative preferences of traffic paths.
+%
+The compiler automatically translates these specifications to router-level BGP configurations, using an effective intermediate representation that compactly encodes the flow of routing information along policy-compliant paths.
 %It uses We introduce data structures and algorithms that
@@
 It is well known that configuring networks is error
-prone and such errors can lead to disruptive
+prone and that such errors can lead to disruptive
 downtimes~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
 For instance, a recent misconfiguration led to an hour-long, nation-wide outage for Time Warner's backbone network~\cite{time-warner}; and a major BGP-related incident makes international news every few months~\cite{bgpmon}.
-
-%For instance, in the context of BGP, Mahajan~~\cite{mahajan+:bgp-misconfiguration}
-%estimated that 200-1200 prefixes suffered from
-%misconfiguration each day and that close to 3 in 4 of all
-%new prefix advertisements were the result of misconfiguration.
-%Moreover, these misconfigurations sometimes cause significant network downtime for
-%individual networks~\cite{time-warner} or even broader internet connectivity problems~\cite{routing-instability,mahajan+:bgp-misconfiguration}.
-%\dpw{Note that \cite{time-warner} and I am not sure about the specifics of the problem there
-%or what exactly was misconfigured.  It is also unclear if our language really helps with the
-%``broader internet connectivity problems'' however, I thought that adding some specific examples
-%would help make the intro more compelling.  Feel free to rewrite.}
-
-%One reason for network configuration being onerous is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.
 
@@
 One such attribute is a list of community strings.
-ASes use such strings to color routes on different criteria (e.g., ``entered on West Coast'') and then use the color later in the routing process.
-Communities are also used to signal to neighbors how they should handle an announcement (e.g., do not export it further).
+ASes use such strings to associate network-specific information with particular routes (\EG, ``entered on West Coast'') and then use the information later in the routing process.
+Communities are also used to signal to neighbors how they should handle an announcement (\EG, do not export it further).
 Another non-global attribute is the multi-exit discriminator (MED).
@@
 The operator may implement the policy by having X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ export externally what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}.
-This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can occur independently, e.g., local services can be assigned new prefixes without updating those routers' configurations.
+This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can occur independently, \EG, local services can be assigned new prefixes without updating those routers' configurations.
 
@@
 Per its policy implementation, X will start "leaking" these prefixes externally.
-Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are reused for other services outside of the datacenter).
+Depending on the rationale for local services, this leak could impact security (\EG, if the services are sensitive) or availability (\EG, if the \CD{PL*} prefixes are reused for other services outside of the datacenter).
 This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter.
@@
 
-To avoid this problem, the operator may disallow "valley" paths, i.e., those that go up, down, and back up again.
+To avoid this problem, the operator may disallow "valley" paths, \IE, those that go up, down, and back up again.
 This guard can be implemented by $X$ and $Y$ rejecting paths through the other.
@@
 If links D--A and X--C fail, X will hear an announcement for \CD{PG2} from D and will thus announce \CD{PG} externally.
-This announcement will bring to X traffic for \CD{PG1} as well, but because valleys are disallowed, X does not have a valid route for \CD{PG1} and will drop all traffic for it despite the fact that a valid path exists through $Y$.
+This announcement will bring traffic for \CD{PG1} to X as well, but because valleys are disallowed, X does not have a valid route for \CD{PG1} and will drop all traffic for it despite the fact that a valid path exists through $Y$.
 
@@
 %
-Second, paths in a control-plane policy may be under-specified (e.g.,
+Second, paths in a control-plane policy may be under-specified (\EG,
 "prefer customer" does not indicate a concrete path). The \sysname
@@
 We also use the standard regular expression abbreviation $r^+$ for $r \cdot r^*$, a sequence of one or more occurrences of $r$.
-Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisements with a particular community value (i.e., an integer value associated with a path).
+Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisements with a particular community value (\IE, an integer value associated with a path).
 %% For example, the constraint
@@
 A constraint of the form $agg(x,l)$ tells the compiler to perform aggregation for prefix $x$ across all links described by $l$.
-It is also often useful to be able to add community tags to exported routes in BGP (e.g., to communicate non-standard information to peers).
+It is also often useful to be able to add community tags to exported routes in BGP (\EG, to communicate non-standard information to peers).
 A constraint of the form $tag(c,t,l)$ adds community tag $c$ for any prefixes matching $t$ across links $l$.
@@
 where $\odot$ stands for an arbitrary regular binary operator, and $r$ is a policy with a single preference.
-The compiler flags preferences nested under a unary operator (i.e., \textit{star} or \textit{negation}) as invalid.
+The compiler flags preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) as invalid.
 
@@
 %The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$.
-While paths in an RIR policy describe the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated, i.e., route announcements flowing in the opposite direction.
+While paths in an RIR policy describe the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated, \IE, route announcements flowing in the opposite direction.
 To capture this idea, for each regular expression $r_i$ in RIR policy, we construct a deterministic finite state machine on the reversed regular expression.
 Each automaton for the reversed regular expression of $r_i$ is a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ consists of all abstract locations (i.e., routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+The alphabet $\Sigma$ consists of all abstract locations (\IE, routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
 %
@@
 For a PGIR vertex $n = (l, \dots) \in V'$, we say that $n$ is a \emph{shadow} of topology location $l$, written as $\tilde{n} = l$, to indicate that the topology location for node $n$ is $l$.
-When two PGIR nodes $m$ and $n$ shadow the same topology location (i.e., $\tilde{m} = \tilde{n}$), we write $m \approx n$.
+When two PGIR nodes $m$ and $n$ shadow the same topology location (\IE, $\tilde{m} = \tilde{n}$), we write $m \approx n$.
 
 Throughout the remainder of the paper, we will the convention that metavariables $m$ and $n$ stand for PGIR nodes and $l$ stands for a topology location.
-Captial letters like $X$, $Y$ refer to concrete topology locations, while capital letters with subscripts such as $X_1$ and $X_2$ refer to concrete PGIR nodes that share a topology location (i.e., $\tilde{X_1}$ = $\tilde{X_2} = X$).
+Captial letters like $X$, $Y$ refer to concrete topology locations, while capital letters with subscripts such as $X_1$ and $X_2$ refer to concrete PGIR nodes that share a topology location (\IE, $\tilde{X_1}$ = $\tilde{X_2} = X$).
 
@@
 Similarly, a node $m$ post-dominates a node $n$ in the PGIR if $m$ appears on every path from $n$ to the end node.
-We can safely remove nodes and edges in the PGIR when any of the following conditions hold, where we have $m$, $m'$ and $n$, $n'$ such that $\tilde{m} = \tilde{m}'$ and $\tilde{n} = \tilde{n}'$.
+We can safely remove nodes and edges in the PGIR when any of the following conditions hold, where we have $m$, $m'$ and $n$, $n'$ such that $m \approx m'$ and $n \approx n'$.
 \begin{itemize}
@@
   \centering
-  \includegraphics[width=.7\columnwidth]{figures/loops}
+  \includegraphics[width=.6\columnwidth]{figures/loops}
   \caption{A Product Graph where preference inference is unsound before considering loops.}
@@
 
-The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available due to loops.
-BGP automatically rejects advertisements to a location where the locations is already contained in the AS path attribute.
+The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available due to loops rejected by BGP. 
+%BGP automatically rejects advertisements to a location where the locations is already contained in the AS path attribute.
 
@@
 %
-More specifically, the compiler checks that, any time there are two shadows $N_1$ and $N_2$ for the same topology location, where $N_1$ appears ``above'' (i.e., can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (i.e., $N_1 <_{lp} N_2$).
+More specifically, the compiler checks that, any time there are two shadows $N_1$ and $N_2$ for the same topology location, where $N_1$ appears ``above'' (\IE, can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (\IE, $N_1 <_{lp} N_2$).
 
@@
 Because $A$ is then disconnected from $X$, the compiler knows that 2 is a lower bound on the number of failures required to potentially introduce an aggregation black hole for prefix \CD{PG1}.
-This process is repeated for other aggregation locations (e.g., $Y$).
+This process is repeated for other aggregation locations (\EG, $Y$).
 
@@
 Currently, \sysname supports generating Quagga router configurations out of the box.
-Users can add new vendor-specific adapters to translate from ABGP to other router configuration languages, or incorporate the compiler into an existing template-based system, e.g., by mixing the \sysname-generated BGP configuration with other, non-BGP configuration elements.
+Users can add new vendor-specific adapters to translate from ABGP to other router configuration languages, or incorporate the compiler into an existing template-based system, \EG, by mixing the \sysname-generated BGP configuration with other, non-BGP configuration elements.
 
@@
 
-Constructing automata for extended regular expressions (i.e., regular expressions with negation and intersection operations) is known to have high complexity~\cite{regex-complexity}.
+Constructing automata for extended regular expressions (\IE, regular expressions with negation and intersection operations) is known to have high complexity~\cite{regex-complexity}.
 The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions efficiently.
@@
 \sysname includes many analyses to identify common mistakes at compile time.
-A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if locations that should be reachable according to the policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator might accidentally anycast a prefix (i.e., originates the prefix from multiple locations), (iv) an aggregate analysis to find when aggregates do not summarize any specific prefix.
+A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if locations that should be reachable according to the policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator might accidentally anycast a prefix (\IE, originates the prefix from multiple locations), (iv) an aggregate analysis to find when aggregates do not summarize any specific prefix.
 
@@
 
-We obtained routing policy for the backbone network and for the datacenters of a large cloud provider.
+We obtained routing policy for Microsoft's backbone network and datacenters.
 Multiple datacenters share this policy.
@@
 For some neighbors, it prefers some links over the others.
-It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA).
-Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, etc.
+It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (\EG, West Coast of the USA).
+Finally, it has many filters, \EG, to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, \ETC
 
@@
 
-We comment briefly on how \sysname-generated configurations differ from configurations or templates generated by operators.
+We comment briefly on how \sysname-generated configurations differ from configurations or templates written by operators.
 %
@@
 
-We are investigating if such differences matter to operators, e.g., if they want to read \sysname configurations, and, if necessary, how to reduce them.
+We are investigating if such differences matter to operators, \EG, if they want to read \sysname configurations, and, if necessary, how to reduce them.
 
@@
 In particular, FatTire allows programmers to define sets of paths together
-with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
+with a fault tolerance level (\IE, tolerate 1 or 2 faults)
 and the compiler generates appropriate OpenFlow rules.

### 2016-06-21 data/backbone.py

@@ -78,7 +78,7 @@ ax1.fill_between(num_nodes, y_stack[0,:], y_stack[1,:], facecolor=color2, alpha=
 ax1.fill_between(num_nodes, y_stack[1,:], y_stack[2,:], facecolor=color3)
 ax1.fill_between(num_nodes, y_stack[2,:], y_stack[3,:], facecolor=color4)
 ax1.set_xlabel('Routers', fontsize=35)
-ax1.set_ylabel('Avg. Time / Prefix (s)', fontsize=35)
+ax1.set_ylabel('Avg. Time / Predicate (s)', fontsize=35)
 ax1.tick_params(axis='both', which='major', labelsize=35)
 ax1.tick_params(axis='both', which='minor', labelsize=35)
 ax1.xaxis.set_ticks([0,40,80,120,160,200])

### 2016-06-21 data/datacenter.py

@@ -79,7 +79,7 @@ ax1.fill_between(num_nodes, y_stack[1,:], y_stack[2,:], facecolor=color3)
 ax1.fill_between(num_nodes, y_stack[2,:], y_stack[3,:], facecolor=color4)
 #ax1.fill_between(num_nodes, y_stack[3,:], y_stack[4,:], facecolor=color5)
 ax1.set_xlabel('Routers', fontsize=35)
-ax1.set_ylabel('Avg. Time / Prefix (s)', fontsize=35)
+ax1.set_ylabel('Avg. Time / Predicate (s)', fontsize=35)
 ax1.tick_params(axis='both', which='major', labelsize=35)
 ax1.tick_params(axis='both', which='minor', labelsize=35)
 ax1.set_xlim([0,1400])

### 2016-06-21 paper/v2/paper-edited.tex
fix formatting issues

@@
 Compilation for the largest backbone network, takes less than 3 minutes total.
-The inclusion of more preferences in the backbone policy increases the size of the PGIR, which leads to PGIR construction and minimization taking proportionally more time.
+The inclusion of both more preferences and more neighboring ASes in the backbone policy increases the size of the resulting PGIR, which in turn leads to PGIR construction and minimization taking proportionally more time.
 

### 2016-06-22 paper/v2/paper-edited.tex
make figure text size consistent

--- 2016-06-21 paper/v2/paper-edited.tex
@@
 %
-The preference function $P$ for node $n = (l, a_1, \dots, a_k)$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $.
-That is, it records which preferences are achieved from each policy automaton for every node in the product construction.
+The preference function $P$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $. That is, it records the path rank of each regular expression matched in the current node.
+% in preferences are achieved from each policy automaton for every node in the product construction.
 %
@@
 %
-For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path, leading to a path that satisfies the preference 1 policy, but which contains a loop.
+For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path, leading to a path that satisfies the preference 2 policy, but which contains a loop.
 %
@@
   \centering
-  \includegraphics[width=.6\columnwidth]{figures/loops}
-  \caption{A Product Graph where preference inference is unsound before considering loops.}
+  \includegraphics[width=.66\columnwidth]{figures/loops}
+  \caption{A Product Graph where preference inference is unsound before considering loops. Path ranks shown by nodes.}
   \label{fig:avoiding-loops}
@@
 Compilation for the largest backbone network, takes less than 3 minutes total.
-The inclusion of more preferences in the backbone policy increases the size of the PGIR, which leads to PGIR construction and minimization taking proportionally more time.
+The inclusion of both more preferences and more neighboring ASes in the backbone policy increases the size of the resulting PGIR, which in turn cleads to PGIR construction and minimization taking proportionally more time.
 

### 2016-06-22 paper/v2/paper-edited.tex
edits

@@
 The language allows operators to specify their objectives naturally, using 
-high-level constraints on both the shape and relative preferences of traffic paths.
+high-level constraints on both the shape and relative preference of traffic paths.
 %
@@
 
-We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies of datacenter and backbone networks.
+We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies for Microsoft's datacenter and backbone networks.
 % and compared these specifications with existing configurations.
-We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds to thousands of routers, compiling in under 9 minutes in all cases.
+We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds or thousands of routers, compiling in under 9 minutes in all cases.
 
@@
 \CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links.
-A similar policy must be configured for \CD{R2} as well.
+A similar type of policy must be configured for \CD{R2} as well.
 Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based import and export filters at each router.
@@
 leave through \CD{Peer} and then \CD{Prov}.  As we
-describe in the next section, the \Exit\ predicate, as well as other
-path predicates used later in this section, is simply a shorthand for
+describe in the next section, the \Exit\ expression, as well as other
+path expressions used later in this section, is simply a shorthand for
 a particular regular expression over paths that is expressible in our policy
@@
      lp       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
-     cc     &::=& agg(x, lp) \BNFALT tag(c, t, lp) & \textit{control constraints} \\
+     cc     &::=& agg(x, lp) \BNFALT tag(d, t, lp) & \textit{control constraints} \\
   \end{array} \]
@@
 The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR).
-Policies in RIR are checked for being well-formed (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR).
+Policies in RIR are checked well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the topology to obtain the Product Graph Intermediate Representation (PGIR).
 The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions.
@@
 \sysname also supports constraints purely on the control-plane behavior of BGP.
-For example, prefix aggregation is an important optimization to reduce routing table size and churn in practice.
-A constraint of the form $agg(x,l)$ tells the compiler to perform aggregation for prefix $x$ across all links described by $l$.
+For example, prefix aggregation is an important optimization to reduce routing table size in practice.
+A constraint of the form $agg(x,lp)$ tells the compiler to perform aggregation for prefix $x$ across all links described by $lp$.
 It is also often useful to be able to add community tags to exported routes in BGP (\EG, to communicate non-standard information to peers).
-A constraint of the form $tag(c,t,l)$ adds community tag $c$ for any prefixes matching $t$ across links $l$.
+A constraint of the form $tag(d,t,lp)$ adds community tag $d$ for any prefixes matching $t$ across links $lp$.
 %% Aggregation, for example, from internal to external locations, is specified using the same regular syntax as before:
@@
 %% where the expression $\In \Link Out$ refers to control messages flowing from any internal to any external location.
-We list only the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, but we also support other constraints such as limiting the maximum number of routes allowed between ASes, or enabling BGP multipath.
+We list only the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, but \sysname also supports other constraints such as limiting the maximum number of routes allowed between ASes, or enabling BGP multipath.
 
@@
 In particular, we want a compact representation that describes all the possible ways BGP route announcements can flow through the network subject to the policy and topology constraints.
-The PGIR captures these constraints by ``intersecting" each of the regular automata corresponding to the RIR path preferences and the topology.
+The PGIR captures these constraints by ``intersecting" each of the regular automata corresponding to the RIR path preferences with the topology.
 Paths through the PGIR correspond to real paths through the topology that satisfy the user constraints.
@@
 While paths in an RIR policy describe the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated, \IE, route announcements flowing in the opposite direction.
-To capture this idea, for each regular expression $r_i$ in RIR policy, we construct a deterministic finite state machine on the reversed regular expression.
+To capture this idea, for each regular expression $r_i$ in an RIR policy, we construct a deterministic finite state machine on the reversed regular expression.
 Each automaton for the reversed regular expression of $r_i$ is a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
@@
 a unique ending vertex $e$,
-and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
+and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of path ranks.
 
@@
 
-Throughout the remainder of the paper, we will the convention that metavariables $m$ and $n$ stand for PGIR nodes and $l$ stands for a topology location.
-Captial letters like $X$, $Y$ refer to concrete topology locations, while capital letters with subscripts such as $X_1$ and $X_2$ refer to concrete PGIR nodes that share a topology location (\IE, $\tilde{X_1}$ = $\tilde{X_2} = X$).
+Throughout the remainder of the paper, we will use the convention that metavariables $m$ and $n$ stand for PGIR nodes and $l$ stands for a topology location.
+Capital letters like $X$ refer to concrete topology locations, while capital letters with subscripts such as $X_1$ and $X_2$ refer to concrete PGIR nodes that share a topology location (\IE, $\tilde{X_1}$ = $\tilde{X_2} = X$).
 
@@
 
-Intuitively, a PGIR tracks the policy states of each automaton as route announcements move between locations.
+Intuitively, the PGIR tracks the policy states of each automaton as route announcements move between locations.
 %
@@
   \centering
-  \includegraphics[width=.66\columnwidth]{figures/loops}
+  \includegraphics[width=.67\columnwidth]{figures/loops}
   \caption{A Product Graph where preference inference is unsound before considering loops. Path ranks shown by nodes.}

### 2016-06-22 paper/v2/paper-edited.tex
edits

@@
 It simplifies operators' task of describing preferred paths, but that simplicity comes at the cost of compilation complexity.
-The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, determine which ones can be honored under failures, and ensure policy compliance under all failure cases.
+The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology and ensure policy compliance under all failure scenarios.
 
@@
 
-     pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
-     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{preferences} \\
+     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
+     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
      x       &::=& d.d.d.d/d & \textit{prefix} \\
@@
 Figure~\ref{fig:rir-syntax} shows the RIR syntax.
-A policy has one or more constraints, each of which has a test on the type of route and a corresponding set of preferred regular paths.
+A policy has one or more constraints.
+The first kind of constraint is a test on the type of route and a corresponding set of preferred regular paths or a control constraint.
 Regular paths are regular expressions where the base characters are abstract locations representing either a router or an external AS.
@@
 
-\sysname also supports constraints purely on the control-plane behavior of BGP.
-For example, prefix aggregation is an important optimization to reduce routing table size in practice.
+\sysname also supports constraints on the control-plane behavior of BGP.
+For example, prefix aggregation is an important optimization to reduce routing table size.
 A constraint of the form $agg(x,lp)$ tells the compiler to perform aggregation for prefix $x$ across all links described by $lp$.
@@
 
-The semantics of RIR is in terms of ranked paths.
-Each preference-based regular path constraint of the form $r_1 \Prefer \dots \Prefer r_j$ maps to a set of concrete paths in the network that match one of the $r_i$.
-A network path is a string of abstract locations of the form $l_1 l_2 \dots l_k$.
-A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$, that is, the path is in the language of the regular expression and is topologically valid.
-%We denote the length of a path $p$ as $\abs{p}$.
-
-A path $p$ has rank:
+We give a semantics to RIR programs using sets of ranked paths.
+Each path constraint $r_1 \Prefer \dots \Prefer r_j$ denotes a set of ranked network paths.
+A network path is a topologically valid string of abstract locations $l_1 l_2 \dots l_k$.
+We use the notation $\abs{p}$ to denote the length of the path $p$.
+A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$, that is, the path is in the language of the regular expression.
+Paths are ranked lexicographically according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the path length.
+Lower ranks indicate \emph{more} preferred paths.
+More formally, a path $p$ has rank:
 $$(\min_i \set{ p \in \mathcal{L}(r_i) }, \abs{p})$$
-which is lexicographically ordered according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the path length $\abs{p}$.
-Lower ranks indicate \emph{more} preferred paths.
-Traffic may be sent on any of the most preferred paths for each pair of starting and ending locations that appear in some specified path.
+%
+The set of ranked paths depends on which paths are valid in the topology, and thus when failures occur, the most preferred routes change. 
+%
+For any source $s$ and destination $d$, \sysname will send traffic along the highest ranked available path from $s$ to $d$.
+
+%Traffic may be sent on any of the most preferred paths for each pair of starting and ending locations that appear in some specified path.
 There is an implicit lowest preference $\emptyset$ to drop traffic when no other route is possible.
 
-The set of ranked paths depends on which paths are valid in the topology, and thus when failures occur, the most preferred routes change.
-The \sysname compiler ensures that generated configurations for a policy always achieve the most preferred path possible given the failures in the topology, using only distributed mechanisms.
+%The \sysname compiler ensures that generated configurations for a policy always achieve the most preferred path possible given the failures in the topology, using only distributed mechanisms.
 
@@
 
-We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
+We use graph dominators~\cite{tarjan-dominance} as a relatively cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
 In the PGIR, a node $m$ dominates a node $n$ if $m$ appears on every path leading from the start node to $n$.
@@
 For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is removed because every path to the end node must always go through node $(W,-,4)$.
-That is, node $(W,1,1$ is post-dominated by node $(W,-,4)$ and both are shadows of topology location $W$.
-Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$.
+That is, node $(W,1,1)$ is post-dominated by node $(W,-,4)$ and both are shadows of topology location $W$.
+Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$, and shadows the topology location $C$.
 

### 2016-06-22 paper/v2/paper-edited.tex
more edits

@@
          &\BNFALT& r^* & \textit{iteration} \\
-     lp       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
-     cc     &::=& agg(x, lp) \BNFALT tag(d, t, lp) & \textit{control constraints} \\
+     ln       &::=& r_1 \rightarrow r_2 & \textit{links} \\
+     cc     &::=& agg(x, ln) \BNFALT tag(d, t, ln) & \textit{control constraints} \\
   \end{array} \]
@@
 For example, prefix aggregation is an important optimization to reduce routing table size.
-A constraint of the form $agg(x,lp)$ tells the compiler to perform aggregation for prefix $x$ across all links described by $lp$.
+A constraint of the form $agg(x,ln)$ tells the compiler to perform aggregation for prefix $x$ across all links described by $ln$.
 It is also often useful to be able to add community tags to exported routes in BGP (\EG, to communicate non-standard information to peers).
-A constraint of the form $tag(d,t,lp)$ adds community tag $d$ for any prefixes matching $t$ across links $lp$.
+A constraint of the form $tag(d,t,ln)$ adds community tag $d$ for any prefixes matching $t$ across links $ln$.
 %% Aggregation, for example, from internal to external locations, is specified using the same regular syntax as before:
@@
 That is, node $(W,1,1)$ is post-dominated by node $(W,-,4)$ and both are shadows of topology location $W$.
-Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$, and shadows the topology location $C$.
+Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$.
 
@@
 %
-For example, if $C$'s shadow $(C,3,2)$ is preferred to $(C,-,2)$, written as $(C,3,2) \leq_{lp} (C,-,2)$,  $C$ will prefer advertisements from $(D,2,2)$ over $(E,-,2)$.
+For example, if $C$'s shadow $(C,3,2)$ can be preferred to $(C,-,2)$, written as $(C,3,2) \leq_{lp} (C,-,2)$, $C$ can prefer advertisements from $(D,2,2)$ over $(E,-,2)$.
 $D$ and $E$ tag their advertisements to let $C$ know which shadow sent the advertisement.
@@
 \para{Regret-free Preferences}
-To order PGIR shadows ($\leq_{lp}$) for each router in a way that is both sound and complete under all failures, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
-A router (location) $l$ has a regret-free preference for a set of advertisements $A$ over $B$ if, whenever $l$ selects an advertisement to destination $d$ from $A$ over another from $B$, there is always some policy-compliant path to $d$ that is at least as good ($\leq_{rank}$ for the final node along the path) as any possible path (not necessily from $l$) to $d$ if $l$ had selected an advertisement from $B$ instead.
+To order PGIR shadows ($\leq_{lp}$) for each router in a way that is policy-compliant under all failures, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
+A router (location) $l$ has a regret-free preference for a set of advertisements $A$ over $B$ if, whenever $l$ selects an advertisement to destination $d$ from $A$ over another from $B$, there is always some policy-compliant path to $d$ that is at least as good ($\leq_{rank}$ for the final node along the path) as any possible path (not necessarily from $l$) to $d$ if $l$ had selected an advertisement from $B$ instead.
 In other words, the preference of $A$ over $B$ at $l$ is regret-free if $l$ is never (under any failure) worse-off by choosing an advertisement from $A$ when available.
@@
 %
-In fact, checking if we are never worse off using $A_1$ instead of $A_2$ corresponds exactly with determining if $A$ has a \textup{Regret-Free} preference for $A_1$ over $A_2$.
+In fact, checking if we are never worse off using $A_1$ instead of $A_2$ corresponds exactly with determining if $A$ has a regret-free preference for $A_1$ over $A_2$.
 %
@@
 
-Instead, we adopt the following simple strategy: $i)$ pick a random path in the PGIR between the prefix origin and aggregation point, $ii)$ remove all similar edges in the PGIR for each topological edges along the chosen path, and $iii)$ repeat until no such path exists.
+Instead, we adopt the following simple strategy: $i)$ pick a random path in the PGIR between the prefix's origin and aggregation point, $ii)$ remove all similar edges in the PGIR for each topology edge along the chosen path, and $iii)$ repeat until no such path exists.
 Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.
@@
 Constructing automata for extended regular expressions (\IE, regular expressions with negation and intersection operations) is known to have high complexity~\cite{regex-complexity}.
-The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions efficiently.
+The \sysname compiler uses regular expression derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions efficiently.
 Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy.
@@
 When computing local preferences and ensuring failure safety, as described in \S\ref{sec:compilation}, the compiler performs memoization of the \textup{Regret-Free} function.
-That is, whenever for two states $N_1$ and $N_2$ we compute $\textup{Regret-Free}(G, N_1, N_2)$, if the function evaluates to $true$, then each of the intermediate related states $m$ and $n$ must also satisfy $\textup{Regret-Free}(G, m, n)$.
+That is, whenever for two states $N_1$ and $N_2$ we compute $\textup{Regret-Free}(G, N_1, N_2)$ and the function evaluates to $true$, then each of the intermediate related states $m$ and $n$ must also satisfy $\textup{Regret-Free}(G, m, n)$.
 Memoizing these states dramatically reduces the amount of work performed to find preferences in the common case.
@@
 
-The naive code generation algorithm described in \S\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in-edge/out-edge pair for every node in the product graph before minimization.
+The naive code generation algorithm described in \S\ref{sec:abgp} is extremely memory inefficient since it generates a separate match-export pair for every unique in-edge/out-edge pair for every node in the product graph before minimization.
 Our implementation performs partial minimization during generation by recognizing common cases such as when there is no restriction on exporting to or importing from neighbors.
@@
 \sysname includes many analyses to identify common mistakes at compile time.
-A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if locations that should be reachable according to the policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator might accidentally anycast a prefix (\IE, originates the prefix from multiple locations), (iv) an aggregate analysis to find when aggregates do not summarize any specific prefix.
+A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if locations that should be reachable according to the policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator might accidentally anycast a prefix (\IE, originates the prefix from multiple locations), (iv) an aggregate analysis to find aggregates that do not summarize any specific prefix.
 
@@
 We apply \sysname on real policies for backbone and datacenter networks.
-Our main goals are to evaluate if its language is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
+Our main goals are to evaluate if its language is expressive enough for real-world policies, the time the compiler takes to generate router configurations, and the size of the resulting configurations.
 
@@
 For the backbone network, the operator mentioned an additional policy not present in the English document, which we added later.
+%
+For both the datacenter and backbone networks, the \sysname compiler was able to guarantee policy-compliance under all possible failure scenarios.
 
@@
 Compilation for the largest backbone network, takes less than 3 minutes total.
-The inclusion of both more preferences and more neighboring ASes in the backbone policy increases the size of the resulting PGIR, which in turn cleads to PGIR construction and minimization taking proportionally more time.
+The inclusion of both more preferences and more neighboring ASes in the backbone policy increases the size of the resulting PGIR, which in turn leads to PGIR construction and minimization taking proportionally more time.
 

### 2016-06-22 paper/v2/paper-edited.tex
edits

@@
 
-We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies for Microsoft's datacenter and backbone networks.
+We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies for datacenter and backbone networks.
 % and compared these specifications with existing configurations.
@@
 
-We obtained routing policy for Microsoft's backbone network and datacenters.
+We obtained routing policy for the backbone network and datacenters of a large cloud provider.
 Multiple datacenters share this policy.

### 2016-06-22 paper/v2/paper-edited.tex
reducing size
space reduction

--- 2016-06-22 paper/v2/paper-edited.tex
@@
 
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10003033.10003068.10003073.10003075</concept_id>
-<concept_desc>Networks~Network control algorithms</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10003033.10003083.10003095</concept_id>
-<concept_desc>Networks~Network reliability</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10003033.10003099.10003104</concept_id>
-<concept_desc>Networks~Network management</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10010940.10010992.10010998.10011000</concept_id>
-<concept_desc>Software and its engineering~Automated static analysis</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10011006.10011050.10011017</concept_id>
-<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[300]{Networks~Network control algorithms}
-\ccsdesc[300]{Networks~Network reliability}
-\ccsdesc[300]{Networks~Network management}
-\ccsdesc[300]{Software and its engineering~Automated static analysis}
-\ccsdesc[300]{Software and its engineering~Domain specific languages}
-
-\printccsdesc
-
-\keywords{Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems}
+%\begin{CCSXML}
+%<ccs2012>
+%<concept>
+%<concept_id>10003033.10003068.10003073.10003075</concept_id>
+%<concept_desc>Networks~Network control algorithms</concept_desc>
+%<concept_significance>300</concept_significance>
+%</concept>
+%<concept>
+%<concept_id>10003033.10003083.10003095</concept_id>
+%<concept_desc>Networks~Network reliability</concept_desc>
+%<concept_significance>300</concept_significance>
+%</concept>
+%<concept>
+%<concept_id>10003033.10003099.10003104</concept_id>
+%<concept_desc>Networks~Network management</concept_desc>
+%<concept_significance>300</concept_significance>
+%</concept>
+%<concept>
+%<concept_id>10011007.10010940.10010992.10010998.10011000</concept_id>
+%<concept_desc>Software and its engineering~Automated static analysis</concept_desc>
+%<concept_significance>300</concept_significance>
+%</concept>
+%<concept>
+%<concept_id>10011007.10011006.10011050.10011017</concept_id>
+%<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
+%<concept_significance>300</concept_significance>
+%</concept>
+%</ccs2012>
+%\end{CCSXML}
+%
+%\ccsdesc[300]{Networks~Network control algorithms}
+%\ccsdesc[300]{Networks~Network reliability}
+%\ccsdesc[300]{Networks~Network management}
+%\ccsdesc[300]{Software and its engineering~Automated static analysis}
+%\ccsdesc[300]{Software and its engineering~Domain specific languages}
+%
+%\printccsdesc
+%
+%\keywords{Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems}
+
+\vspace{0.1in}
+\noindent
+\textbf{CCS Concepts}\\
+$\bullet$ Networks $\rightarrow$ {\em Network control algorithms; Network reliability; Network management;} 
+$\bullet$ Software and its engineering $\rightarrow$ {\em Automated static analysis; Domain specific languages}
+
+\vspace{0.1in}
+\noindent
+\textbf{Keywords}\\
+Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems
 
@@
   \centering
-  \includegraphics[width=.8\columnwidth]{figures/unimplementable}
+  \includegraphics[width=.5\columnwidth]{figures/unimplementable}
   \caption{A network where the policy $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
@@
   \includegraphics[width=.67\columnwidth]{figures/loops}
-  \caption{A Product Graph where preference inference is unsound before considering loops. Path ranks shown by nodes.}
+  \caption{A product graph where preference inference is unsound before considering loops. Path ranks shown by nodes.}
   \label{fig:avoiding-loops}
@@
 
-Consider the partial Product Graph shown in Figure~\ref{fig:avoiding-loops}.
+Consider the partial product graph shown in Figure~\ref{fig:avoiding-loops}.
 Our preference inference algorithm will determine that node $X_1$ should be locally preferred to node $X_2$ since this will result in a better (lower ranked) path to destination $A$.
@@
 
-\section*{Acknowledgments}
-
+\para{Acknowledgements}
 We thank R.
-Aditya, George Chen, and Lihua Yuan for feedback on this work and the SIGCOMM reviewers for comments on the paper.
+Aditya, George Chen, and Lihua Yuan for feedback on the work and the SIGCOMM reviewers for comments on the paper.
 This work is supported in part by the National Science Foundation award CNS-1161595.

### 2016-06-22 paper/v2/paper-edited.tex

@@
 That is, node $(W,1,1)$ is post-dominated by node $(W,-,4)$ and both are shadows of topology location $W$.
-Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$.
+%Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$.
 

### 2016-06-22 paper/v2/paper-edited.tex
making references consistent
edits section 5.1, 5.2

@@
 where $\odot$ stands for an arbitrary regular binary operator, and $r$ is a policy with a single preference.
-The compiler flags preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) as invalid.
+%
+In cases where $r$ does not contain a single preference, such as $(s ~\Prefer~ t) \cdot (u ~\Prefer~ v)$, it is not clear which of the paths $s \cdot v$ and $t \cdot u$ is preferred.
+\sysname rejects such ambiguous policies, requiring instead that operators explicitly specify which paths to prefer --- for example as $(s \cdot u) ~\Prefer~ (s \cdot v) ~\Prefer~ (t \cdot u) ~\Prefer~ (t \cdot v)$.
+%
+\sysname also rejects policies that contain preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) as invalid.
 
@@
 %The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$.
-While paths in an RIR policy describe the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated, \IE, route announcements flowing in the opposite direction.
-To capture this idea, for each regular expression $r_i$ in an RIR policy, we construct a deterministic finite state machine on the reversed regular expression.
-Each automaton for the reversed regular expression of $r_i$ is a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
+While paths in an RIR policy describe the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated --- route announcements flowing in the opposite direction.
+To capture this idea, for each regular expression $r_i$ in an RIR policy, we construct a deterministic finite state machine for the reversed regular expression.
+An automata for regular expression $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
 The alphabet $\Sigma$ consists of all abstract locations (\IE, routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
@@
 
-For a PGIR vertex $n = (l, \dots) \in V'$, we say that $n$ is a \emph{shadow} of topology location $l$, written as $\tilde{n} = l$, to indicate that the topology location for node $n$ is $l$.
+For a PGIR vertex $n = (l, \dots) \in V'$, we say that $n$ is a \emph{shadow} of topology location $l$.
+We also write $\tilde{n} = l$ to indicate that the topology location for node $n$ is $l$.
 When two PGIR nodes $m$ and $n$ shadow the same topology location (\IE, $\tilde{m} = \tilde{n}$), we write $m \approx n$.
@@
 %
-The preference function $P$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $. That is, it records the path rank of each regular expression matched in the current node.
+The preference function $P$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $. That is, it records the path rank of each automaton that has reached a final state.
 % in preferences are achieved from each policy automaton for every node in the product construction.
@@
 Aditya, George Chen, and Lihua Yuan for feedback on the work and the SIGCOMM reviewers for comments on the paper.
-This work is supported in part by the National Science Foundation award CNS-1161595.
+This work is supported in part by the National Science Foundation awards CNS-1161595 and CNS-1111520 as well as a gift from Cisco.
 

### 2016-06-23 paper/v2/paper-edited.tex
Edit name
space saving changes

@@
 \and
-Jitu Padhye\\
+Jitendra Padhye\\
   \affaddr{Microsoft}
@@
 %
-In cases where $r$ does not contain a single preference, such as $(s ~\Prefer~ t) \cdot (u ~\Prefer~ v)$, it is not clear which of the paths $s \cdot v$ and $t \cdot u$ is preferred.
+In cases where $r$ does not contain a single preference, such as $(s ~\Prefer~ t) \cdot (u ~\Prefer~ v)$, it is not clear which of the paths $s \cdot v$ or $t \cdot u$ is preferred.
 \sysname rejects such ambiguous policies, requiring instead that operators explicitly specify which paths to prefer --- for example as $(s \cdot u) ~\Prefer~ (s \cdot v) ~\Prefer~ (t \cdot u) ~\Prefer~ (t \cdot v)$.
 %
-\sysname also rejects policies that contain preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) as invalid.
+Policies that contain preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) are also rejected by \sysname as invalid.
 
@@
 
+\para{Avoiding Loops}
+
+The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available due to loops rejected by BGP.
+%BGP automatically rejects advertisements to a location where the locations is already contained in the AS path attribute.
+
+Consider the partial product graph shown in Figure~\ref{fig:avoiding-loops}.
+Our preference inference algorithm will determine that node $X_1$ should be locally preferred to node $X_2$ since this will result in a better (lower ranked) path to destination $A$.
+However, when applying Algorithm~\ref{alg:failures}, we failed to take into account the possibility of loops.
+In particular, node $A_2$ may be unusable for advertisements that go through $X_1$ since the advertisement may have already gone through $A_1$ previously.
+In this case, $X$ will have made the wrong choice since preferring $X_2$ would have resulted in a better path for the destination $A$ (a path of rank 3 instead of 4).
+
+On the other hand, this would not have been a problem if paths ending at $A_1$ had a lower rank than those ending at $A_2$ or $A_3$.
+For example, if paths ending at $A_1$ had rank 1, then any time $A_2$ is unusable due to a loop with $A_1$, it ultimately does not matter since $A_1$ is preferred anyway.
+%
+In fact, checking if we are never worse off using $A_1$ instead of $A_2$ corresponds exactly with determining if $A$ has a regret-free preference for $A_1$ over $A_2$.
+%
+More specifically, the compiler checks that, any time there are two shadows $N_1$ and $N_2$ for the same topology location, where $N_1$ appears ``above'' (\IE, can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (\IE, $N_1 <_{lp} N_2$).
+
 \begin{figure}[t!]
@@
 
-\para{Avoiding Loops}
-
-The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available due to loops rejected by BGP.
-%BGP automatically rejects advertisements to a location where the locations is already contained in the AS path attribute.
-
-Consider the partial product graph shown in Figure~\ref{fig:avoiding-loops}.
-Our preference inference algorithm will determine that node $X_1$ should be locally preferred to node $X_2$ since this will result in a better (lower ranked) path to destination $A$.
-However, when applying Algorithm~\ref{alg:failures}, we failed to take into account the possibility of loops.
-In particular, node $A_2$ may be unusable for advertisements that go through $X_1$ since the advertisement may have already gone through $A_1$ previously.
-In this case, $X$ will have made the wrong choice since preferring $X_2$ would have resulted in a better path for the destination $A$ (a path of rank 3 instead of 4).
-
-On the other hand, this would not have been a problem if paths ending at $A_1$ had a lower rank than those ending at $A_2$ or $A_3$.
-For example, if paths ending at $A_1$ had rank 1, then any time $A_2$ is unusable due to a loop with $A_1$, it ultimately does not matter since $A_1$ is preferred anyway.
-%
-In fact, checking if we are never worse off using $A_1$ instead of $A_2$ corresponds exactly with determining if $A$ has a regret-free preference for $A_1$ over $A_2$.
-%
-More specifically, the compiler checks that, any time there are two shadows $N_1$ and $N_2$ for the same topology location, where $N_1$ appears ``above'' (\IE, can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (\IE, $N_1 <_{lp} N_2$).
-
-%It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
-%even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$.
-To avoid this situation, the compiler conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the PGIR (i.e., nodes reachable from $x$ in $G_j^R$).
-It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
-
 \subsection{Aggregation-safety analysis}
@@
 Determining when this can happen requires knowledge, not only of the topology, but also of the policy.
-For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated.
+For instance, a policy might require that all traffic for a particular prefix go over a single link before being aggregated.
 If that one link fails, a black hole might be introduced.
@@
 Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.
+
+For example, recall the datacenter example from \S\ref{sec:motivation}, with the policy
+\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
+Figure~\ref{fig:aggregation-safety} shows the PGIR for \CD{PG1}.
+Since we know aggregation will occur at $X$, and that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
+We could remove the $A$--$D$--$X$ path first and woul then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none).
+Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
+Because $A$ is now disconnected from $X$, 2 is a lower bound on the number of failures required to introduce an aggregation black hole for prefix \CD{PG1}.
+This process is repeated for other aggregation locations (\EG, $Y$).
 
@@
 
-For example, recall the datacenter example from \S\ref{sec:motivation}, with the policy
-\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
-Figure~\ref{fig:aggregation-safety} shows the simplified PGIR.
-Since the compiler knows aggregation will occur at $X$, and it knows that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
-We could remove the $A$--$D$--$X$ path first.
-We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none).
-Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
-Because $A$ is then disconnected from $X$, the compiler knows that 2 is a lower bound on the number of failures required to potentially introduce an aggregation black hole for prefix \CD{PG1}.
-This process is repeated for other aggregation locations (\EG, $Y$).
-
 \subsection{Abstract BGP}
@@
 Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
-The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
+The compiler performs a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
 %Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
@@
 In the compilation example all community tags can be removed, since there is never any ambiguity based on the router importing the route and the neighbor the route is being imported from.
-Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
+After removing the communities, the two rules at router $B$ are merged into a single rule.
 
@@
 
-Even when programming the network centrally, it is possible for operators to make mistakes and write incorrect policies.
+Even when programming the network centrally, it is possible for operators to make mistakes.
 \sysname includes many analyses to identify common mistakes at compile time.
-A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if locations that should be reachable according to the policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator might accidentally anycast a prefix (\IE, originates the prefix from multiple locations), (iv) an aggregate analysis to find aggregates that do not summarize any specific prefix.
+A subset includes: (i) a preference analysis to determine when backup paths will never be used, (ii) a reachability analysis to check if locations that should be reachable according to the policy are not reachable after combining the topology and policy, (iii) an anycast analysis to find instances where the operator might accidentally anycast a prefix (\IE, originates the prefix from multiple locations), (iv) an aggregate analysis to find unused aggregates that do not summarize any specific prefix.
 
@@
 The datacenter operator said that he found the language intuitive.
-The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We further found that the datacenter policies were correctly translated.
+The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.}
+%We further found that the datacenter policies were correctly translated. 
 For the backbone network, the operator mentioned an additional policy not present in the English document, which we added later.
 %
-For both the datacenter and backbone networks, the \sysname compiler was able to guarantee policy-compliance under all possible failure scenarios.
+For both the datacenter and backbone networks, \sysname was able to guarantee policy-compliance under all possible failure scenarios.
 
@@
 Figure~\ref{fig:compilation-times} shows the compilation times for datacenter and backbone networks of different sizes.
-For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on predicates in parallel.
+For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on each predicate in parallel.
 A single predicate can describe many prefixes, for example by matching on a disjunction of prefixes.
@@
 
-Total compilation for the largest datacenter is less than 9 minutes total.
-Unlike the datacenter policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases.
-Compilation for the largest backbone network, takes less than 3 minutes total.
+Compilation for the largest datacenter takes less than 9 minutes total.
+Unlike the datacenter policy, the number of predicates for the backbone policy remains relatively fixed as the topology size increases.
+Compilation for the largest backbone network takes less than 3 minutes total.
 The inclusion of both more preferences and more neighboring ASes in the backbone policy increases the size of the resulting PGIR, which in turn leads to PGIR construction and minimization taking proportionally more time.
@@
 
-We comment briefly on how \sysname-generated configurations differ from configurations or templates written by operators.
-%
-In some ways, \sysname configurations are similar.
+We comment briefly on how \sysname-generated configurations differ from configurations written by operators.
+%
+In some ways they are similar.
 For example, preferences among neighboring ASes are implemented with a community value to tag incoming routes according to preference, which is then used at other border routers to influence decisions.

### 2016-06-23 paper/v2/paper-edited.tex
reduced to 14 pages

@@
 
-To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR.
+For each router $r$, the compiler sets a higher local preference for neighbors of a more-preferred PGIR node for $r$.
 For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
@@
 After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
-In the compilation example all community tags can be removed, since there is never any ambiguity based on the router importing the route and the neighbor the route is being imported from.
-After removing the communities, the two rules at router $B$ are merged into a single rule.
+In the ABGP policy shown in Figure~\ref{fig:abgp-config}, all community tags can be removed, since there is never any ambiguity as to the current state of the PGIR based only on the current router importing the route and the neighbor from which the route is being imported.
 
@@
   \Router{B}
-    Match \PEER = C, \COMM = (-,2)
-      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
-             \MED \Arrow 81, \PEER \Arrow W
-    Match \PEER = C, \COMM = (3,2)
+    Match \PEER = C, \COMM = (-,2) or (3,2)
       Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
@@
 languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire},
-as well as path queries~\cite{queries}.
-Each of these languages is oriented around regular expressions, which
-describe paths through a network, and predicates, which classify packets.
-In particular, FatTire allows programmers to define sets of paths together
+and path queries~\cite{queries}.
+Each of these languages uses regular expressions to
+describe paths through a network and predicates to classify packets.
+In particular, FatTire allows programmers to define sets of paths
 with a fault tolerance level (\IE, tolerate 1 or 2 faults)
@@
 at the cost of generating additional rules that tax switch memory.
-In contrast, \sysname relies on distributed
-control plane mechanisms to react to faults, which do not have additional memory cost.
+In contrast, \sysname relies on distributed control plane mechanisms to react to faults, which do not have additional memory cost.
 Because of the differences in the underlying technology, the analyses
@@
 In the past, researchers have tried to tackle this problem by analyzing existing
-firewall configurations~\cite{fang,lumeta,margrave} and
+%firewall configurations~\cite{fang,lumeta,margrave} and
 router configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe,arc} and reporting errors or inconsistencies when they are detected.
@@
 languages and a ``correct-by-construction''
-methodology.  By proposing that network administrators write configurations
-at a high-level of abstraction, a whole host of low-level errors can be avoided and policy implementation can be simplified.
+methodology. Writing configurations at a high level of abstraction simplifies policy implementation and prevents a whole host of low-level errors.
+%By proposing that network administrators write configurations
+%at a high-level of abstraction, a whole host of low-level errors can be avoided and policy implementation can be simplified.
 
@@
 We introduced \sysname, a language and compiler for implementing network-wide policies using a distributed set of devices running BGP.
-Propane allows operators to describe their policy naturally through high-level constraints on both the shape and relative preferences of paths for different types of traffic.
-When \sysname compiles a policy, the resulting BGP configurations are guaranteed to faithfully implement the centralized policy in a purely distributed fashion, regardless of any number of network failures.
-Applying \sysname to real-world networks showed that its language is expressive and its compiler is scalable.
+Propane allows operators to describe their policy through high-level constraints on both the shape and relative preferences of paths for different types of traffic.
+When \sysname compiles a policy, the resulting BGP configurations are guaranteed to
+%remain policy-compliant
+implement the centralized policy in a distributed fashion, 
+regardless of any number of network failures. Applying \sysname to real-world networks showed that its language is expressive and its compiler is scalable.
 

### 2016-06-23 paper/v2/paper-edited.tex
update with copyright information
fix heading capitalization and spelling mistakes

@@
 
+\CopyrightYear{2016} 
 \setcopyright{acmcopyright}
-\conferenceinfo{SIGCOMM '16}{August 22--26, 2016, Florianopolis, Brazil}
+\conferenceinfo{SIGCOMM '16,}{August 22-26, 2016, Florianopolis , Brazil}
+\isbn{978-1-4503-4193-6/16/08}\acmPrice{\$15.00}
+\doi{http://dx.doi.org/10.1145/2934872.2934909}
 
@@
 
-\para{Problem Formulation}
+\para{Problem formulation}
 
@@
 
-\para{Regret-free Preferences}
+\para{Regret-free preferences}
 To order PGIR shadows ($\leq_{lp}$) for each router in a way that is policy-compliant under all failures, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
@@
 
-\para{A Preference Inference Algorithm}
+\para{A preference inference algorithm}
 
@@
 
-\para{Avoiding Loops}
+\para{Avoiding loops}
 
@@
 Since we know aggregation will occur at $X$, and that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
-We could remove the $A$--$D$--$X$ path first and woul then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none).
+We could remove the $A$--$D$--$X$ path first and would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none).
 Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
@@
 
-\para{Acknowledgements}
+\para{Acknowledgments}
 We thank R.

### 2016-06-23 paper/v2/paper-edited.tex
final edits

@@
 %Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.
-Line 3 applies to any other traffic not matching \CD{PCust} and allows the traffic to leave through any direct neighbor with the usual preferences of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
+Line 3 applies to any other traffic not matching \CD{PCust} and allows the traffic to leave through any direct neighbor with the usual preference of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
 To summarize our progress, the \CD{Routing} policy
@@
 \noindent
-The \CD{NoTrans} constraint requires that all traffic not follow a path that transits the network between \CD{Peer} and \CD{Prov}.
+The \CD{NoTrans} constraint requires that all traffic not follow a path that transits our network between \CD{Peer} and \CD{Prov}.
 Additionally, it prevents traffic from ever following paths that leave our network and later go through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
@@
 A policy has one or more constraints.
-The first kind of constraint is a test on the type of route and a corresponding set of preferred regular paths or a control constraint.
+The first kind of constraint is a test on the type of route and a corresponding set of preferred regular paths.
 Regular paths are regular expressions where the base characters are abstract locations representing either a router or an external AS.
 Special \In{} and \Out{} symbols refer to any internal or external location respectively.
-In addition, $\Sigma$ refers to any symbol.
+In addition, $\Sigma$ refers to any location.
 We also use the standard regular expression abbreviation $r^+$ for $r \cdot r^*$, a sequence of one or more occurrences of $r$.
-Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisements with a particular community value (\IE, an integer value associated with a path).
+Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisements with a particular community value attached (\IE, an integer value associated with a path).
 %% For example, the constraint
@@
 
-The next step rewrites the high-level constraints such as $\Enter$ according to the equivalences in Figure~\ref{fig:rir-syntax}.
+The next step rewrites the high-level constraints such as $\Exit$ according to the equivalences in Figure~\ref{fig:rir-syntax}.
 Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression.
-For example, the regular expression $r \cdot (s \Prefer t) \cdot u$ is lifted to $(r \cdot s \cdot u) \Prefer (r \cdot t \cdot u)$ by distributing the preference over the sequence operator.
+For example, the regular expression $r \cdot (s ~\Prefer~ t) \cdot u$ is lifted to $(r \cdot s \cdot u) \Prefer (r \cdot t \cdot u)$ by distributing the preference over the sequence operator.
 In general, we employ the following distributivity equivalences:
@@
 The ``--" state indicates the corresponding automaton cannot accept the current path or any extension of it. Since
-node $(W,5,-)$ is in an accepting state for the first automaton, it indicates that this path has preference 1.
+node $(W,5,-)$ is in an accepting state for the first automaton, it indicates that this path has rank 1.
 
@@
 To make matters worse, the second preference for the path $A \cdot C \cdot D \cdot F \cdot G$ is available in the network but not being used.
-Thus, a path for the best possible route available exists in the network but is not being used by the distributed implementation.
+Thus, a path for the best possible route available after the A--B failure exists in the network, but the distributed implementation will not find it.
 %
@@
 %
-The compiler must determine a \emph{total ordering} of shadow nodes for each router, which reflects the relative preference of advertisements received in each shadow and should be consistent with path ranks in routing policy.
+The compiler must determine a \emph{total ordering} of shadow nodes for each router, which reflects the relative preference of advertisements received in each shadow and should be consistent with path ranks.
 %
@@
 $D$ and $E$ tag their advertisements to let $C$ know which shadow sent the advertisement.
-\$\ref{sec:abgp} discusses tagging in detail.
+Section \ref{sec:abgp} discusses tagging in detail.
 
@@
 
-For example, recall the datacenter example from \S\ref{sec:motivation}, with the policy
+Recall the datacenter example from \S\ref{sec:motivation}, with the policy
 \CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
@@
 It includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the no-export community, as well as for ensuring at least k-failure safety for aggregate prefixes.
-Since each prefix has a separate routing policy, we compile each routing policy in parallel.
+Since each predicate has a separate routing policy, we compile each routing policy in parallel.
 Currently, \sysname supports generating Quagga router configurations out of the box.

### 2016-07-20 paper/abstraction/paper.tex
adding initial abstraction paper outline

\documentclass{sig-alternate-10pt}
%\documentclass[10pt]{sigalternate052015}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{url}
\usepackage{times}
\usepackage{xspace}
\usepackage{listings}
\usepackage{code}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning}
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{balance}
\usepackage[ampersand]{easylist}

\definecolor{princetonorange}{RGB}{255,143,0}
\definecolor{tmlblue}{RGB}{0,58,120}  % tmlblue == Toronto Maple Leafs Blue!

\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\newcommand{\ratul}[1]{\textcolor{blue}{[ratul: #1]}}
\newcommand{\ryan}[1]{\textcolor{green}{[ryan: #1]}}
\newcommand{\dpw}[1]{\textcolor{tmlblue}{[dpw: #1]}}
\newcommand{\todd}[1]{\textcolor{princetonorange}{[todd: #1]}}

\newcommand{\EG}{\emph{e.g.}}
\newcommand{\IE}{\emph{i.e.}}
\newcommand{\ETC}{\emph{etc.}}
\newcommand{\ETAL}{\emph{et al.}}

\newcommand{\sysname}{{\small \sf Diesel}\xspace}

\newcommand{\para}[1]{\paragraph*{\textbf{#1}}}

\newcommand{\set}[1]{\ensuremath{\{ #1 \} }}
\newcommand{\abs}[1]{\ensuremath{ \lvert #1 \rvert }}

\newcommand{\CD}[1]{\texttt{\small #1}}  % code font
\newcommand{\KW}[1]{\texttt{\small\bfseries{#1}}}

\newcommand{\True}{\CD{true}}
\newcommand{\Define}{\KW{define}}
\newcommand{\Prefer}{\texttt{>>}}
\newcommand{\Path}{\texttt{=>}}
\newcommand{\Link}{\texttt{->}}
\newcommand{\Agg}{\KW{agg}}
\newcommand{\Any}{\KW{any}}
\newcommand{\None}{\KW{drop}}
\newcommand{\In}{\KW{in}}
\newcommand{\Out}{\KW{out}}
\newcommand{\AND}{\texttt{\&}}
\newcommand{\OR}{\texttt{|}}
\newcommand{\NOT}{\texttt{!}}
\newcommand{\Intersect}{\ensuremath{\cap}}
\newcommand{\Union}{\ensuremath{\cup}}

\newcommand{\Exit}{\KW{exit}}
\newcommand{\End}{\KW{end}}
\newcommand{\Start}{\KW{start}}
\newcommand{\Enter}{\KW{enter}}
\newcommand{\Later}{\KW{later}}
\newcommand{\Before}{\KW{before}}
\newcommand{\Internal}{\KW{internal}}
\newcommand{\Never}{\KW{never}}
\newcommand{\Only}{\KW{only}}
\newcommand{\Through}{\KW{through}}
\newcommand{\LinkKW}{\KW{link}}
\newcommand{\PathKW}{\KW{path}}
\newcommand{\Novalley}{\KW{novalley}}

\renewcommand{\path}[2]{ #1 \mapsto \ensuremath{#2} }

\begin{document}

%\CopyrightYear{2016} 
%\setcopyright{acmcopyright}
%\conferenceinfo{SIGCOMM '16,}{August 22-26, 2016, Florianopolis , Brazil}
%\isbn{978-1-4503-4193-6/16/08}\acmPrice{\$15.00}
%\doi{http://dx.doi.org/10.1145/2934872.2934909}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\title{Abstraction Compilation Techniques}

%\author{Paper \#324, 14 pages}

\author{%
Ryan Beckett\\
  \affaddr{Princeton}
  %\\
  %\email{rbeckett@princeton.edu}
\and
Ratul Mahajan\\
  \affaddr{Microsoft}
  %\\
  %\email{ratul@microsoft.com}
\and
Todd Millstein\\
  \affaddr{UCLA}
  %\affaddr{University of California, Los Angeles}
  %\\
  %\email{todd@cs.ucla.edu}
\and
Jitendra Padhye\\
  \affaddr{Microsoft}
  %\\
  %\email{padhye@microsoft.com}
\and
David Walker\\
  \affaddr{Princeton}
  %\\
  %\email{dpw@princeton.edu}
}

\maketitle

%=====================================================
%
%
%  **Abstract**
%
%
%=====================================================

% Points to make
%
% (1) Lets operators think about topologies/policies at a high-level of abstraction
%     - matches current thinking (e.g., templates)
%
% (2) Promotes a correct-by-construction methodology
%
%     properties that hold over abstract topologies hold over concrete ones
%      - includes correct forwarding behavior
%      - includes reachability (under k-failures)
%
% (3) Enables reusability (e.g., across datacenters) and expansion (e.g., within a datacenter)
%
% (4) lets us scale compilation/algorithms to large-scale topologies

\textbf{Abstract---}
We develop \sysname, a tool for automated reasoning about end-to-end properties of abstract network topologies. \sysname allows network operators to write a centralized routing policy over a high-level abstraction of their network topology. From such a specification, it generates a distributed collection of BGP router configurations that are guaranteed to implement the centralized routing policy for any concrete instantiation of the abstract topology, and for any combination of network failures in the resulting concrete topology.
%
Additionally, properties proven by \sysname over the abstract topology, such as reachability between a source and destination under k-failures, are also guaranteed to hold under any concrete instantiation of the abstract topology.
%
These strong guarantees allow operators to reason about the routing behavior of their network at a high-level abstraction, while also generating an efficient low-level implementation.
%
In addition, operators are able to safely change or expand their network in any way, so long as the new resulting topology also respects the abstraction.
%
We test \sysname out on ... blah blah blah

%=====================================================
%
%
%  **Keywords**
%
%
%=====================================================

%\vspace{0.1in}
%\noindent
%\textbf{CCS Concepts}\\
%$\bullet$ Networks $\rightarrow$ {\em Network control algorithms; Network reliability; Network management;} 
%$\bullet$ Software and its engineering $\rightarrow$ {\em Automated static analysis; Domain specific languages}

%\vspace{0.1in}
%\noindent
%\textbf{Keywords}\\
%Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems

%=====================================================
%
%
%  **Introduction**
%
%
%=====================================================

\section{Introduction}
\label{sec:introduction}

\begin{easylist}[itemize]
& Network configuration is difficult/error-prone. Operators think of policy at 
  a high level of abstraction, yet implementations:
&& Often configs must be decomposed device-by-device
&& Often need to create reusable configurations for different topologies/policies
&& Ensure different devices/networks kept consistent when policy changes

& Current state of the art is to capture abstractions using parameterized 
  device templates. The same templates can then be reused across multiple 
  devices. Unfortunately, existing template systems have many limitations
&& Templates often still require the operator to reason about network-wide 
   policy device-by-device.
&& Templates do not provide any guarantees of configuration correctness, 
   instead requiring the operator to manually reason about forwarding for 
   any possible concrete network
&&& In addition, operators must reason about possible network failures that
    might arise in one concrete network versus another

& To this end, we develop a language called \sysname to simplify the operators task.
&& \sysname allows the operator to define high-level network abstractions to reflect
   the operator's mental model, and then to write a centralized routing policy over the
   abstraction.
&& We develop an intermediate graph-based representation for compiled, abstract policies,
   and show how to compile \sysname policies to this representation. 
&& We develop several algorithms that operate over this graph representation and verify 
   if properties, such as reachability or no black holes under k-failures, are guaranteed
   to hold under any possible concrete instantiation of the network.
&& As a major use-case, we show how the compilation and failure-safety analysis
   of the Propane configuration-synthesis tool can be extended over abstract topologies.
   Explain what Propane is first...
   Our major result is an abstraction theorem, which states that ...
   The result is that policies compiled with the Propane compiler to distributed configurations 
   are guaranteed to have correct forwarding behavior for any possible concrete instantiation 
   of the network, and for any possible combination of failures in the given concrete network.
&&& Finally, we show how abstract compilation makes it possible to dramatically speed up compilation 
    time for the Propane policies, ...
\end{easylist}

%It is well known that configuring networks is error
%prone and that such errors can lead to disruptive
%downtimes~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
%For instance, a recent misconfiguration led to an hour-long, nation-wide outage for Time Warner's backbone network~\cite{time-warner}; and a major BGP-related incident makes international news every few months~\cite{bgpmon}.%

%A fundamental reason for the prevalence of misconfigurations is the
%semantic mismatch between the intended high-level
%policies and the low-level configurations.
%Many policies involve network-wide properties---prefer a certain neighbor,
%never announce a particular destination externally,
%use a particular path only if another fails---but configurations describe the behavior of
%individual devices.
%%
%Operators must manually decompose network-wide policy into
%device behaviors, such that policy-compliant behavior results from the distributed interactions of
%these devices.
%%
%Policy-compliance must be ensured not only under normal
%circumstances but also during failures.  The need to reason
%about all possible failures exacerbates the challenge
%for network operators.  As a result, configurations that work
%correctly in failure-free environments have nonetheless been found to violate key
%network-wide properties when failures occur~\cite{batfish}.%

%To reduce configuration errors, operators are increasingly adopting an
%approach in which common tasks are captured as parameterized templates~\cite{hatch,thwack}.
%%
%While templates help ensure certain kinds of consistency across devices,
%they do not provide fundamentally different abstractions from existing configuration languages
%or bridge the semantic divide between network-wide policies and device-level configuration.
%Thus, they still require operators to
%manually decompose policies into device behaviors.%

%As a complementary approach, configuration analysis tools can help reduce misconfigurations by checking if low-level configurations match high-level policy~\cite{batfish,feamster+:rcc}. However, such tools cannot help operators with the challenging task of generating configurations in the first place.%

%Software-defined networking (SDN) and its abstractions
%are, in part, the research
%community's response to the difficulty of maintaining policy
%compliance through distributed device interactions~\cite{ethane}.
%Instead of organizing networks around a distributed
%collection of devices that compute forwarding tables through
%mutual interactions, the devices are told how to
%forward packets by a centralized controller. The controller is responsible for ensuring that the
%paths taken are compliant with operator specifications.%

%The centralized control planes of SDN, however, are not a panacea.
%First, while many SDN programming systems~\cite{sdn-languages} provide effective \emph{intra}-domain routing
%abstractions, letting users specify paths within their network,
%they fail to provide a coherent means to specify \emph{inter}-domain routes.
%Second, centralized control planes
%require careful design and engineering to be robust to failures---one must ensure that all devices can communicate with the controller at all times, even under arbitrary failure combinations. Even ignoring failures, it is necessary for the control system to
%scale to meet the demands of large or geographically-distributed networks,
%and to react quickly
%to environmental changes. For this challenge, researchers are exploring
%multi-controller systems with interacting controllers, thus bringing back distributed
%control planes~\cite{mccauley2013extending,onos} and their current programming difficulties.%

%Hence, in this paper, we have two central goals:
%\begin{enumerate}
%\item Foo
%\item Bar
%\end{enumerate}

%=====================================================
%
%
%  **Motivation**
%
%
%=====================================================

\section{Motivation}
\label{sec:motivation}

%\begin{figure}[t!]
%  \centering
%  \includegraphics[width=\columnwidth]{figures/example2}
%  \caption{Policy-compliance under failures is difficult.}
%  \label{fig:example2}
%  \vspace{-1em}
%\end{figure}

\subsection{Example:  The datacenter}

\begin{easylist}[itemize]
& Example of a datacenter with two peers (running BGP).
&& Each tier of the datacenter treats traffic the same
&& Since each tier will treat traffic the same, operator would like to
   avoid writing a separate configuration for each device in a given tier.
&& Operator writes 3 templates (show example of templates, including filters).

& Show example of aggregation-induced black hole
\end{easylist}

%=====================================================
%
%
%  **Propane Language**
%
%
%=====================================================

\section{Propane overview}
\label{sec:propane}

\subsection{Example: The datacenter}

\begin{easylist}[itemize]
& Abstraction of datacenter tiers -- provided by a map from
  nodes in the concrete network to nodes in the abstract network.
  Also provide node and edge constraints.
&& Thus, the new topology contains only those 3 abstract nodes.
&& Rather than writting templates for each device, the operator 
  writes a centralized routing policy for the network (show propane policy)

& Show generated templates from compilation (e.g., use of network-wide abstraction)

& Show example of aggregation safety checking in the abstract network --
  just give the answer + forward reference (matches with concrete example).

& Suppose now we wanted to expand this network, or configure a similar network...
\end{easylist}

\subsection{Language}

Placeholder for formal language definition

%\sysname lets operators configure the network with the
%abstraction that they have centralized control over routing.
%Specifically, the operator simply provides a set of high-level constraints
%that describe the
%paths traffic should---or should not---take and their relative preferences.
%\sysname specifications are written modularly via a series
%of declarations.
%For example, to begin specification of the backbone
%network from the previous section, we first express the idea that
%we prefer that traffic leave the network through \CD{R1} over \CD{R2} (to \CD{Cust}) over \CD{Peer} over \CD{Prov} (policy P1 and P3 from Figure~\ref{fig:example1}):
%%
%\begin{code}
%\Define Prefs = \Exit(R1 \Prefer R2 \Prefer Peer \Prefer Prov)
%\end{code}
%This  statement defines a set of \emph{ranked paths}, which includes
%all paths (and only those paths) for which traffic exits our network
%through either router \CD{R1}, router \CD{R2}, \CD{Peer}, or \CD{Prov}.
%The paths that exit through \CD{R1}
%are preferred (\Prefer) to those that exit through \CD{R2}, which are preferred to those that
%leave through \CD{Peer} and then \CD{Prov}.  As we
%describe in the next section, the \Exit\ expression, as well as other
%path expressions used later in this section, is simply a shorthand for
%a particular regular expression over paths that is expressible in our policy
%language. The preference operator (\Prefer) is flexible and can be used between constraints as well as among individual routers. For example, the above constraint could have been written equivalently as
%\Exit(\CD{R1}) \Prefer \ldots \Prefer ~\Exit(\CD{Prov})%

%To associate ranked paths with
%one or more prefixes, we define a \sysname \emph{policy}.
%Within a policy, statements with the form $t\;$\Path$\;p$
%associate the prefixes defined by the predicate $t$ with the set of
%ranked paths defined by the path expression $p$.  In general,
%prefix predicates can be defined by arbitrary boolean combinations
%(and, or, not) of concrete prefixes and community tags.  Here,
%we assume we have already defined the predicate \CD{PCust} for the
%customer prefixes.
%%
%In the following code, ranked paths are associated with
%customer prefixes,
%and all other prefixes (\CD{true}). Policy statements are processed in
%order with earlier policy statements taking precedence over later
%policy statements. Hence, when the predicate \True{} follows
%the statement involving \CD{PCust}, it is interpreted as
%\CD{\True{} \AND{} \NOT{}PCust}.%
%

%\begin{code}
%\Define Routing =
%    \{PCust \Path Prefs \AND \End(Cust)
%     \True  \Path Prefs \}
%\end{code}
%\noindent%

%Line 2 of this policy
%restricts traffic destined to known customer prefixes (\CD{PCust}) to only follow paths that end at the customer. In addition, it enforces the network-wide preference that traffic leaves through \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
%%
%Line 3 applies to any other traffic not matching \CD{PCust} and allows the traffic to leave through any direct neighbor with the usual preference of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}. To summarize our progress, the \CD{Routing} policy
%implements P1, P3, and P4 from Figure~\ref{fig:example1}.%
%

%Since, routing allows transit traffic by default (\EG, traffic entering from
%\CD{Peer} and leaving through \CD{Prov}), we separately define a
%policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
%disjunction (\OR) and negation (\NOT) of constraints.
%First, we create reusable abstractions for describing traffic that transits our network. In \sysname, this is done by creating a new parameterized definition.
%\begin{code}
%\Define transit(X,Y) = \Enter(X{\OR}Y) \AND \Exit(X{\OR}Y)
%\Define cust-transit(X,Y) = \Later(X) \AND \Later(Y)
%\end{code}
%\noindent
%Here we define transit traffic between groups of neighbors $X$ and $Y$ as traffic that enters the network through some neighbor in $X$ or $Y$ and then also leaves the network through some neighbor in either $X$ or $Y$. Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network. Using these two new abstractions, we can now implement policies P2 and P5 with the following constraint.%

%\begin{code}
%\Define NoTrans =
%  \{\True \Path \NOT{}transit(Peer,Prov) \AND
%           \NOT{}cust-transit(Cust,Prov)\}
%\end{code}
%\noindent
%The \CD{NoTrans} constraint requires that all traffic not follow a path that transits our network between \CD{Peer} and \CD{Prov}.
%Additionally, it prevents traffic from ever following paths that leave our network and later go through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
%and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.%

%Collectively, the constraints above capture the entire policy. From them, our compiler will generate per-device import and export filters, local preferences,
%MED attributes, and community tags to ensure that the policy is
%implemented correctly under all failures.%
%

%Our datacenter example network has three main concerns:
%(1) traffic for the prefix allocated to each top-of-rack router must be able to reach that router,
%(2) local services must not leak outside the datacenter, and
%(3) aggregation must be performed on global prefixes to reduce churn
%in the network.%

%\sysname allows modular specification of each of these constraints. The first constraint is about prefix ownership---we want traffic only for certain prefixes to end up at a particular location. The following definition captures this intent.%
%

%\begin{code}
%\Define Ownership =
%    \{PG1 \Path \End(A)
%     PG2 \Path \End(B)
%     PL1 \Path \End(E)
%     PL2 \Path \End(F)
%     \True \Path \End(\Out)\}
%\end{code}
%\noindent
%This definition says that traffic for prefix \CD{PG1} is allowed to follow only paths that
%end at router \CD{A}; traffic for \CD{PG2},
%but not \CD{PG1}, must
%end at router \CD{B}; and so on.
%Any traffic destined for a prefix that is not a part of the datacenter should be allowed to leave the datacenter and end at some external location, which is otherwise unconstrained.
%The special keyword \Out{} matches any location outside the datacenter network, while the keyword \In{} will match any location inside the network.%

%For the second constraint, we define another policy:%

%\begin{code}
%\Define Locality =
%    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
%\end{code}
%\noindent
%%
%This definition says that traffic for local
%prefixes only follows paths that are internal to the network at each hop.
%This constraint guarantees that the services remain accessible only to locations
%inside the datacenter.%

%As in the backbone example, we can logically conjoin these constraints
%to specify the network-wide policy.
%However, in addition to constraints on the shape of paths,
%\sysname allows the operator to specify constraints on the BGP control plane itself.
%For instance, a constraint on aggregation is included to ensure that
%aggregation for global prefixes is performed from
%locations inside (\In) the network to locations outside (\Out).
%In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG}
%(which we assume is defined earlier)
%when advertised outside the datacenter.%

%\begin{code}
%Ownership \AND{} Locality \AND{} \Agg(PG, \In \Link \Out)
%\end{code}%

%Once \sysname compiles the policy, it is guaranteed to remain compliant under all possible failure scenarios, modulo any aggregation-induced black holes. In the presence of aggregation, the \sysname compiler will also efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.

%=====================================================
%
%
%  **Abstractions**
%
%
%=====================================================

\section{Abstraction}
\label{sec:abstraction}

\begin{easylist}[itemize]
& Define abstractions more formally,
&& e.g., homomorphism between graphs + node/edge constraints

& Give formal semantics of abstract, labelled graph
&& i.e., if a concrete graph + homomorphism is valid
   given an abstract, labelled graph

\end{easylist}

%=====================================================
%
%
%  **Compilation**
%
%
%=====================================================

\section{Compilation}
\label{sec:compilation}

We borrow the intermediate graph-based representation from Propane:

\begin{easylist}[itemize]
& Show compilation from language to RIR

& Show compilation from RIR to Product Graph
&& Note that preferences are general, and it could potentially
   use any implementation (including SDN). But for the sake of 
   simplicity, we will assume a BGP backend like Propane.

& Use the datacenter example from before
&& First define the concretization function for translating the abstract policy
   into the concrete policy
&& Next, show the Product Graphfor both the concrete and abstract policies.

& Show/Define safety analysis simulation relation for both concrete and abstract product graphs
  and how it holds for both.
&& Theorem: if safety analysis holdls in the abstract graph, it holds for the concrete one,
   and the preferences are consistent.

& Show/Define compilation to abstract BGP policies. Give concretization function,
  and compilation definition.

& Give abstraction theorem: commuting of concretization and compilation
\end{easylist}

%The examples above use what we call the front end (FE) of \sysname.
%It simplifies operators' task of describing preferred paths, but that simplicity comes at the cost of compilation complexity. The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology and ensure policy compliance under all failure scenarios.%

%\begin{figure}[t!]
%  \centering
%  \includegraphics[width=.75\columnwidth]{figures/pipeline}
%  \caption{Compilation pipeline stages for Propane.}
%  \label{fig:pipeline}
%  \vspace{-1em}
%\end{figure}%

%% grammar
\newcommand{\BNFALT}{\;\;|\;\;}
\newcommand{\hdr}[2]{\flushleft \chdr{\hspace{5mm}#1}{#2}}
\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}%

%\begin{figure*}[t]\small
%  \begin{minipage}[t]{.45\linewidth}
%  \hdr{Syntax}{}
%  \vspace*{-1\baselineskip}
%  %
%  \[ \begin{array}{rclr}
%    \hline%

%     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
%     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
%     x       &::=& d.d.d.d/d & \textit{prefix} \\
%     t       &::=& \True & \textit{true} \\
%         &\BNFALT& \NOT t & \textit{negation} \\
%         &\BNFALT& t_1 \OR{} t_2 & \textit{disjunction} \\
%         &\BNFALT& t_1 \AND{} t_2 & \textit{conjunction} \\
%         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
%         &\BNFALT& \textit{comm} = d & \textit{community test} \\
%     r       &::=& l & \textit{location} \\
%         &\BNFALT& \emptyset & \textit{empty set} \\
%         &\BNFALT& \In & \textit{internal loc} \\
%         &\BNFALT& \Out & \textit{external loc} \\
%         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
%         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
%         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
%         &\BNFALT& \NOT r & \textit{path negation} \\
%         &\BNFALT& r^* & \textit{iteration} \\
%     ln       &::=& r_1 \rightarrow r_2 & \textit{links} \\
%     cc     &::=& agg(x, ln) \BNFALT tag(d, t, ln) & \textit{control constraints} \\
%  \end{array} \]%

%  \end{minipage}
%  %
%  ~~
%  \vrule
%  ~~
%  %
%  \begin{minipage}[t]{.5\linewidth}\small
%  \hdr{Propane Expansions}{}
%  \vspace*{-1\baselineskip}
%  %
%  \[\begin{array}{rcl}
%    \hline
%    \Any           & = & \Out^* \cdot \In^+ \cdot \Out^* \\
%    \None          & = & \emptyset \\
%    \Internal      & = & \In^+ \\
%    \Only(X)       & = & \Any \cap X^* \\
%    \Never(X)      & = & \Any \cap (!X)^* \\
%    \Through(X)    & = & \Out^* \cdot \In^* \cdot X \cdot \In^* \cdot \Out^* \\
%    \Later(X)      & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
%    \Before(X)     & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
%    \End(X)        & = & \Any \cap (\Sigma^* \cdot X) \\
%    \Start(X)      & = & \Any \cap (X \cdot \Sigma^*) \\
%    \Exit(X)       & = & (\Out^* \cdot \In^* \cdot (X \cap \In) \cdot \Out \cdot \Out^*) \cup \\
%                  &        & (\Out^* \cdot \In^+ \cdot (X \cap \Out) \cdot \Out^*) \\
%    \Enter(X)      & = & (\Out^* \cdot \Out \cdot (X \cap \In) \cdot \In^* \cdot \Out^*) \cup \\
%                  &        & (\Out^* \cdot (X \cap \Out) \cdot \In^+ \cdot \Out^*) \\
%    \LinkKW(X,Y)     & = & \Any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
%    \PathKW(\vec{X}) & = & \Any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
%    \Novalley(\vec{X}) & = & \Any ~ \cap \\
%                  &   & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
%                  &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
%  \end{array} \]%

%  \end{minipage}%

%  \hrulefill%

%  \caption{Regular Intermediate Representation (RIR) syntax (left), and
%           Propane language expansions (right).}
%  \label{fig:rir-syntax}
%  %\vspace{-1em}
%\end{figure*}%

%To handle these challenges, we decompose compilation into multiple stages, shown in  Figure~\ref{fig:pipeline}, and develop efficient algorithms for the translation between stages. The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR). Policies in RIR are checked well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the topology to obtain the Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines safety, it translates the PGIR to an abstract BGP (ABGP) representation. ABGP can then be translated into various vendor-specific device
%configurations as needed.

%The \sysname FE is just a thin layer atop the RIR for describing preference-based path constraints.
%Figure~\ref{fig:rir-syntax} shows the RIR syntax. A policy has one or more constraints. The first kind of constraint is a test on the type of route and a corresponding set of preferred regular paths. Regular paths are regular expressions where the base characters are abstract locations representing either a router or an external AS. Special \In{} and \Out{} symbols refer to any internal or external location respectively. In addition, $\Sigma$ refers to any location. We also use the standard regular expression abbreviation $r^+$ for $r \cdot r^*$, a sequence of one or more occurrences of $r$. Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisements with a particular community value attached (\IE, an integer value associated with a path).%
%

%\sysname also supports constraints on the control-plane behavior of BGP. For example, prefix aggregation is an important optimization to reduce routing table size. A constraint of the form $agg(x,ln)$ tells the compiler to perform aggregation for prefix $x$ across all links described by $ln$. It is also often useful to be able to add community tags to exported routes in BGP (\EG, to communicate non-standard information to peers). A constraint of the form $tag(d,t,ln)$ adds community tag $d$ for any prefixes matching $t$ across links $ln$.
%%
%We list only the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, but \sysname also supports other constraints such as limiting the maximum number of routes allowed between ASes, or enabling BGP multipath.

%\para{Semantics}

%We give a semantics to RIR programs using sets of ranked paths. Each path constraint $r_1 \Prefer \dots \Prefer r_j$ denotes a set of ranked network paths. A network path is a topologically valid string of abstract locations $l_1 l_2 \dots l_k$. We use the notation $\abs{p}$ to denote the length of the path $p$. A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$, that is, the path is in the language of the regular expression. Paths are ranked lexicographically according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the path length. Lower ranks indicate \emph{more} preferred paths. More formally, a path $p$ has rank:
%$$(\min_i \set{ p \in \mathcal{L}(r_i) }, \abs{p})$$
%%
%The set of ranked paths depends on which paths are valid in the topology, and thus when failures occur, the most preferred routes change.
%%
%For any source $s$ and destination $d$, \sysname will send traffic along the highest ranked available path from $s$ to $d$.

%\para{From FE to RIR}

%The first stage in \sysname compilation reduces the FE to the simpler RIR from Figure~\ref{fig:rir-syntax}.
%The main differences between the FE and RIR are: $i)$ FE allows the programmer to specify constraints using a series of (modular) definitions, and combine them later, $ii)$ FE provides high-level names that abstract sets of routes and groups of prefixes/neighbors, and $iii)$ FE allows the preference operator to be used more flexibly.%

%A key constraint when translating FE to RIR is ensuring that all specified routes are well-formed. In particular, each regular path constraint $r$ must satisfy $r \subseteq \Out^* \cdot \In^+ \cdot \Out^*$. It ensures that users only control traffic that goes through their network at some point, and that such traffic does not loop back multiple times through their network.%

%The translation from FE to RIR is based on a set of rewriting rules.
%The first step merges separate constraints. It takes the cross product of per-prefix constraints, where logical conjunction ($r_1 ~\AND~ r_2$) is replaced by intersection on regular constraints ($r_1 \Intersect r_2$), logical disjunction is replaced by union, and logical negation ($\NOT r$) is replaced by path negation ($\Any \cap \NOT(r)$). The additional constraint $\Any$ ensures the routes are well-formed by restricting the paths to only those that go through the user's network.
%%
%For example, in the datacenter FE configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:%

%\begin{code}
%PG1 \Path \End(A)
%PG2 \Path \End(B)
%PL1 \Path \textbf{only}(\In) \Intersect \End(E)
%PL2 \Path \textbf{only}(\In) \Intersect \End(F)
%\True \Path \Exit(\Out)
%\end{code}%

%The next step rewrites the high-level constraints such as $\Exit$ according to the equivalences in Figure~\ref{fig:rir-syntax}. Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression. For example, the regular expression $r \cdot (s ~\Prefer~ t) \cdot u$ is lifted to $(r \cdot s \cdot u) \Prefer (r \cdot t \cdot u)$ by distributing the preference over the sequence operator. In general, we employ the following distributivity equivalences:
%%
%\[
%\begin{array}{c}
%  r \odot (s_1 \Prefer \dots \Prefer s_n) = (r \odot s_1) \Prefer \dots \Prefer (r \odot s_n) \\
%  (s_1 \Prefer \dots \Prefer s_n) \odot r = (s_1 \odot r) \Prefer \dots \Prefer (s_n \odot r)
%\end{array}
%\]
%%
%where $\odot$ stands for an arbitrary regular binary operator, and $r$ is a policy with a single preference.
%%
%In cases where $r$ does not contain a single preference, such as $(s ~\Prefer~ t) \cdot (u ~\Prefer~ v)$, it is not clear which of the paths $s \cdot v$ or $t \cdot u$ is preferred. \sysname rejects such ambiguous policies, requiring instead that operators explicitly specify which paths to prefer --- for example as $(s \cdot u) ~\Prefer~ (s \cdot v) ~\Prefer~ (t \cdot u) ~\Prefer~ (t \cdot v)$.
%%
%Policies that contain preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) are also rejected by \sysname as invalid.

\newcommand{\state}[4]{\node[state,#3](#1)[#4]{#2};}
\newcommand{\transition}[4]{\path[->] (#1) edge [#4] node {#3} (#2);}

%\begin{figure*}[t!]
%  \begin{minipage}[t]{.5\linewidth}%

%  \hdr{Topology}{}
%  \vspace*{-2\baselineskip}%

%  \includegraphics[width=.6\columnwidth]{figures/topology}%

%  \hdr{Policy Automata}{}
%  \vspace*{-0.5\baselineskip}%

%  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.4cm,minimum size=1cm]
%    \state{0}{$0$}{              }{}
%    \state{1}{$1$}{right of=0}{}
%    \state{2}{$2$}{right of=1}{}
%    \state{3}{$3$}{right of=2}{}
%    \state{4}{$4$}{right of=3}{}
%    \state{5}{$5$}{right of=4}{accepting}
%    \transition{0}{1}{out}{}
%    \transition{1}{2}{D}{}
%    \transition{2}{3}{C}{}
%    \transition{3}{4}{A}{}
%    \transition{4}{5}{W}{}
%  \end{tikzpicture}%

%  \vspace*{0.5em}%
%

%  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.6cm]
%    \state{0}{$0$}{              }{}
%    \state{1}{$1$}{right of=0}{}
%    \state{2}{$2$}{right of=1}{}
%    \state{3}{$3$}{right of=2}{}
%    \state{4}{$4$}{right of=3}{accepting}
%    \transition{0}{1}{out}{}
%    \transition{1}{2}{in}{}
%    \transition{2}{2}{A,C,D,E}{loop above}
%    \transition{2}{3}{B}{}
%    \transition{3}{3}{B}{loop above}
%    \transition{3}{2}{A,C,D,E}{bend left}
%    \transition{3}{4}{W}{}
%  \end{tikzpicture}
%  \end{minipage}
%  %
%  ~~
%  ~~
%  %
%  \begin{minipage}[t]{.5\linewidth}
%  \hdr{Product Graph IR}{}
%  \vspace*{-1\baselineskip}
%  %
%  \includegraphics[width=.8\columnwidth]{figures/productgraph}
%  \end{minipage}%

%  \hrulefill
%  \vspace*{.4em}%

%  \caption{Product graph construction for policy $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
%  \label{fig:example-compilation}
%  %\vspace{-1em}
%\end{figure*}

%\subsection{Product graph IR}

%Now that the user policy exists in a simplified form, we must consider the topology. In particular, we want a compact representation that describes all the possible ways BGP route announcements can flow through the network subject to the policy and topology constraints. The PGIR captures these constraints by ``intersecting" each of the regular automata corresponding to the RIR path preferences with the topology. Paths through the PGIR correspond to real paths through the topology that satisfy the user constraints.

%\para{Formal definition}

%While paths in an RIR policy describe the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated --- route announcements flowing in the opposite direction. To capture this idea, for each regular expression $r_i$ in an RIR policy, we construct a deterministic finite state machine for the reversed regular expression. An automata for regular expression $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$). The alphabet $\Sigma$ consists of all abstract locations (\IE, routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
%%
%The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$.
%%
%The combined PGIR is a tuple ($V'$, $E'$, $s$, $e$, $P$) with
%vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
%edges $E' \colon V' \times V'$,
%a unique starting vertex $s$,
%a unique ending vertex $e$,
%and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of path ranks.%

%For a PGIR vertex $n = (l, \dots) \in V'$, we say that $n$ is a \emph{shadow} of topology location $l$. We also write $\tilde{n} = l$ to indicate that the topology location for node $n$ is $l$. When two PGIR nodes $m$ and $n$ shadow the same topology location (\IE, $\tilde{m} = \tilde{n}$), we write $m \approx n$.%

%Throughout the remainder of the paper, we will use the convention that metavariables $m$ and $n$ stand for PGIR nodes and $l$ stands for a topology location. Capital letters like $X$ refer to concrete topology locations, while capital letters with subscripts such as $X_1$ and $X_2$ refer to concrete PGIR nodes that share a topology location (\IE, $\tilde{X_1}$ = $\tilde{X_2} = X$).

%\para{From RIR To PGIR}

%Let $a_i$ and $b_i$ denote states in the regular policy automata.
%The PGIR is constructed by adding an edge from $m = (l_m, a_1, \dots, a_k)$ to $n = (l_n, b_1, \dots, b_k)$ whenever $\sigma_i(a_i, l_n) = b_i$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
%%
%Additionally, we add edges from the start node $s$ to any $n = (l, a_1, \dots, a_k)$ when $\sigma_i(q_{0_i}, l) = a_i$ for each $i$.
%%
%The preference function $P$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $. That is, it records the path rank of each automaton that has reached a final state.
%%
%Finally, there is an edge from each node in the PGIR such that $P(n) \neq \emptyset$ to the special end node $e$. We write $(m \leq_{rank} n)$ if either $P(m) = P(n) = \emptyset$ or $min ~ P(m) \leq min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.%
%

%Intuitively, the PGIR tracks the policy states of each automaton as route announcements move between locations.
%%
%Consider the topology in Figure~\ref{fig:example-compilation}. Suppose we want a primary route from neighbor W that allows traffic to enter the network at $A$ and utilize the C--D link before leaving the network (through $X$ or $Y$). As a backup, we also want to allow traffic to enter the network from $B$, in which case the traffic can also utilize the C--E link before leaving the network. For simplicity, we assume that the route ends in either $X$, $Y$, or $Z$. The RIR for the policy could be written as:
%%
%$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$$
%%
%Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
%%
%The figure also shows the PGIR after intersecting the topology and policy automata. Every path in the PGIR corresponds to a concrete path in the topology. In particular, every path through the PGIR that ends at a node $n$ such that the preference function $P(n) = \set{i_1, \dots, i_k}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_k$.
%%
%For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining a path with the lowest (best) rank of $1$.
%BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton. This possibility is reflected in the product graph by the node with state $(X,1,1)$. From here, if X were to advertise this route to D, it would result in the path $D \cdot X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
%%
%The ``--" state indicates the corresponding automaton cannot accept the current path or any extension of it. Since
%node $(W,5,-)$ is in an accepting state for the first automaton, it indicates that this path has rank 1.

%\subsection{Failure-safety analysis}

%To implement path preferences in routing, BGP uses local preferences on a per-device basis. However, the distributed nature of BGP makes setting preferences locally to achieve a network-wide routing policy difficult. This task becomes even more challenging in the presence of failures since routers running BGP lack a global view of the network.

%\para{An illustrative example}

%To demonstrate the difficulty of generating device-local preferences, consider the simple policy for the topology in Figure~\ref{fig:unimplementable}, which says to prefer the top path over the bottom path:
%%
%$(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G})  \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$.
%%
%How could such a policy be implemented in BGP? Suppose we set the local preferences to have $D$ prefer $E$ over $F$, and have $A$ prefer $B$ over $C$. This works as expected under normal conditions, however, if the A--B link fails, then suddenly $D$ has made the wrong decision by preferring $E$. Traffic will now follow the
%$A \cdot C \cdot D \cdot E \cdot G$ path, even though this path was not allowed by the policy. Thus, the distributed implementation has used a route that is not allowed by the policy. To make matters worse, the second preference for the path $A \cdot C \cdot D \cdot F \cdot G$ is available in the network but not being used. Thus, a path for the best possible route available after the A--B failure exists in the network, but the distributed implementation will not find it.
%%
%The first problem could be fixed by tagging and filtering route advertisements appropriately so that $C$ rejects routes that go through $E$, however the second problem cannot be fixed. In fact, this policy cannot be implemented in BGP in a way that is policy compliant under all failures since $D$ cannot safely choose between $E$ and $F$ without knowing whether the A--B link is available.

%\para{Problem formulation}

%The problem of determining local preferences for each router is reflected in the structure of the PGIR. Whenever a given router appears as multiple shadow nodes in the PGIR, the compiler must decide which shadow to prefer.
%%
%In the example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in shadow $(C,-,2)$ or from $D$ in shadow $(C,3,2)$.
%%
%%
%The compiler must determine a \emph{total ordering} of shadow nodes for each router, which reflects the relative preference of advertisements received in each shadow and should be consistent with path ranks.
%%
%For example, if $C$'s shadow $(C,3,2)$ can be preferred to $(C,-,2)$, written as $(C,3,2) \leq_{lp} (C,-,2)$, $C$ can prefer advertisements from $(D,2,2)$ over $(E,-,2)$. $D$ and $E$ tag their advertisements to let $C$ know which shadow sent the advertisement. Section \ref{sec:abgp} discusses tagging in detail.

%\begin{figure}[t!]
%  \centering
%  \includegraphics[width=.5\columnwidth]{figures/unimplementable}
%  \caption{A network where the policy $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
%  \label{fig:unimplementable}
%  %\vspace{-1em}
%\end{figure}

%\para{Regret-free preferences}

%To order PGIR shadows ($\leq_{lp}$) for each router in a way that is policy-compliant under all failures, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}. A router (location) $l$ has a regret-free preference for a set of advertisements $A$ over $B$ if, whenever $l$ selects an advertisement to destination $d$ from $A$ over another from $B$, there is always some policy-compliant path to $d$ that is at least as good ($\leq_{rank}$ for the final node along the path) as any possible path (not necessarily from $l$) to $d$ if $l$ had selected an advertisement from $B$ instead. In other words, the preference of $A$ over $B$ at $l$ is regret-free if $l$ is never (under any failure) worse-off by choosing an advertisement from $A$ when available. The notion of regret-free preferences can be lifted to PGIR nodes by considering the set of advertisements available to each node.%

%In the example of Figure~\ref{fig:example-compilation}, the choice for $C$ to prefer shadow $(C,3,2)$ to $(C,-,2)$ is regret-free, since there will always be at least as good a path to destination $W$ regardless of any failures that might occur in the network. For example, if the $C$--$A$ link fails, then there is still a backup path from $(C,3,2)$ to $(W,-,4)$ that is just as good as any path from $(C,-,2)$. Likewise, any combination of failures to disconnect $(C,3,2)$ from $(W,-,4)$ would also disconnect $(C,-,2)$ from $(W,-,4)$.

%\para{A preference inference algorithm}

%Searching for precise regret-free preferences in general is hard, and clearly enumerating all possible combinations of failures and preference orderings is intractable. We thus adopt a conservative analysis that we found to be effective and efficient in practice. The idea is to $i)$ search for regret-free preferences by comparing the set of paths available after accepting advertisements in two different PGIR shadows $N_1$ and $N_2$ of topology node $N$, and $ii)$ refine the comparison when necessary by considering where the announcements must have traversed before arriving at $N_1$ or $N_2$.

%\begin{algorithm}[t!]
%\caption{Inferring regret-free preferences}
%\label{alg:failures}
%\begin{algorithmic}[1]
%\Procedure{Regret-free($G$, $N_1$, $N_2$)}{}
%  \If {$N_1 \not\approx N_2$} \Return false
%  \EndIf
%  \State $q \gets Queue()$
%  \State $q.Enqueue (N_1, N_2)$
%  \While {$!q.Empty()$}
%    \State $(m,n) \gets q.Dequeue()$
%    \If {$m \nleq_{rank} n$}
%      \Return false
%    \EndIf
%    \For {$n'$ in adj($G$, $n$)}
%      \If {\big($\exists m' \in \textup{adj}(G,m), m' \approx n'$\big)}
%        \If {$(m',n')$ not marked}
%          \State {mark $(m',n')$ as seen}
%          \State $q.Enqueue(m',n')$
%        \EndIf
%      \Else { \Return $false$}
%      \EndIf
%    \EndFor
%  \EndWhile \\
%  \hspace{\algorithmicindent} \Return true
%\EndProcedure
%\end{algorithmic}
%\end{algorithm}

%Algorithm~\ref{alg:failures} checks whether one shadow can be preferred to another ($N_1 \leq_{lp} N_2$). It walks from nodes $N_1$ and $N_2$ and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, also take a step to an equivalent topology location $(\approx)$. When there is no such equivalent step, the algorithm attempts to take into account where the advertisement must have already traversed. In particular, it checks if there is an equivalent dominator node and, if so, walks from this new node instead.
%%
%The idea is that, since the advertisement must have already passed through the dominator, we can check to see if we are guaranteed to find paths that are at least as good from this new node instead.
%%
%At each step, it requires that the current node reachable from $N_1$ has a path rank that is at least as good as that of the current node reachable from $N_2$ ($m \leq_{rank} n$). The intuition here is that if $m \nleq_{rank} n$, then we can very likely fail every edge in the topology except for the path that leads to the current $m$ and $n$, thereby generating a counterexample.
%Algorithm~\ref{alg:failures} terminates since the number of related states $(m,n)$ that can be explored is finite.%

%For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR shadows according to the $(\leq_{lp})$ relation determined by Algorithm~\ref{alg:failures}. If two nodes are incomparable, then the compiler rejects the policy as unimplementable.

%\para{Avoiding loops}

%The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available due to loops rejected by BGP.%

%Consider the partial product graph shown in Figure~\ref{fig:avoiding-loops}. Our preference inference algorithm will determine that node $X_1$ should be locally preferred to node $X_2$ since this will result in a better (lower ranked) path to destination $A$. However, when applying Algorithm~\ref{alg:failures}, we failed to take into account the possibility of loops. In particular, node $A_2$ may be unusable for advertisements that go through $X_1$ since the advertisement may have already gone through $A_1$ previously. In this case, $X$ will have made the wrong choice since preferring $X_2$ would have resulted in a better path for the destination $A$ (a path of rank 3 instead of 4).%

%On the other hand, this would not have been a problem if paths ending at $A_1$ had a lower rank than those ending at $A_2$ or $A_3$. For example, if paths ending at $A_1$ had rank 1, then any time $A_2$ is unusable due to a loop with $A_1$, it ultimately does not matter since $A_1$ is preferred anyway.
%%
%In fact, checking if we are never worse off using $A_1$ instead of $A_2$ corresponds exactly with determining if $A$ has a regret-free preference for $A_1$ over $A_2$.
%%
%More specifically, the compiler checks that, any time there are two shadows $N_1$ and $N_2$ for the same topology location, where $N_1$ appears ``above'' (\IE, can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (\IE, $N_1 <_{lp} N_2$).

\subsection{Other properties}
\label{sec:property-checking}

\begin{easylist}[itemize]
& Reachability analysis (i.e., are all locations specified in the policy reachable
  after taking topology into account) 
&& Inference rules for reachability
&& Fixed point computation using SMT solver

& Reachability under k-failures (e.g., aggregation black holes)
&& translation to ILP problem
\end{easylist}

%\subsection{Aggregation-safety analysis}
%\label{sec:agg-safety}

%As shown in \S\ref{sec:motivation}, aggregation can lead to subtle black-holing of traffic when failures occur. Determining when this can happen requires knowledge, not only of the topology, but also of the policy. For instance, a policy might require that all traffic for a particular prefix go over a single link before being aggregated. If that one link fails, a black hole might be introduced.
%%
%Because the PGIR encodes the complete user policy and topology, \sysname can efficiently check that aggregates do not black hole traffic for up to $k$ failures.%

%We view the aggregation problem as a variant of the min-cut problem in the PGIR. Specifically, for each prefix that falls under an aggregate, we are interested in finding a lower bound on the number of failures required to disconnect the prefix's origin from its aggregation point. The difficulty, however, is that each link in the topology might appear as multiple links in the PGIR, thus preventing the direct application of standard min-cut algorithms.
%%%

%Instead, we adopt the following simple strategy: $i)$ pick a random path in the PGIR between the prefix's origin and aggregation point, $ii)$ remove all similar edges in the PGIR for each topology edge along the chosen path, and $iii)$ repeat until no such path exists.
%Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.%
%

%Recall the datacenter example from \S\ref{sec:motivation}, with the policy
%\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the PGIR for \CD{PG1}. Since we know aggregation will occur at $X$, and that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first and would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none). Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is now disconnected from $X$, 2 is a lower bound on the number of failures required to introduce an aggregation black hole for prefix \CD{PG1}. This process is repeated for other aggregation locations (\EG, $Y$).

%\subsection{Abstract BGP}
%\label{sec:abgp}
%The final stage of our compiler translates policies from PGIR to a vendor-neutral abstraction of BGP (ABGP).

%\para{From PGIR to ABGP}

%\newcommand{\highlight}[1]{%
%  \colorbox{red!50}{$\displaystyle#1$}}
%\newcommand{\Router}[1]{\KW{Router} #1:}
%\newcommand{\REGEX}[1]{\texttt{regex}(#1)}
%\newcommand{\PEER}{\texttt{peer}}
%\newcommand{\COMM}{\texttt{comm}}
%\newcommand{\MED}{\texttt{MED}}
%\newcommand{\Arrow}{\ensuremath{\leftarrow}}%

%\begin{figure}[t!]
%\begin{code}
%  \Router{A}
%    Match \PEER=C, \COMM=(3,2)
%      Export \COMM \Arrow (4,2),
%             \MED \Arrow 80, \PEER \Arrow W
%  \Router{B}
%    Match \PEER = C, \COMM = (-,2) or (3,2)
%      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
%             \MED \Arrow 81, \PEER \Arrow W
%  \Router{C}
%    Match[LP=99] \PEER = E, \COMM = (-,2)
%      Export \COMM \Arrow (-,2), \PEER \Arrow B
%    Match \PEER = D, \COMM = (2,2)
%      Export \COMM \Arrow (3,2), \PEER \Arrow A,B
%  \Router{D}
%    Match \REGEX{X + Y}
%      Export \COMM \Arrow (2,2), \PEER \Arrow C
%  \Router{E}
%    Match \REGEX{Z}
%      Export \COMM \Arrow (-,2), \PEER \Arrow C
%  \end{code}
%  \vspace{-2em}
%  \caption{Abstract BGP router configurations. \label{fig:abgp-config}}
%  \vspace{-1em}
%\end{figure}

%=====================================================
%
%
%  **Implementation**
%
%
%=====================================================

\section{Implementation}
\label{sec:implementation}

%=====================================================
%
%
%  **Evaluation**
%
%
%=====================================================

\section{Evaluation}
\label{sec:evaluation}

\subsection{Networks studied}

\subsection{Compilation time}

\subsection{Expressiveness}

\begin{easylist}[itemize]
& DCell, BCube, Fattree, others ...
\end{easylist}

%=====================================================
%
%
%  **Related Work**
%
%
%=====================================================

\section{Related Work}
\label{sec:related}

\begin{easylist}[itemize]
& Topology abstraction
&& DCell, BCube, Fattree, ...
&& Condor ...

& Configuration automation
& Configuration analysis
& Configuration synthesis
\end{easylist}

%Our work draws on four threads of prior work.%

%\para{Topology abstraction}%

%\para{Topology design}%

%\para{Configuration automation}
%Many practitioners use configuration templates~\cite{hatch,thwack}, to ensure certain kinds of consistency across similar devices. In addition, configuration languages such as RPSL~\cite{RFC2622}, Yang~\cite{RFC6020}, and Netconf~\cite{RFC6241} allow operators to express routing policy in a vendor-neutral way.
%However, all of these solutions remain low-level, for example, requiring operators to specify exact local preferences. Unlike \sysname, there is no guarantee that these low-level configurations satisfy the original, high-level intent.%

%\para{Configuration analysis}
%The notion that configuring network devices is difficult and error-prone is not new.
%In the past, researchers have tried to tackle this problem by analyzing existing
%router configurations~\cite{feamster+:rcc,ipassure,batfish,bagpipe,arc} and reporting errors or inconsistencies when they are detected.
%Our research is complementary to these analysis
%efforts.  We hope to eliminate bugs by using higher-level
%languages and a ``correct-by-construction''
%methodology. Writing configurations at a high level of abstraction simplifies policy implementation and prevents a whole host of low-level errors.%

%\para{Configuration synthesis}
%ConfigAssure~\cite{narain:lisa05,narain+:configassure}
%is another system designed to
%help users define and debug low-level router
%configurations.  Inputs to
%ConfigAssure include a \emph{configuration database}, which contains a
%collection of tuples over constants and configuration variables, and a
%\emph{requirement}, which is a set of constraints.
%%
%The authors use a combination of logic programming and
%SAT solving to find concrete values for configuration variables.
%ConfigAssure handles configuration for a wide range of protocols and many
%different concerns.  In contrast, the scope of \sysname is much
%narrower.  In return, \sysname offers compact, higher-level
%abstractions customized for our domain, such as regular paths, as well
%as domain-specific analyses customized to those abstractions, such as
%our failure safety analysis.  The implementation technology is also
%entirely different, as we define algorithms over automata and graphs
%as opposed to using logic programming and SAT-based model-finding.

%=====================================================
%
%
%  **Conclusions**
%
%
%=====================================================

\section{Conclusions}
\label{sec:conclusions}

\para{Acknowledgments}

%=====================================================
%
%
%  **Appendix**
%
%
%=====================================================

%\subsection{Propane Properties}
%
%\newtheorem{prop}{Proposition}[section]
%
%Here we investigate the correctness and expressiveness properties of \sysname. We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures? (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?
%
%If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario. We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges. We argue that \sysname is correct by breaking down the claim:
%
%\begin{prop}
%BGP configurations for internal routers produced by \sysname will be stable.
%\end{prop}
%
%\begin{prop}
%BGP configurations produced by \sysname are \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.
%\end{prop}
%
%The Soundness claim follows directly from compilation of the product graph. Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations are Sound.
%
%\begin{prop}
%BGP configurations produced by \sysname are \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
%\end{prop}
%
%The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.  This means there is a valid path in the product graph corresponding to this path, and which is available in the network.
%Assume we are unable to achieve this route in the network. To not achieve this path means that some router along the advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead. This implies that router that makes the ``wrong'' choice appears as a separate node in the product graph. However, from our failure safety check, we know that the other, more-preferred node must have a superset of the paths to accepting states as the less preferred node (from which it stole the route) for at least as good of a final preference. The argument then proceeds by induction on the path length - there are only a finite number of such stealings that can occur, each of which will ultimately still result in a route advertisement reaching $X$ along a most preferred path.
%
%Any \sysname-compiled policy will be \textit{Complete} as a result of the failure safety check.
%

%

%The combination of Soundness and Completeness ensures that the distributed implementation will always send traffic along the best paths possible, yet will also never also use any undesired paths. These properties rely on the fact that \sysname produces stable BGP configurations:

%
%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo} for stable BGP. In particular, any policy with a dispute wheel will not pass the stronger failure safety check by \sysname.
%
%\begin{figure}[t!]
%\includegraphics[width=\columnwidth]{figures/dispute-wheel}
%\label{fig:dispute-wheel}
%\caption{Product graph for a dispute wheel.}
%\end{figure}
%
%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}. If a set of BGP configurations do not have a dispute wheel, then they will converge to their best routes. Any BGP policy with a dispute wheel will not satisfy the failure safety condition in Section~\ref{sec:compilation}. Assume that the preferences in the policy describe a dispute wheel, and we will show that our failure check will reject the policy. Informally, a dispute wheel occurs when there are some number of nodes $u_1, \dots, u_n$ attempting to get a path to a destination node $d$. Each node $u_i$ prefers to go through its neighbor $u_{i+1}$ over route $R_i$ than directly to $d$ with route $Q_i$. Thus the nodes form a wheel of preferences. The product graph for a policy that contains a dispute wheel will look like Figure~\ref{fig:dispute-wheel}, which shows a dispute wheel of size 3. In order to pass the failure safety check for the compiler, the more-preferred node for $u_2$ will need to have a superset of the paths starting from the less-preferred node for $u_2$. In turn, this means that the maximum length path after visiting the more preferred $u_2$ will be $max(Z) = 1 + max(Y)$, similarly, if we look at $u_1$, we will determine that $max(Y) = 1 + max(X)$, and so on. The resulting equations define a system of unsatisfiable equations. Therefore, it is not possible for \sysname to compile a BGP policy that contains a dispute wheel. Since no-dispute-wheel is a sufficient condition for BGP stability, any compiled \sysname policy will be stable.
%

%An important distinction is that BGP might still be instable with respect to other external ASes, since \sysname has no way of configuring their routing policy and can only rely on AS path filters to see what advertisements are observed.

%=====================================================
%
%
%  **Bibliography**
%
%
%=====================================================

\balance

\bibliographystyle{abbrv}
\bibliography{references}

\end{document}

### 2016-10-14 paper/abstraction/paper.tex
updated abstraction paper outline

@@
 
-\newcommand{\sysname}{{\small \sf Diesel}\xspace}
+\newcommand{\sysname}{{\small \sf Propane}\xspace}
 
@@
 
-\title{Abstraction Compilation Techniques}
+\title{An Abstraction-based Approach to Network Synthesis}
 
@@
 %
-% (4) lets us scale compilation/algorithms to large-scale topologies
+% (4) lets us scale synthesis to large-scale topologies
 
 \textbf{Abstract---}
-We develop \sysname, a tool for automated reasoning about end-to-end properties of abstract network topologies.
-\sysname allows network operators to write a centralized routing policy over a high-level abstraction of their network topology.
-From such a specification, it generates a distributed collection of BGP router configurations that are guaranteed to implement the centralized routing policy for any concrete instantiation of the abstract topology, and for any combination of network failures in the resulting concrete topology.
+We develop techniques for automated reasoning about end-to-end properties of abstract network topologies.
+We extend a network synthesis tool, \sysname, to allow network operators to write a high-level routing policy over an abstraction of their network topology.
+From such a specification, \sysname synthesizes a collection router configurations running the distributed Border Gateway Protocol (BGP) that are guaranteed to implement the centralized routing policy for any concrete instantiation of the abstract topology, and for any combination of network failures in the resulting concrete topology.
 %
@@
 %
-These strong guarantees allow operators to reason about the routing behavior of their network at a high-level abstraction, while also generating an efficient low-level implementation.
-%
-In addition, operators are able to safely change or expand their network in any way, so long as the new resulting topology also respects the abstraction.
+Something something, expandable/incremental networks. Something something scales compilation to large networks. Something something, templates easier to understand.
+%These strong guarantees allow operators to reason about the routing behavior of their network at a high-level abstraction, while also generating an efficient low-level implementation.
+%
+%In addition, operators are able to safely change or expand their network in any way, so long as the new resulting topology also respects the abstraction.
 %
@@
 & Network configuration is difficult/error-prone. Operators think of policy at 
-  a high level of abstraction, yet implementations:
+  a high level of abstraction, yet for implementations:
 && Often configs must be decomposed device-by-device
@@
 
-& To this end, we develop a language called \sysname to simplify the operators task.
+& To this end, we build a language called \sysname to simplify the operators task.
 && \sysname allows the operator to define high-level network abstractions to reflect
@@
    abstraction.
-&& We develop an intermediate graph-based representation for compiled, abstract policies,
-   and show how to compile \sysname policies to this representation. 
-&& We develop several algorithms that operate over this graph representation and verify 
-   if properties, such as reachability or no black holes under k-failures, are guaranteed
-   to hold under any possible concrete instantiation of the network.
+&& We extend the \sysname intermediate graph-based representation to support abstract policies,
+   and show how to compile abstract \sysname policies to this representation. 
 && As a major use-case, we show how the compilation and failure-safety analysis
    of the Propane configuration-synthesis tool can be extended over abstract topologies.
-   Explain what Propane is first...
-   Our major result is an abstraction theorem, which states that ...
-   The result is that policies compiled with the Propane compiler to distributed configurations 
+&& We develop an abstract interpretation that operates over this graph representation and verifies 
+   if properties, such as reachability or k-disjoint paths between two nodes, are guaranteed
+   to hold for any possible concrete instantiation of the network.
+&& Our major result is an abstraction theorem, which states that ...
+&& The result is that policies compiled with the Propane compiler to distributed configurations 
    are guaranteed to have correct forwarding behavior for any possible concrete instantiation 
@@
 &&& Finally, we show how abstract compilation makes it possible to dramatically speed up compilation 
-    time for the Propane policies, ...
+    time for the Propane policies, cite some numbers here ... 
 \end{easylist}
+
+% Some useful citations from the previous paper listed below
 
@@
 
-%Hence, in this paper, we have two central goals:
-%\begin{enumerate}
-%\item Foo
-%\item Bar
-%\end{enumerate}
-
 %=====================================================
@@
 
+\subsection{Example:  The Backbone}
+
+\begin{easylist}[itemize]
+& Example of a backbone network with multiple peers
+&& Maybe have a couple of different roles (e.g., special handling to keep traffic in the US)
+&& Could show different abstractions here (e.g., one big switch)
+&& Could be useful to hint at things to come, e.g., takes 2 sec to compile the abstract one
+\end{easylist}
+
 %=====================================================
@@
 
+\subsection{Example: The Backbone}
+
+\begin{easylist}[itemize]
+& Give the policy over the abstract network
+\end{easylist}
+
 \subsection{Language}
 
-Placeholder for formal language definition
+Placeholder for formal language definition syntax + semantics
+
+% Examples of code given below
 
@@
 %
-%  **Abstractions**
-%
-%
-%=====================================================
-
-\section{Abstraction}
-\label{sec:abstraction}
-
-\begin{easylist}[itemize]
-& Define abstractions more formally,
-&& e.g., homomorphism between graphs + node/edge constraints
-
-& Give formal semantics of abstract, labelled graph
-&& i.e., if a concrete graph + homomorphism is valid
-   given an abstract, labelled graph
-
-\end{easylist}
-
-%=====================================================
-%
-%
 %  **Compilation**
@@
    simplicity, we will assume a BGP backend like Propane.
-
-& Use the datacenter example from before
+\end{easylist}
+
+%=====================================================
+%
+%
+%  **Abstractions**
+%
+%
+%=====================================================
+
+\section{Abstraction}
+\label{sec:abstraction}
+
+\begin{easylist}[itemize]
+& Define abstractions more formally,
+&& e.g., homomorphism between graphs + node/edge constraints
+&& Use the datacenter example from before
 && First define the concretization function for translating the abstract policy
    into the concrete policy
-&& Next, show the Product Graphfor both the concrete and abstract policies.
+&& Next, show the Product Graph for both the concrete and abstract policies.
 
@@
 \begin{easylist}[itemize]
-& Reachability analysis (i.e., are all locations specified in the policy reachable
-  after taking topology into account) 
-&& Inference rules for reachability
-&& Fixed point computation using SMT solver
-
-& Reachability under k-failures (e.g., aggregation black holes)
-&& translation to ILP problem
+& Graph homomorphism is not enough -- to coarse an overapproximation
+&& Use node/edge multiplicites to capture more precise constraints on concrete topologies
+&& Show a bunch of examples of fattree, bcube, dcell, hyperX, facebook, google, F10, etc.
+& K-disjoint path analysis 
+&& Useful for aggregation safety (black holes) & reachability
+&& Inference rules as an abstract interpretation using Z3
 \end{easylist}
@@
 
+\begin{easylist}
+& Extension to \sysname
+& lines of code
+& optimizations
+&& Are there any?
+\end{easylist}
+
 %=====================================================
@@
 
+\begin{easylist}
+& Fattree, F10, Facebook, DCell, BCube, hyperX
+& Shortest path routing for each of these topologies but varying different size parameters
+\end{easylist}
+
+\subsection{Analysis Precision}
+
 \subsection{Compilation time}
-
-\subsection{Expressiveness}
-
-\begin{easylist}[itemize]
-& DCell, BCube, Fattree, others ...
-\end{easylist}
 
@@
 \begin{easylist}[itemize]
-& Topology abstraction
-&& DCell, BCube, Fattree, ...
-&& Condor ...
-
+& Topologies: DCell, BCube, Fattree, ...
+& Topology Abstraction: Condor
+& Memory Shape Analysis: Sagiv, others
 & Configuration automation

### 2016-10-14 paper/propane/v1/appendix.tex
updated abstraction paper outline

--- 2016-06-07 paper/v2/paper.tex
@@
-\documentclass{sig-alternate-10pt}
-
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{xcolor}
-\usepackage{url}
-\usepackage{times}
-\usepackage{xspace}
-\usepackage{listings}
-\usepackage{code}  
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{tikz}
-\usetikzlibrary{arrows,automata,positioning}
-\let\proof\relax
-\let\endproof\relax
-\usepackage{amsthm}
-\usepackage{subcaption}
-%\usepackage{geometry}
-
-\definecolor{princetonorange}{RGB}{255,143,0}
-\definecolor{tmlblue}{RGB}{0,58,120}  % tmlblue == Toronto Maple Leafs Blue!
-
-\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
-\newcommand{\ratul}[1]{\textcolor{blue}{[ratul: #1]}}
-\newcommand{\ryan}[1]{\textcolor{green}{[ryan: #1]}}
-\newcommand{\dpw}[1]{\textcolor{tmlblue}{[dpw: #1]}}
-\newcommand{\todd}[1]{\textcolor{princetonorange}{[todd: #1]}}
-
-\newcommand{\EG}{\emph{e.g.}} 
-\newcommand{\IE}{\emph{i.e.}} 
-\newcommand{\ETC}{\emph{etc.}} 
-\newcommand{\ETAL}{\emph{et al.}}
-
-\newcommand{\sysname}{{\small \sf Propane}\xspace}
-
-\newcommand{\para}[1]{\paragraph*{\textbf{#1}}}
-
-\newcommand{\set}[1]{\ensuremath{\{ #1 \} }}
-\newcommand{\abs}[1]{\ensuremath{ \lvert #1 \rvert }}
-
-\newcommand{\CD}[1]{\texttt{\small #1}}  % code font
-\newcommand{\KW}[1]{\texttt{\small\bfseries{#1}}}
-%\newcommand{\KW}[1]{\texttt{#1}}
-\newcommand{\True}{\CD{true}}
-\newcommand{\Define}{\KW{define}}
-\newcommand{\Prefer}{\texttt{>>}}
-\newcommand{\Path}{\texttt{=>}}
-\newcommand{\Link}{\texttt{->}}
-\newcommand{\Agg}{\KW{agg}}
-\newcommand{\Any}{\KW{any}}
-\newcommand{\None}{\KW{none}}
-\newcommand{\In}{\KW{in}}
-\newcommand{\Out}{\KW{out}}
-\newcommand{\AND}{\texttt{\&}}
-\newcommand{\OR}{\texttt{|}}
-\newcommand{\NOT}{\texttt{!}}
-\newcommand{\Intersect}{\ensuremath{\cap}}
-\newcommand{\Union}{\ensuremath{\cup}}
-
-\newcommand{\Exit}{\KW{exit}}
-\newcommand{\End}{\KW{end}}
-\newcommand{\Start}{\KW{start}}
-\newcommand{\Enter}{\KW{enter}}
-\newcommand{\Later}{\KW{later}}
-\newcommand{\Before}{\KW{before}}
-\newcommand{\Internal}{\KW{internal}}
-\newcommand{\Never}{\KW{never}}
-\newcommand{\Only}{\KW{only}}
-\newcommand{\Through}{\KW{through}}
-\newcommand{\LinkKW}{\KW{link}}
-\newcommand{\PathKW}{\KW{path}}
-\newcommand{\Novalley}{\KW{novalley}}
-
-%\let\Url\url
-%\renewcommand*{\LaTeX}{\oldLaTeX\space}
-\renewcommand{\path}[2]{ #1 \mapsto \ensuremath{#2} }
-
-\begin{document}
-
-\special{papersize=8.5in,11in}
-\setlength{\pdfpageheight}{\paperheight}
-\setlength{\pdfpagewidth}{\paperwidth}
-
-\title{Don't Mind the Gap:  Bridging Network-wide Objectives and Device-level Configurations}
-
-%\author{Paper \#324, 14 pages}
-
-\author{%
-Ryan Beckett\\
-  \affaddr{Princeton University}\\
-  \email{rbeckett@princeton.edu}
-\and
-Ratul Mahajan\\
-  \affaddr{Microsoft Research}\\
-  \email{ratul@microsoft.com}
-\and
-Todd Millstein\\
-  \affaddr{University of California, Los Angeles}\\
-  \email{todd@cs.ucla.edu}
-\and
-Jitu Padhye\\
-  \affaddr{Microsoft Research}\\
-  \email{padhye@microsoft.com}
-\and
-David Walker\\
-  \affaddr{Princeton University}\\
-  \email{dpw@princeton.edu}
-}
-
-\maketitle
-
-%\category{CR-number}{subcategory}{third-level}
-%% general terms are not compulsory anymore,
-%% you may leave them out
-%\terms
-%term1, term2
-%\keywords
-%keyword1, keyword2
-
-%=====================================================
-%
-%
-%  **Abstract**
-%
-%
-%=====================================================
-
-%\textbf{Abstract---}
-%% Networks are notoriously difficult to configure correctly.
-%% Operators typically rely on local configuration of individual devices running
-%% distributed control plane protocols to achieve network-wide objectives.
-%% Managing implicit dependencies between device configurations and properly accounting for failures makes
-%% a network operator's work particularly difficult.
-%% %
-%% %The recent move towards software-defined networking has been motivated, in part,
-%% %by the simplicity of the centralized model, where a controller directly manages
-%% %individual devices rather than letting them manage themselves. However distributed
-%% %protocols have many important advantages in scalability,
-%% %latency and fault tolerance over the completely centralized approach.
-%% %
-%% In this paper, we describe a new system -- \sysname, which allows an operator to specify a high-level,
-%% centralized routing policy declaratively, but then to compile it to a purely distributed
-%% implementation, which uses the BGP routing protocol to run on existing, commodity hardware.
-%% %
-%% Propane allows operators to describe the types of paths traffic may (or may not) take
-%% through the network, as well as relative preferences (or backups) between paths.
-%% %
-%% Network policies compiled with \sysname are guaranteed to implement the correct routing policy regardless of the number of failures, if possible.
-If this is not possible, the compiler notifies the user at compile time rather than as the network is in
-%% operation.
-%% %
-%% %\sysname also takes the centralized model one step further by unifying inter and intra-domain routing.
-Operators can specify routing policy for an autonomous system by programming against the abstraction that they can control any route in the wider internet.
-%% %
-%% We have implemented a compiler for \sysname and evaluated it against several real-world configurations for data centers and core backbone networks. We demonstrate the \sysname compiler can scale to
-%% topologies with thousands of routers.
-%
-%\begin{abstract}
-%Traditional network operators have a difficult job: They are charged
-%with achieving network-wide objectives, but they must do so by
-%managing many individual, separate devices, each of which is running a
-%complex distributed control plane protocol.  Bridging the gap between
-%high-level objectives and low-level mechanisms manually is a challenging and
-%error-prone task.
-%%
-%In this paper, we describe our preliminary efforts to design and
-%implement a new language called Propane, which simplifies the task of
-%network management by allowing operators to specify their objectives
-%using end-to-end forwarding paths rather than device-by-device
-%configurations.  A compiler rather than a human bridges the gap
-%between high-level goals and the low-level mechanisms.  More
-%specifically, Propane allows operators to describe and rank the sets
-%of paths that traffic may follow.  Such paths stretch from external
-%ASes, through the user's network, and possibly onward again to other
-%ASes.  The Propane compiler analyzes these user specifications and
-%then compiles them to a collection of BGP configurations, so they may
-%exploit existing distributed fault tolerance mechanisms and
-%execute on existing commodity hardware.  During the compilation
-%process, it automatically synthesizes per-device import and export
-%filters, local preferences, MED attributes, and community tags.  An
-%important feature of the language is that whenever possible, compiled
-%configurations are guaranteed to implement the correct routing policy,
-%regardless of the number of failures.  If correct compilation is
-%impossible, the compiler notifies the user at compile time rather than
-%waiting until the system is in operation and failures have occurred.
-%To date, we have used the language and compiler to experiment with
-%several real-world configurations for data centers and core backbone
-%networks.  We demonstrate our prototype compiler can scale to
-%topologies with thousands of routers.
-%\end{abstract}
-
-\textbf{Abstract---}
-We develop a system called \sysname to help network operators with a challenging and error prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex distributed protocols.
-%
-\sysname allows operators to specify their objectives naturally, describing high-level constraints and preferences on the types of paths that traffic should take through their network or other networks.
-%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
-%
-Our compiler automatically translates these specifications to a collection of BGP router configurations.
-% that can execute on existing commodity hardware.
-%
-We introduce data structures and algorithms that guarantee that the compiled, distributed configurations correctly implement the routing policy under all possible combinations of failures.
-%
-We use \sysname to specify and compile the configurations of real
-data center and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds of routers.
-
-%=====================================================
-%
-%
-%  **Introduction**
-%
-%
-%=====================================================
-
-\section{Introduction}
-\label{sec:introduction}
-
-It is well known that configuring networks is error
-prone and such errors can lead to disruptive network
-downtimes~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
-For instance, a recent misconfiguration led to an hour-long, nation-wide outage for Time Warner's backbone network~\cite{time-warner}; and a major BGP-related incident makes international news every few months~\cite{bgpmon}.
-
-%For instance, in the context of BGP, Mahajan~~\cite{mahajan+:bgp-misconfiguration}
-%estimated that 200-1200 prefixes suffered from
-%misconfiguration each day and that close to 3 in 4 of all
-%new prefix advertisements were the result of misconfiguration.
-%Moreover, these misconfigurations sometimes cause significant network downtime for
-%individual networks~\cite{time-warner} or even broader internet connectivity problems~\cite{routing-instability,mahajan+:bgp-misconfiguration}.
-%\dpw{Note that \cite{time-warner} and I am not sure about the specifics of the problem there
-%or what exactly was misconfigured.  It is also unclear if our language really helps with the
-%``broader internet connectivity problems'' however, I thought that adding some specific examples
-%would help make the intro more compelling.  Feel free to rewrite.}
-
-%One reason for network configuration being onerous is that device configuration languages are low-level and several configuration elements must be kept consistent (e.g., interface addresses) for the device to behave as intended.
-
-A fundamental reason for the prevalence of misconfigurations is the
-semantic mismatch between the intended high-level
-policies and the low-level configurations.
-Many policies involve network-wide properties---prefer a certain neighbor,
-never announce a particular destination externally,
-use a particular path only if another fails---but configurations describe the behavior of
-individual devices.
-%
-Operators therefore must manually decompose network-wide policy into
-device behaviors, such that policy-compliant behavior results from the distributed interactions of
-these devices.
-%
-Policy-compliance must be ensured not only under normal
-circumstances but also during failures.  The need to reason
-about possible failures exacerbates the challenge
-for network operators.  As a result, configurations that work
-correctly in failure-free environments have nonetheless been found to violate key
-network-wide properties when failures occur~\cite{batfish}.
-
-To reduce configuration errors, many practitioners have a adopted a template-based
-approach~\cite{hatch,thwack}, in which common tasks are captured as parameterized templates.
-%
-%More powerful still are systems like
-%ConfigAssure~\cite{narain:lisa05,narain+:configassure}, which use SAT solving
-%and model finding tools to fill in parameters in configurations while
-%ensuring key correctness constraints are satisfied.
-%One step further, systems like
-%ConfigAssure~\cite{narain:lisa05,narain+:configassure} use SAT solving
-%and model finding tools to correctly and consistently fill in some parameters.
-%
-While templates help ensure certain kinds of consistency across devices,
-they do not provide fundamentally different abstractions from existing configuration languages
-or bridge the semantic divide between network-wide policies and device-level configuration.
-%They do not provide fundamentally different abstractions
-%from existing configuration languages and
-Thus, they still require operators to
-manually decompose policies into device behaviors.
-
-Configuration analysis tools~\cite{batfish,feamster+:rcc} have been developed as a complementary approach for reducing misconfigurations by checking that the low-level configurations match high-level operator intent.
-However, such tools cannot help operators come up with the configuration in the first place.
-Further, today's tools can only check correctness under concrete failure scenarios, rather than under all possible failures.
-
-Software-defined networking (SDN) and its abstractions
-are, in part, the research
-community's response to the difficulty of maintaining policy
-compliance through distributed device interactions~\cite{ethane}. Indeed, instead of organizing networks
-around a distributed collection of devices that compute forwarding tables through
-mutual interactions, the devices are told how to
-forward packets by a centralized controller. The controller is responsible for ensuring that the
-paths taken are compliant with operator specifications.
-%Researchers
-%have developed increasingly sophisticated languages that let operators
-%specify desirable network paths~\cite{x,y,z} which are then translated
-%to forwarding tables at runtime.
-
-The centralized control planes of SDN, however, are not a panacea.
-First, while many SDN programming systems~\cite{sdn-languages} provide effective \emph{intra}-domain routing
-abstractions, letting users specify paths within their network,
-they fail to provide a coherent means to specify \emph{inter}-domain routes.
-Second, centralized control planes
-require careful design and engineering to be robust to failures---one must ensure that all devices can communicate with the controller at all times, even under arbitrary failure combinations.
-Even ignoring failures, it is necessary for the control system to
-scale to meet the demands of large or geographically-distributed networks,
-and to react quickly
-to environmental changes. For this challenge, researchers are exploring
-multi-controller systems with interacting controllers, thus bringing back distributed
-control planes~\cite{mccauley2013extending,onos} and their current programming difficulties.
-%However, academic
-%language design and implementation efforts have not kept pace.  For instance, work on many
-%experimental SDN languages~\cite{frenetic,flowlog,vericon,merlin,netkat,kinetic,pga} has not yet shown how to implement fault tolerant
-%multi-controller systems that support their high-level abstractions efficiently.
-
-Hence, in this paper, we have two central goals:
-\begin{enumerate}
-\item Design a new, high-level language with natural abstractions
-for expressing intra-domain routing, inter-domain
-routing and routing alternatives in case of failures.
-\item Define algorithms for compiling these specifications into
-configurations for devices running standard
-distributed control plane algorithms, while ensuring correct behavior
-independent of the number of faults.
-\end{enumerate}
-
-To achieve the first goal, we borrow the idea of using regular
-expressions to specify network paths from
-recent high-level SDN languages such as FatTire~\cite{fattire},
-Merlin~\cite{foster:merlin}, and
-NetKAT~\cite{netkat}.  However, our design also contains several key
-departures from existing languages.  The most important one is semantic:  the paths specified
-can extend from outside the operator's network to inside
-the network, across several devices internally, and then out again. This design
-choice allows users to specify preferences about both external and internal
-routes in the exact same way.
-In addition, we augment the algebra
-of regular expressions to directly support a notion of {\em preferences} and provide a semantics in terms of sets of ranked paths.
-The preferences indicate fail-over behaviors:  among all specified paths that are still available,
-the system guarantees that the distributed implementation will always use the highest-ranked ones.
-Although we target a distributed implementation, the language is more general and could potentially be used in an SDN context.
-
-%We also support network operators by defining a
-%set of common abbreviations for entering, leaving, and traversing
-%the user network and we provide abstractions for managing common features %of
-%control plane algorithms such as route aggregation.  Operators use familiar logical operations
-%to build routes in a modular and compositional manner from these
-%primitives.  Our abbreviations are translated in to our regular-expression-based
-%intermediate representation and compiled from there.
-
-To achieve the second goal, we develop program analysis and compilation
-algorithms that translate the regular policies to a graph-based
-intermediate language and from there to per-device BGP configurations, which include various filters and preferences that govern BGP behavior.
-%import and export filters, local preferences, MED attributes, and community tags.
-We target BGP for pragmatic reasons:
-it is a highly flexible routing protocol,
-it is an industry standard,
-and many networks use it internally as well as externally.
-Despite the advent of SDN, many networks will continue to
-use BGP for the foreseeable future due to existing infrastructure investments, the difficulty of transitioning to SDN, and the scalability and fault-tolerance advantages of a distributed
-control plane.
-
-The BGP configurations produced by our compiler are
-guaranteed to be policy-compliant in the face of
-{\em arbitrary} failures.\footnote{In this paper we assume that BGP is the only control plane protocol running in the network or the other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This does not mean that the implementation is always
-able to send traffic to its ultimate destination
-(\EG in the case of a network partition), but rather that it always respects the
-centralized policy, which may include dropping traffic when there is no route.
-%
-In this way, we provide network operators
-with a strong guarantee that is otherwise impossible to achieve
-today.
-However, some policies simply cannot be implemented correctly in BGP in
- the presence of arbitrary failures.  We develop new
-algorithms to detect such policies
-and report our findings to the operators, so they may fix the policy
-specification at compile time rather than experience undesirable
-behavior after the configurations are deployed.
-%We also analyze route aggregation to detect the possibility of failure-induced black-holes.
-
-%These algorithms differ from
-%standard BGP analysis algorithms~\cite{feamster:rcc,batfish} because they operate on
-%our graph-based intermediate representation, which operates at a higher level
-%of abstraction than raw BGP configurations (and which has the pleasant effect of simplifying our
-%task).
-
-We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies of data center and backbone networks.
-% and compared these specifications with existing configurations.
-We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds of routers, compiling in under 9 minutes in all cases.
-
-%measured the performance of our compiler, demonstrating that our compilation
-%algorithms scale to topologies with several thousand routers.
-%
-%\dpw{The following could be cut for space.}
-%In the remainder of the paper, we review BGP (Section~\ref{sec:background}---readers
-%familiar with BGP may skip this section),
-%further motivate the need for new languages
-%for programming distributed control planes (Section \ref{sec:motivation}),
-%introduce \sysname{} by example (Section \ref{sec:propane}),
-%explain our compiler algorithms (Section \ref{sec:compilation}),
-%present several lemmas justifying the correctness of our techniques (Section \ref{sec:theory}), describe our implementation (Section \ref{sec:implementation})
-%evaluate our work  (Section \ref{sec:evaluation}) and discuss related work (Section \ref{sec:related}).
-
-%% In this paper, we ask if it is possible to program
-%% fully distributed control planes using
-%% \emph{end-to-end},
-%% \emph{network-wide} policies, while handing the job of compiling
-%% such policy.  In particular,
-%% operators should be able to directly express \emph{end-to-end},
-%% \emph{network-wide} policies directly; it is the job of a compiler
-%% to decompose such policies into individual device configurations.
-%% In addition, the resulting forwarding behavior, which emerges through device interactions, must be policy-compliant under all possible failures.
-%% If successful, this approach would combine easy programmability of centralized control planes with the failure robustness and scalability of distributed control planes.
-%% %
-%% More pragmatically, it would help many networks that, for the foreseeable future, will continue to use a distributed control plane, due to the difficulty of migrating to SDN or the inherent scalability and failure-robustness of distributed control.
-
-%% Through \sysname, our system that includes a language and a compiler, we demonstrate the feasibility of programming distributed control planes.
-We focus on BGP, a common and highly flexible way to implement distributed control planes, and show how to automatically generate router BGP configurations from network-wide policies.
-
-%% We face two challenges in designing \sysname that differ from designing a system for programming data planes~\cite{x,y,z}.
-The first is policy specification itself---specifying network {\em policies} is different from specifying network {\em paths}.
-%% %
-%% The specification must compactly capture behavior under all possible failures.
-Since there is no controller at runtime, the routers must be programmed ahead of time, based on the specification, to handle failures.
-%% %
-%% Further, many policies naturally under-specify paths (e.g., "prefer paying neighbors" is not a concrete path).
-%% %
-%% \sysname addresses this specification challenge by allowing operators to express {\em path preferences}, where preference describes a set of valid paths and less-preferred options are taken only when a higher-preference options are unavailable.
-
-%% The direct nature of \sysname specifications brings up the second challenge, of compiling them to router configurations.
-We must compute the sets of paths represented by the intersection of multiple preferences and topology, compute which ones can be honored under a given failure scenario, and ensure policy compliance under all possible failure cases.
-We handle this challenge by compactly capturing policy and topology in a {\em product graph} and developing efficient algorithms that operate on this graph.
-
-%% We evaluate \sysname by using it to encode policies of real backbone and data center networks.
-
-%% \todo{new intro is not complete}
-
-%=====================================================
-%
-%
-%  **Background**
-%
-%
-%=====================================================
-
-\section{Background on BGP}
-\label{sec:background}
-
-%Our work focuses on BGP as it is the most common and flexible way to implement distributed control planes today. In this section, we provide relevant background on BGP.
-
-BGP is a path-vector routing protocol that connects autonomous systems (ASes).
-An AS has one or more routers managed by the same administrative entity.
-ASes exchange routing announcements with their neighbors.
-Each announcement has a destination IP prefix and some attributes (see below), and it indicates that the sending AS is willing to carry traffic destined to that prefix from the receiving AS.
-Traffic flows in the opposite direction, from announcement receivers to senders.
-
-When a route announcement is received by an AS, it is processed by custom import filters that may drop the announcement or modify some attributes.
-If multiple announcements for the same prefix survive import filters, the router selects the best one based on local policy (see below).
-This route is then used to send traffic to the destination.
-It is also advertised to the neighbors, after processing through neighbor-specific export filters that may stop the announcement or modify some attributes.
-
-All routing announcements are accompanied by an AS-path attribute that reflects the sequence of ASes that the announcement has traversed thus far.
-While the AS-path attribute has a global meaning, some attributes are meaningful only within an AS or between neighboring ASes.
-One such attribute is a list of community strings.
-ASes use such strings to color routes on different criteria (e.g., ``entered on West Coast'') and then use the color later in the routing process.
-Communities are also used to signal to neighbors how they should handle an announcement (e.g., do not export it further).
-Another non-global attribute is the multi-exit discriminator (MED).
-It is used when an AS has multiple links to a neighboring AS.
-Its (numeric) values signal to the neighbor how this AS prefers to receive traffic among those links.
-
-The route selection process assigns a {\em local preference} to each
-route that survives the import filters. Routes with higher local
-preference are preferred. Among routes with the same local preference,
-other factors such as AS path length, MEDs, and internal routing cost, are considered in order.
-Because it is considered first during route selection, local preference is highly influential, and ASes may assign this preference based on any aspect of the route.
-A common practice is to assign it based on the commercial relationship with the neighbor.
-For instance, an AS may prefer in order customer ASes (which pay money), peer ASes (with free exchange of traffic), and provider ASes (which charge money for traffic).
-
-In implementing their policy, each network operator assumes that
-neighboring ASes correctly implement BGP and honor contracts related
-to MEDs and communities. \sysname makes the same assumption when
-deriving BGP configurations for a network.
-
-The combination of arbitrary import and export filters and route selection policies at individual routers make BGP a highly flexible routing protocol.
-That flexibility, however, comes at the cost of it being difficult to configure correctly.
-
-%=====================================================
-%
-%
-%  **Motivation**
-%
-%
-%=====================================================
-
-\section{Motivation}
-\label{sec:motivation}
-
-%We motivate our work by describing the current practice in network
-%configuration.
-In traditional networks with distributed control planes, the operators' goal is to generate the configuration of individual devices based on their desired policy.
-This configuration dictates the behavior of a device, how it exchanges routing information with neighbors and how it filters and ranks that information.
-The collective behavior of the devices should implement the desired policy.
-%
-%Device configuration languages are low-level and indirect.
-For instance, instead of allowing operators to express directly the paths they want through the network, they require operators to specify metrics that result in those paths; instead of allowing operators to express directly the types of traffic to not carry through the network, they require operators to select and program an appropriate filtering mechanism (e.g., BGP import or export filters, null routing,  access control lists) and instantiate it on topologically appropriate devices; instead of allowing operators to directly specify that they prefer BGP neighbors in a certain order, they require operators to program local preferences and multi-exit discriminators (MED) at each router and ensure that the numbers are consistent across routers.
-%
-%In many networks today, device configurations are generated manually by operators, without the support of many automated tools.
-It is easy to see the problems with this approach, such as typos, inconsistency across devices, and no guarantees of policy compliance.
-%
-%To reduce such problems, some networks use a template-based approach.
-Configuration templates abstract certain constants into variables (e.g., instead of concrete community value, they may contain a variable {\small \sf{\$$BadNeighbor$)}} and may use a device vendor-neutral syntax.
-Operators manually generate the templates and use tools to translate them into device configuration, by replacing variables with appropriate constants using a database of network information.
-%
-% %and replacing vendor-neutral constructs with their vendor-specific counterparts.
-%
-%%In practice, most networks use a hybrid of templates and manual generation of device configuration.
-Templates are used for standardized and common configuration elements across devices and the result is manually tweaked to obtain the exact desired network behavior.
-%
-%While templates avoids some pitfalls of the fully manual approach, they too are far from ideal.
-The fundamental issue is the semantic mismatch between desired policies and the level of abstraction of templates.
-While many policies are network-wide (e.g., prefer customer networks, or never announce a route to a certain prefix to external neighbors), templates are device-level.
-Operators must still manually decompose network-wide policies into device-level policies that can produce the desired network-wide behavior.
-%This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures.
-We illustrate this point using two examples based on policies that we have seen in practice and we demonstrate the ease with which the
-%examples are described using our new language \sysname.
-
-%Operators today generate the BGP configuration of individual devices based on intended policy. 
-When generating BGP configurations, whether fully manually or aided by templates, the operators face the challenge of decomposing network-wide policies
-into appropriate device-level policies.
-This decomposition is not always straightforward and ensuring policy-compliance is tricky, especially in the face of failures.
-We illustrate this point using two examples based on policies that we have seen in practice.
-The next section shows how \sysname allows operators to directly express these policies.
-%the ease with which the
-%policies can be specified using our new language \sysname.
-%The next section describes how to automatically compile this specification to device-level policies.
-
-\subsection{Example 1:  The Backbone}
-
-Consider the backbone network in Figure~\ref{fig:example1}. It has
-three neighbors, a customer \CD{Cust}, a peer \CD{Peer}, and a provider \CD{Prov}.
-The policy of this network is shown on the right.
-It prefers the neighbors in a certain order (P1) and does not want to act as a transit between \CD{Peer} and \CD{Prov} (P2).
-It prefers to exchange traffic with \CD{Cust} over \CD{R1} rather than \CD{R2} because \CD{R1} is cheaper (P3).
-To guard against another AS "hijacking" prefixes owned by \CD{Cust}, it only sends traffic to them if \CD{Cust} is on the AS path (P4).
-Finally, to guard against \CD{Cust} accidentally becoming a transit for \CD{Prov}, it does not use \CD{Cust} for traffic that will later traverse \CD{Prov} (P5).
-
-To implement P1 of the policy, the operators must compute and assign
-local preferences such that preferences at \CD{Cust}-facing interfaces
-$>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
-the same time, to satisfy P3 the preference at \CD{R2}'s
-\CD{Cust}-facing interface should be lower than that at
-\CD{R1}. Implementing P3 properly will require MEDs to be appropriately configured. 
-To implement P2, the operators can assign communities that
-indicate where a certain routing announcement entered the
-network. Then, \CD{R4} must be configured to not announce to
-$\CD{Peer}$ routes that have communities that correspond to the
-\CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links.
-Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based filters at each router.
-
-Clearly it is difficult to properly configure even this
-small example network manually; devising correct configurations for real networks can quickly become a nightmare.
-Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several neighbor- or prefix-based exceptions to the default behavior.
-A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
-Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually. 
-%\sysname lets operators express such policies easily and intuitively.
-It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=\columnwidth]{figures/example1}
-  \caption{Creating router-level policies is difficult.}
-  \label{fig:example1}
-  \vspace{-1em}
-\end{figure}
-
-\subsection{Example 2:  The Data Center}
-
- While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible.
-Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally.
-This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally.
-Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}.
-The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.
-
-The operator may decide that a simple way to implement the policy is to have X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ announce what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}.
-This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can be done independently (e.g., new prefixes can be assigned to local services without updating router configurations).
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=\columnwidth]{figures/example2}
-  \caption{Policy-compliance under failures is difficult.}
-  \label{fig:example2}
-  \vspace{-1em}
-\end{figure}
-
-However, this implementation does not have the right behavior in the face of failures.
-Suppose links X--G and X--H fail.
-Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D.
-Per policy implementation, X will start "leaking" these prefixes externally.
-Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are used for other services outside of the data center).
-This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter.
-A similar problem will happen if links Y--G and Y--H fail.
-%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
-Link failures in data centers are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.
-
-To avoid this problem, the operator may decide to disallow "valley" paths, i.e., those that go up, down, and back up again.
-This guard can be implemented by $X$ and $Y$ rejecting paths through the other.
-But that creates a different problem in the face of failures---an aggregation-induced blackhole~\cite{route-aggregation}.
-If links D--A and X--C fail, X will hear announcements for \CD{PG2} from D and will thus announce the \CD{PG} externally.
-This announcement will bring to X traffic for \CD{PG1} as well, but because of valley-free filtering, X does not have a valid route for \CD{PG1} and will thus drop all traffic to it.
-
-Thus, we see that devising a configuration that ensures policy compliance in the face of failures is complex and error-prone.
-\sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures (if that is possible; otherwise, it generates a compile-time error).
-For aggregation, it also provides a lower bound to operators on the number of failures under which aggregation will not result in blackholes.
-
-%\subsection{OLD -- Overview}
-%\todo{this subsection can be deleted once we have captured everything in it}
-%
-%Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention).
-%Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
-%
-%\begin{itemize}
-% \item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
-% \item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
-% \item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
-% \item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
-% \item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
-%\end{itemize}
-%
-%
-%Possible Examples:
-%\begin{itemize}
-% \item Basic datacenter with spine preference
-% \item Simple AS that prefers customers over peers over providers
-% \item Combined internal backup routing with preference based entrance into the network using aggregation.
-% \item Something like cold potato routing
-%\end{itemize}
-
-%=====================================================
-%
-%
-%  **Propane Language**
-%
-%
-%=====================================================
-
-\section{Propane overview}
-\label{sec:propane}
-
-Policies for (distributed) control planes differ from data-plane
-policies in a few important ways. First, control-plane
-policies must account for all failures at compile time; there is
-no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
-%
-In \sysname, we enable such specifications through a notion of {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
-%
-Second, paths in a control-plane policy may be under-specified (e.g.,
-"prefer customer" does not indicate a concrete path). The \sysname
-compiler treats such under-specifications as constraints on the set of
-allowed paths and automatically computes valid sets based on topology.
-%
-
-In the rest of this section, we define \sysname policies for the two 
-examples from the previous section, introducing key aspects of
-the \sysname language along the way. The complete syntax of the
-language as well as our strategy for compiling \sysname policies to
-BGP is defined in the next section.
-
-\subsection{Example 1: The Backbone}
-
-%\sysname simplifies network configuration by allowing users to
-%specify end-to-end forwarding paths and associating them with
-%appropriate prefixes.  The \sysname compiler handles the task of
-%generating low-level BGP configurations consistent with the user's
-%specifications.  It automatically synthesizes
-%import-export filters, local preferences, MED attributes, and community tags
-%to ensure policy compliance under all possible failure scenarios.
-
-\sysname allows operators to configure the network with the
-abstraction that they have centralized control over routing.
-Specifically, the operator simply provides a set of high-level constraints
-that describe the 
-different routes traffic may (or may not) take and their relative preferences.
-\sysname specifications are written modularly via a series
-of declarations.
-%These definitions allow users to express the three
-%major elements of any \sysname specification:  \emph{prefixes},
-%\emph{paths} and \emph{policies}.
-For example, to begin specification of the backbone
-network from the previous section, we first express the idea that for routes leading to our customer,
-we prefer using \CD{R1} over \CD{R2} (policy P3 from Figure~\ref{fig:example1}):
-%\begin{lstlisting}[mathescape=true]
-%define ExitCust = $exit(R_1 \gg R_2)$
-%\end{lstlisting}
-\begin{code}
-\Define ExitCust = \Exit(R1 \Prefer R2)
-\end{code}
-This  statement defines a set of \emph{ranked paths}, which includes
-all paths (and only those paths) for which traffic exits our network
-through either router \CD{R1} or \CD{R2}.  The paths that exit through \CD{R1}
-are preferred (\Prefer) to those that exit through \CD{R2}.  As we
-describe in the next section, the \Exit\ predicate, as well as other
-path predicates used later in this section, is simply a shorthand for 
-a particular regular expression over paths that is expressible in our policy
-language.
-
-% DAVE CONVERSIONS
-% C_{pfx} ===> PCust
-% I_{pfx} ===> PInternal
-
-To associate ranked paths with
-one or more prefixes, we define a \sysname \emph{policy}.
-Within a policy, statements with the form $t$\Path$p$
-associate the prefixes defined by the predicate $t$ with the set of
-ranked paths defined by the path expression $p$.  In general,
-prefix predicates can be defined by arbitrary boolean combinations
-(and, or, not) of concrete prefixes and community tags.  Here,
-we assume we have already defined predicates \CD{PCust} for the
-customer prefixes and \CD{PInt} for our internal prefixes.
-In the following code, ranked paths are associated with
-customer prefixes, internal prefixes,
-and all other prefixes (\CD{true}).\footnote{Policy statements are processed in
-order with earlier policy statements taking precedence over later
-policy statements.  Hence, when the prefix predicate \True{} follows
-statements involving \CD{PCust} and \CD{PInt}, it is interpreted as
-\CD{\True{} \AND{} \NOT{}PCust \AND{} \NOT{}PInt}.}
-
-%% \begin{lstlisting}[mathescape=true]
-%% define Routing = {
-%%     $\path{C_{pfx}}{ExitCust \gg end(Cust)}$
-%%     $\path{I_{pfx}}{end(in)}$
-%%     $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
-%% }
-%% \end{lstlisting}
-
-\begin{code}
-\Define Routing = 
-    \{PCust \Path ExitCust \Prefer \End(Cust)
-     PInt  \Path \End(\In)
-     \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)\}
-\end{code}
-\noindent
-Line 2 of this policy 
-defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
-that connections to the customer through both routers fail,
-a backup route (\CD{\End(Cust)}) is defined that admits traffic along
-any path (including those through other networks) that ends at the customer.
-Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \In{} represents any location
-inside the user's network and the keyword \Out{} represents any location
-outside the user's network.
-Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers. To summarize our progress, the \CD{Routing} policy
-implements P1, P3, and P4 from Figure~\ref{fig:example1}.
-
-Since by default routing allows transit traffic (\EG, traffic entering from
-\CD{Peer} and leaving through \CD{Prov}), we separately define a
-policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
-disjunction (\OR) and negation (\NOT) of constraints. 
-%union (\Union), intersection (\Intersect), and negation (\NOT) to
-%specify the appropriate sets of paths.
-%
-%% \begin{lstlisting}[mathescape=true]
-%% define PP = Peer or Prov
-%% define PPTransit = $enter(PP) \AND exit(PP)$
-%% define CustTransit = $later(Cust) \AND later(Prov)$
-
-%% define NoTransit = {
-%%     $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
-%% }
-%% \end{lstlisting}
-\begin{code}
-\Define PP = Peer \OR Prov
-\Define PPTrans   = \Enter(PP) \AND \Exit(PP)
-\Define CustTrans = \Later(Cust) \AND \Later(Prov)
-\Define NoTrans   = \{\True \Path \NOT{}PPTrans \AND \NOT{}CustTrans\}
-\end{code}
-\noindent
-The \CD{NoTrans} constraint above says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}.
-Similarly it prevents traffic from ever following paths that leave our network and later passing through both \CD{Prov} and \CD{Cust}.
-To implement both \CD{Routing}
-and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
-%
-%% \begin{lstlisting}[mathescape=true]
-%% Routing $\AND$  NoTransit
-%% \end{lstlisting}
-%
-These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
-MED attributes, and community tags to ensure that the policy is
-implemented correctly under all failure cases.
-
-\subsection{Example 2: The Data Center}
-
-In our data center,
-there are three main concerns:
-(1) traffic for the prefix block allocated to each top-of-rack router must be able to reach that router,
-(2) local services must not leak outside the data center, and
-(3) aggregation must be performed on global prefixes to reduce churn
-in the network.
-
-\sysname allows us to specify each of these constraints modularly.
-The first constraint is about prefix ownership---namely, we only want traffic for certain prefixes to end up at a particular location.
-The following definition captures this intent.
-
-%% \begin{lstlisting}[mathescape=true]
-%% define Ownership = {
-%%     $\path{p_{g1}}{end(A)}$
-%%     $\path{p_{g2}}{end(B)}$
-%%     $\path{p_{l1}}{end(E)}$
-%%     $\path{p_{l2}}{end(F)}$
-%% }
-%% \end{lstlisting}
-
-\begin{code}
-\Define Ownership = 
-    \{PG1 \Path \End(A)
-     PG2 \Path \End(B)
-     PL1 \Path \End(E)
-     PL2 \Path \End(F)
-     \True \Path \End(\Out)\}
-\end{code}
-\noindent
-In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
-end at router \CD{A}; traffic matching \CD{PG2},
-but not \CD{PG1}, must
-end at router \CD{B}; and so on.
-Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location.
-For the second constraint, we can define another policy:
-
-%% \begin{lstlisting}[mathescape=true]
-%% define Routing = {
-%%     $\path{p_{g*}}{any}$
-%%     $\path{p_{l*}}{\NOT enter(out)}$
-%%     $\path{true}{exit(out)}$
-%% }
-%% \end{lstlisting}
-\begin{code}
-\Define Locality = 
-    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
-\end{code}
-\noindent
-%The first line states that there is no restriction (\Any)
-%on how traffic must traverse the network for global prefixes.
-%aside from the default restriction
-%that traffic must not pass through the user's network and then loop
-%back on itself. 
-%This means traffic for
-%\CD{PG*} may be sent either from other data center routers or
-%from external ASes. 
-The locality constraint ensures that traffic for local
-prefixes only ever follows paths that are internal to the network at each hop. 
-This constraint guarantees that the services remain reachable only to locations
-inside the data center.
-
-As in the backbone example, we can logically conjoin these constraints
-to specify the network-wide policy.
-In addition to constraints on the shape of paths,
-\sysname allows the operator to specify constraints on the BGP control plane.
-For instance, a constraint on aggregation is included to ensure that
-aggregation for global prefixes is performed from
-locations inside (\In) the network to locations outside (\Out). 
-In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG} 
-(which we assume is defined earlier using an appropriate prefix such 
-as \CD{74.3.28.0/24})
-when advertised outside the datacenter.
-
-\begin{code}
-Ownership \AND{} Locality \AND{} \Agg(PG, \In \Link \Out)
-\end{code}
-
-As before, once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. \sysname also ensures safety against aggregation-induced black holes.
-%It can efficiently determine a lower bound on the number of failures necessary to black hole traffic given the user's policy, topology, and placement of specific aggregates.
-
-%%%%OLD TEXT BELOW
-%
-%\section{Propane}
-%\label{sec:propane}
-%
-%\sysname simplifies network configuration by automatically generating low-level BGP configurations from a high-level specification of the network's routing policy.
-%%
-%The operator configures the network with the abstraction that he or she has centralized control over routing and uses a set of high-level constraints to describe the different routes traffic may (or may not) take and their relative preferences.
-%%
-%The \sysname compiler generates BGP configurations for each device in the network that operate in a completely distributed fashion and are correct by construction -- automatically synthesizing import/export filters, local preference and MED attributes, and community tags to ensure policy compliance under all possible failure scenarios.
-%%
-%We now demonstrate \sysname by showing how to configure the networks from the previous examples.
-%
-%\para{Example 1}
-%
-%We now show how to write the routing policy for the backbone network in Section~\ref{sec:motivation}.
-\sysname allows to address each of the requirements in turn.
-First we address requirements (P1), (P3), and (P4) that customers are preferred over peers over providers, and that a customer appear on the path for its prefix.
-The following \sysname code accomplishes these two objectives:
-%
-%\begin{lstlisting}[mathescape=true]
-%define ExitCust = $exit(R_1 \gg R_2)$
-%
-%define Routing = {
-%    $\path{C_{pfx}}{ExitCust \gg end(Cust) }$
-%    $\path{I_{pfx}}{end(in)}$
-%    $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
-%}
-%\end{lstlisting}
-%
-%The first definition defines paths that exit our network to the customer.
-The statement $exit(R_1 \gg R_2)$ restricts us to paths that leave our network through either router $R_1$ or $R_2$, with a preference for $R_1$.
-%The first line of the \textsf{Routing} policy ensures that traffic destined for customer prefixes ($C_{pfx}$) either leaves the network directly to the customer (with a preference for leaving through $R_1$), or simply ends at the customer.
-Not leaving directly to the customer by going through \textit{Peer} or \textit{Prov} is less preferred than leaving directly, and thus serves as a backup route in a direct route is not available.
-%
-%The second line state that traffic for internal prefixes $I_{pfx}$ must end in our network, and is otherwise unconstrained.
-The last line applies to any other traffic, and allows for any routes that leave through a peer with a preference for customers over peers over providers.
-While this still allows transit traffic (e.g., traffic can enter from \textit{Peer} and leave through \textit{Prov}), we can restrict this behavior separately as follows:
-%
-%\begin{lstlisting}[mathescape=true]
-%define PP = Peer or Prov
-%define PPTransit = $enter(PP) \wedge exit(PP)$
-%define CustTransit = $later(Cust) \wedge later(Prov)$
-%
-%define NoTransit = {
-%    $\path{true}{\neg PPTransit \wedge \neg CustTransit}$
-%}
-%\end{lstlisting}
-%
-%The \textsf{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied.
-In particular, it says that, for any prefix, traffice should never both enter and exit the network from \textit{Peer} or \textit{Prov}.
-Similarly it prevents traffic from ever following paths that leave our network and later go through both \textit{Prov} and \textit{Cust}.
-%
-%\begin{lstlisting}[mathescape=true]
-%Routing $\wedge$  NoTransit
-%\end{lstlisting}
-%
-%The final policy is simply the conjunction of the routing and no transit constraints.
-\sysname will generate per-device import and export filters, local preferences and MED attributes, and community tags to ensure that the policy is met under all failure scenarios.
-%
-%
-%\para{Example 2}
-%
-%Consider again the datacenter from Section~\ref{sec:motivation}.
-In this example, there are primarily three main concerns: (1) traffic for the prefix block allocated to each top-of-rack router can reach that router, (2) local services do not leak outside the datacenter, and (3) aggregation is performed on global prefixes to reduce churn in the network.
-%
-%\sysname allows us to decompose and specify each of these constraints in a modular fashion.
-The first constraint is about prefix ownership -- namely, that we only want traffic for certain prefixes to end up at a particular locations.
-The following definition in propane captures this intent:
-%
-%\begin{lstlisting}[mathescape=true]
-%define Ownership = {
-%    $\path{p_{g1}}{end(A)}$
-%    $\path{p_{g2}}{end(B)}$
-%    $\path{p_{l1}}{end(E)}$
-%    $\path{p_{l2}}{end(F)}$
-%}
-%\end{lstlisting}
-%
-%The constraints in the ownership task are read in a top-down fashion.
-Traffic for prefix $p_{g1}$ is only allowed to to follow paths that end at router A.
-Similarly, traffic not matching $p_{g1}$, but which matches $p_{g2}$ must end at router B and so on.
-%%
-%To capture the second constraint, we can define another task for the core routing policy:
-%
-%\begin{lstlisting}[mathescape=true]
-%define Routing = {
-%    $\path{p_{g*}}{any}$
-%    $\path{p_{l*}}{\neg enter(out)}$
-%    $\path{true}{exit(out)}$
-%}
-%\end{lstlisting}
-%
-%The first line states that there is no restriction on how traffic must traverse the network for global prefixes.
-This means traffic for $p_{g*}$ may be sent either from other routers in the datacenter, or from external ASes.
-The second line ensures that traffic for local prefixes never enters the network from an outside location.
-This  guarantees that the services remain reachable only to locations internal to the data center.
-%
-%Finally, we can combine these constraints logically to specify the network-wide policy:
-%
-%\begin{lstlisting}[mathescape=true]
-%Ownership $\wedge$ Routing $\wedge$ agg($p_{agg}$, $in \rightarrow out$)
-%\end{lstlisting}
-%
-%
-%In addition to constraints on the shape of paths, \sysname allows the operator to specify constraints on the BGP control plane.
-Above, a constraint on aggregation is included to ensure that an aggregation for $p_{agg}$ is performed from locations inside the network to locations outside the network.
-%
-%Once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. Similarly, it can check for aggregate-induced black holes up to $k$ failures.
-%
-
-%=====================================================
-%
-%
-%  **Compilation**
-%
-%
-%=====================================================
-
-\section{Compilation}
-\label{sec:compilation}
-
-The front-end (FE) of \sysname simplifies operators' task of describing preferred paths.
-That simplicity, however, comes at the cost of compilation complexity.
-The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology, determine which ones can be honored under failures, and ensure policy compliance under all possible failure cases.
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=.75\columnwidth]{figures/pipeline}
-  \caption{Compilation pipeline stages for Propane.}
-  \label{fig:pipeline}
-  \vspace{-1em}
-\end{figure}
-
-We handle these challenges by breaking compilation into multiple stages and developing efficient algorithms for each (See Figure~\ref{fig:pipeline}).
-The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR).
-Policies in RIR are checked for well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR).
-The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions.
-We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes.
-Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation.
-Vendor-specific adaptors to translate from ABGP to concrete device configurations are easily added to generate concrete configurations.
-
-\subsection{Regular IR (RIR)}
-\label{sec:rir}
-
-%Regular expressions are an expressive formalism that have been used extensively for describing paths through graphs~\cite{bib:todo}, with applications to networks~\cite{bib:todo}.
-Our regular expression language differs from others by allowing operators to describe preferences between paths.
-
-% grammar
-\newcommand{\BNFALT}{\;\;|\;\;}
-\newcommand{\hdr}[2]{\flushleft \chdr{\hspace{5mm}#1}{#2}}
-\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}
-
-\begin{figure*}\small
-  \begin{minipage}[t]{.45\linewidth}
-  \hdr{\large Syntax}{}
-  \vspace*{-1\baselineskip}
-  %
-  \[ \begin{array}{rclr}
-    \hline
-
-     pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
-     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{preferences} \\
-     x       &::=& a.b.c.d/n & \textit{prefix} \\
-     c       &::=& \cdots & \textit{community value} \\
-     t       &::=& \True & \textit{true} \\
-         &\BNFALT& \NOT t & \textit{negation} \\
-         &\BNFALT& t_1 \OR{} t_2 & \textit{disjunction} \\
-         &\BNFALT& t_1 \AND{} t_2 & \textit{conjunction} \\
-         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
-         &\BNFALT& \textit{comm} = c & \textit{community test} \\
-     r       &::=& n & \textit{AS number} \\
-         &\BNFALT& \emptyset & \textit{empty set} \\
-         &\BNFALT& \In & \textit{internal loc} \\
-         &\BNFALT& \Out & \textit{external loc} \\
-         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
-         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
-         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
-         &\BNFALT& \NOT(r) & \textit{path negation} \\
-         &\BNFALT& r^* & \textit{repetition} \\
-     l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
-     cc     &::=& agg(x, l) \BNFALT tag(c, t, l) & \textit{control constraints} \\
-  \end{array} \]
-
-  \end{minipage}
-  %
-  ~~
-  \vrule
-  ~~
-  %
-  \begin{minipage}[t]{.5\linewidth}\small
-  \hdr{\large Propane Expansions}{}
-  \vspace*{-1\baselineskip}
-  %
-  \[\begin{array}{rcl}
-    \hline
-    \Any           & = & \Out^* \cdot \In^+ \cdot \Out^* \\
-    \None          & = & \emptyset \\
-    \Internal      & = & \In^+ \\
-    \Only(X)       & = & \Any \cap X^* \\
-    \Never(X)      & = & \Any \cap (!X)^* \\
-    \Through(X)    & = & \Out^* \cdot \In^* \cdot X \cdot \In^* \cdot \Out^* \\
-    \Later(X)      & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
-    \Before(X)     & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
-    \End(X)        & = & \Any \cap (\Sigma^* \cdot X) \\
-    \Start(X)      & = & \Any \cap (X \cdot \Sigma^*) \\
-    \Exit(X)       & = & (\Out^* \cdot \In^* \cdot (X \cap \In) \cdot \Out \cdot \Out^*) \cup \\
-                  &        & (\Out^* \cdot \In^+ \cdot (X \cap \Out) \cdot \Out^*) \\
-    \Enter(X)      & = & (\Out^* \cdot \Out \cdot (X \cap \In) \cdot \In^* \cdot \Out^*) \cup \\
-                  &        & (\Out^* \cdot (X \cap \Out) \cdot \In^+ \cdot \Out^*) \\
-    \LinkKW(X,Y)     & = & \Any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
-    \PathKW(\vec{X}) & = & \Any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
-    \Novalley(\vec{X}) & = & \Any ~ \cap \\
-                  &   & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
-                  &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
-  \end{array} \]
-
-  \end{minipage}
-
-  \hrulefill
-
-  \caption{Regular Intermediate Language (RIL) syntax (left), and
-           Propane language expansions (right).}
-  \label{fig:rir-syntax}
-  \vspace{-1em}
-\end{figure*}
-
-\para{Syntax}
-The \sysname FE is just a thin layer atop a core, regular-expression language (RIR) for describing preference-based path constraints. 
-Figure~\ref{fig:rir-syntax} shows the RIR syntax.
-A policy consists of one or more constraints, each of which have a test on the type of route, and a corresponding set of preferred regular paths.
-Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS.
-Special \In{} and \Out{} symbols refer to any internal or external location respectively.
-In addition, $\Sigma$ refers to any symbol.
-We also use other standard abbreviations
-for regular expressions such as $r^+$, a sequence of one or more occurrences
-of $r$, when appropriate.
-%% For example, the constraint
-%% \[(\textit{prefix}=74.3.28.0/24) \Link \\
-%% (as200 \cdot \In^+) \Prefer (as100 \cdot \In^+)
-%% \]
-%% describes a more-preferred set of paths for traffic announced by a prefix no less specific than \CD{74.125.28.0/24}, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same.
-The plus operator $\In^+$ stands for $\In \cdot \In^*$, at least one internal hop.
-Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.
-
-\sysname also supports constraints purely on the control-plane behavior of BGP. For example, prefix aggregation is an important optimization to reduce routing table size and churn in practice. 
-%% Aggregation, for example, from internal to external locations, is specified using the same regular syntax as before:
-%% $$\Agg(128.17.0.0/16, \In \Link \Out)$$
-%% where the expression $\In \Link Out$ refers to control messages flowing from any internal to any external location.
-We list only the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, but we also support other constraints such as limiting the maximum number of routes allowed between ASes, or enabling BGP multipath.
-
-\para{Semantics}
-
-The semantics of RIR is in terms of ranked paths.
-Each preference-based regular path constraint (of the form $r_1 \Prefer \dots \Prefer r_j$) maps to a set of concrete paths in the network that match one of $r_i$.
-We denote a network path as a string of abstract locations (routers or external ASes) of the form: $n_1 n_2 \dots n_k$.
-A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$, that is the path is in the language of the regular expression, and $p$ is a topologically-valid path.
-We denote the length of a path $p$ as $\abs{p}$.
-A path $p$ will have a rank:
-$$(\min_i \set{ p \in \mathcal{L}(r_i) }, \abs{p})$$
-where the rank is lexicographically ordered according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the path length.
-Lower ranks indicate \emph{more} preferred paths.
-Traffic may be sent on any of the most preferred paths for each pair of starting and ending locations that appear in some specified path.
-There is an implicit lowest preference to drop traffic: $\emptyset$ when no other route is possible.
-
-The set of ranked paths depends on which paths are valid in the topology, and thus when failures occur, the most preferred routes change.
-The \sysname compiler ensures that generated configurations for a policy always achieve the most preferred path possible given the failures in the topology, using only distributed mechanisms.
-
-\para{Propane FE to RIR}
-
-The main differences between the FE and RIR are: $i)$ FE allows the programmer to specify constraints using a series of (modular) definitions, and combine them later, $ii)$ FE provides high-level names that abstract sets of routes and groups of prefixes/neighbors, and $iii)$ FE allows the preference operator to be used more flexibly.
-
-A key constraint when translating FE to RIR is to ensure that all specified routes are well-formed.
-In particular, each regular path constraint $r$ must satisfy $r \subseteq \Out^* \cdot \In^+ \cdot \Out^*$.
-This ensures that the user only control traffic that goes through the user's network at some point, and that such traffic does not loop back multiple times to the user network.
-
-The translation from \sysname to RIR is based on a set of rewriting rules.
-The first step merges separate constraints.
-It takes the cross product of per-prefix constraints, where logical conjunction ($a \AND b$) is replaced by intersection on regular constraints ($a \Intersect b$), logical disjunction is replaced by union, and logical negation ($\NOT a$) is replaced by ($\Any \cap \NOT(a)$), where $\Any$ ensures the routes are well-formed.
-%
-For example, in the data center configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:
-
-%% \begin{lstlisting}[mathescape=true]
-%% $\path{p_{g1}}{any \cap end(A)}$
-%% $\path{p_{g2}}{any \cap end(B)}$
-%% $\path{p_{l1}}{\neg enter(out) \cap end(E)}$
-%% $\path{p_{l2}}{\neg enter(out) \cap end(F)}$
-%% $\path{true}{exit(out)}$
-%% \end{lstlisting}
-
-\begin{code}
-PG1 \Path \End(A)
-PG2 \Path \End(B)
-PL1 \Path \textbf{only}(\In) \Intersect \End(E)
-PL2 \Path \textbf{only}(\In) \Intersect \End(F)
-\True \Path \Exit(\Out)
-\end{code}
-
-The next step rewrites the high-level constraints such as \textit{enter} according to the equivalences in Figure~\ref{fig:rir-syntax}.
-Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression.
-For example, the regular expression $a \cdot (b \Prefer c) \cdot d$ is lifted to $(a \cdot b \cdot d) \Prefer (a \cdot c \cdot d)$ by distributing the preference over the sequence operator.
-In general, we employ the follwing distributivity equivalences:
-%
-\[ 
-\begin{array}{c}
-  x \odot (y_1 \Prefer \dots \Prefer y_n) = (x \odot y_1) \Prefer \dots \Prefer (x \odot y_n) \\
-  (y_1 \Prefer \dots \Prefer y_n) \odot x = (y_1 \odot x) \Prefer \dots \Prefer (y_n \odot x)
-\end{array}
-\]
-%
-where $\odot$ stands for an arbitrary regular binary operator. Preferences nested under a unary operator, \textit{star} or \textit{negation}, are flagged by the compiler as invalid policies.
-
-\subsection{Product Graph IR}
-
-\newcommand{\state}[4]{\node[state,#3](#1)[#4]{#2};}
-\newcommand{\transition}[4]{\path[->] (#1) edge [#4] node {#3} (#2);}
-
-\begin{figure*}
-  \begin{minipage}[t]{.5\linewidth}
-
-  \hdr{\large Topology}{}
-  \vspace*{-2\baselineskip}
-
-  \includegraphics[width=.6\columnwidth]{figures/topology}
-
-  \hdr{\large Policy Automata}{}
-  \vspace*{-0.5\baselineskip}
-
-  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.4cm,minimum size=1cm]
-    \state{0}{$0$}{              }{}
-    \state{1}{$1$}{right of=0}{}
-    \state{2}{$2$}{right of=1}{}
-    \state{3}{$3$}{right of=2}{}
-    \state{4}{$4$}{right of=3}{}
-    \state{5}{$5$}{right of=4}{accepting}
-    \transition{0}{1}{out}{}
-    \transition{1}{2}{D}{}
-    \transition{2}{3}{C}{}
-    \transition{3}{4}{A}{}
-    \transition{4}{5}{W}{}
-  \end{tikzpicture}
-
-  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.6cm]
-    \state{0}{$0$}{              }{}
-    \state{1}{$1$}{right of=0}{}
-    \state{2}{$2$}{right of=1}{}
-    \state{3}{$3$}{right of=2}{}
-    \state{4}{$4$}{right of=3}{accepting}
-    \transition{0}{1}{out}{}
-    \transition{1}{2}{in}{}
-    \transition{2}{2}{A,C,D,E}{loop above}
-    \transition{2}{3}{B}{}
-    \transition{3}{3}{B}{loop above}
-    \transition{3}{2}{A,C,D,E}{bend left}
-    \transition{3}{4}{W}{}
-  \end{tikzpicture}
-  \end{minipage}
-  %
-  ~~
-  ~~
-  %
-  \begin{minipage}[t]{.5\linewidth}
-  \hdr{\large Product Graph IR}{}
-  \vspace*{-1\baselineskip}
-  %
-  \includegraphics[width=.65\columnwidth]{figures/productgraph}
-  \end{minipage}
-
-  \hrulefill
-  \vspace*{.4em}
-
-  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
-  \label{fig:example-compilation}
-  \vspace{-1em}
-\end{figure*}
-
-Now that the user policy exists in a simplified form, we must consider topology.
-In particular, we want a compact representation that describes all the possible ways BGP route announcements can flow through the network subject to the policy and topology constraints.
-Our PGIR captures these dependencies by ``intersecting" each of the regular automata corresponding to the RIR path preferences, and the topology.
-Paths through the PGIR correspond to real paths through the topology that satisfy the user constraints.
-
-%Finding paths through a graph subject to regular constraints has been studied extensively in the database literature~\ref{bib:todo}, and has been applied to networks in the past~\ref{bib:todo}.
-
-\para{Formal definition}
-
-% Formally define automata
-The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$.
-While paths talk about the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated (i.e., route announcements flowing in the opposite direction).
-To capture this idea, for each regular expression $r_i$, we construct a deterministic finite state machine on the reversed regular expression.
-Each automaton is a tuple: ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ consists of all all abstraction locations (routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
-%
-% Formally define topology
-The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$, and a set of directed edges $E \colon 2^{V \times V}$.
-%
-% Formally define product graph
-The combined PGIR is a tuple: ($V'$, $E'$, $s$, $e$, $P$) with
-vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
-edges $E' \colon 2^{V' \times V'}$,
-a unique starting vertex $s$,
-a unique ending vertex $e$,
-and a preference function $P \colon V \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of preference ranks.
-For a vertex $v' = (v, \dots) \in V'$, we say $loc(v') = v$. 
-Two nodes $x$ and $y$ \emph{shadow} each other in the product graph when $x \in V'$ and $y \in V'$ and $loc(x) = loc(y)$ but $x \neq y$.
-That is, $x$ and $y$ shadow each other when they are different nodes in the PGIR that represent the same topology location.
-
-\para{From RIR To PGIR}
-
-% Formal product construction
-Let $a_i$ and $b_i$ denote states in the regular policy automata.
-The PGIR is constructed by adding an edge from $v_1 = (x, a_1, \dots, a_m)$ to $v_2 = (y, b_1, \dots, b_m)$ whenever $\sigma_i(a_i, y) = b_i$ for each $i$ and $(x,y) \in E$ is a valid topology link.
-%
-Additionally, we add edges from the start node $s$ to any $v = (x, a_1, \dots, a_m)$ when $\sigma_i(q_{0_i}, x) = a_i$ for each $i$.
-%
-The preference function $P$ for node $v = (x, a_1, \dots, a_m)$ is defined as $P(v) = \set{i~\vert~a_i \in F_i} $.
-That is, it records which preferences are achieved from each policy automaton for every node in the product construction.
-%
-Finally, there is an edge from each node in the PGIR such that $P(v) \neq \emptyset$ to the special end node $e$.
-
-Intuitively, PGIR tracks which states of each automaton the policy is in as route announcements move between routers.
-%
-Consider the topology in Figure~\ref{fig:example-compilation}.
-Suppose we want a primary route from W that enters the network from $A$, and utilizes the A--C and C--D links.
-We also want a backup route that enters from $B$, and utilizes the B--C link, but is otherwise unconstrained.
-For simplicity, we assume that the route can end in either $X$, $Y$, or $Z$.
-The RIR for the policy is:
-%
-$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$$
-%
-Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
-%
-The figure also shows the PGIR after intersecting the topology and policy automata.
-Every path in it corresponds to a concrete path in the topology.
-In particular, every path through the PGIR that ends at a node $v$ such that the preference function $P(v) = \set{i_1, \dots, i_m}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_m$.
-%
-For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining the most prefered preference $1$.
-BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
-This is reflected in the product graph by the node with state $(X,1,1)$.
-From here, if X were to advertise this route to D, it would result in the path $D \cdot X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
-%
-The ``--" state indicates the corresponding automaton can not accept the current path or any extension of it.
-Since node $(W,5,-)$ is in an accepting state for the first automata, it indicates this path has preference 1.
-
-\para{Minimization}
-
-Before checking if policies captured by the PGIR are safe, we minimize the PGIR to improve our safety analysis. 
-The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops.
-In particular, BGP's loop prevention mechanism forces an AS to reject any route for which it is already in the AS path.
-%
-For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path, leading to a path that satisfies the preference 1 policy, but which contains a loop.
-%
-It often improves the precision of the failure-safety analysis to eliminate cases that are not possible due to loops. 
-%For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
-We use graph dominators~\cite{tarjan-dominance} as a cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
-In the PGIR, a node $x$ dominates a node $y$ if $x$ appears on every path leading to $y$ from the start node.
-%We can safely remove any PGIR node or edge as long as it never appears on any \emph{simple} path from the \textit{start} node to the \emph{end} node. 
-For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is never on a simple path to the end node since it must go through another $W$ in either case.
-Colored nodes and dashed edges are removed after minimization since they are irrelvant to the BGP decision process.
-%
-%Although fully minimizing this graph is an NP-complete problem,  a simple and efficient algorithm based on graph dominators achieves largely the same effect, greatly simplifying the failure safety analysis.
-
-%A node $x$ dominates $y$ if $x$ appears on every path leading to $y$ from a source node.
-Many efficient algorithms exist for finding graph dominators~\ref{bib:todo}.
-For minimization, we compute the dominator set for each node in both the product graph $G$ with respect to the start node, and in the reversed product graph $G^R$ with respect to the end node.
-The following rules enable efficient minimization of the product graph.
-%
-%\begin{itemize}
-%  \item Remove nodes that never reach the end node
-%  \item Remove nodes not reachable from the $start$ node
-%  \item Remove any node $x$ such that $x$ is dominated by $y$ in $G$ or $G^R$, and $loc(x) = loc(y)$
-%  \item Remove any edge from $x$ to $y$ in $G$ or $G^R$ if there is some node $z$ dominated by $y$ such that $loc(x) = loc(z)$
-%\end{itemize}
-%
-%Repeated application of the above rules leads to removing the colored nodes and dashed lines in Figure~\ref{fig:example-compilation}.
-
-\para{Failure Safety}
-
-To implement path preferences in routing, BGP uses local preferences on a per-device basis.
-However, the distributed nature of BGP makes setting preferences locally to achieve a network-route routing policy difficult, particularly in the presence of failures.
-For example, imagine an extremely simple policy for the topology in Figure~\ref{fig:example-compilation}, which says to prefer one route over another:
-%
-$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D}) \Prefer (\CD{W} \cdot \CD{B} \cdot \CD{C} \cdot \CD{E})$.
-%
-
-How could such a policy be implemented in BGP?
-Suppose we set the local preference at router $C$ to prefer $D$ over $E$, and use the BGP MED attribute to influence $W$ to prefer $A$ over $B$.
-This might work as expected under normal conditions, however, if the A -- C link fails, then suddenly $C$ has made the wrong decision.
-Traffic will now follow the
-$W \cdot B \cdot C \cdot D$ path, even though this path was not specified by the policy.
-This is a violation of \emph{soundness}: The distributed implementation has used a route not specified by the policy.
-To make matters worse, the second preference $W \cdot B \cdot C \cdot E$ is available in the network but not being used.
-This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
-We could solve the first problem by filtering routes that go through $D$ at $B$, however, we can not fix the second problem---$C$ has made the wrong choice.
-In fact, this policy can not be implemented in BGP in a way that is policy compliant under all failures.
-
-%and can not get either the primary or backup route specified, despite the fact that the $W \cdot B \cdot C \cdot E$ path is available in the network.
-
-At a first cut, any time a router must make a decision locally between several route options, there is the possibility it might choose incorrectly.
-The PGIR captures this notion of choice precisely.
-For example, router $D$ in Figure~\ref{fig:example-compilation} appears only once in the PGIR, possibly receiving announcements from $X$ or $Y$.
-However, regardless of whether $D$ chooses a route from $X$ or $Y$, the set of paths allowed by the policy after going through $D$ will be the same in either case.
-This remains true despite any failures that might have occurred in the network.
-Thus $D$ can safely prefer $X$ and $Y$ equally.
-
-The more challenging case is when a topology location occurs in mutliple contexts in the PGIR.
-For example, in the compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an announcement from $E$ and later achieve the backup path, or it can receive an announcement from its neighbor $D$ and later achieve either the primary or backup path.
-Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $E$?
-The important observation is that, if $C$ prefers $D$, then it is never worse off---it will always achieve at least as good a path as if it had choosen $E$.
-For example, suppose $C$ chooses a route from $D$, but cannot achieve its primary path because the $A$ -- $W$ link has failed.
-In this case, the advertisement from $C$ will still be sent along towards the ultimate backup location $W$.
-Since the $(C,3,2)$ node has the same one-step and two-step next hops as node $(C,-,2)$ in the product graph, no possible failure will prevent a route advertisment from reaching $(W,-,4)$ that wouldn't have otherwise prevented it if $C$ had choosen $E$.
-
-In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and enumerating all failures is intractable.
-We thus adopt a conservative analysis based on the observations above.
-The high-level idea is to order each PGIR node according to a \textit{can prefer} relation.
-For example, node $(C,3,2)$ can be preferred to node $(C,-,2)$, but not the other way around.
-Intuitively, a node $N_1$ can be preferred to another node $N_2$ when, for each preference $N_2$ might achieve, there is a better preference that $N_1$ will achieve regardless of failures.
-Formally this means that $N_1$ can be preferred to $N_2$ when:
-%
-$$\forall i, \exists j, j \leq i \wedge protect(G_j, N_1, G_i, N_2)$$
-%
-where \textit{protect} means that, from $N_1$ on the product graph restricted to nodes that can potentially achieve preference $j$ or better, 
-there is always a path to each ending location whenever this is a path from $N_2$ restricted to $G_i$.
-
-\begin{algorithm}[t!]
-\caption{Failure Protection}
-\label{alg:failures}
-\begin{algorithmic}[1]
-\Procedure{Protect($G_1$, $N_1$, $G_2$, $N_2$)}{}
-  \If {$loc(N_1) \neq loc(N_2)$} \Return false
-  \EndIf
-  \State $q \gets Queue()$
-  \State $q.Enqueue (N_1, N_2)$
-  \While {$!q.Empty()$}
-    \State $(n_1,n_2) \gets q.Dequeue()$
-    \For {$x$ in adj($G_2$, $n_2$)}
-      \If {\big($\exists y \in$ adj($G_1$,$n_1$), shadows $x$\big) \textbf{or} \\  
-            \hspace{5.2em} \big($\exists y \in$ $G_1$, dominates $n_1$, shadows $x$\big)}
-        \If {$(x,y)$ not marked}
-          \State {mark $(x,y)$ as seen}
-          \State $q.Enqueue(x,y)$
-        \EndIf
-      \Else { \Return $false$}
-      \EndIf
-    \EndFor
-  \EndWhile
-  \Return true
-  \EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-Algorithm~\ref{alg:failures} defines what it means for one node to \textit{protect} against the failures of another.
-It walks from nodes $N_1$ and $N_2$ in $G_j$ and $G_i$ respectively, and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, take an equivalent step.
-When there is no equivalent step, the algorithm checks to see if there is an equivalent dominator (a topology location the advertisement must have passed through earlier) that can protect against failures instead.
-Thus any time $N_2$ can get to a final location for preference $i$, $N_1$ can get to at least the same final locations for a better preference $j$.
-The algorithm terminates since the number of related states $(x,y)$ that can be expolored is finite.
-
-For each router in the topology, local preferences are now obtained by  sorting the corresponding PGIR nodes according to the \textit{can prefer} relation.
-If two nodes are incomparable, the compiler rejects the policy as unimplementable.
-
-\para{Avoiding Loops}
-
-The checks for failure safety described above overlook one critical point: Paths for a higher preference might not exist due to loops.
-To avoid this situation, the compiler checks that, when node $x$ protects against failures for node $y$, its does so without using any nodes that shadow another node that appears ``above'' $x$ in the PGIR.
-%It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
-%even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$.
-To avoid this situation, the compiler conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the PGIR (i.e., nodes reachable from $x$ in $G_j^R$).
-It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
-
-\para{Aggregation-Induced Black Holes}
-Because the \sysname compiler has the complete user policy and topology, it is also able to efficiently check that aggregates do not black hole traffic for up to $k$ failures.
-The algorithm for aggregation failure safety is detailed in Section~\ref{sec:black-holes} of the appendix.
-\subsection{Abstract BGP}
-
-%\begin{figure}[t!]
-%\centering
-%\includegraphics[width=.9\columnwidth]{figures/config}
-%\caption{Abstract BGP configuration.}
-%\label{fig:abgp-config}
-%\end{figure}
-
-\newcommand{\highlight}[1]{%
-  \colorbox{red!50}{$\displaystyle#1$}}
-\newcommand{\Router}[1]{\KW{Router} #1:}
-\newcommand{\REGEX}[1]{\texttt{regex}(#1)}
-\newcommand{\PEER}{\texttt{peer}}
-\newcommand{\COMM}{\texttt{comm}}
-\newcommand{\MED}{\texttt{MED}}
-\newcommand{\Arrow}{\ensuremath{\leftarrow}}
-
-%\begin{figure}[t!]
-%\begin{lstlisting}[frame=single, mathescape=true]
-%$\Router{A}$
-%  Match $\PEER=C$
-%    Export $\MED \leftarrow 80, \PEER \leftarrow W$
-%$\Router{B}$
-%  Match $\PEER = C$
-%    Export $\COMM \leftarrow \text{noexport}, \MED \leftarrow 81, \PEER \leftarrow W$
-%$\Router{C}$
-%  Match$[LP=99]$ $\PEER = E $
-%    Export $\PEER \leftarrow B$
-%  Match $\PEER = D$
-%    Export $\PEER \leftarrow A,B$
-%$\Router{D}$
-%  Match $\REGEX{X + Y}$
-%    Export $\PEER \leftarrow C$
-%$\Router{E}$
-%  Match $\REGEX{Z}$
-%    Export $\PEER \leftarrow C$
-%\end{lstlisting}
-%\label{fig:config-min}
-%\caption{Abstract BGP minimized configurations}
-%\end{figure}
-
-The final stage of our compiler translates policies from PGIR to a vendor-neutral abstraction of BGP (ABGP).
-% and then from ABGP to actual device configurations.
-
-\para{From PGIR to ABGP}
-
-Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
-The idea is to encode the state of the automaton using BGP community values.
-Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR.
-For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else).
-If it sees such an announcement, it will remove the old community value, and add a new one for state $(4,2)$ before exporting it to $W$.
-
-To ensure preferred paths are always obtained, for each router $r$ in the topology, the compiler sets a higher local preference for neighbors of a more-preferred node for $r$ in the PGIR.
-For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
-
-Since the compiler is only able to control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
-Instead, it translates matches from external ASes into a BGP regular expression filter.
-For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$.
-In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
-The unknown AS topology is modelled as a special node in the PGIR that generates a filter to match any sequence of ASes.
-
-Finally, the external AS $W$ should prefer our internal router $A$ over $B$.
-In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
-In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$.
-Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
-The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
-%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
-Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
-Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.
-
-After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
-In the compilation example, all community tags can be removed since there is never any ambiguity based on the router importing the route, and the neigbor the route is being imported from.
-Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.
-
-\begin{figure}[t!]
-%% \begin{lstlisting}[frame=single, mathescape=true]
-%% $\Router{A}$
-%%   Match $\PEER=C, \COMM=(3,2)$
-%%     Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
-%% $\Router{B}$
-%%   Match $\PEER = C, \COMM = (-,2)$
-%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
-%%            $\MED \leftarrow 81, \PEER \leftarrow W$
-%%   Match $\PEER = C, \COMM = (3,2)$
-%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
-%%            $\MED \leftarrow 81, \PEER \leftarrow W$
-%% $\Router{C}$
-%%   Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
-%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
-%%   Match $\PEER = D, \COMM = (2,2)$
-%%     Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
-%% $\Router{D}$
-%%   Match $\REGEX{X + Y}$
-%%     Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
-%% $\Router{E}$
-%%   Match $\REGEX{Z}$
-%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
-%% \end{lstlisting}
-\begin{code}
-  \Router{A}
-    Match \PEER=C, \COMM=(3,2)
-      Export \COMM \Arrow (4,2), \MED \Arrow 80, \PEER \Arrow W
-  \Router{B}
-    Match \PEER = C, \COMM = (-,2)
-      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
-             \MED \Arrow 81, \PEER \Arrow W
-    Match \PEER = C, \COMM = (3,2)
-      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
-             \MED \Arrow 81, \PEER \Arrow W
-  \Router{C}
-    Match[LP=99] \PEER = E, \COMM = (-,2) 
-      Export \COMM \Arrow (-,2), \PEER \Arrow B
-    Match \PEER = D, \COMM = (2,2)
-      Export \COMM \Arrow (3,2), \PEER \Arrow A,B
-  \Router{D}
-    Match \REGEX{X + Y}
-      Export \COMM \Arrow (2,2), \PEER \Arrow C
-  \Router{E}
-    Match \REGEX{Z}
-      Export \COMM \Arrow (-,2), \PEER \Arrow C
-  \end{code}
-  \vspace{-2em} 
-  \caption{Abstract BGP router configurations. \label{fig:abgp-config}}
-  \vspace{-1em}
-\end{figure}
-
-%=====================================================
-%
-%
-%  **Implementation**
-%
-%
-%=====================================================
-
-\section{Implementation}
-\label{sec:implementation}
-
-We have written a prototype compiler for \sysname that is implemented in roughly 5500 lines of F\# code.
-The compiler includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the no-export community, as well as for ensuring at least k-failure safety for user-specified aggregates.
-Since each prefix has a separate routing policy, the \sysname compiler is able to compile each routing policy in parallel.
-The current compiler produces only ABGP policies, which can be incorporated into an existing template-based system, for example by mixing the \sysname configuration with other configuration components, or by generating vendor-specific configurations.
-
-\para{PG construction}
-
-Constructing automata for extended regular expressions (regular expressions including negation and intersection) are known to have high complexity~\cite{regex-complexity}.
-The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently.
-Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy.
-Similarly, to model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.
-%
-Rather than construct the product graph in full, our implementation prevents exploring parts of the graph when no accepting state is reachable in any of the corresponding regular automata during construction.
-
-%\para{PG Minimization}
-
-%The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\cite{fast-dominance}.
-More complex algorithms with better theoretical complexity exist~\cite{linear-dominance, tarjan-dominance} and may be better suited for large enough topologies.
-All minimization steps are repeated until no more progress can be made.
-
-\para{Failure Safety}
-
-When computing local preferences and failure safety, as described in Section~\ref{sec:compilation}, the compiler performs memoization of the \textit{protect} function.
-That is, whenever for two states $n_1$ and $n_2$ we compute $protect(G_j, n_1, G_i, n_2)$, if the function evaluates to $true$, then each of the intermediate related states $x$ and $y$ must also satisfy $protect(G_j, x, G_i, y)$.
-Memoizing these states significantly cuts down the amount of work that needs to be in the common case.
-
-\para{Configuration generation}
-
-The naive code generation algorithm described in Section~\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair for every node in the product graph before minimization.
-Our implementation performs partial minimization during generation by recognizing common cases where there is no restriction on exporting to or importing from neighbors.
-
-%=====================================================
-%
-%
-%  **Evaluation**
-%
-%
-%=====================================================
-
-\begin{figure}
-  \subcaptionbox{Data center}
-    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-dc.png}}
-  \subcaptionbox{Backbone network}
-    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
-  \caption{Compilation time. \label{fig:compilation-times}}
-  \vspace{-1em}
-\end{figure}
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-We apply \sysname on real policies for backbone and data center networks.
-Our mains goals are to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.
-
-\subsection{Networks studied}
-
-We obtained routing policy for the backbone network and for the data centers of a large cloud provider.
-Multiple data centers share this policy.
-The backbone network connects to the data centers and also has many external BGP neighbors.
-The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for data center routers or actual configurations for the backbone network (where templates are not used because the network has less regular structure).
-
-The networks have the type of policies that we outline earlier (\S\ref{sec:motivation}).
-The backbone network classifies external neighbors into several different categories and prefers paths through them in order.
-It does not want to provide transit among certain types of neighbors.
-For some neighbors, it prefers some links over the others.
-It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA).
-Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, etc.
-
-All routers in the datacenter network run BGP using a private AS number and peer with each other and with the backbone network over eBGP.
-The routers aggregate prefixes when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region.
-They also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
-
-\begin{figure}
-  \subcaptionbox{Data center}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
-  \subcaptionbox{Backbone network}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
-  \caption{Configuration minimization. \label{fig:config-min}}
-  \vspace{-1em}
-\end{figure}
-
-\subsection{Expressiveness}
-
-We found that we could translate all network policies to \sysname.
-We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname.
-The data center operator said that he found the language intuitive.
-The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We found that the data center policies were correctly translated.
-For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.
-
-Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.
-
-\subsection{Compilation time}
-
-%\begin{figure}[t!]
-%  \centering
-%  \begin{minipage}[b]{0.45\linewidth}
-%    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-dc.png}
-%  \end{minipage}
-%  \quad
-%  \begin{minipage}[b]{0.45\linewidth}
-%    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-backbone.png}
-%  \end{minipage}
-%  \caption{Compilation times.}
-%  \label{fig:compilation-times}
-%\end{figure}
-
-%\begin{figure}[t!]
-%  \centering
-%  \begin{minipage}[b]{0.45\linewidth}
-%    \includegraphics[width=1.1\columnwidth]{figures/config-compression-dc.png}
-%  \end{minipage}
-%  \quad
-%  \begin{minipage}[b]{0.45\linewidth}
-%    \includegraphics[width=1.1\columnwidth]{figures/config-compression-backbone.png}
-%  \end{minipage}
-%  \caption{Configuration minimization.}
-%  \label{fig:config-minimization}
-%\end{figure}
-
-We study the compilation of time for both policies as a function of network size.
-Even though the networks we study have a fixed topology and size, we can explore the impact of size because our converted policies are network-wide and the compiler takes topology itself as an input.
-For the data center network, we build and provide as input fat tree~\cite{fattree} topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy.
-We take this approach to smoothly explore different sizes.
-%There is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete data center topologies.
-For a given size, our reported results match those for the concrete topologies.
-
-For the backbone network, the internal topology does not matter since all routers connect in a full iBGP mesh.
-We explore different mesh sizes and randomly map neighboring networks to routers.
-Even though each border router connects to many external peers, we count only the mesh size.
-
-All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
-%
-Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes.
-For both policies, we measure the mean compilation time per prefix since the compiler operates on each prefix in parallel.
-At their largest sizes, the per-prefix compilation time is roughly 10 seconds for the data center network and 45 seconds for the backbone network.
-
-%From the break down of the time by compilation phase, we see that no single compilation phase dominates the running time of the compiler.
-However, construction and minimization of the product graph take the most time.
-
-Total compilation for the largest data center is less than 9 minutes total.
-Unlike the data center policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases.
-Compilation for the largest backbone network, takes less than 3 minutes total.
-The inclusion of more preferences in the backbone policy increases the size of the PGIR, which leads to PGIR construction and minimization taking proportionally more time.
-
-%
-
-\subsection{Configuration size}
-
-Figure~\ref{fig:config-min} shows the size of the compiled ABGP policies as a function of the topology size.
-The naive translation of PGIR to ABGP outlined in \S\ref{sec:compilation} generates extremely large ABGP policies by default.
-To offset this, the compiler performs ABGP configuration minimization both during and after the PGIR to ABGP translation phase.
-%Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
-Minimization is highly effective for both the data center and backbone policies. In all cases, minimized policies are a small fraction of the size of their non-minimized counterparts.
-
-%for i in *.set; do grep bgp $i | wc; done
-However, even minimized configurations are hundreds or thousands of lines per router.
-For the backbone network, the size of \sysname configurations is roughly similar to the BGP components of actual router configurations, though qualitative differences exist (see below).
-We did not have actual configurations for the data center network; they are dynamically generated from templates.
-
-\subsection{Propane vs. operator configurations}
-
-Finally, we comment briefly on how \sysname-generated configurations differ from configurations or templates generated by operators.
-%
-In some cases, \sysname configurations are similar.
-For example, preferences among neighboring ASes are implemented with a community value to tag incoming routes according to preference, which is then used at other border routers to influence decisions.
-
-In other cases, the \sysname configurations are different, relying on a different BGP mechanism to achieve the same result. Some key differences that we observed were:
-
-$i)$ operators used the no-export community to prevent routes from leaking beyond a certain tier of the datacenter, while \sysname selectively imported the route only below the tier;
-%\sysname could use a similar implementation mechanism in the future as an optimization.
-
-$ii)$ operators prevented unneeded propagation of more-specific route announcements from a neighboring AS based on their out-of-band knowledge about the topology, whereas \sysname propagated these advertisements; and
-
-$iii)$ operators used a layer of indirection for community values, using community groups and re-writing values, to implement certain policies in a more maintainable manner, where \sysname uses flat communities.
-
-We are currently investigating if such differences matter to operators (e.g., if they want to read \sysname configurations) and, if necessary, how to reduce them.
-
-%=====================================================
-%
-%
-%  **Related Work**
-%
-%
-%=====================================================
-
-\section{Related Work}
-\label{sec:related}
-
-\paragraph*{SDN Languages}
-\sysname{} was heavily influenced by recent SDN programming
-languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire}, 
-as well as path queries~\cite{queries}.
-Each of these languages is oriented around regular expressions, which
-describe paths through a network, and predicates, which classify packets.
-In particular, FatTire allows programmers to define sets of paths together
-with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
-and the compiler will generate appropriate OpenFlow rules.
-\sysname is more expressive as it allows users to specify preferences among
-paths and it generates distributed implementations that tolerate any number of faults. 
-Because FatTire generates data plane rules up front, 
-specifying higher levels of fault tolerance comes
-at the cost of generating additional rules that tax switch memory.  
-In contrast, \sysname uses traditional distributed
-control plane mechanisms to react to faults, which do not impose additional memory cost.
-Because of the differences in the underlying technology, the analyses
-and compilation algorithms used in \sysname are quite different from
-previous work on SDN. 
-Finally, in addition to using path-based abstractions
-for intra-domain routing, \sysname uses them for inter-domain routing as
-well, unlike any existing SDN language.
-
-\paragraph*{Configuration Automation}
-Many practitioners use configuration templates~\cite{hatch,thwack}, to ensure certain kinds of consistency across similar devices.
-In addition, configuration languages such as RPSL~\cite{RFC2622}, Yang~\cite{RFC6020}, and Netconf~\cite{RFC6241} allow operators to express routing policy in a vendor-neutral way.
-However, all of these solutions remain low-level, for example, requiring operators to specify exact local preferences.
-Unlike \sysname, there is no guarantee that these low-level configurations satisfy the original, high-level intent.
-
-\paragraph*{Configuration Analysis}  
-The notion that configuring network devices is difficult and error-prone is not new.  
-Past researchers have tried to tackle this problem by analyzing existing
-firewall configurations~\cite{fang,lumeta,margrave} and
-BGP configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe} and reporting errors or inconsistencies when they are detected.
-Our research is complementary to these analysis
-efforts.  We hope to eliminate bugs by using higher-level
-languages and a ``correct-by-construction''
-methodology.  By proposing network administrators write configurations
-at a high-level of abstraction, a whole host of low-level errors can be avoided.
-
-\paragraph*{Configuration Synthesis}
-ConfigAssure~\cite{narain:lisa05,narain+:configassure}
-is another system designed to
-help users define and debug low-level router
-configurations.  Inputs to
-ConfigAssure include a \emph{configuration database}, which contains a
-collection of tuples over constants and configuration variables, and a
-\emph{requirement}, which is a set of constraints.  
-%For instance, the tuple \texttt{hsrp(rexa,rA1,int(1),int(2))} states that interface
-%\texttt{rA1} on device \texttt{rexa} belongs to the HSRP group defined
-%by configuration variable \texttt{int(1)} with virtual IP address
-%defined by configuration variable \texttt{int(2)}.  The constraint
-%\texttt{hsrp\_subnet([rexa-rA1,rexb-rB1])} states that a database
-%contains tuples defining HSRP group identifiers and virtual IPs for
-%interfaces \texttt{rA1} and \texttt{rB1} on devices \texttt{rexa} and
-%\texttt{rexb}.  
-The authors use a combination of logic programming and
-SAT solving to find concrete values for configuration variables.
-%such as \texttt{int(1)}.  
-ConfigAssure handles configuration for a wide range of protocols and many
-different concerns.  In contrast, the scope of \sysname is much
-narrower.  In return, \sysname offers compact, higher-level
-abstractions customized for our domain, such as regular paths, as well
-as domain-specific analyses customized to those abstractions, such as
-our failure safety analysis.  The implementation technology is also
-entirely different, as we define algorithms over automata and graphs
-as opposed to using logic programming and SAT-based model-finding.
-
-%We also believe the high-level, centralized nature of \sysname policies
-%has the benefit of making configurations
-%easier to understand and maintain.
-
-%=====================================================
-%
-%
-%  **Conclusions**
-%
-%
-%=====================================================
-
-\section{Conclusions}
-\label{sec:conclusions}
-
-In this paper, we introduced \sysname, a language and compiler for implementing centralized network policies using a distributed set of devices running BGP.
-Propane allows operators to describe network-wide intent directly through high-level constraints on the shape and relative preferences of paths for different types of traffic.
-When \sysname compiles a policy, then the resulting BGP configurations are correct-by-construction, faithfully implementing the centralized policy in a distributed fashion, regardless of failures.
-
-%=====================================================
-%
-%
-%  **Appendix**
-%
-%
-%=====================================================
-
 \section*{Appendix}
@@
 %An important distinction is that BGP might still be instable with respect to other external ASes, since \sysname has no way of configuring their routing policy and can only rely on AS path filters to see what advertisements are observed.
-
-%=====================================================
-%
-%
-%  **Bibliography**
-%
-%
-%=====================================================
-
-\bibliographystyle{abbrv}
-\bibliography{references}
-
-% The bibliography should be embedded for final submission.
-
-\end{document}

### 2016-10-24 scripts/abstract/run.sh
various optimizations

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-DATAFILE=data
+DATANAME=data
 TEMPFILE=temp.csv
 
 PROPANE_CMD="mono ../../src/bin/Release/propane.exe"
@@ -9,21 +9,35 @@ if [ -f $TEMPFILE ] ; then
     rm $TEMPFILE
 fi
 
+if [ ! -d benchmarks/ ] ; then
+    $PROPANE_CMD --bench
+fi
+
 genstats () {
   shopt -s nullglob
-  for f in benchmarks/*$1.xml
+  for f in benchmarks/*$2.xml
   do
-      file=${f%_abs.xml}
-      policy=${file}$1.pro
-      topo=${file}$1.xml
-
-      size=${file#benchmarks/fat}
+    for i in {1..3} 
+    do 
+      file=${f%${2}.xml}
+      policy=${file}$2.pro
+      topo=${file}$2.xml
+      size=${file#benchmarks/"$1"}
       echo "$size" >> $TEMPFILE
+      echo "compiling: $policy"
       $PROPANE_CMD --policy $policy --topo $topo --csv --failures=0 >> $TEMPFILE
+    done
   done
 
-  awk 'NR % 3 != 2' $TEMPFILE > ${DATAFILE}${1}.csv
+  awk 'NR % 3 != 2' $TEMPFILE > ${DATANAME}_${1}${2}.csv
   rm $TEMPFILE
 }
 
-genstats "_abs"
+genstats "fat" "_abs"
+genstats "fat" "_con"
+# genstats "backbone" "_abs"
+# genstats "backbone" "_con"
+
+if [ -d output/ ] ; then
+  rm -r output/
+fi

### 2016-10-25 scripts/abstract/plot.py
Preliminary support for generating templates with guaranteed incremental changes. Add graph scripts

@@ -1,0 +1,165 @@
+import csv
+import sys
+import os.path
+import numpy as np
+import matplotlib.pyplot as plt
+
+direct = os.path.dirname(os.path.realpath(__file__))
+
+def numRuns(data):
+  i = 0
+  start = data[0]
+  while data[i] == start: 
+    i = i+1
+  return i
+
+def average(data,i):
+  d = []
+  acc = 0
+  mean = 0
+  for x in data:
+    acc = acc + 1    
+    mean = mean + x
+    if acc == i:
+      d.append( mean / i )
+      acc = 0
+      mean = 0
+  return d
+
+def sortAll(size, total, agg, sub, core):
+  indicesTotal = {}
+  indicesAgg = {}
+  indicesSub = {}
+  indicesCore = {}
+  for i in range(0, len(size)):
+    indicesTotal[size[i]] = total[i]
+    indicesAgg[size[i]] = agg[i]
+    indicesSub[size[i]] = sub[i]
+    indicesCore[size[i]] = core[i]
+  s = sorted(size)
+  tot = []
+  agg = []
+  sub = []
+  core = []
+  for v in s:
+     tot.append(indicesTotal[v])
+     agg.append(indicesAgg[v])
+     sub.append(indicesSub[v])
+     core.append(indicesCore[v])
+  return s,tot,agg,sub,core
+
+def adjust(size, total, agg, sub, core):
+  i = numRuns(size)
+  a = average(size,i)
+  b = average(total,i)
+  c = average(agg,i)
+  d = average(sub,i)
+  e = average(core,i)
+  return sortAll(a,b,c,d,e)
+
+def plot(file):
+  with open(direct + os.path.sep + file) as f:
+    size = []
+    total = []
+    totalParse = []
+    totalToAbgp = []
+    totalToConfig = []
+    pgConstruct = []
+    pgMinimize = []
+    aggAnalysis = []
+    findOrdering = []
+    genAbgp = []
+    minAbgp = []
+    genCore = []
+    genLowLevel = []
+    substitution = []
+    genVendor = []
+    r = csv.reader(f)
+    parity = False
+    for row in r:
+      parity = not parity
+      if parity: 
+        size.append(int(row[0]))
+      else:
+        total.append(float(row[0]))
+        totalParse.append(float(row[1]))
[…]

### 2016-10-25 scripts/abstract/run.sh

@@ -41,3 +41,7 @@ genstats "fat" "_con"
 if [ -d output/ ] ; then
   rm -r output/
 fi
+
+if [ ! -d graphs/ ] ; then
+  mkdir graphs/
+fi

### 2016-10-26 scripts/abstract/plot.py
backbone abstract benchmarks + bug fixes

@@ -9,7 +9,8 @@ direct = os.path.dirname(os.path.realpath(__file__))
 def numRuns(data):
   i = 0
   start = data[0]
-  while data[i] == start: 
+  l = len(data)
+  while i < l and data[i] == start: 
     i = i+1
   return i
 
@@ -68,6 +69,7 @@ def plot(file):
     pgMinimize = []
     aggAnalysis = []
     findOrdering = []
+    inboundAnalysis = []
     genAbgp = []
     minAbgp = []
     genCore = []
@@ -89,77 +91,83 @@ def plot(file):
         pgMinimize.append(float(row[5]))
         aggAnalysis.append(float(row[6]))
         findOrdering.append(float(row[7]))
-        genAbgp.append(float(row[8]))
-        minAbgp.append(float(row[9]))
-        genCore.append(float(row[10]))
-        genLowLevel.append(float(row[11]))
-        substitution.append(float(row[12]))
-        genVendor.append(float(row[13]))
+        inboundAnalysis.append(float(row[8]))
+        genAbgp.append(float(row[9]))
+        minAbgp.append(float(row[10]))
+        genCore.append(float(row[11]))
+        genLowLevel.append(float(row[12]))
+        substitution.append(float(row[13]))
+        genVendor.append(float(row[14]))
     return adjust(size, total, aggAnalysis, substitution, genCore)
 
-if len(sys.argv) != 3: 
-  print "Invalid Use:"
-  print "   plot.py concrete.csv abstract.csv"
-  exit()
+def makeGraph(con, abs, name, descr):
+  sizeCon, totalCon, _, _, _ = plot(con)
+  sizeAbs, totalAbs, aggAbs, subAbs, genCore = plot(abs)
 
-sizeCon, totalCon, _, _, _ = plot(sys.argv[1])
-sizeAbs, totalAbs, aggAbs, subAbs, genCore = plot(sys.argv[2])
+  # Plot colors
+  color1 = "#FFC09F"
+  color2 = "#ADF7B6"    # "#FFEE93"
+  color3 = "#FCF5C7"
+  color4 = "#A0CED9"
 
-# Plot colors
-color1 = "#FFC09F"
-color2 = "#ADF7B6"    # "#FFEE93"
-color3 = "#FCF5C7"
-color4 = "#A0CED9"
+  # Compilation times
[…]

### 2016-10-26 scripts/abstract/run.sh

@@ -9,13 +9,11 @@ if [ -f $TEMPFILE ] ; then
     rm $TEMPFILE
 fi
 
-if [ ! -d benchmarks/ ] ; then
-    $PROPANE_CMD --bench
-fi
+$PROPANE_CMD --bench
 
 genstats () {
   shopt -s nullglob
-  for f in benchmarks/*$2.xml
+  for f in benchmarks/${1}*$2.xml
   do
     for i in {1..3} 
     do 
@@ -33,10 +31,10 @@ genstats () {
   rm $TEMPFILE
 }
 
-genstats "fat" "_abs"
-genstats "fat" "_con"
 # genstats "backbone" "_abs"
 # genstats "backbone" "_con"
+# genstats "fat" "_abs"
+genstats "fat" "_con"
 
 if [ -d output/ ] ; then
   rm -r output/
@@ -45,3 +43,6 @@ fi
 if [ ! -d graphs/ ] ; then
   mkdir graphs/
 fi
+
+echo "Generating graphs..."
+python plot.py 

### 2016-10-26 scripts/abstract/plot.py
update benchmarks to include abstract analysis for backbone case

@@ -129,7 +129,7 @@ def makeGraph(con, abs, name, descr):
   #====================================================
 
   # stack data lowest -> highest (build, minimize, order, gen, compress)
-  other = map(lambda (x,y,z): x-y-z, zip(totalAbs,aggAbs,subAbs))
+  other = map(lambda (w,x,y,z): w-x-y-z, zip(totalAbs,aggAbs,subAbs,genCore))
   data = (aggAbs, subAbs, genCore, other)
   y_stack = np.cumsum(np.row_stack( data ), axis=0)
 
@@ -155,11 +155,8 @@ def makeGraph(con, abs, name, descr):
   p2 = plt.Rectangle((0, 0), 1, 1, fc=color2, alpha=.7)
   p3 = plt.Rectangle((0, 0), 1, 1, fc=color3, alpha=.7)
   p4 = plt.Rectangle((0, 0), 1, 1, fc=color4, alpha=.7)
-  leg_boxes = [p4, p3, p2]
-  descrs = ["Policy to ABGP", "ABGP to Quagga", "Substitution"]
-  if name == "Fattree":
-    leg_boxes.append(p1)
-    descrs.append("Failure Analysis")
+  leg_boxes = [p4, p3, p2, p1]
+  descrs = ["Policy to ABGP", "ABGP to Quagga", "Substitution", "Failure Analysis"]
   ax1.legend(leg_boxes, descrs, loc=2, fontsize=22)
   fig.savefig(direct + '/graphs/' + name + '-analysis-time.png', bbox_inches='tight')
 

### 2016-10-26 scripts/abstract/run.sh

@@ -23,7 +23,7 @@ genstats () {
       size=${file#benchmarks/"$1"}
       echo "$size" >> $TEMPFILE
       echo "compiling: $policy"
-      $PROPANE_CMD --policy $policy --topo $topo --csv --failures=0 >> $TEMPFILE
+      $PROPANE_CMD --policy $policy --topo $topo --anycast --failures=0 --csv >> $TEMPFILE
     done
   done
 
@@ -31,9 +31,9 @@ genstats () {
   rm $TEMPFILE
 }
 
-# genstats "backbone" "_abs"
-# genstats "backbone" "_con"
-# genstats "fat" "_abs"
+genstats "backbone" "_abs"
+genstats "backbone" "_con"
+genstats "fat" "_abs"
 genstats "fat" "_con"
 
 if [ -d output/ ] ; then

### 2016-10-27 paper/abstraction/paper.tex
adding inference rules
edits to section 2

@@
 
-\newcommand{\sysname}{{\small \sf Propane}\xspace}
+\newcommand{\sysname}{{\small \sf Methane}\xspace}
 
@@
 %\end{figure}
+
+We motivate \sysname using an example data center network adapted from prior work~\cite{propane}.
+Our network, shown in Figure~\ref{fig:example}, is a standard folded-Clos topology with four pods.
+It has eight top-of-rack (ToR) switches, T[1--8]; eight aggregation switches, A[1--8]; and two spine switches, S[1--2].
+Groups of addresses, P[1--8], are for services hosted in each rack.
+Such groups are called address {\em prefixes} because they are compactly encoded using the common prefix that addresses share.
+
+The figure also shows the intended policy.
+Internal connectivity should be complete, i.e., all nodes must be able to talk to each other.
+Pods 1 and 2 host services that are meant to be globally accessible and thus their addresses should be announced externally, but only after the individual prefixes P[1--4] are aggregated into a single prefix PG.
+Finally, pods 3 and 4 host services that are not meant to be externally visible and thus their address should not be announced externally.
+
+To correctly configure the policy above, the network engineer's task is to generate low-level configuration commands for each switch in the network.
+This implies making sure, for instance, that all switch interfaces are assigned correct addresses; all routing adjacencies are correctly configured (e.g., T1's configuration includes A1 as neighbor and vice-versa); all switches announce their own addresses (so that they can be reached for management purposes) and the ToRs announce the correct prefixes for their services; all switches  forward the prefix announcements that they should to each neighbor and not forward those that they should not (e.g., the spines should forward prefixes for local services to internal neighbors but not external neighbors); and the spines announce externally only the aggregate global prefix.
+As many have observed before, such configuration tasks are highly challenging and, consequently, configuration errors are the leading contributor to network outages~\cite{x,y,z,batfish,propane}.
+
+To reduce errors, network engineers are moving toward a template-based approach.
+Here, instead of authoring one configuration file per router, they author one configuration template per {\em role}, where each role is played by one or more routers.\footnote{If a role is played by devices from different vendors, there is one template per role-vendor combination because templates use vendor configuration language.} For instance, the network in Figure~\ref{fig:example} has five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
+Role templates have parameters for various aspects of the configuration (e.g., interface addresses, list of neighbors), and they are compiled to device configurations by instantiating the parameters using a database that stores parameter values for each device.
+
+Templates provide two key advantages.
+First, they help eliminate a class of configuration errors that stem from typos and inconsistencies, e.g., using the wrong address for a switch, having inconsistent addresses for the two ends of a link, and failing to configure one side of a routing adjacency.
+Second, template design work can be re-used when the topology changes while maintaining its basic structure (e.g., adding a new pod to the data center) or multiple networks with similar structures need to be instantiated (e.g., in an organization that runs multiple data centers).
+
+%Second, the engineers need to author and reason about fewer independent ``files"---18 versus 5 in our example but the ratio can be multiple orders of magnitude for large networks.
+
+Today's templates, however, are far from perfect. While they reduce a class of errors, they do not help with deeper, logical bugs.
+%, e.g., incorrect strategy for determining how announcements to a neighbor are forwarded
+%, not realizing when or where aggregation should be used, 
+%and not understanding the interaction between configuration commands. 
+To author correct templates, engineers must still do themselves the conceptually challenging task of breaking down complex, global policies into role templates such that the collective behavior of the templates (upon compilation to configurations) correctly implements the policy under all failure conditions.
+
+As a result, the types of configuration design errors in our example network pointed in prior work~\cite{propane} can occur in template design as well.
+For instance, to keep local prefixes internal the engineer may implement announcement forwarding on spines based on the identity of the neighbor, i.e., do not announce externally anything heard from local aggregators.
+This implementation works correctly when there are no failures but local prefixes can leak to the outside world when failures disconnect a spine from both aggregators in a local pod.
+Specifically, when S1 is disconnected from A5 and A6, it may hear about P5 and P6 from A3 and A4 (via A[5--6]->S2->A[3--4]), and it will then announce those prefixes outside (since they no not come from a local aggregator), leading to a policy violation.
+A correct implementation here would be for each spine to not advertise externally announcements from local aggregators {\em and} reject announcements that have traversed the other spine.
+
+Lacking correctness guarantees, some engineers use simulations to gain confidence that their templates correctly implement policy under a range of failure cases (e.g., all combinations of two link failures), but for large networks these simulations tend to be highly expensive and still do not provide any guarantees beyond the tested cases.
+Further, that simulations over a concrete topology is the basis for checking correctness means that templates cannot be directly re-used when the topology evolves or on another similarly-structured topology.
+
+Templates that work for a given concrete topology may not work for minor variations of the topology.
 

### 2016-10-27 paper/abstraction/paper.tex
first full draft of section 2

@@
 \newcommand{\sysname}{{\small \sf Methane}\xspace}
+\newcommand{\sysnamesec}{{\sf Methane}\xspace}
 
@@
 
-%\begin{figure}[t!]
-%  \centering
-%  \includegraphics[width=\columnwidth]{figures/example2}
-%  \caption{Policy-compliance under failures is difficult.}
-%  \label{fig:example2}
-%  \vspace{-1em}
-%\end{figure}
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=\columnwidth]{figures/example}
+  \caption{An example data center network.}
+  \label{fig:example}
+  \vspace{-1em}
+\end{figure}
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=\columnwidth]{figures/example2}
+  \caption{A modified version of the example in Figure~\ref{fig:example}.}
+  \label{fig:example2}
+  \vspace{-1em}
+\end{figure}
 
@@
 
-To reduce errors, network engineers are moving toward a template-based approach.
+\subsection{Challenges with today's template systems}
+
+To reduce errors, the network engineering community is moving toward a template-based approach.
 Here, instead of authoring one configuration file per router, they author one configuration template per {\em role}, where each role is played by one or more routers.\footnote{If a role is played by devices from different vendors, there is one template per role-vendor combination because templates use vendor configuration language.} For instance, the network in Figure~\ref{fig:example} has five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
@@
 First, they help eliminate a class of configuration errors that stem from typos and inconsistencies, e.g., using the wrong address for a switch, having inconsistent addresses for the two ends of a link, and failing to configure one side of a routing adjacency.
-Second, template design work can be re-used when the topology changes while maintaining its basic structure (e.g., adding a new pod to the data center) or multiple networks with similar structures need to be instantiated (e.g., in an organization that runs multiple data centers).
+Second, templates have the potential for re-use when the topology changes while maintaining its basic structure (e.g., adding a new pod to the data center) or multiple networks with similar structures need to be instantiated (e.g., in an organization that runs multiple data centers).
 
@@
 
-Today's templates, however, are far from perfect. While they reduce a class of errors, they do not help with deeper, logical bugs.
+Today's template systems however, are far from perfect. While they reduce a class of errors, they do not help with deeper, logical bugs.
 %, e.g., incorrect strategy for determining how announcements to a neighbor are forwarded
@@
 Specifically, when S1 is disconnected from A5 and A6, it may hear about P5 and P6 from A3 and A4 (via A[5--6]->S2->A[3--4]), and it will then announce those prefixes outside (since they no not come from a local aggregator), leading to a policy violation.
-A correct implementation here would be for each spine to not advertise externally announcements from local aggregators {\em and} reject announcements that have traversed the other spine.
-
-Lacking correctness guarantees, some engineers use simulations to gain confidence that their templates correctly implement policy under a range of failure cases (e.g., all combinations of two link failures), but for large networks these simulations tend to be highly expensive and still do not provide any guarantees beyond the tested cases.
-Further, that simulations over a concrete topology is the basis for checking correctness means that templates cannot be directly re-used when the topology evolves or on another similarly-structured topology.
-
-Templates that work for a given concrete topology may not work for minor variations of the topology.
+A correct implementation here would be for each spine to not advertise externally announcements from local aggregators {\em and} reject announcements that have traversed the other spine (i.e., disallow "valleys," or up-down-up paths).
+
+Lacking correctness guarantees, engineers use simulations to analyze if templates are correct under a range of failure cases (e.g., combinations of two-link failures), but such analysis is highly expensive for large networks and still does not provide strong guarantees beyond the tested cases.
+
+More importantly, because the analysis is done over a concrete topology, it provides no insight as to when the templates can be safely re-used.
+Templates that work for a given concrete topology may not work for seemingly-minor variations of the topology.
+Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}; it has the same folded-Clos structure and the same five roles.
+One might think that the same templates (but different database entries) can be used for both topologies.
+However, templates that disallow valley paths lead to a less fault-tolerant system for Figure~\ref{fig:example2}.
+
+In particular, aggregation-induced blackholes can occur in Figure~\ref{fig:example2} with only one link failure, while it would take two failures in Figure~\ref{fig:example}.
+Such blackholes occur when a switch announces an aggregate prefix but has no valid path to a more specific prefix within the aggregate.
+In Figure~\ref{fig:example}, a blackhole will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes by virtue of announcing the encompassing aggregate PG.
+In contrast, in Figure~\ref{fig:example}, no such blackhole will occur after a single failure.
+
+Thus, engineers today must reason about the correctness of templates for each concrete topology and each evolution.
+Worse, for some evolutions, they may discover that their old templates will not work anymore and need modifications.
+This discovery is highly onerous because changing the templates implies that the configuration of all the devices needs to change, which can be an unacceptable disruption.
+When that happens, many networks abandon templates entirely and revert to modifying individual configuration files, using localized patches to accomodate evolution.
+This reversion brings backs the class of errors that the templates were designed to prevent.
+
+As an aside, a possible template implementation that works correctly for both networks is: allow valley paths and use an explicit list of local prefixes at spines to decide which announcements should not be forwarded externally.
+
+\subsection{Challenges with concrete synthesis}
+
+As an alternative approach to reduce configuration errors, the research community has developed many systems that take network topology and policy as input and output device configurations that are  guaranteed to be correct under all possible failures.
+Thus, they save the engineers from performing the complex task of breaking down global policies into device configurations.
+
+However, they have two shortcomings, both stemming from operating over concrete topologies.
+The first is a mismatch in abstraction.
+Engineers that run large networks tend to think of them, and develop tools for them, in terms of roles and not individual devices.
+We have thus found that they are reluctant to use a system that does not understand roles as a first-order abstraction.
+There is no guarantee in these systems that the configurations of two devices that serve the same role will be "similar."  If the engineers wanted to sanity-check or (familiarize themselves with) their output, they'll have to consider all device configurations;  there can be orders of magnitude more devices than roles in the network.
+
+A second shortcoming is lack of support for incremental growth.
+When engineers want to expand a network, they would have to input the new, planned topology to the system.
+The new configurations for existing devices may undergo unnecessary changes, beyond those needed to accommodate the expansion.
+For instance, suppose the engineers want to add another pod with local services to the network in Figure~\ref{fig:example}, and (like current aggregators) the aggregators in the new pod will connect to both spines.
+In this network, Propane, a concrete synthesis tool, uses prefix lists at spines to ensure that local prefixes are not advertised externally.
+To accommodate the expansion, the new spine configurations outputted by Propane will not only enable the interfaces that connect to the new aggregators but will also have to update the prefix list filters.
+A system that supports incremental growth should need only interface configuration changes (not filter changes).
+It can configure all local ToRs, including the new ones, to attach a tag to their announcements and filter external announcements at the spines based on this tag.
+Engineers prefer fewer configuration changes because each change runs the risks of poor transient behavior (which synthesis tools do not reason about).
+
+\subsection{\sysnamesec}
+
+\sysname addresses the challenges above with both template systems and concrete synthesis tools.
+It takes as input network policy and an {\em abstract} topology  that captures the different device roles and connectivity.
+It outputs a template for each role.
+Engineers can then use \sysname's template compiler or their own to convert templates into configurations based on the concrete topology and parameter values.
+
+\sysname guarantees that the templates are correct, that is, when compiled to device configurations, the network will correctly implement the specified policy.
+These guarantees hold for any valid concrete topology that matches the specified abstract topology; and when a valid concrete topology evolves to another valid concrete topology, only necessary changes are needed to device configurations.
 
@@
 
+\newcommand{\inference}[4]{
+    \node[draw, anchor=west] at (#1 + .4, 1.25) {#3};
+    \node at (#1 + .34, .6) {$e_1$};
+    \node at (#1 + .34, 1.9) {$e_2$};
+    \node at (#1, -.8) {#2};
+    \node at (#1, 3.3) {#4};
+    \draw [] (#1, 2.5) circle [radius=0.45] node {$m$};
+    \draw [] (#1, 0) circle [radius=0.45] node {$n$};
+    \draw [] (#1, .45) -- (#1, 2.05);
+}
+
+\begin{figure*}[t!]
+  \begin{minipage}[t]{.5\linewidth}%
+  \begin{tikzpicture}
+    \inference{0}{L$(j,k)$}{$\vDash e_1 > 0$}{S$(min(j*k,e_1),1)$}
+    \inference{10}{A$(j,k)$}{$e_2 > 0$}{A$(1,min(j,e2))$}
+  \end{tikzpicture}
+  \end{minipage}
+
+  %
+  \vspace*{3em}
+  %
+  \begin{minipage}[t]{.5\linewidth}%
+  \begin{tikzpicture}
+    \inference{0}{L$(j,k)$}{$e_1=n$}{A$(min(j*k,n),1)$}
+    \inference{10}{L$(j,k)$}{$e_1=n$}{A$(1,j)$}
+  \end{tikzpicture}
+  \end{minipage}
+
+  %
+  \vspace*{3em}
+  %
+  \begin{minipage}[t]{.5\linewidth}%
+  \begin{tikzpicture}
+    \inference{0}{L$(j,k)$}{$e_1 > 0$, $e_2 > 0$}{S$(min(j*k,n-\dfrac{(m-j)*e_1}{e_2}),1)$}
+  \end{tikzpicture}
+  \end{minipage}
+
+  %
+  \vspace*{3em}
+  %
+  \begin{minipage}[t]{.5\linewidth}%
+  \begin{tikzpicture}
+    \inference{10}{L$(j,k)$ ~~~ L$(j- m ~\text{mod}~ \big(\dfrac{n}{e_1}\big),1)$}{$e_1 > 0$, $e_2 > 0$}{}
+  \end{tikzpicture}
+  \end{minipage}
+  %
+  \vspace*{1em}
+  \hrule
+  \vspace*{1em}
+  \caption{Abstract k-disjoint path analysis inference rules.}
+  \label{fig:abstract-analysis}
+  %\vspace{-1em}
+\end{figure*}
+
 %\subsection{Aggregation-safety analysis}

### 2016-10-28 scripts/abstract/run.sh
update benchmarks

@@ -9,6 +9,7 @@ if [ -f $TEMPFILE ] ; then
     rm $TEMPFILE
 fi
 
+echo "Creating benchmarks..."
 $PROPANE_CMD --bench
 
 genstats () {
@@ -23,7 +24,12 @@ genstats () {
       size=${file#benchmarks/"$1"}
       echo "$size" >> $TEMPFILE
       echo "compiling: $policy"
-      $PROPANE_CMD --policy $policy --topo $topo --anycast --failures=0 --csv >> $TEMPFILE
+      if [ $2 == "_con" ] ; then
+        flag="--no-failures"
+      else
+        flag="--failures=0"
+      fi
+      $PROPANE_CMD --policy $policy --topo $topo --anycast $flag --csv >> $TEMPFILE
     done
   done
 
@@ -31,7 +37,7 @@ genstats () {
   rm $TEMPFILE
 }
 
-genstats "backbone" "_abs"
+#genstats "backbone" "_abs"
 genstats "backbone" "_con"
 genstats "fat" "_abs"
 genstats "fat" "_con"

### 2016-10-30 paper/abstraction/paper.tex
add preliminary evaluation section

@@
 \usepackage[ampersand]{easylist}
+\usepackage{pifont}
+\newcommand{\cmark}{\ding{51}}
+\newcommand{\xmark}{\ding{55}}
 
@@
 
-\subsection{Networks studied}
-
-\begin{easylist}
-& Fattree, F10, Facebook, DCell, BCube, hyperX
-& Shortest path routing for each of these topologies but varying different size parameters
-\end{easylist}
-
-\subsection{Analysis Precision}
+We apply \sysname on policies for backbone and datacenter networks.
+We aim to evaluate the expressiveness of our abstract multiplicity annotations, the precision of the abstract disjoint-path analysis, and the compilation time of \sysname both with abstraction and without.
+
+\subsection{Analysis precision}
+
+\begin{figure}[t!]
+  \begin{center}
+      \begin{tabular}{| l l | c | c | c |}
+      \hline
+      \textbf{Topology} & \textbf{Variant} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
+      Fattree 
+         & Google &  & \cmark & \cmark  \\ 
+         & Facebook &  & \cmark & \cmark \\
+         & F10 &  & \cmark & \cmark \\ \hline
+      Recursive
+         & BCube & $k$ & \cmark & \xmark \\
+         & DCell & $k$ & \cmark & \xmark \\
+         & HCN & $h$ & \cmark & \xmark \\ \hline
+      Hypercube
+         & Standard & $N$ & \cmark & \cmark \\
+         & HyperX & $L$ & \cmark & \cmark \\ \hline
+      Random \footnote{foo}
+         & Scafida &  & ??? & ??? \\
+         & JellyFish &  & ??? & ??? \\
+
+      \hline
+      \end{tabular}
+  \end{center}
+  \caption{Abstract Analysis Precision.}
+  \label{fig:analysis-precision}
+\end{figure}
+
+We evaluate the expressiveness and precision of our abstract analysis on a range of different network topologies found in both the network literature and production.
+For each topology in figure~\ref{fig:analysis-precision} we define a suitable abstraction.
+Since many topologies have tunable parameters (e.g., the recursion depth $k$ for the DCell topology), we list all such parameters that are fixed for our abstraction.
+We implement a shortest path routing policy over the topology and record the precision of the abstract analysis in terms of whether or not it is able to accurately prove reachability and/or the correct number of disjoint paths between all pairs of nodes.
+
+\para{Fat Tree Topologies}
+
+The Fat Tree topology is one of the most widely used datacenter topologies.
+We look at the precision of our analysis on three variants of the Fat Tree~\cite{foo} topology used in practice: the Google Fat Tree, the Facebook Fat Tree, and the F10 fault tolerant Fat Tree.
+For each Fat Tree variant, we use a tiered abstraction similar to that in our previous example \ryan{Reference}.
+Each Fat Tree topology is parameterized over the number of pods $k$, which can be scaled up in the abstraction to allow for expansion.
+For all Fat Tree variants, the analysis is precise enough to determine the exact number of disjoint paths between all pairs of concrete routers.
+
+\para{Recursive Topologies}
+
+We also model several recursive topologies using our abstractions.
+These include the BCube, DCell, and HCN topologies.
+Each topology includes a recursion depth parameter ($k$, $k$, and $h$ respectively), which we must fix.
+For a recursive topology with depth $d$, we model it as an abstract topology consisting of abstract nodes for each of the depth $d-1$ subcomponents.
+This allows for safe expansion within a subcomponent, but not from increasing the recursion depth.
+The analysis is able to accurately determine reachability (i.e., at least 1 disjoint path) for each recursive topology, but is overly conservative in determining k-disjoint paths.
+For the BCube topology, it is able to to determine the correct number of disjoint paths between some pairs of nodes, but not all.
+
+\para{Hypercube Topologies}
+
+Hypercube variants can be used as an alternative to Clos-style topologies for networks with high-radix (port density) switches.
+The HyperX topology can be viewed as a generalization of the hypercube, which includes parameters $L$ for the lattice dimension of the network, $S_i$ for the node multiplicity of each dimension $i$, $K_i$ for the bandwidth of links for each dimension, and $T$ for the number of terminal nodes (servers) connected to each router.
+For a fixed number of dimensions $L$, we abstract each full mesh of $S_L$ nodes into its own abstract node.
+The $S_{x-1}$ groups of abstract nodes can be captured using pods of the abstract $S_x$ nodes.
+
+\para{Random Network Topologies}
+
+Random networks such as Scafida and Jellyfish have seen a great deal of interest in academia.
+These topologies were designed with an eye towards incremental expansion and are based on probabilistic arguments of bisection bandwidth in random regular graphs.
+However, because the topologies are created randomly, there are no hard guarantees on the connectivity between different routers.
+We can trivially represent these networks using a \emph{one big switch} abstraction for the entire network.
 
 \subsection{Compilation time}
+
+\begin{figure}
+  \subcaptionbox{Datacenter}
+    {\includegraphics[width=.49\columnwidth]{figures/Fattree-time.png}}
+  \subcaptionbox{Backbone}
+    {\includegraphics[width=.49\columnwidth]{figures/backbone-time.png}} \\
+  \caption{Concrete vs. Abstract Compilation Time. \label{fig:compilation-times}}
+  \vspace{-1em}
+\end{figure}
+
+\begin{figure}[t!]
+  \subcaptionbox{Datacenter}
+    {\includegraphics[width=.49\columnwidth]{figures/Fattree-analysis-time.png}}
+  \subcaptionbox{Backbone}
+    {\includegraphics[width=.49\columnwidth]{figures/backbone-analysis-time.png}} \\
+  \caption{Abstract Compilation Time by Phase. \label{fig:abstract-breakdown}}
+  \vspace{-1em}
+\end{figure}
+
+Using abstraction allows us to naturally scale network synthesis in \sysname.
+We evaluate compilation time in \sysname both with and without abstraction using routing policy for backbone and datacenter networks inspired by configurations obtained from a large cloud provider.
+
+\para{Routing Policy}
+
+Routers in the datacenter network run BGP using private AS numbers and peer with each other and with the backbone network over eBGP.
+The routers aggregate some prefix blocks when announcing them to the backbone network, and they keep some prefixes internal.
+The policy also ensures bogons and private address space from external neighbors is dropped.
+The data center prefers that traffic leave through certain peers over others and ensures that transit traffic between peers is never allowed in the datacenter.
+
+The backbone network classifies external neighbors into several different categories based on commercial relationship and prefers paths through them in order.
+Similar to the datacenter, it prevents bogons and private address space from external neighbors, drops transit traffic between certain peers but not through others, and aggregates internal prefixes at the border of the network.
+
+\para{Network Topology}
+
+For both networks, we use the same routing policy but scale the size of the underlying topology.
+For the datacenter networks, we use a standard Fat Tree topology and scale the size of the topology according the the number of pods $k$, starting with 4 pods and ending with 24 pods.
+The abstract topology uses a single abstract node for each tier of the datacenter, an additional abstract node for tier 0 to separate local and global prefixes, as well as a single abstract node for each group of equivalent eBGP neighbor.
+
+For the backbone networks, we split the network into two parts: a collection of border routers and a fully-connected internal core.
+We scale the backbone networks from 10 to 250 routers.
+The abstract topology uses a single abstract node for the network border routers and another abstract node for the network core.
+Backbone eBGP-speaking peers are grouped into abstract nodes based on their commercial relationship to the current AS (e.g., customer, provider, peer).
+
+\para{Results}
+
+Figure~\ref{fig:compilation-times} shows compilation time for the same policies for both the abstract and concrete versions of the policies described above.
+All experiments are run on an 8 core, 2.4 GHz Intel i7 processor Mac with 8GB of Ram.
+
+For both the datacenter and backbone networks, the abstract compilation starts off slightly slower than concrete compilation for small topologies due to the overhead of the abstract k-disjoint path analysis for aggregation black-hole safety.
+However, as the size of the topology increases, abstract compilation becomes orders of magnitude faster than concrete compilation.
+In all cases for both networks, abstract compilation takes less than 10 seconds to complete.
+
+Figure~ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract compilation.
+Notably, the abstract analysis takes the majority of the time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost.
+In particular, the number of calls to Z3 remains constant the across topology size.
+The seesaw behavior for the data center networks results from differences in time taken by Z3 to minimize the same constraints with different parameters.
 

### 2016-10-30 scripts/abstract/plot.py

@@ -112,16 +112,16 @@ def makeGraph(con, abs, name, descr):
 
   # Compilation times
   fig = plt.figure()
-  plt.plot(sizeCon, totalCon, label="Concrete", linewidth=3.0, color="cornflowerblue")
-  plt.plot(sizeAbs, totalAbs, label="Abstract", linewidth=3.0, linestyle='--', color="lightsalmon")
-  plt.xlabel(descr, fontsize=25)
-  plt.ylabel('Compilation Time (sec)', fontsize=25)
-  plt.tick_params(axis='both', which='major', labelsize=25)
-  plt.tick_params(axis='both', which='minor', labelsize=25)
+  plt.plot(sizeCon, totalCon, label="Concrete", linewidth=5.0, color="cornflowerblue")
+  plt.plot(sizeAbs, totalAbs, label="Abstract", linewidth=5.0, linestyle='--', color="lightsalmon")
+  plt.xlabel(descr, fontsize=28)
+  plt.ylabel('Compilation Time (sec)', fontsize=28)
+  plt.tick_params(axis='both', which='major', labelsize=28)
+  plt.tick_params(axis='both', which='minor', labelsize=28)
   if name == "Fattree":
-    plt.xlim([4, 30])
+    plt.xlim([4, 24])
   else:
-    plt.xlim([10,200])
+    plt.xlim([10,240])
   plt.legend(loc=2, fontsize=22)
   plt.yscale('log')
   fig.savefig(direct + '/graphs/' + name + '-time.png', bbox_inches='tight')
@@ -141,15 +141,16 @@ def makeGraph(con, abs, name, descr):
   ax1.fill_between(sizeAbs, y_stack[0,:], y_stack[1,:], facecolor=color2, alpha=.7)
   ax1.fill_between(sizeAbs, y_stack[1,:], y_stack[2,:], facecolor=color3)
   ax1.fill_between(sizeAbs, y_stack[2,:], y_stack[3,:], facecolor=color4)
-  ax1.set_xlabel(descr, fontsize=25)
-  ax1.set_ylabel('Compilation Time (sec)', fontsize=25)
-  ax1.tick_params(axis='both', which='major', labelsize=25)
-  ax1.tick_params(axis='both', which='minor', labelsize=25)
-  ax1.set_ylim([0,14])
+  ax1.set_xlabel(descr, fontsize=28)
[…]

### 2016-10-30 scripts/abstract/run.sh

@@ -24,12 +24,8 @@ genstats () {
       size=${file#benchmarks/"$1"}
       echo "$size" >> $TEMPFILE
       echo "compiling: $policy"
-      if [ $2 == "_con" ] ; then
-        flag="--no-failures"
-      else
-        flag="--failures=0"
-      fi
-      $PROPANE_CMD --policy $policy --topo $topo --anycast $flag --csv >> $TEMPFILE
+      # mask output by not specifying minimum k
+      $PROPANE_CMD --policy $policy --topo $topo --anycast --failures=0 --csv >> $TEMPFILE
     done
   done
 
@@ -37,8 +33,8 @@ genstats () {
   rm $TEMPFILE
 }
 
-#genstats "backbone" "_abs"
-genstats "backbone" "_con"
+genstats "core" "_abs"
+genstats "core" "_con"
 genstats "fat" "_abs"
 genstats "fat" "_con"
 

### 2016-10-30 paper/abstraction/paper.tex
add simple implementation section

@@
 
-\begin{easylist}
-& Extension to \sysname
-& lines of code
-& optimizations
-&& Are there any?
-\end{easylist}
+The \sysname compiler is implemented in approximately 9500 lines of F\# code.
+The compiler accepts both concrete and abstract topologies and will generate router configurations for open-source Quagga routers.
+Operators can specify their required fault tolerance level for aggregation safety.
+The abstract safety analysis uses Z3Opt \ryan{reference} to minimize variables subject to the annotated constraints.
+
+The compiler performs the following to improve its performance.
+
+\para{Z3 memoization}
+
+Although the k-disjoint path analysis takes place over the Product Graph representation, which may differ from the topology (e.g., for non-shortest paths routing), each application of the inference rules from figure~\ref{fig:abstract-analysis} depends only on the topology.
+Therefore, we lazily apply the rules and cache the satisfiability and minimization calls to Z3 after their first use.
+Doing this significantly speeds up the failure safety analysis.
+Furthermore, the cached results can be shared across different prefixes, each of which may have a unique Product graph representation.
+In practice, this means that after performing the abstract analysis for one prefix, the analysis becomes essentially "free" for any subsequent prefixes.
+
+\para{Fast Substitution}
+
+Substitution after compiling a policy abstractly can be expensive since each router must substitute all template variables for each of its connected peers.
+In practice, because many routers often share the same concrete peers, memoizing the substitution function greatly improves performance.
 
@@
          & BCube & $k$ & \cmark & \xmark \\
-         & DCell & $k$ & \cmark & \xmark \\
-         & HCN & $h$ & \cmark & \xmark \\ \hline
+         & DCell & $k$ & \cmark & \xmark \\ \hline
+         %& HCN & $h$ & \cmark & \xmark \\ 
       Hypercube
@@
 We also model several recursive topologies using our abstractions.
-These include the BCube, DCell, and HCN topologies.
-Each topology includes a recursion depth parameter ($k$, $k$, and $h$ respectively), which we must fix.
+These include the BCube and DCell topologies.
+Each topology includes a recursion depth parameter ($k$), which we must fix.
 For a recursive topology with depth $d$, we model it as an abstract topology consisting of abstract nodes for each of the depth $d-1$ subcomponents.

### 2016-10-31 paper/abstraction/paper.tex
start section 3

@@
 \newcommand{\Enter}{\KW{enter}}
-\newcommand{\Later}{\KW{later}}
-\newcommand{\Before}{\KW{before}}
+\newcommand{\Eventually}{\KW{eventually}}
+\newcommand{\Already}{\KW{already}}
 \newcommand{\Internal}{\KW{internal}}
 \newcommand{\Never}{\KW{never}}
-\newcommand{\Only}{\KW{only}}
+\newcommand{\Always}{\KW{always}}
 \newcommand{\Through}{\KW{through}}
@@
 
-\subsection{Example:  The datacenter}
-
-\begin{easylist}[itemize]
-& Example of a datacenter with two peers (running BGP).
-&& Each tier of the datacenter treats traffic the same
-&& Since each tier will treat traffic the same, operator would like to
-   avoid writing a separate configuration for each device in a given tier.
-&& Operator writes 3 templates (show example of templates, including filters).
-
-& Show example of aggregation-induced black hole
-\end{easylist}
-
-\subsection{Example:  The Backbone}
-
-\begin{easylist}[itemize]
-& Example of a backbone network with multiple peers
-&& Maybe have a couple of different roles (e.g., special handling to keep traffic in the US)
-&& Could show different abstractions here (e.g., one big switch)
-&& Could be useful to hint at things to come, e.g., takes 2 sec to compile the abstract one
-\end{easylist}
-
 %=====================================================
@@
 
-\section{Propane overview}
+\section{Methane overview}
 \label{sec:propane}
 
-\subsection{Example: The datacenter}
-
-\begin{easylist}[itemize]
-& Abstraction of datacenter tiers -- provided by a map from
-  nodes in the concrete network to nodes in the abstract network.
-  Also provide node and edge constraints.
-&& Thus, the new topology contains only those 3 abstract nodes.
-&& Rather than writting templates for each device, the operator
-  writes a centralized routing policy for the network (show propane policy)
-
-& Show generated templates from compilation (e.g., use of network-wide abstraction)
-
-& Show example of aggregation safety checking in the abstract network --
-  just give the answer + forward reference (matches with concrete example).
-
-& Suppose now we wanted to expand this network, or configure a similar network...
-\end{easylist}
-
-\subsection{Example: The Backbone}
-
-\begin{easylist}[itemize]
-& Give the policy over the abstract network
-\end{easylist}
-
-\subsection{Language}
-
-Placeholder for formal language definition syntax + semantics
-
-% Examples of code given below
-
-%\sysname lets operators configure the network with the
-%abstraction that they have centralized control over routing.
-%Specifically, the operator simply provides a set of high-level constraints
-%that describe the
-%paths traffic should---or should not---take and their relative preferences.
-%\sysname specifications are written modularly via a series
-%of declarations.
-%For example, to begin specification of the backbone
-%network from the previous section, we first express the idea that
-%we prefer that traffic leave the network through \CD{R1} over \CD{R2} (to \CD{Cust}) over \CD{Peer} over \CD{Prov} (policy P1 and P3 from Figure~\ref{fig:example1}):
-%%
-%\begin{code}
-%\Define Prefs = \Exit(R1 \Prefer R2 \Prefer Peer \Prefer Prov)
-%\end{code}
+\sysname builds on the Propane network configuration synthesis language to let
+operators specify \emph{network-wide} routing policy at a high level of abstraction.
+A \sysname policy consists of a sequence of ranked constraints on the paths traffic should 
+or should not take for certain IP prefix destinations.
+
+\subsection{Concrete Methane}
+
+Consider again the datacenter from figure~\ref{fig:example}. To configure the datacenter routing
+policy, we would start by writing the following definition in \sysname:
+%
+\begin{code}
+\Define Routing =
+    \{P1 \Path \End(T1)
+     P2 \Path \End(T2)
+     P3 \Path \End(T3)
+     P4 \Path \End(T4)
+     P5 \Path \End(T5)
+     P6 \Path \End(T6)
+     P7 \Path \End(T7)
+     P8 \Path \End(T8)
+     \True \Path \Exit(Peer1 \Prefer Peer2) \}
+\end{code}
+\noindent%
+
+This defines a group of constraints for basic routing behavior. The first line states 
+that traffic destined for prefix $P1$ must follow a path that ends up at destination router $T1$.
+A similar constraint is added for each of the prefixes P[2-8]. The final rule matches all other
+prefix destinations and allows traffic to follow a path that leaves the datacenter through either
+of its peers (Peer1 or Peer2) with a preference for leaving through Peer1. The \Prefer symbol indicates
+that traffic should satisfy the constraint on the left whenever possible, and only resort to the backup (right)
+when this is not possible due to failures.
+
+Next we can add the locality constraint for prefixes P[5-8]. We do this by adding another group of constraints:
+%
+\begin{code}
+\Define Locality =
+    \{P5 | P6 | P7 | P8 \Path \Always(\In)\}
+\end{code}
+\noindent%
+
+The Locality constraint applies to any traffic destined for a local prefix and adds
+the constraint that the traffic must follow a path that matches an internal location 
+(\IE, a router inside the datacenter) at each hop of the path. This prevents traffic 
+from ever entering from or leaving through an external peer.
+
+Finally, for all traffic in the datacenter, we will disallow valley routing. This constraint
+can be captured with the following additions to the policy:
+%
+\begin{code}
+\Define Tor = \{T1,T2,T3,T4,T5,T6,T7,T8\}
+\Define Agg = \{A1,A2,A3,A4,A5,A6,A7,A8\}
+\Define Spn = \{S1,S2\}
+
+\Define ValleyFree =
+    \{\True \Path \Novalley(Tor,Agg,Spn)\}
+\end{code}
+\noindent%
+
+The first three lines define groups of routers. The top of rack (Tor) routers T[1-8], the 
+aggregation routers (Agg) A[1-8], and the spine routers (Spn) S[1-2]. The next line 
+adds a new constraint that applies to all traffic and ensures that traffic never follows a 
+path that forms a valley between any of these three groups (\EG, going from Spn to Agg to Spn again).
+As we will see in section \ryan{reference}, each of these constraints such as the valley free constraint
+are really just syntactic sugar for regular expressions over topology locations.
+
+The final policy is declared to as the conjunction of each of these constraints:
+%
+\begin{code}
+\Define Main = 
+    Routing & 
+    Locality & 
+    ValleyFree & 
+    \Agg(PG, \In -> \Out)
+\end{code}
+\noindent%
+The last part of the policy declares that we want to perform aggregation for global prefixes
+by summarizing them into the more general prefix PG at the border of the datacenter
+(\IE along any edge starting inside our datacenter and ending outside).
+
+\subsection{Abstract Methane}
+
 %This  statement defines a set of \emph{ranked paths}, which includes
@@
 %language.
-The preference operator (\Prefer) is flexible and can be used between constraints as well as among individual routers.
+The preference operator (\Prefer) is flexible and can be used between constraints as well as among %individual routers.
 For example, the above constraint could have been written equivalently as
 %\Exit(\CD{R1}) \Prefer \ldots \Prefer ~\Exit(\CD{Prov})%
-
 %To associate ranked paths with
@@
 %customer prefixes.
-%%
+%
 %In the following code, ranked paths are associated with
@@
 %\CD{\True{} \AND{} \NOT{}PCust}.%
-%
 
@@
 %\noindent%
-
 %Line 2 of this policy
@@
 To summarize our progress, the \CD{Routing} policy
-%implements P1, P3, and P4 from Figure~\ref{fig:example1}.%
-%
+%implements P1, P3, and P4 from Figure~\ref{fig:example1}.%%
 
@@
 %\Define transit(X,Y) = \Enter(X{\OR}Y) \AND \Exit(X{\OR}Y)
-%\Define cust-transit(X,Y) = \Later(X) \AND \Later(Y)
+%\Define cust-transit(X,Y) = \Eventually(X) \AND \Eventually(Y)
 %\end{code}
@@
 Using these two new abstractions, we can now implement policies P2 and P5 with the following constraint.%
-
 %\begin{code}
@@
 %and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.%
-
 %Collectively, the constraints above capture the entire policy. From them, our compiler will generate per-device import and export filters, local preferences,
 %MED attributes, and community tags to ensure that the policy is
-%implemented correctly under all failures.%
-%
+%implemented correctly under all failures.%%
 
@@
 %in the network.%
-
 %\sysname allows modular specification of each of these constraints.
 The first constraint is about prefix ownership---we want traffic only for certain prefixes to end up at a particular location.
-The following definition captures this intent.%
-%
+The following definition captures this intent.%%
 
@@
 %The special keyword \Out{} matches any location outside the datacenter network, while the keyword \In{} will match any location inside the network.%
-
 %For the second constraint, we define another policy:%
-
 %\begin{code}
@@
 %inside the datacenter.%
-
 %As in the backbone example, we can logically conjoin these constraints
@@
 %when advertised outside the datacenter.%
-
 %\begin{code}
@@
 %\end{code}%
-
 %Once \sysname compiles the policy, it is guaranteed to remain compliant under all possible failure scenarios, modulo any aggregation-induced black holes.
@@
 
-%\begin{figure*}[t]\small
-%  \begin{minipage}[t]{.45\linewidth}
-%  \hdr{Syntax}{}
-%  \vspace*{-1\baselineskip}
-%  %
-%  \[ \begin{array}{rclr}
-%    \hline%
-
-%     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
-%     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
-%     x       &::=& d.d.d.d/d & \textit{prefix} \\
-%     t       &::=& \True & \textit{true} \\
-%         &\BNFALT& \NOT t & \textit{negation} \\
-%         &\BNFALT& t_1 \OR{} t_2 & \textit{disjunction} \\
-%         &\BNFALT& t_1 \AND{} t_2 & \textit{conjunction} \\
-%         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
-%         &\BNFALT& \textit{comm} = d & \textit{community test} \\
-%     r       &::=& l & \textit{location} \\
-%         &\BNFALT& \emptyset & \textit{empty set} \\
-%         &\BNFALT& \In & \textit{internal loc} \\
-%         &\BNFALT& \Out & \textit{external loc} \\
-%         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
-%         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
-%         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
-%         &\BNFALT& \NOT r & \textit{path negation} \\
-%         &\BNFALT& r^* & \textit{iteration} \\
-%     ln       &::=& r_1 \rightarrow r_2 & \textit{links} \\
-%     cc     &::=& agg(x, ln) \BNFALT tag(d, t, ln) & \textit{control constraints} \\
-%  \end{array} \]%
-
-%  \end{minipage}
-%  %
-%  ~~
-%  \vrule
-%  ~~
-%  %
-%  \begin{minipage}[t]{.5\linewidth}\small
-%  \hdr{Propane Expansions}{}
-%  \vspace*{-1\baselineskip}
-%  %
-%  \[\begin{array}{rcl}
-%    \hline
-%    \Any           & = & \Out^* \cdot \In^+ \cdot \Out^* \\
-%    \None          & = & \emptyset \\
-%    \Internal      & = & \In^+ \\
-%    \Only(X)       & = & \Any \cap X^* \\
-%    \Never(X)      & = & \Any \cap (!X)^* \\
-%    \Through(X)    & = & \Out^* \cdot \In^* \cdot X \cdot \In^* \cdot \Out^* \\
-%    \Later(X)      & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
-%    \Before(X)     & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
-%    \End(X)        & = & \Any \cap (\Sigma^* \cdot X) \\
-%    \Start(X)      & = & \Any \cap (X \cdot \Sigma^*) \\
-%    \Exit(X)       & = & (\Out^* \cdot \In^* \cdot (X \cap \In) \cdot \Out \cdot \Out^*) \cup \\
-%                  &        & (\Out^* \cdot \In^+ \cdot (X \cap \Out) \cdot \Out^*) \\
-%    \Enter(X)      & = & (\Out^* \cdot \Out \cdot (X \cap \In) \cdot \In^* \cdot \Out^*) \cup \\
-%                  &        & (\Out^* \cdot (X \cap \Out) \cdot \In^+ \cdot \Out^*) \\
-%    \LinkKW(X,Y)     & = & \Any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
-%    \PathKW(\vec{X}) & = & \Any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
-%    \Novalley(\vec{X}) & = & \Any ~ \cap \\
-%                  &   & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
-%                  &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
-%  \end{array} \]%
-
-%  \end{minipage}%
-
-%  \hrulefill%
-
-%  \caption{Regular Intermediate Representation (RIR) syntax (left), and
-%           Propane language expansions (right).}
-%  \label{fig:rir-syntax}
-%  %\vspace{-1em}
-%\end{figure*}%
+\begin{figure*}[t]\small
+  \begin{minipage}[t]{.45\linewidth}
+  \hdr{Syntax}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rclr}
+    \hline%
+
+     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
+     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
+     x       &::=& d.d.d.d/d & \textit{prefix} \\
+     t       &::=& \True & \textit{true} \\
+         &\BNFALT& \neg t & \textit{negation} \\
+         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
+         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
+         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
+     r       &::=& l & \textit{location} \\
+         &\BNFALT& \emptyset & \textit{empty set} \\
+         &\BNFALT& \In & \textit{internal loc} \\
+         &\BNFALT& \Out & \textit{external loc} \\
+         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
+         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
+         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
+         &\BNFALT& \NOT r & \textit{path negation} \\
+         &\BNFALT& r^* & \textit{iteration} \\
+     cc     &::=& agg(x, r_1 \rightarrow r_2)  & \textit{control constraints} \\
+  \end{array} \]%
+
+  \end{minipage}
+  %
+  ~~
+  \vrule
+  ~~
+  %
+  \begin{minipage}[t]{.5\linewidth}\small
+  \hdr{Propane Expansions}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[\begin{array}{rcl}
+    \hline
+    \Any               & = & \Sigma^* \\
+    \None              & = & \emptyset \\
+    \Internal          & = & \In^+ \\
+    \Always(X)         & = & X^* \\
+    \Never(X)          & = & (!X)^* \\
+    \Through(X)        & = & \Sigma^* \cdot X \cdot \Sigma^* \\
+    \Eventually(X)     & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
+    \Already(X)        & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
+    \End(X)            & = & \Sigma^* \cdot X \\
+    \Start(X)          & = & X \cdot \Sigma^* \\
+    \Enter(X)          & = & \Sigma^* \cdot \Out \cdot (X \cap \In) \cdot \Sigma^* ~ \cup \\
+                       &   & \Sigma^* \cdot (X \cap \Out) \cdot \In \cdot \Sigma^* \\
+    \Exit(X)           & = & \Sigma^* \cdot \In \cdot (X \cap \Out) \cdot \Sigma^* ~ \cup \\
+                       &   & \Sigma^* \cdot (X \cap \In) \cdot \Out \cdot \Sigma^* \\
+    \LinkKW(X,Y)       & = & \Sigma^* \cdot X \cdot Y \cdot \Sigma^* \\
+    \PathKW(\vec{X})   & = & \Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^* \\
+    \Novalley(\vec{X}) & = & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
+                       &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
+  \end{array} \]%
+
+  \end{minipage}%
+
+  \hrulefill%
+
+  \caption{Regular Intermediate Representation (RIR) syntax (left), and
+           Propane language expansions (right).}
+  \label{fig:rir-syntax}
+  %\vspace{-1em}
+\end{figure*}%
 

### 2016-10-31 paper/abstraction/paper.tex
Update section 3 with abstractions

@@
 \usepackage[ampersand]{easylist}
+\usepackage{textcomp}
 \usepackage{pifont}
@@
 \Define Spn = \{S1,S2\}
-
 \Define ValleyFree =
@@
 
+From this policy, \sysname can synthesize device-level BGP configurations for every router in 
+the network that guarantee correct forwarding behavior under all possible failure combinations. 
+Synthesizing configurations for each device from a network-wide specification both simplifies 
+network configuration by writing policy in one place rather than dozens and simultaneously prevents 
+a large class of errors associated with manual configuration by construction. For example, 
+the compiler ensures configurations are always in sync and prevents the operator from having 
+to manually consider failure scenarios.
+
 \subsection{Abstract Methane}
+
+Although the concrete \sysname policy can help prevent a number of configuration errors, 
+the policy is intricately linked to the actual structure of the concrete network.
+For example, each prefix in the routing constraint is enumerated with its concrete destination 
+location, and the definition of the valleyfree constraint depends on the actual routers that 
+comprise each tier of the datacenter. 
+%
+This is unfortunate since any expansion of our datacenter network will require a corresponding 
+change to the policy. Furthermore, there is no guarantee that a safe policy can be found 
+for the expanded network, and even if one can be found, it may require changes to every
+configuration in the network -- a huge barrier to adoption in practice.
+
+Abstract \sysname solves this problem in two ways. First, it allows operators to abstract
+the network into a role-based topology and write a routing specification over this abstraction instead.
+Second, it introduces prefix template variables into the language to allow writing policies that are 
+parameterized over prefix destination.
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=.6\columnwidth]{figures/example3}
+  \caption{Role-based abstraction for the datacenter in Figure~\ref{fig:example1}.}
+  \label{fig:example3}
+  \vspace{-1em}
+\end{figure}
+
+Consider again the datacenter routing policy we wrote before. 
+%
+We will now rewrite the policy over the network abstraction shown in figure~\ref{fig:example3}.
+This abstraction splits the network into 5 roles: local tor, global tor, local aggregator, global 
+aggregator, and spine. Intuitively, each concrete router in the network must map to exactly one role.
+Whenever there is a link between routers in the concrete network, there must be an associated link
+between their abstract roles. Thus the role-based abstraction is an overapproximation of the connectivity
+of the concrete network.
+
+The new routing policy can only refer to locations in the abstract topology. We choose these 5 roles,
+since its gives us fine enough granularity to implement our policy, but is general enough to enable 
+expansion (\EG, by adding new concrete routers for a given role).
+
+We can modify the concrete routing policy for this abstraction in the following way. First we change the Routing policy:
+%
+\begin{code}
+\Define Routing =
+    \{\$PG \Path \End(TG)
+     \$PL \Path \End(TL)
+     \True \Path \Exit(Peer1 \Prefer Peer2) \}
+\end{code}
+\noindent%
+
+Here we introduce two prefix \emph{template} variables. The policy says that traffic for each 
+global prefix associated with the template variable \$PG should end up at its corresponding 
+destination router contained in the abstract TG role. The second line does something similar 
+for all local prefixes. Finally, the last line remains the same as before.
+
+Next we can modify the Locality constraint for the abstraction in a straightforward way:
+%
+\begin{code}
+\Define Locality = \{\$PL \Path \Always(\In)\}
+\end{code}
+\noindent%
+
+Finally, we can add the "valleyfree" constraint. We are able to encode this constraint for the
+abstract topology because we have retained enough structure to understand what a valley is. 
+%
+\begin{code}
+\Define Tor = \{TL,TG\}
+\Define Agg = \{AL,AG\}
+\Define Spn = \{S\}
+\Define ValleyFree =
+    \{\True \Path \Novalley(Tor,Agg,Spn)\}
+\end{code}
+\noindent%
+
+The constraint prevents traffic from over taking a path that traverses 
+either [Agg->Tor->Agg] or [Spn->Agg->Spn]. The final policy remains the same as before,
+by combining each of these policies together.
+%
+\begin{code}
+\Define Main = 
+    Routing & 
+    Locality & 
+    ValleyFree & 
+    \Agg(PG, \In -> \Out)
+\end{code}
+\noindent%
+
+When \sysname compiles the above policy, it guarantees that the forwarding behavior 
+of the network will be correct for any concrete instantiation of the abstract network,
+and for any combination of failures that may occur in the concrete network.
+Furthermore, if we want to expand our network for example by adding additional spine 
+routers, \sysname will guarantee that the expansion will be incremental (\IE, only
+configurations for routers local to the expansion will need to change).
 

### 2016-10-31 paper/abstraction/paper.tex
start with compilation example
remove conceret methane

@@
 
-\sysname builds on the Propane network configuration synthesis language to let
-operators specify \emph{network-wide} routing policy at a high level of abstraction.
-A \sysname policy consists of a sequence of ranked constraints on the paths traffic should 
-or should not take for certain IP prefix destinations.
-
-\subsection{Concrete Methane}
-
-Consider again the datacenter from figure~\ref{fig:example}. To configure the datacenter routing
-policy, we would start by writing the following definition in \sysname:
+As we have seen, writing correct network configurations is challenging task.
+Operators must manually decompose network-wide policies into device configurations,
+reason about all combination of network failures, parameterize configurations to 
+allow for change, and write configurations in a way amenable to incremental change.
+We now give an overview of \sysname, a system that facilitates all of these tasks.
+
+%\subsection{Concrete Methane}%
+
+%Consider again the datacenter from figure~\ref{fig:example}. To configure the datacenter routing
+%policy, we would start by writing the following definition in \sysname:
+%%
+%\begin{code}
+%\Define Routing =
+%    \{P1 \Path \End(T1)
+%     P2 \Path \End(T2)
+%     P3 \Path \End(T3)
+%     P4 \Path \End(T4)
+%     P5 \Path \End(T5)
+%     P6 \Path \End(T6)
+%     P7 \Path \End(T7)
+%     P8 \Path \End(T8)
+%     \True \Path \Exit(Peer1 \Prefer Peer2) \}
+%\end{code}
+%\noindent%%
+
+%This defines a group of constraints for basic routing behavior. The first line states 
+%that traffic destined for prefix $P1$ must follow a path that ends up at destination router $T1$.
+%A similar constraint is added for each of the prefixes P[2-8]. The final rule matches all other
+%prefix destinations and allows traffic to follow a path that leaves the datacenter through either
+%of its peers (Peer1 or Peer2) with a preference for leaving through Peer1. The \Prefer symbol indicates
+%that traffic should satisfy the constraint on the left whenever possible, and only resort to the backup (right)
+%when this is not possible due to failures.%
+
+%Next we can add the locality constraint for prefixes P[5-8]. We do this by adding another group of constraints:
+%%
+%\begin{code}
+%\Define Locality =
+%    \{P5 | P6 | P7 | P8 \Path \Always(\In)\}
+%\end{code}
+%\noindent%%
+
+%The Locality constraint applies to any traffic destined for a local prefix and adds
+%the constraint that the traffic must follow a path that matches an internal location 
+%(\IE, a router inside the datacenter) at each hop of the path. This prevents traffic 
+%from ever entering from or leaving through an external peer.%
+
+%Finally, for all traffic in the datacenter, we will disallow valley routing. This constraint
+%can be captured with the following additions to the policy:
+%%
+%\begin{code}
+%\Define Tor = \{T1,T2,T3,T4,T5,T6,T7,T8\}
+%\Define Agg = \{A1,A2,A3,A4,A5,A6,A7,A8\}
+%\Define Spn = \{S1,S2\}
+%\Define ValleyFree =
+%    \{\True \Path \Novalley(Tor,Agg,Spn)\}
+%\end{code}
+%\noindent%%
+
+%The first three lines define groups of routers. The top of rack (Tor) routers T[1-8], the 
+%aggregation routers (Agg) A[1-8], and the spine routers (Spn) S[1-2]. The next line 
+%adds a new constraint that applies to all traffic and ensures that traffic never follows a 
+%path that forms a valley between any of these three groups (\EG, going from Spn to Agg to Spn again).
+%As we will see in section \ryan{reference}, each of these constraints such as the valley free constraint
+%are really just syntactic sugar for regular expressions over topology locations.%
+
+%The final policy is declared to as the conjunction of each of these constraints:
+%%
+%\begin{code}
+%\Define Main = 
+%    Routing & 
+%    Locality & 
+%    ValleyFree & 
+%    \Agg(PG, \In -> \Out)
+%\end{code}
+%\noindent%
+%The last part of the policy declares that we want to perform aggregation for global prefixes
+%by summarizing them into the more general prefix PG at the border of the datacenter
+%(\IE along any edge starting inside our datacenter and ending outside).%
+
+%From this policy, \sysname can synthesize device-level BGP configurations for every router in 
+%the network that guarantee correct forwarding behavior under all possible failure combinations. 
+%Synthesizing configurations for each device from a network-wide specification both simplifies 
+%network configuration by writing policy in one place rather than dozens and simultaneously prevents 
+%a large class of errors associated with manual configuration by construction. For example, 
+%the compiler ensures configurations are always in sync and prevents the operator from having 
+%to manually consider failure scenarios.
+
+\subsection{Abstract Methane}
+
+\sysname builds on the Propane network configuration synthesis language, 
+which lets operators specify a \emph{network-wide} routing policy, by adding
+support for compiling policies parameterized over different topology.
+In particular, a \sysname policy consists of predicates matching
+certain classes of traffic, paired with a list of ranked constraints 
+on the paths traffic should prefer to take for the predicate.
+
+Consider again the datacenter from earlier. Ideally, we would like
+to find device configuration templates for each router that, taken together, ensure correct forwarding
+behavior for both of the datacenter topologies in figures~\ref{fig:example} and~\ref{fig:example2}.
+
+\sysname achieves this by allowing the operator to abstract the network into 
+a role-based topology that captures a class of concrete topologies and then write a 
+routing specification over this abstraction. Figure~\ref{fig:example3} shows an example of one 
+such abstraction for the datacenter networks. The network is partitioned into 5 different roles:
+local tor (TL), global tor (TG), local aggregator (AL), global aggregator (AG), and spine (S).
+Each router in the concrete topology maps to exactly one abstract role.
+
+%Although the concrete \sysname policy can help prevent a number of configuration errors, 
+%the policy is intricately linked to the actual structure of the concrete network.
+%For example, each prefix in the routing constraint is enumerated with its concrete destination 
+%location, and the definition of the valleyfree constraint depends on the actual routers that 
+%comprise each tier of the datacenter. 
+%
+%This is unfortunate since any expansion of our datacenter network will require a corresponding 
+%change to the policy. Furthermore, there is no guarantee that a safe policy can be found 
+%for the expanded network, and even if one can be found, it may require changes to every
+%configuration in the network -- a huge barrier to adoption in practice.
+
+%Abstract \sysname solves this problem in two ways. First, it allows operators to abstract
+%the network into a role-based topology and write a routing specification over this abstraction instead.
+%Second, it introduces prefix template variables into the language to allow writing policies that are 
+%parameterized over prefix destination.
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=.6\columnwidth]{figures/example3}
+  \caption{Role-based abstraction for the datacenter in Figure~\ref{fig:example}.}
+  \label{fig:example3}
+  \vspace{-1em}
+\end{figure}
+
+Consider again the datacenter routing policy we wrote before. 
+%
+We will now rewrite the policy over the network abstraction shown in figure~\ref{fig:example3}.
+This abstraction splits the network into 5 roles: local tor, global tor, local aggregator, global 
+aggregator, and spine. Intuitively, each concrete router in the network must map to exactly one role.
+Whenever there is a link between routers in the concrete network, there must be an associated link
+between their abstract roles. Thus the role-based abstraction is an overapproximation of the connectivity
+of the concrete network.
+
+The new routing policy can only refer to locations in the abstract topology. We choose these 5 roles,
+since its gives us fine enough granularity to implement our policy, but is general enough to enable 
+expansion (\EG, by adding new concrete routers for a given role).
+
+We can modify the concrete routing policy for this abstraction in the following way. First we change the Routing policy:
 %
@@
 \Define Routing =
-    \{P1 \Path \End(T1)
-     P2 \Path \End(T2)
-     P3 \Path \End(T3)
-     P4 \Path \End(T4)
-     P5 \Path \End(T5)
-     P6 \Path \End(T6)
-     P7 \Path \End(T7)
-     P8 \Path \End(T8)
+    \{\$PG \Path \End(TG)
+     \$PL \Path \End(TL)
      \True \Path \Exit(Peer1 \Prefer Peer2) \}
@@
 
-This defines a group of constraints for basic routing behavior. The first line states 
-that traffic destined for prefix $P1$ must follow a path that ends up at destination router $T1$.
-A similar constraint is added for each of the prefixes P[2-8]. The final rule matches all other
-prefix destinations and allows traffic to follow a path that leaves the datacenter through either
-of its peers (Peer1 or Peer2) with a preference for leaving through Peer1. The \Prefer symbol indicates
-that traffic should satisfy the constraint on the left whenever possible, and only resort to the backup (right)
-when this is not possible due to failures.
-
-Next we can add the locality constraint for prefixes P[5-8]. We do this by adding another group of constraints:
+Here we introduce two prefix \emph{template} variables. The policy says that traffic for each 
+global prefix associated with the template variable \$PG should end up at its corresponding 
+destination router contained in the abstract TG role. The second line does something similar 
+for all local prefixes. Finally, the last line remains the same as before.
+
+Next we can modify the Locality constraint for the abstraction in a straightforward way:
 %
 \begin{code}
-\Define Locality =
-    \{P5 | P6 | P7 | P8 \Path \Always(\In)\}
+\Define Locality = \{\$PL \Path \Always(\In)\}
 \end{code}
@@
 
-The Locality constraint applies to any traffic destined for a local prefix and adds
-the constraint that the traffic must follow a path that matches an internal location 
-(\IE, a router inside the datacenter) at each hop of the path. This prevents traffic 
-from ever entering from or leaving through an external peer.
-
-Finally, for all traffic in the datacenter, we will disallow valley routing. This constraint
-can be captured with the following additions to the policy:
+Finally, we can add the "valleyfree" constraint. We are able to encode this constraint for the
+abstract topology because we have retained enough structure to understand what a valley is. 
 %
 \begin{code}
-\Define Tor = \{T1,T2,T3,T4,T5,T6,T7,T8\}
-\Define Agg = \{A1,A2,A3,A4,A5,A6,A7,A8\}
-\Define Spn = \{S1,S2\}
+\Define Tor = \{TL,TG\}
+\Define Agg = \{AL,AG\}
+\Define Spn = \{S\}
 \Define ValleyFree =
@@
 
-The first three lines define groups of routers. The top of rack (Tor) routers T[1-8], the 
-aggregation routers (Agg) A[1-8], and the spine routers (Spn) S[1-2]. The next line 
-adds a new constraint that applies to all traffic and ensures that traffic never follows a 
-path that forms a valley between any of these three groups (\EG, going from Spn to Agg to Spn again).
-As we will see in section \ryan{reference}, each of these constraints such as the valley free constraint
-are really just syntactic sugar for regular expressions over topology locations.
-
-The final policy is declared to as the conjunction of each of these constraints:
+The constraint prevents traffic from over taking a path that traverses 
+either [Agg->Tor->Agg] or [Spn->Agg->Spn]. The final policy remains the same as before,
+by combining each of these policies together.
 %
@@
 \noindent%
-The last part of the policy declares that we want to perform aggregation for global prefixes
-by summarizing them into the more general prefix PG at the border of the datacenter
-(\IE along any edge starting inside our datacenter and ending outside).
-
-From this policy, \sysname can synthesize device-level BGP configurations for every router in 
-the network that guarantee correct forwarding behavior under all possible failure combinations. 
-Synthesizing configurations for each device from a network-wide specification both simplifies 
-network configuration by writing policy in one place rather than dozens and simultaneously prevents 
-a large class of errors associated with manual configuration by construction. For example, 
-the compiler ensures configurations are always in sync and prevents the operator from having 
-to manually consider failure scenarios.
-
-\subsection{Abstract Methane}
-
-Although the concrete \sysname policy can help prevent a number of configuration errors, 
-the policy is intricately linked to the actual structure of the concrete network.
-For example, each prefix in the routing constraint is enumerated with its concrete destination 
-location, and the definition of the valleyfree constraint depends on the actual routers that 
-comprise each tier of the datacenter. 
-%
-This is unfortunate since any expansion of our datacenter network will require a corresponding 
-change to the policy. Furthermore, there is no guarantee that a safe policy can be found 
-for the expanded network, and even if one can be found, it may require changes to every
-configuration in the network -- a huge barrier to adoption in practice.
-
-Abstract \sysname solves this problem in two ways. First, it allows operators to abstract
-the network into a role-based topology and write a routing specification over this abstraction instead.
-Second, it introduces prefix template variables into the language to allow writing policies that are 
-parameterized over prefix destination.
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=.6\columnwidth]{figures/example3}
-  \caption{Role-based abstraction for the datacenter in Figure~\ref{fig:example1}.}
-  \label{fig:example3}
-  \vspace{-1em}
-\end{figure}
-
-Consider again the datacenter routing policy we wrote before. 
-%
-We will now rewrite the policy over the network abstraction shown in figure~\ref{fig:example3}.
-This abstraction splits the network into 5 roles: local tor, global tor, local aggregator, global 
-aggregator, and spine. Intuitively, each concrete router in the network must map to exactly one role.
-Whenever there is a link between routers in the concrete network, there must be an associated link
-between their abstract roles. Thus the role-based abstraction is an overapproximation of the connectivity
-of the concrete network.
-
-The new routing policy can only refer to locations in the abstract topology. We choose these 5 roles,
-since its gives us fine enough granularity to implement our policy, but is general enough to enable 
-expansion (\EG, by adding new concrete routers for a given role).
-
-We can modify the concrete routing policy for this abstraction in the following way. First we change the Routing policy:
-%
-\begin{code}
-\Define Routing =
-    \{\$PG \Path \End(TG)
-     \$PL \Path \End(TL)
-     \True \Path \Exit(Peer1 \Prefer Peer2) \}
-\end{code}
-\noindent%
-
-Here we introduce two prefix \emph{template} variables. The policy says that traffic for each 
-global prefix associated with the template variable \$PG should end up at its corresponding 
-destination router contained in the abstract TG role. The second line does something similar 
-for all local prefixes. Finally, the last line remains the same as before.
-
-Next we can modify the Locality constraint for the abstraction in a straightforward way:
-%
-\begin{code}
-\Define Locality = \{\$PL \Path \Always(\In)\}
-\end{code}
-\noindent%
-
-Finally, we can add the "valleyfree" constraint. We are able to encode this constraint for the
-abstract topology because we have retained enough structure to understand what a valley is. 
-%
-\begin{code}
-\Define Tor = \{TL,TG\}
-\Define Agg = \{AL,AG\}
-\Define Spn = \{S\}
-\Define ValleyFree =
-    \{\True \Path \Novalley(Tor,Agg,Spn)\}
-\end{code}
-\noindent%
-
-The constraint prevents traffic from over taking a path that traverses 
-either [Agg->Tor->Agg] or [Spn->Agg->Spn]. The final policy remains the same as before,
-by combining each of these policies together.
-%
-\begin{code}
-\Define Main = 
-    Routing & 
-    Locality & 
-    ValleyFree & 
-    \Agg(PG, \In -> \Out)
-\end{code}
-\noindent%
 
@@
 
-%This  statement defines a set of \emph{ranked paths}, which includes
-%all paths (and only those paths) for which traffic exits our network
-%through either router \CD{R1}, router \CD{R2}, \CD{Peer}, or \CD{Prov}.
-%The paths that exit through \CD{R1}
-%are preferred (\Prefer) to those that exit through \CD{R2}, which are preferred to those that
-%leave through \CD{Peer} and then \CD{Prov}.  As we
-%describe in the next section, the \Exit\ expression, as well as other
-%path expressions used later in this section, is simply a shorthand for
-%a particular regular expression over paths that is expressible in our policy
-%language.
-The preference operator (\Prefer) is flexible and can be used between constraints as well as among %individual routers.
-For example, the above constraint could have been written equivalently as
-%\Exit(\CD{R1}) \Prefer \ldots \Prefer ~\Exit(\CD{Prov})%
-%To associate ranked paths with
-%one or more prefixes, we define a \sysname \emph{policy}.
-%Within a policy, statements with the form $t\;$\Path$\;p$
-%associate the prefixes defined by the predicate $t$ with the set of
-%ranked paths defined by the path expression $p$.  In general,
-%prefix predicates can be defined by arbitrary boolean combinations
-%(and, or, not) of concrete prefixes and community tags.  Here,
-%we assume we have already defined the predicate \CD{PCust} for the
-%customer prefixes.
-%
-%In the following code, ranked paths are associated with
-%customer prefixes,
-%and all other prefixes (\CD{true}). Policy statements are processed in
-%order with earlier policy statements taking precedence over later
-%policy statements. Hence, when the predicate \True{} follows
-%the statement involving \CD{PCust}, it is interpreted as
-%\CD{\True{} \AND{} \NOT{}PCust}.%
-
-%\begin{code}
-%\Define Routing =
-%    \{PCust \Path Prefs \AND \End(Cust)
-%     \True  \Path Prefs \}
-%\end{code}
-%\noindent%
-%Line 2 of this policy
-%restricts traffic destined to known customer prefixes (\CD{PCust}) to only follow paths that end at the customer.
-In addition, it enforces the network-wide preference that traffic leaves through \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
-%%
-%Line 3 applies to any other traffic not matching \CD{PCust} and allows the traffic to leave through any direct neighbor with the usual preference of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
-To summarize our progress, the \CD{Routing} policy
-%implements P1, P3, and P4 from Figure~\ref{fig:example1}.%%
-
-%Since, routing allows transit traffic by default (\EG, traffic entering from
-%\CD{Peer} and leaving through \CD{Prov}), we separately define a
-%policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
-%disjunction (\OR) and negation (\NOT) of constraints.
-%First, we create reusable abstractions for describing traffic that transits our network. In \sysname, this is done by creating a new parameterized definition.
-%\begin{code}
-%\Define transit(X,Y) = \Enter(X{\OR}Y) \AND \Exit(X{\OR}Y)
-%\Define cust-transit(X,Y) = \Eventually(X) \AND \Eventually(Y)
-%\end{code}
-%\noindent
-%Here we define transit traffic between groups of neighbors $X$ and $Y$ as traffic that enters the network through some neighbor in $X$ or $Y$ and then also leaves the network through some neighbor in either $X$ or $Y$.
-Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network.
-Using these two new abstractions, we can now implement policies P2 and P5 with the following constraint.%
-%\begin{code}
-%\Define NoTrans =
-%  \{\True \Path \NOT{}transit(Peer,Prov) \AND
-%           \NOT{}cust-transit(Cust,Prov)\}
-%\end{code}
-%\noindent
-%The \CD{NoTrans} constraint requires that all traffic not follow a path that transits our network between \CD{Peer} and \CD{Prov}.
-%Additionally, it prevents traffic from ever following paths that leave our network and later go through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
-%and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.%
-%Collectively, the constraints above capture the entire policy. From them, our compiler will generate per-device import and export filters, local preferences,
-%MED attributes, and community tags to ensure that the policy is
-%implemented correctly under all failures.%%
-
-%Our datacenter example network has three main concerns:
-%(1) traffic for the prefix allocated to each top-of-rack router must be able to reach that router,
-%(2) local services must not leak outside the datacenter, and
-%(3) aggregation must be performed on global prefixes to reduce churn
-%in the network.%
-%\sysname allows modular specification of each of these constraints.
-The first constraint is about prefix ownership---we want traffic only for certain prefixes to end up at a particular location.
-The following definition captures this intent.%%
-
-%\begin{code}
-%\Define Ownership =
-%    \{PG1 \Path \End(A)
-%     PG2 \Path \End(B)
-%     PL1 \Path \End(E)
-%     PL2 \Path \End(F)
-%     \True \Path \End(\Out)\}
-%\end{code}
-%\noindent
-%This definition says that traffic for prefix \CD{PG1} is allowed to follow only paths that
-%end at router \CD{A}; traffic for \CD{PG2},
-%but not \CD{PG1}, must
-%end at router \CD{B}; and so on.
-%Any traffic destined for a prefix that is not a part of the datacenter should be allowed to leave the datacenter and end at some external location, which is otherwise unconstrained.
-%The special keyword \Out{} matches any location outside the datacenter network, while the keyword \In{} will match any location inside the network.%
-%For the second constraint, we define another policy:%
-%\begin{code}
-%\Define Locality =
-%    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
-%\end{code}
-%\noindent
-%%
-%This definition says that traffic for local
-%prefixes only follows paths that are internal to the network at each hop.
-%This constraint guarantees that the services remain accessible only to locations
-%inside the datacenter.%
-%As in the backbone example, we can logically conjoin these constraints
-%to specify the network-wide policy.
-%However, in addition to constraints on the shape of paths,
-%\sysname allows the operator to specify constraints on the BGP control plane itself.
-%For instance, a constraint on aggregation is included to ensure that
-%aggregation for global prefixes is performed from
-%locations inside (\In) the network to locations outside (\Out).
-%In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG}
-%(which we assume is defined earlier)
-%when advertised outside the datacenter.%
-%\begin{code}
-%Ownership \AND{} Locality \AND{} \Agg(PG, \In \Link \Out)
-%\end{code}%
-%Once \sysname compiles the policy, it is guaranteed to remain compliant under all possible failure scenarios, modulo any aggregation-induced black holes.
-In the presence of aggregation, the \sysname compiler will also efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.
-
-%=====================================================
-%
-%
-%  **Compilation**
-%
-%
-%=====================================================
-
-\section{Compilation}
-\label{sec:compilation}
-
-We borrow the intermediate graph-based representation from Propane:
-
-\begin{easylist}[itemize]
-& Show compilation from language to RIR
-
-& Show compilation from RIR to Product Graph
-&& Note that preferences are general, and it could potentially
-   use any implementation (including SDN). But for the sake of
-   simplicity, we will assume a BGP backend like Propane.
-\end{easylist}
-
-%=====================================================
-%
-%
-%  **Abstractions**
-%
-%
-%=====================================================
-
-\section{Abstraction}
-\label{sec:abstraction}
-
-\begin{easylist}[itemize]
-& Define abstractions more formally,
-&& e.g., homomorphism between graphs + node/edge constraints
-&& Use the datacenter example from before
-&& First define the concretization function for translating the abstract policy
-   into the concrete policy
-&& Next, show the Product Graph for both the concrete and abstract policies.
-
-& Show/Define safety analysis simulation relation for both concrete and abstract product graphs
-  and how it holds for both.
-&& Theorem: if safety analysis holdls in the abstract graph, it holds for the concrete one,
-   and the preferences are consistent.
-
-& Show/Define compilation to abstract BGP policies. Give concretization function,
-  and compilation definition.
-
-& Give abstraction theorem: commuting of concretization and compilation
-\end{easylist}
-
-%The examples above use what we call the front end (FE) of \sysname.
-%It simplifies operators' task of describing preferred paths, but that simplicity comes at the cost of compilation complexity.
-The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology and ensure policy compliance under all failure scenarios.%
-
-%\begin{figure}[t!]
-%  \centering
-%  \includegraphics[width=.75\columnwidth]{figures/pipeline}
-%  \caption{Compilation pipeline stages for Propane.}
-%  \label{fig:pipeline}
-%  \vspace{-1em}
-%\end{figure}%
+\subsection{Language}
+
+\ryan{TODO: introduce language + semantics}
 
@@
 
+%=====================================================
+%
+%
+%  **Compilation**
+%
+%
+%=====================================================
+
+\section{Compilation}
+\label{sec:compilation}
+
+We borrow the intermediate graph-based representation from Propane:
+
+\begin{easylist}[itemize]
+& Show compilation from language to RIR
+
+& Show compilation from RIR to Product Graph
+&& Note that preferences are general, and it could potentially
+   use any implementation (including SDN). But for the sake of
+   simplicity, we will assume a BGP backend like Propane.
+\end{easylist}
+
+\newcommand{\state}[4]{\node[state,#3](#1)[#4]{#2};}
+\newcommand{\transition}[4]{\path[->] (#1) edge [#4] node {#3} (#2);}
+
+\begin{figure*}[t!]
+  \begin{minipage}[t]{.2\linewidth}
+  \hdr{Policy Automata}{}
+  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
+    \state{0}{$0$}{              }{}
+    \state{1}{$1$}{right of=0}{accepting}
+    \transition{0}{0}{out}{loop above}
+    \transition{0}{1}{Peer1}{}
+    \transition{1}{1}{in}{loop above}
+  \end{tikzpicture}
+
+  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
+    \state{0}{$0$}{              }{}
+    \state{1}{$1$}{right of=0}{accepting}
+    \transition{0}{0}{out}{loop above}
+    \transition{0}{1}{Peer2}{}
+    \transition{1}{1}{in}{loop above}
+  \end{tikzpicture}%
+  \end{minipage}
+  %
+  ~~~~~~
+  %
+  \begin{minipage}[t]{.45\linewidth}
+  \hdr{Concrete Topology}{}
+  \includegraphics[width=\columnwidth]{figures/example}
+  \end{minipage}%
+  %
+  \begin{minipage}[t]{.35\linewidth}
+  \hdr{Abstract Topology}{}
+  \includegraphics[width=.75\columnwidth]{figures/example3}
+  \end{minipage}%
+
+  \begin{minipage}[t]{.6\linewidth}
+  \hdr{Concrete Product Graph}{}
+  %\includegraphics[width=.65\columnwidth]{figures/example3}
+  \end{minipage}%
+  \begin{minipage}[t]{.4\linewidth}
+  \hdr{Abstract Product Graph}{}
+
+    \begin{tikzpicture}
+      \draw [] (0, 0) circle [radius=0.45] node {start};
+      \draw [] (-1, -1) circle [radius=0.45] node {$(S,0,0)$};
+      %\draw [] (0, .45) -- (0, 2.05);
+    \end{tikzpicture}
+
+  \end{minipage}%
+
+  \hrulefill
+  \vspace*{.4em}%
+
+  \caption{Product graph construction for policy $true \Path \Exit(\text{Peer1} \Prefer \text{Peer2})$.}
+  \label{fig:example-compilation}
+  %\vspace{-1em}
+\end{figure*}
+
+%=====================================================
+%
+%
+%  **Abstractions**
+%
+%
+%=====================================================
+
+\section{Abstraction}
+\label{sec:abstraction}
+
+\begin{easylist}[itemize]
+& Define abstractions more formally,
+&& e.g., homomorphism between graphs + node/edge constraints
+&& Use the datacenter example from before
+&& First define the concretization function for translating the abstract policy
+   into the concrete policy
+&& Next, show the Product Graph for both the concrete and abstract policies.
+
+& Show/Define safety analysis simulation relation for both concrete and abstract product graphs
+  and how it holds for both.
+&& Theorem: if safety analysis holdls in the abstract graph, it holds for the concrete one,
+   and the preferences are consistent.
+
+& Show/Define compilation to abstract BGP policies. Give concretization function,
+  and compilation definition.
+
+& Give abstraction theorem: commuting of concretization and compilation
+\end{easylist}
+
+%The examples above use what we call the front end (FE) of \sysname.
+%It simplifies operators' task of describing preferred paths, but that simplicity comes at the cost of compilation complexity.
+The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology and ensure policy compliance under all failure scenarios.%
+
+%\begin{figure}[t!]
+%  \centering
+%  \includegraphics[width=.75\columnwidth]{figures/pipeline}
+%  \caption{Compilation pipeline stages for Propane.}
+%  \label{fig:pipeline}
+%  \vspace{-1em}
+%\end{figure}%
+
 %To handle these challenges, we decompose compilation into multiple stages, shown in  Figure~\ref{fig:pipeline}, and develop efficient algorithms for the translation between stages.
@@
 %Policies that contain preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) are also rejected by \sysname as invalid.
-
-\newcommand{\state}[4]{\node[state,#3](#1)[#4]{#2};}
-\newcommand{\transition}[4]{\path[->] (#1) edge [#4] node {#3} (#2);}
-
-%\begin{figure*}[t!]
-%  \begin{minipage}[t]{.5\linewidth}%
-
-%  \hdr{Topology}{}
-%  \vspace*{-2\baselineskip}%
-
-%  \includegraphics[width=.6\columnwidth]{figures/topology}%
-
-%  \hdr{Policy Automata}{}
-%  \vspace*{-0.5\baselineskip}%
-
-%  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.4cm,minimum size=1cm]
-%    \state{0}{$0$}{              }{}
-%    \state{1}{$1$}{right of=0}{}
-%    \state{2}{$2$}{right of=1}{}
-%    \state{3}{$3$}{right of=2}{}
-%    \state{4}{$4$}{right of=3}{}
-%    \state{5}{$5$}{right of=4}{accepting}
-%    \transition{0}{1}{out}{}
-%    \transition{1}{2}{D}{}
-%    \transition{2}{3}{C}{}
-%    \transition{3}{4}{A}{}
-%    \transition{4}{5}{W}{}
-%  \end{tikzpicture}%
-
-%  \vspace*{0.5em}%
-%
-
-%  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.6cm]
-%    \state{0}{$0$}{              }{}
-%    \state{1}{$1$}{right of=0}{}
-%    \state{2}{$2$}{right of=1}{}
-%    \state{3}{$3$}{right of=2}{}
-%    \state{4}{$4$}{right of=3}{accepting}
-%    \transition{0}{1}{out}{}
-%    \transition{1}{2}{in}{}
-%    \transition{2}{2}{A,C,D,E}{loop above}
-%    \transition{2}{3}{B}{}
-%    \transition{3}{3}{B}{loop above}
-%    \transition{3}{2}{A,C,D,E}{bend left}
-%    \transition{3}{4}{W}{}
-%  \end{tikzpicture}
-%  \end{minipage}
-%  %
-%  ~~
-%  ~~
-%  %
-%  \begin{minipage}[t]{.5\linewidth}
-%  \hdr{Product Graph IR}{}
-%  \vspace*{-1\baselineskip}
-%  %
-%  \includegraphics[width=.8\columnwidth]{figures/productgraph}
-%  \end{minipage}%
-
-%  \hrulefill
-%  \vspace*{.4em}%
-
-%  \caption{Product graph construction for policy $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
-%  \label{fig:example-compilation}
-%  %\vspace{-1em}
-%\end{figure*}
 
@@
 
-Figure~ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract compilation.
+Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract compilation.
 Notably, the abstract analysis takes the majority of the time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost.

### 2016-10-31 paper/abstraction/paper.tex
update section 3

@@
 routing specification over this abstraction. Figure~\ref{fig:example3} shows an example of one 
-such abstraction for the datacenter networks. The network is partitioned into 5 different roles:
+such abstraction for the datacenter networks.
+
+The network is partitioned into 5 different roles:
 local tor (TL), global tor (TG), local aggregator (AL), global aggregator (AG), and spine (S).
-Each router in the concrete topology maps to exactly one abstract role.
+Intuitively, each concrete router in the network must map to exactly one role.
+Whenever there is a link between routers in the concrete network, there must be an associated link
+between their abstract roles. Thus the role-based abstraction is an overapproximation of the connectivity
+of the concrete network.
+
+In order to refine the abstraction to capture more precisely the kinds of concrete networks of interest, 
+we introduce a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
+with a symbolic variable (\EG, $e1, e2, \ldots$) that denotes a constraint on the number of nodes/edges 
+that may appear in any given concrete network. Operators can then add constraints to relate symbolic 
+variables taken from any valid SMT theory. For example, in Figure~\ref{fig:example3}, the variable $e1$
+represents the number of outgoing edges from any concrete node mapped to the TG role to other concrete
+nodes mapped to the AG role. Similarly, we introduce a node multiplicity variable for each role. For example,
+the multiplicity variable $AG$ represents the number of concrete nodes that map the the AG role. We can then 
+add constraints over these symbolic variables to capture invariants in the concrete networks. For example, 
+if we only want to consider networks where TG and AG routers form a full mesh in each pod we would add the
+following constraints: $e1 = AG$, $e2 = TG$. \ryan{how to add the constraints to the image? in latex or powerpoint?}
 
@@
   \centering
-  \includegraphics[width=.6\columnwidth]{figures/example3}
-  \caption{Role-based abstraction for the datacenter in Figure~\ref{fig:example}.}
+  \includegraphics[width=.7\columnwidth]{figures/example3}
+  \caption{Role-based abstraction for the datacenters in Figure~\ref{fig:example}.}
   \label{fig:example3}
@@
 
-Consider again the datacenter routing policy we wrote before. 
-%
-We will now rewrite the policy over the network abstraction shown in figure~\ref{fig:example3}.
-This abstraction splits the network into 5 roles: local tor, global tor, local aggregator, global 
-aggregator, and spine. Intuitively, each concrete router in the network must map to exactly one role.
-Whenever there is a link between routers in the concrete network, there must be an associated link
-between their abstract roles. Thus the role-based abstraction is an overapproximation of the connectivity
-of the concrete network.
-
-The new routing policy can only refer to locations in the abstract topology. We choose these 5 roles,
-since its gives us fine enough granularity to implement our policy, but is general enough to enable 
-expansion (\EG, by adding new concrete routers for a given role).
-
-We can modify the concrete routing policy for this abstraction in the following way. First we change the Routing policy:
+Now let us configure the datacenter networks by writing a routing policy over the 
+abstract topology. The first part of the policy will be:
 %
@@
      \$PL \Path \End(TL)
-     \True \Path \Exit(Peer1 \Prefer Peer2) \}
+     \True \Path \Exit(Peer1 \Prefer Peer2)\}
 \end{code}
@@
 
-Here we introduce two prefix \emph{template} variables. The policy says that traffic for each 
-global prefix associated with the template variable \$PG should end up at its corresponding 
-destination router contained in the abstract TG role. The second line does something similar 
-for all local prefixes. Finally, the last line remains the same as before.
-
-Next we can modify the Locality constraint for the abstraction in a straightforward way:
+This defines a group of constraints for the basic routing behavior. 
+%
+The first line introduces a prefix \emph{template} variable. It says that traffic for each 
+global prefix associated with the template variable \$PG has the constraint that it should follow 
+a path that ends at its corresponding destination router contained in the abstract TG role. 
+The second line does the same thing for all local prefixes. 
+The final rule matches all other
+IP prefix destinations and allows traffic to follow a path that leaves the datacenter through either
+of its peers (Peer1 or Peer2) with a preference for leaving through Peer1. The \Prefer~ symbol indicates
+that traffic should satisfy the constraint on the left whenever possible, and only resort to the backup (right)
+when this is not possible due to failures.%
+
+Next we can capture the constraint that traffic for local prefixes must stay local to the datacenter.
+We do this with the following \sysname code:
 %
@@
 \noindent%
-
-Finally, we can add the "valleyfree" constraint. We are able to encode this constraint for the
-abstract topology because we have retained enough structure to understand what a valley is. 
+%
+The Locality constraint applies to any traffic destined for a local prefix and adds
+the constraint that the traffic must follow a path that matches an internal location 
+(\IE, a router inside the datacenter) at each hop of the path. This prevents traffic 
+from ever entering from or leaving through an external peer. Finally, we can combine 
+these constraints together as follows:
+
+%
+%Finally, we can add the "valleyfree" constraint. We are able to encode this constraint for the
+%abstract topology because we have retained enough structure to understand what a valley is. 
+%
+%\begin{code}
+%\Define Tor = \{TL,TG\}
+%\Define Agg = \{AL,AG\}
+%\Define Spn = \{S\}
+%\Define ValleyFree =
+%    \{\True \Path \Novalley(Tor,Agg,Spn)\}
+%\end{code}
+%\noindent%
+%
+%The constraint prevents traffic from over taking a path that traverses 
+%either [Agg->Tor->Agg] or [Spn->Agg->Spn]. The final policy remains the same as before,
+%by combining each of these policies together.
+%
 %
 \begin{code}
-\Define Tor = \{TL,TG\}
-\Define Agg = \{AL,AG\}
-\Define Spn = \{S\}
-\Define ValleyFree =
-    \{\True \Path \Novalley(Tor,Agg,Spn)\}
+\Define Main = Routing & Locality & \Agg(PG, \In -> \Out)
 \end{code}
@@
 
-The constraint prevents traffic from over taking a path that traverses 
-either [Agg->Tor->Agg] or [Spn->Agg->Spn]. The final policy remains the same as before,
-by combining each of these policies together.
-%
-\begin{code}
-\Define Main = 
-    Routing & 
-    Locality & 
-    ValleyFree & 
-    \Agg(PG, \In -> \Out)
-\end{code}
-\noindent%
+This defines the main policy as the conjunction of the Routing and Locality constraints. It 
+also declares an additional constraint that we want to perform aggregation for global prefixes
+by summarizing them into the more general prefix PG at the border of the datacenter
+(\IE along any edge starting inside our datacenter and ending outside).
 
@@
 and for any combination of failures that may occur in the concrete network.
-Furthermore, if we want to expand our network for example by adding additional spine 
-routers, \sysname will guarantee that the expansion will be incremental (\IE, only
+Furthermore, \sysname will generate configurations in such a way that,
+if we want to expand our network (\EG, by adding additional spine routers as in 
+figure~\ref{fig:example2}), the expansion will be incremental (\IE, only
 configurations for routers local to the expansion will need to change).
+
+\subsection{Abstract Analysis}
+
+Although \sysname can ensure correct forwarding behavior independent of the 
+exact concrete topology or failure scenario, it is often useful to be able 
+to ask "what if" questions. To this end, we develop sound analyses over the
+abstract topology to answer questions about worst-case connectivity.
 

### 2016-11-01 paper/abstraction/paper.tex
pass on 2

@@
   \centering
-  \includegraphics[width=\columnwidth]{figures/example}
+  \includegraphics[width=2.5in]{figures/example}
   \caption{An example data center network.}
@@
   \centering
-  \includegraphics[width=\columnwidth]{figures/example2}
+  \includegraphics[width=2.5in]{figures/example2}
   \caption{A modified version of the example in Figure~\ref{fig:example}.}
@@
 Our network, shown in Figure~\ref{fig:example}, is a standard folded-Clos topology with four pods.
-It has eight top-of-rack (ToR) switches, T[1--8]; eight aggregation switches, A[1--8]; and two spine switches, S[1--2].
-Groups of addresses, P[1--8], are for services hosted in each rack.
-Such groups are called address {\em prefixes} because they are compactly encoded using the common prefix that addresses share.
-
-The figure also shows the intended policy.
+T[1--8] denote top-of-rack (ToR) switches, A[1--8] denote aggregation switches, and S[1--2] denote spine switches.
+P[1--8] denote groups of addresses for services hosted in each rack.
+Such groups are called address {\em prefixes} because they are encoded using the adresses' shared prefix.
+Assume that all nodes are running the border gateway protocol (BGP), as is common in large data centers~\cite{x}.
+\todo{more detail on BGP?}
+
+The intended policy for this network is as follows.
 Internal connectivity should be complete, i.e., all nodes must be able to talk to each other.
-Pods 1 and 2 host services that are meant to be globally accessible and thus their addresses should be announced externally, but only after the individual prefixes P[1--4] are aggregated into a single prefix PG.
-Finally, pods 3 and 4 host services that are not meant to be externally visible and thus their address should not be announced externally.
+Services in Pods 1 and 2 should be globally accessible and thus their addresses should be announced externally, but only after aggregating individual prefixes P[1--4] into a single prefix PG.
+Finally, services in Pods 3 and 4 should be not be externally visible and thus their address should not be announced externally.
 
 To correctly configure the policy above, the network engineer's task is to generate low-level configuration commands for each switch in the network.
-This implies making sure, for instance, that all switch interfaces are assigned correct addresses; all routing adjacencies are correctly configured (e.g., T1's configuration includes A1 as neighbor and vice-versa); all switches announce their own addresses (so that they can be reached for management purposes) and the ToRs announce the correct prefixes for their services; all switches  forward the prefix announcements that they should to each neighbor and not forward those that they should not (e.g., the spines should forward prefixes for local services to internal neighbors but not external neighbors); and the spines announce externally only the aggregate global prefix.
-As many have observed before, such configuration tasks are highly challenging and, consequently, configuration errors are the leading contributor to network outages~\cite{x,y,z,batfish,propane}.
-
-\subsection{Challenges with today's template systems}
-
-To reduce errors, the network engineering community is moving toward a template-based approach.
-Here, instead of authoring one configuration file per router, they author one configuration template per {\em role}, where each role is played by one or more routers.\footnote{If a role is played by devices from different vendors, there is one template per role-vendor combination because templates use vendor configuration language.} For instance, the network in Figure~\ref{fig:example} has five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
-Role templates have parameters for various aspects of the configuration (e.g., interface addresses, list of neighbors), and they are compiled to device configurations by instantiating the parameters using a database that stores parameter values for each device.
-
-Templates provide two key advantages.
+This implies ensuring, for instance, that all switch interfaces are assigned correct addresses; all routing adjacencies are correctly configured (e.g., T1's configuration includes A1 as neighbor and vice-versa); all switches announce their own addresses (so that they can be reached for management purposes) and the ToRs announce the correct prefixes for their services; all switches  forward the prefix announcements that they should to each neighbor and not forward those that they should not (e.g., the spines should forward prefixes for local services to internal neighbors but not external neighbors); and the spines announce externally only the aggregate global prefix.
+
+As many have observed before, such configuration tasks are highly challenging. Consequently, configuration errors are the leading cause of network outages~\cite{x,y,z,batfish,propane}.
+
+\subsection{Limitations of concrete synthesis}
+
+In response, researchers have developed systems that synthesize low-level device configurations from high-level policy statements~\cite{x,y,propane}.
+%They take network topology and policy as input and output device configurations that are  guaranteed to be correct under all possible failures.
+Thus, they save the engineers from performing the complex task of breaking down global policies into device configurations.
+These systems offer appealing guarantees that the generated configurations correctly implement policy, even under arbitrary combinations of failures.
+
+However, our conversations with network engineers reveal that they have two limitations that discourage adoption.
+The first is a mismatch in abstraction.
+Engineers of large networks tend to think of the network, and develop tools, in terms of roles and not individual devices.
+A {\em role} refers to specific functionality and is played by one or more routers.
+The network in Figure~\ref{fig:example} has five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
+Engineers are reluctant to use a system that does not understand roles as a first-order abstraction.
+A superficial use of tags to group similar devices is not enough.
+For instance, there is no guarantee in concrete synthesis systems that the configurations of two devices with the same role will be similar.
+If the engineers wanted to debug, or simply understand, their output, they'll have to consider all device configurations instead of role configurations;  there can be orders of magnitude more devices than roles in the network.
+
+A second limitation is inability to support network evolution.
+Networks evolve all the time as nodes and links are added or removed and the addresses of services are changed.
+A system that supports evolution should ensure that correctly supporting such changes requires only small changes to network configurations.
+Engineers want to minimize changes to device configurations because each change runs the risk of poor, dynamic behavior during the change.
+
+Concrete synthesis tools do not accommodate evolution well.
+When engineers want to modify the network, they would use the new topology as input to the system.
+(Old inputs or configurations are not supplied.) In the resulting output, existing device configurations may undergo unnecessary changes, beyond those needed to accommodate the modification.
+Suppose we want to modify the prefix of local ToR T8 in  Figure~\ref{fig:example}.
+To accommodate the modification, Propane, a concrete synthesis tool, will not only change T8's configuration but also those of the two spines because it uses prefix lists at spines to ensure that local prefixes are not advertised externally.
+As we show later, there is a way to design the configurations of this network in a way that does not require spine configuration changes to accommodate ToR prefix modifications, by exposing the inherent structure in this topology to the synthesis tool.
+
+%nof the new spine configurations outputted by Propane will not only enable the interfaces that connect to the new aggregators but will also have to update the prefix list filters.
+A system that supports incremental growth should need only interface configuration changes (not filter changes).
+It can configure all local ToRs, including the new ones, to attach a tag to their announcements and filter external announcements at the spines based on this tag.
+Engineers prefer fewer configuration changes because each change runs the risks of poor transient behavior (which synthesis tools do not reason about).
+
+%For instance, suppose the engineers want to add another pod with local services to the network in Figure~\ref{fig:example}.
+In this network, Propane, a concrete synthesis tool, uses prefix lists at spines to ensure that local prefixes are not advertised externally.
+To accommodate the expansion, the new spine configurations outputted by Propane will not only enable the interfaces that connect to the new aggregators but will also have to update the prefix list filters.
+A system that supports incremental growth should need only interface configuration changes (not filter changes).
+It can configure all local ToRs, including the new ones, to attach a tag to their announcements and filter external announcements at the spines based on this tag.
+Engineers prefer fewer configuration changes because each change runs the risks of poor transient behavior (which synthesis tools do not reason about).
+
+\subsection{Limitations of today's template systems}
+
+To simplify network configuration, and thus reduce errors, the network engineering community is adopting a template-based approach~\cite{x,y}.
+Instead of authoring one configuration file per router, engineers author one configuration template per role.\footnote{If a role is played by devices from different vendors, there is one template per role-vendor combination because templates use vendor configuration language.} Templates have parameters for various aspects of the configuration (e.g., interface addresses, neighbor list) and are compiled to device configurations by instantiating the parameters using a database of per-device values.
+
+%Templates provide two key advantages.
 First, they help eliminate a class of configuration errors that stem from typos and inconsistencies, e.g., using the wrong address for a switch, having inconsistent addresses for the two ends of a link, and failing to configure one side of a routing adjacency.
@@
 
-%Second, the engineers need to author and reason about fewer independent ``files"---18 versus 5 in our example but the ratio can be multiple orders of magnitude for large networks.
-
-Today's template systems however, are far from perfect. While they reduce a class of errors, they do not help with deeper, logical bugs.
-%, e.g., incorrect strategy for determining how announcements to a neighbor are forwarded
-%, not realizing when or where aggregation should be used,
-%and not understanding the interaction between configuration commands.
-To author correct templates, engineers must still do themselves the conceptually challenging task of breaking down complex, global policies into role templates such that the collective behavior of the templates (upon compilation to configurations) correctly implements the policy under all failure conditions.
-
-As a result, the types of configuration design errors in our example network pointed in prior work~\cite{propane} can occur in template design as well.
+While templates operate at the right level of abstraction, today's template systems have two limitations.
+The first is that they offer no guarantees on correctness.
+To author correct templates, engineers must do manually the conceptually challenging task of breaking down complex, global policies into role templates such that the collective behavior of the templates (upon compilation to configurations) correctly implements the policy under all failure conditions.
+
+As a result, the types of configuration design errors pointed in prior work~\cite{propane} can occur in template design as well.
 For instance, to keep local prefixes internal the engineer may implement announcement forwarding on spines based on the identity of the neighbor, i.e., do not announce externally anything heard from local aggregators.
-This implementation works correctly when there are no failures but local prefixes can leak to the outside world when failures disconnect a spine from both aggregators in a local pod.
+This implementation is appealing because it does not require changes to spine configurations when ToR prefixes change.
+But it works correctly only when there are no failures; local prefixes can leak externally when failures disconnect a spine from both aggregators in a local pod.
 Specifically, when S1 is disconnected from A5 and A6, it may hear about P5 and P6 from A3 and A4 (via A[5--6]->S2->A[3--4]), and it will then announce those prefixes outside (since they no not come from a local aggregator), leading to a policy violation.
-A correct implementation here would be for each spine to not advertise externally announcements from local aggregators {\em and} reject announcements that have traversed the other spine (i.e., disallow "valleys," or up-down-up paths).
-
-Lacking correctness guarantees, engineers use simulations to analyze if templates are correct under a range of failure cases (e.g., combinations of two-link failures), but such analysis is highly expensive for large networks and still does not provide strong guarantees beyond the tested cases.
+
+%A correct implementation here would be for each spine to not advertise externally announcements from local aggregators {\em and} reject announcements that have traversed the other spine (i.e., disallow "valleys," or up-down-up paths).
+
+%Lacking correctness guarantees, engineers use simulations to analyze if templates are correct under a range of failure cases (e.g., combinations of two-link failures), but such analysis is highly expensive for large networks and still does not provide strong guarantees beyond the tested cases.
+
+The second limitation of today's template systems is that, like concrete synthesis tools, they do not support network evolution.
+In theory, templates are appealing because operators do not have to redesign templates when the topology changes while keeping its structure of roles and their inter-connectivity.
+In practice, however, there is no way to \todo{ ...
+continue here ...}
 
@@
 As an aside, a possible template implementation that works correctly for both networks is: allow valley paths and use an explicit list of local prefixes at spines to decide which announcements should not be forwarded externally.
-
-\subsection{Challenges with concrete synthesis}
-
-As an alternative approach to reduce configuration errors, the research community has developed many systems that take network topology and policy as input and output device configurations that are  guaranteed to be correct under all possible failures.
-Thus, they save the engineers from performing the complex task of breaking down global policies into device configurations.
-
-However, they have two shortcomings, both stemming from operating over concrete topologies.
-The first is a mismatch in abstraction.
-Engineers that run large networks tend to think of them, and develop tools for them, in terms of roles and not individual devices.
-We have thus found that they are reluctant to use a system that does not understand roles as a first-order abstraction.
-There is no guarantee in these systems that the configurations of two devices that serve the same role will be "similar."  If the engineers wanted to sanity-check or (familiarize themselves with) their output, they'll have to consider all device configurations;  there can be orders of magnitude more devices than roles in the network.
-
-A second shortcoming is lack of support for incremental growth.
-When engineers want to expand a network, they would have to input the new, planned topology to the system.
-The new configurations for existing devices may undergo unnecessary changes, beyond those needed to accommodate the expansion.
-For instance, suppose the engineers want to add another pod with local services to the network in Figure~\ref{fig:example}, and (like current aggregators) the aggregators in the new pod will connect to both spines.
-In this network, Propane, a concrete synthesis tool, uses prefix lists at spines to ensure that local prefixes are not advertised externally.
-To accommodate the expansion, the new spine configurations outputted by Propane will not only enable the interfaces that connect to the new aggregators but will also have to update the prefix list filters.
-A system that supports incremental growth should need only interface configuration changes (not filter changes).
-It can configure all local ToRs, including the new ones, to attach a tag to their announcements and filter external announcements at the spines based on this tag.
-Engineers prefer fewer configuration changes because each change runs the risks of poor transient behavior (which synthesis tools do not reason about).
 

### 2016-11-01 paper/abstraction/paper.tex
another pass on 2

@@
 Networks evolve all the time as nodes and links are added or removed and the addresses of services are changed.
-A system that supports evolution should ensure that correctly supporting such changes requires only small changes to network configurations.
-Engineers want to minimize changes to device configurations because each change runs the risk of poor, dynamic behavior during the change.
+A system that supports evolution would ensure that supporting such evolution requires only small changes to network configurations.
+Engineers want to minimize changes to device configurations because each change runs the risk of poor, transient behavior due to poor router software or routing protocol dynamics~\cite{ratulbgpmisconfigs}.
 
 Concrete synthesis tools do not accommodate evolution well.
-When engineers want to modify the network, they would use the new topology as input to the system.
-(Old inputs or configurations are not supplied.) In the resulting output, existing device configurations may undergo unnecessary changes, beyond those needed to accommodate the modification.
+When engineers want to modify the network, they would use the new topology as input to the system; old inputs or configurations are not uses.
+In the resulting output, existing device configurations may undergo unnecessary changes, beyond those needed to accommodate the modification.
 Suppose we want to modify the prefix of local ToR T8 in  Figure~\ref{fig:example}.
 To accommodate the modification, Propane, a concrete synthesis tool, will not only change T8's configuration but also those of the two spines because it uses prefix lists at spines to ensure that local prefixes are not advertised externally.
-As we show later, there is a way to design the configurations of this network in a way that does not require spine configuration changes to accommodate ToR prefix modifications, by exposing the inherent structure in this topology to the synthesis tool.
+As we show later, there is a way to design the configurations of this network in a way that does not require spine configuration changes to accommodate ToR prefix (and other) modifications, by exposing the inherent structure in this topology to the synthesis tool.
 
@@
 The first is that they offer no guarantees on correctness.
-To author correct templates, engineers must do manually the conceptually challenging task of breaking down complex, global policies into role templates such that the collective behavior of the templates (upon compilation to configurations) correctly implements the policy under all failure conditions.
+To author correct templates, engineers must do manually the conceptually challenging task of breaking down complex, global policies into role templates such that the collective behavior of configurations derived from the templates correctly implements the policy under all failure conditions.
 
@@
 Specifically, when S1 is disconnected from A5 and A6, it may hear about P5 and P6 from A3 and A4 (via A[5--6]->S2->A[3--4]), and it will then announce those prefixes outside (since they no not come from a local aggregator), leading to a policy violation.
-
-%A correct implementation here would be for each spine to not advertise externally announcements from local aggregators {\em and} reject announcements that have traversed the other spine (i.e., disallow "valleys," or up-down-up paths).
+A possible correct implementation here would be for each spine to not advertise externally announcements from local aggregators {\em and} reject announcements that have traversed the other spine (i.e., disallow "valleys," or up-down-up paths).
 
@@
 The second limitation of today's template systems is that, like concrete synthesis tools, they do not support network evolution.
-In theory, templates are appealing because operators do not have to redesign templates when the topology changes while keeping its structure of roles and their inter-connectivity.
-In practice, however, there is no way to \todo{ ...
-continue here ...}
-
-More importantly, because the analysis is done over a concrete topology, it provides no insight as to when the templates can be safely re-used.
-Templates that work for a given concrete topology may not work for seemingly-minor variations of the topology.
-Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}; it has the same folded-Clos structure and the same five roles.
-One might think that the same templates (but different database entries) can be used for both topologies.
-However, templates that disallow valley paths lead to a less fault-tolerant system for Figure~\ref{fig:example2}.
-
-In particular, aggregation-induced blackholes can occur in Figure~\ref{fig:example2} with only one link failure, while it would take two failures in Figure~\ref{fig:example}.
+In theory, being role-based, templates do not have to be redesigned when the network evolves while keeping its basic structure of roles and their inter-connectivity.
+In practice, however, it is not guaranteed that templates that work for a given topology also work for seemingly-minor variations of the topology.
+
+Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}, with the same folded-Clos structure and five roles.
+One might think that the same templates (with different database entries) can be re-used across topologies.
+However, that is not necessarily true.
+For instance, templates that disallow valley paths lead to a less fault-tolerant system for Figure~\ref{fig:example2}.
+In particular, aggregation-induced blackholes~\cite{x} can occur in Figure~\ref{fig:example2} with only one link failure, while it would take two failures in Figure~\ref{fig:example}.
 Such blackholes occur when a switch announces an aggregate prefix but has no valid path to a more specific prefix within the aggregate.
@@
 
-Thus, engineers today must reason about the correctness of templates for each concrete topology and each evolution.
+Thus, engineers today must reason about the correctness of templates for each evolution (using expensive simulations because current systems do not provide any correctness guarantee by design).
 Worse, for some evolutions, they may discover that their old templates will not work anymore and need modifications.
-This discovery is highly onerous because changing the templates implies that the configuration of all the devices needs to change, which can be an unacceptable disruption.
-When that happens, many networks abandon templates entirely and revert to modifying individual configuration files, using localized patches to accomodate evolution.
-This reversion brings backs the class of errors that the templates were designed to prevent.
-
-As an aside, a possible template implementation that works correctly for both networks is: allow valley paths and use an explicit list of local prefixes at spines to decide which announcements should not be forwarded externally.
+This discovery is highly problematic because changing the templates implies that the configuration of all the devices needs to change, which can be an unacceptable disruption.
+When that happens, many networks abandon templates entirely and revert to hand-crafting configuration files, using localized patches to accommodate evolution.
+This reversion brings backs the complexity and errors that the templates were meant to prevent.
+
+%As an aside, a possible template implementation that works correctly for both networks is: allow valley paths and use an explicit list of local prefixes at spines to decide which announcements should not be forwarded externally.
+
+\begin{figure}
+\begin{tabular}{p{0.7in}|p{0.7in}p{0.7in}p{0.7in}}
+& Abstraction level & Correctness guarantees & Support evolution  \\ \hline
+Concrete synthesis & \xmark & \cmark & \xmark \\ \hline
+Template systems & \cmark & \xmark & \xmark \\ \hline
+\sysname & \cmark & \cmark & \cmark \\ 
+\end{tabular}
+\caption{Properties of different methods for generating device configurations.}
+\end{figure}
 
@@
 
-\sysname addresses the challenges above with both template systems and concrete synthesis tools.
-It takes as input network policy and an {\em abstract} topology  that captures the different device roles and connectivity.
-It outputs a template for each role.
-Engineers can then use \sysname's template compiler or their own to convert templates into configurations based on the concrete topology and parameter values.
-
-\sysname guarantees that the templates are correct, that is, when compiled to device configurations, the network will correctly implement the specified policy.
-These guarantees hold for any valid concrete topology that matches the specified abstract topology; and when a valid concrete topology evolves to another valid concrete topology, only necessary changes are needed to device configurations.
+As Table~\ref{fig:marketing} shows, \sysname addresses the limitations with both concrete synthesis and current template systems.
+It operates at the right level of abstraction, guarantees the correctness of configurations, and supports network evolution.
+It takes as input network policy and an {\em abstract} topology  that describes device roles and connectivity.
+It outputs a template for each role, which can be compiled to configurations based on the concrete topology and parameter values.
+\sysname guarantees that its templates are correct, i.e., the configurations generated from them correctly implement the specified policy for {\em any} concrete topology that matches the abstract topology; and when a valid concrete topology evolves to another valid concrete topology, only necessary changes are needed to device configurations.
+
+The next section introduces \sysname using the example in Figure~\ref{fig:example}, and the following sections provide more detail on how we generate the templates and formally define the correctness guarantees.
 

### 2016-11-01 paper/abstraction/paper.tex
stashing changes
add section 3.3

@@
 \renewcommand{\path}[2]{ #1 \mapsto \ensuremath{#2} }
+
+%% grammar
+\newcommand{\BNFALT}{\;\;|\;\;}
+\newcommand{\hdr}[2]{\flushleft \chdr{\hspace{5mm}#1}{#2}}
+\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}%
 
@@
 
-\subsection{Abstract Methane}
+\subsection{Abstract Synthesis}
 
@@
 
+\para{Topology Abstraction}
+
 Consider again the datacenter from earlier. Ideally, we would like
@@
 
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=\columnwidth]{figures/example3}
+  \caption{Role-based abstraction for the datacenters in Figure~\ref{fig:example}.}
+  \label{fig:example3}
+  \vspace{-1em}
+\end{figure}
+
 In order to refine the abstraction to capture more precisely the kinds of concrete networks of interest,
@@
 with a symbolic variable (\EG, $e1, e2, \ldots$) that denotes a constraint on the number of nodes/edges
-that may appear in any given concrete network. Operators can then add constraints to relate symbolic
-variables taken from any valid SMT theory. For example, in Figure~\ref{fig:example3}, the variable $e1$
-represents the number of outgoing edges from any concrete node mapped to the TG role to other concrete
-nodes mapped to the AG role. Similarly, we introduce a node multiplicity variable for each role. For example,
-the multiplicity variable $AG$ represents the number of concrete nodes that map the the AG role. We can then
-add constraints over these symbolic variables to capture invariants in the concrete networks. For example,
-if we only want to consider networks where TG and AG routers form a full mesh in each pod we would add the
-following constraints: $e1 = AG$, $e2 = TG$. \ryan{how to add the constraints to the image? in latex or powerpoint?}
+that may appear in any given concrete network. Operators can then capture concrete network invariants by adding constraints on the symbolic variables using logical formula.
+
+For example, in Figure~\ref{fig:example3}, the first two constraints: $e1 = AG$ and $e2 = TG$ declare that, within any pod P, the number of outgoing edges from $TG$ to $AG$ is equal to the number of nodes that map to $AG$.
+Similarly, the number of outgoing edges from $AG$ to $TG$ is equal to the number of nodes that map toe $TG$.
+These constraints capture the fact that, within any given pod, the global aggregators and tors are in a full mesh.
+Furthermore, the constraints $TG = AG$ and $TG \geq 2$ ensure that the number of concrete nodes in role $TG$ is always equal to the number of concrete nodes in role $AG$.
+Similar constraints also appear for the local aggregators and tors.
+%
+The constraint $e3 \geq 2$ says that, in each pod, each aggregator node has at least 2 outgoing edges to nodes in the spine role.
+Symmetrically, the constraint $e4 \geq 1$ says that, for each pod P, each node in the spine role has at least one outgoing edge to a node in the $AG$ role.
+Again, similar constraints appear for the local aggregator role.
+Finally, the constraints $S \geq 2$, $S \pmod AG = 0$, and $S \pmod AL = 0$ ensure that there are at least 2 routers in the spine role, and that the number of spine routers is always divisible by the number of global and local aggregators.
+%
+The last two constraints are interesting in that they do not involve a simple inequality. In general operators can write constraints using logical formula over any SMT theory.
+
+All the guarantees provided by \sysname hold for any instantiation of the abstract network.
+This means that operators can safely expand their network in the future so long as the new network also satisfies these logical constraints.
 
@@
 
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=.7\columnwidth]{figures/example3}
-  \caption{Role-based abstraction for the datacenters in Figure~\ref{fig:example}.}
-  \label{fig:example3}
-  \vspace{-1em}
-\end{figure}
-
-Now let us configure the datacenter networks by writing a routing policy over the
-abstract topology. The first part of the policy will be:
+\para{Routing Policy}
+
+Now let us configure each of the datacenter networks from \S\ref{sec:motivation} by writing a routing policy over the abstract topology.
+In \sysname, we can capture the basic routing behavior with the following constraints:
 %
@@
 \Define Routing =
-    \{\$PG \Path \End(TG)
+    \$PG  \Path \End(TG)
     \$PL  \Path \End(TL)
-     \True \Path \Exit(Peer1 \Prefer Peer2)\}
+    \True \Path \Exit(Peer1 \Prefer Peer2)
 \end{code}
@@
 
-This defines a group of constraints for the basic routing behavior.
-%
-The first line introduces a prefix \emph{template} variable. It says that traffic for each
-global prefix associated with the template variable \$PG has the constraint that it should follow
-a path that ends at its corresponding destination router contained in the abstract TG role.
+The first line introduces a prefix \emph{template} variable.
+It says that traffic for each global prefix associated with the template variable \$PG has the constraint that it should follow a path that ends at its corresponding destination router contained in the abstract TG role.
 The second line does the same thing for all local prefixes.
-The final rule matches all other
-IP prefix destinations and allows traffic to follow a path that leaves the datacenter through either
-of its peers (Peer1 or Peer2) with a preference for leaving through Peer1. The \Prefer~ symbol indicates
-that traffic should satisfy the constraint on the left whenever possible, and only resort to the backup (right)
-when this is not possible due to failures.%
+%
+The final rule matches all other IP prefix destinations and allows traffic to follow a path that leaves the datacenter through either of its peers (Peer1 or Peer2) with a preference for leaving through Peer1.
+The \Prefer~ symbol indicates that traffic should satisfy the constraint on the left whenever possible, and only resort to the backup (right) when this is not possible due to failures.%
 
@@
 \begin{code}
-\Define Locality = \{\$PL \Path \Always(\In)\}
+\Define Locality = 
+    \$PL \Path \Always(\In)
 \end{code}
@@
 %
-The Locality constraint applies to any traffic destined for a local prefix and adds
-the constraint that the traffic must follow a path that matches an internal location
-(\IE, a router inside the datacenter) at each hop of the path. This prevents traffic
-from ever entering from or leaving through an external peer. Finally, we can combine
-these constraints together as follows:
-
-%
-%Finally, we can add the "valleyfree" constraint. We are able to encode this constraint for the
-%abstract topology because we have retained enough structure to understand what a valley is.
-%
-%\begin{code}
-%\Define Tor = \{TL,TG\}
-%\Define Agg = \{AL,AG\}
-%\Define Spn = \{S\}
-%\Define ValleyFree =
-%    \{\True \Path \Novalley(Tor,Agg,Spn)\}
-%\end{code}
-%\noindent%
+The Locality constraint applies to any traffic destined for a local prefix described by the \$PL prefix template variable and adds the constraint that the traffic must follow a path that matches an internal location (\IE, a router inside the datacenter) at each hop of the path.
+This prevents traffic from ever entering from or leaving through an external peer.
+Finally, we can combine these constraints together as follows:
+
+\begin{code}
+Routing & Locality & \Agg(PG, \In -> \Out)
+\end{code}
+\noindent%
+
+This tells \sysname to find BGP router configurations that satisfy the conjunction of the Routing and Locality constraints.
+It also declares an additional constraint that we want to perform aggregation for global prefixes by summarizing them as the more general prefix PG at the border of the datacenter (\IE along any edge starting inside our datacenter and ending at a peer outside the datacenter).
+
+When \sysname compiles the above policy, it guarantees that the forwarding behavior of the network will be correct for any concrete instantiation of the abstract network, and for any combination of failures that may occur in the concrete network.
+Furthermore, \sysname will generate configurations in such a way that, if we want to expand our network, for example by adding additional spine routers as in figure~\ref{fig:example2}, then the expansion can be performed incrementally (\IE, only configurations for routers local to the expansion will need to change).
+
+\subsection{Abstract Analysis}
+
+Although \sysname can ensure correct forwarding behavior independent of the exact concrete topology or failure scenario, it is often useful to be able to ask "what if" questions about other network properties.
+For example, an operator may require a certain level fault tolerance between between different collections of routers.
+Importantly, such analysis depends, not only on the network topology, but also on the underlying routing policy.
+To this end, we develop a sound analysis over abstract topologies to answer questions about the number of disjoint paths between pairs of nodes.
+
+Suppose we want to find a worst-case lower bound on the number of disjoint paths between any global tor and spine router from figure~\ref{fig:example3} after applying the routing policy.
+This would give us a bound on the fault tolerance for, not only the current datacenter, but any sound expansion of it.
+Furthermore, this can be used as a lightweight verification tool to detect certain classes of configuration bugs.
+For example, since we are performing aggregation at the border of the datacenter, we might introduce what is known as an aggregation black hole if enough failures occur to disconnect a tor from a spine.
+
+The disjoint path analysis works in the following way.
+For each abstract role in the network, we learn invariants about the number of disjoint paths to routers in that role.
+These invariants contain a sequence of labels followed by a pair of numbers $(i,j)$.
+For example, the analysis would start with a fact of the form: $S_P S_{TG} (1,1)$.
+This means that, there is some group of nodes of size 1 in the TG role in some pod P such that each node has 1 disjoint path to it (and all such paths are edge-disjoint).
+Since we know that the each node in the TG role is in a full mesh with nodes in the AG role within any given pod, we might infer a fact for AG of the form: $S_P A_{AG}(e1,1)$.
+This says that any group of nodes of size e1 in the AG role is reachable with at least 1 edge-disjoint path to each such node.
+%
+If we run the abstract analysis over the abstract network from figure~\ref{fig:example3} the analysis will learn a fact of the form $A_{S}(1,2)$, which means that any single spine node is reachable via 2 disjoint paths from any global tor node \ryan{it will actually be 1, we need to add a constraint on e1}.
+
+Suppose now that we want to disallow paths with valleys (\IE, paths that go down and then up at some point). Such a constraint can be added to the routing policy simply:
+\begin{code}
+\Define ValleyFree =
+    \True \Path \Novalley(\{TL,TG\},\{AL,AG\},\{S\})
+\end{code}
+\noindent%
+
+This adds a constraint that applies to all traffic and prevents valleys by defining each level in the datacenter.
+Because the abstract analysis is policy sensitive, if we were to run the it with the same abstract topology but the new routing policy, it would only be able to infer that there is a single disjoint path to any given spine router in the worst case.
+In fact this is exactly the case for the concrete network from figure~\ref{fig:example2}.
+
 %
@@
 %
-\begin{code}
-\Define Main = Routing & Locality & \Agg(PG, \In -> \Out)
-\end{code}
-\noindent%
-
-This defines the main policy as the conjunction of the Routing and Locality constraints. It
-also declares an additional constraint that we want to perform aggregation for global prefixes
-by summarizing them into the more general prefix PG at the border of the datacenter
-(\IE along any edge starting inside our datacenter and ending outside).
-
-When \sysname compiles the above policy, it guarantees that the forwarding behavior
-of the network will be correct for any concrete instantiation of the abstract network,
-and for any combination of failures that may occur in the concrete network.
-Furthermore, \sysname will generate configurations in such a way that,
-if we want to expand our network (\EG, by adding additional spine routers as in
-figure~\ref{fig:example2}), the expansion will be incremental (\IE, only
-configurations for routers local to the expansion will need to change).
-
-\subsection{Abstract Analysis}
-
-Although \sysname can ensure correct forwarding behavior independent of the
-exact concrete topology or failure scenario, it is often useful to be able
-to ask "what if" questions. To this end, we develop sound analyses over the
-abstract topology to answer questions about worst-case connectivity.
 
 \subsection{Language}
-
-\ryan{TODO: introduce language + semantics}
-
-%% grammar
-\newcommand{\BNFALT}{\;\;|\;\;}
-\newcommand{\hdr}[2]{\flushleft \chdr{\hspace{5mm}#1}{#2}}
-\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}%
-
-\begin{figure*}[t]\small
-  \begin{minipage}[t]{.45\linewidth}
-  \hdr{Syntax}{}
-  \vspace*{-1\baselineskip}
-  %
-  \[ \begin{array}{rclr}
-    \hline%
-
-     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
-     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
-     x       &::=& d.d.d.d/d & \textit{prefix} \\
-     t       &::=& \True & \textit{true} \\
-         &\BNFALT& \neg t & \textit{negation} \\
-         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
-         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
-         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
-     r       &::=& l & \textit{location} \\
-         &\BNFALT& \emptyset & \textit{empty set} \\
-         &\BNFALT& \In & \textit{internal loc} \\
-         &\BNFALT& \Out & \textit{external loc} \\
-         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
-         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
-         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
-         &\BNFALT& \NOT r & \textit{path negation} \\
-         &\BNFALT& r^* & \textit{iteration} \\
-     cc     &::=& agg(x, r_1 \rightarrow r_2)  & \textit{control constraints} \\
-  \end{array} \]%
-
-  \end{minipage}
-  %
-  ~~
-  \vrule
-  ~~
-  %
-  \begin{minipage}[t]{.5\linewidth}\small
-  \hdr{Propane Expansions}{}
-  \vspace*{-1\baselineskip}
-  %
-  \[\begin{array}{rcl}
-    \hline
-    \Any               & = & \Sigma^* \\
-    \None              & = & \emptyset \\
-    \Internal          & = & \In^+ \\
-    \Always(X)         & = & X^* \\
-    \Never(X)          & = & (!X)^* \\
-    \Through(X)        & = & \Sigma^* \cdot X \cdot \Sigma^* \\
-    \Eventually(X)     & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
-    \Already(X)        & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
-    \End(X)            & = & \Sigma^* \cdot X \\
-    \Start(X)          & = & X \cdot \Sigma^* \\
-    \Enter(X)          & = & \Sigma^* \cdot \Out \cdot (X \cap \In) \cdot \Sigma^* ~ \cup \\
-                       &   & \Sigma^* \cdot (X \cap \Out) \cdot \In \cdot \Sigma^* \\
-    \Exit(X)           & = & \Sigma^* \cdot \In \cdot (X \cap \Out) \cdot \Sigma^* ~ \cup \\
-                       &   & \Sigma^* \cdot (X \cap \In) \cdot \Out \cdot \Sigma^* \\
-    \LinkKW(X,Y)       & = & \Sigma^* \cdot X \cdot Y \cdot \Sigma^* \\
-    \PathKW(\vec{X})   & = & \Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^* \\
-    \Novalley(\vec{X}) & = & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
-                       &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
-  \end{array} \]%
-
-  \end{minipage}%
-
-  \hrulefill%
-
-  \caption{Regular Intermediate Representation (RIR) syntax (left), and
-           Propane language expansions (right).}
-  \label{fig:rir-syntax}
-  %\vspace{-1em}
-\end{figure*}%
 
@@
 %
-%  **Appendix**
-%
-%
-%=====================================================
-
-%\subsection{Propane Properties}
-%
-%\newtheorem{prop}{Proposition}[section]
-%
-%Here we investigate the correctness and expressiveness properties of \sysname.
-We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures?
-(2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?
-%
-%If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario.
-We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges.
-We argue that \sysname is correct by breaking down the claim:
-%
-%\begin{prop}
-%BGP configurations for internal routers produced by \sysname will be stable.
-%\end{prop}
-%
-%\begin{prop}
-%BGP configurations produced by \sysname are \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.
-%\end{prop}
-%
-%The Soundness claim follows directly from compilation of the product graph.
-Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations are Sound.
-%
-%\begin{prop}
-%BGP configurations produced by \sysname are \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
-%\end{prop}
-%
-%The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.
-This means there is a valid path in the product graph corresponding to this path, and which is available in the network.
-%Assume we are unable to achieve this route in the network.
-To not achieve this path means that some router along the advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead.
-This implies that router that makes the ``wrong'' choice appears as a separate node in the product graph.
-However, from our failure safety check, we know that the other, more-preferred node must have a superset of the paths to accepting states as the less preferred node (from which it stole the route) for at least as good of a final preference.
-The argument then proceeds by induction on the path length - there are only a finite number of such stealings that can occur, each of which will ultimately still result in a route advertisement reaching $X$ along a most preferred path.
-%
-%Any \sysname-compiled policy will be \textit{Complete} as a result of the failure safety check.
-%
-
-%
-
-%The combination of Soundness and Completeness ensures that the distributed implementation will always send traffic along the best paths possible, yet will also never also use any undesired paths.
-These properties rely on the fact that \sysname produces stable BGP configurations:
-
-%
-%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo} for stable BGP.
-In particular, any policy with a dispute wheel will not pass the stronger failure safety check by \sysname.
-%
-%\begin{figure}[t!]
-%\includegraphics[width=\columnwidth]{figures/dispute-wheel}
-%\label{fig:dispute-wheel}
-%\caption{Product graph for a dispute wheel.}
-%\end{figure}
-%
-%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}.
-If a set of BGP configurations do not have a dispute wheel, then they will converge to their best routes.
-Any BGP policy with a dispute wheel will not satisfy the failure safety condition in Section~\ref{sec:compilation}.
-Assume that the preferences in the policy describe a dispute wheel, and we will show that our failure check will reject the policy.
-Informally, a dispute wheel occurs when there are some number of nodes $u_1, \dots, u_n$ attempting to get a path to a destination node $d$.
-Each node $u_i$ prefers to go through its neighbor $u_{i+1}$ over route $R_i$ than directly to $d$ with route $Q_i$.
-Thus the nodes form a wheel of preferences.
-The product graph for a policy that contains a dispute wheel will look like Figure~\ref{fig:dispute-wheel}, which shows a dispute wheel of size 3.
-In order to pass the failure safety check for the compiler, the more-preferred node for $u_2$ will need to have a superset of the paths starting from the less-preferred node for $u_2$.
-In turn, this means that the maximum length path after visiting the more preferred $u_2$ will be $max(Z) = 1 + max(Y)$, similarly, if we look at $u_1$, we will determine that $max(Y) = 1 + max(X)$, and so on.
-The resulting equations define a system of unsatisfiable equations.
-Therefore, it is not possible for \sysname to compile a BGP policy that contains a dispute wheel.
-Since no-dispute-wheel is a sufficient condition for BGP stability, any compiled \sysname policy will be stable.
-%
-
-%An important distinction is that BGP might still be instable with respect to other external ASes, since \sysname has no way of configuring their routing policy and can only rely on AS path filters to see what advertisements are observed.
-
-%=====================================================
-%
-%
 %  **Bibliography**
@@
 
+%=====================================================
+%
+%
+%  **Appendix**
+%
+%
+%=====================================================
+
+\appendix
+
+\begin{figure*}[t]\small
+  \begin{minipage}[t]{.45\linewidth}
+  \hdr{Syntax}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rclr}
+    \hline%
+
+     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
+     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
+     x       &::=& d.d.d.d/d & \textit{prefix} \\
+     t       &::=& \True & \textit{true} \\
+         &\BNFALT& \neg t & \textit{negation} \\
+         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
+         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
+         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
+     r       &::=& l & \textit{location} \\
+         &\BNFALT& \emptyset & \textit{empty set} \\
+         &\BNFALT& \In & \textit{internal loc} \\
+         &\BNFALT& \Out & \textit{external loc} \\
+         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
+         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
+         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
+         &\BNFALT& \NOT r & \textit{path negation} \\
+         &\BNFALT& r^* & \textit{iteration} \\
+     cc     &::=& agg(x, r_1 \rightarrow r_2)  & \textit{control constraints} \\
+  \end{array} \]%
+
+  \end{minipage}
+  %
+  ~~
+  \vrule
+  ~~
+  %
+  \begin{minipage}[t]{.5\linewidth}\small
+  \hdr{Propane Expansions}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[\begin{array}{rcl}
+    \hline
+    \Any               & = & \Sigma^* \\
+    \None              & = & \emptyset \\
+    \Internal          & = & \In^+ \\
+    \Always(X)         & = & X^* \\
+    \Never(X)          & = & (!X)^* \\
+    \Through(X)        & = & \Sigma^* \cdot X \cdot \Sigma^* \\
+    \Eventually(X)     & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
+    \Already(X)        & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
+    \End(X)            & = & \Sigma^* \cdot X \\
+    \Start(X)          & = & X \cdot \Sigma^* \\
+    \Enter(X)          & = & \Sigma^* \cdot \Out \cdot (X \cap \In) \cdot \Sigma^* ~ \cup \\
+                       &   & \Sigma^* \cdot (X \cap \Out) \cdot \In \cdot \Sigma^* \\
+    \Exit(X)           & = & \Sigma^* \cdot \In \cdot (X \cap \Out) \cdot \Sigma^* ~ \cup \\
+                       &   & \Sigma^* \cdot (X \cap \In) \cdot \Out \cdot \Sigma^* \\
+    \LinkKW(X,Y)       & = & \Sigma^* \cdot X \cdot Y \cdot \Sigma^* \\
+    \PathKW(\vec{X})   & = & \Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^* \\
+    \Novalley(\vec{X}) & = & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
+                       &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
+  \end{array} \]%
+
+  \end{minipage}%
+
+  \hrulefill%
+
+  \caption{Regular Intermediate Representation (RIR) syntax (left), and
+           Propane language expansions (right).}
+  \label{fig:rir-syntax}
+  %\vspace{-1em}
+\end{figure*}%
+
 \end{document}

### 2016-11-01 paper/abstraction/paper.tex
update compilation image to use smaller concrete topology
pass over section 2

@@
 
-We motivate \sysname using an example data center network adapted from prior work~\cite{propane}.
-Our network, shown in Figure~\ref{fig:example}, is a standard folded-Clos topology with four pods.
-T[1--8] denote top-of-rack (ToR) switches, A[1--8] denote aggregation switches, and S[1--2] denote spine switches.
-P[1--8] denote groups of addresses for services hosted in each rack.
+%We motivate \sysname using an example data center network. Our network, 
+Consider the data center network shown in Figure~\ref{fig:example}.  The boxes in the diagram
+represent \emph{switches}, and these switches play several different roles:  T[1--8] denote top-of-rack (ToR) switches, A[1--8] denote aggregation switches, and S[1--2] denote spine switches.
+The spine switches are connected to the
+rest of the internet; any traffic to or from the outside world flows through them.  The aggregation switches
+serve as a bridge between spine and ToR switches.   Finally, each ToR switch is
+connected to a set servers (``a rack''): P[1--8] denote groups of addresses for services hosted in each rack.
 Such groups are called address {\em prefixes} because they are encoded using the adresses' shared prefix.
-Assume that all nodes are running the border gateway protocol (BGP), as is common in large data centers~\cite{x}.
-\todo{more detail on BGP?}
-
-The intended policy for this network is as follows.
-Internal connectivity should be complete, i.e., all nodes must be able to talk to each other.
+
+We assume that each switch is running an instance of the \emph{Border Gateway Protocol} (BGP), 
+as is common in large data centers. In this protocol, adjacent switches use BGP to exchange messages
+with one another concerning the availability of routes to destinations.  A BGP \emph{configuration}
+(one for each switch) dictates which offered routes a switch will select and how to propagate chosen routes to its 
+neighbours.\footnote{If this submission is accepted and more space is available in the final version, 
+we will give a detailed explanation of BGP for the PLDI audience.  Henceforth, we assume knowledge of basic BGP
+mechanics.}
+
+%Assume that all nodes are running the border gateway protocol (BGP), as is common in large data centers~\cite{x}. \todo{more detail on BGP?}
+
+The intended high-level operator policy for this network is as follows.
+Internal connectivity should be complete, \IE, all nodes must be able to talk to each other.
 Services in Pods 1 and 2 should be globally accessible and thus their addresses should be announced externally, but only after aggregating individual prefixes P[1--4] into a single prefix PG.
-Finally, services in Pods 3 and 4 should be not be externally visible and thus their address should not be announced externally.
-
-To correctly configure the policy above, the network engineer's task is to generate low-level configuration commands for each switch in the network.
-This implies ensuring, for instance, that all switch interfaces are assigned correct addresses; all routing adjacencies are correctly configured (e.g., T1's configuration includes A1 as neighbor and vice-versa); all switches announce their own addresses (so that they can be reached for management purposes) and the ToRs announce the correct prefixes for their services; all switches  forward the prefix announcements that they should to each neighbor and not forward those that they should not (e.g., the spines should forward prefixes for local services to internal neighbors but not external neighbors); and the spines announce externally only the aggregate global prefix.
-
-As many have observed before, such configuration tasks are highly challenging. Consequently, configuration errors are the leading cause of network outages~\cite{x,y,z,batfish,propane}.
+Finally, services in Pods 3 and 4 not should be externally visible and thus their address should not be announced externally.
+
+To correctly configure the policy above, the network engineer's task is to generate low-level configurations for each switch in the network.
+This implies ensuring, for instance, that all switch interfaces are assigned correct addresses; all routing adjacencies are correctly configured (\EG, T1's configuration includes A1 as neighbor and vice-versa); all switches announce their own addresses (so that they can be reached for management purposes) and the ToRs announce the correct prefixes for their services; all switches  forward the prefix announcements that they should to each neighbor and not forward those that they should not (\EG, the spines should forward prefixes for local services to internal neighbors but not external neighbors); and the spines announce externally only the aggregate global prefix.
+\dpw{Do we need to explain aggregation here?}
+
+As many have observed before, such configuration tasks are highly challenging. Consequently, configuration errors are the leading cause of network outages~\cite{juniper-study,bgpmon,batfish,propane}.
 
@@
 
-In response, researchers have developed systems that synthesize low-level device configurations from high-level policy statements~\cite{x,y,propane}.
+In response, researchers have developed systems that synthesize low-level device configurations from high-level policy statements~\cite{narain:lisa05,narain+:configassure,dadc,propane}.
 %They take network topology and policy as input and output device configurations that are  guaranteed to be correct under all possible failures.
 Thus, they save the engineers from performing the complex task of breaking down global policies into device configurations.
-These systems offer appealing guarantees that the generated configurations correctly implement policy, even under arbitrary combinations of failures.
-
-However, our conversations with network engineers reveal that they have two limitations that discourage adoption.
+These systems eliminate entire classes of configuration errors by construction, and, in the case of
+Propane~\cite{propane}, guarantee that high-level policy is implemented correctly, even in the presence of 
+arbitrary combinations of failures.
+
+However, our conversations with network engineers at two major cloud providers reveal that they have two limitations that discourage adoption.
 The first is a mismatch in abstraction.
-Engineers of large networks tend to think of the network, and develop tools, in terms of roles and not individual devices.
+Engineers of large, structured networks tend to think of the network, and to develop management tools, using \emph{roles}, and not individual devices.
 A {\em role} refers to specific functionality and is played by one or more routers.
 The network in Figure~\ref{fig:example} has five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
-Engineers are reluctant to use a system that does not understand roles as a first-order abstraction.
-A superficial use of tags to group similar devices is not enough.
-For instance, there is no guarantee in concrete synthesis systems that the configurations of two devices with the same role will be similar.
-If the engineers wanted to debug, or simply understand, their output, they'll have to consider all device configurations instead of role configurations;  there can be orders of magnitude more devices than roles in the network.
-
-A second limitation is inability to support network evolution.
+Engineers are naturally reluctant to use a system that does not
+understand roles as a first-order abstraction because they think about 
+network policy in terms of roles, and, even more importantly, if they want to debug, analyze or 
+understand system output, they will have to consider 
+\emph{hundreds} of independent device configurations instead of just
+\emph{a handful} of role configurations. Unfortunately, even if two devices play the same role,
+there is no guarantee a concrete synthesis system will generate (syntactically) similar configurations,
+making vetting system outputs extremely difficult.
+
+A second limitation is the inability to support network evolution.
 Networks evolve all the time as nodes and links are added or removed and the addresses of services are changed.
-A system that supports evolution would ensure that supporting such evolution requires only small changes to network configurations.
+A system that supports evolution would ensure that
+small changes in topology require small, local changes in network configurations as opposed to pervasive
+changes across many devices.
 Engineers want to minimize changes to device configurations because each change runs the risk of poor, transient behavior due to poor router software or routing protocol dynamics~\cite{ratulbgpmisconfigs}.
-
-Concrete synthesis tools do not accommodate evolution well.
-When engineers want to modify the network, they would use the new topology as input to the system; old inputs or configurations are not uses.
-In the resulting output, existing device configurations may undergo unnecessary changes, beyond those needed to accommodate the modification.
-Suppose we want to modify the prefix of local ToR T8 in  Figure~\ref{fig:example}.
-To accommodate the modification, Propane, a concrete synthesis tool, will not only change T8's configuration but also those of the two spines because it uses prefix lists at spines to ensure that local prefixes are not advertised externally.
-As we show later, there is a way to design the configurations of this network in a way that does not require spine configuration changes to accommodate ToR prefix (and other) modifications, by exposing the inherent structure in this topology to the synthesis tool.
+%These networks must be highly
+%available; it isn't plausible to bring down an entire data center network, or large portions of it, to make
+%incremental changes.
+
+Unfortunately, in general, any change in network topology requires re-execution of a
+concrete synthesis engine, from scratch,
+on the changed topology.  The result may be 
+a completely different set of configurations.  However, even if such configurations are
+largely semantically similar to existing configurations, they may be syntactically different,
+and may cause considerable network disruption when updates are pushed to switches.
+For instance, suppose an operator wants to modify the prefix of local ToR T8 in Figure~\ref{fig:example}.
+To accommodate the modification, Propane, a concrete synthesis tool, will, at a minimum, not only change T8's configuration but also those of the two spines because it uses prefix lists at spines to ensure that local prefixes are not advertised externally.
+As we show later, there is a way to design the configurations of this network to avoid spine configuration changes while accommodating ToR prefix (and other) modifications.
+Our new
+abstraction-based synthesis framework synthesizes evolution-friendly roles automatically.
 
@@
 
-To simplify network configuration, and thus reduce errors, the network engineering community is adopting a template-based approach~\cite{x,y}.
-Instead of authoring one configuration file per router, engineers author one configuration template per role.\footnote{If a role is played by devices from different vendors, there is one template per role-vendor combination because templates use vendor configuration language.} Templates have parameters for various aspects of the configuration (e.g., interface addresses, neighbor list) and are compiled to device configurations by instantiating the parameters using a database of per-device values.
+To simplify network configuration, and thus reduce errors, the network engineering community is adopting a template-based approach~\cite{hatch,thwack}.
+Instead of authoring one configuration file per router, engineers author one configuration template per role.\footnote{If a role is played by devices from different vendors, there is one template per role-vendor combination because templates use vendor configuration language.} Templates have parameters for various aspects of the configuration (\EG, interface addresses, neighbor list) and are compiled to device configurations by instantiating the parameters using a database of per-device values.
 
@@
 While templates operate at the right level of abstraction, today's template systems have two limitations.
-The first is that they offer no guarantees on correctness.
-To author correct templates, engineers must do manually the conceptually challenging task of breaking down complex, global policies into role templates such that the collective behavior of configurations derived from the templates correctly implements the policy under all failure conditions.
+The first is that they offer no correctness guarantees.
+To author correct templates, engineers must break down complex, network-wide routing policy into role templates such that the collective behavior of the configurations generated from the templates correctly implements the desired high-level policy under all failure conditions.
+This is a challenging, manual task, with no tools available to support template verification.
 
 As a result, the types of configuration design errors pointed in prior work~\cite{propane} can occur in template design as well.
-For instance, to keep local prefixes internal the engineer may implement announcement forwarding on spines based on the identity of the neighbor, i.e., do not announce externally anything heard from local aggregators.
+For instance, to keep local prefixes internal the engineer may implement announcement forwarding on spines based on the identity of the neighbor, \IE, do not announce externally anything heard from local aggregators.
 This implementation is appealing because it does not require changes to spine configurations when ToR prefixes change.
@@
 Specifically, when S1 is disconnected from A5 and A6, it may hear about P5 and P6 from A3 and A4 (via A[5--6]->S2->A[3--4]), and it will then announce those prefixes outside (since they no not come from a local aggregator), leading to a policy violation.
-A possible correct implementation here would be for each spine to not advertise externally announcements from local aggregators {\em and} reject announcements that have traversed the other spine (i.e., disallow "valleys," or up-down-up paths).
+A possible correct implementation here would be for each spine to block messages headed to external peers from local aggregators {\em and} to reject announcements that have traversed the other spine (\IE, to disallow "valleys," or up-down-up paths).
 
@@
 The second limitation of today's template systems is that, like concrete synthesis tools, they do not support network evolution.
-In theory, being role-based, templates do not have to be redesigned when the network evolves while keeping its basic structure of roles and their inter-connectivity.
+One might hope that important network properties such as connectivity and fault tolerance persist when networks evolve in ways consistent with existing roles and templates.
+However, existing
+template systems provide no guarantees that seemingly-minor variations of a given topology have similar properties.    
+%In theory, templates do not have to be redesigned when the network evolves while keeping its basic structure of roles and their inter-connectivity.
 In practice, however, it is not guaranteed that templates that work for a given topology also work for seemingly-minor variations of the topology.
@@
 However, that is not necessarily true.
-For instance, templates that disallow valley paths lead to a less fault-tolerant system for Figure~\ref{fig:example2}.
-In particular, aggregation-induced blackholes~\cite{x} can occur in Figure~\ref{fig:example2} with only one link failure, while it would take two failures in Figure~\ref{fig:example}.
-Such blackholes occur when a switch announces an aggregate prefix but has no valid path to a more specific prefix within the aggregate.
-In Figure~\ref{fig:example}, a blackhole will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes by virtue of announcing the encompassing aggregate PG.
+For example,
+data centers are often susceptable to a phenomenon called an \emph{aggregation-induced black hole}~\cite{route-aggregation}.
+Such black holes occur when a switch announces an aggregate prefix but has no valid path to a more specific prefix within the aggregate, so the black hole will draw traffic, but that traffic will be unable
+to reach its destination.
+For instance, if a network operator uses templates designed for Figure~\ref{fig:example}, which
+disallow valley paths, on Figure~\ref{fig:example2}, they will find that while it takes two link failures to
+trigger a black hole in  Figure~\ref{fig:example}, it takes only 1 failure to trigger a black hole in
+ Figure~\ref{fig:example2}.   
+More specifically, in Figure~\ref{fig:example2}, a blackhole will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes by virtue of announcing the encompassing aggregate PG.
 In contrast, in Figure~\ref{fig:example}, no such blackhole will occur after a single failure.
 
-Thus, engineers today must reason about the correctness of templates for each evolution (using expensive simulations because current systems do not provide any correctness guarantee by design).
-Worse, for some evolutions, they may discover that their old templates will not work anymore and need modifications.
-This discovery is highly problematic because changing the templates implies that the configuration of all the devices needs to change, which can be an unacceptable disruption.
-When that happens, many networks abandon templates entirely and revert to hand-crafting configuration files, using localized patches to accommodate evolution.
-This reversion brings backs the complexity and errors that the templates were meant to prevent.
+Thus, engineers today must reason about the correctness of templates for each topology change (using expensive simulations because current systems do not provide any correctness guarantee by design).
+Worse, for some changes, they may discover that their old templates will not work anymore and need modifications.
+~\dpw{Note: This is going to be true for Methane too.}  This discovery is highly problematic because changing a template will cause a change in the configurations of all the devices that use that template---in many cases, an unacceptable disruption.
+When that happens, network operators may abandon templates entirely and revert to hand-crafting configuration files, using localized patches to accommodate evolution.
+Such patches reintroduce the complexity and errors that templates were meant to prevent.
 
@@
 \begin{figure}
-\begin{tabular}{p{0.7in}|p{0.7in}p{0.7in}p{0.7in}}
-& Abstraction level & Correctness guarantees & Support evolution  \\ \hline
-Concrete synthesis & \xmark & \cmark & \xmark \\ \hline
-Template systems & \cmark & \xmark & \xmark \\ \hline
-\sysname & \cmark & \cmark & \cmark \\ 
+\begin{tabular}{|p{0.6in}|p{0.6in}p{0.7in}p{0.6in}|} 
+\hline
+& Abstract Roles & Correctness Guarantees & Evolution Support  \\ \hline
+Concrete Synthesis & \xmark & \cmark & \xmark \\ \hline
+Template Systems & \cmark & \xmark & \xmark \\ \hline
+\sysname & \cmark & \cmark & \cmark \\  \hline
 \end{tabular}
-\caption{Properties of different methods for generating device configurations.}
+\caption{Comparing configuration techniques.}
+\label{fig:marketing}
 \end{figure}
@@
 
-As Table~\ref{fig:marketing} shows, \sysname addresses the limitations with both concrete synthesis and current template systems.
-It operates at the right level of abstraction, guarantees the correctness of configurations, and supports network evolution.
-It takes as input network policy and an {\em abstract} topology  that describes device roles and connectivity.
-It outputs a template for each role, which can be compiled to configurations based on the concrete topology and parameter values.
-\sysname guarantees that its templates are correct, i.e., the configurations generated from them correctly implement the specified policy for {\em any} concrete topology that matches the abstract topology; and when a valid concrete topology evolves to another valid concrete topology, only necessary changes are needed to device configurations.
+As Table~\ref{fig:marketing} shows, \sysname addresses the limitations of both concrete synthesis and current template systems.
+It operates at the right level of abstraction for network operators, provides strong guarantees about compiled configurations, supports verification of important correctness properties, and supports network evolution.
+As inputs, \sysname takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an
+{\em abstract} topology that describes device roles and 
+connectivity invariants.  It outputs a template for each role.  Per-device configurations may be generated
+from templates by instantiating their parameters with concrete values drawn from the network topology. 
+\sysname provides strong guarantees about its templates: 
+(1) the configurations generated from them correctly implement the specified policy for {\em any} concrete topology that matches the given abstract topology; and (2) if you add or remove a single node or edge in a way compatible
+with the abstract topology, only configurations of adjacent devices ever need to be updated.
 
@@
   %
-  \begin{minipage}[t]{.45\linewidth}
+  \begin{minipage}[t]{.4\linewidth}
   \hdr{Concrete Topology}{}
-  \includegraphics[width=\columnwidth]{figures/example}
+  \includegraphics[width=.7\columnwidth]{figures/topology-con}
   \end{minipage}%
   %
-  \begin{minipage}[t]{.35\linewidth}
+  \begin{minipage}[t]{.4\linewidth}
   \hdr{Abstract Topology}{}
-  \includegraphics[width=.75\columnwidth]{figures/example3}
+  \includegraphics[width=.57\columnwidth]{figures/topology-abs}
   \end{minipage}%
@@
 The abstract safety analysis uses Z3Opt \ryan{reference} to minimize variables subject to the annotated constraints.
+Since the analysis typically calls Z3 with many times with relatively simple optimization problems, we use a timeout of 200ms.
 

### 2016-11-02 paper/abstraction/paper.tex
update section 4

@@
 %
-%  **Propane Language**
+%  **Methane Overview**
 %
@@
 \section{Methane overview}
-\label{sec:propane}
+\label{sec:overview}
 
@@
 
-Suppose now that we want to disallow paths with valleys (\IE, paths that go down and then up at some point). Such a constraint can be added to the routing policy simply:
+Suppose now that we want to disallow paths with valleys (\IE, paths that go down and then up at some point). Such a constraint can be added to the routing policy in \sysname:
 \begin{code}
@@
 
-\subsection{Language}
-
 %=====================================================
@@
 
-\section{Compilation}
+\section{Configuration Synthesis}
 \label{sec:compilation}
 
-We borrow the intermediate graph-based representation from Propane:
+Configuration synthesis for network configurations is challenging for a number of reasons.
+First, although \sysname polices specify stable network-wide routing behavior, actual configurations are per-device and run distributed algorithms to compute routes.
+Thus the compiler must ensure that the result of the distributed computation matches the policy.
+Furthermore the distributed computation must compute the correct paths under all possible combinations of failures.
+Second, \sysname must find configurations that work across any valid concrete network topology matching the abstraction provided as input.
+Finally, \sysname must ensure that the resulting configurations can be evolved incrementally so that local changes to the topology ensure that only local changes to configurations are required to ensure global routing correctness.
+
+In this section, we introduce the idea of topology abstraction, describe how \sysname synthesizes network configurations over these abstractions, and formalize the guarantees provided by \sysname.
+
+\subsection{Methane Language}
+
+The syntax introduced in \S\ref{sec:overview} is just syntactic sugar for a core language based on regular expressions.
+Figure~\ref{fig:syntax} shows a simplified version of the core \sysname syntax that omits some details such as aggregation.
+The full langauge definition can be found in the appendix.
+A policy has one or more constraints, each of which consists of a test on the type of traffic being matched and a corresponding set of preferred regular expressions describing network paths.
+Regular expressions are defined over network locations, where each location is either a router inside the operators network, or an external neighbor.
+There are two special characters \In~ and \Out, which match any internal and external location respectively.
+There are two types of predicates: a test for a concrete prefix $d.d.d.d/[d..d]$ matches an IP prefix with value $d.d.d.d$ and length in the range $[d..d]$ where metavariable $d$ represents an integer.
+For example, the IP prefix 148.0.1.0/[24..32] would match traffic destined for IP address 148.0.1.* with a subnet length between 24 and 32 bits.
+\ryan{this needs to be explained clearer}.
+
+Converting from the high-level syntax from \S\ref{sec:overview} to the core syntax is straightforward.
+For example, the predicate $\True$ becomes $0.0.0.0/[0..32]$.
+Preferences are lifted to the top level of the regular expression when unambiguous.
+For example, the constraint $\Exit(\sf{Peer1} \Prefer \sf{Peer2})$ becomes $\Exit(\sf{Peer1}) \Prefer \Exit(\sf{Peer2})$ before being rewritten into regular expressions.
+Each modular set of constraints are joined prefix-by-prefix by taking the intersection of their constraints.
+For example, the data center policy from \S\ref{sec:overview} would result in the following \sysname policy:
+%
+\begin{code}
+\$PG  \Path \End(TG) & !transit(\Out,\Out),
+\$PL  \Path \End(TL) & \Always(\In) & !transit(\Out,\Out),
+\True \Path 
+    \Exit(Peer1) & !transit(\Out,\Out) \Prefer 
+    \Exit(Peer2) & !transit(\Out,\Out)
+\end{code}
+\noindent%
+%
+Finally, each constraint desugars to a regular expression. For example, the constraint $\Always(\In)$ becomes $\In^*$ and the constraint $\End({\small \mathsf{T0}})$ becomes $\Sigma^* \cdot \sf{T0}$.
+
+\subsection{Topology Abstraction}
+
+\subsection{Configuration Synthesis}
+
+\subsection{Substitution Theorem}
 
 \begin{easylist}[itemize]
-& Show compilation from language to RIR
-
-& Show compilation from RIR to Product Graph
-&& Note that preferences are general, and it could potentially
-   use any implementation (including SDN). But for the sake of
-   simplicity, we will assume a BGP backend like Propane.
+& Define abstractions more formally,
+&& e.g., homomorphism between graphs + node/edge constraints
+
+&& First show how to compile to the Product Graph, and from there to the ABGP
+&& Show/Define safety analysis simulation relation for both concrete and abstract product graphs
+  and how it holds for both.
+&& Next define the concretization & subst. functions for translating the abstract policy
+   into the concrete policy, using the ABGP example for reference
+
+&& Theorem: if safety analysis holdls in the abstract graph, it holds for the concrete one,
+   and the preferences are consistent.
+
+& Give abstraction theorem: commuting of concretization and compilation
 \end{easylist}
+
+\begin{figure}[t]\small
+  \begin{minipage}[t]{\linewidth}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rclr}
+     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
+     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
+     t       &::=& \$x & \textit{template variable} \\
+         &\BNFALT& d.d.d.d/[d..d] & \textit{prefix test} \\
+     r       &::=& l & \textit{location} \\
+         &\BNFALT& \emptyset & \textit{empty set} \\
+         &\BNFALT& \In & \textit{internal loc} \\
+         &\BNFALT& \Out & \textit{external loc} \\
+         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
+         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
+         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
+         &\BNFALT& \NOT r & \textit{path negation} \\
+         &\BNFALT& r^* & \textit{iteration} \\
+  \end{array} \]%
+
+  \end{minipage}
+  \vspace{1em}
+  \caption{Simplified \sysname syntax.}
+  \label{fig:syntax}
+  %\vspace{-1em}
+\end{figure}%
 
@@
 
+  \vspace{2em}
   \begin{minipage}[t]{.6\linewidth}
     \hdr{Concrete Product Graph}{}
-  %\includegraphics[width=.65\columnwidth]{figures/example3}
+    \includegraphics[width=.9\columnwidth]{figures/pg-con}
   \end{minipage}%
@@
   \hdr{Abstract Product Graph}{}
-
-    \begin{tikzpicture}
-      \draw [] (0, 0) circle [radius=0.45] node {start};
-      \draw [] (-1, -1) circle [radius=0.45] node {$(S,0,0)$};
-      %\draw [] (0, .45) -- (0, 2.05);
-    \end{tikzpicture}
+    \includegraphics[width=.9\columnwidth]{figures/pg-abs}
 
@@
 
-\section{Abstraction}
-\label{sec:abstraction}
-
-\begin{easylist}[itemize]
-& Define abstractions more formally,
-&& e.g., homomorphism between graphs + node/edge constraints
-&& Use the datacenter example from before
-&& First define the concretization function for translating the abstract policy
-   into the concrete policy
-&& Next, show the Product Graph for both the concrete and abstract policies.
-
-& Show/Define safety analysis simulation relation for both concrete and abstract product graphs
-  and how it holds for both.
-&& Theorem: if safety analysis holdls in the abstract graph, it holds for the concrete one,
-   and the preferences are consistent.
-
-& Show/Define compilation to abstract BGP policies. Give concretization function,
-  and compilation definition.
-
-& Give abstraction theorem: commuting of concretization and compilation
-\end{easylist}
+\section{Analysis}
+\label{sec:analysis}
 
@@
     \inference{0}{L$(j,k)$}{$\vDash e_1 > 0$}{S$(min(j*k,e_1),1)$}
-    \inference{10}{A$(j,k)$}{$e_2 > 0$}{A$(1,min(j,e2))$}
-  \end{tikzpicture}
-  \end{minipage}
-
-  %
-  \vspace*{3em}
-  %
-  \begin{minipage}[t]{.5\linewidth}%
-  \begin{tikzpicture}
-    \inference{0}{L$(j,k)$}{$e_1=n$}{A$(min(j*k,n),1)$}
-    \inference{10}{L$(j,k)$}{$e_1=n$}{A$(1,j)$}
+    \inference{5}{A$(j,k)$}{$e_2 > 0$}{A$(1,min(j,e2))$}
+    \inference{10}{L$(j,k)$}{$e_1=n$}{A$(min(j*k,n),1)$}
+    \inference{15}{L$(j,k)$}{$e_1=n$}{A$(1,j)$}
   \end{tikzpicture}
@@
     \inference{0}{L$(j,k)$}{$e_1 > 0$, $e_2 > 0$}{S$(min(j*k,n-\dfrac{(m-j)*e_1}{e_2}),1)$}
-  \end{tikzpicture}
-  \end{minipage}
-
-  %
-  \vspace*{3em}
-  %
-  \begin{minipage}[t]{.5\linewidth}%
-  \begin{tikzpicture}
     \inference{10}{L$(j,k)$ ~~~ L$(j- m ~\text{mod}~ \big(\dfrac{n}{e_1}\big),1)$}{$e_1 > 0$, $e_2 > 0$}{}
@@
   \end{minipage}
-  %
+
   \vspace*{1em}
@@
   \begin{center}
-      \begin{tabular}{| l l | c | c | c |}
+      \begin{tabular}{| l | c | c | c |}
       \hline
-      \textbf{Topology} & \textbf{Variant} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
-      Fattree
-         & Google &  & \cmark & \cmark  \\
-         & Facebook &  & \cmark & \cmark \\
-         & F10 &  & \cmark & \cmark \\ \hline
-      Recursive
-         & BCube & $k$ & \cmark & \xmark \\
-         & DCell & $k$ & \cmark & \xmark \\ \hline
+      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
+      Google Fattree & & \cmark & \cmark  \\ \hline
+      Facebook Fattree & & \cmark & \cmark \\ \hline
+      Microsoft Fattree & & & \\ \hline
+      F10 Fattree & & \cmark & \cmark \\ \hline
+      BCube & $k$ & \cmark & \xmark \\ \hline
+      DCell & $k$ & \cmark & \xmark \\ \hline
          %& HCN & $h$ & \cmark & \xmark \\
-      Hypercube
-         & Standard & $N$ & \cmark & \cmark \\
-         & HyperX & $L$ & \cmark & \cmark \\ \hline
-      Random \footnote{foo}
-         & Scafida &  & ??? & ??? \\
-         & JellyFish &  & ??? & ??? \\
-
-      \hline
+      Butterfly & $n$ & \cmark & \cmark \\ \hline
+      Hypercube & $N$ & \cmark & \cmark \\ \hline
+      HyperX & $L$ & \cmark & \cmark \\ \hline
       \end{tabular}
@@
 \end{figure}
+
+%\begin{figure}[t!]
+%  \begin{center}
+%      \begin{tabular}{| l l | c | c | c |}
+%      \hline
+%      \textbf{Topology} & \textbf{Variant} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
+%      Fattree
+%         & Google &  & \cmark & \cmark  \\
+%         & Facebook &  & \cmark & \cmark \\
+%         & F10 &  & \cmark & \cmark \\ \hline
+%      Recursive
+%         & BCube & $k$ & \cmark & \xmark \\
+%         & DCell & $k$ & \cmark & \xmark \\ \hline
+%         %& HCN & $h$ & \cmark & \xmark \\
+%      Hypercube
+%         & Standard & $N$ & \cmark & \cmark \\
+%         & HyperX & $L$ & \cmark & \cmark \\ \hline
+%      Random \footnote{foo}
+%         & Scafida &  & ??? & ??? \\
+%         & JellyFish &  & ??? & ??? \\
+%      \hline
+%      \end{tabular}
+%  \end{center}
+%  \caption{Abstract Analysis Precision.}
+%  \label{fig:analysis-precision}
+%\end{figure}
 
@@
 
-\para{Random Network Topologies}
-
-Random networks such as Scafida and Jellyfish have seen a great deal of interest in academia.
+%\para{Random Network Topologies}
+%
+%Random networks such as Scafida and Jellyfish have seen a great deal of interest in academia.
 These topologies were designed with an eye towards incremental expansion and are based on probabilistic arguments of bisection bandwidth in random regular graphs.

### 2016-11-02 paper/abstraction/paper.tex
updates to section 4

@@
 
-In this section, we introduce the idea of topology abstraction, describe how \sysname synthesizes network configurations over these abstractions, and formalize the guarantees provided by \sysname.
+In this section, we formalize the \sysname language and topology abstraction, describe how \sysname synthesizes network configurations over these abstractions, and formalize the guarantees provided by \sysname.
 
 \subsection{Methane Language}
-
-The syntax introduced in \S\ref{sec:overview} is just syntactic sugar for a core language based on regular expressions.
-Figure~\ref{fig:syntax} shows a simplified version of the core \sysname syntax that omits some details such as aggregation.
-The full langauge definition can be found in the appendix.
-A policy has one or more constraints, each of which consists of a test on the type of traffic being matched and a corresponding set of preferred regular expressions describing network paths.
-Regular expressions are defined over network locations, where each location is either a router inside the operators network, or an external neighbor.
-There are two special characters \In~ and \Out, which match any internal and external location respectively.
-There are two types of predicates: a test for a concrete prefix $d.d.d.d/[d..d]$ matches an IP prefix with value $d.d.d.d$ and length in the range $[d..d]$ where metavariable $d$ represents an integer.
-For example, the IP prefix 148.0.1.0/[24..32] would match traffic destined for IP address 148.0.1.* with a subnet length between 24 and 32 bits.
-\ryan{this needs to be explained clearer}.
-
-Converting from the high-level syntax from \S\ref{sec:overview} to the core syntax is straightforward.
-For example, the predicate $\True$ becomes $0.0.0.0/[0..32]$.
-Preferences are lifted to the top level of the regular expression when unambiguous.
-For example, the constraint $\Exit(\sf{Peer1} \Prefer \sf{Peer2})$ becomes $\Exit(\sf{Peer1}) \Prefer \Exit(\sf{Peer2})$ before being rewritten into regular expressions.
-Each modular set of constraints are joined prefix-by-prefix by taking the intersection of their constraints.
-For example, the data center policy from \S\ref{sec:overview} would result in the following \sysname policy:
-%
-\begin{code}
-\$PG  \Path \End(TG) & !transit(\Out,\Out),
-\$PL  \Path \End(TL) & \Always(\In) & !transit(\Out,\Out),
-\True \Path 
-    \Exit(Peer1) & !transit(\Out,\Out) \Prefer 
-    \Exit(Peer2) & !transit(\Out,\Out)
-\end{code}
-\noindent%
-%
-Finally, each constraint desugars to a regular expression. For example, the constraint $\Always(\In)$ becomes $\In^*$ and the constraint $\End({\small \mathsf{T0}})$ becomes $\Sigma^* \cdot \sf{T0}$.
-
-\subsection{Topology Abstraction}
-
-\subsection{Configuration Synthesis}
-
-\subsection{Substitution Theorem}
-
-\begin{easylist}[itemize]
-& Define abstractions more formally,
-&& e.g., homomorphism between graphs + node/edge constraints
-
-&& First show how to compile to the Product Graph, and from there to the ABGP
-&& Show/Define safety analysis simulation relation for both concrete and abstract product graphs
-  and how it holds for both.
-&& Next define the concretization & subst. functions for translating the abstract policy
-   into the concrete policy, using the ABGP example for reference
-
-&& Theorem: if safety analysis holdls in the abstract graph, it holds for the concrete one,
-   and the preferences are consistent.
-
-& Give abstraction theorem: commuting of concretization and compilation
-\end{easylist}
 
@@
 \end{figure}%
+
+The syntax introduced in \S\ref{sec:overview} is just syntactic sugar for a core language based on regular expressions.
+Figure~\ref{fig:syntax} shows a simplified version of the core \sysname syntax that omits some details such as aggregation.
+The full langauge definition can be found in the appendix.
+
+A policy has one or more constraints, each of which consists of a test on the type of traffic being matched and a corresponding set of preferred regular expressions describing network paths.
+Regular expressions are defined over network locations, where each location is either a router inside the operators network, or an external neighbor.
+There are two special characters \In~ and \Out, which match any internal and external location respectively.
+There are two types of predicates: a test for a concrete prefix $d.d.d.d/[d..d]$ matches an IP prefix with value $d.d.d.d$ and length in the range $[d..d]$ where metavariable $d$ represents an integer.
+For example, the IP prefix 148.0.1.0/[24..32] would match traffic destined for IP address 148.0.1.* with a subnet length between 24 and 32 bits.
+\ryan{this needs to be explained clearer}.
+
+Converting from the high-level syntax from \S\ref{sec:overview} to the core syntax is straightforward.
+For example, the predicate $\True$ becomes $0.0.0.0/[0..32]$.
+Preferences are lifted to the top level of the regular expression when unambiguous.
+For example, the constraint $\Exit(\sf{Peer1} \Prefer \sf{Peer2})$ becomes $\Exit(\sf{Peer1}) \Prefer \Exit(\sf{Peer2})$ before being rewritten into regular expressions.
+Each modular set of constraints are joined prefix-by-prefix by taking the intersection of their constraints.
+For example, the combining the Routing and Locality constraints in the data center policy from \S\ref{sec:overview} would result in the following \sysname policy:
+%
+\begin{code}
+\$PG  \Path \End(TG),
+\$PL  \Path \End(TL) \ensuremath{\cap} \Always(\In),
+\True \Path \Exit(Peer1) \Prefer \Exit(Peer2)
+\end{code}
+\noindent%
+%
+Finally, each constraint desugars to a regular expression. For example, the constraint $\Always(\In)$ becomes $\In^*$ and the constraint $\End({\small \mathsf{T0}})$ becomes $\Sigma^* \cdot \sf{T0}$.
+
+\subsection{Topology Abstraction}
+
+\subsection{Product Graph}
+
+A key step for \sysname to generate device configurations is to build a data structure amenable to joint analysis of both the topology and routing policy.
+Intutively, \sysname captures both topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology into a data structure called the Product Graph.
+
+The Product Graph is a compact representation of all paths distributed protocol messages might be passed through the network in order to result in policy-compliant paths.
+Although \sysname policies describe the routes that traffic should take through the network, network protocols (including BGP) typically disseminate router information in the opposite direction. 
+For example, a router Y will tell its neighbor X that it has a route to the destination meaning that X can send traffic through Y. For this reason, we start by compiling
+
+Since each predicate in a \sysname policy has its own set of regular expression path constraints, \sysname constructs one Product Graph per prefix and generates configuration on a per-prefix basis.
+
+\para{Formal definition}
+
+\ryan{TODO: this was copied from previous paper for reference}
+
+For each regular expression $r_i$ in an RIR policy, we construct a DFA for the reversed regular expression.
+An automata for regular expression $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
+The alphabet $\Sigma$ consists of all abstract locations (\IE, routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+%
+The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$.
+%
+The Product Graph is constructed as a tuple ($V'$, $E'$, $s$, $P$) with
+vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
+edges $E' \colon V' \times V'$,
+a unique starting vertex $s$,
+and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of path ranks.
+
+For a Product Graph vertex $n = (l, \dots) \in V'$, we say that $n$ is a \emph{shadow} of topology location $l$.
+We also write $\tilde{n} = l$ to indicate that the topology location for node $n$ is $l$.
+When two PGIR nodes $m$ and $n$ shadow the same topology location (\IE, $\tilde{m} = \tilde{n}$), we write $m \approx n$.
+
+\ryan{TODO: this was copied from previous paper for reference}
+
+\para{From RIR To PGIR}
+
+Let $a_i$ and $b_i$ denote states in the regular policy automata.
+The PGIR is constructed by adding an edge from $m = (l_m, a_1, \dots, a_k)$ to $n = (l_n, b_1, \dots, b_k)$ whenever $\sigma_i(a_i, l_n) = b_i$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
+%
+Additionally, we add edges from the start node $s$ to any $n = (l, a_1, \dots, a_k)$ when $\sigma_i(q_{0_i}, l) = a_i$ for each $i$.
+%
+The preference function $P$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $. That is, it records the path rank of each automaton that has reached a final state.
+% in preferences are achieved from each policy automaton for every node in the product construction.
+%
+We write $(m \leq_{rank} n)$ if either $P(m) = P(n) = \emptyset$ or $min ~ P(m) \leq min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.
+
+Figure~\ref{fig:example-compilation} shows an example of constructing a Product Graph for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview}: 
+%
+%\begin{code}
+%\True \Path \Exit(\sf{Peer1}) \Prefer \Exit(\sf{Peer2})
+%\end{code}
+%\noindent%
+%
+The first automaton represents the more preferred constraint $\Exit(Peer1)$ and the second automaton represents the less preferred constraint $\Exit(Peer2)$.
+The Product Graph representation is shown for both an instance of a concrete network matching the abstraction from \S\ref{sec:overview} as well as for the abstraction itself.
+
+Each node in the Product Graph tracks both where a protocol message is in the topology as well as how much progress has been made towards satisfying each policy constraint.
+In this example, all routes that eventually leave through Peer1 will lead to an accepting state for the first automaton and all routes that eventually leave through Peer2 will lead to an accepting state for the second automaton.
+Note that the translation from the topology to the Product Graph preserves the graph homomorphism property.
+\ryan{TODO: explain this more formally}
+
+\subsection{Substitution Theorem}
+
+\begin{easylist}[itemize]
+& homomorphism between graphs + node/edge constraints
+& First show how to compile to the Product Graph, and from there to the ABGP
+& Show/Define safety analysis simulation relation for both concrete and abstract product graphs
+  and how it holds for both.
+&& Next define the concretization & subst. functions for translating the abstract policy
+   into the concrete policy, using the ABGP example for reference
+&& Theorem: if safety analysis holdls in the abstract graph, it holds for the concrete one,
+   and the preferences are consistent.
+
+& Give abstraction theorem: commuting of concretization and compilation
+\end{easylist}
 

### 2016-11-02 paper/abstraction/paper.tex
pass through section 3

@@
 As we have seen, writing correct network configurations is challenging task.
-Operators must manually decompose network-wide policies into device configurations,
-reason about all combination of network failures, parameterize configurations to
-allow for change, and write configurations in a way amenable to incremental change.
-We now give an overview of \sysname, a system that facilitates all of these tasks.
+Operators must manually decompose network-wide policies into distributed device configurations, reason about all combinations of network failures, and parameterize configurations to allow for change, ideally in a way that is amenable to incremental change.
+In this section, we give an overview of the \sysname system, which gives operators a principled way to accomplish all of these tasks.
 
@@
 
-\sysname builds on the Propane network configuration synthesis language,
-which lets operators specify a \emph{network-wide} routing policy, by adding
-support for compiling policies parameterized over different topology.
-In particular, a \sysname policy consists of predicates matching
-certain classes of traffic, paired with a list of ranked constraints
-on the paths traffic should prefer to take for the predicate.
+\sysname builds on the Propane network configuration synthesis tool, by supporting both synthesis for and reasoning over parameterized classes of topologies and their interactions with user-specified routing policy.
+\sysname takes as input, (1) a topology abstraction in the form of a graph homomorphism annotated with logical constraints about node and edge mutliplicities, and (2) a domain-specific routing policy that consists of a mapping from predicates matching various classes of traffic, to a list of ranked constraints on the paths traffic matching the predicate should prefer to take through the network.
 
@@
 
-Consider again the datacenter from earlier. Ideally, we would like
-to find device configuration templates for each router that, taken together, ensure correct forwarding
-behavior for both of the datacenter topologies in figures~\ref{fig:example} and~\ref{fig:example2}.
-
-\sysname achieves this by allowing the operator to abstract the network into
-a role-based topology that captures a class of concrete topologies and then write a
-routing specification over this abstraction. Figure~\ref{fig:example3} shows an example of one
-such abstraction for the datacenter networks.
-
-The network is partitioned into 5 different roles:
-local tor (TL), global tor (TG), local aggregator (AL), global aggregator (AG), and spine (S).
-Intuitively, each concrete router in the network must map to exactly one role.
-Whenever there is a link between routers in the concrete network, there must be an associated link
-between their abstract roles. Thus the role-based abstraction is an overapproximation of the connectivity
-of the concrete network.
+Consider again the networks from \S\ref{sec:motivation}. Ideally, we would like
+to find a suitable topology abstraction that can describe both of the datacenters from figures~\ref{fig:example} and~\ref{fig:example2} as well as any reasonable generalization of these datacenters.
+\sysname provides several abstraction mechanisms to achieve this goal.
+
+The first is a role-based abstraction that allows an operator to map routers in the concrete network to ``roles" or routers in the abstract network.
+Figure~\ref{fig:example3} shows an example of an abstraction for both datacenter networks from \S\ref{sec:motivation}.
+In particular the concrete networks are abstracted into a new topology with 5 different roles: local tor (TL), global tor (TG), local aggregator (AL), global aggregator (AG), and spine (S).
+
+More specifically, a network topology is a graph $G$ = ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$.
+A role-based abstraction is a graph homomorphism from $G$ to an abstract graph $G^A$ = ($V^A$,$E^A$).
+A graph homorphism $f : G \rightarrow G^A$ is a function that maps each node in the concrete graph to a node in the abstract graph such that, whenever $(u,v) \in E$, then $(f(u),f(v)) \in E^A$.
 
@@
 
+The role-based abstraction therefore overapproximates the connectivity of the underlying concrete graphs.
+Unfortunately this abstraction alone loses a lot of information about the underlying structure of the concrete network.
+For example, with this abstraction any spine router in a concrete network may or may not be connected to any aggregator router.
+%
 In order to refine the abstraction to capture more precisely the kinds of concrete networks of interest,
@@
 For example, in Figure~\ref{fig:example3}, the first two constraints: $e1 = AG$ and $e2 = TG$ declare that, within any pod P, the number of outgoing edges from $TG$ to $AG$ is equal to the number of nodes that map to $AG$.
-Similarly, the number of outgoing edges from $AG$ to $TG$ is equal to the number of nodes that map toe $TG$.
+Similarly, the number of outgoing edges from $AG$ to $TG$ is equal to the number of nodes that map to $TG$.
 These constraints capture the fact that, within any given pod, the global aggregators and tors are in a full mesh.
-Furthermore, the constraints $TG = AG$ and $TG \geq 2$ ensure that the number of concrete nodes in role $TG$ is always equal to the number of concrete nodes in role $AG$.
+Furthermore, the constraints $TG = AG$ and $TG \geq 2$ ensure that the number of concrete nodes in role $TG$ is always equal to the number of concrete nodes in role $AG$, which is at least 2.
 Similar constraints also appear for the local aggregators and tors.
@@
 Again, similar constraints appear for the local aggregator role.
-Finally, the constraints $S \geq 2$, $S \pmod AG = 0$, and $S \pmod AL = 0$ ensure that there are at least 2 routers in the spine role, and that the number of spine routers is always divisible by the number of global and local aggregators.
-%
-The last two constraints are interesting in that they do not involve a simple inequality. In general operators can write constraints using logical formula over any SMT theory.
+Finally, the constraints $S \geq 2$, $(S \mod AG) = 0$, and $(S \mod AL) = 0$ ensure that there are at least 2 routers in the spine role, and that the number of spine routers is always divisible by the number of global and local aggregators.
+%
+The last two constraints are interesting in that they do not involve a simple inequality.
+In general operators can write constraints using logical formula for any theory supported by modern SMT solvers.
 
@@
 
-Now let us configure each of the datacenter networks from \S\ref{sec:motivation} by writing a routing policy over the abstract topology.
-In \sysname, we can capture the basic routing behavior with the following constraints:
+Next let us see how to configure each of the datacenter networks from \S\ref{sec:motivation} by writing a \sysname routing policy over the new abstract topology.
+In \sysname, we can capture the basic routing behavior for the datacenters with the following constraints:
 %
@@
 \Define Routing =
-    \$PG  \Path \End(TG)
-    \$PL  \Path \End(TL)
+    \$GP  \Path \End(TG)
+    \$LP  \Path \End(TL)
     \True \Path \Exit(Peer1 \Prefer Peer2)
@@
 The first line introduces a prefix \emph{template} variable.
-It says that traffic for each global prefix associated with the template variable \$PG has the constraint that it should follow a path that ends at its corresponding destination router contained in the abstract TG role.
+It says that traffic for each global prefix associated with the template variable \$GP has the constraint that it should follow a path that ends at its corresponding destination router contained in the abstract TG role.
 The second line does the same thing for all local prefixes.
@@
 The final rule matches all other IP prefix destinations and allows traffic to follow a path that leaves the datacenter through either of its peers (Peer1 or Peer2) with a preference for leaving through Peer1.
-The \Prefer~ symbol indicates that traffic should satisfy the constraint on the left whenever possible, and only resort to the backup (right) when this is not possible due to failures.%
+The \Prefer~symbol indicates that traffic should satisfy the constraint on the left whenever possible (\IE, a path exists in the network), and only resort to the backup (right) when this is not possible due to failures.%
 
 Next we can capture the constraint that traffic for local prefixes must stay local to the datacenter.
-We do this with the following \sysname code:
+We do this with the following \sysname constraint:
 %
@@
 \Define Locality = 
-    \$PL \Path \Always(\In)
+    \$LP \Path \Always(\In)
 \end{code}
@@
 %
-The Locality constraint applies to any traffic destined for a local prefix described by the \$PL prefix template variable and adds the constraint that the traffic must follow a path that matches an internal location (\IE, a router inside the datacenter) at each hop of the path.
+The Locality constraint applies to any traffic destined for a local prefix described by the \$LP prefix template variable and adds the constraint that the traffic must follow a path that matches an internal location (\IE, a router inside the datacenter) at each hop of the path.
 This prevents traffic from ever entering from or leaving through an external peer.
@@
 This tells \sysname to find BGP router configurations that satisfy the conjunction of the Routing and Locality constraints.
-It also declares an additional constraint that we want to perform aggregation for global prefixes by summarizing them as the more general prefix PG at the border of the datacenter (\IE along any edge starting inside our datacenter and ending at a peer outside the datacenter).
+It also declares an additional constraint that we want to perform prefix summarization (as PG) for global prefixes at the border of the datacenter (\IE, along any edge starting inside our datacenter and ending at a peer outside the datacenter).
 
 When \sysname compiles the above policy, it guarantees that the forwarding behavior of the network will be correct for any concrete instantiation of the abstract network, and for any combination of failures that may occur in the concrete network.
-Furthermore, \sysname will generate configurations in such a way that, if we want to expand our network, for example by adding additional spine routers as in figure~\ref{fig:example2}, then the expansion can be performed incrementally (\IE, only configurations for routers local to the expansion will need to change).
+Furthermore, \sysname will generate configurations in such a way that, if we want to expand our network, for example by adding or removing a spine routers as in figure~\ref{fig:example2}, then the expansion can be performed by only ever touching device configurations that are adjacent to the change.
 
@@
 For example, an operator may require a certain level fault tolerance between between different collections of routers.
-Importantly, such analysis depends, not only on the network topology, but also on the underlying routing policy.
+Such analysis depends, not only on the network topology, but also on the underlying routing policy, both of which \sysname has access to.
 To this end, we develop a sound analysis over abstract topologies to answer questions about the number of disjoint paths between pairs of nodes.
 
-Suppose we want to find a worst-case lower bound on the number of disjoint paths between any global tor and spine router from figure~\ref{fig:example3} after applying the routing policy.
-This would give us a bound on the fault tolerance for, not only the current datacenter, but any sound expansion of it.
-Furthermore, this can be used as a lightweight verification tool to detect certain classes of configuration bugs.
-For example, since we are performing aggregation at the border of the datacenter, we might introduce what is known as an aggregation black hole if enough failures occur to disconnect a tor from a spine.
-
-The disjoint path analysis works in the following way.
+Suppose we want to find a worst-case lower bound on the fault tolerance between any global tor and spine router from figure~\ref{fig:example3} for any concrete topology after applying the routing policy.
+This can be used as a lightweight verification tool to detect certain classes of configuration bugs.
+For example, since the network is performing prefix summarization at the border of the datacenter, we might introduce a black hole after enough failures occur to disconnect a tor from a spine router.
+
+We develop a disjoint path analysis works in the following way.
 For each abstract role in the network, we learn invariants about the number of disjoint paths to routers in that role.
@@
 For example, the analysis would start with a fact of the form: $S_P S_{TG} (1,1)$.
-This means that, there is some group of nodes of size 1 in the TG role in some pod P such that each node has 1 disjoint path to it (and all such paths are edge-disjoint).
+This means that, there is some group of nodes of size 1 in the TG role in some pod P such that any initial node in the TG role has 1 disjoint path to it (and all such paths are edge-disjoint).
 Since we know that the each node in the TG role is in a full mesh with nodes in the AG role within any given pod, we might infer a fact for AG of the form: $S_P A_{AG}(e1,1)$.
-This says that any group of nodes of size e1 in the AG role is reachable with at least 1 edge-disjoint path to each such node.
-%
-If we run the abstract analysis over the abstract network from figure~\ref{fig:example3} the analysis will learn a fact of the form $A_{S}(1,2)$, which means that any single spine node is reachable via 2 disjoint paths from any global tor node \ryan{it will actually be 1, we need to add a constraint on e1}.
+This says that any group of nodes of size e1 in the AG role is reachable with at least 1 edge-disjoint path to each such node from any initial node in the TG role.
+%
+If we run the abstract analysis over the abstract network from figure~\ref{fig:example3} the analysis will learn a fact of the form $A_{S}(1,2)$, which means that any single spine node is reachable via 2 disjoint paths from any initial global tor node \ryan{it will actually be 1, we need to add a constraint on e1}.
 
@@
 This adds a constraint that applies to all traffic and prevents valleys by defining each level in the datacenter.
-Because the abstract analysis is policy sensitive, if we were to run the it with the same abstract topology but the new routing policy, it would only be able to infer that there is a single disjoint path to any given spine router in the worst case.
+Because the abstract analysis is policy sensitive, if we were to run it again with the same abstract topology but the new routing policy, it would only be able to infer that there is a single disjoint path to any given spine router in the worst case.
 In fact this is exactly the case for the concrete network from figure~\ref{fig:example2}.
@@
 
-\subsection{Topology Abstraction}
-
 \subsection{Product Graph}
@@
 
-\ryan{TODO: this was copied from previous paper for reference}
-
-For each regular expression $r_i$ in an RIR policy, we construct a DFA for the reversed regular expression.
-An automata for regular expression $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ consists of all abstract locations (\IE, routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
-%
-The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$.
-%
-The Product Graph is constructed as a tuple ($V'$, $E'$, $s$, $P$) with
+For each regular expression $r_i$ from $r_1 ~\Prefer~ ..
+~\Prefer~ r_k$, we construct a DFA for the reverse of $r_i$.
+An automaton for $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
+The alphabet $\Sigma = G^A$ is the set of topology locations, $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+%
+The Product Graph is a tuple ($V'$, $E'$, $s$, $P$) with
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
@@
 
-For a Product Graph vertex $n = (l, \dots) \in V'$, we say that $n$ is a \emph{shadow} of topology location $l$.
-We also write $\tilde{n} = l$ to indicate that the topology location for node $n$ is $l$.
-When two PGIR nodes $m$ and $n$ shadow the same topology location (\IE, $\tilde{m} = \tilde{n}$), we write $m \approx n$.
-
 \ryan{TODO: this was copied from previous paper for reference}
 
-\para{From RIR To PGIR}
-
-Let $a_i$ and $b_i$ denote states in the regular policy automata.
-The PGIR is constructed by adding an edge from $m = (l_m, a_1, \dots, a_k)$ to $n = (l_n, b_1, \dots, b_k)$ whenever $\sigma_i(a_i, l_n) = b_i$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
+The Product Graph is constructed by adding an edge from state $m = (l_m, a_1, \dots, a_k)$ to $n = (l_n, b_1, \dots, b_k)$ whenever $\sigma_i(a_i, l_n) = b_i$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
 %
@@
 We write $(m \leq_{rank} n)$ if either $P(m) = P(n) = \emptyset$ or $min ~ P(m) \leq min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.
+%
+For a Product Graph if vertex $m,n = (l, \dots) \in V'$, we say that $m$ and $n$ are shadows, written: $m \approx n$.
 
@@
 In this example, all routes that eventually leave through Peer1 will lead to an accepting state for the first automaton and all routes that eventually leave through Peer2 will lead to an accepting state for the second automaton.
-Note that the translation from the topology to the Product Graph preserves the graph homomorphism property.
-\ryan{TODO: explain this more formally}
 
@@
 \begin{easylist}[itemize]
-& homomorphism between graphs + node/edge constraints
 & First show how to compile to the Product Graph, and from there to the ABGP
@@
   and how it holds for both.
-&& Next define the concretization & subst. functions for translating the abstract policy
+& Next define the concretization & subst. functions for translating the abstract policy
    into the concrete policy, using the ABGP example for reference
-&& Theorem: if safety analysis holdls in the abstract graph, it holds for the concrete one,
+& Lemma: if safety analysis holdls in the abstract graph, it holds for the concrete one,
    and the preferences are consistent.
-
 & Give abstraction theorem: commuting of concretization and compilation

### 2016-11-02 paper/abstraction/paper.tex
intro edits

@@
 \newcommand{\sysnamesec}{{\sf Methane}\xspace}
+\newcommand{\propane}{{\small \sf Propane}\xspace}
 
@@
 
-\section{Introduction}
-\label{sec:introduction}
+\section{Outline/Notes}
 
@@
 %=====================================================
+
+\section{Introduction}
+\label{sec:introduction}
+
+% Hence, one approach to improving network
+% reliability is to develop better languages for network configuration.
+% Such languages should be defined at a higher level of abstraction than
+% existing configuration languages and provide support built-in support for
+% verification of important properties, thereby avoiding entire classes
+% of configuration errors automatically.
+
+An important class of networks are the large \emph{structured networks}
+commonly deployed in industrial data centers.  These networks run
+many critical services and every second of downtime is at best
+costly and at worst dangerous.  Unfortunately, it is an enormous 
+challenge to keep these complex networks up and
+running 24/7~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
+Moreover, while hardware faults, rodents, power failures and natural
+disasters can all cause significant downtime, studies have shown that
+\emph{human error}, which occurs during network configuration or
+update, is the single large cause of these
+outages~\cite{juniper-study}.
+
+% These networks often
+% host a myriad of services and every second of downtime imposes significant
+% financial cost or disruption to consumers.  
+Such networks typically have uniform, tree-shaped topologies that involve
+hundreds or even thousands of devices.  Since it is not possible for humans
+to think about configuring each individual device independently, 
+network operators typically classify the devices, assigning them a particular
+\emph{role} such as ``top-of-rack switch'' or ``tier-one aggregation switch.''
+Each such role is codified as a \emph{configuration template}---essentially
+a macro that may be instantiated with different concrete values to
+generate a configuration for each device that plays the role.
+
+Such templates have no particular semantics other than the semantics
+that one obtains from instantiating a template's parameters.  Moreover,
+template construction is a manual process:  network engineers do their
+best to design templates by hand that will work effectively in the context 
+of their particular network topology.  However, there is no support for
+validating key properties such as connectivity and fault tolerance, 
+aside from instantiating the templates and testing.  In addition,
+network engineers have no tools to help them design for network
+evolution.  For instance, the process of adding new equipment to
+expand the capacity of data center may not be compatible with the original
+templates, or may cause a trickle-down of changes to be made network-wide.
+Unfortunately, each change to a router configuration typically incurs
+some risk of temporary instable in a network, so minimizing such changes
+is an important design goal.  It is no wonder that a major
+network outage, such as the one that grounded all United Air flights
+in July 2015~\cite{x}, makes international news every few months.
+
+To combat these problems, in this paper, we present \sysname, a 
+new high-level language designed to 
+provide improved support for the configuration of large, structured networks.
+\sysname allows network operators to define abstract network topologies that
+classify devices in terms of abstract roles and specify the connectivity
+invariants satisfied by each role.  For instance, a programmer may
+define separate roles for ``top-of-rack switch'' and 
+``tier-one aggregation switch'' and specify that every top-of-rack switch
+is connected to at least two different tier-one aggregation switches.
+
+In order to specify \emph{routing policy} for such abstract networks,
+\sysname borrows notation from the recently-defined \propane
+programming language~\cite{propane}.  However, whereas \propane policies
+refer to individual devices, \sysname policies allows users to
+refer to abstract roles.  The \sysname compiler compiles these role-based
+policies into templates, with one template per role, and these templates
+may be instantiated to generate concrete configurations.
+
+During compilation, the \sysname compiler also analyzes policy with respect to the
+abstract topology and guarantees that the configurations will 
+faithfully implement the high-level policy on \emph{any} concrete
+topology that satisfies the given connectivity invariants.  The compiler
+will also optionally perform a second fault tolerance analysis that 
+determines the minimum number of link failures required to disconnect
+\emph{any} concrete topology that once again satisfies the connectivity
+invariants.
+
+Finally, generated \sysname configurations are designed to
+be \emph{evolution-friendly} in the sense that if an operator adds or
+removes any single link or device, they are guaranteed that only 
+the configurations of adjacent devices need change (for instance, to
+activate a port on which the new device is connected).  Doing so
+helps minimize network instability as data centers are expanded or devices are
+temporarily taken offline for maintenance.
+
+As an aside, a pleasant side effect of this new compiler
+infrastructure, designed to make life easier on network operators, is
+that for structured networks, it scales substantially better than its
+competitor \propane does: as the number of individual devices in a
+network grows, the number of distinct roles will often stay constant.
+Consequently, the \sysname compiler may be two orders of magnitude
+faster than \propane for large structured networks.
+
+To summarize, the central contribution of this paper are:
+
+\begin{enumerate}
+\item Design of new network topology abstraction mechanisms involving roles and
+connectivity invariants.
+\item Design of two new algorithms for analyzing abstract networks: one which
+guarantees correct compilation and one which determines fault tolerance 
+properties of network policy.  Both algorithms provide guarantees for any 
+concrete network satisfying the abstract connectivity invariants.
+\item Design of template generation algorithms that support network
+evolution with minimal change to existing devices.
+\item Implementation and evaluation of a \sysname compiler that generates 
+configuration templates and is up to two orders of magnitude faster 
+than its closest competitor on large networks.
+\end{enumerate}
+
+%% Indeed, over the last several years, many researchers have begun to
+%% develop such languages~\cite{frenetic,pyretic,pane,nettle,netkat}.
+%% However, the bulk of this research has targeted software-defined
+%% networks (SDN), a new networking technology that has emerged over the last
+%% decade.  Unfortunately, the vast majority of today's networks
+%% continue to use traditional networking techology---upgrading to SDN is
+%% expensive and technically challenging.
+
+%% In a traditional network, every router runs an independent instance of 
+%% a distributed protocol that
+%% exchange messages about available routes to destination addresses.  
+%% Each router is configured independently, but the overall behavior
+%% of the network---the paths from one server to another, for instance---depend
+%% upon the
 

### 2016-11-02 paper/abstraction/paper.tex
stashing changes

@@
 
+\newcommand{\state}[4]{\node[state,#3](#1)[#4]{#2};}
+\newcommand{\transition}[4]{\path[->] (#1) edge [#4] node {#3} (#2);}
+
+\begin{figure*}[t!]
+  \begin{minipage}[t]{.2\linewidth}
+  \hdr{Policy Automata}{}
+    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
+      \state{0}{$0$}{              }{}
+      \state{1}{$1$}{right of=0}{accepting}
+      \transition{0}{0}{out}{loop above}
+      \transition{0}{1}{Peer1}{}
+      \transition{1}{1}{in}{loop above}
+    \end{tikzpicture}
+
+    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
+      \state{0}{$0$}{              }{}
+      \state{1}{$1$}{right of=0}{accepting}
+      \transition{0}{0}{out}{loop above}
+      \transition{0}{1}{Peer2}{}
+      \transition{1}{1}{in}{loop above}
+    \end{tikzpicture}%
+  \end{minipage}
+  %
+  ~~~~~~
+  %
+  \begin{minipage}[t]{.4\linewidth}
+    \hdr{Concrete Topology}{}
+    \includegraphics[width=.7\columnwidth]{figures/topology-con}
+  \end{minipage}%
+  %
+  \begin{minipage}[t]{.4\linewidth}
+    \hdr{Abstract Topology}{}
+    \includegraphics[width=.57\columnwidth]{figures/topology-abs}
+  \end{minipage}%
+
+  \vspace{2em}
+  \begin{minipage}[t]{.6\linewidth}
+    \hdr{Concrete Product Graph}{}
+    \includegraphics[width=.9\columnwidth]{figures/pg-con}
+  \end{minipage}%
+  \begin{minipage}[t]{.4\linewidth}
+  \hdr{Abstract Product Graph}{}
+    \includegraphics[width=.9\columnwidth]{figures/pg-abs}
+
+  \end{minipage}%
+
+  \hrulefill
+  \vspace*{.4em}%
+
+  \caption{Product graph construction for policy $true \Path \Exit(\text{Peer1} \Prefer \text{Peer2})$.}
+  \label{fig:example-compilation}
+  %\vspace{-1em}
+\end{figure*}
+
+\subsection{Product graph distributed configurations}
+
+The translation from the Product Graph to per-device configurations that run the distributed BGP protocol consists of 2 steps.
+The first step is to generate per-device BGP import and export filters based on the edges in the Product Graph.
+The idea is to attach a tag to every route advertisement that routers send to their neighbors that encodes the current state of the automata.
+For example...
+\ryan{show example here}.
+This ensures that BGP will only find paths that exist in the Product Graph, and are thus allowed by the policy.
+
+The second step is to find, for each router, a total ordering of Product Graph neighbors that tells it which advertisements to prefer in the routing protocol to others.
+In general, because BGP is distributed, each router does not have a full picture of the entire network when choosing which path to use.
+It is therefore possible for a router to choose a path that results in a less preferred network-wide path even though a better one is available in the network.
+In general, finding a collection of preferences to ensure correct end-to-end paths for all failures is a hard problem.
+The Propane tool introduced a conservative, yet effective algorithm for determining route preferences based on the following simulation relation:
+
 \subsection{Substitution Theorem}
@@
 
-\newcommand{\state}[4]{\node[state,#3](#1)[#4]{#2};}
-\newcommand{\transition}[4]{\path[->] (#1) edge [#4] node {#3} (#2);}
-
-\begin{figure*}[t!]
-  \begin{minipage}[t]{.2\linewidth}
-  \hdr{Policy Automata}{}
-    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
-      \state{0}{$0$}{              }{}
-      \state{1}{$1$}{right of=0}{accepting}
-      \transition{0}{0}{out}{loop above}
-      \transition{0}{1}{Peer1}{}
-      \transition{1}{1}{in}{loop above}
-    \end{tikzpicture}
-
-    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
-      \state{0}{$0$}{              }{}
-      \state{1}{$1$}{right of=0}{accepting}
-      \transition{0}{0}{out}{loop above}
-      \transition{0}{1}{Peer2}{}
-      \transition{1}{1}{in}{loop above}
-    \end{tikzpicture}%
-  \end{minipage}
-  %
-  ~~~~~~
-  %
-  \begin{minipage}[t]{.4\linewidth}
-    \hdr{Concrete Topology}{}
-    \includegraphics[width=.7\columnwidth]{figures/topology-con}
-  \end{minipage}%
-  %
-  \begin{minipage}[t]{.4\linewidth}
-    \hdr{Abstract Topology}{}
-    \includegraphics[width=.57\columnwidth]{figures/topology-abs}
-  \end{minipage}%
-
-  \vspace{2em}
-  \begin{minipage}[t]{.6\linewidth}
-    \hdr{Concrete Product Graph}{}
-    \includegraphics[width=.9\columnwidth]{figures/pg-con}
-  \end{minipage}%
-  \begin{minipage}[t]{.4\linewidth}
-  \hdr{Abstract Product Graph}{}
-    \includegraphics[width=.9\columnwidth]{figures/pg-abs}
-
-  \end{minipage}%
-
-  \hrulefill
-  \vspace*{.4em}%
-
-  \caption{Product graph construction for policy $true \Path \Exit(\text{Peer1} \Prefer \text{Peer2})$.}
-  \label{fig:example-compilation}
-  %\vspace{-1em}
-\end{figure*}
-
 %=====================================================
@@
 \label{sec:analysis}
-
-%The examples above use what we call the front end (FE) of \sysname.
-%It simplifies operators' task of describing preferred paths, but that simplicity comes at the cost of compilation complexity.
-The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology and ensure policy compliance under all failure scenarios.%
-
-%\begin{figure}[t!]
-%  \centering
-%  \includegraphics[width=.75\columnwidth]{figures/pipeline}
-%  \caption{Compilation pipeline stages for Propane.}
-%  \label{fig:pipeline}
-%  \vspace{-1em}
-%\end{figure}%
-
-%To handle these challenges, we decompose compilation into multiple stages, shown in  Figure~\ref{fig:pipeline}, and develop efficient algorithms for the translation between stages.
-The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR).
-Policies in RIR are checked well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the topology to obtain the Product Graph Intermediate Representation (PGIR).
-The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions.
-We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes.
-Once the compiler determines safety, it translates the PGIR to an abstract BGP (ABGP) representation.
-ABGP can then be translated into various vendor-specific device
-%configurations as needed.
-
-%The \sysname FE is just a thin layer atop the RIR for describing preference-based path constraints.
-%Figure~\ref{fig:rir-syntax} shows the RIR syntax.
-A policy has one or more constraints.
-The first kind of constraint is a test on the type of route and a corresponding set of preferred regular paths.
-Regular paths are regular expressions where the base characters are abstract locations representing either a router or an external AS.
-Special \In{} and \Out{} symbols refer to any internal or external location respectively.
-In addition, $\Sigma$ refers to any location.
-We also use the standard regular expression abbreviation $r^+$ for $r \cdot r^*$, a sequence of one or more occurrences of $r$.
-Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisements with a particular community value attached (\IE, an integer value associated with a path).%
-%
-
-%\sysname also supports constraints on the control-plane behavior of BGP.
-For example, prefix aggregation is an important optimization to reduce routing table size.
-A constraint of the form $agg(x,ln)$ tells the compiler to perform aggregation for prefix $x$ across all links described by $ln$.
-It is also often useful to be able to add community tags to exported routes in BGP (\EG, to communicate non-standard information to peers).
-A constraint of the form $tag(d,t,ln)$ adds community tag $d$ for any prefixes matching $t$ across links $ln$.
-%%
-%We list only the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, but \sysname also supports other constraints such as limiting the maximum number of routes allowed between ASes, or enabling BGP multipath.
 
@@
 
-%\para{From FE to RIR}
-
-%The first stage in \sysname compilation reduces the FE to the simpler RIR from Figure~\ref{fig:rir-syntax}.
-%The main differences between the FE and RIR are: $i)$ FE allows the programmer to specify constraints using a series of (modular) definitions, and combine them later, $ii)$ FE provides high-level names that abstract sets of routes and groups of prefixes/neighbors, and $iii)$ FE allows the preference operator to be used more flexibly.%
-
-%A key constraint when translating FE to RIR is ensuring that all specified routes are well-formed.
-In particular, each regular path constraint $r$ must satisfy $r \subseteq \Out^* \cdot \In^+ \cdot \Out^*$.
-It ensures that users only control traffic that goes through their network at some point, and that such traffic does not loop back multiple times through their network.%
-
-%The translation from FE to RIR is based on a set of rewriting rules.
-%The first step merges separate constraints.
-It takes the cross product of per-prefix constraints, where logical conjunction ($r_1 ~\AND~ r_2$) is replaced by intersection on regular constraints ($r_1 \Intersect r_2$), logical disjunction is replaced by union, and logical negation ($\NOT r$) is replaced by path negation ($\Any \cap \NOT(r)$).
-The additional constraint $\Any$ ensures the routes are well-formed by restricting the paths to only those that go through the user's network.
-%%
-%For example, in the datacenter FE configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:%
-
-%\begin{code}
-%PG1 \Path \End(A)
-%PG2 \Path \End(B)
-%PL1 \Path \textbf{only}(\In) \Intersect \End(E)
-%PL2 \Path \textbf{only}(\In) \Intersect \End(F)
-%\True \Path \Exit(\Out)
-%\end{code}%
-
-%The next step rewrites the high-level constraints such as $\Exit$ according to the equivalences in Figure~\ref{fig:rir-syntax}.
-Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression.
-For example, the regular expression $r \cdot (s ~\Prefer~ t) \cdot u$ is lifted to $(r \cdot s \cdot u) \Prefer (r \cdot t \cdot u)$ by distributing the preference over the sequence operator.
-In general, we employ the following distributivity equivalences:
-%%
-%\[
-%\begin{array}{c}
-%  r \odot (s_1 \Prefer \dots \Prefer s_n) = (r \odot s_1) \Prefer \dots \Prefer (r \odot s_n) \\
-%  (s_1 \Prefer \dots \Prefer s_n) \odot r = (s_1 \odot r) \Prefer \dots \Prefer (s_n \odot r)
-%\end{array}
-%\]
-%%
-%where $\odot$ stands for an arbitrary regular binary operator, and $r$ is a policy with a single preference.
-%%
-%In cases where $r$ does not contain a single preference, such as $(s ~\Prefer~ t) \cdot (u ~\Prefer~ v)$, it is not clear which of the paths $s \cdot v$ or $t \cdot u$ is preferred.
-\sysname rejects such ambiguous policies, requiring instead that operators explicitly specify which paths to prefer --- for example as $(s \cdot u) ~\Prefer~ (s \cdot v) ~\Prefer~ (t \cdot u) ~\Prefer~ (t \cdot v)$.
-%%
-%Policies that contain preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) are also rejected by \sysname as invalid.
-
-%\subsection{Product graph IR}
-
-%Now that the user policy exists in a simplified form, we must consider the topology.
-In particular, we want a compact representation that describes all the possible ways BGP route announcements can flow through the network subject to the policy and topology constraints.
-The PGIR captures these constraints by ``intersecting" each of the regular automata corresponding to the RIR path preferences with the topology.
-Paths through the PGIR correspond to real paths through the topology that satisfy the user constraints.
-
-%\para{Formal definition}
-
-%While paths in an RIR policy describe the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated --- route announcements flowing in the opposite direction.
-To capture this idea, for each regular expression $r_i$ in an RIR policy, we construct a deterministic finite state machine for the reversed regular expression.
-An automata for regular expression $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ consists of all abstract locations (\IE, routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
-%%
-%The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$.
-%%
-%The combined PGIR is a tuple ($V'$, $E'$, $s$, $e$, $P$) with
-%vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
-%edges $E' \colon V' \times V'$,
-%a unique starting vertex $s$,
-%a unique ending vertex $e$,
-%and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of path ranks.%
-
-%For a PGIR vertex $n = (l, \dots) \in V'$, we say that $n$ is a \emph{shadow} of topology location $l$.
-We also write $\tilde{n} = l$ to indicate that the topology location for node $n$ is $l$.
-When two PGIR nodes $m$ and $n$ shadow the same topology location (\IE, $\tilde{m} = \tilde{n}$), we write $m \approx n$.%
-
-%Throughout the remainder of the paper, we will use the convention that metavariables $m$ and $n$ stand for PGIR nodes and $l$ stands for a topology location.
-Capital letters like $X$ refer to concrete topology locations, while capital letters with subscripts such as $X_1$ and $X_2$ refer to concrete PGIR nodes that share a topology location (\IE, $\tilde{X_1}$ = $\tilde{X_2} = X$).
-
-%\para{From RIR To PGIR}
-
-%Let $a_i$ and $b_i$ denote states in the regular policy automata.
-%The PGIR is constructed by adding an edge from $m = (l_m, a_1, \dots, a_k)$ to $n = (l_n, b_1, \dots, b_k)$ whenever $\sigma_i(a_i, l_n) = b_i$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
-%%
-%Additionally, we add edges from the start node $s$ to any $n = (l, a_1, \dots, a_k)$ when $\sigma_i(q_{0_i}, l) = a_i$ for each $i$.
-%%
-%The preference function $P$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $. That is, it records the path rank of each automaton that has reached a final state.
-%%
-%Finally, there is an edge from each node in the PGIR such that $P(n) \neq \emptyset$ to the special end node $e$.
-We write $(m \leq_{rank} n)$ if either $P(m) = P(n) = \emptyset$ or $min ~ P(m) \leq min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.%
-%
-
-%Intuitively, the PGIR tracks the policy states of each automaton as route announcements move between locations.
-%%
-%Consider the topology in Figure~\ref{fig:example-compilation}.
-Suppose we want a primary route from neighbor W that allows traffic to enter the network at $A$ and utilize the C--D link before leaving the network (through $X$ or $Y$).
-As a backup, we also want to allow traffic to enter the network from $B$, in which case the traffic can also utilize the C--E link before leaving the network.
-For simplicity, we assume that the route ends in either $X$, $Y$, or $Z$.
-The RIR for the policy could be written as:
-%%
-%$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$$
-%%
-%Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
-%%
-%The figure also shows the PGIR after intersecting the topology and policy automata.
-Every path in the PGIR corresponds to a concrete path in the topology.
-In particular, every path through the PGIR that ends at a node $n$ such that the preference function $P(n) = \set{i_1, \dots, i_k}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_k$.
-%%
-%For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining a path with the lowest (best) rank of $1$.
-%BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
-This possibility is reflected in the product graph by the node with state $(X,1,1)$.
-From here, if X were to advertise this route to D, it would result in the path $D \cdot X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
-%%
-%The ``--" state indicates the corresponding automaton cannot accept the current path or any extension of it. Since
-%node $(W,5,-)$ is in an accepting state for the first automaton, it indicates that this path has rank 1.
-
-%\subsection{Failure-safety analysis}
-
-%To implement path preferences in routing, BGP uses local preferences on a per-device basis.
-However, the distributed nature of BGP makes setting preferences locally to achieve a network-wide routing policy difficult.
-This task becomes even more challenging in the presence of failures since routers running BGP lack a global view of the network.
-
-%\para{An illustrative example}
-
-%To demonstrate the difficulty of generating device-local preferences, consider the simple policy for the topology in Figure~\ref{fig:unimplementable}, which says to prefer the top path over the bottom path:
-%%
-%$(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G})  \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$.
-%%
-%How could such a policy be implemented in BGP?
-Suppose we set the local preferences to have $D$ prefer $E$ over $F$, and have $A$ prefer $B$ over $C$.
-This works as expected under normal conditions, however, if the A--B link fails, then suddenly $D$ has made the wrong decision by preferring $E$.
-Traffic will now follow the
-%$A \cdot C \cdot D \cdot E \cdot G$ path, even though this path was not allowed by the policy.
-Thus, the distributed implementation has used a route that is not allowed by the policy.
-To make matters worse, the second preference for the path $A \cdot C \cdot D \cdot F \cdot G$ is available in the network but not being used.
-Thus, a path for the best possible route available after the A--B failure exists in the network, but the distributed implementation will not find it.
-%%
-%The first problem could be fixed by tagging and filtering route advertisements appropriately so that $C$ rejects routes that go through $E$, however the second problem cannot be fixed.
-In fact, this policy cannot be implemented in BGP in a way that is policy compliant under all failures since $D$ cannot safely choose between $E$ and $F$ without knowing whether the A--B link is available.
-
-%\para{Problem formulation}
-
-%The problem of determining local preferences for each router is reflected in the structure of the PGIR.
-Whenever a given router appears as multiple shadow nodes in the PGIR, the compiler must decide which shadow to prefer.
-%%
-%In the example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in shadow $(C,-,2)$ or from $D$ in shadow $(C,3,2)$.
-%%
-%%
-%The compiler must determine a \emph{total ordering} of shadow nodes for each router, which reflects the relative preference of advertisements received in each shadow and should be consistent with path ranks.
-%%
-%For example, if $C$'s shadow $(C,3,2)$ can be preferred to $(C,-,2)$, written as $(C,3,2) \leq_{lp} (C,-,2)$, $C$ can prefer advertisements from $(D,2,2)$ over $(E,-,2)$.
-$D$ and $E$ tag their advertisements to let $C$ know which shadow sent the advertisement.
-Section \ref{sec:abgp} discusses tagging in detail.
-
-%\begin{figure}[t!]
-%  \centering
-%  \includegraphics[width=.5\columnwidth]{figures/unimplementable}
-%  \caption{A network where the policy $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
-%  \label{fig:unimplementable}
-%  %\vspace{-1em}
-%\end{figure}
-
-%\para{Regret-free preferences}
-
-%To order PGIR shadows ($\leq_{lp}$) for each router in a way that is policy-compliant under all failures, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
-A router (location) $l$ has a regret-free preference for a set of advertisements $A$ over $B$ if, whenever $l$ selects an advertisement to destination $d$ from $A$ over another from $B$, there is always some policy-compliant path to $d$ that is at least as good ($\leq_{rank}$ for the final node along the path) as any possible path (not necessarily from $l$) to $d$ if $l$ had selected an advertisement from $B$ instead.
-In other words, the preference of $A$ over $B$ at $l$ is regret-free if $l$ is never (under any failure) worse-off by choosing an advertisement from $A$ when available.
-The notion of regret-free preferences can be lifted to PGIR nodes by considering the set of advertisements available to each node.%
-
-%In the example of Figure~\ref{fig:example-compilation}, the choice for $C$ to prefer shadow $(C,3,2)$ to $(C,-,2)$ is regret-free, since there will always be at least as good a path to destination $W$ regardless of any failures that might occur in the network.
-For example, if the $C$--$A$ link fails, then there is still a backup path from $(C,3,2)$ to $(W,-,4)$ that is just as good as any path from $(C,-,2)$.
-Likewise, any combination of failures to disconnect $(C,3,2)$ from $(W,-,4)$ would also disconnect $(C,-,2)$ from $(W,-,4)$.
-
-%\para{A preference inference algorithm}
-
-%Searching for precise regret-free preferences in general is hard, and clearly enumerating all possible combinations of failures and preference orderings is intractable.
-We thus adopt a conservative analysis that we found to be effective and efficient in practice.
-The idea is to $i)$ search for regret-free preferences by comparing the set of paths available after accepting advertisements in two different PGIR shadows $N_1$ and $N_2$ of topology node $N$, and $ii)$ refine the comparison when necessary by considering where the announcements must have traversed before arriving at $N_1$ or $N_2$.
-
-%\begin{algorithm}[t!]
-%\caption{Inferring regret-free preferences}
-%\label{alg:failures}
-%\begin{algorithmic}[1]
-%\Procedure{Regret-free($G$, $N_1$, $N_2$)}{}
-%  \If {$N_1 \not\approx N_2$} \Return false
-%  \EndIf
-%  \State $q \gets Queue()$
-%  \State $q.Enqueue (N_1, N_2)$
-%  \While {$!q.Empty()$}
-%    \State $(m,n) \gets q.Dequeue()$
-%    \If {$m \nleq_{rank} n$}
-%      \Return false
-%    \EndIf
-%    \For {$n'$ in adj($G$, $n$)}
-%      \If {\big($\exists m' \in \textup{adj}(G,m), m' \approx n'$\big)}
-%        \If {$(m',n')$ not marked}
-%          \State {mark $(m',n')$ as seen}
-%          \State $q.Enqueue(m',n')$
-%        \EndIf
-%      \Else { \Return $false$}
-%      \EndIf
-%    \EndFor
-%  \EndWhile \\
-%  \hspace{\algorithmicindent} \Return true
-%\EndProcedure
-%\end{algorithmic}
-%\end{algorithm}
-
-%Algorithm~\ref{alg:failures} checks whether one shadow can be preferred to another ($N_1 \leq_{lp} N_2$).
-It walks from nodes $N_1$ and $N_2$ and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, also take a step to an equivalent topology location $(\approx)$.
-When there is no such equivalent step, the algorithm attempts to take into account where the advertisement must have already traversed.
-In particular, it checks if there is an equivalent dominator node and, if so, walks from this new node instead.
-%%
-%The idea is that, since the advertisement must have already passed through the dominator, we can check to see if we are guaranteed to find paths that are at least as good from this new node instead.
-%%
-%At each step, it requires that the current node reachable from $N_1$ has a path rank that is at least as good as that of the current node reachable from $N_2$ ($m \leq_{rank} n$).
-The intuition here is that if $m \nleq_{rank} n$, then we can very likely fail every edge in the topology except for the path that leads to the current $m$ and $n$, thereby generating a counterexample.
-%Algorithm~\ref{alg:failures} terminates since the number of related states $(m,n)$ that can be explored is finite.%
-
-%For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR shadows according to the $(\leq_{lp})$ relation determined by Algorithm~\ref{alg:failures}.
-If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
-
-%\para{Avoiding loops}
-
-%The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available due to loops rejected by BGP.%
-
-%Consider the partial product graph shown in Figure~\ref{fig:avoiding-loops}.
-Our preference inference algorithm will determine that node $X_1$ should be locally preferred to node $X_2$ since this will result in a better (lower ranked) path to destination $A$.
-However, when applying Algorithm~\ref{alg:failures}, we failed to take into account the possibility of loops.
-In particular, node $A_2$ may be unusable for advertisements that go through $X_1$ since the advertisement may have already gone through $A_1$ previously.
-In this case, $X$ will have made the wrong choice since preferring $X_2$ would have resulted in a better path for the destination $A$ (a path of rank 3 instead of 4).%
-
-%On the other hand, this would not have been a problem if paths ending at $A_1$ had a lower rank than those ending at $A_2$ or $A_3$.
-For example, if paths ending at $A_1$ had rank 1, then any time $A_2$ is unusable due to a loop with $A_1$, it ultimately does not matter since $A_1$ is preferred anyway.
-%%
-%In fact, checking if we are never worse off using $A_1$ instead of $A_2$ corresponds exactly with determining if $A$ has a regret-free preference for $A_1$ over $A_2$.
-%%
-%More specifically, the compiler checks that, any time there are two shadows $N_1$ and $N_2$ for the same topology location, where $N_1$ appears ``above'' (\IE, can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (\IE, $N_1 <_{lp} N_2$).
-
 \subsection{Other properties}
@@
 \begin{easylist}[itemize]
-& Graph homomorphism is not enough -- to coarse an overapproximation
-&& Use node/edge multiplicites to capture more precise constraints on concrete topologies
-&& Show a bunch of examples of fattree, bcube, dcell, hyperX, facebook, google, F10, etc.
 & K-disjoint path analysis

### 2016-11-02 paper/abstraction/paper.tex
rewrite product graph formalization

@@
 
-\subsection{Abstract Synthesis}
-
-\sysname builds on the Propane network configuration synthesis tool, by supporting both synthesis for and reasoning over parameterized classes of topologies and their interactions with user-specified routing policy.
+\subsection{Abstract Compilation}
+
+\sysname builds on the Propane network configuration tool, by supporting both synthesis for and reasoning over parameterized classes of topologies and their interactions with user-specified routing policy.
 \sysname takes as input, (1) a topology abstraction in the form of a graph homomorphism annotated with logical constraints about node and edge mutliplicities, and (2) a domain-specific routing policy that consists of a mapping from predicates matching various classes of traffic, to a list of ranked constraints on the paths traffic matching the predicate should prefer to take through the network.
@@
 
-\section{Configuration Synthesis}
+\section{Compilation}
 \label{sec:compilation}
@@
 
-\ryan{TODO: this was copied from previous paper for reference}
-
-The Product Graph is constructed by adding an edge from state $m = (l_m, a_1, \dots, a_k)$ to $n = (l_n, b_1, \dots, b_k)$ whenever $\sigma_i(a_i, l_n) = b_i$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
-%
-Additionally, we add edges from the start node $s$ to any $n = (l, a_1, \dots, a_k)$ when $\sigma_i(q_{0_i}, l) = a_i$ for each $i$.
-%
-The preference function $P$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $. That is, it records the path rank of each automaton that has reached a final state.
-% in preferences are achieved from each policy automaton for every node in the product construction.
-%
-We write $(m \leq_{rank} n)$ if either $P(m) = P(n) = \emptyset$ or $min ~ P(m) \leq min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.
-%
-For a Product Graph if vertex $m,n = (l, \dots) \in V'$, we say that $m$ and $n$ are shadows, written: $m \approx n$.
+The Product Graph is constructed by adding an edge from state $m = (l_m, q_{m_1}, \dots, q_{m_k})$ to $n = (l_n, q_{n_1}, \dots, q_{n_k})$ whenever $\sigma_i(q_{m_i}, l_n) = q_{n_i}$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
+%
+We add edges from the start node $s$ to any $m = (l, q_{m_1}, \dots, q_{m_k})$ when $\sigma_i(q_{0_i}, l) = q_{m_i}$ for each $i$.
+%
+The preference function $P(m)$ denotes the rank of paths through the Product Graph ending at node $m$ and is defined as $P(m) = \set{i~\vert~q_{m_i} \in F_i}$. 
+%
+We write $(m \leq_{rank} n)$ if $P(m) = \emptyset$ or $\min ~ P(m) \leq \min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.
+%
+We write $m \approx n$ whenever two vertices $m,n = (l, \dots) \in V'$ share the same topology location $l$.
 

### 2016-11-03 paper/abstraction/paper.tex
update preference inference section

@@
 \newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}%
+
+\newtheorem{thm}{Theorem}[section]
+\newtheorem{defn}{Definition}
+\newtheorem{lem}[thm]{Lemma}
 
@@
 
+\ryan{we may need to add notransit constraint to make the compilation section simpler}
+
 This tells \sysname to find BGP router configurations that satisfy the conjunction of the Routing and Locality constraints.
@@
 %
-We write $(m \leq_{rank} n)$ if $P(m) = \emptyset$ or $\min ~ P(m) \leq \min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.
+We write $worse(m,n)$ if $P(n) = \emptyset$ or $\min ~ P(m) \geq \min ~ P(n)$, which means that paths ending at PGIR node $m$ are worse (higher rank) than paths ending at $n$.
 %
@@
 
-The translation from the Product Graph to per-device configurations that run the distributed BGP protocol consists of 2 steps.
-The first step is to generate per-device BGP import and export filters based on the edges in the Product Graph.
+The translation from the Product Graph to per-device configurations that run the distributed BGP protocol involves several ideas.
+
+The first idea is to tag every protocol message with a BGP community value that relays the state of each automaton when advertising a route to a neighbor.
+Routers can then allow route advertisements that correspond to an edge in the Product Graph (\IE, from a neighbor with the correct state) and block those that don't.
+This ensures that any path computed by BGP will be a valid path in the Product Graph, and thus is allowed by the policy.
+For example, in the concrete Product Graph in figure~\ref{fig:example-compilation}, router $S1$ will allow a route advertisement from its neighbor $P1$ and also from neighbor $P2$.
+If it uses neighbor $P1$, then it will add the tag $(1,0)$ before informing its neighbors about its route.
+On the other hand, if it uses neighbor $P2$, then it will add the tag $(0,1)$ before informing its neighbors about the route.
+
+%The first step is to generate per-device BGP import and export filters based on the edges in the Product Graph.
 The idea is to attach a tag to every route advertisement that routers send to their neighbors that encodes the current state of the automata.
@@
 
-The second step is to find, for each router, a total ordering of Product Graph neighbors that tells it which advertisements to prefer in the routing protocol to others.
-In general, because BGP is distributed, each router does not have a full picture of the entire network when choosing which path to use.
-It is therefore possible for a router to choose a path that results in a less preferred network-wide path even though a better one is available in the network.
-In general, finding a collection of preferences to ensure correct end-to-end paths for all failures is a hard problem.
-The Propane tool introduced a conservative, yet effective algorithm for determining route preferences based on the following simulation relation:
+However, letting BGP find some allowed path is not enough.
+\sysname must ensure BGP always computes the \emph{best} path according to the user's preferences, even when failures occur.
+The second idea is to totally order advertisements each router might receive from neighbors in the Product Graph by preference.
+For example, to satisfy the policy that leaving through $\sf{P1}$ is preferred to leaving through $\sf{P2}$, router $S1$ should prefer a route it hears from $P1$ over one from $P2$.
+Similarly, router $A1$ should prefer routes tagged with $(1,0)$ over those tagged with $(0,1)$.
+
+In general, because BGP is distributed, each router does not have a full view of the entire network when choosing which path to use.
+Because finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem, Propane introduced a conservative, yet effective algorithm for determining route preferences based on the following observation about the structure of the Product Graph:
+
+\begin{defn}
+The product graph can be viewed as a labelled transition system where
+$m\overset{l}{\rightarrow}n$ if edge $(m,n) \in E'$ and $loc(n) = l$. We write $m \leq m'$ if $m$ simulates $m'$ with respect to the ``worse" relation on node rankings.
+\end{defn}
+
+We can assign BGP local preferences for the policy in the following way: Check if each router has a total order with respect to the simulation relation ($\leq$) for its corresponding Product Graph nodes.
+If so, then simply sort the nodes and prefer advertisements from peers of node $m$ over those of node $m'$ if $m' \leq m$.
+
+For example, in the concrete product graph we have $(S1,0,1) \leq (S1,1,0)$ but not the other way around.
+Therefore, advertisements received at $S1$ in state $(0,1)$ must be preferred to those received in state $(1,0)$.
+Observe also that in the abstract product graph, node $(S,0,1) \leq (S,1,0)$.
+This leads us the the following lemma:
+
+\begin{lem}
+\label{lem:preference}
+$m \leq m'$ in the concrete product graph iff $f(m) \leq f(m')$ in the abstract product graph under the lifted graph homomorphism $f$.
+\end{lem}
+
+Intuitively, Lemma~\ref{lem:preference} hints that we will be able to infer BGP local preferences over the abstract product graph rather than the concrete product graph.
 

### 2016-11-03 paper/abstraction/paper.tex
remove old outline

@@
 
-\section{Outline/Notes}
-
-\begin{easylist}[itemize]
-& Network configuration is difficult/error-prone. Operators think of policy at
-  a high level of abstraction, yet for implementations:
-&& Often configs must be decomposed device-by-device
-&& Often need to create reusable configurations for different topologies/policies
-&& Ensure different devices/networks kept consistent when policy changes
-
-& Current state of the art is to capture abstractions using parameterized
-  device templates. The same templates can then be reused across multiple
-  devices. Unfortunately, existing template systems have many limitations
-&& Templates often still require the operator to reason about network-wide
-   policy device-by-device.
-&& Templates do not provide any guarantees of configuration correctness,
-   instead requiring the operator to manually reason about forwarding for
-   any possible concrete network
-&&& In addition, operators must reason about possible network failures that
-    might arise in one concrete network versus another
-
-& To this end, we build a language called \sysname to simplify the operators task.
-&& \sysname allows the operator to define high-level network abstractions to reflect
-   the operator's mental model, and then to write a centralized routing policy over the
-   abstraction.
-&& We extend the \sysname intermediate graph-based representation to support abstract policies,
-   and show how to compile abstract \sysname policies to this representation.
-&& As a major use-case, we show how the compilation and failure-safety analysis
-   of the Propane configuration-synthesis tool can be extended over abstract topologies.
-&& We develop an abstract interpretation that operates over this graph representation and verifies
-   if properties, such as reachability or k-disjoint paths between two nodes, are guaranteed
-   to hold for any possible concrete instantiation of the network.
-&& Our major result is an abstraction theorem, which states that ...
-&& The result is that policies compiled with the Propane compiler to distributed configurations
-   are guaranteed to have correct forwarding behavior for any possible concrete instantiation
-   of the network, and for any possible combination of failures in the given concrete network.
-&&& Finally, we show how abstract compilation makes it possible to dramatically speed up compilation
-    time for the Propane policies, cite some numbers here ...
-\end{easylist}
-
-% Some useful citations from the previous paper listed below
-
-%It is well known that configuring networks is error
-%prone and that such errors can lead to disruptive
-%downtimes~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
-%For instance, a recent misconfiguration led to an hour-long, nation-wide outage for Time Warner's backbone network~\cite{time-warner}; and a major BGP-related incident makes international news every few months~\cite{bgpmon}.%
-
-%A fundamental reason for the prevalence of misconfigurations is the
-%semantic mismatch between the intended high-level
-%policies and the low-level configurations.
-%Many policies involve network-wide properties---prefer a certain neighbor,
-%never announce a particular destination externally,
-%use a particular path only if another fails---but configurations describe the behavior of
-%individual devices.
-%%
-%Operators must manually decompose network-wide policy into
-%device behaviors, such that policy-compliant behavior results from the distributed interactions of
-%these devices.
-%%
-%Policy-compliance must be ensured not only under normal
-%circumstances but also during failures.  The need to reason
-%about all possible failures exacerbates the challenge
-%for network operators.  As a result, configurations that work
-%correctly in failure-free environments have nonetheless been found to violate key
-%network-wide properties when failures occur~\cite{batfish}.%
-
-%To reduce configuration errors, operators are increasingly adopting an
-%approach in which common tasks are captured as parameterized templates~\cite{hatch,thwack}.
-%%
-%While templates help ensure certain kinds of consistency across devices,
-%they do not provide fundamentally different abstractions from existing configuration languages
-%or bridge the semantic divide between network-wide policies and device-level configuration.
-%Thus, they still require operators to
-%manually decompose policies into device behaviors.%
-
-%As a complementary approach, configuration analysis tools can help reduce misconfigurations by checking if low-level configurations match high-level policy~\cite{batfish,feamster+:rcc}.
-However, such tools cannot help operators with the challenging task of generating configurations in the first place.%
-
-%Software-defined networking (SDN) and its abstractions
-%are, in part, the research
-%community's response to the difficulty of maintaining policy
-%compliance through distributed device interactions~\cite{ethane}.
-%Instead of organizing networks around a distributed
-%collection of devices that compute forwarding tables through
-%mutual interactions, the devices are told how to
-%forward packets by a centralized controller. The controller is responsible for ensuring that the
-%paths taken are compliant with operator specifications.%
-
-%The centralized control planes of SDN, however, are not a panacea.
-%First, while many SDN programming systems~\cite{sdn-languages} provide effective \emph{intra}-domain routing
-%abstractions, letting users specify paths within their network,
-%they fail to provide a coherent means to specify \emph{inter}-domain routes.
-%Second, centralized control planes
-%require careful design and engineering to be robust to failures---one must ensure that all devices can communicate with the controller at all times, even under arbitrary failure combinations.
-Even ignoring failures, it is necessary for the control system to
-%scale to meet the demands of large or geographically-distributed networks,
-%and to react quickly
-%to environmental changes. For this challenge, researchers are exploring
-%multi-controller systems with interacting controllers, thus bringing back distributed
-%control planes~\cite{mccauley2013extending,onos} and their current programming difficulties.%
-
-%=====================================================
-%
-%
-%  **Motivation**
-%
-%
-%=====================================================
-
 \section{Introduction}
@@
 %% upon the
+
+%=====================================================
+%
+%
+%  **Motivation**
+%
+%
+%=====================================================
 

### 2016-11-03 paper/abstraction/paper.tex
stashing changes

@@
 \emph{role} such as ``top-of-rack switch'' or ``tier-one aggregation switch.''
-Each such role is codified as a \emph{configuration template}---essentially
-a macro that may be instantiated with different concrete values to
+Each such role is codified as a \emph{configuration template}---a macro 
+that may be instantiated with different concrete values to
 generate a configuration for each device that plays the role.
 
-Such templates have no particular semantics other than the semantics
-that one obtains from instantiating a template's parameters.  Moreover,
+Unfortunately, such templates have no particular semantics other than the 
+semantics
+that one obtains from instantiating a template's parameters.  
+\dpw{add blah blah about low-level, assembly language, device by device}
+Moreover,
 template construction is a manual process:  network engineers do their
-best to design templates by hand that will work effectively in the context 
+best to design templates that will work effectively in the context 
 of their particular network topology.  However, there is no support for
-validating key properties such as connectivity and fault tolerance, 
+validating key properties of an assembly of templates, such as connectivity 
+and fault tolerance, 
 aside from instantiating the templates and testing.  In addition,
@@
 templates, or may cause a trickle-down of changes to be made network-wide.
-Unfortunately, each change to a router configuration typically incurs
+Each change to a router configuration typically incurs
 some risk of temporary instable in a network, so minimizing such changes
@@
 
-To combat these problems, in this paper, we present \sysname, a 
+To combat these problems, we present \sysname, a 
 new high-level language designed to 
 provide improved support for the configuration of large, structured networks.
-\sysname allows network operators to define abstract network topologies that
-classify devices in terms of abstract roles and specify the connectivity
-invariants satisfied by each role.  For instance, a programmer may
+\sysname allows network operators to define \emph{abstract network topologies} 
+that
+classify devices in terms of their roles and how they are connected
+to one another.  For instance, a programmer may
 define separate roles for ``top-of-rack switch'' and 
 ``tier-one aggregation switch'' and specify that every top-of-rack switch
-is connected to at least two different tier-one aggregation switches.
-
-In order to specify \emph{routing policy} for such abstract networks,
+is connected to at least two different tier-one aggregation switches,
+thereby providing a degree of fault tolerance of one aggregation switch
+were to fail.
+
+To specify \emph{routing policy} for such abstract networks,
 \sysname borrows notation from the recently-defined \propane
-programming language~\cite{propane}.  However, whereas \propane policies
-refer to individual devices, \sysname policies allows users to
-refer to abstract roles.  The \sysname compiler compiles these role-based
+programming language~\cite{propane}.  As such, it is able to
+specify the paths that traffic should flow along at a high-level of
+abstraction.  However, whereas \propane policies
+refer to paths of individual devices, \sysname policies 
+refer to paths of abstract roles.  The \sysname compiler compiles such
 policies into templates, with one template per role, and these templates
@@
 
-To summarize, the central contribution of this paper are:
+To summarize, the central contributions of this paper are:
 
 \begin{enumerate}
-\item Design of new network topology abstraction mechanisms involving roles and
-connectivity invariants.
-\item Design of two new algorithms for analyzing abstract networks: one which
+\item Design of new topology abstractions involving roles and
+connectivity invariants for network programmers.
+\item Design of two new algorithms for analyzing routing policy over 
+abstract networks: one which
 guarantees correct compilation and one which determines fault tolerance 
@@
 \item Design of template generation algorithms that support network
-evolution with minimal change to existing devices.
+evolution.
 \item Implementation and evaluation of a \sysname compiler that generates 
@@
 
-\section{Motivation}
+\section{Background and Motivation}
 \label{sec:motivation}
@@
 
+\paragraph*{Background}  Traditional routers use 
+distributed protocols to exchange messages about available routes. 
+One such protocol is the Border Gateway Protocol (BGP).  BGP is the
+standard for inter-domain routing (the act of exchanging routing information 
+between independently-owned networks) and is also commonly used in
+data centers because it allows operators to define relatively flexible
+routing policy while also scaling effectively to large networks.
+When used within a data center, each router is configured with its own \emph{AS number},
+which identifies it.
+
+Each BGP message (also called a \emph{route announcement}) contains a 
+\emph{destination prefix}, such as 10.1.1.0/24,\footnote{An address
+such as 10.1.1.0 is 32 bits, with each of the four values representing 8 bits.  
+A prefix such
+as 10.1.1.0/24 denotes the set of addresses that begin with the first
+24 bits of 10.1.1.0, \IE, all addresses that begin with 10.1.1.} as well as an
+\emph{AS path}, such as XYZ (where each of X, Y and Z would be an AS number).  
+Such messages indicate that the set of addresses
+denoted by the prefix may be reached by following the path XYZ. 
+A BGP message may also contain additional attributes, such as 
+\emph{local preference} attribute and one or more
+\emph{community values}.
+
+A BGP router may receive messages about the same prefix from several
+of its \emph{peers} (\IE, neighbouring routers).  When this occurs,
+it processes the messages as follows:
+\begin{enumerate}
+\item It \emph{filters} (drops) some of the incoming messages based on
+any their attributes (AS path, community values, peer it came from, \ETC),
+and optionally modifies attributes of the messages it does not drop.
+This is usually called the \emph{import} stage.
+\item From the remaining messages, it selects the one message it
+most \emph{prefers}. Selection is based on a number of criteria, but the
+most important is the local preference number: Higher local preferences
+are preferred.  Ties are broken by AS path length --- BGP defaults to 
+shortest path routing in such cases.
+\item Finally, it \emph{exports} the preferred message to selected neighbors,
+adding its own AS number to the path and optionally adding or
+modifying attributes.
+\end{enumerate}
+When a BGP router is configured, the user tunes the import and export
+stages of the above process, choosing which messages to import, how to
+modify them and how to export them.  By modifying the local preferences
+on messages in the inport phase, the user determines which messages will
+be selected.  This in turn determines how traffic destined for the given
+address will be routed.  Keep in mind that if BGP messages to a destination
+are propagated in one direction (left-to-right), then traffic will wind
+up flowing in the opposite direction (right-to-left).
+
+Rather than export 2$^n$ addresses in the same range, routers will
+often perform \emph{route aggregation}, and export a single (32-$n$)-bit
+prefix.  During aggregation, whenever an advertisement for 
+\emph{any} of the 2$^n$ addresses
+reaches the router, the \emph{entire} aggregate prefix will be announced.
+While useful for decreasing announcements and avoiding churn, such
+aggregation can be dangerous:  If a message for one of the 2$^n$ addresses (X)
+reaches the aggregation router, but another one of the addresses (Y)
+cannot reach the aggregation router due to a failure then the aggregate
+will be announced, possibly drawing traffic to Y, even though Y cannot be
+reached.  This is known as an \emph{aggregation-induced black hole}~\cite{route-aggregation}.
+Networks should be configured to be sufficiently fault tolerant to minimize
+the chances of such black holes.
+
+\paragraph*{An Example}
 %We motivate \sysname using an example data center network. Our network, 
@@
 connected to a set servers (``a rack''): P[1--8] denote groups of addresses for services hosted in each rack. 
-Such groups are called address {\em prefixes} because they are encoded using the adresses' shared prefix.
-
-We assume that each switch is running an instance of the \emph{Border Gateway Protocol} (BGP), 
-as is common in large data centers. In this protocol, adjacent switches use BGP to exchange messages
-with one another concerning the availability of routes to destinations.  A BGP \emph{configuration}
-(one for each switch) dictates which offered routes a switch will select and how to propagate chosen routes to its 
-neighbours.\footnote{If this submission is accepted and more space is available in the final version, 
-we will give a detailed explanation of BGP for the PLDI audience.  Henceforth, we assume knowledge of basic BGP
-mechanics.}
+% Such groups are called address {\em prefixes} because they are encoded using the adresses' shared prefix.
+
+%% We assume that each switch is running an instance of the \emph{Border Gateway Protocol} (BGP), 
+%% as is common in large data centers. In this protocol, adjacent switches use BGP to exchange messages
+%% with one another concerning the availability of routes to destinations.  A BGP \emph{configuration}
+%% (one for each switch) dictates which offered routes a switch will select and how to propagate chosen routes to its 
+%% neighbours.\footnote{If this submission is accepted and more space is available in the final version, 
+%% we will give a detailed explanation of BGP for the PLDI audience.  Henceforth, we assume knowledge of basic BGP
+%% mechanics.}
 
@@
 
-\subsection{Limitations of concrete synthesis}
+\paragraph*{Limitations of concrete synthesis}
 
@@
 
-\subsection{Limitations of today's template systems}
+\paragraph*{Limitations of today's template systems}
 
@@
 
-\subsection{Product graph distributed configurations}
+\subsection{Compilation to configurations}
 

### 2016-11-03 paper/abstraction/paper.tex
background
adding compilation to abgp

@@
 %
-The Product Graph is a tuple ($V'$, $E'$, $s$, $P$) with
+The Product Graph is a tuple ($G'$, $s$, $P$) where $G' = (V',E')$ is a new graph with 
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
@@
 %
-We write $worse(m,n)$ if $P(n) = \emptyset$ or $\min ~ P(m) \geq \min ~ P(n)$, which means that paths ending at PGIR node $m$ are worse (higher rank) than paths ending at $n$.
-%
-We write $m \approx n$ whenever two vertices $m,n = (l, \dots) \in V'$ share the same topology location $l$.
+Finally, we write $\tilde{m} = l$ to extract the topology location from a product graph node, when $m = (l, \dots) \in V'$.
 
@@
 In this example, all routes that eventually leave through Peer1 will lead to an accepting state for the first automaton and all routes that eventually leave through Peer2 will lead to an accepting state for the second automaton.
+
+From Figure~\ref{fig:example-compilation} we can see that both the concrete and abstract product graphs share a similar structure. This leads us to the following observation
+
+\begin{defn}
+If we have a graph homomorphism $f : G \rightarrow G^A$, concrete product graph $PG = (G',s,P)$ and abstract product graph $PG^A = (G'^A, s^A, P^A)$, then we can construct a new, lifted homomorphism $f_{pg} : G' \rightarrow G'^A$ in the following way:
+\[ \begin{array}{rcl}
+  f_{pg}( s ) & = & s^A  \\
+  f_{pg}( (l,q_1,\ldots,q_n) ) & = & (f(l),q_1,\ldots,q_n) \\
+\end{array} \]
+\end{defn}
 
@@
 
+\para{Route filtering}
+
 The first idea is to tag every protocol message with a BGP community value that relays the state of each automaton when advertising a route to a neighbor.
@@
 On the other hand, if it uses neighbor $P2$, then it will add the tag $(0,1)$ before informing its neighbors about the route.
-
-%The first step is to generate per-device BGP import and export filters based on the edges in the Product Graph.
-The idea is to attach a tag to every route advertisement that routers send to their neighbors that encodes the current state of the automata.
-For example...
-\ryan{show example here}.
-This ensures that BGP will only find paths that exist in the Product Graph, and are thus allowed by the policy.
-
-However, letting BGP find some allowed path is not enough.
-\sysname must ensure BGP always computes the \emph{best} path according to the user's preferences, even when failures occur.
+%
+However, letting BGP find some allowed path is not enough. \sysname must ensure BGP always computes the \emph{best} path according to the user's preferences, even when failures occur.
+
+\para{Preference Search}
 The second idea is to totally order advertisements each router might receive from neighbors in the Product Graph by preference.
@@
 \begin{defn}
-The product graph can be viewed as a labelled transition system where
-$m\overset{l}{\rightarrow}n$ if edge $(m,n) \in E'$ and $loc(n) = l$. We write $m \leq m'$ if $m$ simulates $m'$ with respect to the ``worse" relation on node rankings.
+Let $m \geq_{rank} n$ be a relation over Product Graph vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$.
+Intuitively $m \geq_{rank} n$ means that paths ending at PGIR node $m$ are no better (higher rank) than paths ending at $n$.
+%
+\end{defn}
+\noindent
+%
+
+\begin{defn}
+The product graph can be viewed as a labelled transition system by pushing the topology location from each directed edge's target node onto the edge.
+That is, $m\overset{l}{\rightarrow}n$ if edge $(m,n) \in E'$ and $\tilde{n} = l$.
+\end{defn}
+
+For example, in concrete product graph we would have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$
+
+\begin{defn}
+We write $m \leq m'$ if the subgraph reachable from $m$ and $m'$ respectively form a simulation relation with respect to the $\geq_{rank}$ relation on node rankings.
 \end{defn}
@@
 
-For example, in the concrete product graph we have $(S1,0,1) \leq (S1,1,0)$ but not the other way around.
-Therefore, advertisements received at $S1$ in state $(0,1)$ must be preferred to those received in state $(1,0)$.
-Observe also that in the abstract product graph, node $(S,0,1) \leq (S,1,0)$.
-This leads us the the following lemma:
+For example, in the concrete product graph we have $(S1,0,1) \leq (S1,1,0)$ since nodes on the left side of the product graph can always match transitions made on the right hand side while always maintaining a node ranking that is at least as good as that on the right hand side (since they match the preferred rank 1 automaton).
+This relation does not hold the other way around.
+Therefore, advertisements received at $S1$ in state $(1,0)$ must be preferred to those received in state $(0,1)$.
+
+Notice also that in the abstract product graph, node $(S,0,1) \leq (S,1,0)$. This leads us the the following observation:
 
@@
 \label{lem:preference}
-$m \leq m'$ in the concrete product graph iff $f(m) \leq f(m')$ in the abstract product graph under the lifted graph homomorphism $f$.
+$m \leq m'$ in the concrete product graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph under the lifted graph homomorphism $f_{pg}$.
 \end{lem}
 
-Intuitively, Lemma~\ref{lem:preference} hints that we will be able to infer BGP local preferences over the abstract product graph rather than the concrete product graph.
-
-\subsection{Substitution Theorem}
+Lemma~\ref{lem:preference} gives us reason to believe that we can perform compilation over the abstract product graph and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.
+
+\newcommand{\highlight}[1]{%
+  \colorbox{red!50}{$\displaystyle#1$}}
+\newcommand{\Router}[1]{\KW{Router} #1:}
+\newcommand{\REGEX}[1]{\texttt{regex}(#1)}
+\newcommand{\PEER}{\texttt{peer}}
+\newcommand{\PREFIX}{\texttt{prefix}}
+\newcommand{\IF}{\texttt{if}}
+\newcommand{\THEN}{\texttt{then}}
+\newcommand{\COMM}{\texttt{comm}}
+\newcommand{\MED}{\texttt{MED}}
+\newcommand{\Arrow}{\ensuremath{\leftarrow}}
+
+\para{BGP configurations}
+
+\begin{figure*}[t!]
+  \begin{minipage}[t]{.54\linewidth}
+    \hdr{Concrete Configuration}{}
+    \begin{code}
+      \Router{S1}
+        Match[100] \PREFIX=GP1, \PEER=*
+          \PEER \Arrow *
+        Match[100] \PREFIX=GP2, \PEER=*
+          \PEER \Arrow *
+        ...
+        Match[100] \PREFIX=LP1, \PEER=\{AG1, ..., AL1, ...\}
+          \PEER \Arrow \{AG1, ..., AL1, ...\}
+        Match[100] \PREFIX=LP2, \PEER=\{AG1, ..., AL1, ...\}
+          \PEER \Arrow \{AG1, ..., AL1, ...\}
+        ...
+        Match[110] \PREFIX=0.0.0.0/[0..32], \PEER=P1, 
+          \PEER \Arrow *, \COMM \Arrow (1,0)
+        Match[100] \PREFIX=0.0.0.0/[0..32], \PEER=P2, 
+          \PEER \Arrow *, \COMM \Arrow (0,1)
+        ...
+      \end{code}
+  \end{minipage}
+  %
+  \begin{minipage}[t]{.4\linewidth}
+    \hdr{Template Configuration}{}
+    \begin{code}
+      \Router{S}
+        Match[100] \PREFIX=\$GP, \PEER=*
+          \PEER \Arrow *
+        Match[100] \PREFIX=\$LP, \PEER=\{AG, AL\}
+          \PEER \Arrow \{AG, AL\}
+        Match[110] 0.0.0.0/[0..32], \PEER=P1, 
+          \PEER \Arrow *, \COMM \Arrow (1,0)
+        Match[100] 0.0.0.0/[0..32], \PEER=P2, 
+          \PEER \Arrow *, \COMM \Arrow (0,1)
+        ...
+      \end{code}
+  \end{minipage}%
+
+  \hrulefill
+  \vspace*{.4em}%
+
+  \caption{Spine configurations for concrete and abstract policies.}
+  \label{fig:bgp-configs}
+\end{figure*}
+
+By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations.
+In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
+Figure~\ref{fig:bgp-configs} shows partial a configuration for the spine routers in the concrete and abstract policies.
+
+\subsection{Compilation Correctness}
 
@@
 & First show how to compile to the Product Graph, and from there to the ABGP
-& Show/Define safety analysis simulation relation for both concrete and abstract product graphs
-  and how it holds for both.
 & Next define the concretization & subst. functions for translating the abstract policy
    into the concrete policy, using the ABGP example for reference
-& Lemma: if safety analysis holdls in the abstract graph, it holds for the concrete one,
-   and the preferences are consistent.
 & Give abstraction theorem: commuting of concretization and compilation

### 2016-11-03 paper/abstraction/paper.tex
add incrementality section

@@
     \begin{code}
-      \Router{S1}
+      \Router{S1, S2}
         Match[100] \PREFIX=GP1, \PEER=*
@@
 
-  \caption{Spine configurations for concrete and abstract policies.}
+  \caption{Spine configurations for concrete and abstract policies. \ryan{TODO: this would look good in powerpoint and by connecting related components}}
   \label{fig:bgp-configs}
@@
 In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
-Figure~\ref{fig:bgp-configs} shows partial a configuration for the spine routers in the concrete and abstract policies.
+Figure~\ref{fig:bgp-configs} shows part of the configuration for the spine routers for the concrete and abstract policies.
+
+The spine switches have a default rule for the prefix $0.0.0.0/[0..32]$ that will match advertisements from peer $P1$ and $P2$.
+The match for $P1$ is preferred since it has a higher BGP local-preference attribtue (110).
+If an advertisement from $P1$ is available the spine attaches the community tag $(1,0)$ and advertises the route to all its peers.
+If only an advertisement from the backup $P2$ is available, then it attaches the tag $(0,1)$ and advertises this to all peers instead.
+
+In the template configuration, it will have additional policy for the local and global prefixes.
+It will match any global prefix from any peer and re-advertise the route to all of its peers.
+For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to all other internal peers.
+The concrete configurations will have a similar configuration for each local and global prefix.
 
@@
 \end{easylist}
+
+\subsection{Incrementality}
+
+Suppose that we want to expand the concrete datacenter by adding an additional tor router in the TG role.
+Per the network routing policy, this new ToR router will advertise its own owned prefix.
+Because the new topology matches the abstraction, the compiled templates will remain the same.
+However, in the spine router configurations, the match on the global prefix template variable \$GP will be expanded to include the new prefix owned by the ToR.
+In other words, the concrete configurations obtained after substitution will include an additional match on the new prefix.
+Unfortunately, this means a small change to the topology can result in many configurations far from the change needing to change too.
+
+The key observation is that the template variables tell us exactly where change can happen.
+For example, the only way in which the spine routers depend on anything nonlocal is in the prefix template variables.
+Instead, we replace each match on a template variable (\EG, matching \$GP) with a test on a new community tag that we associate with each template variable.
+So long as we ensure that routers always add the appropriate tags to the prefixes they originate, then the policies will be equivalent.
+
+Specifically, this ensures that each router has a template that has no dependency on any other non-adjacent router.
+If we make a change to the concrete network that matches the abstraction, then the templates do not change, and thus only configurations adjacent to the changes must also change.
 

### 2016-11-03 paper/abstraction/paper.tex
added incremental section, start abstract analysis

@@
 
-\section{Analysis}
+\section{Abstract Analysis}
 \label{sec:analysis}
 
-%\para{Semantics}
-
-%We give a semantics to RIR programs using sets of ranked paths.
-Each path constraint $r_1 \Prefer \dots \Prefer r_j$ denotes a set of ranked network paths.
-A network path is a topologically valid string of abstract locations $l_1 l_2 \dots l_k$.
-We use the notation $\abs{p}$ to denote the length of the path $p$.
-A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$, that is, the path is in the language of the regular expression.
-Paths are ranked lexicographically according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the path length.
-Lower ranks indicate \emph{more} preferred paths.
-More formally, a path $p$ has rank:
-%$$(\min_i \set{ p \in \mathcal{L}(r_i) }, \abs{p})$$
-%%
-%The set of ranked paths depends on which paths are valid in the topology, and thus when failures occur, the most preferred routes change.
-%%
-%For any source $s$ and destination $d$, \sysname will send traffic along the highest ranked available path from $s$ to $d$.
-
-\subsection{Other properties}
+In the previous section we saw that \sysname can synthesize correct device configurations by operating directly over the abstract representation.
+However, in practice operators would often like to reason about other properties about their network.
+In this section we present an analysis that operates over the network abstraction to find a lower bound on the number of disjoint paths between pairs of concrete nodes.
+Answering questions about the number of disjoint paths allows operators to reason about many useful network properties such as reachability (\IE, is there at least one path) and fault tolerance (\EG, how many failures will disconnect certain routers).
+An important point is that the analysis takes place over the structure of the product graph, and so takes both the topology and routing policy into account.
+
+\subsection{Abstract k-disjoint paths}
 \label{sec:property-checking}
-
-\begin{easylist}[itemize]
-& K-disjoint path analysis
-&& Useful for aggregation safety (black holes) & reachability
-&& Inference rules as an abstract interpretation using Z3
-\end{easylist}
 
@@
 
-%\subsection{Aggregation-safety analysis}
-%\label{sec:agg-safety}
-
-%As shown in \S\ref{sec:motivation}, aggregation can lead to subtle black-holing of traffic when failures occur.
-Determining when this can happen requires knowledge, not only of the topology, but also of the policy.
-For instance, a policy might require that all traffic for a particular prefix go over a single link before being aggregated.
-If that one link fails, a black hole might be introduced.
-%%
-%Because the PGIR encodes the complete user policy and topology, \sysname can efficiently check that aggregates do not black hole traffic for up to $k$ failures.%
-
-%We view the aggregation problem as a variant of the min-cut problem in the PGIR.
-Specifically, for each prefix that falls under an aggregate, we are interested in finding a lower bound on the number of failures required to disconnect the prefix's origin from its aggregation point.
-The difficulty, however, is that each link in the topology might appear as multiple links in the PGIR, thus preventing the direct application of standard min-cut algorithms.
-%%%
-
-%Instead, we adopt the following simple strategy: $i)$ pick a random path in the PGIR between the prefix's origin and aggregation point, $ii)$ remove all similar edges in the PGIR for each topology edge along the chosen path, and $iii)$ repeat until no such path exists.
-%Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.%
-%
-
-%Recall the datacenter example from \S\ref{sec:motivation}, with the policy
-%\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
-Figure~\ref{fig:aggregation-safety} shows the PGIR for \CD{PG1}.
-Since we know aggregation will occur at $X$, and that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
-We could remove the $A$--$D$--$X$ path first and would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none).
-Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
-Because $A$ is now disconnected from $X$, 2 is a lower bound on the number of failures required to introduce an aggregation black hole for prefix \CD{PG1}.
-This process is repeated for other aggregation locations (\EG, $Y$).
-
-%\subsection{Abstract BGP}
-%\label{sec:abgp}
-%The final stage of our compiler translates policies from PGIR to a vendor-neutral abstraction of BGP (ABGP).
-
-%\para{From PGIR to ABGP}
-
-%\newcommand{\highlight}[1]{%
-%  \colorbox{red!50}{$\displaystyle#1$}}
-%\newcommand{\Router}[1]{\KW{Router} #1:}
-%\newcommand{\REGEX}[1]{\texttt{regex}(#1)}
-%\newcommand{\PEER}{\texttt{peer}}
-%\newcommand{\COMM}{\texttt{comm}}
-%\newcommand{\MED}{\texttt{MED}}
-%\newcommand{\Arrow}{\ensuremath{\leftarrow}}%
-
-%\begin{figure}[t!]
-%\begin{code}
-%  \Router{A}
-%    Match \PEER=C, \COMM=(3,2)
-%      Export \COMM \Arrow (4,2),
-%             \MED \Arrow 80, \PEER \Arrow W
-%  \Router{B}
-%    Match \PEER = C, \COMM = (-,2) or (3,2)
-%      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
-%             \MED \Arrow 81, \PEER \Arrow W
-%  \Router{C}
-%    Match[LP=99] \PEER = E, \COMM = (-,2)
-%      Export \COMM \Arrow (-,2), \PEER \Arrow B
-%    Match \PEER = D, \COMM = (2,2)
-%      Export \COMM \Arrow (3,2), \PEER \Arrow A,B
-%  \Router{D}
-%    Match \REGEX{X + Y}
-%      Export \COMM \Arrow (2,2), \PEER \Arrow C
-%  \Router{E}
-%    Match \REGEX{Z}
-%      Export \COMM \Arrow (-,2), \PEER \Arrow C
-%  \end{code}
-%  \vspace{-2em}
-%  \caption{Abstract BGP router configurations. \label{fig:abgp-config}}
-%  \vspace{-1em}
-%\end{figure}
+In order to infer bounds on the number of disjoint paths between nodes we use information about the structure of the underlying concrete topologies encoded in the abstraction pod structure and node + edge multiplicity constraints.
+
+The idea is to maintain, for each role in the abstract product graph, facts learned about the number of disjoint paths to some number of concrete routers in that role from a given source location.
+More specifically, we maintain facts of the form:
+%
+\[ \begin{array}{c}
+  L_{X_1}, \ldots, L_{X_n}(j,k) 
+\end{array} \]
+\noindent
+%
+Each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all".
+There is one label in the nesting for each pod scope in the network abstraction hierarchy.
+So for a given node, $L_{X_1}$ would correspond to the outermost pod scope, while $L_{X_n}$ would correspond the the node's label.
+The value $j$ tells us the number of concrete nodes in the group that are reachable, and the value $k$ tells us the number of disjoint paths to each of the $j$ nodes such that all $j*k$ paths are disjoint.
 

### 2016-11-03 paper/abstraction/paper.tex
add analysis image

@@
 
-\subsection{Abstract k-disjoint paths}
-\label{sec:property-checking}
-
 \newcommand{\inference}[4]{
@@
 
+\subsection{Abstract k-disjoint paths}
+\label{sec:property-checking}
+
 In order to infer bounds on the number of disjoint paths between nodes we use information about the structure of the underlying concrete topologies encoded in the abstraction pod structure and node + edge multiplicity constraints.
@@
 So for a given node, $L_{X_1}$ would correspond to the outermost pod scope, while $L_{X_n}$ would correspond the the node's label.
-The value $j$ tells us the number of concrete nodes in the group that are reachable, and the value $k$ tells us the number of disjoint paths to each of the $j$ nodes such that all $j*k$ paths are disjoint.
+
+Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete router in the abstract source, for ``some"/``all" scopes $X_1$, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds.
+The base case $L_{X_n}(j,k)$ means that for ``some"/``all" groups of size $j$ concrete routers, there are $k$ disjoint paths to each such that all $j*k$ paths are disjoint
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=.66\columnwidth]{figures/analysis}
+  \end{center}
+  \caption{Abstract disjoint path analysis with valleyfree routing for global prefixes. \label{fig:compilation-times}}
+  \vspace{-1em}
+\end{figure}
+
+For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of size 2 concrete routers in role TL such that they each have 4 disjoint to them from the source and all 8 paths are disjoint.
+
+%suppose we want to compute the number of disjoint paths from the local ToR role $(TL,0,0)$ for  
+\ryan{TODO: probably need a new image for local prefixes?}
 

### 2016-11-03 paper/abstraction/paper.tex
temp commit

@@
 
-\section{Background and Motivation}
+\section{Background}
+\label{sec:background}
+
+In this work, we focus on synthesizing configurations for a network that runs the Border Gateway Protocol (BGP), which is the standard for routing across independent organizations and inside large datacenters.
+It scales effectively and allows operators to define flexible policies.
+
+The interactions among BGP routers determines how the network forwards traffic.
+To invite traffic from a neighbor to a destination, routers announce the destination's address {\em prefix} (e.g., 10.1.1.0/24\footnote{An IP(v4) address
+such as 10.1.1.0 is 32 bits, with each of the four values representing 8 bits.
+A prefix such as 10.1.1.0/24 denotes the set of addresses that share the first 24 bits with 10.1.1.0, \IE, all addresses that begin with 10.1.1.}) to the neighbor.
+In this way, traffic flows in the opposite direction to such {\em route announcements.}
+
+Route announcements contain additional attributes.
+A common one is {\em AS path}, which denotes the sequence of Autonomous Systems that will be traversed to reach the destination.
+When BGP is used inside a datacenter, each router tends to be its own AS.
+Optional attributes include one or more {\em communities}, which are arbitrary strings.
+Operators agree on what each community value means out of band.
+
+A BGP router may receive one or more announcements from different neighbors for the same prefix.
+It selects the best one(s) based on its {\em import policy}.
+These policies are a function of the AS path, community values, or the neighbor that sent the announcement, and may even filter some announcements altogether (i.e., not use them even if no other announcements to the destination are available).
+Then, based on the {\em export policy}, the router announces the selected route to one or more neighbors, after adding itself to the AS path and, optionally, modifying the set of community values.
+
+%When this occurs,
+%it processes the messages as follows:
+%\begin{enumerate}
+%\item It \emph{filters} (drops) some of the incoming messages based on
+%any their attributes (AS path, community values, peer it came from, \ETC),
+%and optionally modifies attributes of the messages it does not drop.
+%This is usually called the \emph{import} stage.
+%\item From the remaining messages, it selects the one message it
+%most \emph{prefers}. Selection is based on a number of criteria, but the
+%most important is the local preference number: Higher local preferences
+%are preferred.  Ties are broken by AS path length --- BGP defaults to
+%shortest path routing in such cases.
+%\item Finally, it \emph{exports} the preferred message to selected neighbors,
+%adding its own AS number to the path and optionally adding or
+%modifying attributes.
+%\end{enumerate}
+%When a BGP router is configured, the user tunes the import and export
+%stages of the above process, choosing which messages to import, how to
+%modify them and how to export them.  By modifying the local preferences
+%on messages in the inport phase, the user determines which messages will
+%be selected.  This in turn determines how traffic destined for the given
+%address will be routed.  Keep in mind that if BGP messages to a destination
+%are propagated in one direction (left-to-right), then traffic will wind
+%up flowing in the opposite direction (right-to-left).
+
+A BGP router may also perform {\em route aggregation} when exporting to certain neighbors.
+That is, instead of announcing multiple prefixes it may announce a single covering prefix (e.g., 10.1.0.0/16 instead of 10.1.[1--255].0/24).
+The covering prefix is announced as long as the router has a valid route to any of the covered prefixes.
+Aggregation helps reduce the memory consumption of routers, but it can lead to traffic black holes~\cite{route-aggregation}.
+A router that announces 10.1.0.0/16, because it has a route to 10.1.1.0/24, may also get traffic for 10.1.2.0/24 to which it has no route.
+
+%Rather than export 2$^n$ addresses in the same range, routers will
+%often perform \emph{route aggregation}, and export a single (32-$n$)-bit
+%prefix.  During aggregation, whenever an advertisement for
+%\emph{any} of the 2$^n$ addresses
+%reaches the router, the \emph{entire} aggregate prefix will be announced.
+%While useful for decreasing announcements and avoiding churn, such
+%aggregation can be dangerous:  If a message for one of the 2$^n$ addresses (X)
+%reaches the aggregation router, but another one of the addresses (Y)
+%cannot reach the aggregation router due to a failure then the aggregate
+%will be announced, possibly drawing traffic to Y, even though Y cannot be
+%reached.  This is known as an \emph{aggregation-induced black hole}~\cite{route-aggregation}.
+%Networks should be configured to be sufficiently fault tolerant to minimize
+%the chances of such black holes.
+
+\section{Motivation}
 \label{sec:motivation}
+
+Configuring a BGP network requires configuring, among other things, the import and export policies for each router such that traffic flows in a way that is compliant with the network's global policies.
+We demonstrate the difficulty of this task using an example.
 
@@
 
-\paragraph*{Background}  Traditional routers use 
-distributed protocols to exchange messages about available routes. 
-One such protocol is the Border Gateway Protocol (BGP).  BGP is the
-standard for inter-domain routing (the act of exchanging routing information 
-between independently-owned networks) and is also commonly used in
-data centers because it allows operators to define relatively flexible
-routing policy while also scaling effectively to large networks.
-When used within a data center, each router is configured with its own \emph{AS number},
-which identifies it.
-
-Each BGP message (also called a \emph{route announcement}) contains a 
-\emph{destination prefix}, such as 10.1.1.0/24,\footnote{An address
-such as 10.1.1.0 is 32 bits, with each of the four values representing 8 bits.  
-A prefix such
-as 10.1.1.0/24 denotes the set of addresses that begin with the first
-24 bits of 10.1.1.0, \IE, all addresses that begin with 10.1.1.} as well as an
-\emph{AS path}, such as XYZ (where each of X, Y and Z would be an AS number).  
-Such messages indicate that the set of addresses
-denoted by the prefix may be reached by following the path XYZ. 
-A BGP message may also contain additional attributes, such as 
-\emph{local preference} attribute and one or more
-\emph{community values}.
-
-A BGP router may receive messages about the same prefix from several
-of its \emph{peers} (\IE, neighbouring routers).  When this occurs,
-it processes the messages as follows:
-\begin{enumerate}
-\item It \emph{filters} (drops) some of the incoming messages based on
-any their attributes (AS path, community values, peer it came from, \ETC),
-and optionally modifies attributes of the messages it does not drop.
-This is usually called the \emph{import} stage.
-\item From the remaining messages, it selects the one message it
-most \emph{prefers}. Selection is based on a number of criteria, but the
-most important is the local preference number: Higher local preferences
-are preferred.  Ties are broken by AS path length --- BGP defaults to 
-shortest path routing in such cases.
-\item Finally, it \emph{exports} the preferred message to selected neighbors,
-adding its own AS number to the path and optionally adding or
-modifying attributes.
-\end{enumerate}
-When a BGP router is configured, the user tunes the import and export
-stages of the above process, choosing which messages to import, how to
-modify them and how to export them.  By modifying the local preferences
-on messages in the inport phase, the user determines which messages will
-be selected.  This in turn determines how traffic destined for the given
-address will be routed.  Keep in mind that if BGP messages to a destination
-are propagated in one direction (left-to-right), then traffic will wind
-up flowing in the opposite direction (right-to-left).
-
-Rather than export 2$^n$ addresses in the same range, routers will
-often perform \emph{route aggregation}, and export a single (32-$n$)-bit
-prefix.  During aggregation, whenever an advertisement for 
-\emph{any} of the 2$^n$ addresses
-reaches the router, the \emph{entire} aggregate prefix will be announced.
-While useful for decreasing announcements and avoiding churn, such
-aggregation can be dangerous:  If a message for one of the 2$^n$ addresses (X)
-reaches the aggregation router, but another one of the addresses (Y)
-cannot reach the aggregation router due to a failure then the aggregate
-will be announced, possibly drawing traffic to Y, even though Y cannot be
-reached.  This is known as an \emph{aggregation-induced black hole}~\cite{route-aggregation}.
-Networks should be configured to be sufficiently fault tolerant to minimize
-the chances of such black holes.
-
-\paragraph*{An Example}
-%We motivate \sysname using an example data center network. Our network, 
-Consider the data center network shown in Figure~\ref{fig:example}.  The boxes in the diagram
-represent \emph{switches}, and these switches play several different roles:  T[1--8] denote top-of-rack (ToR) switches, A[1--8] denote aggregation switches, and S[1--2] denote spine switches.
+Consider the data center network in Figure~\ref{fig:example}. The boxes in the diagram
+represent \emph{switches}.
+Using terminology for fat tree networks~\cite{fattree}, T[1--8] denote top-of-rack (ToR) switches, A[1--8] denote aggregation switches, and S[1--2] denote spine switches.
 The spine switches are connected to the
-rest of the internet; any traffic to or from the outside world flows through them.  The aggregation switches
-serve as a bridge between spine and ToR switches.   Finally, each ToR switch is
-connected to a set servers (``a rack''): P[1--8] denote groups of addresses for services hosted in each rack. 
-% Such groups are called address {\em prefixes} because they are encoded using the adresses' shared prefix.
+rest of the Internet; any traffic to or from the outside world flows through them.  The aggregation switches 
+bridge the spines to the ToRs which attach to a set of servers (``a rack''). P[1--8] denote address prefixes for services hosted in each rack.
 

### 2016-11-04 paper/abstraction/paper.tex
stashing changes

@@
 
-\title{An Abstraction-based Approach to Network Synthesis}
+\title{Network Configuration Synthesis with Abstract Topologies}
 
@@
 network operators typically classify the devices, assigning them a particular
-\emph{role} such as ``top-of-rack switch'' or ``tier-one aggregation switch.''
+\emph{role} such as ``top-of-rack router'' or ``tier-one aggregation router.''
 Each such role is codified as a \emph{configuration template}---a macro
@@
 to one another.  For instance, a programmer may
-define separate roles for ``top-of-rack switch'' and
-``tier-one aggregation switch'' and specify that every top-of-rack switch
-is connected to at least two different tier-one aggregation switches,
-thereby providing a degree of fault tolerance of one aggregation switch
+define separate roles for ``top-of-rack router'' and
+``tier-one aggregation router'' and specify that every top-of-rack router
+is connected to at least two different tier-one aggregation routers,
+thereby providing a degree of fault tolerance of one aggregation router
 were to fail.
@@
 
+Configuring a BGP network requires configuring, among other things, the import and export policies for individual routers such that traffic flows in a way that is compliant with the network's global policies.
+Making matters worse, configuring the policies of individual routers requires tweaking low-level primitives for route selection preferences, route modification rules, and filtering and aggregation criteria.
+
 \section{Motivation}
 \label{sec:motivation}
-
-Configuring a BGP network requires configuring, among other things, the import and export policies for each router such that traffic flows in a way that is compliant with the network's global policies.
-We demonstrate the difficulty of this task using an example.
 
@@
 
-Consider the data center network in Figure~\ref{fig:example}. The boxes in the diagram
-represent \emph{switches}.
-Using terminology for fat tree networks~\cite{fattree}, T[1--8] denote top-of-rack (ToR) switches, A[1--8] denote aggregation switches, and S[1--2] denote spine switches.
-The spine switches are connected to the
-rest of the Internet; any traffic to or from the outside world flows through them.  The aggregation switches 
-bridge the spines to the ToRs which attach to a set of servers (``a rack''). P[1--8] denote address prefixes for services hosted in each rack.
-
-%% We assume that each switch is running an instance of the \emph{Border Gateway Protocol} (BGP),
-%% as is common in large data centers. In this protocol, adjacent switches use BGP to exchange messages
+We demonstrate the difficulty of configuring networks using the example data center network in Figure~\ref{fig:example}.
+The boxes denote routers.
+Using terminology for fat tree networks~\cite{fattree}, T[1--8] denote top-of-rack (ToR) routers, A[1--8] denote aggregation routers, and S[1--2] denote spine routers.
+The spine routers are connected to the
+rest of the Internet through Peer[1--2]. The aggregation routers
+bridge the spine to the ToRs routers. The ToR routers attach to a set of servers (``a rack'') that host services with address prefixes P[1--8].
+
+%% We assume that each router is running an instance of the \emph{Border Gateway Protocol} (BGP),
+%% as is common in large data centers. In this protocol, adjacent routers use BGP to exchange messages
 %% with one another concerning the availability of routes to destinations.  A BGP \emph{configuration}
-%% (one for each switch) dictates which offered routes a switch will select and how to propagate chosen routes to its
+%% (one for each router) dictates which offered routes a router will select and how to propagate chosen routes to its
 %% neighbours.\footnote{If this submission is accepted and more space is available in the final version,
@@
 
-The intended high-level operator policy for this network is as follows.
-Internal connectivity should be complete, \IE, all nodes must be able to talk to each other.
-Services in Pods 1 and 2 should be globally accessible and thus their addresses should be announced externally, but only after aggregating individual prefixes P[1--4] into a single prefix PG.
-Finally, services in Pods 3 and 4 not should be externally visible and thus their address should not be announced externally.
-
-To correctly configure the policy above, the network engineer's task is to generate low-level configurations for each switch in the network.
-This implies ensuring, for instance, that all switch interfaces are assigned correct addresses; all routing adjacencies are correctly configured (\EG, T1's configuration includes A1 as neighbor and vice-versa); all switches announce their own addresses (so that they can be reached for management purposes) and the ToRs announce the correct prefixes for their services; all switches  forward the prefix announcements that they should to each neighbor and not forward those that they should not (\EG, the spines should forward prefixes for local services to internal neighbors but not external neighbors); and the spines announce externally only the aggregate global prefix.
-\dpw{Do we need to explain aggregation here?}
-
-As many have observed before, such configuration tasks are highly challenging. Consequently, configuration errors are the leading cause of network outages~\cite{juniper-study,bgpmon,batfish,propane}.
-
-\paragraph*{Limitations of concrete synthesis}
-
-In response, researchers have developed systems that synthesize low-level device configurations from high-level policy statements~\cite{narain:lisa05,narain+:configassure,dadc,propane}.
-%They take network topology and policy as input and output device configurations that are  guaranteed to be correct under all possible failures.
-Thus, they save the engineers from performing the complex task of breaking down global policies into device configurations.
-These systems eliminate entire classes of configuration errors by construction, and, in the case of
-Propane~\cite{propane}, guarantee that high-level policy is implemented correctly, even in the presence of
-arbitrary combinations of failures.
-
-However, our conversations with network engineers at two major cloud providers reveal that they have two limitations that discourage adoption.
-The first is a mismatch in abstraction.
-Engineers of large, structured networks tend to think of the network, and to develop management tools, using \emph{roles}, and not individual devices.
-A {\em role} refers to specific functionality and is played by one or more routers.
+The intended policy for this network is:
+$p1)$ complete internal connectivity, \IE, all routers should be able to talk to each other;
+$p2)$ services in Pods[1--2] should be globally accessible;
+$p3)$ prefixes for global service should be aggregated into a covering prefix PG when announced outside;
+$p4)$ services in Pods[3--4] should not be externally accessible;
+$p5)$ prefer Peer 1 over Peer 2, \IE, when both peers announce a prefix, send traffic through peer 1;
+$p6)$ datacenter routers should not transit traffic between peers 1 and 2; and
+$p7)$ no loss in connectivity after any single-link failure.
+
+To correctly configure this policy, network operators must generate configurations for each router.
+This implies ensuring, for instance, that all router interfaces are assigned correct addresses; all routing adjacencies are correctly configured (\EG, T1's configuration includes A1 as neighbor and vice-versa); all routers announce their own addresses (so that they can be reached from other routers) and the ToRs announce the correct prefixes for their services; all routers  forward the prefix announcements that they should to each neighbor and not forward those that they should not (\EG, the spines should forward prefixes for local services to internal neighbors but not external neighbors); and the spines announce externally only the aggregate global prefix.
+Such configuration tasks are highly complex~\cite{juniper-study,bgpmon,batfish,propane}.
+
+To simplify network configuration, the operations community is adopting a template-based approach~\cite{hatch,thwack}.
+Instead of authoring a configuration file per router, operators author one configuration template per role.
+%
+A {\em role} refers to specific functionality and is played by one or more routers.\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor configuration language.}
+%
 The network in Figure~\ref{fig:example} has five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
-Engineers are naturally reluctant to use a system that does not
-understand roles as a first-order abstraction because they think about
-network policy in terms of roles, and, even more importantly, if they want to debug, analyze or
+%
+Templates have parameters for various aspects of the configuration (\EG, interface addresses, neighbor list) and are compiled to device configurations by instantiating the parameters using a database of network information.
+
+%Templates provide two key advantages.
+First, they help eliminate a class of configuration errors that stem from typos and inconsistencies, e.g., using the wrong address for a router, having inconsistent addresses for the two ends of a link, and failing to configure one side of a routing adjacency.
+Second, templates have the potential for re-use when the topology changes while maintaining its basic structure (e.g., adding a new pod to the data center) or multiple networks with similar structures need to be instantiated (e.g., in an organization that runs multiple data centers).
+
+\para{Templates today} While templates help avoid a class of configuration errors (e.g., inconsistent routing adjacencies), they are difficult to author.
+Operators must manually decompose complex, network-wide routing policy into role templates such that the collective behavior of the configurations generated from them will correctly implement the policy, under failures and as the network evolves.
+
+This task is error-prone, and no tools exist today for template verification; in fact, such tools would be difficult to build as templates have no semantics, of policies or topologies they were intended to work for, independent of the configurations they produce.
+Today, operators test (not verify) templates by simulating their generated configurations over the current or known future topologies.
+
+%As a result, the types of configuration design errors pointed in prior work~\cite{propane} can occur in template design as well.
+For instance, to keep local prefixes internal the engineer may implement announcement forwarding on spines based on the identity of the neighbor, \IE, do not announce externally anything heard from local aggregators.
+This implementation is appealing because it does not require changes to spine configurations when ToR prefixes change.
+But it works correctly only when there are no failures; local prefixes can leak externally when failures disconnect a spine from both aggregators in a local pod.
+Specifically, when S1 is disconnected from A5 and A6, it may hear about P5 and P6 from A3 and A4 (via A[5--6]->S2->A[3--4]), and it will then announce those prefixes outside (since they no not come from a local aggregator), leading to a policy violation.
+A possible correct implementation here would be for each spine to block messages headed to external peers from local aggregators {\em and} to reject announcements that have traversed the other spine (\IE, to disallow "valleys," or up-down-up paths).
+
+%Lacking correctness guarantees, engineers use simulations to analyze if templates are correct under a range of failure cases (e.g., combinations of two-link failures), but such analysis is highly expensive for large networks and still does not provide strong guarantees beyond the tested cases.
+
+%The second limitation of today's template systems is that, like concrete synthesis tools, they do not support network evolution.
+One might hope that important network properties such as connectivity and fault tolerance persist when networks evolve in ways consistent with existing roles and templates.
+However, existing template systems provide no guarantees that seemingly-minor variations of a given topology have similar properties.
+%In theory, templates do not have to be redesigned when the network evolves while keeping its basic structure of roles and their inter-connectivity.
+In practice, however, it is not guaranteed that templates that work for a given topology also work for seemingly-minor variations of the topology.
+
+Such simulations provide some assurance that the templates work correctly for the simulated topologies but little assurance for other topologies that may arise after the network evolves.
+It is hard to predict all future topologies in advance, templates that work for one topology may not work for seemingly-inconsequential variations.
+
+Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}; it has the same five roles, connected in a similar hierarchy.
+One might think that the same templates (with different database entries) can be used for both topologies, but that is not true.
+For instance, consider templates that disallow ``valley" paths, which go up, down, and then up again; it is a common to disallow valley paths in a data center because they are longer than shortest paths.
+These templates will work perfectly for Figure~\ref{fig:example}, but violate the fault tolerance requirement ($p7$) when used for Figure~\ref{fig:example}.
+Specifically, in Figure~\ref{fig:example2}, an aggregation-induced blackhole (\S\ref{sec:motivation}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces  the covering prefix PG (because it gets routes for P[3--4]).
+In contrast, in Figure~\ref{fig:example}, no such blackhole will occur after a single link failure because spine routers have two links to each pod.
+
+Thus, today, operators test templates for each topology change.
+For some changes, they may discover that their old templates will not work anymore.
+~\dpw{Note: This is going to be true for Methane too.} ~\ratul{Not really; our abstract topologies encode all possible future topologies}
+This discovery is highly problematic because changing a template may cause a configuration change of all the devices that use that template---an unacceptable disruption in many cases.
+When that happens, network operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the topological change.
+Such patches reintroduce the complexity and errors that templates were meant to prevent.
+
+\para{Configuration synthesis with concrete topologies}
+Many recent systems generate router configurations using high-level policy statements~\cite{narain:lisa05,narain+:configassure,dadc,propane} and the network's concrete topology.
+%These systems eliminate entire classes of configuration errors by construction, and, in the case of
+%Propane~\cite{propane}, guarantee that high-level policy is implemented correctly, even in the presence of
+%arbitrary combinations of failures.
+They are able to provide strong guarantees on configuration correctness but 
+our conversations with operators at two major cloud providers reveal that they have two limitations that discourage adoption.
+The first is abstraction mismatch.
+Operators of large networks think of the network, and to develop management tools, using \emph{roles}, and not individual devices.
+They are naturally reluctant to use a system that does not
+understand roles as a first-order abstraction. If they want to debug, analyze or
 understand system output, they will have to consider
@@
 \emph{a handful} of role configurations. Unfortunately, even if two devices play the same role,
-there is no guarantee a concrete synthesis system will generate (syntactically) similar configurations,
-making vetting system outputs extremely difficult.
-
-A second limitation is the inability to support network evolution.
+there is no guarantee a concrete synthesis system will generate (syntactically) similar configurations.
+
+%A second limitation is the inability to support network evolution.
 Networks evolve all the time as nodes and links are added or removed and the addresses of services are changed.
 A system that supports evolution would ensure that
-small changes in topology require small, local changes in network configurations as opposed to pervasive
-changes across many devices.
+%small changes in topology require small, local changes in network configurations as opposed to pervasive
+%changes across many devices.
 Engineers want to minimize changes to device configurations because each change runs the risk of poor, transient behavior due to poor router software or routing protocol dynamics~\cite{ratulbgpmisconfigs}.
@@
 
-Unfortunately, in general, any change in network topology requires re-execution of a
+Second, these systems become even more brittle in the face of network evolution.
+Any change in network topology requires re-execution of a
 concrete synthesis engine, from scratch,
 on the changed topology.  The result may be
-a completely different set of configurations.  However, even if such configurations are
-largely semantically similar to existing configurations, they may be syntactically different,
-and may cause considerable network disruption when updates are pushed to switches.
-For instance, suppose an operator wants to modify the prefix of local ToR T8 in Figure~\ref{fig:example}.
+a completely different set of configurations.  Even if such configurations are
+largely semantically similar to existing configurations, they may be syntactically different and cause considerable network disruption when updates are pushed to routers.
+
+%For instance, suppose an operator wants to modify the prefix of local ToR T8 in Figure~\ref{fig:example}.
 To accommodate the modification, Propane, a concrete synthesis tool, will, at a minimum, not only change T8's configuration but also those of the two spines because it uses prefix lists at spines to ensure that local prefixes are not advertised externally.
 As we show later, there is a way to design the configurations of this network to avoid spine configuration changes while accommodating ToR prefix (and other) modifications.
-Our new
-abstraction-based synthesis framework synthesizes evolution-friendly roles automatically.
+Our new abstraction-based synthesis framework synthesizes evolution-friendly roles automatically.
 
@@
 
-\paragraph*{Limitations of today's template systems}
-
-To simplify network configuration, and thus reduce errors, the network engineering community is adopting a template-based approach~\cite{hatch,thwack}.
-Instead of authoring one configuration file per router, engineers author one configuration template per role.\footnote{If a role is played by devices from different vendors, there is one template per role-vendor combination because templates use vendor configuration language.} Templates have parameters for various aspects of the configuration (\EG, interface addresses, neighbor list) and are compiled to device configurations by instantiating the parameters using a database of per-device values.
-
-%Templates provide two key advantages.
-First, they help eliminate a class of configuration errors that stem from typos and inconsistencies, e.g., using the wrong address for a switch, having inconsistent addresses for the two ends of a link, and failing to configure one side of a routing adjacency.
-Second, templates have the potential for re-use when the topology changes while maintaining its basic structure (e.g., adding a new pod to the data center) or multiple networks with similar structures need to be instantiated (e.g., in an organization that runs multiple data centers).
-
-While templates operate at the right level of abstraction, today's template systems have two limitations.
-The first is that they offer no correctness guarantees.
-To author correct templates, engineers must break down complex, network-wide routing policy into role templates such that the collective behavior of the configurations generated from the templates correctly implements the desired high-level policy under all failure conditions.
-This is a challenging, manual task, with no tools available to support template verification.
-
-As a result, the types of configuration design errors pointed in prior work~\cite{propane} can occur in template design as well.
-For instance, to keep local prefixes internal the engineer may implement announcement forwarding on spines based on the identity of the neighbor, \IE, do not announce externally anything heard from local aggregators.
-This implementation is appealing because it does not require changes to spine configurations when ToR prefixes change.
-But it works correctly only when there are no failures; local prefixes can leak externally when failures disconnect a spine from both aggregators in a local pod.
-Specifically, when S1 is disconnected from A5 and A6, it may hear about P5 and P6 from A3 and A4 (via A[5--6]->S2->A[3--4]), and it will then announce those prefixes outside (since they no not come from a local aggregator), leading to a policy violation.
-A possible correct implementation here would be for each spine to block messages headed to external peers from local aggregators {\em and} to reject announcements that have traversed the other spine (\IE, to disallow "valleys," or up-down-up paths).
-
-%Lacking correctness guarantees, engineers use simulations to analyze if templates are correct under a range of failure cases (e.g., combinations of two-link failures), but such analysis is highly expensive for large networks and still does not provide strong guarantees beyond the tested cases.
-
-The second limitation of today's template systems is that, like concrete synthesis tools, they do not support network evolution.
-One might hope that important network properties such as connectivity and fault tolerance persist when networks evolve in ways consistent with existing roles and templates.
-However, existing
-template systems provide no guarantees that seemingly-minor variations of a given topology have similar properties.
-%In theory, templates do not have to be redesigned when the network evolves while keeping its basic structure of roles and their inter-connectivity.
-In practice, however, it is not guaranteed that templates that work for a given topology also work for seemingly-minor variations of the topology.
-
-Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}, with the same folded-Clos structure and five roles.
-One might think that the same templates (with different database entries) can be re-used across topologies.
-However, that is not necessarily true.
-For example,
-data centers are often susceptable to a phenomenon called an \emph{aggregation-induced black hole}~\cite{route-aggregation}.
-Such black holes occur when a switch announces an aggregate prefix but has no valid path to a more specific prefix within the aggregate, so the black hole will draw traffic, but that traffic will be unable
-to reach its destination.
-For instance, if a network operator uses templates designed for Figure~\ref{fig:example}, which
-disallow valley paths, on Figure~\ref{fig:example2}, they will find that while it takes two link failures to
-trigger a black hole in  Figure~\ref{fig:example}, it takes only 1 failure to trigger a black hole in
- Figure~\ref{fig:example2}.
-More specifically, in Figure~\ref{fig:example2}, a blackhole will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes by virtue of announcing the encompassing aggregate PG.
-In contrast, in Figure~\ref{fig:example}, no such blackhole will occur after a single failure.
-
-Thus, engineers today must reason about the correctness of templates for each topology change (using expensive simulations because current systems do not provide any correctness guarantee by design).
-Worse, for some changes, they may discover that their old templates will not work anymore and need modifications.
-~\dpw{Note: This is going to be true for Methane too.}  This discovery is highly problematic because changing a template will cause a change in the configurations of all the devices that use that template---in many cases, an unacceptable disruption.
-When that happens, network operators may abandon templates entirely and revert to hand-crafting configuration files, using localized patches to accommodate evolution.
-Such patches reintroduce the complexity and errors that templates were meant to prevent.
-
 %As an aside, a possible template implementation that works correctly for both networks is: allow valley paths and use an explicit list of local prefixes at spines to decide which announcements should not be forwarded externally.
 
-\begin{figure}
-\begin{tabular}{|p{0.6in}|p{0.6in}p{0.7in}p{0.6in}|}
-\hline
-& Abstract Roles & Correctness Guarantees & Evolution Support  \\ \hline
-Concrete Synthesis & \xmark & \cmark & \xmark \\ \hline
-Template Systems & \cmark & \xmark & \xmark \\ \hline
-\sysname & \cmark & \cmark & \cmark \\  \hline
-\end{tabular}
-\caption{Comparing configuration techniques.}
-\label{fig:marketing}
-\end{figure}
-
-\subsection{\sysnamesec}
-
-As Table~\ref{fig:marketing} shows, \sysname addresses the limitations of both concrete synthesis and current template systems.
+%\begin{figure}
+%\begin{tabular}{|p{0.6in}|p{0.6in}p{0.7in}p{0.6in}|}
+%\hline
+%& Abstract Roles & Correctness Guarantees & Evolution Support  \\ \hline
+%Concrete Synthesis & \xmark & \cmark & \xmark \\ \hline
+%Template Systems & \cmark & \xmark & \xmark \\ \hline
+%\sysname & \cmark & \cmark & \cmark \\  \hline
+%\end{tabular}
+%\caption{Comparing configuration techniques.}
+%\label{fig:marketing}
+%\end{figure}
+
+%\subsection{\sysnamesec}
+%
+%As Table~\ref{fig:marketing} shows, \sysname addresses the limitations of both concrete synthesis and current template systems.
 It operates at the right level of abstraction for network operators, provides strong guarantees about compiled configurations, supports verification of important correctness properties, and supports network evolution.
-As inputs, \sysname takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an
-{\em abstract} topology that describes device roles and
-connectivity invariants.  It outputs a template for each role.  Per-device configurations may be generated
-from templates by instantiating their parameters with concrete values drawn from the network topology.
-\sysname provides strong guarantees about its templates:
-(1) the configurations generated from them correctly implement the specified policy for {\em any} concrete topology that matches the given abstract topology; and (2) if you add or remove a single node or edge in a way compatible
-with the abstract topology, only configurations of adjacent devices ever need to be updated.
-
-The next section introduces \sysname using the example in Figure~\ref{fig:example}, and the following sections provide more detail on how we generate the templates and formally define the correctness guarantees.
 
@@
 
-As we have seen, writing correct network configurations is challenging task.
+\sysname is a system to generate provably-correct templates.
+As inputs, it takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an {\em abstract} topology that describes device roles and
+connectivity invariants.  It outputs a template for each role, from which per-device configurations can be generated by instantiating parameters with values drawn from the network topology.
+\sysname provides strong guarantees about its templates:
+(1) the configurations generated from them correctly implement the specified policy for {\em any} concrete topology that matches the given abstract topology; and (2) if nodes or edges are added or removed in a way compatible
+with the abstract topology, only configurations of adjacent devices ever need to be updated.
+
+This section introduces \sysname using the example in Figure~\ref{fig:example}, and the following sections detail template generation and formally define the correctness guarantees.
+
+%As we have seen, writing correct network configurations is challenging task.
 Operators must manually decompose network-wide policies into distributed device configurations, reason about all combinations of network failures, and parameterize configurations to allow for change, ideally in a way that is amenable to incremental change.
@@
 
-The spine switches have a default rule for the prefix $0.0.0.0/[0..32]$ that will match advertisements from peer $P1$ and $P2$.
+The spine routers have a default rule for the prefix $0.0.0.0/[0..32]$ that will match advertisements from peer $P1$ and $P2$.
 The match for $P1$ is preferred since it has a higher BGP local-preference attribtue (110).
@@
     \node at (#1, 3.3) {#4};
-    \draw [] (#1, 2.5) circle [radius=0.45] node {$m$};
-    \draw [] (#1, 0) circle [radius=0.45] node {$n$};
+    \draw [] (#1, 2.5) circle [radius=0.45] node {$n$};
+    \draw [] (#1, 0) circle [radius=0.45] node {$m$};
     \draw [] (#1, .45) -- (#1, 2.05);
@@
   \caption{Abstract k-disjoint path analysis inference rules.}
-  \label{fig:abstract-analysis}
+  \label{fig:inference-rules}
   %\vspace{-1em}
@@
 
-For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of size 2 concrete routers in role TL such that they each have 4 disjoint to them from the source and all 8 paths are disjoint.
-
-%suppose we want to compute the number of disjoint paths from the local ToR role $(TL,0,0)$ for
-\ryan{TODO: probably need a new image for local prefixes?}
+For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of size 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.
+
+In order to learn information about disjoint paths between routers, we develop a series of sound inference rules for facts of the above form.
+Figure~\ref{fig:inference-rules} shows each of the inference rules.
 
@@
 
-Hypercube variants can be used as an alternative to Clos-style topologies for networks with high-radix (port density) switches.
+Hypercube variants can be used as an alternative to Clos-style topologies for networks with high-radix (port density) routers.
 The HyperX topology can be viewed as a generalization of the hypercube, which includes parameters $L$ for the lattice dimension of the network, $S_i$ for the node multiplicity of each dimension $i$, $K_i$ for the bandwidth of links for each dimension, and $T$ for the number of terminal nodes (servers) connected to each router.
@@
 However, because the topologies are created randomly, there are no hard guarantees on the connectivity between different routers.
-We can trivially represent these networks using a \emph{one big switch} abstraction for the entire network.
+We can trivially represent these networks using a \emph{one big router} abstraction for the entire network.
 

### 2016-11-04 paper/abstraction/paper.tex
updates

@@
     \node at (#1, 3.3) {#4};
-    \draw [] (#1, 2.5) circle [radius=0.45] node {$n$};
-    \draw [] (#1, 0) circle [radius=0.45] node {$m$};
+    \draw [] (#1, 2.5) circle [radius=0.45] node {$m$};
+    \draw [] (#1, 0) circle [radius=0.45] node {$n$};
     \draw [] (#1, .45) -- (#1, 2.05);
@@
   \caption{Abstract k-disjoint path analysis inference rules.}
-  \label{fig:inference-rules}
+  \label{fig:abstract-analysis}
   %\vspace{-1em}
@@
 
-For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of size 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.
-
-In order to learn information about disjoint paths between routers, we develop a series of sound inference rules for facts of the above form.
-Figure~\ref{fig:inference-rules} shows each of the inference rules.
+For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of size 2 concrete routers in role TL such that they each have 4 disjoint to them from the source and all 8 paths are disjoint.
+
+%suppose we want to compute the number of disjoint paths from the local ToR role $(TL,0,0)$ for
+\ryan{TODO: probably need a new image for local prefixes?}
 

### 2016-11-04 paper/abstraction/paper.tex
stashing changes
rework inference rules
add local and global pod inference rules

--- 2016-11-04 paper/abstraction/paper.tex
@@
 
-\newcommand{\inference}[4]{
+\newcommand{\inference}[7]{
     \node[draw, anchor=west] at (#1 + .4, 1.25) {#3};
-    \node at (#1 + .34, .6) {$e_1$};
-    \node at (#1 + .34, 1.9) {$e_2$};
+    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{#5}};
+    \node at (#1 + .34, .6) {#6};
+    \node at (#1 + .34, 1.9) {#7};
     \node at (#1, -.8) {#2};
@@
     \draw [] (#1, 0) circle [radius=0.45] node {$m$};
-    \draw [] (#1, .45) -- (#1, 2.05);
+    \draw [->] (#1, .45) -- (#1, 2.05);
 }
 
+\newcommand{\inferencenobox}[7]{
+    \node[anchor=west] at (#1 + .4, 1.25) {#3};
+    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{#5}};
+    \node at (#1 + .34, .6) {#6};
+    \node at (#1 + .34, 1.9) {#7};
+    \node at (#1, -.8) {#2};
+    \node at (#1, 3.3) {#4};
+    \draw [] (#1, 2.5 - .2) circle [radius=0.45] node {$n$};
+    \draw [] (#1, .2) circle [radius=0.45] node {$m$};
+    \draw [->] (#1, .2 + .45) -- (#1, 2.5 - .45 - .2);
+}
+
+\newcommand{\inferencetwo}[1]{
+    \node[draw, anchor=west] at (#1 + 2, 1.25) {$e_i > 0$};
+    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{I-striping}};
+    \node at (#1 - 1 - .11, .6) {$e_1$};
+    \node at (#1 + .11, 1.9) {$e_2$};
+    \node at (#1 + 2 + .11, .6) {$e_3$};
+    \node at (#1 + .11 + .8, 1.9) {$e_4$};
+    \node at (#1 - 1, -.8) {L$(j,k)$};
+    \node at (#1 +. 5, 3.3) {S$(min(j*k,g),1)$};
+    \node at (#1 + 2, -.8) {L$\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
+    \node at (#1, 3.3) {};
+    \draw [] (#1 + .5, 2.5) circle [radius=0.45] node {$n$};
+    \draw [] (#1 - 1, 0) circle [radius=0.45] node {$m$};
+    \draw [] (#1 + 2, 0) circle [radius=0.45] node {$o$};
+    \draw [->] (#1 - 1, .45) -- (#1 + .5, 2.05);
+    \draw [<-] (#1 + 2, .45) -- (#1 + .5, 2.05);
+}
+
+\newcommand{\inferencelocal}[1]{
+    \inferencenobox{#1}{L$_1(j,k)$}{}{L$_2(j',k')$}{I-local}{}{}
+    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_1(j,k)$}{}{$\ldots$ L$_P$ L$_2(j',k')$}{}{}{}
+    \node[anchor=east] at (#1 + 3 - .6, 2.6) {P};
+    \draw[dashed] (#1+2 - .2, -.44) rectangle (#1+3+1 + .1, 2.95);
+}
+
+\newcommand{\inferenceglobal}[1]{
+    \inferencenobox{#1}{L$_1(j,k)$}{}{L$_2(j',k')$}{I-global}{}{}
+    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_1(j,k)$}{}{$\ldots$ A$_P$ L$_2(j',k')$}{}{}{}  
+    \node[anchor=east] at (#1 + 3 - .6, .54) {P};  
+    \node[anchor=east] at (#1 + 3 - .6, 2.6) {Q};
+    \draw[dashed] (#1+2 - .2, -.44) rectangle (#1+3+1 + .1, .9);
+    \draw[dashed] (#1+2 - .2, 1.6) rectangle (#1+3+1 + .1, 2.95);
+}
+
 \begin{figure*}[t!]
-  \begin{minipage}[t]{.5\linewidth}%
+  \begin{minipage}[t]{\linewidth}%
   \begin{tikzpicture}
-    \inference{0}{L$(j,k)$}{$\vDash e_1 > 0$}{S$(min(j*k,e_1),1)$}
-    \inference{5}{A$(j,k)$}{$e_2 > 0$}{A$(1,min(j,e2))$}
-    \inference{10}{L$(j,k)$}{$e_1=n$}{A$(min(j*k,n),1)$}
-    \inference{15}{L$(j,k)$}{$e_1=n$}{A$(1,j)$}
+    \inference{0}{L$(j,k)$}{$e_1 > 0$}{S$(min(j*k,e_1),1)$}{I-out1}{$e_1$}{$e_2$}
+    \inference{4.5}{A$(j,k)$}{$e_2 > 0$}{A$(1,min(j,e2))$}{I-out2}{$e_1$}{$e_2$}
+    \inference{9}{L$(j,k)$}{$e_1=n$}{A$(min(j*k,n),1)$}{I-mesh1}{$e_1$}{$e_2$}
+    \inference{13.5}{L$(j,k)$}{$e_1=n$}{A$(1,j)$}{I-mesh2}{$e_1$}{$e_2$}
   \end{tikzpicture}
@@
 
-  %
-  \vspace*{3em}
-  %
-  \begin{minipage}[t]{.5\linewidth}%
+  \vspace*{1em}
+  \begin{minipage}[t]{\linewidth}%
   \begin{tikzpicture}
-    \inference{0}{L$(j,k)$}{$e_1 > 0$, $e_2 > 0$}{S$(min(j*k,n-\dfrac{(m-j)*e_1}{e_2}),1)$}
-    \inference{10}{L$(j,k)$ ~~~ L$(j- m ~\text{mod}~ \big(\dfrac{n}{e_1}\big),1)$}{$e_1 > 0$, $e_2 > 0$}{}
+    % \inference{0}{L$(j,k)$}{$e_i > 0$}{S$(min(j*k,g),1)$}{I-out3}{$e_1$}{$e_2$}
+    \inferencetwo{0}
+    \node[anchor=west] at (2,2.4) {where $g=n-\dfrac{(m-j)*e_1}{e_2}$};
+    \inference{11}{L$(j,k)$}{$bisec(X)$}{A$(1,min(k,X))$}{I-bisec}{}{}
   \end{tikzpicture}
@@
   \vspace*{1em}
+  \begin{minipage}[t]{\linewidth}%
+  \begin{tikzpicture}
+    \inferencelocal{0}
+    \inferenceglobal{10}
+  \end{tikzpicture}
+  \end{minipage}
+
   \hrule
   \vspace*{1em}
-  \caption{Abstract k-disjoint path analysis inference rules.}
+  \caption{Abstract k-disjoint path analysis inference rules. \ryan{added bisec idea a possibility, we can remove this}}
   \label{fig:inference-rules}
@@
 
-In order to learn information about disjoint paths between routers, we develop a series of sound inference rules for facts of the above form.
+\subsection{Inference rules}
+
+In order to learn information about disjoint paths between routers, we develop a series of sound inference rules for facts of this form.
 Figure~\ref{fig:inference-rules} shows each of the inference rules.
@@
 
-\begin{figure}
+\begin{figure}[t!]
   \subcaptionbox{Datacenter}
@@
 
-\begin{figure*}[t]\small
+\begin{figure*}[t!]\small
   \begin{minipage}[t]{.45\linewidth}

### 2016-11-04 paper/abstraction/paper.tex
add inference rule explanations

@@
 \newcommand{\inference}[7]{
-    \node[draw, anchor=west] at (#1 + .4, 1.25) {#3};
+    \node[draw, anchor=west] at (#1 + .5, 2.5 / 2) {#3};
+    \node[anchor=east] at (#1 - .4, 2.5 / 2) {\textbf{#5}};
+    \node at (#1 + .34, .6 + .2) {#6};
+    \node at (#1 + .34, 1.9 - .2) {#7};
+    \node at (#1, -.6) {#2};
+    \node at (#1, 2.5 + .4 + .2) {#4};
+    \draw [] (#1, 2.5 - .2) circle [radius=0.4] node {$n$};
+    \draw [] (#1, .2) circle [radius=0.4] node {$m$};
+    \draw [->] (#1, .4 + .2) -- (#1, 2.5 - .4 - .2);
+}
+
+\newcommand{\inferencenobox}[7]{
+    \node[anchor=west] at (#1 + .1, 1.25) {#3};
     \node[anchor=east] at (#1 - .4, 1.25) {\textbf{#5}};
@@
     \node at (#1 + .34, 1.9) {#7};
-    \node at (#1, -.8) {#2};
-    \node at (#1, 3.3) {#4};
-    \draw [] (#1, 2.5) circle [radius=0.45] node {$n$};
-    \draw [] (#1, 0) circle [radius=0.45] node {$m$};
-    \draw [->] (#1, .45) -- (#1, 2.05);
-}
-
-\newcommand{\inferencenobox}[7]{
-    \node[anchor=west] at (#1 + .4, 1.25) {#3};
-    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{#5}};
-    \node at (#1 + .34, .6) {#6};
-    \node at (#1 + .34, 1.9) {#7};
-    \node at (#1, -.8) {#2};
-    \node at (#1, 3.3) {#4};
-    \draw [] (#1, 2.5 - .2) circle [radius=0.45] node {$n$};
-    \draw [] (#1, .2) circle [radius=0.45] node {$m$};
-    \draw [->] (#1, .2 + .45) -- (#1, 2.5 - .45 - .2);
+    \node at (#1, -.6) {#2};
+    \node at (#1, 2.5 + .4 + .2) {#4};
+    \draw [] (#1, 2.5 - .2) circle [radius=0.4] node {$n$};
+    \draw [] (#1, .2) circle [radius=0.4] node {$m$};
+    \draw [->] (#1, .2 + .4) -- (#1, 2.5 - .4 - .2);
 }
@@
     \node at (#1 - 1 - .11, .6) {$e_1$};
-    \node at (#1 + .11, 1.9) {$e_2$};
+    \node at (#1 + .11, 1.5) {$e_2$};
     \node at (#1 + 2 + .11, .6) {$e_3$};
-    \node at (#1 + .11 + .8, 1.9) {$e_4$};
+    \node at (#1 + .11 + .8, 1.5) {$e_4$};
     \node at (#1 - 1, -.8) {L$(j,k)$};
-    \node at (#1 +. 5, 3.3) {S$(min(j*k,g),1)$};
+    \node at (#1 +. 5, 2.9) {S$(min(j*k,g),1)$};
     \node at (#1 + 2, -.8) {L$\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
     \node at (#1, 3.3) {};
-    \draw [] (#1 + .5, 2.5) circle [radius=0.45] node {$n$};
-    \draw [] (#1 - 1, 0) circle [radius=0.45] node {$m$};
-    \draw [] (#1 + 2, 0) circle [radius=0.45] node {$o$};
-    \draw [->] (#1 - 1, .45) -- (#1 + .5, 2.05);
-    \draw [<-] (#1 + 2, .45) -- (#1 + .5, 2.05);
+    \draw [] (#1 + .5, 2.01) circle [radius=0.4] node {$n$};
+    \draw [] (#1 - 1, 0) circle [radius=0.4] node {$m$};
+    \draw [] (#1 + 2, 0) circle [radius=0.4] node {$o$};
+    \draw [->] (#1 - 1, .4) -- (#1 + .5, 2 - .4);
+    \draw [<-] (#1 + 2, .4) -- (#1 + .5, 2 - .4);
 }
@@
 \newcommand{\inferencelocal}[1]{
-    \inferencenobox{#1}{L$_1(j,k)$}{}{L$_2(j',k')$}{I-local}{}{}
-    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_1(j,k)$}{}{$\ldots$ L$_P$ L$_2(j',k')$}{}{}{}
-    \node[anchor=east] at (#1 + 3 - .6, 2.6) {P};
-    \draw[dashed] (#1+2 - .2, -.44) rectangle (#1+3+1 + .1, 2.95);
+    \inferencenobox{#1}{L$_m(j,k)$}{}{L$_n(j',k')$}{I-local}{}{}
+    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_m(j,k)$}{}{$\ldots$ L$_P$ L$_n(j',k')$}{}{}{}
+    \node[anchor=east] at (#1 + 3 - .6, 2.5) {P};
+    \draw[dashed] (#1+2 - .2, -.34) rectangle (#1+3+1 + .1, 2.85);
 }
@@
     \inferencenobox{#1}{L$_1(j,k)$}{}{L$_2(j',k')$}{I-global}{}{}
-    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_1(j,k)$}{}{$\ldots$ A$_P$ L$_2(j',k')$}{}{}{}  
-    \node[anchor=east] at (#1 + 3 - .6, .54) {P};  
-    \node[anchor=east] at (#1 + 3 - .6, 2.6) {Q};
-    \draw[dashed] (#1+2 - .2, -.44) rectangle (#1+3+1 + .1, .9);
-    \draw[dashed] (#1+2 - .2, 1.6) rectangle (#1+3+1 + .1, 2.95);
+    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_m(j,k)$}{}{$\ldots$ A$_Q$ L$_n(j',k')$}{}{}{}  
+    \node[anchor=east] at (#1 + 3 - .6, .4) {P};  
+    \node[anchor=east] at (#1 + 3 - .6, 2.5) {Q};
+    \draw[dashed] (#1+2 - .2, -.34) rectangle (#1+3+1 + .1, .8);
+    \draw[dashed] (#1+2 - .2, 1.7) rectangle (#1+3+1 + .1, 2.85);
 }
@@
     \inferencetwo{0}
-    \node[anchor=west] at (2,2.4) {where $g=n-\dfrac{(m-j)*e_1}{e_2}$};
-    \inference{11}{L$(j,k)$}{$bisec(X)$}{A$(1,min(k,X))$}{I-bisec}{}{}
+    \node[anchor=west] at (2,2) {where $g=n-\dfrac{(m-j)*e_1}{e_2}$};
+    \inferencenobox{11}{L$(j,k)$}{$bisec(X)$}{A$(1,min(k,X))$}{I-bisec}{}{}
   \end{tikzpicture}
@@
 
+\newcommand{\infrule}[1]{{\small \sf #1}\xspace}
+
 In order to learn information about disjoint paths between routers, we develop a series of sound inference rules for facts of this form.
 Figure~\ref{fig:inference-rules} shows each of the inference rules.
+The rules are read from bottom to top.
+The label on the bottom left corresponds to a known fact of the form $L(j,k)$.
+We use $L$ to represent a rule that is parametric over the particular label.
+The labels on other nodes correspond to learned facts from applying the inference rule.
+Conditions that must be \emph{valid} for the node and edge multiplicities are shown in a box.
+
+In general, the inference rules try to learn information about (1) the largest number of disjoint paths to any single node in an abstract role and (2) the largest reachable group in a particular role with at least one disjoint path to each as this tends to be a valuable invariant.
+
+The first rule, \infrule{I-out1} applies to a learned fact of the form L$(j,k)$ where the number of out edges at the current node is greater than 0.
+In the worst case, the largest group of nodes we could hope to reach at the top node would be $e_1$ since all j nodes at the bottom may have the same outgoing edges to the nodes at the top.
+Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$.
+Since adding edges from between the nodes keeps the existing paths disjoint, and since we can not exceed the current number of disjoint paths to the node on the bottom, the largest reachable group for the top node will be $min(j*k,e_1)$.
+However, since we do not know for certain that all $j$ nodes have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
+
+The rule \infrule{I-out2} follows a similar line of reasoning.
+It says that if any group of size $j$ with $k$ disjoint paths to each is reachable in the bottom node, and there is at least one incoming edge for each top node, then there are $min(j,e_2)$ disjoint paths to any single node in the top role.
+This is because we can choose the $j$ nodes on the bottom for which we want to find disjoint paths, and then use each of the $e_2$ incoming edges for the particular node at the top connecting it to the bottom, which preserve the disjointedness.
+
+The two rules \infrule{I-mesh1} and \infrule{I-mesh2} handle the case where there is a full mesh between the two roles.
+This happens when the number of outgoing edges from the bottom $e_1$ is equal to the number of nodes on the top $n$.
+The first case for \infrule{I-mesh1} says that we can find disjoint paths to each node in the top role restricted to the number of disjoint paths we started with.
+The second case for \infrule{I-mesh2} uses the fact that each node in the top role is connected to each node in the bottom role to infer that there can be $j$ disjoint paths to any single node in the top role.
+
+The rule \infrule{I-striping} is the most complicated case.
+It starts with the fact L$(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid.
+The first inference for role $n$ tries to find the largest reachable group with disjoint paths to each.
+The idea is similar to the rule \infrule{I-out1}, but is able to use the fact that $e_2 > 0$ to learn more about the structure of the concrete topology.
+In particular it uses the following inequality, where $g$ represents the size of the group for the top role:
+%
+\[ \begin{array}{c}
+  (m-j)*e_1 \geq (n-g)*e_2
+\end{array} \]
+\noindent
+%
+This captures the fact that the remaining nodes ($m-j$) for which we are not considering, each have $e_1$ outgoing edges and must be able to fill the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each.
+Solving the inequality yields:
+%
+\[ \begin{array}{c}
+  g \geq n - \dfrac{(m-j)*e_1}{e_2}
+\end{array} \]
+\noindent
+%
+The second part of the rule allows uses a similar idea to reason about the "striping", or overlap between roles $m$ and $o$ with respect to role $n$.
+Often times this rule is applied when $m$ and $o$ are in fact the same role.
+
+The rule \infrule{I-bisec} can be thought of as a programmer assertion about the bisection between two roles.
+The rule applies to an edge that has been annotated with a $bisec(X)$ statement, which means that there are $X$ disjoint paths between any node in role $m$ and any node in role $n$.
+Annotations of this form are useful for a "one big switch" type of abstraction where part of a complex network is abstracted into a single node.
+
+Finally, the \infrule{I-local} and \infrule{I-global} rules allow us to lift each of the other rules to reason across pod hierarchies.
+The first rule, \infrule{I-local}, says that if you have an inference from L$_m(j,k)$ to L$_n(j',k')$ on the left, then if both nodes are in the same local pod P, you can leave all labels up to P unchanged.
+The global rule \infrule{I-global} says the same thing except when the edge goes between pods, you can infer the fact for all pods Q since the multiplicities apply equally to each pod.
+
+\subsection{An inference algorithm}
+
+The abstract disjoint path analysis computes
 

### 2016-11-04 paper/abstraction/paper.tex
explain algorithm via example

@@
 
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=.66\columnwidth]{figures/analysis}
-  \end{center}
-  \caption{Abstract disjoint path analysis with valleyfree routing for global prefixes. \label{fig:compilation-times}}
-  \vspace{-1em}
-\end{figure}
-
 For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of size 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.
@@
 
-The abstract disjoint path analysis computes
+The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies the inference rules from Figure~\ref{fig:inference-rules} until a fixed point is reached.
+Inference rule conditions are checked for validity over all concrete topologies using the Z3 \ryan{cite} SMT solver.
+In order to ensure termination, we make the observation that, for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
+Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the Z3 optimizing constraint solver.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=.66\columnwidth]{figures/analysis}
+  \end{center}
+  \caption{Abstract disjoint path analysis with valleyfree routing for global prefixes. \label{fig:compilation-times}}
+  \label{fig:example-inference}
+  \vspace{-1em}
+\end{figure}
+
+Consider again the datacenter example from \S\ref{sec:overview}. For global prefixes we used the routing policy:
+%
+\[ \begin{array}{c}
+  \$PG \Path end(TG)
+\end{array} \]
+\noindent
+%
+Suppose now we additionally add the valleyfree constraint that traffic never has takes a path with a down-up in it.
+Figure~\ref{fig:example-inference} shows the abstract product graph representation for this routing policy.
+The inference algorith starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$
+\ryan{todo}
 

### 2016-11-05 paper/abstraction/paper.tex
add analysis example

@@
     \node at (#1 +. 5, 2.9) {S$(min(j*k,g),1)$};
-    \node at (#1 + 2, -.8) {L$\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
+    \node at (#1 + 2, -.8) {S$\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
     \node at (#1, 3.3) {};
@@
 The rule applies to an edge that has been annotated with a $bisec(X)$ statement, which means that there are $X$ disjoint paths between any node in role $m$ and any node in role $n$.
-Annotations of this form are useful for a "one big switch" type of abstraction where part of a complex network is abstracted into a single node.
+Annotations of this form are useful for a "one big switch" \ryan{cite} type of abstraction where part of a complex network is abstracted into a single node.
 
@@
   \begin{center}
-    \includegraphics[width=.66\columnwidth]{figures/analysis}
+    \includegraphics[width=\columnwidth]{figures/analysis}
   \end{center}
@@
 Figure~\ref{fig:example-inference} shows the abstract product graph representation for this routing policy.
-The inference algorith starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$
-\ryan{todo}
+The inference algorithm starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$ (\IE, no restriction on the number of disjoint paths initially).
+%
+The first step applies the rule \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles.
+This invokes a call to Z3Opt to minimize the expression $min(\infty, AG)$, which gives us 2.
+Therefore, the algorithm learns a new invariant of the form $S_P A_{AG} (2,1)$ for node $(AG, 0)$ to indicate that in some pod P, any group of 2 nodes is reachable.
+%
+The next step uses the inference rule \infrule{I-out2} to learn that any single spine node is reachable.
+It also can apply rule \infrule{I-striping} to determine that there is some group of at least 2 spine routers reachable at node $(S,0)$ and also that there is some group of at least 2 nodes reachable in the AL role in state $(AL,0)$.
+
+\ryan{inference should only infer some}
+
+Note that, because each inference rule only applies to directed edges in the product graph, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
+It is this restriction that ensures that the analysis is both topology and policy dependent.
+
+The next step is to use \infrule{I-mesh2} together with \infrule{I-local} to infer than any single node in the TL role for any pod P is reachable via at least 2 disjoint paths.
+This process will continue until a fixed point is reached.
+
+In this case, the algorithm was able to infer that, with the valleyfree routing policy, any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a prefix originator in role TG.
+Note that, in this case, the analysis is precise.
+There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router.
+In this case, the analysis can be used to determine the number of failures that can induce an aggregation black-hole at the border of the datacenter.
 

### 2016-11-05 paper/abstraction/paper.tex
cleanup some fonts

@@
 For example, the predicate $\True$ becomes $0.0.0.0/[0..32]$.
-Preferences are lifted to the top level of the regular expression when unambiguous.
-For example, the constraint $\Exit(\sf{Peer1} \Prefer \sf{Peer2})$ becomes $\Exit(\sf{Peer1}) \Prefer \Exit(\sf{Peer2})$ before being rewritten into regular expressions.
+Preferences are lifted to the top level of the regular expression when their use is unambiguous.
+For example, the constraint $\Exit\CD{(Peer1} ~\Prefer~ \CD{Peer2)}$ becomes $\Exit\CD{(Peer1)} \Prefer~ \Exit\CD{(Peer2)}$ before being rewritten into regular expressions.
 Each modular set of constraints are joined prefix-by-prefix by taking the intersection of their constraints.
@@
 %
-Finally, each constraint desugars to a regular expression. For example, the constraint $\Always(\In)$ becomes $\In^*$ and the constraint $\End({\small \mathsf{T0}})$ becomes $\Sigma^* \cdot \sf{T0}$.
+Finally, each constraint desugars to a regular expression. For example, the constraint $\Always\CD{(\In)}$ becomes $\In^*$ and the constraint $\CD{\End(T0)}$ becomes $\mathtt{\Sigma}^* \cdot \CD{T0}$.
 
@@
 
-For each regular expression $r_i$ from $r_1 ~\Prefer~ ..
+For each regular expression constraint $r_i$ from $r_1 ~\Prefer~ ..
 ~\Prefer~ r_k$, we construct a DFA for the reverse of $r_i$.
 An automaton for $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma = G^A$ is the set of topology locations, $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+The alphabet $\Sigma = G^A$ is the set of topology locations for the abstraction, $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
 %
@@
 %
-The first automaton represents the more preferred constraint $\Exit(Peer1)$ and the second automaton represents the less preferred constraint $\Exit(Peer2)$.
+The first automaton represents the more preferred constraint $\CD{\Exit(Peer1)}$ and the second automaton represents the less preferred constraint $\CD{\Exit(Peer2)}$.
 The Product Graph representation is shown for both an instance of a concrete network matching the abstraction from \S\ref{sec:overview} as well as for the abstraction itself.
@@
 
-For example, in the concrete product graph we have $(S1,0,1) \leq (S1,1,0)$ since nodes on the left side of the product graph can always match transitions made on the right hand side while always maintaining a node ranking that is at least as good as that on the right hand side (since they match the preferred rank 1 automaton).
+For example, in the concrete product graph the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the product graph can always match transitions made on the right hand side while always maintaining a node ranking that is at least as good as that on the right hand side (since they match the preferred rank 1 automaton).
 This relation does not hold the other way around.
@@
 
-Notice also that in the abstract product graph, node $(S,0,1) \leq (S,1,0)$. This leads us the the following observation:
+Notice also that in the abstract product graph the inequality $(S,0,1) \leq (S,1,0)$ holds. This leads us the the following observation:
 
@@
 
-Consider again the datacenter example from \S\ref{sec:overview}. For global prefixes we used the routing policy:
-%
-\[ \begin{array}{c}
-  \$PG \Path end(TG)
-\end{array} \]
+Consider again the datacenter example from \S\ref{sec:overview}.
+Suppose now we add the valleyfree constraint that traffic never has takes a path with a down-up in it for the routing policy for global prefixes:
+%
+\begin{code}
+\$GP  \Path \End(TG) \ensuremath{\cap} \Novalley(\{TG,TL\},\{AG,AL\},\{S\})
+\end{code}
 \noindent
 %
-Suppose now we additionally add the valleyfree constraint that traffic never has takes a path with a down-up in it.
 Figure~\ref{fig:example-inference} shows the abstract product graph representation for this routing policy.
@@
 It also can apply rule \infrule{I-striping} to determine that there is some group of at least 2 spine routers reachable at node $(S,0)$ and also that there is some group of at least 2 nodes reachable in the AL role in state $(AL,0)$.
-
-\ryan{inference should only infer some}
 

### 2016-11-06 paper/abstraction/appendix.tex
add part of appendix

\documentclass[twocolumn]{sig-alternate-10pt}
%\documentclass[twocolumn]{article}
%\documentclass[10pt]{sigalternate052015}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{url}
\usepackage{times}
\usepackage{xspace}
\usepackage{listings}
\usepackage{code}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning}
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{balance}
\usepackage[ampersand]{easylist}
\usepackage{textcomp}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

\definecolor{princetonorange}{RGB}{255,143,0}
\definecolor{tmlblue}{RGB}{0,58,120}  % tmlblue == Toronto Maple Leafs Blue!

\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\newcommand{\ratul}[1]{\textcolor{blue}{[ratul: #1]}}
\newcommand{\ryan}[1]{\textcolor{green}{[ryan: #1]}}
\newcommand{\dpw}[1]{\textcolor{tmlblue}{[dpw: #1]}}
\newcommand{\todd}[1]{\textcolor{princetonorange}{[todd: #1]}}

\newcommand{\EG}{\emph{e.g.}}
\newcommand{\IE}{\emph{i.e.}}
\newcommand{\ETC}{\emph{etc.}}
\newcommand{\ETAL}{\emph{et al.}}

\newcommand{\sysname}{{\small \sf Methane}\xspace}
\newcommand{\sysnamesec}{{\sf Methane}\xspace}
\newcommand{\propane}{{\small \sf Propane}\xspace}

\newcommand{\para}[1]{\paragraph*{\textbf{#1}}}

\newcommand{\set}[1]{\ensuremath{\{ #1 \} }}
\newcommand{\abs}[1]{\ensuremath{ \lvert #1 \rvert }}

\newcommand{\CD}[1]{\texttt{\small #1}}  % code font
\newcommand{\KW}[1]{\texttt{\small\bfseries{#1}}}

\newcommand{\True}{\CD{true}}
\newcommand{\Define}{\KW{define}}
\newcommand{\Prefer}{\texttt{>>}}
\newcommand{\Path}{\texttt{=>}}
\newcommand{\Link}{\texttt{->}}
\newcommand{\Agg}{\KW{agg}}
\newcommand{\Any}{\KW{any}}
\newcommand{\None}{\KW{drop}}
\newcommand{\In}{\KW{in}}
\newcommand{\Out}{\KW{out}}
\newcommand{\AND}{\texttt{\&}}
\newcommand{\OR}{\texttt{|}}
\newcommand{\NOT}{\texttt{!}}
\newcommand{\Intersect}{\ensuremath{\cap}}
\newcommand{\Union}{\ensuremath{\cup}}

\newcommand{\Exit}{\KW{exit}}
\newcommand{\End}{\KW{end}}
\newcommand{\Start}{\KW{start}}
\newcommand{\Enter}{\KW{enter}}
\newcommand{\Eventually}{\KW{eventually}}
\newcommand{\Already}{\KW{already}}
\newcommand{\Internal}{\KW{internal}}
\newcommand{\Never}{\KW{never}}
\newcommand{\Always}{\KW{always}}
\newcommand{\Through}{\KW{through}}
\newcommand{\LinkKW}{\KW{link}}
\newcommand{\PathKW}{\KW{path}}
\newcommand{\Novalley}{\KW{novalley}}

\renewcommand{\path}[2]{ #1 \mapsto \ensuremath{#2} }

%% grammar
\newcommand{\BNFALT}{\;\;|\;\;}
\newcommand{\hdr}[2]{\flushleft \chdr{\hspace{5mm}#1}{#2}}
\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}%

\newtheorem{thm}{Theorem}[section]
\newtheorem{defn}{Definition}
\newtheorem{lem}[thm]{Lemma}

\begin{document}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\appendix

\onecolumn
\section{Preliminaries}

\subsection{Methane}

The full \sysname syntax as well as expansions from constraints into regular expressions are shown in Figure~\ref{fig:syntax}. The language includes constraints of the form $\CD{\Agg(pfx, \ensuremath{r_1 \rightarrow r_2})}$ that say that aggregation for summary prefix $\CD{pfx}$ will occur from any single location matching $\CD{\ensuremath{r_1}}$ to any location matching $\CD{\ensuremath{r_2}}$.

\begin{figure*}[h!]\small
  \begin{minipage}[t]{.45\linewidth}
  \hdr{Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
    \hline%

     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
     pfx     &::=& d.d.d.d/[d..d] & \textit{prefix} \\
     t       &::=& \$x & \textit{template variable} \\
         &\BNFALT& pfx & \textit{prefix test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
     cc     &::=& agg(pfx, r_1 \rightarrow r_2)  & \textit{control constraints} \\
  \end{array} \]%

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}\small
  \hdr{Expansions}{}
  \vspace*{-1\baselineskip}
  %
  \[\begin{array}{rcl}
    \hline
    \Any               & = & \Sigma^* \\
    \None              & = & \emptyset \\
    \Internal          & = & \In^+ \\
    \Always(X)         & = & X^* \\
    \Never(X)          & = & (!X)^* \\
    \Through(X)        & = & \Sigma^* \cdot X \cdot \Sigma^* \\
    \End(X)            & = & \Sigma^* \cdot X \\
    \Start(X)          & = & X \cdot \Sigma^* \\
    \Enter(X)          & = & \Sigma^* \cdot \Out \cdot (X \cap \In) \cdot \Sigma^* ~ \cup \\
                       &   & \Sigma^* \cdot (X \cap \Out) \cdot \In \cdot \Sigma^* \\
    \Exit(X)           & = & \Sigma^* \cdot \In \cdot (X \cap \Out) \cdot \Sigma^* ~ \cup \\
                       &   & \Sigma^* \cdot (X \cap \In) \cdot \Out \cdot \Sigma^* \\
    \LinkKW(X,Y)       & = & \Sigma^* \cdot X \cdot Y \cdot \Sigma^* \\
    \PathKW(\vec{X})   & = & \Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^* \\
    \Novalley(\vec{X}) & = & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
                       &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
  \end{array} \]%

  \end{minipage}%

  \hrulefill%
  \vspace{1em}

  \caption{Methane syntax and expansions.}
  \label{fig:syntax}
  %\vspace{-1em}
\end{figure*}%

\subsection{BGP Configuration}

We define syntax for an abstraction of BGP configurations -- called ABGP -- in Figure~\ref{fig:abgp-syntax}. An ABGP policy consists of a map from topology locations $l$ to router configurations $rc$. Each router configuration $rc$ is a sequence of prefix (templates) $t$ and their corresponding prefix configuration $pc$. A prefix configuration $pc$ is a sequence of match actions $ma$. Each match action $ma$ consists of a preference value $n$, followed by a set of peers $ns$ and community value (\IE, state of the product graph) $n$, and the exports the route to a new set of neighbors $ns$ and updates the community value $n$.

\vspace{2em}
\begin{figure}[h!]\small

  \hrulefill%
  \vspace{1em}

  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
  \end{array} \]%

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}(PG,ord) = \{ \\
     ~~~~~ \{ l \rightarrow rc ~\vert \\
     ~~~~~~~~~ l \in internal(V) \\
     ~~~~~~~~~ m = (l,q_m) \in PG, \\
     ~~~~~~~~~ in = \{ b_i ~\vert~ n_i = (b_i,q_n) \in \text{adjIn}(PG,m) \} \\
     ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG,m) \} \\
     ~~~~~~~~~ rc = ord(m) : (in,q_n) \rightarrow (out,q_m) \\

     ~~~~~ \}
  \end{array} \]%

  \end{minipage}

  \vspace{1em}
  \hrulefill%
  \vspace{1em}

  \caption{Simplified BGP syntax.}
  \label{fig:abgp-syntax}
\end{figure}%

We assume a particular router $l$ appears at most once in any abgp specification.
An abgp configuration is a partial function from router to prefix configuration.
We write $abgp(l)$ to apply such a config to a router location $l$.
%
We often build configs using set-builder notation.  For instance,
$\{l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc)\}$ denotes the abgp policy

\[ \begin{array}{c}
  l_1 \rightarrow rc_{11},... \\
  ...           \\
  l_k \rightarrow rc_{1k},... \\
\end{array} \]

where $l_1, ..., l_k$ are the nodes in the topology
and each $rc_{ij}$ satisfies $p(l_i,rc_{ij})$. Similarly for $rc$.

Figure~\ref{fig:abgp-syntax} also defines the translation of the product graph $PG = (G', s, P)$ to the ABGP representation. It looks at each incoming neighbor with the same community state $q_n$ and matches any of those neighbor with the preference provided by the ordering $ord$ obtained from the search for local preferences. It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.

\subsection{Concretization}

Here we define what it means to concretize an abstract \sysname policy. 
Concretization takes as input, a policy and a map $m$ from template prefix to a set of concrete prefixes.

\[ \begin{array}{rcl}
  con(\emptyset,m)                        & = & \emptyset \\
  con(l,m)                                & = & \Sigma ~ \{ l_i \in f^{-1}(l) \} \\
  con(r_1 \cup r_2,m)                     & = & con(r_1,m) \cup con(r_2,m) \\
  con(r_1 \cap r_2,m)                     & = & con(r_1,m) \cap con(r_2,m) \\
  con(!r,m)                               & = & !con(r,m) \\
  con(r^*,m)                              & = & con(r,m)^* \\
  con(pfx \Rightarrow r_1, \dots, r_n,m)  & = & pfx \Rightarrow con(r_1,m), \dots, con(r_n,m) \\
  con(\$x \Rightarrow r_1, \dots, r_n,m)  & = & \{ pfx \Rightarrow con(r_1,m), \dots, con(r_n,m) ~\vert~ {pfx} \in m(x) \} \\
\end{array} \]

For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$. For each template variable, we replace it with a single entry for each of its corresponding concrete values under the supplied mapping $m$.
We can also define concretization over the ABGP policy as:

\[ \begin{array}{rcl}
     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,m) 
        & = & 
        \{ x \rightarrow con(rc_i,m)  ~\vert~ x \in f^{-1}(l_i) \}
        \\
     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,m) 
        & = &  
        \{ pfx \rightarrow con(pc_i,m) ~\vert~ pfx \in m(t_i) \}
        \\
     con(ma_1, \dots, ma_k,m) 
        & = &
        con(ma_1,m), \dots, con(ma_k,m)
        \\
     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),m) 
        & = & 
        n_1 : (con({ns}_1,m), n_2) \rightarrow (con({ns}_2,m),n_3)
        \\
     con(\{ l_1, ~\dots,~ l_k \}, m) 
        & = &  
        \bigcup ~ \{ f^{-1}(l_i) \}
        \\
\end{array} \]

\subsection{Notation}

Throughout the remainder of the appendix, we use the following convention for metavariables:

\[ \begin{array}{ll}
  \text{Product Graph nodes} & n,m,o \\
  \text{Topology locations} & a,b,c \\
  \text{Automata states} & q_i \\
  \text{Topologies} & G, G^A \\
  \text{Product Graph} & PG, PG^A \\
  \text{Automata} & M_i, M_i^A \\
\end{array} \]

We use capital letters for abstract topology/product graph nodes and we use lower case letters for concrete topology nodes. By default, product graph nodes with different subscripts refer to nodes that share the same topology location (\IE, $n_1 \approx n_2$). A superscript $G^A$ refers to the abstract version (in this case of the topology), while the non-superscripted value refers to the concrete version.

\section{Substitution Theorem}

The goal of this section is to prove that the concretization and compilation functions commute. That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values afterwards.

\end{document}

### 2016-11-06 paper/abstraction/paper.tex
add part of appendix

@@
 
+Foo
+
 \begin{easylist}[itemize]
@@
 
+\section{Start}
+
 \begin{figure*}[t!]\small
@@
      p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
-     x       &::=& d.d.d.d/d & \textit{prefix} \\
-     t       &::=& \True & \textit{true} \\
-         &\BNFALT& \neg t & \textit{negation} \\
+     pfx     &::=& d.d.d.d/[d..d] & \textit{prefix} \\
+     t       &::=& \$x & \textit{template variable} \\
          &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
-         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
-         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
+         &\BNFALT& pfx & \textit{prefix test} \\
      r       &::=& l & \textit{location} \\
@@
          &\BNFALT& r^* & \textit{iteration} \\
-     cc     &::=& agg(x, r_1 \rightarrow r_2)  & \textit{control constraints} \\
+     cc     &::=& agg(pfx, r_1 \rightarrow r_2)  & \textit{control constraints} \\
   \end{array} \]%
@@
     \Through(X)        & = & \Sigma^* \cdot X \cdot \Sigma^* \\
-    \Eventually(X)     & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
-    \Already(X)        & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
     \End(X)            & = & \Sigma^* \cdot X \\
@@
 
+foo
+
+\begin{figure}[t]\small
+  \begin{minipage}[t]{\linewidth}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rclr}
+     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
+     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
+     t       &::=& \$x & \textit{template variable} \\
+         &\BNFALT& d.d.d.d/[d..d] & \textit{prefix test} \\
+     r       &::=& l & \textit{location} \\
+         &\BNFALT& \emptyset & \textit{empty set} \\
+         &\BNFALT& \In & \textit{internal loc} \\
+         &\BNFALT& \Out & \textit{external loc} \\
+         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
+         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
+         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
+         &\BNFALT& \NOT r & \textit{path negation} \\
+         &\BNFALT& r^* & \textit{iteration} \\
+  \end{array} \]%
+
+  \end{minipage}
+  \vspace{1em}
+  \caption{Simplified BGP syntax.}
+  \label{fig:abgp-syntax}
+\end{figure}%
+
+blah
+
 \end{document}

### 2016-11-06 paper/abstraction/appendix.tex
start adding substitution theorem to the appendix

@@
 \onecolumn
-\section{Preliminaries}
+\section{Definitions}
 
@@
 
+\subsection{Abstraction}
+
+A network topology is a graph $G$ = ($V, E$), where $V$ is a set of vertices and $E \colon V \times V$ a set of directed edges.
+A role-based abstraction is a graph homomorphism from $G$ to an abstract graph $G^A$ = ($V^A$,$E^A$).
+A graph homorphism $f : G \rightarrow G^A$ is a function that maps each node in the concrete graph to a node in the abstract graph such that, whenever $(u,v) \in E$, then $(f(u),f(v)) \in E^A$.
+We write $f^{-1}(v)$ to denote the set of concrete nodes mapping to the abstract node $v$.
+Given a path as a sequence of locations $p = l_1, \dots, l_k$ we define $f(p) = f(l_1), \dots, f(l_k)$.
+
 \subsection{Notation}
@@
 
+\subsection{Automata}
+
+\newcommand{\Lang}{\ensuremath{\mathcal{L}}}
+
+\begin{lem}
+  For any map $m$ and regular expression $r$ over abstract locations, path $p \in \Lang(con(r,m)) \iff f(p) \in \Lang(r)$.
+\end{lem}
+\begin{proof}
+By induction on the structure of $r$
+
+\emph{Case $\emptyset$:}
+  \[ \begin{array}{lll}
+    p \in \Lang(con(\emptyset)) &\iff& f(p) \in \Lang(\emptyset) \\
+    p \in \emptyset &\iff& f(p) \in \emptyset \\
+  \end{array} \]
+
+\emph{Case $l$:}
+  \[ \begin{array}{lll}
+    p \in \Lang(con(l)) &\iff& f(p) \in \Lang(l) \\
+    p \in \Lang(\Sigma ~ f^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
+    p \in \bigcup f^{-1}(l) &\iff& f(p) \in \Lang(l) \\
+    p \in f^{-1}(l) &\iff& f(p) \in \{ l \} \\
+    p \in f^{-1}(l) &\iff& f(p) = l \\
+    \text{by homomorphism} & & \\
+  \end{array} \]
+
+\emph{Case $r_1 \cup r_2$:}
+  \[ \begin{array}{lll}
+    p \in \Lang(con(r_1 \cup r_1)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
+    p \in \Lang(con(r_1) \cup con(r_1)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
+    p \in \Lang(con(r_1)) \cup \Lang(con(r_1)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
+    p \in \Lang(con(r_1)) \vee p \in \Lang(con(r_1)) 
+       &\iff& 
+       f(p) \in \Lang(r_1) \vee f(p) \in \Lang(r_2) \\
+    \text{by cases + IH} & & \\
+  \end{array} \]
+
+\emph{Case $r_1 \cap r_2$:} 
+  \[ \begin{array}{c}
+    \text{symmetric to } \cup \text{ case}
+  \end{array} \]
+
+\emph{Case $!r$:}
+  \[ \begin{array}{lll}
+    p \in \Lang(con(!r)) &\iff& f(p) \in \Lang(!r) \\
+    p \in \Lang(!con(r)) &\iff& f(p) \in \Lang(!r) \\
+    p \in \Sigma^* - \Lang(con(r)) &\iff& f(p) \in \Sigma^* - \Lang(r) \\
+    \text{by IH} & & \\
+  \end{array} \]
+
+\emph{Case $r^*$:}
+  \[ \begin{array}{lll}
+    p \in \Lang(con(r^*)) &\iff& f(p) \in \Lang(r^*) \\
+    \ryan{TODO} & & \\
+  \end{array} \]
+
+\end{proof}
+
+\begin{defn}
+If $r$ complies to state machine $M^A$, then we compile the policy $con(r)$ in the following way:
+
+  \[ \begin{array}{ll}
+    1. & \sigma^A(q,f(l)) = q' \iff \sigma(q,l) = q' \\
+    2. & q \in F^A \iff q \in F \\
+  \end{array} \]
+
+That is, we construct a new automata over the same states and final states, but with a different transition function $\sigma$. This ensures that there is a bisimulation between the two state machines.
+
+\end{defn}
+
+\begin{lem}
+  $M^A$ matches $f(p)$ $\iff$ $M$ matches $p$.
+\end{lem}
+
+\begin{proof}
+  Suppose $M^A$ matches $f(p) = A_1, \dots, A_k$, then there exists a trace through $M^A$ of the form:
+
+  $$q_0, q_1, \dots, q_{k+1}$$
+
+  where $\sigma^A(q_i, A_i) = q_{i+1}$ and $q_{k+1} \in F^A$. We must show that $M$ matches $p = a_1, \dots, a_k$.
+
+  From the construction of the automaton, we know that $\sigma(q_i, a_i) = q_{i+1}$ and $q_{k+1} \in F \iff q_{k+1} \in F^A$. Therefore, the trace $q_0, q_1, \dots, q_{k+1}$ is accepted by $M$. 
+  %
+  The same proof is symmetric for the other direction.
+\end{proof}
+
+\begin{thm}
+  $M$ matches $p$ $\iff$ $p \in \Lang(con(r))$
+  \begin{proof}
+    \[ \begin{array}{lllr}
+      M ~\text{matches}~ p &\iff& M^A ~\text{matches}~ f(p) & \textit{previous lemma} \\
+                         &\iff& f(p) \in \Lang(r) & \textit{automaton construction} \\
+                         &\iff& p \in \Lang(con(r)) & \textit{first lemma} \\
+    \end{array} \]
+
+  \end{proof}
+\end{thm}
+
+\subsection{Product Graph}
+
+\begin{defn}
+  Because compilation guarantees that the automata states are the same under the concretization function, we can lift the graph homomorphism $f$ to a new homomorphism $f_{pg}$ over the product graph in the following way:
+  \[ \begin{array}{rcl}
+    f_{pg}( s ) & = & s^A  \\
+    f_{pg}( (l,q_1,\ldots,q_n) ) & = & (f(l),q_1,\ldots,q_n) \\
+  \end{array} \]
+\end{defn}
+
+\begin{lem}
+  If, for product graph $PG = (G,s,P)$ with $G=(V,E)$, if we have the following:
+
+  \[ \begin{array}{ll}
+    1. & (a,b) ~\text{is an edge in the concrete topology} \\
+    2. & \tilde{m} = a \\
+    3. & f_{pg}(m) = M \\
+    4. & (M,N) ~ \text{is an edge in the product graph}~ PG^A \\
+    5. & \tilde{N} = f(b) \\
+  \end{array} \]
+
+  then there exists a node $n$ in the concrete product graph $PG$ where:
+
+  \[ \begin{array}{ll}
+    1. & \tilde{n} = b \\
+    2. & f_{pg}(n) = N \\
+    3. & (m,n) ~ \text{is an edge in the product graph}~ PG \\
+    4. & P(n) = P(N) \\
+  \end{array} \]
+
+  \begin{proof}
+
+    suppose that $m = (a, q_1, \dots, q_k)$.
+Then we know that $M = (f(a), q_1, \dots, q_k)$.
+Also suppose there is some $b$ such that $N = (f(b), s_1, \dots, s_k)$ since $f^{-1}(N) \neq \emptyset$.
+This means that, since $(a,b)$ is an edge in the concrete topology, so $(f(a),f(b))$ is an edge in the abstract topology.
+Also we know that $\tilde{N} = f(b)$.
+
+    Let us take the node $n = (b, s_1, \dots, s_k)$.
+
+    \begin{easylist}
+      & Clearly $\tilde{n} = b$
+      & Clearly $f_{pg}(n) = (f(b), s_1, \dots, s_k) = N$
+      & For each regular expression $\sigma^A(q_i, f(b)) = s_i$.
+This means that for each regular expression, $\sigma(q_i, b) = s_i$.
+It follows that $(m,n)$ is an edge in the product graph by definition.
+      & Since the final states are the same for each state $q_i$ of each product graph state, it follows that $P(n) = P^A(f(n)) = P^A(N)$.
+    \end{easylist}
+
+  \end{proof}
+\end{lem}
+
+\begin{thm}
+  $m \leq m'$ in the concrete product graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph under the lifted graph homomorphism $f_{pg}$.
+
+  \begin{proof}
+    $(\leftarrow)$
+
+    Suppose we have a simulation relation from the subgraphs rooted at nodes $M$ and $M'$ with $M' \geq_{rank} M$ in the abstract product graph.
+Assume that $\tilde{M} = f(a)$ and $\tilde{N} = f(b)$.
+For each neighbor $N'$, if we can make a move from $M'$:
+
+    $$M' \overset{\tilde{N'}}{\rightarrow} N'$$
+
+    then we also make a similar move for $M$ for some $N$ where $N \approx N'$ and $N' \geq_{rank} N$:
+
+    $$M \overset{\tilde{N}}{\rightarrow} N$$
+
+    We must show that the same relation holds for $m$ and $m'$.
+
+    Now assume $m'$ has a neighbor $n'$ where $\tilde{m} = a$ and $\tilde{n} = b$.
+Then clearly $(a,b)$ is a valid topology edge since it is a transition in the product graph.
+We now apply the previous lemma with the following facts:
+
+    \[ \begin{array}{ll}
+      1. & (a,b) ~\text{is a topology edge} \\
+      2. & \tilde{m} = a \\
+      3. & f_{pg}(m) = M \\
+      4. & (M,N) ~\text{is an edge in}~ PG^A \\
+      5. & \tilde{N} = f(b) \\
+    \end{array} \]
+
+    This lets us conclude that there exists a node $n'$ such that:
+
+    \[ \begin{array}{ll}
+      1. & \tilde{n} = b \\
+      2. & f_{pg}(n) = N \\
+      3. & (m,n) ~\text{is an edge in}~ PG \\
+      4. & P(n) = P(N) \\
+    \end{array} \]
+
+    Thus if we have $m' \overset{b}{\rightarrow} n'$, then we also have $m \overset{b}{\rightarrow} n$.
+The previous lemma can also be used to show that $P(n') = P(N')$ in a symmetric fashion, so we are guaranteed that $n' \geq_{rank} n$ from the fact that $N' \geq_{rank} N$.
+
+  \end{proof}
+
+  \begin{proof}
+    $(\rightarrow)$
+
+    This is the simpler case. We assume we have $m' \overset{b}{\rightarrow} n'$ implies $m \overset{b}{\rightarrow} n$.
+    Simply take $N = f_{pg}(n)$ and $N' = f_{pg}(n')$.
+If we know that $M' \overset{b}{\rightarrow} N'$ then we already know that $M \overset{b}{\rightarrow} N$ from the homomorphism.
+All that's required is to show that $N' \geq_{rank} N$.
+This follows trivially from the fact that $P(n) = P(N)$ and $P(n') = P(N')$.
+  \end{proof}
+
+\end{thm}
+
 \end{document}

### 2016-11-06 paper/abstraction/appendix.tex
update substitution proof in appendix

@@
   \[ \begin{array}{l}
-     \textbf{compile}_\textbf{ABGP}(PG,ord) = \{ \\
+     \textbf{compile}_\textbf{ABGP}(PG,ord) = \\
      ~~~~~ \{ l \rightarrow rc ~\vert \\
@@
      ~~~~~~~~~ rc = ord(m) : (in,q_n) \rightarrow (out,q_m) \\
-
      ~~~~~ \}
@@
         & = & 
-        \{ x \rightarrow con(rc_i,m)  ~\vert~ x \in f^{-1}(l_i) \}
+        \{ x \rightarrow con(rc_i,x,m)  ~\vert~ x \in f^{-1}(l_i) \}
         \\
-     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,m) 
+     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,x,m) 
         & = &  
-        \{ pfx \rightarrow con(pc_i,m) ~\vert~ pfx \in m(t_i) \}
+        \{ pfx \rightarrow con(pc_i,x,m) ~\vert~ pfx \in m(t_i) \}
         \\
-     con(ma_1, \dots, ma_k,m) 
+     con(ma_1, \dots, ma_k,x,m) 
         & = &
-        con(ma_1,m), \dots, con(ma_k,m)
+        con(ma_1,x,m), \dots, con(ma_k,x,m)
         \\
-     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),m) 
+     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),x,m) 
         & = & 
-        n_1 : (con({ns}_1,m), n_2) \rightarrow (con({ns}_2,m),n_3)
+        n_1 : ( con({ns}_1,E^{-1},x,m), n_2) \rightarrow (con({ns}_2,E,x,m),n_3)
         \\
-     con(\{ l_1, ~\dots,~ l_k \}, m) 
+     con(\{ l_1, ~\dots,~ l_k \}, R, x, m) 
         & = &  
-        \bigcup ~ \{ f^{-1}(l_i) \}
+        \bigcup ~ \{ f^{-1}(l_i) \} \cap R
         \\
@@
 
+\subsection{Substitution}
+
+\begin{defn}
+  The previous theorem tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
+  We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.
+\end{defn}
+
+\begin{thm}
+  $con(compile_{ABGP}(compile_{PG}(pol))) = compile_{ABGP}(compile_{PG}(con(pol)))$
+
+  \begin{proof}
+
+    We know from the previous theorems the following:
+
+    \[ \begin{array}{lll}
+       PG^A, ord^A      &=& compile_{PG}(pol) \\
+       PG, ord          &=& compile_{PG}(con(pol)) \\
+    \end{array} \]%
+
+    where for all product graph nodes $m$ we have $ord(m) = ord^A(f(m))$. Therefore we must prove:
+
+    $$compile_{ABGP}(PG,ord) = con(compile_{ABGP}(PG^A,ord^A))$$
+
+    \ryan{need to worry about prefixes}
+
+    \[ \begin{array}{l}
+       \textbf{compile}_\textbf{ABGP}(PG,ord) = \\
+       ~~~~~ \{ l \rightarrow rc ~\vert \\
+       ~~~~~~~~~ l \in internal(V) \\
+       ~~~~~~~~~ m = (l,q_m) \in PG, \\
+       ~~~~~~~~~ in = \{ b_i ~\vert~ n_i = (b_i,q_n) \in \text{adjIn}(PG,m) \} \\
+       ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG,m) \} \\
+       ~~~~~~~~~ rc = ord(m) : (in,q_n) \rightarrow (out,q_m) \\
+       ~~~~~ \}
+    \end{array} \]%
+
+    \[ \begin{array}{l}
+       \textbf{compile}_\textbf{ABGP}(PG,ord) = \\
+       ~~~~~ \{ l \rightarrow rc ~\vert \\
+       ~~~~~~~~~ l \in internal(V) \\
+       ~~~~~~~~~ m = (l,q_m) \in PG, \\
+       ~~~~~~~~~ in = \{ b_i ~\vert~ n_i = (b_i,q_n) \in \text{adjIn}(PG,m) \} \\
+       ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG,m) \} \\
+       ~~~~~~~~~ rc = ord^A(f(m)) : (in,q_n) \rightarrow (out,q_m) \\
+       ~~~~~ \}
+    \end{array} \]%
+
+    \[ \begin{array}{l}
+       \textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
+       ~~~~~ \{ l \rightarrow rc ~\vert \\
+       ~~~~~~~~~ l \in internal(V) \\
+       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
+       ~~~~~~~~~ in = \bigcup \{ f^{-1}(b_i) ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \} \cap E^{-1} \\
+       ~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \}) \cap E \\
+       ~~~~~~~~~ rc = ord^A(M) : (in,q_N) \rightarrow (out,q_M)) \\
+       ~~~~~ \}
+    \end{array} \]%
+
+    \[ \begin{array}{l}
+       \textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
+       ~~~~~ \{ l' \rightarrow rc ~\vert \\
+       ~~~~~~~~~ l' \in f^{-1}(l) \\
+       ~~~~~~~~~ l \in internal(V^A) \\
+       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
+       ~~~~~~~~~ in = \bigcup \{ f^{-1}(b_i) ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \} \cap E^{-1} \\
+       ~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \}) \cap E \\ 
+       ~~~~~~~~~ rc = ord^A(M) : (in,q_N) \rightarrow (out,q_M)) \\
+       ~~~~~ \}
+    \end{array} \]%
+
+    \[ \begin{array}{l}
+       \textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
+       ~~~~~ \{ l' \rightarrow rc ~\vert \\
+       ~~~~~~~~~ l' \in f^{-1}(l) \\
+       ~~~~~~~~~ l \in internal(V^A) \\
+       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
+       ~~~~~~~~~ in = con(\{ b_i ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \}) \\
+       ~~~~~~~~~ out = con(\{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \}) \\
+       ~~~~~~~~~ rc = ord^A(M) : (in,q_N) \rightarrow (out,q_M)) \\
+       ~~~~~ \}
+    \end{array} \]%
+
+    \[ \begin{array}{l}
+       \textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
+       ~~~~~ \{ l' \rightarrow rc ~\vert \\
+       ~~~~~~~~~ l' \in f^{-1}(l) \\
+       ~~~~~~~~~ l \in internal(V^A) \\
+       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
+       ~~~~~~~~~ in = \{ b_i ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \} \\
+       ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \} \\
+       ~~~~~~~~~ rc = ord^A(M) : (con(in),q_N) \rightarrow (con(out),q_M)) \\
+       ~~~~~ \}
+    \end{array} \]%
+
+    \[ \begin{array}{l}
+       \textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
+       ~~~~~ \{ l' \rightarrow rc ~\vert \\
+       ~~~~~~~~~ l' \in f^{-1}(l) \\
+       ~~~~~~~~~ l \in internal(V^A) \\
+       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
+       ~~~~~~~~~ in = \{ b_i ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \} \\
+       ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \} \\
+       ~~~~~~~~~ rc = con(ord^A(M) : (in,q_N) \rightarrow (out,q_M)) \\
+       ~~~~~ \}
+    \end{array} \]%
+
+    \[ \begin{array}{l}
+       \textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
+       ~~~~~ \{ l' \rightarrow con(rc) ~\vert \\
+       ~~~~~~~~~ l' \in f^{-1}(l) \\
+       ~~~~~~~~~ l \in internal(V^A) \\
+       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
+       ~~~~~~~~~ in = \{ b_i ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \} \\
+       ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \} \\
+       ~~~~~~~~~ rc = ord^A(M) : (in,q_N) \rightarrow (out,q_M) \\
+       ~~~~~ \}
+    \end{array} \]%
+
+    \[ \begin{array}{l}
+       con(\textbf{compile}_\textbf{ABGP}(PG^A,ord^A) = \\
+       ~~~~~ \{ l \rightarrow rc ~\vert \\
+       ~~~~~~~~~ l \in internal(V^A) \\
+       ~~~~~~~~~ M = (l,q_M) \in PG^A, \\
+       ~~~~~~~~~ in = \{ b_i ~\vert~ N_i = (b_i,q_N) \in \text{adjIn}(PG^A,M) \} \\
+       ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG^A,M) \} \\
+       ~~~~~~~~~ rc = ord^A(M) : (in,q_N) \rightarrow (out,q_M) \\
+       ~~~~~ \})
+    \end{array} \]%
+
+  \end{proof}
+
+\end{thm}
+
 \end{document}

### 2016-11-07 paper/abstraction/appendix.tex
update substitution proof

--- 2016-11-06 paper/abstraction/appendix.tex
@@
      abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
-     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
+     rc   &::=& ps_1 \rightarrow {pc}_1, ~\dots,~ ps_k \rightarrow {pc}_k & \textit{router config} \\
      pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
      ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
+     ps   &::=& \{ t_1, ~\dots,~ t_k \} & \textit{predicates} \\
      ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
@@
   \[ \begin{array}{l}
-     \textbf{compile}_\textbf{ABGP}(PG,ord) = \{ \\
-     ~~~~~ \{ l \rightarrow rc ~\vert \\
-     ~~~~~~~~~ l \in internal(V) \\
-     ~~~~~~~~~ m = (l,q_m) \in PG, \\
-     ~~~~~~~~~ in = \{ b_i ~\vert~ n_i = (b_i,q_n) \in \text{adjIn}(PG,m) \} \\
-     ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG,m) \} \\
-     ~~~~~~~~~ rc = ord(m) : (in,q_n) \rightarrow (out,q_m) \\
-
-     ~~~~~ \}
+     \textbf{compile}_\textbf{ABGP}( (ps_1,PG_1,ord_1), \dots, (ps_k,PG_k,ord_k) ) = \\
+     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ ps_i \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
   \end{array} \]%
@@
 
-  \caption{Simplified BGP syntax.}
+  \caption{BGP syntax and compilation.}
   \label{fig:abgp-syntax}
@@
 
+\subsection{Substitution}
+
+\begin{defn}
+  The previous theorem tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
+  We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.
+\end{defn}
+
+\begin{thm}
+  $con(compile_{ABGP}(compile_{PG}(pol))) = compile_{ABGP}(compile_{PG}(con(pol)))$
+
+  \begin{proof}
+
+    We know from the previous theorems and the definition of concretization, we have the following:
+
+    \[ \begin{array}{lll}
+       (t_1, PG^A_1, ord^A_1), \dots, (t_k,PG^A_k,ord^A_k)    &=& compile_{PG}(pol) \\
+       (\Gamma(t1), PG_1, ord_1), \dots, (\Gamma(t_k),PG_k,ord_k)  &=& compile_{PG}(con(pol)) \\
+    \end{array} \]%
+
+    where for all product graph nodes $m$ we have $ord_i(m) = ord^A_i(f(m))$.
+
+  \[ \begin{array}{l}
+     \textbf{compile}_\textbf{ABGP}( (\Gamma(t_1),PG_1,ord_1), \dots, (\Gamma(t_k),PG_k,ord_k) ) = \\
+     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ \Gamma(t_i) \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord_i(M) : (in,q_n) \rightarrow (out,q_m) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
+     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG_i,m) \} \\ 
+     ~~~~~~~~~~~~~~~~~~ ma = ord_i(f(m)) : (in,q_n) \rightarrow (out,q_m) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
+     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ f^{-1}(b) ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \cap E^{-1} \\
+     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A_i,M) \}) \cap E \\ 
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
+     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
+     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ f^{-1}(b) ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \cap E^{-1} \\
+     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A_i,M) \}) \cap E \\ 
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
+     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
+     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = con(\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = con(\{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \}) \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
+     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
+     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = con(ord^A_i(M) : (in,q_n) \rightarrow (out,q_M)) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
+     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ pfx \rightarrow con(ma) ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
+     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
+     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ con(\bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \}) \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     \textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
+     ~~~~~ \{ l' \rightarrow rc ~\vert~ con(rc) = \\
+     ~~~~~~~ \bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     con(\textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) ) = \\
+     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \}) \\
+  \end{array} \]%
+
+  \end{proof}
+
+\end{thm}
+
 \end{document}

### 2016-11-07 paper/abstraction/paper.tex
edits

@@
 Such simulations provide some assurance that the templates work correctly for the simulated topologies but little assurance for other topologies that may arise after the network evolves.
-It is hard to predict all future topologies in advance, templates that work for one topology may not work for seemingly-inconsequential variations.
+Templates that work for one topology may not work for seemingly-inconsequential variations.
+Unfotunately, currently,
+there is no way to predict which variations will behave correctly for a given set of templates.
+Worse, when operators discover their old templates no longer work, a change to a template will
+cause a change to all devices that use that template---an unacceptable disruption in many cases.
+When that happens, network operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the topological change.
+Such patches reintroduce the complexity and errors that templates were meant to prevent.
+
+%% For some changes, they may discover that their old templates will not work anymore.
+~\dpw{Note: This is going to be true for Methane too.} ~\ratul{Not really; our abstract topologies encode all possible future topologies} ~\dpw{Our abstract topologies precisely define a set of topologies for which our
+%% This discovery is highly problematic because changing a template may cause a configuration change of all the devices that use that template---an unacceptable disruption in many cases.
+When that happens, network operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the topological change.
+%% Such patches reintroduce the complexity and errors that templates were meant to prevent.
 
@@
 For instance, consider templates that disallow ``valley" paths, which go up, down, and then up again; it is a common to disallow valley paths in a data center because they are longer than shortest paths.
-These templates will work perfectly for Figure~\ref{fig:example}, but violate the fault tolerance requirement ($p7$) when used for Figure~\ref{fig:example}.
+These templates will work perfectly for Figure~\ref{fig:example}, but violate the fault tolerance requirement ($p7$) when used for Figure~\ref{fig:example2}.
 Specifically, in Figure~\ref{fig:example2}, an aggregation-induced blackhole (\S\ref{sec:motivation}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces  the covering prefix PG (because it gets routes for P[3--4]).
@@
 
-Thus, today, operators test templates for each topology change.
+%% Thus, today, operators test templates for each topology change.
 For some changes, they may discover that their old templates will not work anymore.
-~\dpw{Note: This is going to be true for Methane too.} ~\ratul{Not really; our abstract topologies encode all possible future topologies}
-This discovery is highly problematic because changing a template may cause a configuration change of all the devices that use that template---an unacceptable disruption in many cases.
+~\dpw{Note: This is going to be true for Methane too.} ~\ratul{Not really; our abstract topologies encode all possible future topologies} ~\dpw{Our abstract topologies precisely define a set of topologies for which our
+%% This discovery is highly problematic because changing a template may cause a configuration change of all the devices that use that template---an unacceptable disruption in many cases.
 When that happens, network operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the topological change.
-Such patches reintroduce the complexity and errors that templates were meant to prevent.
+%% Such patches reintroduce the complexity and errors that templates were meant to prevent.
 
@@
 
-\sysname is a system to generate provably-correct templates.
+\sysname is a system for generating provably-correct templates.
 As inputs, it takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an {\em abstract} topology that describes device roles and

### 2016-11-07 paper/abstraction/paper.tex
edits to intro and sec 3

@@
 commonly deployed in industrial data centers.  These networks run
-many critical services and every second of downtime is at best
-costly and at worst dangerous.  Unfortunately, it is an enormous
+many critical services; every second of downtime is
+costly at best and dangerous at worst.  Unfortunately, it is an enormous
 challenge to keep these complex networks up and
@@
 \emph{human error}, which occurs during network configuration or
-update, is the single large cause of these
+update, is the single largest cause of these
 outages~\cite{juniper-study}.
@@
 that one obtains from instantiating a template's parameters.
-\dpw{add blah blah about low-level, assembly language, device by device}
 Moreover,
-template construction is a manual process:  network engineers do their
-best to design templates that will work effectively in the context
-of their particular network topology.  However, there is no support for
-validating key properties of an assembly of templates, such as connectivity
-and fault tolerance,
-aside from instantiating the templates and testing.  In addition,
+template construction is a low-level, manual process:  
+network engineers do their
+best to design templates using assembly-language-like primitives.
+They hope their templates
+that will work properly, test them using simulations, but
+there is no support for verification of key network-wide properties 
+such as connectivity and fault tolerance. In addition,
 network engineers have no tools to help them design for network
@@
 some risk of temporary instable in a network, so minimizing such changes
-is an important design goal.  It is no wonder that a major
-network outage, such as the one that grounded all United Air flights
-in July 2015~\cite{x}, makes international news every few months.
+is an important design goal.  
+%It is no wonder that a major
+%network outage, such as the one that grounded all United Air flights
+%in July 2015~\cite{x}, makes international news every few months.
 
@@
 determines the minimum number of link failures required to disconnect
-\emph{any} concrete topology that once again satisfies the connectivity
-invariants.
+\emph{any} valid concrete topology.
 
@@
 \begin{enumerate}
-\item Design of new topology abstractions involving roles and
-connectivity invariants for network programmers.
+\item Design of new topology abstractions for network programming
+based on graph homomorphisms and connectivity invariants.
 \item Design of two new algorithms for analyzing routing policy over
@@
   \includegraphics[width=\columnwidth]{figures/example3}
-  \caption{Role-based abstraction for the datacenters in Figure~\ref{fig:example}.}
+  \caption{An abstraction for the datacenters in Figure~\ref{fig:example}.}
   \label{fig:example3}

### 2016-11-07 paper/abstraction/appendix.tex
changing proof to account for origination:

--- 2016-11-06 paper/abstraction/appendix.tex
@@
 
+\para{Syntax}
+
 We define syntax for an abstraction of BGP configurations -- called ABGP -- in Figure~\ref{fig:abgp-syntax}.
@@
      ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
+     ps   &::=& \{ t_1, ~\dots,~ t_k \} & \textit{predicates} \\
      ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
@@
   \[ \begin{array}{l}
-     \textbf{compile}_\textbf{ABGP}(PG,ord) = \{ \\
-     ~~~~~ \{ l \rightarrow rc ~\vert \\
-     ~~~~~~~~~ l \in internal(V) \\
-     ~~~~~~~~~ m = (l,q_m) \in PG, \\
-     ~~~~~~~~~ in = \{ b_i ~\vert~ n_i = (b_i,q_n) \in \text{adjIn}(PG,m) \} \\
-     ~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG,m) \} \\
-     ~~~~~~~~~ rc = ord(m) : (in,q_n) \rightarrow (out,q_m) \\
+     \textbf{compile}_\textbf{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
+     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
+     \\
+     \textbf{compile}( p_1, \dots, p_k ) = \\
+     ~~~~~~ compile_{ABGP}(compile_{PG}(p_1), \dots, compile_{PG}(p_k)) \\
 
-     ~~~~~ \}
   \end{array} \]%
@@
 
-Figure~\ref{fig:abgp-syntax} also defines the translation of the product graph $PG = (G', s, P)$ to the ABGP representation.
+\para{Compilation}
+
+Figure~\ref{fig:abgp-syntax} also defines compilation from a \sysname policy to an ABGP policy.
+It starts by compiling separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$, the particular test $t_i$, and the preference ordering $ord_i$.
+
+The function $compile_{ABGP}$ then takes tuples of $(t_i, PG_i, ord_i)$ and returns an ABGP policy.
 It looks at each incoming neighbor with the same community state $q_n$ and matches any of those neighbor with the preference provided by the ordering $ord$ obtained from the search for local preferences.
@@
 Here we define what it means to concretize an abstract \sysname policy. 
-Concretization takes as input, a policy and a map $m$ from template prefix to a set of concrete prefixes.
+Concretization takes as input, a policy and a context $\Gamma$ mapping from a template prefix to a set of pairs of a concrete prefix and a concrete location where the prefix is owned.
 
-\[ \begin{array}{rcl}
-  con(\emptyset,m)                        & = & \emptyset \\
-  con(l,m)                                & = & \Sigma ~ \{ l_i \in f^{-1}(l) \} \\
-  con(r_1 \cup r_2,m)                     & = & con(r_1,m) \cup con(r_2,m) \\
-  con(r_1 \cap r_2,m)                     & = & con(r_1,m) \cap con(r_2,m) \\
-  con(!r,m)                               & = & !con(r,m) \\
-  con(r^*,m)                              & = & con(r,m)^* \\
-  con(pfx \Rightarrow r_1, \dots, r_n,m)  & = & pfx \Rightarrow con(r_1,m), \dots, con(r_n,m) \\
-  con(\$x \Rightarrow r_1, \dots, r_n,m)  & = & \{ pfx \Rightarrow con(r_1,m), \dots, con(r_n,m) ~\vert~ {pfx} \in m(x) \} \\
+\[ \begin{array}{lcl}
+  con(\emptyset,\Gamma)                        & = & \emptyset \\
+  con(l,\Gamma)                                & = & \Sigma ~ f^{-1}(l) \\
+  con(r_1 \cup r_2,\Gamma)                     & = & con(r_1,\Gamma) \cup con(r_2,\Gamma) \\
+  con(r_1 \cap r_2,\Gamma)                     & = & con(r_1,\Gamma) \cap con(r_2,\Gamma) \\
+  con(!r,\Gamma)                               & = & !con(r,\Gamma) \\
+  con(r^*,\Gamma)                              & = & con(r,\Gamma)^* \\
+  con(pfx \Rightarrow r_1, \dots, r_k,\Gamma)  & = & pfx \Rightarrow con(r_1,\Gamma), \dots, con(r_k,\Gamma) \\
+  con(\$x \Rightarrow r_1, \dots, r_k,\Gamma)  & = & \{ pfx \Rightarrow con(r_1,\Gamma) \cap \textbf{end}(l), \dots, \\
+  & & ~~~~~~~~~~~~~~~ con(r_k,\Gamma) \cap \textbf{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \} \\
 \end{array} \]
@@
 For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$.
-For each template variable, we replace it with a single entry for each of its corresponding concrete values under the supplied mapping $m$.
+For each template variable, we replace it with a new entry for each of its corresponding concrete values under the supplied mapping $\Gamma$.
+We also intersect the resulting concretized regular expression with $\textbf{end}(l)$ to capture the fact that traffic is owned by the concrete location $l$.
+\textbf{Note}: we need the side condition that $\textbf{end}(l) \cap con(r_i,\Gamma) \neq \emptyset$ if $con(r_i,\Gamma) \neq \emptyset$.
 We can also define concretization over the ABGP policy as:
 
-\[ \begin{array}{rcl}
-     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,m) 
+\[ \begin{array}{lcl}
+     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,G) 
         & = & 
-        \{ x \rightarrow con(rc_i,m)  ~\vert~ x \in f^{-1}(l_i) \}
+        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
         \\
-     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,m) 
+     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,G) 
         & = &  
-        \{ pfx \rightarrow con(pc_i,m) ~\vert~ pfx \in m(t_i) \}
+        con(t_1 \rightarrow {pc}_1,\ell,\Gamma,G), \dots, con(t_k \rightarrow {pc}_k,\ell,\Gamma,G)
         \\
-     con(ma_1, \dots, ma_k,m) 
+     con(pfx \rightarrow {pc},\ell,\Gamma,G) 
         & = &  
-        con(ma_1,m), \dots, con(ma_k,m)
+        pfx \rightarrow con(pc,\text{true},\ell,\Gamma,G)
         \\
-     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),m) 
+     con(\$x \rightarrow {pc},\ell,\Gamma,G) 
         & = &  
-        n_1 : (con({ns}_1,m), n_2) \rightarrow (con({ns}_2,m),n_3)
+        \{ pfx \rightarrow con(pc, l=\ell, \ell,\Gamma,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
         \\
-     con(\{ l_1, ~\dots,~ l_k \}, m) 
+     con(ma_1, \dots, ma_k,o,\ell,\Gamma,G) 
         & = &
-        \bigcup ~ \{ f^{-1}(l_i) \}
+        con(ma_1,o,\ell,\Gamma,G), \dots, con(ma_k,o,\ell,\Gamma,G)
+        \\
+
+     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,G) 
+        & = & \textbf{if}~ ns_1 = G.s ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
+        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,G),n_3)
+
+        \\
+     con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,G) 
+        & = &  
+        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
         \\
@@
 That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values afterwards.
+First we need a few helper theorems about compilation.
 
@@
 
+\subsection{Substitution}
+
+\begin{defn}
+  The previous theorem tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
+  We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.
+\end{defn}
+
+\begin{thm}
+  $con(compile(pol)) = compile(con(pol))$
+
+  \begin{proof}
+
+    We know from the previous theorems and the definition of concretization, we have the following:
+
+    \[ \begin{array}{lll}
+       (t_1, PG^A_1, ord^A_1), \dots, (t_k,PG^A_k,ord^A_k)    &=& compile_{ABGP}(pol) \\
+       (\Gamma(t1), PG_1, ord_1), \dots, (\Gamma(t_k),PG_k,ord_k)  &=& compile_{ABGP}(con(pol)) \\
+    \end{array} \]%
+
+    where for all product graph nodes $m$ we have $ord_i(m) = ord^A_i(f(m))$, and $PG_i$ and $PG^A_i$ are related by a bisimulation induced by $f$.
+
+  \[ \begin{array}{l}
+     \textbf{compile}( (\Gamma(t_1),PG_1,ord_1), \dots, (\Gamma(t_k),PG_k,ord_k) ) = \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ \Gamma(t_i) \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord_i(M) : (in,q_n) \rightarrow (out,q_m) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG_i,m) \} \\ 
+     ~~~~~~~~~~~~~~~~~~ ma = ord_i(f(m)) : (in,q_n) \rightarrow (out,q_m) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ f^{-1}(b) ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \cap E^{-1} \\
+     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A_i,M) \}) \cap E \\ 
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
+     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ f^{-1}(b) ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \cap E^{-1} \\
+     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A_i,M) \}) \cap E \\ 
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
+     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = con(\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = con(\{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \}) \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
+     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = con(ord^A_i(M) : (in,q_n) \rightarrow (out,q_M)) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ pfx \rightarrow con(ma) ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
+     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ con(\bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \}) \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     ~~~~~ \{ l' \rightarrow rc ~\vert~ con(rc) = \\
+     ~~~~~~~ \bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     ~~~~~ con(\{ l \rightarrow rc ~\vert~ rc = \\
+     ~~~~~~~ \bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \}) \\
+  \end{array} \]%
+
+  \[ \begin{array}{l}
+     = con(\textbf{compile}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) )) \\
+  \end{array} \]%
+
+  \end{proof}
+
+\end{thm}
+
 \end{document}

### 2016-11-07 paper/abstraction/paper.tex
small wording fixes to the first three sections

@@
 We develop techniques for automated reasoning about end-to-end properties of abstract network topologies.
-We extend a network synthesis tool, \sysname, to allow network operators to write a high-level routing policy over an abstraction of their network topology.
-From such a specification, \sysname synthesizes a collection router configurations running the distributed Border Gateway Protocol (BGP) that are guaranteed to implement the centralized routing policy for any concrete instantiation of the abstract topology, and for any combination of network failures in the resulting concrete topology.
+We develop a network synthesis tool, \sysname, to allow network operators to write a high-level routing policy over an abstraction of their network topology.
+From such a specification, \sysname synthesizes a collection of router configurations running the distributed Border Gateway Protocol (BGP) that are guaranteed to implement the centralized routing policy for any concrete instantiation of the abstract topology, and for any combination of network failures in the resulting concrete topology.
 %
@@
 network engineers do their
-best to design templates using assembly-language-like primitives.
+best to design templates despite the assembly-language-like primitives for network configuration.
 They hope their templates
-that will work properly, test them using simulations, but
+will work properly and test concrete instantiations of them using simulations, but
 there is no support for verification of key network-wide properties 
@@
 Each change to a router configuration typically incurs
-some risk of temporary instable in a network, so minimizing such changes
+some risk of temporary instability in a network, so minimizing such changes
 is an important design goal.  
@@
 is connected to at least two different tier-one aggregation routers,
-thereby providing a degree of fault tolerance of one aggregation router
+thereby providing a degree of fault tolerance if one aggregation router
 were to fail.
@@
 The boxes denote routers.
-Using terminology for fat tree networks~\cite{fattree}, T[1--8] denote top-of-rack (ToR) routers, A[1--8] denote aggregation routers, and S[1--2] denote spine routers.
+Using terminology for fat tree networks~\cite{fattree}, S[1--2] denote spine routers, A[1--8] denote aggregation routers, and T[1--8] denote top-of-rack (ToR) routers.
 The spine routers are connected to the
 rest of the Internet through Peer[1--2]. The aggregation routers
-bridge the spine to the ToRs routers. The ToR routers attach to a set of servers (``a rack'') that host services with address prefixes P[1--8].
+bridge the spine to the ToR routers. The ToR routers attach to a set of servers (``a rack'') that host services with address prefixes P[1--8].
 
@@
 %
-A {\em role} refers to specific functionality and is played by one or more routers.\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor configuration language.}
+A {\em role} refers to specific functionality and is played by one or more routers.\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor-specific configuration languages.}
 %
@@
 For instance, consider templates that disallow ``valley" paths, which go up, down, and then up again; it is a common to disallow valley paths in a data center because they are longer than shortest paths.
-These templates will work perfectly for Figure~\ref{fig:example}, but violate the fault tolerance requirement ($p7$) when used for Figure~\ref{fig:example2}.
+These templates will work perfectly for Figure~\ref{fig:example} but silently violate the fault tolerance requirement ($p7$) when used for Figure~\ref{fig:example2}.
 Specifically, in Figure~\ref{fig:example2}, an aggregation-induced blackhole (\S\ref{sec:motivation}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces  the covering prefix PG (because it gets routes for P[3--4]).
@@
 The first is abstraction mismatch.
-Operators of large networks think of the network, and to develop management tools, using \emph{roles}, and not individual devices.
+Operators of large networks think of the network, and develop management tools, using \emph{roles}, and not individual devices.
 They are naturally reluctant to use a system that does not

### 2016-11-07 paper/abstraction/appendix.tex
update language equivalence proof for appendix

@@
      con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,G) 
-        & = & \textbf{if}~ ns_1 = G.s ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
+        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
         &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,G),n_3)
@@
   \text{Product Graph} & PG, PG^A \\
-  \text{Automata} & M_i, M_i^A \\
+  \text{Automata} & M, M^A \\
 \end{array} \]
@@
 
-\begin{defn}
-If $r$ complies to state machine $M^A$, then we compile the policy $con(r)$ in the following way:
+%\begin{defn}
+%If $r$ complies to state machine $M^A$, then we compile the policy $con(r)$ in the following way:%
 
-  \[ \begin{array}{ll}
-    1. & \sigma^A(q,f(l)) = q' \iff \sigma(q,l) = q' \\
-    2. & q \in F^A \iff q \in F \\
+%  \[ \begin{array}{ll}
+%    1. & \sigma^A(q,f(l)) = q' \iff \sigma(q,l) = q' \\
+%    2. & q \in F^A \iff q \in F \\
+%  \end{array} \]%
+
+%That is, we construct a new automata over the same states and final states, but with a different transition function $\sigma$.
+This ensures that there is a bisimulation between the two state machines.%
+
+%\end{defn}%
+%
+
+%\begin{lem}
+%  $M^A$ matches $f(p)$ $\iff$ $M$ matches $p$.
+%\end{lem}%
+
+%\begin{proof}
+%  Suppose $M^A$ matches $f(p) = A_1, \dots, A_k$, then there exists a trace through $M^A$ of the form:%
+
+%  $$q_0, q_1, \dots, q_{k+1}$$%
+
+%  where $\sigma^A(q_i, A_i) = q_{i+1}$ and $q_{k+1} \in F^A$. We must show that $M$ matches $p = a_1, \dots, a_k$. %
+
+%  From the construction of the automaton, we know that $\sigma(q_i, a_i) = q_{i+1}$ and $q_{k+1} \in F \iff q_{k+1} \in F^A$. Therefore, the trace $q_0, q_1, \dots, q_{k+1}$ is accepted by $M$. 
+%  %
+%  The same proof is symmetric for the other direction.
+%\end{proof}%
+%
+
+%\begin{lem}
+%  $M$ matches $p$ $\iff$ $p \in \Lang(con(r))$
+%  \begin{proof}
+%    \[ \begin{array}{lllr}
+%      M ~\text{matches}~ p &\iff& M^A ~\text{matches}~ f(p) & \textit{previous lemma} \\
+%                         &\iff& f(p) \in \Lang(r) & \textit{automaton construction} \\
+%                         &\iff& p \in \Lang(con(r)) & \textit{first lemma} \\
+%    \end{array} \]%
+
+%  \end{proof}
+%\end{lem}
+
+\begin{lem}
+  Consider the PG created from compiling the constraint $p = (t ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$ with state machine $M^A_i$ for each $r_i$.
+We know that, for each $(pfx ~\Path~ r'_1 ~\Prefer~,\dots, ~\Prefer~ r'_k) \in con(p)$ where $r'_i$ is of the form $r \cap \text{end}(L)$ we can constuct state machine $M_i$ for $r'_i$ in the following way:
+
+    \[ \begin{array}{lll}
+      1. & \sigma(q_0,l) = q' \iff \sigma^A(q,f(l)) = q' & \textbf{for each}~~ l \in L \\
+      2. & \sigma(q,l) = q' \iff \sigma^A(q,f(l)) = q' & \textbf{for each}~~ l \in \Sigma \\
+      3. & q \in F \iff q \in F^A & \\
     \end{array} \]
 
-That is, we construct a new automata over the same states and final states, but with a different transition function $\sigma$. This ensures that there is a bisimulation between the two state machines.
+  then $M_i$ matches $p$ $\iff$ $p \in \Lang(r_i')$
 
-\end{defn}
+  \vspace{1em}
+  \begin{proof} by cases on $t$
 
-\begin{lem}
-  $M^A$ matches $f(p)$ $\iff$ $M$ matches $p$.
-\end{lem}
+    \vspace{1em}
 
-\begin{proof}
-  Suppose $M^A$ matches $f(p) = A_1, \dots, A_k$, then there exists a trace through $M^A$ of the form:
+    \textbf{Case} $(\$x ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$
 
-  $$q_0, q_1, \dots, q_{k+1}$$
+    \[ \begin{array}{lcl}
+      con(p) &=& pfx_1 ~\Path~ con(r_1) \cap \text{end}(l_1), ~\Prefer~ \dots ~\Prefer~ con(r_k) \cap \text{end}(l_1)  \\
+             & & \dots, \\
+             & & pfx_n ~\Path~ con(r_1) \cap \text{end}(l_n), ~\Prefer~ \dots ~\Prefer~ con(r_k) \cap \text{end}(l_n)
+    \end{array} \]
 
-  where $\sigma^A(q_i, A_i) = q_{i+1}$ and $q_{k+1} \in F^A$. We must show that $M$ matches $p = a_1, \dots, a_k$.
+    Case ($\Rightarrow$)
 
-  From the construction of the automaton, we know that $\sigma(q_i, a_i) = q_{i+1}$ and $q_{k+1} \in F \iff q_{k+1} \in F^A$. Therefore, the trace $q_0, q_1, \dots, q_{k+1}$ is accepted by $M$. 
+    Assume $M_i$ matches $p$.
+Then this means that $M^A_i$ matches $f(p)$.
+If we have a trace of string of the form $ p = x_1 \cdot \dots \cdot x_n$, then $f(p) = f(x_1) \cdot \dots \cdot f(x_n)$.
+For each transition $\sigma(q,l) = q'$ in the concrete automaton, we have transition $\sigma(q,f(l)) = q'$ in the abstract automaton, and they have the same final states, so this trace is accepting for $M^A_i$.
+Because $M^A_i$ matches $f(p)$, this means that $f(p) \in \Lang(r_i)$.
+From our above lemma, this means that $p \in \Lang(con(r_i))$.
+We also know that, since $L = \{ l_i \}$, the first transition $\sigma(q_0,l_i)$ is the only transition allowed from the initial state for $M_i$.
+So this means that $p \in \Lang(\text{end}(l_i))$.
+Since we know that $p \in \Lang(con(r_i))$ and $p \in \Lang(\text{end}(l_i))$, we know that $p \in \Lang(con(r_i) \cap \text{end}(l_i))$ and thus $p \in \Lang(r'_i)$.
+
+    \vspace{1em}
+    Case ($\Leftarrow$)
+
+    Assume $p \in \Lang(r'_i)$.
+This means that $p \in \Lang(con(r_i) \cap \text{end}(l_i))$.
+In turn, this means that $p \in \Lang(con(r_i))$ and $p \in \Lang(\text{end}(l_i))$.
+From the above lemma, we know that $f(p) \in \Lang(r_i)$, which means that $M^A_i$ matches $f(p)$.
     %
-  The same proof is symmetric for the other direction.
+    Consider any string of the form $p = l_i \cdot x_2 \cdot \dots \cdot x_n$ such that $p \in \Lang(con(r_i) \cap \text{end}(l_i))$. Clearly there is a transition defined for $\sigma(q_0,l_i) = q_1$.
+    %
+    This means that $M^A_i$ matches $f(l_i) \cdot f(x_2) \cdot \dots \cdot f(x_n)$
+    %
+    For each transition $\sigma^A(q,f(x_i)) = q'$, we have $\sigma(q,x_i) = q'$ in $M_i$.
+    %
+    Thus the string $l_i \cdot x_2 \cdot \dots \cdot x_n$ is accepted along the same path of automaton states.
+
+  \vspace{1em}
+
+  \textbf{Case} $(pfx ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$
+
+    \[ \begin{array}{lcl}
+      con(p) &=& pfx_1 ~\Path~ con(r_1) \cap \text{end}(\Sigma^*), ~\Prefer~ \dots ~\Prefer~ con(r_k) \cap \text{end}(\Sigma^*) \\
+    \end{array} \]
+
+    First we observe that: $M^A_i$ matches $f(p)$ $\iff$ $M_i$ matches $p$.
+    %
+    Suppose $M^A_i$ matches $f(p) = A_1, \dots, A_k$, then there exists a trace through $M^A_i$ of the form:%
+    %
+    $q_0, q_1, \dots, q_{k+1}$
+    %
+    where $\sigma^A_i(q_i, A_i) = q_{i+1}$ and $q_{k+1} \in F^A$. We must show that $M_i$ matches $p = a_1, \dots, a_k$. %
+    %
+    From the construction of the automaton, we know that $\sigma_i(q_i, a_i) = q_{i+1}$ and $q_{k+1} \in F \iff q_{k+1} \in F^A_i$.
+Therefore, the trace $q_0, q_1, \dots, q_{k+1}$ is accepted by $M_i$.
+    %
+    The same proof is symmetric for the other direction. It follows that:
+
+    \[ \begin{array}{lll}
+      M ~\text{matches}~ p &\iff& M^A ~\text{matches}~ f(p) \\
+                         &\iff& f(p) \in \Lang(r) \\
+                         &\iff& p \in \Lang(con(r)) \\
+    \end{array} \]%
+
   \end{proof}
 
-\begin{thm}
-  $M$ matches $p$ $\iff$ $p \in \Lang(con(r))$
-  \begin{proof}
-    \[ \begin{array}{lllr}
-      M ~\text{matches}~ p &\iff& M^A ~\text{matches}~ f(p) & \textit{previous lemma} \\
-                         &\iff& f(p) \in \Lang(r) & \textit{automaton construction} \\
-                         &\iff& p \in \Lang(con(r)) & \textit{first lemma} \\
-    \end{array} \]
-
-  \end{proof}
-\end{thm}
+\end{lem}
 

### 2016-11-08 paper/abstraction/appendix.tex
update appendix

@@
 \newtheorem{lem}[thm]{Lemma}
+\newtheorem*{cor}{Corollary}
 
@@
 
+We compile regular expressions to automata.
+As a side condition, we ensure that there are no transitions from some state $q$ to the initial state: $\sigma(q,x) = q_0$.
+This is done by creating another state $q_0'$ with the same transition function as $q_0$ and all other states transition to $q_0'$ instead of $q_0$.
+
 \begin{lem}
-  For any map $m$ and regular expression $r$ over abstract locations, path $p \in \Lang(con(r,m)) \iff f(p) \in \Lang(r)$.
+  For any map $\Gamma$ and regular expression $r$ over abstract locations, path $p \in \Lang(con(r,\Gamma)) \iff f(p) \in \Lang(r)$.
 \end{lem}
@@
   Consider the PG created from compiling the constraint $p = (t ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$ with state machine $M^A_i$ for each $r_i$.
-We know that, for each $(pfx ~\Path~ r'_1 ~\Prefer~,\dots, ~\Prefer~ r'_k) \in con(p)$ where $r'_i$ is of the form $r \cap \text{end}(L)$ we can constuct state machine $M_i$ for $r'_i$ in the following way:
+We know that, for each $(pfx ~\Path~ r'_1 ~\Prefer~,\dots, ~\Prefer~ r'_k) \in con(p)$ where $r'_i$ is of the form $r \cap \text{end}(L)$ we can constuct state machine $M_i$ for $r'_i$ over the same states in the following way:
 
@@
 
+\begin{cor}
+  foo
+\end{cor}
+
 \subsection{Product Graph}
@@
 \begin{lem}
-  If, for product graph $PG = (G,s,P)$ with $G=(V,E)$, if we have the following:
+  If $f_{pg}(n) = N$, then $P(n) = P^A(N)$.
+
+  \begin{proof}
+    Assume $n = (a,q_1,\dots,q_k)$. We know that $f_{pg}(n) = (f(a),q_1,\dots,q_k)$. 
+    We also know that $q_i \in F_i \iff q_i \in F^A_i$. 
+    By the definition of the preference function $P$, then $P(n) = P^A(N)$.
+  \end{proof}
+
+\end{lem}
+
+\begin{lem}
+  If, for abstract product graph $PG$, if we have the following:
 
@@
     3. & (m,n) ~ \text{is an edge in the product graph}~ PG \\
-    4. & P(n) = P(N) \\
   \end{array} \]
@@
 Also suppose there is some $b$ such that $N = (f(b), s_1, \dots, s_k)$ since $f^{-1}(N) \neq \emptyset$.
-This means that, since $(a,b)$ is an edge in the concrete topology, so $(f(a),f(b))$ is an edge in the abstract topology.
+This means that, since $(a,b)$ is an edge in the concrete topology, $(f(a),f(b))$ is an edge in the abstract topology.
 Also we know that $\tilde{N} = f(b)$.
@@
       & For each regular expression $\sigma^A(q_i, f(b)) = s_i$.
-This means that for each regular expression, $\sigma(q_i, b) = s_i$.
+This means that for each regular expression, $\sigma(q_i, b) = s_i$ if $q_i \neq q_{0_i}$.
+We know that $q_i \neq q_{0_i}$ due to the side condition for automaton construction.
 It follows that $(m,n)$ is an edge in the product graph by definition.
-      & Since the final states are the same for each state $q_i$ of each product graph state, it follows that $P(n) = P^A(f(n)) = P^A(N)$.
     \end{easylist}

### 2016-11-08 paper/abstraction/appendix.tex
updating substitution theorem

@@
 
+\begin{defn}
+  Assign $ord(m) = ord^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
+  Clearly $ord(m) \leq ord(m') \iff m \leq m'$ and $ord(f_{pg}(m)) \leq ord(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
+\end{defn}
+
 \subsection{Substitution}
@@
 \begin{thm}
-  $con(compile(pol)) = compile(con(pol))$
+  $compile(con(pol)) = con(compile(pol))$
 
-  \begin{proof}
+  \begin{proof} \text{ }
 
-    We know from the previous theorems and the definition of concretization, we have the following:
+    Suppose that $pol = p_1, \dots, p_n$. Each $p_i$ has the form $(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik})$. Then by evaulating:
 
-    \[ \begin{array}{lll}
-       (t_1, PG^A_1, ord^A_1), \dots, (t_k,PG^A_k,ord^A_k)    &=& compile_{ABGP}(pol) \\
-       (\Gamma(t1), PG_1, ord_1), \dots, (\Gamma(t_k),PG_k,ord_k)  &=& compile_{ABGP}(con(pol)) \\
-    \end{array} \]%
+    \[ \begin{array}{lcl}
+      con(pol) & = & con(p_1,\dots,p_n) \\
+               & = & con(p_1), \dots, con(p_n) \\
+               & = & con(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k}), \\
+               &   & \dots, \\
+               &   & con(t_n ~\Path~ r_{n1} ~\Prefer~,\dots, ~\Prefer~ r_{nk}) \\
+    \end{array} \]
 
-    where for all product graph nodes $m$ we have $ord_i(m) = ord^A_i(f(m))$, and $PG_i$ and $PG^A_i$ are related by a bisimulation induced by $f$.
+    For each test $t_i$, if $t_i = pfx$, then we get
+
+    \[ \begin{array}{lcl}
+        con({pfx}_{i1} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik}) 
+           & = & {pfx}_{i1} ~\Path~ con(r_{i1}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik}) \\
+    \end{array} \]
+
+    For each test $t_i$, if $t_i = \$x$, then we get
+
+    \[ \begin{array}{lcl}
+        con(\$x_{i} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik}) 
+            & = & {pfx}_{i1} ~\Path~ con(r_{i1}) \cap \text{end}(l_{i1}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik}) \cap \text{end}(l_{i1}), \\
+            &   & \dots, \\ 
+            &   & {pfx}_{ij} ~\Path~ con(r_{i1}) \cap \text{end}(l_{ij}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik}) \cap \text{end}(l_{ij}), \\
+            &   & \\
+            &   & \text{for each } (pfx_{ij}, l_{ij}) \in \Gamma(x) \\
+    \end{array} \]
+
+    Next we compute $compile(con(pol))$:
+
+    \[ \begin{array}{lcl}
+        compile(con(pol)) &=& compile_{ABGP}( \\
+                          & & ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k} ), \\
+                          & & ~~~~ \dots, \\
+                          & & ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk} ), \\
+                          & & ~~~~ \dots, \\
+                          & & ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k} ), \\
+                          & & ~~~~ \dots, \\
+                          & & ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk} ) \\
+                          & & ) \\
+    \end{array} \]
+
+    This results in a series of prefixes, product graphs, and orderings of the form: $(pfx_{ij}, PG_{ij}, ord_{ij})$.
+
+    \vspace{1em}
+    Similarly, we can compute $compile(pol)$:
+
+    \[ \begin{array}{lcl}
+        compile(pol) &=& compile_{ABGP}( \\
+                     & & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k} ), \\
+                     & & ~~~~ \dots, \\
+                     & & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik} ), \\
+                     & & ) \\
+    \end{array} \]
+
+    This results in a series of prefixes, product graphs, and orderings of the form $(t_i, PG^A_i, ord^A_i)$.
+
+    We know the follwing:
+
+    \begin{itemize}
+      \item each $PG^A_i$ and $PG_ij$ are related by a bisimulation induced by $f_{pg}$ for thos product graphs
+      \item each $ord^A_i$ and $ord_{ij}$ have the property that $ord^A(f_{pg}(m)) = ord_{ij}(m)$
+      \item each $t_i$ has either $t_i = pfx_{ij}$ or $t_i = \$x$ and $\exists l, (pfx_{ij},l) \in \Gamma(x)$.
+    \end{itemize}
+
+    %where for all product graph nodes $m$ we have $ord_i(m) = ord^A_i(f(m))$, and $PG_i$ and $PG^A_i$ are related by a bisimulation induced by $f$.
 

### 2016-11-08 paper/abstraction/paper.tex
pass over intro

@@
 
-An important class of networks are the large \emph{structured networks}
-commonly deployed in industrial data centers.  These networks run
-many critical services; every second of downtime is
-costly at best and dangerous at worst.  Unfortunately, it is an enormous
-challenge to keep these complex networks up and
-running 24/7~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
-Moreover, while hardware faults, rodents, power failures and natural
-disasters can all cause significant downtime, studies have shown that
-\emph{human error}, which occurs during network configuration or
-update, is the single largest cause of these
-outages~\cite{juniper-study}.
-
-% These networks often
-% host a myriad of services and every second of downtime imposes significant
-% financial cost or disruption to consumers.
-Such networks typically have uniform, tree-shaped topologies that involve
-hundreds or even thousands of devices.  Since it is not possible for humans
-to think about configuring each individual device independently,
-network operators typically classify the devices, assigning them a particular
-\emph{role} such as ``top-of-rack router'' or ``tier-one aggregation router.''
-Each such role is codified as a \emph{configuration template}---a macro
-that may be instantiated with different concrete values to
-generate a configuration for each device that plays the role.
-
-Unfortunately, such templates have no particular semantics other than the
-semantics
-that one obtains from instantiating a template's parameters.
-Moreover,
-template construction is a low-level, manual process:  
-network engineers do their
-best to design templates despite the assembly-language-like primitives for network configuration.
-They hope their templates
-will work properly and test concrete instantiations of them using simulations, but
-there is no support for verification of key network-wide properties 
-such as connectivity and fault tolerance. In addition,
-network engineers have no tools to help them design for network
-evolution.  For instance, the process of adding new equipment to
-expand the capacity of data center may not be compatible with the original
-templates, or may cause a trickle-down of changes to be made network-wide.
-Each change to a router configuration typically incurs
-some risk of temporary instability in a network, so minimizing such changes
-is an important design goal.  
+%An important class of networks are the large \emph{structured networks}
+%commonly deployed in industrial data centers.
+
+Computer networks run many critical services, and every second of downtime is
+costly at best and dangerous at worst.  Keeping these complex systems up and running 24/7 is an enormous challenge~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
+%
+While hardware faults, rodents, power failures and natural disasters all pose problems, studies have consistently shown that human error in network configuration is one of the most error-prone task and the leading cause of network outages~\cite{juniper-study,xx}.
+
+To manage and configure large networks today, instead of considering individual devices, operators classify devices devices into {\em roles}.
+A role refers to specific functionality and is played by one or more devices.
+For instance, in a data center, roles may correspond to "top-of-rack," "aggregation," and "spine" switches; and in a backbone network, they may correspond to "core" and "border" routers.
+While the network may have hundreds or thousands of devices---a scale that is impossible for humans to handle---there tend to be a handful of roles.
+%
+Operators author a configuration {\em template} for each role.
+Templates are macros that can be instantiated with different concrete values, based on the network topology, to generate a configuration for each device.
+
+Unfortunately, template construction is a low-level, manual process.
+Operators manually decompose network-wide routing and fault-tolerance policies (e.g., prefer one end-to-end path over another or no loss in connectivity after any one-link failure) across roles and encode them using assembly-language-like configuration primitives (e.g., role A should not transmit routing information from B to C).
+Such decomposition tasks are highly complex~\cite{propane}.
+
+Worse, operators can never be sure that the generated templates correctly implement the policy,  beyond testing some concrete instantiations using simulation or verification tools~\cite{x,y}.
+Testing based on concrete instantiations is insufficient because large networks evolve continuously, as devices and links are added or taken offline for maintenance.
+Templates that work for the current network topology, may or may not work for future topologies.
+Updating the templates, if found to not work for a future topology, may cause trickle-down, network-wide configuration changes, which is highly disruptive.
+Building sophisticated tools for validating templates is difficult because the templates today have no particular semantics---which policies they implement and for which topologies---other than the semantics of the configurations that one obtains from instantiating them.
+
 %It is no wonder that a major
@@
 
-To combat these problems, we present \sysname, a
-new high-level language designed to
-provide improved support for the configuration of large, structured networks.
-\sysname allows network operators to define \emph{abstract network topologies}
-that
-classify devices in terms of their roles and how they are connected
-to one another.  For instance, a programmer may
-define separate roles for ``top-of-rack router'' and
-``tier-one aggregation router'' and specify that every top-of-rack router
-is connected to at least two different tier-one aggregation routers,
-thereby providing a degree of fault tolerance if one aggregation router
-were to fail.
-
-To specify \emph{routing policy} for such abstract networks,
-\sysname borrows notation from the recently-defined \propane
-programming language~\cite{propane}.  As such, it is able to
-specify the paths that traffic should flow along at a high-level of
-abstraction.  However, whereas \propane policies
-refer to paths of individual devices, \sysname policies
-refer to paths of abstract roles.  The \sysname compiler compiles such
-policies into templates, with one template per role, and these templates
-may be instantiated to generate concrete configurations.
-
-During compilation, the \sysname compiler also analyzes policy with respect to the
-abstract topology and guarantees that the configurations will
-faithfully implement the high-level policy on \emph{any} concrete
-topology that satisfies the given connectivity invariants.  The compiler
-will also optionally perform a second fault tolerance analysis that
-determines the minimum number of link failures required to disconnect
-\emph{any} valid concrete topology.
-
-Finally, generated \sysname configurations are designed to
-be \emph{evolution-friendly} in the sense that if an operator adds or
-removes any single link or device, they are guaranteed that only
-the configurations of adjacent devices need change (for instance, to
-activate a port on which the new device is connected).  Doing so
-helps minimize network instability as data centers are expanded or devices are
-temporarily taken offline for maintenance.
-
+Given the challenges of generating and validating network configurations, one might think that operators will be receptive to systems that can generate provably-correct configurations from high-level policy specifications~\cite{x,y,z,configassure,propane}.
+However, our conversations with two major cloud providers reveal that operators of large networks are reluctant to use such systems.
+While they think of their network abstractly, in terms of roles, these systems require concrete topologies, with no understanding of roles as a first-order abstraction.
+Even if two devices play the same role,
+there is no guarantee that the systems will generate (syntactically) similar configurations; if the operators want to debug or analyze system output, they will have to consider
+hundreds of device configurations instead of a handful of role configurations.
+These systems become even more brittle when the network evolves.
+Any change in network topology requires re-execution of the engine, from scratch, on the changed topology.
+The result may be
+a completely different set of configurations.
+
+We present \sysname, a system to generate provably-correct role templates.
+It allows operators to input \emph{abstract network topologies} in terms of roles and their connectivity.
+For instance, they may specify roles for ``top-of-rack'' and ``aggregation" switches and specify that every top-of-rack switch connects to at least two aggregation switches (to tolerate the failure of a link to an aggregation switch).
+Other inputs to \sysname include the routing policy of the network and its fault-tolerance requirements (e.g., the number of link failures to tolerate).
+For routing policy, we borrow notation from Propane~\cite{propane},  which specifies traffic paths at a high-level of abstraction.
+But while Propane policies
+refer concrete devices, \sysname policies refer to abstract roles.
+
+Based on these inputs, the \sysname compiler generates one template per role.
+It guarantees that, when the templates are instantiated to configurations for {\em any} concrete topology that complies with the abstract topology, the result network will correctly implement the routing policy and meet the fault-tolerance requirements.
+We show how fault-tolerance analysis can be done over abstract topology itself using \todo{say something cool about about the inference rules and such}.
+
+\sysname templates are also evolution-friendly.
+When the network migrates from one concrete topology to another, both of which comply with the abstract topology, it is guaranteed that only the configurations of devices that acquire or lose a neighboring device needs to change (e.g., to activate a port on which the new device is connected).
+No other device in the network is impacted.
+
+\todo{Talk about evaluation result here ... roll the point about faster compilation there.}
 As an aside, a pleasant side effect of this new compiler
@@
 
-\para{Configuration synthesis with concrete topologies}
-Many recent systems generate router configurations using high-level policy statements~\cite{narain:lisa05,narain+:configassure,dadc,propane} and the network's concrete topology.
-%These systems eliminate entire classes of configuration errors by construction, and, in the case of
-%Propane~\cite{propane}, guarantee that high-level policy is implemented correctly, even in the presence of
-%arbitrary combinations of failures.
-They are able to provide strong guarantees on configuration correctness but 
-our conversations with operators at two major cloud providers reveal that they have two limitations that discourage adoption.
+%\para{Configuration synthesis with concrete topologies}
+%Many recent systems generate router configurations using high-level policy statements~\cite{narain:lisa05,narain+:configassure,dadc,propane} and the network's concrete topology.
+%%These systems eliminate entire classes of configuration errors by construction, and, in the case of
+%%Propane~\cite{propane}, guarantee that high-level policy is implemented correctly, even in the presence of
+%%arbitrary combinations of failures.
+%They are able to provide strong guarantees on configuration correctness but
+%our conversations with operators at two major cloud providers reveal that they have two limitations that discourage adoption.
 The first is abstraction mismatch.
@@
 They are naturally reluctant to use a system that does not
-understand roles as a first-order abstraction. If they want to debug, analyze or
-understand system output, they will have to consider
-\emph{hundreds} of independent device configurations instead of just
-\emph{a handful} of role configurations. Unfortunately, even if two devices play the same role,
-there is no guarantee a concrete synthesis system will generate (syntactically) similar configurations.
-
-%A second limitation is the inability to support network evolution.
+%understand roles as a first-order abstraction. If they want to debug, analyze or
+%understand system output, they will have to consider
+%\emph{hundreds} of independent device configurations instead of just
+%\emph{a handful} of role configurations. Unfortunately, even if two devices play the same role,
+%there is no guarantee a concrete synthesis system will generate (syntactically) similar configurations.
+%
+%%A second limitation is the inability to support network evolution.
 Networks evolve all the time as nodes and links are added or removed and the addresses of services are changed.
 A system that supports evolution would ensure that
-%small changes in topology require small, local changes in network configurations as opposed to pervasive
-%changes across many devices.
+%%small changes in topology require small, local changes in network configurations as opposed to pervasive
+%%changes across many devices.
 Engineers want to minimize changes to device configurations because each change runs the risk of poor, transient behavior due to poor router software or routing protocol dynamics~\cite{ratulbgpmisconfigs}.
-%These networks must be highly
-%available; it isn't plausible to bring down an entire data center network, or large portions of it, to make
-%incremental changes.
-
-Second, these systems become even more brittle in the face of network evolution.
-Any change in network topology requires re-execution of a
-concrete synthesis engine, from scratch,
-on the changed topology.  The result may be
-a completely different set of configurations.  Even if such configurations are
-largely semantically similar to existing configurations, they may be syntactically different and cause considerable network disruption when updates are pushed to routers.
+%%These networks must be highly
+%%available; it isn't plausible to bring down an entire data center network, or large portions of it, to make
+%%incremental changes.
+%
+%Second, these systems become even more brittle in the face of network evolution.
+%Any change in network topology requires re-execution of a
+%concrete synthesis engine, from scratch,
+%on the changed topology.  The result may be
+%a completely different set of configurations.  Even if such configurations are
+%largely semantically similar to existing configurations, they may be syntactically different and cause considerable network disruption when updates are pushed to routers.
 

### 2016-11-08 paper/abstraction/appendix.tex
finish substitution proof modulo a few helpers

@@
      \textbf{compile}_\textbf{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
-     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
-     ~~~~~~~ \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
+     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~ l \in internal(V), \\
+     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
      \\
@@
      ~~~~~~ compile_{ABGP}(compile_{PG}(p_1), \dots, compile_{PG}(p_k)) \\
-
   \end{array} \]%
@@
     \begin{itemize}
-      \item each $PG^A_i$ and $PG_ij$ are related by a bisimulation induced by $f_{pg}$ for thos product graphs
+      \item each $PG^A_i$ and $PG_ij$ are related by $f_{pg}$
       \item each $ord^A_i$ and $ord_{ij}$ have the property that $ord^A(f_{pg}(m)) = ord_{ij}(m)$
-      \item each $t_i$ has either $t_i = pfx_{ij}$ or $t_i = \$x$ and $\exists l, (pfx_{ij},l) \in \Gamma(x)$.
     \end{itemize}
 
-    %where for all product graph nodes $m$ we have $ord_i(m) = ord^A_i(f(m))$, and $PG_i$ and $PG^A_i$ are related by a bisimulation induced by $f$.
+  \[ \begin{array}{l}
+     con(\textbf{compile}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) )) \\
+  \end{array} \]%
+
+Unfold definition of compile
 
   \[ \begin{array}{l}
-     \textbf{compile}( (\Gamma(t_1),PG_1,ord_1), \dots, (\Gamma(t_k),PG_k,ord_k) ) = \\
+     ~~~~~ con(\{ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \}) \\
   \end{array} \]%
 
+  Apply the definition of $con$
+
   \[ \begin{array}{l}
-     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
-     ~~~~~~~ \bigcup~ \{ \Gamma(t_i) \rightarrow ma ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma = ord_i(M) : (in,q_n) \rightarrow (out,q_m) \} \} \\
+     ~~~~~ \{ \ell \rightarrow con(rc) ~\vert~ \\
+     ~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_n) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \} \\
   \end{array} \]%
 
+  Rewrite $con$ on $rc$
+
   \[ \begin{array}{l}
-     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
-     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
-     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\dots) \in \text{adjOut}(PG_i,m) \} \\ 
-     ~~~~~~~~~~~~~~~~~~ ma = ord_i(f(m)) : (in,q_n) \rightarrow (out,q_m) \} \} \\
+     ~~~~~ \{ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~ rc = con(\bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \} \\
   \end{array} \]%
 
+  Apply definition of $con$
+
   \[ \begin{array}{l}
-     ~~~~~ \{ l \rightarrow rc ~\vert~ rc = \\
-     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
-     ~~~~~~~~~~~~~~~~~~ l \in internal(V), \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ f^{-1}(b) ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \cap E^{-1} \\
-     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A_i,M) \}) \cap E \\ 
-     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+     ~~~~~ \{ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~ rc = \bigcup_i~ con(\{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \} \\
   \end{array} \]%
 
+  \vspace{1em}
+  \textbf{Case 1}: Assume $t_i = pfx$. Look at:
+
   \[ \begin{array}{l}
-     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
-     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
-     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
-     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~ con(\{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ f^{-1}(b) ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \cap E^{-1} \\
-     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ f^{-1}(c) ~\vert~ (c,\dots) \in \text{adjOut}(PG^A_i,M) \}) \cap E \\ 
-     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \\
   \end{array} \]%
 
+  Apply definition of $con$
+
   \[ \begin{array}{l}
-     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
-     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
-     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
-     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~ \{ pfx \rightarrow con(ma_1, \dots, ma_k) ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = con(\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = con(\{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \}) \\
-     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
   \end{array} \]%
 
+  Apply definition of $con$
+
   \[ \begin{array}{l}
-     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
-     ~~~~~~~ \bigcup~ \{ pfx \rightarrow ma ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
-     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
-     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~ \{ pfx \rightarrow con(ma_1), \dots, con(ma_k) ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma = con(ord^A_i(M) : (in,q_n) \rightarrow (out,q_M)) \} \} \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \\
   \end{array} \]%
 
+  Apply definition of $con$
+
   \[ \begin{array}{l}
-     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
-     ~~~~~~~ \bigcup~ \{ pfx \rightarrow con(ma) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ pfx \in \Gamma(t_i), \\
-     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
-     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~ con(\{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M), \text{true}) \}) \\
   \end{array} \]%
 
+  Apply definition of $con$
+
   \[ \begin{array}{l}
-     ~~~~~ \{ l' \rightarrow rc ~\vert~ rc = \\
-     ~~~~~~~ con(\bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
-     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \}) \} \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (con(in),q_N) \rightarrow (con(out),q_M) \} \\
   \end{array} \]%
 
+  Rewrite on $in$ and $out$
+
   \[ \begin{array}{l}
-     ~~~~~ \{ l' \rightarrow rc ~\vert~ con(rc) = \\
-     ~~~~~~~ \bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ l' \in f^{-1}(l), \\
-     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \} \\
+     ~~~~~~~~~~~~~~~~~~ in = con(\{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}) \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
   \end{array} \]%
 
+  Apply definition of $con$
+
   \[ \begin{array}{l}
-     ~~~~~ con(\{ l \rightarrow rc ~\vert~ rc = \\
-     ~~~~~~~ \bigcup~ \{ t_i \rightarrow ma ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \}) \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b \in f^{-1}(B), (B,\ell) \in G.E, (B,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c \in f^{-1}(C), (C,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
   \end{array} \]%
 
+  From the relation between concrete ($PG$) and abstract ($PG^A$) product graphs
+
   \[ \begin{array}{l}
-     = con(\textbf{compile}( (t_1,PG^A_1,ord^A_1), \dots, (t_k,PG^A_k,ord^A_k) )) \\
+     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG_{i1},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) \} \\
+  \end{array} \]%
+
+  \ryan {Proof that we can change this to concrete topology}
+
+  Since $ord^A_i(f_{pg}(m)) = ord_{i1}(m)$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG_{i1},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_N) \rightarrow (out,q_M) \} \\
+  \end{array} \]%
+
+  Since product graphs have equivalent states
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{i1},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
+  \end{array} \]%
+
+  \vspace{1em}
+  \textbf{Case 2}: Assume $t_i = \$x$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ con(\{ \$x \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \\
+  \end{array} \]%
+
+  Apply the definition of $con$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx_{ij} \rightarrow con(ma_1, \dots, ma_k) ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
+  \end{array} \]%
+
+  Apply definition $con$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx_{ij} \rightarrow con(ma_1), \dots, con(ma_k) ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
+  \end{array} \]%
+
+  Rewrite $con$ on $ma_h$.
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M), l_{ij} = \ell) \} \\
+  \end{array} \]%
+
+  Apply definition of $con$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = \textbf{if}~ in=\{ G.s \} \text{ and } l_{ij} \neq \ell ~\textbf{then}~ \bullet \\ 
+     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else}~ ord^A_i(M) : (con(in),q_N) \rightarrow (con(out),q_M) \} \\
+  \end{array} \]%
+
+  \textbf{Observation}: 
+  By filtering the cases where $in = \{ G.s \}$ and $l_{ij} \neq \ell$ we get the same thing as before after applying the definition of $con$:
+
+ \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{ij},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
+  \end{array} \]%
+
+  This works because each $PG_{ij}$ was constructed from $con(r_{ijk}) \cap end(l_{ij})$.
+This means that the only state in $PG_{ij}$ connected to the start node $G.s$ is a node for $l_{ij}$.
+This was ensured by the fact that the transition function for each regular expression $\sigma_{ijk}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{ij} \}$ from the construction of the automata.
+
+  \vspace{1em}
+  \textbf{Merging Cases}:
+
+  In the first case, we got a result of the form:
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{i1},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
+  \end{array} \]%
+
+  In the second case, we got a result of the form:
+
+ \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{ij},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
+  \end{array} \]%
+
+  Putting these together, we get the following:
+
+  \[ \begin{array}{l}
+     ~~~~~ \{ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~ l \in internal(V^A), \\
+     ~~~~~~~~~ rc = \bigcup_{ij}~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{ij},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
+  \end{array} \]%
+
+  Finally, we observe that this is equivalent to the following:
+
+  \[ \begin{array}{l}
+     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~ l \in internal(V), \\
+     ~~~~~~~~~ rc = \bigcup_{ij}~ con(\{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{ij},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
+  \end{array} \]%
+
+  This is exactly the definition of compilation for the concretized policy
+
+  \[ \begin{array}{l}
+     = \textbf{compile}( (pfx_{11},PG_{11},ord_{11}), \dots, (pfx_{ij},PG_{ij},ord_{ij}) ) \\
   \end{array} \]%

### 2016-11-08 paper/abstraction/appendix.tex
complete substitution proof

@@
 
-\newtheorem{thm}{Theorem}[section]
+\newtheorem{thm}{Theorem}
 \newtheorem{defn}{Definition}
@@
     p \in \Lang(con(r^*)) &\iff& f(p) \in \Lang(r^*) \\
-    \ryan{TODO} & & \\
+    p \in \Lang(con(r)^*) &\iff& f(p) \in \Lang(r^*) \\
+    p \in \bigcup_{i \in \mathbb{N}} \Lang(con(r))^i &\iff& f(p) \in \bigcup_{i \in \mathbb{N}} \in \Lang(r)^i \\
+    \text{Follows from IH and definition of } \Lang(r)^i & & \\
   \end{array} \]
@@
 
-\begin{cor}
-  foo
-\end{cor}
-
 \subsection{Product Graph}
@@
 
-\begin{thm}
+\begin{lem}
   $m \leq m'$ in the concrete product graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph under the lifted graph homomorphism $f_{pg}$.
@@
   \begin{proof}
-    $(\leftarrow)$
+    $(\Leftarrow)$
 
@@
   \begin{proof}
-    $(\rightarrow)$
+    $(\Rightarrow)$
 
@@
 
-\end{thm}
+\end{lem}
 
@@
 
-\subsection{Substitution}
-
 \begin{defn}
@@
 
+\subsection{Substitution}
+
+\begin{lem}
+
+  For concrete ($PG$) and abstract ($PG^A$) product graphs related by $f_{pg}$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~ in = \bigcup_B~ \{ b \in f^{-1}(B), (b,\ell) \in G.E, (B,q_N) \in \text{adjIn}(PG^A,M) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \bigcup_C~ \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(M) : (in,q_N) \rightarrow (out,q_M) \} \\
+  \end{array} \]%
+
+  Is equivalent to
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG, \\
+     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) \} \\
+  \end{array} \]%
+
+  \begin{proof}
+    For each $M$ there exists at least one $m$ such that $f_{pg}(m) = M$.
+Note that $f_{pg}$ overapproximates the connectivity of the product graph, by virtue of being a graph homomorphism.
+For each concrete node $n$ such that $n = (b,q_n) \in adjIn(PG,m)$ we know that if $f_{pg}(n) = N$ where $N = (f(b),q_N)$, then $N \in adjIn(PG^A,M)$ and $q_n = q_N$ from the homomorphism.
+Thus by taking $\bigcup f^{-1}(f(b))$, for each such $f(b)$ for node $N$ that shares the same state $q_N$, we get a superset of the locations from the concrete graph.
+However, by restricting those locations to only those that appear in the topology $(b,\ell)$, we get exactly the set that appears in the concrete product graph.
+This is because we know $q_n \rightarrow q_m$ from the abstract product graph is a valid transition and the topology edge exists.
+  \end{proof}
+
+\end{lem}
+
+\vspace{2em}
 \begin{thm}
@@
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b \in f^{-1}(B), (B,\ell) \in G.E, (B,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c \in f^{-1}(C), (C,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ in = \bigcup_B~ \{ b \in f^{-1}(B), (b,\ell) \in G.E, (B,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \bigcup_C~ \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
      ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
@@
 
-  From the relation between concrete ($PG$) and abstract ($PG^A$) product graphs
+  From the relation between concrete ($PG$) and abstract ($PG^A$) product graphs given by the previous lemma
 
@@
   \end{array} \]%
-
-  \ryan {Proof that we can change this to concrete topology}
 

### 2016-11-08 paper/abstraction/appendix.tex
clean up substitution proof

@@
-\documentclass[twocolumn]{sig-alternate-10pt}
+\documentclass[twocolumn, openany]{sig-alternate-10pt}
 %\documentclass[twocolumn]{article}
@@
 
+\onecolumn
+
 \appendix
 
-\onecolumn
 \section{Definitions}
@@
 The language includes constraints of the form $\CD{\Agg(pfx, \ensuremath{r_1 \rightarrow r_2})}$ that say that aggregation for summary prefix $\CD{pfx}$ will occur from any single location matching $\CD{\ensuremath{r_1}}$ to any location matching $\CD{\ensuremath{r_2}}$.
+For simplicity, we prove the substitution property for \sysname for the fragment without aggregation.
 
@@
 A prefix configuration $pc$ is a sequence of match actions $ma$.
-Each match action $ma$ consists of a preference value $n$, followed by a set of peers $ns$ and community value (\IE, state of the product graph) $n$, and the exports the route to a new set of neighbors $ns$ and updates the community value $n$.
+Each match action $ma$ consists of a preference value $n_1$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $n_2$, as well as export neighbors $ns_2$ and the updated community value $n_3$.
 
@@
 
+\para{Compilation}
+
+Figure~\ref{fig:abgp-syntax} also defines compilation from a \sysname policy to an ABGP policy.
+It starts by compiling separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$, the particular test $t_i$, and the preference ordering $ord_i$.
+
+The function $compile_{ABGP}$ then takes tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy.
+It looks at each incoming neighbor with the same community state $q_n$ and matches any of those neighbor with the preference provided by the ordering $ord$ obtained from the search for local preferences.
+It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.
+
+\vspace{1em}
+
 We assume a particular router $l$ appears at most once in any abgp specification.
-An abgp configuration is a partial function from router to prefix configuration.
-We write $abgp(l)$ to apply such a config to a router location $l$.
-%
 We often build configs using set-builder notation.  For instance,
@@
 where $l_1, ..., l_k$ are the nodes in the topology
-and each $rc_{ij}$ satisfies $p(l_i,rc_{ij})$. Similarly for $rc$.
-
-\para{Compilation}
-
-Figure~\ref{fig:abgp-syntax} also defines compilation from a \sysname policy to an ABGP policy.
-It starts by compiling separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$, the particular test $t_i$, and the preference ordering $ord_i$.
-
-The function $compile_{ABGP}$ then takes tuples of $(t_i, PG_i, ord_i)$ and returns an ABGP policy.
-It looks at each incoming neighbor with the same community state $q_n$ and matches any of those neighbor with the preference provided by the ordering $ord$ obtained from the search for local preferences.
-It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.
+and each $rc_{ij}$ satisfies $p(l_i,rc_{ij})$.
 
@@
 
-Here we define what it means to concretize an abstract \sysname policy. 
+We define what it means to concretize an abstract \sysname policy. 
 Concretization takes as input, a policy and a context $\Gamma$ mapping from a template prefix to a set of pairs of a concrete prefix and a concrete location where the prefix is owned.
@@
 \[ \begin{array}{lcl}
-  con(\emptyset,\Gamma)                        & = & \emptyset \\
-  con(l,\Gamma)                                & = & \Sigma ~ f^{-1}(l) \\
-  con(r_1 \cup r_2,\Gamma)                     & = & con(r_1,\Gamma) \cup con(r_2,\Gamma) \\
-  con(r_1 \cap r_2,\Gamma)                     & = & con(r_1,\Gamma) \cap con(r_2,\Gamma) \\
-  con(!r,\Gamma)                               & = & !con(r,\Gamma) \\
-  con(r^*,\Gamma)                              & = & con(r,\Gamma)^* \\
-  con(pfx \Rightarrow r_1, \dots, r_k,\Gamma)  & = & pfx \Rightarrow con(r_1,\Gamma), \dots, con(r_k,\Gamma) \\
-  con(\$x \Rightarrow r_1, \dots, r_k,\Gamma)  & = & \{ pfx \Rightarrow con(r_1,\Gamma) \cap \textbf{end}(l), \dots, \\
-  & & ~~~~~~~~~~~~~~~ con(r_k,\Gamma) \cap \textbf{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \} \\
+  con(\emptyset,\Gamma,f)                        & = & \emptyset \\
+  con(l,\Gamma,f)                                & = & \Sigma ~ f^{-1}(l) \\
+  con(r_1 \cup r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cup con(r_2,\Gamma,f) \\
+  con(r_1 \cap r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cap con(r_2,\Gamma,f) \\
+  con(!r,\Gamma,f)                               & = & !con(r,\Gamma,f) \\
+  con(r^*,\Gamma,f)                              & = & con(r,\Gamma,f)^* \\
+  con(pfx \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & pfx \Rightarrow con(r_1,\Gamma,f), \dots, con(r_k,\Gamma,f) \\
+  con(\$x \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & 
+       \{ pfx \Rightarrow con(r_1,\Gamma,f) \cap \text{end}(l), 
+          \dots, 
+          con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \} \\
+  %& & ~~~~~~~~~~~~~~~ \dots, \\
+  %& & ~~~~~~~~~~~~~~~ con(r_k,\Gamma,G) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x),  ~l \in G.V \} \\
+  con(p_1, \dots, p_n, \Gamma, f)                & = & con(p_1,\Gamma,f), \dots, con(p_n,\Gamma,f) \\
 \end{array} \]
@@
 For each template variable, we replace it with a new entry for each of its corresponding concrete values under the supplied mapping $\Gamma$.
-We also intersect the resulting concretized regular expression with $\textbf{end}(l)$ to capture the fact that traffic is owned by the concrete location $l$.
-\textbf{Note}: we need the side condition that $\textbf{end}(l) \cap con(r_i,\Gamma) \neq \emptyset$ if $con(r_i,\Gamma) \neq \emptyset$.
+We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that traffic is owned by the concrete location $l$.
+\textbf{Note}: we need the side condition that $\text{end}(l) \cap con(r_i,\Gamma) \neq \emptyset$ if $con(r_i,\Gamma) \neq \emptyset$.
 We can also define concretization over the ABGP policy as:
@@
 \[ \begin{array}{lcl}
-     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,G) 
+     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G) 
         & = & 
-        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
+        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
         \\
-     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,G) 
+     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G) 
         & = &  
-        con(t_1 \rightarrow {pc}_1,\ell,\Gamma,G), \dots, con(t_k \rightarrow {pc}_k,\ell,\Gamma,G)
+        con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
         \\
-     con(pfx \rightarrow {pc},\ell,\Gamma,G) 
+     con(pfx \rightarrow {pc},\ell,\Gamma,f,G) 
         & = &  
-        pfx \rightarrow con(pc,\text{true},\ell,\Gamma,G)
+        pfx \rightarrow con(pc,\text{true},\ell,\Gamma,f,G)
         \\
-     con(\$x \rightarrow {pc},\ell,\Gamma,G) 
+     con(\$x \rightarrow {pc},\ell,\Gamma,f,G) 
         & = &  
-        \{ pfx \rightarrow con(pc, l=\ell, \ell,\Gamma,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
+        \{ pfx \rightarrow con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
         \\
-     con(ma_1, \dots, ma_k,o,\ell,\Gamma,G) 
+     con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G) 
         & = &
-        con(ma_1,o,\ell,\Gamma,G), \dots, con(ma_k,o,\ell,\Gamma,G)
+        con(ma_1,o,\ell,\Gamma,f,G), \dots, con(ma_k,o,\ell,\Gamma,f,G)
         \\
 
-     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,G) 
+     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
         & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
-        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,G),n_3)
+        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,f,G),n_3)
 
         \\
-     con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,G) 
+     con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G) 
         & = &  
@@
 \end{array} \]
+
+We use the symbol $\bullet$ to denote that a particular value in a sequence is removed from the sequence.
 
@@
 
-The goal of this section is to prove that the concretization and compilation functions commute.
-That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values afterwards.
+The goal of this section is to prove that the concretization and compilation functions commute: 
+$$con(compile(pol),\Gamma,f,G) = compile(con(pol,\Gamma,f))$$ 
+That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values on after compilation is complete.
+Note that the theorem states that the resulting ABGP policies are actually syntactically equivalent and not semantically equivalent.
 First we need a few helper theorems about compilation.
@@
 
+\vspace{1em}
 \begin{lem}
-  For any map $\Gamma$ and regular expression $r$ over abstract locations, path $p \in \Lang(con(r,\Gamma)) \iff f(p) \in \Lang(r)$.
+  For any $\Gamma$, $f$, and $r$, path $p \in \Lang(con(r,\Gamma,f)) \iff f(p) \in \Lang(r)$.
 \end{lem}
@@
   \[ \begin{array}{lll}
-    p \in \Lang(con(\emptyset)) &\iff& f(p) \in \Lang(\emptyset) \\
+    p \in \Lang(con(\emptyset,\Gamma,f)) &\iff& f(p) \in \Lang(\emptyset) \\
     p \in \emptyset &\iff& f(p) \in \emptyset \\
@@
   \[ \begin{array}{lll}
-    p \in \Lang(con(l)) &\iff& f(p) \in \Lang(l) \\
+    p \in \Lang(con(l,\Gamma,f)) &\iff& f(p) \in \Lang(l) \\
     p \in \Lang(\Sigma ~ f^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
@@
   \[ \begin{array}{lll}
-    p \in \Lang(con(r_1 \cup r_1)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
-    p \in \Lang(con(r_1) \cup con(r_1)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
-    p \in \Lang(con(r_1)) \cup \Lang(con(r_1)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
-    p \in \Lang(con(r_1)) \vee p \in \Lang(con(r_1)) 
+    p \in \Lang(con(r_1 \cup r_1,\Gamma,f)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
+    p \in \Lang(con(r_1,\Gamma,f) \cup con(r_1,\Gamma,f)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
+    p \in \Lang(con(r_1,\Gamma,f)) \cup \Lang(con(r_1,\Gamma,f)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
+    p \in \Lang(con(r_1,\Gamma,f)) \vee p \in \Lang(con(r_1,\Gamma,f)) 
        &\iff& 
@@
   \[ \begin{array}{c}
-    \text{symmetric to } \cup \text{ case}
+    \text{symmetric to } \cup \text{ case with } \wedge \text{ instead of } \vee
   \end{array} \]
@@
   \[ \begin{array}{lll}
-    p \in \Lang(con(!r)) &\iff& f(p) \in \Lang(!r) \\
-    p \in \Lang(!con(r)) &\iff& f(p) \in \Lang(!r) \\
-    p \in \Sigma^* - \Lang(con(r)) &\iff& f(p) \in \Sigma^* - \Lang(r) \\
+    p \in \Lang(con(!r,\Gamma,f)) &\iff& f(p) \in \Lang(!r) \\
+    p \in \Lang(!con(r,\Gamma,f)) &\iff& f(p) \in \Lang(!r) \\
+    p \in \Sigma^* - \Lang(con(r,\Gamma,f)) &\iff& f(p) \in \Sigma^* - \Lang(r) \\
     \text{by IH} & & \\
@@
   \[ \begin{array}{lll}
-    p \in \Lang(con(r^*)) &\iff& f(p) \in \Lang(r^*) \\
-    p \in \Lang(con(r)^*) &\iff& f(p) \in \Lang(r^*) \\
-    p \in \bigcup_{i \in \mathbb{N}} \Lang(con(r))^i &\iff& f(p) \in \bigcup_{i \in \mathbb{N}} \in \Lang(r)^i \\
+    p \in \Lang(con(r^*,\Gamma,f)) &\iff& f(p) \in \Lang(r^*) \\
+    p \in \Lang(con(r,\Gamma,f)^*) &\iff& f(p) \in \Lang(r^*) \\
+    p \in \bigcup_{i \in \mathbb{N}} \Lang(con(r,\Gamma,f))^i &\iff& f(p) \in \bigcup_{i \in \mathbb{N}} \in \Lang(r)^i \\
     \text{Follows from IH and definition of } \Lang(r)^i & & \\
@@
   Consider the PG created from compiling the constraint $p = (t ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$ with state machine $M^A_i$ for each $r_i$.
-We know that, for each $(pfx ~\Path~ r'_1 ~\Prefer~,\dots, ~\Prefer~ r'_k) \in con(p)$ where $r'_i$ is of the form $r \cap \text{end}(L)$ we can constuct state machine $M_i$ for $r'_i$ over the same states in the following way:
+We know that, for each $(pfx ~\Path~ r'_1 ~\Prefer~,\dots, ~\Prefer~ r'_k) \in con(p,\Gamma,f)$ where $r'_i$ is of the form $r \cap \text{end}(L)$ we can constuct state machine $M_i$ for $r'_i$ over the same states in the following way:
 
@@
     \[ \begin{array}{lcl}
-      con(p) &=& pfx_1 ~\Path~ con(r_1) \cap \text{end}(l_1), ~\Prefer~ \dots ~\Prefer~ con(r_k) \cap \text{end}(l_1)  \\
+      con(p) &=& pfx_1 ~\Path~ con(r_1,\Gamma,f) \cap \text{end}(l_1), ~\Prefer~ \dots ~\Prefer~ con(r_k,\Gamma,f) \cap \text{end}(l_1)  \\
              & & \dots, \\
-             & & pfx_n ~\Path~ con(r_1) \cap \text{end}(l_n), ~\Prefer~ \dots ~\Prefer~ con(r_k) \cap \text{end}(l_n)
+             & & pfx_n ~\Path~ con(r_1,\Gamma,f) \cap \text{end}(l_n), ~\Prefer~ \dots ~\Prefer~ con(r_k,\Gamma,f) \cap \text{end}(l_n)
     \end{array} \]
@@
 Because $M^A_i$ matches $f(p)$, this means that $f(p) \in \Lang(r_i)$.
-From our above lemma, this means that $p \in \Lang(con(r_i))$.
+From our above lemma, this means that $p \in \Lang(con(r_i,\Gamma,f))$.
 We also know that, since $L = \{ l_i \}$, the first transition $\sigma(q_0,l_i)$ is the only transition allowed from the initial state for $M_i$.
 So this means that $p \in \Lang(\text{end}(l_i))$.
-Since we know that $p \in \Lang(con(r_i))$ and $p \in \Lang(\text{end}(l_i))$, we know that $p \in \Lang(con(r_i) \cap \text{end}(l_i))$ and thus $p \in \Lang(r'_i)$.
+Since we know that $p \in \Lang(con(r_i,\Gamma,f))$ and $p \in \Lang(\text{end}(l_i))$, we know that $p \in \Lang(con(r_i,\Gamma,f) \cap \text{end}(l_i))$ and thus $p \in \Lang(r'_i)$.
 
@@
     \[ \begin{array}{lcl}
-      con(p) &=& pfx_1 ~\Path~ con(r_1) \cap \text{end}(\Sigma^*), ~\Prefer~ \dots ~\Prefer~ con(r_k) \cap \text{end}(\Sigma^*) \\
+      con(p,\Gamma,f) &=& pfx_1 ~\Path~ con(r_1,\Gamma,f) \cap \text{end}(\Sigma^*), ~\Prefer~ \dots ~\Prefer~ con(r_k,\Gamma,f) \cap \text{end}(\Sigma^*) \\
     \end{array} \]
@@
                          &\iff& f(p) \in \Lang(r) \\
-                         &\iff& p \in \Lang(con(r)) \\
+                         &\iff& p \in \Lang(con(r,\Gamma,f)) \\
     \end{array} \]%
@@
 
+\vspace{1em}
 \subsection{Product Graph}
@@
 
+\vspace{1em}
 \begin{lem}
@@
 
+\vspace{1em}
 \begin{defn}
@@
 
+\vspace{1em}
 \subsection{Substitution}
@@
 \begin{thm}
-  $compile(con(pol)) = con(compile(pol))$
+  For any $\Gamma$, $f$, $G$ such that $\Gamma$ is well-formed with respect to $G$,
+  $$con(compile(pol),\Gamma,f,G) = compile(con(pol,\Gamma,f))$$
 
@@
     \[ \begin{array}{lcl}
-      con(pol) & = & con(p_1,\dots,p_n) \\
-               & = & con(p_1), \dots, con(p_n) \\
-               & = & con(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k}), \\
+      con(pol,\Gamma,f) & = & con(p_1,\dots,p_n,\Gamma,f) \\
+                        & = & con(p_1,\Gamma,f), \dots, con(p_n,\Gamma,f) \\
+                        & = & con(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k},\Gamma,f), \\
                         &   & \dots, \\
-               &   & con(t_n ~\Path~ r_{n1} ~\Prefer~,\dots, ~\Prefer~ r_{nk}) \\
+                        &   & con(t_n ~\Path~ r_{n1} ~\Prefer~,\dots, ~\Prefer~ r_{nk},\Gamma,f) \\
     \end{array} \]
@@
 
+    \[ \begin{array}{ll}
+          & con({pfx}_{i1} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik},\Gamma,f) \\
+        = & {pfx}_{i1} ~\Path~ con(r_{i1},\Gamma,f) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik},\Gamma,f) \\
+    \end{array} \]
+
+    For each test $t_i$, if $t_i = \$x$, then we get
+
     \[ \begin{array}{lcl}
-        con({pfx}_{i1} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik}) 
-           & = & {pfx}_{i1} ~\Path~ con(r_{i1}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik}) \\
-    \end{array} \]
-
-    For each test $t_i$, if $t_i = \$x$, then we get
-
-    \[ \begin{array}{lcl}
-        con(\$x_{i} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik}) 
-            & = & {pfx}_{i1} ~\Path~ con(r_{i1}) \cap \text{end}(l_{i1}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik}) \cap \text{end}(l_{i1}), \\
+        con(\$x_{i} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik},\Gamma,f) 
+            & = & {pfx}_{i1} ~\Path~ con(r_{i1},\Gamma,f) \cap \text{end}(l_{i1}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik},\Gamma,f) \cap \text{end}(l_{i1}), \\
             &   & \dots, \\ 
-            &   & {pfx}_{ij} ~\Path~ con(r_{i1}) \cap \text{end}(l_{ij}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik}) \cap \text{end}(l_{ij}), \\
+            &   & {pfx}_{ij} ~\Path~ con(r_{i1},\Gamma,f) \cap \text{end}(l_{ij}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik},\Gamma,f) \cap \text{end}(l_{ij}), \\
             &   & \\
@@
 
-    Next we compute $compile(con(pol))$:
-
-    \[ \begin{array}{lcl}
-        compile(con(pol)) &=& compile_{ABGP}( \\
-                          & & ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k} ), \\
-                          & & ~~~~ \dots, \\
-                          & & ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk} ), \\
-                          & & ~~~~ \dots, \\
-                          & & ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k} ), \\
-                          & & ~~~~ \dots, \\
-                          & & ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk} ) \\
-                          & & ) \\
-    \end{array} \]
-
+    Next we compute $compile(con(pol,\Gamma,f))$:
+
+    \[ \begin{array}{ll}
+        & compile(con(pol,\Gamma,f))  \\
+                          & \\
+                         =& compile_{ABGP}( \\
+                          &  ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k} ), \\
+                          &  ~~~~ \dots, \\
+                          &  ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk} ), \\
+                          &  ~~~~ \dots, \\
+                          &  ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k} ), \\
+                          &  ~~~~ \dots, \\
+                          &  ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk} ) \\
+                          &  ) \\
+    \end{array} \]
+
+    \vspace{.5em}
     This results in a series of prefixes, product graphs, and orderings of the form: $(pfx_{ij}, PG_{ij}, ord_{ij})$.
@@
 
-    \[ \begin{array}{lcl}
-        compile(pol) &=& compile_{ABGP}( \\
-                     & & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k} ), \\
-                     & & ~~~~ \dots, \\
-                     & & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik} ), \\
-                     & & ) \\
+    \[ \begin{array}{ll}
+        & compile(pol)  \\
+                      & \\
+                     =& compile_{ABGP}( \\
+                      & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k} ), \\
+                      & ~~~~ \dots, \\
+                      & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik} ), \\
+                      & ) \\
     \end{array} \]
@@
   \[ \begin{array}{l}
-     con(\textbf{compile}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) )) \\
+     con(\textbf{compile}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) ), \Gamma,f,G) \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \}) \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \}, \Gamma,f,G) \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~ \{ \ell \rightarrow con(rc) ~\vert~ \\
+     ~~~~~ \{ \ell \rightarrow con(rc,\ell,\Gamma,f,G)) ~\vert~ \\
      ~~~~~~~~~ \ell \in f^{-1}(l), \\
@@
      ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}, \ell,\Gamma,f,G) \} \\
   \end{array} \]%
@@
      ~~~~~~~~~ con(\{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \},\ell,\Gamma,f,G) \\
+  \end{array} \]%
+
+  Apply definition of $con$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx \rightarrow con(ma_1, \dots, ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
+  \end{array} \]%
+
+  Apply definition of $con$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ \{ pfx \rightarrow con(ma_1,\text{true},\ell,\Gamma,f,G), \dots, con(ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow con(ma_1, \dots, ma_k) ~\vert~ \\
+     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
@@
      ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M), \text{true},\ell,\Gamma,f,G) \}) \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow con(ma_1), \dots, con(ma_k) ~\vert~ \\
+     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
@@
      ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \\
-  \end{array} \]%
-
-  Apply definition of $con$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ con(\{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M), \text{true}) \}) \\
-  \end{array} \]%
-
-  Apply definition of $con$
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M) \} \\
+  \end{array} \]%
+
+  Rewrite on $in$ and $out$
 
@@
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (con(in),q_N) \rightarrow (con(out),q_M) \} \\
-  \end{array} \]%
-
-  Rewrite on $in$ and $out$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = con(\{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}) \\
+     ~~~~~~~~~~~~~~~~~~ in = con(\{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \},\ell,\Gamma,f,G) \\
+     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G) \\
      ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
@@
      ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \},\ell,\Gamma,f,G) \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx_{ij} \rightarrow con(ma_1, \dots, ma_k) ~\vert~ \\
+     ~~~~~~~~~ \{ pfx_{ij} \rightarrow con(ma_1, \dots, ma_k,l_{ij} = \ell,\ell,\Gamma,f,G) ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx_{ij} \rightarrow con(ma_1), \dots, con(ma_k) ~\vert~ \\
+     ~~~~~~~~~ \{ pfx_{ij} \rightarrow con(ma_1,l_{ij} = \ell,\ell,\Gamma,f,G), \dots, \\ 
+     ~~~~~~~~~~~~~~~~~~~~~~~~~~~ con(ma_k,l_{ij} = \ell,\ell,\Gamma,f,G) ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
@@
      ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M), l_{ij} = \ell) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),l_{ij} = \ell,\ell,\Gamma,f,G) \} \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~~~~ ma_h = \textbf{if}~ in=\{ G.s \} \text{ and } l_{ij} \neq \ell ~\textbf{then}~ \bullet \\ 
-     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else}~ ord^A_i(M) : (con(in),q_N) \rightarrow (con(out),q_M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else}~ ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M) \} \\
   \end{array} \]%
@@
   \textbf{Observation}: 
-  By filtering the cases where $in = \{ G.s \}$ and $l_{ij} \neq \ell$ we get the same thing as before after applying the definition of $con$:
+  By filtering the cases where $in = \{ G.s \}$ and $l_{ij} \neq \ell$ we get the same thing as before after applying the definition of $con$, however for each $(pfx_{ij}, l_{ij}) \in \Gamma(x)$.
 

### 2016-11-08 paper/abstraction/paper.tex
remove appendix from main paper

@@
 
-\appendix
-
-\section{Start}
-
-\begin{figure*}[t!]\small
-  \begin{minipage}[t]{.45\linewidth}
-  \hdr{Syntax}{}
-  \vspace*{-1\baselineskip}
-  %
-  \[ \begin{array}{rclr}
-    \hline%
-
-     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
-     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
-     pfx     &::=& d.d.d.d/[d..d] & \textit{prefix} \\
-     t       &::=& \$x & \textit{template variable} \\
-         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
-         &\BNFALT& pfx & \textit{prefix test} \\
-     r       &::=& l & \textit{location} \\
-         &\BNFALT& \emptyset & \textit{empty set} \\
-         &\BNFALT& \In & \textit{internal loc} \\
-         &\BNFALT& \Out & \textit{external loc} \\
-         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
-         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
-         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
-         &\BNFALT& \NOT r & \textit{path negation} \\
-         &\BNFALT& r^* & \textit{iteration} \\
-     cc     &::=& agg(pfx, r_1 \rightarrow r_2)  & \textit{control constraints} \\
-  \end{array} \]%
-
-  \end{minipage}
-  %
-  ~~
-  \vrule
-  ~~
-  %
-  \begin{minipage}[t]{.5\linewidth}\small
-  \hdr{Propane Expansions}{}
-  \vspace*{-1\baselineskip}
-  %
-  \[\begin{array}{rcl}
-    \hline
-    \Any               & = & \Sigma^* \\
-    \None              & = & \emptyset \\
-    \Internal          & = & \In^+ \\
-    \Always(X)         & = & X^* \\
-    \Never(X)          & = & (!X)^* \\
-    \Through(X)        & = & \Sigma^* \cdot X \cdot \Sigma^* \\
-    \End(X)            & = & \Sigma^* \cdot X \\
-    \Start(X)          & = & X \cdot \Sigma^* \\
-    \Enter(X)          & = & \Sigma^* \cdot \Out \cdot (X \cap \In) \cdot \Sigma^* ~ \cup \\
-                       &   & \Sigma^* \cdot (X \cap \Out) \cdot \In \cdot \Sigma^* \\
-    \Exit(X)           & = & \Sigma^* \cdot \In \cdot (X \cap \Out) \cdot \Sigma^* ~ \cup \\
-                       &   & \Sigma^* \cdot (X \cap \In) \cdot \Out \cdot \Sigma^* \\
-    \LinkKW(X,Y)       & = & \Sigma^* \cdot X \cdot Y \cdot \Sigma^* \\
-    \PathKW(\vec{X})   & = & \Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^* \\
-    \Novalley(\vec{X}) & = & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
-                       &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
-  \end{array} \]%
-
-  \end{minipage}%
-
-  \hrulefill%
-
-  \caption{Regular Intermediate Representation (RIR) syntax (left), and
-           Propane language expansions (right).}
-  \label{fig:rir-syntax}
-  %\vspace{-1em}
-\end{figure*}%
-
-foo
-
-\begin{figure}[t]\small
-  \begin{minipage}[t]{\linewidth}
-  \vspace*{-1\baselineskip}
-  %
-  \[ \begin{array}{rclr}
-     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
-     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
-     t       &::=& \$x & \textit{template variable} \\
-         &\BNFALT& d.d.d.d/[d..d] & \textit{prefix test} \\
-     r       &::=& l & \textit{location} \\
-         &\BNFALT& \emptyset & \textit{empty set} \\
-         &\BNFALT& \In & \textit{internal loc} \\
-         &\BNFALT& \Out & \textit{external loc} \\
-         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
-         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
-         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
-         &\BNFALT& \NOT r & \textit{path negation} \\
-         &\BNFALT& r^* & \textit{iteration} \\
-  \end{array} \]%
-
-  \end{minipage}
-  \vspace{1em}
-  \caption{Simplified BGP syntax.}
-  \label{fig:abgp-syntax}
-\end{figure}%
-
-blah
-
 \end{document}

### 2016-11-08 paper/abstraction/appendix.tex
add formal definitions

@@
 
+\newcommand{\Con}{\text{con}}
+
 \vspace{2em}
@@
 
-  \begin{minipage}[t]{.5\linewidth}
+  \begin{minipage}[t]{.46\linewidth}
+  \hdr{ABGP Syntax}{}
   \vspace*{-1\baselineskip}
@@
   %
-  ~~
-  \vrule
-  ~~
   %
   \begin{minipage}[t]{.5\linewidth}
+  \hdr{Compilation}{}
   \vspace*{-1\baselineskip}
@@
   \[ \begin{array}{l}
-     \textbf{compile}_\textbf{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
+     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
      ~~~~~ \{ l \rightarrow rc ~\vert~ \\
@@
      \\
-     \textbf{compile}( p_1, \dots, p_k ) = \\
-     ~~~~~~ compile_{ABGP}(compile_{PG}(p_1), \dots, compile_{PG}(p_k)) \\
-  \end{array} \]%
-
+     \text{compile}( p_1, \dots, p_k ) = \\
+     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1), \dots, \text{compile}_\text{PG}(p_k)) \\
+  \end{array} \]%
   \end{minipage}
@@
   \vspace{1em}
+  \vspace{1em}
+
+  \begin{minipage}[t]{\linewidth}
+  \hdr{ABGP Concretization}{}
+  \vspace*{-2\baselineskip}
+  %
+  \[ \begin{array}{lcl}
+     \\
+     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G) 
+        & = & 
+        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
+        \\
+     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G) 
+        & = &  
+        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
+        \\
+     \Con(pfx \rightarrow {pc},\ell,\Gamma,f,G) 
+        & = &  
+        pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
+        \\
+     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G) 
+        & = &  
+        \{ pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
+        \\
+     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G) 
+        & = &
+        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
+        \\
+
+     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
+        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
+        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)
+
+        \\
+     \Con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G) 
+        & = &  
+        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
+        \\
+  \end{array} \]%
+  \end{minipage}
+
+  \vspace{1em}
+  \vspace{1em}
+
+  \begin{minipage}[t]{\linewidth}
+  \hdr{Policy Concretization}{}
+  \vspace*{-2\baselineskip}
+  %
+  \[ \begin{array}{lcl}
+     \\
+     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
+     \Con(l, \Gamma, f)              &=& \Sigma ~ f^{-1}(l) \\
+     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
+     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
+     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
+     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\
+
+     \Con(pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=& 
+          pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\
+
+     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
+
+         \{ pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~,
+           \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \}  \\
+
+     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\
+
+  \end{array} \]%
+  \end{minipage}
+
+  \vspace{1em}
   \hrulefill%
@@
 
-  \caption{BGP syntax and compilation.}
+  \caption{BGP syntax and compilation and concretization.}
   \label{fig:abgp-syntax}
+
 \end{figure}%
@@
 
-\[ \begin{array}{lcl}
-  con(\emptyset,\Gamma,f)                        & = & \emptyset \\
-  con(l,\Gamma,f)                                & = & \Sigma ~ f^{-1}(l) \\
-  con(r_1 \cup r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cup con(r_2,\Gamma,f) \\
-  con(r_1 \cap r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cap con(r_2,\Gamma,f) \\
-  con(!r,\Gamma,f)                               & = & !con(r,\Gamma,f) \\
-  con(r^*,\Gamma,f)                              & = & con(r,\Gamma,f)^* \\
-  con(pfx \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & pfx \Rightarrow con(r_1,\Gamma,f), \dots, con(r_k,\Gamma,f) \\
-  con(\$x \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & 
-       \{ pfx \Rightarrow con(r_1,\Gamma,f) \cap \text{end}(l), 
-          \dots, 
-          con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \} \\
-  %& & ~~~~~~~~~~~~~~~ \dots, \\
-  %& & ~~~~~~~~~~~~~~~ con(r_k,\Gamma,G) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x),  ~l \in G.V \} \\
-  con(p_1, \dots, p_n, \Gamma, f)                & = & con(p_1,\Gamma,f), \dots, con(p_n,\Gamma,f) \\
-\end{array} \]
+%\[ \begin{array}{lcl}
+%  con(\emptyset,\Gamma,f)                        & = & \emptyset \\
+%  con(l,\Gamma,f)                                & = & \Sigma ~ f^{-1}(l) \\
+%  con(r_1 \cup r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cup con(r_2,\Gamma,f) \\
+%  con(r_1 \cap r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cap con(r_2,\Gamma,f) \\
+%  con(!r,\Gamma,f)                               & = & !con(r,\Gamma,f) \\
+%  con(r^*,\Gamma,f)                              & = & con(r,\Gamma,f)^* \\
+%  con(pfx \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & pfx \Rightarrow con(r_1,\Gamma,f), \dots, con(r_k,\Gamma,f) \\
+%  con(\$x \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & 
+%       \{ pfx \Rightarrow con(r_1,\Gamma,f) \cap \text{end}(l), 
+%          \dots, 
+%          con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \} \\
+%  %& & ~~~~~~~~~~~~~~~ \dots, \\
+%  %& & ~~~~~~~~~~~~~~~ con(r_k,\Gamma,G) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x),  ~l \in G.V \} \\
+%  con(p_1, \dots, p_n, \Gamma, f)                & = & con(p_1,\Gamma,f), \dots, con(p_n,\Gamma,f) \\
+%\end{array} \]
 
@@
 
-\[ \begin{array}{lcl}
-     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G) 
-        & = & 
-        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
-        \\
-     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G) 
-        & = &  
-        con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
-        \\
-     con(pfx \rightarrow {pc},\ell,\Gamma,f,G) 
-        & = &  
-        pfx \rightarrow con(pc,\text{true},\ell,\Gamma,f,G)
-        \\
-     con(\$x \rightarrow {pc},\ell,\Gamma,f,G) 
-        & = &  
-        \{ pfx \rightarrow con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
-        \\
-     con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G) 
-        & = &
-        con(ma_1,o,\ell,\Gamma,f,G), \dots, con(ma_k,o,\ell,\Gamma,f,G)
-        \\
-
-     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
-        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
-        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,f,G),n_3)
-
-        \\
-     con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G) 
-        & = &  
-        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
-        \\
-\end{array} \]
+%\[ \begin{array}{lcl}
+%     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G) 
+%        & = & 
+%        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
+%        \\
+%     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G) 
+%        & = &  
+%        con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
+%        \\
+%     con(pfx \rightarrow {pc},\ell,\Gamma,f,G) 
+%        & = &  
+%        pfx \rightarrow con(pc,\text{true},\ell,\Gamma,f,G)
+%        \\
+%     con(\$x \rightarrow {pc},\ell,\Gamma,f,G) 
+%        & = &  
+%        \{ pfx \rightarrow con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
+%        \\
+%     con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G) 
+%        & = &
+%        con(ma_1,o,\ell,\Gamma,f,G), \dots, con(ma_k,o,\ell,\Gamma,f,G)
+%        \\%
+
+%     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
+%        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
+%        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,f,G),n_3)%
+
+%        \\
+%     con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G) 
+%        & = &  
+%        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
+%        \\
+%\end{array} \]
 

### 2016-11-08 paper/abstraction/paper.tex
add formal definitions

@@
 
-Foo
+\newcommand{\Con}{\text{con}}
+
+\vspace{2em}
+\begin{figure*}[t!]\small
+
+  \hrulefill%
+  \vspace{1em}
+
+  \begin{minipage}[t]{.46\linewidth}
+  \hdr{ABGP Syntax}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rclr}
+     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
+     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
+     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
+     ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
+     ps   &::=& \{ t_1, ~\dots,~ t_k \} & \textit{predicates} \\
+     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
+  \end{array} \]%
+
+  \end{minipage}
+  %
+  %
+  \begin{minipage}[t]{.5\linewidth}
+  \hdr{Compilation}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{l}
+     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
+     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~ l \in internal(V), \\
+     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
+     \\
+     \text{compile}( p_1, \dots, p_k ) = \\
+     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1), \dots, \text{compile}_\text{PG}(p_k)) \\
+  \end{array} \]%
+  \end{minipage}
+
+  \vspace{1em}
+  \vspace{1em}
+
+  \vspace*{-2\baselineskip}
+  \begin{minipage}[t]{\linewidth}
+  \hdr{Policy Concretization}{}
+  \vspace*{-2\baselineskip}
+  %
+  \[ \begin{array}{lcl}
+     \\
+     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
+     \Con(l, \Gamma, f)              &=& \Sigma ~ f^{-1}(l) \\
+     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
+     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
+     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
+     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\
+
+     \Con(pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=& 
+          pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\
+
+     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
+
+         \{ pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~,
+           \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \}  \\
+
+     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\
+
+  \end{array} \]%
+  \end{minipage}
+
+  \vspace{1em}
+  \vspace{1em}
+
+  \begin{minipage}[t]{\linewidth}
+  \hdr{ABGP Concretization}{}
+  \vspace*{-2\baselineskip}
+  %
+  \[ \begin{array}{lcl}
+     \\
+     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G) 
+        & = & 
+        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
+        \\
+     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G) 
+        & = &  
+        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
+        \\
+     \Con(pfx \rightarrow {pc},\ell,\Gamma,f,G) 
+        & = &  
+        pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
+        \\
+     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G) 
+        & = &  
+        \{ pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
+        \\
+     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G) 
+        & = &
+        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
+        \\
+
+     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
+        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
+        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)
+
+        \\
+     \Con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G) 
+        & = &  
+        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
+        \\
+  \end{array} \]%
+  \end{minipage}
+
+  \vspace{1em}
+  \hrulefill%
+  \vspace{1em}
+
+  \caption{ABGP syntax (a), compilation from product graphs (b), Policy concretization (c), and ABGP concretization (d).}
+  \label{fig:abgp-syntax}
+
+\end{figure*}%
 

### 2016-11-09 paper/abstraction/paper.tex
add concretization theorem
stashing changes

@@
      t       &::=& \$x & \textit{template variable} \\
-         &\BNFALT& d.d.d.d/[d..d] & \textit{prefix test} \\
+         &\BNFALT& d.d.d.d/[d..d] ~~~~~~~~~~~~~~~~~~~  & \textit{prefix test} \\
      r       &::=& l & \textit{location} \\
@@
      \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
-        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
+        & = & \textbf{if}~ ns_1 = \{\text{start}\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
         &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)
@@
 
-  \caption{ABGP syntax (a), compilation from product graphs (b), Policy concretization (c), and ABGP concretization (d).}
-  \label{fig:abgp-syntax}
+  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
+  \label{fig:concretization}
 
@@
 \end{easylist}
+
+\begin{thm}
+  For any context $\Gamma$, concrete topology $G$, homomorphism $f : G \rightarrow G^A$, and policy $pol$,
+  $$\Con(\text{compile}(pol), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f))$$
+\end{thm}
 

### 2016-11-09 paper/abstraction/paper.tex
add structure for compilation correctness proof

@@
       \Router{S1, S2}
-        Match[100] \PREFIX=GP1, \PEER=*
+        Match[100] \PREFIX=GP1, \PEER=\{AG1, ..., AL1, ...\}
           \PEER \Arrow *
-        Match[100] \PREFIX=GP2, \PEER=*
+        Match[100] \PREFIX=GP2, \PEER=\{AG1, ..., AL1, ...\}
           \PEER \Arrow *
@@
       \Router{S}
-        Match[100] \PREFIX=\$GP, \PEER=*
+        Match[100] \PREFIX=\$GP, \PEER=\{AG, AL\}
           \PEER \Arrow *
@@
         & = & 
-        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
+        \bigcup_i~ \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
         \\
@@
 
-\begin{easylist}[itemize]
-& First show how to compile to the Product Graph, and from there to the ABGP
-& Next define the concretization & subst. functions for translating the abstract policy
-   into the concrete policy, using the ABGP example for reference
-& Give abstraction theorem: commuting of concretization and compilation
-\end{easylist}
+An important observation is that the topology abstraction $f$ is preserved throughout compilation.
+This is reflected in the structure of the template and concrete configurations from Figure~\ref{fig:bgp-configs}.
+At a first cut, the configurations appear the same except for the fact that (1) the abstract locations are replaced with the union of all concrete locations in the concrete configurations, and (2) the prefix templates are replaced with an entry for each unique prefix in the concrete policy.
+
+In this section, we formalize this observation.
+We introduce a simple language for BGP configurations called ABGP and define compilation over both concrete and abstract topologies to ABGP.
+In addition we define a concretization function for both \sysname policies as well as ABGP configurations that take an abstract policy/configuration and turn it into a concrete policy/configuration.
+The main theoretical result is that the compilation and concretization functions commute.
+This means we can perform compilation over the abstract representation to generate templates, and only concretize these templates when we need to instantiate the network.
+
+\para{ABGP language}
+
+We introduct a simple language for BGP configurations called ABGP. Figure~\ref{fig:concretization} shows the syntax for an ABGP policy.
+
+ An ABGP policy consists of a map from topology locations $l$ to router configurations $rc$.
+Each router configuration $rc$ is a sequence of prefix (templates) $t$ and their corresponding prefix configuration $pc$.
+A prefix configuration $pc$ is a sequence of match actions $ma$.
+Each match action $ma$ consists of a preference value $n_1$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $n_2$, as well as export neighbors $ns_2$ and the updated community value $n_3$.
+
+ \vspace{1em}
+
+We assume a particular router $l$ appears at most once in any abgp specification.
+We often build configs using set-builder notation.  For instance,
+$\{l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc)\}$ denotes the abgp policy
+
+\[ \begin{array}{c}
+  l_1 \rightarrow rc_{11},... \\
+  ...           \\
+  l_k \rightarrow rc_{1k},... \\
+\end{array} \]
+
+where $l_1, ..., l_k$ are the nodes in the topology
+and each $rc_{ij}$ satisfies $p(l_i,rc_{ij})$.
+
+\para{Compilation}
+
+Figure~\ref{fig:abgp-syntax} also defines compilation from a \sysname policy to an ABGP policy.
+It starts by compiling separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$, the particular test $t_i$, and the preference ordering $ord_i$.
+
+The function $compile_{ABGP}$ then takes tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy.
+It looks at each incoming neighbor with the same community state $q_n$ and matches any of those neighbor with the preference provided by the ordering $ord$ obtained from the search for local preferences.
+It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.
+
+\para{Concretization}
+
+We define what it means to concretize an abstract \sysname policy. 
+Concretization takes as input, a policy and a context $\Gamma$ mapping from a template prefix to a set of pairs of a concrete prefix and a concrete location where the prefix is owned.
+
+For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$.
+For each template variable, we replace it with a new entry for each of its corresponding concrete values under the supplied mapping $\Gamma$.
+We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that traffic is owned by the concrete location $l$.
+\textbf{Note}: we need the side condition that $\text{end}(l) \cap con(r_i,\Gamma) \neq \emptyset$ if $con(r_i,\Gamma) \neq \emptyset$.
+We can also define concretization over the ABGP policy as:
+
+We use the symbol $\bullet$ to denote that a particular value in a sequence is removed from the sequence.
 

### 2016-11-09 paper/abstraction/paper.tex
change order of compilation and analysis sections
edits to section 5

@@
 %
-%  **Compilation**
-%
-%
-%=====================================================
-
-\section{Compilation}
-\label{sec:compilation}
+%  **Language and Product Graph**
+%
+%
+%=====================================================
+
+\section{Language}
+\label{sec:language}
 
 Configuration synthesis for network configurations is challenging for a number of reasons.
-First, although \sysname polices specify stable network-wide routing behavior, actual configurations are per-device and run distributed algorithms to compute routes.
-Thus the compiler must ensure that the result of the distributed computation matches the policy.
-Furthermore the distributed computation must compute the correct paths under all possible combinations of failures.
-Second, \sysname must find configurations that work across any valid concrete network topology matching the abstraction provided as input.
+First, although \sysname polices specify network-wide routing behavior, actual configurations are per-device and run distributed algorithms to compute routes.
+Thus the compiler must ensure that the result of the distributed interaction of devices correctly implements the policy including when failures occur.
+Second, \sysname must find configurations that work for any valid concrete network topology matching the user-specified abstraction.
 Finally, \sysname must ensure that the resulting configurations can be evolved incrementally so that local changes to the topology ensure that only local changes to configurations are required to ensure global routing correctness.
 
-In this section, we formalize the \sysname language and topology abstraction, describe how \sysname synthesizes network configurations over these abstractions, and formalize the guarantees provided by \sysname.
+In this section, we formalize the \sysname language and describe how \sysname translates policies to a graph-based intermediate representation.
 
@@
 
-The syntax introduced in \S\ref{sec:overview} is just syntactic sugar for a core language based on regular expressions.
+The syntax introduced in \S\ref{sec:overview} is syntactic sugar for a core language based on regular expressions.
 Figure~\ref{fig:syntax} shows a simplified version of the core \sysname syntax that omits some details such as aggregation.
-The full langauge definition can be found in the appendix.
-
-A policy has one or more constraints, each of which consists of a test on the type of traffic being matched and a corresponding set of preferred regular expressions describing network paths.
-Regular expressions are defined over network locations, where each location is either a router inside the operators network, or an external neighbor.
-There are two special characters \In~ and \Out, which match any internal and external location respectively.
-There are two types of predicates: a test for a concrete prefix $d.d.d.d/[d..d]$ matches an IP prefix with value $d.d.d.d$ and length in the range $[d..d]$ where metavariable $d$ represents an integer.
-For example, the IP prefix 148.0.1.0/[24..32] would match traffic destined for IP address 148.0.1.* with a subnet length between 24 and 32 bits.
-\ryan{this needs to be explained clearer}.
-
-Converting from the high-level syntax from \S\ref{sec:overview} to the core syntax is straightforward.
-For example, the predicate $\True$ becomes $0.0.0.0/[0..32]$.
-Preferences are lifted to the top level of the regular expression when their use is unambiguous.
-For example, the constraint $\Exit\CD{(Peer1} ~\Prefer~ \CD{Peer2)}$ becomes $\Exit\CD{(Peer1)} \Prefer~ \Exit\CD{(Peer2)}$ before being rewritten into regular expressions.
-Each modular set of constraints are joined prefix-by-prefix by taking the intersection of their constraints.
-For example, the combining the Routing and Locality constraints in the data center policy from \S\ref{sec:overview} would result in the following \sysname policy:
-%
-\begin{code}
-\$PG  \Path \End(TG),
-\$PL  \Path \End(TL) \ensuremath{\cap} \Always(\In),
-\True \Path \Exit(Peer1) \Prefer \Exit(Peer2)
-\end{code}
-\noindent%
-%
-Finally, each constraint desugars to a regular expression. For example, the constraint $\Always\CD{(\In)}$ becomes $\In^*$ and the constraint $\CD{\End(T0)}$ becomes $\mathtt{\Sigma}^* \cdot \CD{T0}$.
+The full langauge definition, including aggregation, can be found in the appendix.
+
+A policy has one or more constraints, each of which consists of a test on the type of traffic being matched and a list of regular expressions describing preferred network paths.
+Regular expressions are defined over network locations, where each location is either a router inside the operator's network, or an external neighbor connected to the operator's network.
+Two special characters \In~ and \Out, will match any internal and external location respectively.
+There are two types of predicates: a test for a concrete prefix $d.d.d.d/[d..d]$ matches a range of IP prefixes (\EG, 1.2.3.4/[24..32]) where metavariable $d$ represents an integer.
+
+Converting from the high-level syntax from \S\ref{sec:overview} to the core syntax is straightforward. The predicate $\True$ becomes the prefix range $0.0.0.0/[0..32]$. 
+%
+Each constraint desugars to a regular expression. For example, the constraint $\Always\CD{(\In)}$ becomes $\In^*$ and the constraint $\CD{\End(T0)}$ becomes $\mathtt{\Sigma}^* \cdot \CD{T0}$.
+%
+Preferences are lifted to the top level of the regular expression when their use is unambiguous, and separate sets of constraints are joined prefix-by-prefix by taking the intersection of their constraints.
+
+%For example, the combining the Routing and Locality constraints in the data center policy from \S\ref{sec:overview} would result in the following \sysname policy:
+%
+%\begin{code}
+%\$PG  \Path \End(TG),
+%\$PL  \Path \End(TL) \ensuremath{\cap} \Always(\In),
+%\True \Path \Exit(Peer1) \Prefer \Exit(Peer2)
+%\end{code}
+%\noindent%
+%
 
@@
 
-The Product Graph is a compact representation of all paths distributed protocol messages might be passed through the network in order to result in policy-compliant paths.
-Although \sysname policies describe the routes that traffic should take through the network, network protocols (including BGP) typically disseminate router information in the opposite direction.
-For example, a router Y will tell its neighbor X that it has a route to the destination meaning that X can send traffic through Y. For this reason, we start by compiling
-
-Since each predicate in a \sysname policy has its own set of regular expression path constraints, \sysname constructs one Product Graph per prefix and generates configuration on a per-prefix basis.
-
-\para{Formal definition}
-
+The Product Graph is a compact representation of all paths distributed protocol messages might be passed through the network in order to find policy-compliant paths dynamically.
+%
+%Although \sysname policies describe the routes that traffic should take through the network, network protocols (including BGP) typically disseminate router information in the opposite direction.
+For example, a router Y will tell its neighbor X that it has a route to the destination meaning that X can send traffic through Y.
+For this reason, we start by compiling
+%
+Because \sysname policies can have a separate routing policy for each predicate matching traffic, we construct one such Product Graph for each predicate.
+
+\para{Product Graph construction}
+
+We construct a Product Graph in the following way.
 For each regular expression constraint $r_i$ from $r_1 ~\Prefer~ ..
 ~\Prefer~ r_k$, we construct a DFA for the reverse of $r_i$.
-An automaton for $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma = G^A$ is the set of topology locations for the abstraction, $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
-%
-The Product Graph is a tuple ($G'$, $s$, $P$) where $G' = (V',E')$ is a new graph with
+A DFA for $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
+The alphabet $\Sigma$ is the set of topology locations, $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+%
+The Product Graph is a tuple ($G'$, $start$, $P$) where $G' = (V',E')$ is a new graph with
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
 edges $E' \colon V' \times V'$,
-a unique starting vertex $s$,
-and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of path ranks.
+a unique starting vertex $start$,
+and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$, mapping nodes in the product graph to a set of path ranks.
 
@@
 %
-We add edges from the start node $s$ to any $m = (l, q_{m_1}, \dots, q_{m_k})$ when $\sigma_i(q_{0_i}, l) = q_{m_i}$ for each $i$.
+We add edges from the start node to any $m = (l, q_{m_1}, \dots, q_{m_k})$ when $\sigma_i(q_{0_i}, l) = q_{m_i}$ for each $i$.
 %
@@
 %
-Finally, we write $\tilde{m} = l$ to extract the topology location from a product graph node, when $m = (l, \dots) \in V'$.
-
-Figure~\ref{fig:example-compilation} shows an example of constructing a Product Graph for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview}:
+Finally, we write $\tilde{m} = l$ to extract the topology location from a product graph node, when $m = (l, q_{m_1}, \dots, q_{m_k}) \in V'$.
+
+Figure~\ref{fig:example-compilation} shows an example of a Product Graph for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview} ($\True ~\Path~ \CD{\Exit(Peer1)} ~\Prefer~ \CD{\Exit(Peer2)}$).
 %
@@
 The first automaton represents the more preferred constraint $\CD{\Exit(Peer1)}$ and the second automaton represents the less preferred constraint $\CD{\Exit(Peer2)}$.
-The Product Graph representation is shown for both an instance of a concrete network matching the abstraction from \S\ref{sec:overview} as well as for the abstraction itself.
+The Product Graph representation is shown for both an instance of a simple concrete network matching the abstraction from \S\ref{sec:overview} as well as for the abstract topology itself.
 
 Each node in the Product Graph tracks both where a protocol message is in the topology as well as how much progress has been made towards satisfying each policy constraint.
-In this example, all routes that eventually leave through Peer1 will lead to an accepting state for the first automaton and all routes that eventually leave through Peer2 will lead to an accepting state for the second automaton.
-
-From Figure~\ref{fig:example-compilation} we can see that both the concrete and abstract product graphs share a similar structure. This leads us to the following observation
+In this example, all routes that eventually leave through Peer1 (protocol message sent from $P_1$) will lead to an accepting state for the first automaton and all routes that eventually leave through Peer2 will lead to an accepting state for the second automaton.
+
+One interesting observation is that the Product Graph for both the concrete and abstract networks share a similar structure. This leads us to the following observation
 
 \begin{defn}
-If we have a graph homomorphism $f : G \rightarrow G^A$, concrete product graph $PG = (G',s,P)$ and abstract product graph $PG^A = (G'^A, s^A, P^A)$, then we can construct a new, lifted homomorphism $f_{pg} : G' \rightarrow G'^A$ in the following way:
+If we have a graph homomorphism $f : G \rightarrow G^A$, concrete product graph $PG = (G',start,P)$ and abstract product graph $PG^A = (G'^A, start^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$:
 \[ \begin{array}{rcl}
@@
 
-\subsection{Compilation to configurations}
+%=====================================================
+%
+%
+%  **Abstractions**
+%
+%
+%=====================================================
+
+\section{Abstract Analysis}
+\label{sec:analysis}
+
+In the previous section we saw that \sysname can synthesize correct device configurations by operating directly over the abstract representation.
+However, in practice operators would often like to reason about other properties about their network.
+In this section we present an analysis that operates over the network abstraction to find a lower bound on the number of disjoint paths between pairs of concrete nodes.
+Answering questions about the number of disjoint paths allows operators to reason about many useful network properties such as reachability (\IE, is there at least one path) and fault tolerance (\EG, how many failures will disconnect certain routers).
+An important point is that the analysis takes place over the structure of the product graph, and so takes both the topology and routing policy into account.
+
+\newcommand{\inference}[7]{
+    \node[draw, anchor=west] at (#1 + .5, 2.5 / 2) {#3};
+    \node[anchor=east] at (#1 - .4, 2.5 / 2) {\textbf{#5}};
+    \node at (#1 + .34, .6 + .2) {#6};
+    \node at (#1 + .34, 1.9 - .2) {#7};
+    \node at (#1, -.6) {#2};
+    \node at (#1, 2.5 + .4 + .2) {#4};
+    \draw [] (#1, 2.5 - .2) circle [radius=0.4] node {$n$};
+    \draw [] (#1, .2) circle [radius=0.4] node {$m$};
+    \draw [->] (#1, .4 + .2) -- (#1, 2.5 - .4 - .2);
+}
+
+\newcommand{\inferencenobox}[7]{
+    \node[anchor=west] at (#1 + .1, 1.25) {#3};
+    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{#5}};
+    \node at (#1 + .34, .6) {#6};
+    \node at (#1 + .34, 1.9) {#7};
+    \node at (#1, -.6) {#2};
+    \node at (#1, 2.5 + .4 + .2) {#4};
+    \draw [] (#1, 2.5 - .2) circle [radius=0.4] node {$n$};
+    \draw [] (#1, .2) circle [radius=0.4] node {$m$};
+    \draw [->] (#1, .2 + .4) -- (#1, 2.5 - .4 - .2);
+}
+
+\newcommand{\inferencetwo}[1]{
+    \node[draw, anchor=west] at (#1 + 2, 1.25) {$e_i > 0$};
+    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{I-striping}};
+    \node at (#1 - 1 - .11, .6) {$e_1$};
+    \node at (#1 + .11, 1.5) {$e_2$};
+    \node at (#1 + 2 + .11, .6) {$e_3$};
+    \node at (#1 + .11 + .8, 1.5) {$e_4$};
+    \node at (#1 - 1, -.8) {L$(j,k)$};
+    \node at (#1 +. 5, 2.9) {S$(min(j*k,g),1)$};
+    \node at (#1 + 2, -.8) {S$\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
+    \node at (#1, 3.3) {};
+    \draw [] (#1 + .5, 2.01) circle [radius=0.4] node {$n$};
+    \draw [] (#1 - 1, 0) circle [radius=0.4] node {$m$};
+    \draw [] (#1 + 2, 0) circle [radius=0.4] node {$o$};
+    \draw [->] (#1 - 1, .4) -- (#1 + .5, 2 - .4);
+    \draw [<-] (#1 + 2, .4) -- (#1 + .5, 2 - .4);
+}
+
+\newcommand{\inferencelocal}[1]{
+    \inferencenobox{#1}{L$_m(j,k)$}{}{L$_n(j',k')$}{I-local}{}{}
+    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_m(j,k)$}{}{$\ldots$ L$_P$ L$_n(j',k')$}{}{}{}
+    \node[anchor=east] at (#1 + 3 - .6, 2.5) {P};
+    \draw[dashed] (#1+2 - .2, -.34) rectangle (#1+3+1 + .1, 2.85);
+}
+
+\newcommand{\inferenceglobal}[1]{
+    \inferencenobox{#1}{L$_1(j,k)$}{}{L$_2(j',k')$}{I-global}{}{}
+    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_m(j,k)$}{}{$\ldots$ A$_Q$ L$_n(j',k')$}{}{}{}
+    \node[anchor=east] at (#1 + 3 - .6, .4) {P};
+    \node[anchor=east] at (#1 + 3 - .6, 2.5) {Q};
+    \draw[dashed] (#1+2 - .2, -.34) rectangle (#1+3+1 + .1, .8);
+    \draw[dashed] (#1+2 - .2, 1.7) rectangle (#1+3+1 + .1, 2.85);
+}
+
+\begin{figure*}[t!]
+  \begin{minipage}[t]{\linewidth}%
+  \begin{tikzpicture}
+    \inference{0}{L$(j,k)$}{$e_1 > 0$}{S$(min(j*k,e_1),1)$}{I-out1}{$e_1$}{$e_2$}
+    \inference{4.5}{A$(j,k)$}{$e_2 > 0$}{A$(1,min(j,e2))$}{I-out2}{$e_1$}{$e_2$}
+    \inference{9}{L$(j,k)$}{$e_1=n$}{A$(min(j*k,n),1)$}{I-mesh1}{$e_1$}{$e_2$}
+    \inference{13.5}{L$(j,k)$}{$e_1=n$}{A$(1,j)$}{I-mesh2}{$e_1$}{$e_2$}
+  \end{tikzpicture}
+  \end{minipage}
+
+  \vspace*{1em}
+  \begin{minipage}[t]{\linewidth}%
+  \begin{tikzpicture}
+    % \inference{0}{L$(j,k)$}{$e_i > 0$}{S$(min(j*k,g),1)$}{I-out3}{$e_1$}{$e_2$}
+    \inferencetwo{0}
+    \node[anchor=west] at (2,2) {where $g=n-\dfrac{(m-j)*e_1}{e_2}$};
+    \inferencenobox{11}{L$(j,k)$}{$bisec(X)$}{A$(1,min(k,X))$}{I-bisec}{}{}
+  \end{tikzpicture}
+  \end{minipage}
+
+  \vspace*{1em}
+  \begin{minipage}[t]{\linewidth}%
+  \begin{tikzpicture}
+    \inferencelocal{0}
+    \inferenceglobal{10}
+  \end{tikzpicture}
+  \end{minipage}
+
+  \hrule
+  \vspace*{1em}
+  \caption{Abstract k-disjoint path analysis inference rules. \ryan{added bisec idea a possibility, we can remove this}}
+  \label{fig:inference-rules}
+  %\vspace{-1em}
+\end{figure*}
+
+\subsection{Abstract k-disjoint paths}
+\label{sec:property-checking}
+
+In order to infer bounds on the number of disjoint paths between nodes we use information about the structure of the underlying concrete topologies encoded in the abstraction pod structure and node + edge multiplicity constraints.
+
+The idea is to maintain, for each role in the abstract product graph, facts learned about the number of disjoint paths to some number of concrete routers in that role from a given source location.
+More specifically, we maintain facts of the form:
+%
+\[ \begin{array}{c}
+  L_{X_1}, \ldots, L_{X_n}(j,k)
+\end{array} \]
+\noindent
+%
+Each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all".
+There is one label in the nesting for each pod scope in the network abstraction hierarchy.
+So for a given node, $L_{X_1}$ would correspond to the outermost pod scope, while $L_{X_n}$ would correspond the the node's label.
+
+Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete router in the abstract source, for ``some"/``all" scopes $X_1$, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds.
+The base case $L_{X_n}(j,k)$ means that for ``some"/``all" groups of size $j$ concrete routers, there are $k$ disjoint paths to each such that all $j*k$ paths are disjoint
+
+For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of size 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.
+
+\subsection{Inference rules}
+
+\newcommand{\infrule}[1]{{\small \sf #1}\xspace}
+
+In order to learn information about disjoint paths between routers, we develop a series of sound inference rules for facts of this form.
+Figure~\ref{fig:inference-rules} shows each of the inference rules.
+The rules are read from bottom to top.
+The label on the bottom left corresponds to a known fact of the form $L(j,k)$.
+We use $L$ to represent a rule that is parametric over the particular label.
+The labels on other nodes correspond to learned facts from applying the inference rule.
+Conditions that must be \emph{valid} for the node and edge multiplicities are shown in a box.
+
+In general, the inference rules try to learn information about (1) the largest number of disjoint paths to any single node in an abstract role and (2) the largest reachable group in a particular role with at least one disjoint path to each as this tends to be a valuable invariant.
+
+The first rule, \infrule{I-out1} applies to a learned fact of the form L$(j,k)$ where the number of out edges at the current node is greater than 0.
+In the worst case, the largest group of nodes we could hope to reach at the top node would be $e_1$ since all j nodes at the bottom may have the same outgoing edges to the nodes at the top.
+Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$.
+Since adding edges from between the nodes keeps the existing paths disjoint, and since we can not exceed the current number of disjoint paths to the node on the bottom, the largest reachable group for the top node will be $min(j*k,e_1)$.
+However, since we do not know for certain that all $j$ nodes have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
+
+The rule \infrule{I-out2} follows a similar line of reasoning.
+It says that if any group of size $j$ with $k$ disjoint paths to each is reachable in the bottom node, and there is at least one incoming edge for each top node, then there are $min(j,e_2)$ disjoint paths to any single node in the top role.
+This is because we can choose the $j$ nodes on the bottom for which we want to find disjoint paths, and then use each of the $e_2$ incoming edges for the particular node at the top connecting it to the bottom, which preserve the disjointedness.
+
+The two rules \infrule{I-mesh1} and \infrule{I-mesh2} handle the case where there is a full mesh between the two roles.
+This happens when the number of outgoing edges from the bottom $e_1$ is equal to the number of nodes on the top $n$.
+The first case for \infrule{I-mesh1} says that we can find disjoint paths to each node in the top role restricted to the number of disjoint paths we started with.
+The second case for \infrule{I-mesh2} uses the fact that each node in the top role is connected to each node in the bottom role to infer that there can be $j$ disjoint paths to any single node in the top role.
+
+The rule \infrule{I-striping} is the most complicated case.
+It starts with the fact L$(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid.
+The first inference for role $n$ tries to find the largest reachable group with disjoint paths to each.
+The idea is similar to the rule \infrule{I-out1}, but is able to use the fact that $e_2 > 0$ to learn more about the structure of the concrete topology.
+In particular it uses the following inequality, where $g$ represents the size of the group for the top role:
+%
+\[ \begin{array}{c}
+  (m-j)*e_1 \geq (n-g)*e_2
+\end{array} \]
+\noindent
+%
+This captures the fact that the remaining nodes ($m-j$) for which we are not considering, each have $e_1$ outgoing edges and must be able to fill the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each.
+Solving the inequality yields:
+%
+\[ \begin{array}{c}
+  g \geq n - \dfrac{(m-j)*e_1}{e_2}
+\end{array} \]
+\noindent
+%
+The second part of the rule allows uses a similar idea to reason about the "striping", or overlap between roles $m$ and $o$ with respect to role $n$.
+Often times this rule is applied when $m$ and $o$ are in fact the same role.
+
+The rule \infrule{I-bisec} can be thought of as a programmer assertion about the bisection between two roles.
+The rule applies to an edge that has been annotated with a $bisec(X)$ statement, which means that there are $X$ disjoint paths between any node in role $m$ and any node in role $n$.
+Annotations of this form are useful for a "one big switch" \ryan{cite} type of abstraction where part of a complex network is abstracted into a single node.
+
+Finally, the \infrule{I-local} and \infrule{I-global} rules allow us to lift each of the other rules to reason across pod hierarchies.
+The first rule, \infrule{I-local}, says that if you have an inference from L$_m(j,k)$ to L$_n(j',k')$ on the left, then if both nodes are in the same local pod P, you can leave all labels up to P unchanged.
+The global rule \infrule{I-global} says the same thing except when the edge goes between pods, you can infer the fact for all pods Q since the multiplicities apply equally to each pod.
+
+\subsection{An inference algorithm}
+
+The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies the inference rules from Figure~\ref{fig:inference-rules} until a fixed point is reached.
+Inference rule conditions are checked for validity over all concrete topologies using the Z3 \ryan{cite} SMT solver.
+In order to ensure termination, we make the observation that, for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
+Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the Z3 optimizing constraint solver.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=\columnwidth]{figures/analysis}
+  \end{center}
+  \caption{Abstract disjoint path analysis with valleyfree routing for global prefixes. \label{fig:compilation-times}}
+  \label{fig:example-inference}
+  \vspace{-1em}
+\end{figure}
+
+Consider again the datacenter example from \S\ref{sec:overview}.
+Suppose now we add the valleyfree constraint that traffic never has takes a path with a down-up in it for the routing policy for global prefixes:
+%
+\begin{code}
+\$GP  \Path \End(TG) \ensuremath{\cap} \Novalley(\{TG,TL\},\{AG,AL\},\{S\})
+\end{code}
+\noindent
+%
+Figure~\ref{fig:example-inference} shows the abstract product graph representation for this routing policy.
+The inference algorithm starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$ (\IE, no restriction on the number of disjoint paths initially).
+%
+The first step applies the rule \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles.
+This invokes a call to Z3Opt to minimize the expression $min(\infty, AG)$, which gives us 2.
+Therefore, the algorithm learns a new invariant of the form $S_P A_{AG} (2,1)$ for node $(AG, 0)$ to indicate that in some pod P, any group of 2 nodes is reachable.
+%
+The next step uses the inference rule \infrule{I-out2} to learn that any single spine node is reachable.
+It also can apply rule \infrule{I-striping} to determine that there is some group of at least 2 spine routers reachable at node $(S,0)$ and also that there is some group of at least 2 nodes reachable in the AL role in state $(AL,0)$.
+
+Note that, because each inference rule only applies to directed edges in the product graph, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
+It is this restriction that ensures that the analysis is both topology and policy dependent.
+
+The next step is to use \infrule{I-mesh2} together with \infrule{I-local} to infer than any single node in the TL role for any pod P is reachable via at least 2 disjoint paths.
+This process will continue until a fixed point is reached.
+
+In this case, the algorithm was able to infer that, with the valleyfree routing policy, any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a prefix originator in role TG.
+Note that, in this case, the analysis is precise.
+There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router.
+In this case, the analysis can be used to determine the number of failures that can induce an aggregation black-hole at the border of the datacenter.
+
+%=====================================================
+%
+%
+%  **Compilation to BGP**
+%
+%
+%=====================================================
+
+\section{Compilation}
 
@@
 If we make a change to the concrete network that matches the abstraction, then the templates do not change, and thus only configurations adjacent to the changes must also change.
-
-%=====================================================
-%
-%
-%  **Abstractions**
-%
-%
-%=====================================================
-
-\section{Abstract Analysis}
-\label{sec:analysis}
-
-In the previous section we saw that \sysname can synthesize correct device configurations by operating directly over the abstract representation.
-However, in practice operators would often like to reason about other properties about their network.
-In this section we present an analysis that operates over the network abstraction to find a lower bound on the number of disjoint paths between pairs of concrete nodes.
-Answering questions about the number of disjoint paths allows operators to reason about many useful network properties such as reachability (\IE, is there at least one path) and fault tolerance (\EG, how many failures will disconnect certain routers).
-An important point is that the analysis takes place over the structure of the product graph, and so takes both the topology and routing policy into account.
-
-\newcommand{\inference}[7]{
-    \node[draw, anchor=west] at (#1 + .5, 2.5 / 2) {#3};
-    \node[anchor=east] at (#1 - .4, 2.5 / 2) {\textbf{#5}};
-    \node at (#1 + .34, .6 + .2) {#6};
-    \node at (#1 + .34, 1.9 - .2) {#7};
-    \node at (#1, -.6) {#2};
-    \node at (#1, 2.5 + .4 + .2) {#4};
-    \draw [] (#1, 2.5 - .2) circle [radius=0.4] node {$n$};
-    \draw [] (#1, .2) circle [radius=0.4] node {$m$};
-    \draw [->] (#1, .4 + .2) -- (#1, 2.5 - .4 - .2);
-}
-
-\newcommand{\inferencenobox}[7]{
-    \node[anchor=west] at (#1 + .1, 1.25) {#3};
-    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{#5}};
-    \node at (#1 + .34, .6) {#6};
-    \node at (#1 + .34, 1.9) {#7};
-    \node at (#1, -.6) {#2};
-    \node at (#1, 2.5 + .4 + .2) {#4};
-    \draw [] (#1, 2.5 - .2) circle [radius=0.4] node {$n$};
-    \draw [] (#1, .2) circle [radius=0.4] node {$m$};
-    \draw [->] (#1, .2 + .4) -- (#1, 2.5 - .4 - .2);
-}
-
-\newcommand{\inferencetwo}[1]{
-    \node[draw, anchor=west] at (#1 + 2, 1.25) {$e_i > 0$};
-    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{I-striping}};
-    \node at (#1 - 1 - .11, .6) {$e_1$};
-    \node at (#1 + .11, 1.5) {$e_2$};
-    \node at (#1 + 2 + .11, .6) {$e_3$};
-    \node at (#1 + .11 + .8, 1.5) {$e_4$};
-    \node at (#1 - 1, -.8) {L$(j,k)$};
-    \node at (#1 +. 5, 2.9) {S$(min(j*k,g),1)$};
-    \node at (#1 + 2, -.8) {S$\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
-    \node at (#1, 3.3) {};
-    \draw [] (#1 + .5, 2.01) circle [radius=0.4] node {$n$};
-    \draw [] (#1 - 1, 0) circle [radius=0.4] node {$m$};
-    \draw [] (#1 + 2, 0) circle [radius=0.4] node {$o$};
-    \draw [->] (#1 - 1, .4) -- (#1 + .5, 2 - .4);
-    \draw [<-] (#1 + 2, .4) -- (#1 + .5, 2 - .4);
-}
-
-\newcommand{\inferencelocal}[1]{
-    \inferencenobox{#1}{L$_m(j,k)$}{}{L$_n(j',k')$}{I-local}{}{}
-    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_m(j,k)$}{}{$\ldots$ L$_P$ L$_n(j',k')$}{}{}{}
-    \node[anchor=east] at (#1 + 3 - .6, 2.5) {P};
-    \draw[dashed] (#1+2 - .2, -.34) rectangle (#1+3+1 + .1, 2.85);
-}
-
-\newcommand{\inferenceglobal}[1]{
-    \inferencenobox{#1}{L$_1(j,k)$}{}{L$_2(j',k')$}{I-global}{}{}
-    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_m(j,k)$}{}{$\ldots$ A$_Q$ L$_n(j',k')$}{}{}{}
-    \node[anchor=east] at (#1 + 3 - .6, .4) {P};
-    \node[anchor=east] at (#1 + 3 - .6, 2.5) {Q};
-    \draw[dashed] (#1+2 - .2, -.34) rectangle (#1+3+1 + .1, .8);
-    \draw[dashed] (#1+2 - .2, 1.7) rectangle (#1+3+1 + .1, 2.85);
-}
-
-\begin{figure*}[t!]
-  \begin{minipage}[t]{\linewidth}%
-  \begin{tikzpicture}
-    \inference{0}{L$(j,k)$}{$e_1 > 0$}{S$(min(j*k,e_1),1)$}{I-out1}{$e_1$}{$e_2$}
-    \inference{4.5}{A$(j,k)$}{$e_2 > 0$}{A$(1,min(j,e2))$}{I-out2}{$e_1$}{$e_2$}
-    \inference{9}{L$(j,k)$}{$e_1=n$}{A$(min(j*k,n),1)$}{I-mesh1}{$e_1$}{$e_2$}
-    \inference{13.5}{L$(j,k)$}{$e_1=n$}{A$(1,j)$}{I-mesh2}{$e_1$}{$e_2$}
-  \end{tikzpicture}
-  \end{minipage}
-
-  \vspace*{1em}
-  \begin{minipage}[t]{\linewidth}%
-  \begin{tikzpicture}
-    % \inference{0}{L$(j,k)$}{$e_i > 0$}{S$(min(j*k,g),1)$}{I-out3}{$e_1$}{$e_2$}
-    \inferencetwo{0}
-    \node[anchor=west] at (2,2) {where $g=n-\dfrac{(m-j)*e_1}{e_2}$};
-    \inferencenobox{11}{L$(j,k)$}{$bisec(X)$}{A$(1,min(k,X))$}{I-bisec}{}{}
-  \end{tikzpicture}
-  \end{minipage}
-
-  \vspace*{1em}
-  \begin{minipage}[t]{\linewidth}%
-  \begin{tikzpicture}
-    \inferencelocal{0}
-    \inferenceglobal{10}
-  \end{tikzpicture}
-  \end{minipage}
-
-  \hrule
-  \vspace*{1em}
-  \caption{Abstract k-disjoint path analysis inference rules. \ryan{added bisec idea a possibility, we can remove this}}
-  \label{fig:inference-rules}
-  %\vspace{-1em}
-\end{figure*}
-
-\subsection{Abstract k-disjoint paths}
-\label{sec:property-checking}
-
-In order to infer bounds on the number of disjoint paths between nodes we use information about the structure of the underlying concrete topologies encoded in the abstraction pod structure and node + edge multiplicity constraints.
-
-The idea is to maintain, for each role in the abstract product graph, facts learned about the number of disjoint paths to some number of concrete routers in that role from a given source location.
-More specifically, we maintain facts of the form:
-%
-\[ \begin{array}{c}
-  L_{X_1}, \ldots, L_{X_n}(j,k)
-\end{array} \]
-\noindent
-%
-Each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all".
-There is one label in the nesting for each pod scope in the network abstraction hierarchy.
-So for a given node, $L_{X_1}$ would correspond to the outermost pod scope, while $L_{X_n}$ would correspond the the node's label.
-
-Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete router in the abstract source, for ``some"/``all" scopes $X_1$, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds.
-The base case $L_{X_n}(j,k)$ means that for ``some"/``all" groups of size $j$ concrete routers, there are $k$ disjoint paths to each such that all $j*k$ paths are disjoint
-
-For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of size 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.
-
-\subsection{Inference rules}
-
-\newcommand{\infrule}[1]{{\small \sf #1}\xspace}
-
-In order to learn information about disjoint paths between routers, we develop a series of sound inference rules for facts of this form.
-Figure~\ref{fig:inference-rules} shows each of the inference rules.
-The rules are read from bottom to top.
-The label on the bottom left corresponds to a known fact of the form $L(j,k)$.
-We use $L$ to represent a rule that is parametric over the particular label.
-The labels on other nodes correspond to learned facts from applying the inference rule.
-Conditions that must be \emph{valid} for the node and edge multiplicities are shown in a box.
-
-In general, the inference rules try to learn information about (1) the largest number of disjoint paths to any single node in an abstract role and (2) the largest reachable group in a particular role with at least one disjoint path to each as this tends to be a valuable invariant.
-
-The first rule, \infrule{I-out1} applies to a learned fact of the form L$(j,k)$ where the number of out edges at the current node is greater than 0.
-In the worst case, the largest group of nodes we could hope to reach at the top node would be $e_1$ since all j nodes at the bottom may have the same outgoing edges to the nodes at the top.
-Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$.
-Since adding edges from between the nodes keeps the existing paths disjoint, and since we can not exceed the current number of disjoint paths to the node on the bottom, the largest reachable group for the top node will be $min(j*k,e_1)$.
-However, since we do not know for certain that all $j$ nodes have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
-
-The rule \infrule{I-out2} follows a similar line of reasoning.
-It says that if any group of size $j$ with $k$ disjoint paths to each is reachable in the bottom node, and there is at least one incoming edge for each top node, then there are $min(j,e_2)$ disjoint paths to any single node in the top role.
-This is because we can choose the $j$ nodes on the bottom for which we want to find disjoint paths, and then use each of the $e_2$ incoming edges for the particular node at the top connecting it to the bottom, which preserve the disjointedness.
-
-The two rules \infrule{I-mesh1} and \infrule{I-mesh2} handle the case where there is a full mesh between the two roles.
-This happens when the number of outgoing edges from the bottom $e_1$ is equal to the number of nodes on the top $n$.
-The first case for \infrule{I-mesh1} says that we can find disjoint paths to each node in the top role restricted to the number of disjoint paths we started with.
-The second case for \infrule{I-mesh2} uses the fact that each node in the top role is connected to each node in the bottom role to infer that there can be $j$ disjoint paths to any single node in the top role.
-
-The rule \infrule{I-striping} is the most complicated case.
-It starts with the fact L$(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid.
-The first inference for role $n$ tries to find the largest reachable group with disjoint paths to each.
-The idea is similar to the rule \infrule{I-out1}, but is able to use the fact that $e_2 > 0$ to learn more about the structure of the concrete topology.
-In particular it uses the following inequality, where $g$ represents the size of the group for the top role:
-%
-\[ \begin{array}{c}
-  (m-j)*e_1 \geq (n-g)*e_2
-\end{array} \]
-\noindent
-%
-This captures the fact that the remaining nodes ($m-j$) for which we are not considering, each have $e_1$ outgoing edges and must be able to fill the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each.
-Solving the inequality yields:
-%
-\[ \begin{array}{c}
-  g \geq n - \dfrac{(m-j)*e_1}{e_2}
-\end{array} \]
-\noindent
-%
-The second part of the rule allows uses a similar idea to reason about the "striping", or overlap between roles $m$ and $o$ with respect to role $n$.
-Often times this rule is applied when $m$ and $o$ are in fact the same role.
-
-The rule \infrule{I-bisec} can be thought of as a programmer assertion about the bisection between two roles.
-The rule applies to an edge that has been annotated with a $bisec(X)$ statement, which means that there are $X$ disjoint paths between any node in role $m$ and any node in role $n$.
-Annotations of this form are useful for a "one big switch" \ryan{cite} type of abstraction where part of a complex network is abstracted into a single node.
-
-Finally, the \infrule{I-local} and \infrule{I-global} rules allow us to lift each of the other rules to reason across pod hierarchies.
-The first rule, \infrule{I-local}, says that if you have an inference from L$_m(j,k)$ to L$_n(j',k')$ on the left, then if both nodes are in the same local pod P, you can leave all labels up to P unchanged.
-The global rule \infrule{I-global} says the same thing except when the edge goes between pods, you can infer the fact for all pods Q since the multiplicities apply equally to each pod.
-
-\subsection{An inference algorithm}
-
-The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies the inference rules from Figure~\ref{fig:inference-rules} until a fixed point is reached.
-Inference rule conditions are checked for validity over all concrete topologies using the Z3 \ryan{cite} SMT solver.
-In order to ensure termination, we make the observation that, for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
-Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the Z3 optimizing constraint solver.
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=\columnwidth]{figures/analysis}
-  \end{center}
-  \caption{Abstract disjoint path analysis with valleyfree routing for global prefixes. \label{fig:compilation-times}}
-  \label{fig:example-inference}
-  \vspace{-1em}
-\end{figure}
-
-Consider again the datacenter example from \S\ref{sec:overview}.
-Suppose now we add the valleyfree constraint that traffic never has takes a path with a down-up in it for the routing policy for global prefixes:
-%
-\begin{code}
-\$GP  \Path \End(TG) \ensuremath{\cap} \Novalley(\{TG,TL\},\{AG,AL\},\{S\})
-\end{code}
-\noindent
-%
-Figure~\ref{fig:example-inference} shows the abstract product graph representation for this routing policy.
-The inference algorithm starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$ (\IE, no restriction on the number of disjoint paths initially).
-%
-The first step applies the rule \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles.
-This invokes a call to Z3Opt to minimize the expression $min(\infty, AG)$, which gives us 2.
-Therefore, the algorithm learns a new invariant of the form $S_P A_{AG} (2,1)$ for node $(AG, 0)$ to indicate that in some pod P, any group of 2 nodes is reachable.
-%
-The next step uses the inference rule \infrule{I-out2} to learn that any single spine node is reachable.
-It also can apply rule \infrule{I-striping} to determine that there is some group of at least 2 spine routers reachable at node $(S,0)$ and also that there is some group of at least 2 nodes reachable in the AL role in state $(AL,0)$.
-
-Note that, because each inference rule only applies to directed edges in the product graph, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
-It is this restriction that ensures that the analysis is both topology and policy dependent.
-
-The next step is to use \infrule{I-mesh2} together with \infrule{I-local} to infer than any single node in the TL role for any pod P is reachable via at least 2 disjoint paths.
-This process will continue until a fixed point is reached.
-
-In this case, the algorithm was able to infer that, with the valleyfree routing policy, any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a prefix originator in role TG.
-Note that, in this case, the analysis is precise.
-There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router.
-In this case, the analysis can be used to determine the number of failures that can induce an aggregation black-hole at the border of the datacenter.
 

### 2016-11-09 paper/abstraction/paper.tex
edit section 6

@@
 
-  \caption{Product graph construction for policy $true \Path \Exit(\text{Peer1} \Prefer \text{Peer2})$.}
+  \caption{Product graph construction for policy $\True ~\Path~ \CD{\Exit(\text{Peer1}} ~\Prefer~ \CD{\text{Peer2})}$.}
   \label{fig:example-compilation}
@@
 
-In the previous section we saw that \sysname can synthesize correct device configurations by operating directly over the abstract representation.
-However, in practice operators would often like to reason about other properties about their network.
+In practice, operators would often like to reason about a variety of properties for, not only their current network topology, but also future versions of it.
 In this section we present an analysis that operates over the network abstraction to find a lower bound on the number of disjoint paths between pairs of concrete nodes.
-Answering questions about the number of disjoint paths allows operators to reason about many useful network properties such as reachability (\IE, is there at least one path) and fault tolerance (\EG, how many failures will disconnect certain routers).
-An important point is that the analysis takes place over the structure of the product graph, and so takes both the topology and routing policy into account.
+Answering questions about the number of disjoint paths between nodes allows operators to reason about many useful network properties such as reachability (\IE, is there at least one path) and fault tolerance (\EG, how many failures will disconnect certain routers).
+Because the analysis takes place over the product graph rather than the topology, it is able to take into account the constraints imposed by the routing policy.
 
@@
     \node[anchor=west] at (2,2) {where $g=n-\dfrac{(m-j)*e_1}{e_2}$};
-    \inferencenobox{11}{L$(j,k)$}{$bisec(X)$}{A$(1,min(k,X))$}{I-bisec}{}{}
+    \inferencenobox{11}{L$(j,k)$}{$mincut(X)$}{A$(1,min(k,X))$}{I-mincut}{}{}
   \end{tikzpicture}
@@
   \vspace*{1em}
-  \caption{Abstract k-disjoint path analysis inference rules. \ryan{added bisec idea a possibility, we can remove this}}
+  \caption{Abstract k-disjoint path analysis inference rules.}
   \label{fig:inference-rules}
@@
 
-In order to infer bounds on the number of disjoint paths between nodes we use information about the structure of the underlying concrete topologies encoded in the abstraction pod structure and node + edge multiplicity constraints.
-
-The idea is to maintain, for each role in the abstract product graph, facts learned about the number of disjoint paths to some number of concrete routers in that role from a given source location.
+In order to infer bounds on the number of disjoint paths between concrete nodes we use information about the structure of the underlying concrete topologies encoded in the abstraction constraints.
+%
+The idea is to maintain, for each node in the abstract product graph, quantified facts learned about the number of disjoint paths from a source node to some number of concrete routers in that role.
 More specifically, we maintain facts of the form:
@@
 Each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all".
-There is one label in the nesting for each pod scope in the network abstraction hierarchy.
-So for a given node, $L_{X_1}$ would correspond to the outermost pod scope, while $L_{X_n}$ would correspond the the node's label.
-
-Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete router in the abstract source, for ``some"/``all" scopes $X_1$, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds.
+There is one label in for each pod label in the abstraction pod hierarchy.
+For a given node, $L_{X_1}$ would correspond to the outermost pod, $L_{X_{n-1}}$ would correspond to the innermost pod, and $L_{X_n}$ to the the node itself.
+
+Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete router in the abstract source role, for ``some"/``all" pods $X_1$, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds.
 The base case $L_{X_n}(j,k)$ means that for ``some"/``all" groups of size $j$ concrete routers, there are $k$ disjoint paths to each such that all $j*k$ paths are disjoint
-
-For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of size 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.
+%
+For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.
 
@@
 The rules are read from bottom to top.
-The label on the bottom left corresponds to a known fact of the form $L(j,k)$.
-We use $L$ to represent a rule that is parametric over the particular label.
+The label on the bottom left corresponds to a known fact of the form described above.
+We use $L$ to represent a rule that is parametric over the particular label ($S$ or $A$).
 The labels on other nodes correspond to learned facts from applying the inference rule.
-Conditions that must be \emph{valid} for the node and edge multiplicities are shown in a box.
-
-In general, the inference rules try to learn information about (1) the largest number of disjoint paths to any single node in an abstract role and (2) the largest reachable group in a particular role with at least one disjoint path to each as this tends to be a valuable invariant.
-
-The first rule, \infrule{I-out1} applies to a learned fact of the form L$(j,k)$ where the number of out edges at the current node is greater than 0.
-In the worst case, the largest group of nodes we could hope to reach at the top node would be $e_1$ since all j nodes at the bottom may have the same outgoing edges to the nodes at the top.
+Conditions that must be \emph{valid} for the rule to apply are shown in a box next to the rule.
+
+In general, the inference rules try to learn information about both the largest number of disjoint paths to any single node in an abstract role and the largest reachable group in a particular role with at least one disjoint path to each.
+
+The first rule, \infrule{I-out1} applies to a learned fact of the form L$(j,k)$ where the number of outgoing edges from any concrete node in the $m$ role is greater than 0.
+In the worst case, the largest group of concrete nodes we could hope to reach at the $n$ role would be $e_1$ since all j nodes at the bottom may have the same outgoing edges to the concrete nodes at the top.
 Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$.
-Since adding edges from between the nodes keeps the existing paths disjoint, and since we can not exceed the current number of disjoint paths to the node on the bottom, the largest reachable group for the top node will be $min(j*k,e_1)$.
+Since adding edges between the nodes keeps the existing paths disjoint, and since we can not exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the top node will be $min(j*k,e_1)$.
 However, since we do not know for certain that all $j$ nodes have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
@@
 The rule \infrule{I-out2} follows a similar line of reasoning.
-It says that if any group of size $j$ with $k$ disjoint paths to each is reachable in the bottom node, and there is at least one incoming edge for each top node, then there are $min(j,e_2)$ disjoint paths to any single node in the top role.
-This is because we can choose the $j$ nodes on the bottom for which we want to find disjoint paths, and then use each of the $e_2$ incoming edges for the particular node at the top connecting it to the bottom, which preserve the disjointedness.
+It says that if any group of size $j$ with $k$ disjoint paths to each is reachable in the bottom role, and there is at least one incoming edge for each concrete node in the top role, then there are $min(j,e_2)$ disjoint paths to any single concrete node in the top role.
+This is because we can choose the $j$ nodes on the bottom for which we want to find disjoint paths, and then use each of the $e_2$ disjoint incoming edges for the particular node at the top connecting it to the bottom.
 
@@
 The rule \infrule{I-striping} is the most complicated case.
-It starts with the fact L$(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid.
+It starts with the fact L$(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid given the constraints.
 The first inference for role $n$ tries to find the largest reachable group with disjoint paths to each.
 The idea is similar to the rule \infrule{I-out1}, but is able to use the fact that $e_2 > 0$ to learn more about the structure of the concrete topology.
-In particular it uses the following inequality, where $g$ represents the size of the group for the top role:
+In particular it uses the following inequality, where $g$ represents the size of the group for the role $n$:
 %
@@
 %
-This captures the fact that the remaining nodes ($m-j$) for which we are not considering, each have $e_1$ outgoing edges and must be able to fill the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each.
+This captures the fact that the remaining nodes ($m-j$) that are not part of the group in the bottom role, each have $e_1$ outgoing edges and must be able to at least "fill" the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each.
 Solving the inequality yields:
@@
 %
-The second part of the rule allows uses a similar idea to reason about the "striping", or overlap between roles $m$ and $o$ with respect to role $n$.
-Often times this rule is applied when $m$ and $o$ are in fact the same role.
-
-The rule \infrule{I-bisec} can be thought of as a programmer assertion about the bisection between two roles.
-The rule applies to an edge that has been annotated with a $bisec(X)$ statement, which means that there are $X$ disjoint paths between any node in role $m$ and any node in role $n$.
+The second part of the rule allows uses a similar idea to reason about the overlap between roles $m$ and $o$ with respect to role $n$.
+This rule is useful particularly useful for datacenter topologies where routers in one tier of the datacenter often have a particular striping pattern with another tier.
+
+The rule \infrule{I-mincut} can be thought of as an assertion about the fault tolerance between two roles.
+The rule applies to an edge that has been annotated with a $mincut(X)$ statement, which means that there are at least $X$ disjoint paths between any node in role $m$ and any node in role $n$.
 Annotations of this form are useful for a "one big switch" \ryan{cite} type of abstraction where part of a complex network is abstracted into a single node.
+For example, to model an ISP backbone network the operator might abstract the network into separate geograph regions with two abstract roles per region.
+One role for the border routers of the network, and another role for the core of the network.
+Mincut annotations could be used to describe the fault tolerance both within region cores as well as across regions.
 
@@
 
-The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies the inference rules from Figure~\ref{fig:inference-rules} until a fixed point is reached.
+The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies the inference rules from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
 Inference rule conditions are checked for validity over all concrete topologies using the Z3 \ryan{cite} SMT solver.
 In order to ensure termination, we make the observation that, for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
-Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the Z3 optimizing constraint solver.
+Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimization framework Z3Opt.
 
@@
 Consider again the datacenter example from \S\ref{sec:overview}.
-Suppose now we add the valleyfree constraint that traffic never has takes a path with a down-up in it for the routing policy for global prefixes:
+Suppose now we add the valleyfree constraint that traffic never takes a path with a down-up in it for the routing policy for global prefixes:
 %
@@
 The first step applies the rule \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles.
-This invokes a call to Z3Opt to minimize the expression $min(\infty, AG)$, which gives us 2.
+This invokes a call to Z3Opt to minimize the expression $min(\infty, AG)$, which results in 2.
 Therefore, the algorithm learns a new invariant of the form $S_P A_{AG} (2,1)$ for node $(AG, 0)$ to indicate that in some pod P, any group of 2 nodes is reachable.
@@
 
-In this case, the algorithm was able to infer that, with the valleyfree routing policy, any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a prefix originator in role TG.
+In this case, the algorithm was able to infer that, with the valleyfree routing policy, any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a router in role TG.
 Note that, in this case, the analysis is precise.
-There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router.
-In this case, the analysis can be used to determine the number of failures that can induce an aggregation black-hole at the border of the datacenter.
+There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router due to the valleyfree constraint.
+In this case, a bound on the fault tolerance between a tor and spine router can be used to ensure that an aggregation-induced black hole will not occur at the border of the datacenter until a certain number of failures occur.
 

### 2016-11-09 paper/abstraction/paper.tex
edits

@@
 
-The first idea is to tag every protocol message with a BGP community value that relays the state of each automaton when advertising a route to a neighbor.
-Routers can then allow route advertisements that correspond to an edge in the Product Graph (\IE, from a neighbor with the correct state) and block those that don't.
-This ensures that any path computed by BGP will be a valid path in the Product Graph, and thus is allowed by the policy.
+The first idea is to tag every protocol message with a BGP community value that encodes the state of each automaton when advertising a route to a neighbor.
+Routers can then allow route advertisements that correspond to an edge in the Product Graph and block those that don't.
+%This ensures that any path computed by BGP will be a valid path in the Product Graph, and thus is allowed by the policy. 
 For example, in the concrete Product Graph in figure~\ref{fig:example-compilation}, router $S1$ will allow a route advertisement from its neighbor $P1$ and also from neighbor $P2$.
-If it uses neighbor $P1$, then it will add the tag $(1,0)$ before informing its neighbors about its route.
-On the other hand, if it uses neighbor $P2$, then it will add the tag $(0,1)$ before informing its neighbors about the route.
-%
-However, letting BGP find some allowed path is not enough. \sysname must ensure BGP always computes the \emph{best} path according to the user's preferences, even when failures occur.
+If it uses the path provided by neighbor $P1$, then it will add the tag $(1,0)$ before informing its neighbors about this route.
+On the other hand, if it uses neighbor $P2$, then it will add the tag $(0,1)$ instead.
 
 \para{Preference Search}
-The second idea is to totally order advertisements each router might receive from neighbors in the Product Graph by preference.
-For example, to satisfy the policy that leaving through $\sf{P1}$ is preferred to leaving through $\sf{P2}$, router $S1$ should prefer a route it hears from $P1$ over one from $P2$.
+The second idea is to have each router totally order advertisements from neighbors.
+For example, to satisfy the policy that leaving through $\sf{P1}$ is preferred to leaving through $\sf{P2}$, router $S1$ should prefer a message it hears from $P1$ over one from $P2$.
 Similarly, router $A1$ should prefer routes tagged with $(1,0)$ over those tagged with $(0,1)$.
-
-In general, because BGP is distributed, each router does not have a full view of the entire network when choosing which path to use.
-Because finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem, Propane introduced a conservative, yet effective algorithm for determining route preferences based on the following observation about the structure of the Product Graph:
+%In general, because BGP is distributed, each router does not have a full view of the entire network when choosing which path to use.
+Because finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem,
+Propane introduced a conservative, yet effective algorithm for determining route preferences based on the following observation about the structure of the Product Graph:
 
@@
 Let $m \geq_{rank} n$ be a relation over Product Graph vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$.
-Intuitively $m \geq_{rank} n$ means that paths ending at PGIR node $m$ are no better (higher rank) than paths ending at $n$.
+Intuitively $m \geq_{rank} n$ means that paths ending at PGIR node $m$ are no better than paths ending at $n$.
 %
@@
 
+%\begin{defn}
+The product graph can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge.
+That is, $m\overset{l}{\rightarrow}n$ if edge $(m,n) \in E'$ and $\tilde{n} = l$.
+%\end{defn}
+%
+For example, in the concrete product graph we would have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.
+
 \begin{defn}
-The product graph can be viewed as a labelled transition system by pushing the topology location from each directed edge's target node onto the edge.
-That is, $m\overset{l}{\rightarrow}n$ if edge $(m,n) \in E'$ and $\tilde{n} = l$.
+We write $m \leq m'$ if the subgraph reachable from $m$ and $m'$ respectively form a simulation relation with respect to the $\geq_{rank}$ relation.
 \end{defn}
 
-For example, in concrete product graph we would have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$
-
-\begin{defn}
-We write $m \leq m'$ if the subgraph reachable from $m$ and $m'$ respectively form a simulation relation with respect to the $\geq_{rank}$ relation on node rankings.
-\end{defn}
-
-We can assign BGP local preferences for the policy in the following way: Check if each router has a total order with respect to the simulation relation ($\leq$) for its corresponding Product Graph nodes.
-If so, then simply sort the nodes and prefer advertisements from peers of node $m$ over those of node $m'$ if $m' \leq m$.
-
-For example, in the concrete product graph the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the product graph can always match transitions made on the right hand side while always maintaining a node ranking that is at least as good as that on the right hand side (since they match the preferred rank 1 automaton).
-This relation does not hold the other way around.
+If each router has a total order with respect to the simulation relation ($\leq$) for its corresponding Product Graph nodes, then we simply sort the nodes and prefer advertisements from peers of node $m$ over those of node $m'$ if $m' \leq m$.
+%
+For example, in the concrete product graph the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the product graph can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation.
+This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$.
 Therefore, advertisements received at $S1$ in state $(1,0)$ must be preferred to those received in state $(0,1)$.
@@
 
-  \caption{Spine configurations for concrete and abstract policies. \ryan{TODO: this would look good in powerpoint and by connecting related components}}
+  \caption{Spine configurations for concrete and abstract policies.}
   \label{fig:bgp-configs}
@@
 
-By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations.
+%By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations.
 In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
-Figure~\ref{fig:bgp-configs} shows part of the configuration for the spine routers for the concrete and abstract policies.
-
-The spine routers have a default rule for the prefix $0.0.0.0/[0..32]$ that will match advertisements from peer $P1$ and $P2$.
-The match for $P1$ is preferred since it has a higher BGP local-preference attribtue (110).
-If an advertisement from $P1$ is available the spine attaches the community tag $(1,0)$ and advertises the route to all its peers.
+Figure~\ref{fig:bgp-configs} shows part of the final configuration for spine routers for the concrete and abstract policies.
+%
+For prefix $0.0.0.0/[0..32]$, the spine routers will match advertisements from peer $P1$ and $P2$.
+The match for $P1$ is preferred since it has a higher BGP local-preference attribute (110).
+If an advertisement from $P1$ is available the spine uses this and attaches the community tag $(1,0)$ and advertises the route to all its peers.
 If only an advertisement from the backup $P2$ is available, then it attaches the tag $(0,1)$ and advertises this to all peers instead.
-
-In the template configuration, it will have additional policy for the local and global prefixes.
-It will match any global prefix from any peer and re-advertise the route to all of its peers.
-For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to all other internal peers.
-The concrete configurations will have a similar configuration for each local and global prefix.
+%
+There is also additional policy for the Product Graphs from constraints for the local and global prefixes.
+In the template configuration, it matches any global prefix from any internal peer and re-advertise the route to all of its peers.
+For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers (thus implementing the Locality constraint).
+The concrete configurations have a similar configuration for each local and global prefix.
 

### 2016-11-09 paper/abstraction/appendix.tex
update pgir images. describe concretization functions

@@
      ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
-     ps   &::=& \{ t_1, ~\dots,~ t_k \} & \textit{predicates} \\
      ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
+     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
   \end{array} \]%

### 2016-11-09 paper/abstraction/paper.tex
update pgir images. describe concretization functions

@@
 
-\subsection{Compilation Correctness}
+\section{Concretization}
 
@@
      pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
-     ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
-     ps   &::=& \{ t_1, ~\dots,~ t_k \} & \textit{predicates} \\
+     ma   &::=& d_1 : ({ns}_1, d_2) \rightarrow ({ns}_2, d_3) & \textit{match action} \\
      ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
+     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
+     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
      ~~~~~ \{ l \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~ l \in internal(V), \\
+     ~~~~~~~~~ l \in internal(G.V), \\
      ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
@@
      \\
-     \text{compile}( p_1, \dots, p_k ) = \\
-     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1), \dots, \text{compile}_\text{PG}(p_k)) \\
+     \text{compile}( p_1, \dots, p_k, G) = \\
+     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G)) \\
   \end{array} \]%
@@
 
-An important observation is that the topology abstraction $f$ is preserved throughout compilation.
-This is reflected in the structure of the template and concrete configurations from Figure~\ref{fig:bgp-configs}.
-At a first cut, the configurations appear the same except for the fact that (1) the abstract locations are replaced with the union of all concrete locations in the concrete configurations, and (2) the prefix templates are replaced with an entry for each unique prefix in the concrete policy.
-
+One interesting observation is that the spine template configuration and concrete spine configurations are structured similarly.
 In this section, we formalize this observation.
-We introduce a simple language for BGP configurations called ABGP and define compilation over both concrete and abstract topologies to ABGP.
-In addition we define a concretization function for both \sysname policies as well as ABGP configurations that take an abstract policy/configuration and turn it into a concrete policy/configuration.
-The main theoretical result is that the compilation and concretization functions commute.
-This means we can perform compilation over the abstract representation to generate templates, and only concretize these templates when we need to instantiate the network.
+We introduce a simple language for BGP configurations called ABGP and define compilation policies over both concrete and abstract topologies to ABGP.
+In addition we define a concretization function for that translates an abstract \sysname policy or ABGP configuration to a concrete \sysname policy or ABGP configuration respectively.
+The main result is that the compilation and concretization functions commute.
+This means performing compilation over the abstract representation first allows us to generate templates, and only concretize these templates when we need to instantiate the network.
 
@@
 
-We introduct a simple language for BGP configurations called ABGP. Figure~\ref{fig:concretization} shows the syntax for an ABGP policy.
-
- An ABGP policy consists of a map from topology locations $l$ to router configurations $rc$.
-Each router configuration $rc$ is a sequence of prefix (templates) $t$ and their corresponding prefix configuration $pc$.
-A prefix configuration $pc$ is a sequence of match actions $ma$.
-Each match action $ma$ consists of a preference value $n_1$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $n_2$, as well as export neighbors $ns_2$ and the updated community value $n_3$.
-
- \vspace{1em}
-
-We assume a particular router $l$ appears at most once in any abgp specification.
-We often build configs using set-builder notation.  For instance,
+We introduct a simple language for BGP configurations called ABGP.
+Figure~\ref{fig:concretization} shows the syntax for an ABGP policy.
+An ABGP policy maps topology locations $l$ to router configurations $rc$.
+Each router configuration $rc$ is a sequence of predicates $t$ and their corresponding configuration $pc$.
+A prefix configuration $pc$ is a sequence of match actions.
+Each match action $ma$ consists of a preference value $d_1$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $d_2$ expected from those neighbors, as well as export neighbors $ns_2$ and the community value $d_3$ to attach before sending to those neighbors.
+
+\para{Compilation}
+
+Figure~\ref{fig:concretization} defines compilation from a \sysname policy to an ABGP policy.
+It starts by compiling ($\text{compile}_\text{PG}$) separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$.
+The function $\text{compile}_\text{PG}$ returns the test $t_i$, product graph $PG_i$, and the preference ordering $ord_i$.
+%
+The function $\text{compile}_\text{ABGP}$ then takes a sequence of tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy.
+For each internal router, it looks at each set of neighbor with the same community state $q_n$ and matches any of those neighbors with the preference provided by the ordering $ord$.
+It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.
+
+%We assume a particular router $l$ appears at most once in any abgp specification.
+We build configs using set-builder notation.  For instance,
 $\{l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc)\}$ denotes the abgp policy
-
+%
 \[ \begin{array}{c}
-  l_1 \rightarrow rc_{11},... \\
+  l_1 \rightarrow rc_{1},... \\
   ...           \\
-  l_k \rightarrow rc_{1k},... \\
+  l_k \rightarrow rc_{k},... \\
 \end{array} \]
@@
 where $l_1, ..., l_k$ are the nodes in the topology
-and each $rc_{ij}$ satisfies $p(l_i,rc_{ij})$.
-
-\para{Compilation}
-
-Figure~\ref{fig:abgp-syntax} also defines compilation from a \sysname policy to an ABGP policy.
-It starts by compiling separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$, the particular test $t_i$, and the preference ordering $ord_i$.
-
-The function $compile_{ABGP}$ then takes tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy.
-It looks at each incoming neighbor with the same community state $q_n$ and matches any of those neighbor with the preference provided by the ordering $ord$ obtained from the search for local preferences.
-It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.
+and each $rc_{i}$ satisfies $p(l_i,rc_{i})$. We also use the $\bigcup$ operator to denote sequence concatenation.
 
@@
 
-We define what it means to concretize an abstract \sysname policy. 
-Concretization takes as input, a policy and a context $\Gamma$ mapping from a template prefix to a set of pairs of a concrete prefix and a concrete location where the prefix is owned.
-
+Concretization for a \sysname policy takes as input, the policy and a context 
+$\Gamma : Var \rightarrow 2^{Prefix \times V}$, 
+which maps from a template prefix to a set of pairs of a concrete prefix and a concrete location that "owns" the prefix.
+%
 For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$.
-For each template variable, we replace it with a new entry for each of its corresponding concrete values under the supplied mapping $\Gamma$.
-We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that traffic is owned by the concrete location $l$.
-\textbf{Note}: we need the side condition that $\text{end}(l) \cap con(r_i,\Gamma) \neq \emptyset$ if $con(r_i,\Gamma) \neq \emptyset$.
-We can also define concretization over the ABGP policy as:
-
-We use the symbol $\bullet$ to denote that a particular value in a sequence is removed from the sequence.
+For each template variable, we replace it with a new entry for each of its corresponding concrete prefixes under the supplied mapping $\Gamma$.
+We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that this traffic is owned by the concrete location $l$.
+
+We also define concretization over the ABGP policy in a similar manner.
+We replace each abstract router configuration $l \rightarrow rc$ a new entry for each concrete location $\ell \in f^{-1}(l)$.
+The concrete location $\ell$ is passed as a parameter to $con$ to remember the current router.
+%
+To concretize a prefix policy with a template ($\$x \rightarrow pc$) we replace it with a sequence of policies, one for each prefix in context ($(pfx,l) \in \Gamma(x)$).
+Match action statements where the set of import neighbors is the singleton set containing the product graph start node $\{ start \}$ and we are not currently at looking at the router configuration for the location specified in the context $l$, then we drop the match action.
+This is denoted with the $\bullet$ symbol.
+Finally, to concretize a set of neighbors, we again use $f^{-1}$ to find the set of concrete neighbors under the inverse homomorphism, but then restrict it to those that are actually connected in the underlying concrete topology with $G.E$.
 
 \begin{thm}
-  For any context $\Gamma$, concrete topology $G$, homomorphism $f : G \rightarrow G^A$, and policy $pol$,
-  $$\Con(\text{compile}(pol), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f))$$
+  For any context $\Gamma$, topology $G$, abstract topology $G^A$, homomorphism $f : G \rightarrow G^A$, and policy $pol$,
+  $$\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$$
 \end{thm}
@@
 
-Suppose that we want to expand the concrete datacenter by adding an additional tor router in the TG role.
-Per the network routing policy, this new ToR router will advertise its own owned prefix.
+Suppose that we want to expand our example concrete datacenter by adding an additional tor router in the TG role.
+Per the network routing policy, this new tor router will advertise its new owned prefix.
 Because the new topology matches the abstraction, the compiled templates will remain the same.
-However, in the spine router configurations, the match on the global prefix template variable \$GP will be expanded to include the new prefix owned by the ToR.
+However, in the spine router configurations, the match on the global prefix template variable \$GP will be expanded to include the new prefix owned by the added tor.
 In other words, the concrete configurations obtained after substitution will include an additional match on the new prefix.
-Unfortunately, this means a small change to the topology can result in many configurations far from the change needing to change too.
-
-The key observation is that the template variables tell us exactly where change can happen.
-For example, the only way in which the spine routers depend on anything nonlocal is in the prefix template variables.
-Instead, we replace each match on a template variable (\EG, matching \$GP) with a test on a new community tag that we associate with each template variable.
-So long as we ensure that routers always add the appropriate tags to the prefixes they originate, then the policies will be equivalent.
-
-Specifically, this ensures that each router has a template that has no dependency on any other non-adjacent router.
+Unfortunately, this means that a small change to the topology can result in many configurations far from the change needing to change too.
+
+The key insight is that the template variables tell us exactly where change can happen.
+For example, the only way in which the spine routers depend on anything non-local is in the match on prefix template variables.
+Instead, we can associate a new unique community tag for each template variable like \$GP.
+We can replace each match on \$GP with a test on the new community tag.
+The new added tor will now simply attach the new community tag to advertisements for its prefix so downstream routers can just match the community tag.
+This ensures that each router has a template that has no dependency on any other non-adjacent router.
 If we make a change to the concrete network that matches the abstraction, then the templates do not change, and thus only configurations adjacent to the changes must also change.

### 2016-11-09 paper/abstraction/paper.tex
make images smaller:

@@
      p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
-     t       &::=& \$x & \textit{template variable} \\
-         &\BNFALT& d.d.d.d/[d..d] ~~~~~~~~~~~~~~~~~~~  & \textit{prefix test} \\
+     t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \textit{template variable} \\
      r       &::=& l & \textit{location} \\
@@
 \begin{figure*}[t!]
-  \begin{minipage}[t]{.2\linewidth}
+  \begin{minipage}[t]{.4\linewidth}
   \hdr{Policy Automata}{}
@@
       \transition{1}{1}{in}{loop above}
+      \node at (1,-1){Rank 1 DFA};
     \end{tikzpicture}
-
+    ~~~~~
     \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
@@
       \transition{1}{1}{in}{loop above}
+      \node at (1,-1){Rank 2 DFA};
     \end{tikzpicture}%
@@
   %
-  \begin{minipage}[t]{.4\linewidth}
+  \begin{minipage}[t]{.3\linewidth}
     \hdr{Concrete Topology}{}
@@
   %
-  \begin{minipage}[t]{.4\linewidth}
+  \begin{minipage}[t]{.3\linewidth}
     \hdr{Abstract Topology}{}
@@
 
-  \vspace{2em}
+  \vspace{1em}
   \begin{minipage}[t]{.6\linewidth}
@@
 
-\section{Compilation}
-
-The translation from the Product Graph to per-device configurations that run the distributed BGP protocol involves several ideas.
-
-\para{Route filtering}
-
-The first idea is to tag every protocol message with a BGP community value that encodes the state of each automaton when advertising a route to a neighbor.
-Routers can then allow route advertisements that correspond to an edge in the Product Graph and block those that don't.
-%This ensures that any path computed by BGP will be a valid path in the Product Graph, and thus is allowed by the policy. 
-For example, in the concrete Product Graph in figure~\ref{fig:example-compilation}, router $S1$ will allow a route advertisement from its neighbor $P1$ and also from neighbor $P2$.
-If it uses the path provided by neighbor $P1$, then it will add the tag $(1,0)$ before informing its neighbors about this route.
-On the other hand, if it uses neighbor $P2$, then it will add the tag $(0,1)$ instead.
-
-\para{Preference Search}
-The second idea is to have each router totally order advertisements from neighbors.
-For example, to satisfy the policy that leaving through $\sf{P1}$ is preferred to leaving through $\sf{P2}$, router $S1$ should prefer a message it hears from $P1$ over one from $P2$.
-Similarly, router $A1$ should prefer routes tagged with $(1,0)$ over those tagged with $(0,1)$.
-%In general, because BGP is distributed, each router does not have a full view of the entire network when choosing which path to use.
-Because finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem,
-Propane introduced a conservative, yet effective algorithm for determining route preferences based on the following observation about the structure of the Product Graph:
-
-\begin{defn}
-Let $m \geq_{rank} n$ be a relation over Product Graph vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$.
-Intuitively $m \geq_{rank} n$ means that paths ending at PGIR node $m$ are no better than paths ending at $n$.
-%
-\end{defn}
-\noindent
-%
-
-%\begin{defn}
-The product graph can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge.
-That is, $m\overset{l}{\rightarrow}n$ if edge $(m,n) \in E'$ and $\tilde{n} = l$.
-%\end{defn}
-%
-For example, in the concrete product graph we would have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.
-
-\begin{defn}
-We write $m \leq m'$ if the subgraph reachable from $m$ and $m'$ respectively form a simulation relation with respect to the $\geq_{rank}$ relation.
-\end{defn}
-
-If each router has a total order with respect to the simulation relation ($\leq$) for its corresponding Product Graph nodes, then we simply sort the nodes and prefer advertisements from peers of node $m$ over those of node $m'$ if $m' \leq m$.
-%
-For example, in the concrete product graph the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the product graph can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation.
-This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$.
-Therefore, advertisements received at $S1$ in state $(1,0)$ must be preferred to those received in state $(0,1)$.
-
-Notice also that in the abstract product graph the inequality $(S,0,1) \leq (S,1,0)$ holds. This leads us the the following observation:
-
-\begin{lem}
-\label{lem:preference}
-$m \leq m'$ in the concrete product graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph under the lifted graph homomorphism $f_{pg}$.
-\end{lem}
-
-Lemma~\ref{lem:preference} gives us reason to believe that we can perform compilation over the abstract product graph and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.
-
 \newcommand{\highlight}[1]{%
@@
 \newcommand{\Router}[1]{\KW{Router} #1:}
+\newcommand{\Template}[1]{\KW{Template} #1:}
 \newcommand{\REGEX}[1]{\texttt{regex}(#1)}
@@
 
-\para{BGP configurations}
-
-\begin{figure*}[t!]
-  \begin{minipage}[t]{.54\linewidth}
-    \hdr{Concrete Configuration}{}
+\begin{figure}[t!]
   \begin{code}
-      \Router{S1, S2}
-        Match[100] \PREFIX=GP1, \PEER=\{AG1, ..., AL1, ...\}
-          \PEER \Arrow *
-        Match[100] \PREFIX=GP2, \PEER=\{AG1, ..., AL1, ...\}
-          \PEER \Arrow *
-        ...
-        Match[100] \PREFIX=LP1, \PEER=\{AG1, ..., AL1, ...\}
-          \PEER \Arrow \{AG1, ..., AL1, ...\}
-        Match[100] \PREFIX=LP2, \PEER=\{AG1, ..., AL1, ...\}
-          \PEER \Arrow \{AG1, ..., AL1, ...\}
-        ...
-        Match[110] \PREFIX=0.0.0.0/[0..32], \PEER=P1,
-          \PEER \Arrow *, \COMM \Arrow (1,0)
-        Match[100] \PREFIX=0.0.0.0/[0..32], \PEER=P2,
-          \PEER \Arrow *, \COMM \Arrow (0,1)
-        ...
-      \end{code}
-  \end{minipage}
-  %
-  \begin{minipage}[t]{.4\linewidth}
-    \hdr{Template Configuration}{}
-    \begin{code}
-      \Router{S}
+    \Template{S}
       Match[100] \PREFIX=\$GP, \PEER=\{AG, AL\}
@@
         \PEER \Arrow \{AG, AL\}
-        Match[110] 0.0.0.0/[0..32], \PEER=P1,
+      Match[110] \PREFIX=true \PEER=\{P1\},
         \PEER \Arrow *, \COMM \Arrow (1,0)
-        Match[100] 0.0.0.0/[0..32], \PEER=P2,
+      Match[100] \PREFIX=true \PEER=\{P2\},
         \PEER \Arrow *, \COMM \Arrow (0,1)
@@
   \end{code}
-  \end{minipage}%
-
-  \hrulefill
-  \vspace*{.4em}%
-
-  \caption{Spine configurations for concrete and abstract policies.}
+
+  \vspace{-2em}
+  \begin{code}
+    \Router{S1, S2}
+      Match[100] \PREFIX=GP1, \PEER=\{AG1, AL1, ...\}
+        \PEER \Arrow *
+      Match[100] \PREFIX=GP2, \PEER=\{AG1, AL1, ...\}
+        \PEER \Arrow *
+      ...
+      Match[100] \PREFIX=LP1, \PEER=\{AG1, AL1, ...\}
+        \PEER \Arrow \{AG1, AL1, ...\}
+      Match[100] \PREFIX=LP2, \PEER=\{AG1, AL1, ...\}
+        \PEER \Arrow \{AG1, AL1, ...\}
+      ...
+      Match[110] \PREFIX=true, \PEER=\{P1\},
+        \PEER \Arrow *, \COMM \Arrow (1,0)
+      Match[100] \PREFIX=true, \PEER=\{P2\},
+        \PEER \Arrow *, \COMM \Arrow (0,1)
+      ...
+    \end{code}
+
+  \vspace{-1em}
+  \caption{Spine template and concrete configurations.}
   \label{fig:bgp-configs}
-\end{figure*}
+\end{figure}
+
+\section{Compilation}
+
+The translation from the Product Graph to per-device configurations that run the distributed BGP protocol involves several ideas.
+
+\para{Route filtering}
+
+The first idea is to tag every protocol message with a BGP community value that encodes the state of each automaton when advertising a route to a neighbor.
+Routers can then allow route advertisements that correspond to an edge in the Product Graph and block those that don't.
+%This ensures that any path computed by BGP will be a valid path in the Product Graph, and thus is allowed by the policy. 
+For example, in the concrete Product Graph in figure~\ref{fig:example-compilation}, router $S1$ will allow a route advertisement from its neighbor $P1$ and also from neighbor $P2$.
+If it uses the path provided by neighbor $P1$, then it will add the tag $(1,0)$ before informing its neighbors about this route.
+On the other hand, if it uses neighbor $P2$, then it will add the tag $(0,1)$ instead.
+
+\para{Preference Search}
+The second idea is to have each router totally order advertisements from neighbors.
+For example, to satisfy the policy that leaving through $\sf{P1}$ is preferred to leaving through $\sf{P2}$, router $S1$ should prefer a message it hears from $P1$ over one from $P2$.
+Similarly, router $A1$ should prefer routes tagged with $(1,0)$ over those tagged with $(0,1)$.
+%In general, because BGP is distributed, each router does not have a full view of the entire network when choosing which path to use.
+Because finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem,
+Propane introduced a conservative, yet effective algorithm for determining route preferences based on the following observation about the structure of the Product Graph:
+
+\begin{defn}
+Let $m \geq_{rank} n$ be a relation over Product Graph vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$.
+Intuitively $m \geq_{rank} n$ means that paths ending at PGIR node $m$ are no better than paths ending at $n$.
+%
+\end{defn}
+\noindent
+%
+
+%\begin{defn}
+The product graph can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge.
+That is, $m\overset{l}{\rightarrow}n$ if edge $(m,n) \in E'$ and $\tilde{n} = l$.
+%\end{defn}
+%
+For example, in the concrete product graph we would have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.
+
+\begin{defn}
+We write $m \leq m'$ if the subgraph reachable from $m$ and $m'$ respectively form a simulation relation with respect to the $\geq_{rank}$ relation.
+\end{defn}
+
+If each router has a total order with respect to the simulation relation ($\leq$) for its corresponding Product Graph nodes, then we simply sort the nodes and prefer advertisements from peers of node $m$ over those of node $m'$ if $m' \leq m$.
+%
+For example, in the concrete product graph the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the product graph can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation.
+This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$.
+Therefore, advertisements received at $S1$ in state $(1,0)$ must be preferred to those received in state $(0,1)$.
+
+Notice also that in the abstract product graph the inequality $(S,0,1) \leq (S,1,0)$ holds. This leads us the the following observation:
+
+\begin{lem}
+\label{lem:preference}
+$m \leq m'$ in the concrete product graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph under the lifted graph homomorphism $f_{pg}$.
+\end{lem}
+
+Lemma~\ref{lem:preference} gives us reason to believe that we can perform compilation over the abstract product graph and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.
+
+\para{BGP configurations}
 
@@
 
-\section{Concretization}
+%=====================================================
+%
+%
+%  **Concretization**
+%
+%
+%=====================================================
 
@@
   \label{fig:concretization}
-
 \end{figure*}%
+
+\section{Concretization}
 

### 2016-11-10 paper/abstraction/paper.tex
add citations for topologies + Z3

@@
     \node at (#1 + .11 + .8, 1.5) {$e_4$};
-    \node at (#1 - 1, -.8) {L$(j,k)$};
-    \node at (#1 +. 5, 2.9) {S$(min(j*k,g),1)$};
-    \node at (#1 + 2, -.8) {S$\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
+    \node at (#1 - 1, -.8) {L$_m(j,k)$};
+    \node at (#1 +. 5, 2.9) {S$_n(min(j*k,g),1)$};
+    \node at (#1 + 2, -.8) {S$_o\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
     \node at (#1, 3.3) {};
@@
   \begin{tikzpicture}
-    \inference{0}{L$(j,k)$}{$e_1 > 0$}{S$(min(j*k,e_1),1)$}{I-out1}{$e_1$}{$e_2$}
-    \inference{4.5}{A$(j,k)$}{$e_2 > 0$}{A$(1,min(j,e2))$}{I-out2}{$e_1$}{$e_2$}
-    \inference{9}{L$(j,k)$}{$e_1=n$}{A$(min(j*k,n),1)$}{I-mesh1}{$e_1$}{$e_2$}
-    \inference{13.5}{L$(j,k)$}{$e_1=n$}{A$(1,j)$}{I-mesh2}{$e_1$}{$e_2$}
+    \inference{0}{L$_m(j,k)$}{$e_1 > 0$}{S$_n(min(j*k,e_1),1)$}{I-out1}{$e_1$}{$e_2$}
+    \inference{4.5}{A$_m(j,k)$}{$e_2 > 0$}{A$_n(1,min(j,e2))$}{I-out2}{$e_1$}{$e_2$}
+    \inference{9}{L$_m(j,k)$}{$e_1=n$}{A$_n(min(j*k,n),1)$}{I-mesh1}{$e_1$}{$e_2$}
+    \inference{13.5}{L$_m(j,k)$}{$e_1=n$}{A$_n(1,j)$}{I-mesh2}{$e_1$}{$e_2$}
   \end{tikzpicture}
@@
 The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies the inference rules from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
-Inference rule conditions are checked for validity over all concrete topologies using the Z3 \ryan{cite} SMT solver.
+Inference rule conditions can be checked for validity over all concrete topologies using an SMT solver.
 In order to ensure termination, we make the observation that, for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
-Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimization framework Z3Opt.
+Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimization framework $\nu$Z~\cite{z3opt}.
 
@@
 The first step applies the rule \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles.
-This invokes a call to Z3Opt to minimize the expression $min(\infty, AG)$, which results in 2.
+This invokes a call to $\nu$Z to minimize the expression $min(\infty, AG)$, which results in 2.
 Therefore, the algorithm learns a new invariant of the form $S_P A_{AG} (2,1)$ for node $(AG, 0)$ to indicate that in some pod P, any group of 2 nodes is reachable.
@@
 Operators can specify their required fault tolerance level for aggregation safety.
-The abstract safety analysis uses Z3Opt \ryan{reference} to minimize variables subject to the annotated constraints.
-Since the analysis typically calls Z3 with many times with relatively simple optimization problems, we use a timeout of 200ms.
+The abstract safety analysis uses $\nu$Z~\cite{z3opt} test validity and to minimize variables subject to the annotated constraints.
+Since the analysis typically calls the SMT solver with many times with relatively simple optimization problems, we use a timeout of 200ms.
 
@@
       \textbf{Topology} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
-      Google Fattree & & \cmark & \cmark  \\ \hline
-      Facebook Fattree & & \cmark & \cmark \\ \hline
-      Microsoft Fattree & & & \\ \hline
-      F10 Fattree & & \cmark & \cmark \\ \hline
-      BCube & $k$ & \cmark & \xmark \\ \hline
-      DCell & $k$ & \cmark & \xmark \\ \hline
+      Fattree~\cite{fattree} & & \cmark & \cmark  \\ \hline
+      Facebook Fattree~\cite{facebook-fattree} & & \cmark & \cmark \\ \hline
+      F10 Fattree~\cite{f10-fattree} & & \cmark & \cmark \\ \hline
+      VL2 Fattree~\cite{vl2-fattree} & & & \\ \hline
+      BCube~\cite{bcube} & $k$ & \cmark & \xmark \\ \hline
+      DCell~\cite{dcell} & $k$ & \cmark & \xmark \\ \hline
          %& HCN & $h$ & \cmark & \xmark \\
-      Butterfly & $n$ & \cmark & \cmark \\ \hline
+      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark \\ \hline
       Hypercube & $N$ & \cmark & \cmark \\ \hline
-      HyperX & $L$ & \cmark & \cmark \\ \hline
+      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark \\ \hline
       \end{tabular}
@@
 The Fat Tree topology is one of the most widely used datacenter topologies.
-We look at the precision of our analysis on three variants of the Fat Tree~\cite{foo} topology used in practice: the Google Fat Tree, the Facebook Fat Tree, and the F10 fault tolerant Fat Tree.
-For each Fat Tree variant, we use a tiered abstraction similar to that in our previous example \ryan{Reference}.
+We look at the precision of our analysis on four variants of the Fat Tree topology used in practice: a Standard Fat Tree~\cite{fattree}, the Facebook Fat Tree~\cite{facebook-fattree}, the F10 fault tolerant Fat Tree~\cite{f10-fattree}, and the VL2 topology~\cite{vl2-fattree}.
+For each Fat Tree variant, we use a tiered abstraction similar to that in our previous example.
 Each Fat Tree topology is parameterized over the number of pods $k$, which can be scaled up in the abstraction to allow for expansion.
@@
 We also model several recursive topologies using our abstractions.
-These include the BCube and DCell topologies.
+These include the BCube~\cite{bcube} and Dcell~\cite{dcell} topologies.
 Each topology includes a recursion depth parameter ($k$), which we must fix.
@@
 Hypercube variants can be used as an alternative to Clos-style topologies for networks with high-radix (port density) routers.
-The HyperX topology can be viewed as a generalization of the hypercube, which includes parameters $L$ for the lattice dimension of the network, $S_i$ for the node multiplicity of each dimension $i$, $K_i$ for the bandwidth of links for each dimension, and $T$ for the number of terminal nodes (servers) connected to each router.
+The HyperX~\cite{hyperx} topology can be viewed as a generalization of the hypercube and butterfly topologies, which includes parameters $L$ for the lattice dimension of the network, $S_i$ for the node multiplicity of each dimension $i$, $K_i$ for the bandwidth of links for each dimension, and $T$ for the number of terminal nodes (servers) connected to each router.
 For a fixed number of dimensions $L$, we abstract each full mesh of $S_L$ nodes into its own abstract node.

### 2016-11-10 paper/abstraction/paper.tex
update pg pictures

@@
   \hdr{Policy Automata}{}
+  \vspace{1em}
     \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
@@
     \hdr{Concrete Topology}{}
+    \vspace{1em}
     \includegraphics[width=.7\columnwidth]{figures/topology-con}
@@
     \hdr{Abstract Topology}{}
+    \vspace{1em}
     \includegraphics[width=.57\columnwidth]{figures/topology-abs}
@@
   \hdr{Abstract Product Graph}{}
-    \includegraphics[width=.9\columnwidth]{figures/pg-abs}
+    \includegraphics[width=.88\columnwidth]{figures/pg-abs}
 
@@
 
-The compiler performs the following to improve its performance.
-
-\para{Z3 memoization}
-
-Although the k-disjoint path analysis takes place over the Product Graph representation, which may differ from the topology (e.g., for non-shortest paths routing), each application of the inference rules from figure~\ref{fig:abstract-analysis} depends only on the topology.
-Therefore, we lazily apply the rules and cache the satisfiability and minimization calls to Z3 after their first use.
-Doing this significantly speeds up the failure safety analysis.
-Furthermore, the cached results can be shared across different prefixes, each of which may have a unique Product graph representation.
-In practice, this means that after performing the abstract analysis for one prefix, the analysis becomes essentially "free" for any subsequent prefixes.
-
-\para{Fast Substitution}
-
-Substitution after compiling a policy abstractly can be expensive since each router must substitute all template variables for each of its connected peers.
+%The compiler performs the following to improve its performance.
+%
+%\para{Z3 memoization}
+
+Although the disjoint path analysis takes place over the Product Graph, each application of the inference rules from figure~\ref{fig:inference-rules} depends only on the topology.
+Therefore, we lazily apply the rules and cache the satisfiability and minimization calls to $\nu$Z after their first use.
+Furthermore, the cached results are shared across different prefixes, each of which may have a unique Product graph representation.
+
+%\para{Fast Substitution}
+%
+%Substitution after compiling a policy abstractly can be expensive since each router must substitute all template variables for each of its connected peers.
 In practice, because many routers often share the same concrete peers, memoizing the substitution function greatly improves performance.
@@
       Fattree~\cite{fattree} & & \cmark & \cmark  \\ \hline
-      Facebook Fattree~\cite{facebook-fattree} & & \cmark & \cmark \\ \hline
-      F10 Fattree~\cite{f10-fattree} & & \cmark & \cmark \\ \hline
-      VL2 Fattree~\cite{vl2-fattree} & & & \\ \hline
+      Facebook~\cite{facebook-fattree} & & \cmark & \cmark \\ \hline
+      F10~\cite{f10-fattree} & & \cmark & \cmark \\ \hline
+      VL2~\cite{vl2-fattree} & & & \\ \hline
       BCube~\cite{bcube} & $k$ & \cmark & \xmark \\ \hline

### 2016-11-10 paper/abstraction/paper.tex
pass on 4

@@
 
-\sysname is a system for generating provably-correct templates.
-As inputs, it takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an {\em abstract} topology that describes device roles and
-connectivity invariants.  It outputs a template for each role, from which per-device configurations can be generated by instantiating parameters with values drawn from the network topology.
-\sysname provides strong guarantees about its templates:
-(1) the configurations generated from them correctly implement the specified policy for {\em any} concrete topology that matches the given abstract topology; and (2) if nodes or edges are added or removed in a way compatible
+\sysname is a system for generating provably-correct templates from the network's policy and an {\em abstract} topology that describes device roles and connectivity invariants.
+%As inputs, it takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an {\em abstract} topology that describes device roles and connectivity invariants.
+It outputs a template for each role, from which per-device configurations can be generated by instantiating parameters with values drawn from the network topology.
+It guarantees that:
+(1) the configurations generated from its templates correctly implement the network's policy for {\em any} concrete topology that matches the abstract topology; and (2) if nodes or edges are added or removed in a way compatible
 with the abstract topology, only configurations of adjacent devices ever need to be updated.
 
-This section introduces \sysname using the example in Figure~\ref{fig:example}, and the following sections detail template generation and formally define the correctness guarantees.
+This section introduces \sysname using the examples in \S\ref{sec:motivation}, and the following sections detail template generation and formally define the correctness guarantees.
 
@@
 
-\subsection{Abstract Compilation}
-
-\sysname builds on the Propane network configuration tool, by supporting both synthesis for and reasoning over parameterized classes of topologies and their interactions with user-specified routing policy.
-\sysname takes as input, (1) a topology abstraction in the form of a graph homomorphism annotated with logical constraints about node and edge mutliplicities, and (2) a domain-specific routing policy that consists of a mapping from predicates matching various classes of traffic, to a list of ranked constraints on the paths traffic matching the predicate should prefer to take through the network.
-
-\para{Topology Abstraction}
-
-Consider again the networks from \S\ref{sec:motivation}. Ideally, we would like
-to find a suitable topology abstraction that can describe both of the datacenters from figures~\ref{fig:example} and~\ref{fig:example2} as well as any reasonable generalization of these datacenters.
+\subsection{Inputs}
+
+\sysname takes as input the network's abstract topology and its policy.
+The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous failures a the network can withstand without loosing connectivity.
+
+\para{Abstract topology}
+Abstract topologies in \sysname capture the basic connectivity structure of the network, which holds when the network is originally designed and as it evolves.
+They are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
+We designed these abstractions to be able to precisely capture most real network topologies, while being amenable to the fault tolerance analysis and configuration synthesis that is done by our compiler.
+
+%Ideally, we would like to find a suitable topology abstraction that can describe both of the datacenters from figures~\ref{fig:example} and~\ref{fig:example2} as well as any reasonable generalization of these datacenters.
 \sysname provides several abstraction mechanisms to achieve this goal.
 
-The first is a role-based abstraction that allows an operator to map routers in the concrete network to ``roles" or routers in the abstract network.
+We introduce our topology abstractions using the networks from \S\ref{sec:motivation}.
+The first is a role-based abstraction that allows an operator to map routers in the concrete network to roles in the abstract network.
 Figure~\ref{fig:example3} shows an example of an abstraction for both datacenter networks from \S\ref{sec:motivation}.
-In particular the concrete networks are abstracted into a new topology with 5 different roles: local tor (TL), global tor (TG), local aggregator (AL), global aggregator (AG), and spine (S).
+In particular the concrete networks are abstracted into a new topology with 5 different roles: local ToR (TL), global ToR (TG), local aggregator (AL), global aggregator (AG), and spine (S).
 
@@
 The role-based abstraction therefore overapproximates the connectivity of the underlying concrete graphs.
-Unfortunately this abstraction alone loses a lot of information about the underlying structure of the concrete network.
+Unfortunately, by itself, this abstraction loses a lot of information about the underlying structure of the concrete network, which would hinder a useful analysis of its fault-tolerance.
 For example, with this abstraction any spine router in a concrete network may or may not be connected to any aggregator router.
@@
 Similarly, the number of outgoing edges from $AG$ to $TG$ is equal to the number of nodes that map to $TG$.
-These constraints capture the fact that, within any given pod, the global aggregators and tors are in a full mesh.
+These constraints capture the fact that, within any given pod, the global aggregators and ToRs are in a full mesh.
 Furthermore, the constraints $TG = AG$ and $TG \geq 2$ ensure that the number of concrete nodes in role $TG$ is always equal to the number of concrete nodes in role $AG$, which is at least 2.
-Similar constraints also appear for the local aggregators and tors.
+Similar constraints also appear for the local aggregators and ToRs.
 %
@@
 
-\para{Routing Policy}
-
-Next let us see how to configure each of the datacenter networks from \S\ref{sec:motivation} by writing a \sysname routing policy over the new abstract topology.
-In \sysname, we can capture the basic routing behavior for the datacenters with the following constraints:
+\para{Routing policy} Routing policies in \sysname consist of mappings from predicates matching various classes of traffic to a list of ranked constraints on the paths that the traffic matching the predicate should prefer to take through the network.
+We borrow syntax from Propane~\cite{propane} but, instead of concrete prefixes and nodes, \sysname specifications use abstract prefixes and nodes.
+
+Let us see how to configure each of the datacenter networks from \S\ref{sec:motivation} by writing a \sysname routing policy over the new abstract topology.
+We can capture the basic routing behavior for the datacenters with the following constraints:
 %
@@
 
-\subsection{Abstract Analysis}
-
-Although \sysname can ensure correct forwarding behavior independent of the exact concrete topology or failure scenario, it is often useful to be able to ask "what if" questions about other network properties.
+\para{Fault-tolerance policy} This policy specifies how many link failures the network should be able to withstand before connectivity loss for traffic occurs.
+Operators can  specify different tolerance levels for different pairs of abstract nodes.
+For instance, they may say that ToR to spine connectivity should be robust to 2 failures, i.e., no ToR-spine pair should lose connectivity as long as the number of simultaneous link failures is 2 or fewer (for any combination of links); and ToR-to-ToR connectivity should be be robust to 1 failure.
+
+\subsection{Compilation}
+
+%\sysname builds on the Propane network configuration tool, by supporting both synthesis for and reasoning over parameterized classes of topologies and their interactions with user-specified routing policy.
+
+%Although \sysname can ensure correct forwarding behavior independent of the exact concrete topology or failure scenario, it is often useful to be able to ask "what if" questions about other network properties.
 For example, an operator may require a certain level fault tolerance between between different collections of routers.
 Such analysis depends, not only on the network topology, but also on the underlying routing policy, both of which \sysname has access to.
-To this end, we develop a sound analysis over abstract topologies to answer questions about the number of disjoint paths between pairs of nodes.
-
-Suppose we want to find a worst-case lower bound on the fault tolerance between any global tor and spine router from figure~\ref{fig:example3} for any concrete topology after applying the routing policy.
-This can be used as a lightweight verification tool to detect certain classes of configuration bugs.
+The \sysname compiler generates templates from the inputs above in three phases.
+First, it combines the abstract topology and routing policy into a {\em product graph} that compactly captures the flow of routing information over the topology in a policy-compliant manner.
+The algorithm for this phase builds on the Propane compiler, which was designed for concrete topologies and policy; we show that it can be extended to abstract inputs and that the extensions are correct.
+
+Second, \sysname evaluates if the fault-tolerance policy can be met, considering the joint impact of the abstract topology and routing policy.
+Joint analysis is needed, and topology alone is not enough, because connectivity for traffic will suffer even when functional paths exists in the topology if those paths are not allowed by routing policy.
+It implies that we cannot use standard graph theoretic algorithms here.
+
+Instead, we develop a sound analysis that is based on computing the minimum number of disjoint policy-compliant paths between pairs of nodes over abstract topologies.
+If this number for a pair of nodes is less than the desired fault-tolerance level, we declare that the policy cannot be met.
+
+Suppose we want to compute the number of of disjoint paths between any global ToR and spine router in Figure~\ref{fig:example3} for any concrete topology after applying the routing policy.
+%This can be used as a lightweight verification tool to detect certain classes of configuration bugs.
 For example, since the network is performing prefix summarization at the border of the datacenter, we might introduce a black hole after enough failures occur to disconnect a tor from a spine router.
-
-We develop a disjoint path analysis works in the following way.
+We proceed as follows.
 For each abstract role in the network, we learn invariants about the number of disjoint paths to routers in that role.
@@
 %
-If we run the abstract analysis over the abstract network from figure~\ref{fig:example3} the analysis will learn a fact of the form $A_{S}(1,2)$, which means that any single spine node is reachable via 2 disjoint paths from any initial global tor node \ryan{it will actually be 1, we need to add a constraint on e1}.
-
-Suppose now that we want to disallow paths with valleys (\IE, paths that go down and then up at some point). Such a constraint can be added to the routing policy in \sysname:
-\begin{code}
-\Define ValleyFree =
-    \True \Path \Novalley(\{TL,TG\},\{AL,AG\},\{S\})
-\end{code}
-\noindent%
-
-This adds a constraint that applies to all traffic and prevents valleys by defining each level in the datacenter.
-Because the abstract analysis is policy sensitive, if we were to run it again with the same abstract topology but the new routing policy, it would only be able to infer that there is a single disjoint path to any given spine router in the worst case.
-In fact this is exactly the case for the concrete network from figure~\ref{fig:example2}.
+If we run the abstract analysis over the abstract network from Figure~\ref{fig:example3} the analysis will learn a fact of the form $A_{S}(1,2)$, which means that any single spine node is reachable via 2 disjoint paths from any initial global tor node \ryan{it will actually be 1, we need to add a constraint on e1}.
+
+Suppose now that the routing policy disallowed paths with valleys (\IE, paths that go down and then up at some point). 
+%Such a constraint can be added to the routing policy in \sysname:
+%\begin{code}
+%\Define ValleyFree =
+%    \True \Path \Novalley(\{TL,TG\},\{AL,AG\},\{S\})
+%\end{code}
+%\noindent%
+%This adds a constraint that applies to all traffic and prevents valleys by defining each level in the datacenter.
+Because our analysis is policy sensitive, if we were to run it again with the same abstract topology but the new routing policy, it would only be able to infer that there is a single disjoint path to any given spine router in the worst case.
+In fact this is exactly the case for the concrete network from Figure~\ref{fig:example2}.
+
+Finally, if \sysname deems that the fault-tolerance policy can be met, it generates templates for the abstract topology, which can be instantiated into BGP configurations based on the concrete topology.
+During concretization, we confirm that the concrete topology adheres to the original abstract topology.
 

### 2016-11-10 paper/abstraction/paper.tex
update to correct template

@@
-\documentclass{sig-alternate-10pt}
+\documentclass[numbers, 10pt, preprint]{sigplanconf}
 %\documentclass[10pt]{sigalternate052015}
@@
 
+\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country}
+\copyrightyear{20yy}
+\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
+\copyrightdoi{nnnnnnn.nnnnnnn}
+
+\titlebanner{DRAFT -- do not distribute}        % These are ignored unless
+\preprintfooter{submission for PLDI 2017}   % 'preprint' option specified.
+
 \title{Network Configuration Synthesis with Abstract Topologies}
@@
 
-\author{%
-Ryan Beckett\\
-  \affaddr{Princeton}
-  %\\
-  %\email{rbeckett@princeton.edu}
-\and
-Ratul Mahajan\\
-  \affaddr{Microsoft}
-  %\\
-  %\email{ratul@microsoft.com}
-\and
-Todd Millstein\\
-  \affaddr{UCLA}
-  %\affaddr{University of California, Los Angeles}
-  %\\
-  %\email{todd@cs.ucla.edu}
-\and
-Jitendra Padhye\\
-  \affaddr{Microsoft}
-  %\\
-  %\email{padhye@microsoft.com}
-\and
-David Walker\\
-  \affaddr{Princeton}
-  %\\
-  %\email{dpw@princeton.edu}
-}
+%\authorinfo{Ryan Beckett \and David Walker}{Princeton}{}
+%\authorinfo{Ratul Mahajan \and Jitendra Padhye}{Microsoft}{}
+%\authorinfo{Todd Millstein}{UCLA}{}
+
+\authorinfo{}{}{}
+
+%\author{%
+%Ryan Beckett\\
+%  \affaddr{Princeton}
+%  %\\
+%  %\email{rbeckett@princeton.edu}
+%\and
+%Ratul Mahajan\\
+%  \affaddr{Microsoft}
+%  %\\
+%  %\email{ratul@microsoft.com}
+%\and
+%Todd Millstein\\
+%  \affaddr{UCLA}
+%  %\affaddr{University of California, Los Angeles}
+%  %\\
+%  %\email{todd@cs.ucla.edu}
+%\and
+%Jitendra Padhye\\
+%  \affaddr{Microsoft}
+%  %\\
+%  %\email{padhye@microsoft.com}
+%\and
+%David Walker\\
+%  \affaddr{Princeton}
+%  %\\
+%  %\email{dpw@princeton.edu}
+%}
 
@@
      pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
-     ma   &::=& d_1 : ({ns}_1, d_2) \rightarrow ({ns}_2, d_3) & \textit{match action} \\
+     ma   &::=& lp : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
      ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
      t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
+     c    &   & & \textit{community value} \\
+     lp   &   & & \textit{local preference} \\
   \end{array} \]%
@@
 %
-%  **Implementation**
-%
-%
-%=====================================================
-
-\section{Implementation}
-\label{sec:implementation}
+%  **Implementation and Evaluation**
+%
+%
+%=====================================================
+
+\section{Implementation and Evaluation}
+\label{sec:evaluation}
 
@@
 
-%The compiler performs the following to improve its performance.
-%
-%\para{Z3 memoization}
-
 Although the disjoint path analysis takes place over the Product Graph, each application of the inference rules from figure~\ref{fig:inference-rules} depends only on the topology.
@@
 
-%\para{Fast Substitution}
-%
-%Substitution after compiling a policy abstractly can be expensive since each router must substitute all template variables for each of its connected peers.
-In practice, because many routers often share the same concrete peers, memoizing the substitution function greatly improves performance.
-
-%=====================================================
-%
-%
-%  **Evaluation**
-%
-%
-%=====================================================
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-We apply \sysname on policies for backbone and datacenter networks.
+To evaluate \sysname, we apply it on policies for backbone and datacenter networks.
 We aim to evaluate the expressiveness of our abstract multiplicity annotations, the precision of the abstract disjoint-path analysis, and the compilation time of \sysname both with abstraction and without.
@@
 
-\bibliographystyle{abbrv}
+\bibliographystyle{abbrvnat}
 \bibliography{references}

### 2016-11-10 paper/abstraction/paper.tex
update definitions with changes from discussion w/Dave

@@
 \newcommand{\Con}{\text{con}}
+\newcommand{\Pfx}{\mathit{pfx}}
 
@@
   \[ \begin{array}{rclr}
+     d    &   & & \textit{integer} \\
+     c    &   & & \textit{community} \\
+     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
+     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
+     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
+     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
+     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
      abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
-     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
-     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
-     ma   &::=& lp : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
-     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
-     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
-     c    &   & & \textit{community value} \\
-     lp   &   & & \textit{local preference} \\
+
   \end{array} \]%
@@
      \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
-     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
+     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
      ~~~~~~~~~ l \in internal(G.V), \\
-     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~ rc = \mathit{append}_i~  \\
+     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_i,m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
      ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
      \\
      \text{compile}( p_1, \dots, p_k, G) = \\
-     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G)) \\
+     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
   \end{array} \]%
@@
      \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
-     \Con(l, \Gamma, f)              &=& \Sigma ~ f^{-1}(l) \\
+     \Con(l, \Gamma, f)              &=& \Sigma_i ~ f_i^{-1}(l) \\
      \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
@@
 
-     \Con(pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
-          pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\
+     \Con(\Pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
+          \Pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\
 
@@
 
-         \{ pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~,
-           \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \}  \\
+         \{ \Pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~,
+           \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (\Pfx,l) \in \Gamma(x) \}  \\
 
@@
         & = &
-        \bigcup_i~ \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
+        \mathit{append}_i~ [~ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) ~]
         \\
@@
         \\
-     \Con(pfx \rightarrow {pc},\ell,\Gamma,f,G)
+     \Con(\Pfx \rightarrow {pc},\ell,\Gamma,f,G)
         & = &
-        pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
+        \Pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
         \\
@@
         & = &
-        \{ pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
+        [~ \Pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (\Pfx, l) \in \Gamma(x) ~]
         \\

### 2016-11-10 paper/abstraction/appendix.tex
updating appendix with new definitions

--- 2016-11-08 paper/abstraction/appendix.tex
@@
 
-We define syntax for an abstraction of BGP configurations -- called ABGP -- in Figure~\ref{fig:abgp-syntax}.
-An ABGP policy consists of a map from topology locations $l$ to router configurations $rc$.
-Each router configuration $rc$ is a sequence of prefix (templates) $t$ and their corresponding prefix configuration $pc$.
-A prefix configuration $pc$ is a sequence of match actions $ma$.
-Each match action $ma$ consists of a preference value $n_1$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $n_2$, as well as export neighbors $ns_2$ and the updated community value $n_3$.
+\newcommand{\Con}{\text{con}}
+\newcommand{\Pfx}{\mathit{pfx}}%
 
 \vspace{2em}
-\begin{figure}[h!]\small
+\begin{figure*}[t!]\small%
 
   \hrulefill%
-  \vspace{1em}
-
+
+  \vspace{1em}%
+  \begin{minipage}[t]{.46\linewidth}
+  \hdr{ABGP Syntax}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rclr}
+     d    &   & & \textit{integer} \\
+     c    &   & & \textit{community} \\
+     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
+     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
+     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
+     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
+     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
+     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\%
+  \end{array} \]%%
+
+  \end{minipage}
+  %
+  %
   \begin{minipage}[t]{.5\linewidth}
+  \hdr{Compilation}{}
   \vspace*{-1\baselineskip}
   %
-  \[ \begin{array}{rclr}
-     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
-     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
-     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
-     ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
-     ps   &::=& \{ t_1, ~\dots,~ t_k \} & \textit{predicates} \\
-     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
-  \end{array} \]%
-
-  \end{minipage}
-  %
-  ~~
-  \vrule
-  ~~
-  %
-  \begin{minipage}[t]{.5\linewidth}
-  \vspace*{-1\baselineskip}
-  %
-  \[ \begin{array}{l}
-     \textbf{compile}_\textbf{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
-     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~ l \in internal(V), \\
-     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+  \[ \begin{array}{l}
+     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
+     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~ l \in internal(G.V), \\
+     ~~~~~~~~~ rc = \mathit{append}_i~  \\
+     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_i,m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
      ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
      \\
-     \textbf{compile}( p_1, \dots, p_k ) = \\
-     ~~~~~~ compile_{ABGP}(compile_{PG}(p_1), \dots, compile_{PG}(p_k)) \\
-  \end{array} \]%
-
-  \end{minipage}
-
-  \vspace{1em}
-  \hrulefill%
-  \vspace{1em}
-
-  \caption{BGP syntax and compilation.}
-  \label{fig:abgp-syntax}
-\end{figure}%
-
-\para{Compilation}
-
-Figure~\ref{fig:abgp-syntax} also defines compilation from a \sysname policy to an ABGP policy.
-It starts by compiling separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$, the particular test $t_i$, and the preference ordering $ord_i$.
-
-The function $compile_{ABGP}$ then takes tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy.
-It looks at each incoming neighbor with the same community state $q_n$ and matches any of those neighbor with the preference provided by the ordering $ord$ obtained from the search for local preferences.
-It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.
-
-\vspace{1em}
-
-We assume a particular router $l$ appears at most once in any abgp specification.
-We often build configs using set-builder notation.  For instance,
-$\{l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc)\}$ denotes the abgp policy
-
-\[ \begin{array}{c}
-  l_1 \rightarrow rc_{11},... \\
-  ...           \\
-  l_k \rightarrow rc_{1k},... \\
-\end{array} \]
-
-where $l_1, ..., l_k$ are the nodes in the topology
-and each $rc_{ij}$ satisfies $p(l_i,rc_{ij})$.
-
-\subsection{Concretization}
-
-We define what it means to concretize an abstract \sysname policy. 
-Concretization takes as input, a policy and a context $\Gamma$ mapping from a template prefix to a set of pairs of a concrete prefix and a concrete location where the prefix is owned.
-
+     \text{compile}( p_1, \dots, p_k, G) = \\
+     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
+  \end{array} \]%
+  \end{minipage}%
+
+  \vspace{1em}
+  \vspace{1em}%
+
+  \vspace*{-2\baselineskip}
+  \begin{minipage}[t]{1.01\linewidth}
+  \hdr{Policy Concretization}{}
+  \vspace*{-2\baselineskip}
+  %
   \[ \begin{array}{lcl}
-  con(\emptyset,\Gamma,f)                        & = & \emptyset \\
-  con(l,\Gamma,f)                                & = & \Sigma ~ f^{-1}(l) \\
-  con(r_1 \cup r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cup con(r_2,\Gamma,f) \\
-  con(r_1 \cap r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cap con(r_2,\Gamma,f) \\
-  con(!r,\Gamma,f)                               & = & !con(r,\Gamma,f) \\
-  con(r^*,\Gamma,f)                              & = & con(r,\Gamma,f)^* \\
-  con(pfx \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & pfx \Rightarrow con(r_1,\Gamma,f), \dots, con(r_k,\Gamma,f) \\
-  con(\$x \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & 
-       \{ pfx \Rightarrow con(r_1,\Gamma,f) \cap \text{end}(l), 
-          \dots, 
-          con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \} \\
-  %& & ~~~~~~~~~~~~~~~ \dots, \\
-  %& & ~~~~~~~~~~~~~~~ con(r_k,\Gamma,G) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x),  ~l \in G.V \} \\
-  con(p_1, \dots, p_n, \Gamma, f)                & = & con(p_1,\Gamma,f), \dots, con(p_n,\Gamma,f) \\
-\end{array} \]
-
-For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$.
-For each template variable, we replace it with a new entry for each of its corresponding concrete values under the supplied mapping $\Gamma$.
-We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that traffic is owned by the concrete location $l$.
-\textbf{Note}: we need the side condition that $\text{end}(l) \cap con(r_i,\Gamma) \neq \emptyset$ if $con(r_i,\Gamma) \neq \emptyset$.
-We can also define concretization over the ABGP policy as:
-
+     \\
+     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
+     \Con(l, \Gamma, f)              &=& \Sigma_i ~ f_i^{-1}(l) \\
+     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
+     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
+     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
+     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\%
+     \Con(\Pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
+          \Pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\%
+     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&%
+         [~ \Pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~, \\%
+         & & ~~~~~~~~~~~~~~~ \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (\Pfx,l) \in \Gamma(x) ~]  \\%
+     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\%
+
+  \end{array} \]%
+  \end{minipage}%
+
+  \vspace{1em}
+  \vspace{1em}%
+
+  \begin{minipage}[t]{\linewidth}
+  \hdr{ABGP Concretization}{}
+  \vspace*{-2\baselineskip}
+  %
   \[ \begin{array}{lcl}
-     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G) 
+     \\
+     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G)
         & = &
-        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
+        \mathit{append}_i~ [~ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) ~]
         \\
-     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G) 
+     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
         & = &
-        con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
+        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
         \\
-     con(pfx \rightarrow {pc},\ell,\Gamma,f,G) 
+     \Con(\Pfx \rightarrow {pc},\ell,\Gamma,f,G)
         & = &
-        pfx \rightarrow con(pc,\text{true},\ell,\Gamma,f,G)
+        \Pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
         \\
-     con(\$x \rightarrow {pc},\ell,\Gamma,f,G) 
+     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G)
         & = &
-        \{ pfx \rightarrow con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
+        [~ \Pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (\Pfx, l) \in \Gamma(x) ~]
         \\
-     con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G) 
+     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G)
         & = &
-        con(ma_1,o,\ell,\Gamma,f,G), \dots, con(ma_k,o,\ell,\Gamma,f,G)
+        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
+        \\%
+     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G)
+        & = & \textbf{if}~ ns_1 = \{\text{start}\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
+        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)%
+
         \\
-
-     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
-        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
-        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,f,G),n_3)
-
-        \\
-     con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G) 
+     \Con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G)
         & = &
@@
         \\
-\end{array} \]
-
-We use the symbol $\bullet$ to denote that a particular value in a sequence is removed from the sequence.
+  \end{array} \]%
+  \end{minipage}%
+
+  \vspace{1em}
+  \hrulefill%
+  \vspace{1em}%
+
+  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
+  \label{fig:concretization}
+\end{figure*}%
+
+\para{ABGP language}
+
+We introduct a simple language for BGP configurations called ABGP.
+Figure~\ref{fig:concretization} shows the syntax for an ABGP policy.
+An ABGP policy maps topology locations $l$ to router configurations $rc$.
+Each router configuration $rc$ is a sequence of predicates $t$ and their corresponding configuration $pc$.
+A prefix configuration $pc$ is a sequence of match actions.
+Each match action $ma$ consists of a preference value $d$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $c_1$ expected from those neighbors, as well as export neighbors $ns_2$ and the community value $c_2$ to attach before sending to those neighbors.%
+
+\para{Compilation}
+
+Figure~\ref{fig:concretization} defines compilation from a \sysname policy to an ABGP policy.
+It starts by compiling ($\text{compile}_\text{PG}$) separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$.
+The function $\text{compile}_\text{PG}$ returns the test $t_i$, product graph $PG_i$, and the preference ordering $ord_i$.
+%
+The function $\text{compile}_\text{ABGP}$ then takes a sequence of tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy.
+For each internal router, it looks at each set of neighbor with the same community state $q_n$ and matches any of those neighbors with the preference provided by the ordering $ord$.
+It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.%
+
+We assume a particular router $l$ appears at most once in any abgp specification.
+We build configs using list-comprehension notation. For instance,
+$[~ l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc) ~]$ denotes the abgp policy
+%
+\[ \begin{array}{c}
+  l_1 \rightarrow rc_{1},... \\
+  ...           \\
+  l_k \rightarrow rc_{k},... \\
+\end{array} \]
+
+where $l_1, ..., l_k$ are the nodes in the topology
+and each $rc_{i}$ satisfies $p(l_i,rc_{i})$. We also use the $\mathit{append}$ operator to denote sequence concatenation.%
+
+\subsection{Concretization}
+
+Concretization for a \sysname policy takes as input, the policy and a context
+$\Gamma : Var \rightarrow 2^{Prefix \times V}$,
+which maps from a template prefix to a set of pairs of a concrete prefix and a concrete location that "owns" the prefix.
+%
+For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$.
+For each template variable, we replace it with a new entry for each of its corresponding concrete prefixes under the supplied mapping $\Gamma$.
+We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that this traffic is owned by the concrete location $l$.%
+
+We also define concretization over the ABGP policy in a similar manner.
+We replace each abstract router configuration $l \rightarrow rc$ a new entry for each concrete location $\ell \in f^{-1}(l)$.
+The concrete location $\ell$ is passed as a parameter to $con$ to remember the current router.
+%
+To concretize a prefix policy with a template ($\$x \rightarrow pc$) we replace it with a sequence of policies, one for each prefix in context ($(pfx,l) \in \Gamma(x)$).
+Match action statements where the set of import neighbors is the singleton set containing the product graph start node $\{ start \}$ and we are not currently at looking at the router configuration for the location specified in the context $l$, then we drop the match action.
+This is denoted with the $\bullet$ symbol.
+Finally, to concretize a set of neighbors, we again use $f^{-1}$ to find the set of concrete neighbors under the inverse homomorphism, but then restrict it to those that are actually connected in the underlying concrete topology with $G.E$.
 
@@
 The goal of this section is to prove that the concretization and compilation functions commute: 
-$$con(compile(pol),\Gamma,f,G) = compile(con(pol,\Gamma,f))$$ 
+$$con(compile(pol,G^A),\Gamma,f,G) = compile(con(pol,\Gamma,f), G)$$ 
 That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values on after compilation is complete.
@@
     p \in \Lang(con(l,\Gamma,f)) &\iff& f(p) \in \Lang(l) \\
-    p \in \Lang(\Sigma ~ f^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
-    p \in \bigcup f^{-1}(l) &\iff& f(p) \in \Lang(l) \\
+    p \in \Lang(\Sigma_i ~ f_i^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
+    p \in \bigcup_i f_i^{-1}(l) &\iff& f(p) \in \Lang(l) \\
     p \in f^{-1}(l) &\iff& f(p) \in \{ l \} \\
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A, \\
-     ~~~~~~~~~~~~~~~~~~ in = \bigcup_B~ \{ b \in f^{-1}(B), (b,\ell) \in G.E, (B,q_N) \in \text{adjIn}(PG^A,M) \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \bigcup_C~ \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(M) : (in,q_N) \rightarrow (out,q_M) \} \\
+     ~~~~~~~~~~~~~~~~~~ I = \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(\{b\in f^{-1}(B), (b,\ell) \in G.E, B \in BS\},q_N) ~\vert~ (\_,q_N) \in I, BS=\{B~\vert~ (B,q_N) \in I \} \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG, \\
-     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m) \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) \} \\
+     ~~~~~~~~~~~~~~~~~~ I = \text{adjIn}(PG,m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in I, bs=\{ b ~\vert~ (b,q_N) \in I\} \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%

### 2016-11-10 paper/abstraction/paper.tex
updating appendix with new definitions

--- 2016-11-10 paper/abstraction/paper.tex
@@
 \newcommand{\Con}{\text{con}}
-
-\vspace{2em}
-\begin{figure*}[t!]\small
-
-  \hrulefill%
-  \vspace{1em}
-
-  \begin{minipage}[t]{.46\linewidth}
-  \hdr{ABGP Syntax}{}
-  \vspace*{-1\baselineskip}
-  %
-  \[ \begin{array}{rclr}
-     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
-     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
-     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
-     ma   &::=& lp : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
-     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
-     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
-     c    &   & & \textit{community value} \\
-     lp   &   & & \textit{local preference} \\
-  \end{array} \]%
-
-  \end{minipage}
-  %
-  %
-  \begin{minipage}[t]{.5\linewidth}
-  \hdr{Compilation}{}
-  \vspace*{-1\baselineskip}
-  %
-  \[ \begin{array}{l}
-     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
-     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~ l \in internal(G.V), \\
-     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
-     \\
-     \text{compile}( p_1, \dots, p_k, G) = \\
-     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G)) \\
-  \end{array} \]%
-  \end{minipage}
-
-  \vspace{1em}
-  \vspace{1em}
-
-  \vspace*{-2\baselineskip}
-  \begin{minipage}[t]{\linewidth}
-  \hdr{Policy Concretization}{}
-  \vspace*{-2\baselineskip}
-  %
-  \[ \begin{array}{lcl}
-     \\
-     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
-     \Con(l, \Gamma, f)              &=& \Sigma ~ f^{-1}(l) \\
-     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
-     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
-     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
-     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\
-
-     \Con(pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
-          pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\
-
-     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
-
-         \{ pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~,
-           \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \}  \\
-
-     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\
-
-  \end{array} \]%
-  \end{minipage}
-
-  \vspace{1em}
-  \vspace{1em}
-
-  \begin{minipage}[t]{\linewidth}
-  \hdr{ABGP Concretization}{}
-  \vspace*{-2\baselineskip}
-  %
-  \[ \begin{array}{lcl}
-     \\
-     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G)
-        & = &
-        \bigcup_i~ \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
-        \\
-     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
-        & = &
-        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
-        \\
-     \Con(pfx \rightarrow {pc},\ell,\Gamma,f,G)
-        & = &
-        pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
-        \\
-     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G)
-        & = &
-        \{ pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
-        \\
-     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G)
-        & = &
-        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
-        \\
-
-     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G)
-        & = & \textbf{if}~ ns_1 = \{\text{start}\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
-        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)
-
-        \\
-     \Con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G)
-        & = &
-        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
-        \\
-  \end{array} \]%
-  \end{minipage}
-
-  \vspace{1em}
-  \hrulefill%
-  \vspace{1em}
-
-  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
-  \label{fig:concretization}
-\end{figure*}%
+\newcommand{\Pfx}{\mathit{pfx}}%
+
+%\vspace{2em}
+%\begin{figure*}[t!]\small%
+
+%  \hrulefill%
+%  \vspace{1em}%
+
+%  \begin{minipage}[t]{.46\linewidth}
+%  \hdr{ABGP Syntax}{}
+%  \vspace*{-1\baselineskip}
+%  %
+%  \[ \begin{array}{rclr}
+%     d    &   & & \textit{integer} \\
+%     c    &   & & \textit{community} \\
+%     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
+%     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
+%     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
+%     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
+%     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
+%     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\%
+
+%  \end{array} \]%%
+
+%  \end{minipage}
+%  %
+%  %
+%  \begin{minipage}[t]{.5\linewidth}
+%  \hdr{Compilation}{}
+%  \vspace*{-1\baselineskip}
+%  %
+%  \[ \begin{array}{l}
+%     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
+%     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
+%     ~~~~~~~~~ l \in internal(G.V), \\
+%     ~~~~~~~~~ rc = \mathit{append}_i~  \\
+%     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+%     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
+%     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_i,m), \\
+%     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
+%     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
+%     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
+%     \\
+%     \text{compile}( p_1, \dots, p_k, G) = \\
+%     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
+%  \end{array} \]%
+%  \end{minipage}%
+
+%  \vspace{1em}
+%  \vspace{1em}%
+
+%  \vspace*{-2\baselineskip}
+%  \begin{minipage}[t]{1.01\linewidth}
+%  \hdr{Policy Concretization}{}
+%  \vspace*{-2\baselineskip}
+%  %
+%  \[ \begin{array}{lcl}
+%     \\
+%     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
+%     \Con(l, \Gamma, f)              &=& \Sigma_i ~ f_i^{-1}(l) \\
+%     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
+%     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
+%     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
+%     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\%
+
+%     \Con(\Pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
+%          \Pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\%
+
+%     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&%
+
+%         [~ \Pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~, \\%
+
+%         & & ~~~~~~~~~~~~~~~ \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (\Pfx,l) \in \Gamma(x) ~]  \\%
+
+%     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\%
+
+%  \end{array} \]%
+%  \end{minipage}%
+
+%  \vspace{1em}
+%  \vspace{1em}%
+
+%  \begin{minipage}[t]{\linewidth}
+%  \hdr{ABGP Concretization}{}
+%  \vspace*{-2\baselineskip}
+%  %
+%  \[ \begin{array}{lcl}
+%     \\
+%     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G)
+%        & = &
+%        \mathit{append}_i~ [~ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) ~]
+%        \\
+%     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
+%        & = &
+%        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
+%        \\
+%     \Con(\Pfx \rightarrow {pc},\ell,\Gamma,f,G)
+%        & = &
+%        \Pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
+%        \\
+%     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G)
+%        & = &
+%        [~ \Pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (\Pfx, l) \in \Gamma(x) ~]
+%        \\
+%     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G)
+%        & = &
+%        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
+%        \\%
+
+%     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G)
+%        & = & \textbf{if}~ ns_1 = \{\text{start}\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
+%        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)%
+
+%        \\
+%     \Con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G)
+%        & = &
+%        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
+%        \\
+%  \end{array} \]%
+%  \end{minipage}%
+
+%  \vspace{1em}
+%  \hrulefill%
+%  \vspace{1em}%
+
+%  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
+%  \label{fig:concretization}
+%\end{figure*}%
 
@@
 
-\para{ABGP language}
-
-We introduct a simple language for BGP configurations called ABGP.
+%\para{ABGP language}%
+
+%We introduct a simple language for BGP configurations called ABGP.
 Figure~\ref{fig:concretization} shows the syntax for an ABGP policy.
@@
 A prefix configuration $pc$ is a sequence of match actions.
-Each match action $ma$ consists of a preference value $d_1$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $d_2$ expected from those neighbors, as well as export neighbors $ns_2$ and the community value $d_3$ to attach before sending to those neighbors.
-
-\para{Compilation}
-
-Figure~\ref{fig:concretization} defines compilation from a \sysname policy to an ABGP policy.
+Each match action $ma$ consists of a preference value $d_1$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $d_2$ expected from those neighbors, as well as export neighbors $ns_2$ and the community value $d_3$ to attach before sending to those neighbors.%
+%
+
+%\para{Compilation}%
+
+%Figure~\ref{fig:concretization} defines compilation from a \sysname policy to an ABGP policy.
 It starts by compiling ($\text{compile}_\text{PG}$) separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$.
 The function $\text{compile}_\text{PG}$ returns the test $t_i$, product graph $PG_i$, and the preference ordering $ord_i$.
-%
-The function $\text{compile}_\text{ABGP}$ then takes a sequence of tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy.
+%%
+%The function $\text{compile}_\text{ABGP}$ then takes a sequence of tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy.
 For each internal router, it looks at each set of neighbor with the same community state $q_n$ and matches any of those neighbors with the preference provided by the ordering $ord$.
-It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.
-
-%We assume a particular router $l$ appears at most once in any abgp specification.
-We build configs using set-builder notation.  For instance,
-$\{l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc)\}$ denotes the abgp policy
-%
-\[ \begin{array}{c}
-  l_1 \rightarrow rc_{1},... \\
-  ...           \\
-  l_k \rightarrow rc_{k},... \\
-\end{array} \]
-
-where $l_1, ..., l_k$ are the nodes in the topology
-and each $rc_{i}$ satisfies $p(l_i,rc_{i})$. We also use the $\bigcup$ operator to denote sequence concatenation.
-
-\para{Concretization}
-
-Concretization for a \sysname policy takes as input, the policy and a context
-$\Gamma : Var \rightarrow 2^{Prefix \times V}$,
-which maps from a template prefix to a set of pairs of a concrete prefix and a concrete location that "owns" the prefix.
-%
-For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$.
+It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.%
+
+%%We assume a particular router $l$ appears at most once in any abgp specification.
+%We build configs using set-builder notation.  For instance,
+%$\{l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc)\}$ denotes the abgp policy
+%%
+%\[ \begin{array}{c}
+%  l_1 \rightarrow rc_{1},... \\
+%  ...           \\
+%  l_k \rightarrow rc_{k},... \\
+%\end{array} \]
+
+%where $l_1, ..., l_k$ are the nodes in the topology
+%and each $rc_{i}$ satisfies $p(l_i,rc_{i})$. We also use the $\bigcup$ operator to denote sequence concatenation.%
+
+%\para{Concretization}%
+
+%Concretization for a \sysname policy takes as input, the policy and a context
+%$\Gamma : Var \rightarrow 2^{Prefix \times V}$,
+%which maps from a template prefix to a set of pairs of a concrete prefix and a concrete location that "owns" the prefix.
+%%
+%For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$.
 For each template variable, we replace it with a new entry for each of its corresponding concrete prefixes under the supplied mapping $\Gamma$.
-We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that this traffic is owned by the concrete location $l$.
-
-We also define concretization over the ABGP policy in a similar manner.
+We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that this traffic is owned by the concrete location $l$.%
+
+%We also define concretization over the ABGP policy in a similar manner.
 We replace each abstract router configuration $l \rightarrow rc$ a new entry for each concrete location $\ell \in f^{-1}(l)$.
 The concrete location $\ell$ is passed as a parameter to $con$ to remember the current router.
-%
-To concretize a prefix policy with a template ($\$x \rightarrow pc$) we replace it with a sequence of policies, one for each prefix in context ($(pfx,l) \in \Gamma(x)$).
+%%
+%To concretize a prefix policy with a template ($\$x \rightarrow pc$) we replace it with a sequence of policies, one for each prefix in context ($(pfx,l) \in \Gamma(x)$).
 Match action statements where the set of import neighbors is the singleton set containing the product graph start node $\{ start \}$ and we are not currently at looking at the router configuration for the location specified in the context $l$, then we drop the match action.

### 2016-11-10 paper/abstraction/appendix.tex
update concretization proof with new definitions

@@
 
+\ryan{Update me}
+
 \end{lem}
@@
 \begin{thm}
-  For any $\Gamma$, $f$, $G$ such that $\Gamma$ is well-formed with respect to $G$,
-  $$con(compile(pol),\Gamma,f,G) = compile(con(pol,\Gamma,f))$$
-
+  For any context $\Gamma$, concrete topology $G$, abstract topology $G^A$, homomorphism $f : G \rightarrow G^A$:
+
+  $$con(compile(pol,G^A),\Gamma,f,G) = compile(con(pol,\Gamma,f),G)$$
+
+  \vspace{1em}
   \begin{proof} \text{ }
@@
 
-    Next we compute $compile(con(pol,\Gamma,f))$:
+    Next we compute $compile(con(pol,\Gamma,f), G)$:
 
     \[ \begin{array}{ll}
-        & compile(con(pol,\Gamma,f))  \\
+        & compile(con(pol,\Gamma,f), G)  \\
                           & \\
                          =& compile_{ABGP}( \\
-                          &  ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k} ), \\
+                          &  ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k},G ), \\
                           &  ~~~~ \dots, \\
-                          &  ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk} ), \\
+                          &  ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk},G ), \\
                           &  ~~~~ \dots, \\
-                          &  ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k} ), \\
+                          &  ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k},G ), \\
                           &  ~~~~ \dots, \\
-                          &  ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk} ) \\
+                          &  ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk},G ) \\
                           &  ) \\
@@
     \vspace{1em}
-    Similarly, we can compute $compile(pol)$:
+    Similarly, we can compute $compile(pol, G^A)$:
 
     \[ \begin{array}{ll}
-        & compile(pol)  \\
+        & compile(pol,G^A)  \\
                       & \\
                      =& compile_{ABGP}( \\
-                      & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k} ), \\
+                      & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k}, G^A ), \\
                       & ~~~~ \dots, \\
-                      & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik} ), \\
+                      & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik}, G^A ), \\
                       & ) \\
@@
     \begin{itemize}
-      \item each $PG^A_i$ and $PG_ij$ are related by $f_{pg}$
+      \item each $PG^A_i$ and $PG_{ij}$ are related by $f_{pg}$
+      \vspace{-.2em}
       \item each $ord^A_i$ and $ord_{ij}$ have the property that $ord^A(f_{pg}(m)) = ord_{ij}(m)$
@@
   \[ \begin{array}{l}
-     con(\textbf{compile}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) ), \Gamma,f,G) \\
-  \end{array} \]%
-
-Unfold definition of compile
-
-  \[ \begin{array}{l}
-     ~~~~~ con(\{ l \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~ l \in internal(V^A), \\
-     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     con(\textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) ), \Gamma,f,G) \\
+  \end{array} \]%
+
+Unfold definition of $\text{compile}_\text{ABGP}$
+
+  \[ \begin{array}{l}
+     ~~~~~ con([~ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~ l \in internal(G^A.V), \\
+     ~~~~~~~~~ rc = \mathit{append}_i~  \\
+     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
      ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_n) \rightarrow (out,q_M) \} \}, \Gamma,f,G) \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma,f,G) \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~ \{ \ell \rightarrow con(rc,\ell,\Gamma,f,G)) ~\vert~ \\
+     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
      ~~~~~~~~~ \ell \in f^{-1}(l), \\
-     ~~~~~~~~~ l \in internal(V^A), \\
-     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~ l \in internal(G^A.V), \\
+     ~~~~~~~~~ rc = \mathit{append}_i~  \\
+     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_n) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_n) \in pin \} \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
+  \end{array} \]%
+
+  Rewrite $con$ on $rc$
+
+  \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
+     ~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~ l \in internal(G^A.V), \\
+     ~~~~~~~~~ rc = con(\mathit{append}_i~  \\
+     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
+  \end{array} \]%
+
+  Apply definition of $con$
+
+  \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
+     ~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~ l \in internal(G^A.V), \\
+     ~~~~~~~~~ rc = \mathit{append}_i~  \\
+     ~~~~~~~~~~~~~~~ con([~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
      ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \} \\
-  \end{array} \]%
-
-  Rewrite $con$ on $rc$
-
-  \[ \begin{array}{l}
-     ~~~~~ \{ \ell \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~ \ell \in f^{-1}(l), \\
-     ~~~~~~~~~ l \in internal(V^A), \\
-     ~~~~~~~~~ rc = con(\bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}, \ell,\Gamma,f,G) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
+  \end{array} \]%
+
+  \vspace{1em}
+  \textbf{Case 1}: Assume $t_i = pfx_{i1}$. Look at:
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ con([~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~ \{ \ell \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~ \ell \in f^{-1}(l), \\
-     ~~~~~~~~~ l \in internal(V^A), \\
-     ~~~~~~~~~ rc = \bigcup_i~ con(\{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}, \ell,\Gamma,f,G) \} \\
-  \end{array} \]%
-
-  \vspace{1em}
-  \textbf{Case 1}: Assume $t_i = pfx$. Look at:
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ con(\{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1, \dots, ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
      ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \},\ell,\Gamma,f,G) \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow con(ma_1, \dots, ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1,\text{true},\ell,\Gamma,f,G), \dots, con(ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
      ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow con(ma_1,\text{true},\ell,\Gamma,f,G), \dots, con(ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
      ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \}) \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\text{true},\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
      ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M), \text{true},\ell,\Gamma,f,G) \}) \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M),\ell,\Gamma,f,G) ~] \\
+  \end{array} \]%
+
+  Rewrite on $in$ and $out$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (con(in,\ell,\Gamma,f,G),q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
+     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
+  \end{array} \]%
+
+  Rewrite $con$ on $in$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=con(\{B ~\vert~ (B,q_N) \in pin \},\ell,\Gamma,f,G) \} \\
+     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \} \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{c~\vert~ c \in f^{-1}(C),~ (c,\ell) \in G.E,~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
+  \end{array} \]%
+
+  From the relation between concrete ($PG$) and abstract ($PG^A$) product graphs given by the previous lemma
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
+  \end{array} \]%
+
+  Since $ord^A_i(f_{pg}(m)) = ord_{i1}(m)$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord_{i1}(m) : (in,q_N) \rightarrow (out,q_M) ~] \\
+  \end{array} \]%
+
+  Since product graphs have equivalent states
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
+  \end{array} \]%
+
+  \vspace{1em}
+  \textbf{Case 2}: Assume $t_i = \$x$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ con([~ \$x \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
      ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M) \} \\
-  \end{array} \]%
-
-  Rewrite on $in$ and $out$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = con(\{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \},\ell,\Gamma,f,G) \\
-     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G) \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
+  \end{array} \]%
+
+  Apply the definition of $con$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ [~ \Pfx_{ij} \rightarrow con(ma_1, \dots, ma_k,\ell,\Gamma,f,G) ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
+  \end{array} \]%
+
+  Apply definition $con$
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ [~ \Pfx_{ij} \rightarrow con(ma_1,\ell,\Gamma,f,G), \dots, \\ 
+     ~~~~~~~~~~~~~~~~~~~~~~~~~~ con(ma_k,\ell,\Gamma,f,G) ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
+  \end{array} \]%
+
+  Rewrite $con$ on $ma_h$.
+
+  \[ \begin{array}{l}
+     ~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\ 
+     ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),l_{ij},\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \bigcup_B~ \{ b \in f^{-1}(B), (b,\ell) \in G.E, (B,q_N) \in \text{adjIn}(PG^A_i,M) \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \bigcup_C~ \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
-  \end{array} \]%
-
-  From the relation between concrete ($PG$) and abstract ($PG^A$) product graphs given by the previous lemma
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG_{i1},m) \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) \} \\
-  \end{array} \]%
-
-  Since $ord^A_i(f_{pg}(m)) = ord_{i1}(m)$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG_{i1},m) \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_N) \rightarrow (out,q_M) \} \\
-  \end{array} \]%
-
-  Since product graphs have equivalent states
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{i1},m) \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
-  \end{array} \]%
-
-  \vspace{1em}
-  \textbf{Case 2}: Assume $t_i = \$x$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ con(\{ \$x \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
+     ~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\ 
+     ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
      ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \},\ell,\Gamma,f,G) \\
-  \end{array} \]%
-
-  Apply the definition of $con$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx_{ij} \rightarrow con(ma_1, \dots, ma_k,l_{ij} = \ell,\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
-  \end{array} \]%
-
-  Apply definition $con$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx_{ij} \rightarrow con(ma_1,l_{ij} = \ell,\ell,\Gamma,f,G), \dots, \\ 
-     ~~~~~~~~~~~~~~~~~~~~~~~~~~~ con(ma_k,l_{ij} = \ell,\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) \} \\
-  \end{array} \]%
-
-  Rewrite $con$ on $ma_h$.
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),l_{ij} = \ell,\ell,\Gamma,f,G) \} \\
-  \end{array} \]%
-
-  Apply definition of $con$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ B ~\vert~ (B,q_N) \in \text{adjIn}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = \textbf{if}~ in=\{ G.s \} \text{ and } l_{ij} \neq \ell ~\textbf{then}~ \bullet \\ 
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = \textbf{if}~ in=\{ G.s \} \text{ and } l_{ij} \neq \ell ~\textbf{then}~ \bullet \\ 
      ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else}~ ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M) \} \\
@@
   \textbf{Observation}: 
-  By filtering the cases where $in = \{ G.s \}$ and $l_{ij} \neq \ell$ we get the same thing as before after applying the definition of $con$, however for each $(pfx_{ij}, l_{ij}) \in \Gamma(x)$.
-
- \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+  By filtering the cases where $in = \{ \mathit{start} \}$ and $l_{ij} \neq \ell$ we get the same thing as before after applying the definition of $con$ for each $(pfx_{ij}, l_{ij}) \in \Gamma(x)$.
+
+ \[ \begin{array}{l}
+     ~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
      ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{ij},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{ij},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}) \\
      ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
   \end{array} \]%
@@
   This works because each $PG_{ij}$ was constructed from $con(r_{ijk}) \cap end(l_{ij})$.
-This means that the only state in $PG_{ij}$ connected to the start node $G.s$ is a node for $l_{ij}$.
+This means that the only state in $PG_{ij}$ connected to the start node ($\mathit{start}$) is a node for $l_{ij}$.
 This was ensured by the fact that the transition function for each regular expression $\sigma_{ijk}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{ij} \}$ from the construction of the automata.
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{i1},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}) \\
      ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
   \end{array} \]%
@@
  \[ \begin{array}{l}
-     ~~~~~~~~~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
      ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{ij},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{ij},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}) \\
      ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~ \{ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
      ~~~~~~~~~ \ell \in f^{-1}(l), \\
-     ~~~~~~~~~ l \in internal(V^A), \\
-     ~~~~~~~~~ rc = \bigcup_{ij}~ \{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~ l \in internal(G^A.V), \\
+     ~~~~~~~~~ rc = \mathit{append}_{ij}~  \\
+     ~~~~~~~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{ij},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{ij},m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
      ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~ l \in internal(V), \\
-     ~~~~~~~~~ rc = \bigcup_{ij}~ con(\{ pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~ l \in internal(G.V), \\
+     ~~~~~~~~~ rc = \mathit{append}_{ij}~  \\
+     ~~~~~~~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_{ij},m) \}) \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{ij},m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
      ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) \} \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     = \textbf{compile}( (pfx_{11},PG_{11},ord_{11}), \dots, (pfx_{ij},PG_{ij},ord_{ij}) ) \\
+     = \textbf{compile}_\textbf{ABGP}( (pfx_{11},PG_{11},ord_{11}), \dots, (pfx_{ij},PG_{ij},ord_{ij}) ) \\
   \end{array} \]%

### 2016-11-10 paper/abstraction/paper.tex
update concretization proof with new definitions

@@
 Notably, the abstract analysis takes the majority of the time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost.
-In particular, the number of calls to Z3 remains constant the across topology size.
-The seesaw behavior for the data center networks results from differences in time taken by Z3 to minimize the same constraints with different parameters.
+In particular, the number of calls to $\nu$Z remains constant the across topology size.
+The seesaw behavior for the data center networks results from differences in time taken by $\nu$Z to minimize the same constraints with different parameters.
 

### 2016-11-11 paper/abstraction/appendix.tex
update proof with better syntax

@@
      ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_i,m), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
      \\
@@
      ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A, \\
-     ~~~~~~~~~~~~~~~~~~ I = \text{adjIn}(PG^A,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(\{b\in f^{-1}(B), (b,\ell) \in G.E, B \in BS\},q_N) ~\vert~ (\_,q_N) \in I, BS=\{B~\vert~ (B,q_N) \in I \} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ I = \mathit{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(BS,q_N) ~\vert~ (\_,q_N) \in I, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in I \} \}) \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \mathit{adjOut}(PG^A,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in I, bs=\{ b ~\vert~ (b,q_N) \in I\} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \mathit{adjOut}(PG,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
 For each concrete node $n$ such that $n = (b,q_n) \in adjIn(PG,m)$ we know that if $f_{pg}(n) = N$ where $N = (f(b),q_N)$, then $N \in adjIn(PG^A,M)$ and $q_n = q_N$ from the homomorphism.
-Thus by taking $\bigcup f^{-1}(f(b))$, for each such $f(b)$ for node $N$ that shares the same state $q_N$, we get a superset of the locations from the concrete graph.
+Thus by taking $f^{-1}(B) = f^{-1}(f(b))$, for each such $f(b)$ for node $N$ that shares the same state $q_N$, we get a superset of the locations from the concrete graph.
 However, by restricting those locations to only those that appear in the topology $(b,\ell)$, we get exactly the set that appears in the concrete product graph.
-This is because we know $q_n \rightarrow q_m$ from the abstract product graph is a valid transition and the topology edge exists.
+    This is because we know $q_N \rightarrow q_M$ from the abstract product graph is a valid transition, which means that $q_n \rightarrow q_m$ is a valid concrete product graph transition, and if there is a topology edge $(b,\ell)$, then there must be a product graph edge $(n,m)$.
+Therefore:
+    $$\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \}$$
+    is equivalent to
+    $$\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\}$$
+    This also holds for the case with adjOut.
+Further, note that because we are looking at a particular location $l$, there can only be at most one such $m = (l,q_N)$ such that $f_{pg}(m) = M = (f(l), q_N)$.
+If there is no such $m$ where $f_{pg}(m) = M$, then the above expression will produce the empty set after filtering with the topology.
+Going over each $M$ then is equivalent to going over each $m$ so long as we throw away imports $\mathit{out}$ that are empty.
+
   \end{proof}
@@
      ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma,f,G) \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma,f,G) \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_n) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_n) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~ con([~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ con([~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1, \dots, ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1,\text{true},\ell,\Gamma,f,G), \dots, con(ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\text{true},\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\text{true},\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M),\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M),\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (con(in,\ell,\Gamma,f,G),q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (con(in,\ell,\Gamma,f,G),q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=con(\{B ~\vert~ (B,q_N) \in pin \},\ell,\Gamma,f,G) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=con(\{B ~\vert~ (B,q_N) \in pin \},\ell,\Gamma,f,G) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset,
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{c~\vert~ c \in f^{-1}(C),~ (c,\ell) \in G.E,~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{c~\vert~ c \in f^{-1}(C),~ (c,\ell) \in G.E,~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_M) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{i1},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}), \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord_{i1}(m) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_M) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{i1},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}), \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
+     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{i1},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}), \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ con([~ \$x \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),l_{ij},\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),l_{ij},\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = \textbf{if}~ in=\{ G.s \} \text{ and } l_{ij} \neq \ell ~\textbf{then}~ \bullet \\ 
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = \textbf{if}~ in=\{ G.s \} \text{ and } l_{ij} \neq \ell ~\textbf{then}~ \bullet \\ 
      ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else}~ ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M) \} \\
@@
      ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{ij},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
+     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{ij}, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{ij},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}), \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{ij},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
+     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{ij}, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{ij},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}), \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{ij},m), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{ij}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{ij},m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
   \end{array} \]%

### 2016-11-11 paper/abstraction/appendix.tex
update proof

--- 2016-11-10 paper/abstraction/appendix.tex
@@
      ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_i,m), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
      \\
@@
      ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A, \\
-     ~~~~~~~~~~~~~~~~~~ I = \text{adjIn}(PG^A,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(\{b\in f^{-1}(B), (b,\ell) \in G.E, B \in BS\},q_N) ~\vert~ (\_,q_N) \in I, BS=\{B~\vert~ (B,q_N) \in I \} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A,M) \} \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~ pin = \mathit{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \} \}), \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \mathit{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
      ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
@@
      ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG, \\
-     ~~~~~~~~~~~~~~~~~~ I = \text{adjIn}(PG,m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in I, bs=\{ b ~\vert~ (b,q_N) \in I\} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \} \\
+     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_M) \in PG, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in I, bs=\{ b ~\vert~ (b,q_N) \in pin\} \}), \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathit{adjOut}(PG,m) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
      ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
@@
 For each concrete node $n$ such that $n = (b,q_n) \in adjIn(PG,m)$ we know that if $f_{pg}(n) = N$ where $N = (f(b),q_N)$, then $N \in adjIn(PG^A,M)$ and $q_n = q_N$ from the homomorphism.
-Thus by taking $\bigcup f^{-1}(f(b))$, for each such $f(b)$ for node $N$ that shares the same state $q_N$, we get a superset of the locations from the concrete graph.
+Thus by taking $f^{-1}(B) = f^{-1}(f(b))$, for each such $f(b)$ for node $N$ that shares the same state $q_N$, we get a superset of the locations from the concrete graph.
 However, by restricting those locations to only those that appear in the topology $(b,\ell)$, we get exactly the set that appears in the concrete product graph.
-This is because we know $q_n \rightarrow q_m$ from the abstract product graph is a valid transition and the topology edge exists.
+    This is because we know $q_N \rightarrow q_M$ from the abstract product graph is a valid transition, which means that $q_n \rightarrow q_m$ is a valid concrete product graph transition, and if there is a topology edge $(b,\ell)$, then there must be a product graph edge $(n,m)$.
+Therefore:
+    $$\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \}$$
+    is equivalent to
+    $$\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\}$$
+    This also holds for the case with adjOut.
+Further, note that because we are looking at a particular location $l$, there can only be at most one such $m = (l,q_N)$ such that $f_{pg}(m) = M = (f(l), q_N)$.
+If there is no such $m$ where $f_{pg}(m) = M$, then the above expression will produce the empty set after filtering with the topology.
+Going over each $M$ then is equivalent to going over each $m$ so long as we throw away imports $\mathit{in}$ that are empty.
+
   \end{proof}
 
-\ryan{Update me}
-
 \end{lem}
 
-\vspace{2em}
 \begin{thm}
@@
 
-  \vspace{1em}
   \begin{proof} \text{ }
@@
      ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma,f,G) \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma,f,G) \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_n) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_n) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~ con([~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ con([~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1, \dots, ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1,\text{true},\ell,\Gamma,f,G), \dots, con(ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\text{true},\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\text{true},\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M),\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M),\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (con(in,\ell,\Gamma,f,G),q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (con(in,\ell,\Gamma,f,G),q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=con(\{B ~\vert~ (B,q_N) \in pin \},\ell,\Gamma,f,G) \} \\
-     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=con(\{B ~\vert~ (B,q_N) \in pin \},\ell,\Gamma,f,G) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{c~\vert~ c \in f^{-1}(C),~ (c,\ell) \in G.E,~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{c~\vert~ c \in f^{-1}(C),~ (c,\ell) \in G.E,~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_M) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{i1},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}), \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord_{i1}(m) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_M) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{i1},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}), \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{i1},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
+     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{i1}, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{i1},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}), \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~ con([~ \$x \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),l_{ij},\ell,\Gamma,f,G) ~] \\
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),l_{ij},\ell,\Gamma,f,G) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = \textbf{if}~ in=\{ G.s \} \text{ and } l_{ij} \neq \ell ~\textbf{then}~ \bullet \\ 
+     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = \textbf{if}~ in=\{ G.s \} \text{ and } l_{ij} \neq \ell ~\textbf{then}~ \bullet \\ 
      ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else}~ ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M) \} \\
@@
      ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{ij},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
+     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{ij}, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{ij},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}), \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{ij},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}) \\
-     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
-     ~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
+     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{ij}, \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{ij},m), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}), \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \}, \\
+     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
   \end{array} \]%
@@
      ~~~~~~~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_{ij},m), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \} \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_n} = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{ij}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{ij},m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
   \end{array} \]%

### 2016-11-11 paper/abstraction/paper.tex
update examples for consistency

@@
   \[ \begin{array}{rclr}
-     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
-     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
-     t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \textit{template variable} \\
-     r       &::=& l & \textit{location} \\
-         &\BNFALT& \emptyset & \textit{empty set} \\
-         &\BNFALT& \In & \textit{internal loc} \\
-         &\BNFALT& \Out & \textit{external loc} \\
-         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
-         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
-         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
-         &\BNFALT& \NOT r & \textit{path negation} \\
-         &\BNFALT& r^* & \textit{iteration} \\
+     pol     &::=& p_1, \dots, p_n & \textit{policy} \\
+     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{path preferences} \\
+     t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \textit{predicate} \\
+     r       &::=& l \BNFALT \emptyset \BNFALT \In \BNFALT \Out \BNFALT r_1 \cup r_2 \BNFALT & \textit{regular path} \\
+             &   & r_1 \cap r_2 \BNFALT r_1 \cdot r_2 \BNFALT \NOT r \BNFALT r^* \\
+%         &\BNFALT& \emptyset & \textit{empty set} \\
+%         &\BNFALT& \In & \textit{internal loc} \\
+%         &\BNFALT& \Out & \textit{external loc} \\
+%         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
+%         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
+%         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
+%         &\BNFALT& \NOT r & \textit{path negation} \\
+%         &\BNFALT& r^* & \textit{iteration} \\
   \end{array} \]%
@@
   \end{minipage}
-  \vspace{1em}
+  \vspace{-.3em}
   \caption{Simplified \sysname syntax.}

### 2016-11-11 paper/abstraction/paper.tex
edits
working through section 4

@@
 \usepackage{textcomp}
+\usepackage{enumitem}
 \usepackage{pifont}
@@
 
-To summarize, the central contributions of this paper are:
-
-\begin{enumerate}
+\vspace{1em}
+\noindent
+\textbf{Contributions}: To summarize, the contributions are:
+%
+\begin{itemize}[noitemsep,nolistsep,label={\large\textbullet}]
 \item Design of new topology abstractions for network programming
@@
 than its closest competitor on large networks.
-\end{enumerate}
+\end{itemize}
 
@@
 It outputs a template for each role, from which per-device configurations can be generated by instantiating parameters with values drawn from the network topology.
-It guarantees that:
-(1) the configurations generated from its templates correctly implement the network's policy for {\em any} concrete topology that matches the abstract topology; and (2) if nodes or edges are added or removed in a way compatible
-with the abstract topology, only configurations of adjacent devices ever need to be updated.
-
-This section introduces \sysname using the examples in \S\ref{sec:motivation}, and the following sections detail template generation and formally define the correctness guarantees.
-
-%As we have seen, writing correct network configurations is challenging task.
-Operators must manually decompose network-wide policies into distributed device configurations, reason about all combinations of network failures, and parameterize configurations to allow for change, ideally in a way that is amenable to incremental change.
-In this section, we give an overview of the \sysname system, which gives operators a principled way to accomplish all of these tasks.
-
-%\subsection{Concrete Methane}%
-
-%Consider again the datacenter from figure~\ref{fig:example}. To configure the datacenter routing
-%policy, we would start by writing the following definition in \sysname:
-%%
-%\begin{code}
-%\Define Routing =
-%    \{P1 \Path \End(T1)
-%     P2 \Path \End(T2)
-%     P3 \Path \End(T3)
-%     P4 \Path \End(T4)
-%     P5 \Path \End(T5)
-%     P6 \Path \End(T6)
-%     P7 \Path \End(T7)
-%     P8 \Path \End(T8)
-%     \True \Path \Exit(Peer1 \Prefer Peer2) \}
-%\end{code}
-%\noindent%%
-
-%This defines a group of constraints for basic routing behavior. The first line states
-%that traffic destined for prefix $P1$ must follow a path that ends up at destination router $T1$.
-%A similar constraint is added for each of the prefixes P[2-8]. The final rule matches all other
-%prefix destinations and allows traffic to follow a path that leaves the datacenter through either
-%of its peers (Peer1 or Peer2) with a preference for leaving through Peer1. The \Prefer symbol indicates
-%that traffic should satisfy the constraint on the left whenever possible, and only resort to the backup (right)
-%when this is not possible due to failures.%
-
-%Next we can add the locality constraint for prefixes P[5-8]. We do this by adding another group of constraints:
-%%
-%\begin{code}
-%\Define Locality =
-%    \{P5 | P6 | P7 | P8 \Path \Always(\In)\}
-%\end{code}
-%\noindent%%
-
-%The Locality constraint applies to any traffic destined for a local prefix and adds
-%the constraint that the traffic must follow a path that matches an internal location
-%(\IE, a router inside the datacenter) at each hop of the path. This prevents traffic
-%from ever entering from or leaving through an external peer.%
-
-%Finally, for all traffic in the datacenter, we will disallow valley routing. This constraint
-%can be captured with the following additions to the policy:
-%%
-%\begin{code}
-%\Define Tor = \{T1,T2,T3,T4,T5,T6,T7,T8\}
-%\Define Agg = \{A1,A2,A3,A4,A5,A6,A7,A8\}
-%\Define Spn = \{S1,S2\}
-%\Define ValleyFree =
-%    \{\True \Path \Novalley(Tor,Agg,Spn)\}
-%\end{code}
-%\noindent%%
-
-%The first three lines define groups of routers. The top of rack (Tor) routers T[1-8], the
-%aggregation routers (Agg) A[1-8], and the spine routers (Spn) S[1-2]. The next line
-%adds a new constraint that applies to all traffic and ensures that traffic never follows a
-%path that forms a valley between any of these three groups (\EG, going from Spn to Agg to Spn again).
-%As we will see in section \ryan{reference}, each of these constraints such as the valley free constraint
-%are really just syntactic sugar for regular expressions over topology locations.%
-
-%The final policy is declared to as the conjunction of each of these constraints:
-%%
-%\begin{code}
-%\Define Main =
-%    Routing &
-%    Locality &
-%    ValleyFree &
-%    \Agg(PG, \In -> \Out)
-%\end{code}
-%\noindent%
-%The last part of the policy declares that we want to perform aggregation for global prefixes
-%by summarizing them into the more general prefix PG at the border of the datacenter
-%(\IE along any edge starting inside our datacenter and ending outside).%
-
-%From this policy, \sysname can synthesize device-level BGP configurations for every router in
-%the network that guarantee correct forwarding behavior under all possible failure combinations.
-%Synthesizing configurations for each device from a network-wide specification both simplifies
-%network configuration by writing policy in one place rather than dozens and simultaneously prevents
-%a large class of errors associated with manual configuration by construction. For example,
-%the compiler ensures configurations are always in sync and prevents the operator from having
-%to manually consider failure scenarios.
+%It guarantees that:
+%(1) the configurations generated from its templates correctly implement the network's policy for {\em any} concrete topology that matches the abstract topology; and (2) if nodes or edges are added or removed in a way compatible
+%with the abstract topology, only configurations of devices adjacent to the change ever need to be updated.
+%
+%This section introduces \sysname using the examples in \S\ref{sec:motivation}.
+%, and the following sections detail template generation and formally define the correctness guarantees.
+%
+When \sysname compiles a policy, it guarantees that the forwarding behavior of the network will be correct for any concrete instantiation of the abstract network, and for any combination of failures that may occur in the concrete network.
+Furthermore, \sysname will generate configurations in such a way that, if an operator expands their network in a way compatible with the abstraction, then only configurations of devices adjacent to the change ever need to be updated.
 
@@
 \sysname takes as input the network's abstract topology and its policy.
-The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous failures a the network can withstand without loosing connectivity.
+The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous failures the network can withstand without loosing connectivity.
 
 \para{Abstract topology}
-Abstract topologies in \sysname capture the basic connectivity structure of the network, which holds when the network is originally designed and as it evolves.
-They are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
+Abstract topologies in \sysname capture connectivity invariants of the network that hold both when network is first instantiated and as it evolves.
+These invariantes are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
+%
 We designed these abstractions to be able to precisely capture most real network topologies, while being amenable to the fault tolerance analysis and configuration synthesis that is done by our compiler.
@@
 
-We introduce our topology abstractions using the networks from \S\ref{sec:motivation}.
+We introduce our topology abstractions using the networks from \S\ref{sec:motivation}. Topology abstractions consist of several components.
 The first is a role-based abstraction that allows an operator to map routers in the concrete network to roles in the abstract network.
@@
 A role-based abstraction is a graph homomorphism from $G$ to an abstract graph $G^A$ = ($V^A$,$E^A$).
-A graph homorphism $f : G \rightarrow G^A$ is a function that maps each node in the concrete graph to a node in the abstract graph such that, whenever $(u,v) \in E$, then $(f(u),f(v)) \in E^A$.
+A graph homorphism $f : G \rightarrow G^A$ maps each node in the concrete graph to a node in the abstract graph such that, whenever $(u,v) \in E$, then $(f(u),f(v)) \in E^A$.
 
@@
 The role-based abstraction therefore overapproximates the connectivity of the underlying concrete graphs.
-Unfortunately, by itself, this abstraction loses a lot of information about the underlying structure of the concrete network, which would hinder a useful analysis of its fault-tolerance.
+On its own, this abstraction loses a lot of information about the underlying structure of the concrete network, making it difficult to reason precisely about fault-tolerance.
+%which would hinder a useful analysis of its fault-tolerance. 
 For example, with this abstraction any spine router in a concrete network may or may not be connected to any aggregator router.
@@
 In order to refine the abstraction to capture more precisely the kinds of concrete networks of interest,
-we introduce a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
-with a symbolic variable (\EG, $e1, e2, \ldots$) that denotes a constraint on the number of nodes/edges
-that may appear in any given concrete network. Operators can then capture concrete network invariants by adding constraints on the symbolic variables using logical formula.
-
-For example, in Figure~\ref{fig:example3}, the first two constraints: $e1 = AG$ and $e2 = TG$ declare that, within any pod P, the number of outgoing edges from $TG$ to $AG$ is equal to the number of nodes that map to $AG$.
-Similarly, the number of outgoing edges from $AG$ to $TG$ is equal to the number of nodes that map to $TG$.
+we introduce several additional concepts.
+The first is the idea of topology hierarchy captured by P and Q, which say that nodes in the tor and aggregator roles are grouped into a number of smaller pods.
+The second is a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
+with a symbolic variable (\EG, $e1, e2, \ldots$) that denotes a constraint on the number of edges (and nodes) that may appear in any given concrete network.
+Operators can capture concrete network invariants by adding constraints on the symbolic variables using logical formula.
+
+For example, in Figure~\ref{fig:example3}, the first two constraints: $e1 = AG$ and $e2 = TG$ say that, within any pod P, the number of outgoing edges from a node in the $TG$ role to a node in the $AG$ role is equal to the number of nodes in the $AG$.
+Similarly, the number of outgoing edges from $AG$ to $TG$ is equal to the number of nodes in the $TG$ role.
 These constraints capture the fact that, within any given pod, the global aggregators and ToRs are in a full mesh.
-Furthermore, the constraints $TG = AG$ and $TG \geq 2$ ensure that the number of concrete nodes in role $TG$ is always equal to the number of concrete nodes in role $AG$, which is at least 2.
-Similar constraints also appear for the local aggregators and ToRs.
+Furthermore, the constraints $AG = AL$ and $AG \leq S$ ensure that, within pods P and Q, the $AG$ and $TG$ roles have the same number of routers, which is less than the number of routers in the spine role $S$.
 %
@@
 Symmetrically, the constraint $e4 \geq 1$ says that, for each pod P, each node in the spine role has at least one outgoing edge to a node in the $AG$ role.
-Again, similar constraints appear for the local aggregator role.
-Finally, the constraints $S \geq 2$, $(S \mod AG) = 0$, and $(S \mod AL) = 0$ ensure that there are at least 2 routers in the spine role, and that the number of spine routers is always divisible by the number of global and local aggregators.
-%
-The last two constraints are interesting in that they do not involve a simple inequality.
+Similar constraints appear for the local aggregator role.
+The constraint $2 \leq S \leq 4$ makes explicit the possibility for growth, for example by growing the network from that of Figure~\ref{fig:example} to that of Figure~\ref{fig:example2}.
+In general, we need not bound the number of spine routers to admit more concrete topologies at the expense of analysis precision.
+Finally, we include the constraints $(S \mod AG) = 0$, and $(S \mod AL) = 0$ simply to show that constraints do not have to inequalities.
 In general operators can write constraints using logical formula for any theory supported by modern SMT solvers.
+
+\ryan{mention mincut}
 
@@
 
-\para{Routing policy} Routing policies in \sysname consist of mappings from predicates matching various classes of traffic to a list of ranked constraints on the paths that the traffic matching the predicate should prefer to take through the network.
-We borrow syntax from Propane~\cite{propane} but, instead of concrete prefixes and nodes, \sysname specifications use abstract prefixes and nodes.
-
-Let us see how to configure each of the datacenter networks from \S\ref{sec:motivation} by writing a \sysname routing policy over the new abstract topology.
-We can capture the basic routing behavior for the datacenters with the following constraints:
+\para{Routing policy} Routing policies in \sysname consist of an ordered sequence of both a predicate matching various classes of traffic and a list of ranked constraints on the paths that the traffic matching the predicate should prefer to take through the network.
+We borrow syntax from Propane~\cite{propane} but, instead of concrete prefixes and nodes, \sysname specifications can use abstract prefixes and nodes.
+
+Let us see how to configure each of the datacenter networks from \S\ref{sec:motivation} by writing a \sysname routing policy over the abstract topology.
+We can capture the basic routing behavior for the datacenters with the following policy:
 %
@@
     \$LP  \Path \End(TL)
-    \True \Path \Exit(Peer1 \Prefer Peer2)
+    \True \Path \End(\Out) & \Exit(P1 \Prefer P2)
 \end{code}
@@
 The first line introduces a prefix \emph{template} variable.
-It says that traffic for each global prefix associated with the template variable \$GP has the constraint that it should follow a path that ends at its corresponding destination router contained in the abstract TG role.
-The second line does the same thing for all local prefixes.
-%
-The final rule matches all other IP prefix destinations and allows traffic to follow a path that leaves the datacenter through either of its peers (Peer1 or Peer2) with a preference for leaving through Peer1.
-The \Prefer~symbol indicates that traffic should satisfy the constraint on the left whenever possible (\IE, a path exists in the network), and only resort to the backup (right) when this is not possible due to failures.%
+It says that traffic for each global prefix associated with the template variable $\CD{\$GP}$ has the constraint that it should follow a path that ends at its corresponding destination router contained in the $\CD{TG}$ role.
+The second line does the same for all local prefixes.
+%
+The final rule matches all other IP prefix destinations and allows traffic to follow a path that leaves the datacenter, ending up at some outside location, through either of its peers $\CD{P1}$ or $\CD{P2}$ with a preference for leaving through $\CD{P1}$ over $\CD{P2}$.
+The $\CD{\Prefer}$~symbol indicates that traffic should satisfy the constraint on the left whenever possible (\IE, a path exists in the network), and only resort to the backup (right) when this is not possible due to network failures.%
 
 Next we can capture the constraint that traffic for local prefixes must stay local to the datacenter.
-We do this with the following \sysname constraint:
+This is written as the following \sysname constraint:
 %
 \begin{code}
-\Define Locality =
+\Define Local =
     \$LP \Path \Always(\In)
@@
 %
-The Locality constraint applies to any traffic destined for a local prefix described by the \$LP prefix template variable and adds the constraint that the traffic must follow a path that matches an internal location (\IE, a router inside the datacenter) at each hop of the path.
+The Local constraint applies to any traffic destined for a local prefix described by the \$LP prefix template variable and adds the constraint that the traffic must follow a path that matches an internal location (\IE, a router inside the datacenter) at each hop of the path.
 This prevents traffic from ever entering from or leaving through an external peer.
-Finally, we can combine these constraints together as follows:
-
+
+It is also common practice to prevent peers (\EG, $\CD{P1}$ and $\CD{P2}$) from communicating by sending data through the datacenter. Such a constraint can be added to \sysname in the following way:
+%
 \begin{code}
-Routing & Locality & \Agg(PG, \In -> \Out)
+\Define Peer = \{P1,P2\}
+\Define BlockPeers =
+    \True \Path !(\Enter(Peer) & \Exit(Peer))
 \end{code}
 \noindent%
-
-\ryan{we may need to add notransit constraint to make the compilation section simpler}
-
-This tells \sysname to find BGP router configurations that satisfy the conjunction of the Routing and Locality constraints.
+%
+We define a $\CD{Peer}$ to be either $\CD{P1}$ or $\CD{P2}$ and disallow paths where traffic both enters the datacenter through a peer and exits through a peer.
+Finally, we can combine these constraints together as follows:
+
+\begin{code}
+Routing & Local & BlockPeers & \Agg(PG, \In -> \Out)
+\end{code}
+\noindent%
+
+This tells \sysname to find BGP router configurations that satisfy the conjunction of the Routing and Local constraints.
 It also declares an additional constraint that we want to perform prefix summarization (as PG) for global prefixes at the border of the datacenter (\IE, along any edge starting inside our datacenter and ending at a peer outside the datacenter).
-
-When \sysname compiles the above policy, it guarantees that the forwarding behavior of the network will be correct for any concrete instantiation of the abstract network, and for any combination of failures that may occur in the concrete network.
-Furthermore, \sysname will generate configurations in such a way that, if we want to expand our network, for example by adding or removing a spine routers as in figure~\ref{fig:example2}, then the expansion can be performed by only ever touching device configurations that are adjacent to the change.
 
@@
 
-%For example, the combining the Routing and Locality constraints in the data center policy from \S\ref{sec:overview} would result in the following \sysname policy:
+%For example, the combining the Routing and Local constraints in the data center policy from \S\ref{sec:overview} would result in the following \sysname policy:
 %
@@
 In the template configuration, it matches any global prefix from any internal peer and re-advertise the route to all of its peers.
-For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers (thus implementing the Locality constraint).
+For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers (thus implementing the Local constraint).
 The concrete configurations have a similar configuration for each local and global prefix.

### 2016-11-11 paper/abstraction/paper.tex
related work

@@
 
-\begin{easylist}[itemize]
-& Topologies: DCell, BCube, Fattree, ...
-& Topology Abstraction: Condor
-& Memory Shape Analysis: Sagiv, others
-& Configuration automation
-& Configuration analysis
-& Configuration synthesis
-\end{easylist}
-
-%Our work draws on four threads of prior work.%
-
-%\para{Topology abstraction}%
-
-%\para{Topology design}%
-
-%\para{Configuration automation}
-%Many practitioners use configuration templates~\cite{hatch,thwack}, to ensure certain kinds of consistency across similar devices.
-In addition, configuration languages such as RPSL~\cite{RFC2622}, Yang~\cite{RFC6020}, and Netconf~\cite{RFC6241} allow operators to express routing policy in a vendor-neutral way.
-%However, all of these solutions remain low-level, for example, requiring operators to specify exact local preferences.
-Unlike \sysname, there is no guarantee that these low-level configurations satisfy the original, high-level intent.%
-
-%\para{Configuration analysis}
-%The notion that configuring network devices is difficult and error-prone is not new.
-%In the past, researchers have tried to tackle this problem by analyzing existing
-%router configurations~\cite{feamster+:rcc,ipassure,batfish,bagpipe,arc} and reporting errors or inconsistencies when they are detected.
-%Our research is complementary to these analysis
-%efforts.  We hope to eliminate bugs by using higher-level
-%languages and a ``correct-by-construction''
-%methodology. Writing configurations at a high level of abstraction simplifies policy implementation and prevents a whole host of low-level errors.%
+Our work is related to four threads of prior work.
+
+\para{Network synthesis} Many recent systems focus on allowing operators to specify  their policies at a high level.
+These can be classified into two classes.
+The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell the switches how to forward packets~\cite{x,y,z}.
+The second class, and to which our work belongs, targets conventional networks and generates switch configuration, based on which the switches interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
+Almost all large networks (old or new) use the conventional paradigm because that scales better~\cite{bgp-in-dc}.
+
+While we borrow much from existing configuration synthesis work, especially Propane~\cite{propane}, our goal is to generate role templates from abstract topologies, rather than switch configurations from concrete topologies.
+This goal aligns better with operators' mental models and tools and permits network evolution with minimal disruption to existing switches.
+In the process, develop new abstractions for network topologies, fault-tolerance analysis algorithms for abstract topologies, and assign formal semantics to templates.
+
+\para{Topology design} Network topology design, especially for data centers, is another active research area, with researchers exploring designs with different properties~\cite{x,y,z}.
+We do not develop new designs but develop abstractions that can capture these designs (and their evolution) and algorithms that can analyze the fault tolerance of abstract topologies.
+
+While not the focus of this paper, our tools can enable operators to pick the right design for their networks, more quickly and with stronger guarantees.
+Today, when picking the design, operators analyze its multiple concrete instantiations because available analysis tools only work with concrete topologies~\cite{condor}.
+This process is time-consuming and not fool-proof; analyzing large, concrete topologies (with potentially thousands of nodes) takes a lot of time and the analysis does not cover the entire space of topologies that may arise.
+
+\para{Network verification}
+A complementary approach to reducing configuration errors is by analyzing the forwarding rules or configuration of the network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,symmetries}.
+Our focus, in contrast, is on a correct-by-construction approach.
+It has the downside that operators must learn to express policies in a new language, but it saves them from the challenging and time-consuming task of configuration generation and provides stronger guarantees on correctness.
+
+\para{Memory shape analysis} \todo{Sagiv, others}
 

### 2016-11-11 paper/abstraction/paper.tex
stashing changes

@@
 A role refers to specific functionality and is played by one or more devices.
-For instance, in a data center, roles may correspond to "top-of-rack," "aggregation," and "spine" switches; and in a backbone network, they may correspond to "core" and "border" routers.
+For instance, in a data center, roles may correspond to "top-of-rack," "aggregation," and "spine" routers; and in a backbone network, they may correspond to "core" and "border" routers.
 While the network may have hundreds or thousands of devices---a scale that is impossible for humans to handle---there tend to be a handful of roles.
@@
 It allows operators to input \emph{abstract network topologies} in terms of roles and their connectivity.
-For instance, they may specify roles for ``top-of-rack'' and ``aggregation" switches and specify that every top-of-rack switch connects to at least two aggregation switches (to tolerate the failure of a link to an aggregation switch).
+For instance, they may specify roles for ``top-of-rack'' and ``aggregation" routers and specify that every top-of-rack router connects to at least two aggregation routers (to tolerate the failure of a link to an aggregation router).
 Other inputs to \sysname include the routing policy of the network and its fault-tolerance requirements (e.g., the number of link failures to tolerate).
@@
 Operators can  specify different tolerance levels for different pairs of abstract nodes.
-For instance, they may say that ToR to spine connectivity should be robust to 2 failures, i.e., no ToR-spine pair should lose connectivity as long as the number of simultaneous link failures is 2 or fewer (for any combination of links); and ToR-to-ToR connectivity should be be robust to 1 failure.
+For instance, they may say that ToR to spine connectivity should be robust to 2 failures, \IE, no ToR-spine pair should lose connectivity as long as the number of simultaneous link failures is 2 or fewer (for any combination of links); and ToR-to-ToR connectivity should be be robust to 1 failure.
+\ryan{tor or ToR?}
 
@@
 
-\section{Language}
+\section{Product Graph Generation}
 \label{sec:language}
@@
     \node[draw, anchor=west] at (#1 + .5, 2.5 / 2) {#3};
-    \node[anchor=east] at (#1 - .4, 2.5 / 2) {\textbf{#5}};
+    \node[] at (#1, 2.5 / 2 + 2.5) {\textbf{#5}};
     \node at (#1 + .34, .6 + .2) {#6};
@@
     \node[anchor=west] at (#1 + .1, 1.25) {#3};
-    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{#5}};
+    \node[] at (#1, 2.5 / 2 + 2.5) {\textbf{#5}};
     \node at (#1 + .34, .6) {#6};
@@
     \node[draw, anchor=west] at (#1 + 2, 1.25) {$e_i > 0$};
-    \node[anchor=east] at (#1 - .4, 1.25) {\textbf{I-striping}};
+    \node[] at (#1 + .46, 1.25 + 2.5) {\textbf{I-striping}};
     \node at (#1 - 1 - .11, .6) {$e_1$};
@@
 
-\newcommand{\inferencelocal}[1]{
-    \inferencenobox{#1}{L$_m(j,k)$}{}{L$_n(j',k')$}{I-local}{}{}
-    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_m(j,k)$}{}{$\ldots$ L$_P$ L$_n(j',k')$}{}{}{}
-    \node[anchor=east] at (#1 + 3 - .6, 2.5) {P};
-    \draw[dashed] (#1+2 - .2, -.34) rectangle (#1+3+1 + .1, 2.85);
+\newcommand{\inferencelocal}[2]{
+    \node[] at (#1 + 1.2, 2.5 / 2 + 2.5) {\textbf{I-local}};
+    \inferencenobox{#1}{L$_m(j,k)$}{}{L$_n(j',k')$}{}{}{}
+    \inferencenobox{#1+2 + #2}{$\ldots$ L$_P$ L$_m(j,k)$}{}{$\ldots$ L$_P$ L$_n(j',k')$}{}{}{}
+    \node[anchor=east] at (#1 + 2 + #2 - .6, 2.5) {P};
+    \draw[dashed] (#1+1 + #2 - .2, -.34) rectangle (#1+3 + #2 + .1, 2.85);
 }
 
-\newcommand{\inferenceglobal}[1]{
-    \inferencenobox{#1}{L$_1(j,k)$}{}{L$_2(j',k')$}{I-global}{}{}
-    \inferencenobox{#1+3}{$\ldots$ L$_P$ L$_m(j,k)$}{}{$\ldots$ A$_Q$ L$_n(j',k')$}{}{}{}
-    \node[anchor=east] at (#1 + 3 - .6, .4) {P};
-    \node[anchor=east] at (#1 + 3 - .6, 2.5) {Q};
-    \draw[dashed] (#1+2 - .2, -.34) rectangle (#1+3+1 + .1, .8);
-    \draw[dashed] (#1+2 - .2, 1.7) rectangle (#1+3+1 + .1, 2.85);
+\newcommand{\inferenceglobal}[2]{
+    \node[] at (#1 + 1.2, 2.5 / 2 + 2.5) {\textbf{I-global}};
+    \inferencenobox{#1}{L$_1(j,k)$}{}{L$_2(j',k')$}{}{}{}
+    \inferencenobox{#1+2+#2}{$\ldots$ L$_P$ L$_m(j,k)$}{}{$\ldots$ A$_Q$ L$_n(j',k')$}{}{}{}
+    \node[anchor=east] at (#1 + 2 + #2 - .6, .4) {P};
+    \node[anchor=east] at (#1 + 2 + #2 - .6, 2.5) {Q};
+    \draw[dashed] (#1+1+#2 - .2, -.34) rectangle (#1+3+#2 + .1, .8);
+    \draw[dashed] (#1+1+#2 - .2, 1.7) rectangle (#1+3+#2 + .1, 2.85);
 }
@@
     \inference{0}{L$_m(j,k)$}{$e_1 > 0$}{S$_n(min(j*k,e_1),1)$}{I-out1}{$e_1$}{$e_2$}
-    \inference{4.5}{A$_m(j,k)$}{$e_2 > 0$}{A$_n(1,min(j,e2))$}{I-out2}{$e_1$}{$e_2$}
-    \inference{9}{L$_m(j,k)$}{$e_1=n$}{A$_n(min(j*k,n),1)$}{I-mesh1}{$e_1$}{$e_2$}
-    \inference{13.5}{L$_m(j,k)$}{$e_1=n$}{A$_n(1,j)$}{I-mesh2}{$e_1$}{$e_2$}
+    \inference{3.5}{A$_m(j,k)$}{$e_2 > 0$}{A$_n(1,min(j,e2))$}{I-out2}{$e_1$}{$e_2$}
+    \inference{7}{L$_m(j,k)$}{$e_1=n$}{A$_n(min(j*k,n),1)$}{I-mesh1}{$e_1$}{$e_2$}
+    \inference{10.5}{L$_m(j,k)$}{$e_1=n$}{A$_n(1,j)$}{I-mesh2}{$e_1$}{$e_2$}
+    \inferencenobox{14}{L$(j,k)$}{$mincut(X)$}{A$(1,min(k,X))$}{I-mincut}{}{}
   \end{tikzpicture}
@@
     \inferencetwo{0}
-    \node[anchor=west] at (2,2) {where $g=n-\dfrac{(m-j)*e_1}{e_2}$};
-    \inferencenobox{11}{L$(j,k)$}{$mincut(X)$}{A$(1,min(k,X))$}{I-mincut}{}{}
-  \end{tikzpicture}
-  \end{minipage}
-
-  \vspace*{1em}
-  \begin{minipage}[t]{\linewidth}%
-  \begin{tikzpicture}
-    \inferencelocal{0}
-    \inferenceglobal{10}
+    \node[anchor=west] at (1,2.2) {where $g=n-\dfrac{(m-j)*e_1}{e_2}$};
+    \inferencelocal{6.5}{.4}
+    \inferenceglobal{12}{.4}
   \end{tikzpicture}
@@
 These can be classified into two classes.
-The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell the switches how to forward packets~\cite{x,y,z}.
-The second class, and to which our work belongs, targets conventional networks and generates switch configuration, based on which the switches interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
+The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell routers how to forward packets~\cite{x,y,z}.
+The second class, and to which our work belongs, targets conventional networks and generates router configuration, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
 Almost all large networks (old or new) use the conventional paradigm because that scales better~\cite{bgp-in-dc}.
 
-While we borrow much from existing configuration synthesis work, especially Propane~\cite{propane}, our goal is to generate role templates from abstract topologies, rather than switch configurations from concrete topologies.
-This goal aligns better with operators' mental models and tools and permits network evolution with minimal disruption to existing switches.
+While we borrow much from existing configuration synthesis work, especially Propane~\cite{propane}, our goal is to generate role templates from abstract topologies, rather than router configurations from concrete topologies.
+This goal aligns better with operators' mental models and tools and permits network evolution with minimal disruption to existing routers.
 In the process, develop new abstractions for network topologies, fault-tolerance analysis algorithms for abstract topologies, and assign formal semantics to templates.
@@
 
-\para{Acknowledgments}
+To help configure large networks correctly, we develop \sysname, the first system that can generate role templates from high-level specifications of network topology and policy.
+\sysname is based on new abstractions for capturing network topologies, and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance.
+Our analysis operates entirely in the abstract domain and guarantees correctness for all concrete instantiations of the topology.
+Experiments with many types of real-world topologies and policies show that our abstractions and analysis are precise and that, for large networks, configuration synthesis is two orders of magnitude faster than systems that operate over concrete topologies.
 

### 2016-11-12 paper/abstraction/paper.tex
edits for 1-3

--- 2016-11-11 paper/abstraction/paper.tex
@@
 %
-Something something, expandable/incremental networks. Something something scales compilation to large networks. Something something, templates easier to understand.
 %These strong guarantees allow operators to reason about the routing behavior of their network at a high-level abstraction, while also generating an efficient low-level implementation.
@@
 %In addition, operators are able to safely change or expand their network in any way, so long as the new resulting topology also respects the abstraction.
-%
-We test \sysname out on ... blah blah blah
 
@@
 
-We present \sysname, a system to generate provably-correct role templates.
+We present \sysname, a system to generate provably-correct configuration templates.
 It allows operators to input \emph{abstract network topologies} in terms of roles and their connectivity.
@@
 Other inputs to \sysname include the routing policy of the network and its fault-tolerance requirements (e.g., the number of link failures to tolerate).
-For routing policy, we borrow notation from Propane~\cite{propane},  which specifies traffic paths at a high-level of abstraction.
+For routing policy, we borrow notation from Propane~\cite{propane}, a language for specifying traffic paths at a high-level of abstraction.
 But while Propane policies
@@
 Based on these inputs, the \sysname compiler generates one template per role.
-It guarantees that, when the templates are instantiated to configurations for {\em any} concrete topology that complies with the abstract topology, the result network will correctly implement the routing policy and meet the fault-tolerance requirements.
-We show how fault-tolerance analysis can be done over abstract topology itself using \todo{say something cool about about the inference rules and such}.
+It guarantees that, when the templates are instantiated to configurations for {\em any} concrete topology that respects the abstraction, the resulting network will correctly implement the routing policy and meet the fault-tolerance requirements.
+To check fault-tolerance properties, we develop a new analysis over the abstraction based on a collection of inference rules about the number of disjoint paths between devices in different roles.
 
 \sysname templates are also evolution-friendly.
-When the network migrates from one concrete topology to another, both of which comply with the abstract topology, it is guaranteed that only the configurations of devices that acquire or lose a neighboring device needs to change (e.g., to activate a port on which the new device is connected).
+When the network migrates from one concrete topology to another, both of which comply with the abstract topology, it is guaranteed that only the configurations of devices that acquire a new neighboring device need to change (e.g., to activate a port on which the new device is connected).
 No other device in the network is impacted.
 
-\todo{Talk about evaluation result here ... roll the point about faster compilation there.}
-As an aside, a pleasant side effect of this new compiler
-infrastructure, designed to make life easier on network operators, is
-that for structured networks, it scales substantially better than its
-competitor \propane does: as the number of individual devices in a
+In addition to creating reusable templates, 
+%synthesizing configurations by working directly with an abstract topology means that 
+\sysname can scale substantially better than its nearest competitor \propane does: as the number of individual devices in a
 network grows, the number of distinct roles will often stay constant.
-Consequently, the \sysname compiler may be two orders of magnitude
-faster than \propane for large structured networks.
+Consequently, the \sysname compiler can be two orders of magnitude
+faster than \propane, taking less than 10 seconds to synthesize templates for large structured networks.
+
+%\todo{Talk about evaluation result here ... roll the point about faster compilation there.}
 
@@
 concrete network satisfying the abstract connectivity invariants.
-\item Design of template generation algorithms that support network
+\item Design of template generation strategies that support network
 evolution.
@@
 
-Route announcements contain additional attributes.
-A common one is {\em AS path}, which denotes the sequence of Autonomous Systems that will be traversed to reach the destination.
-When BGP is used inside a datacenter, each router tends to be its own AS.
-Optional attributes include one or more {\em communities}, which are arbitrary strings.
-Operators agree on what each community value means out of band.
+Route announcements contain additional attributes. A common one is {\em AS path}, which denotes the sequence of Autonomous Systems that will be traversed to reach the destination. 
+%When BGP is used inside a datacenter, each router tends to be its own AS. 
+Optional attributes include one or more {\em communities}, which are arbitrary strings. Operators agree on what each community value means out of band.
 
 A BGP router may receive one or more announcements from different neighbors for the same prefix.
-It selects the best one(s) based on its {\em import policy}.
-These policies are a function of the AS path, community values, or the neighbor that sent the announcement, and may even filter some announcements altogether (i.e., not use them even if no other announcements to the destination are available).
-Then, based on the {\em export policy}, the router announces the selected route to one or more neighbors, after adding itself to the AS path and, optionally, modifying the set of community values.
+It selects the best one based on its local {\em import policy}.
+These policies are a function of the AS path, communities, or the neighbor that sent the announcement, and may even filter some announcements altogether (i.e., not use them even if no other announcements to the destination are available).
+Then, based on the local {\em export policy}, the router announces the selected route to one or more neighbors, after adding itself to the AS path and, optionally, modifying the set of communities.
 
@@
 The spine routers are connected to the
-rest of the Internet through Peer[1--2]. The aggregation routers
+rest of the Internet through neighbors N[1--2]. The aggregation routers
 bridge the spine to the ToR routers. The ToR routers attach to a set of servers (``a rack'') that host services with address prefixes P[1--8].
@@
 The intended policy for this network is:
-$p1)$ complete internal connectivity, \IE, all routers should be able to talk to each other;
-$p2)$ services in Pods[1--2] should be globally accessible;
-$p3)$ prefixes for global service should be aggregated into a covering prefix PG when announced outside;
-$p4)$ services in Pods[3--4] should not be externally accessible;
-$p5)$ prefer Peer 1 over Peer 2, \IE, when both peers announce a prefix, send traffic through peer 1;
-$p6)$ datacenter routers should not transit traffic between peers 1 and 2; and
-$p7)$ no loss in connectivity after any single-link failure.
+$(1)$ complete internal connectivity, \IE, all routers should be able to talk to each other;
+$(2)$ services in Pods[1--2] should be globally accessible;
+$(3)$ prefixes for global service should be aggregated into a covering prefix PG when announced outside;
+$(4)$ services in Pods[3--4] should not be externally accessible;
+$(5)$ paths should be valley-free, \IE, never go down then back up.
+$(6)$ prefer neighbor N1 over N2, \IE, when both neighbors announce a prefix, send traffic through N1;
+$(7)$ datacenter routers should not transit traffic between N1 and N2; and
+$(8)$ no loss in connectivity after any single-link failure.
 
@@
 %
-The network in Figure~\ref{fig:example} has five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
+The network in Figure~\ref{fig:example} might have five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
 %
@@
 
-\para{Templates today} While templates help avoid a class of configuration errors (e.g., inconsistent routing adjacencies), they are difficult to author.
+While templates help avoid a class of configuration errors (e.g., inconsistent routing adjacencies), they are difficult to author.
 Operators must manually decompose complex, network-wide routing policy into role templates such that the collective behavior of the configurations generated from them will correctly implement the policy, under failures and as the network evolves.
 
-This task is error-prone, and no tools exist today for template verification; in fact, such tools would be difficult to build as templates have no semantics, of policies or topologies they were intended to work for, independent of the configurations they produce.
+%This task is error-prone, and no tools exist today for template verification; in fact, such tools would be difficult to build as templates have no semantics, of policies or topologies they were intended to work for, independent of the configurations they produce.
 Today, operators test (not verify) templates by simulating their generated configurations over the current or known future topologies.
@@
 
-Such simulations provide some assurance that the templates work correctly for the simulated topologies but little assurance for other topologies that may arise after the network evolves.
+%Such simulations provide some assurance that the templates work correctly for the simulated topologies but little assurance for other topologies that may arise after the network evolves.
+
 Templates that work for one topology may not work for seemingly-inconsequential variations.  
-Unfotunately, currently,
-there is no way to predict which variations will behave correctly for a given set of templates.
-Worse, when operators discover their old templates no longer work, a change to a template will
+%Unfotunately, currently, there is no way to predict which variations will behave correctly for a given set of templates.
+Worse, when operators discover their old templates no longer work, changing a template will
 cause a change to all devices that use that template---an unacceptable disruption in many cases.
-When that happens, network operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the topological change.
+When that happens, operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the change.
 Such patches reintroduce the complexity and errors that templates were meant to prevent.
@@
 Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}; it has the same five roles, connected in a similar hierarchy.
-One might think that the same templates (with different database entries) can be used for both topologies, but that is not true.
-For instance, consider templates that disallow ``valley" paths, which go up, down, and then up again; it is a common to disallow valley paths in a data center because they are longer than shortest paths.
-These templates will work perfectly for Figure~\ref{fig:example} but silently violate the fault tolerance requirement ($p7$) when used for Figure~\ref{fig:example2}.
-Specifically, in Figure~\ref{fig:example2}, an aggregation-induced blackhole (\S\ref{sec:motivation}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces  the covering prefix PG (because it gets routes for P[3--4]).
+One might think that the same templates (with different database entries) can be used for both topologies.
+However, because the templates are configured to disallow ``valley" paths, which go down, and then up, these templates will work perfectly for Figure~\ref{fig:example} but silently violate the fault tolerance requirement ($(8)$) when used for Figure~\ref{fig:example2}.
+Specifically, in Figure~\ref{fig:example2}, an aggregation-induced blackhole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]).
 In contrast, in Figure~\ref{fig:example}, no such blackhole will occur after a single link failure because spine routers have two links to each pod.

### 2016-11-12 paper/abstraction/paper.tex
edits for 1-3

@@
 While templates help avoid a class of configuration errors (e.g., inconsistent routing adjacencies), they are difficult to author.
-Operators must manually decompose complex, network-wide routing policy into role templates such that the collective behavior of the configurations generated from them will correctly implement the policy, under failures and as the network evolves.
+Operators must manually decompose complex, network-wide routing policy into role templates such that the collective behavior of the configurations generated from them will correctly implement the policy, both when failures occur and as the network evolves.
 

### 2016-11-12 paper/abstraction/paper.tex
minor edits

--- 2016-11-11 paper/abstraction/paper.tex
@@
 \textbf{Abstract---}
-We develop techniques for automated reasoning about end-to-end properties of abstract network topologies.
-We develop a network synthesis tool, \sysname, to allow network operators to write a high-level routing policy over an abstraction of their network topology.
-From such a specification, \sysname synthesizes a collection of router configurations running the distributed Border Gateway Protocol (BGP) that are guaranteed to implement the centralized routing policy for any concrete instantiation of the abstract topology, and for any combination of network failures in the resulting concrete topology.
-%
-Additionally, properties proven by \sysname over the abstract topology, such as reachability between a source and destination under k-failures, are also guaranteed to hold under any concrete instantiation of the abstract topology.
-%
-Something something, expandable/incremental networks. Something something scales compilation to large networks. Something something, templates easier to understand.
-%These strong guarantees allow operators to reason about the routing behavior of their network at a high-level abstraction, while also generating an efficient low-level implementation.
-%
-%In addition, operators are able to safely change or expand their network in any way, so long as the new resulting topology also respects the abstraction.
+We develop techniques for automated reasoning about end-to-end properties of
+abstract network topologies, and embody them in a network synthesis tool called
+\sysname. \sysname allows network operators to write a high-level routing policy
+over an abstraction of their network topology. From such a specification,
+\sysname synthesizes a collection of router configurations running the
+distributed Border Gateway Protocol (BGP) that are guaranteed to implement the
+centralized routing policy for any concrete instantiation of the abstract
+topology, and for any combination of network failures in the resulting concrete
+topology.
+%
+Additionally, properties proven by \sysname over the abstract topology, such as
+reachability between a source and destination under k-failures, are also
+guaranteed to hold under any concrete instantiation of the abstract topology.
+%
+Something something, expandable/incremental networks. Something something scales
+compilation to large networks. Something something, templates easier to
+understand.
+%These strong guarantees allow operators to reason about the routing behavior of
+%their network at a high-level abstraction, while also generating an efficient
+%low-level implementation.
+%
+%In addition, operators are able to safely change or expand their network in any
+%way, so long as the new resulting topology also respects the abstraction.
 %
@@
 
-%\vspace{0.1in}
-%\noindent
-%\textbf{CCS Concepts}\\
-%$\bullet$ Networks $\rightarrow$ {\em Network control algorithms; Network reliability; Network management;}
-%$\bullet$ Software and its engineering $\rightarrow$ {\em Automated static analysis; Domain specific languages}
-
-%\vspace{0.1in}
-%\noindent
-%\textbf{Keywords}\\
-%Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems
+%\vspace{0.1in} \noindent \textbf{CCS Concepts}\\ $\bullet$ Networks
+%$\rightarrow$ {\em Network control algorithms; Network reliability; Network
+%management;} $\bullet$ Software and its engineering $\rightarrow$ {\em
+%Automated static analysis; Domain specific languages}
+
+%\vspace{0.1in} \noindent \textbf{Keywords}\\ Propane; Domain-specific Language;
+%BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems
 
@@
 
-\section{Introduction}
-\label{sec:introduction}
-
-% Hence, one approach to improving network
-% reliability is to develop better languages for network configuration.
-% Such languages should be defined at a higher level of abstraction than
-% existing configuration languages and provide support built-in support for
-% verification of important properties, thereby avoiding entire classes
-% of configuration errors automatically.
+\section{Introduction} \label{sec:introduction}
+
+% Hence, one approach to improving network reliability is to develop better
+% languages for network configuration.  Such languages should be defined at a
+% higher level of abstraction than existing configuration languages and provide
+% support built-in support for verification of important properties, thereby
+% avoiding entire classes of configuration errors automatically.
 
@@
 Computer networks run many critical services, and every second of downtime is
-costly at best and dangerous at worst.  Keeping these complex systems up and running 24/7 is an enormous challenge~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
-%
-While hardware faults, rodents, power failures and natural disasters all pose problems, studies have consistently shown that human error in network configuration is one of the most error-prone task and the leading cause of network outages~\cite{juniper-study,xx}.
-
-To manage and configure large networks today, instead of considering individual devices, operators classify devices devices into {\em roles}.
-A role refers to specific functionality and is played by one or more devices.
-For instance, in a data center, roles may correspond to "top-of-rack," "aggregation," and "spine" routers; and in a backbone network, they may correspond to "core" and "border" routers.
-While the network may have hundreds or thousands of devices---a scale that is impossible for humans to handle---there tend to be a handful of roles.
-%
-Operators author a configuration {\em template} for each role.
-Templates are macros that can be instantiated with different concrete values, based on the network topology, to generate a configuration for each device.
-
-Unfortunately, template construction is a low-level, manual process.
-Operators manually decompose network-wide routing and fault-tolerance policies (e.g., prefer one end-to-end path over another or no loss in connectivity after any one-link failure) across roles and encode them using assembly-language-like configuration primitives (e.g., role A should not transmit routing information from B to C).
-Such decomposition tasks are highly complex~\cite{propane}.
-
-Worse, operators can never be sure that the generated templates correctly implement the policy,  beyond testing some concrete instantiations using simulation or verification tools~\cite{x,y}.
-Testing based on concrete instantiations is insufficient because large networks evolve continuously, as devices and links are added or taken offline for maintenance.
-Templates that work for the current network topology, may or may not work for future topologies.
-Updating the templates, if found to not work for a future topology, may cause trickle-down, network-wide configuration changes, which is highly disruptive.
-Building sophisticated tools for validating templates is difficult because the templates today have no particular semantics---which policies they implement and for which topologies---other than the semantics of the configurations that one obtains from instantiating them.
+costly at best and dangerous at worst.  Keeping these complex systems up and
+running 24/7 is an enormous
+challenge~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
+%
+While hardware faults, backhoes, power failures and natural disasters all pose
+problems, studies have consistently shown that human error in network
+configuration is one of the leading cause of network
+outages~\cite{juniper-study,xx}.
+
+To manage and configure large networks today, instead of considering individual
+devices, operators classify devices devices into {\em roles}. A role refers to
+specific functionality and is played by one or more devices. For instance, in a
+data center, roles may correspond to "top-of-rack," "aggregation," and "spine"
+routers; and in a backbone network, they may correspond to "core" and "border"
+routers. While the network may have hundreds or thousands of devices---a scale
+that is impossible for humans to handle---there tend to be a handful of roles.
+%
+Operators author a configuration {\em template} for each role. Templates are
+macros that can be instantiated with different concrete values, based on the
+network topology, to generate a configuration for each device.
+
+Unfortunately, template construction is a low-level, manual process. Operators
+manually decompose network-wide routing and fault-tolerance policies (e.g.,
+prefer one end-to-end path over another or no loss in connectivity after any
+one-link failure) across roles and encode them using assembly-language-like
+configuration primitives (e.g., role A should not transmit routing information
+from B to C). Such decomposition tasks are highly complex~\cite{propane}.
+
+Worse, operators can never be sure that the generated templates correctly
+implement the policy,  beyond testing some concrete instantiations using
+simulation or verification tools~\cite{x,y}. Testing based on concrete
+instantiations is insufficient because large networks evolve continuously, as
+devices and links are added or taken offline for maintenance. Templates that
+work for the current network topology, may or may not work for future
+topologies. Updating the templates, if found to not work for a future topology,
+may cause trickle-down, network-wide configuration changes, which is highly
+disruptive. Building sophisticated tools for validating templates is difficult
+because the templates today have no particular semantics---which policies they
+implement and for which topologies---other than the semantics of the
+configurations that one obtains from instantiating them.
 
@@
 
-Given the challenges of generating and validating network configurations, one might think that operators will be receptive to systems that can generate provably-correct configurations from high-level policy specifications~\cite{x,y,z,configassure,propane}.
-However, our conversations with two major cloud providers reveal that operators of large networks are reluctant to use such systems.
-While they think of their network abstractly, in terms of roles, these systems require concrete topologies, with no understanding of roles as a first-order abstraction.
-Even if two devices play the same role,
-there is no guarantee that the systems will generate (syntactically) similar configurations; if the operators want to debug or analyze system output, they will have to consider
-hundreds of device configurations instead of a handful of role configurations.
-These systems become even more brittle when the network evolves.
-Any change in network topology requires re-execution of the engine, from scratch, on the changed topology.
-The result may be
-a completely different set of configurations.
-
-We present \sysname, a system to generate provably-correct role templates.
-It allows operators to input \emph{abstract network topologies} in terms of roles and their connectivity.
-For instance, they may specify roles for ``top-of-rack'' and ``aggregation" routers and specify that every top-of-rack router connects to at least two aggregation routers (to tolerate the failure of a link to an aggregation router).
-Other inputs to \sysname include the routing policy of the network and its fault-tolerance requirements (e.g., the number of link failures to tolerate).
-For routing policy, we borrow notation from Propane~\cite{propane},  which specifies traffic paths at a high-level of abstraction.
-But while Propane policies
-refer concrete devices, \sysname policies refer to abstract roles.
-
-Based on these inputs, the \sysname compiler generates one template per role.
-It guarantees that, when the templates are instantiated to configurations for {\em any} concrete topology that complies with the abstract topology, the result network will correctly implement the routing policy and meet the fault-tolerance requirements.
-We show how fault-tolerance analysis can be done over abstract topology itself using \todo{say something cool about about the inference rules and such}.
-
-\sysname templates are also evolution-friendly.
-When the network migrates from one concrete topology to another, both of which comply with the abstract topology, it is guaranteed that only the configurations of devices that acquire or lose a neighboring device needs to change (e.g., to activate a port on which the new device is connected).
-No other device in the network is impacted.
+Given the challenges of generating and validating network configurations, one
+might think that operators will be receptive to systems that can generate
+provably-correct configurations from high-level policy
+specifications~\cite{x,y,z,configassure,propane}. However, our conversations
+with two major cloud providers reveal that operators of large networks are
+reluctant to use such systems. While they think of their network abstractly, in
+terms of roles, these systems require concrete topologies, with no understanding
+of roles as a first-order abstraction.  Even if two devices play the same role,
+there is no guarantee that the systems will generate (syntactically) similar
+configurations; if the operators want to debug or analyze system output, they
+will have to consider hundreds of device configurations instead of a handful of
+role configurations. These systems become even more brittle when the network
+evolves. Any change in network topology requires re-execution of the engine,
+from scratch, on the changed topology.  The result may be a completely different
+set of configurations.
+
+We present \sysname, a system to generate provably-correct role templates. It
+allows operators to input \emph{abstract network topologies} in terms of roles
+and their connectivity. For instance, they may specify roles for ``top-of-rack''
+and ``aggregation" routers and specify that every top-of-rack router connects to
+at least two aggregation routers (to tolerate the failure of a link to an
+aggregation router). Other inputs to \sysname include the routing policy of the
+network and its fault-tolerance requirements (e.g., the number of link failures
+to tolerate). For routing policy, we borrow notation from
+Propane~\cite{propane},  which specifies traffic paths at a high-level of
+abstraction. But while Propane policies refer to concrete devices, \sysname
+policies refer to abstract roles.
+
+Based on these inputs, the \sysname compiler generates one template per role. It
+guarantees that, when the templates are instantiated to configurations for {\em
+any} concrete topology that complies with the abstract topology, the result
+network will correctly implement the routing policy and meet the fault-tolerance
+requirements. We show how fault-tolerance analysis can be done over abstract
+topology itself using \todo{say something cool about about the inference rules
+and such}.
+
+\sysname templates are also evolution-friendly. When the network migrates from
+one concrete topology to another, both of which comply with the abstract
+topology, it is guaranteed that only the configurations of devices that acquire
+or lose a neighboring device needs to change (e.g., to activate a port on which
+the new device is connected).  No other device in the network is impacted.
 

### 2016-11-12 paper/abstraction/paper.tex
remove duplicate template text

--- 2016-11-12 paper/abstraction/paper.tex
@@
 
-While templates help avoid a class of configuration errors (e.g., inconsistent routing adjacencies), they are difficult to author.
-Operators must manually decompose complex, network-wide routing policy into role templates such that the collective behavior of the configurations generated from them will correctly implement the policy, under failures and as the network evolves.
+%While templates help avoid a class of configuration errors (e.g., inconsistent routing adjacencies), they provide no guarantees
+Templates that work for one topology may not work for seemingly-inconsequential variations.  
+%Unfotunately, currently, there is no way to predict which variations will behave correctly for a given set of templates.
+Worse, when operators discover their old templates no longer work, changing a template will
+cause a change to all devices that use that template---an unacceptable disruption in many cases.
+When that happens, operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the change.
+Such patches reintroduce the complexity and errors that templates were meant to prevent.
+
+%they are difficult to author.
+Operators must manually decompose complex, network-wide routing policy into role templates such that the collective behavior of the configurations generated from them will correctly implement the policy, both when failures occur and as the network evolves.
 
@@
 
-Templates that work for one topology may not work for seemingly-inconsequential variations.  
+%Templates that work for one topology may not work for seemingly-inconsequential variations.  
 %Unfotunately, currently, there is no way to predict which variations will behave correctly for a given set of templates.
-Worse, when operators discover their old templates no longer work, changing a template will
-cause a change to all devices that use that template---an unacceptable disruption in many cases.
+%Worse, when operators discover their old templates no longer work, changing a template will
+%cause a change to all devices that use that template---an unacceptable disruption in many cases.
 When that happens, operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the change.
-Such patches reintroduce the complexity and errors that templates were meant to prevent.
+%Such patches reintroduce the complexity and errors that templates were meant to prevent.
 

### 2016-11-12 paper/abstraction/paper.tex
edit section 4

@@
 
-\sysname is a system for generating provably-correct templates from the network's policy and an {\em abstract} topology that describes device roles and connectivity invariants.
+In this section we give an overview of \sysname, a system for generating provably-correct templates from the network's policy and an {\em abstract} topology that describes device roles and connectivity invariants.
 %As inputs, it takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an {\em abstract} topology that describes device roles and connectivity invariants.
@@
 %
-When \sysname compiles a policy, it guarantees that the forwarding behavior of the network will be correct for any concrete instantiation of the abstract network, and for any combination of failures that may occur in the concrete network.
-Furthermore, \sysname will generate configurations in such a way that, if an operator expands their network in a way compatible with the abstraction, then only configurations of devices adjacent to the change ever need to be updated.
+When \sysname generates templates, it guarantees that the forwarding behavior of the network will be correct for any instantiation of the templates on a concrete network that repects the abstraction. 
+%Furthermore, \sysname will generate configurations in such a way that, if an operator expands their network in a way compatible with the abstraction, then only configurations of devices adjacent to the change ever need to be updated.
 
@@
 \para{Abstract topology}
-Abstract topologies in \sysname capture connectivity invariants of the network that hold both when network is first instantiated and as it evolves.
-These invariantes are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
+Abstract topologies in \sysname define structural and role-based invariants that capture a collection of concrete networks.
+These invariants are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities and connectivity.
 %
@@
 Figure~\ref{fig:example3} shows an example of an abstraction for both datacenter networks from \S\ref{sec:motivation}.
-In particular the concrete networks are abstracted into a new topology with 5 different roles: local ToR (TL), global ToR (TG), local aggregator (AL), global aggregator (AG), and spine (S).
+In the example, the concrete networks are abstracted into a new topology with 5 different roles: local ToR (TL), global ToR (TG), local aggregator (AL), global aggregator (AG), and spine (S).
 
@@
 
-All the guarantees provided by \sysname hold for any instantiation of the abstract network.
+%All the guarantees provided by \sysname hold for any instantiation of the abstract network.
 This means that operators can safely expand their network in the future so long as the new network also satisfies these logical constraints.

### 2016-11-12 paper/abstraction/paper.tex

@@
 \textbf{Abstract---}
-We develop techniques for automated reasoning about end-to-end properties of abstract network topologies.
-We develop a network synthesis tool, \sysname, to allow network operators to write a high-level routing policy over an abstraction of their network topology.
-From such a specification, \sysname synthesizes a collection of router configurations running the distributed Border Gateway Protocol (BGP) that are guaranteed to implement the centralized routing policy for any concrete instantiation of the abstract topology, and for any combination of network failures in the resulting concrete topology.
-%
-Additionally, properties proven by \sysname over the abstract topology, such as reachability between a source and destination under k-failures, are also guaranteed to hold under any concrete instantiation of the abstract topology.
-%
-%These strong guarantees allow operators to reason about the routing behavior of their network at a high-level abstraction, while also generating an efficient low-level implementation.
-%
-%In addition, operators are able to safely change or expand their network in any way, so long as the new resulting topology also respects the abstraction.
+We develop techniques for automated reasoning about end-to-end properties of
+abstract network topologies, and embody them in a network synthesis tool called
+\sysname. \sysname allows network operators to write a high-level routing policy
+over an abstraction of their network topology. From such a specification,
+\sysname synthesizes a collection of router configurations running the
+distributed Border Gateway Protocol (BGP) that are guaranteed to implement the
+centralized routing policy for any concrete instantiation of the abstract
+topology, and for any combination of network failures in the resulting concrete
+topology.
+%
+Additionally, properties proven by \sysname over the abstract topology, such as
+reachability between a source and destination under k-failures, are also
+guaranteed to hold under any concrete instantiation of the abstract topology.
+%
+Something something, expandable/incremental networks. Something something scales
+compilation to large networks. Something something, templates easier to
+understand.
+%These strong guarantees allow operators to reason about the routing behavior of
+%their network at a high-level abstraction, while also generating an efficient
+%low-level implementation.
+%
+%In addition, operators are able to safely change or expand their network in any
+%way, so long as the new resulting topology also respects the abstraction.
+%
+We test \sysname out on ... blah blah blah
 
@@
 
-Given the challenges of generating and validating network configurations, one might think that operators will be receptive to systems that can generate provably-correct configurations from high-level policy specifications~\cite{x,y,z,configassure,propane}.
-However, our conversations with two major cloud providers reveal that operators of large networks are reluctant to use such systems.
-While they think of their network abstractly, in terms of roles, these systems require concrete topologies, with no understanding of roles as a first-order abstraction.
-Even if two devices play the same role,
-there is no guarantee that the systems will generate (syntactically) similar configurations; if the operators want to debug or analyze system output, they will have to consider
-hundreds of device configurations instead of a handful of role configurations.
-These systems become even more brittle when the network evolves.
-Any change in network topology requires re-execution of the engine, from scratch, on the changed topology.
-The result may be
-a completely different set of configurations.
-
-We present \sysname, a system to generate provably-correct configuration templates.
-It allows operators to input \emph{abstract network topologies} in terms of roles and their connectivity.
-For instance, they may specify roles for ``top-of-rack'' and ``aggregation" routers and specify that every top-of-rack router connects to at least two aggregation routers (to tolerate the failure of a link to an aggregation router).
-Other inputs to \sysname include the routing policy of the network and its fault-tolerance requirements (e.g., the number of link failures to tolerate).
-For routing policy, we borrow notation from Propane~\cite{propane}, a language for specifying traffic paths at a high-level of abstraction.
-But while Propane policies
-refer concrete devices, \sysname policies refer to abstract roles.
-
-Based on these inputs, the \sysname compiler generates one template per role.
-It guarantees that, when the templates are instantiated to configurations for {\em any} concrete topology that respects the abstraction, the resulting network will correctly implement the routing policy and meet the fault-tolerance requirements.
-To check fault-tolerance properties, we develop a new analysis over the abstraction based on a collection of inference rules about the number of disjoint paths between devices in different roles.
-
-\sysname templates are also evolution-friendly.
-When the network migrates from one concrete topology to another, both of which comply with the abstract topology, it is guaranteed that only the configurations of devices that acquire a new neighboring device need to change (e.g., to activate a port on which the new device is connected).
-No other device in the network is impacted.
+Given the challenges of generating and validating network configurations, one
+might think that operators will be receptive to systems that can generate
+provably-correct configurations from high-level policy
+specifications~\cite{x,y,z,configassure,propane}. However, our conversations
+with two major cloud providers reveal that operators of large networks are
+reluctant to use such systems. While they think of their network abstractly, in
+terms of roles, these systems require concrete topologies, with no understanding
+of roles as a first-order abstraction.  Even if two devices play the same role,
+there is no guarantee that the systems will generate (syntactically) similar
+configurations; if the operators want to debug or analyze system output, they
+will have to consider hundreds of device configurations instead of a handful of
+role configurations. These systems become even more brittle when the network
+evolves. Any change in network topology requires re-execution of the engine,
+from scratch, on the changed topology.  The result may be a completely different
+set of configurations.
+
+We present \sysname, a system to generate provably-correct role templates. It
+allows operators to input \emph{abstract network topologies} in terms of roles
+and their connectivity. For instance, they may specify roles for ``top-of-rack''
+and ``aggregation" routers and specify that every top-of-rack router connects to
+at least two aggregation routers (to tolerate the failure of a link to an
+aggregation router). Other inputs to \sysname include the routing policy of the
+network and its fault-tolerance requirements (e.g., the number of link failures
+to tolerate). For routing policy, we borrow notation from
+Propane~\cite{propane},  which specifies traffic paths at a high-level of
+abstraction. But while Propane policies refer to concrete devices, \sysname
+policies refer to abstract roles.
+
+Based on these inputs, the \sysname compiler generates one template per role. It
+guarantees that, when the templates are instantiated to configurations for {\em
+any} concrete topology that complies with the abstract topology, the result
+network will correctly implement the routing policy and meet the fault-tolerance
+requirements. We show how fault-tolerance analysis can be done over abstract
+topology itself using \todo{say something cool about about the inference rules
+and such}.
+
+\sysname templates are also evolution-friendly. When the network migrates from
+one concrete topology to another, both of which comply with the abstract
+topology, it is guaranteed that only the configurations of devices that acquire
+or lose a neighboring device needs to change (e.g., to activate a port on which
+the new device is connected).  No other device in the network is impacted.
 

### 2016-11-12 paper/abstraction/paper.tex
stashing changes

@@
 we introduce several additional concepts.
-The first is the idea of topology hierarchy captured by P and Q, which say that nodes in the tor and aggregator roles are grouped into a number of smaller pods.
+The first is the idea of a topology hierarchy captured by P and Q, which say that nodes in the tor and aggregator roles are grouped into a number of smaller pods.
 The second is a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
@@
 
-For example, in Figure~\ref{fig:example3}, the first two constraints: $e1 = AG$ and $e2 = TG$ say that, within any pod P, the number of outgoing edges from a node in the $TG$ role to a node in the $AG$ role is equal to the number of nodes in the $AG$.
-Similarly, the number of outgoing edges from $AG$ to $TG$ is equal to the number of nodes in the $TG$ role.
+For example, in Figure~\ref{fig:example3}, the first two constraints: $e1 = AG$ and $e2 = TG$ say that, within any pod P, the number of outgoing edges from a node in the $TG$ role to a node in the $AG$ role is equal to the number of nodes in the $AG$ role.
+Similarly, the number of outgoing edges from a node in the $AG$ role to a node in the $TG$ role is equal to the number of nodes in the $TG$ role.
 These constraints capture the fact that, within any given pod, the global aggregators and ToRs are in a full mesh.
@@
 The constraint $2 \leq S \leq 4$ makes explicit the possibility for growth, for example by growing the network from that of Figure~\ref{fig:example} to that of Figure~\ref{fig:example2}.
-In general, we need not bound the number of spine routers to admit more concrete topologies at the expense of analysis precision.
-Finally, we include the constraints $(S \mod AG) = 0$, and $(S \mod AL) = 0$ simply to show that constraints do not have to inequalities.
-In general operators can write constraints using logical formula for any theory supported by modern SMT solvers.
-
-\ryan{mention mincut}
+In general, we need not bound the number of spine routers to admit more concrete topologies, potentially at the expense of analysis precision.
+Finally, we include the constraints $(S \mod AG) = 0$, and $(S \mod AL) = 0$ simply to show that constraints do not have to be inequalities.
+In general operators can write constraints using logical formula from any theory supported by modern SMT solvers.
+
+A final type of abstraction is the $mincut(1)$ constraint between the spine role S and N[1--2].
+The mincut constraint says that any node in the spine role has at least one path to any node in the neighbor N1 (and N2) role.
+Annotations of this form are often useful for a "one big switch" \ryan{cite} type of abstraction where part of a complex network is abstracted into a single node.
+For example, to model an ISP backbone network the operator might abstract the network into separate geographic regions with two abstract roles per region -- one role for the border routers of the network, and another role for the core of the network.
+Mincut annotations could be used to describe the fault tolerance both within region cores as well as across regions.
 
@@
 The rule applies to an edge that has been annotated with a $mincut(X)$ statement, which means that there are at least $X$ disjoint paths between any node in role $m$ and any node in role $n$.
-Annotations of this form are useful for a "one big switch" \ryan{cite} type of abstraction where part of a complex network is abstracted into a single node.
-For example, to model an ISP backbone network the operator might abstract the network into separate geograph regions with two abstract roles per region.
-One role for the border routers of the network, and another role for the core of the network.
-Mincut annotations could be used to describe the fault tolerance both within region cores as well as across regions.
 

### 2016-11-12 paper/abstraction/paper.tex
sync with policy numbers

@@
 
-\para{Routing policy} Routing policies in \sysname consist of an ordered sequence of both a predicate matching various classes of traffic and a list of ranked constraints on the paths that the traffic matching the predicate should prefer to take through the network.
+\para{Routing policy} Routing policies in \sysname consist of an ordered sequence of both a predicate matching a class of traffic and a list of ranked constraints on the paths that the traffic matching the predicate should prefer to take through the network.
 We borrow syntax from Propane~\cite{propane} but, instead of concrete prefixes and nodes, \sysname specifications can use abstract prefixes and nodes.
@@
 Let us see how to configure each of the datacenter networks from \S\ref{sec:motivation} by writing a \sysname routing policy over the abstract topology.
-We can capture the basic routing behavior for the datacenters with the following policy:
+We can capture the basic routing behavior, constraints (1, 2, 6), for the datacenters with the following policy:
 %
@@
 
-Next we can capture the constraint that traffic for local prefixes must stay local to the datacenter.
-This is written as the following \sysname constraint:
+Next we can capture constraint (4) that traffic for local prefixes must stay local to the datacenter:
 %
@@
 %
-The Local constraint applies to any traffic destined for a local prefix described by the \$LP prefix template variable and adds the constraint that the traffic must follow a path that matches an internal location (\IE, a router inside the datacenter) at each hop of the path.
-This prevents traffic from ever entering from or leaving through an external peer.
-
-It is also common practice to prevent peers (\EG, $\CD{P1}$ and $\CD{P2}$) from communicating by sending data through the datacenter. Such a constraint can be added to \sysname in the following way:
+The Local constraint applies to any traffic destined for a local prefix described by the $\CD{\$LP}$ prefix template variable and adds the constraint that the traffic must follow a path that matches an internal location (\IE, a router inside the datacenter) at each hop of the path.
+%
+The constraint to prevent "valleys" (5) is implemented as:
+%
+\begin{code}
+\Define NoValley =
+    \True \Path \Novalley(\{TG,TL\},\{AG,AL\},\{S\})
+\end{code}
+\noindent%
+%
+This policy applies to all traffic and prevents valley paths by adding the $\Novalley$ constraint with arguments corresponding to each datacenter level.
+%
+Constraint (7) to prevent transit traffic between neighbors is expressed in \sysname as:
 %
@@
 \Define Peer = \{P1,P2\}
-\Define BlockPeers =
+\Define NoTransit =
     \True \Path !(\Enter(Peer) & \Exit(Peer))
@@
 \begin{code}
-Routing & Local & BlockPeers & \Agg(PG, \In -> \Out)
+Routing & Local & NoTransit & 
+NoValley & \Agg(PG, \In -> \Out)
 \end{code}
@@
 
-This tells \sysname to find BGP router configurations that satisfy the conjunction of the Routing and Local constraints.
+This instructs \sysname to find BGP router configurations that satisfy the conjunction of the Routing and Local constraints.
 It also declares an additional constraint that we want to perform prefix summarization (as PG) for global prefixes at the border of the datacenter (\IE, along any edge starting inside our datacenter and ending at a peer outside the datacenter).

### 2016-11-12 paper/abstraction/paper.tex
reduce section 4.2

@@
 
-This instructs \sysname to find BGP router configurations that satisfy the conjunction of the Routing and Local constraints.
+This instructs \sysname to find BGP router configurations that satisfy the conjunction of all the constraints.
 It also declares an additional constraint that we want to perform prefix summarization (as PG) for global prefixes at the border of the datacenter (\IE, along any edge starting inside our datacenter and ending at a peer outside the datacenter).
@@
 Operators can  specify different tolerance levels for different pairs of abstract nodes.
-For instance, they may say that ToR to spine connectivity should be robust to 2 failures, \IE, no ToR-spine pair should lose connectivity as long as the number of simultaneous link failures is 2 or fewer (for any combination of links); and ToR-to-ToR connectivity should be be robust to 1 failure.
-\ryan{tor or ToR?}
+For instance, they may say that ToR to spine connectivity should be robust to 2 failures, \IE, no ToR-spine pair should lose connectivity as long as the number of simultaneous link failures is 2 or fewer; and ToR-to-ToR connectivity should be be robust to 1 failure.
 
@@
 
-Second, \sysname evaluates if the fault-tolerance policy can be met, considering the joint impact of the abstract topology and routing policy.
-Joint analysis is needed, and topology alone is not enough, because connectivity for traffic will suffer even when functional paths exists in the topology if those paths are not allowed by routing policy.
-It implies that we cannot use standard graph theoretic algorithms here.
-
-Instead, we develop a sound analysis that is based on computing the minimum number of disjoint policy-compliant paths between pairs of nodes over abstract topologies.
-If this number for a pair of nodes is less than the desired fault-tolerance level, we declare that the policy cannot be met.
+Second, \sysname checks if the fault-tolerance policy can be met by considering the joint impact of the abstract topology and routing policy.
+Joint analysis is needed, because connectivity for traffic will suffer even when functional paths exists in the topology if those paths are not allowed by routing policy.
+It implies that we cannot use standard graph theoretic algorithms.
+
+Instead, we develop a sound analysis based on computing the minimum number of disjoint policy-compliant paths between pairs of nodes over abstract topologies.
+If this number for a pair of nodes is less than the desired fault-tolerance level, \sysname declares that the policy cannot be met.
 
@@
 For example, since the network is performing prefix summarization at the border of the datacenter, we might introduce a black hole after enough failures occur to disconnect a tor from a spine router.
-We proceed as follows.
 For each abstract role in the network, we learn invariants about the number of disjoint paths to routers in that role.
@@
 %
-If we run the abstract analysis over the abstract network from Figure~\ref{fig:example3} the analysis will learn a fact of the form $A_{S}(1,2)$, which means that any single spine node is reachable via 2 disjoint paths from any initial global tor node \ryan{it will actually be 1, we need to add a constraint on e1}.
-
-Suppose now that the routing policy disallowed paths with valleys (\IE, paths that go down and then up at some point).
-%Such a constraint can be added to the routing policy in \sysname:
-%\begin{code}
-%\Define ValleyFree =
-%    \True \Path \Novalley(\{TL,TG\},\{AL,AG\},\{S\})
-%\end{code}
-%\noindent%
-%This adds a constraint that applies to all traffic and prevents valleys by defining each level in the datacenter.
-Because our analysis is policy sensitive, if we were to run it again with the same abstract topology but the new routing policy, it would only be able to infer that there is a single disjoint path to any given spine router in the worst case.
-In fact this is exactly the case for the concrete network from Figure~\ref{fig:example2}.
-
-Finally, if \sysname deems that the fault-tolerance policy can be met, it generates templates for the abstract topology, which can be instantiated into BGP configurations based on the concrete topology.
-During concretization, we confirm that the concrete topology adheres to the original abstract topology.
+After one more inference the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node 
+In fact, due the the valley-free routing constraint, a single path is the most information we can infer, since this is exactly the worst-case fault-tolerance for the concrete network from Figure~\ref{fig:example2}.
+
+If \sysname finds that the fault-tolerance policy can be met, it generates templates for the abstract topology, which can be instantiated into BGP configurations based on the concrete topology.
+During concretization, we confirm that the concrete topology adheres to the abstract topology.
 

### 2016-11-12 paper/abstraction/paper.tex
clean up product graph construction

@@
     \$LP  \Path \End(TL)
-    \True \Path \End(\Out) & \Exit(P1 \Prefer P2)
+    \True \Path \End(\Out) & \Exit(N1 \Prefer N2)
 \end{code}
@@
 %
-The final rule matches all other IP prefix destinations and allows traffic to follow a path that leaves the datacenter, ending up at some outside location, through either of its peers $\CD{P1}$ or $\CD{P2}$ with a preference for leaving through $\CD{P1}$ over $\CD{P2}$.
+The final rule matches all other IP prefix destinations and allows traffic to follow a path that leaves the datacenter, ending up at some outside location, through either of its peers $\CD{N1}$ or $\CD{N2}$ with a preference for leaving through $\CD{N1}$ over $\CD{N2}$.
 The $\CD{\Prefer}$~symbol indicates that traffic should satisfy the constraint on the left whenever possible (\IE, a path exists in the network), and only resort to the backup (right) when this is not possible due to network failures.%
@@
 \begin{code}
-\Define Peer = \{P1,P2\}
+\Define Peer = \{N1,N2\}
 \Define NoTransit =
@@
 %
-We define a $\CD{Peer}$ to be either $\CD{P1}$ or $\CD{P2}$ and disallow paths where traffic both enters the datacenter through a peer and exits through a peer.
+We define a $\CD{Peer}$ to be either $\CD{N1}$ or $\CD{N2}$ and disallow paths where traffic both enters the datacenter through a peer and exits through a peer.
 Finally, we can combine these constraints together as follows:
@@
 
-Configuration synthesis for network configurations is challenging for a number of reasons.
+%Configuration synthesis for network configurations is challenging for a number of reasons.
 First, although \sysname polices specify network-wide routing behavior, actual configurations are per-device and run distributed algorithms to compute routes.
@@
 
-In this section, we formalize the \sysname language and describe how \sysname translates policies to a graph-based intermediate representation.
-
-\subsection{Methane Language}
+%In this section, we formalize the \sysname language and describe how \sysname translates policies to a graph-based intermediate representation.
+
+%\subsection{Methane Language}
 
@@
      pol     &::=& p_1, \dots, p_n & \textit{policy} \\
-     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{path preferences} \\
+     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT a & \textit{path preferences}  \\
      t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \textit{predicate} \\
+     a      &::=& agg(t, r_1 \rightarrow r_2) & \textit{aggregation} \\
      r       &::=& l \BNFALT \emptyset \BNFALT \In \BNFALT \Out \BNFALT r_1 \cup r_2 \BNFALT & \textit{regular path} \\
@@
   \vspace{-.3em}
-  \caption{Simplified \sysname syntax.}
+  \caption{\sysname core syntax.}
   \label{fig:syntax}
@@
 
-The syntax introduced in \S\ref{sec:overview} is syntactic sugar for a core language based on regular expressions.
-Figure~\ref{fig:syntax} shows a simplified version of the core \sysname syntax that omits some details such as aggregation.
-The full langauge definition, including aggregation, can be found in the appendix.
-
-A policy has one or more constraints, each of which consists of a test on the type of traffic being matched and a list of regular expressions describing preferred network paths.
-Regular expressions are defined over network locations, where each location is either a router inside the operator's network, or an external neighbor connected to the operator's network.
-Two special characters \In~ and \Out, will match any internal and external location respectively.
-There are two types of predicates: a test for a concrete prefix $d.d.d.d/[d..d]$ matches a range of IP prefixes (\EG, 1.2.3.4/[24..32]) where metavariable $d$ represents an integer.
+The syntax introduced in \S\ref{sec:overview} is just syntactic sugar for a core language based on regular expressions. Figure~\ref{fig:syntax} shows the core \sysname syntax.
+%
+A policy has one or more constraints, each of which is either an aggregation constraint or a path constraint.
+Path constraints consists of a test on a prefix destination and a list of regular expressions describing preferred network paths.
+Regular paths are defined over network locations, where each location is either a router inside the operator's network, or an external neighbor connected to the operator's network.
+Values \In~ and \Out, will match any internal and external location respectively.
+There are two types of predicates: a test for a concrete prefix $d.d.d.d/[d..d]$ matches a range of IP prefixes (\EG, 10.0.1.0/[24..32]) where metavariable $d$ represents an integer.
 
@@
 %
-Preferences are lifted to the top level of the regular expression when their use is unambiguous, and separate sets of constraints are joined prefix-by-prefix by taking the intersection of their constraints.
+Preferences are lifted to the top level of the regular expression when their use is unambiguous, and separate sets of constraints are joined prefix-by-prefix by taking the set intersection of their constraints.
 
@@
 
-\subsection{Product Graph}
-
 A key step for \sysname to generate device configurations is to build a data structure amenable to joint analysis of both the topology and routing policy.
-Intutively, \sysname captures both topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology into a data structure called the Product Graph.
-
-The Product Graph is a compact representation of all paths distributed protocol messages might be passed through the network in order to find policy-compliant paths dynamically.
+Intutively, \sysname captures both topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology into a data structure called the Product Graph~\cite{propane}.
+
+The Product Graph compactly encodes all paths protocol messages should be passed along through the network in order to guarantee the devices find policy-compliant paths dynamically.
 %
@@
 
-\para{Product Graph construction}
-
-We construct a Product Graph in the following way.
-For each regular expression constraint $r_i$ from $r_1 ~\Prefer~ ..
+For each regular path constraint $r_i$ from $r_1 ~\Prefer~ ..
 ~\Prefer~ r_k$, we construct a DFA for the reverse of $r_i$.
@@
 
-Figure~\ref{fig:example-compilation} shows an example of a Product Graph for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview} ($\True ~\Path~ \CD{\Exit(Peer1)} ~\Prefer~ \CD{\Exit(Peer2)}$).
+Figure~\ref{fig:example-compilation} shows an example of a Product Graph for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview} ($\True ~\Path~ \CD{\Exit(N1 \Prefer~N2)}$).
 %
@@
 %
-The first automaton represents the more preferred constraint $\CD{\Exit(Peer1)}$ and the second automaton represents the less preferred constraint $\CD{\Exit(Peer2)}$.
-The Product Graph representation is shown for both an instance of a simple concrete network matching the abstraction from \S\ref{sec:overview} as well as for the abstract topology itself.
-
-Each node in the Product Graph tracks both where a protocol message is in the topology as well as how much progress has been made towards satisfying each policy constraint.
-In this example, all routes that eventually leave through Peer1 (protocol message sent from $P_1$) will lead to an accepting state for the first automaton and all routes that eventually leave through Peer2 will lead to an accepting state for the second automaton.
-
-One interesting observation is that the Product Graph for both the concrete and abstract networks share a similar structure. This leads us to the following observation
+The first automaton represents the more preferred constraint $\CD{\Exit(N1)}$ and the second automaton represents the less preferred constraint $\CD{\Exit(N2)}$.
+The Product Graph is shown for both an instance of a simple concrete network matching the abstraction from \S\ref{sec:overview} as well as for the abstract topology.
+
+Paths through the Product Graph represent paths through the topology that protocol messages may use to ensure policy-compliant.
+For example, in the concrete Product Graph, all messages from N1 are not blocked at each spine router.
+Paths for a destination learned through N1 will end in an accepting state for the first automaton (\EG, node (T1,1,0)).
+Similarly, paths for a destination learned through N2 will end in an accepting state for the second automaton.
+
+One interesting observation is that the Product Graph for both the concrete and abstract networks share a similar structure. This leads us to the following observation:
 
 \begin{defn}
-If we have a graph homomorphism $f : G \rightarrow G^A$, concrete product graph $PG = (G',start,P)$ and abstract product graph $PG^A = (G'^A, start^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$:
+If we have a graph homomorphism $f : G \rightarrow G^A$, concrete product graph $PG = (G',\mathit{start},P)$ and abstract product graph $PG^A = (G'^A, \mathit{start}^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$:
 \[ \begin{array}{rcl}
-  f_{pg}( s ) & = & s^A  \\
+  f_{pg}( \mathit{start} ) & = & \mathit{start}^A  \\
   f_{pg}( (l,q_1,\ldots,q_n) ) & = & (f(l),q_1,\ldots,q_n) \\
@@
 
-\para{Memory shape analysis} \todo{Sagiv, others}
-
 %\para{Configuration synthesis}

### 2016-11-12 paper/abstraction/paper.tex
edit 6.1

@@
 
-In practice, operators would often like to reason about a variety of properties for, not only their current network topology, but also future versions of it.
-In this section we present an analysis that operates over the network abstraction to find a lower bound on the number of disjoint paths between pairs of concrete nodes.
+%In practice, operators would often like to reason about a variety of properties for, not only their current network topology, but also future versions of it.
+The Product Graph provides a convenient representation to capture the joint impact of both topology and routing policy.
+In this section we present an analysis that operates over the abstract Product Graph to find a lower bound on the number of disjoint paths between pairs of concrete nodes.
 Answering questions about the number of disjoint paths between nodes allows operators to reason about many useful network properties such as reachability (\IE, is there at least one path) and fault tolerance (\EG, how many failures will disconnect certain routers).
-Because the analysis takes place over the product graph rather than the topology, it is able to take into account the constraints imposed by the routing policy.
 
@@
 
-In order to infer bounds on the number of disjoint paths between concrete nodes we use information about the structure of the underlying concrete topologies encoded in the abstraction constraints.
-%
-The idea is to maintain, for each node in the abstract product graph, quantified facts learned about the number of disjoint paths from a source node to some number of concrete routers in that role.
+To infer bounds on the number of disjoint paths between concrete nodes we use information about the structure of the underlying concrete topologies encoded in abstraction constraints.
+%
+The idea is to maintain, for each node in the abstract Product Graph, facts learned about the number of disjoint paths to some number of concrete routers in the node's role.
 More specifically, we maintain facts of the form:
@@
 %
-Each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all".
-There is one label in for each pod label in the abstraction pod hierarchy.
-For a given node, $L_{X_1}$ would correspond to the outermost pod, $L_{X_{n-1}}$ would correspond to the innermost pod, and $L_{X_n}$ to the the node itself.
-
-Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete router in the abstract source role, for ``some"/``all" pods $X_1$, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds.
-The base case $L_{X_n}(j,k)$ means that for ``some"/``all" groups of size $j$ concrete routers, there are $k$ disjoint paths to each such that all $j*k$ paths are disjoint
+Each label $L \in \{S,A\}$ is either $S$, which stands for "some" or is $A$, which stands for "all".
+There is one label for each pod in the abstraction pod hierarchy.
+For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the the node itself.
+
+Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for "some"/``all" pods $X_1$, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds.
+The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers, there are $k$ disjoint paths to each such that all $j*k$ paths are disjoint.
 %
@@
 
-In order to learn information about disjoint paths between routers, we develop a series of sound inference rules for facts of this form.
+In order to learn information about disjoint paths, we develop a collection of sound inference rules for facts of this form.
 Figure~\ref{fig:inference-rules} shows each of the inference rules.
 The rules are read from bottom to top.
-The label on the bottom left corresponds to a known fact of the form described above.
-We use $L$ to represent a rule that is parametric over the particular label ($S$ or $A$).
-The labels on other nodes correspond to learned facts from applying the inference rule.
+The label on the bottom left represents a known fact of the form described above.
+We use $L$ to represent a rule that is parametric over the label ($S$ or $A$).
+The labels on other nodes correspond to facts learned after applying the inference rule.
 Conditions that must be \emph{valid} for the rule to apply are shown in a box next to the rule.
 
-In general, the inference rules try to learn information about both the largest number of disjoint paths to any single node in an abstract role and the largest reachable group in a particular role with at least one disjoint path to each.
+In general, the inference rules try to learn information about both the largest number of disjoint paths to any single node in an abstract role as well as the largest reachable group in a particular role with at least one disjoint path to each.
 
@@
 Since adding edges between the nodes keeps the existing paths disjoint, and since we can not exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the top node will be $min(j*k,e_1)$.
-However, since we do not know for certain that all $j$ nodes have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
+Since we do not know for certain that all $j$ nodes have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
 
@@
 This captures the fact that the remaining nodes ($m-j$) that are not part of the group in the bottom role, each have $e_1$ outgoing edges and must be able to at least "fill" the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each.
-Solving the inequality yields:
-%
-\[ \begin{array}{c}
-  g \geq n - \dfrac{(m-j)*e_1}{e_2}
-\end{array} \]
-\noindent
-%
+Solving the inequality gives the lower bound for $g$ used in Figure~\ref{fig:inference-rules}.
+
 The second part of the rule allows uses a similar idea to reason about the overlap between roles $m$ and $o$ with respect to role $n$.
@@
 
-The rule \infrule{I-mincut} can be thought of as an assertion about the fault tolerance between two roles.
+The rule \infrule{I-mincut} can be thought of as an assertion about the fault tolerance between nodes in two roles.
 The rule applies to an edge that has been annotated with a $mincut(X)$ statement, which means that there are at least $X$ disjoint paths between any node in role $m$ and any node in role $n$.

### 2016-11-12 paper/abstraction/paper.tex
edit 6.2

@@
 The rule \infrule{I-striping} is the most complicated case.
-It starts with the fact L$(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid given the constraints.
+It starts with the fact L$_m(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid given the constraints.
 The first inference for role $n$ tries to find the largest reachable group with disjoint paths to each.
@@
 %
-This captures the fact that the remaining nodes ($m-j$) that are not part of the group in the bottom role, each have $e_1$ outgoing edges and must be able to at least "fill" the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each.
+The remaining nodes ($m-j$) that are not part of the reachable group in the bottom role, each have $e_1$ outgoing edges and must be able to at least "fill" the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each.
 Solving the inequality gives the lower bound for $g$ used in Figure~\ref{fig:inference-rules}.
@@
 The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies the inference rules from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
-Inference rule conditions can be checked for validity over all concrete topologies using an SMT solver.
+Inference rule conditions are checked for validity over all concrete topologies using an SMT solver.
 In order to ensure termination, we make the observation that, for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
-Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimization framework $\nu$Z~\cite{z3opt}.
+Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing constraint solver $\nu$Z~\cite{z3opt}.
 
@@
 
-Consider again the datacenter example from \S\ref{sec:overview}.
-Suppose now we add the valleyfree constraint that traffic never takes a path with a down-up in it for the routing policy for global prefixes:
+Recall the policy for global prefixes in the datacenter. 
 %
 \begin{code}
-\$GP \Path \End(TG) \ensuremath{\cap} \Novalley(\{TG,TL\},\{AG,AL\},\{S\})
+\$GP \Path \End(TG) \ensuremath{\cap} 
+       \Novalley(\{TG,TL\},\{AG,AL\},\{S\}) \ensuremath{\cap} 
+       !(\Enter(Peer) & \Exit(Peer))
 \end{code}
@@
 %
-Figure~\ref{fig:example-inference} shows the abstract product graph representation for this routing policy.
+Figure~\ref{fig:example-inference} shows part of the abstract Product Graph representation for this routing policy.
 The inference algorithm starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$ (\IE, no restriction on the number of disjoint paths initially).
@@
 
-Note that, because each inference rule only applies to directed edges in the product graph, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
-It is this restriction that ensures that the analysis is both topology and policy dependent.
-
-The next step is to use \infrule{I-mesh2} together with \infrule{I-local} to infer than any single node in the TL role for any pod P is reachable via at least 2 disjoint paths.
+Note that, because each inference rule only applies to directed edges in the Product Graph, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
+This restriction ensures that the analysis is policy-sensitive.
+
+The next step is to use \infrule{I-mesh2} together with \infrule{I-local} to infer than any single node in the TL role for any pod Q is reachable via at least 2 disjoint paths.
 This process will continue until a fixed point is reached.
 
-In this case, the algorithm was able to infer that, with the valleyfree routing policy, any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a router in role TG.
+In this case, the algorithm was able to infer that any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a router in role TG.
 Note that, in this case, the analysis is precise.
 There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router due to the valleyfree constraint.
-In this case, a bound on the fault tolerance between a tor and spine router can be used to ensure that an aggregation-induced black hole will not occur at the border of the datacenter until a certain number of failures occur.
+In this case in particular, the bound on the fault tolerance between a tor and spine router can be used to determine that an aggregation-induced black hole may arise at the border of the datacenter after a single failures in some topologies.
 

### 2016-11-12 paper/abstraction/paper.tex
update compilation section 7

@@
 
-The first idea is to tag every protocol message with a BGP community value that encodes the state of each automaton when advertising a route to a neighbor.
-Routers can then allow route advertisements that correspond to an edge in the Product Graph and block those that don't.
-%This ensures that any path computed by BGP will be a valid path in the Product Graph, and thus is allowed by the policy.
-For example, in the concrete Product Graph in figure~\ref{fig:example-compilation}, router $S1$ will allow a route advertisement from its neighbor $P1$ and also from neighbor $P2$.
-If it uses the path provided by neighbor $P1$, then it will add the tag $(1,0)$ before informing its neighbors about this route.
-On the other hand, if it uses neighbor $P2$, then it will add the tag $(0,1)$ instead.
+The first idea is to tag every protocol message with a BGP community that encodes the state of each DFA when advertising a route to a neighbor.
+Routers then allow route advertisements that correspond to an edge in the Product Graph and block those that do not.
+For example, in the concrete Product Graph in figure~\ref{fig:example-compilation}, router S1 will allow an advertisement from its neighbors N1 and N2.
+If it uses the path advertised by neighbor N1, then it will add the tag $(1,0)$ before sending this to its neighbors.
+If it uses neighbor N2, then it will add the tag $(0,1)$ instead.
 
@@
 The second idea is to have each router totally order advertisements from neighbors.
-For example, to satisfy the policy that leaving through $\sf{P1}$ is preferred to leaving through $\sf{P2}$, router $S1$ should prefer a message it hears from $P1$ over one from $P2$.
-Similarly, router $A1$ should prefer routes tagged with $(1,0)$ over those tagged with $(0,1)$.
+For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, router S1 should prefer a message it hears from N1 over N2.
+Similarly, router A1 should prefer routes tagged with $(1,0)$ over those tagged with $(0,1)$.
 %In general, because BGP is distributed, each router does not have a full view of the entire network when choosing which path to use.
 Because finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem,
-Propane introduced a conservative, yet effective algorithm for determining route preferences based on the following observation about the structure of the Product Graph:
+Propane introduced a conservative search strategy for determining route preferences.
+To make this work for abstract topologies, we modify the search based on the following observation about the structure of the Product Graph:
 
@@
 Let $m \geq_{rank} n$ be a relation over Product Graph vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$.
-Intuitively $m \geq_{rank} n$ means that paths ending at PGIR node $m$ are no better than paths ending at $n$.
+Intuitively $m \geq_{rank} n$ means that paths ending at Product Graph node $m$ are no better in terms of preference than paths ending at $n$.
 %
@@
 
-If each router has a total order with respect to the simulation relation ($\leq$) for its corresponding Product Graph nodes, then we simply sort the nodes and prefer advertisements from peers of node $m$ over those of node $m'$ if $m' \leq m$.
+If we determine that each router has a total order with respect to the simulation relation ($\leq$) for its corresponding Product Graph nodes, then we can simply sort the nodes and prefer advertisements from peers of node $m$ over those of node $m'$ whenever $m' \leq m$.
+This condition ensures that BGP devices will converge to the most preferred paths in the network even when failures occur.
 %
@@
 This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$.
-Therefore, advertisements received at $S1$ in state $(1,0)$ must be preferred to those received in state $(0,1)$.
-
-Notice also that in the abstract product graph the inequality $(S,0,1) \leq (S,1,0)$ holds. This leads us the the following observation:
+Therefore, advertisements received at $S1$ in state $(1,0)$ must be preferred to those received at $S1$ in state $(0,1)$.
+%
+Notice that in the abstract product graph $(S,0,1) \leq (S,1,0)$ also holds. This leads us the the following observation:
 
@@
 \label{lem:preference}
-$m \leq m'$ in the concrete product graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph under the lifted graph homomorphism $f_{pg}$.
+$m \leq m'$ in the concrete Product Graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract Product Graph.
 \end{lem}
 
-Lemma~\ref{lem:preference} gives us reason to believe that we can perform compilation over the abstract product graph and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.
+This gives us reason to believe that we can perform compilation over the abstract product graph directly and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.
 
@@
 In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
-Figure~\ref{fig:bgp-configs} shows part of the final configuration for spine routers for the concrete and abstract policies.
-%
-For prefix $0.0.0.0/[0..32]$, the spine routers will match advertisements from peer $P1$ and $P2$.
-The match for $P1$ is preferred since it has a higher BGP local-preference attribute (110).
-If an advertisement from $P1$ is available the spine uses this and attaches the community tag $(1,0)$ and advertises the route to all its peers.
-If only an advertisement from the backup $P2$ is available, then it attaches the tag $(0,1)$ and advertises this to all peers instead.
-%
-There is also additional policy for the Product Graphs from constraints for the local and global prefixes.
-In the template configuration, it matches any global prefix from any internal peer and re-advertise the route to all of its peers.
-For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers (thus implementing the Local constraint).
+Figure~\ref{fig:bgp-configs} shows part of the final configuration for spine routers for the concrete and abstract policies in a vendor-neutral syntax.
+%
+For prefix $\True$ ($0.0.0.0/[0..32]$), the spine routers will match advertisements from peer N1 and N2.
+The match for N1 is preferred since it has a higher BGP local-preference attribute (110).
+If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers.
+If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
+%
+The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertise the route to all of its peers ($*$).
+For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers.
 The concrete configurations have a similar configuration for each local and global prefix.

### 2016-11-12 paper/abstraction/paper.tex
edit section 8

@@
 \newcommand{\propane}{{\small \sf Propane}\xspace}
+\newcommand{\mbgp}{{\small \sf mBGP}\xspace}
 
@@
 
-\section{Concretization}
-
-One interesting observation is that the spine template configuration and concrete spine configurations are structured similarly.
-In this section, we formalize this observation.
-We introduce a simple language for BGP configurations called ABGP and define compilation policies over both concrete and abstract topologies to ABGP.
-In addition we define a concretization function for that translates an abstract \sysname policy or ABGP configuration to a concrete \sysname policy or ABGP configuration respectively.
-The main result is that the compilation and concretization functions commute.
-This means performing compilation over the abstract representation first allows us to generate templates, and only concretize these templates when we need to instantiate the network.
+\section{Properties}
+
+\para{Concretization}
+
+One observation is that the spine template configuration and concrete spine configurations are structured similarly.
+We formalize this idea by defining a simple, vendor-neutral language for BGP configurations called \mbgp and formally define compilation for policies over both concrete and abstract topologies to \mbgp.
+In addition we define a two concretization ($con$) functions that translates an abstract \sysname policy and \mbgp configuration to a concrete \sysname policy and concrete \mbgp configuration respectively.
+Concretization takes a context $\Gamma : \mathit{Var} \rightarrow 2^{\mathit{Prefix} \times V}$ that maps each template variable to a set of pairs of a concrete prefix and topology location where the prefix is owned.
+The main theoretical result is that the compilation and concretization functions commute.
+More specifically:
 
@@
   For any context $\Gamma$, topology $G$, abstract topology $G^A$, homomorphism $f : G \rightarrow G^A$, and policy $pol$,
-  $$\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$$
+
+  \noindent
+  $\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$
+  \label{thm:concretization}
 \end{thm}
-
-\subsection{Incrementality}
-
-Suppose that we want to expand our example concrete datacenter by adding an additional tor router in the TG role.
-Per the network routing policy, this new tor router will advertise its new owned prefix.
+%
+\vspace{-1em}
+Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix.
+
+\para{Incrementality}
+
+Suppose that an operator want to expand the concrete datacenter by adding an additional ToR router to the TG role.
+Per the network routing policy, the new ToR router will advertise any owned prefixes provided by looking up {\small \$GP} in $\Gamma$.
 Because the new topology matches the abstraction, the compiled templates will remain the same.
-However, in the spine router configurations, the match on the global prefix template variable \$GP will be expanded to include the new prefix owned by the added tor.
-In other words, the concrete configurations obtained after substitution will include an additional match on the new prefix.
-Unfortunately, this means that a small change to the topology can result in many configurations far from the change needing to change too.
-
-The key insight is that the template variables tell us exactly where change can happen.
-For example, the only way in which the spine routers depend on anything non-local is in the match on prefix template variables.
-Instead, we can associate a new unique community tag for each template variable like \$GP.
-We can replace each match on \$GP with a test on the new community tag.
-The new added tor will now simply attach the new community tag to advertisements for its prefix so downstream routers can just match the community tag.
-This ensures that each router has a template that has no dependency on any other non-adjacent router.
-If we make a change to the concrete network that matches the abstraction, then the templates do not change, and thus only configurations adjacent to the changes must also change.
+However, in the spine router configurations, the match on the global prefix template variable {\small \$GP} must be expanded when concretizing the template to include the new prefixes added by the ToR.
+Unfortunately, this small change to the topology results in a change to every single spine router configuration.
+
+However, template variables tell us exactly where this kind of change can happen.
+The only way in which the spine routers depend on anything non-local is in the match on prefix template variables.
+Instead, we can associate a new unique community tag for template variable {\small \$GP} and then replace each match on {\small \$GP} with a test on the new community tag.
+The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can just match the community tag.
 

### 2016-11-12 paper/abstraction/paper.tex
edit eval section

@@
 
-\section{Implementation and Evaluation}
-\label{sec:evaluation}
+\section{Implementation}
+\label{sec:implementation}
 
 The \sysname compiler is implemented in approximately 9500 lines of F\# code.
-The compiler accepts both concrete and abstract topologies and will generate router configurations for open-source Quagga routers.
-Operators can specify their required fault tolerance level for aggregation safety.
-The abstract safety analysis uses $\nu$Z~\cite{z3opt} test validity and to minimize variables subject to the annotated constraints.
-Since the analysis typically calls the SMT solver with many times with relatively simple optimization problems, we use a timeout of 200ms.
+The compiler accepts both concrete and abstract topologies and will generate configurations for open-source Quagga routers by default.
+The abstract analysis uses $\nu$Z~\cite{z3opt} to test validity and to minimize variables subject to the annotated constraints.
+Since the analysis typically calls the SMT solver many times with relatively simple optimization problems, we use a short timeout of 200ms.
 
@@
 
+\section{Evaluation}
+\label{sec:evaluation}
+
 To evaluate \sysname, we apply it on policies for backbone and datacenter networks.
-We aim to evaluate the expressiveness of our abstract multiplicity annotations, the precision of the abstract disjoint-path analysis, and the compilation time of \sysname both with abstraction and without.
+We aim to evaluate the expressiveness of our abstracttions, the precision of the abstract disjoint-path analysis, and the compilation time of \sysname both with abstraction and without.
 
@@
       \hline
-      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
+      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachability} & \textbf{K-paths} \\ \hline
       Fattree~\cite{fattree} & & \cmark & \cmark  \\ \hline
@@
       BCube~\cite{bcube} & $k$ & \cmark & \xmark \\ \hline
-      DCell~\cite{dcell} & $k$ & \cmark & \xmark \\ \hline
+      Dcell~\cite{dcell} & $k$ & \cmark & \xmark \\ \hline
          %& HCN & $h$ & \cmark & \xmark \\
@@
 
-We evaluate the expressiveness and precision of our abstract analysis on a range of different network topologies found in both the network literature and production.
-For each topology in figure~\ref{fig:analysis-precision} we define a suitable abstraction.
-Since many topologies have tunable parameters (e.g., the recursion depth $k$ for the DCell topology), we list all such parameters that are fixed for our abstraction.
+We evaluate the expressiveness and precision of our abstract analysis on a range of different network topologies found in network literature and in production networks.
+For each topology in Figure~\ref{fig:analysis-precision} we define a suitable abstraction.
+Since many topologies have tunable parameters (e.g., the recursion depth $k$ for the Dcell topology), we list all such parameters that are fixed for our abstraction.
 We implement a shortest path routing policy over the topology and record the precision of the abstract analysis in terms of whether or not it is able to accurately prove reachability and/or the correct number of disjoint paths between all pairs of nodes.
@@
 
-The Fat Tree topology is one of the most widely used datacenter topologies.
-We look at the precision of our analysis on four variants of the Fat Tree topology used in practice: a Standard Fat Tree~\cite{fattree}, the Facebook Fat Tree~\cite{facebook-fattree}, the F10 fault tolerant Fat Tree~\cite{f10-fattree}, and the VL2 topology~\cite{vl2-fattree}.
-For each Fat Tree variant, we use a tiered abstraction similar to that in our previous example.
-Each Fat Tree topology is parameterized over the number of pods $k$, which can be scaled up in the abstraction to allow for expansion.
-For all Fat Tree variants, the analysis is precise enough to determine the exact number of disjoint paths between all pairs of concrete routers.
+The fat tree topology is a widely used datacenter topology.
+We look at the precision of our analysis on four fat tree variants used in practice: a standard fat tree~\cite{fattree}, the Facebook fat tree~\cite{facebook-fattree}, the F10 fault tolerant fat tree~\cite{f10-fattree}, and the VL2 topology~\cite{vl2-fattree}.
+For each fat tree variant, we use a tiered abstraction similar to that in our previous example.
+Each fat tree topology is parameterized over the number of pods $k$, which can be scaled up in the abstraction to allow for expansion.
+For all fat tree variants, the analysis is precise enough to determine the exact number of disjoint paths between all pairs of concrete routers.
 
@@
 
-We also model several recursive topologies using our abstractions.
+We also model several recursive topologies.
 These include the BCube~\cite{bcube} and Dcell~\cite{dcell} topologies.
 Each topology includes a recursion depth parameter ($k$), which we must fix.
-For a recursive topology with depth $d$, we model it as an abstract topology consisting of abstract nodes for each of the depth $d-1$ subcomponents.
+For a recursive topology with depth $d$, we model it as an abstract topology consisting of an abstract node for each of the depth $d-1$ subcomponents.
 This allows for safe expansion within a subcomponent, but not from increasing the recursion depth.
@@
 Hypercube variants can be used as an alternative to Clos-style topologies for networks with high-radix (port density) routers.
-The HyperX~\cite{hyperx} topology can be viewed as a generalization of the hypercube and butterfly topologies, which includes parameters $L$ for the lattice dimension of the network, $S_i$ for the node multiplicity of each dimension $i$, $K_i$ for the bandwidth of links for each dimension, and $T$ for the number of terminal nodes (servers) connected to each router.
+The HyperX~\cite{hyperx} topology can be viewed as a generalization of the hypercube and butterfly topologies, which includes parameters $L$ for the lattice dimension of the network, and $S_i$ for the node multiplicity of each dimension $i$.
+%$K_i$ for the bandwidth of links for each dimension, 
+%and $T$ for the number of terminal nodes (servers) connected to each router. 
 For a fixed number of dimensions $L$, we abstract each full mesh of $S_L$ nodes into its own abstract node.
 The $S_{x-1}$ groups of abstract nodes can be captured using pods of the abstract $S_x$ nodes.
+For all hypercube variants, the abstract analysis is precise.
 
@@
 
-Routers in the datacenter network run BGP using private AS numbers and peer with each other and with the backbone network over eBGP.
+Routers in the datacenter network run BGP using private AS numbers and peer with each other and with backbone networks over BGP as well.
 The routers aggregate some prefix blocks when announcing them to the backbone network, and they keep some prefixes internal.
-The policy also ensures bogons and private address space from external neighbors is dropped.
+The policy also ensures that private address space from external neighbors is dropped.
 The data center prefers that traffic leave through certain peers over others and ensures that transit traffic between peers is never allowed in the datacenter.
 
-The backbone network classifies external neighbors into several different categories based on commercial relationship and prefers paths through them in order.
-Similar to the datacenter, it prevents bogons and private address space from external neighbors, drops transit traffic between certain peers but not through others, and aggregates internal prefixes at the border of the network.
+The backbone network classifies neighbors into several categories based on commercial relationship and prefers paths through them in order.
+Similar to the datacenter, it prevents private address space from external neighbors, drops transit traffic between certain peers but not through others, and aggregates internal prefixes at the border of the network.
 
@@
 
-For both networks, we use the same routing policy but scale the size of the underlying topology.
-For the datacenter networks, we use a standard Fat Tree topology and scale the size of the topology according the the number of pods $k$, starting with 4 pods and ending with 24 pods.
-The abstract topology uses a single abstract node for each tier of the datacenter, an additional abstract node for tier 0 to separate local and global prefixes, as well as a single abstract node for each group of equivalent eBGP neighbor.
-
-For the backbone networks, we split the network into two parts: a collection of border routers and a fully-connected internal core.
+For both networks, we use the fix routing policy but scale the size of the underlying topology.
+For the datacenter networks, we use a fat tree topology and scale the size of the topology according the the number of pods $k$, starting with 4 pods and ending with 24 pods.
+The abstract topology uses one abstract node for each tier of the datacenter with an additional abstract node to separate local and global prefixes.
+A single abstract node is used for each class of neighbor.
+
+For the backbone networks, we split the network into two parts: a collection of border routers and an internal core.
 We scale the backbone networks from 10 to 250 routers.
 The abstract topology uses a single abstract node for the network border routers and another abstract node for the network core.
-Backbone eBGP-speaking peers are grouped into abstract nodes based on their commercial relationship to the current AS (e.g., customer, provider, peer).
+Backbone neighbors are grouped into abstract nodes based on their commercial relationship to the current AS (e.g., customer, provider, peer).
 
@@
 Figure~\ref{fig:compilation-times} shows compilation time for the same policies for both the abstract and concrete versions of the policies described above.
-All experiments are run on an 8 core, 2.4 GHz Intel i7 processor Mac with 8GB of Ram.
-
-For both the datacenter and backbone networks, the abstract compilation starts off slightly slower than concrete compilation for small topologies due to the overhead of the abstract k-disjoint path analysis for aggregation black-hole safety.
+All experiments are run on an 8 core, 2.4 GHz Intel i7 processor Mac with 8GB of Ram, and the time taken is the average of 3 runs.
+
+For both the networks, the abstract compilation starts off slightly slower than concrete compilation for small topologies due to the overhead of the abstract analysis for fault-tolerance.
 However, as the size of the topology increases, abstract compilation becomes orders of magnitude faster than concrete compilation.
@@
 In particular, the number of calls to $\nu$Z remains constant the across topology size.
-The seesaw behavior for the data center networks results from differences in time taken by $\nu$Z to minimize the same constraints with different parameters.
+The seesaw behavior for the data center networks results from differences in time taken by $\nu$Z to minimize similar constraints with different values.
 

### 2016-11-12 paper/abstraction/paper.tex
rework eval section

@@
 %
-Each constraint desugars to a regular expression. For example, the constraint $\Always\CD{(\In)}$ becomes $\In^*$ and the constraint $\CD{\End(T0)}$ becomes $\mathtt{\Sigma}^* \cdot \CD{T0}$.
+Each constraint desugars to a regular expression. For example, the constraint $\Always\CD{(\In)}$ becomes $\In^*$ and the constraint $\CD{\End(TG)}$ becomes $\mathtt{\Sigma}^* \cdot \CD{TG}$.
 %
@@
       \transition{0}{0}{out}{loop above}
-      \transition{0}{1}{Peer1}{}
+      \transition{0}{1}{N1}{}
       \transition{1}{1}{in}{loop above}
@@
       \transition{0}{0}{out}{loop above}
-      \transition{0}{1}{Peer2}{}
+      \transition{0}{1}{N2}{}
       \transition{1}{1}{in}{loop above}
@@
 
-  \caption{Product graph construction for policy $\True ~\Path~ \CD{\Exit(\text{Peer1}} ~\Prefer~ \CD{\text{Peer2})}$.}
+  \caption{Product graph construction for policy $\True ~\Path~ \CD{\Exit(\text{N1}} ~\Prefer~ \CD{\text{N2})}$.}
   \label{fig:example-compilation}
@@
 We evaluate the expressiveness and precision of our abstract analysis on a range of different network topologies found in network literature and in production networks.
+The analysis is precise if it finds a tight lower-bound on the fault-tolerance (\IE, there is actually a concrete network with that fault tolerance).
 For each topology in Figure~\ref{fig:analysis-precision} we define a suitable abstraction.
-Since many topologies have tunable parameters (e.g., the recursion depth $k$ for the Dcell topology), we list all such parameters that are fixed for our abstraction.
-We implement a shortest path routing policy over the topology and record the precision of the abstract analysis in terms of whether or not it is able to accurately prove reachability and/or the correct number of disjoint paths between all pairs of nodes.
+Since many topologies have tunable parameters (\EG, the recursion depth $k$ for the Dcell topology), we list all such parameters that are fixed for the abstraction.
+We implement a shortest path routing policy over the topology and record the precision of the analysis in terms of whether or not it is able to accurately prove reachability and/or the correct number of disjoint paths between all pairs of nodes.
 
@@
 We evaluate compilation time in \sysname both with and without abstraction using routing policy for backbone and datacenter networks inspired by configurations obtained from a large cloud provider.
-
-\para{Routing Policy}
+For both types networks, we fix routing policy but scale the size of the underlying topology.
+
+\para{Datacenter}
 
@@
 
-The backbone network classifies neighbors into several categories based on commercial relationship and prefers paths through them in order.
-Similar to the datacenter, it prevents private address space from external neighbors, drops transit traffic between certain peers but not through others, and aggregates internal prefixes at the border of the network.
-
-\para{Network Topology}
-
-For both networks, we use the fix routing policy but scale the size of the underlying topology.
-For the datacenter networks, we use a fat tree topology and scale the size of the topology according the the number of pods $k$, starting with 4 pods and ending with 24 pods.
+We use a fat tree topology and scale the size of the topology according the the number of pods $k$, starting with 4 pods and ending with 24 pods.
 The abstract topology uses one abstract node for each tier of the datacenter with an additional abstract node to separate local and global prefixes.
@@
 
+\para{Backbone}
+
+The backbone policy classifies neighbors into several categories based on commercial relationship and prefers paths through them in order.
+Similar to the datacenter, it drops private address space from  neighbors, drops transit traffic between certain peers but not others, and aggregates internal prefixes at the border of the network.
+
 For the backbone networks, we split the network into two parts: a collection of border routers and an internal core.
 We scale the backbone networks from 10 to 250 routers.
-The abstract topology uses a single abstract node for the network border routers and another abstract node for the network core.
+The abstract topology uses a single abstract node for the network border routers and another abstract node for the network core with mincut annotation both within the core and between the core and border roles.
 Backbone neighbors are grouped into abstract nodes based on their commercial relationship to the current AS (e.g., customer, provider, peer).

### 2016-11-12 paper/abstraction/paper.tex
typos

@@
 we introduce several additional concepts.
-The first is the idea of a topology hierarchy captured by P and Q, which say that nodes in the tor and aggregator roles are grouped into a number of smaller pods.
+The first is the idea of a topology hierarchy captured by P and Q, which say that nodes in the ToR and aggregator roles are grouped into a number of smaller pods.
 The second is a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
@@
 
+\dpw{we could flip the order of this description:  give simple concrete $S_A(j,k)$ first and
+then go to the general.}
 To infer bounds on the number of disjoint paths between concrete nodes we use information about the structure of the underlying concrete topologies encoded in abstraction constraints.
@@
 Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for "some"/``all" pods $X_1$, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds.
-The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers, there are $k$ disjoint paths to each such that all $j*k$ paths are disjoint.
+The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers, there are $k$ edge-disjoint paths to each such that all $j*k$ paths are disjoint.
 %

### 2016-11-12 paper/abstraction/paper.tex
edits to 4

@@
 \newcommand{\Novalley}{\KW{novalley}}
-
+\newcommand{\Mincut}{\mathit{mincut}}
 \renewcommand{\path}[2]{ #1 \mapsto \ensuremath{#2} }
@@
 In general, we need not bound the number of spine routers to admit more concrete topologies, potentially at the expense of analysis precision.
-Finally, we include the constraints $(S \mod AG) = 0$, and $(S \mod AL) = 0$ simply to show that constraints do not have to be inequalities.
-In general operators can write constraints using logical formula from any theory supported by modern SMT solvers.
-
-A final type of abstraction is the $mincut(1)$ constraint between the spine role S and N[1--2].
+We include the constraints $(S \mod AG) = 0$, and $(S \mod AL) = 0$ simply to show that constraints do not have to be inequalities.
+Operators can write constraints using logical formula from any theory supported by modern SMT solvers.
+
+A final type of abstraction is the $\Mincut(1)$ constraint between the spine role S and N[1--2].
 The mincut constraint says that any node in the spine role has at least one path to any node in the neighbor N1 (and N2) role.
-Annotations of this form are often useful for a "one big switch" \ryan{cite} type of abstraction where part of a complex network is abstracted into a single node.
-For example, to model an ISP backbone network the operator might abstract the network into separate geographic regions with two abstract roles per region -- one role for the border routers of the network, and another role for the core of the network.
-Mincut annotations could be used to describe the fault tolerance both within region cores as well as across regions.
+Annotations of this form are often useful for a "one big switch" abstraction \cite{Casado:2010} in which part of a complex network is represented as a single node.
+For example, to model an ISP backbone network the operator might divide the network into separate geographic regions with two abstract roles per region -- one role for the border routers of the network, and another role for the core of the network.
+Mincut annotations can be used to describe the degree of fault tolerance both within region cores as well as across regions.
 
@@
 \para{Routing policy} Routing policies in \sysname consist of an ordered sequence of both a predicate matching a class of traffic and a list of ranked constraints on the paths that the traffic matching the predicate should prefer to take through the network.
-We borrow syntax from Propane~\cite{propane} but, instead of concrete prefixes and nodes, \sysname specifications can use abstract prefixes and nodes.
+We borrow syntax from Propane~\cite{propane}, but instead of concrete prefixes and nodes, \sysname specifications can use abstract prefixes and nodes.
 
 Let us see how to configure each of the datacenter networks from \S\ref{sec:motivation} by writing a \sysname routing policy over the abstract topology.
-We can capture the basic routing behavior, constraints (1, 2, 6), for the datacenters with the following policy:
+We can capture the basic routing behavior, constraints (1, 2, 6), for the datacenters as follows:
 %
@@
 
-If \sysname finds that the fault-tolerance policy can be met, it generates templates for the abstract topology, which can be instantiated into BGP configurations based on the concrete topology.
-During concretization, we confirm that the concrete topology adheres to the abstract topology.
+If \sysname finds that the fault-tolerance policy can be met, it generates templates for the abstract topology.  Per-device BGP configurations can in turn be generated from the templates 
+using information in the concrete topology. To ensure the process is sound, 
+\sysname checks that the given concrete topology is an instance of the abstract topology.
 

### 2016-11-12 paper/abstraction/paper.tex
update images
edits to 4

@@
 Second, \sysname checks if the fault-tolerance policy can be met by considering the joint impact of the abstract topology and routing policy.
-Joint analysis is needed, because connectivity for traffic will suffer even when functional paths exists in the topology if those paths are not allowed by routing policy.
-It implies that we cannot use standard graph theoretic algorithms.
-
-Instead, we develop a sound analysis based on computing the minimum number of disjoint policy-compliant paths between pairs of nodes over abstract topologies.
-If this number for a pair of nodes is less than the desired fault-tolerance level, \sysname declares that the policy cannot be met.
-
-Suppose we want to compute the number of of disjoint paths between any global ToR and spine router in Figure~\ref{fig:example3} for any concrete topology after applying the routing policy.
+Joint analysis is needed, because connectivity depends on both: traffic will not flow along
+valid topological paths if the routing policy disallows it. 
+\dpw{I deleted this:  ``It implies that we cannot use standard graph theoretic algorithms.''  I don't know of any ``standard'' graph-theoretic algorithm
+we could use but I can't completely rule it out either because I don't
+know all graph theoretic algorithms and it wouldn't completely shock 
+me if somewhere there were algorithms for analyzing graphs modulo
+isomorphisms that might be related tangentially.  Basically, I think
+it brings up the possibility that we should compare with graph-theoretic
+algorithms but then we don't do so in any detail
+so I thought it was better to drop it.}
+
+Instead, we develop a sound analysis based on computing the minimum
+number of edge-disjoint policy-compliant paths between pairs of nodes
+over abstract topologies. If this number for a pair of nodes is less
+than the desired fault-tolerance level, \sysname declares that the
+policy cannot be met.  More specifically,
+for each abstract role in the network, our analysis will learn facts about the
+number of disjoint paths to routers in that role.  For example,
+the fact $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
+in the $S$ (Spine) role, there are 6 disjoint paths to the group---3 
+for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
+\emph{some} group of 2 nodes has the property as opposed to all.
+More generally, there is one quantifier ($A$ for all groups
+and $S$ for exists a group).  When nodes are nested within pods,
+there is one quantifier for each level of the hierarchy, so
+$S_P S_{TG} (i,j)$ means that for some pod from the $P$ group of pods
+and for some nodes in the $TG$ role within that pod, there exists a
+group of $i$ nodes with $j$ paths to each node in the group.
+
+As an example, suppose we want to compute the number of of disjoint paths 
+between any
+global ToR and spine router in Figure~\ref{fig:example3}.
 %This can be used as a lightweight verification tool to detect certain classes of configuration bugs.
 For example, since the network is performing prefix summarization at the border of the datacenter, we might introduce a black hole after enough failures occur to disconnect a tor from a spine router.
-For each abstract role in the network, we learn invariants about the number of disjoint paths to routers in that role.
-These invariants contain a sequence of labels followed by a pair of numbers $(i,j)$.
-For example, the analysis would start with a fact of the form: $S_P S_{TG} (1,1)$.
-This means that, there is some group of nodes of size 1 in the TG role in some pod P such that any initial node in the TG role has 1 disjoint path to it (and all such paths are edge-disjoint).
-Since we know that the each node in the TG role is in a full mesh with nodes in the AG role within any given pod, we might infer a fact for AG of the form: $S_P A_{AG}(e1,1)$.
-This says that any group of nodes of size e1 in the AG role is reachable with at least 1 edge-disjoint path to each such node from any initial node in the TG role.
-%
-After one more inference the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node 
-In fact, due the the valley-free routing constraint, a single path is the most information we can infer, since this is exactly the worst-case fault-tolerance for the concrete network from Figure~\ref{fig:example2}.
+The analysis begins with the fact
+$S_P S_{TG} (1,1)$---there is some group of
+nodes of size 1 in the $TG$ role in some pod $P$ such that any initial
+node in the $TG$ role has 1 disjoint path to it (and all such paths are
+edge-disjoint). Since the abstract topology specifies that each node in 
+the $TG$ role is in
+a full mesh with nodes in the $AG$ role within any given pod, we 
+infer the fact $S_P A_{AG}(e1,1)$. This says that
+any group of nodes of size e1 in the $AG$ role is reachable with at
+least 1 path to each such node from any initial node in
+the $TG$ role.
+%
+After one more step, the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node 
+In fact, due the the valley-free routing constraint, a single path is 
+the worst-case fault-tolerance level for the concrete network from 
+Figure~\ref{fig:example2}.
 
@@
 \begin{figure}[t!]
-  \begin{code}
-    \Template{S}
-      Match[100] \PREFIX=\$GP, \PEER=\{AG, AL\}
-        \PEER \Arrow *
-      Match[100] \PREFIX=\$LP, \PEER=\{AG, AL\}
-        \PEER \Arrow \{AG, AL\}
-      Match[110] \PREFIX=true \PEER=\{P1\},
-        \PEER \Arrow *, \COMM \Arrow (1,0)
-      Match[100] \PREFIX=true \PEER=\{P2\},
-        \PEER \Arrow *, \COMM \Arrow (0,1)
-      ...
-  \end{code}
-
-  \vspace{-2em}
-  \begin{code}
-    \Router{S1, S2}
-      Match[100] \PREFIX=GP1, \PEER=\{AG1, AL1, ...\}
-        \PEER \Arrow *
-      Match[100] \PREFIX=GP2, \PEER=\{AG1, AL1, ...\}
-        \PEER \Arrow *
-      ...
-      Match[100] \PREFIX=LP1, \PEER=\{AG1, AL1, ...\}
-        \PEER \Arrow \{AG1, AL1, ...\}
-      Match[100] \PREFIX=LP2, \PEER=\{AG1, AL1, ...\}
-        \PEER \Arrow \{AG1, AL1, ...\}
-      ...
-      Match[110] \PREFIX=true, \PEER=\{P1\},
-        \PEER \Arrow *, \COMM \Arrow (1,0)
-      Match[100] \PREFIX=true, \PEER=\{P2\},
-        \PEER \Arrow *, \COMM \Arrow (0,1)
-      ...
-    \end{code}
-
+%  \begin{code}
+%    \Template{S}
+%      Match[100] \PREFIX=\$GP, \PEER=\{AG, AL\}
+%        \PEER \Arrow *
+%      Match[100] \PREFIX=\$LP, \PEER=\{AG, AL\}
+%        \PEER \Arrow \{AG, AL\}
+%      Match[110] \PREFIX=true \PEER=\{P1\},
+%        \PEER \Arrow *, \COMM \Arrow (1,0)
+%      Match[100] \PREFIX=true \PEER=\{P2\},
+%        \PEER \Arrow *, \COMM \Arrow (0,1)
+%      ...
+%  \end{code}%
+
+%  \vspace{-2em}
+%  \begin{code}
+%    \Router{S1, S2}
+%      Match[100] \PREFIX=GP1, \PEER=\{AG1, AL1, ...\}
+%        \PEER \Arrow *
+%      Match[100] \PREFIX=GP2, \PEER=\{AG1, AL1, ...\}
+%        \PEER \Arrow *
+%      ...
+%      Match[100] \PREFIX=LP1, \PEER=\{AG1, AL1, ...\}
+%        \PEER \Arrow \{AG1, AL1, ...\}
+%      Match[100] \PREFIX=LP2, \PEER=\{AG1, AL1, ...\}
+%        \PEER \Arrow \{AG1, AL1, ...\}
+%      ...
+%      Match[110] \PREFIX=true, \PEER=\{P1\},
+%        \PEER \Arrow *, \COMM \Arrow (1,0)
+%      Match[100] \PREFIX=true, \PEER=\{P2\},
+%        \PEER \Arrow *, \COMM \Arrow (0,1)
+%      ...
+%    \end{code}
+
+  \begin{center}
+  \includegraphics[width=.8\columnwidth]{figures/configs}  
+  \end{center}
   \vspace{-1em}

### 2016-11-12 paper/abstraction/paper.tex
adding figure
edits

@@
 \subsection{Compilation}
+\label{subsec:compilation}
 
@@
 %In practice, operators would often like to reason about a variety of properties for, not only their current network topology, but also future versions of it.
-The Product Graph provides a convenient representation to capture the joint impact of both topology and routing policy.
+%% The Product Graph provides a convenient representation to capture the joint impact of both topology and routing policy.
 In this section we present an analysis that operates over the abstract Product Graph to find a lower bound on the number of disjoint paths between pairs of concrete nodes.
@@
 
-\subsection{Abstract k-disjoint paths}
-\label{sec:property-checking}
-
-\dpw{we could flip the order of this description:  give simple concrete $S_A(j,k)$ first and
-then go to the general.}
+%\subsection{Abstract k-disjoint paths}
+%\label{sec:property-checking}
+
+%
 To infer bounds on the number of disjoint paths between concrete nodes we use information about the structure of the underlying concrete topologies encoded in abstraction constraints.
 %
-The idea is to maintain, for each node in the abstract Product Graph, facts learned about the number of disjoint paths to some number of concrete routers in the node's role.
+As discussed informally in~\ref{subsec:compilation},
+for each node in the abstract Product Graph, 
+the idea is to maintain facts learned about the number of disjoint paths 
+to some number of concrete routers in the node's role. 
 More specifically, we maintain facts of the form:
@@
 %
-Each label $L \in \{S,A\}$ is either $S$, which stands for "some" or is $A$, which stands for "all".
+where each label $L \in \{S,A\}$ is either $S$, which stands for "some" or is $A$, which stands for "all".
 There is one label for each pod in the abstraction pod hierarchy.
 For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the the node itself.
-
-Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for "some"/``all" pods $X_1$, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds.
-The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers, there are $k$ edge-disjoint paths to each such that all $j*k$ paths are disjoint.
-%
-For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.
+Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for some/all pods $X_1, \ldots, X_{n-1}$
+and for some/all groups of nodes in the role $X_n$ of size $j$,
+%, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds. The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers, 
+there are $k$ paths to each such that all $j*k$ paths are edge-disjoint.
+%
+%For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.
 
@@
 
-The first rule, \infrule{I-out1} applies to a learned fact of the form L$(j,k)$ where the number of outgoing edges from any concrete node in the $m$ role is greater than 0.
-In the worst case, the largest group of concrete nodes we could hope to reach at the $n$ role would be $e_1$ since all j nodes at the bottom may have the same outgoing edges to the concrete nodes at the top.
+The first rule, \infrule{I-out1} applies to a learned fact of the form $L_m(j,k)$ where the number of outgoing edges from any concrete node in the $m$ role is greater than 0.
+In the worst case, the largest group of concrete nodes we could hope to reach at the $n$ role would be $e_1$ since all j nodes at the bottom may have outgoing edges to the same concrete nodes at the top.
 Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$.
@@
 The match for N1 is preferred since it has a higher BGP local-preference attribute (110).
-If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers.
+If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers ({\large $*$}).
 If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.

### 2016-11-12 paper/abstraction/paper.tex
placeholder abstract

@@
 \textbf{Abstract---}
-We develop techniques for automated reasoning about end-to-end properties of
-abstract network topologies, and embody them in a network synthesis tool called
-\sysname. \sysname allows network operators to write a high-level routing policy
-over an abstraction of their network topology. From such a specification,
-\sysname synthesizes a collection of router configurations running the
-distributed Border Gateway Protocol (BGP) that are guaranteed to implement the
-centralized routing policy for any concrete instantiation of the abstract
-topology, and for any combination of network failures in the resulting concrete
-topology.
-%
-Additionally, properties proven by \sysname over the abstract topology, such as
-reachability between a source and destination under k-failures, are also
-guaranteed to hold under any concrete instantiation of the abstract topology.
-%
-Something something, expandable/incremental networks. Something something scales
-compilation to large networks. Something something, templates easier to
-understand.
+\ryan{Copied from conclusion for reference}
+We develop \sysname, the first system that can generate device configuration templates for large networks from high-level specifications of network topology and policy.
+\sysname is based on new abstractions for capturing parameterized network topologies, and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance.
+Our analysis operates entirely in the abstract domain and guarantees correctness for all concrete instantiations of the topology.
+Experiments with many types of real-world topologies and policies show that our abstractions and analysis are precise and that, for large networks, configuration synthesis is two orders of magnitude faster than systems that operate over concrete topologies.
+
+%We develop techniques for automated reasoning about end-to-end properties of
+%abstract network topologies, and embody them in a network synthesis tool called
+%\sysname. \sysname allows network operators to write a high-level routing policy
+%over an abstraction of their network topology. From such a specification,
+%\sysname synthesizes a collection of router configurations running the
+%distributed Border Gateway Protocol (BGP) that are guaranteed to implement the
+%centralized routing policy for any concrete instantiation of the abstract
+%topology, and for any combination of network failures in the resulting concrete
+%topology.
+%
+%Additionally, properties proven by \sysname over the abstract topology, such as
+%reachability between a source and destination under k-failures, are also
+%guaranteed to hold under any concrete instantiation of the abstract topology.
+%
+%Something something, expandable/incremental networks. Something something scales
+%compilation to large networks. Something something, templates easier to
+%understand.
 %These strong guarantees allow operators to reason about the routing behavior of
@@
 %
-We test \sysname out on ... blah blah blah
+%We test \sysname out on ... blah blah blah
 
@@
 The match for N1 is preferred since it has a higher BGP local-preference attribute (110).
-If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers ({\large $*$}).
+If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers ($*$).
 If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
 %
-The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertise the route to all of its peers ($*$).
+The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertises the route to all of its peers.
 For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers.

### 2016-11-12 paper/abstraction/paper.tex
move section 8 into 7
update templates to include bth incremental and concrete versions

@@
   \begin{center}
-  \includegraphics[width=.8\columnwidth]{figures/configs}  
+  \includegraphics[width=\columnwidth]{figures/configs}  
   \end{center}
   \vspace{-1em}
-  \caption{Spine template and concrete configurations.}
+  \caption{Spine template and concrete configurations (left), and evolution friendly templates (right).}
   \label{fig:bgp-configs}
@@
 
-\section{Compilation}
-
-The translation from the Product Graph to per-device configurations that run the distributed BGP protocol involves several ideas.
+\section{Template Generation}
+
+The translation from the Product Graph to per-device templates that run the distributed BGP protocol involves several ideas.
 
@@
 The concrete configurations have a similar configuration for each local and global prefix.
-
-%=====================================================
-%
-%
-%  **Concretization**
-%
-%
-%=====================================================
 
@@
 
-\section{Properties}
+\para{Incrementality}
+
+Suppose that an operator want to expand the concrete datacenter by adding an additional ToR router to the TG role.
+Per the network routing policy, the new ToR router will advertise any owned prefixes provided by looking up {\small \$GP} in $\Gamma$.
+Because the new topology matches the abstraction, the compiled templates will remain the same.
+However, in the spine router configurations, the match on the global prefix template variable {\small \$GP} must be expanded when concretizing the template to include the new prefixes added by the ToR.
+Unfortunately, this small change to the topology results in a change to every single spine router configuration.
+
+However, template variables tell us exactly where this kind of change can happen.
+The only way in which the spine routers depend on anything non-local is in the match on prefix template variables.
+Instead, we can associate a new unique community tag for template variable {\small \$GP} and then replace each match on {\small \$GP} with a test on the new community tag.
+The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can just match the community tag.
 
@@
 Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix.
-
-\para{Incrementality}
-
-Suppose that an operator want to expand the concrete datacenter by adding an additional ToR router to the TG role.
-Per the network routing policy, the new ToR router will advertise any owned prefixes provided by looking up {\small \$GP} in $\Gamma$.
-Because the new topology matches the abstraction, the compiled templates will remain the same.
-However, in the spine router configurations, the match on the global prefix template variable {\small \$GP} must be expanded when concretizing the template to include the new prefixes added by the ToR.
-Unfortunately, this small change to the topology results in a change to every single spine router configuration.
-
-However, template variables tell us exactly where this kind of change can happen.
-The only way in which the spine routers depend on anything non-local is in the match on prefix template variables.
-Instead, we can associate a new unique community tag for template variable {\small \$GP} and then replace each match on {\small \$GP} with a test on the new community tag.
-The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can just match the community tag.
 

### 2016-11-12 paper/abstraction/paper.tex
update concretization section

@@
 In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
-Figure~\ref{fig:bgp-configs} shows part of the final configuration for spine routers for the concrete and abstract policies in a vendor-neutral syntax.
+Figure~\ref{fig:bgp-configs} (left) shows part of the final configuration for spine routers for the concrete and abstract policies in a vendor-neutral syntax.
 %
@@
 
-\para{Incrementality}
-
-Suppose that an operator want to expand the concrete datacenter by adding an additional ToR router to the TG role.
-Per the network routing policy, the new ToR router will advertise any owned prefixes provided by looking up {\small \$GP} in $\Gamma$.
-Because the new topology matches the abstraction, the compiled templates will remain the same.
-However, in the spine router configurations, the match on the global prefix template variable {\small \$GP} must be expanded when concretizing the template to include the new prefixes added by the ToR.
-Unfortunately, this small change to the topology results in a change to every single spine router configuration.
-
-However, template variables tell us exactly where this kind of change can happen.
-The only way in which the spine routers depend on anything non-local is in the match on prefix template variables.
-Instead, we can associate a new unique community tag for template variable {\small \$GP} and then replace each match on {\small \$GP} with a test on the new community tag.
-The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can just match the community tag.
-
 \para{Concretization}
@@
 Concretization takes a context $\Gamma : \mathit{Var} \rightarrow 2^{\mathit{Prefix} \times V}$ that maps each template variable to a set of pairs of a concrete prefix and topology location where the prefix is owned.
-The main theoretical result is that the compilation and concretization functions commute.
-More specifically:
+Intuitively, the spine template in concretized by replacing each abstract role with the set of all concrete routers that map to that role and each prefix template variable with a new entry in the configuration for each individual prefix provided by the context $\Gamma$.
+The main theoretical result is that the compilation and concretization functions commute:
 
@@
 Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix.
+
+\para{Incrementality}
+
+Suppose that an operator want to expand the concrete datacenter by adding an additional ToR router to the TG role.
+Per the network routing policy, the new ToR router will advertise any owned prefixes provided by looking up {\small \$GP} in $\Gamma$.
+Because the new topology matches the abstraction, the compiled templates will remain the same.
+However, in the spine router configurations, the match on the global prefix template variable {\small \$GP} must be expanded when concretizing the template to include the new prefixes added by the ToR.
+Unfortunately, this small change to the topology results in a change to every single spine router configuration.
+
+However, template variables tell us exactly where this kind of change can happen.
+The only way in which the spine routers depend on anything non-local is in the match on prefix template variables.
+Instead, we can associate a new unique community tag for template variable {\small \$GP} and then replace each match on {\small \$GP} with a test on the new community tag.
+The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can just match the community tag.
 

### 2016-11-12 paper/abstraction/paper.tex
space savings

@@
 valid topological paths if the routing policy disallows it.
-\dpw{I deleted this:  ``It implies that we cannot use standard graph theoretic algorithms.''  I don't know of any ``standard'' graph-theoretic algorithm
-we could use but I can't completely rule it out either because I don't
-know all graph theoretic algorithms and it wouldn't completely shock 
-me if somewhere there were algorithms for analyzing graphs modulo
-isomorphisms that might be related tangentially.  Basically, I think
-it brings up the possibility that we should compare with graph-theoretic
-algorithms but then we don't do so in any detail
-so I thought it was better to drop it.}
 

### 2016-11-12 paper/abstraction/paper.tex
rewordings

@@
 
-\section{Abstract Analysis}
+\section{Fault-tolerance Analysis}
 \label{sec:analysis}
@@
 The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can just match the community tag.
+Figure~\ref{fig:bgp-configs} (right) shows the templates after the transformation.
 
@@
 The compiler accepts both concrete and abstract topologies and will generate configurations for open-source Quagga routers by default.
-The abstract analysis uses $\nu$Z~\cite{z3opt} to test validity and to minimize variables subject to the annotated constraints.
+The fault-tolerance analysis uses $\nu$Z~\cite{z3opt} to test validity and to minimize variables subject to the annotated constraints.
 Since the analysis typically calls the SMT solver many times with relatively simple optimization problems, we use a short timeout of 200ms.
@@
   \end{center}
-  \caption{Abstract Analysis Precision.}
+  \caption{Fault-tolerance analysis precision.}
   \label{fig:analysis-precision}
@@
 
-We evaluate the expressiveness and precision of our abstract analysis on a range of different network topologies found in network literature and in production networks.
+We evaluate the expressiveness and precision of our fault-tolerance analysis on a range of different network topologies found in network literature and in production networks.
 The analysis is precise if it finds a tight lower-bound on the fault-tolerance (\IE, there is actually a concrete network with that fault tolerance).
@@
 The $S_{x-1}$ groups of abstract nodes can be captured using pods of the abstract $S_x$ nodes.
-For all hypercube variants, the abstract analysis is precise.
+For all hypercube variants, the fault-tolerance analysis is precise.
 
@@
 
-For both the networks, the abstract compilation starts off slightly slower than concrete compilation for small topologies due to the overhead of the abstract analysis for fault-tolerance.
+For both the networks, the abstract compilation starts off slightly slower than concrete compilation for small topologies due to the overhead of the fault-tolerance analysis.
 However, as the size of the topology increases, abstract compilation becomes orders of magnitude faster than concrete compilation.
@@
 Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract compilation.
-Notably, the abstract analysis takes the majority of the time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost.
+Notably, the fault-tolerance analysis takes the majority of the time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost.
 In particular, the number of calls to $\nu$Z remains constant the across topology size.

### 2016-11-12 paper/abstraction/paper.tex
more edits

@@
 \usepackage{code}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
 \usepackage{tikz}
@@
 \usepackage{balance}
-\usepackage[ampersand]{easylist}
 \usepackage{textcomp}
@@
 The \sysname compiler generates templates from the inputs above in three phases.
-First, it combines the abstract topology and routing policy into a {\em product graph} that compactly captures the flow of routing information over the topology in a policy-compliant manner.
+First, it combines the abstract topology and routing policy into a {\em product graph} (PG) that compactly captures the flow of routing information over the topology in a policy-compliant manner.
 The algorithm for this phase builds on the Propane compiler, which was designed for concrete topologies and policy; we show that it can be extended to abstract inputs and that the extensions are correct.
@@
 A key step for \sysname to generate device configurations is to build a data structure amenable to joint analysis of both the topology and routing policy.
-Intutively, \sysname captures both topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology into a data structure called the Product Graph~\cite{propane}.
-
-The Product Graph compactly encodes all paths protocol messages should be passed along through the network in order to guarantee the devices find policy-compliant paths dynamically.
+Intutively, \sysname captures both topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology into a data structure called the Product Graph~\cite{propane} (PG).
+
+The PG compactly encodes all paths protocol messages should be passed along through the network in order to guarantee the devices find policy-compliant paths dynamically.
 %
@@
 %
-Because \sysname policies can have a separate routing policy for each predicate matching traffic, we construct one such Product Graph for each predicate.
+Because \sysname policies can have a separate routing policy for each predicate matching traffic, we construct one such PG for each predicate.
 
@@
 %
-The Product Graph is a tuple ($G'$, $start$, $P$) where $G' = (V',E')$ is a new graph with
+The PG is a tuple ($G'$, $start$, $P$) where $G' = (V',E')$ is a new graph with
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
@@
 a unique starting vertex $start$,
-and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$, mapping nodes in the product graph to a set of path ranks.
-
-The Product Graph is constructed by adding an edge from state $m = (l_m, q_{m_1}, \dots, q_{m_k})$ to $n = (l_n, q_{n_1}, \dots, q_{n_k})$ whenever $\sigma_i(q_{m_i}, l_n) = q_{n_i}$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
+and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$, mapping nodes in the PG to a set of path ranks.
+
+The PG is constructed by adding an edge from state $m = (l_m, q_{m_1}, \dots, q_{m_k})$ to $n = (l_n, q_{n_1}, \dots, q_{n_k})$ whenever $\sigma_i(q_{m_i}, l_n) = q_{n_i}$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
 %
@@
 %
-The preference function $P(m)$ denotes the rank of paths through the Product Graph ending at node $m$ and is defined as $P(m) = \set{i~\vert~q_{m_i} \in F_i}$.
-%
-Finally, we write $\tilde{m} = l$ to extract the topology location from a product graph node, when $m = (l, q_{m_1}, \dots, q_{m_k}) \in V'$.
-
-Figure~\ref{fig:example-compilation} shows an example of a Product Graph for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview} ($\True ~\Path~ \CD{\Exit(N1 \Prefer~N2)}$).
+The preference function $P(m)$ denotes the rank of paths through the PG ending at node $m$ and is defined as $P(m) = \set{i~\vert~q_{m_i} \in F_i}$.
+%
+Finally, we write $\tilde{m} = l$ to extract the topology location from a PG node, when $m = (l, q_{m_1}, \dots, q_{m_k}) \in V'$.
+
+Figure~\ref{fig:example-compilation} shows an example of a PG for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview} ($\True ~\Path~ \CD{\Exit(N1 \Prefer~N2)}$).
 %
@@
 The first automaton represents the more preferred constraint $\CD{\Exit(N1)}$ and the second automaton represents the less preferred constraint $\CD{\Exit(N2)}$.
-The Product Graph is shown for both an instance of a simple concrete network matching the abstraction from \S\ref{sec:overview} as well as for the abstract topology.
-
-Paths through the Product Graph represent paths through the topology that protocol messages may use to ensure policy-compliant.
-For example, in the concrete Product Graph, all messages from N1 are not blocked at each spine router.
+The PG is shown for both an instance of a simple concrete network matching the abstraction from \S\ref{sec:overview} as well as for the abstract topology.
+
+Paths through the PG represent paths through the topology that protocol messages may use to ensure policy-compliant.
+For example, in the concrete PG, all messages from N1 are not blocked at each spine router.
 Paths for a destination learned through N1 will end in an accepting state for the first automaton (\EG, node (T1,1,0)).
@@
 
-One interesting observation is that the Product Graph for both the concrete and abstract networks share a similar structure. This leads us to the following observation:
+One interesting observation is that the PG for both the concrete and abstract networks share a similar structure. This leads us to the following observation:
 
 \begin{defn}
-If we have a graph homomorphism $f : G \rightarrow G^A$, concrete product graph $PG = (G',\mathit{start},P)$ and abstract product graph $PG^A = (G'^A, \mathit{start}^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$:
+If we have a graph homomorphism $f : G \rightarrow G^A$, concrete $PG = (G',\mathit{start},P)$ and abstract $PG^A = (G'^A, \mathit{start}^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$:
 \[ \begin{array}{rcl}
@@
 
-  \caption{Product graph construction for policy $\True ~\Path~ \CD{\Exit(\text{N1}} ~\Prefer~ \CD{\text{N2})}$.}
+  \caption{Product Graph construction for policy $\True ~\Path~ \CD{\Exit(\text{N1}} ~\Prefer~ \CD{\text{N2})}$.}
   \label{fig:example-compilation}
@@
 As discussed informally in~\ref{subsec:compilation},
-for each node in the abstract Product Graph, 
+for each node in the abstract PG, 
 the idea is to maintain facts learned about the number of disjoint paths 
@@
 %
-Figure~\ref{fig:example-inference} shows part of the abstract Product Graph representation for this routing policy.
+Figure~\ref{fig:example-inference} shows part of the abstract PG representation for this routing policy.
 The inference algorithm starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$ (\IE, no restriction on the number of disjoint paths initially).
@@
 
-Note that, because each inference rule only applies to directed edges in the Product Graph, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
+Note that, because each inference rule only applies to directed edges in the PG, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
 This restriction ensures that the analysis is policy-sensitive.
@@
 
-The translation from the Product Graph to per-device templates that run the distributed BGP protocol involves several ideas.
+The translation from the PG to per-device templates that run the distributed BGP protocol involves several ideas.
 
@@
 The first idea is to tag every protocol message with a BGP community that encodes the state of each DFA when advertising a route to a neighbor.
-Routers then allow route advertisements that correspond to an edge in the Product Graph and block those that do not.
-For example, in the concrete Product Graph in figure~\ref{fig:example-compilation}, router S1 will allow an advertisement from its neighbors N1 and N2.
+Routers then allow route advertisements that correspond to an edge in the PG and block those that do not.
+For example, in the concrete PG in figure~\ref{fig:example-compilation}, router S1 will allow an advertisement from its neighbors N1 and N2.
 If it uses the path advertised by neighbor N1, then it will add the tag $(1,0)$ before sending this to its neighbors.
@@
 Propane introduced a conservative search strategy for determining route preferences.
-To make this work for abstract topologies, we modify the search based on the following observation about the structure of the Product Graph:
+To make this work for abstract topologies, we modify the search based on the following observation about the structure of the PG:
 
 \begin{defn}
-Let $m \geq_{rank} n$ be a relation over Product Graph vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$.
-Intuitively $m \geq_{rank} n$ means that paths ending at Product Graph node $m$ are no better in terms of preference than paths ending at $n$.
+Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$.
+Intuitively $m \geq_{rank} n$ means that paths ending at PG node $m$ are no better in terms of preference than paths ending at $n$.
 %
@@
 %\begin{defn}
-The product graph can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge.
+The PG can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge.
 That is, $m\overset{l}{\rightarrow}n$ if edge $(m,n) \in E'$ and $\tilde{n} = l$.
@@
 %
-For example, in the concrete product graph we would have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.
+For example, in the concrete PG we would have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.
 
@@
 
-If we determine that each router has a total order with respect to the simulation relation ($\leq$) for its corresponding Product Graph nodes, then we can simply sort the nodes and prefer advertisements from peers of node $m$ over those of node $m'$ whenever $m' \leq m$.
+If we determine that each router has a total order with respect to the simulation relation ($\leq$) for its corresponding PG nodes, then we can simply sort the nodes and prefer advertisements from peers of node $m$ over those of node $m'$ whenever $m' \leq m$.
 This condition ensures that BGP devices will converge to the most preferred paths in the network even when failures occur.
 %
-For example, in the concrete product graph the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the product graph can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation.
+For example, in the concrete PG the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation.
 This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$.
@@
 %
-Notice that in the abstract product graph $(S,0,1) \leq (S,1,0)$ also holds. This leads us the the following observation:
+Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds. This leads us the the following observation:
 
@@
 \label{lem:preference}
-$m \leq m'$ in the concrete Product Graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract Product Graph.
+$m \leq m'$ in the concrete PG iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract PG.
 \end{lem}
 
-This gives us reason to believe that we can perform compilation over the abstract product graph directly and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.
+This gives us reason to believe that we can perform compilation over the abstract PG directly and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.
 
@@
 
-Although the disjoint path analysis takes place over the Product Graph, each application of the inference rules from figure~\ref{fig:inference-rules} depends only on the topology.
+Although the disjoint path analysis takes place over the PG, each application of the inference rules from figure~\ref{fig:inference-rules} depends only on the topology.
 Therefore, we lazily apply the rules and cache the satisfiability and minimization calls to $\nu$Z after their first use.
-Furthermore, the cached results are shared across different prefixes, each of which may have a unique Product graph representation.
+Furthermore, the cached results are shared across different prefixes, each of which may have a unique PG representation.
 

### 2016-11-12 paper/abstraction/paper.tex
more edits

@@
 network will correctly implement the routing policy and meet the fault-tolerance
-requirements. We show how fault-tolerance analysis can be done over abstract
-topology itself using \todo{say something cool about about the inference rules
-and such}.
+requirements. We show how fault-tolerance analysis can be done over the abstract
+topology itself by inferring the worst-case number of edge-disjoint paths in some concrete topology using an optimizing SMT solver.
 
@@
 concrete network satisfying the abstract connectivity invariants.
-\item Design of template generation strategies that support network
+\item Design of a template generation strategy that supports network
 evolution.
@@
   \includegraphics[width=\columnwidth]{figures/example3}
+  \vspace{-2em}
   \caption{An abstraction for the datacenters in Figure~\ref{fig:example}.}
@@
 we introduce several additional concepts.
-The first is the idea of a topology hierarchy captured by P and Q, which say that nodes in the ToR and aggregator roles are grouped into a number of smaller pods.
+The first is the idea of a topology hierarchy captured by P and Q, which indicate that nodes in the ToR and aggregator roles are grouped into a number of smaller pods.
 The second is a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
@@
 %
-The Local constraint applies to any traffic destined for a local prefix described by the $\CD{\$LP}$ prefix template variable and adds the constraint that the traffic must follow a path that matches an internal location (\IE, a router inside the datacenter) at each hop of the path.
-%
-The constraint to prevent "valleys" (5) is implemented as:
+The Local constraint applies to any traffic destined for a local prefix described by the $\CD{\$LP}$ prefix template variable and adds the constraint that the traffic must follow a path that matches an internal location (\IE, in the datacenter) at each hop of the path.
+%
+The constraint to prevent "valleys" (5) is written:
 %
@@
 \begin{defn}
-If we have a graph homomorphism $f : G \rightarrow G^A$, concrete $PG = (G',\mathit{start},P)$ and abstract $PG^A = (G'^A, \mathit{start}^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$:
+If we have a graph homomorphism $f : G \rightarrow G^A$, concrete $PG = (G',\mathit{start},P)$ and abstract $PG^A = (G'^A, \mathit{start}^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$ as follows:
 \[ \begin{array}{rcl}
@@
 %
-Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds. This leads us the the following observation:
+Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds.
 
@@
 
-This gives us reason to believe that we can perform compilation over the abstract PG directly and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.
+Lemma~\ref{lem:preference} gives us reason to believe that we can perform compilation over the abstract PG directly and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.
 
@@
 
-The \sysname compiler is implemented in approximately 9500 lines of F\# code.
-The compiler accepts both concrete and abstract topologies and will generate configurations for open-source Quagga routers by default.
-The fault-tolerance analysis uses $\nu$Z~\cite{z3opt} to test validity and to minimize variables subject to the annotated constraints.
-Since the analysis typically calls the SMT solver many times with relatively simple optimization problems, we use a short timeout of 200ms.
+The \sysname compiler is implemented in around 9500 lines of F\# code.
+The compiler accepts both concrete and abstract topologies and will generate configurations for open-source Quagga~\cite{quagga} routers by default.
+The fault-tolerance analysis uses $\nu$Z~\cite{z3opt} to test validity and minimize variables subject to the topology constraints.
+Since the analysis typically calls the SMT solver many times with relatively small optimization problems, we use a timeout of 200ms.
 

### 2016-11-12 paper/abstraction/paper.tex
minor edits

@@
 
-\newtheorem{thm}{Theorem}
-\newtheorem{defn}{Definition}
+\newtheorem{thm}{Theorem}[section]
+\newtheorem{defn}{Definition}[section]
 \newtheorem{lem}[thm]{Lemma}
@@
 
-\subsection{Compilation}
+\subsection{Template Generation}
 \label{subsec:compilation}
@@
 First, it combines the abstract topology and routing policy into a {\em product graph} (PG) that compactly captures the flow of routing information over the topology in a policy-compliant manner.
-The algorithm for this phase builds on the Propane compiler, which was designed for concrete topologies and policy; we show that it can be extended to abstract inputs and that the extensions are correct.
+The algorithm for this phase builds on the \propane compiler, which was designed for concrete networks; we show that it can be extended to abstract inputs and that the extensions are correct.
 
@@
 
-The PG compactly encodes all paths protocol messages should be passed along through the network in order to guarantee the devices find policy-compliant paths dynamically.
+The PG compactly encodes all paths that protocol messages should be passed along through the network in order to guarantee that the devices find policy-compliant paths dynamically.
 %
@@
 
-The PG is constructed by adding an edge from state $m = (l_m, q_{m_1}, \dots, q_{m_k})$ to $n = (l_n, q_{n_1}, \dots, q_{n_k})$ whenever $\sigma_i(q_{m_i}, l_n) = q_{n_i}$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
-%
-We add edges from the start node to any $m = (l, q_{m_1}, \dots, q_{m_k})$ when $\sigma_i(q_{0_i}, l) = q_{m_i}$ for each $i$.
+The PG is constructed by adding an edge from state $m = (l_m, q_{m_1}, \dots, q_{m_k})$ to $n = (l_n, q_{n_1}, \dots, q_{n_k})$ whenever $\sigma_i(q_{m_i}, l_n) = q_{n_i}$ for each $i$ and $(l_m,l_n) \in E$.
+%
+We add edges from the $\mathit{start}$ node to any $m = (l, q_{m_1}, \dots, q_{m_k})$ when $\sigma_i(q_{0_i}, l) = q_{m_i}$ for each $i$.
 %
@@
 
-Figure~\ref{fig:example-compilation} shows an example of a PG for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview} ($\True ~\Path~ \CD{\Exit(N1 \Prefer~N2)}$).
+Figure~\ref{fig:example-compilation} shows an example of a PG for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview}.
 %
@@
 \begin{defn}
+\label{def:homomorphism}
 If we have a graph homomorphism $f : G \rightarrow G^A$, concrete $PG = (G',\mathit{start},P)$ and abstract $PG^A = (G'^A, \mathit{start}^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$ as follows:
@@
 \end{defn}
+
+As we will see in \S\ref{sec:generation}, we have proven that our generation strategy commutes with concrete expansion, meaning that we obtain the same results if we expand the abstraction early, or if we defer the expansion until after template generation.
+%
+Definition~\ref{def:homomorphism} provides some intuition concerning why our strategy for generating templates is correct.
+%Abstract product graphs are related to concrete product graphs via a graph homomorphism, just as abstract topologies are related to concrete topologies via a graph homomorphism.
 
@@
 \section{Template Generation}
+\label{sec:generation}
 
@@
 
-Lemma~\ref{lem:preference} gives us reason to believe that we can perform compilation over the abstract PG directly and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.
+Lemma~\ref{lem:preference} tells us that inferring preferences over the abstract PG before concrete expansion is equivalent to inferring preferences over an already-expanded concrete PG.
 
@@
 \begin{thm}
-  For any context $\Gamma$, topology $G$, abstract topology $G^A$, homomorphism $f : G \rightarrow G^A$, and policy $pol$,
-
-  \noindent
-  $\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$
+  For any context $\Gamma$, topologies $G$ and $G^A$, homomorphism $f : G \rightarrow G^A$, and policy $pol$,
+  $$\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$$
   \label{thm:concretization}
@@
 To evaluate \sysname, we apply it on policies for backbone and datacenter networks.
-We aim to evaluate the expressiveness of our abstracttions, the precision of the abstract disjoint-path analysis, and the compilation time of \sysname both with abstraction and without.
+We aim to evaluate the expressiveness of our abstracttions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.
 
@@
 
-\subsection{Compilation time}
+\subsection{Generation time}
 
@@
     {\includegraphics[width=.49\columnwidth]{figures/backbone-time.png}} \\
-  \caption{Concrete vs. Abstract Compilation Time. \label{fig:compilation-times}}
+  \caption{Concrete vs. Abstract Generation Time. \label{fig:compilation-times}}
   \vspace{-1em}
@@
     {\includegraphics[width=.49\columnwidth]{figures/backbone-analysis-time.png}} \\
-  \caption{Abstract Compilation Time by Phase. \label{fig:abstract-breakdown}}
+  \caption{Abstract Generation Time by Phase. \label{fig:abstract-breakdown}}
   \vspace{-1em}
@@
 Using abstraction allows us to naturally scale network synthesis in \sysname.
-We evaluate compilation time in \sysname both with and without abstraction using routing policy for backbone and datacenter networks inspired by configurations obtained from a large cloud provider.
+We evaluate generation time in \sysname both with and without abstraction using routing policy for backbone and datacenter networks inspired by configurations obtained from a large cloud provider.
 For both types networks, we fix routing policy but scale the size of the underlying topology.
@@
 
-Figure~\ref{fig:compilation-times} shows compilation time for the same policies for both the abstract and concrete versions of the policies described above.
+Figure~\ref{fig:compilation-times} shows generation time for the same policies for both the abstract and concrete versions of the policies described above.
 All experiments are run on an 8 core, 2.4 GHz Intel i7 processor Mac with 8GB of Ram, and the time taken is the average of 3 runs.
 
-For both the networks, the abstract compilation starts off slightly slower than concrete compilation for small topologies due to the overhead of the fault-tolerance analysis.
-However, as the size of the topology increases, abstract compilation becomes orders of magnitude faster than concrete compilation.
-In all cases for both networks, abstract compilation takes less than 10 seconds to complete.
-
-Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract compilation.
+For both the networks, the abstract generation starts off slightly slower than concrete generation for small topologies due to the overhead of the fault-tolerance analysis.
+However, as the size of the topology increases, abstract generation becomes orders of magnitude faster than concrete generation.
+In all cases for both networks, abstract generation takes less than 10 seconds to complete.
+
+Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract generation.
 Notably, the fault-tolerance analysis takes the majority of the time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost.

### 2016-11-12 paper/abstraction/paper.tex
more space savings

@@
 \para{Abstract topology}
-Abstract topologies in \sysname define structural and role-based invariants that capture a collection of concrete networks.
-These invariants are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities and connectivity.
-%
-We designed these abstractions to be able to precisely capture most real network topologies, while being amenable to the fault tolerance analysis and configuration synthesis that is done by our compiler.
+Abstract topologies in \sysname define structural and role-based invariants that describe a collection of concrete networks.
+These invariants are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
+%
+We designed these abstractions to be able to precisely capture many real network topologies, while also being amenable to fault-tolerance analysis and configuration synthesis.
 
@@
 The role-based abstraction therefore overapproximates the connectivity of the underlying concrete graphs.
-On its own, this abstraction loses a lot of information about the underlying structure of the concrete network, making it difficult to reason precisely about fault-tolerance.
+On its own, this abstraction loses a lot of information about the structure of concrete networks, making it difficult to reason precisely about fault-tolerance.
 %which would hinder a useful analysis of its fault-tolerance.
@@
   \label{fig:inference-rules}
-  %\vspace{-1em}
+  \vspace{-1.4em}
 \end{figure*}
@@
   \end{center}
-  \caption{Abstract disjoint path analysis with valleyfree routing for global prefixes. \label{fig:compilation-times}}
+  \vspace{-1.4em}
+  \caption{Abstract disjoint path analysis for global prefixes. \label{fig:compilation-times}}
   \label{fig:example-inference}
-  \vspace{-1em}
+  \vspace{0em}
 \end{figure}
@@
   \vspace{-1em}
-  \caption{Spine template and concrete configurations (left), and evolution friendly templates (right).}
+  \caption{Spine template and concrete configurations (left), and evolution-friendly templates (right).}
   \label{fig:bgp-configs}
@@
 Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$.
-Intuitively $m \geq_{rank} n$ means that paths ending at PG node $m$ are no better in terms of preference than paths ending at $n$.
+Intuitively $m \geq_{rank} n$ means that paths ending at PG node $m$ are no better than paths ending at $n$.
 %
@@
       \hline
-      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachability} & \textbf{K-paths} \\ \hline
+      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
       Fattree~\cite{fattree} & & \cmark & \cmark  \\ \hline
@@
   \end{center}
+  \vspace{-.6em}
   \caption{Fault-tolerance analysis precision.}
   \label{fig:analysis-precision}
+  \vspace{-1em}
 \end{figure}
@@
     {\includegraphics[width=.49\columnwidth]{figures/backbone-time.png}} \\
+  \vspace{-.6em}
   \caption{Concrete vs. Abstract Generation Time. \label{fig:compilation-times}}
@@
     {\includegraphics[width=.49\columnwidth]{figures/backbone-analysis-time.png}} \\
+  \vspace{-.6em}
   \caption{Abstract Generation Time by Phase. \label{fig:abstract-breakdown}}

### 2016-11-12 paper/abstraction/paper.tex
more edits

@@
 
-\para{Fault-tolerance policy} This policy specifies how many link failures the network should be able to withstand before connectivity loss for traffic occurs.
+\para{Fault-tolerance policy} This policy specifies how many link failures the network should be able to withstand before traffic experiences connectivity loss.
 Operators can specify different tolerance levels for different pairs of abstract nodes.
@@
 
-Instead, we develop a sound analysis based on computing the minimum
-number of edge-disjoint policy-compliant paths between pairs of nodes
-over abstract topologies. If this number for a pair of nodes is less
-than the desired fault-tolerance level, \sysname declares that the
+We develop a sound analysis based on computing the minimum
+number of edge-disjoint, policy-compliant paths between pairs of nodes
+over abstract topologies. If this number is less
+than the desired fault-tolerance level for a pair of nodes, \sysname declares that the
 policy cannot be met.  More specifically,

### 2016-11-12 paper/abstraction/paper.tex
pass over intro

--- 2016-11-12 paper/abstraction/paper.tex
@@
 
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{defn}{Definition}[section]
+\newtheorem{thm}{Theorem}
+\newtheorem{defn}{Definition}
 \newtheorem{lem}[thm]{Lemma}
@@
 Computer networks run many critical services, and every second of downtime is
-costly at best and dangerous at worst.  Keeping these complex systems up and
+costly at best and dangerous at worst.  Yet, keeping these systems
 running 24/7 is an enormous
@@
 While hardware faults, backhoes, power failures and natural disasters all pose
-problems, studies have consistently shown that human error in network
-configuration is one of the leading cause of network
+problems, studies have consistently shown that human errors in network
+configuration is one of the leading cause of 
 outages~\cite{juniper-study,xx}.
 
-To manage and configure large networks today, instead of considering individual
-devices, operators classify devices devices into {\em roles}. A role refers to
-specific functionality and is played by one or more devices. For instance, in a
-data center, roles may correspond to "top-of-rack," "aggregation," and "spine"
-routers; and in a backbone network, they may correspond to "core" and "border"
+To configure large networks, instead of considering individual
+devices, operators classify devices into {\em roles}. A role refers to
+specific functionality and is served by one or more devices. For instance, in a
+data center, roles may be "top-of-rack," "aggregation," and "spine"
+routers; and in a backbone network, they may be "core" and "border"
 routers. While the network may have hundreds or thousands of devices---a scale
@@
 Operators author a configuration {\em template} for each role. Templates are
-macros that can be instantiated with different concrete values, based on the
-network topology, to generate a configuration for each device.
+macros that, given a network topology, can be instantiated with different concrete values to generate device configurations.
 
@@
 manually decompose network-wide routing and fault-tolerance policies (e.g.,
-prefer one end-to-end path over another or no loss in connectivity after any
-one-link failure) across roles and encode them using assembly-language-like
+prefer one path over another, or a link failure should not cause connectivity loss) across different roles and encode the decomposition using assembly-language-like
 configuration primitives (e.g., role A should not transmit routing information
-from B to C). Such decomposition tasks are highly complex~\cite{propane}.
-
-Worse, operators can never be sure that the generated templates correctly
-implement the policy,  beyond testing some concrete instantiations using
-simulation or verification tools~\cite{x,y}. Testing based on concrete
-instantiations is insufficient because large networks evolve continuously, as
+from B to C). Such decomposition and encoding is highly complex~\cite{propane}.
+
+Worse, operators can never be sure that their templates correctly implement the policy. %
+Formally verifying them is difficult; today's hand-generated templates have no particular semantics---which policies they implement and for which topologies---other than those of the configurations obtained from instantiating them.
+%
+Thus, operators validate templates by testing some concrete instantiations using
+simulation or verification tools~\cite{x,y}. This testing is insufficient because large networks evolve continuously, as
 devices and links are added or taken offline for maintenance. Templates that
 work for the current network topology, may or may not work for future
-topologies. Updating the templates, if found to not work for a future topology,
+topologies, and it is intractable to test all possible future topologies. Updating the templates, if found to not work for a future topology,
 may cause trickle-down, network-wide configuration changes, which is highly
-disruptive. Building sophisticated tools for validating templates is difficult
-because the templates today have no particular semantics---which policies they
-implement and for which topologies---other than the semantics of the
-configurations that one obtains from instantiating them.
+disruptive. 
+%Building sophisticated tools for validating templates is difficult
 
@@
 reluctant to use such systems. While they think of their network abstractly, in
-terms of roles, these systems require concrete topologies, with no understanding
-of roles as a first-order abstraction.  Even if two devices play the same role,
+terms of roles, these systems only understand concrete topologies, with no understanding of roles.  Even if two devices play the same role,
 there is no guarantee that the systems will generate (syntactically) similar
@@
 evolves. Any change in network topology requires re-execution of the engine,
-from scratch, on the changed topology.  The result may be a completely different
+from scratch, on the new topology.  The result may be a completely different
 set of configurations.
@@
 network and its fault-tolerance requirements (e.g., the number of link failures
-to tolerate). For routing policy, we borrow notation from
-Propane~\cite{propane},  which specifies traffic paths at a high-level of
-abstraction. But while Propane policies refer to concrete devices, \sysname
+to tolerate). For high-level specification of routing policy, we borrow notation from
+Propane~\cite{propane}. But while Propane policies refer to concrete devices, \sysname
 policies refer to abstract roles.
@@
 network will correctly implement the routing policy and meet the fault-tolerance
-requirements. We show how fault-tolerance analysis can be done over the abstract
-topology itself by inferring the worst-case number of edge-disjoint paths in some concrete topology using an optimizing SMT solver.
-
-\sysname templates are also evolution-friendly. When the network migrates from
+requirements.
+We show how precise fault-tolerance analysis can be done in the abstract domain by using a set of sound inference rules to infer the lower bound on the number of edge-disjoint paths in any concrete topology.
+%Our analysis uses a set of sound inference rules and  using an optimizing SMT solver.
+
+\sysname's abstract reasoning provides two other benefits. First, its templates are evolution friendly. When the network migrates from
 one concrete topology to another, both of which comply with the abstract
-topology, it is guaranteed that only the configurations of devices that acquire
-or lose a neighboring device needs to change (e.g., to activate a port on which
-the new device is connected).  No other device in the network is impacted.
-
-In addition to creating reusable templates, 
-%synthesizing configurations by working directly with an abstract topology means that 
-\sysname can scale substantially better than its nearest competitor \propane does: as the number of individual devices in a
-network grows, the number of distinct roles will often stay constant.
+topology, only the configurations of devices that acquire or lose a neighbor need to change.
+This guarantee is the best that any system can give as neighbor relationships are explicitly configured in devices.
+%No other device in the network is impacted.
+
+Second, \sysname can scale substantially better than its nearest competitor \propane that operates over concrete topologies. As the number of devices in a
+network grows, the number of distinct roles will often stay constant~\cite{surgeries-popl16}.
 Consequently, the \sysname compiler can be two orders of magnitude
@@
 \noindent
-\textbf{Contributions}: To summarize, the contributions are:
+\textbf{Contributions}: To summarize, our contributions are:
 %
@@
 concrete network satisfying the abstract connectivity invariants.
-\item Design of a template generation strategy that supports network
-evolution.
-\item Implementation and evaluation of a \sysname compiler that generates
-configuration templates and is up to two orders of magnitude faster
-than its closest competitor on large networks.
+%\item Design of a template generation strategy that supports network
+%evolution.
+\item Implementation and evaluation of the \sysname compiler that generates
+provably-correct templates and is much faster
+than a compiler based on concrete topologies.
 \end{itemize}
@@
 
-\subsection{Template Generation}
+\subsection{Compilation}
 \label{subsec:compilation}
@@
 First, it combines the abstract topology and routing policy into a {\em product graph} (PG) that compactly captures the flow of routing information over the topology in a policy-compliant manner.
-The algorithm for this phase builds on the \propane compiler, which was designed for concrete networks; we show that it can be extended to abstract inputs and that the extensions are correct.
+The algorithm for this phase builds on the Propane compiler, which was designed for concrete topologies and policy; we show that it can be extended to abstract inputs and that the extensions are correct.
 
@@
 
-The PG compactly encodes all paths that protocol messages should be passed along through the network in order to guarantee that the devices find policy-compliant paths dynamically.
+The PG compactly encodes all paths protocol messages should be passed along through the network in order to guarantee the devices find policy-compliant paths dynamically.
 %
@@
 
-The PG is constructed by adding an edge from state $m = (l_m, q_{m_1}, \dots, q_{m_k})$ to $n = (l_n, q_{n_1}, \dots, q_{n_k})$ whenever $\sigma_i(q_{m_i}, l_n) = q_{n_i}$ for each $i$ and $(l_m,l_n) \in E$.
-%
-We add edges from the $\mathit{start}$ node to any $m = (l, q_{m_1}, \dots, q_{m_k})$ when $\sigma_i(q_{0_i}, l) = q_{m_i}$ for each $i$.
+The PG is constructed by adding an edge from state $m = (l_m, q_{m_1}, \dots, q_{m_k})$ to $n = (l_n, q_{n_1}, \dots, q_{n_k})$ whenever $\sigma_i(q_{m_i}, l_n) = q_{n_i}$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
+%
+We add edges from the start node to any $m = (l, q_{m_1}, \dots, q_{m_k})$ when $\sigma_i(q_{0_i}, l) = q_{m_i}$ for each $i$.
 %
@@
 
-Figure~\ref{fig:example-compilation} shows an example of a PG for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview}.
+Figure~\ref{fig:example-compilation} shows an example of a PG for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview} ($\True ~\Path~ \CD{\Exit(N1 \Prefer~N2)}$).
 %
@@
 \begin{defn}
-\label{def:homomorphism}
 If we have a graph homomorphism $f : G \rightarrow G^A$, concrete $PG = (G',\mathit{start},P)$ and abstract $PG^A = (G'^A, \mathit{start}^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$ as follows:
@@
 \end{defn}
-
-As we will see in \S\ref{sec:generation}, we have proven that our generation strategy commutes with concrete expansion, meaning that we obtain the same results if we expand the abstraction early, or if we defer the expansion until after template generation.
-%
-Definition~\ref{def:homomorphism} provides some intuition concerning why our strategy for generating templates is correct.
-%Abstract product graphs are related to concrete product graphs via a graph homomorphism, just as abstract topologies are related to concrete topologies via a graph homomorphism.
 
@@
 \section{Template Generation}
-\label{sec:generation}
 
@@
 
-Lemma~\ref{lem:preference} tells us that inferring preferences over the abstract PG before concrete expansion is equivalent to inferring preferences over an already-expanded concrete PG.
+Lemma~\ref{lem:preference} gives us reason to believe that we can perform compilation over the abstract PG directly and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.
 
@@
 \begin{thm}
-  For any context $\Gamma$, topologies $G$ and $G^A$, homomorphism $f : G \rightarrow G^A$, and policy $pol$,
-  $$\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$$
+  For any context $\Gamma$, topology $G$, abstract topology $G^A$, homomorphism $f : G \rightarrow G^A$, and policy $pol$,
+
+  \noindent
+  $\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$
   \label{thm:concretization}
@@
 To evaluate \sysname, we apply it on policies for backbone and datacenter networks.
-We aim to evaluate the expressiveness of our abstracttions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.
+We aim to evaluate the expressiveness of our abstracttions, the precision of the abstract disjoint-path analysis, and the compilation time of \sysname both with abstraction and without.
 
@@
 
-\subsection{Generation time}
+\subsection{Compilation time}
 
@@
     {\includegraphics[width=.49\columnwidth]{figures/backbone-time.png}} \\
-  \caption{Concrete vs. Abstract Generation Time. \label{fig:compilation-times}}
+  \caption{Concrete vs. Abstract Compilation Time. \label{fig:compilation-times}}
   \vspace{-1em}
@@
     {\includegraphics[width=.49\columnwidth]{figures/backbone-analysis-time.png}} \\
-  \caption{Abstract Generation Time by Phase. \label{fig:abstract-breakdown}}
+  \caption{Abstract Compilation Time by Phase. \label{fig:abstract-breakdown}}
   \vspace{-1em}
@@
 Using abstraction allows us to naturally scale network synthesis in \sysname.
-We evaluate generation time in \sysname both with and without abstraction using routing policy for backbone and datacenter networks inspired by configurations obtained from a large cloud provider.
+We evaluate compilation time in \sysname both with and without abstraction using routing policy for backbone and datacenter networks inspired by configurations obtained from a large cloud provider.
 For both types networks, we fix routing policy but scale the size of the underlying topology.
@@
 
-Figure~\ref{fig:compilation-times} shows generation time for the same policies for both the abstract and concrete versions of the policies described above.
+Figure~\ref{fig:compilation-times} shows compilation time for the same policies for both the abstract and concrete versions of the policies described above.
 All experiments are run on an 8 core, 2.4 GHz Intel i7 processor Mac with 8GB of Ram, and the time taken is the average of 3 runs.
 
-For both the networks, the abstract generation starts off slightly slower than concrete generation for small topologies due to the overhead of the fault-tolerance analysis.
-However, as the size of the topology increases, abstract generation becomes orders of magnitude faster than concrete generation.
-In all cases for both networks, abstract generation takes less than 10 seconds to complete.
-
-Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract generation.
+For both the networks, the abstract compilation starts off slightly slower than concrete compilation for small topologies due to the overhead of the fault-tolerance analysis.
+However, as the size of the topology increases, abstract compilation becomes orders of magnitude faster than concrete compilation.
+In all cases for both networks, abstract compilation takes less than 10 seconds to complete.
+
+Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract compilation.
 Notably, the fault-tolerance analysis takes the majority of the time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost.

### 2016-11-13 paper/abstraction/paper.tex
pass over abstract

@@
 \textbf{Abstract---}
-\ryan{Copied from conclusion for reference}
-We develop \sysname, the first system that can generate device configuration templates for large networks from high-level specifications of network topology and policy.
+We develop \sysname, a system to generate provably-correct configurations for large, evolving networks from high-level specifications of their topology, routing policy, and fault-tolerance requirements.
+It is based on new abstractions for capturing parameterized network topologies, and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance.
+Our analysis operates entirely on abstract topologies and guarantees correctness for all concrete instantiations of the topology.
+Its output is also guaranteed to require minimal changes to the configurations of existing devices when the topology evolves to include new devices or links.
+Our experiments with many types of real-world topologies and policies show that our abstractions and fault-tolerance analysis are precise.
+They also show that, for large networks, our configuration synthesis is two orders of magnitude faster than systems that operate over concrete topologies.
+
+%\ryan{Copied from conclusion for reference}
+%We develop \sysname, the first system that can generate device configuration templates for large networks from high-level specifications of network topology and policy.
 \sysname is based on new abstractions for capturing parameterized network topologies, and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance.

### 2016-11-13 paper/abstraction/paper.tex
1,2,3

@@
 
-\titlebanner{DRAFT -- do not distribute}        % These are ignored unless
+%\titlebanner{DRAFT -- do not distribute}        % These are ignored unless
 \preprintfooter{submission for PLDI 2017}   % 'preprint' option specified.
@@
 \begin{itemize}[noitemsep,nolistsep,label={\large\textbullet}]
-\item Design of new topology abstractions for network programming
-based on graph homomorphisms and connectivity invariants.
-\item Design of two new algorithms for analyzing routing policy over
-abstract networks: one which
-guarantees correct compilation and one which determines fault tolerance
-properties of network policy.  Both algorithms provide guarantees for any
-concrete network satisfying the abstract connectivity invariants.
+\item New topology abstractions for network programming
+based on graph homomorphisms and connectivity rules.
+\item New algorithms for analyzing routing policy and fault tolerance over
+abstract topologies.
+%one which guarantees correct compilation and one which determines fault tolerance
+%properties of network policy.
+%Both algorithms provide guarantees for any
+%concrete network satisfying the abstract connectivity invariants.
 %\item Design of a template generation strategy that supports network
@@
 
-In this work, we focus on synthesizing configurations for a network that runs the Border Gateway Protocol (BGP), which is the standard for routing across independent organizations and inside large datacenters.
+In this work, we focus on synthesizing configurations for a network that runs the Border Gateway Protocol (BGP), the standard for routing across independent organizations and inside large datacenters.
 It scales effectively and allows operators to define flexible policies.
 
-The interactions among BGP routers determines how the network forwards traffic.
-To invite traffic from a neighbor to a destination, routers announce the destination's address {\em prefix} (e.g., 10.1.1.0/24\footnote{An IP(v4) address
+We provide a brief background on BGP focused on aspects relevant to our work.
+How a BGP-based network carries traffic depends on how the routers exchange and process routing announcements.
+To invite traffic from a neighbor to a destination, routers announce the destination's address {\em prefix} (e.g., 10.1.1.0/24\footnote{An IP address
 such as 10.1.1.0 is 32 bits, with each of the four values representing 8 bits.
-A prefix such as 10.1.1.0/24 denotes the set of addresses that share the first 24 bits with 10.1.1.0, \IE, all addresses that begin with 10.1.1.}) to the neighbor.
-In this way, traffic flows in the opposite direction to such {\em route announcements.}
-
-Route announcements contain additional attributes. A common one is {\em AS path}, which denotes the sequence of Autonomous Systems that will be traversed to reach the destination.
+The prefix 10.1.1.0/24 denotes the set of addresses that share the first 24 bits with 10.1.1.0, \IE, all addresses that begin with 10.1.1.}) to the neighbor.
+Traffic flows in the opposite direction to such route announcements.
+
+All route announcements carry {\em AS path}, the sequence of BGP speakers (called Autonomous Systems) that will be traversed to reach the destination.
 %When BGP is used inside a datacenter, each router tends to be its own AS.
-Optional attributes include one or more {\em communities}, which are arbitrary strings. Operators agree on what each community value means out of band.
-
-A BGP router may receive one or more announcements from different neighbors for the same prefix.
-It selects the best one based on its local {\em import policy}.
-These policies are a function of the AS path, communities, or the neighbor that sent the announcement, and may even filter some announcements altogether (i.e., not use them even if no other announcements to the destination are available).
-Then, based on the local {\em export policy}, the router announces the selected route to one or more neighbors, after adding itself to the AS path and, optionally, modifying the set of communities.
+Optionally, they may also include one or more {\em communities}, which are arbitrary tags whose semantics are agreed upon out of band.
+
+When a BGP router receives one or more announcements for a prefix from different neighbors, it selects which one to use (if any) based on its configuration.
+This selection can depend on the AS path, communities, or the neighbor that sent the announcement, and it can even discard certain announcements (i.e., never use them for sending traffic).
+Then, based again on its configuration, the router forwards the selected route to one or more neighbors, after adding itself to the AS path, and optionally, modifying communities.
 
@@
 
-A BGP router may also perform {\em route aggregation} when exporting to certain neighbors.
-That is, instead of announcing multiple prefixes it may announce a single covering prefix (e.g., 10.1.0.0/16 instead of 10.1.[1--255].0/24).
-The covering prefix is announced as long as the router has a valid route to any of the covered prefixes.
+When announcing destinations to certain neighbors, a BGP router may perform {\em route aggregation}, \IE, announce a single prefix that covers multiple prefixes (e.g., announce 10.1.0.0/16 instead of 10.1.[1--255].0/24).
+The covering prefix is announced as long as the router has a valid route for {\em any} of the covered prefixes.
 Aggregation helps reduce the memory consumption of routers, but it can lead to traffic black holes~\cite{route-aggregation}.
@@
 
-Configuring a BGP network requires configuring, among other things, the import and export policies for individual routers such that traffic flows in a way that is compliant with the network's global policies.
+%Configuring a BGP network requires configuring, among other things, the import and export policies for individual routers such that traffic flows in a way that is compliant with the network's global policies.
 Making matters worse, configuring the policies of individual routers requires tweaking low-level primitives for route selection preferences, route modification rules, and filtering and aggregation criteria.
+
+%Configuring a BGP network requires configuring how each router announces various prefixes to different neighbors and how it selects among possibly multiple announcements for a prefix from different neighbors.
+
+%The operators goal is that the collective impact of these configurations traffic flows in a way that is compliant with the network's global policies.
 
@@
 
-We demonstrate the difficulty of configuring networks using the example data center network in Figure~\ref{fig:example}.
+We demonstrate the difficulty of configuring networks today using the data center example in Figure~\ref{fig:example}.
 The boxes denote routers.
-Using terminology for fat tree networks~\cite{fattree}, S[1--2] denote spine routers, A[1--8] denote aggregation routers, and T[1--8] denote top-of-rack (ToR) routers.
-The spine routers are connected to the
-rest of the Internet through neighbors N[1--2]. The aggregation routers
-bridge the spine to the ToR routers. The ToR routers attach to a set of servers (``a rack'') that host services with address prefixes P[1--8].
+Using terminology for fat tree networks~\cite{fattree}, S[1--2] are spine routers, A[1--8] are aggregation routers,\footnote{This term is not related to BGP route aggregation.} and T[1--8] are top-of-rack (ToR) routers.
+The spine routers connect to the Internet through neighbors N[1--2].
+%The aggregation routers bridge the spine to the ToR routers. 
+The ToR routers attach to a set of servers (``a rack'') that host services with address prefixes P[1--8].
 
@@
 The intended policy for this network is:
-$(1)$ complete internal connectivity, \IE, all routers should be able to talk to each other;
-$(2)$ services in Pods[1--2] should be globally accessible;
+$(1)$ complete internal connectivity, \IE, all routers should be able to reach each other;
+$(2)$ services in Pods[1--2] should be accessible from outside;
 $(3)$ prefixes for global service should be aggregated into a covering prefix PG when announced outside;
 $(4)$ services in Pods[3--4] should not be externally accessible;
-$(5)$ paths should be valley-free, \IE, never go down then back up.
+$(5)$ traffic paths should be valley-free, \IE, not go down then back up.
 $(6)$ prefer neighbor N1 over N2, \IE, when both neighbors announce a prefix, send traffic through N1;
-$(7)$ datacenter routers should not transit traffic between N1 and N2; and
+$(7)$ routers should not transit traffic between N1 and N2; and
 $(8)$ no loss in connectivity after any single-link failure.
 
-To correctly configure this policy, network operators must generate configurations for each router.
-This implies ensuring, for instance, that all router interfaces are assigned correct addresses; all routing adjacencies are correctly configured (\EG, T1's configuration includes A1 as neighbor and vice-versa); all routers announce their own addresses (so that they can be reached from other routers) and the ToRs announce the correct prefixes for their services; all routers  forward the prefix announcements that they should to each neighbor and not forward those that they should not (\EG, the spines should forward prefixes for local services to internal neighbors but not external neighbors); and the spines announce externally only the aggregate global prefix.
+To correctly configure this policy, operators must generate configurations for each router, which implies ensuring, for instance, that all routing adjacencies are correctly configured (\EG, T1's configuration includes A1 as neighbor and vice-versa); the ToRs announce the correct prefixes for their services; all routers  forward the prefix announcements that they should to each neighbor and not forward others (\EG, the spines should forward prefixes for local services to internal neighbors but not to external neighbors); and the spines announce externally only the covering global prefix.
 Such configuration tasks are highly complex~\cite{juniper-study,bgpmon,batfish,propane}.
 
-To simplify network configuration, the operations community is adopting a template-based approach~\cite{hatch,thwack}.
-Instead of authoring a configuration file per router, operators author one configuration template per role.
-%
-A {\em role} refers to specific functionality and is played by one or more routers.\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor-specific configuration languages.}
+To simplify network configuration, operators are adopting a template-based approach~\cite{hatch,thwack}. Instead of authoring a configuration per router, operators author a template per role.
+%
+A {\em role} is a specific function that is served by one or more routers.
+%\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor configuration languages.}
 %
@@
 %
-Templates have parameters for various aspects of the configuration (\EG, interface addresses, neighbor list) and are compiled to device configurations by instantiating the parameters using a database of network information.
+Templates have parameters for various aspects of the configuration (\EG, neighbor list) and are compiled to device configurations by instantiating the parameters using the network topology and a database of network information.
 
@@
 %While templates help avoid a class of configuration errors (e.g., inconsistent routing adjacencies), they provide no guarantees
-Templates that work for one topology may not work for seemingly-inconsequential variations.
+As described earlier (\S\ref{sec:introduction}), templates are hard to author and hard to validate.
+At the same time, templates that work for one topology may not work for seemingly-inconsequential variations (which may arise after the network evolves).
+Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}: it has the same five roles, connected in a similar hierarchy.
+One might think that the same templates (with different database entries) can be used for both cases.
+However, if the templates are configured to disallow ``valley" paths (per policy (5) above), they will work for Figure~\ref{fig:example} but silently violate the fault tolerance policy ($(8)$) when used for Figure~\ref{fig:example2}.
+Specifically, in Figure~\ref{fig:example2}, an aggregation-based blackhole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]).
+No such blackhole will occur in Figure~\ref{fig:example} after a single link failure because spine routers have two links to each pod.
+
 %Unfotunately, currently, there is no way to predict which variations will behave correctly for a given set of templates.
-Worse, when operators discover their old templates no longer work, changing a template will
-cause a change to all devices that use that template---an unacceptable disruption in many cases.
+
+Today, if operators discover their old templates no longer work, changing a template will
+cause a change to all devices that use it---an unacceptable disruption in many cases.
 When that happens, operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the change.
@@
 %% Such patches reintroduce the complexity and errors that templates were meant to prevent.
-
-Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}; it has the same five roles, connected in a similar hierarchy.
-One might think that the same templates (with different database entries) can be used for both topologies.
-However, because the templates are configured to disallow ``valley" paths, which go down, and then up, these templates will work perfectly for Figure~\ref{fig:example} but silently violate the fault tolerance requirement ($(8)$) when used for Figure~\ref{fig:example2}.
-Specifically, in Figure~\ref{fig:example2}, an aggregation-induced blackhole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]).
-In contrast, in Figure~\ref{fig:example}, no such blackhole will occur after a single link failure because spine routers have two links to each pod.
 

### 2016-11-13 paper/abstraction/paper.tex
typo fix
add examples for hyperx and bcube
add text to match images

@@
   \vspace{-2em}
-  \caption{An abstraction for the datacenters in Figure~\ref{fig:example}.}
+  \caption{An abstraction for the network in Figure~\ref{fig:example}.}
   \label{fig:example3}
@@
 
+Recall the policy for global prefixes in the datacenter.
+%
+\begin{code}
+\$GP \Path \End(TG) \ensuremath{\cap}
+       \Novalley(\{TG,TL\},\{AG,AL\},\{S\}) \ensuremath{\cap}
+       !(\Enter(Peer) & \Exit(Peer))
+\end{code}
+\noindent
+%
+Figure~\ref{fig:example-inference} shows part of the abstract PG representation for this routing policy.
+The inference algorithm starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$ (\IE, no restriction on the number of disjoint paths initially).
+%
+The first step applies the rule \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles.
+This invokes a call to $\nu$Z to minimize the expression $min(\infty, AG)$, which results in 2.
+Therefore, the algorithm learns a new invariant of the form $S_P A_{AG} (2,1)$ for node $(AG, 0)$ to indicate that in some pod P, any group of 2 nodes is reachable.
+%
+The next step uses the inference rule \infrule{I-out2} to learn that any single spine node is reachable.
+It also can apply rule \infrule{I-striping} to determine that there is some group of at least 2 spine routers reachable at node $(S,0)$ and also that there is some group of at least 2 nodes reachable in the AL role in state $(AL,0)$.
+
+Note that, because each inference rule only applies to directed edges in the PG, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
+This restriction ensures that the analysis is policy-sensitive.
+
+The next step is to use \infrule{I-mesh2} together with \infrule{I-local} to infer than any single node in the TL role for any pod Q is reachable via at least 2 disjoint paths.
+This process will continue until a fixed point is reached.
+
+In this case, the algorithm was able to infer that any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a router in role TG.
+Note that, in this case, the analysis is precise.
+There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router due to the valleyfree constraint.
+In this case in particular, the bound on the fault tolerance between a tor and spine router can be used to determine that an aggregation-induced black hole may arise at the border of the datacenter after a single failures in some topologies.
+
 \begin{figure}
@@
 \end{figure}
-
-Recall the policy for global prefixes in the datacenter.
-%
-\begin{code}
-\$GP \Path \End(TG) \ensuremath{\cap}
-       \Novalley(\{TG,TL\},\{AG,AL\},\{S\}) \ensuremath{\cap}
-       !(\Enter(Peer) & \Exit(Peer))
-\end{code}
-\noindent
-%
-Figure~\ref{fig:example-inference} shows part of the abstract PG representation for this routing policy.
-The inference algorithm starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$ (\IE, no restriction on the number of disjoint paths initially).
-%
-The first step applies the rule \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles.
-This invokes a call to $\nu$Z to minimize the expression $min(\infty, AG)$, which results in 2.
-Therefore, the algorithm learns a new invariant of the form $S_P A_{AG} (2,1)$ for node $(AG, 0)$ to indicate that in some pod P, any group of 2 nodes is reachable.
-%
-The next step uses the inference rule \infrule{I-out2} to learn that any single spine node is reachable.
-It also can apply rule \infrule{I-striping} to determine that there is some group of at least 2 spine routers reachable at node $(S,0)$ and also that there is some group of at least 2 nodes reachable in the AL role in state $(AL,0)$.
-
-Note that, because each inference rule only applies to directed edges in the PG, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
-This restriction ensures that the analysis is policy-sensitive.
-
-The next step is to use \infrule{I-mesh2} together with \infrule{I-local} to infer than any single node in the TL role for any pod Q is reachable via at least 2 disjoint paths.
-This process will continue until a fixed point is reached.
-
-In this case, the algorithm was able to infer that any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a router in role TG.
-Note that, in this case, the analysis is precise.
-There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router due to the valleyfree constraint.
-In this case in particular, the bound on the fault tolerance between a tor and spine router can be used to determine that an aggregation-induced black hole may arise at the border of the datacenter after a single failures in some topologies.
 
@@
 
-\begin{figure}[t!]
-%  \begin{code}
-%    \Template{S}
-%      Match[100] \PREFIX=\$GP, \PEER=\{AG, AL\}
-%        \PEER \Arrow *
-%      Match[100] \PREFIX=\$LP, \PEER=\{AG, AL\}
-%        \PEER \Arrow \{AG, AL\}
-%      Match[110] \PREFIX=true \PEER=\{P1\},
-%        \PEER \Arrow *, \COMM \Arrow (1,0)
-%      Match[100] \PREFIX=true \PEER=\{P2\},
-%        \PEER \Arrow *, \COMM \Arrow (0,1)
-%      ...
-%  \end{code}%
-
-%  \vspace{-2em}
-%  \begin{code}
-%    \Router{S1, S2}
-%      Match[100] \PREFIX=GP1, \PEER=\{AG1, AL1, ...\}
-%        \PEER \Arrow *
-%      Match[100] \PREFIX=GP2, \PEER=\{AG1, AL1, ...\}
-%        \PEER \Arrow *
-%      ...
-%      Match[100] \PREFIX=LP1, \PEER=\{AG1, AL1, ...\}
-%        \PEER \Arrow \{AG1, AL1, ...\}
-%      Match[100] \PREFIX=LP2, \PEER=\{AG1, AL1, ...\}
-%        \PEER \Arrow \{AG1, AL1, ...\}
-%      ...
-%      Match[110] \PREFIX=true, \PEER=\{P1\},
-%        \PEER \Arrow *, \COMM \Arrow (1,0)
-%      Match[100] \PREFIX=true, \PEER=\{P2\},
-%        \PEER \Arrow *, \COMM \Arrow (0,1)
-%      ...
-%    \end{code}
-
-  \begin{center}
-  \includegraphics[width=\columnwidth]{figures/configs}
-  \end{center}
-  \vspace{-1em}
-  \caption{Spine template and concrete configurations (left), and evolution-friendly templates (right).}
-  \label{fig:bgp-configs}
-\end{figure}
-
 \section{Template Generation}
@@
 Lemma~\ref{lem:preference} tells us that inferring preferences over the abstract PG before concrete expansion is equivalent to inferring preferences over an already-expanded concrete PG.
+
+\begin{figure}[t!]
+  \begin{center}
+    \includegraphics[width=\columnwidth]{figures/configs}
+  \end{center}
+  \vspace{-1em}
+  \caption{Spine template and concrete configurations (left), and evolution-friendly templates (right).}
+  \label{fig:bgp-configs}
+\end{figure}
 
@@
   For any context $\Gamma$, topologies $G$ and $G^A$, homomorphism $f : G \rightarrow G^A$, and policy $pol$,
-  $$\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$$
+
+  \vspace{1em}
+  \noindent
+  $\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$
   \label{thm:concretization}
@@
 %
-\vspace{-1em}
+\vspace{-.8em}
 Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix.
@@
 We aim to evaluate the expressiveness of our abstracttions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.
+
+\begin{figure}[t!]
+  \begin{minipage}[t]{\linewidth}
+    \hdr{HyperX}{}
+    \vspace{.6em}
+    \includegraphics[width=\linewidth]{figures/hyperx}
+  \end{minipage}%
+
+  \vspace{1.4em}
+  \begin{minipage}[t]{\linewidth}
+    \hdr{BCube}{}
+    \vspace{.3em}
+    \includegraphics[width=\linewidth]{figures/bcube}
+  \end{minipage}%
+
+  \caption{Example abstractions for HyperX and BCube.}
+  \vspace*{-1em}%
+  \label{fig:example-abstractions}
+\end{figure}
 
@@
 
-%\begin{figure}[t!]
-%  \begin{center}
-%      \begin{tabular}{| l l | c | c | c |}
-%      \hline
-%      \textbf{Topology} & \textbf{Variant} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
-%      Fattree
-%         & Google &  & \cmark & \cmark  \\
-%         & Facebook &  & \cmark & \cmark \\
-%         & F10 &  & \cmark & \cmark \\ \hline
-%      Recursive
-%         & BCube & $k$ & \cmark & \xmark \\
-%         & DCell & $k$ & \cmark & \xmark \\ \hline
-%         %& HCN & $h$ & \cmark & \xmark \\
-%      Hypercube
-%         & Standard & $N$ & \cmark & \cmark \\
-%         & HyperX & $L$ & \cmark & \cmark \\ \hline
-%      Random \footnote{foo}
-%         & Scafida &  & ??? & ??? \\
-%         & JellyFish &  & ??? & ??? \\
-%      \hline
-%      \end{tabular}
-%  \end{center}
-%  \caption{Abstract Analysis Precision.}
-%  \label{fig:analysis-precision}
-%\end{figure}
-
 We evaluate the expressiveness and precision of our fault-tolerance analysis on a range of different network topologies found in network literature and in production networks.
@@
 These include the BCube~\cite{bcube} and Dcell~\cite{dcell} topologies.
-Each topology includes a recursion depth parameter ($k$), which we must fix.
-For a recursive topology with depth $d$, we model it as an abstract topology consisting of an abstract node for each of the depth $d-1$ subcomponents.
+Each topology includes a recursion depth parameter ($k$), which we fix.
+For a recursive topology with depth $k$, we model it as an abstract topology consisting of a pod to represent all depth $k-1$ subcomponents.
 This allows for safe expansion within a subcomponent, but not from increasing the recursion depth.
+For BCube, we model each tier of the datacenter as a separate role. Figure~\ref{fig:example-abstractions} shows an example of a BCube abstraction for $k=1$.
 The analysis is able to accurately determine reachability (i.e., at least 1 disjoint path) for each recursive topology, but is overly conservative in determining k-disjoint paths.
@@
 
-Hypercube variants can be used as an alternative to Clos-style topologies for networks with high-radix (port density) routers.
-The HyperX~\cite{hyperx} topology can be viewed as a generalization of the hypercube and butterfly topologies, which includes parameters $L$ for the lattice dimension of the network, and $S_i$ for the node multiplicity of each dimension $i$.
+Hypercube variants can be used as an alternative to Clos-style topologies for networks with port density routers.
+The HyperX~\cite{hyperx} topology is a generalization of the hypercube and butterfly topologies, which includes parameters $L$ for the lattice dimension of the network, and $S_i$ for the node multiplicity of each dimension $i$.
 %$K_i$ for the bandwidth of links for each dimension,
@@
 For a fixed number of dimensions $L$, we abstract each full mesh of $S_L$ nodes into its own abstract node.
-The $S_{x-1}$ groups of abstract nodes can be captured using pods of the abstract $S_x$ nodes.
+Nodes in dimension $S_{x-1}$ are abstracted using pods of abstract nodes from dimension $S_x$.
+Figure~\ref{fig:example-abstractions} shows an example for $L=2$.
 For all hypercube variants, the fault-tolerance analysis is precise.

### 2016-11-13 paper/abstraction/paper.tex
reorganize images

@@
 
-The syntax introduced in \S\ref{sec:overview} is just syntactic sugar for a core language based on regular expressions. Figure~\ref{fig:syntax} shows the core \sysname syntax.
-%
-A policy has one or more constraints, each of which is either an aggregation constraint or a path constraint.
-Path constraints consists of a test on a prefix destination and a list of regular expressions describing preferred network paths.
-Regular paths are defined over network locations, where each location is either a router inside the operator's network, or an external neighbor connected to the operator's network.
-Values \In~ and \Out, will match any internal and external location respectively.
-There are two types of predicates: a test for a concrete prefix $d.d.d.d/[d..d]$ matches a range of IP prefixes (\EG, 10.0.1.0/[24..32]) where metavariable $d$ represents an integer.
-
-Converting from the high-level syntax from \S\ref{sec:overview} to the core syntax is straightforward. The predicate $\True$ becomes the prefix range $0.0.0.0/[0..32]$.
-%
-Each constraint desugars to a regular expression. For example, the constraint $\Always\CD{(\In)}$ becomes $\In^*$ and the constraint $\CD{\End(TG)}$ becomes $\mathtt{\Sigma}^* \cdot \CD{TG}$.
-%
-Preferences are lifted to the top level of the regular expression when their use is unambiguous, and separate sets of constraints are joined prefix-by-prefix by taking the set intersection of their constraints.
-
-%For example, the combining the Routing and Local constraints in the data center policy from \S\ref{sec:overview} would result in the following \sysname policy:
-%
-%\begin{code}
-%\$PG  \Path \End(TG),
-%\$PL  \Path \End(TL) \ensuremath{\cap} \Always(\In),
-%\True \Path \Exit(Peer1) \Prefer \Exit(Peer2)
-%\end{code}
-%\noindent%
-%
-
-A key step for \sysname to generate device configurations is to build a data structure amenable to joint analysis of both the topology and routing policy.
-Intutively, \sysname captures both topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology into a data structure called the Product Graph~\cite{propane} (PG).
-
-The PG compactly encodes all paths that protocol messages should be passed along through the network in order to guarantee that the devices find policy-compliant paths dynamically.
-%
-%Although \sysname policies describe the routes that traffic should take through the network, network protocols (including BGP) typically disseminate router information in the opposite direction.
-For example, a router Y will tell its neighbor X that it has a route to the destination meaning that X can send traffic through Y.
-For this reason, we start by compiling
-%
-Because \sysname policies can have a separate routing policy for each predicate matching traffic, we construct one such PG for each predicate.
-
-For each regular path constraint $r_i$ from $r_1 ~\Prefer~ ..
-~\Prefer~ r_k$, we construct a DFA for the reverse of $r_i$.
-A DFA for $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ is the set of topology locations, $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
-%
-The PG is a tuple ($G'$, $start$, $P$) where $G' = (V',E')$ is a new graph with
-vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
-edges $E' \colon V' \times V'$,
-a unique starting vertex $start$,
-and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$, mapping nodes in the PG to a set of path ranks.
-
-The PG is constructed by adding an edge from state $m = (l_m, q_{m_1}, \dots, q_{m_k})$ to $n = (l_n, q_{n_1}, \dots, q_{n_k})$ whenever $\sigma_i(q_{m_i}, l_n) = q_{n_i}$ for each $i$ and $(l_m,l_n) \in E$.
-%
-We add edges from the $\mathit{start}$ node to any $m = (l, q_{m_1}, \dots, q_{m_k})$ when $\sigma_i(q_{0_i}, l) = q_{m_i}$ for each $i$.
-%
-The preference function $P(m)$ denotes the rank of paths through the PG ending at node $m$ and is defined as $P(m) = \set{i~\vert~q_{m_i} \in F_i}$.
-%
-Finally, we write $\tilde{m} = l$ to extract the topology location from a PG node, when $m = (l, q_{m_1}, \dots, q_{m_k}) \in V'$.
-
-Figure~\ref{fig:example-compilation} shows an example of a PG for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview}.
-%
-%\begin{code}
-%\True \Path \Exit(\sf{Peer1}) \Prefer \Exit(\sf{Peer2})
-%\end{code}
-%\noindent%
-%
-The first automaton represents the more preferred constraint $\CD{\Exit(N1)}$ and the second automaton represents the less preferred constraint $\CD{\Exit(N2)}$.
-The PG is shown for both an instance of a simple concrete network matching the abstraction from \S\ref{sec:overview} as well as for the abstract topology.
-
-Paths through the PG represent paths through the topology that protocol messages may use to ensure policy-compliant.
-For example, in the concrete PG, all messages from N1 are not blocked at each spine router.
-Paths for a destination learned through N1 will end in an accepting state for the first automaton (\EG, node (T1,1,0)).
-Similarly, paths for a destination learned through N2 will end in an accepting state for the second automaton.
-
-One interesting observation is that the PG for both the concrete and abstract networks share a similar structure. This leads us to the following observation:
-
-\begin{defn}
-\label{def:homomorphism}
-If we have a graph homomorphism $f : G \rightarrow G^A$, concrete $PG = (G',\mathit{start},P)$ and abstract $PG^A = (G'^A, \mathit{start}^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$ as follows:
-\[ \begin{array}{rcl}
-  f_{pg}( \mathit{start} ) & = & \mathit{start}^A  \\
-  f_{pg}( (l,q_1,\ldots,q_n) ) & = & (f(l),q_1,\ldots,q_n) \\
-\end{array} \]
-\end{defn}
-
-As we will see in \S\ref{sec:generation}, we have proven that our generation strategy commutes with concrete expansion, meaning that we obtain the same results if we expand the abstraction early, or if we defer the expansion until after template generation.
-%
-Definition~\ref{def:homomorphism} provides some intuition concerning why our strategy for generating templates is correct.
-%Abstract product graphs are related to concrete product graphs via a graph homomorphism, just as abstract topologies are related to concrete topologies via a graph homomorphism.
-
 \newcommand{\state}[4]{\node[state,#3](#1)[#4]{#2};}
@@
 \end{figure*}
+
+The syntax introduced in \S\ref{sec:overview} is just syntactic sugar for a core language based on regular expressions. Figure~\ref{fig:syntax} shows the core \sysname syntax.
+%
+A policy has one or more constraints, each of which is either an aggregation constraint or a path constraint.
+Path constraints consists of a test on a prefix destination and a list of regular expressions describing preferred network paths.
+Regular paths are defined over network locations, where each location is either a router inside the operator's network, or an external neighbor connected to the operator's network.
+Values \In~ and \Out, will match any internal and external location respectively.
+There are two types of predicates: a test for a concrete prefix $d.d.d.d/[d..d]$ matches a range of IP prefixes (\EG, 10.0.1.0/[24..32]) where metavariable $d$ represents an integer.
+
+Converting from the high-level syntax from \S\ref{sec:overview} to the core syntax is straightforward. The predicate $\True$ becomes the prefix range $0.0.0.0/[0..32]$.
+%
+Each constraint desugars to a regular expression. For example, the constraint $\Always\CD{(\In)}$ becomes $\In^*$ and the constraint $\CD{\End(TG)}$ becomes $\mathtt{\Sigma}^* \cdot \CD{TG}$.
+%
+Preferences are lifted to the top level of the regular expression when their use is unambiguous, and separate sets of constraints are joined prefix-by-prefix by taking the set intersection of their constraints.
+
+%For example, the combining the Routing and Local constraints in the data center policy from \S\ref{sec:overview} would result in the following \sysname policy:
+%
+%\begin{code}
+%\$PG  \Path \End(TG),
+%\$PL  \Path \End(TL) \ensuremath{\cap} \Always(\In),
+%\True \Path \Exit(Peer1) \Prefer \Exit(Peer2)
+%\end{code}
+%\noindent%
+%
+
+A key step for \sysname to generate device configurations is to build a data structure amenable to joint analysis of both the topology and routing policy.
+Intutively, \sysname captures both topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology into a data structure called the Product Graph~\cite{propane} (PG).
+
+The PG compactly encodes all paths that protocol messages should be passed along through the network in order to guarantee that the devices find policy-compliant paths dynamically.
+%
+%Although \sysname policies describe the routes that traffic should take through the network, network protocols (including BGP) typically disseminate router information in the opposite direction.
+For example, a router Y will tell its neighbor X that it has a route to the destination meaning that X can send traffic through Y.
+For this reason, we start by compiling
+%
+Because \sysname policies can have a separate routing policy for each predicate matching traffic, we construct one such PG for each predicate.
+
+For each regular path constraint $r_i$ from $r_1 ~\Prefer~ ..
+~\Prefer~ r_k$, we construct a DFA for the reverse of $r_i$.
+A DFA for $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
+The alphabet $\Sigma$ is the set of topology locations, $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+%
+The PG is a tuple ($G'$, $start$, $P$) where $G' = (V',E')$ is has
+vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
+edges $E' \colon V' \times V'$,
+a unique starting vertex $start$,
+and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$, mapping nodes in the PG to a set of path ranks.
+
+The PG is constructed by adding an edge from state $m = (l_m, q_{m_1}, \dots, q_{m_k})$ to $n = (l_n, q_{n_1}, \dots, q_{n_k})$ whenever $\sigma_i(q_{m_i}, l_n) = q_{n_i}$ for each $i$ and $(l_m,l_n) \in E$.
+%
+We add edges from the $\mathit{start}$ node to any $m = (l, q_{m_1}, \dots, q_{m_k})$ when $\sigma_i(q_{0_i}, l) = q_{m_i}$ for each $i$.
+%
+The preference function $P(m)$ denotes the rank of paths through the PG ending at node $m$ and is defined as $P(m) = \set{i~\vert~q_{m_i} \in F_i}$.
+%
+Finally, we write $\tilde{m} = l$ to extract the topology location from a PG node, when $m = (l, q_{m_1}, \dots, q_{m_k}) \in V'$.
+
+Figure~\ref{fig:example-compilation} shows an example of a PG for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview}.
+%
+%\begin{code}
+%\True \Path \Exit(\sf{Peer1}) \Prefer \Exit(\sf{Peer2})
+%\end{code}
+%\noindent%
+%
+The first automaton represents the more preferred constraint $\CD{\Exit(N1)}$ and the second automaton represents the less preferred constraint $\CD{\Exit(N2)}$.
+The PG is shown for both an instance of a simple concrete network matching the abstraction from \S\ref{sec:overview} as well as for the abstract topology.
+
+Paths through the PG represent paths through the topology that protocol messages may use to ensure policy-compliant.
+For example, in the concrete PG, all messages from N1 are not blocked at each spine router.
+Paths for a destination learned through N1 will end in an accepting state for the first automaton (\EG, node (T1,1,0)).
+Similarly, paths for a destination learned through N2 will end in an accepting state for the second automaton.
+
+One interesting observation is that the PG for both the concrete and abstract networks share a similar structure. This leads us to the following observation:
+
+\begin{defn}
+\label{def:homomorphism}
+If we have a graph homomorphism $f : G \rightarrow G^A$, concrete $PG = (G',\mathit{start},P)$ and abstract $PG^A = (G'^A, \mathit{start}^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$ as follows:
+\[ \begin{array}{rcl}
+  f_{pg}( \mathit{start} ) & = & \mathit{start}^A  \\
+  f_{pg}( (l,q_1,\ldots,q_n) ) & = & (f(l),q_1,\ldots,q_n) \\
+\end{array} \]
+\end{defn}
+
+As we will see in \S\ref{sec:generation}, we have proven that our generation strategy commutes with concrete expansion, meaning that we obtain the same results if we expand the abstraction early, or if we defer the expansion until after template generation.
+%
+Definition~\ref{def:homomorphism} provides some intuition concerning why our strategy for generating templates is correct.
+%Abstract product graphs are related to concrete product graphs via a graph homomorphism, just as abstract topologies are related to concrete topologies via a graph homomorphism.
 

### 2016-11-13 paper/abstraction/paper.tex
restructure section 4

@@
 
-In this section we give an overview of \sysname, a system for generating provably-correct templates from the network's policy and an {\em abstract} topology that describes device roles and connectivity invariants.
+%In this section we give an overview of \sysname, a system for generating provably-correct templates from the network's policy and an {\em abstract} topology that describes device roles and connectivity invariants.
 %As inputs, it takes a global, network-wide policy (as opposed to a per-device or even per-role policy) and an {\em abstract} topology that describes device roles and connectivity invariants.
@@
 %
-When \sysname generates templates, it guarantees that the forwarding behavior of the network will be correct for any instantiation of the templates on a concrete network that repects the abstraction.
+%When \sysname generates templates, it guarantees that the forwarding behavior of the network will be correct for any instantiation of the templates on a concrete network that repects the abstraction.
 %Furthermore, \sysname will generate configurations in such a way that, if an operator expands their network in a way compatible with the abstraction, then only configurations of devices adjacent to the change ever need to be updated.
 
-\subsection{Inputs}
+%\subsection{Inputs}
 
@@
 
-\subsection{Template Generation}
-\label{subsec:compilation}
+\para{Template Generation}
 
@@
 than the desired fault-tolerance level for a pair of nodes, \sysname declares that the
-policy cannot be met.  More specifically,
+policy cannot be met.  
+\ryan{Possibly cut here}
+More specifically,
 for each abstract role in the network, our analysis will learn facts about the
@@
 
+\ryan{Possibly cut here}
 As an example, suppose we want to compute the number of of disjoint paths

### 2016-11-13 paper/abstraction/paper.tex
reference to mix-mode networks in abstract topology

@@
 \para{Abstract topology}
-Abstract topologies in \sysname define structural and role-based invariants that describe a collection of concrete networks.
-These invariants are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
-%
-We designed these abstractions to be able to precisely capture many real network topologies, while also being amenable to fault-tolerance analysis and configuration synthesis.
+Abstract topologies in \sysname define structural and role-based invariants that compactly describe all concrete networks that can emerge as the network evolves.
+They are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
+%
+We designed the abstractions to be able to precisely capture real network topologies, while being amenable to fault-tolerance analysis in the abstract domain.
 
@@
 %
-In order to refine the abstraction to capture more precisely the kinds of concrete networks of interest,
+To capture more precisely the kinds of concrete networks of interest,
 we introduce several additional concepts.
@@
 The second is a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
-with a symbolic variable (\EG, $e1, e2, \ldots$) that denotes a constraint on the number of edges (and nodes) that may appear in any given concrete network.
-Operators can capture concrete network invariants by adding constraints on the symbolic variables using logical formula.
+with a symbolic variable (\EG, $e1$) that denotes a constraint on the number of edges (and nodes) that may appear in any valid concrete network.
+Operators can capture concrete network invariants by adding constraints on the symbolic variables using logical formulas.
 
@@
 A final type of abstraction is the $\Mincut(1)$ constraint between the spine role S and N[1--2].
-The mincut constraint says that any node in the spine role has at least one path to any node in the neighbor N1 (and N2) role.
-Annotations of this form are often useful for a "one big switch" abstraction \cite{Casado:2010} in which part of a complex network is represented as a single node.
-For example, to model an ISP backbone network the operator might divide the network into separate geographic regions with two abstract roles per region -- one role for the border routers of the network, and another role for the core of the network.
+It says that any node in the spine role has at least one path to any node in the neighbor N1 (and N2) role.
+Such annotations are useful for a "one big switch" abstraction \cite{Casado:2010} in which part of a complex network is represented as a single node.
+For example, to model an ISP backbone network the operator might divide the network into separate geographic regions with two roles per region---one for the border routers and another for the core of the network.
 Mincut annotations can be used to describe the degree of fault tolerance both within region cores as well as across regions.
+
+Our topology abstractions can trivially capture concrete topologies; there will be a one-to-one correspondence between abstract and concrete nodes (and edges).
+This ability enables operators to define complex networks in which they expect some (e.g., legacy) parts of the network to not evolve and others to evolve.
+It also means that our compiler subsumes those that operate only over concrete topologies.
 

### 2016-11-13 paper/abstraction/paper.tex
separate analysis by all/some pairs. add valleyfree results

@@
   \begin{center}
-      \begin{tabular}{| l | c | c | c |}
+      \begin{tabular}{| l | c | c | c | c | c | }
       \hline
-      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
-      Fattree~\cite{fattree} & & \cmark & \cmark  \\ \hline
-      Facebook~\cite{facebook-fattree} & & \cmark & \cmark \\ \hline
-      F10~\cite{f10-fattree} & & \cmark & \cmark \\ \hline
-      VL2~\cite{vl2-fattree} & & & \\ \hline
-      BCube~\cite{bcube} & $k$ & \cmark & \xmark \\ \hline
-      Dcell~\cite{dcell} & $k$ & \cmark & \xmark \\ \hline
+      \textbf{Topology} & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
+      & & Some & All & Some & All \\ 
+      & & Pairs & Pairs & Pairs & Pairs \\ \hline
+
+      Fattree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \xmark  \\ \hline
+      Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
+      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \xmark \\ \hline
+      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \xmark \\ \hline
+      BCube~\cite{bcube} & $k$ & \cmark & \cmark & \xmark & \xmark \\ \hline
+      Dcell~\cite{dcell} & $k$ & \cmark & \cmark & \xmark & \xmark \\ \hline
          %& HCN & $h$ & \cmark & \xmark \\
-      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark \\ \hline
-      Hypercube & $N$ & \cmark & \cmark \\ \hline
-      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark \\ \hline
+      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark & \cmark & \cmark \\ \hline
+      Hypercube & $N$ & \cmark & \cmark & \cmark & \cmark \\ \hline
+      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark & \cmark & \cmark \\ \hline
       \end{tabular}
@@
   \vspace{-.6em}
-  \caption{Fault-tolerance analysis precision.}
+  \caption{Fault-tolerance analysis precision for various topologies with shortest path routing.}
   \label{fig:analysis-precision}
   \vspace{-1em}
+\end{figure}
+
+\begin{figure}[t!]
+  \begin{center}
+      \begin{tabular}{| l | c | c | c | c | }
+      \hline
+      \textbf{Clos Variant} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
+      & Some & All & Some & All \\ 
+      & Pairs & Pairs & Pairs & Pairs \\ \hline
+
+      Fattree & \cmark & \cmark & \cmark & \cmark  \\ \hline
+      Facebook & \cmark & \cmark & \cmark & \cmark \\ \hline
+      F10 & \cmark & \cmark & \cmark & \cmark \\ \hline
+      VL2 & \cmark & \cmark & \cmark & \cmark \\ \hline
+      \end{tabular}
+  \end{center}
+  \vspace{-.6em}
+  \caption{Fault-tolerance analysis precision for fat tree topologies with valley-free routing.}
+  \label{fig:analysis-precision}
 \end{figure}

### 2016-11-14 paper/abstraction/paper.tex
add concrete templates

@@
 
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=1.02\columnwidth]{figures/templates}
+  \caption{Example of a small part of a router template for the datacenter spine role.}
+  \label{fig:example2}
+  \vspace{-1em}
+\end{figure}
+
 We demonstrate the difficulty of configuring networks today using the data center example in Figure~\ref{fig:example}.
@@
 Templates have parameters for various aspects of the configuration (\EG, neighbor list) and are compiled to device configurations by instantiating the parameters using the network topology and a database of network information.
+\ryan{TODO: discuss figure}
 
@@
 
-\para{Template Generation}
+\para{Synthesis}
 
@@
 valid topological paths if the routing policy disallows it.
-
+%
 We develop a sound analysis based on computing the minimum
@@
 policy cannot be met.
-\ryan{Possibly cut here}
-More specifically,
-for each abstract role in the network, our analysis will learn facts about the
-number of disjoint paths to routers in that role.  For example,
-the fact $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
-in the $S$ (Spine) role, there are 6 disjoint paths to the group---3
-for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
-\emph{some} group of 2 nodes has the property as opposed to all.
-More generally, there is one quantifier ($A$ for all groups
-and $S$ for exists a group).  When nodes are nested within pods,
-there is one quantifier for each level of the hierarchy, so
-$S_P S_{TG} (i,j)$ means that for some pod from the $P$ group of pods
-and for some nodes in the $TG$ role within that pod, there exists a
-group of $i$ nodes with $j$ paths to each node in the group.
-
-\ryan{Possibly cut here}
-As an example, suppose we want to compute the number of of disjoint paths
-between any
-global ToR and spine router in Figure~\ref{fig:example3}.
-%This can be used as a lightweight verification tool to detect certain classes of configuration bugs.
-For example, since the network is performing prefix summarization at the border of the datacenter, we might introduce a black hole after enough failures occur to disconnect a tor from a spine router.
-The analysis begins with the fact
-$S_P S_{TG} (1,1)$---there is some group of
-nodes of size 1 in the $TG$ role in some pod $P$ such that any initial
-node in the $TG$ role has 1 disjoint path to it (and all such paths are
-edge-disjoint). Since the abstract topology specifies that each node in
-the $TG$ role is in
-a full mesh with nodes in the $AG$ role within any given pod, we
-infer the fact $S_P A_{AG}(e1,1)$. This says that
-any group of nodes of size e1 in the $AG$ role is reachable with at
-least 1 path to each such node from any initial node in
-the $TG$ role.
-%
-After one more step, the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node
-In fact, due the the valley-free routing constraint, a single path is
-the worst-case fault-tolerance level for the concrete network from
-Figure~\ref{fig:example2}.
-
-If \sysname finds that the fault-tolerance policy can be met, it generates templates for the abstract topology.  Per-device BGP configurations can in turn be generated from the templates
+%\ryan{Possibly cut here}
+%More specifically,
+%for each abstract role in the network, our analysis will learn facts about the
+%number of disjoint paths to routers in that role.  For example,
+%the fact $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
+%in the $S$ (Spine) role, there are 6 disjoint paths to the group---3
+%for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
+%\emph{some} group of 2 nodes has the property as opposed to all.
+%More generally, there is one quantifier ($A$ for all groups
+%and $S$ for exists a group).  When nodes are nested within pods,
+%there is one quantifier for each level of the hierarchy, so
+%$S_P S_{TG} (i,j)$ means that for some pod from the $P$ group of pods
+%and for some nodes in the $TG$ role within that pod, there exists a
+%group of $i$ nodes with $j$ paths to each node in the group.
+
+%\ryan{Possibly cut here}
+%As an example, suppose we want to compute the number of of disjoint paths between any global ToR and spine router in Figure~\ref{fig:example3}.
+%The analysis begins with the fact
+%$S_P S_{TG} (1,1)$---there is some group of
+%nodes of size 1 in the $TG$ role in some pod $P$ such that any initial
+%node in the $TG$ role has 1 disjoint path to it (and all such paths are
+%edge-disjoint). Since the abstract topology specifies that each node in
+%the $TG$ role is in
+%a full mesh with nodes in the $AG$ role within any given pod, we
+%infer the fact $S_P A_{AG}(e1,1)$. This says that
+%any group of nodes of size e1 in the $AG$ role is reachable with at
+%least 1 path to each such node from any initial node in
+%the $TG$ role.
+%
+%After one more step, the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node
+%In fact, due the the valley-free routing constraint, a single path is
+%the worst-case fault-tolerance level for the concrete network from
+%Figure~\ref{fig:example2}.
+
+If \sysname determines that the fault-tolerance policy can be met, it generates templates for the abstract topology.  Per-device BGP configurations can in turn be generated from the templates
 using information in the concrete topology. To ensure the process is sound,

### 2016-11-14 paper/abstraction/paper.tex
begin mark phase

@@
 
-% Points to make
-%
-% (1) Lets operators think about topologies/policies at a high-level of abstraction
-%     - matches current thinking (e.g., templates)
-%
-% (2) Promotes a correct-by-construction methodology
-%
-%     properties that hold over abstract topologies hold over concrete ones
-%      - includes correct forwarding behavior
-%      - includes reachability (under k-failures)
-%
-% (3) Enables reusability (e.g., across datacenters) and expansion (e.g., within a datacenter)
-%
-% (4) lets us scale synthesis to large-scale topologies
-
 \textbf{Abstract---}
@@
   \centering
-  \includegraphics[width=1.02\columnwidth]{figures/templates}
-  \caption{Example of a small part of a router template for the datacenter spine role.}
-  \label{fig:example2}
+  \includegraphics[width=\columnwidth]{figures/templates}
+  \caption{Example of a small configuration component of a router template for the datacenter spine role.}
+  \label{fig:templates}
   \vspace{-1em}
@@
 %
-The network in Figure~\ref{fig:example} might have five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
-%
-Templates have parameters for various aspects of the configuration (\EG, neighbor list) and are compiled to device configurations by instantiating the parameters using the network topology and a database of network information.
-\ryan{TODO: discuss figure}
+For example, the network in Figure~\ref{fig:example} might have five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
+%
+Figure~\ref{fig:templates} shows an example of what a small component of a template for the spine role in the two datacenters might look like.
+The template has parameters for various aspects of the configuration (\EG, neighbor list, local prefixes) and are compiled to low-level device configurations by instantiating the parameters using the network topology and a database of network information.
 

### 2016-11-14 paper/abstraction/paper.tex
mark phase 1 complete

@@
 We develop \sysname, a system to generate provably-correct configurations for large, evolving networks from high-level specifications of their topology, routing policy, and fault-tolerance requirements.
-It is based on new abstractions for capturing parameterized network topologies, and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance.
+It is based on new abstractions for capturing parameterized network topologies and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance.
 Our analysis operates entirely on abstract topologies and guarantees correctness for all concrete instantiations of the topology.
 Its output is also guaranteed to require minimal changes to the configurations of existing devices when the topology evolves to include new devices or links.
-Our experiments with many types of real-world topologies and policies show that our abstractions and fault-tolerance analysis are precise.
-They also show that, for large networks, our configuration synthesis is two orders of magnitude faster than systems that operate over concrete topologies.
+Our experiments with many real-world topologies and policies show that our abstractions and fault-tolerance analysis are effective and that, for large networks, configuration synthesis with \sysname is two orders of magnitude faster than similar systems that operate over concrete topologies.
 
@@
 While hardware faults, backhoes, power failures and natural disasters all pose
-problems, studies have consistently shown that human errors in network
-configuration is one of the leading cause of
+problems, studies have shown that human error in network
+configuration is one of the leading causes of
 outages~\cite{juniper-study,xx}.
@@
 Unfortunately, template construction is a low-level, manual process. Operators
-manually decompose network-wide routing and fault-tolerance policies (e.g.,
+must decompose network-wide routing and fault-tolerance policies (e.g.,
 prefer one path over another, or a link failure should not cause connectivity loss) across different roles and encode the decomposition using assembly-language-like
@@
 guarantees that, when the templates are instantiated to configurations for {\em
-any} concrete topology that complies with the abstract topology, the result
+any} concrete topology that complies with the abstract topology, the resulting
 network will correctly implement the routing policy and meet the fault-tolerance
 requirements.
-We show how precise fault-tolerance analysis can be done in the abstract domain by using a set of sound inference rules to infer the lower bound on the number of edge-disjoint paths in any concrete topology.
+We show how fault-tolerance analysis can be done in the abstract domain by using a set of sound inference rules to infer the lower bound on the number of edge-disjoint paths in any concrete topology.
 %Our analysis uses a set of sound inference rules and  using an optimizing SMT solver.
@@
 In general, we need not bound the number of spine routers to admit more concrete topologies, potentially at the expense of analysis precision.
-We include the constraints $(S \mod AG) = 0$, and $(S \mod AL) = 0$ simply to show that constraints do not have to be inequalities.
-Operators can write constraints using logical formula from any theory supported by modern SMT solvers.
+We also include the constraints $(S \mod AG) = 0$, and $(S \mod AL) = 0$~simply to show that constraints do not have to be in the form of inequalities.
+Operators can write constraints using logical formulas from any theory supported by modern SMT solvers.
 
@@
 This instructs \sysname to find BGP router configurations that satisfy the conjunction of all the constraints.
-It also declares an additional constraint that we want to perform prefix summarization (as PG) for global prefixes at the border of the datacenter (\IE, along any edge starting inside our datacenter and ending at a peer outside the datacenter).
+It also declares an additional constraint that we want to perform prefix aggregation, as covering prefix PG, for global prefixes at the border of the datacenter (\IE, along any edge starting inside our datacenter and ending at a peer outside the datacenter).
 
@@
 
-The syntax introduced in \S\ref{sec:overview} is just syntactic sugar for a core language based on regular expressions. Figure~\ref{fig:syntax} shows the core \sysname syntax.
+The syntax introduced in \S\ref{sec:overview} is just syntactic sugar for a core language based on regular expressions. Figure~\ref{fig:syntax} shows the \sysname syntax.
 %
@@
 %
-Preferences are lifted to the top level of the regular expression when their use is unambiguous, and separate sets of constraints are joined prefix-by-prefix by taking the set intersection of their constraints.
+Preferences are lifted to the top level of the regular expression when their use is unambiguous, and separate sets of constraints are joined prefix-by-prefix by taking the regular expression intersection of their constraints.
 
@@
 A key step for \sysname to generate device configurations is to build a data structure amenable to joint analysis of both the topology and routing policy.
-Intutively, \sysname captures both topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology into a data structure called the Product Graph~\cite{propane} (PG).
-
-The PG compactly encodes all paths that protocol messages should be passed along through the network in order to guarantee that the devices find policy-compliant paths dynamically.
+Intuitively, \sysname captures both topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology into a new data structure called the Product Graph~\cite{propane} (PG).
+
+The PG compactly encodes all paths that protocol messages should be passed along through the network in order to guarantee that the BGP-speaking devices find policy-compliant paths dynamically.
 %
@@
 
-Figure~\ref{fig:example-compilation} shows an example of a PG for the policy that applies to all external traffic from the datacenter example in \S\ref{sec:overview}.
+Figure~\ref{fig:example-compilation} shows the PG for the datacenter policy that applies to all external traffic ($\CD{\True \Path \Exit(N1~\Prefer~N2)}$).
 %
@@
 
-Paths through the PG represent paths through the topology that protocol messages may use to ensure policy-compliant.
-For example, in the concrete PG, all messages from N1 are not blocked at each spine router.
+Paths through the PG represent paths through the topology that protocol messages may use to ensure policy-compliance.
+For example, in the concrete PG, all messages from N1 are not blocked at spine routers S1 and S2.
 Paths for a destination learned through N1 will end in an accepting state for the first automaton (\EG, node (T1,1,0)).
@@
 \label{def:homomorphism}
-If we have a graph homomorphism $f : G \rightarrow G^A$, concrete $PG = (G',\mathit{start},P)$ and abstract $PG^A = (G'^A, \mathit{start}^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$ as follows:
+If we have a graph homomorphism $f : G \rightarrow G^A$, concrete product graph $PG = (G',\mathit{start},P)$ and abstract product graph $PG^A = (G'^A, \mathit{start}^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$ in the following way:
 \[ \begin{array}{rcl}
@@
 \end{defn}
-
+%
 As we will see in \S\ref{sec:generation}, we have proven that our generation strategy commutes with concrete expansion, meaning that we obtain the same results if we expand the abstraction early, or if we defer the expansion until after template generation.

### 2016-11-14 paper/abstraction/paper.tex
sweep phase

@@
 %
-To infer bounds on the number of disjoint paths between concrete nodes we use information about the structure of the underlying concrete topologies encoded in abstraction constraints.
-%
-As discussed informally in~\ref{subsec:compilation},
-for each node in the abstract PG,
+To infer bounds on the number of edge-disjoint paths between concrete nodes, we use information about the structure of the underlying concrete topologies encoded in abstraction constraints.
+%
+For each node in the abstract PG,
 the idea is to maintain facts learned about the number of disjoint paths
 to some number of concrete routers in the node's role.
-More specifically, we maintain facts of the form:
+More specifically, we maintain invariants of the form:
 %
@@
 %
-where each label $L \in \{S,A\}$ is either $S$, which stands for "some" or is $A$, which stands for "all".
+where each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all".
 There is one label for each pod in the abstraction pod hierarchy.
@@
 there are $k$ paths to each such that all $j*k$ paths are edge-disjoint.
-%
-%For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.
+
+For example,
+an inference of the form $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
+in the $S$ (Spine) role, there are 6 disjoint paths to the group---3
+for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
+\emph{some} group of 2 nodes has the property as opposed to all.
 
@@
 
-In order to learn information about disjoint paths, we develop a collection of sound inference rules for facts of this form.
+To learn information about disjoint paths, we develop a collection of sound inference rules for invariants of this form.
 Figure~\ref{fig:inference-rules} shows each of the inference rules.
@@
 The global rule \infrule{I-global} says the same thing except when the edge goes between pods, you can infer the fact for all pods Q since the multiplicities apply equally to each pod.
-
-\subsection{An inference algorithm}
-
-The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies the inference rules from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
-Inference rule conditions are checked for validity over all concrete topologies using an SMT solver.
-In order to ensure termination, we make the observation that, for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
-Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing constraint solver $\nu$Z~\cite{z3opt}.
-
-Recall the policy for global prefixes in the datacenter.
-%
-\begin{code}
-\$GP \Path \End(TG) \ensuremath{\cap}
-       \Novalley(\{TG,TL\},\{AG,AL\},\{S\}) \ensuremath{\cap}
-       !(\Enter(Peer) & \Exit(Peer))
-\end{code}
-\noindent
-%
-Figure~\ref{fig:example-inference} shows part of the abstract PG representation for this routing policy.
-The inference algorithm starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$ (\IE, no restriction on the number of disjoint paths initially).
-%
-The first step applies the rule \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles.
-This invokes a call to $\nu$Z to minimize the expression $min(\infty, AG)$, which results in 2.
-Therefore, the algorithm learns a new invariant of the form $S_P A_{AG} (2,1)$ for node $(AG, 0)$ to indicate that in some pod P, any group of 2 nodes is reachable.
-%
-The next step uses the inference rule \infrule{I-out2} to learn that any single spine node is reachable.
-It also can apply rule \infrule{I-striping} to determine that there is some group of at least 2 spine routers reachable at node $(S,0)$ and also that there is some group of at least 2 nodes reachable in the AL role in state $(AL,0)$.
-
-Note that, because each inference rule only applies to directed edges in the PG, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
-This restriction ensures that the analysis is policy-sensitive.
-
-The next step is to use \infrule{I-mesh2} together with \infrule{I-local} to infer than any single node in the TL role for any pod Q is reachable via at least 2 disjoint paths.
-This process will continue until a fixed point is reached.
-
-In this case, the algorithm was able to infer that any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a router in role TG.
-Note that, in this case, the analysis is precise.
-There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router due to the valleyfree constraint.
-In this case in particular, the bound on the fault tolerance between a tor and spine router can be used to determine that an aggregation-induced black hole may arise at the border of the datacenter after a single failures in some topologies.
 
@@
 \end{figure}
+
+\subsection{An inference algorithm}
+
+The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies the inference rules from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
+Inference rule conditions are checked for validity over all concrete topologies using an SMT solver.
+In order to ensure termination, we make the observation that, for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
+Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing constraint solver $\nu$Z~\cite{z3opt}.
+
+Recall the policy for global prefixes in the datacenter.
+%
+\begin{code}
+\$GP \Path \End(TG) \ensuremath{\cap}
+       \Novalley(\{TG,TL\},\{AG,AL\},\{S\}) \ensuremath{\cap}
+       !(\Enter(Peer) & \Exit(Peer))
+\end{code}
+\noindent
+%
+Figure~\ref{fig:example-inference} shows part of the abstract PG representation for this routing policy.
+The inference algorithm starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$ (\IE, no restriction on the number of disjoint paths initially).
+%
+The first step applies the rule \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles.
+This invokes a call to $\nu$Z to minimize the expression $min(\infty, AG)$, which results in 2.
+Therefore, the algorithm learns a new invariant of the form $S_P A_{AG} (2,1)$ for node $(AG, 0)$ to indicate that in some pod P, any group of 2 nodes is reachable.
+%
+The next step uses the inference rule \infrule{I-out2} to learn that any single spine node is reachable.
+It also can apply rule \infrule{I-striping} to determine that there is some group of at least 2 spine routers reachable at node $(S,0)$ and also that there is some group of at least 2 nodes reachable in the AL role in state $(AL,0)$.
+
+Note that, because each inference rule only applies to directed edges in the PG, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
+This restriction ensures that the analysis is policy-sensitive.
+
+The next step is to use \infrule{I-mesh2} together with \infrule{I-local} to infer than any single node in the TL role for any pod Q is reachable via at least 2 disjoint paths.
+This process will continue until a fixed point is reached.
+
+In this case, the algorithm was able to infer that any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a router in role TG.
+Note that, in this case, the analysis is precise.
+There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router due to the valleyfree constraint.
+In this case in particular, the bound on the fault tolerance between a tor and spine router can be used to determine that an aggregation-induced black hole may arise at the border of the datacenter after a single failures in some topologies.
 
@@
 
-%\para{ABGP language}%
-
-%We introduct a simple language for BGP configurations called ABGP.
-Figure~\ref{fig:concretization} shows the syntax for an ABGP policy.
-An ABGP policy maps topology locations $l$ to router configurations $rc$.
-Each router configuration $rc$ is a sequence of predicates $t$ and their corresponding configuration $pc$.
-A prefix configuration $pc$ is a sequence of match actions.
-Each match action $ma$ consists of a preference value $d_1$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $d_2$ expected from those neighbors, as well as export neighbors $ns_2$ and the community value $d_3$ to attach before sending to those neighbors.%
-%
-
-%\para{Compilation}%
-
-%Figure~\ref{fig:concretization} defines compilation from a \sysname policy to an ABGP policy.
-It starts by compiling ($\text{compile}_\text{PG}$) separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$.
-The function $\text{compile}_\text{PG}$ returns the test $t_i$, product graph $PG_i$, and the preference ordering $ord_i$.
-%%
-%The function $\text{compile}_\text{ABGP}$ then takes a sequence of tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy.
-For each internal router, it looks at each set of neighbor with the same community state $q_n$ and matches any of those neighbors with the preference provided by the ordering $ord$.
-It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.%
-
-%%We assume a particular router $l$ appears at most once in any abgp specification.
-%We build configs using set-builder notation.  For instance,
-%$\{l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc)\}$ denotes the abgp policy
-%%
-%\[ \begin{array}{c}
-%  l_1 \rightarrow rc_{1},... \\
-%  ...           \\
-%  l_k \rightarrow rc_{k},... \\
-%\end{array} \]
-
-%where $l_1, ..., l_k$ are the nodes in the topology
-%and each $rc_{i}$ satisfies $p(l_i,rc_{i})$. We also use the $\bigcup$ operator to denote sequence concatenation.%
-
-%\para{Concretization}%
-
-%Concretization for a \sysname policy takes as input, the policy and a context
-%$\Gamma : Var \rightarrow 2^{Prefix \times V}$,
-%which maps from a template prefix to a set of pairs of a concrete prefix and a concrete location that "owns" the prefix.
-%%
-%For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$.
-For each template variable, we replace it with a new entry for each of its corresponding concrete prefixes under the supplied mapping $\Gamma$.
-We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that this traffic is owned by the concrete location $l$.%
-
-%We also define concretization over the ABGP policy in a similar manner.
-We replace each abstract router configuration $l \rightarrow rc$ a new entry for each concrete location $\ell \in f^{-1}(l)$.
-The concrete location $\ell$ is passed as a parameter to $con$ to remember the current router.
-%%
-%To concretize a prefix policy with a template ($\$x \rightarrow pc$) we replace it with a sequence of policies, one for each prefix in context ($(pfx,l) \in \Gamma(x)$).
-Match action statements where the set of import neighbors is the singleton set containing the product graph start node $\{ start \}$ and we are not currently at looking at the router configuration for the location specified in the context $l$, then we drop the match action.
-This is denoted with the $\bullet$ symbol.
-Finally, to concretize a set of neighbors, we again use $f^{-1}$ to find the set of concrete neighbors under the inverse homomorphism, but then restrict it to those that are actually connected in the underlying concrete topology with $G.E$.
-
 \begin{thm}
@@
   \vspace{-.6em}
-  \caption{Fault-tolerance analysis precision for various topologies with shortest path routing.}
+  \caption{Fault-tolerance analysis precision for all topologies with shortest path routing.}
   \label{fig:analysis-precision}
@@
   \caption{Fault-tolerance analysis precision for fat tree topologies with valley-free routing.}
-  \label{fig:analysis-precision}
+  \label{fig:analysis-precision2}
 \end{figure}
 
-We evaluate the expressiveness and precision of our fault-tolerance analysis on a range of different network topologies found in network literature and in production networks.
+We evaluate the expressiveness of \sysname's abstractions and the precision of the fault-tolerance analysis on a range of different network topologies found both in the network literature and in production networks.
 The analysis is precise if it finds a tight lower-bound on the fault-tolerance (\IE, there is actually a concrete network with that fault tolerance).
@@
 Since many topologies have tunable parameters (\EG, the recursion depth $k$ for the Dcell topology), we list all such parameters that are fixed for the abstraction.
-We implement a shortest path routing policy over the topology and record the precision of the analysis in terms of whether or not it is able to accurately prove reachability and/or the correct number of disjoint paths between all pairs of nodes.
+For all topologies (Figure~\ref{fig:analysis-precision}), we implement a shortest path routing policy.
+Additionally, for clos-style topologies, we implement a valley-free routing policy (Figure~\ref{fig:analysis-precision2}) for comparison.
+In each case, we record the precision of the analysis in terms of whether or not it is able to accurately prove reachability and/or the correct number of disjoint paths between some or all pairs of nodes from a fixed source.
 
@@
 Each fat tree topology is parameterized over the number of pods $k$, which can be scaled up in the abstraction to allow for expansion.
-For all fat tree variants, the analysis is precise enough to determine the exact number of disjoint paths between all pairs of concrete routers.
+For all fat tree variants, the analysis correctly computes the number of ToR to ToR disjoint paths, but can lose precision between ToR to spine routers due to valley paths.
+For a valley-free routing policy, the analysis is precise for ToR to spine connectivity.
 
@@
 Hypercube variants can be used as an alternative to Clos-style topologies for networks with port density routers.
-The HyperX~\cite{hyperx} topology is a generalization of the hypercube and butterfly topologies, which includes parameters $L$ for the lattice dimension of the network, and $S_i$ for the node multiplicity of each dimension $i$.
+The HyperX~\cite{hyperx} topology generalizes the hypercube and butterfly topologies and includes parameters $L$ for the lattice dimension of the network, and $S_i$ for the node multiplicity of each dimension $i$.
 %$K_i$ for the bandwidth of links for each dimension,
@@
 
-Using abstraction allows us to naturally scale network synthesis in \sysname.
 We evaluate generation time in \sysname both with and without abstraction using routing policy for backbone and datacenter networks inspired by configurations obtained from a large cloud provider.
-For both types networks, we fix routing policy but scale the size of the underlying topology.
+For both types networks, we fix the routing policy and scale the size of the underlying topology.
 
@@
 
-Routers in the datacenter network run BGP using private AS numbers and peer with each other and with backbone networks over BGP as well.
-The routers aggregate some prefix blocks when announcing them to the backbone network, and they keep some prefixes internal.
+Routers in the datacenter network run BGP using private AS numbers and peer with multiple backbone networks.
+The routers aggregate some prefix blocks when announcing them to the backbone network, and keep some prefixes internal.
 The policy also ensures that private address space from external neighbors is dropped.
-The data center prefers that traffic leave through certain peers over others and ensures that transit traffic between peers is never allowed in the datacenter.
+The data center prefers that traffic leave through certain peers over others and ensures that transit traffic between peers is dropped.
 
 We use a fat tree topology and scale the size of the topology according the the number of pods $k$, starting with 4 pods and ending with 24 pods.
-The abstract topology uses one abstract node for each tier of the datacenter with an additional abstract node to separate local and global prefixes.
-A single abstract node is used for each class of neighbor.
+The abstract topology uses one abstract node for each tier of the datacenter with an additional abstract node for separate local and global ToRs.
 
@@
 We scale the backbone networks from 10 to 250 routers.
-The abstract topology uses a single abstract node for the network border routers and another abstract node for the network core with mincut annotation both within the core and between the core and border roles.
-Backbone neighbors are grouped into abstract nodes based on their commercial relationship to the current AS (e.g., customer, provider, peer).
+The abstract topology uses a single abstract node for the border routers and another for the network core with mincut annotations both within the core and between the core and border roles.
+Neighbors are grouped into roles based on their commercial relationship to the current AS.
 
@@
 
-Figure~\ref{fig:compilation-times} shows generation time for the same policies for both the abstract and concrete versions of the policies described above.
-All experiments are run on an 8 core, 2.4 GHz Intel i7 processor Mac with 8GB of Ram, and the time taken is the average of 3 runs.
-
-For both the networks, the abstract generation starts off slightly slower than concrete generation for small topologies due to the overhead of the fault-tolerance analysis.
+Figure~\ref{fig:compilation-times} shows total configuration generation time for \sysname vs the concrete network synthesis tool \propane.
+All experiments were run on an 8 core, 2.4 GHz Intel i7 processor machine running Mac with 16GB of Ram.
+
+For both networks, the abstract generation starts off slightly slower than \propane's concrete generation for small topologies due to the overhead of the fault-tolerance analysis.
 However, as the size of the topology increases, abstract generation becomes orders of magnitude faster than concrete generation.
@@
 
-Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract generation.
-Notably, the fault-tolerance analysis takes the majority of the time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost.
-In particular, the number of calls to $\nu$Z remains constant the across topology size.
+Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of \sysname.
+Notably, the fault-tolerance analysis takes the most time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost.
+In particular, the number of calls to $\nu$Z remains constant across topology size.
 The seesaw behavior for the data center networks results from differences in time taken by $\nu$Z to minimize similar constraints with different values.
@@
 
-\para{Topology design} Network topology design, especially for data centers, is another active research area, with researchers exploring designs with different properties~\cite{x,y,z}.
-We do not develop new designs but develop abstractions that can capture these designs (and their evolution) and algorithms that can analyze the fault tolerance of abstract topologies.
+\para{Topology design} Network topology design, especially for data centers, is another active research area, with researchers exploring designs with different properties~\cite{fattree,facebook-fattree,f10-fattree,vl2,bcube,dcell,hyperx,butterfly}.
+We do not develop new designs but develop abstractions that can capture these designs (and their evolution).
+%and algorithms that can analyze the fault tolerance of abstract topologies.
 

### 2016-11-14 paper/abstraction/paper.tex
wordsmithing 4

--- 2016-11-14 paper/abstraction/paper.tex
@@
 
-We introduce our topology abstractions using the networks from \S\ref{sec:motivation}. Topology abstractions consist of several components.
-The first is a role-based abstraction that allows an operator to map routers in the concrete network to roles in the abstract network.
-Figure~\ref{fig:example3} shows an example of an abstraction for both datacenter networks from \S\ref{sec:motivation}.
+%We introduce our topology abstractions using the networks from \S\ref{sec:motivation}.
+Our topology abstractions consist of several concepts.
+The primary one is a role-based abstraction that allows an operator to map routers in the concrete network to roles in the abstract network.
+Figure~\ref{fig:example3} shows an example of this abstraction for both networks from \S\ref{sec:motivation}.
 In the example, the concrete networks are abstracted into a new topology with 5 different roles: local ToR (TL), global ToR (TG), local aggregator (AL), global aggregator (AG), and spine (S).
-
-More specifically, a network topology is a graph $G$ = ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$.
-A role-based abstraction is a graph homomorphism from $G$ to an abstract graph $G^A$ = ($V^A$,$E^A$).
-A graph homorphism $f : G \rightarrow G^A$ maps each node in the concrete graph to a node in the abstract graph such that, whenever $(u,v) \in E$, then $(f(u),f(v)) \in E^A$.
 
@@
 
+More specifically, a network topology is a graph $G$ = ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$.
+A role-based abstraction is a graph homomorphism from $G$ to an abstract graph $G^A$ = ($V^A$,$E^A$).
+A graph homorphism $f : G \rightarrow G^A$ maps each node in the concrete graph to a node in the abstract graph such that, whenever $(u,v) \in E$, then $(f(u),f(v)) \in E^A$.
 The role-based abstraction therefore overapproximates the connectivity of the underlying concrete graphs.
-On its own, this abstraction loses a lot of information about the structure of concrete networks, making it difficult to reason precisely about fault-tolerance.
+
+On its own, this abstraction loses a lot of information about the concrete network's structure, making it difficult to reason precisely about fault-tolerance.
 %which would hinder a useful analysis of its fault-tolerance.
-For example, with this abstraction any spine router in a concrete network may or may not be connected to any aggregator router.
-%
-To capture more precisely the kinds of concrete networks of interest,
-we introduce several additional concepts.
-The first is the idea of a topology hierarchy captured by P and Q, which indicate that nodes in the ToR and aggregator roles are grouped into a number of smaller pods.
-The second is a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
+For example, with this abstraction any spine router may or may not connect to any aggregator router.
+%
+To capture concrete networks more precisely, 
+we introduce additional concepts. The first is topology hierarchy, captured by P and Q, which indicate that nodes in the ToR and aggregator roles are grouped into pods.
+The second is node and edge \emph{multiplicity}. Each edge (and node) is labelled
 with a symbolic variable (\EG, $e1$) that denotes a constraint on the number of edges (and nodes) that may appear in any valid concrete network.
@@
 
-For example, in Figure~\ref{fig:example3}, the first two constraints: $e1 = AG$ and $e2 = TG$ say that, within any pod P, the number of outgoing edges from a node in the $TG$ role to a node in the $AG$ role is equal to the number of nodes in the $AG$ role.
-Similarly, the number of outgoing edges from a node in the $AG$ role to a node in the $TG$ role is equal to the number of nodes in the $TG$ role.
-These constraints capture the fact that, within any given pod, the global aggregators and ToRs are in a full mesh.
+For example, in Figure~\ref{fig:example3}, the first two constraints: $e1 = AG$ and $e2 = TG$ say that, within any pod P, the number of outgoing edges from a node in the $TG$ role to a node in the $AG$ role equals the number of nodes in the $AG$ role.
+Similarly, the number of outgoing edges from a node in the $AG$ role to a node in the $TG$ role equals the number of nodes in the $TG$ role.
+These constraints capture the fact that, within any pod, the global aggregators and ToRs are in a full mesh.
 Furthermore, the constraints $AG = AL$ and $AG \leq S$ ensure that, within pods P and Q, the $AG$ and $TG$ roles have the same number of routers, which is less than the number of routers in the spine role $S$.
@@
 Similar constraints appear for the local aggregator role.
-The constraint $2 \leq S \leq 4$ makes explicit the possibility for growth, for example by growing the network from that of Figure~\ref{fig:example} to that of Figure~\ref{fig:example2}.
+The constraint $2 \leq S \leq 4$ makes explicit the possibility for growth, for example, by growing the network from Figure~\ref{fig:example} to Figure~\ref{fig:example2}.
 In general, we need not bound the number of spine routers to admit more concrete topologies, potentially at the expense of analysis precision.
 We also include the constraints $(S \mod AG) = 0$, and $(S \mod AL) = 0$~simply to show that constraints do not have to be in the form of inequalities.
-Operators can write constraints using logical formulas from any theory supported by modern SMT solvers.
-
-A final type of abstraction is the $\Mincut(1)$ constraint between the spine role S and N[1--2].
-It says that any node in the spine role has at least one path to any node in the neighbor N1 (and N2) role.
-Such annotations are useful for a "one big switch" abstraction \cite{Casado:2010} in which part of a complex network is represented as a single node.
-For example, to model an ISP backbone network the operator might divide the network into separate geographic regions with two roles per region---one for the border routers and another for the core of the network.
-Mincut annotations can be used to describe the degree of fault tolerance both within region cores as well as across regions.
+Operators can use logical formulas from any theory supported by modern SMT solvers.
+
+A final concept is the $\Mincut(1)$ constraint between the spine role S and N[1--2].
+It says that any spine router has at least one path to any node in the neighbor N1 (and N2) role.
+Such annotations are useful for a "one big switch" abstraction \cite{Casado:2010} in which a complex, unstructured network is represented as a single node.
+As another use case, an ISP backbone can be modeled by dividing the network into separate geographic regions with two roles per region---one for the border routers and another for the network core.
+Mincut annotations can describe the degree of fault tolerance both within regional cores and across regions.
 
@@
 
-\para{Routing policy} Routing policies in \sysname consist of an ordered sequence of both a predicate matching a class of traffic and a list of ranked constraints on the paths that the traffic matching the predicate should prefer to take through the network.
-We borrow syntax from Propane~\cite{propane}, but instead of concrete prefixes and nodes, \sysname specifications can use abstract prefixes and nodes.
-
-Let us see how to configure each of the datacenter networks from \S\ref{sec:motivation} by writing a \sysname routing policy over the abstract topology.
-We can capture the basic routing behavior, constraints (1, 2, 6), for the datacenters as follows:
+\para{Routing policy} Routing policies in \sysname consist of an ordered sequence of $i)$ a predicate that matches a class of traffic; and $ii)$ paths that the traffic should take through the network, ranked per their relative preference.
+\sysname borrows syntax from Propane~\cite{propane}, but instead of concrete predicates and paths, uses abstract predicates and paths.
+
+Let us see how to express the routing policy of the networks in \S\ref{sec:motivation} over the abstract topology. We can capture the basic routing behavior, constraints (1, 2, 6),  as follows:
 %
@@
 
-The first line introduces a prefix \emph{template} variable.
-It says that traffic for each global prefix associated with the template variable $\CD{\$GP}$ has the constraint that it should follow a path that ends at its corresponding destination router contained in the $\CD{TG}$ role.
+The second line introduces a prefix \emph{template} variable $\CD{\$GP}$.
+It says that traffic for each global prefix associated with the variable should follow a path that ends at its corresponding destination router in the $\CD{TG}$ role.
 The second line does the same for all local prefixes.
 %
-The final rule matches all other IP prefix destinations and allows traffic to follow a path that leaves the datacenter, ending up at some outside location, through either of its peers $\CD{N1}$ or $\CD{N2}$ with a preference for leaving through $\CD{N1}$ over $\CD{N2}$.
-The $\CD{\Prefer}$~symbol indicates that traffic should satisfy the constraint on the left whenever possible (\IE, a path exists in the network), and only resort to the backup (right) when this is not possible due to network failures.%
-
-Next we can capture constraint (4) that traffic for local prefixes must stay local to the datacenter:
+The final rule matches all other IP prefix destinations and allows traffic to follow a path that leaves the datacenter, ending at some outside location, through neighbors $\CD{N1}$ or $\CD{N2}$ with a preference for leaving through $\CD{N1}$.
+The $\CD{\Prefer}$~symbol indicates that traffic should satisfy the constraint on the left and resort to the backup (right) only when that is not possible due to network failures.%
+
+Next we can capture constraint (4) that traffic for local prefixes must stay within in the datacenter:
 %
@@
 %
-The Local constraint applies to any traffic destined for a local prefix described by the $\CD{\$LP}$ prefix template variable and adds the constraint that the traffic must follow a path that matches an internal location (\IE, in the datacenter) at each hop of the path.
-%
-The constraint to prevent "valleys" (5) is written:
+The Local constraint applies to any traffic destined for a local prefix described by the variable $\CD{\$LP}$ and adds the constraint that the traffic must follow a path that matches an internal location (\IE, in the datacenter) at each hop of the path.
+%
+The constraint to prevent "valleys" (5) is written as:
 %
@@
 %
-Constraint (7) to prevent transit traffic between neighbors is expressed in \sysname as:
+Constraint (7) to prevent transit traffic between neighbors is expressed as:
 %
@@
 %
-We define a $\CD{Peer}$ to be either $\CD{N1}$ or $\CD{N2}$ and disallow paths where traffic both enters the datacenter through a peer and exits through a peer.
-Finally, we can combine these constraints together as follows:
+We define a $\CD{Peer}$ as $\CD{N1}$ or $\CD{N2}$ and disallow paths where traffic both enters and exits the datacenter through a peer.
+
+Finally, we can combine these constraints together as:
 
@@
 \end{code}
-\noindent%
-
-This instructs \sysname to find BGP router configurations that satisfy the conjunction of all the constraints.
-It also declares an additional constraint that we want to perform prefix aggregation, as covering prefix PG, for global prefixes at the border of the datacenter (\IE, along any edge starting inside our datacenter and ending at a peer outside the datacenter).
+\noindent
+This instructs \sysname to satisfy the conjunction of all the constraints.
+It also declares that we want to perform route aggregation, as covering prefix PG, for global prefixes at the border of the datacenter (\IE, along any edge that connects the inside of the datacenter to the outside).
 
@@
 First, it combines the abstract topology and routing policy into a {\em product graph} (PG) that compactly captures the flow of routing information over the topology in a policy-compliant manner.
-The algorithm for this phase builds on the \propane compiler, which was designed for concrete networks; we show that it can be extended to abstract inputs and that the extensions are correct.
+The algorithm for this phase builds on the \propane compiler (for concrete networks); we show that it can be extended to abstract inputs and that the extensions are correct.
 
@@
 
-If \sysname determines that the fault-tolerance policy can be met, it generates templates for the abstract topology.  Per-device BGP configurations can in turn be generated from the templates
+If it can be met, \sysname generates templates for each node in the abstract topology.  Per-device BGP configurations can in turn be generated from the templates
 using information in the concrete topology. To ensure the process is sound,
 \sysname checks that the given concrete topology is an instance of the abstract topology.
+
+The following sections detail each of the three phases.
 

### 2016-11-14 paper/abstraction/paper.tex
wordsmithing 5

@@
 
-The syntax introduced in \S\ref{sec:overview} is just syntactic sugar for a core language based on regular expressions. Figure~\ref{fig:syntax} shows the \sysname syntax.
-%
-A policy has one or more constraints, each of which is either an aggregation constraint or a path constraint.
-Path constraints consists of a test on a prefix destination and a list of regular expressions describing preferred network paths.
-Regular paths are defined over network locations, where each location is either a router inside the operator's network, or an external neighbor connected to the operator's network.
+The first step for the \sysname compiler is to build the product graph (PG), a data structure that is amenable to joint analysis of the topology and routing policy.
+As a precursor to this step, we convert the routing policy syntax in \S\ref{sec:overview} to a core language based on regular expressions, shown in Figure~\ref{fig:syntax}.
+%
+A policy has one or more constraints, each an aggregation or a path constraint.
+Path constraints have a test on a destination prefix and a list of regular expressions describing network paths.
+Regular paths are defined over network locations, where each location is either a router inside the operator's network, or an external neighbor connected to that network.
 Values \In~ and \Out, will match any internal and external location respectively.
-There are two types of predicates: a test for a concrete prefix $d.d.d.d/[d..d]$ matches a range of IP prefixes (\EG, 10.0.1.0/[24..32]) where metavariable $d$ represents an integer.
+There are two types of predicates, as shown.
+A test for a concrete prefix $d.d.d.d/[d..d]$ matches a range of IP prefixes (\EG, 10.0.1.0/[24..32]) where metavariable $d$ represents an integer.
 
@@
 
-A key step for \sysname to generate device configurations is to build a data structure amenable to joint analysis of both the topology and routing policy.
-Intuitively, \sysname captures both topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology into a new data structure called the Product Graph~\cite{propane} (PG).
-
-The PG compactly encodes all paths that protocol messages should be passed along through the network in order to guarantee that the BGP-speaking devices find policy-compliant paths dynamically.
+%After converting the routing policy to the regular expression based language, 
+We are now ready to generate the PG.
+Intuitively, the PG captures topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology.
+%The PG compactly encodes all paths that protocol messages should be passed along through the network in order to guarantee that the BGP-speaking devices find policy-compliant paths dynamically.
 %
@@
 %
-Because \sysname policies can have a separate routing policy for each predicate matching traffic, we construct one such PG for each predicate.
+Because there can be a separate routing policy for each predicate matching traffic, we construct one PG for each predicate.
 
@@
 
-Paths through the PG represent paths through the topology that protocol messages may use to ensure policy-compliance.
+Paths through the PG represent paths through the topology that BGP announcements may use to ensure policy-compliance.
 For example, in the concrete PG, all messages from N1 are not blocked at spine routers S1 and S2.
@@
 
-One interesting observation is that the PG for both the concrete and abstract networks share a similar structure. This leads us to the following observation:
+Interestingly, the concrete and abstract PGs have a similar structure, which leads to the following observation:
 
@@
 %
-Definition~\ref{def:homomorphism} provides some intuition concerning why our strategy for generating templates is correct.
+Definition~\ref{def:homomorphism} provides intuition as to why our strategy for generating templates is correct.
 %Abstract product graphs are related to concrete product graphs via a graph homomorphism, just as abstract topologies are related to concrete topologies via a graph homomorphism.

### 2016-11-14 paper/abstraction/paper.tex
add all relevant citations

@@
 configuration is one of the leading causes of
-outages~\cite{juniper-study,xx}.
+outages~\cite{juniper-study,yankee-study}.
 
@@
 Thus, operators validate templates by testing some concrete instantiations using
-simulation or verification tools~\cite{x,y}. This testing is insufficient because large networks evolve continuously, as
+simulation or verification tools~\cite{feamster+:rcc, batfish, era, arc, bagpipe}. This testing is insufficient because large networks evolve continuously as
 devices and links are added or taken offline for maintenance. Templates that
-work for the current network topology, may or may not work for future
+work for the current topology, may or may not work for future
 topologies, and it is intractable to test all possible future topologies. Updating the templates, if found to not work for a future topology,
@@
 provably-correct configurations from high-level policy
-specifications~\cite{x,y,z,configassure,propane}. However, our conversations
+specifications~\cite{narain+:configassure,propane}. However, our conversations
 with two major cloud providers reveal that operators of large networks are
@@
 Second, \sysname can scale substantially better than its nearest competitor \propane that operates over concrete topologies. As the number of devices in a
-network grows, the number of distinct roles will often stay constant~\cite{surgeries-popl16}.
+network grows, the number of distinct roles will often stay constant~\cite{surgery}.
 Consequently, the \sysname compiler can be two orders of magnitude
@@
       BCube~\cite{bcube} & $k$ & \cmark & \cmark & \xmark & \xmark \\ \hline
-      Dcell~\cite{dcell} & $k$ & \cmark & \cmark & \xmark & \xmark \\ \hline
+      DCell~\cite{dcell} & $k$ & \cmark & \cmark & \xmark & \xmark \\ \hline
          %& HCN & $h$ & \cmark & \xmark \\
@@
 For each topology in Figure~\ref{fig:analysis-precision} we define a suitable abstraction.
-Since many topologies have tunable parameters (\EG, the recursion depth $k$ for the Dcell topology), we list all such parameters that are fixed for the abstraction.
+Since many topologies have tunable parameters (\EG, the recursion depth $k$ for the DCell topology), we list all such parameters that are fixed for the abstraction.
 For all topologies (Figure~\ref{fig:analysis-precision}), we implement a shortest path routing policy.
@@
 We also model several recursive topologies.
-These include the BCube~\cite{bcube} and Dcell~\cite{dcell} topologies.
+These include the BCube~\cite{bcube} and DCell~\cite{dcell} topologies.
 Each topology includes a recursion depth parameter ($k$), which we fix.
@@
 These can be classified into two classes.
-The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell routers how to forward packets~\cite{x,y,z}.
+The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell routers how to forward packets~\cite{foster:merlin,fattire,netgen}.
 The second class, and to which our work belongs, targets conventional networks and generates router configuration, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
@@
 
-\para{Topology design} Network topology design, especially for data centers, is another active research area, with researchers exploring designs with different properties~\cite{fattree,facebook-fattree,f10-fattree,vl2,bcube,dcell,hyperx,butterfly}.
+\para{Topology design} Network topology design, especially for data centers, is another active research area, with researchers exploring designs with different properties~\cite{fattree,facebook-fattree,f10-fattree,vl2-fattree,bcube,dcell,hyperx,butterfly}.
 We do not develop new designs but develop abstractions that can capture these designs (and their evolution).
-%and algorithms that can analyze the fault tolerance of abstract topologies.
-
-While not the focus of this paper, our tools can enable operators to pick the right design for their networks, more quickly and with stronger guarantees.
-Today, when picking the design, operators analyze its multiple concrete instantiations because available analysis tools only work with concrete topologies~\cite{condor}.
+
+While not the focus of this paper, \sysname can enable operators to pick the right design for their networks, more quickly and with stronger guarantees.
+Today, when picking a design, operators analyze its multiple concrete instantiations because available analysis tools work with concrete topologies~\cite{condor}.
 This process is time-consuming and not fool-proof; analyzing large, concrete topologies (with potentially thousands of nodes) takes a lot of time and the analysis does not cover the entire space of topologies that may arise.
@@
 \para{Network verification}
-A complementary approach to reducing configuration errors is by analyzing the forwarding rules or configuration of the network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,symmetries}.
+A complementary approach to reducing configuration errors is by analyzing the forwarding rules or configuration of the network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery}.
 Our focus, in contrast, is on a correct-by-construction approach.
-It has the downside that operators must learn to express policies in a new language, but it saves them from the challenging and time-consuming task of configuration generation and provides stronger guarantees on correctness.
+It has the downside that operators must learn to express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation and correct-by-construction guarantees.
 

### 2016-11-14 paper/abstraction/paper.tex
update section 6 to talk about merging abstract paths

@@
 the idea is to maintain facts learned about the number of disjoint paths
-to some number of concrete routers in the node's role.
+to groups of concrete routers in the node's role.
 More specifically, we maintain invariants of the form:
@@
 where each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all".
-There is one label for each pod in the abstraction pod hierarchy.
+There is one label for each pod in the abstraction pod hierarchy under which the abstract node appears.
 For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the the node itself.
@@
 For example,
-an inference of the form $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
-in the $S$ (Spine) role, there are 6 disjoint paths to the group---3
-for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
-\emph{some} group of 2 nodes has the property as opposed to all.
+an inference of the form $A_{Q} A_{TL}(2,3)$ states that, from some fixed source location, for \emph{all} pods Q, and \emph{all} groups of 2 nodes in the TL role, there are 6 disjoint paths to the group---3 for each of the 2 nodes.
 
@@
 
-To learn information about disjoint paths, we develop a collection of sound inference rules for invariants of this form.
+To learn information about disjoint paths, we develop a collection of sound inference rules for invariants of the above form.
 Figure~\ref{fig:inference-rules} shows each of the inference rules.
 The rules are read from bottom to top.
-The label on the bottom left represents a known fact of the form described above.
+The label on the bottom left represents a known invariant.
 We use $L$ to represent a rule that is parametric over the label ($S$ or $A$).
-The labels on other nodes correspond to facts learned after applying the inference rule.
+The labels on other nodes correspond to new invariants learned after applying the inference rule.
 Conditions that must be \emph{valid} for the rule to apply are shown in a box next to the rule.
@@
 
-The first rule, \infrule{I-out1} applies to a learned fact of the form $L_m(j,k)$ where the number of outgoing edges from any concrete node in the $m$ role is greater than 0.
+The first rule, \infrule{I-out1} applies to a learned invariant of the form $L_m(j,k)$ where the number of outgoing edges from any concrete node in the $m$ role is greater than 0.
 In the worst case, the largest group of concrete nodes we could hope to reach at the $n$ role would be $e_1$ since all j nodes at the bottom may have outgoing edges to the same concrete nodes at the top.
 Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$.
-Since adding edges between the nodes keeps the existing paths disjoint, and since we can not exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the top node will be $min(j*k,e_1)$.
-Since we do not know for certain that all $j$ nodes have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
+Since adding disjoint edges between the nodes keeps the existing paths disjoint, and since we can not exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the role $n$ on the top will be $min(j*k,e_1)$.
+However, because we do not know for certain that all $j$ nodes in role $m$ have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
 
@@
 The rule \infrule{I-striping} is the most complicated case.
-It starts with the fact L$_m(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid given the constraints.
+It starts with the invariant L$_m(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid given the constraints.
 The first inference for role $n$ tries to find the largest reachable group with disjoint paths to each.
@@
 Finally, the \infrule{I-local} and \infrule{I-global} rules allow us to lift each of the other rules to reason across pod hierarchies.
-The first rule, \infrule{I-local}, says that if you have an inference from L$_m(j,k)$ to L$_n(j',k')$ on the left, then if both nodes are in the same local pod P, you can leave all labels up to P unchanged.
-The global rule \infrule{I-global} says the same thing except when the edge goes between pods, you can infer the fact for all pods Q since the multiplicities apply equally to each pod.
+The first rule, \infrule{I-local}, says that if there is an inference from L$_m(j,k)$ to L$_n(j',k')$ on the left, then if both nodes are in the same local pod P, we can leave all labels up to P unchanged.
+The global rule \infrule{I-global} says that when the edge goes between pods, we can infer the fact for all pods Q since the multiplicities apply uniformly for each pod.
 
@@
 In order to ensure termination, we make the observation that, for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
-Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing constraint solver $\nu$Z~\cite{z3opt}.
+Therefore, for each inference $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing SMT solver $\nu$Z~\cite{z3opt}.
+
+The algorithm associates with each inference, the set of abstract locations used to derive the inference, \IE, an overapproximation of set of concrete locations used for the edge-disjoint paths.
+When applying an inference rule between an invariant at role $m$, with a set of abstract locations $C$, to learn an invariant at role $n$, we associate the new invariant with the set $C \cup \{ n \}$.
+%
+When, at a single PG node there is an inference $L_{X_1} \dots L_{X_{n-1}}$ A$_m(j,k)$ with location set $C$ and inference $L_{X_1} \dots L_{X_{n-1}}$ L$_m(j',k')$ with location set $D$, where $C \cap D = \emptyset$, we add a new inference with location set $C \cup D$:
+%
+$$L_{X_1} \dots L_{X_{n-1}} L_m(\min(j, j'), k + k')$$ 
+%
+\noindent
+The idea is that, because non-overlapping abstract paths can never contain overlapping concrete paths, due to the graph homomorphism property, we can merge inferences about these disjoint paths in the abstraction.
 

### 2016-11-14 paper/abstraction/paper.tex
stashing changes

@@
 For each node in the abstract PG,
-the idea is to maintain facts learned about the number of disjoint paths
+the idea is to maintain invariants learned about the number of disjoint paths
 to groups of concrete routers in the node's role.

### 2016-11-14 paper/abstraction/paper.tex
small typo fixes

@@
 specific functionality and is served by one or more devices. For instance, in a
-data center, roles may be "top-of-rack," "aggregation," and "spine"
-routers; and in a backbone network, they may be "core" and "border"
+data center, roles may be ``top-of-rack,'' ``aggregation,'' and ``spine''
+routers; and in a backbone network, they may be ``core'' and ``border''
 routers. While the network may have hundreds or thousands of devices---a scale
@@
 
-All route announcements carry {\em AS path}, the sequence of BGP speakers (called Autonomous Systems) that will be traversed to reach the destination.
+All route announcements carry an {\em AS path}, the sequence of BGP speakers (called Autonomous Systems) that will be traversed to reach the destination.
 %When BGP is used inside a datacenter, each router tends to be its own AS.

### 2016-11-14 paper/abstraction/paper.tex
small typo fixes

@@
 \sysname takes as input the network's abstract topology and its policy.
-The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous failures the network can withstand without loosing connectivity.
+The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous failures the network can withstand without losing connectivity.
 
@@
 %
-The constraint to prevent "valleys" (5) is written as:
+The constraint to prevent ``valleys" (5) is written as:
 %

### 2016-11-14 paper/abstraction/paper.tex
add edits to section 6

@@
 
-The rule \infrule{I-out2} follows a similar line of reasoning.
+Consider rule \infrule{I-out2}, and consider any node in the role $n$.
+There are $e_2$ incoming edges to that node.
+Due to the fact that A$_m(j,k)$, we know that at least j of those $e_2$ edges are connected to nodes with disjoint paths from the origin.
+Hence we infer A$_n(1,min(j,e_2))$.
+
+%The rule \infrule{I-out2} follows a similar line of reasoning.
 It says that if any group of size $j$ with $k$ disjoint paths to each is reachable in the bottom role, and there is at least one incoming edge for each concrete node in the top role, then there are $min(j,e_2)$ disjoint paths to any single concrete node in the top role.
@@
 The two rules \infrule{I-mesh1} and \infrule{I-mesh2} handle the case where there is a full mesh between the two roles.
-This happens when the number of outgoing edges from the bottom $e_1$ is equal to the number of nodes on the top $n$.
-The first case for \infrule{I-mesh1} says that we can find disjoint paths to each node in the top role restricted to the number of disjoint paths we started with.
-The second case for \infrule{I-mesh2} uses the fact that each node in the top role is connected to each node in the bottom role to infer that there can be $j$ disjoint paths to any single node in the top role.
+This happens when the number of outgoing edges ($e_1$) nodes in role $m$ equals the number of nodes on top ($n$).
+\infrule{I-mesh1} says that we can find disjoint paths to each node in the top role restricted to the number of disjoint paths we started with.
+\infrule{I-mesh2} uses the fact that each node in the top role is connected to each node in the bottom role to infer that there can be $j$ disjoint paths to any single node in the top role.
+
+The annotation $mincut(X)$ appearing on a n edge in an assertion about the fault tolerance between nodes in two roles.
+The rule \infrule{I-mincut} uses such assertions.
+To each node in role $n$, we can construct at least the minimum of $X$ and $k$ disjoint paths.
+
+%The rule \infrule{I-mincut} can be thought of as an assertion about the fault tolerance between nodes in two roles.
+The rule applies to an edge that has been annotated with a $mincut(X)$ statement, which means that there are at least $X$ disjoint paths between any node in role $m$ and any node in role $n$.
 
@@
 %
-The remaining nodes ($m-j$) that are not part of the reachable group in the bottom role, each have $e_1$ outgoing edges and must be able to at least "fill" the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each.
+The remaining nodes ($m-j$) that are not part of the reachable group in the bottom role, each have $e_1$ outgoing edges and must be able to at least ``fill" the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each.
 Solving the inequality gives the lower bound for $g$ used in Figure~\ref{fig:inference-rules}.
@@
 
-The rule \infrule{I-mincut} can be thought of as an assertion about the fault tolerance between nodes in two roles.
-The rule applies to an edge that has been annotated with a $mincut(X)$ statement, which means that there are at least $X$ disjoint paths between any node in role $m$ and any node in role $n$.
-
-Finally, the \infrule{I-local} and \infrule{I-global} rules allow us to lift each of the other rules to reason across pod hierarchies.
+Finally, rules \infrule{I-local} and \infrule{I-global} allow us to reason across pod hierarchies.
 The first rule, \infrule{I-local}, says that if there is an inference from L$_m(j,k)$ to L$_n(j',k')$ on the left, then if both nodes are in the same local pod P, we can leave all labels up to P unchanged.
@@
 
-The algorithm associates with each inference, the set of abstract locations used to derive the inference, \IE, an overapproximation of set of concrete locations used for the edge-disjoint paths.
+%The algorithm associates with each inference, the set of abstract locations used to derive the inference, \IE, an overapproximation of set of concrete locations used for the edge-disjoint paths.
 When applying an inference rule between an invariant at role $m$, with a set of abstract locations $C$, to learn an invariant at role $n$, we associate the new invariant with the set $C \cup \{ n \}$.
 %
-When, at a single PG node there is an inference $L_{X_1} \dots L_{X_{n-1}}$ A$_m(j,k)$ with location set $C$ and inference $L_{X_1} \dots L_{X_{n-1}}$ L$_m(j',k')$ with location set $D$, where $C \cap D = \emptyset$, we add a new inference with location set $C \cup D$:
-%
-$$L_{X_1} \dots L_{X_{n-1}} L_m(\min(j, j'), k + k')$$ 
-%
-\noindent
-The idea is that, because non-overlapping abstract paths can never contain overlapping concrete paths, due to the graph homomorphism property, we can merge inferences about these disjoint paths in the abstraction.
+%When, at a single PG node there is an inference $L_{X_1} \dots L_{X_{n-1}}$ A$_m(j,k)$ with location set $C$ and inference $L_{X_1} \dots L_{X_{n-1}}$ L$_m(j',k')$ with location set $D$, where $C \cap D = \emptyset$, we add a new inference with location set $C \cup D$:
+%
+%$$L_{X_1} \dots L_{X_{n-1}} L_m(\min(j, j'), k + k')$$ 
+%
+%\noindent
+%The idea is that, because non-overlapping abstract paths can never contain overlapping concrete paths, due to the graph homomorphism property, we can merge inferences about these disjoint paths in the abstraction.
 

### 2016-11-14 paper/abstraction/paper.tex
edits for section 6

@@
   \includegraphics[width=\columnwidth]{figures/templates}
-  \caption{Example of a small configuration component of a router template for the datacenter spine role.}
+  \caption{Idealized small configuration component for the datacenter spine role based on router templates from a large cloud provider (\IE, macros over gobbledygook).}
   \label{fig:templates}
-  \vspace{-1em}
+  \vspace{-.8em}
 \end{figure}
@@
 As described earlier (\S\ref{sec:introduction}), templates are hard to author and hard to validate.
-At the same time, templates that work for one topology may not work for seemingly-inconsequential variations (which may arise after the network evolves).
+Worse, templates that work for one topology may not work for seemingly-inconsequential variations (which may arise after the network evolves).
 Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}: it has the same five roles, connected in a similar hierarchy.
@@
     \inferencetwo{0}
-    \node[anchor=west] at (1,2.2) {where $g=n-\dfrac{(m-j)*e_1}{e_2}$};
+    \node[anchor=west] at (1,2.2) {where $g \geq n-\dfrac{(m-j)*e_1}{e_2}$};
     \inferencelocal{6.5}{.4}
@@
 Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$.
-Since adding disjoint edges between the nodes keeps the existing paths disjoint, and since we can not exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the role $n$ on the top will be $min(j*k,e_1)$.
-However, because we do not know for certain that all $j$ nodes in role $m$ have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
+Since extending the existing disjoint paths with disjoint edges keeps the paths disjoint, and since we can not exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the role $n$ on the top will be $min(j*k,e_1)$.
+%
+We conservatively use $1$ for the number of disjoint paths to each node in role $n$, since when $n$ is very large, all reachable nodes in role $m$ might only have a single edge to completely different nodes in $n$.
+%However, because we do not know for certain that all $j$ nodes in role $m$ have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
+%For example, if $n$ is very large, then each node in role $m$ may have only a single edge to each reachable node in role $n$.
 
@@
 There are $e_2$ incoming edges to that node.
-Due to the fact that A$_m(j,k)$, we know that at least j of those $e_2$ edges are connected to nodes with disjoint paths from the origin.
-Hence we infer A$_n(1,min(j,e_2))$.
+Due to the fact that $A_m(j,k)$, we know that at least j of those $e_2$ edges are connected to nodes with disjoint paths from the origin.
+Hence we infer $A_n(1,min(j,e_2))$.
 
@@
 The rule \infrule{I-striping} is the most complicated case.
-It starts with the invariant L$_m(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid given the constraints.
+It starts with the invariant $L_m(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid given the constraints.
 The first inference for role $n$ tries to find the largest reachable group with disjoint paths to each.
@@
 Finally, rules \infrule{I-local} and \infrule{I-global} allow us to reason across pod hierarchies.
-The first rule, \infrule{I-local}, says that if there is an inference from L$_m(j,k)$ to L$_n(j',k')$ on the left, then if both nodes are in the same local pod P, we can leave all labels up to P unchanged.
+The first rule, \infrule{I-local}, says that if there is an inference from $L_m(j,k)$ to $L_n(j',k')$ on the left, then if both nodes are in the same local pod P, we can leave all labels up to P unchanged.
 The global rule \infrule{I-global} says that when the edge goes between pods, we can infer the fact for all pods Q since the multiplicities apply uniformly for each pod.

### 2016-11-14 paper/abstraction/paper.tex
more edits

@@
 
-The annotation $mincut(X)$ appearing on a n edge in an assertion about the fault tolerance between nodes in two roles.
+The annotation $mincut(X)$ appearing on an edge in an assertion about the fault tolerance between nodes in two different roles.
 The rule \infrule{I-mincut} uses such assertions.
-To each node in role $n$, we can construct at least the minimum of $X$ and $k$ disjoint paths.
+To each node in role $n$, from a node in role $m$, we can construct at least the minimum of $X$ and $k$ disjoint paths.
 

### 2016-11-14 paper/abstraction/paper.tex
add early explanation of regex constraints
typo fixes

@@
 It says that traffic for each global prefix associated with the variable should follow a path that ends at its corresponding destination router in the $\CD{TG}$ role.
-The second line does the same for all local prefixes.
+As we will see in \S\ref{sec:language}, constraints like $\CD{\End(TG)}$ are just syntactic sugar for regular expressions describing network paths.
+The second line has a similar policy for local prefixes.
 %
@@
 Regular paths are defined over network locations, where each location is either a router inside the operator's network, or an external neighbor connected to that network.
-Values \In~ and \Out, will match any internal and external location respectively.
+Values \In\ and \Out\ will match any internal and external location respectively.
 There are two types of predicates, as shown.
@@
 %
-The PG is a tuple ($G'$, $start$, $P$) where $G' = (V',E')$ is has
+The PG is a tuple ($G'$, $start$, $P$) where $G' = (V',E')$ has
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
@@
 Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$.
-Since extending the existing disjoint paths with disjoint edges keeps the paths disjoint, and since we can not exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the role $n$ on the top will be $min(j*k,e_1)$.
+Since extending the existing disjoint paths with disjoint edges keeps the paths disjoint, and since we cannot exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the role $n$ on the top will be $min(j*k,e_1)$.
 %
@@
 The two rules \infrule{I-mesh1} and \infrule{I-mesh2} handle the case where there is a full mesh between the two roles.
-This happens when the number of outgoing edges ($e_1$) nodes in role $m$ equals the number of nodes on top ($n$).
+This happens when the number of outgoing edges ($e_1$) from nodes in role $m$ equals the number of nodes on top ($n$).
 \infrule{I-mesh1} says that we can find disjoint paths to each node in the top role restricted to the number of disjoint paths we started with.
@@
 
-The annotation $mincut(X)$ appearing on an edge in an assertion about the fault tolerance between nodes in two different roles.
+The annotation $mincut(X)$ appearing on an edge is an assertion about the fault tolerance between nodes in two different roles.
 The rule \infrule{I-mincut} uses such assertions.
@@
 %
-The remaining nodes ($m-j$) that are not part of the reachable group in the bottom role, each have $e_1$ outgoing edges and must be able to at least ``fill" the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each.
+The remaining nodes ($m-j$) that are not part of the reachable group in the bottom role, each have $e_1$ outgoing edges and must be able to at least ``fill" the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$), which each have $e_2$ incoming edges.
 Solving the inequality gives the lower bound for $g$ used in Figure~\ref{fig:inference-rules}.
 
-The second part of the rule allows uses a similar idea to reason about the overlap between roles $m$ and $o$ with respect to role $n$.
+The second part of the rule uses a similar idea to reason about the overlap between roles $m$ and $o$ with respect to role $n$.
 This rule is useful particularly useful for datacenter topologies where routers in one tier of the datacenter often have a particular striping pattern with another tier.
@@
 
-Note that, because each inference rule only applies to directed edges in the PG, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
+Note that, because each inference rule only applies to directed edges in the PG, the algorithm cannot make any inferences about connectivity from the AL role to the S role since there is no directed edge from AL to S.
 This restriction ensures that the analysis is policy-sensitive.
@@
 Note that, in this case, the analysis is precise.
-There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router due to the valleyfree constraint.
-In this case in particular, the bound on the fault tolerance between a tor and spine router can be used to determine that an aggregation-induced black hole may arise at the border of the datacenter after a single failures in some topologies.
+There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global ToR from a spine router due to the valley-free constraint.
+In this case in particular, the bound on the fault tolerance between a ToR and spine router can be used to determine that an aggregation-induced black hole may arise at the border of the datacenter after a single failure in some topologies.
 

### 2016-11-14 paper/abstraction/paper.tex
tweaks

@@
 We formalize this idea by defining a simple, vendor-neutral language for BGP configurations called \mbgp and formally define compilation for policies over both concrete and abstract topologies to \mbgp.
-In addition we define a two concretization ($con$) functions that translates an abstract \sysname policy and \mbgp configuration to a concrete \sysname policy and concrete \mbgp configuration respectively.
+In addition we define two concretization ($con$) functions that translate an abstract \sysname policy and \mbgp configuration to a concrete \sysname policy and concrete \mbgp configuration respectively.
 Concretization takes a context $\Gamma : \mathit{Var} \rightarrow 2^{\mathit{Prefix} \times V}$ that maps each template variable to a set of pairs of a concrete prefix and topology location where the prefix is owned.
-Intuitively, the spine template in concretized by replacing each abstract role with the set of all concrete routers that map to that role and each prefix template variable with a new entry in the configuration for each individual prefix provided by the context $\Gamma$.
+Intuitively, the spine template is concretized by replacing each abstract role with the set of all concrete routers that map to that role and each prefix template variable with a new entry in the configuration for each individual prefix provided by the context $\Gamma$.
 The main theoretical result is that the compilation and concretization functions commute:
@@
 The only way in which the spine routers depend on anything non-local is in the match on prefix template variables.
-Instead, we can associate a new unique community tag for template variable {\small \$GP} and then replace each match on {\small \$GP} with a test on the new community tag.
-The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can just match the community tag.
+Therefore, we can avoid having to modify the configurations for the spine routers by associating a new unique community tag for template variable {\small \$GP} and then replacing each match on {\small \$GP} with a test on the new community tag.
+The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can match against it.
 Figure~\ref{fig:bgp-configs} (right) shows the templates after the transformation.

### 2016-11-14 paper/abstraction/paper.tex
add overview for section 6

@@
 
-%
-To infer bounds on the number of edge-disjoint paths between concrete nodes, we use information about the structure of the underlying concrete topologies encoded in abstraction constraints.
+The possibility of network failures only exacerbates the difficulty of constructing correct configurations. 
+Link failures in networks occur frequently; it is not uncommon for a large network to experience dozens of such failures in any given day~\cite{dc-failure-study}.
+However, existing tools~\cite{condor,propane} can only reason about about fault-tolerance for concrete topologies.
+The problem for \sysname is significantly harder because it must verify that all possible concrete instantiations of an abstract topology satisfy the desired fault-tolerance requirements, which requires a fundamentally different approach.
+
+%
+We frame satisfying the fault-tolerance policy provided by the user as an analysis problem over the structure of the PG.
+In particular, in this section we develop an analysis that uses information about the structure of  concrete instantiations of the abstract topology to infer bounds on the number of edge-disjoint paths between pairs of concrete nodes.
+
 %

### 2016-11-14 paper/abstraction/paper.tex
edits to 9.1

--- 2016-11-14 paper/abstraction/paper.tex
@@
   \includegraphics[width=\columnwidth]{figures/templates}
-  \caption{Idealized small configuration component for the datacenter spine role based on router templates from a large cloud provider (\IE, macros over gobbledygook).}
+  \caption{Example of a small configuration component of a router template for the datacenter spine role.}
   \label{fig:templates}
-  \vspace{-.8em}
+  \vspace{-1em}
 \end{figure}
@@
 As described earlier (\S\ref{sec:introduction}), templates are hard to author and hard to validate.
-Worse, templates that work for one topology may not work for seemingly-inconsequential variations (which may arise after the network evolves).
+At the same time, templates that work for one topology may not work for seemingly-inconsequential variations (which may arise after the network evolves).
 Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}: it has the same five roles, connected in a similar hierarchy.
@@
 \sysname takes as input the network's abstract topology and its policy.
-The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous failures the network can withstand without losing connectivity.
+The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous failures the network can withstand without loosing connectivity.
 
@@
 It says that traffic for each global prefix associated with the variable should follow a path that ends at its corresponding destination router in the $\CD{TG}$ role.
-As we will see in \S\ref{sec:language}, constraints like $\CD{\End(TG)}$ are just syntactic sugar for regular expressions describing network paths.
-The second line has a similar policy for local prefixes.
+The second line does the same for all local prefixes.
 %
@@
 %
-The constraint to prevent ``valleys" (5) is written as:
+The constraint to prevent "valleys" (5) is written as:
 %
@@
 Regular paths are defined over network locations, where each location is either a router inside the operator's network, or an external neighbor connected to that network.
-Values \In\ and \Out\ will match any internal and external location respectively.
+Values \In~ and \Out, will match any internal and external location respectively.
 There are two types of predicates, as shown.
@@
 %
-The PG is a tuple ($G'$, $start$, $P$) where $G' = (V',E')$ has
+The PG is a tuple ($G'$, $start$, $P$) where $G' = (V',E')$ is has
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
@@
     \inferencetwo{0}
-    \node[anchor=west] at (1,2.2) {where $g \geq n-\dfrac{(m-j)*e_1}{e_2}$};
+    \node[anchor=west] at (1,2.2) {where $g=n-\dfrac{(m-j)*e_1}{e_2}$};
     \inferencelocal{6.5}{.4}
@@
 Furthermore, the total number of disjoint paths to the $j$ nodes at the bottom is equal to $j*k$.
-Since extending the existing disjoint paths with disjoint edges keeps the paths disjoint, and since we cannot exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the role $n$ on the top will be $min(j*k,e_1)$.
-%
-We conservatively use $1$ for the number of disjoint paths to each node in role $n$, since when $n$ is very large, all reachable nodes in role $m$ might only have a single edge to completely different nodes in $n$.
-%However, because we do not know for certain that all $j$ nodes in role $m$ have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
-%For example, if $n$ is very large, then each node in role $m$ may have only a single edge to each reachable node in role $n$.
-
-Consider rule \infrule{I-out2}, and consider any node in the role $n$.
-There are $e_2$ incoming edges to that node.
-Due to the fact that $A_m(j,k)$, we know that at least j of those $e_2$ edges are connected to nodes with disjoint paths from the origin.
-Hence we infer $A_n(1,min(j,e_2))$.
-
-%The rule \infrule{I-out2} follows a similar line of reasoning.
+Since adding disjoint edges between the nodes keeps the existing paths disjoint, and since we can not exceed the current number of disjoint paths to the concrete nodes in role $m$ on the bottom, the largest reachable group for the role $n$ on the top will be $min(j*k,e_1)$.
+However, because we do not know for certain that all $j$ nodes in role $m$ have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
+
+The rule \infrule{I-out2} follows a similar line of reasoning.
 It says that if any group of size $j$ with $k$ disjoint paths to each is reachable in the bottom role, and there is at least one incoming edge for each concrete node in the top role, then there are $min(j,e_2)$ disjoint paths to any single concrete node in the top role.
@@
 The two rules \infrule{I-mesh1} and \infrule{I-mesh2} handle the case where there is a full mesh between the two roles.
-This happens when the number of outgoing edges ($e_1$) from nodes in role $m$ equals the number of nodes on top ($n$).
-\infrule{I-mesh1} says that we can find disjoint paths to each node in the top role restricted to the number of disjoint paths we started with.
-\infrule{I-mesh2} uses the fact that each node in the top role is connected to each node in the bottom role to infer that there can be $j$ disjoint paths to any single node in the top role.
-
-The annotation $mincut(X)$ appearing on an edge is an assertion about the fault tolerance between nodes in two different roles.
-The rule \infrule{I-mincut} uses such assertions.
-To each node in role $n$, from a node in role $m$, we can construct at least the minimum of $X$ and $k$ disjoint paths.
-
-%The rule \infrule{I-mincut} can be thought of as an assertion about the fault tolerance between nodes in two roles.
-The rule applies to an edge that has been annotated with a $mincut(X)$ statement, which means that there are at least $X$ disjoint paths between any node in role $m$ and any node in role $n$.
+This happens when the number of outgoing edges from the bottom $e_1$ is equal to the number of nodes on the top $n$.
+The first case for \infrule{I-mesh1} says that we can find disjoint paths to each node in the top role restricted to the number of disjoint paths we started with.
+The second case for \infrule{I-mesh2} uses the fact that each node in the top role is connected to each node in the bottom role to infer that there can be $j$ disjoint paths to any single node in the top role.
 
 The rule \infrule{I-striping} is the most complicated case.
-It starts with the invariant $L_m(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid given the constraints.
+It starts with the invariant L$_m(j,k)$ at role $m$ and can be applied if each edge multiplicity $e_i > 0$ is valid given the constraints.
 The first inference for role $n$ tries to find the largest reachable group with disjoint paths to each.
@@
 %
-The remaining nodes ($m-j$) that are not part of the reachable group in the bottom role, each have $e_1$ outgoing edges and must be able to at least ``fill" the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$), which each have $e_2$ incoming edges.
+The remaining nodes ($m-j$) that are not part of the reachable group in the bottom role, each have $e_1$ outgoing edges and must be able to at least "fill" the incoming edges for the remaining nodes not in the reachable group at the top ($n-g$) with $e_2$ incoming edges each.
 Solving the inequality gives the lower bound for $g$ used in Figure~\ref{fig:inference-rules}.
 
-The second part of the rule uses a similar idea to reason about the overlap between roles $m$ and $o$ with respect to role $n$.
+The second part of the rule allows uses a similar idea to reason about the overlap between roles $m$ and $o$ with respect to role $n$.
 This rule is useful particularly useful for datacenter topologies where routers in one tier of the datacenter often have a particular striping pattern with another tier.
 
-Finally, rules \infrule{I-local} and \infrule{I-global} allow us to reason across pod hierarchies.
-The first rule, \infrule{I-local}, says that if there is an inference from $L_m(j,k)$ to $L_n(j',k')$ on the left, then if both nodes are in the same local pod P, we can leave all labels up to P unchanged.
+The rule \infrule{I-mincut} can be thought of as an assertion about the fault tolerance between nodes in two roles.
+The rule applies to an edge that has been annotated with a $mincut(X)$ statement, which means that there are at least $X$ disjoint paths between any node in role $m$ and any node in role $n$.
+
+Finally, the \infrule{I-local} and \infrule{I-global} rules allow us to lift each of the other rules to reason across pod hierarchies.
+The first rule, \infrule{I-local}, says that if there is an inference from L$_m(j,k)$ to L$_n(j',k')$ on the left, then if both nodes are in the same local pod P, we can leave all labels up to P unchanged.
 The global rule \infrule{I-global} says that when the edge goes between pods, we can infer the fact for all pods Q since the multiplicities apply uniformly for each pod.
@@
 
-%The algorithm associates with each inference, the set of abstract locations used to derive the inference, \IE, an overapproximation of set of concrete locations used for the edge-disjoint paths.
+The algorithm associates with each inference, the set of abstract locations used to derive the inference, \IE, an overapproximation of set of concrete locations used for the edge-disjoint paths.
 When applying an inference rule between an invariant at role $m$, with a set of abstract locations $C$, to learn an invariant at role $n$, we associate the new invariant with the set $C \cup \{ n \}$.
 %
-%When, at a single PG node there is an inference $L_{X_1} \dots L_{X_{n-1}}$ A$_m(j,k)$ with location set $C$ and inference $L_{X_1} \dots L_{X_{n-1}}$ L$_m(j',k')$ with location set $D$, where $C \cap D = \emptyset$, we add a new inference with location set $C \cup D$:
-%
-%$$L_{X_1} \dots L_{X_{n-1}} L_m(\min(j, j'), k + k')$$ 
-%
-%\noindent
-%The idea is that, because non-overlapping abstract paths can never contain overlapping concrete paths, due to the graph homomorphism property, we can merge inferences about these disjoint paths in the abstraction.
+When, at a single PG node there is an inference $L_{X_1} \dots L_{X_{n-1}}$ A$_m(j,k)$ with location set $C$ and inference $L_{X_1} \dots L_{X_{n-1}}$ L$_m(j',k')$ with location set $D$, where $C \cap D = \emptyset$, we add a new inference with location set $C \cup D$:
+%
+$$L_{X_1} \dots L_{X_{n-1}} L_m(\min(j, j'), k + k')$$
+%
+\noindent
+The idea is that, because non-overlapping abstract paths can never contain overlapping concrete paths, due to the graph homomorphism property, we can merge inferences about these disjoint paths in the abstraction.
 
@@
 
-Note that, because each inference rule only applies to directed edges in the PG, the algorithm cannot make any inferences about connectivity from the AL role to the S role since there is no directed edge from AL to S.
+Note that, because each inference rule only applies to directed edges in the PG, the algorithm can not make any inferences about connectivity from the AL role to the S role since there is no directed edge between them.
 This restriction ensures that the analysis is policy-sensitive.
@@
 Note that, in this case, the analysis is precise.
-There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global ToR from a spine router due to the valley-free constraint.
-In this case in particular, the bound on the fault tolerance between a ToR and spine router can be used to determine that an aggregation-induced black hole may arise at the border of the datacenter after a single failure in some topologies.
+There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global tor from a spine router due to the valleyfree constraint.
+In this case in particular, the bound on the fault tolerance between a tor and spine router can be used to determine that an aggregation-induced black hole may arise at the border of the datacenter after a single failures in some topologies.
 
@@
 
-To evaluate \sysname, we apply it on policies for backbone and datacenter networks.
-We aim to evaluate the expressiveness of our abstracttions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.
+We evaluate \sysname by applying it on policies for backbone and datacenter networks.
+We aim to evaluate the expressiveness of our abstractions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.
 
@@
 
-\subsection{Analysis precision}
+\subsection{Expressiveness and precision}
 
@@
   \begin{center}
-      \begin{tabular}{| l | c | c | c | c | c | }
+      \begin{tabular}{| l | c| c | c | c | c | }
       \hline
-      \textbf{Topology} & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
+       & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
       & & Some & All & Some & All \\
       & & Pairs & Pairs & Pairs & Pairs \\ \hline
+
+      \multicolumn{6}{l}{\textbf{Tree-based topologies, valley-free routing}} \\ \hline
+
+      Fattree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \cmark  \\ \hline
+      Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
+      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
+      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
+%      \end{tabular}
+%  \end{center}
+%  \vspace{-.6em}
+%  \caption{Expressiveness and analysis precision for fat tree topologies with valley-free routing policy.}
+%  \label{fig:analysis-precision2}
+%\end{figure}
+%
+%\begin{figure}[t!]
+%  \begin{center}
+%      \begin{tabular}{| l | c | c | c | c | c | }
+%      \hline
+%      \textbf{Topology} & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
+%      & & Some & All & Some & All \\
+%      & & Pairs & Pairs & Pairs & Pairs \\ \hline
+
+      \multicolumn{6}{l}{\textbf{All topologies, shortest-path routing}} \\ \hline
 
@@
   \vspace{-.6em}
-  \caption{Fault-tolerance analysis precision for all topologies with shortest path routing.}
+  \caption{Expressiveness and precision of \sysname.}
   \label{fig:analysis-precision}
@@
 
-\begin{figure}[t!]
-  \begin{center}
-      \begin{tabular}{| l | c | c | c | c | }
-      \hline
-      \textbf{Clos Variant} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
-      & Some & All & Some & All \\
-      & Pairs & Pairs & Pairs & Pairs \\ \hline
-
-      Fattree & \cmark & \cmark & \cmark & \cmark  \\ \hline
-      Facebook & \cmark & \cmark & \cmark & \cmark \\ \hline
-      F10 & \cmark & \cmark & \cmark & \cmark \\ \hline
-      VL2 & \cmark & \cmark & \cmark & \cmark \\ \hline
-      \end{tabular}
-  \end{center}
-  \vspace{-.6em}
-  \caption{Fault-tolerance analysis precision for fat tree topologies with valley-free routing.}
-  \label{fig:analysis-precision2}
-\end{figure}
-
-We evaluate the expressiveness of \sysname's abstractions and the precision of the fault-tolerance analysis on a range of different network topologies found both in the network literature and in production networks.
-The analysis is precise if it finds a tight lower-bound on the fault-tolerance (\IE, there is actually a concrete network with that fault tolerance).
-For each topology in Figure~\ref{fig:analysis-precision} we define a suitable abstraction.
+We evaluate the expressiveness of \sysname's topology abstractions and the precision of its fault-tolerance analysis on a range of network topologies found in production networks and in the networking literature.
+We characterize expressiveness by checking if our abstractions allow the topologies to evolve arbitrarily or certain aspects must be fixed (i.e., cannot be symbolic).
+We measure precision by checking if we find a tight lower-bound on fault-tolerance (\IE, there exists a concrete network with that fault-tolerance level).
+
+The top part of Figure~\ref{fig:analysis-precision} shows the results for common real-world settings: tree-based topologies coupled with valley-free routing.
+We consider four variants of tree topologies: a standard fat tree~\cite{fattree}, the Facebook fat tree~\cite{facebook-fattree}, the F10 fault-tolerant fat tree~\cite{f10-fattree}, and VL2~\cite{vl2-fattree}.
+These variants differ in the number of tiers and the connectivity pattern between roles.
+For each, we use a tiered abstraction similar to that in our example (\S\ref{sec:overview}) and parameterize over the number of pods, which can be scaled to allow expansion.
+We report precision of both analyzing reachability and computing the number of disjoint paths, and we report if \sysname is precise for all pairs of abstract nodes or only some of them.
+%"All pairs" precision implies "some pairs" precision, but not the other way around.
+
+Our results are encouraging for these realistic settings.
+Our abstractions are perfectly expressive for all tree-based topologies---we did not have to fix any aspect of their structure---and the analysis is precise in all cases.
+
+%For each topology in Figure~\ref{fig:analysis-precision} we define a suitable abstraction.
 Since many topologies have tunable parameters (\EG, the recursion depth $k$ for the DCell topology), we list all such parameters that are fixed for the abstraction.
@@
 
-\para{Fat Tree Topologies}
-
-The fat tree topology is a widely used datacenter topology.
+%\para{Fat Tree Topologies}
+%
+%The fat tree topology is a widely used datacenter topology.
 We look at the precision of our analysis on four fat tree variants used in practice: a standard fat tree~\cite{fattree}, the Facebook fat tree~\cite{facebook-fattree}, the F10 fault tolerant fat tree~\cite{f10-fattree}, and the VL2 topology~\cite{vl2-fattree}.
@@
 Each fat tree topology is parameterized over the number of pods $k$, which can be scaled up in the abstraction to allow for expansion.
-For all fat tree variants, the analysis correctly computes the number of ToR to ToR disjoint paths, but can lose precision between ToR to spine routers due to valley paths.
-For a valley-free routing policy, the analysis is precise for ToR to spine connectivity.
+
+To stress our abstractions and analysis, we consider additional topologies from the literature.
 
 \para{Recursive Topologies}
-
-We also model several recursive topologies.
-These include the BCube~\cite{bcube} and DCell~\cite{dcell} topologies.
-Each topology includes a recursion depth parameter ($k$), which we fix.
+These topologies include BCube~\cite{bcube} and DCell~\cite{dcell}.
+Each topology includes a recursion depth parameter ($k$), which we fixed while abstracting them.
 For a recursive topology with depth $k$, we model it as an abstract topology consisting of a pod to represent all depth $k-1$ subcomponents.
-This allows for safe expansion within a subcomponent, but not from increasing the recursion depth.
+This allows for safe expansion within a subcomponent, but does not allow changing the recursion depth dynamically.
 For BCube, we model each tier of the datacenter as a separate role. Figure~\ref{fig:example-abstractions} shows an example of a BCube abstraction for $k=1$.
-The analysis is able to accurately determine reachability (i.e., at least 1 disjoint path) for each recursive topology, but is overly conservative in determining k-disjoint paths.
-For the BCube topology, it is able to to determine the correct number of disjoint paths between some pairs of nodes, but not all.
 
 \para{Hypercube Topologies}
-
 Hypercube variants can be used as an alternative to Clos-style topologies for networks with port density routers.
@@
 Figure~\ref{fig:example-abstractions} shows an example for $L=2$.
-For all hypercube variants, the fault-tolerance analysis is precise.
+%For all hypercube variants, the fault-tolerance analysis is precise.
+
+The bottom part of Figure~\ref{fig:analysis-precision} shows the results for all types of topologies coupled with shortest-path routing.
+(Valley-free routing is not meaningful for non-tree-based topologies.) For all tree-based topologies, analysis is precise for determining reachability, but for three of them, it does not compute a tight bound for edge-disjoint paths for all router pairs.
+Specifically, it underestimates ToR-to-spine paths; it fails to account for circuitous paths that traverse another spine because it could not disambiguate two concrete spines that map to the same abstract role.
+%For all fat tree variants, the analysis correctly computes the number of ToR to ToR disjoint paths, but can lose precision between ToR to spine routers due to valley paths.
+For a valley-free routing policy, the analysis is precise for ToR to spine connectivity.
+For both recursive topologies, the analysis can accurately determine reachability (i.e., at least 1 disjoint path) but is conservative in determining k-disjoint paths.
+For the BCube topology, it is able to to determine the correct number of disjoint paths between some pairs of nodes, but not all.
+For all hypercube topologies, \sysname's fault-tolerance analysis is precise.
 

### 2016-11-14 paper/abstraction/paper.tex
remove git message

--- 2016-11-14 paper/abstraction/paper.tex
@@
 It says that any spine router has at least one path to any node in the neighbor N1 (and N2) role.
-Such annotations are useful for a "one big switch" abstraction \cite{Casado:2010} in which a complex, unstructured network is represented as a single node.
+Such annotations are useful for a ``one big switch" abstraction \cite{Casado:2010} in which a complex, unstructured network is represented as a single node.
 As another use case, an ISP backbone can be modeled by dividing the network into separate geographic regions with two roles per region---one for the border routers and another for the network core.
@@
 
-%Configuration synthesis for network configurations is challenging for a number of reasons.
-First, although \sysname polices specify network-wide routing behavior, actual configurations are per-device and run distributed algorithms to compute routes.
-Thus the compiler must ensure that the result of the distributed interaction of devices correctly implements the policy including when failures occur.
-Second, \sysname must find configurations that work for any valid concrete network topology matching the user-specified abstraction.
-Finally, \sysname must ensure that the resulting configurations can be evolved incrementally so that local changes to the topology ensure that only local changes to configurations are required to ensure global routing correctness.
-
-%In this section, we formalize the \sysname language and describe how \sysname translates policies to a graph-based intermediate representation.
-
-%\subsection{Methane Language}
-
 \begin{figure}[t]\small
@@
              &   & r_1 \cap r_2 \BNFALT r_1 \cdot r_2 \BNFALT \NOT r \BNFALT r^* \\
-%         &\BNFALT& \emptyset & \textit{empty set} \\
-%         &\BNFALT& \In & \textit{internal loc} \\
-%         &\BNFALT& \Out & \textit{external loc} \\
-%         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
-%         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
-%         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
-%         &\BNFALT& \NOT r & \textit{path negation} \\
-%         &\BNFALT& r^* & \textit{iteration} \\
   \end{array} \]%
@@
 A test for a concrete prefix $d.d.d.d/[d..d]$ matches a range of IP prefixes (\EG, 10.0.1.0/[24..32]) where metavariable $d$ represents an integer.
+A prefix template test {\small\$x}, for variable $x$, represents a collection of many tests, one for each prefix represented by the template.
 

### 2016-11-14 paper/abstraction/paper.tex
adding edits for section 6

@@
 
-The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies the inference rules from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
+The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies every inference rule from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
 Inference rule conditions are checked for validity over all concrete topologies using an SMT solver.
-In order to ensure termination, we make the observation that, for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
+Because the inference rules may continue to yield larger and larger symbolic expressions, we make the following observation to ensure termination: for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
 Therefore, for each inference $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing SMT solver $\nu$Z~\cite{z3opt}.
+Invariants learned with $j=0$ or $k=0$ provide no useful information and are discarded.
 
@@
 %
-The first step applies the rule \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles.
-This invokes a call to $\nu$Z to minimize the expression $min(\infty, AG)$, which results in 2.
+The first step applies each inference rule to this initial fact.
+Rules \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles results in a call to $\nu$Z to minimize the expression $min(\infty, AG)$, which results in 2.
 Therefore, the algorithm learns a new invariant of the form $S_P A_{AG} (2,1)$ for node $(AG, 0)$ to indicate that in some pod P, any group of 2 nodes is reachable.
 %
-The next step uses the inference rule \infrule{I-out2} to learn that any single spine node is reachable.
-It also can apply rule \infrule{I-striping} to determine that there is some group of at least 2 spine routers reachable at node $(S,0)$ and also that there is some group of at least 2 nodes reachable in the AL role in state $(AL,0)$.
+The algorithm will then eventually apply \infrule{I-out2} to learn that any single spine node is reachable at $(S,0)$.
+It will also apply \infrule{I-striping} to determine that there is some group of at least 2 spine routers reachable at $(S,0)$ and that there is some group of at least 2 nodes reachable in the AL role in state $(AL,0)$.
 
 Note that, because each inference rule only applies to directed edges in the PG, the algorithm cannot make any inferences about connectivity from the AL role to the S role since there is no directed edge from AL to S.
-This restriction ensures that the analysis is policy-sensitive.
+This restriction ensures that the analysis remains policy-sensitive.
 
@@
 
-In this case, the algorithm was able to infer that any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a router in role TG.
+The algorithm was able to infer that any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a router in role TG.
 Note that, in this case, the analysis is precise.
 There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global ToR from a spine router due to the valley-free constraint.
-In this case in particular, the bound on the fault tolerance between a ToR and spine router can be used to determine that an aggregation-induced black hole may arise at the border of the datacenter after a single failure in some topologies.
+The bound on the fault tolerance between ToR and spine routers can also be used to determine that an aggregation-induced black hole may arise at the border of the datacenter after a single failure in some concrete instantiation.
 
@@
 
+\para{Results}
 The bottom part of Figure~\ref{fig:analysis-precision} shows the results for all types of topologies coupled with shortest-path routing.

### 2016-11-14 paper/abstraction/paper.tex
clarify metavariables

@@
   \[ \begin{array}{rclr}
-     pol     &::=& p_1, \dots, p_n & \textit{policy} \\
-     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT a & \textit{path preferences}  \\
-     t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \textit{predicate} \\
-     a      &::=& agg(t, r_1 \rightarrow r_2) & \textit{aggregation} \\
-     r       &::=& l \BNFALT \emptyset \BNFALT \In \BNFALT \Out \BNFALT r_1 \cup r_2 \BNFALT & \textit{regular path} \\
+     d       &\in& \textit{Integers} \\
+     x       &\in& \textit{Variables} \\
+     pol     &::=& p_1, \dots, p_n & \text{Policy} \\
+     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT a & \text{Path Preferences}  \\
+     t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \text{Predicate} \\
+     a      &::=& \mathit{agg}(t, r_1 \rightarrow r_2) & \text{Aggregation} \\
+     r       &::=& l \BNFALT \emptyset \BNFALT \CD{in} \BNFALT \CD{out} \BNFALT r_1 \cup r_2 \BNFALT & \text{Regular Path} \\
              &   & r_1 \cap r_2 \BNFALT r_1 \cdot r_2 \BNFALT \NOT r \BNFALT r^* \\

### 2016-11-14 paper/abstraction/paper.tex
change expansion to template instantiation

@@
 %
-As we will see in \S\ref{sec:generation}, we have proven that our generation strategy commutes with concrete expansion, meaning that we obtain the same results if we expand the abstraction early, or if we defer the expansion until after template generation.
+As we will see in \S\ref{sec:generation}, we have proven that our generation strategy commutes with template instantiation, meaning that we obtain the same results if we instantiate the abstraction early, or if we defer the instantiation until after template generation.
 %
@@
 
-Lemma~\ref{lem:preference} tells us that inferring preferences over the abstract PG before concrete expansion is equivalent to inferring preferences over an already-expanded concrete PG.
+Lemma~\ref{lem:preference} tells us that inferring preferences for the abstract PG before template instantiation is equivalent to inferring preferences for an already-instantiated concrete PG.
 
@@
 For both recursive topologies, the analysis can accurately determine reachability (i.e., at least 1 disjoint path) but is conservative in determining k-disjoint paths. 
-For the BCube topology, it is able to to determine the correct number of disjoint paths between some pairs of nodes, but not all.
+%For the BCube topology, it is able to to determine the correct number of disjoint paths between some pairs of nodes, but not all.
 For all hypercube topologies, \sysname's fault-tolerance analysis is precise.

### 2016-11-15 paper/abstraction/paper.tex
adding a section on incrementality

@@
 
+\subsection{Incrementality}
+\label{sec:incrementality}
+
+The design of \sysname guarantees that network evolution requires configuration changes only for nodes that acquire or lose a neighbor.
+We experimentally confirmed that our implementation provides this guarantee.
+To the networks we studied above, we made a range of changes, including adding and removing routers and pods and changing the prefix that a router originates.
+In each case, we found the guarantee to hold; for prefix changes, only the originator's configuration changed.
+In contrast, all router configurations were modified with Propane because it heavily uses prefix lists which are sensitive to such changes.
+While Propane may be made friendlier to network evolution (e.g., prefix lists are unnecessary at aggregation routers), its fundamental limitation will remain because it does not understand roles and the network's underlying structure that \sysname leverages.
+
 %=====================================================

### 2016-11-15 paper/abstraction/paper.tex
minor edits

@@
     \node[] at (#1 + 1.2, 2.5 / 2 + 2.5) {\textbf{I-local}};
-    \inferencenobox{#1}{L$_m(j,k)$}{}{L$_n(j',k')$}{}{}{}
-    \inferencenobox{#1+2 + #2}{$\ldots$ L$_P$ L$_m(j,k)$}{}{$\ldots$ L$_P$ L$_n(j',k')$}{}{}{}
+    \inferencenobox{#1}{X}{}{Y}{}{}{}
+    \inferencenobox{#1+2 + #2}{$\ldots$ L$_P$ X}{}{$\ldots$ L$_P$ Y}{}{}{}
     \node[anchor=east] at (#1 + 2 + #2 - .6, 2.5) {P};
@@
     \node[] at (#1 + 1.2, 2.5 / 2 + 2.5) {\textbf{I-global}};
-    \inferencenobox{#1}{L$_1(j,k)$}{}{L$_2(j',k')$}{}{}{}
-    \inferencenobox{#1+2+#2}{$\ldots$ L$_P$ L$_m(j,k)$}{}{$\ldots$ A$_Q$ L$_n(j',k')$}{}{}{}
+    \inferencenobox{#1}{X}{}{Y}{}{}{}
+    \inferencenobox{#1+2+#2}{L$_P$ X}{}{A$_Q$ Y}{}{}{}
     \node[anchor=east] at (#1 + 2 + #2 - .6, .4) {P};
@@
 
-The possibility of network failures only exacerbates the difficulty of constructing correct configurations.
+The possibility of network failures exacerbates the difficulty of constructing correct configurations.
 Link failures in networks occur frequently; it is not uncommon for a large network to experience dozens of such failures in any given day~\cite{dc-failure-study}.
-However, existing tools~\cite{condor,propane} can only reason about about fault-tolerance for concrete topologies.
-The problem for \sysname is significantly harder because it must verify that all possible concrete instantiations of an abstract topology satisfy the desired fault-tolerance requirements, which requires a fundamentally different approach.
+However, existing tools~\cite{condor,propane} can reason about fault-tolerance only for concrete topologies.
+The problem for \sysname is harder because it must verify that all possible concrete instantiations of an abstract topology satisfy the fault-tolerance requirements, which requires a fundamentally different approach.
 
@@
 We frame satisfying the fault-tolerance policy provided by the user as an analysis problem over the structure of the PG.
-In particular, in this section we develop an analysis that uses information about the structure of  concrete instantiations of the abstract topology to infer bounds on the number of edge-disjoint paths between pairs of concrete nodes.
+In particular, we develop an analysis that uses information about the structure of  concrete instantiations of the abstract topology to infer bounds on the number of edge-disjoint paths between pairs of concrete nodes.
 
@@
 
-To learn information about disjoint paths, we develop a collection of sound inference rules for invariants of the above form.
-Figure~\ref{fig:inference-rules} shows each of the inference rules.
-The rules are read from bottom to top.
-The label on the bottom left represents a known invariant.
+To learn about disjoint paths, we develop a collection of sound inference rules for invariants of the form above.
+Figure~\ref{fig:inference-rules} shows each rule.
+They are read from bottom to top.
+The label on the bottom left is a known invariant.
 We use $L$ to represent a rule that is parametric over the label ($S$ or $A$).
-The labels on other nodes correspond to new invariants learned after applying the inference rule.
-Conditions that must be \emph{valid} for the rule to apply are shown in a box next to the rule.
-
-In general, the inference rules try to learn information about both the largest number of disjoint paths to any single node in an abstract role as well as the largest reachable group in a particular role with at least one disjoint path to each.
+The labels on other nodes correspond to invariants learned after applying the inference rule.
+The adjacent box shows the conditions that must be \emph{valid} for the rule to apply.
+
+In general, the inference rules try to learn about both the largest number of disjoint paths to any single node in an abstract role as well as the largest reachable group in a particular role with at least one disjoint path to each.
 
@@
 
-Finally, rules \infrule{I-local} and \infrule{I-global} allow us to reason across pod hierarchies.
-The first rule, \infrule{I-local}, says that if there is an inference from $L_m(j,k)$ to $L_n(j',k')$ on the left, then if both nodes are in the same local pod P, we can leave all labels up to P unchanged.
-The global rule \infrule{I-global} says that when the edge goes between pods, we can infer the fact for all pods Q since the multiplicities apply uniformly for each pod.
+Finally, rules \infrule{I-local} and \infrule{I-global} reason across pod hierarchies.
+\infrule{I-local} says that if there is an inference from $L_m(j,k)$ to $L_n(j',k')$ on the left, then if both nodes are in the same pod P, we can leave all labels up to P unchanged.
+\infrule{I-global} says that when the edge goes across pods, we can infer the fact for all pods Q since the multiplicities apply uniformly for each pod.
 
@@
 
-The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies every inference rule from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
+Our analysis starts from a fixed source location $src$ and repeatedly applies every inference rule from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
 Inference rule conditions are checked for validity over all concrete topologies using an SMT solver.
-Because the inference rules may continue to yield larger and larger symbolic expressions, we make the following observation to ensure termination: for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
+Because the inference rules may continue to yield increasingly larger symbolic expressions, we make the following observation to ensure termination: for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
 Therefore, for each inference $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing SMT solver $\nu$Z~\cite{z3opt}.
@@
 
-The algorithm was able to infer that any node in the spine role has at least 1 disjoint path and any node in the TL node has at least 2 disjoint paths to a router in role TG.
-Note that, in this case, the analysis is precise.
+The algorithm was able to infer that any spine router has at least 1 disjoint path and any TL router has at least 2 disjoint paths to a TG router.
+In this case, the analysis is precise.
 There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global ToR from a spine router due to the valley-free constraint.
-The bound on the fault tolerance between ToR and spine routers can also be used to determine that an aggregation-induced black hole may arise at the border of the datacenter after a single failure in some concrete instantiation.
+The bound on the fault tolerance between ToR and spine routers can also be used to determine that an aggregation-induced black hole may arise at the datacenter boundary after a single failure in some concrete instantiation.
 
@@
 
-The first idea is to tag every protocol message with a BGP community that encodes the state of each DFA when advertising a route to a neighbor.
-Routers then allow route advertisements that correspond to an edge in the PG and block those that do not.
+The first idea is to tag every BGP announcement with a community that encodes the state of each DFA when advertising a route to a neighbor.
+Routers then allow announcements that correspond to an edge in the PG and block others.
 For example, in the concrete PG in figure~\ref{fig:example-compilation}, router S1 will allow an advertisement from its neighbors N1 and N2.
@@
 The second idea is to have each router totally order advertisements from neighbors.
-For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, router S1 should prefer a message it hears from N1 over N2.
-Similarly, router A1 should prefer routes tagged with $(1,0)$ over those tagged with $(0,1)$.
+For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, S1 should prefer a message it hears from N1 over N2.
+Similarly, A1 should prefer routes tagged with $(1,0)$ over those with $(0,1)$.
 %In general, because BGP is distributed, each router does not have a full view of the entire network when choosing which path to use.
@@
 Propane introduced a conservative search strategy for determining route preferences.
-To make this work for abstract topologies, we modify the search based on the following observation about the structure of the PG:
+To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:
 
@@
 
-If we determine that each router has a total order with respect to the simulation relation ($\leq$) for its corresponding PG nodes, then we can simply sort the nodes and prefer advertisements from peers of node $m$ over those of node $m'$ whenever $m' \leq m$.
+If we determine that each router has a total order with respect to the simulation relation ($\leq$) for its corresponding PG nodes, then we can simply sort the nodes and prefer advertisements from peers of node $m$ over those of $m'$ whenever $m' \leq m$.
 This condition ensures that BGP devices will converge to the most preferred paths in the network even when failures occur.
@@
 \para{Concretization}
-
-One observation is that the spine template configuration and concrete spine configurations are structured similarly.
-We formalize this idea by defining a simple, vendor-neutral language for BGP configurations called \mbgp and formally define compilation for policies over both concrete and abstract topologies to \mbgp.
+Observe that the spine template and concrete configurations are structured similarly.
+We formalize this observation by defining a simple, vendor-neutral language for BGP configurations called \mbgp and formally define compilation for policies over both concrete and abstract topologies to \mbgp.
 In addition we define two concretization ($con$) functions that translate an abstract \sysname policy and \mbgp configuration to a concrete \sysname policy and concrete \mbgp configuration respectively.
@@
 Intuitively, the spine template is concretized by replacing each abstract role with the set of all concrete routers that map to that role and each prefix template variable with a new entry in the configuration for each individual prefix provided by the context $\Gamma$.
-The main theoretical result is that the compilation and concretization functions commute:
+Our main theoretical result is that the compilation and concretization functions commute:
 
@@
 \vspace{-.8em}
-Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix.
+Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix. These results also help assign semantics to templates.
 
@@
 
-Suppose that an operator want to expand the concrete datacenter by adding an additional ToR router to the TG role.
+Suppose an operator wants to expand the concrete datacenter by adding an additional ToR router to the TG role.
 Per the network routing policy, the new ToR router will advertise any owned prefixes provided by looking up {\small \$GP} in $\Gamma$.
@@
 The only way in which the spine routers depend on anything non-local is in the match on prefix template variables.
-Therefore, we can avoid having to modify the configurations for the spine routers by associating a new unique community tag for template variable {\small \$GP} and then replacing each match on {\small \$GP} with a test on the new community tag.
+Therefore, we can prevent modifications to the spine routers' configurations by associating a new unique community tag for template variable {\small \$GP} and then replacing each match on {\small \$GP} with a test on the new community tag.
 The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can match against it.

### 2016-11-15 paper/abstraction/paper.tex
small edits to 7
derivations

--- 2016-11-15 paper/abstraction/paper.tex
@@
 
+\newcommand{\derivation}[3]{
+    \node at (#1, -.6) {#2};
+    \node at (#1, 3.1) {#3};
+    \node at (#1, -.6 + .9) {$\mathcal{E}$};
+    \node at (#1, 3.1 - .9) {$\mathcal{D}$};
+    \node at (#1, 2.5/2) {.};
+    \node at (#1, 2.5/2 - .26) {.};
+    \node at (#1, 2.5/2 + .26) {.};
+}
+
 \newcommand{\inferencetwo}[1]{
@@
 \newcommand{\inferencelocal}[2]{
-    \node[] at (#1 + 1.2, 2.5 / 2 + 2.5) {\textbf{I-local}};
-    \inferencenobox{#1}{X}{}{Y}{}{}{}
-    \inferencenobox{#1+2 + #2}{$\ldots$ L$_P$ X}{}{$\ldots$ L$_P$ Y}{}{}{}
+
+    \node[] at (#1 + 1.2, 1.25 + 2.5) {\textbf{I-local}};
+
+    \derivation{#1}{X}{Y}
+    \derivation{#1+2+#2}{L$_P$ X}{L$_P$ Y}
+    %\inferencenobox{#1}{X}{}{Y}{}{}{}
+    %\inferencenobox{#1+2 + #2}{$\ldots$ L$_P$ X}{}{$\ldots$ L$_P$ Y}{}{}{}
     \node[anchor=east] at (#1 + 2 + #2 - .6, 2.5) {P};
@@
     \node[] at (#1 + 1.2, 2.5 / 2 + 2.5) {\textbf{I-global}};
-    \inferencenobox{#1}{X}{}{Y}{}{}{}
-    \inferencenobox{#1+2+#2}{L$_P$ X}{}{A$_Q$ Y}{}{}{}
+    %\inferencenobox{#1}{X}{}{Y}{}{}{}
+    %\inferencenobox{#1+2+#2}{L$_P$ X}{}{A$_Q$ Y}{}{}{}
+    \derivation{#1}{X}{Y}
+    \derivation{#1+2+#2}{L$_P$ X}{A$_Q$ Y}
+
     \node[anchor=east] at (#1 + 2 + #2 - .6, .4) {P};
@@
 
-Our analysis starts from a fixed source location $src$ and repeatedly applies every inference rule from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
-Inference rule conditions are checked for validity over all concrete topologies using an SMT solver.
-Because the inference rules may continue to yield increasingly larger symbolic expressions, we make the following observation to ensure termination: for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
+The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly tries to apply every inference rule from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
+The algorithm applies an inference rule when the rule condition is valid given the abstract topology constraints.
+This ensures that the condition holds for all concrete instantiations of the topology.
+Because the inference rules may continue to yield larger and larger symbolic expressions, we make the following observation to ensure termination: for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
 Therefore, for each inference $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing SMT solver $\nu$Z~\cite{z3opt}.

### 2016-11-15 paper/abstraction/paper.tex
more edits

@@
 The possibility of network failures exacerbates the difficulty of constructing correct configurations.
-Link failures in networks occur frequently; it is not uncommon for a large network to experience dozens of such failures in any given day~\cite{dc-failure-study}.
-However, existing tools~\cite{condor,propane} can reason about fault-tolerance only for concrete topologies.
-The problem for \sysname is harder because it must verify that all possible concrete instantiations of an abstract topology satisfy the fault-tolerance requirements, which requires a fundamentally different approach.
+Link failures in networks occur frequently; it is not uncommon for a large network to experience dozens of failures in any given day~\cite{dc-failure-study}.
+However, existing tools~\cite{condor,propane} reason about fault-tolerance only for concrete topologies.
+The problem for \sysname is harder because it must verify that all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy, which requires a fundamentally different approach.
 
@@
 Finally, rules \infrule{I-local} and \infrule{I-global} reason across pod hierarchies.
-\infrule{I-local} says that if there is an inference from $L_m(j,k)$ to $L_n(j',k')$ on the left, then if both nodes are in the same pod P, we can leave all labels up to P unchanged.
+\infrule{I-local} says that if there is an inference from $X$ to $Y$, then the derivation can be used inside pod P by leaving the P-label unchanged.
 \infrule{I-global} says that when the edge goes across pods, we can infer the fact for all pods Q since the multiplicities apply uniformly for each pod.
@@
 The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly tries to apply every inference rule from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
-The algorithm applies an inference rule when the rule condition is valid given the abstract topology constraints.
+The algorithm applies an inference rule when the rule's condition is valid given the abstract topology constraints.
 This ensures that the condition holds for all concrete instantiations of the topology.
@@
 Therefore, for each inference $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing SMT solver $\nu$Z~\cite{z3opt}.
-Invariants learned with $j=0$ or $k=0$ provide no useful information and are discarded.
+Invariants learned with $j=0$ or $k=0$ are discarded.
 
@@
 
-The algorithm was able to infer that any spine router has at least 1 disjoint path and any TL router has at least 2 disjoint paths to a TG router.
+The algorithm was able to infer that there is at least 1 disjoint path to any spine router, and at least 2 disjoint paths to any TL router.
 In this case, the analysis is precise.
 There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global ToR from a spine router due to the valley-free constraint.
-The bound on the fault tolerance between ToR and spine routers can also be used to determine that an aggregation-induced black hole may arise at the datacenter boundary after a single failure in some concrete instantiation.
+%The bound on the fault tolerance between ToR and spine routers can also be used to determine that an aggregation-induced black hole may arise at the datacenter boundary after a single failure in some concrete instantiation.
 
@@
 The bottom part of Figure~\ref{fig:analysis-precision} shows the results for all types of topologies coupled with shortest-path routing.
-(Valley-free routing is not meaningful for non-tree-based topologies.) For all tree-based topologies, analysis is precise for determining reachability, but for three of them, it does not compute a tight bound for edge-disjoint paths for all router pairs.
-Specifically, it underestimates ToR-to-spine paths; it fails to account for circuitous paths that traverse another spine because it could not disambiguate two concrete spines that map to the same abstract role.
+(Valley-free routing is not meaningful for non-tree-based topologies.) For all tree-based topologies, the analysis is precise for determining reachability, but for three of them, it does not compute a tight bound for disjoint paths for all router pairs.
+Specifically, it underestimates ToR-to-spine paths; it fails to account for some circuitous paths that traverse another spine because it could not disambiguate two concrete spines that map to the same abstract role.
 %For all fat tree variants, the analysis correctly computes the number of ToR to ToR disjoint paths, but can lose precision between ToR to spine routers due to valley paths.
 For a valley-free routing policy, the analysis is precise for ToR to spine connectivity.
-For both recursive topologies, the analysis can accurately determine reachability (i.e., at least 1 disjoint path) but is conservative in determining k-disjoint paths.
+For both recursive topologies, the analysis can accurately determine reachability but is conservative in determining disjoint paths.
 %For the BCube topology, it is able to to determine the correct number of disjoint paths between some pairs of nodes, but not all.
@@
 
-We use a fat tree topology and scale the size of the topology according the the number of pods $k$, starting with 4 pods and ending with 24 pods.
-The abstract topology uses one abstract node for each tier of the datacenter with an additional abstract node for separate local and global ToRs.
+We use a fat tree topology and scale the size of the topology according the the number of pods $k$.
+The abstract topology uses one abstract node for each tier of the datacenter with an additional node for separate local and global ToRs.
 
@@
 The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell routers how to forward packets~\cite{foster:merlin,fattire,netgen}.
-The second class, and to which our work belongs, targets conventional networks and generates router configuration, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
-Almost all large networks (old or new) use the conventional paradigm because that scales better~\cite{bgp-in-dc}.
+The second class, to which our work belongs, targets conventional networks and generates router configuration, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
+%Almost all large networks (old or new) use the conventional paradigm because that scales better~\cite{bgp-in-dc}.
 
@@
 Our analysis operates entirely in the abstract domain and guarantees correctness for all concrete instantiations of the topology.
-Experiments with many types of real-world topologies and policies show that our abstractions and analysis are precise and that, for large networks, configuration synthesis is two orders of magnitude faster than systems that operate over concrete topologies.
+Experiments with many types of real-world topologies and policies show that our abstractions and analysis are effective and that, for large networks, configuration synthesis is two orders of magnitude faster than systems that operate over concrete topologies.
 

### 2016-11-15 paper/abstraction/paper.tex
tiny edits
pass over 9.2, 9.3

@@
 
-\begin{figure}[t!]
-  \begin{minipage}[t]{\linewidth}
-    \hdr{HyperX}{}
-    \vspace{.6em}
-    \includegraphics[width=\linewidth]{figures/hyperx}
-  \end{minipage}%
-
-  \vspace{1.4em}
-  \begin{minipage}[t]{\linewidth}
-    \hdr{BCube}{}
-    \vspace{.3em}
-    \includegraphics[width=\linewidth]{figures/bcube}
-  \end{minipage}%
-
-  \caption{Example abstractions for HyperX and BCube.}
-  \vspace*{-1em}%
-  \label{fig:example-abstractions}
-\end{figure}
-
 \subsection{Expressiveness and precision}
@@
 
+\begin{figure}[t!]
+  \begin{minipage}[t]{\linewidth}
+    \hdr{HyperX}{}
+    \vspace{.6em}
+    \includegraphics[width=\linewidth]{figures/hyperx}
+  \end{minipage}%
+
+  \vspace{1.4em}
+  \begin{minipage}[t]{\linewidth}
+    \hdr{BCube}{}
+    \vspace{.3em}
+    \includegraphics[width=\linewidth]{figures/bcube}
+  \end{minipage}%
+
+  \caption{Example abstractions for HyperX and BCube.}
+  \vspace*{-1em}%
+  \label{fig:example-abstractions}
+\end{figure}
+
 To stress our abstractions and analysis, we consider additional topologies from the literature.
@@
 
-\subsection{Generation time}
+\subsection{Synthesis time}
 
@@
   \vspace{-.6em}
-  \caption{Concrete vs. Abstract Generation Time. \label{fig:compilation-times}}
+  \caption{Concrete vs. Abstract Synthesis Time. \label{fig:compilation-times}}
   \vspace{-1em}
@@
   \vspace{-.6em}
-  \caption{Abstract Generation Time by Phase. \label{fig:abstract-breakdown}}
+  \caption{Abstract Synthesis Time by Phase. \label{fig:abstract-breakdown}}
   \vspace{-1em}
@@
 
-We evaluate generation time in \sysname both with and without abstraction using routing policy for backbone and datacenter networks inspired by configurations obtained from a large cloud provider.
-For both types networks, we fix the routing policy and scale the size of the underlying topology.
+We evaluate synthesis time in \sysname using routing policy for backbone and datacenter networks inspired by configurations from a large cloud provider.
+For both types of networks, we fix the routing policy and scale the topology.
 
@@
 
-Routers in the datacenter network run BGP using private AS numbers and peer with multiple backbone networks.
-The routers aggregate some prefix blocks when announcing them to the backbone network, and keep some prefixes internal.
-The policy also ensures that private address space from external neighbors is dropped.
-The data center prefers that traffic leave through certain peers over others and ensures that transit traffic between peers is dropped.
-
-We use a fat tree topology and scale the size of the topology according the the number of pods $k$.
-The abstract topology uses one abstract node for each tier of the datacenter with an additional node for separate local and global ToRs.
+Routers in the datacenter network run BGP using unique AS numbers and connect to multiple external neighbors.
+The routers aggregate some prefix blocks when announcing them to external neighbors, and keep some prefixes internal.
+The data center prefers that traffic leave through certain neighbors over others and should not transit traffic between neighbors.
+The policy also says that the datacenter routers not use external neighbors to reach ``private" destinations  (i.e., those in the part of the IP address space reserved for private use).
+
+We use a fat tree~\cite{fattree} and scale it by increasing the number of pods. The abstract topology uses one abstract node for each tier with additional nodes for local and global ToRs.
 
@@
 
-The backbone policy classifies neighbors into several categories based on commercial relationship and prefers paths through them in order.
-Similar to the datacenter, it drops private address space from  neighbors, drops transit traffic between certain peers but not others, and aggregates internal prefixes at the border of the network.
-
-For the backbone networks, we split the network into two parts: a collection of border routers and an internal core.
-We scale the backbone networks from 10 to 250 routers.
-The abstract topology uses a single abstract node for the border routers and another for the network core with mincut annotations both within the core and between the core and border roles.
-Neighbors are grouped into roles based on their commercial relationship to the current AS.
+The backbone policy classifies neighbors into several categories based on commercial relationship~\cite{gao-rexford} and prefers paths through them in order.
+Similar to the datacenter, it blocks private destinations from neighbors, drops transit traffic between certain neighbors but not others, and aggregates internal prefixes at the border of the network.
+
+We scale the backbone network from 10 to 250 routers.
+To abstract it, we split it into two parts: border routers that connect to external neighbors and an internal core.
+We use one abstract node for the border routers and one for the network core with mincut annotations both within the core and between the core and border roles.
+For neighbors, there is one abstract role per commercial category.
 
@@
 
-Figure~\ref{fig:compilation-times} shows total configuration generation time for \sysname vs the concrete network synthesis tool \propane.
+Figure~\ref{fig:compilation-times} shows total configuration synthesis time for \sysname and the concrete network synthesis tool Propane.
 All experiments were run on an 8 core, 2.4 GHz Intel i7 processor machine running Mac with 16GB of Ram.
 
-For both networks, the abstract generation starts off slightly slower than \propane's concrete generation for small topologies due to the overhead of the fault-tolerance analysis.
-However, as the size of the topology increases, abstract generation becomes orders of magnitude faster than concrete generation.
-In all cases for both networks, abstract generation takes less than 10 seconds to complete.
+For both networks, the abstract synthesis is slightly slower than concrete synthesis for small topologies due to the overhead of the fault-tolerance analysis.
+However, as the topology size increases, abstract synthesis becomes orders of magnitude faster.
+In all cases for both networks, it takes less than 10 seconds to complete.
 
 Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of \sysname.
-Notably, the fault-tolerance analysis takes the most time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost.
+The fault-tolerance analysis takes the most time, but that does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost.
 In particular, the number of calls to $\nu$Z remains constant across topology size.
@@
 
-The design of \sysname guarantees that network evolution requires configuration changes only for nodes that acquire or lose a neighbor.
+\sysname compilation strategy guarantees that network evolution requires configuration changes only for nodes that acquire or lose a neighbor.
 We experimentally confirmed that our implementation provides this guarantee.
-To the networks we studied above, we made a range of changes, including adding and removing routers and pods and changing the prefix that a router originates.
+For the networks we studied above, we made a range of changes, including adding and removing routers and pods and changing prefixes that routers originate.
 In each case, we found the guarantee to hold; for prefix changes, only the originator's configuration changed.
@@
 
-Our work is related to four threads of prior work.
+Our work is related to three threads of prior work.
 

### 2016-11-15 paper/abstraction/paper.tex
more edits

@@
 
-\newcommand{\sysname}{{\small \sf Methane}\xspace}
+\newcommand{\sysname}{{\text{}\small \sf Methane}\xspace}
 \newcommand{\sysnamesec}{{\sf Methane}\xspace}
-\newcommand{\propane}{{\small \sf Propane}\xspace}
 \newcommand{\mbgp}{{\small \sf mBGP}\xspace}
@@
 
-\newcommand{\CD}[1]{\texttt{\small #1}}  % code font
+\newcommand{\CD}[1]{\texttt{\small #1}}
 \newcommand{\KW}[1]{\texttt{\small\bfseries{#1}}}
@@
 Its output is also guaranteed to require minimal changes to the configurations of existing devices when the topology evolves to include new devices or links.
-Our experiments with many real-world topologies and policies show that our abstractions and fault-tolerance analysis are effective and that, for large networks, configuration synthesis with \sysname is two orders of magnitude faster than similar systems that operate over concrete topologies.
+Our experiments with many real-world topologies and policies show that our abstractions and fault-tolerance analysis are effective and that, for large networks, configuration synthesis with \sysname is two orders of magnitude faster than systems that operate over concrete topologies.
 
@@
 
-Based on these inputs, the \sysname compiler generates one template per role. It
+Based on these inputs, \sysname generates one template per role. It
 guarantees that, when the templates are instantiated to configurations for {\em
@@
 
-Second, \sysname can scale substantially better than its nearest competitor \propane that operates over concrete topologies. As the number of devices in a
+Second, \sysname can scale substantially better than its nearest competitor Propane that operates over concrete topologies. As the number of devices in a
 network grows, the number of distinct roles will often stay constant~\cite{surgery}.
-Consequently, the \sysname compiler can be two orders of magnitude
-faster than \propane, taking less than 10 seconds to synthesize templates for large structured networks.
-
-%\todo{Talk about evaluation result here ... roll the point about faster compilation there.}
+Consequently, \sysname can be two orders of magnitude
+faster than Propane, taking less than 10 seconds to synthesize templates for large structured networks.
 
@@
 %evolution.
-\item Implementation and evaluation of the \sysname compiler that generates
+\item Implementation and evaluation of the \sysname tool that generates
 provably-correct templates and is much faster
-than a compiler based on concrete topologies.
+than tools based on concrete topologies.
 \end{itemize}
@@
 
-In this work, we focus on synthesizing configurations for a network that runs the Border Gateway Protocol (BGP), the standard for routing across independent organizations and inside large datacenters.
+In this work, we focus on synthesizing configurations for a network that runs the Border Gateway Protocol (BGP), the standard for routing across independent organizations and inside large data centers.
 It scales effectively and allows operators to define flexible policies.
@@
 All route announcements carry an {\em AS path}, the sequence of BGP speakers (called Autonomous Systems) that will be traversed to reach the destination.
-%When BGP is used inside a datacenter, each router tends to be its own AS.
+%When BGP is used inside a data center, each router tends to be its own AS.
 Optionally, they may also include one or more {\em communities}, which are arbitrary tags whose semantics are agreed upon out of band.
@@
   \includegraphics[width=\columnwidth]{figures/templates}
-  \caption{Idealized small configuration component for the datacenter spine role based on router templates from a large cloud provider (\IE, macros over gobbledygook).}
+  \caption{Idealized small configuration component for the data center spine role based on router templates from a large cloud provider (\IE, macros over gobbledygook).}
   \label{fig:templates}
@@
 %
-Figure~\ref{fig:templates} shows an example of what a small component of a template for the spine role in the two datacenters might look like.
+Figure~\ref{fig:templates} shows an example of what a small component of a template for the spine role in the two data centers might look like.
 The template has parameters for various aspects of the configuration (\EG, neighbor list, local prefixes) and are compiled to low-level device configurations by instantiating the parameters using the network topology and a database of network information.
@@
 
-%While templates help avoid a class of configuration errors (e.g., inconsistent routing adjacencies), they provide no guarantees
 As described earlier (\S\ref{sec:introduction}), templates are hard to author and hard to validate.
@@
 
-%Ideally, we would like to find a suitable topology abstraction that can describe both of the datacenters from figures~\ref{fig:example} and~\ref{fig:example2} as well as any reasonable generalization of these datacenters.
+%Ideally, we would like to find a suitable topology abstraction that can describe both of the data centers from figures~\ref{fig:example} and~\ref{fig:example2} as well as any reasonable generalization of these data centers.
 \sysname provides several abstraction mechanisms to achieve this goal.
@@
 
-Our topology abstractions can trivially capture concrete topologies; there will be a one-to-one correspondence between abstract and concrete nodes (and edges).
+Our topology abstractions can also capture concrete topologies; there will be a one-to-one correspondence between abstract and concrete nodes (and edges).
 This ability enables operators to define complex networks in which they expect some (e.g., legacy) parts of the network to not evolve and others to evolve.
-It also means that our compiler subsumes those that operate only over concrete topologies.
+%It also means that our compiler subsumes those that operate only over concrete topologies.
 
@@
 %location, and the definition of the valleyfree constraint depends on the actual routers that
-%comprise each tier of the datacenter.
-%
-%This is unfortunate since any expansion of our datacenter network will require a corresponding
+%comprise each tier of the data center.
+%
+%This is unfortunate since any expansion of our data center network will require a corresponding
 %change to the policy. Furthermore, there is no guarantee that a safe policy can be found
@@
 %
-The final rule matches all other IP prefix destinations and allows traffic to follow a path that leaves the datacenter, ending at some outside location, through neighbors $\CD{N1}$ or $\CD{N2}$ with a preference for leaving through $\CD{N1}$.
+The final rule matches all other IP prefix destinations and allows traffic to follow a path that leaves the data center, ending at some outside location, through neighbors $\CD{N1}$ or $\CD{N2}$ with a preference for leaving through $\CD{N1}$.
 The $\CD{\Prefer}$~symbol indicates that traffic should satisfy the constraint on the left and resort to the backup (right) only when that is not possible due to network failures.%
 
-Next we can capture constraint (4) that traffic for local prefixes must stay within in the datacenter:
+Next we can capture constraint (4) that traffic for local prefixes must stay within in the data center:
 %
@@
 %
-The Local constraint applies to any traffic destined for a local prefix described by the variable $\CD{\$LP}$ and adds the constraint that the traffic must follow a path that matches an internal location (\IE, in the datacenter) at each hop of the path.
+The Local constraint applies to any traffic destined for a local prefix described by the variable $\CD{\$LP}$ and adds the constraint that the traffic must follow a path that matches an internal location (\IE, in the data center) at each hop of the path.
 %
@@
 %
-This policy applies to all traffic and prevents valley paths by adding the $\Novalley$ constraint with arguments corresponding to each datacenter level.
+This policy applies to all traffic and prevents valley paths by adding the $\Novalley$ constraint with arguments corresponding to each data center level.
 %
@@
 %
-We define a $\CD{Peer}$ as $\CD{N1}$ or $\CD{N2}$ and disallow paths where traffic both enters and exits the datacenter through a peer.
+We define a $\CD{Peer}$ as $\CD{N1}$ or $\CD{N2}$ and disallow paths where traffic both enters and exits the data center through a peer.
 
@@
 This instructs \sysname to satisfy the conjunction of all the constraints.
-It also declares that we want to perform route aggregation, as covering prefix PG, for global prefixes at the border of the datacenter (\IE, along any edge that connects the inside of the datacenter to the outside).
+It also declares that we want to perform route aggregation, as covering prefix PG, for global prefixes at the border of the data center (\IE, along any edge that connects the inside of the data center to the outside).
 
@@
 
-\para{Synthesis}
-
-%\sysname builds on the Propane network configuration tool, by supporting both synthesis for and reasoning over parameterized classes of topologies and their interactions with user-specified routing policy.
-
-%Although \sysname can ensure correct forwarding behavior independent of the exact concrete topology or failure scenario, it is often useful to be able to ask "what if" questions about other network properties.
-For example, an operator may require a certain level fault tolerance between between different collections of routers.
-Such analysis depends, not only on the network topology, but also on the underlying routing policy, both of which \sysname has access to.
-The \sysname compiler generates templates from the inputs above in three phases.
+% The \text{} is needed for some reason for formatting
+\para{Synthesis} \sysname generates templates from the inputs above in three phases.
 First, it combines the abstract topology and routing policy into a {\em product graph} (PG) that compactly captures the flow of routing information over the topology in a policy-compliant manner.
-The algorithm for this phase builds on the \propane compiler (for concrete networks); we show that it can be extended to abstract inputs and that the extensions are correct.
+The algorithm for this phase builds on Propane (for concrete networks); we show that it can be extended to abstract inputs and that the extensions are correct.
 
 Second, \sysname checks if the fault-tolerance policy can be met by considering the joint impact of the abstract topology and routing policy.
-Joint analysis is needed, because connectivity depends on both: traffic will not flow along
-valid topological paths if the routing policy disallows it.
+Joint analysis is needed, because connectivity depends on both: traffic will not flow along valid topological paths if the routing policy disallows it.
 %
@@
 
-Figure~\ref{fig:example-compilation} shows the PG for the datacenter policy that applies to all external traffic ($\CD{\True \Path \Exit(N1~\Prefer~N2)}$).
+Figure~\ref{fig:example-compilation} shows the PG for the data center policy that applies to all external traffic ($\CD{\True \Path \Exit(N1~\Prefer~N2)}$).
 %
@@
     \node[] at (#1 + 1.2, 1.25 + 2.5) {\textbf{I-local}};
-
     \derivation{#1}{X}{Y}
     \derivation{#1+2+#2}{L$_P$ X}{L$_P$ Y}
+    \node[anchor=east] at (#1 + .5 + #2, 2.5 / 2) {$\Rightarrow$};
     %\inferencenobox{#1}{X}{}{Y}{}{}{}
@@
     \derivation{#1+2+#2}{L$_P$ X}{A$_Q$ Y}
+    \node[anchor=east] at (#1 + .5 + #2, 2.5 / 2) {$\Rightarrow$};
 
@@
     \inference{10.5}{L$_m(j,k)$}{$e_1=n$}{A$_n(1,j)$}{I-mesh2}{$e_1$}{$e_2$}
-    \inferencenobox{14}{L$(j,k)$}{$mincut(X)$}{A$(1,min(k,X))$}{I-mincut}{}{}
+    \inferencenobox{14}{L$(j,k)$}{$\Mincut(X)$}{A$(1,min(k,X))$}{I-mincut}{}{}
   \end{tikzpicture}
@@
 
-The annotation $mincut(X)$ appearing on an edge is an assertion about the fault tolerance between nodes in two different roles.
+The annotation $\Mincut(X)$ appearing on an edge is an assertion about the fault tolerance between nodes in two different roles.
 The rule \infrule{I-mincut} uses such assertions.
@@
 The second part of the rule uses a similar idea to reason about the overlap between roles $m$ and $o$ with respect to role $n$.
-This rule is useful particularly useful for datacenter topologies where routers in one tier of the datacenter often have a particular striping pattern with another tier.
+This rule is useful particularly useful for data center topologies where routers in one tier of the data center often have a particular striping pattern with another tier.
 
@@
 
-Recall the policy for global prefixes in the datacenter.
+Recall the policy for global prefixes in the data center.
 %
@@
 In this case, the analysis is precise.
-There exists a concrete network, namely the datacenter from Figure~\ref{fig:example2}, where a single failure can disconnect a global ToR from a spine router due to the valley-free constraint.
-%The bound on the fault tolerance between ToR and spine routers can also be used to determine that an aggregation-induced black hole may arise at the datacenter boundary after a single failure in some concrete instantiation.
+There exists a concrete network, namely the data center from Figure~\ref{fig:example2}, where a single failure can disconnect a global ToR from a spine router due to the valley-free constraint.
+%The bound on the fault tolerance between ToR and spine routers can also be used to determine that an aggregation-induced black hole may arise at the data center boundary after a single failure in some concrete instantiation.
 
@@
 
-Suppose an operator wants to expand the concrete datacenter by adding an additional ToR router to the TG role.
+Suppose an operator wants to expand the concrete data center by adding an additional ToR router to the TG role.
 Per the network routing policy, the new ToR router will advertise any owned prefixes provided by looking up {\small \$GP} in $\Gamma$.
@@
 
-The \sysname compiler is implemented in around 9500 lines of F\# code.
+\sysname is implemented in approximately 9500 lines of F\# code.
 The compiler accepts both concrete and abstract topologies and will generate configurations for open-source Quagga~\cite{quagga} routers by default.
@@
 
-We evaluate \sysname by applying it on policies for backbone and datacenter networks.
+We evaluate \sysname by applying it on policies for backbone and data center networks.
 We aim to evaluate the expressiveness of our abstractions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.
@@
 %
-%The fat tree topology is a widely used datacenter topology.
+%The fat tree topology is a widely used data center topology.
 We look at the precision of our analysis on four fat tree variants used in practice: a standard fat tree~\cite{fattree}, the Facebook fat tree~\cite{facebook-fattree}, the F10 fault tolerant fat tree~\cite{f10-fattree}, and the VL2 topology~\cite{vl2-fattree}.
@@
 This allows for safe expansion within a subcomponent, but does not allow changing the recursion depth dynamically.
-For BCube, we model each tier of the datacenter as a separate role. Figure~\ref{fig:example-abstractions} shows an example of a BCube abstraction for $k=1$.
+For BCube, we model each tier of the data center as a separate role. Figure~\ref{fig:example-abstractions} shows an example of a BCube abstraction for $k=1$.
 
@@
 \begin{figure}[t!]
-  \subcaptionbox{Datacenter}
+  \subcaptionbox{Data center}
     {\includegraphics[width=.49\columnwidth]{figures/Fattree-time.png}}
@@
 \begin{figure}[t!]
-  \subcaptionbox{Datacenter}
+  \subcaptionbox{Data center}
     {\includegraphics[width=.49\columnwidth]{figures/Fattree-analysis-time.png}}
@@
 
-We evaluate synthesis time in \sysname using routing policy for backbone and datacenter networks inspired by configurations from a large cloud provider.
-For both types of networks, we fix the routing policy and scale the topology.
-
-\para{Datacenter}
-
-Routers in the datacenter network run BGP using unique AS numbers and connect to multiple external neighbors.
-The routers aggregate some prefix blocks when announcing them to external neighbors, and keep some prefixes internal.
-The data center prefers that traffic leave through certain neighbors over others and should not transit traffic between neighbors.
-The policy also says that the datacenter routers not use external neighbors to reach ``private" destinations  (i.e., those in the part of the IP address space reserved for private use).
-
-We use a fat tree~\cite{fattree} and scale it by increasing the number of pods. The abstract topology uses one abstract node for each tier with additional nodes for local and global ToRs.
+We evaluate generation time in \sysname both with and without abstraction using routing policy for backbone and data center networks inspired by configurations obtained from a large cloud provider.
+For both types networks, we fix the routing policy and scale the size of the underlying topology.
+
+\para{Data center}
+
+Routers in the data center network run BGP using private AS numbers and peer with multiple backbone networks.
+The routers aggregate some prefix blocks when announcing them to the backbone network, and keep some prefixes internal.
+The policy also ensures that private address space from external neighbors is dropped.
+The data center prefers that traffic leave through certain peers over others and ensures that transit traffic between peers is dropped.
+
+We use a fat tree topology and scale the size of the topology according the the number of pods $k$.
+The abstract topology uses one abstract node for each tier of the data center with an additional node for separate local and global ToRs.
 
@@
 
-The backbone policy classifies neighbors into several categories based on commercial relationship~\cite{gao-rexford} and prefers paths through them in order.
-Similar to the datacenter, it blocks private destinations from neighbors, drops transit traffic between certain neighbors but not others, and aggregates internal prefixes at the border of the network.
+The backbone policy classifies neighbors into several categories based on commercial relationship and prefers paths through them in order.
+Similar to the data center, it drops private address space from  neighbors, drops transit traffic between certain peers but not others, and aggregates internal prefixes at the border of the network.
 
@@
 
-Figure~\ref{fig:compilation-times} shows total configuration synthesis time for \sysname and the concrete network synthesis tool Propane.
+Figure~\ref{fig:compilation-times} shows total configuration generation time for \sysname vs the concrete network synthesis tool Propane.
 All experiments were run on an 8 core, 2.4 GHz Intel i7 processor machine running Mac with 16GB of Ram.
 
-For both networks, the abstract synthesis is slightly slower than concrete synthesis for small topologies due to the overhead of the fault-tolerance analysis.
-However, as the topology size increases, abstract synthesis becomes orders of magnitude faster.
-In all cases for both networks, it takes less than 10 seconds to complete.
+For both networks, the abstract generation starts off slightly slower than Propane's concrete generation for small topologies due to the overhead of the fault-tolerance analysis.
+However, as the size of the topology increases, abstract generation becomes orders of magnitude faster than concrete generation.
+In all cases for both networks, abstract generation takes less than 10 seconds to complete.
 

### 2016-11-15 paper/abstraction/paper.tex
a few edits

@@
 routers. While the network may have hundreds or thousands of devices---a scale
-that is impossible for humans to handle---there tend to be a handful of roles.
+that is impossible for humans to handle---there tend to be only a handful of roles.
 %
@@
 requirements.
-We show how fault-tolerance analysis can be done in the abstract domain by using a set of sound inference rules to infer the lower bound on the number of edge-disjoint paths in any concrete topology.
+We show how fault-tolerance analysis can be done in the abstract domain by using a set of sound inference rules to infer a lower bound on the number of edge-disjoint paths in any concrete topology.
 %Our analysis uses a set of sound inference rules and  using an optimizing SMT solver.
@@
 %evolution.
-\item Implementation and evaluation of the \sysname tool that generates
+\item Implementation and evaluation of the \sysname compiler that generates
 provably-correct templates and is much faster
-than tools based on concrete topologies.
+than compilers based on concrete topologies.
 \end{itemize}
@@
 One might think that the same templates (with different database entries) can be used for both cases.
-However, if the templates are configured to disallow ``valley" paths (per policy (5) above), they will work for Figure~\ref{fig:example} but silently violate the fault tolerance policy ($(8)$) when used for Figure~\ref{fig:example2}.
+However, if the templates are configured to disallow ``valley" paths (per policy (5) above), they will work for Figure~\ref{fig:example} but silently violate the fault tolerance policy $(8)$ when used for Figure~\ref{fig:example2}.
 Specifically, in Figure~\ref{fig:example2}, an aggregation-based blackhole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]).
@@
 A role-based abstraction is a graph homomorphism from $G$ to an abstract graph $G^A$ = ($V^A$,$E^A$).
-A graph homorphism $f : G \rightarrow G^A$ maps each node in the concrete graph to a node in the abstract graph such that, whenever $(u,v) \in E$, then $(f(u),f(v)) \in E^A$.
+A graph homomorphism $f : G \rightarrow G^A$ maps each node in the concrete graph to a node in the abstract graph such that, whenever $(u,v) \in E$, then $(f(u),f(v)) \in E^A$.
 The role-based abstraction therefore overapproximates the connectivity of the underlying concrete graphs.
@@
 %
-The Local constraint applies to any traffic destined for a local prefix described by the variable $\CD{\$LP}$ and adds the constraint that the traffic must follow a path that matches an internal location (\IE, in the data center) at each hop of the path.
+The Local policy adds the $\CD{\Always(\In)}$ constraint for each local prefix described by the template variable $\CD{\$LP}$.
+This constraint ensures that traffic follows a path that matches an internal location (\IE, in the data center) at each hop of the path.
 %
@@
 %
-This policy applies to all traffic and prevents valley paths by adding the $\Novalley$ constraint with arguments corresponding to each data center level.
+This policy applies to all traffic and prevents valley paths by adding the $\Novalley$ constraint with arguments corresponding to each level in the data center.
 %
@@
 Operators can specify different tolerance levels for different pairs of abstract nodes.
-For instance, they may say that ToR to spine connectivity should be robust to 2 failures, \IE, no ToR-spine pair should lose connectivity as long as the number of simultaneous link failures is 2 or fewer; and ToR-to-ToR connectivity should be be robust to 1 failure.
+For instance, they may say that ToR to spine connectivity should be robust to 2 failures, \IE, no ToR-spine pair should lose connectivity as long as the number of simultaneous link failures is 2 or fewer; and ToR-to-ToR connectivity should be robust to 1 failure.
 
@@
 The labels on other nodes correspond to invariants learned after applying the inference rule.
-The adjacent box shows the conditions that must be \emph{valid} for the rule to apply.
+The adjacent box shows the conditions that must be \emph{valid}, given the abstraction constraints, for the rule to apply.
+Validity ensures that the condition holds for all concrete instantiations of the topology.
 
@@
 The second part of the rule uses a similar idea to reason about the overlap between roles $m$ and $o$ with respect to role $n$.
-This rule is useful particularly useful for data center topologies where routers in one tier of the data center often have a particular striping pattern with another tier.
+This rule is particularly useful for data center topologies where routers in one tier of the data center often have a particular striping pattern with another tier.
 
@@
 The algorithm applies an inference rule when the rule's condition is valid given the abstract topology constraints.
-This ensures that the condition holds for all concrete instantiations of the topology.
-Because the inference rules may continue to yield larger and larger symbolic expressions, we make the following observation to ensure termination: for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
+Because the inference rules may continue to yield larger and larger symbolic expressions, we make the following observation to ensure termination: for any invariant learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
 Therefore, for each inference $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing SMT solver $\nu$Z~\cite{z3opt}.

### 2016-11-15 paper/abstraction/paper.tex
minor edits to abstract

@@
 \textbf{Abstract---}
-We develop \sysname, a system to generate provably-correct configurations for large, evolving networks from high-level specifications of their topology, routing policy, and fault-tolerance requirements.
-It is based on new abstractions for capturing parameterized network topologies and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance.
-Our analysis operates entirely on abstract topologies and guarantees correctness for all concrete instantiations of the topology.
-Its output is also guaranteed to require minimal changes to the configurations of existing devices when the topology evolves to include new devices or links.
-Our experiments with many real-world topologies and policies show that our abstractions and fault-tolerance analysis are effective and that, for large networks, configuration synthesis with \sysname is two orders of magnitude faster than systems that operate over concrete topologies.
+We develop \sysname, a system to synthesize provably-correct configurations for large, evolving networks from high-level specifications of topology, routing policy, and fault-tolerance requirements.
+It is based on new abstractions for capturing parameterized network topologies and their evolution, and algorithms to analyze the impact of topology and routing policy on fault tolerance.
+Our algorithms operates entirely on abstract topologies and guarantees correctness for all its concrete instantiations.
+\sysname also guarantees that minimal changes to existing device configurations are required when the network evolves to add or remove devices and links.
+Our experiments with real-world topologies and policies show that our abstractions and algorithms are effective and that, for large networks, \sysname synthesizes configurations two orders of magnitude faster than systems that operate over concrete topologies.
 

### 2016-11-15 paper/abstraction/paper.tex
edits

@@
 \newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}%
+
+\newcommand{\Topo}[1]{\ensuremath{{\mathrm{topo}}(#1)}}
+\newcommand{\Pref}{\ensuremath{\mathrm{pref}}}
+
+\newcommand{\Conserv}{\cal{C}}
 
@@
 
-Second, \sysname can scale substantially better than its nearest competitor Propane that operates over concrete topologies. As the number of devices in a
+Second, \sysname can scale substantially better than its nearest competitor Propane, which operates over concrete topologies. As the number of devices in a
 network grows, the number of distinct roles will often stay constant~\cite{surgery}.
@@
 It scales effectively and allows operators to define flexible policies.
-
 We provide a brief background on BGP focused on aspects relevant to our work.
-How a BGP-based network carries traffic depends on how the routers exchange and process routing announcements.
+
+The way in which a BGP-based network forwards traffic depends on how the routers exchange and process \emph{routing announcements}.
 To invite traffic from a neighbor to a destination, routers announce the destination's address {\em prefix} (e.g., 10.1.1.0/24\footnote{An IP address
@@
 When a BGP router receives one or more announcements for a prefix from different neighbors, it selects which one to use (if any) based on its configuration.
-This selection can depend on the AS path, communities, or the neighbor that sent the announcement, and it can even discard certain announcements (i.e., never use them for sending traffic).
+This selection can depend on the AS path, communities, or the neighbor that sent the announcement, and it can even discard certain announcements (\IE, never use them for sending traffic).
 Then, based again on its configuration, the router forwards the selected route to one or more neighbors, after adding itself to the AS path, and optionally, modifying communities.
@@
 
-When announcing destinations to certain neighbors, a BGP router may perform {\em route aggregation}, \IE, announce a single prefix that covers multiple prefixes (e.g., announce 10.1.0.0/16 instead of 10.1.[1--255].0/24).
+When announcing destinations to certain neighbors, a BGP router may perform {\em route aggregation}, \IE, announce a single prefix that covers multiple prefixes (\EG, announce 10.1.0.0/16 instead of 10.1.[1--255].0/24).
 The covering prefix is announced as long as the router has a valid route for {\em any} of the covered prefixes.
@@
 These constraints capture the fact that, within any pod, the global aggregators and ToRs are in a full mesh.
-Furthermore, the constraints $AG = AL$ and $AG \leq S$ ensure that, within pods P and Q, the $AG$ and $TG$ roles have the same number of routers, which is less than the number of routers in the spine role $S$.
+Furthermore, the constraints $AG = AL$ and $AG \leq S$ ensure that, within pods P and Q, the $AG$ and $TG$ roles have the same number of routers, which is less than or equal to the number of routers in the spine role $S$.
 %
@@
 First, it combines the abstract topology and routing policy into a {\em product graph} (PG) that compactly captures the flow of routing information over the topology in a policy-compliant manner.
-The algorithm for this phase builds on Propane (for concrete networks); we show that it can be extended to abstract inputs and that the extensions are correct.
+The algorithm for this phase builds on Propane (for concrete networks); we show that it can be extended to abstract inputs.
+%and that the extensions are correct.
 
@@
 %After one more step, the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node
-%In fact, due the the valley-free routing constraint, a single path is
+%In fact, due the valley-free routing constraint, a single path is
 %the worst-case fault-tolerance level for the concrete network from
@@
 %
-The PG is a tuple ($G'$, $start$, $P$) where $G' = (V',E')$ has
+The PG is a tuple ($G'$, $start$, \Pref) where $G' = (V',E')$ has
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
@@
 a unique starting vertex $start$,
-and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$, mapping nodes in the PG to a set of path ranks.
+and a preference function $\Pref \colon V' \rightarrow 2^{\set{1, \dots, j}}$, mapping nodes in the PG to a set of path ranks.
 
@@
 %
-The preference function $P(m)$ denotes the rank of paths through the PG ending at node $m$ and is defined as $P(m) = \set{i~\vert~q_{m_i} \in F_i}$.
-%
-Finally, we write $\tilde{m} = l$ to extract the topology location from a PG node, when $m = (l, q_{m_1}, \dots, q_{m_k}) \in V'$.
+The preference function $\Pref(m)$ denotes the rank of paths through the PG ending at node $m$ and is defined as $\Pref(m) = \set{i~\vert~q_{m_i} \in F_i}$.
+%
+Finally, we write $\Topo{m} = l$ to extract the topology location from a PG node, when $m = (l, q_{m_1}, \dots, q_{m_k}) \in V'$.
 
@@
 
-\begin{defn}
-\label{def:homomorphism}
-If we have a graph homomorphism $f : G \rightarrow G^A$, concrete product graph $PG = (G',\mathit{start},P)$ and abstract product graph $PG^A = (G'^A, \mathit{start}^A, P^A)$, then we can construct a new homomorphism $f_{pg} : G' \rightarrow G'^A$ in the following way:
+\begin{lem}
+\label{lem:homomorphism}
+If we have a graph homomorphism $f : G \rightarrow G^A$, concrete product graph $PG = (G',\mathit{start},\Pref)$ and abstract product graph $PG^A = (G'^A, \mathit{start}^A, \Pref^A)$, then there is a homomorphism $f_{pg} : G' \rightarrow G'^A$ where:
 \[ \begin{array}{rcl}
@@
 \end{array} \]
-\end{defn}
-%
-As we will see in \S\ref{sec:generation}, we have proven that our generation strategy commutes with template instantiation, meaning that we obtain the same results if we instantiate the abstraction early, or if we defer the instantiation until after template generation.
-%
-Definition~\ref{def:homomorphism} provides intuition as to why our strategy for generating templates is correct.
+\end{lem}
+%
+As shown in \S\ref{sec:generation}, our generation strategy commutes with template instantiation, meaning that we obtain the same results if we instantiate the abstraction early, or if we defer the instantiation until after template generation.
+%
+%Lemma~\ref{lem:homomorphism} provides intuition as to why our strategy for generating templates is correct.
 %Abstract product graphs are related to concrete product graphs via a graph homomorphism, just as abstract topologies are related to concrete topologies via a graph homomorphism.
@@
 However, existing tools~\cite{condor,propane} reason about fault-tolerance only for concrete topologies.
-The problem for \sysname is harder because it must verify that all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy, which requires a fundamentally different approach.
+\sysname provides substantially stronger guarantees: all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy.
+
+%The problem for \sysname is harder because it must verify that all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy, which requires a fundamentally different approach.
 
@@
 We frame satisfying the fault-tolerance policy provided by the user as an analysis problem over the structure of the PG.
-In particular, we develop an analysis that uses information about the structure of  concrete instantiations of the abstract topology to infer bounds on the number of edge-disjoint paths between pairs of concrete nodes.
+In particular, we develop an analysis that uses information embedded in the abstract topology to infer bounds on the number of edge-disjoint paths between pairs of concrete nodes.
 
@@
 For each node in the abstract PG,
-the idea is to maintain invariants learned about the number of disjoint paths
+the idea is to infer facts learned about the number of disjoint paths
 to groups of concrete routers in the node's role.
-More specifically, we maintain invariants of the form:
+More specifically, we maintain fact of the form:
 %
@@
 There is one label for each pod in the abstraction pod hierarchy under which the abstract node appears.
-For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the the node itself.
+For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the node itself.
 Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for some/all pods $X_1, \ldots, X_{n-1}$
@@
 For example,
-an inference of the form $A_{Q} A_{TL}(2,3)$ states that, from some fixed source location, for \emph{all} pods Q, and \emph{all} groups of 2 nodes in the TL role, there are 6 disjoint paths to the group---3 for each of the 2 nodes.
+an inference of the form $A_{Q} A_{TL}(2,3)$ states that, from the given source location, for \emph{all} pods Q, and \emph{all} groups of 2 nodes in the TL role, there are 6 disjoint paths to the group---3 for each of the 2 nodes.
 
@@
 
-To learn about disjoint paths, we develop a collection of sound inference rules for invariants of the form above.
-Figure~\ref{fig:inference-rules} shows each rule.
-They are read from bottom to top.
-The label on the bottom left is a known invariant.
+Figure~\ref{fig:inference-rules} displays the collection of rules used to infer facts about disjoint paths.
+Each rule is read from bottom to top.
+The label on the bottom left is a known fact.
 We use $L$ to represent a rule that is parametric over the label ($S$ or $A$).
-The labels on other nodes correspond to invariants learned after applying the inference rule.
-The adjacent box shows the conditions that must be \emph{valid}, given the abstraction constraints, for the rule to apply.
-Validity ensures that the condition holds for all concrete instantiations of the topology.
-
-In general, the inference rules try to learn about both the largest number of disjoint paths to any single node in an abstract role as well as the largest reachable group in a particular role with at least one disjoint path to each.
-
-The first rule, \infrule{I-out1} applies to a learned invariant of the form $L_m(j,k)$ where the number of outgoing edges from any concrete node in the $m$ role is greater than 0.
+The labels on other nodes correspond to facts learned after applying the inference rule.
+The adjacent box shows the conditions that must be valid, given the abstraction constraints, for the rule to apply.
+%Validity ensures that the condition holds for all concrete instantiations of the topology.
+
+Some of the inference rules (\EG, \infrule{I-out2} and \infrule{I-mesh2}) try to learn about the largest number of disjoint paths to any single node in an abstract role, while others (\EG, \infrule{I-out1} and \infrule{I-mesh1}) try to learn about the largest reachable group in a particular role with at least one disjoint path to each node in that group.
+Both kinds of rules are useful.
+
+The first rule, \infrule{I-out1} applies to a learned fact of the form $L_m(j,k)$ where the number of outgoing edges from any concrete node in the $m$ role is greater than 0.
 In the worst case, the largest group of concrete nodes we could hope to reach at the $n$ role would be $e_1$ since all j nodes at the bottom may have outgoing edges to the same concrete nodes at the top.
@@
 
-\subsection{An inference algorithm}
+\subsection{Inference algorithm}
 
@@
 Therefore, for each inference $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing SMT solver $\nu$Z~\cite{z3opt}.
-Invariants learned with $j=0$ or $k=0$ are discarded.
+Facts learned with $j=0$ or $k=0$ are discarded.
 
@@
 The first step applies each inference rule to this initial fact.
-Rules \infrule{I-mesh1} together with \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles results in a call to $\nu$Z to minimize the expression $min(\infty, AG)$, which results in 2.
+The algorithm uses rules \infrule{I-mesh1} and \infrule{I-local} to reason about connectivity within a single pod for the TG and AG roles.
+It makes a call to $\nu$Z to minimize the expression $min(\infty, AG)$, which results in 2.
 Therefore, the algorithm learns a new invariant of the form $S_P A_{AG} (2,1)$ for node $(AG, 0)$ to indicate that in some pod P, any group of 2 nodes is reachable.
@@
 
-The next step is to use \infrule{I-mesh2} together with \infrule{I-local} to infer than any single node in the TL role for any pod Q is reachable via at least 2 disjoint paths.
+The next step is to use \infrule{I-mesh2} together with \infrule{I-local} to infer that any single node in the TL role for any pod Q is reachable via at least 2 disjoint paths.
 This process will continue until a fixed point is reached.
@@
 Routers then allow announcements that correspond to an edge in the PG and block others.
-For example, in the concrete PG in figure~\ref{fig:example-compilation}, router S1 will allow an advertisement from its neighbors N1 and N2.
+For example, in the concrete PG in Figure~\ref{fig:example-compilation}, router S1 will allow an advertisement from its neighbors N1 and N2.
 If it uses the path advertised by neighbor N1, then it will add the tag $(1,0)$ before sending this to its neighbors.
@@
 \begin{defn}
-Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$.
-Intuitively $m \geq_{rank} n$ means that paths ending at PG node $m$ are no better than paths ending at $n$.
+Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $\min (\Pref(m)) \geq \min (\Pref(n))$ or $\Pref(n) = \emptyset$.
+Intuitively $m \geq_{rank} n$ means that paths ending at node $m$ are no better than paths ending at $n$.
 %
@@
 The PG can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge.
-That is, $m\overset{l}{\rightarrow}n$ if edge $(m,n) \in E'$ and $\tilde{n} = l$.
+That is, $m\overset{l}{\rightarrow}n$ if edge $(m,n) \in E'$ and $\Topo{n} = l$.
 %\end{defn}
@@
 \begin{defn}
-We write $m \leq m'$ if the subgraph reachable from $m$ and $m'$ respectively form a simulation relation with respect to the $\geq_{rank}$ relation.
+We write $m \leq m'$ if the subgraph reachable from $m$ and $m'$ respectively form a simulation relation with respect to $\geq_{rank}$.
 \end{defn}
@@
 This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$.
-Therefore, advertisements received at $S1$ in state $(1,0)$ must be preferred to those received at $S1$ in state $(0,1)$.
+Therefore, advertisements received at $S1$ with tag $(1,0)$ must be preferred to those received at $S1$ with tag $(0,1)$.
 %
@@
 
-Suppose an operator wants to expand the concrete data center by adding an additional ToR router to the TG role.
+Suppose an operator wants to expand the concrete data center from Figure~\ref{fig:example} by adding an additional ToR router to the TG role.
 Per the network routing policy, the new ToR router will advertise any owned prefixes provided by looking up {\small \$GP} in $\Gamma$.
@@
 The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can match against it.
-Figure~\ref{fig:bgp-configs} (right) shows the templates after the transformation.
+Figure~\ref{fig:bgp-configs} (right) shows several templates after the transformation.
 
@@
 The compiler accepts both concrete and abstract topologies and will generate configurations for open-source Quagga~\cite{quagga} routers by default.
-The fault-tolerance analysis uses $\nu$Z~\cite{z3opt} to test validity and minimize variables subject to the topology constraints.
+The fault-tolerance analysis uses $\nu$Z~\cite{z3opt} to both test validity and minimize variables subject to the topology constraints.
 Since the analysis typically calls the SMT solver many times with relatively small optimization problems, we use a timeout of 200ms.
 
-Although the disjoint path analysis takes place over the PG, each application of the inference rules from figure~\ref{fig:inference-rules} depends only on the topology.
+Although the disjoint path analysis takes place over the PG, each application of the inference rules from Figure~\ref{fig:inference-rules} depends only on the topology.
 Therefore, we lazily apply the rules and cache the satisfiability and minimization calls to $\nu$Z after their first use.
@@
 
-      Fattree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \xmark  \\ \hline
+      Fattree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \Conserv  \\ \hline
       Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
-      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \xmark \\ \hline
-      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \xmark \\ \hline
-      BCube~\cite{bcube} & $k$ & \cmark & \cmark & \xmark & \xmark \\ \hline
-      DCell~\cite{dcell} & $k$ & \cmark & \cmark & \xmark & \xmark \\ \hline
+      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \Conserv \\ \hline
+      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \Conserv \\ \hline
+      BCube~\cite{bcube} & $k$ & \cmark & \cmark & \Conserv & \Conserv \\ \hline
+      DCell~\cite{dcell} & $k$ & \cmark & \cmark & \Conserv & \Conserv \\ \hline
          %& HCN & $h$ & \cmark & \xmark \\
@@
 We report precision of both analyzing reachability and computing the number of disjoint paths, and we report if \sysname is precise for all pairs of abstract nodes or only some of them.
+We record a check when the analysis is precise and a \Conserv{} when the analysis is conservative.
 %"All pairs" precision implies "some pairs" precision, but not the other way around.
@@
 
-We use a fat tree topology and scale the size of the topology according the the number of pods $k$.
+We use a fat tree topology and scale the size of the topology according the number of pods $k$.
 The abstract topology uses one abstract node for each tier of the data center with an additional node for separate local and global ToRs.
@@
 The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell routers how to forward packets~\cite{foster:merlin,fattire,netgen}.
-The second class, to which our work belongs, targets conventional networks and generates router configuration, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
+The second class, to which our work belongs, targets conventional networks and generates control-plane router configurations.
+%, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
 %Almost all large networks (old or new) use the conventional paradigm because that scales better~\cite{bgp-in-dc}.
@@
 This goal aligns better with operators' mental models and tools and permits network evolution with minimal disruption to existing routers.
-In the process, develop new abstractions for network topologies, fault-tolerance analysis algorithms for abstract topologies, and assign formal semantics to templates.
+In the process, we develop new abstractions for network topologies, compilation algorithms that generate templates, and analysis techniques that operate over classes of networks.
 
@@
 \para{Network verification}
-A complementary approach to reducing configuration errors is by analyzing the forwarding rules or configuration of the network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery}.
+A complementary approach to reducing configuration errors is by analyzing the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery}.
 Our focus, in contrast, is on a correct-by-construction approach.
-It has the downside that operators must learn to express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation and correct-by-construction guarantees.
+It has the downside that operators must learn to express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation.
 

### 2016-11-15 paper/abstraction/paper.tex
add back ratul edits

@@
 
-Routers in the data center network run BGP using private AS numbers and peer with multiple backbone networks.
-The routers aggregate some prefix blocks when announcing them to the backbone network, and keep some prefixes internal.
-The policy also ensures that private address space from external neighbors is dropped.
-The data center prefers that traffic leave through certain peers over others and ensures that transit traffic between peers is dropped.
-
-We use a fat tree topology and scale the size of the topology according the number of pods $k$.
-The abstract topology uses one abstract node for each tier of the data center with an additional node for separate local and global ToRs.
+Routers in the data center network run BGP using unique AS numbers and connect to multiple external neighbors.
+The routers aggregate some prefix blocks when announcing them to external neighbors, and keep some prefixes internal.
+The data center prefers that traffic leave through certain neighbors over others and should not transit traffic between neighbors.
+The policy also says that the data center routers not use external neighbors to reach ``private" destinations  (i.e., those in the part of the IP address space reserved for private use).
+
+We use a fat tree~\cite{fattree} and scale it by increasing the number of pods. The abstract topology uses one abstract node for each tier with additional nodes for local and global ToRs.
 
@@
 
-The backbone policy classifies neighbors into several categories based on commercial relationship and prefers paths through them in order.
-Similar to the data center, it drops private address space from  neighbors, drops transit traffic between certain peers but not others, and aggregates internal prefixes at the border of the network.
+The backbone policy classifies neighbors into several categories based on commercial relationship~\cite{gao-rexford} and prefers paths through them in order.
+Similar to the datacenter, it blocks private destinations from neighbors, drops transit traffic between certain neighbors but not others, and aggregates internal prefixes at the border of the network.
 
@@
 
-For both networks, the abstract generation starts off slightly slower than Propane's concrete generation for small topologies due to the overhead of the fault-tolerance analysis.
-However, as the size of the topology increases, abstract generation becomes orders of magnitude faster than concrete generation.
-In all cases for both networks, abstract generation takes less than 10 seconds to complete.
+For both networks, the abstract synthesis is slightly slower than concrete synthesis for small topologies due to the overhead of the fault-tolerance analysis.
+However, as the topology size increases, abstract synthesis becomes orders of magnitude faster.
+In all cases for both networks, it takes less than 10 seconds to complete.
 
@@
 
-\sysname compilation strategy guarantees that network evolution requires configuration changes only for nodes that acquire or lose a neighbor.
+\sysname's compilation strategy guarantees that network evolution requires configuration changes only for nodes that acquire or lose a neighbor.
 We experimentally confirmed that our implementation provides this guarantee.

### 2016-11-15 paper/abstraction/paper.tex
fix size

@@
   \label{fig:inference-rules}
-  \vspace{-1.4em}
+  \vspace{-.8em}
 \end{figure*}
@@
 %
-\vspace{-.8em}
+\vspace{-.6em}
 Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix. These results also help assign semantics to templates.
@@
   \label{fig:analysis-precision}
-  \vspace{-1em}
+  %\vspace{-1em}
 \end{figure}
@@
   \caption{Example abstractions for HyperX and BCube.}
-  \vspace*{-1em}%
+  %\vspace*{-1em}%
   \label{fig:example-abstractions}
@@
 While we borrow much from existing configuration synthesis work, especially Propane~\cite{propane}, our goal is to generate role templates from abstract topologies, rather than router configurations from concrete topologies.
-This goal aligns better with operators' mental models and tools and permits network evolution with minimal disruption to existing routers.
+This goal aligns better with operators' mental models and tools and permits network evolution with minimal disruption.
 In the process, we develop new abstractions for network topologies, compilation algorithms that generate templates, and analysis techniques that operate over classes of networks.

### 2016-11-15 paper/abstraction/paper.tex
fix references. fix spelling mistakes

@@
 However, if the templates are configured to disallow ``valley" paths (per policy (5) above), they will work for Figure~\ref{fig:example} but silently violate the fault tolerance policy $(8)$ when used for Figure~\ref{fig:example2}.
-Specifically, in Figure~\ref{fig:example2}, an aggregation-based blackhole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]).
-No such blackhole will occur in Figure~\ref{fig:example} after a single link failure because spine routers have two links to each pod.
+Specifically, in Figure~\ref{fig:example2}, an aggregation-based black hole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]).
+No such black hole will occur in Figure~\ref{fig:example} after a single link failure because spine routers have two links to each pod.
 
@@
 A graph homomorphism $f : G \rightarrow G^A$ maps each node in the concrete graph to a node in the abstract graph such that, whenever $(u,v) \in E$, then $(f(u),f(v)) \in E^A$.
-The role-based abstraction therefore overapproximates the connectivity of the underlying concrete graphs.
+The role-based abstraction therefore over-approximates the connectivity of the underlying concrete graphs.
 
@@
 
-      Fattree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \cmark  \\ \hline
+      Fat tree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \cmark  \\ \hline
       Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
@@
 
-      Fattree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \Conserv  \\ \hline
+      Fat tree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \Conserv  \\ \hline
       Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
@@
 \para{Network verification}
-A complementary approach to reducing configuration errors is by analyzing the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery}.
+A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery}.
 Our focus, in contrast, is on a correct-by-construction approach.
-It has the downside that operators must learn to express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation.
+It has the downside that operators must express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation.
 

### 2016-11-15 scripts/abstract/plot.py

@@ -110,12 +110,12 @@ def makeGraph(con, abs, name, descr):
   color3 = "#FCF5C7"
   color4 = "#A0CED9"
 
-  # Compilation times
+  # Synthesis times
   fig = plt.figure()
   plt.plot(sizeCon, totalCon, label="Concrete", linewidth=5.0, color="cornflowerblue")
   plt.plot(sizeAbs, totalAbs, label="Abstract", linewidth=5.0, linestyle='--', color="lightsalmon")
   plt.xlabel(descr, fontsize=28)
-  plt.ylabel('Compilation Time (sec)', fontsize=28)
+  plt.ylabel('Synthesis Time (sec)', fontsize=28)
   plt.tick_params(axis='both', which='major', labelsize=28)
   plt.tick_params(axis='both', which='minor', labelsize=28)
   if name == "Fattree":
@@ -143,7 +143,7 @@ def makeGraph(con, abs, name, descr):
   ax1.fill_between(sizeAbs, y_stack[1,:], y_stack[2,:], facecolor=color3)
   ax1.fill_between(sizeAbs, y_stack[2,:], y_stack[3,:], facecolor=color4)
   ax1.set_xlabel(descr, fontsize=28)
-  ax1.set_ylabel('Compilation Time (sec)', fontsize=28)
+  ax1.set_ylabel('Synthesis Time (sec)', fontsize=28)
   ax1.tick_params(axis='both', which='major', labelsize=28)
   ax1.tick_params(axis='both', which='minor', labelsize=28)
   if name == "Fattree":

### 2016-11-15 paper/abstraction/paper.tex
add citations

@@
 It is based on new abstractions for capturing parameterized network topologies and their evolution, and algorithms to analyze the impact of topology and routing policy on fault tolerance.
-Our algorithms operates entirely on abstract topologies and guarantees correctness for all its concrete instantiations.
+Our algorithms operate entirely on abstract topologies and guarantee correctness for all its concrete instantiations.
 \sysname also guarantees that minimal changes to existing device configurations are required when the network evolves to add or remove devices and links.
@@
 \vspace{-.6em}
-Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix. These results also help assign semantics to templates.
+Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix.
 
@@
 The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell routers how to forward packets~\cite{foster:merlin,fattire,netgen}.
-The second class, to which our work belongs, targets conventional networks and generates control-plane router configurations.
+The second class, to which our work belongs, targets conventional networks and generates control-plane router configurations~\cite{synet-synthesis,narain+:configassure,propane}.
 %, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
@@
 \para{Network verification}
-A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery}.
+A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery,coalgebraic}.
 Our focus, in contrast, is on a correct-by-construction approach.

### 2016-11-15 paper/abstraction/paper.tex
more edits

@@
 may cause trickle-down, network-wide configuration changes, which is highly
-disruptive.
+disruptive in production networks with live traffic.
 %Building sophisticated tools for validating templates is difficult
@@
   \label{fig:syntax}
-  %\vspace{-1em}
+  %\vspace{-1.4em}
 \end{figure}%
@@
   \caption{Example abstractions for HyperX and BCube.}
-  %\vspace*{-1em}%
+  \vspace*{-1em}%
   \label{fig:example-abstractions}

### 2016-11-15 paper/abstraction/paper.tex
remove bottom left text

@@
 %\titlebanner{DRAFT -- do not distribute}        % These are ignored unless
-\preprintfooter{submission for PLDI 2017}   % 'preprint' option specified.
+%\preprintfooter{submission for PLDI 2017}   % 'preprint' option specified.
 
@@
 topologies, and it is intractable to test all possible future topologies. Updating the templates, if found to not work for a future topology,
-may cause trickle-down, network-wide configuration changes, which is highly
+may cause trickle-down, network-wide configuration changes that are highly
 disruptive in production networks with live traffic.
@@
 provably-correct configurations from high-level policy
-specifications~\cite{narain+:configassure,propane}. However, our conversations
+specifications~\cite{narain+:configassure,propane,synet-synthesis}. However, our conversations
 with two major cloud providers reveal that operators of large networks are
@@
 aggregation router). Other inputs to \sysname include the routing policy of the
-network and its fault-tolerance requirements (e.g., the number of link failures
+network and its fault-tolerance requirements (e.g., the number of simultaneous link failures
 to tolerate). For high-level specification of routing policy, we borrow notation from

### 2017-02-26 paper/abstraction/paper.tex
put names on paper
intro and abstract

@@
 
-\newcommand{\sysname}{{\text{}\small \sf Methane}\xspace}
-\newcommand{\sysnamesec}{{\sf Methane}\xspace}
+\newcommand{\sysname}{{\text{}\small \sf Propane/AT}\xspace}
+\newcommand{\sysnamesec}{{\sf Propane/AT}\xspace}
+
+\newcommand{\Propane}{{\text{}\small \sf Propane}\xspace}
 \newcommand{\mbgp}{{\small \sf mBGP}\xspace}
@@
 
-\title{Network Configuration Synthesis with Abstract Topologies}
+\title{Network Configuration Synthesis with Abstract Topologies \vspace{1cm}}
 
@@
 
-%\authorinfo{Ryan Beckett \and David Walker}{Princeton}{}
-%\authorinfo{Ratul Mahajan \and Jitendra Padhye}{Microsoft}{}
-%\authorinfo{Todd Millstein}{UCLA}{}
-
-\authorinfo{}{}{}
+\authorinfo{Ryan Beckett}{Princeton}{}
+\authorinfo{Ratul Mahajan}{Microsoft}{}
+\authorinfo{Todd Millstein}{UCLA}{}
+\authorinfo{Jitendra Padhye}{Microsoft}{} 
+\authorinfo{David Walker}{Princeton}{}
 
@@
 \textbf{Abstract---}
-We develop \sysname, a system to synthesize provably-correct configurations for large, evolving networks from high-level specifications of topology, routing policy, and fault-tolerance requirements.
-It is based on new abstractions for capturing parameterized network topologies and their evolution, and algorithms to analyze the impact of topology and routing policy on fault tolerance.
-Our algorithms operate entirely on abstract topologies and guarantee correctness for all its concrete instantiations.
-\sysname also guarantees that minimal changes to existing device configurations are required when the network evolves to add or remove devices and links.
-Our experiments with real-world topologies and policies show that our abstractions and algorithms are effective and that, for large networks, \sysname synthesizes configurations two orders of magnitude faster than systems that operate over concrete topologies.
+We develop \sysname, a system to synthesize provably-correct
+BGP configurations for large, evolving networks from high-level
+specifications of topology, routing policy, and fault-tolerance
+requirements. \sysname is based on new abstractions for capturing
+parameterized network topologies and their evolution, and algorithms
+to analyze the impact of topology and routing policy on fault
+tolerance. Our algorithms operate entirely on abstract topologies.  We
+prove that the properties established by our analyses hold for every
+concrete instantiation of the given abstract topology. \sysname
+also guarantees that minimal changes to existing device configurations
+are required when the network evolves to add or remove devices and
+links. Our experiments with real-world topologies and policies show
+that our abstractions and algorithms are effective, and that, for large
+networks, \sysname synthesizes configurations two orders of magnitude
+faster than systems that operate over concrete topologies.
 
@@
 
-%\vspace{0.1in} \noindent \textbf{Keywords}\\ Propane; Domain-specific Language;
+%\vspace{0.1in} \noindent \textbf{Keywords}\\ \Propane; Domain-specific Language;
 %BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems
@@
 
-Unfortunately, template construction is a low-level, manual process. Operators
-must decompose network-wide routing and fault-tolerance policies (e.g.,
-prefer one path over another, or a link failure should not cause connectivity loss) across different roles and encode the decomposition using assembly-language-like
-configuration primitives (e.g., role A should not transmit routing information
-from B to C). Such decomposition and encoding is highly complex~\cite{propane}.
-
-Worse, operators can never be sure that their templates correctly implement the policy. %
-Formally verifying them is difficult; today's hand-generated templates have no particular semantics---which policies they implement and for which topologies---other than those of the configurations obtained from instantiating them.
-%
-Thus, operators validate templates by testing some concrete instantiations using
-simulation or verification tools~\cite{feamster+:rcc, batfish, era, arc, bagpipe}. This testing is insufficient because large networks evolve continuously as
-devices and links are added or taken offline for maintenance. Templates that
+Unfortunately, templates use the same low-level constructs as ordinary router configurations (\EG,
+add a tag to this particular announcement; remove a tag from that announcement).  In both templatized
+and non-templatized configurations, ensuring that a collection of low-level, local configurations
+achieves some important global, network-wide policy, such as a guarantee of connectivity in the face of 
+failures, is extremely challenging.
+%
+%Worse, operators can never be sure that their templates correctly implement the policy. %
+%Formally verifying them is difficult; today's hand-generated templates have no particular semantics---which 
+%policies they implement and for which topologies---other than those of the configurations obtained from 
+%instantiating them.
+%
+In order to validate their templates, operators will typically first instantiate a template with appropriate
+concrete parameters
+and then test it using various scenarios.  In general, like in any complex software system, such testing is 
+bound to be incomplete.
+%Thus, operators validate templates by testing some concrete instantiations using
+%simulation or verification tools~\cite{feamster+:rcc, batfish, era, arc, bagpipe}. 
+Moreover, even if network operators were to instantiate their templates using their initial network 
+configuration and to verify key properties using a tool such as Bagpipe~\cite{bagpipe}, the guarantees
+provided would not hold as large networks evolve frequently over time.  In particular,
+devices and links are sometimes taken offline for maintenance and sometimes added to expand
+capacity.  Unfortunately, templates that
 work for the current topology, may or may not work for future
-topologies, and it is intractable to test all possible future topologies. Updating the templates, if found to not work for a future topology,
-may cause trickle-down, network-wide configuration changes that are highly
+topologies. Problems that occur may cause operators to make small, non-uniform, one-off changes to particular routers,
+which defeats the purpose of a template system.  An even worse situation occurs when
+operators feel obligated to update many (non-local) devices to extend or change their network.  
+Such network-wide configuration changes entail a great deal of risk and may be highly
 disruptive in production networks with live traffic.
+%Ideally, network engineers would like some guarantees about the future, namely that 
+%certain types of changes to the network topology may be (1) made \emph{locally}, and do not require
+%updates of routers far from the source of the change, and (2) do not violate key properties, such
+%as fault tolerance.
+%Updating the templates, if found to not work for a future topology,
+%may cause trickle-down, network-wide configuration changes that are highly
+%disruptive in production networks with live traffic.
 %Building sophisticated tools for validating templates is difficult
@@
 reluctant to use such systems. While they think of their network abstractly, in
-terms of roles, these systems only understand concrete topologies, with no understanding of roles.  Even if two devices play the same role,
+terms of roles, synthesis systems operate over concrete topologies.  
+Even if two devices play the same role, operators cannot specify policy in terms of
+this role and even if specifications for the two devices are similar,
 there is no guarantee that the systems will generate (syntactically) similar
-configurations; if the operators want to debug or analyze system output, they
-will have to consider hundreds of device configurations instead of a handful of
-role configurations. These systems become even more brittle when the network
-evolves. Any change in network topology requires re-execution of the engine,
+configurations.  Perhaps most importantly, if the operators want to debug or analyze system output, they
+will have to consider hundreds of device configurations instead of just a handful of
+role configurations. Finally, current synthesis systems are brittle in the face of network
+evolution: Any change in network topology requires re-execution of the engine,
 from scratch, on the new topology.  The result may be a completely different
-set of configurations.
-
-We present \sysname, a system to generate provably-correct role templates. It
+set of configurations.  No administrator of a large network is
+able to shut down a production network, upgrade policy on all devices and 
+then restart their network.
+
+To address the challenge of configuration synthesis in the presence of abstract roles, we present \sysname. 
+%BGP, unlike link state protocols
+%such as OSPF, is also particularly
+%useful in our setting because it contains features that help us localize the effects of changes.
+\sysname
 allows operators to input \emph{abstract network topologies} in terms of roles
@@
 aggregation router). Other inputs to \sysname include the routing policy of the
-network and its fault-tolerance requirements (e.g., the number of simultaneous link failures
-to tolerate). For high-level specification of routing policy, we borrow notation from
-Propane~\cite{propane}. But while Propane policies refer to concrete devices, \sysname
-policies refer to abstract roles.
-
-Based on these inputs, \sysname generates one template per role. It
-guarantees that, when the templates are instantiated to configurations for {\em
-any} concrete topology that complies with the abstract topology, the resulting
-network will correctly implement the routing policy and meet the fault-tolerance
-requirements.
-We show how fault-tolerance analysis can be done in the abstract domain by using a set of sound inference rules to infer a lower bound on the number of edge-disjoint paths in any concrete topology.
-%Our analysis uses a set of sound inference rules and  using an optimizing SMT solver.
-
-\sysname's abstract reasoning provides two other benefits. First, its templates are evolution friendly. When the network migrates from
+network and its fault-tolerance requirements (\EG, the number of simultaneous link failures
+to tolerate). For high-level specification of routing policy, we borrow notation from the original
+\Propane system~\cite{propane}.  However, while \Propane policies refer to concrete devices,
+\sysname policies refer to abstract roles.
+
+Based on these inputs, \sysname generates one template per role. 
+These templates specify routing policy using the Border Gateway Protocol (BGP).
+BGP is a useful target for synthesis, as it is the standard protocol
+for interdomain routing and it is also commonly used
+within data centers due to its scalability properties.  However, it is far from the only control
+plane protocol; synthesis of configurations for other common protocols such as OSPF is beyond the 
+scope of this paper.
+
+During synthesis, our compiler performs an important analysis over abstract topologies to determine
+the fault tolerance properties of the specified policy.  This analysis determines the
+number of failures require to disconnect one abstract location from another given the constraints
+specified by the abstract topology.  The analysis is specified by a collection of inference rules
+and we prove these inference rules are sound: any concrete instance of the abstract topology will
+adhere to the given fault tolerance property. \dpw{Ryan: check this.}
+%% first analysis determines whether a user policy can be implemented correctly using BGP in
+%% the face of failures (\ie, given any number of failures, will the traffic flow along one of the 
+%% specified paths if such a path is available).  The second analysis determines the number of failures
+%% required to disconnect one abstract location from another.  
+%% Our synthesis algorithm comes with a strong guarantee come with a strong
+%% guarantee:  when the templates are instantiated with parameters, giving rise to concrete configurations,
+%% and those concrete configurations  {\em
+%% any} concrete topology that complies with the abstract topology, the resulting
+%% network will correctly implement the routing policy and meet the fault-tolerance
+%% requirements.
+
+%% We show how fault-tolerance analysis can be done in the abstract domain by using a set of sound inference rules to infer a lower bound on the number of edge-disjoint paths in any concrete topology.
+%% %Our analysis uses a set of sound inference rules and  using an optimizing SMT solver.
+
+\sysname provides two other benefits. First, its templates are evolution friendly. 
+When the network migrates from
 one concrete topology to another, both of which comply with the abstract
 topology, only the configurations of devices that acquire or lose a neighbor need to change. 
-This guarantee is the best that any system can give as neighbor relationships are explicitly configured in devices.
+This guarantee is the best that any system can give as neighbor relationships are explicitly 
+configured in devices.  We achieve this guarantee in part by relying on the ability of BGP
+to tag announcements with abstract values.  These abstract values make it possible to change
+the source of an announcement without the target being aware of a change happening.  Other control
+plane protocols that do not provide such tagging mechanisms or that implement link-state protocols as opposed to
+path-vector protocols would not be able to avail themselves of these techniques.
 %No other device in the network is impacted.
 
-Second, \sysname can scale substantially better than its nearest competitor Propane, which operates over concrete topologies. As the number of devices in a
+Second, \sysname can scale substantially better than its nearest competitor, the original \Propane system, 
+which operates over concrete topologies. As the number of devices in a
 network grows, the number of distinct roles will often stay constant~\cite{surgery}.
 Consequently, \sysname can be two orders of magnitude
-faster than Propane, taking less than 10 seconds to synthesize templates for large structured networks.
+faster than \Propane, taking less than 10 seconds to synthesize templates for large structured networks.
 
@@
 \item Implementation and evaluation of the \sysname compiler that generates
-provably-correct templates and is much faster
+provably-correct BGP templates and is much faster
 than compilers based on concrete topologies.
@@
 %%These systems eliminate entire classes of configuration errors by construction, and, in the case of
-%%Propane~\cite{propane}, guarantee that high-level policy is implemented correctly, even in the presence of
+%%\Propane~\cite{propane}, guarantee that high-level policy is implemented correctly, even in the presence of
 %%arbitrary combinations of failures.
@@
 %For instance, suppose an operator wants to modify the prefix of local ToR T8 in Figure~\ref{fig:example}.
-To accommodate the modification, Propane, a concrete synthesis tool, will, at a minimum, not only change T8's configuration but also those of the two spines because it uses prefix lists at spines to ensure that local prefixes are not advertised externally.
+To accommodate the modification, \Propane, a concrete synthesis tool, will, at a minimum, not only change T8's configuration but also those of the two spines because it uses prefix lists at spines to ensure that local prefixes are not advertised externally.
 As we show later, there is a way to design the configurations of this network to avoid spine configuration changes while accommodating ToR prefix (and other) modifications.
@@
 
-%nof the new spine configurations outputted by Propane will not only enable the interfaces that connect to the new aggregators but will also have to update the prefix list filters.
+%nof the new spine configurations outputted by \Propane will not only enable the interfaces that connect to the new aggregators but will also have to update the prefix list filters.
 A system that supports incremental growth should need only interface configuration changes (not filter changes).
@@
 %For instance, suppose the engineers want to add another pod with local services to the network in Figure~\ref{fig:example}.
-In this network, Propane, a concrete synthesis tool, uses prefix lists at spines to ensure that local prefixes are not advertised externally.
-To accommodate the expansion, the new spine configurations outputted by Propane will not only enable the interfaces that connect to the new aggregators but will also have to update the prefix list filters.
+In this network, \Propane, a concrete synthesis tool, uses prefix lists at spines to ensure that local prefixes are not advertised externally.
+To accommodate the expansion, the new spine configurations outputted by \Propane will not only enable the interfaces that connect to the new aggregators but will also have to update the prefix list filters.
 A system that supports incremental growth should need only interface configuration changes (not filter changes).
@@
 \para{Routing policy} Routing policies in \sysname consist of an ordered sequence of $i)$ a predicate that matches a class of traffic; and $ii)$ paths that the traffic should take through the network, ranked per their relative preference.
-\sysname borrows syntax from Propane~\cite{propane}, but instead of concrete predicates and paths, uses abstract predicates and paths.
+\sysname borrows syntax from \Propane~\cite{propane}, but instead of concrete predicates and paths, uses abstract predicates and paths.
 
@@
 First, it combines the abstract topology and routing policy into a {\em product graph} (PG) that compactly captures the flow of routing information over the topology in a policy-compliant manner.
-The algorithm for this phase builds on Propane (for concrete networks); we show that it can be extended to abstract inputs.
+The algorithm for this phase builds on \Propane (for concrete networks); we show that it can be extended to abstract inputs.
 %and that the extensions are correct.
@@
 Because finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem,
-Propane introduced a conservative search strategy for determining route preferences.
+\Propane introduced a conservative search strategy for determining route preferences.
 To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:
@@
 
-Figure~\ref{fig:compilation-times} shows total configuration generation time for \sysname vs the concrete network synthesis tool Propane.
+Figure~\ref{fig:compilation-times} shows total configuration generation time for \sysname vs the concrete network synthesis tool \Propane.
 All experiments were run on an 8 core, 2.4 GHz Intel i7 processor machine running Mac with 16GB of Ram.
@@
 In each case, we found the guarantee to hold; for prefix changes, only the originator's configuration changed.
-In contrast, all router configurations were modified with Propane because it heavily uses prefix lists which are sensitive to such changes.
-While Propane may be made friendlier to network evolution (e.g., prefix lists are unnecessary at aggregation routers), its fundamental limitation will remain because it does not understand roles and the network's underlying structure that \sysname leverages.
+In contrast, all router configurations were modified with \Propane because it heavily uses prefix lists which are sensitive to such changes.
+While \Propane may be made friendlier to network evolution (e.g., prefix lists are unnecessary at aggregation routers), its fundamental limitation will remain because it does not understand roles and the network's underlying structure that \sysname leverages.
 
@@
 
-While we borrow much from existing configuration synthesis work, especially Propane~\cite{propane}, our goal is to generate role templates from abstract topologies, rather than router configurations from concrete topologies.
+While we borrow much from existing configuration synthesis work, especially \Propane~\cite{propane}, our goal is to generate role templates from abstract topologies, rather than router configurations from concrete topologies.
 This goal aligns better with operators' mental models and tools and permits network evolution with minimal disruption.

### 2017-03-07 paper/abstraction/paper.tex
adding to section 7

@@
 
+\newcommand{\Con}{\text{con}}
+\newcommand{\Pfx}{\mathit{pfx}}%
+
+\vspace{2em}
+\begin{figure*}[t!]\small%
+
+  \hrulefill%
+
+  \vspace{1em}%
+  \begin{minipage}[t]{.47\linewidth}
+  \hdr{ABGP Syntax}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rclr}
+     d    &   & & \textit{integer} \\
+     c    &   & & \textit{community} \\
+     l    &   & & \textit{location} \\
+     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
+     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
+     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
+     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
+     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
+     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\%
+  \end{array} \]%%
+
+  \end{minipage}
+  %
+  %
+  \begin{minipage}[t]{.49\linewidth}
+  \hdr{Compilation}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{l}
+     \mathrm{compile}_\mathrm{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
+     ~~~~~ [~ l \rightarrow rc ~\vert~ l \in \mathrm{internal}(G.V), ~rc = \mathrm{append}_i~  \\
+     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \mathrm{adjIn}(PG_i,m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathrm{adjOut}(PG_i,m) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \mathrm{ord}_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~] \\
+     \\
+     \mathrm{compile}( p_1, \dots, p_k, G) = \\
+     ~~~~~~ \mathrm{compile}_\mathrm{ABGP}(\mathrm{compile}_\mathrm{PG}(p_1,G), \dots, \mathrm{compile}_\mathrm{PG}(p_k,G), G) \\
+  \end{array} \]%
+  \end{minipage}%
+
+  \vspace{1em}
+  \hrulefill%
+  %\vspace{1em}%
+
+  \caption{Abstract BGP syntax (left), and compilation from product graphs (right).}
+  \label{fig:concretization}
+\end{figure*}%
+
 \section{Template Generation}
@@
 
-The translation from the PG to per-device templates that run the distributed BGP protocol involves several ideas.
-
-\para{Route filtering}
+At a high level, the translation from the PG to per-device templates that run the distributed BGP protocol involves the following high-level ideas: First, BGP messages are tagged to record the state of the product graph as messages are passed between routers.
+This information allows routers to drop messages that do not correspond to any path not permitted.
+Next, we must search for a ranking of messages for each router in the network such that, under those preferences, the network as a whole satisfies the \sysname policy's preferences.
+Finally, templates can be soundly concretized for the actual network by replacing instances of abstract neighbors with the union of all concrete neighbors.
+Finally, by modifying compilation slightly we can further ensure that every configuration depends only on its immediate neighbors.
+This guarantees that any change made to the concrete topology will result in a minimal number of changes.
+
+We look at each of these steps in turn.
+
+\para{Tagging and Filtering}
 
@@
 The concrete configurations have a similar configuration for each local and global prefix.
-
-\newcommand{\Con}{\text{con}}
-\newcommand{\Pfx}{\mathit{pfx}}%
 

### 2017-03-08 paper/abstraction/paper.tex
rewrite tagging section

@@
 
-  \hrulefill%
-
-  \vspace{1em}%
+  %\hrulefill%
+
+  %\vspace{1em}%
   \begin{minipage}[t]{.47\linewidth}
@@
   \begin{minipage}[t]{.49\linewidth}
-  \hdr{Compilation}{}
+  \hdr{Compilation to ABGP}{}
   \vspace*{-1\baselineskip}
@@
 
-At a high level, the translation from the PG to per-device templates that run the distributed BGP protocol involves the following high-level ideas: First, BGP messages are tagged to record the state of the product graph as messages are passed between routers.
-This information allows routers to drop messages that do not correspond to any path not permitted.
-Next, we must search for a ranking of messages for each router in the network such that, under those preferences, the network as a whole satisfies the \sysname policy's preferences.
-Finally, templates can be soundly concretized for the actual network by replacing instances of abstract neighbors with the union of all concrete neighbors.
-Finally, by modifying compilation slightly we can further ensure that every configuration depends only on its immediate neighbors.
-This guarantees that any change made to the concrete topology will result in a minimal number of changes.
-
-We look at each of these steps in turn.
+At a high level, the translation from the PG to per-device templates that run the distributed BGP protocol involves the following high-level ideas: (1) Every BGP message is tagged to record the state of the product graph as messages are passed between routers.
+The tags allow BGP to only search for valid paths in the PG by dropping messages that do not correspond to any edge in the PG.
+(2) To ensure BGP always finds the \emph{most preferred} paths in the network, we must rank messages for each router in the network by giving them a preference such that, under those preferences, the network as a whole satisfies the \sysname policy's end-to-end network preferences.
+(3) We introduce a simple, vendor-independent BGP configuration language called mBGP and describe a compilation function that uses the inferred preference ordering to generate concrete configurations from a concrete topology, or templates from an abstract topology.
+(4) Templates can then be soundly instantiated for a concrete network by replacing instances of abstract neighbors with the union of all concrete neighbors under the homomorphism.
+We prove that concretization and compilation commute.
+(5) By modifying compilation slightly we can further ensure that every configuration depends only on its immediate neighbors.
+This guarantees that any change made to the concrete topology will result in a minimal number of changes to the configurations.
+
+We now look at each of these steps in turn.
 
@@
 
-The first idea is to tag every BGP announcement with a community that encodes the state of each DFA when advertising a route to a neighbor.
-Routers then allow announcements that correspond to an edge in the PG and block others.
-For example, in the concrete PG in Figure~\ref{fig:example-compilation}, router S1 will allow an advertisement from its neighbors N1 and N2.
-If it uses the path advertised by neighbor N1, then it will add the tag $(1,0)$ before sending this to its neighbors.
-If it uses neighbor N2, then it will add the tag $(0,1)$ instead.
+The BGP routing protocol standard allows for the use of \emph{community tags}, collections of 32-bit integer tags that can be attached or removed arbitrarily from routing advertisements. 
+Community tags serve as a simple form of \emph{memory}, and operators routinely use such tags to implement policy (e.g., to prevent transit traffic by recording where a message enters the network and blocking upon egress accordingly).
+
+The idea for template generation is to use community tags to record the state of the automata from the Product Graph in every BGP announcement and update these tags whenever messages are passed between routers.
+Such a tagging mechanism is used to ensure that BGP only considers paths that are allowed by the \sysname policy, routers will allow advertisments that correspond to an edge in the PG and block any advertisments that do not.
+
+For example, in the concrete PG in Figure~\ref{fig:example-compilation}, router S1 appears in two different PG nodes: $(S1,1,0)$ and $(S1,0,1)$.
+These nodes have two different peers than can send them messages in the PG: $(N1,0,0)$ and $(N2,0,0)$.
+Therefore, S1 will not block an advertisement from peer $N1$ and will also not block an advertisement from peer $N2$.
+If S1 uses the path advertised by neighbor N1, then it will add the tag $(1,0)$ to the advertisement before sending this to its neighbors A1 and A2.
+If S1 uses a path advertised from neighbor N2, then it will add the tag $(0,1)$ instead.
+Similarly, router A1 appears in two separate PG nodes.
+It will not block advertisements from S1 if they either have the $(1,0)$ tag or the $(0,1)$ tag attached.
+If A1 chooses a path with tag $(1,0)$ attached, then it will export the path to its neighbors without modifying the tag.
+If A1 chooses a path with tag $(0,1)$ attached, it will also export the path to its neighbors without modifying the tag.
 
 \para{Preference Search}
-The second idea is to have each router totally order advertisements from neighbors.
+
+Tagging and filtering according to the PG with community values in BGP allows the protocol to only search for paths to the destination that are allowed by the policy.
+However, finding \emph{some} path to the destination is not enough.
+We must ensure that each router uses the \emph{best} path to the destination according to the policy.
+Further, this must continue to hold as elements of the network fail.
+To this end, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routers learned from another neighbor.
+
+The idea then is to have each router totally order advertisements from different neighbors (possibly with different tags).
 For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, S1 should prefer a message it hears from N1 over N2.

### 2017-03-08 paper/abstraction/paper.tex
rewrite preference search section

@@
 
-Tagging and filtering according to the PG with community values in BGP allows the protocol to only search for paths to the destination that are allowed by the policy.
+Tagging and filtering according to the PG with community values in BGP forces the protocol to only search for paths to the destination that are allowed by the policy (\IE are paths in the PG).
 However, finding \emph{some} path to the destination is not enough.
-We must ensure that each router uses the \emph{best} path to the destination according to the policy.
-Further, this must continue to hold as elements of the network fail.
-To this end, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routers learned from another neighbor.
-
-The idea then is to have each router totally order advertisements from different neighbors (possibly with different tags).
+We must ensure that each router uses its \emph{best} available path to the destination according to the policy.
+Further, this must continue to hold as additional elements of the network fail.
+In the example from Figure~\ref{fig:example-compilation}, the policy was $\True ~\Path~ \CD{\Exit(N1\Prefer N2)}$, which indicates that paths through N1 should be used whenever possible, and paths through N2 should only be used as a backup.
+If router S1 allows advertisements from both N1 and N2 but does not prefer one advertisement over another, it might end up choosing to use a path through N2 even though a more preferred path through N1 exists and is available\footnote{ties between equally preferred paths can be broken nondeterministic based on message ordering}.
+On the other hand, if the S1-N1 link fails, then the best available path is through N2.
+
+To enforce correct network-wide preferences, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routers learned from another neighbor.
+The challenge is to find a collection of device-local preferences that correctly enforce the network-wide preferences from the policy for all failures.
+
+The idea then is to search for such a device-local preference function for each router that totally order advertisements from different neighbors (possibly with different tags).
 For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, S1 should prefer a message it hears from N1 over N2.
 Similarly, A1 should prefer routes tagged with $(1,0)$ over those with $(0,1)$.
-%In general, because BGP is distributed, each router does not have a full view of the entire network when choosing which path to use.
-Because finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem,
-\Propane introduced a conservative search strategy for determining route preferences.
+Intuitively, S1 should prefer a message from N1 because it results in an accepting state for automata 1, which is more preferred than automata 2.
+Further, it can result in downstream routers such as A1 receiving a message in a more preferred state $(A1,1,0)$ instead of $(A1,0,1)$.
+
+In general, because BGP is distributed, each router does not have a view of the entire network when choosing which path to use and finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem.
+\Propane introduced a conservative search strategy for determining route preferences that works well in practice.
 To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:

### 2017-03-08 paper/abstraction/paper.tex
expand on total ordering inference

@@
 \newcommand{\xmark}{\ding{55}}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 
@@
 
+\begin{algorithm}[t!]
+\caption{Checking safe neighbor preferences}
+\label{alg:failures}
+\begin{algorithmic}[1]
+\Procedure{$\leq$($N_1$, $N_2$)}{}
+  \If {$N_1 \not\approx N_2$} \Return false
+  \EndIf
+  \State $q \gets Queue()$
+  \State $q.Enqueue (N_1, N_2)$
+  \While {$!q.Empty()$}
+    \State $(m,n) \gets q.Dequeue()$
+    \If {$m \nleq_{rank} n$}
+      \Return false
+    \EndIf
+    \For {$n'$ in adjOut($PG$, $n$)}
+      \If {\big($\exists m' \in \textup{adjOut}(PG,m), m' \approx n'$\big)}
+        \If {$(m',n')$ not marked}
+          \State {mark $(m',n')$ as seen}
+          \State $q.Enqueue(m',n')$
+        \EndIf
+      \Else { \Return $false$}
+      \EndIf
+    \EndFor
+  \EndWhile \\
+  \hspace{\algorithmicindent} \Return true
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
 %=====================================================
@@
 In the example from Figure~\ref{fig:example-compilation}, the policy was $\True ~\Path~ \CD{\Exit(N1\Prefer N2)}$, which indicates that paths through N1 should be used whenever possible, and paths through N2 should only be used as a backup.
-If router S1 allows advertisements from both N1 and N2 but does not prefer one advertisement over another, it might end up choosing to use a path through N2 even though a more preferred path through N1 exists and is available\footnote{ties between equally preferred paths can be broken nondeterministic based on message ordering}.
+If router S1 allows advertisements from both N1 and N2 but does not prefer one advertisement over another, it might end up choosing to use a path through N2 even though a more preferred path through N1 exists and is available\footnote{ties between equally preferred paths can be broken nondeterministically}.
 On the other hand, if the S1-N1 link fails, then the best available path is through N2.
@@
 The PG can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge.
-That is, $m\overset{l}{\rightarrow}n$ if edge $(m,n) \in E'$ and $\Topo{n} = l$.
+That is, $m\overset{l}{\rightarrow}n$ if there is an edge $(m,n)$ in the PG and $\Topo{n} = l$.
 %\end{defn}
@@
 
-If we determine that each router has a total order with respect to the simulation relation ($\leq$) for its corresponding PG nodes, then we can simply sort the nodes and prefer advertisements from peers of node $m$ over those of $m'$ whenever $m' \leq m$.
+The existence of multiple nodes in the PG for the same topology location (\EG, $(S1,1,0)$ and $(S1,0,1)$) indicates that S1 can receive advertisements in different contexts and must choose between messages received in these different contexts.
+Node $m$ is preferred to $m'$ if, $m' \geq_{rank} m$ and, transitively, for each neighbor of $m'$, $m$ has a corresponding neighbor that is more preferred.
+Algorithm~\ref{alg:failures} shows a simple procedure for determining if a nPG ode $N1$ can safely be preferred to a PG node $N2$.
+
+For each router, its corresponding PG nodes are then sorted according the the $\leq$ operator.
+If $\leq$ defines a total order on PG nodes, then the compiler can simply prefer advertisements from peers of node $m$ over those of $m'$ whenever $m' \leq m$.
 This condition ensures that BGP devices will converge to the most preferred paths in the network even when failures occur.
+However, if $\leq$ does not form a total order, then the policy is rejected as being potentially unsafe under some failure conditions.
+
 %

### 2017-03-09 paper/propane/SOSR/propane.tex
add sosr extended abstract

--- 2016-06-23 paper/v2/paper-edited.tex
@@
 %\documentclass{sig-alternate-10pt}
-\documentclass[10pt]{sigalternate052015}
+\documentclass[10pt]{acmart}
 
@@
 \usepackage{url}
-\usepackage{times}
 \usepackage{xspace}
-\usepackage{listings}
 \usepackage{code}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{tikz}
-\usetikzlibrary{arrows,automata,positioning}
-\let\proof\relax
-\let\endproof\relax
-\usepackage{amsthm}
-\usepackage{subcaption}
 %\usepackage{geometry}
-
-\usepackage{balance}
+%\usepackage{balance}
 
@@
 
-\setcopyright{acmcopyright}
-\conferenceinfo{SIGCOMM '16}{August 22--26, 2016, Florianopolis, Brazil}
-
-\special{papersize=8.5in,11in}
-\setlength{\pdfpageheight}{\paperheight}
-\setlength{\pdfpagewidth}{\paperwidth}
+%\special{papersize=8.5in,11in}
+%\setlength{\pdfpageheight}{\paperheight}
+%\setlength{\pdfpagewidth}{\paperwidth}
 
@@
 
-\author{%
-Ryan Beckett\\
-  \affaddr{Princeton}
-  %\\
-  %\email{rbeckett@princeton.edu}
-\and
-Ratul Mahajan\\
-  \affaddr{Microsoft}
-  %\\
-  %\email{ratul@microsoft.com}
-\and
-Todd Millstein\\
-  \affaddr{UCLA}
-  %\affaddr{University of California, Los Angeles}
-  %\\
-  %\email{todd@cs.ucla.edu}
-\and
-Jitendra Padhye\\
-  \affaddr{Microsoft}
-  %\\
-  %\email{padhye@microsoft.com}
-\and
-David Walker\\
-  \affaddr{Princeton}
-  %\\
-  %\email{dpw@princeton.edu}
-}
+%\author{%
+%Ryan Beckett\\
+%  \affaddr{Princeton}
+%  %\\
+%  %\email{rbeckett@princeton.edu}
+%\and
+%Ratul Mahajan\\
+%  \affaddr{Microsoft}
+%  %\\
+%  %\email{ratul@microsoft.com}
+%\and
+%Todd Millstein\\
+%  \affaddr{UCLA}
+%  %\affaddr{University of California, Los Angeles}
+%  %\\
+%  %\email{todd@cs.ucla.edu}
+%\and
+%Jitendra Padhye\\
+%  \affaddr{Microsoft}
+%  %\\
+%  %\email{padhye@microsoft.com}
+%\and
+%David Walker\\
+%  \affaddr{Princeton}
+%  %\\
+%  %\email{dpw@princeton.edu}
+%}
 
-\maketitle
+%\maketitle
 
@@
 We show that \sysname can effectively express the policies of datacenter and backbone networks of a large cloud provider;  and despite its strong guarantees, our compiler scales to networks with hundreds or thousands of routers.
-
-%=====================================================
-%
-%
-%  **Keywords**
-%
-%
-%=====================================================
-
-%\category{CR-number}{subcategory}{third-level}
-
-%\begin{CCSXML}
-%<ccs2012>
-%<concept>
-%<concept_id>10003033.10003068.10003073.10003075</concept_id>
-%<concept_desc>Networks~Network control algorithms</concept_desc>
-%<concept_significance>300</concept_significance>
-%</concept>
-%<concept>
-%<concept_id>10003033.10003083.10003095</concept_id>
-%<concept_desc>Networks~Network reliability</concept_desc>
-%<concept_significance>300</concept_significance>
-%</concept>
-%<concept>
-%<concept_id>10003033.10003099.10003104</concept_id>
-%<concept_desc>Networks~Network management</concept_desc>
-%<concept_significance>300</concept_significance>
-%</concept>
-%<concept>
-%<concept_id>10011007.10010940.10010992.10010998.10011000</concept_id>
-%<concept_desc>Software and its engineering~Automated static analysis</concept_desc>
-%<concept_significance>300</concept_significance>
-%</concept>
-%<concept>
-%<concept_id>10011007.10011006.10011050.10011017</concept_id>
-%<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
-%<concept_significance>300</concept_significance>
-%</concept>
-%</ccs2012>
-%\end{CCSXML}
-%
-%\ccsdesc[300]{Networks~Network control algorithms}
-%\ccsdesc[300]{Networks~Network reliability}
-%\ccsdesc[300]{Networks~Network management}
-%\ccsdesc[300]{Software and its engineering~Automated static analysis}
-%\ccsdesc[300]{Software and its engineering~Domain specific languages}
-%
-%\printccsdesc
-%
-%\keywords{Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems}
-
-\vspace{0.1in}
-\noindent
-\textbf{CCS Concepts}\\
-$\bullet$ Networks $\rightarrow$ {\em Network control algorithms; Network reliability; Network management;} 
-$\bullet$ Software and its engineering $\rightarrow$ {\em Automated static analysis; Domain specific languages}
-
-\vspace{0.1in}
-\noindent
-\textbf{Keywords}\\
-Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems
-
-%% general terms are not compulsory anymore,
-%% you may leave them out
-%\terms Network Programming Language, Distributed Program Synthesis
-%\keywords Propane Language, BGP, Synthesis, Compilation
 
@@
 %
-%  **Background**
-%
-%
-%=====================================================
-
-\section{Background on BGP}
-\label{sec:background}
-
-%Our work focuses on BGP as it is the most common and flexible way to implement distributed control planes today. In this section, we provide relevant background on BGP.
-
-BGP is a path-vector routing protocol that connects autonomous systems (ASes).
-An AS has one or more routers managed by the same administrative entity.
-ASes exchange routing announcements with their neighbors.
-Each announcement has a destination IP prefix and some attributes (see below), and it indicates that the sending AS is willing to carry traffic destined to that prefix from the receiving AS.
-Traffic flows in the opposite direction, from announcement receivers to senders.
-
-When a route announcement is received by an AS, it is processed by custom import filters that may drop the announcement or modify some attributes.
-If multiple announcements for the same prefix survive import filters, the router selects the best one based on local policy (see below).
-This route is then used to send traffic to the destination.
-It is also advertised to the neighbors, after processing through neighbor-specific export filters that may stop the announcement or modify some attributes.
-
-All routing announcements are accompanied by an AS-path attribute that reflects the sequence of ASes that the announcement has traversed thus far.
-While the AS-path attribute has a global meaning, some attributes are meaningful only within an AS or between neighboring ASes.
-One such attribute is a list of community strings.
-ASes use such strings to associate network-specific information with particular routes (\EG, ``entered on West Coast'') and then use the information later in the routing process.
-Communities are also used to signal to neighbors how they should handle an announcement (\EG, do not export it further).
-Another non-global attribute is the multi-exit discriminator (MED).
-It is used when an AS has multiple links to a neighboring AS.
-Its (numeric) values signal to the neighbor how this AS prefers to receive traffic among those links.
-
-The route selection process assigns a {\em local preference} to each
-route that survives the import filters. Routes with higher local
-preference are preferred. Among routes with the same local preference,
-other factors such as AS path length, MEDs, and internal routing cost, are considered in order.
-Because it is considered first during route selection, local preference is highly influential, and ASes may assign this preference based on any aspect of the route.
-A common practice is to assign it based on the commercial relationship with the neighbor.
-For instance, an AS may prefer in order customer ASes (which pay money), peer ASes (with free exchange of traffic), and provider ASes (which charge money for traffic).
-
-The combination of arbitrary import and export filters and route selection policies at individual routers make BGP a highly flexible routing protocol.
-That flexibility, however, comes at the cost of it being difficult to configure correctly.
-When configuring BGP, network operators assume that
-neighboring ASes correctly implement BGP and honor contracts for MEDs and communities. \sysname makes the same assumption when
-deriving BGP configurations for a network.
-
-%=====================================================
-%
-%
-%  **Motivation**
-%
-%
-%=====================================================
-
-\section{Motivation}
-\label{sec:motivation}
-
-%We motivate our work by describing the current practice in network
-%configuration.
-In traditional networks with distributed control planes, the operators' goal is to generate the configuration of individual devices based on their desired policy.
-This configuration dictates the behavior of a device, how it exchanges routing information with neighbors and how it filters and ranks that information.
-The collective behavior of the devices should implement the desired policy.
-%
-%Device configuration languages are low-level and indirect.
-For instance, instead of allowing operators to express directly the paths they want through the network, they require operators to specify metrics that result in those paths; instead of allowing operators to express directly the types of traffic to not carry through the network, they require operators to select and program an appropriate filtering mechanism (e.g., BGP import or export filters, null routing,  access control lists) and instantiate it on topologically appropriate devices; instead of allowing operators to directly specify that they prefer BGP neighbors in a certain order, they require operators to program local preferences and multi-exit discriminators (MED) at each router and ensure that the numbers are consistent across routers.
-%
-%In many networks today, device configurations are generated manually by operators, without the support of many automated tools.
-It is easy to see the problems with this approach, such as typos, inconsistency across devices, and no guarantees of policy compliance.
-%
-%To reduce such problems, some networks use a template-based approach.
-Configuration templates abstract certain constants into variables (e.g., instead of concrete community value, they may contain a variable {\small \sf{\$$BadNeighbor$)}} and may use a device vendor-neutral syntax.
-Operators manually generate the templates and use tools to translate them into device configuration, by replacing variables with appropriate constants using a database of network information.
-%
-% %and replacing vendor-neutral constructs with their vendor-specific counterparts.
-%
-%%In practice, most networks use a hybrid of templates and manual generation of device configuration.
-Templates are used for standardized and common configuration elements across devices and the result is manually tweaked to obtain the exact desired network behavior.
-%
-%While templates avoids some pitfalls of the fully manual approach, they too are far from ideal.
-The fundamental issue is the semantic mismatch between desired policies and the level of abstraction of templates.
-While many policies are network-wide (e.g., prefer customer networks, or never announce a route to a certain prefix to external neighbors), templates are device-level.
-Operators must still manually decompose network-wide policies into device-level policies that can produce the desired network-wide behavior.
-%This decomposition is not always straightforward and ensuring policy-compliance can be hard, especially in the face of failures.
-We illustrate this point using two examples based on policies that we have seen in practice and we demonstrate the ease with which the
-%examples are described using our new language \sysname.
-
-%Operators today generate the BGP configuration of individual devices based on intended policy.
-When generating BGP configurations, whether manually or aided by templates, the operators face the challenge of decomposing network-wide policies
-into correct device-level policies.
-This decomposition is not always straightforward and ensuring policy-compliance is tricky, especially in the face of failures.
-In this section, we illustrate this difficulty using two examples based on policies that we have seen in practice.
-The next section shows how \sysname allows operators to express these policies naturally.
-%the ease with which the
-%policies can be specified using our new language \sysname.
-%The next section describes how to automatically compile this specification to device-level policies.
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=\columnwidth]{figures/example1}
-  \caption{Creating router-level policies is difficult.}
-  \label{fig:example1}
-  \vspace{-1em}
-\end{figure}
-
-\subsection{Example 1:  The backbone}
-
-Consider the backbone network in Figure~\ref{fig:example1}. It has
-three neighbors, a customer \CD{Cust}, a peer \CD{Peer}, and a provider \CD{Prov}.
-The policy of this network is shown on the right.
-It prefers that traffic leave the network through neighbors in a certain order (P1) and does not want to act as a transit between \CD{Peer} and \CD{Prov} (P2).
-It prefers to exchange traffic with \CD{Cust} over \CD{R1} rather than \CD{R2} because \CD{R1} is cheaper (P3).
-To guard against another AS "hijacking" prefixes owned by \CD{Cust}, the network only sends traffic to a neighbor if \CD{Cust} is on the AS path (P4).
-Finally, to guard against \CD{Cust} accidentally becoming a transit for \CD{Prov}, it does not use \CD{Cust} for traffic that will later traverse \CD{Prov} (P5).
-
-To implement policy P1, the operators must compute and assign
-local preferences such that preferences at \CD{Cust}-facing interfaces
-$>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
-the same time, to satisfy P3, the preference at \CD{R2}'s
-\CD{Cust}-facing interface should be lower than that at
-\CD{R1}. Implementing P3 will also require MEDs to be appropriately configured on \CD{R1} and \CD{R2}.
-To implement P2, the operators can assign communities that
-indicate where a certain routing announcement entered the
-network. Then, \CD{R4} must be configured to not announce to
-$\CD{Peer}$ routes that have communities that correspond to the
-\CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links.
-A similar type of policy must be configured for \CD{R2} as well.
-Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based import and export filters at each router.
-
-Clearly, it is difficult to correctly configure even this
-small example network manually; correctly configuring real, larger networks can quickly become a nightmare.
-Such networks have hundreds of neighbors spanning multiple commercial-relationship classes, differing numbers of links to each neighbor, along with several neighbor- or prefix-based exceptions to the default behavior.
-A large AS with many peers in different geographic locations may be faced with complex challenges such as keeping traffic within national boundaries.
-Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually.
-%\sysname lets operators express such policies easily and intuitively.
-It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=\columnwidth]{figures/example2}
-  \caption{Policy-compliance under failures is difficult.}
-  \label{fig:example2}
-  \vspace{-1em}
-\end{figure}
-
-\subsection{Example 2:  The datacenter}
-
- While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible.
-Consider the datacenter network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, datacenter networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally.
-This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally.
-Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}.
-The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.
-
-The operator may implement the policy by having X and Y: $i)$ not export externally what they hear from G and H, routers that belong to the local services cluster; and $ii)$ export externally what they hear from routers C and D and aggregate to \CD{PG} if an announcement is subset of \CD{PG}.
-This implementation is appealing because X and Y do not need to be made aware of which prefixes are global versus local and IP address assignment can occur independently, \EG, local services can be assigned new prefixes without updating those routers' configurations.
-
-However, this implementation has incorrect behavior in the face of failures.
-Suppose links X--G and X--H fail.
-Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D.
-Per its policy implementation, X will start "leaking" these prefixes externally.
-Depending on the rationale for local services, this leak could impact security (\EG, if the services are sensitive) or availability (\EG, if the \CD{PL*} prefixes are reused for other services outside of the datacenter).
-This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter.
-A similar problem will occur if links Y--G and Y--H fail.
-%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
-Link failures in datacenters are frequent and it is not uncommon to have many failed links at a given time~\cite{dc-failure-study}.
-
-To avoid this problem, the operator may disallow "valley" paths, \IE, those that go up, down, and back up again.
-This guard can be implemented by $X$ and $Y$ rejecting paths through the other.
-But that creates a different problem in the face of failures---an aggregation-induced black hole~\cite{route-aggregation}.
-If links D--A and X--C fail, X will hear an announcement for \CD{PG2} from D and will thus announce \CD{PG} externally.
-This announcement will bring traffic for \CD{PG1} to X as well, but because valleys are disallowed, X does not have a valid route for \CD{PG1} and will drop all traffic for it despite the fact that a valid path exists through $Y$.
-
-Thus, we see that devising a configuration that ensures policy compliance in the face of failures is complex and error-prone.
-\sysname lets operators implement their high-level policy specification in a way that guarantees compliance under all failures if possible---otherwise, it generates a compile-time error.
-For aggregation, it also provides a lower bound to operators on the number of failures under which aggregation will not result in black holes.
-
-%\subsection{OLD -- Overview}
-%\todo{this subsection can be deleted once we have captured everything in it}
-%
-%Sources of bugs we fix. (It seems like the main advantage of our approach is not just fixing bugs though - it is easily describing high-level intention).
-%Perhaps the best way to do this is by going through a bunch of examples in section 2 and showing how you could easily introduce bugs:
-%
-%\begin{itemize}
-% \item Out of sync, or copy paste errors due to replicated configs (never an issue due to centralized control)
-% \item Correct filtering to ensure no undesired traffic can flow through the network (e.g., best practices, like an AS should filter customers for their prefix, are implemented automatically )
-% \item Failures can easily lead to unexpected behavior (e.g., a datacenter failure scenario w/instability.)
-% \item Trying to do anything interesting, like get backups correct is difficult (e.g., setting up aggregation wrong)
-% \item Related to the last point, things like aggregation can introduce black holes. We have the information needed to prevent this
-%\end{itemize}
-%
-%
-%Possible Examples:
-%\begin{itemize}
-% \item Basic datacenter with spine preference
-% \item Simple AS that prefers customers over peers over providers
-% \item Combined internal backup routing with preference based entrance into the network using aggregation.
-% \item Something like cold potato routing
-%\end{itemize}
-
-%=====================================================
-%
-%
-%  **Propane Language**
-%
-%
-%=====================================================
-
-\section{Propane overview}
-\label{sec:propane}
-
-Policies for (distributed) control planes differ from data-plane
-policies in a few important ways. First, they must account for all failures at compile time; there is
-no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
-%
-In \sysname, we enable such specifications through {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
-%
-Second, paths in a control-plane policy may be under-specified (\EG,
-"prefer customer" does not indicate a concrete path). The \sysname
-compiler treats such under-specifications as constraints on the set of
-allowed paths and automatically computes valid sets based on the topology.
-%
-
-This section introduces the \sysname language using the
-examples from the previous section.
-%, introducing key aspects of
-%the \sysname language along the way.
-The next section describes the complete syntax of the
-language as well as our strategy for compiling it to
-BGP.
-
-\subsection{Example 1: The backbone}
-
-%\sysname simplifies network configuration by allowing users to
-%specify end-to-end forwarding paths and associating them with
-%appropriate prefixes.  The \sysname compiler handles the task of
-%generating low-level BGP configurations consistent with the user's
-%specifications.  It automatically synthesizes
-%import-export filters, local preferences, MED attributes, and community tags
-%to ensure policy compliance under all possible failure scenarios.
-
-\sysname lets operators configure the network with the
-abstraction that they have centralized control over routing.
-Specifically, the operator simply provides a set of high-level constraints
-that describe the
-paths traffic should---or should not---take and their relative preferences.
-\sysname specifications are written modularly via a series
-of declarations.
-%These definitions allow users to express the three
-%major elements of any \sysname specification:  \emph{prefixes},
-%\emph{paths} and \emph{policies}.
-For example, to begin specification of the backbone
-network from the previous section, we first express the idea that
-we prefer that traffic leave the network through \CD{R1} over \CD{R2} (to \CD{Cust}) over \CD{Peer} over \CD{Prov} (policy P1 and P3 from Figure~\ref{fig:example1}):
-%\begin{lstlisting}[mathescape=true]
-%define ExitCust = $exit(R_1 \gg R_2)$
-%\end{lstlisting}
-\begin{code}
-\Define Prefs = \Exit(R1 \Prefer R2 \Prefer Peer \Prefer Prov)
-\end{code}
-This  statement defines a set of \emph{ranked paths}, which includes
-all paths (and only those paths) for which traffic exits our network
-through either router \CD{R1}, router \CD{R2}, \CD{Peer}, or \CD{Prov}.
-The paths that exit through \CD{R1}
-are preferred (\Prefer) to those that exit through \CD{R2}, which are preferred to those that
-leave through \CD{Peer} and then \CD{Prov}.  As we
-describe in the next section, the \Exit\ expression, as well as other
-path expressions used later in this section, is simply a shorthand for
-a particular regular expression over paths that is expressible in our policy
-language.
-The preference operator (\Prefer) is flexible and can be used between constraints as well as among individual routers.
-For example, the above constraint could have been written equivalently as
-\Exit(\CD{R1}) \Prefer \ldots \Prefer ~\Exit(\CD{Prov})
-
-To associate ranked paths with
-one or more prefixes, we define a \sysname \emph{policy}.
-Within a policy, statements with the form $t\;$\Path$\;p$
-associate the prefixes defined by the predicate $t$ with the set of
-ranked paths defined by the path expression $p$.  In general,
-prefix predicates can be defined by arbitrary boolean combinations
-(and, or, not) of concrete prefixes and community tags.  Here,
-we assume we have already defined the predicate \CD{PCust} for the
-customer prefixes.
-%and \CD{PInt} for our internal prefixes.
-In the following code, ranked paths are associated with
-customer prefixes,
-and all other prefixes (\CD{true}). Policy statements are processed in
-order with earlier policy statements taking precedence over later
-policy statements. Hence, when the predicate \True{} follows
-the statement involving \CD{PCust}, it is interpreted as
-\CD{\True{} \AND{} \NOT{}PCust}.
-
-%% \begin{lstlisting}[mathescape=true]
-%% define Routing = {
-%%     $\path{C_{pfx}}{ExitCust \gg end(Cust)}$
-%%     $\path{I_{pfx}}{end(in)}$
-%%     $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
-%% }
-%% \end{lstlisting}
-
-\begin{code}
-\Define Routing =
-    \{PCust \Path Prefs \AND \End(Cust)
-     \True  \Path Prefs \}
-\end{code}
-\noindent
-
-Line 2 of this policy
-restricts traffic destined to known customer prefixes (\CD{PCust}) to only follow paths that end at the customer.
-In addition, it enforces the network-wide preference that traffic leaves through \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
-%defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
-%that connections to the customer through both routers fail,
-%a backup route (\CD{\End(Cust)}) is defined that admits traffic along
-%any path (including those through other networks) that ends at the customer.
-%Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.
-Line 3 applies to any other traffic not matching \CD{PCust} and allows the traffic to leave through any direct neighbor with the usual preferences of \CD{R1} over \CD{R2} over \CD{Peer} over \CD{Prov}.
-To summarize our progress, the \CD{Routing} policy
-implements P1, P3, and P4 from Figure~\ref{fig:example1}.
-
-Since, routing allows transit traffic by default (\EG, traffic entering from
-\CD{Peer} and leaving through \CD{Prov}), we separately define a
-policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
-disjunction (\OR) and negation (\NOT) of constraints.
-First, we create reusable abstractions for describing traffic that transits our network. In \sysname, this is done by creating a new parameterized definition.
-\begin{code}
-\Define transit(X,Y) = \Enter(X{\OR}Y) \AND \Exit(X{\OR}Y)
-\Define cust-transit(X,Y) = \Later(X) \AND \Later(Y)
-\end{code}
-\noindent
-Here we define transit traffic between groups of neighbors $X$ and $Y$ as traffic that enters the network through some neighbor in $X$ or $Y$ and then also leaves the network through some neighbor in either $X$ or $Y$.
-Similarly, we define customer transit for customer $X$ and provider $Y$ as traffic that later goes through both $X$ and $Y$ after leaving our network.
-Using these two new abstractions, we can now implement policies P2 and P5 with the following constraint.
-
-\begin{code}
-\Define NoTrans =
-  \{\True \Path \NOT{}transit(Peer,Prov) \AND
-           \NOT{}cust-transit(Cust,Prov)\}
-\end{code}
-\noindent
-The \CD{NoTrans} constraint requires that all traffic not follow a path that transits the network between \CD{Peer} and \CD{Prov}.
-Additionally, it prevents traffic from ever following paths that leave our network and later go through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
-and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
-%
-%% \begin{lstlisting}[mathescape=true]
-%% Routing $\AND$  NoTransit
-%% \end{lstlisting}
-%
-
-Collectively, the constraints above capture the entire policy. From them, our compiler will generate per-device import and export filters, local preferences,
-MED attributes, and community tags to ensure that the policy is
-implemented correctly under all failures.
-
-\subsection{Example 2: The datacenter}
-
-Our datacenter example network has three main concerns:
-(1) traffic for the prefix allocated to each top-of-rack router must be able to reach that router,
-(2) local services must not leak outside the datacenter, and
-(3) aggregation must be performed on global prefixes to reduce churn
-in the network.
-
-\sysname allows modular specification of each of these constraints.
-The first constraint is about prefix ownership---we want traffic only for certain prefixes to end up at a particular location.
-The following definition captures this intent.
-
-%% \begin{lstlisting}[mathescape=true]
-%% define Ownership = {
-%%     $\path{p_{g1}}{end(A)}$
-%%     $\path{p_{g2}}{end(B)}$
-%%     $\path{p_{l1}}{end(E)}$
-%%     $\path{p_{l2}}{end(F)}$
-%% }
-%% \end{lstlisting}
-
-\begin{code}
-\Define Ownership =
-    \{PG1 \Path \End(A)
-     PG2 \Path \End(B)
-     PL1 \Path \End(E)
-     PL2 \Path \End(F)
-     \True \Path \End(\Out)\}
-\end{code}
-\noindent
-This definition says that traffic for prefix \CD{PG1} is allowed to follow only paths that
-end at router \CD{A}; traffic for \CD{PG2},
-but not \CD{PG1}, must
-end at router \CD{B}; and so on.
-Any traffic destined for a prefix that is not a part of the datacenter should be allowed to leave the datacenter and end at some external location, which is otherwise unconstrained.
-The special keyword \Out{} matches any location outside the datacenter network, while the keyword \In{} will match any location inside the network.
-
-For the second constraint, we define another policy:
-
-%% \begin{lstlisting}[mathescape=true]
-%% define Routing = {
-%%     $\path{p_{g*}}{any}$
-%%     $\path{p_{l*}}{\NOT enter(out)}$
-%%     $\path{true}{exit(out)}$
-%% }
-%% \end{lstlisting}
-\begin{code}
-\Define Locality =
-    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
-\end{code}
-\noindent
-%The first line states that there is no restriction (\Any)
-%on how traffic must traverse the network for global prefixes.
-%aside from the default restriction
-%that traffic must not pass through the user's network and then loop
-%back on itself.
-%This means traffic for
-%\CD{PG*} may be sent either from other datacenter routers or
-%from external ASes.
-This definition says that traffic for local
-prefixes only follows paths that are internal to the network at each hop.
-This constraint guarantees that the services remain accessible only to locations
-inside the datacenter.
-
-As in the backbone example, we can logically conjoin these constraints
-to specify the network-wide policy.
-However, in addition to constraints on the shape of paths,
-\sysname allows the operator to specify constraints on the BGP control plane itself.
-For instance, a constraint on aggregation is included to ensure that
-aggregation for global prefixes is performed from
-locations inside (\In) the network to locations outside (\Out).
-In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG}
-(which we assume is defined earlier)
-when advertised outside the datacenter.
-
-\begin{code}
-Ownership \AND{} Locality \AND{} \Agg(PG, \In \Link \Out)
-\end{code}
-
-Once \sysname compiles the policy, it is guaranteed to remain compliant under all possible failure scenarios, modulo any aggregation-induced black holes.
-In the presence of aggregation, the \sysname compiler will also efficiently find a lower bound on the number of failures required to create an aggregation-induced black hole.
-
-%%%%OLD TEXT BELOW
-%
-%\section{Propane}
-%\label{sec:propane}
-%
-%\sysname simplifies network configuration by automatically generating low-level BGP configurations from a high-level specification of the network's routing policy.
-%%
-%The operator configures the network with the abstraction that he or she has centralized control over routing and uses a set of high-level constraints to describe the different routes traffic may (or may not) take and their relative preferences.
-%%
-%The \sysname compiler generates BGP configurations for each device in the network that operate in a completely distributed fashion and are correct by construction -- automatically synthesizing import/export filters, local preference and MED attributes, and community tags to ensure policy compliance under all possible failure scenarios.
-%%
-%We now demonstrate \sysname by showing how to configure the networks from the previous examples.
-%
-%\para{Example 1}
-%
-%We now show how to write the routing policy for the backbone network in Section~\ref{sec:motivation}.
-\sysname allows to address each of the requirements in turn.
-First we address requirements (P1), (P3), and (P4) that customers are preferred over peers over providers, and that a customer appear on the path for its prefix.
-The following \sysname code accomplishes these two objectives:
-%
-%\begin{lstlisting}[mathescape=true]
-%define ExitCust = $exit(R_1 \gg R_2)$
-%
-%define Routing = {
-%    $\path{C_{pfx}}{ExitCust \gg end(Cust) }$
-%    $\path{I_{pfx}}{end(in)}$
-%    $\path{true}{ExitCust \gg exit(Peer) \gg exit(Prov)}$
-%}
-%\end{lstlisting}
-%
-%The first definition defines paths that exit our network to the customer.
-The statement $exit(R_1 \gg R_2)$ restricts us to paths that leave our network through either router $R_1$ or $R_2$, with a preference for $R_1$.
-%The first line of the \textsf{Routing} policy ensures that traffic destined for customer prefixes ($C_{pfx}$) either leaves the network directly to the customer (with a preference for leaving through $R_1$), or simply ends at the customer.
-Not leaving directly to the customer by going through \textit{Peer} or \textit{Prov} is less preferred than leaving directly, and thus serves as a backup route in a direct route is not available.
-%
-%The second line state that traffic for internal prefixes $I_{pfx}$ must end in our network, and is otherwise unconstrained.
-The last line applies to any other traffic, and allows for any routes that leave through a peer with a preference for customers over peers over providers.
-While this still allows transit traffic (e.g., traffic can enter from \textit{Peer} and leave through \textit{Prov}), we can restrict this behavior separately as follows:
-%
-%\begin{lstlisting}[mathescape=true]
-%define PP = Peer or Prov
-%define PPTransit = $enter(PP) \wedge exit(PP)$
-%define CustTransit = $later(Cust) \wedge later(Prov)$
-%
-%define NoTransit = {
-%    $\path{true}{\neg PPTransit \wedge \neg CustTransit}$
-%}
-%\end{lstlisting}
-%
-%The \textsf{NoTransit} constraint above ensures that requirements (P2) and (P5) are satisfied.
-In particular, it says that, for any prefix, traffice should never both enter and exit the network from \textit{Peer} or \textit{Prov}.
-Similarly it prevents traffic from ever following paths that leave our network and later go through both \textit{Prov} and \textit{Cust}.
-%
-%\begin{lstlisting}[mathescape=true]
-%Routing $\wedge$  NoTransit
-%\end{lstlisting}
-%
-%The final policy is simply the conjunction of the routing and no transit constraints.
-\sysname will generate per-device import and export filters, local preferences and MED attributes, and community tags to ensure that the policy is met under all failure scenarios.
-%
-%
-%\para{Example 2}
-%
-%Consider again the datacenter from Section~\ref{sec:motivation}.
-In this example, there are primarily three main concerns: (1) traffic for the prefix block allocated to each top-of-rack router can reach that router, (2) local services do not leak outside the datacenter, and (3) aggregation is performed on global prefixes to reduce churn in the network.
-%
-%\sysname allows us to decompose and specify each of these constraints in a modular fashion.
-The first constraint is about prefix ownership -- namely, that we only want traffic for certain prefixes to end up at a particular locations.
-The following definition in propane captures this intent:
-%
-%\begin{lstlisting}[mathescape=true]
-%define Ownership = {
-%    $\path{p_{g1}}{end(A)}$
-%    $\path{p_{g2}}{end(B)}$
-%    $\path{p_{l1}}{end(E)}$
-%    $\path{p_{l2}}{end(F)}$
-%}
-%\end{lstlisting}
-%
-%The constraints in the ownership task are read in a top-down fashion.
-Traffic for prefix $p_{g1}$ is only allowed to to follow paths that end at router A.
-Similarly, traffic not matching $p_{g1}$, but which matches $p_{g2}$ must end at router B and so on.
-%%
-%To capture the second constraint, we can define another task for the core routing policy:
-%
-%\begin{lstlisting}[mathescape=true]
-%define Routing = {
-%    $\path{p_{g*}}{any}$
-%    $\path{p_{l*}}{\neg enter(out)}$
-%    $\path{true}{exit(out)}$
-%}
-%\end{lstlisting}
-%
-%The first line states that there is no restriction on how traffic must traverse the network for global prefixes.
-This means traffic for $p_{g*}$ may be sent either from other routers in the datacenter, or from external ASes.
-The second line ensures that traffic for local prefixes never enters the network from an outside location.
-This  guarantees that the services remain reachable only to locations internal to the datacenter.
-%
-%Finally, we can combine these constraints logically to specify the network-wide policy:
-%
-%\begin{lstlisting}[mathescape=true]
-%Ownership $\wedge$ Routing $\wedge$ agg($p_{agg}$, $in \rightarrow out$)
-%\end{lstlisting}
-%
-%
-%In addition to constraints on the shape of paths, \sysname allows the operator to specify constraints on the BGP control plane.
-Above, a constraint on aggregation is included to ensure that an aggregation for $p_{agg}$ is performed from locations inside the network to locations outside the network.
-%
-%Once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. Similarly, it can check for aggregate-induced black holes up to $k$ failures.
-%
-
-%=====================================================
-%
-%
-%  **Compilation**
-%
-%
-%=====================================================
-
-\section{Compilation}
-\label{sec:compilation}
-
-The examples above use what we call the front end (FE) of \sysname.
-It simplifies operators' task of describing preferred paths, but that simplicity comes at the cost of compilation complexity.
-The compiler must efficiently compute the sets of paths represented by the intersection of preferences and topology and ensure policy compliance under all failure scenarios.
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=.75\columnwidth]{figures/pipeline}
-  \caption{Compilation pipeline stages for Propane.}
-  \label{fig:pipeline}
-  \vspace{-1em}
-\end{figure}
-
-% grammar
-\newcommand{\BNFALT}{\;\;|\;\;}
-\newcommand{\hdr}[2]{\flushleft \chdr{\hspace{5mm}#1}{#2}}
-\newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}
-
-\begin{figure*}[t]\small
-  \begin{minipage}[t]{.45\linewidth}
-  \hdr{Syntax}{}
-  \vspace*{-1\baselineskip}
-  %
-  \[ \begin{array}{rclr}
-    \hline
-
-     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
-     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
-     x       &::=& d.d.d.d/d & \textit{prefix} \\
-     t       &::=& \True & \textit{true} \\
-         &\BNFALT& \NOT t & \textit{negation} \\
-         &\BNFALT& t_1 \OR{} t_2 & \textit{disjunction} \\
-         &\BNFALT& t_1 \AND{} t_2 & \textit{conjunction} \\
-         &\BNFALT& \textit{prefix} = x & \textit{prefix test} \\
-         &\BNFALT& \textit{comm} = d & \textit{community test} \\
-     r       &::=& l & \textit{location} \\
-         &\BNFALT& \emptyset & \textit{empty set} \\
-         &\BNFALT& \In & \textit{internal loc} \\
-         &\BNFALT& \Out & \textit{external loc} \\
-         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
-         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
-         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
-         &\BNFALT& \NOT r & \textit{path negation} \\
-         &\BNFALT& r^* & \textit{iteration} \\
-     ln       &::=& r_1 \rightarrow r_2 & \textit{links} \\
-     cc     &::=& agg(x, ln) \BNFALT tag(d, t, ln) & \textit{control constraints} \\
-  \end{array} \]
-
-  \end{minipage}
-  %
-  ~~
-  \vrule
-  ~~
-  %
-  \begin{minipage}[t]{.5\linewidth}\small
-  \hdr{Propane Expansions}{}
-  \vspace*{-1\baselineskip}
-  %
-  \[\begin{array}{rcl}
-    \hline
-    \Any           & = & \Out^* \cdot \In^+ \cdot \Out^* \\
-    \None          & = & \emptyset \\
-    \Internal      & = & \In^+ \\
-    \Only(X)       & = & \Any \cap X^* \\
-    \Never(X)      & = & \Any \cap (!X)^* \\
-    \Through(X)    & = & \Out^* \cdot \In^* \cdot X \cdot \In^* \cdot \Out^* \\
-    \Later(X)      & = & \Out^* \cdot (X \cap \Out) \cdot \Out^* \cdot \In^+ \cdot \Out^* \\
-    \Before(X)     & = & \Out^* \cdot \In^+ \cdot \Out^* \cdot (X \cap \Out) \cdot \Out^* \\
-    \End(X)        & = & \Any \cap (\Sigma^* \cdot X) \\
-    \Start(X)      & = & \Any \cap (X \cdot \Sigma^*) \\
-    \Exit(X)       & = & (\Out^* \cdot \In^* \cdot (X \cap \In) \cdot \Out \cdot \Out^*) \cup \\
-                  &        & (\Out^* \cdot \In^+ \cdot (X \cap \Out) \cdot \Out^*) \\
-    \Enter(X)      & = & (\Out^* \cdot \Out \cdot (X \cap \In) \cdot \In^* \cdot \Out^*) \cup \\
-                  &        & (\Out^* \cdot (X \cap \Out) \cdot \In^+ \cdot \Out^*) \\
-    \LinkKW(X,Y)     & = & \Any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
-    \PathKW(\vec{X}) & = & \Any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
-    \Novalley(\vec{X}) & = & \Any ~ \cap \\
-                  &   & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
-                  &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
-  \end{array} \]
-
-  \end{minipage}
-
-  \hrulefill
-
-  \caption{Regular Intermediate Representation (RIR) syntax (left), and
-           Propane language expansions (right).}
-  \label{fig:rir-syntax}
-  %\vspace{-1em}
-\end{figure*}
-
-To handle these challenges, we decompose compilation into multiple stages, shown in  Figure~\ref{fig:pipeline}, and develop efficient algorithms for the translation between stages.
-The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR).
-Policies in RIR are checked well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the topology to obtain the Product Graph Intermediate Representation (PGIR).
-The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions.
-We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes.
-Once the compiler determines safety, it translates the PGIR to an abstract BGP (ABGP) representation.
-ABGP can then be translated into various vendor-specific device
-configurations as needed.
-%The \sysname compiler currently generates
-% Quagga router configurations from ABGP.
-
-\subsection{Regular IR (RIR)}
-\label{sec:rir}
-
-%\para{Syntax}
-The \sysname FE is just a thin layer atop the RIR for describing preference-based path constraints.
-Figure~\ref{fig:rir-syntax} shows the RIR syntax.
-A policy has one or more constraints.
-The first kind of constraint is a test on the type of route and a corresponding set of preferred regular paths or a control constraint.
-Regular paths are regular expressions where the base characters are abstract locations representing either a router or an external AS.
-Special \In{} and \Out{} symbols refer to any internal or external location respectively.
-In addition, $\Sigma$ refers to any symbol.
-We also use the standard regular expression abbreviation $r^+$ for $r \cdot r^*$, a sequence of one or more occurrences of $r$.
-Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisements with a particular community value (\IE, an integer value associated with a path).
-%% For example, the constraint
-%% \[(\textit{prefix}=74.3.28.0/24) \Link \\
-%% (as200 \cdot \In^+) \Prefer (as100 \cdot \In^+)
-%% \]
-%% describes a more-preferred set of paths for traffic announced by a prefix no less specific than \CD{74.125.28.0/24}, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same.
-The plus operator $\In^+$ stands for $\In \cdot \In^*$, at least one internal hop.
-Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.
-
-\sysname also supports constraints on the control-plane behavior of BGP.
-For example, prefix aggregation is an important optimization to reduce routing table size.
-A constraint of the form $agg(x,ln)$ tells the compiler to perform aggregation for prefix $x$ across all links described by $ln$.
-It is also often useful to be able to add community tags to exported routes in BGP (\EG, to communicate non-standard information to peers).
-A constraint of the form $tag(d,t,ln)$ adds community tag $d$ for any prefixes matching $t$ across links $ln$.
-%% Aggregation, for example, from internal to external locations, is specified using the same regular syntax as before:
-%% $$\Agg(128.17.0.0/16, \In \Link \Out)$$
-%% where the expression $\In \Link Out$ refers to control messages flowing from any internal to any external location.
-We list only the route aggregation and community tagging constraints in Figure~\ref{fig:rir-syntax}, but \sysname also supports other constraints such as limiting the maximum number of routes allowed between ASes, or enabling BGP multipath.
-
-\para{Semantics}
-
-We give a semantics to RIR programs using sets of ranked paths.
-Each path constraint $r_1 \Prefer \dots \Prefer r_j$ denotes a set of ranked network paths.
-A network path is a topologically valid string of abstract locations $l_1 l_2 \dots l_k$.
-We use the notation $\abs{p}$ to denote the length of the path $p$.
-A regular expression $r$ matches path $p$, if $p \in \mathcal{L}(r)$, that is, the path is in the language of the regular expression.
-Paths are ranked lexicographically according to (1) the most preferred regular expression matched, and (2) as a tie breaker, the path length.
-Lower ranks indicate \emph{more} preferred paths.
-More formally, a path $p$ has rank:
-$$(\min_i \set{ p \in \mathcal{L}(r_i) }, \abs{p})$$
-%
-The set of ranked paths depends on which paths are valid in the topology, and thus when failures occur, the most preferred routes change.
-%
-For any source $s$ and destination $d$, \sysname will send traffic along the highest ranked available path from $s$ to $d$.
-
-%Traffic may be sent on any of the most preferred paths for each pair of starting and ending locations that appear in some specified path.
-There is an implicit lowest preference $\emptyset$ to drop traffic when no other route is possible.
-
-%The \sysname compiler ensures that generated configurations for a policy always achieve the most preferred path possible given the failures in the topology, using only distributed mechanisms.
-
-\para{From FE to RIR}
-
-The first stage in \sysname compilation reduces the FE to the simpler RIR from Figure~\ref{fig:rir-syntax}.
-The main differences between the FE and RIR are: $i)$ FE allows the programmer to specify constraints using a series of (modular) definitions, and combine them later, $ii)$ FE provides high-level names that abstract sets of routes and groups of prefixes/neighbors, and $iii)$ FE allows the preference operator to be used more flexibly.
-
-A key constraint when translating FE to RIR is ensuring that all specified routes are well-formed.
-In particular, each regular path constraint $r$ must satisfy $r \subseteq \Out^* \cdot \In^+ \cdot \Out^*$.
-It ensures that users only control traffic that goes through their network at some point, and that such traffic does not loop back multiple times through their network.
-
-The translation from FE to RIR is based on a set of rewriting rules.
-The first step merges separate constraints.
-It takes the cross product of per-prefix constraints, where logical conjunction ($r_1 ~\AND~ r_2$) is replaced by intersection on regular constraints ($r_1 \Intersect r_2$), logical disjunction is replaced by union, and logical negation ($\NOT r$) is replaced by path negation ($\Any \cap \NOT(r)$).
-The additional constraint $\Any$ ensures the routes are well-formed by restricting the paths to only those that go through the user's network.
-%
-For example, in the datacenter FE configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:
-
-%% \begin{lstlisting}[mathescape=true]
-%% $\path{p_{g1}}{any \cap end(A)}$
-%% $\path{p_{g2}}{any \cap end(B)}$
-%% $\path{p_{l1}}{\neg enter(out) \cap end(E)}$
-%% $\path{p_{l2}}{\neg enter(out) \cap end(F)}$
-%% $\path{true}{exit(out)}$
-%% \end{lstlisting}
-
-\begin{code}
-PG1 \Path \End(A)
-PG2 \Path \End(B)
-PL1 \Path \textbf{only}(\In) \Intersect \End(E)
-PL2 \Path \textbf{only}(\In) \Intersect \End(F)
-\True \Path \Exit(\Out)
-\end{code}
-
-The next step rewrites the high-level constraints such as $\Enter$ according to the equivalences in Figure~\ref{fig:rir-syntax}.
-Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression.
-For example, the regular expression $r \cdot (s \Prefer t) \cdot u$ is lifted to $(r \cdot s \cdot u) \Prefer (r \cdot t \cdot u)$ by distributing the preference over the sequence operator.
-In general, we employ the following distributivity equivalences:
-%
-\[
-\begin{array}{c}
-  r \odot (s_1 \Prefer \dots \Prefer s_n) = (r \odot s_1) \Prefer \dots \Prefer (r \odot s_n) \\
-  (s_1 \Prefer \dots \Prefer s_n) \odot r = (s_1 \odot r) \Prefer \dots \Prefer (s_n \odot r)
-\end{array}
-\]
-%
-where $\odot$ stands for an arbitrary regular binary operator, and $r$ is a policy with a single preference.
-%
-In cases where $r$ does not contain a single preference, such as $(s ~\Prefer~ t) \cdot (u ~\Prefer~ v)$, it is not clear which of the paths $s \cdot v$ or $t \cdot u$ is preferred.
-\sysname rejects such ambiguous policies, requiring instead that operators explicitly specify which paths to prefer --- for example as $(s \cdot u) ~\Prefer~ (s \cdot v) ~\Prefer~ (t \cdot u) ~\Prefer~ (t \cdot v)$.
-%
-Policies that contain preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) are also rejected by \sysname as invalid.
-
-\newcommand{\state}[4]{\node[state,#3](#1)[#4]{#2};}
-\newcommand{\transition}[4]{\path[->] (#1) edge [#4] node {#3} (#2);}
-
-\begin{figure*}[t!]
-  \begin{minipage}[t]{.5\linewidth}
-
-  \hdr{Topology}{}
-  \vspace*{-2\baselineskip}
-
-  \includegraphics[width=.6\columnwidth]{figures/topology}
-
-  \hdr{Policy Automata}{}
-  \vspace*{-0.5\baselineskip}
-
-  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.4cm,minimum size=1cm]
-    \state{0}{$0$}{              }{}
-    \state{1}{$1$}{right of=0}{}
-    \state{2}{$2$}{right of=1}{}
-    \state{3}{$3$}{right of=2}{}
-    \state{4}{$4$}{right of=3}{}
-    \state{5}{$5$}{right of=4}{accepting}
-    \transition{0}{1}{out}{}
-    \transition{1}{2}{D}{}
-    \transition{2}{3}{C}{}
-    \transition{3}{4}{A}{}
-    \transition{4}{5}{W}{}
-  \end{tikzpicture}
-
-  \vspace*{0.5em}
-
-  \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=1.6cm]
-    \state{0}{$0$}{              }{}
-    \state{1}{$1$}{right of=0}{}
-    \state{2}{$2$}{right of=1}{}
-    \state{3}{$3$}{right of=2}{}
-    \state{4}{$4$}{right of=3}{accepting}
-    \transition{0}{1}{out}{}
-    \transition{1}{2}{in}{}
-    \transition{2}{2}{A,C,D,E}{loop above}
-    \transition{2}{3}{B}{}
-    \transition{3}{3}{B}{loop above}
-    \transition{3}{2}{A,C,D,E}{bend left}
-    \transition{3}{4}{W}{}
-  \end{tikzpicture}
-  \end{minipage}
-  %
-  ~~
-  ~~
-  %
-  \begin{minipage}[t]{.5\linewidth}
-  \hdr{Product Graph IR}{}
-  \vspace*{-1\baselineskip}
-  %
-  \includegraphics[width=.8\columnwidth]{figures/productgraph}
-  \end{minipage}
-
-  \hrulefill
-  \vspace*{.4em}
-
-  \caption{Product graph construction for policy $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$.}
-  \label{fig:example-compilation}
-  %\vspace{-1em}
-\end{figure*}
-
-\subsection{Product graph IR}
-
-Now that the user policy exists in a simplified form, we must consider the topology.
-In particular, we want a compact representation that describes all the possible ways BGP route announcements can flow through the network subject to the policy and topology constraints.
-The PGIR captures these constraints by ``intersecting" each of the regular automata corresponding to the RIR path preferences with the topology.
-Paths through the PGIR correspond to real paths through the topology that satisfy the user constraints.
-
-%Finding paths through a graph subject to regular constraints has been studied extensively in the database literature~\ref{bib:todo}, and has been applied to networks in the past~\ref{bib:todo}.
-
-\para{Formal definition}
-
-% Formally define automata
-%The RIR policy is an ordered sequence of regular expressions $r_1 \Prefer \dots \Prefer r_j$.
-While paths in an RIR policy describe the direction traffic flows through the network, to implement the policy with BGP we are concerned about the way control-plane information is disseminated --- route announcements flowing in the opposite direction.
-To capture this idea, for each regular expression $r_i$ in an RIR policy, we construct a deterministic finite state machine for the reversed regular expression.
-An automata for regular expression $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ consists of all abstract locations (\IE, routers or ASes), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
-%
-% Formally define topology
-The topology is represented as a graph ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$.
-%
-% Formally define product graph
-The combined PGIR is a tuple ($V'$, $E'$, $s$, $e$, $P$) with
-vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
-edges $E' \colon V' \times V'$,
-a unique starting vertex $s$,
-a unique ending vertex $e$,
-and a preference function $P \colon V' \rightarrow 2^{\set{1, \dots, j}}$ , which maps nodes in the product graph to a set of path ranks.
-
-For a PGIR vertex $n = (l, \dots) \in V'$, we say that $n$ is a \emph{shadow} of topology location $l$.
-We also write $\tilde{n} = l$ to indicate that the topology location for node $n$ is $l$.
-When two PGIR nodes $m$ and $n$ shadow the same topology location (\IE, $\tilde{m} = \tilde{n}$), we write $m \approx n$.
-
-Throughout the remainder of the paper, we will use the convention that metavariables $m$ and $n$ stand for PGIR nodes and $l$ stands for a topology location.
-Capital letters like $X$ refer to concrete topology locations, while capital letters with subscripts such as $X_1$ and $X_2$ refer to concrete PGIR nodes that share a topology location (\IE, $\tilde{X_1}$ = $\tilde{X_2} = X$).
-
-\para{From RIR To PGIR}
-
-% Formal product construction
-Let $a_i$ and $b_i$ denote states in the regular policy automata.
-The PGIR is constructed by adding an edge from $m = (l_m, a_1, \dots, a_k)$ to $n = (l_n, b_1, \dots, b_k)$ whenever $\sigma_i(a_i, l_n) = b_i$ for each $i$ and $(l_m,l_n) \in E$ is a valid topology link.
-%
-Additionally, we add edges from the start node $s$ to any $n = (l, a_1, \dots, a_k)$ when $\sigma_i(q_{0_i}, l) = a_i$ for each $i$.
-%
-The preference function $P$ is defined as $P(n) = \set{i~\vert~a_i \in F_i} $. That is, it records the path rank of each automaton that has reached a final state.
-% in preferences are achieved from each policy automaton for every node in the product construction.
-%
-Finally, there is an edge from each node in the PGIR such that $P(n) \neq \emptyset$ to the special end node $e$.
-We write $(m \leq_{rank} n)$ if either $P(m) = P(n) = \emptyset$ or $min ~ P(m) \leq min ~ P(n)$, which means that paths ending at PGIR node $m$ are better (lower rank) than paths ending at $n$.
-
-Intuitively, the PGIR tracks the policy states of each automaton as route announcements move between locations.
-%
-Consider the topology in Figure~\ref{fig:example-compilation}.
-Suppose we want a primary route from neighbor W that allows traffic to enter the network at $A$ and utilize the C--D link before leaving the network (through $X$ or $Y$).
-As a backup, we also want to allow traffic to enter the network from $B$, in which case the traffic can also utilize the C--E link before leaving the network.
-For simplicity, we assume that the route ends in either $X$, $Y$, or $Z$.
-The RIR for the policy could be written as:
-%
-$$(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^+ \cdot \Out)$$
-%
-Figure~\ref{fig:example-compilation} shows the policy automata for each regular expression preference. Since we are interested in the flow of control messages, the automata match backwards.
-%
-The figure also shows the PGIR after intersecting the topology and policy automata.
-Every path in the PGIR corresponds to a concrete path in the topology.
-In particular, every path through the PGIR that ends at a node $n$ such that the preference function $P(n) = \set{i_1, \dots, i_k}$ is non-empty, is a valid topological path that satisfies the policy constraints and results in a particular path with preferences $i_1$ through $i_k$.
-%
-For example, the path $X \cdot D \cdot C \cdot A \cdot W$ is a valid path in the topology that BGP route announcements might take, which would lead to obtaining a path with the lowest (best) rank of $1$.
-BGP control messages can start from peer X, which would match the $\Out$ transition from both automata, leading to state $1$ in the first automaton, and state $1$ in the second automaton.
-This possibility is reflected in the product graph by the node with state $(X,1,1)$.
-From here, if X were to advertise this route to D, it would result in the path $D \cdot X$, which would lead to state $2$ in the first automaton, and state $2$ in the second automaton, and so on.
-%
-The ``--" state indicates the corresponding automaton cannot accept the current path or any extension of it. Since
-node $(W,5,-)$ is in an accepting state for the first automaton, it indicates that this path has preference 1.
-
-\para{Minimization}
-After building the PGIR as described above,
-we minimize it in order to improve the precision of the subsequent analysis that checks if the policies captured by it are safe under failures.
-The minimization is based on the observation that, although every path in the PGIR is a valid path in the topology, we do not want to consider paths that form loops.
-In particular, BGP's loop prevention mechanism forces an AS to reject any route that is already in the AS path.
-%
-For example, in Figure~\ref{fig:example-compilation}, the path $W \cdot A \cdot C \cdot B \cdot W$ is a valid topological path, leading to a path that satisfies the preference 2 policy, but which contains a loop.
-%
-%The precision of the failure-safety analysis often increases when nodes and edges that are not possible due to loops are eliminated.
-%For example, if we can safely remove a PGIR edge, then we do not have to consider what happens when the edge has failed.
-
-We use graph dominators~\cite{tarjan-dominance} as a relatively cheap approximation for removing many nodes and edges in the PGIR that are never on any \emph{simple} (loop free) path between the start and end nodes.
-In the PGIR, a node $m$ dominates a node $n$ if $m$ appears on every path leading from the start node to $n$.
-Similarly, a node $m$ post-dominates a node $n$ in the PGIR if $m$ appears on every path from $n$ to the end node.
-We can safely remove nodes and edges in the PGIR when any of the following conditions hold, where we have $m$, $m'$ and $n$, $n'$ such that $m \approx m'$ and $n \approx n'$.
-\begin{itemize}
-\setlength{\itemsep}{1pt}
-\setlength{\parskip}{0pt}
-\setlength{\parsep}{0pt}
-\item Remove $m$ if it is not reachable from the start node
-\item Remove $m$ if it can not reach the end node
-\item Remove $m$ if it is (post-)dominated by some $m'$
-\item Remove edge ($m$, $n$) if some $m'$ post-dominates $n$
-\item Remove edge ($m$, $n$) if some $n'$ dominates $m$
-\end{itemize}
-For example, node $(W,1,1)$ in Figure~\ref{fig:example-compilation} is removed because every path to the end node must always go through node $(W,-,4)$.
-That is, node $(W,1,1)$ is post-dominated by node $(W,-,4)$ and both are shadows of topology location $W$.
-%Similarly, the edge from $(C,3,2)$ to $(D,-,2)$ is removed since node $(C,-,2)$ post-dominates $(D,-,2)$.
-
-We repeatedly apply the minimizations above until no further minimization is possible.
-In the example from Figure~\ref{fig:example-compilation}, colored nodes and dashed edges show edges and nodes removed after minimization.
-
-\subsection{Failure-safety analysis}
-
-To implement path preferences in routing, BGP uses local preferences on a per-device basis.
-However, the distributed nature of BGP makes setting preferences locally to achieve a network-wide routing policy difficult.
-This task becomes even more challenging in the presence of failures since routers running BGP lack a global view of the network.
-
-\para{An illustrative example}
-
-To demonstrate the difficulty of generating device-local preferences, consider the simple policy for the topology in Figure~\ref{fig:unimplementable}, which says to prefer the top path over the bottom path:
-%
-$(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G})  \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$.
-%
-How could such a policy be implemented in BGP?
-Suppose we set the local preferences to have $D$ prefer $E$ over $F$, and have $A$ prefer $B$ over $C$.
-This works as expected under normal conditions, however, if the A--B link fails, then suddenly $D$ has made the wrong decision by preferring $E$.
-Traffic will now follow the
-$A \cdot C \cdot D \cdot E \cdot G$ path, even though this path was not allowed by the policy.
-Thus, the distributed implementation has used a route that is not allowed by the policy.
-To make matters worse, the second preference for the path $A \cdot C \cdot D \cdot F \cdot G$ is available in the network but not being used.
-Thus, a path for the best possible route available exists in the network but is not being used by the distributed implementation.
-%
-The first problem could be fixed by tagging and filtering route advertisements appropriately so that $C$ rejects routes that go through $E$, however the second problem cannot be fixed.
-In fact, this policy cannot be implemented in BGP in a way that is policy compliant under all failures since $D$ cannot safely choose between $E$ and $F$ without knowing whether the A--B link is available.
-
-\para{Problem Formulation}
-
-The problem of determining local preferences for each router is reflected in the structure of the PGIR.
-Whenever a given router appears as multiple shadow nodes in the PGIR, the compiler must decide which shadow to prefer.
-%
-In the example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in shadow $(C,-,2)$ or from $D$ in shadow $(C,3,2)$.
-%
-%
-The compiler must determine a \emph{total ordering} of shadow nodes for each router, which reflects the relative preference of advertisements received in each shadow and should be consistent with path ranks in routing policy.
-%
-For example, if $C$'s shadow $(C,3,2)$ can be preferred to $(C,-,2)$, written as $(C,3,2) \leq_{lp} (C,-,2)$, $C$ can prefer advertisements from $(D,2,2)$ over $(E,-,2)$.
-$D$ and $E$ tag their advertisements to let $C$ know which shadow sent the advertisement.
-\$\ref{sec:abgp} discusses tagging in detail.
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=.5\columnwidth]{figures/unimplementable}
-  \caption{A network where the policy $(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G}) \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$ is unimplementable in BGP under arbitrary failures.}
-  \label{fig:unimplementable}
-  %\vspace{-1em}
-\end{figure}
-
-\para{Regret-free Preferences}
-To order PGIR shadows ($\leq_{lp}$) for each router in a way that is policy-compliant under all failures, we introduce the notion of \emph{regret-free} preferences, motivated by the observations from the example in Figure~\ref{fig:unimplementable}.
-A router (location) $l$ has a regret-free preference for a set of advertisements $A$ over $B$ if, whenever $l$ selects an advertisement to destination $d$ from $A$ over another from $B$, there is always some policy-compliant path to $d$ that is at least as good ($\leq_{rank}$ for the final node along the path) as any possible path (not necessarily from $l$) to $d$ if $l$ had selected an advertisement from $B$ instead.
-In other words, the preference of $A$ over $B$ at $l$ is regret-free if $l$ is never (under any failure) worse-off by choosing an advertisement from $A$ when available.
-The notion of regret-free preferences can be lifted to PGIR nodes by considering the set of advertisements available to each node.
-
-In the example of Figure~\ref{fig:example-compilation}, the choice for $C$ to prefer shadow $(C,3,2)$ to $(C,-,2)$ is regret-free, since there will always be at least as good a path to destination $W$ regardless of any failures that might occur in the network.
-For example, if the $C$--$A$ link fails, then there is still a backup path from $(C,3,2)$ to $(W,-,4)$ that is just as good as any path from $(C,-,2)$.
-Likewise, any combination of failures to disconnect $(C,3,2)$ from $(W,-,4)$ would also disconnect $(C,-,2)$ from $(W,-,4)$.
-
-%We now explain this property more formally in terms of the structure of the PGIR. We use the notation $path(s,d)$ to say that there exists a path in the PGIR from $s$ to $d$.
-%
-%Preferences (for the PGIR) are \emph{regret-free} if, given (i) any combination of failed topology links\footnote{Note that a single failure in the topology may correspond to zero or more failed nodes/edges in the PGIR}, (ii) a fixed topology (advertisement) destination $d$, and (iii) two contexts $N_1 < N_2$, then whever there exists a $d'$ such that $loc(d') = d$ and $path(N_2,d')$, then there exists a $d''$ such that $loc(d'') = d$ and $path(N_1,d'')$ with $d'' \leq_{rank} d'$.
-%
-%The property simply says that if router $N$ prefers context $N_1$ to $N_2$, then any time there is a path from $N_2$ to some destination $d$, then there exists a better (lower ranked) path from $N_1$ to destination $d$.
-%
-
-\para{A Preference Inference Algorithm}
-
-%For example, in our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an announcement from $E$ and later achieve the backup path, or it can receive an announcement from its neighbor $D$ and later achieve either the primary or backup path.
-Is it safe for $C$ to prefer its neighbor $D$ over its other neighbor $E$?
-The important observation is that, if $C$ prefers $D$, then it is never worse off---it will always achieve at least as good a path as if it had choosen $E$.
-%For example, suppose $C$ chooses a route from $D$, but cannot achieve its primary path because the $A$ -- $W$ link has failed.
-In this case, the advertisement from $C$ will still be sent along towards the ultimate backup location $W$.
-Since the $(C,3,2)$ node has the same one-step and two-step next hops as node $(C,-,2)$ in the product graph, no possible failure will prevent a route advertisment from reaching $(W,-,4)$ that wouldn't have otherwise prevented it if $C$ had choosen $E$.
-
-Searching for precise regret-free preferences in general is hard, and clearly enumerating all possible combinations of failures and preference orderings is intractable.
-We thus adopt a conservative analysis that we found to be effective and efficient in practice.
-The idea is to $i)$ search for regret-free preferences by comparing the set of paths available after accepting advertisements in two different PGIR shadows $N_1$ and $N_2$ of topology node $N$, and $ii)$ refine the comparison when necessary by considering where the announcements must have traversed before arriving at $N_1$ or $N_2$.
-
-\begin{algorithm}[t!]
-\caption{Inferring regret-free preferences}
-\label{alg:failures}
-\begin{algorithmic}[1]
-\Procedure{Regret-free($G$, $N_1$, $N_2$)}{}
-  \If {$N_1 \not\approx N_2$} \Return false
-  \EndIf
-  \State $q \gets Queue()$
-  \State $q.Enqueue (N_1, N_2)$
-  \While {$!q.Empty()$}
-    \State $(m,n) \gets q.Dequeue()$
-    \If {$m \nleq_{rank} n$}
-      \Return false
-    \EndIf
-    \For {$n'$ in adj($G$, $n$)}
-      \If {\big($\exists m' \in \textup{adj}(G,m), m' \approx n'$\big) \textbf{or} \\
-            \hspace{5.2em}
-            \big($\exists m' \in$ $G$, dominates $m$, $m' \approx n'$\big)}
-        \If {$(m',n')$ not marked}
-          \State {mark $(m',n')$ as seen}
-          \State $q.Enqueue(m',n')$
-        \EndIf
-      \Else { \Return $false$}
-      \EndIf
-    \EndFor
-  \EndWhile \\
-  \hspace{\algorithmicindent} \Return true
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-Algorithm~\ref{alg:failures} checks whether one shadow can be preferred to another ($N_1 \leq_{lp} N_2$).
-It walks from nodes $N_1$ and $N_2$ and ensures that for every \textit{step} $N_2$ can take to some new topology location, $N_1$ can, at the very least, also take a step to an equivalent topology location $(\approx)$.
-When there is no such equivalent step, the algorithm attempts to take into account where the advertisement must have already traversed.
-In particular, it checks if there is an equivalent dominator node and, if so, walks from this new node instead.
-%
-The idea is that, since the advertisement must have already passed through the dominator, we can check to see if we are guaranteed to find paths that are at least as good from this new node instead.
-%
-At each step, it requires that the current node reachable from $N_1$ has a path rank that is at least as good as that of the current node reachable from $N_2$ ($m \leq_{rank} n$).
-The intuition here is that if $m \nleq_{rank} n$, then we can very likely fail every edge in the topology except for the path that leads to the current $m$ and $n$, thereby generating a counterexample.
-Algorithm~\ref{alg:failures} terminates since the number of related states $(m,n)$ that can be explored is finite.
-
-For each router in the topology, local preferences are now obtained by sorting the corresponding PGIR shadows according to the $(\leq_{lp})$ relation determined by Algorithm~\ref{alg:failures}.
-If two nodes are incomparable, then the compiler rejects the policy as unimplementable.
-
-\para{Avoiding Loops}
-
-The checks for failure safety described above overlook one critical point: A better (lower rank) path might not be available due to loops rejected by BGP.
-%BGP automatically rejects advertisements to a location where the locations is already contained in the AS path attribute.
-
-Consider the partial product graph shown in Figure~\ref{fig:avoiding-loops}.
-Our preference inference algorithm will determine that node $X_1$ should be locally preferred to node $X_2$ since this will result in a better (lower ranked) path to destination $A$.
-However, when applying Algorithm~\ref{alg:failures}, we failed to take into account the possibility of loops.
-In particular, node $A_2$ may be unusable for advertisements that go through $X_1$ since the advertisement may have already gone through $A_1$ previously.
-In this case, $X$ will have made the wrong choice since preferring $X_2$ would have resulted in a better path for the destination $A$ (a path of rank 3 instead of 4).
-
-On the other hand, this would not have been a problem if paths ending at $A_1$ had a lower rank than those ending at $A_2$ or $A_3$.
-For example, if paths ending at $A_1$ had rank 1, then any time $A_2$ is unusable due to a loop with $A_1$, it ultimately does not matter since $A_1$ is preferred anyway.
-%
-In fact, checking if we are never worse off using $A_1$ instead of $A_2$ corresponds exactly with determining if $A$ has a regret-free preference for $A_1$ over $A_2$.
-%
-More specifically, the compiler checks that, any time there are two shadows $N_1$ and $N_2$ for the same topology location, where $N_1$ appears ``above'' (\IE, can reach) $N_2$ in the PGIR, then $N_1$ must be strictly preferred to $N_2$ (\IE, $N_1 <_{lp} N_2$).
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=.67\columnwidth]{figures/loops}
-  \caption{A product graph where preference inference is unsound before considering loops. Path ranks shown by nodes.}
-  \label{fig:avoiding-loops}
-  %\vspace{-1em}
-\end{figure}
-
-\subsection{Aggregation-safety analysis}
-
-%\para{Aggregation Safety}
-\label{sec:agg-safety}
-
-As shown in \S\ref{sec:motivation}, aggregation can lead to subtle black-holing of traffic when failures occur.
-Determining when this can happen requires knowledge, not only of the topology, but also of the policy.
-For instance, a policy might require that all traffic for a particular prefix go over a single link before being aggregated.
-If that one link fails, a black hole might be introduced.
-%
-Because the PGIR encodes the complete user policy and topology, \sysname can efficiently check that aggregates do not black hole traffic for up to $k$ failures.
-
-We view the aggregation problem as a variant of the min-cut problem in the PGIR.
-Specifically, for each prefix that falls under an aggregate, we are interested in finding a lower bound on the number of failures required to disconnect the prefix's origin from its aggregation point.
-The difficulty, however, is that each link in the topology might appear as multiple links in the PGIR, thus preventing the direct application of standard min-cut algorithms.
-%
-
-Instead, we adopt the following simple strategy: $i)$ pick a random path in the PGIR between the prefix's origin and aggregation point, $ii)$ remove all similar edges in the PGIR for each topology edge along the chosen path, and $iii)$ repeat until no such path exists.
-Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.
-
-For example, recall the datacenter example from \S\ref{sec:motivation}, with the policy
-\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate.
-Figure~\ref{fig:aggregation-safety} shows the PGIR for \CD{PG1}.
-Since we know aggregation will occur at $X$, and that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$.
-We could remove the $A$--$D$--$X$ path first and woul then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none).
-Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process.
-Because $A$ is now disconnected from $X$, 2 is a lower bound on the number of failures required to introduce an aggregation black hole for prefix \CD{PG1}.
-This process is repeated for other aggregation locations (\EG, $Y$).
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=\columnwidth]{figures/aggregation}
-  \caption{Aggregation safety for a datacenter.}
-  \label{fig:aggregation-safety}
-  \vspace{-1em}
-\end{figure}
-
-\subsection{Abstract BGP}
-\label{sec:abgp}
-
-The final stage of our compiler translates policies from PGIR to a vendor-neutral abstraction of BGP (ABGP).
-% and then from ABGP to actual device configurations.
-
-\para{From PGIR to ABGP}
-
-Once we have the total ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward.
-The idea is to encode the state of the automata using BGP community values.
-Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR.
-For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else).
-If it sees such an announcement, it will remove the old community value and add a new one for state $(4,2)$ before exporting it to $W$.
-
-For each router $r$, the compiler sets a higher local preference for neighbors of a more-preferred PGIR node for $r$.
-For example, $C$ will prefer an advertisement from $D$ in state $(2,2)$ over an advertisement from $E$ in state $(-,2)$.
-
-Since the compiler can control community tagging only for routers under the control of the AS being programmed, it cannot match on communities for external ASes.
-Instead, it translates matches from external ASes into a BGP regular expression filter.
-For example, node $D$ in Figure~\ref{fig:example-compilation} would match the single hop external paths $X$ or $Y$.
-In general, if routes are allowed from beyond $X$ or $Y$, these will also be captured in the BGP regular expression filters.
-The unknown AS topology is modeled as a special node in the PGIR that generates a filter to match any sequence of ASes.
-
-Finally, the external AS $W$ should prefer our internal router $A$ over $B$.
-In general, it is not possible to reliably control traffic entering the network beyond certain special cases.
-In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$.
-Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic.
-The compiler performs a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
-%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default.
-Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
-Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.
-
-After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on.
-In the ABGP policy shown in Figure~\ref{fig:abgp-config}, all community tags can be removed, since there is never any ambiguity as to the current state of the PGIR based only on the current router importing the route and the neighbor from which the route is being imported.
-
-\newcommand{\highlight}[1]{%
-  \colorbox{red!50}{$\displaystyle#1$}}
-\newcommand{\Router}[1]{\KW{Router} #1:}
-\newcommand{\REGEX}[1]{\texttt{regex}(#1)}
-\newcommand{\PEER}{\texttt{peer}}
-\newcommand{\COMM}{\texttt{comm}}
-\newcommand{\MED}{\texttt{MED}}
-\newcommand{\Arrow}{\ensuremath{\leftarrow}}
-
-\begin{figure}[t!]
-\begin{code}
-  \Router{A}
-    Match \PEER=C, \COMM=(3,2)
-      Export \COMM \Arrow (4,2),
-             \MED \Arrow 80, \PEER \Arrow W
-  \Router{B}
-    Match \PEER = C, \COMM = (-,2) or (3,2)
-      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
-             \MED \Arrow 81, \PEER \Arrow W
-  \Router{C}
-    Match[LP=99] \PEER = E, \COMM = (-,2)
-      Export \COMM \Arrow (-,2), \PEER \Arrow B
-    Match \PEER = D, \COMM = (2,2)
-      Export \COMM \Arrow (3,2), \PEER \Arrow A,B
-  \Router{D}
-    Match \REGEX{X + Y}
-      Export \COMM \Arrow (2,2), \PEER \Arrow C
-  \Router{E}
-    Match \REGEX{Z}
-      Export \COMM \Arrow (-,2), \PEER \Arrow C
-  \end{code}
-  \vspace{-2em}
-  \caption{Abstract BGP router configurations. \label{fig:abgp-config}}
-  \vspace{-1em}
-\end{figure}
-
-%=====================================================
-%
-%
-%  **Implementation**
-%
-%
-%=====================================================
-
-\section{Implementation}
-\label{sec:implementation}
-
-Our \sysname compiler is implemented in roughly 6700 lines of F\# code.
-It includes command-line flags for enabling or disabling the use of the BGP MED attribute, AS path prepending, the no-export community, as well as for ensuring at least k-failure safety for aggregate prefixes.
-Since each prefix has a separate routing policy, we compile each routing policy in parallel.
-Currently, \sysname supports generating Quagga router configurations out of the box.
-Users can add new vendor-specific adapters to translate from ABGP to other router configuration languages, or incorporate the compiler into an existing template-based system, \EG, by mixing the \sysname-generated BGP configuration with other, non-BGP configuration elements.
-
-Our compiler includes the following features that improve its performance and usability.
-
-\para{Efficient PGIR construction}
-
-Constructing automata for extended regular expressions (\IE, regular expressions with negation and intersection operations) is known to have high complexity~\cite{regex-complexity}.
-The \sysname compiler uses regular expression derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions efficiently.
-Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy.
-To model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.
-%
-Rather than construct the product graph in full, our implementation prevents exploring parts of the graph during construction when no automata has a reachable accepting state.
-
-%\para{PG Minimization}
-
-%The \sysname compiler uses a fast algorithm for computing graph dominators by storing sets of dominators in a compact representation known as a dominator tree~\cite{fast-dominance}.
-More complex algorithms with better theoretical complexity exist~\cite{linear-dominance, tarjan-dominance} and may be better suited for large enough topologies.
-All minimization steps are repeated until no more progress can be made.
-
-\para{Fast failure-safety analysis}
-
-When computing local preferences and ensuring failure safety, as described in \S\ref{sec:compilation}, the compiler performs memoization of the \textup{Regret-Free} function.
-That is, whenever for two states $N_1$ and $N_2$ we compute $\textup{Regret-Free}(G, N_1, N_2)$ and the function evaluates to $true$, then each of the intermediate related states $m$ and $n$ must also satisfy $\textup{Regret-Free}(G, m, n)$.
-Memoizing these states dramatically reduces the amount of work performed to find preferences in the common case.
-
-\para{Efficient configuration generation}
-
-The naive code generation algorithm described in \S\ref{sec:abgp} is extremely memory inefficient since it generates a separate match-export pair for every unique in-edge/out-edge pair for every node in the product graph before minimization.
-Our implementation performs partial minimization during generation by recognizing common cases such as when there is no restriction on exporting to or importing from neighbors.
-
-\para{Checking policy correctness}
-
-Even when programming the network centrally, it is possible for operators to make mistakes.
-\sysname includes many analyses to identify common mistakes at compile time.
-A subset includes: (i) a preference analysis to determine when backup paths will never be used, (ii) a reachability analysis to check if locations that should be reachable according to the policy are not reachable after combining the topology and policy, (iii) an anycast analysis to find instances where the operator might accidentally anycast a prefix (\IE, originates the prefix from multiple locations), (iv) an aggregate analysis to find unused aggregates that do not summarize any specific prefix.
-
-%=====================================================
-%
-%
-%  **Evaluation**
-%
-%
-%=====================================================
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-We apply \sysname on real policies for backbone and datacenter networks.
-Our main goals are to evaluate if its language is expressive enough for real-world policies, the time the compiler takes to generate router configurations, and the size of the resulting configurations.
-
-\subsection{Networks studied}
-
-We obtained routing policy for the backbone network and datacenters of a large cloud provider.
-Multiple datacenters share this policy.
-The backbone network connects to the datacenters and also has many external BGP neighbors.
-The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for datacenter routers or actual configurations for the backbone network (where templates are not used because the network has a less regular structure).
-
-The networks have the types of policies that we outlined earlier (\S\ref{sec:motivation}).
-The backbone network classifies external neighbors into several different categories and prefers paths through them in order.
-It does not want to provide transit among certain types of neighbors.
-For some neighbors, it prefers some links over the others.
-It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (\EG, West Coast of the USA).
-Finally, it has many filters, \EG, to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, \ETC
-
-Routers in the datacenter network run BGP using private AS numbers and peer with each other and with the backbone network over eBGP.
-The routers aggregate some prefix blocks when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region.
-The datacenter networks also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.
-
-\begin{figure}
-  \subcaptionbox{Datacenter}
-    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-dc.png}}
-  \subcaptionbox{Backbone}
-    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
-  \caption{Compilation time. \label{fig:compilation-times}}
-  \vspace{-1em}
-\end{figure}
-
-\subsection{Expressiveness}
-
-We found that we could translate all network policies to \sysname.
-We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname.
-The datacenter operator said that he found the language intuitive.
-The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.}
-%We further found that the datacenter policies were correctly translated. 
-For the backbone network, the operator mentioned an additional policy not present in the English document, which we added later.
-%
-For both the datacenter and backbone networks, \sysname was able to guarantee policy-compliance under all possible failure scenarios.
-
-Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the routing policies for \sysname were 43 lines for the backbone network and 31 lines for the datacenter networks.
-
-\begin{figure}[t!]
-  \subcaptionbox{Datacenter}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
-  \subcaptionbox{Backbone}
-    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
-  \caption{Configuration minimization. \label{fig:config-min}}
-  \vspace{-1em}
-\end{figure}
-
-\subsection{Compilation time}
-
-%\begin{figure}[t!]
-%  \centering
-%  \begin{minipage}[b]{0.45\linewidth}
-%    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-dc.png}
-%  \end{minipage}
-%  \quad
-%  \begin{minipage}[b]{0.45\linewidth}
-%    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-backbone.png}
-%  \end{minipage}
-%  \caption{Compilation times.}
-%  \label{fig:compilation-times}
-%\end{figure}
-
-%\begin{figure}[t!]
-%  \centering
-%  \begin{minipage}[b]{0.45\linewidth}
-%    \includegraphics[width=1.1\columnwidth]{figures/config-compression-dc.png}
-%  \end{minipage}
-%  \quad
-%  \begin{minipage}[b]{0.45\linewidth}
-%    \includegraphics[width=1.1\columnwidth]{figures/config-compression-backbone.png}
-%  \end{minipage}
-%  \caption{Configuration minimization.}
-%  \label{fig:config-minimization}
-%\end{figure}
-
-We study the compilation of time for both policies as a function of network size.
-Even though the networks we study have a fixed topology and size, we can explore the impact of size because the policies are network-wide and the compiler takes the topology itself as an input.
-For the datacenter network, we build and provide as input fat tree~\cite{fattree} topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy.
-%We take this approach to smoothly explore different sizes.
-%There is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete datacenter topologies.
-For a given size, our reported results match those for the concrete topologies.
-For the backbone network, the internal topology does not matter since all routers connect to each other through iBGP.
-We explore different (full iBGP) mesh sizes and randomly map neighboring networks to routers.
-Even though each border router connects to many external peers, we count only the mesh size.
-
-All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
-%
-Figure~\ref{fig:compilation-times} shows the compilation times for datacenter and backbone networks of different sizes.
-For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on each predicate in parallel.
-A single predicate can describe many prefixes, for example by matching on a disjunction of prefixes.
-At their largest sizes, the per-predicate compilation time is roughly 10 seconds for the datacenter network and 45 seconds for the backbone network.
-
-%From the break down of the time by compilation phase, we see that no single compilation phase dominates the running time of the compiler.
-However, construction and minimization of the product graph take the most time.
-
-Compilation for the largest datacenter takes less than 9 minutes total.
-Unlike the datacenter policy, the number of predicates for the backbone policy remains relatively fixed as the topology size increases.
-Compilation for the largest backbone network takes less than 3 minutes total.
-The inclusion of both more preferences and more neighboring ASes in the backbone policy increases the size of the resulting PGIR, which in turn leads to PGIR construction and minimization taking proportionally more time.
-
-In both examples, we observe that Algorithm~\ref{alg:failures} for inferring \textup{Regret-Free} preferences is efficient, taking only a small fraction of the total running time.
-PGIR minimization is the most expensive compilation phase.
-If needed, minimization can be limited to a fixed number of iterations for large networks.
-Both the backbone and datacenter policies could be successfully compiled without performing minimization.
-
-%
-
-\subsection{Configuration size}
-
-Figure~\ref{fig:config-min} shows the size of the compiled ABGP policies as a function of the topology size.
-The naive translation of PGIR to ABGP outlined in \S\ref{sec:compilation} generates extremely large ABGP policies by default.
-To offset this, the compiler performs ABGP configuration minimization both during and after the PGIR to ABGP translation phase.
-%Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
-Minimization is highly effective for both the datacenter and backbone policies. In all cases, minimized policies are a small fraction of the size of their non-minimized counterparts.
-
-%for i in *.set; do grep bgp $i | wc; done
-However, even minimized configurations are hundreds or thousands of lines per router.
-For the backbone network, the size of \sysname configurations is roughly similar to the BGP components of actual router configurations, though qualitative differences exist (see below).
-We did not have actual configurations for the datacenter network; they are dynamically generated from templates.
-
-\subsection{Propane vs. operator configurations}
-
-We comment briefly on how \sysname-generated configurations differ from configurations written by operators.
-%
-In some ways they are similar.
-For example, preferences among neighboring ASes are implemented with a community value to tag incoming routes according to preference, which is then used at other border routers to influence decisions.
-
-In other ways, the \sysname configurations are different, relying on a different BGP mechanism to achieve the same result. Some key differences that we observed were:
-
-$i)$ operators used the no-export community to prevent routes from leaking beyond a certain tier of the datacenter, while \sysname selectively imported the route only below the tier;
-%\sysname could use a similar implementation mechanism in the future as an optimization.
-
-$ii)$ operators prevented unneeded propagation of more-specific route announcements from a less-preferred neighboring AS based on their out-of-band knowledge about the topology, whereas \sysname propagated these advertisements;
-
-$iii)$ operators used a layer of indirection for community values, using community groups and re-writing values, to implement certain policies in a more maintainable manner, where \sysname uses flat communities; and
-
-$iv)$ operators used BGP regular expression filters to enforce certain invariants that are independent of any particular prefix, whereas \sysname enforced these invariants per prefix.
-
-We are investigating if such differences matter to operators, \EG, if they want to read \sysname configurations, and, if necessary, how to reduce them.
-
-%=====================================================
-%
-%
-%  **Related Work**
-%
-%
-%=====================================================
-
-\section{Related Work}
-\label{sec:related}
-
-Our work draws on four threads of prior work.
-
-\para{SDN languages}
-\sysname{} was heavily influenced by SDN programming
-languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire},
-and path queries~\cite{queries}.
-Each of these languages uses regular expressions to
-describe paths through a network and predicates to classify packets.
-In particular, FatTire allows programmers to define sets of paths
-with a fault tolerance level (\IE, tolerate 1 or 2 faults)
-and the compiler generates appropriate OpenFlow rules.
-\sysname is more expressive as it allows users to specify preferences among
-paths, and it generates distributed implementations that tolerate any number of faults.
-Because FatTire generates data plane rules up front,
-specifying higher levels of fault tolerance comes
-at the cost of generating additional rules that tax switch memory.
-In contrast, \sysname relies on distributed control plane mechanisms to react to faults, which do not have additional memory cost.
-Because of the differences in the underlying technology, the analyses
-and compilation algorithms used in \sysname are quite different from
-previous work on SDN.
-Finally, in addition to using path-based abstractions
-for intra-domain routing, \sysname uses them for inter-domain routing as
-well, unlike existing SDN languages.
-
-\para{Configuration automation}
-Many practitioners use configuration templates~\cite{hatch,thwack}, to ensure certain kinds of consistency across similar devices.
-In addition, configuration languages such as RPSL~\cite{RFC2622}, Yang~\cite{RFC6020}, and Netconf~\cite{RFC6241} allow operators to express routing policy in a vendor-neutral way.
-However, all of these solutions remain low-level, for example, requiring operators to specify exact local preferences.
-Unlike \sysname, there is no guarantee that these low-level configurations satisfy the original, high-level intent.
-
-\para{Configuration analysis}
-The notion that configuring network devices is difficult and error-prone is not new.
-In the past, researchers have tried to tackle this problem by analyzing existing
-%firewall configurations~\cite{fang,lumeta,margrave} and
-router configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe,arc} and reporting errors or inconsistencies when they are detected.
-Our research is complementary to these analysis
-efforts.  We hope to eliminate bugs by using higher-level
-languages and a ``correct-by-construction''
-methodology. Writing configurations at a high level of abstraction simplifies policy implementation and prevents a whole host of low-level errors.
-%By proposing that network administrators write configurations
-%at a high-level of abstraction, a whole host of low-level errors can be avoided and policy implementation can be simplified.
-
-\para{Configuration synthesis}
-ConfigAssure~\cite{narain:lisa05,narain+:configassure}
-is another system designed to
-help users define and debug low-level router
-configurations.  Inputs to
-ConfigAssure include a \emph{configuration database}, which contains a
-collection of tuples over constants and configuration variables, and a
-\emph{requirement}, which is a set of constraints.
-%For instance, the tuple \texttt{hsrp(rexa,rA1,int(1),int(2))} states that interface
-%\texttt{rA1} on device \texttt{rexa} belongs to the HSRP group defined
-%by configuration variable \texttt{int(1)} with virtual IP address
-%defined by configuration variable \texttt{int(2)}.  The constraint
-%\texttt{hsrp\_subnet([rexa-rA1,rexb-rB1])} states that a database
-%contains tuples defining HSRP group identifiers and virtual IPs for
-%interfaces \texttt{rA1} and \texttt{rB1} on devices \texttt{rexa} and
-%\texttt{rexb}.
-The authors use a combination of logic programming and
-SAT solving to find concrete values for configuration variables.
-%such as \texttt{int(1)}.
-ConfigAssure handles configuration for a wide range of protocols and many
-different concerns.  In contrast, the scope of \sysname is much
-narrower.  In return, \sysname offers compact, higher-level
-abstractions customized for our domain, such as regular paths, as well
-as domain-specific analyses customized to those abstractions, such as
-our failure safety analysis.  The implementation technology is also
-entirely different, as we define algorithms over automata and graphs
-as opposed to using logic programming and SAT-based model-finding.
-
-%We also believe the high-level, centralized nature of \sysname policies
-%has the benefit of making configurations
-%easier to understand and maintain.
-
-%=====================================================
-%
-%
-%  **Future Work**
-%
-%
-%=====================================================
-
-%\section{Future Work}
-%
-%There are a number of possible directions for future work in programming distributed control planes.
-One option would be to integrate a model of the environment into the compiler.
-For example, many ASes make use of informal peering agreements (e.g., tagging routes with certain communities) to enable a wider range of policies.
-A compiler with this information, could automatically derive routes conforming to these agreements.
-%
-%Another direction would be to perform policy verification at the level of centralized language.
-There has been great deal of work on verification of the data plane, but much less so on control plane verification.
-The \sysname language provides a high-level abstraction of the control plane, which could be amenable to verification or checking equivalence of policies.
-For example, an operator could check if adding aggregation at various points in the network as an optimization ever changes routing behavior.
-The automata-based representation of the product graph may lend itself well to this kinds of analysis.
-%
-%While we target BGP in this paper as a distributed backend for \sysname due to its expressiveness, scalability, and uniformity, it should be possible to use other protocols to achieve different types of routing policies (e.g., OSPF).
-In particular, one could potentially combine different distributed routing protocols through route redistribution to achieve a larger variety of policies.
-%
-%Another possible future direction is automate AS-wide load balancing for BGP.
-Load-balancing with BGP across external ASes is difficult since there are few mechanisms at the operators disposal.
-However BGP policies can artificially prepend to the AS path to increases its length, and influence peer decisions.
-The product graph representation describes, not only which neighbors routers should prefer, but also which neighbors it is indifferent towards.
-Thus the compiler knowns when it can safely perform load-balancing across different neighbors.
-
-%=====================================================
-%
-%
 %  **Conclusions**
@@
 
-\para{Acknowledgements}
-We thank R.
-Aditya, George Chen, and Lihua Yuan for feedback on the work and the SIGCOMM reviewers for comments on the paper.
-This work is supported in part by the National Science Foundation awards CNS-1161595 and CNS-1111520 as well as a gift from Cisco.
-
-%=====================================================
-%
-%
-%  **Appendix**
-%
-%
-%=====================================================
-
-%\subsection{Propane Properties}
-%
-%\newtheorem{prop}{Proposition}[section]
-%
-%Here we investigate the correctness and expressiveness properties of \sysname.
-We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures?
-(2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?
-%
-%If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario.
-We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges.
-We argue that \sysname is correct by breaking down the claim:
-%
-%\begin{prop}
-%BGP configurations for internal routers produced by \sysname will be stable.
-%\end{prop}
-%
-%\begin{prop}
-%BGP configurations produced by \sysname are \textit{Sound} with respect to the policy: That is, any route traffic takes in the network, is a valid route specified by the policy.
-%\end{prop}
-%
-%The Soundness claim follows directly from compilation of the product graph.
-Since every path through the product graph (from start to end) must match the user's policy, and since the compiled configurations use communities to ensure only valid routes through the product graph are used, the resulting BGP configurations are Sound.
-%
-%\begin{prop}
-%BGP configurations produced by \sysname are \textit{Complete}: That is, the distributed implementation always obtains a most preferred route between two nodes when the corresponding path exists in the network.
-%\end{prop}
-%
-%The argument for completeness is as follows: Assume the most preferred path that exists in the network is between two nodes $X$ and $Y$.
-This means there is a valid path in the product graph corresponding to this path, and which is available in the network.
-%Assume we are unable to achieve this route in the network.
-To not achieve this path means that some router along the advertisement route from $Y$ to $X$ preferred to accept an advertisement from another peer instead.
-This implies that router that makes the ``wrong'' choice appears as a separate node in the product graph.
-However, from our failure safety check, we know that the other, more-preferred node must have a superset of the paths to accepting states as the less preferred node (from which it stole the route) for at least as good of a final preference.
-The argument then proceeds by induction on the path length - there are only a finite number of such stealings that can occur, each of which will ultimately still result in a route advertisement reaching $X$ along a most preferred path.
-%
-%Any \sysname-compiled policy will be \textit{Complete} as a result of the failure safety check.
-%
-
-%
-
-%The combination of Soundness and Completeness ensures that the distributed implementation will always send traffic along the best paths possible, yet will also never also use any undesired paths.
-These properties rely on the fact that \sysname produces stable BGP configurations:
-
-%
-%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo} for stable BGP.
-In particular, any policy with a dispute wheel will not pass the stronger failure safety check by \sysname.
-%
-%\begin{figure}[t!]
-%\includegraphics[width=\columnwidth]{figures/dispute-wheel}
-%\label{fig:dispute-wheel}
-%\caption{Product graph for a dispute wheel.}
-%\end{figure}
-%
-%The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}.
-If a set of BGP configurations do not have a dispute wheel, then they will converge to their best routes.
-Any BGP policy with a dispute wheel will not satisfy the failure safety condition in Section~\ref{sec:compilation}.
-Assume that the preferences in the policy describe a dispute wheel, and we will show that our failure check will reject the policy.
-Informally, a dispute wheel occurs when there are some number of nodes $u_1, \dots, u_n$ attempting to get a path to a destination node $d$.
-Each node $u_i$ prefers to go through its neighbor $u_{i+1}$ over route $R_i$ than directly to $d$ with route $Q_i$.
-Thus the nodes form a wheel of preferences.
-The product graph for a policy that contains a dispute wheel will look like Figure~\ref{fig:dispute-wheel}, which shows a dispute wheel of size 3.
-In order to pass the failure safety check for the compiler, the more-preferred node for $u_2$ will need to have a superset of the paths starting from the less-preferred node for $u_2$.
-In turn, this means that the maximum length path after visiting the more preferred $u_2$ will be $max(Z) = 1 + max(Y)$, similarly, if we look at $u_1$, we will determine that $max(Y) = 1 + max(X)$, and so on.
-The resulting equations define a system of unsatisfiable equations.
-Therefore, it is not possible for \sysname to compile a BGP policy that contains a dispute wheel.
-Since no-dispute-wheel is a sufficient condition for BGP stability, any compiled \sysname policy will be stable.
-%
-
-%An important distinction is that BGP might still be instable with respect to other external ASes, since \sysname has no way of configuring their routing policy and can only rely on AS path filters to see what advertisements are observed.
-
 %=====================================================
@@
 
-\balance
+%\balance
 

### 2017-03-09 paper/propane/SOSR/sosr.tex
add sosr extended abstract

\documentclass[sigchi]{acmart}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{url}
\usepackage{xspace}
\usepackage{code}

\newcommand{\EG}{\emph{e.g.}}
\newcommand{\IE}{\emph{i.e.}}
\newcommand{\ETC}{\emph{etc.}}
\newcommand{\ETAL}{\emph{et al.}}
\newcommand{\sysname}{{\small \sf Propane}\xspace}
\newcommand{\para}[1]{\paragraph*{\textbf{#1}}}

\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers

\begin{document}
\title{Propane: Programming Distributed Control Planes}
\subtitle{Extended Abstract (demo)}

\author{Ryan Beckett}
\affiliation{%
  \institution{Princeton University}
}
\email{rbeckett@cs.princeton.edu}

\author{Ratul Mahajan}
\affiliation{%
  \institution{Microsoft Research}
}
\email{ratul@microsoft.com}

\author{Todd Millstein}
\affiliation{%
  \institution{University of California, Los Angeles}
}
\email{todd@cs.ucla.edu}

\author{Jitendra Padhye}
\affiliation{
  \institution{Microsoft Research}
}
\email{padhye@microsoft.com}

\author{David Walker}
\affiliation{%
  \institution{Princeton University}
}
\email{dpw@princeton.edu}

\begin{abstract}

We describe \sysname, a new system with a language for specifying the end-to-end routing behavior of the network and a compiler for implementing the policies using the a collection of device configurations for the BGP routing protocol that run on unmodified vendor hardware. Propane allows operators to describe their policy through high-level constraints on both the shape and relative preferences of paths for different types of traffic. Constraints can describe paths both through the user's network, as well as through other networks that are not directly under the user's control.
When \sysname compiles a policy, the resulting BGP configurations are guaranteed to 
%remain policy-compliant
correctly implement the centralized policy in a distributed fashion -- without any centralized coordination and regardless of any number of network failures. We will demo \sysname by showing how to write and compile a simple data center routing configuration.

%%\textbf{Abstract---}
%Networks are notoriously difficult to configure correctly.
%Operators typically rely on local configuration of individual devices running
%distributed control plane protocols to achieve network-wide objectives.
%Managing implicit dependencies between device configurations and properly accounting for failures makes
%a network operator's work particularly difficult.
%%% %
%The recent move towards software-defined networking has been motivated, in part,
%by the simplicity of the centralized model, where a controller directly manages
%individual devices rather than letting them manage themselves. However distributed
%protocols have many important advantages in scalability,
%latency and fault tolerance over the completely centralized approach.
%%% %
%In this paper, we describe a new system -- \sysname, which allows an operator to specify a high-level,
%centralized routing policy declaratively, but then to compile it to a purely distributed
%implementation, which uses the BGP routing protocol to run on existing, commodity hardware.
%%% %
%Propane allows operators to describe the types of paths traffic may (or may not) take
%through the network, as well as relative preferences (or backups) between paths.
%%% %
%Network policies compiled with \sysname are guaranteed to implement the correct routing policy regardless of the number of failures, if possible.  If this is not possible, the compiler notifies the user at compile time rather than as the network is in operation.
%%% %
%\sysname also takes the centralized model one step further by unifying inter and intra-domain routing. Operators can specify routing policy for an autonomous system by programming against the abstraction that they can control any route in the wider internet.
%%% %
%%% We have implemented a compiler for \sysname and evaluated it against several real-world configurations for datacenters and core backbone networks. We demonstrate the \sysname compiler can scale to
%%% topologies with thousands of routers.

\end{abstract}

\maketitle

\section{Introduction}

Operators of traditional networks have a difficult job: They are charged
with achieving a wide variety of network-wide objectives, but they must do so by
managing and configuring many individual, separate devices, each of which runs
complex distributed control plane protocols. However, existing languages
for network configuration provided by vendors are too low level, requiring operators to work with assembly-language-like configuration primitives such as route-filters, community tags, and local-preference among routes. Further, the distributed nature of the network makes implementing network-wide policy more difficult. Many policies involve network-wide properties, for example to prefer a certain neighbor, keep certain traffic in a geographic region, or use a particular path only as a backup -- yet configurations describe the behavior of individual devices.

%
It is up to the operator then to perform the intellectually challenging task of decomposing a network-wide policy into a collection of distributed device policies such that their distributed interactions emulate the original policy.

To make matters worse, the possibility for network failures is an 
ever-present concern that significantly complicates the operator's task. 
Reasoning about all possible combinations of failures
and their potential impact on a distributed system is simply too hard for most humans. 
It is not surprising then that configurations that work correctly in fault-free 
environments, have been found to result in incorrect behavior when network 
elements go down~\cite{batfish}.
%
%
As a consequence of the difficulty of achieving network-wide objectives through device-level configuration, in practice, configuration errors are responsible for a large fraction of highly disruptive network outages~\cite{juniper-study,yankee-study,mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study,time-warner}.

%For instance, a recent misconfiguration led to an hour-long, nation-wide outage for Time Warner's backbone network~\cite{time-warner}; and a major BGP-related incident makes international news every few months~\cite{bgpmon}.

%To combat misconfiguration, operators have adopted several

%To reduce configuration errors, operators are increasingly adopting an
%approach in which common tasks are captured as parameterized templates~\cite{hatch,thwack}.

%
%More powerful still are systems like
%ConfigAssure~\cite{narain:lisa05,narain+:configassure}, which use SAT solving
%and model finding tools to fill in parameters in configurations while
%ensuring key correctness constraints are satisfied.
%One step further, systems like
%ConfigAssure~\cite{narain:lisa05,narain+:configassure} use SAT solving
%and model finding tools to correctly and consistently fill in some parameters.
%

%While templates help ensure certain kinds of consistency across devices,
%they do not provide fundamentally different abstractions from existing configuration languages
%or bridge the semantic divide between network-wide policies and device-level configuration.

%They do not provide fundamentally different abstractions
%from existing configuration languages and

%Thus, they still require operators to
%manually decompose policies into device behaviors.

%As a complementary approach, configuration analysis tools can help reduce misconfigurations by checking if low-level configurations match high-level policy~\cite{batfish,feamster+:rcc}. However, such tools cannot help operators with the challenging task of generating configurations in the first place.

%Further, today's tools cannot verify correctness under concrete failure scenarios, rather than under all possible failures.

In recent years, Software-defined networking (SDN) has emerged as an alternative 
approach to traditional network configuration. Rather than organizing routing policy
around a collection of configurations that compute routes via well-known distributed
protocols, users can directly program the forwarding tables of SDN-enabled switches via
a centralized controller. It is the job of the controller then, which has a centralized view
of the network to make sure that the routing policy is implemented correctly.

However, the SDN approach comes with its own set of challenges. For one, centralized SDN systems introduce a potential single point of failure and thus must be carefully designed with robustness in mind. The controller(s) must always be able to communicate with every switch even when failures occur, or if the network is large and geographically-distributed. Furthermore, such systems must also be carefully engineered for low-latency and scalability since the centralized controller can quickly become a potential performance bottleneck. For many of these challenges, researchers have looked at systems with multiple, interacting controllers, thus bringing back some aspects of distributed
control planes~\cite{mccauley2013extending,onos}.
Second, current SDN systems focus only on configuration of intra-domain routing policy, forcing users to fall back to traditional methods for configuring inter-domain routing policy.
More pragmatically, many networks will continue to use a distributed control plane for the foreseeable future, due to the difficulty of migrating to SDN or the inherent scalability and failure-robustness of distributed control.

\para{Language Overview}
We will demo our recent efforts to design and
implement a new language called \sysname, which greatly simplifies the task of
network management by allowing operators to specify their objectives
using high-level, \emph{end-to-end} constraints on forwarding paths rather than writing explicit device-by-device configurations.

The \sysname compiler rather than a human is responsible for bridging the gap
between high-level goals and the low-level mechanisms.  More
specifically, \sysname allows operators to describe the kinds of paths
traffic may or may not follow, as well as the relative preferences of such paths.
Paths can reference both devices in the network as well as other networks that are not under the control of the operator.

Taken together, these constraints allow users to write rich routing policies for the network. For example, then can require that two nodes be reachable, that traffic never leaves a particular part of the network, or that traffic is waypointed through middleboxes.
Preferences allow operators to write policies that describe desired behavior after network failures occur, such as preferring to use routes through one neighboring network over another, or using particular paths only as backups for other paths.

The \sysname language also supports network operators by defining a
set of common abbreviations for entering, leaving, and traversing
the user network and provides abstractions for managing common features of
control plane algorithms such as route aggregation.  
Operators use familiar logical operations to build routes in a modular and 
compositional manner from these primitives.

\para{Compiler Overview}

\sysname analyzes these user specifications and
then compiles them to a collection of BGP configurations, so they may
exploit existing distributed policy and fault tolerance mechanisms and
execute on existing commodity hardware. During the compilation
process, the compiler automatically synthesizes low-level configuration 
primitives such as per-device import and export
filters as well as BGP local preferences, MED attributes, and community tags.
The compiler accomplishes this by first transforming the policy into a graph-based intermediate 
representation that is more amenable to compilation and analysis.

An important feature of the language is that if possible, compiled
configurations are guaranteed to implement the correct routing policy,
regardless of any number of failures that might occur in the network.  
If correct compilation is impossible, the compiler notifies the user 
at compile time rather than waiting until the system is deployed in operation
and failures have occurred in the network.

This guarantee does not mean that the implementation is always
able to send traffic to its ultimate destination
(e.g., in the case of a network partition), but rather that it always respects the
centralized policy, which may include dropping traffic when there is no route.

Overall, we believe the approach \sysname combines easy programmability of centralized control planes with the failure robustness and scalability of distributed control planes.

\para{Demo Overview}
The \sysname demo will give a brief overview of the language and compiler by demonstrating how to write and compile a simple \sysname policy for a data center network. We will then demonstrate how the generated configurations can be emulated using Quagga router software with the open-source CORE network emulator.
An overview of what the demo can look like can be found here:

\vspace{1em}
\begin{sloppypar}
\url{https://drive.google.com/open?id=0B-rjACAtTwE_c0JGczdNRFBYcEE}
\end{sloppypar}

\para{Acknowledgments}
We thank R. Aditya, George Chen, and Lihua Yuan for feedback on the work and the SIGCOMM reviewers for comments on the paper. This work is supported in part by the National Science Foundation awards CNS-1161595 and CNS-1111520 as well as a gift from Cisco.

\bibliographystyle{abbrv}
\bibliography{references}

\end{document}

### 2017-03-11 paper/propane/SOSR/sosr.tex
remove pdf
finalize sosr submission

@@
-\documentclass[sigchi]{acmart}
+\documentclass[10pt]{sig-alternate}
 
@@
 \usepackage{amssymb}
-\usepackage{xcolor}
 \usepackage{url}
 \usepackage{xspace}
-\usepackage{code}
 
 \newcommand{\EG}{\emph{e.g.}}
-\newcommand{\IE}{\emph{i.e.}}
-\newcommand{\ETC}{\emph{etc.}}
-\newcommand{\ETAL}{\emph{et al.}}
 \newcommand{\sysname}{{\small \sf Propane}\xspace}
@@
 
-\settopmatter{printacmref=false} % Removes citation information below abstract
-\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
-\pagestyle{plain} % removes running headers
+\newfont{\mycrnotice}{ptmr8t at 7pt}
+\newfont{\myconfname}{ptmri8t at 7pt}
+\let\crnotice\mycrnotice
+\let\confname\myconfname
+
+\permission{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
+Copyrights for components of this work owned by others than ACM must be honored.
+Abstracting with credit is permitted.
+To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee.
+Request permissions from Permissions@acm.org.}
+
+\conferenceinfo{SOSR'17,}{April 3--4, 2017, Santa Clara, CA.} 
+\copyrightetc{\copyright~2017 ACM. ISBN \the\acmcopyr}
+\crdata{xxx.\\
+DOI: http://dx.doi.org/10.1145/XXX.XXXXXXX}
+% Update the XXX's to the DOI assigned by ACM rightsreview forms
+\clubpenalty=10000 
+\widowpenalty = 10000
 
 \begin{document}
-\title{Propane: Programming Distributed Control Planes}
-\subtitle{Extended Abstract (demo)}
+\title{Demo: Programming Distributed Control Planes}
+\subtitle{Invited Demo}
 
-\author{Ryan Beckett}
-\affiliation{%
-  \institution{Princeton University}
+\author{%
+Ryan Beckett\\
+  \affaddr{Princeton}
+  %\\
+  %\email{rbeckett@princeton.edu}
+\and
+Ratul Mahajan\\
+  \affaddr{Microsoft}
+  %\\
+  %\email{ratul@microsoft.com}
+\and
+Jitendra Padhye\\
+  \affaddr{Microsoft}
+  %\\
+  %\email{padhye@microsoft.com}
+\and
+Todd Millstein\\
+  \affaddr{UCLA}
+  %\affaddr{University of California, Los Angeles}
+  %\\
+  %\email{todd@cs.ucla.edu}
+\and
+David Walker\\
+  \affaddr{Princeton}
+  %\\
+  %\email{dpw@princeton.edu}
 }
-\email{rbeckett@cs.princeton.edu}
-
-\author{Ratul Mahajan}
-\affiliation{%
-  \institution{Microsoft Research}
-}
-\email{ratul@microsoft.com}
-
-\author{Todd Millstein}
-\affiliation{%
-  \institution{University of California, Los Angeles}
-}
-\email{todd@cs.ucla.edu}
-
-\author{Jitendra Padhye}
-\affiliation{
-  \institution{Microsoft Research}
-}
-\email{padhye@microsoft.com}
-
-\author{David Walker}
-\affiliation{%
-  \institution{Princeton University}
-}
-\email{dpw@princeton.edu}
-
-\begin{abstract}
-
-We describe \sysname, a new system with a language for specifying the end-to-end routing behavior of the network and a compiler for implementing the policies using the a collection of device configurations for the BGP routing protocol that run on unmodified vendor hardware.
-Propane allows operators to describe their policy through high-level constraints on both the shape and relative preferences of paths for different types of traffic.
-Constraints can describe paths both through the user's network, as well as through other networks that are not directly under the user's control.
-When \sysname compiles a policy, the resulting BGP configurations are guaranteed to 
-%remain policy-compliant
-correctly implement the centralized policy in a distributed fashion -- without any centralized coordination and regardless of any number of network failures.
-We will demo \sysname by showing how to write and compile a simple data center routing configuration.
-
-%%\textbf{Abstract---}
-%Networks are notoriously difficult to configure correctly.
-%Operators typically rely on local configuration of individual devices running
-%distributed control plane protocols to achieve network-wide objectives.
-%Managing implicit dependencies between device configurations and properly accounting for failures makes
-%a network operator's work particularly difficult.
-%%% %
-%The recent move towards software-defined networking has been motivated, in part,
-%by the simplicity of the centralized model, where a controller directly manages
-%individual devices rather than letting them manage themselves. However distributed
-%protocols have many important advantages in scalability,
-%latency and fault tolerance over the completely centralized approach.
-%%% %
-%In this paper, we describe a new system -- \sysname, which allows an operator to specify a high-level,
-%centralized routing policy declaratively, but then to compile it to a purely distributed
-%implementation, which uses the BGP routing protocol to run on existing, commodity hardware.
-%%% %
-%Propane allows operators to describe the types of paths traffic may (or may not) take
-%through the network, as well as relative preferences (or backups) between paths.
-%%% %
-%Network policies compiled with \sysname are guaranteed to implement the correct routing policy regardless of the number of failures, if possible.
-If this is not possible, the compiler notifies the user at compile time rather than as the network is in operation.
-%%% %
-%\sysname also takes the centralized model one step further by unifying inter and intra-domain routing.
-Operators can specify routing policy for an autonomous system by programming against the abstraction that they can control any route in the wider internet.
-%%% %
-%%% We have implemented a compiler for \sysname and evaluated it against several real-world configurations for datacenters and core backbone networks. We demonstrate the \sysname compiler can scale to
-%%% topologies with thousands of routers.
-
-\end{abstract}
 
@@
 
+\begin{abstract} 
+We describe \sysname, a system that consists of a language for specifying the end-to-end routing policy for a network and a compiler for implementing the policy by generating a collection of device configurations for the BGP routing protocol that run on unmodified vendor hardware.
+\sysname allows operators to describe their policy through high-level constraints on both the shape and preference of paths for different types of traffic.
+Constraints can describe paths both through the user's network, as well as through other networks that are not under the user's control.
+When \sysname compiles a policy, the resulting BGP configurations are guaranteed to 
+correctly implement the centralized policy in a distributed fashion -- without any centralized coordination and regardless of any number of network failures.
+\end{abstract}
+
+%=====================================================
+%
+%
+%  **Keywords**
+%
+%
+%=====================================================
+
+\category{C.2.3}{Computer-Communication Networks}{Network Operations}
+\category{D.2.2}{Software Engineering}{Design Tools and Techniques}
+
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10003033.10003083.10003098</concept_id>
+<concept_desc>Networks~Network manageability</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10003033.10003099.10003104</concept_id>
+<concept_desc>Networks~Network management</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10003033.10003068.10003073.10003075</concept_id>
+<concept_desc>Networks~Network control algorithms</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10011006.10011050.10011017</concept_id>
+<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Networks~Network manageability}
+\ccsdesc[500]{Networks~Network management}
+\ccsdesc[300]{Networks~Network control algorithms}
+\ccsdesc[500]{Software and its engineering~Domain specific languages}
+
+\keywords{Propane; Domain-specific Language; BGP; Compilation; Fault Tolerance; Distributed Systems}
+
+%=====================================================
+%
+%
+%  **Introduction**
+%
+%
+%=====================================================
+
 \section{Introduction}
 
-Operators of traditional networks have a difficult job: They are charged
+Operators of networks have a difficult job: They are charged
 with achieving a wide variety of network-wide objectives, but they must do so by
 managing and configuring many individual, separate devices, each of which runs
-complex distributed control plane protocols. However, existing languages
-for network configuration provided by vendors are too low level, requiring operators to work with assembly-language-like configuration primitives such as route-filters, community tags, and local-preference among routes.
-Further, the distributed nature of the network makes implementing network-wide policy more difficult.
+complex distributed control plane protocols. 
 Many policies involve network-wide properties, for example to prefer a certain neighbor, keep certain traffic in a geographic region, or use a particular path only as a backup -- yet configurations describe the behavior of individual devices.
-
+%
+In addition, existing languages
+for network configuration provided by vendors are too low level, requiring operators to work with assembly-language-like primitives such as route-filters, community tags, and local-preference. 
 %
@@
 It is not surprising then that configurations that work correctly in fault-free 
-environments, have been found to result in incorrect behavior when network 
-elements go down~\cite{batfish}.
+environments, may not work when network elements go down~\cite{batfish}.
 %
-%
-As a consequence of the difficulty of achieving network-wide objectives through device-level configuration, in practice, configuration errors are responsible for a large fraction of highly disruptive network outages~\cite{juniper-study,yankee-study,mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study,time-warner}.
+As a consequence of the difficulty of achieving network-wide objectives through device-level configuration, in practice, configuration errors are responsible for a large number of highly disruptive network outages~\cite{time-warner,batfish,mahajan+:bgp-misconfiguration,yankee-study,juniper-study}.
 
-%For instance, a recent misconfiguration led to an hour-long, nation-wide outage for Time Warner's backbone network~\cite{time-warner}; and a major BGP-related incident makes international news every few months~\cite{bgpmon}.
-
-%To combat misconfiguration, operators have adopted several
-
-%To reduce configuration errors, operators are increasingly adopting an
-%approach in which common tasks are captured as parameterized templates~\cite{hatch,thwack}.
-
-%
-%More powerful still are systems like
-%ConfigAssure~\cite{narain:lisa05,narain+:configassure}, which use SAT solving
-%and model finding tools to fill in parameters in configurations while
-%ensuring key correctness constraints are satisfied.
-%One step further, systems like
-%ConfigAssure~\cite{narain:lisa05,narain+:configassure} use SAT solving
-%and model finding tools to correctly and consistently fill in some parameters.
-%
-
-%While templates help ensure certain kinds of consistency across devices,
-%they do not provide fundamentally different abstractions from existing configuration languages
-%or bridge the semantic divide between network-wide policies and device-level configuration.
-
-%They do not provide fundamentally different abstractions
-%from existing configuration languages and
-
-%Thus, they still require operators to
-%manually decompose policies into device behaviors.
-
-%As a complementary approach, configuration analysis tools can help reduce misconfigurations by checking if low-level configurations match high-level policy~\cite{batfish,feamster+:rcc}.
-However, such tools cannot help operators with the challenging task of generating configurations in the first place.
-
-%Further, today's tools cannot verify correctness under concrete failure scenarios, rather than under all possible failures.
-
-In recent years, Software-defined networking (SDN) has emerged as an alternative 
-approach to traditional network configuration. Rather than organizing routing policy
-around a collection of configurations that compute routes via well-known distributed
+In recent years, Software-Defined Networking (SDN) has become an alternative 
+approach to traditional network configuration. Rather than defining routing policy
+through a collection of configurations that compute routes via well-known distributed
 protocols, users can directly program the forwarding tables of SDN-enabled switches via
-a centralized controller. It is the job of the controller then, which has a centralized view
-of the network to make sure that the routing policy is implemented correctly.
+a centralized controller.
 
@@
 For many of these challenges, researchers have looked at systems with multiple, interacting controllers, thus bringing back some aspects of distributed
-control planes~\cite{mccauley2013extending,onos}.
+control planes~\cite{onos,mccauley2013extending}.
 Second, current SDN systems focus only on configuration of intra-domain routing policy, forcing users to fall back to traditional methods for configuring inter-domain routing policy.
@@
 \para{Language Overview}
-We will demo our recent efforts to design and
-implement a new language called \sysname, which greatly simplifies the task of
-network management by allowing operators to specify their objectives
-using high-level, \emph{end-to-end} constraints on forwarding paths rather than writing explicit device-by-device configurations.
-
-The \sysname compiler rather than a human is responsible for bridging the gap
-between high-level goals and the low-level mechanisms.  More
-specifically, \sysname allows operators to describe the kinds of paths
-traffic may or may not follow, as well as the relative preferences of such paths.
+Our recent effort to simplify the task of programming distributed control planes has lead to the design and implementation of a new language called \sysname, which allows operators to specify their objectives using high-level, \emph{end-to-end} constraints on forwarding paths rather than writing explicit device-by-device configurations.
+%
+More specifically, \sysname allows operators to describe the kinds of paths traffic may or may not follow, as well as the relative preferences of such paths.
 Paths can reference both devices in the network as well as other networks that are not under the control of the operator.
 
-Taken together, these constraints allow users to write rich routing policies for the network.
-For example, then can require that two nodes be reachable, that traffic never leaves a particular part of the network, or that traffic is waypointed through middleboxes.
-Preferences allow operators to write policies that describe desired behavior after network failures occur, such as preferring to use routes through one neighboring network over another, or using particular paths only as backups for other paths.
+Taken together, these constraints allow users to describe a wide variety of rich routing policies.
+For example, a user can require that two nodes be reachable, that traffic never leaves a particular part of the network, or that traffic is waypointed through middleboxes.
+In addition, path preferences allow operators to write policies that describe the desired behavior of the network after failures occur, such as preferring to use routes through one neighboring network over another, or using particular paths only as backups for other paths when they become unavailable.
 
-The \sysname language also supports network operators by defining a
-set of common abbreviations for entering, leaving, and traversing
-the user network and provides abstractions for managing common features of
-control plane algorithms such as route aggregation.  
-Operators use familiar logical operations to build routes in a modular and 
-compositional manner from these primitives.
+%The \sysname language also supports network operators by defining a set of common abbreviations for entering, leaving, and traversing the user network and provides abstractions for managing common features of control plane algorithms such as route aggregation.
+Operators use familiar logical operations to build routes in a modular and compositional manner.
 
@@
 
-\sysname analyzes these user specifications and
-then compiles them to a collection of BGP configurations, so they may
-exploit existing distributed policy and fault tolerance mechanisms and
-execute on existing commodity hardware. During the compilation
-process, the compiler automatically synthesizes low-level configuration 
-primitives such as per-device import and export
-filters as well as BGP local preferences, MED attributes, and community tags.
-The compiler accomplishes this by first transforming the policy into a graph-based intermediate 
-representation that is more amenable to compilation and analysis.
+The \sysname compiler rather than a human is responsible for bridging the gap between high-level goals and the low-level mechanisms.
+\sysname analyzes these user specifications and then compiles them to a collection of BGP configurations, so they may exploit existing distributed policy and fault tolerance mechanisms and execute on existing commodity hardware.
+During the compilation process, the compiler automatically synthesizes low-level configuration primitives such as per-device import and export filters as well as BGP local preferences, MED attributes, and community tags.
+The compiler accomplishes this by first transforming the policy into a graph-based intermediate representation that is more amenable to compilation and analysis.
 
-An important feature of the language is that if possible, compiled
-configurations are guaranteed to implement the correct routing policy,
-regardless of any number of failures that might occur in the network.  
-If correct compilation is impossible, the compiler notifies the user 
-at compile time rather than waiting until the system is deployed in operation
-and failures have occurred in the network.
+An important feature of the language is that if possible, compiled configurations are guaranteed to implement the correct routing policy, regardless of any number of failures that might occur in the network.
+This guarantee does not mean that the implementation can, for example, ensure that two nodes are always reachable (\EG, when there is no path available in the topology), but rather that traffic is always forwarded according to the centralized policy, which may require dropping traffic when there is no path.
+If correct compilation is impossible, the compiler notifies the user at compile time rather than waiting until the system is deployed in operation and failures have occurred in the network.
 
-This guarantee does not mean that the implementation is always
-able to send traffic to its ultimate destination
-(e.g., in the case of a network partition), but rather that it always respects the
-centralized policy, which may include dropping traffic when there is no route.
-
-Overall, we believe the approach \sysname combines easy programmability of centralized control planes with the failure robustness and scalability of distributed control planes.
+Overall, we believe the approach taken with \sysname combines easy programmability of centralized control planes with the failure robustness and scalability of distributed control planes.
 
@@
 We thank R.
-Aditya, George Chen, and Lihua Yuan for feedback on the work and the SIGCOMM reviewers for comments on the paper.
-This work is supported in part by the National Science Foundation awards CNS-1161595 and CNS-1111520 as well as a gift from Cisco.
+Aditya, George Chen, and Lihua Yuan for feedback on the work and the SIGCOMM reviewers for comments on the work.
+This work is supported in part by the National Science Foundation awards CNS-1161595 as well as a gift from Cisco.
 

### 2017-03-12 paper/abstraction/paper.tex
add sosr extended abstract
more edits to section 7

@@
 
-\begin{algorithm}[t!]
-\caption{Checking safe neighbor preferences}
-\label{alg:failures}
-\begin{algorithmic}[1]
-\Procedure{$\leq$($N_1$, $N_2$)}{}
-  \If {$N_1 \not\approx N_2$} \Return false
-  \EndIf
-  \State $q \gets Queue()$
-  \State $q.Enqueue (N_1, N_2)$
-  \While {$!q.Empty()$}
-    \State $(m,n) \gets q.Dequeue()$
-    \If {$m \nleq_{rank} n$}
-      \Return false
-    \EndIf
-    \For {$n'$ in adjOut($PG$, $n$)}
-      \If {\big($\exists m' \in \textup{adjOut}(PG,m), m' \approx n'$\big)}
-        \If {$(m',n')$ not marked}
-          \State {mark $(m',n')$ as seen}
-          \State $q.Enqueue(m',n')$
-        \EndIf
-      \Else { \Return $false$}
-      \EndIf
-    \EndFor
-  \EndWhile \\
-  \hspace{\algorithmicindent} \Return true
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
 %=====================================================
@@
 
+\section{Template Generation}
+\label{sec:generation}
+
+At a high level, the translation from the PG representation to per-device templates that run the distributed BGP protocol involves the following steps: (1) Every BGP message is tagged to record the state of the product graph as messages are passed between routers.
+The tags allow BGP to only search for valid paths by dropping messages that do not correspond to any edge in the PG.
+(2) To ensure that BGP always converges to the \emph{most preferred} paths in the network, we must rank route advertisements for each router by giving them a preference such that, under those preferences, the network as a whole satisfies the \sysname policy's end-to-end network preferences.
+
+We introduce a simple, vendor-independent BGP configuration language called \mbgp and describe a compilation function that uses the inferred preference ordering to generate concrete configurations from a concrete topology, or templates from an abstract topology.
+Templates can then be soundly instantiated for a concrete network by replacing instances of abstract neighbors with the union of all concrete neighbors under the inverse homomorphism.
+We prove that concretization and compilation commute.
+By modifying compilation slightly we can further ensure that every configuration depends only on its immediate neighbors.
+This guarantees that any change made to the concrete topology will result in a minimal number of changes to the configurations.
+
+We now look at each of these steps in turn.
+
+\para{Tagging and Filtering}
+
+The BGP routing protocol standard allows for the use of \emph{community tags}, 32-bit integer tags that can be arbitrarily attached to, or removed from routing advertisements. 
+Community tags serve as a simple form of \emph{history}, and operators routinely use such tags to implement policy.
+For example, operators might record where an advertisment enters the network using community tags and then conditionally block the export of the advertisment later to other peers to prevent becoming a transit point between peers.
+
+The idea for template generation is to use community tags to record the state of the automata from the Product Graph in every BGP announcement and update these tags whenever messages are passed between routers.
+Such a tagging mechanism is used to ensure that BGP only considers paths that are allowed by the \sysname policy (\IE, paths in the PG).
+Routers will allow advertisments that correspond to an edge in the PG and block any advertisments that do not.
+
+For example, in the concrete PG in Figure~\ref{fig:example-compilation}, router S1 appears in two different PG nodes: $(S1,1,0)$ and $(S1,0,1)$.
+These nodes have two different peers that can send them messages in the PG: $(N1,0,0)$ and $(N2,0,0)$.
+Therefore, S1 will allow an advertisement from peer $N1$ and will also allow an advertisement from peer $N2$.
+If S1 uses the path advertised by neighbor N1, then it will add the tag $(1,0)$ to the advertisement before sending this to its neighbors A1 and A2.
+If S1 uses a path advertised from neighbor N2, then it will add the tag $(0,1)$ instead.
+Similarly, router A1 appears in two separate PG nodes.
+It will not block advertisements from S1 if they either have the $(1,0)$ tag or the $(0,1)$ tag attached.
+In either case, it will not modify the tag before exporting the route to its neighbors.
+
+%If A1 chooses a path with tag $(1,0)$ attached, then it will export the path to its neighbors without modifying the tag.
+If A1 chooses a path with tag $(0,1)$ attached, it will also export the path to its neighbors without modifying the tag.
+
+%\begin{algorithm}[t!]
+%\caption{Checking safe neighbor preferences}
+%\label{alg:failures}
+%\begin{algorithmic}[1]
+%\Procedure{$\leq$($N_1$, $N_2$)}{}
+%  \If {$N_1 \not\approx N_2$} \Return false
+%  \EndIf
+%  \State $q \gets Queue()$
+%  \State $q.Enqueue (N_1, N_2)$
+%  \While {$!q.Empty()$}
+%    \State $(m,n) \gets q.Dequeue()$
+%    \If {$m \nleq_{rank} n$}
+%      \Return false
+%    \EndIf
+%    \For {$n'$ in adjOut($PG$, $n$)}
+%      \If {\big($\exists m' \in \textup{adjOut}(PG,m), m' \approx n'$\big)}
+%        \If {$(m',n')$ not marked}
+%          \State {mark $(m',n')$ as seen}
+%          \State $q.Enqueue(m',n')$
+%        \EndIf
+%      \Else { \Return $false$}
+%      \EndIf
+%    \EndFor
+%  \EndWhile \\
+%  \hspace{\algorithmicindent} \Return true
+%\EndProcedure
+%\end{algorithmic}
+%\end{algorithm}
+
 \newcommand{\Con}{\text{con}}
@@
   \[ \begin{array}{l}
-     \mathrm{compile}_\mathrm{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
+     \mathrm{compile}_\mathrm{ABGP}( [(t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k)], G ) = \\
      ~~~~~ [~ l \rightarrow rc ~\vert~ l \in \mathrm{internal}(G.V), ~rc = \mathrm{append}_i~  \\
@@
      \mathrm{compile}( p_1, \dots, p_k, G) = \\
-     ~~~~~~ \mathrm{compile}_\mathrm{ABGP}(\mathrm{compile}_\mathrm{PG}(p_1,G), \dots, \mathrm{compile}_\mathrm{PG}(p_k,G), G) \\
+     ~~~~~~ \mathrm{compile}_\mathrm{ABGP}([\mathrm{compile}_\mathrm{PG}(p_1,G), \dots, \mathrm{compile}_\mathrm{PG}(p_k,G)], G) \\
   \end{array} \]%
@@
 
-\section{Template Generation}
-\label{sec:generation}
-
-At a high level, the translation from the PG to per-device templates that run the distributed BGP protocol involves the following high-level ideas: (1) Every BGP message is tagged to record the state of the product graph as messages are passed between routers.
-The tags allow BGP to only search for valid paths in the PG by dropping messages that do not correspond to any edge in the PG.
-(2) To ensure BGP always finds the \emph{most preferred} paths in the network, we must rank messages for each router in the network by giving them a preference such that, under those preferences, the network as a whole satisfies the \sysname policy's end-to-end network preferences.
-(3) We introduce a simple, vendor-independent BGP configuration language called mBGP and describe a compilation function that uses the inferred preference ordering to generate concrete configurations from a concrete topology, or templates from an abstract topology.
-(4) Templates can then be soundly instantiated for a concrete network by replacing instances of abstract neighbors with the union of all concrete neighbors under the homomorphism.
-We prove that concretization and compilation commute.
-(5) By modifying compilation slightly we can further ensure that every configuration depends only on its immediate neighbors.
-This guarantees that any change made to the concrete topology will result in a minimal number of changes to the configurations.
-
-We now look at each of these steps in turn.
-
-\para{Tagging and Filtering}
-
-The BGP routing protocol standard allows for the use of \emph{community tags}, collections of 32-bit integer tags that can be attached or removed arbitrarily from routing advertisements. 
-Community tags serve as a simple form of \emph{memory}, and operators routinely use such tags to implement policy (e.g., to prevent transit traffic by recording where a message enters the network and blocking upon egress accordingly).
-
-The idea for template generation is to use community tags to record the state of the automata from the Product Graph in every BGP announcement and update these tags whenever messages are passed between routers.
-Such a tagging mechanism is used to ensure that BGP only considers paths that are allowed by the \sysname policy, routers will allow advertisments that correspond to an edge in the PG and block any advertisments that do not.
-
-For example, in the concrete PG in Figure~\ref{fig:example-compilation}, router S1 appears in two different PG nodes: $(S1,1,0)$ and $(S1,0,1)$.
-These nodes have two different peers than can send them messages in the PG: $(N1,0,0)$ and $(N2,0,0)$.
-Therefore, S1 will not block an advertisement from peer $N1$ and will also not block an advertisement from peer $N2$.
-If S1 uses the path advertised by neighbor N1, then it will add the tag $(1,0)$ to the advertisement before sending this to its neighbors A1 and A2.
-If S1 uses a path advertised from neighbor N2, then it will add the tag $(0,1)$ instead.
-Similarly, router A1 appears in two separate PG nodes.
-It will not block advertisements from S1 if they either have the $(1,0)$ tag or the $(0,1)$ tag attached.
-If A1 chooses a path with tag $(1,0)$ attached, then it will export the path to its neighbors without modifying the tag.
-If A1 chooses a path with tag $(0,1)$ attached, it will also export the path to its neighbors without modifying the tag.
-
 \para{Preference Search}
 
-Tagging and filtering according to the PG with community values in BGP forces the protocol to only search for paths to the destination that are allowed by the policy (\IE are paths in the PG).
+Tagging and filtering according to the PG with community values in BGP forces the protocol to only consider paths to the destination that are allowed by the policy.
 However, finding \emph{some} path to the destination is not enough.
@@
 On the other hand, if the S1-N1 link fails, then the best available path is through N2.
-
-To enforce correct network-wide preferences, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routers learned from another neighbor.
-The challenge is to find a collection of device-local preferences that correctly enforce the network-wide preferences from the policy for all failures.
-
-The idea then is to search for such a device-local preference function for each router that totally order advertisements from different neighbors (possibly with different tags).
-For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, S1 should prefer a message it hears from N1 over N2.
-Similarly, A1 should prefer routes tagged with $(1,0)$ over those with $(0,1)$.
-Intuitively, S1 should prefer a message from N1 because it results in an accepting state for automata 1, which is more preferred than automata 2.
-Further, it can result in downstream routers such as A1 receiving a message in a more preferred state $(A1,1,0)$ instead of $(A1,0,1)$.
-
-In general, because BGP is distributed, each router does not have a view of the entire network when choosing which path to use and finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem.
-\Propane introduced a conservative search strategy for determining route preferences that works well in practice.
-To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:
-
-\begin{defn}
-Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $\min (\Pref(m)) \geq \min (\Pref(n))$ or $\Pref(n) = \emptyset$.
-Intuitively $m \geq_{rank} n$ means that paths ending at node $m$ are no better than paths ending at $n$.
-%
-\end{defn}
-\noindent
-%
-
-%\begin{defn}
-The PG can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge.
-That is, $m\overset{l}{\rightarrow}n$ if there is an edge $(m,n)$ in the PG and $\Topo{n} = l$.
-%\end{defn}
-%
-For example, in the concrete PG we would have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.
-
-\begin{defn}
-We write $m \leq m'$ if the subgraph reachable from $m$ and $m'$ respectively form a simulation relation with respect to $\geq_{rank}$.
-\end{defn}
-
-The existence of multiple nodes in the PG for the same topology location (\EG, $(S1,1,0)$ and $(S1,0,1)$) indicates that S1 can receive advertisements in different contexts and must choose between messages received in these different contexts.
-Node $m$ is preferred to $m'$ if, $m' \geq_{rank} m$ and, transitively, for each neighbor of $m'$, $m$ has a corresponding neighbor that is more preferred.
-Algorithm~\ref{alg:failures} shows a simple procedure for determining if a nPG ode $N1$ can safely be preferred to a PG node $N2$.
-
-For each router, its corresponding PG nodes are then sorted according the the $\leq$ operator.
-If $\leq$ defines a total order on PG nodes, then the compiler can simply prefer advertisements from peers of node $m$ over those of $m'$ whenever $m' \leq m$.
-This condition ensures that BGP devices will converge to the most preferred paths in the network even when failures occur.
-However, if $\leq$ does not form a total order, then the policy is rejected as being potentially unsafe under some failure conditions.
-
-%
-For example, in the concrete PG the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation.
-This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$.
-Therefore, advertisements received at $S1$ with tag $(1,0)$ must be preferred to those received at $S1$ with tag $(0,1)$.
-%
-Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds.
-
-\begin{lem}
-\label{lem:preference}
-$m \leq m'$ in the concrete PG iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract PG.
-\end{lem}
-
-Lemma~\ref{lem:preference} tells us that inferring preferences for the abstract PG before template instantiation is equivalent to inferring preferences for an already-instantiated concrete PG.
 
@@
 
-\para{BGP configurations}
+To enforce correct network-wide preferences, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routers learned from another neighbor.
+The challenge is to find a collection of device-local preferences that correctly enforce the network-wide preferences from the policy for all failures.
+
+The idea then is to search for such a device-local preference function for each router that totally orders advertisements from different neighbors (possibly with different tags).
+For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, S1 should prefer a message it hears from N1 over N2.
+Similarly, A1 should prefer routes tagged with $(1,0)$ over those with $(0,1)$.
+Intuitively, S1 should prefer a message from N1 because it results in an accepting state for automata 1, which indicates a more preferred path.
+Further, it can result in downstream routers such as A1 obtaining a route that is accepting for automata 1 as well, \IE $(A1,1,0)$ instead of $(A1,0,1)$.
+
+In general, because BGP is distributed, each router does not have a view of the entire network when choosing which path to use, and finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem.
+\Propane introduced a conservative search strategy for determining route preferences that works well in practice.
+To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:
+
+\begin{defn}
+Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $\min (\Pref(m)) \geq \min (\Pref(n))$ or $\Pref(n) = \emptyset$.
+Intuitively $m \geq_{rank} n$ means that paths ending at node $m$ are no better than paths ending at $n$.
+%
+\end{defn}
+\noindent
+%
+
+%\begin{defn}
+The PG can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge.
+That is, $m\overset{l}{\rightarrow}n$ if there is an edge $(m,n)$ in the PG and $\Topo{n} = l$.
+%\end{defn}
+%
+For example, in the concrete PG we would have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.
+
+\begin{defn}
+We write $m \leq n$ if the subgraph reachable from $m$ and $n$ respectively form a simulation relation with respect to $\geq_{rank}$.
+\end{defn}
+
+More specifically, we say that $m \leq n$ if $m \geq_{rank} n$ and for every transition $n\overset{l}{\rightarrow}n'$ from PG node $n$ there exists a transition $m\overset{l}{\rightarrow}m'$ from $m$ and $m' \leq n'$.
+%
+Intuitively, the $m \leq n$ relation means advertisements received for node $m$ can safely be preferred over those received for node $n$ after accounting for the network-wide impact of the choice.
+For example in Figure~\ref{fig:example-compilation}, S1 can receive advertisements in two different contexts ($(S1,1,0)$ and $(S1,0,1)$) and must choose between messages received in these different contexts.
+Advertisements are preferred in state $(S1,1,0)$ because it results in a better path for S1 ($(S1,0,1) \geq_{rank} (S1,1,0)$) and downstream routers such as A1 will also obtain paths no worse than if S1 had choosen $(S1,1,0)$ instead.
+The policy is guaranteed to be safe from failures because if a link fails in the topology, then $m \leq n$ will still hold since any transition that becomes unusable for $m$ also becomes unusable for $n$.
+That is $m \leq n$ before the failure implies $m \leq n$ after the failure.
+
+For each router, its corresponding PG nodes are then sorted according the the $\leq$ operator.
+If the operator defines a total order on PG nodes, then the compiler can simply prefer advertisements from peers of node $m$ over those of $n$ whenever $n \leq m$.
+However, if $\leq$ does not form a total order, then the policy is rejected as being potentially unsafe under some failure conditions.
+
+%
+For example, in the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation.
+This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$.
+Therefore, advertisements received at $S1$ with tag $(1,0)$ must be preferred to those received at $S1$ with tag $(0,1)$.
+%
+Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds.
+
+\begin{lem}
+\label{lem:preference}
+$m \leq n$ in the concrete PG iff $f_{pg}(m) \leq f_{pg}(n)$ in the abstract PG.
+\end{lem}
+
+Lemma~\ref{lem:preference} tells us that inferring preferences for the abstract PG before template instantiation is equivalent to inferring preferences for an already-instantiated concrete PG.
+
+\para{mBGP}
+
+\para{Compilation}
 

### 2017-03-12 paper/abstraction/paper.tex
more edits to section 7. Remove paragraph widows

@@
 
-\authorinfo{Ryan Beckett}{Princeton}{}
-\authorinfo{Ratul Mahajan}{Microsoft}{}
-\authorinfo{Todd Millstein}{UCLA}{}
-\authorinfo{Jitendra Padhye}{Microsoft}{} 
-\authorinfo{David Walker}{Princeton}{}
-
-%\author{%
-%Ryan Beckett\\
-%  \affaddr{Princeton}
-%  %\\
-%  %\email{rbeckett@princeton.edu}
-%\and
-%Ratul Mahajan\\
-%  \affaddr{Microsoft}
-%  %\\
-%  %\email{ratul@microsoft.com}
-%\and
-%Todd Millstein\\
-%  \affaddr{UCLA}
-%  %\affaddr{University of California, Los Angeles}
-%  %\\
-%  %\email{todd@cs.ucla.edu}
-%\and
-%Jitendra Padhye\\
-%  \affaddr{Microsoft}
-%  %\\
-%  %\email{padhye@microsoft.com}
-%\and
-%David Walker\\
-%  \affaddr{Princeton}
-%  %\\
-%  %\email{dpw@princeton.edu}
-%}
+\authorinfo{Ryan Beckett}{Princeton University}{rbeckett@cs.princeton.edu}
+\authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
+\authorinfo{Todd Millstein}{University of California, Los Angeles}{todd@cs.ucla.edu}
+\authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
+\authorinfo{David Walker}{Princeton University}{dpw@cs.princeton.edu}
 
@@
 networks, \sysname synthesizes configurations two orders of magnitude
-faster than systems that operate over concrete topologies.
-
-%\ryan{Copied from conclusion for reference}
-%We develop \sysname, the first system that can generate device configuration templates for large networks from high-level specifications of network topology and policy.
-\sysname is based on new abstractions for capturing parameterized network topologies, and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance.
-Our analysis operates entirely in the abstract domain and guarantees correctness for all concrete instantiations of the topology.
-Experiments with many types of real-world topologies and policies show that our abstractions and analysis are precise and that, for large networks, configuration synthesis is two orders of magnitude faster than systems that operate over concrete topologies.
-
-%We develop techniques for automated reasoning about end-to-end properties of
-%abstract network topologies, and embody them in a network synthesis tool called
-%\sysname. \sysname allows network operators to write a high-level routing policy
-%over an abstraction of their network topology. From such a specification,
-%\sysname synthesizes a collection of router configurations running the
-%distributed Border Gateway Protocol (BGP) that are guaranteed to implement the
-%centralized routing policy for any concrete instantiation of the abstract
-%topology, and for any combination of network failures in the resulting concrete
-%topology.
-%
-%Additionally, properties proven by \sysname over the abstract topology, such as
-%reachability between a source and destination under k-failures, are also
-%guaranteed to hold under any concrete instantiation of the abstract topology.
-%
-%Something something, expandable/incremental networks. Something something scales
-%compilation to large networks. Something something, templates easier to
-%understand.
-%These strong guarantees allow operators to reason about the routing behavior of
-%their network at a high-level abstraction, while also generating an efficient
-%low-level implementation.
-%
-%In addition, operators are able to safely change or expand their network in any
-%way, so long as the new resulting topology also respects the abstraction.
-%
-%We test \sysname out on ... blah blah blah
+faster than systems that operate on concrete topologies.
 
@@
 %=====================================================
-
-%\vspace{0.1in} \noindent \textbf{CCS Concepts}\\ $\bullet$ Networks
-%$\rightarrow$ {\em Network control algorithms; Network reliability; Network
-%management;} $\bullet$ Software and its engineering $\rightarrow$ {\em
-%Automated static analysis; Domain specific languages}
-
-%\vspace{0.1in} \noindent \textbf{Keywords}\\ \Propane; Domain-specific Language;
-%BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems
 
@@
 work for the current topology, may or may not work for future
-topologies. Problems that occur may cause operators to make small, non-uniform, one-off changes to particular routers,
+topologies. Problems that occur may cause operators to make small, non-uniform changes to particular routers,
 which defeats the purpose of a template system.  An even worse situation occurs when
-operators feel obligated to update many (non-local) devices to extend or change their network.  
+operators feel obligated to update many devices to extend or change their network.  
 Such network-wide configuration changes entail a great deal of risk and may be highly
@@
 \sysname
-allows operators to input \emph{abstract network topologies} in terms of roles
+allows operators to input \emph{abstract topologies} in terms of roles
 and their connectivity. For instance, they may specify roles for ``top-of-rack''
@@
 for interdomain routing and it is also commonly used
-within data centers due to its scalability properties.  However, it is far from the only control
-plane protocol; synthesis of configurations for other common protocols such as OSPF is beyond the 
+within data centers due to its scalability.  However, it is far from the only control
+plane protocol; synthesis of configurations for other protocols such as OSPF is beyond the 
 scope of this paper.
@@
 During synthesis, our compiler performs an important analysis over abstract topologies to determine
-the fault tolerance properties of the specified policy.  This analysis determines the
-number of failures require to disconnect one abstract location from another given the constraints
-specified by the abstract topology.  The analysis is specified by a collection of inference rules
-and we prove these inference rules are sound: any concrete instance of the abstract topology will
-adhere to the given fault tolerance property. \dpw{Ryan: check this.}
+the fault tolerance properties of the specified policy.  This analysis determines a worst-case 
+lower bound on the number of link failures require to disconnect one abstract location from another 
+given the constraints specified by the abstract topology. Any concrete instance of the abstract topology will adhere to the given fault tolerance property.
 %% first analysis determines whether a user policy can be implemented correctly using BGP in
@@
 %evolution.
-\item Implementation and evaluation of the \sysname compiler that generates
+\item Implementation and evaluation of a \sysname compiler that generates
 provably-correct BGP templates and is much faster
@@
   \label{fig:syntax}
-  %\vspace{-1.4em}
+  %\vspace{-0.8em}
 \end{figure}%
@@
   \label{fig:inference-rules}
-  \vspace{-.8em}
+  \vspace{-1em}
 \end{figure*}
@@
 However, existing tools~\cite{condor,propane} reason about fault-tolerance only for concrete topologies.
-\sysname provides substantially stronger guarantees: all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy.
+\sysname provides stronger guarantees: all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy.
 
@@
 %
-We frame satisfying the fault-tolerance policy provided by the user as an analysis problem over the structure of the PG.
+We frame satisfying the fault-tolerance requirements as an analysis problem over the structure of the PG.
 In particular, we develop an analysis that uses information embedded in the abstract topology to infer bounds on the number of edge-disjoint paths between pairs of concrete nodes.
@@
   \begin{minipage}[t]{.47\linewidth}
-  \hdr{ABGP Syntax}{}
+  \hdr{mBGP Syntax}{}
   \vspace*{-1\baselineskip}
@@
      rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
-     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\%
+     mbgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{mbgp policy} \\%
   \end{array} \]%%
@@
   \begin{minipage}[t]{.49\linewidth}
-  \hdr{Compilation to ABGP}{}
+  \hdr{Compilation to mBGP}{}
   \vspace*{-1\baselineskip}
@@
   \[ \begin{array}{l}
-     \mathrm{compile}_\mathrm{ABGP}( [(t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k)], G ) = \\
+     \mathrm{compile}_\mathrm{mBGP}( [(t_1,PG_1,pref_1), \dots, (t_k,PG_k,pref_k)], G ) = \\
      ~~~~~ [~ l \rightarrow rc ~\vert~ l \in \mathrm{internal}(G.V), ~rc = \mathrm{append}_i~  \\
@@
      ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathrm{adjOut}(PG_i,m) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma = \mathrm{ord}_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \mathrm{pref}_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~] \\
      \\
      \mathrm{compile}( p_1, \dots, p_k, G) = \\
-     ~~~~~~ \mathrm{compile}_\mathrm{ABGP}([\mathrm{compile}_\mathrm{PG}(p_1,G), \dots, \mathrm{compile}_\mathrm{PG}(p_k,G)], G) \\
+     ~~~~~~ \mathrm{compile}_\mathrm{mBGP}([\mathrm{compile}_\mathrm{PG}(p_1,G), \dots, \mathrm{compile}_\mathrm{PG}(p_k,G)], G) \\
   \end{array} \]%
@@
 %
-Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds.
+Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds. This leads to the following observation:
 
@@
 \para{mBGP}
+To characterize compilation we first introduce a simple, vendor independent configuration language for the BGP protocol called \mbgp.
+The syntax for \mbgp is shown in Figure~\ref{fig:concretization} (left).
+An \mbgp policy consists of a sequence of router configurations (one for each internal topology location $l$).
+A router configuration is an ordered sequence of a predicate describing the traffic, and a predicate configuration.
+A predicate is either a template variable $\$\mathrm{x}$ or a prefix.
+A predicate configuration is a collection of match action statements, where each match action indicates that the router will match advertisements from any of a set of peers $ns_1$ with a particular community tag $c_1$ with local preference $d$, before exporting the route to another set of peers $ns_2$ with a new community tag $c_2$.
 
@@
 
-%By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations.
-In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
-Figure~\ref{fig:bgp-configs} (left) shows part of the final configuration for spine routers for the concrete and abstract policies in a vendor-neutral syntax.
+Figure~\ref{fig:concretization} (right) defines compilation from \sysname to \mbgp.
+It proceeds by compiling constraints $p_i$ in the original \sysname policy to a tuple of: the predicate $t_i$, the product graph $PG_i$, and the preference function $pref_i$.
+These tuples are passed the the $\mathrm{compile}_\mathrm{mBGP}$ function, along with the network topology $G$.
+For each internal router in the topology $l$, and each predicate $t_i$ in the \sysname policy, compilation goes through each node $m$ for $l$ in $PG_i$, and groups the inbound neighbors of $m$ by tag ($q_n$) into sets ($in$).
+It allows imports from these neighbors before exporting to the outbound neighbors of $m$.
+The local preference for these imports is given by $\mathrm{pref}_i(m)$.
+
+Figure~\ref{fig:bgp-configs} (left) shows part of the generated \mbgp configuration for spine routers for both the concrete and abstract policies.
+For brevity, we using the symbol ($*$) to denote the set of all neighbors and omit tags when irrelevant.
 %
@@
 For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers.
-The concrete configurations have a similar configuration for each local and global prefix.
-
-%\vspace{2em}
-%\begin{figure*}[t!]\small%
-
-%  \hrulefill%
-%  \vspace{1em}%
-
-%  \begin{minipage}[t]{.46\linewidth}
-%  \hdr{ABGP Syntax}{}
-%  \vspace*{-1\baselineskip}
-%  %
-%  \[ \begin{array}{rclr}
-%     d    &   & & \textit{integer} \\
-%     c    &   & & \textit{community} \\
-%     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
-%     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
-%     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
-%     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
-%     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
-%     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\%
-
-%  \end{array} \]%%
-
-%  \end{minipage}
-%  %
-%  %
-%  \begin{minipage}[t]{.5\linewidth}
-%  \hdr{Compilation}{}
-%  \vspace*{-1\baselineskip}
-%  %
-%  \[ \begin{array}{l}
-%     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
-%     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
-%     ~~~~~~~~~ l \in internal(G.V), \\
-%     ~~~~~~~~~ rc = \mathit{append}_i~  \\
-%     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-%     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
-%     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_i,m), \\
-%     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
-%     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
-%     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
-%     \\
-%     \text{compile}( p_1, \dots, p_k, G) = \\
-%     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
-%  \end{array} \]%
-%  \end{minipage}%
-
-%  \vspace{1em}
-%  \vspace{1em}%
-
-%  \vspace*{-2\baselineskip}
-%  \begin{minipage}[t]{1.01\linewidth}
-%  \hdr{Policy Concretization}{}
-%  \vspace*{-2\baselineskip}
-%  %
-%  \[ \begin{array}{lcl}
-%     \\
-%     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
-%     \Con(l, \Gamma, f)              &=& \Sigma_i ~ f_i^{-1}(l) \\
-%     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
-%     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
-%     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
-%     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\%
-
-%     \Con(\Pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
-%          \Pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\%
-
-%     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&%
-
-%         [~ \Pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~, \\%
-
-%         & & ~~~~~~~~~~~~~~~ \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (\Pfx,l) \in \Gamma(x) ~]  \\%
-
-%     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\%
-
-%  \end{array} \]%
-%  \end{minipage}%
-
-%  \vspace{1em}
-%  \vspace{1em}%
-
-%  \begin{minipage}[t]{\linewidth}
-%  \hdr{ABGP Concretization}{}
-%  \vspace*{-2\baselineskip}
-%  %
-%  \[ \begin{array}{lcl}
-%     \\
-%     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G)
-%        & = &
-%        \mathit{append}_i~ [~ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) ~]
-%        \\
-%     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
-%        & = &
-%        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
-%        \\
-%     \Con(\Pfx \rightarrow {pc},\ell,\Gamma,f,G)
-%        & = &
-%        \Pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
-%        \\
-%     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G)
-%        & = &
-%        [~ \Pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (\Pfx, l) \in \Gamma(x) ~]
-%        \\
-%     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G)
-%        & = &
-%        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
-%        \\%
-
-%     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G)
-%        & = & \textbf{if}~ ns_1 = \{\text{start}\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
-%        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)%
-
-%        \\
-%     \Con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G)
-%        & = &
-%        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
-%        \\
-%  \end{array} \]%
-%  \end{minipage}%
-
-%  \vspace{1em}
-%  \hrulefill%
-%  \vspace{1em}%
-
-%  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
-%  \label{fig:concretization}
-%\end{figure*}%
+The concrete configurations for S1 and S2 obtained from compilation for the concerete PG from Figure~\ref{fig:example-compilation} have a similar structure for each local and global prefix where local routes are reflected downward, while global routes are advertised to all peers.
 
 \para{Concretization}
-Observe that the spine template and concrete configurations are structured similarly.
-We formalize this observation by defining a simple, vendor-neutral language for BGP configurations called \mbgp and formally define compilation for policies over both concrete and abstract topologies to \mbgp.
-In addition we define two concretization ($con$) functions that translate an abstract \sysname policy and \mbgp configuration to a concrete \sysname policy and concrete \mbgp configuration respectively.
+The similar structure between the spine template and concrete configurations is not a coincidence.
+We formalize this observation by defining a two concretization function ($con$), one for \sysname policies and another for \mbgp policies.
+%
 Concretization takes a context $\Gamma : \mathit{Var} \rightarrow 2^{\mathit{Prefix} \times V}$ that maps each template variable to a set of pairs of a concrete prefix and topology location where the prefix is owned.
-Intuitively, the spine template is concretized by replacing each abstract role with the set of all concrete routers that map to that role and each prefix template variable with a new entry in the configuration for each individual prefix provided by the context $\Gamma$.
+
+Both concretization functions traverse the policy and substitute each instance of a topology loction $l$ in the template policy with the set of all concrete locations that map to $l$, given by the inverse homomorphism $f^{-1}(l) = \{l' ~\vert~ f(l') = l \}$.
+Additionally, whenver a pair $(pfx,l) \in \Gamma(x)$, then a new entry is added to the concretized policy where $pfx$ replaces $\$\mathrm{x}$ and adds the constraint that traffic ends at $l$ ($\CD{\End(l)}$).
+%
+For example, the spine template in Figure~\ref{fig:bgp-configs}, is obtained by substituting $\{ A1,A2 \}$ for $AG$ and $\{ A3,A4 \}$ for $AL$ and by also replacing the entry for {\small \$GP} with entries for {\small GP1} and {\small GP2} given by the context (\EG, a database).
+
 Our main theoretical result is that the compilation and concretization functions commute:
@@
 \vspace{-.6em}
-Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix.
+Full definitions of concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix.
 
@@
 
-However, template variables tell us exactly where this kind of change can happen.
-The only way in which the spine routers depend on anything non-local is in the match on prefix template variables.
-Therefore, we can prevent modifications to the spine routers' configurations by associating a new unique community tag for template variable {\small \$GP} and then replacing each match on {\small \$GP} with a test on the new community tag.
+More generally, each configuration template depends on two things: the routing policy and the abstract topology.
+If the policy remains fixed and a change to the concrete topology preserves the topology abstraction, then the generated templates will not change.
+Further, each template has policy only in terms of its immediate neighbors.
+Because abstract neighbors are substituted for concrete neighbors during concretization, it would seem as though the generated configurations will also only depend on their concrete neighbors.
+However, prefix template variables allow for the possibility of introducing new prefixes in the context $\Gamma$ after a change.
+For example, when adding a new ToR router with its own unique prefix, the spine configurations would need to know about this new prefix.
+%
+In fact, the only way in which the concrete configurations can depend on anything non-local is when instantiating prefix template variables.
+
+To prevent the non-local changes induced by template variables, we modify compilation in the following ways.
+First, we associate a new unique community tag for each template variable (\EG, {\small \$GP}), and add this tag where the route is originated (\EG, role TG).
+Then, template variable tests elsewhere in the policy are replaced with a new test on this tag.
+Finally, during template instantiation the tags are left unmodified.
+%Therefore, we can prevent modifications to the spine routers' configurations by associating a new unique community tag for template variable {\small \$GP} and then replacing each match on {\small \$GP} with a test on the new community tag.
 The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can match against it.
-Figure~\ref{fig:bgp-configs} (right) shows several templates after the transformation.
+Figure~\ref{fig:bgp-configs} (right) shows the spine and ToR templates after this transformation.
 
@@
 We evaluate the expressiveness of \sysname's topology abstractions and the precision of its fault-tolerance analysis on a range of network topologies found in production networks and in the networking literature.
-We characterize expressiveness by checking if our abstractions allow the topologies to evolve arbitrarily or certain aspects must be fixed (i.e., cannot be symbolic).
-We measure precision by checking if we find a tight lower-bound on fault-tolerance (\IE, there exists a concrete network with that fault-tolerance level).
+We characterize expressiveness by checking if the abstractions allow the topologies to evolve arbitrarily or certain aspects must be fixed (\IE, cannot be symbolic).
+We measure precision by checking if we find a tight lower-bound on fault-tolerance (\IE, there is a concrete network with that fault-tolerance).
 
@@
 
-  \vspace{1.4em}
+  \vspace{1em}
   \begin{minipage}[t]{\linewidth}
     \hdr{BCube}{}
-    \vspace{.3em}
+    \vspace{.1em}
     \includegraphics[width=\linewidth]{figures/bcube}
@@
 We evaluate generation time in \sysname both with and without abstraction using routing policy for backbone and data center networks inspired by configurations obtained from a large cloud provider.
-For both types networks, we fix the routing policy and scale the size of the underlying topology.
+For both types networks, we fix the routing policy and scale the size of the topology.
 
@@
 In contrast, all router configurations were modified with \Propane because it heavily uses prefix lists which are sensitive to such changes.
-While \Propane may be made friendlier to network evolution (e.g., prefix lists are unnecessary at aggregation routers), its fundamental limitation will remain because it does not understand roles and the network's underlying structure that \sysname leverages.
+While \Propane may be made friendlier to network evolution (e.g., prefix lists are unnecessary at aggregation routers), its fundamental limitation will remain because it does not understand roles and the network's structure that \sysname leverages.
 

### 2017-03-12 paper/abstraction/paper.tex
tweaks for length

@@
 \authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
-\authorinfo{Todd Millstein}{University of California, Los Angeles}{todd@cs.ucla.edu}
+\authorinfo{Todd Millstein}{UCLA}{todd@cs.ucla.edu}
 \authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
@@
 
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=\columnwidth]{figures/templates}
-  \caption{Idealized small configuration component for the data center spine role based on router templates from a large cloud provider (\IE, macros over gobbledygook).}
-  \label{fig:templates}
-  \vspace{-.8em}
-\end{figure}
-
 We demonstrate the difficulty of configuring networks today using the data center example in Figure~\ref{fig:example}.
@@
 $(8)$ no loss in connectivity after any single-link failure.
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=\columnwidth]{figures/templates}
+  \caption{Idealized small configuration component for the data center spine based on templates from a cloud provider.}
+  \label{fig:templates}
+  \vspace{-1em}
+\end{figure}
 
@@
 
-  \caption{Abstract BGP syntax (left), and compilation from product graphs (right).}
+  \caption{mBGP syntax (left), and compilation from product graphs (right).}
   \label{fig:concretization}
+  \vspace{-.8em}
 \end{figure*}%

### 2017-03-13 paper/abstraction/paper.tex
more edits, shrinking

@@
 \newcommand{\Topo}[1]{\ensuremath{{\mathrm{topo}}(#1)}}
-\newcommand{\Pref}{\ensuremath{\mathrm{pref}}}
+\newcommand{\Pref}{\ensuremath{\mathrm{rank}}}
 
@@
   \includegraphics[width=2.5in]{figures/example}
+  \vspace{-.8em}
   \caption{An example data center network.}
   \label{fig:example}
-  \vspace{-1em}
+  \vspace{-.8em}
 \end{figure}
@@
   \includegraphics[width=2.5in]{figures/example2}
+  \vspace{-.8em}
   \caption{A modified version of the example in Figure~\ref{fig:example}.}
   \label{fig:example2}
-  \vspace{-1em}
+  \vspace{-.8em}
 \end{figure}
@@
   \label{fig:templates}
-  \vspace{-1em}
+  \vspace{-.8em}
 \end{figure}
@@
 Figure~\ref{fig:templates} shows an example of what a small component of a template for the spine role in the two data centers might look like.
-The template has parameters for various aspects of the configuration (\EG, neighbor list, local prefixes) and are compiled to low-level device configurations by instantiating the parameters using the network topology and a database of network information.
+The template has parameters for various aspects of the configuration (\EG, neighbor list, local prefixes) and is compiled to low-level device configurations by instantiating the parameters using the network topology and a database of network information.
 
@@
   \includegraphics[width=\columnwidth]{figures/example3}
-  \vspace{-2em}
+  \vspace{-2.2em}
   \caption{An abstraction for the network in Figure~\ref{fig:example}.}
   \label{fig:example3}
-  \vspace{-1em}
+  \vspace{-.8em}
 \end{figure}
@@
 
-Our topology abstractions can also capture concrete topologies; there will be a one-to-one correspondence between abstract and concrete nodes (and edges).
-This ability enables operators to define complex networks in which they expect some (e.g., legacy) parts of the network to not evolve and others to evolve.
+Our topology abstractions can also capture concrete topologies; there will be a one-to-one correspondence between abstract and concrete nodes/edges.
+This allows operators to define complex networks in which some (e.g., legacy) parts of the network can not evolve while others can.
 %It also means that our compiler subsumes those that operate only over concrete topologies.
@@
 The second line introduces a prefix \emph{template} variable $\CD{\$GP}$.
-It says that traffic for each global prefix associated with the variable should follow a path that ends at its corresponding destination router in the $\CD{TG}$ role.
+Template variables represent multiple instances of a rule for different concrete prefixes that can be provided by an external source (\EG, a database).
+The line says that traffic for each global prefix associated with the variable should follow a path that ends at its corresponding destination router in the $\CD{TG}$ role.
 As we will see in \S\ref{sec:language}, constraints like $\CD{\End(TG)}$ are just syntactic sugar for regular expressions describing network paths.
@@
 %
-The final rule matches all other IP prefix destinations and allows traffic to follow a path that leaves the data center, ending at some outside location, through neighbors $\CD{N1}$ or $\CD{N2}$ with a preference for leaving through $\CD{N1}$.
+The final rule matches all other IP prefix destinations and allows traffic to follow a path that leaves the data center, ending at some external role ($\CD{\Out}$), through neighbors $\CD{N1}$ or $\CD{N2}$ with a preference for leaving through $\CD{N1}$.
 The $\CD{\Prefer}$~symbol indicates that traffic should satisfy the constraint on the left and resort to the backup (right) only when that is not possible due to network failures.%
@@
 The Local policy adds the $\CD{\Always(\In)}$ constraint for each local prefix described by the template variable $\CD{\$LP}$.
-This constraint ensures that traffic follows a path that matches an internal location (\IE, in the data center) at each hop of the path.
+This constraint ensures that traffic follows a path that matches an internal role (\IE, in the data center) at each hop of the path.
 %
@@
 Routing & Local & NoTransit &
-NoValley & \Agg(PG, \In -> \Out)
+NoValley & \Agg(GP_AGG, \In -> \Out)
 \end{code}
@@
 This instructs \sysname to satisfy the conjunction of all the constraints.
-It also declares that we want to perform route aggregation, as covering prefix PG, for global prefixes at the border of the data center (\IE, along any edge that connects the inside of the data center to the outside).
+It also declares that we want to perform route aggregation, with covering prefix {\small GP\_AGG}, for global prefixes at the border of the data center (\IE, along any edge that connects the inside of the data center to the outside).
+In this case, {\small GP\_AGG} is declared as a concrete prefix rather than a template because a single aggregate prefix will be used to summarize all less-specific prefixes.
 
@@
      x       &\in& \textit{Variables} \\
+     l       &\in& \textit{Topology Locations} \\
      pol     &::=& p_1, \dots, p_n & \text{Policy} \\
@@
   \end{minipage}
-  \vspace{-.3em}
+  \vspace{-.4em}
   \caption{\sysname core syntax.}
   \label{fig:syntax}
-  %\vspace{-0.8em}
+  \vspace{-0.8em}
 \end{figure}%
@@
     \vspace{1em}
-    \includegraphics[width=.7\columnwidth]{figures/topology-con}
+    \includegraphics[width=.62\columnwidth]{figures/topology-con}
   \end{minipage}%
@@
     \vspace{1em}
-    \includegraphics[width=.57\columnwidth]{figures/topology-abs}
+    \includegraphics[width=.505\columnwidth]{figures/topology-abs}
   \end{minipage}%
@@
     \hdr{Concrete Product Graph}{}
-    \includegraphics[width=.9\columnwidth]{figures/pg-con}
+    \includegraphics[width=.8\columnwidth]{figures/pg-con}
   \end{minipage}%
@@
   \hdr{Abstract Product Graph}{}
-    \includegraphics[width=.88\columnwidth]{figures/pg-abs}
+    \includegraphics[width=.795\columnwidth]{figures/pg-abs}
 
@@
   \hrulefill
-  \vspace*{.4em}%
-
+  \vspace*{-.4em}%
   \caption{Product Graph construction for policy $\True ~\Path~ \CD{\Exit(\text{N1}} ~\Prefer~ \CD{\text{N2})}$.}
   \label{fig:example-compilation}
-  %\vspace{-1em}
+  \vspace{-.8em}
 \end{figure*}
@@
 %
-Because there can be a separate routing policy for each predicate matching traffic, we construct one PG for each predicate.
-
-For each regular path constraint $r_i$ from $r_1 ~\Prefer~ ..
+Because there can be a separate routing policy for each predicate $t$ in the policy, we construct one PG for each predicate.
+
+For each regular path constraint $r_i$ from $r_1 ~\Prefer~ ...
 ~\Prefer~ r_k$, we construct a DFA for the reverse of $r_i$.
 A DFA for $r_i$ is defined as a tuple ($\Sigma, Q_i, F_i, q_{0_i}, \sigma_i$).
-The alphabet $\Sigma$ is the set of topology locations, $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
-%
-The PG is a tuple ($G'$, $start$, \Pref) where $G' = (V',E')$ has
+The alphabet $\Sigma$ is the set of topology locations (\IE, routers or roles), $Q_i$ is the set of states for automaton i, $F_i$ is the set of final states, $q_{0_i}$ is the initial state, and $\sigma_i \colon Q_i \times \Sigma \rightarrow Q_i$ is the state transition function.
+%
+The PG for a graph $G=(V,E)$ is a tuple ($G'$, $start$, \Pref) where $G' = (V',E')$ has
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
@@
 a unique starting vertex $start$,
-and a preference function $\Pref \colon V' \rightarrow 2^{\set{1, \dots, j}}$, mapping nodes in the PG to a set of path ranks.
+and a ranking function $\Pref \colon V' \rightarrow 2^{\set{1, \dots, j}}$, mapping nodes in the PG to a set of path ranks.
 
@@
 %
-The preference function $\Pref(m)$ denotes the rank of paths through the PG ending at node $m$ and is defined as $\Pref(m) = \set{i~\vert~q_{m_i} \in F_i}$.
+The ranking function $\Pref(m)$ denotes the rank of paths through the PG ending at node $m$ and is defined as $\Pref(m) = \set{i~\vert~q_{m_i} \in F_i}$.
 %
 Finally, we write $\Topo{m} = l$ to extract the topology location from a PG node, when $m = (l, q_{m_1}, \dots, q_{m_k}) \in V'$.
+For the remainder of the paper, we use the term location to refer to both a router in the case of a concrete topology/PG, or a role in the case of an abstract topology/PG.
 
@@
 Answering questions about the number of disjoint paths between nodes allows operators to reason about many useful network properties such as reachability (\IE, is there at least one path) and fault tolerance (\EG, how many failures will disconnect certain routers).
+
+%\subsection{Abstract k-disjoint paths}
+%\label{sec:property-checking}
+
+The possibility of network failures exacerbates the difficulty of constructing correct configurations.
+Link failures in networks occur frequently; it is not uncommon for a large network to experience dozens of failures in any given day~\cite{dc-failure-study}.
+However, existing tools~\cite{condor,propane} reason about fault-tolerance only for concrete topologies.
+\sysname provides stronger guarantees: all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy.
+
+%The problem for \sysname is harder because it must verify that all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy, which requires a fundamentally different approach.
+
+%
+We frame satisfying the fault-tolerance requirements as an analysis problem over the structure of the PG.
+In particular, we develop an analysis that uses information embedded in the abstract topology to infer bounds on the number of edge-disjoint paths between pairs of concrete nodes.
+
+%
+For each node in the abstract PG,
+the idea is to infer facts learned about the number of disjoint paths
+to groups of concrete routers in the node's role.
+More specifically, we maintain fact of the form:
+%
+\[ \begin{array}{c}
+  L_{X_1}, \ldots, L_{X_n}(j,k)
+\end{array} \]
+\noindent
+%
+where each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all".
+There is one label for each pod in the abstraction pod hierarchy under which the abstract node appears.
+For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the node itself.
+Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for some/all pods $X_1, \ldots, X_{n-1}$
+and for some/all groups of nodes in the role $X_n$ of size $j$,
+%, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds. The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers,
+there are $k$ paths to each such that all $j*k$ paths are edge-disjoint.
+
+For example,
+an inference of the form $A_{Q} A_{TL}(2,3)$ states that, from the given source location, for \emph{all} pods Q, and \emph{all} groups of 2 nodes in the TL role, there are 6 disjoint paths to the group---3 for each of the 2 nodes.
 
@@
   \hrule
-  \vspace*{1em}
+  \vspace*{.4em}
   \caption{Abstract k-disjoint path analysis inference rules.}
   \label{fig:inference-rules}
-  \vspace{-1em}
+  \vspace{-.8em}
 \end{figure*}
-
-%\subsection{Abstract k-disjoint paths}
-%\label{sec:property-checking}
-
-The possibility of network failures exacerbates the difficulty of constructing correct configurations.
-Link failures in networks occur frequently; it is not uncommon for a large network to experience dozens of failures in any given day~\cite{dc-failure-study}.
-However, existing tools~\cite{condor,propane} reason about fault-tolerance only for concrete topologies.
-\sysname provides stronger guarantees: all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy.
-
-%The problem for \sysname is harder because it must verify that all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy, which requires a fundamentally different approach.
-
-%
-We frame satisfying the fault-tolerance requirements as an analysis problem over the structure of the PG.
-In particular, we develop an analysis that uses information embedded in the abstract topology to infer bounds on the number of edge-disjoint paths between pairs of concrete nodes.
-
-%
-For each node in the abstract PG,
-the idea is to infer facts learned about the number of disjoint paths
-to groups of concrete routers in the node's role.
-More specifically, we maintain fact of the form:
-%
-\[ \begin{array}{c}
-  L_{X_1}, \ldots, L_{X_n}(j,k)
-\end{array} \]
-\noindent
-%
-where each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all".
-There is one label for each pod in the abstraction pod hierarchy under which the abstract node appears.
-For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the node itself.
-Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for some/all pods $X_1, \ldots, X_{n-1}$
-and for some/all groups of nodes in the role $X_n$ of size $j$,
-%, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds. The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers,
-there are $k$ paths to each such that all $j*k$ paths are edge-disjoint.
-
-For example,
-an inference of the form $A_{Q} A_{TL}(2,3)$ states that, from the given source location, for \emph{all} pods Q, and \emph{all} groups of 2 nodes in the TL role, there are 6 disjoint paths to the group---3 for each of the 2 nodes.
 
@@
 We use $L$ to represent a rule that is parametric over the label ($S$ or $A$).
-The labels on other nodes correspond to facts learned after applying the inference rule.
-The adjacent box shows the conditions that must be valid, given the abstraction constraints, for the rule to apply.
+Labels on other nodes correspond to facts learned after applying the rule.
+The box shows the conditions that must be valid, given the abstraction constraints, for the rule to apply.
 %Validity ensures that the condition holds for all concrete instantiations of the topology.
@@
 
+\subsection{Inference algorithm}
+
+The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly tries to apply every inference rule from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
+The algorithm applies an inference rule when the rule's condition is valid given the abstract topology constraints.
+Because the inference rules may continue to yield larger and larger symbolic expressions, we make the following observation to ensure termination: for any invariant learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
+Therefore, for each inference $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing SMT solver $\nu$Z~\cite{z3opt}.
+
+At a higher level, what is happening is that each inference rule is attempting to learn the maximum possible fault tolerance information possible as a function of the symbolic inputs, and $\nu$Z~\cite{z3opt} will minimize this maximum by accounting for all possible topologies that meet the abstraction.
+Facts learned with $j=0$ or $k=0$ are discarded.
+
+%The algorithm associates with each inference, the set of abstract locations used to derive the inference, \IE, an overapproximation of set of concrete locations used for the edge-disjoint paths.
+When applying an inference rule between an invariant at role $m$, with a set of abstract locations $C$, to learn an invariant at role $n$, we associate the new invariant with the set $C \cup \{ n \}$.
+%
+%When, at a single PG node there is an inference $L_{X_1} \dots L_{X_{n-1}}$ A$_m(j,k)$ with location set $C$ and inference $L_{X_1} \dots L_{X_{n-1}}$ L$_m(j',k')$ with location set $D$, where $C \cap D = \emptyset$, we add a new inference with location set $C \cup D$:
+%
+%$$L_{X_1} \dots L_{X_{n-1}} L_m(\min(j, j'), k + k')$$
+%
+%\noindent
+%The idea is that, because non-overlapping abstract paths can never contain overlapping concrete paths, due to the graph homomorphism property, we can merge inferences about these disjoint paths in the abstraction.
+
 \begin{figure}
@@
   \end{center}
-  \vspace{-1.4em}
+  \vspace{-1em}
   \caption{Abstract disjoint path analysis for global prefixes. \label{fig:compilation-times}}
   \label{fig:example-inference}
-  \vspace{0em}
+  \vspace{-.8em}
 \end{figure}
-
-\subsection{Inference algorithm}
-
-The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly tries to apply every inference rule from Figure~\ref{fig:inference-rules} until it reaches a fixed point.
-The algorithm applies an inference rule when the rule's condition is valid given the abstract topology constraints.
-Because the inference rules may continue to yield larger and larger symbolic expressions, we make the following observation to ensure termination: for any invariant learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$.
-Therefore, for each inference $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the optimizing SMT solver $\nu$Z~\cite{z3opt}.
-Facts learned with $j=0$ or $k=0$ are discarded.
-
-%The algorithm associates with each inference, the set of abstract locations used to derive the inference, \IE, an overapproximation of set of concrete locations used for the edge-disjoint paths.
-When applying an inference rule between an invariant at role $m$, with a set of abstract locations $C$, to learn an invariant at role $n$, we associate the new invariant with the set $C \cup \{ n \}$.
-%
-%When, at a single PG node there is an inference $L_{X_1} \dots L_{X_{n-1}}$ A$_m(j,k)$ with location set $C$ and inference $L_{X_1} \dots L_{X_{n-1}}$ L$_m(j',k')$ with location set $D$, where $C \cap D = \emptyset$, we add a new inference with location set $C \cup D$:
-%
-%$$L_{X_1} \dots L_{X_{n-1}} L_m(\min(j, j'), k + k')$$
-%
-%\noindent
-%The idea is that, because non-overlapping abstract paths can never contain overlapping concrete paths, due to the graph homomorphism property, we can merge inferences about these disjoint paths in the abstraction.
 
@@
 The tags allow BGP to only search for valid paths by dropping messages that do not correspond to any edge in the PG.
-(2) To ensure that BGP always converges to the \emph{most preferred} paths in the network, we must rank route advertisements for each router by giving them a preference such that, under those preferences, the network as a whole satisfies the \sysname policy's end-to-end network preferences.
+(2) To ensure that BGP always finds the \emph{best} paths in the network, we must rank route advertisements for each router locally such that, under this ranking function, the network as a whole satisfies the \sysname policy's end-to-end network preferences.
 
 We introduce a simple, vendor-independent BGP configuration language called \mbgp and describe a compilation function that uses the inferred preference ordering to generate concrete configurations from a concrete topology, or templates from an abstract topology.
-Templates can then be soundly instantiated for a concrete network by replacing instances of abstract neighbors with the union of all concrete neighbors under the inverse homomorphism.
+Templates can then be soundly instantiated for a concrete network by replacing instances of abstract neighbors with the union of all concrete neighbors under the inverse homomorphism, and by replacing prefix template variables with separate entries for each concrete prefix provided by a context.
 We prove that concretization and compilation commute.
@@
 Community tags serve as a simple form of \emph{history}, and operators routinely use such tags to implement policy.
-For example, operators might record where an advertisment enters the network using community tags and then conditionally block the export of the advertisment later to other peers to prevent becoming a transit point between peers.
+For example, operators might record where an advertisment enters the network using community tags and then conditionally block the export of the advertisment later to other peers to prevent becoming a transit point.
 
@@
 
-For example, in the concrete PG in Figure~\ref{fig:example-compilation}, router S1 appears in two different PG nodes: $(S1,1,0)$ and $(S1,0,1)$.
-These nodes have two different peers that can send them messages in the PG: $(N1,0,0)$ and $(N2,0,0)$.
-Therefore, S1 will allow an advertisement from peer $N1$ and will also allow an advertisement from peer $N2$.
+For example, in the concrete PG in Figure~\ref{fig:example-compilation}, router S1 appears in two PG nodes: $(S1,1,0)$ and $(S1,0,1)$.
+These nodes have two peers that can send them messages in the PG: $(N1,0,0)$ and $(N2,0,0)$.
+Therefore, S1 will allow advertisements from both peer $N1$ and peer $N2$.
 If S1 uses the path advertised by neighbor N1, then it will add the tag $(1,0)$ to the advertisement before sending this to its neighbors A1 and A2.
@@
 Similarly, router A1 appears in two separate PG nodes.
-It will not block advertisements from S1 if they either have the $(1,0)$ tag or the $(0,1)$ tag attached.
+It will allow advertisements from S1 if they either have the $(1,0)$ tag or the $(0,1)$ tag attached.
 In either case, it will not modify the tag before exporting the route to its neighbors.
-
-%If A1 chooses a path with tag $(1,0)$ attached, then it will export the path to its neighbors without modifying the tag.
-If A1 chooses a path with tag $(0,1)$ attached, it will also export the path to its neighbors without modifying the tag.
 
@@
   \hrulefill%
-  %\vspace{1em}%
-
+  \vspace{-.8em}
   \caption{mBGP syntax (left), and compilation from product graphs (right).}
@@
   \label{fig:bgp-configs}
+  \vspace{-.6em}
 \end{figure}
@@
 Similarly, A1 should prefer routes tagged with $(1,0)$ over those with $(0,1)$.
-Intuitively, S1 should prefer a message from N1 because it results in an accepting state for automata 1, which indicates a more preferred path.
-Further, it can result in downstream routers such as A1 obtaining a route that is accepting for automata 1 as well, \IE $(A1,1,0)$ instead of $(A1,0,1)$.
+Intuitively, S1 should prefer a message from N1 because it results in an accepting state for automata 1, which indicates a better path.
+Further, it can result in downstream routers such as A1 using a path that is accepting for automata 1 as well.
 
@@
 Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $\min (\Pref(m)) \geq \min (\Pref(n))$ or $\Pref(n) = \emptyset$.
-Intuitively $m \geq_{rank} n$ means that paths ending at node $m$ are no better than paths ending at $n$.
+Intuitively $m \geq_{rank} n$ means that paths ending at node $m$ have higher automata rank and are thus no better than paths ending at $n$.
 %
@@
 %
-For prefix $\True$ ($0.0.0.0/[0..32]$), the spine routers will match advertisements from peer N1 and N2.
+For prefix $\True$, the spine routers will match advertisements from peer N1 and N2.
 The match for N1 is preferred since it has a higher BGP local-preference attribute (110).
-If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers ($*$).
+If an advertisement from N1 is choosen, the spine attaches the community tag $(1,0)$ before sending the route to all its peers ($*$).
 If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
 %
-The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertises the route to all of its peers.
+The template configuration matches any global prefix {\small \$GP} from any internal peer and re-advertises the route to all of its peers.
 For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers.
@@
 Suppose an operator wants to expand the concrete data center from Figure~\ref{fig:example} by adding an additional ToR router to the TG role.
-Per the network routing policy, the new ToR router will advertise any owned prefixes provided by looking up {\small \$GP} in $\Gamma$.
+Per the network routing policy, the new router will advertise any owned prefixes provided by looking up {\small \$GP} in $\Gamma$.
 Because the new topology matches the abstraction, the compiled templates will remain the same.
-However, in the spine router configurations, the match on the global prefix template variable {\small \$GP} must be expanded when concretizing the template to include the new prefixes added by the ToR.
-Unfortunately, this small change to the topology results in a change to every single spine router configuration.
+However, in the spine configurations, the match on the global prefix template variable {\small \$GP} must be expanded when concretizing the template to include the new prefixes added by the ToR.
+Unfortunately, this small change to the topology results in a change to every single spine configuration.
 
@@
 
-\sysname is implemented in approximately 9500 lines of F\# code.
-The compiler accepts both concrete and abstract topologies and will generate configurations for open-source Quagga~\cite{quagga} routers by default.
+\sysname is implemented in around 9500 lines of F\# code.
+The compiler accepts both concrete and abstract topologies and will generate evolution-friendly configurations for Cisco and Quagga~\cite{quagga} routers by default.
 The fault-tolerance analysis uses $\nu$Z~\cite{z3opt} to both test validity and minimize variables subject to the topology constraints.
@@
 
-Although the disjoint path analysis takes place over the PG, each application of the inference rules from Figure~\ref{fig:inference-rules} depends only on the topology.
+Although the disjoint path analysis takes place over the PG, each application of the inference rules from Figure~\ref{fig:inference-rules} depends on the topology locations, but not the automata states.
 Therefore, we lazily apply the rules and cache the satisfiability and minimization calls to $\nu$Z after their first use.
@@
   \end{center}
-  \vspace{-.6em}
+  \vspace{-.8em}
   \caption{Expressiveness and precision of \sysname.}
   \label{fig:analysis-precision}
-  %\vspace{-1em}
+  \vspace{-.8em}
 \end{figure}
@@
   \caption{Example abstractions for HyperX and BCube.}
-  \vspace*{-1em}%
   \label{fig:example-abstractions}
+  \vspace{-.8em}%
 \end{figure}
@@
   \caption{Concrete vs. Abstract Synthesis Time. \label{fig:compilation-times}}
-  \vspace{-1em}
+  \vspace{-1.2em}
 \end{figure}
@@
 
-We scale the backbone network from 10 to 250 routers.
+We scale the backbone network from 10 to 240 routers.
 To abstract it, we split it into two parts: border routers that connect to external neighbors and an internal core.

### 2017-03-13 paper/abstraction/paper.tex
add legend to figure 3

@@
 \sysname takes as input the network's abstract topology and its policy.
-The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous failures the network can withstand without losing connectivity.
+The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous link failures the network can withstand without losing connectivity.
 
@@
   \includegraphics[width=\columnwidth]{figures/example3}
-  \vspace{-2.2em}
+  \vspace{-1.3em}
   \caption{An abstraction for the network in Figure~\ref{fig:example}.}
   \label{fig:example3}
-  \vspace{-.8em}
+  \vspace{-.6em}
 \end{figure}
@@
 
-Our topology abstractions can also capture concrete topologies; there will be a one-to-one correspondence between abstract and concrete nodes/edges.
+Our topology abstractions can also capture concrete topologies by using a one-to-one correspondence between abstract and concrete nodes/edges.
 This allows operators to define complex networks in which some (e.g., legacy) parts of the network can not evolve while others can.
@@
 For each node in the abstract PG,
-the idea is to infer facts learned about the number of disjoint paths
+the idea is to infer facts learned about the number of edge-disjoint paths
 to groups of concrete routers in the node's role.

### 2017-03-13 paper/propane/SOSR/sosr.tex
more edits to section 7
add copyright info to SOSR submission

@@
 
-\conferenceinfo{SOSR'17,}{April 3--4, 2017, Santa Clara, CA.} 
-\copyrightetc{\copyright~2017 ACM. ISBN \the\acmcopyr}
-\crdata{xxx.\\
-DOI: http://dx.doi.org/10.1145/XXX.XXXXXXX}
-% Update the XXX's to the DOI assigned by ACM rightsreview forms
-\clubpenalty=10000 
-\widowpenalty = 10000
+%\conferenceinfo{SOSR'17,}{April 3--4, 2017, Santa Clara, CA.} 
+%\copyrightetc{\copyright~2017 ACM. ISBN \the\acmcopyr}
+%\crdata{xxx.\\
+%DOI: http://dx.doi.org/10.1145/XXX.XXXXXXX}
+%% Update the XXX's to the DOI assigned by ACM rightsreview forms
+%\clubpenalty=10000 
+%\widowpenalty = 10000
 
@@
 
+\CopyrightYear{2017} 
+\setcopyright{acmlicensed}
+\conferenceinfo{SOSR '17,}{April 03 - 04, 2017, Santa Clara, CA, USA}
+\isbn{978-1-4503-4947-5/17/04}\acmPrice{\$15.00}
+\doi{http://dx.doi.org/10.1145/3050220.3063774}
+
 \maketitle
@@
 %
-%  **Keywords**
+%  **Keywords and Descriptions**
 %
@@
 
-\keywords{Propane; Domain-specific Language; BGP; Compilation; Fault Tolerance; Distributed Systems}
+\keywords{Propane; Domain-specific Language; BGP; Fault Tolerance; Compilation, SDN, Network Control Plane}
 

### 2017-03-13 paper/abstraction/paper.tex
small tweaks

@@
 \authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
-\authorinfo{Todd Millstein}{UCLA}{todd@cs.ucla.edu}
+\authorinfo{Todd Millstein\thanks{Supported in part by National Science Foundation award
+CNS-1161595.}}{UCLA}{todd@cs.ucla.edu}
 \authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
@@
 capacity.  Unfortunately, templates that
-work for the current topology, may or may not work for future
-topologies. Problems that occur may cause operators to make small, non-uniform changes to particular routers,
+work for the current topology may or may not work for future
+topologies. Problems that occur may cause operators to make small, non-uniform changes to particular router configurations,
 which defeats the purpose of a template system.  An even worse situation occurs when
@@
 
-During synthesis, our compiler performs an important analysis over abstract topologies to determine
+During synthesis, our compiler performs an analysis over abstract topologies to determine
 the fault tolerance properties of the specified policy.  This analysis determines a worst-case 
@@
 
-\section{Methane overview}
+\section{Propane/AT overview}
 \label{sec:overview}
@@
 Our topology abstractions can also capture concrete topologies by using a one-to-one correspondence between abstract and concrete nodes/edges.
-This allows operators to define complex networks in which some (e.g., legacy) parts of the network can not evolve while others can.
+This allows operators to define complex networks in which some (e.g., legacy) parts of the network cannot evolve while others can.
 %It also means that our compiler subsumes those that operate only over concrete topologies.

### 2017-03-14 paper/abstraction/appendix.tex
update examples for consistency
stashing changes

@@
 
-\newcommand{\sysname}{{\small \sf Methane}\xspace}
-\newcommand{\sysnamesec}{{\sf Methane}\xspace}
+\newcommand{\sysname}{{\small \sf Propane/AT}\xspace}
+\newcommand{\sysnamesec}{{\sf Propane/AT}\xspace}
 \newcommand{\propane}{{\small \sf Propane}\xspace}
@@
 
+\newcommand{\Con}{\text{con}}
+\newcommand{\Pfx}{\mathit{pfx}}%
+
 \renewcommand{\path}[2]{ #1 \mapsto \ensuremath{#2} }
@@
 
-\section{Definitions}
-
-\subsection{Methane}
-
-The full \sysname syntax as well as expansions from constraints into regular expressions are shown in Figure~\ref{fig:syntax}.
-The language includes constraints of the form $\CD{\Agg(pfx, \ensuremath{r_1 \rightarrow r_2})}$ that say that aggregation for summary prefix $\CD{pfx}$ will occur from any single location matching $\CD{\ensuremath{r_1}}$ to any location matching $\CD{\ensuremath{r_2}}$.
-For simplicity, we prove the substitution property for \sysname for the fragment without aggregation.
+\vspace{2em}
+\section{Definitions Reference}
 
@@
   \begin{minipage}[t]{.45\linewidth}
-  \hdr{Syntax}{}
+  \hdr{Propane/AT Syntax}{}
   \vspace*{-1\baselineskip}
@@
   \[ \begin{array}{rclr}
-    \hline%
-
      pol     &::=& p_1, \dots, p_n & \textit{policies} \\
@@
   %
-  ~~
-  \vrule
-  ~~
-  %
   \begin{minipage}[t]{.5\linewidth}\small
-  \hdr{Expansions}{}
+  \hdr{Propane/AT Expansions}{}
   \vspace*{-1\baselineskip}
   %
-  \[\begin{array}{rcl}
-    \hline
+  \[\begin{array}{lcl}
     \Any               & = & \Sigma^* \\
@@
 
-  \hrulefill%
-  \vspace{1em}
-
-  \caption{Methane syntax and expansions.}
-  \label{fig:syntax}
-  %\vspace{-1em}
-\end{figure*}%
-
-\subsection{BGP Configuration}
-
-\para{Syntax}
-
-\newcommand{\Con}{\text{con}}
-\newcommand{\Pfx}{\mathit{pfx}}%
-
-\vspace{2em}
-\begin{figure*}[t!]\small%
-
-  \hrulefill%
-
-  \vspace{1em}%
+  \vspace{1em}
   \begin{minipage}[t]{.46\linewidth}
-  \hdr{ABGP Syntax}{}
+  \hdr{mBGP Syntax}{}
   \vspace*{-1\baselineskip}
@@
      rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
-     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\%
+     mbgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{mBGP policy} \\%
   \end{array} \]%%
@@
   \[ \begin{array}{l}
-     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
+     \text{compile}_\text{mBGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
      ~~~~~ [~ l \rightarrow rc ~\vert~ \\
@@
      \text{compile}( p_1, \dots, p_k, G) = \\
-     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
+     ~~~~~~ \text{compile}_\text{mBGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
   \end{array} \]%
@@
 
-  \vspace{1em}
-  \vspace{1em}%
+  \vspace{3em}
 
@@
   \begin{minipage}[t]{1.01\linewidth}
-  \hdr{Policy Concretization}{}
+  \hdr{Propane/AT Concretization}{}
   \vspace*{-2\baselineskip}
@@
 
-  \vspace{1em}
-  \vspace{1em}%
+  \vspace{2em}
 
   \begin{minipage}[t]{\linewidth}
-  \hdr{ABGP Concretization}{}
+  \hdr{mBGP Concretization}{}
   \vspace*{-2\baselineskip}
@@
 
-  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
-  \label{fig:concretization}
+  \caption{\sysname syntax and expansions.}
+  \label{fig:syntax}
+  %\vspace{-1em}
 \end{figure*}%
 
-\para{ABGP language}
-
-We introduct a simple language for BGP configurations called ABGP.
-Figure~\ref{fig:concretization} shows the syntax for an ABGP policy.
-An ABGP policy maps topology locations $l$ to router configurations $rc$.
-Each router configuration $rc$ is a sequence of predicates $t$ and their corresponding configuration $pc$.
-A prefix configuration $pc$ is a sequence of match actions.
-Each match action $ma$ consists of a preference value $d$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $c_1$ expected from those neighbors, as well as export neighbors $ns_2$ and the community value $c_2$ to attach before sending to those neighbors.%
-
-\para{Compilation}
-
-Figure~\ref{fig:concretization} defines compilation from a \sysname policy to an ABGP policy.
-It starts by compiling ($\text{compile}_\text{PG}$) separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$.
-The function $\text{compile}_\text{PG}$ returns the test $t_i$, product graph $PG_i$, and the preference ordering $ord_i$.
-%
-The function $\text{compile}_\text{ABGP}$ then takes a sequence of tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy.
-For each internal router, it looks at each set of neighbor with the same community state $q_n$ and matches any of those neighbors with the preference provided by the ordering $ord$.
-It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.%
-
-We assume a particular router $l$ appears at most once in any abgp specification.
+\newpage
+
+\section{Definitions}
+
+For reference, the full \sysname syntax as well as expansions from constraints into regular expressions are shown in Figure~\ref{fig:syntax}.
+The language includes constraints of the form $\CD{\Agg(pfx, \ensuremath{r_1 \rightarrow r_2})}$ that say that aggregation for summary prefix $\CD{pfx}$ will occur from any single location matching $\CD{\ensuremath{r_1}}$ to any location matching $\CD{\ensuremath{r_2}}$.
+For simplicity, we prove the substitution property for \sysname for the fragment without aggregation.
+mBGP syntax and compilation, as described in the paper, as well as concretization functions ($con$) are shown in Figure~\ref{fig:concretization}.
+
+\subsection{Compilation}
+
+We assume a particular router $l$ appears at most once in any mBGP specification.
 We build configs using list-comprehension notation. For instance,
-$[~ l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc) ~]$ denotes the abgp policy
+$[~ l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc) ~]$ denotes the mBGP policy
 %
@@
 
-We also define concretization over the ABGP policy in a similar manner.
+We also define concretization over the mBGP policy in a similar manner.
 We replace each abstract router configuration $l \rightarrow rc$ a new entry for each concrete location $\ell \in f^{-1}(l)$.
@@
 That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values on after compilation is complete.
-Note that the theorem states that the resulting ABGP policies are actually syntactically equivalent and not semantically equivalent.
+Note that the theorem states that the resulting mBGP policies are actually syntactically equivalent and not semantically equivalent.
 First we need a few helper theorems about compilation.
@@
                           & \\
-                         =& compile_{ABGP}( \\
+                         =& compile_{mBGP}( \\
                           &  ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k},G ), \\
@@
                       & \\
-                     =& compile_{ABGP}( \\
+                     =& compile_{mBGP}( \\
                       & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k}, G^A ), \\
@@
   \[ \begin{array}{l}
-     con(\textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) ), \Gamma,f,G) \\
-  \end{array} \]%
-
-Unfold definition of $\text{compile}_\text{ABGP}$
+     con(\textbf{compile}_\textbf{mBGP}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) ), \Gamma,f,G) \\
+  \end{array} \]%
+
+Unfold definition of $\text{compile}_\text{mBGP}$
 
@@
   \[ \begin{array}{l}
-     = \textbf{compile}_\textbf{ABGP}( (pfx_{11},PG_{11},ord_{11}), \dots, (pfx_{ij},PG_{ij},ord_{ij}) ) \\
+     = \textbf{compile}_\textbf{mBGP}( (pfx_{11},PG_{11},ord_{11}), \dots, (pfx_{ij},PG_{ij},ord_{ij}) ) \\
   \end{array} \]%

### 2017-03-14 paper/abstraction/paper.tex
adjust author info for more space

@@
 \newcommand{\xmark}{\ding{55}}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
 
@@
 
-\authorinfo{Ryan Beckett}{Princeton University}{rbeckett@cs.princeton.edu}
-\authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
-\authorinfo{Todd Millstein\thanks{Supported in part by National Science Foundation award
-CNS-1161595.}}{UCLA}{todd@cs.ucla.edu}
-\authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
-\authorinfo{David Walker}{Princeton University}{dpw@cs.princeton.edu}
+%\authorinfo{Ryan Beckett}{Princeton University}{rbeckett@cs.princeton.edu}
+%\authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
+%\authorinfo{Todd Millstein}{UCLA}{todd@cs.ucla.edu}
+%\authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
+%\authorinfo{David Walker}{Princeton University}{dpw@cs.princeton.edu}
+
+%\numberofauthors{1}
+
+\authorinfo{Ryan Beckett$^*$\and Ratul Mahajan$^\dagger$\and Todd Millstein$^\S$\and Jitendra Padhye$^\dagger$\and David Walker$^*$}
+{Princeton University$^*$, Microsoft Research$^\dagger$, University of California Los Angeles$^\S$}
+{\{rbeckett,dpw\}@cs.princeton.edu, \{ratul,padhye\}@microsoft.com, todd@cs.ucla.edu}
 
@@
 
+\para{Acknowledgments}
+We thank the PLDI reviewers for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 as well as Cisco award 677002.
+
 %=====================================================

### 2017-03-14 paper/abstraction/paper.tex
describe list comprehension syntax in paper

@@
     \vspace{1em}
-    \includegraphics[width=.62\columnwidth]{figures/topology-con}
+    \includegraphics[width=.60\columnwidth]{figures/topology-con}
   \end{minipage}%
@@
     \vspace{1em}
-    \includegraphics[width=.505\columnwidth]{figures/topology-abs}
+    \includegraphics[width=.49\columnwidth]{figures/topology-abs}
   \end{minipage}%
@@
     \node[] at (#1 + .46, 1.25 + 2.5) {\textbf{I-striping}};
-    \node at (#1 - 1 - .11, .6) {$e_1$};
-    \node at (#1 + .11, 1.5) {$e_2$};
-    \node at (#1 + 2 + .11, .6) {$e_3$};
-    \node at (#1 + .11 + .8, 1.5) {$e_4$};
-    \node at (#1 - 1, -.8) {L$_m(j,k)$};
-    \node at (#1 +. 5, 2.9) {S$_n(min(j*k,g),1)$};
-    \node at (#1 + 2, -.8) {S$_o\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
-    \node at (#1, 3.3) {};
-    \draw [] (#1 + .5, 2.01) circle [radius=0.4] node {$n$};
-    \draw [] (#1 - 1, 0) circle [radius=0.4] node {$m$};
-    \draw [] (#1 + 2, 0) circle [radius=0.4] node {$o$};
-    \draw [->] (#1 - 1, .4) -- (#1 + .5, 2 - .4);
-    \draw [<-] (#1 + 2, .4) -- (#1 + .5, 2 - .4);
+    \node at (#1 - 1 - .11, .6 + .2) {$e_1$};
+    \node at (#1 + .11, 1.5 + .2) {$e_2$};
+    \node at (#1 + 2 + .11, .6 + .2) {$e_3$};
+    \node at (#1 + .11 + .8, 1.5 + .2) {$e_4$};
+    \node at (#1 - 1, -.8 + .2) {L$_m(j,k)$};
+    \node at (#1 +. 5, 2.9 + .2) {S$_n(min(j*k,g),1)$};
+    \node at (#1 + 2, -.8 + .2) {S$_o\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
+    \node at (#1, 3.3 + .2) {};
+    \draw [] (#1 + .5, 2.01 + .2) circle [radius=0.4] node {$n$};
+    \draw [] (#1 - 1, 0 + .2) circle [radius=0.4] node {$m$};
+    \draw [] (#1 + 2, 0 + .2) circle [radius=0.4] node {$o$};
+    \draw [->] (#1 - 1, .4 + .2) -- (#1 + .5, 2 - .4 + .2);
+    \draw [<-] (#1 + 2, .4 + .2) -- (#1 + .5, 2 - .4 + .2);
 }
@@
 
-  \vspace*{1em}
+  \vspace*{.2em}
   \begin{minipage}[t]{\linewidth}%
@@
 For example, in the concrete PG in Figure~\ref{fig:example-compilation}, router S1 appears in two PG nodes: $(S1,1,0)$ and $(S1,0,1)$.
-These nodes have two peers that can send them messages in the PG: $(N1,0,0)$ and $(N2,0,0)$.
+These nodes have two peers that can send them messages: $(N1,0,0)$ and $(N2,0,0)$.
 Therefore, S1 will allow advertisements from both peer $N1$ and peer $N2$.
@@
   \[ \begin{array}{rclr}
-     d    &   & & \textit{integer} \\
-     c    &   & & \textit{community} \\
-     l    &   & & \textit{location} \\
+     d    &\in& \textit{Integers} & \\
+     c    &\in& \textit{Communities} & \\
+     l    &\in& \textit{Topology Locations} & \\
      t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
@@
   \label{fig:concretization}
-  \vspace{-.8em}
+  \vspace{-.4em}
 \end{figure*}%
@@
 On the other hand, if the S1-N1 link fails, then the best available path is through N2.
+
+To enforce correct network-wide preferences, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routers learned from another neighbor.
+The challenge is to find a collection of device-local preferences that correctly enforce the network-wide preferences from the policy for all failures.
+
+The idea then is to search for such a device-local preference function for each router that totally orders advertisements from different neighbors (possibly with different tags).
+For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, S1 should prefer a message it hears from N1 over N2.
+Similarly, A1 should prefer routes tagged with $(1,0)$ over those with $(0,1)$.
+Intuitively, S1 should prefer a message from N1 because it results in an accepting state for automata 1, which indicates a better path.
+Further, it can result in downstream routers such as A1 using a path that is accepting for automata 1 as well.
+
+In general, because BGP is distributed, each router does not have a view of the entire network when choosing which path to use, and finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem.
+\Propane introduced a conservative search strategy for determining route preferences that works well in practice.
+To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:
+
+\begin{defn}
+Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $\Topo{m} = \Topo{n}$ and either $\min (\Pref(m)) \geq \min (\Pref(n))$ or $\Pref(n) = \emptyset$.
+%
+\end{defn}
+\noindent
+%
+Intuitively $m \geq_{rank} n$ means that paths ending at node $n$ have lower automata rank and are thus better than paths ending at $m$.
+%\begin{defn}
+The PG can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge.
+That is, $m\overset{l}{\rightarrow}n$ if there is an edge $(m,n)$ in the PG and $\Topo{n} = l$.
+%\end{defn}
+%
+For example, in the concrete PG we have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.
+
+\begin{defn}
+We write $m \leq n$ if the subgraph reachable from $m$ and $n$ respectively form a simulation relation with respect to $\geq_{rank}$.
+\end{defn}
+
+More specifically, we say that $m \leq n$ if $m \geq_{rank} n$ and for every transition $n\overset{l}{\rightarrow}n'$ from PG node $n$ there exists a transition $m\overset{l}{\rightarrow}m'$ from $m$ and $m' \leq n'$.
+%
+If $m \leq n$, then advertisements received for node $m$ can safely be preferred over those received for node $n$ after accounting for the network-wide impact of the choice.
+For example in Figure~\ref{fig:example-compilation}, S1 can receive advertisements in two different contexts ($(S1,1,0)$ and $(S1,0,1)$) and must choose between messages received in these different contexts.
+Advertisements are preferred in state $(S1,1,0)$ because it results in a better path for S1 ($(S1,0,1) \geq_{rank} (S1,1,0)$) and downstream routers such as A1 will also obtain paths no worse than if S1 had choosen $(S1,1,0)$ instead.
+The policy is guaranteed to be safe from failures because if a link fails in the topology, then $m \leq n$ will still hold since any transition that becomes unusable for $m$ also becomes unusable for $n$.
+That is $m \leq n$ before the failure implies $m \leq n$ after the failure.
+
+For each router, its corresponding PG nodes are then sorted according the the $\leq$ operator.
+If the operator defines a total order on PG nodes, then the compiler can simply prefer advertisements from peers of node $m$ over those of $n$ whenever $n \leq m$.
+However, if $\leq$ does not form a total order, then the policy is rejected as being potentially unsafe under some failure conditions.
+
+%
+For example, in the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation.
+This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$.
+Therefore, advertisements received at $S1$ with tag $(1,0)$ must be preferred to those received at $S1$ with tag $(0,1)$.
+%
+Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds. This leads to the following observation:
+
+\begin{lem}
+\label{lem:preference}
+$m \leq n$ in the concrete PG iff $f_{pg}(m) \leq f_{pg}(n)$ in the abstract PG.
+\end{lem}
+
+Lemma~\ref{lem:preference} tells us that inferring preferences for the abstract PG before template instantiation is equivalent to inferring preferences for an already-instantiated concrete PG.
 
@@
 
-To enforce correct network-wide preferences, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routers learned from another neighbor.
-The challenge is to find a collection of device-local preferences that correctly enforce the network-wide preferences from the policy for all failures.
-
-The idea then is to search for such a device-local preference function for each router that totally orders advertisements from different neighbors (possibly with different tags).
-For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, S1 should prefer a message it hears from N1 over N2.
-Similarly, A1 should prefer routes tagged with $(1,0)$ over those with $(0,1)$.
-Intuitively, S1 should prefer a message from N1 because it results in an accepting state for automata 1, which indicates a better path.
-Further, it can result in downstream routers such as A1 using a path that is accepting for automata 1 as well.
-
-In general, because BGP is distributed, each router does not have a view of the entire network when choosing which path to use, and finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem.
-\Propane introduced a conservative search strategy for determining route preferences that works well in practice.
-To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:
-
-\begin{defn}
-Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $\min (\Pref(m)) \geq \min (\Pref(n))$ or $\Pref(n) = \emptyset$.
-Intuitively $m \geq_{rank} n$ means that paths ending at node $m$ have higher automata rank and are thus no better than paths ending at $n$.
-%
-\end{defn}
-\noindent
-%
-
-%\begin{defn}
-The PG can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge.
-That is, $m\overset{l}{\rightarrow}n$ if there is an edge $(m,n)$ in the PG and $\Topo{n} = l$.
-%\end{defn}
-%
-For example, in the concrete PG we would have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.
-
-\begin{defn}
-We write $m \leq n$ if the subgraph reachable from $m$ and $n$ respectively form a simulation relation with respect to $\geq_{rank}$.
-\end{defn}
-
-More specifically, we say that $m \leq n$ if $m \geq_{rank} n$ and for every transition $n\overset{l}{\rightarrow}n'$ from PG node $n$ there exists a transition $m\overset{l}{\rightarrow}m'$ from $m$ and $m' \leq n'$.
-%
-Intuitively, the $m \leq n$ relation means advertisements received for node $m$ can safely be preferred over those received for node $n$ after accounting for the network-wide impact of the choice.
-For example in Figure~\ref{fig:example-compilation}, S1 can receive advertisements in two different contexts ($(S1,1,0)$ and $(S1,0,1)$) and must choose between messages received in these different contexts.
-Advertisements are preferred in state $(S1,1,0)$ because it results in a better path for S1 ($(S1,0,1) \geq_{rank} (S1,1,0)$) and downstream routers such as A1 will also obtain paths no worse than if S1 had choosen $(S1,1,0)$ instead.
-The policy is guaranteed to be safe from failures because if a link fails in the topology, then $m \leq n$ will still hold since any transition that becomes unusable for $m$ also becomes unusable for $n$.
-That is $m \leq n$ before the failure implies $m \leq n$ after the failure.
-
-For each router, its corresponding PG nodes are then sorted according the the $\leq$ operator.
-If the operator defines a total order on PG nodes, then the compiler can simply prefer advertisements from peers of node $m$ over those of $n$ whenever $n \leq m$.
-However, if $\leq$ does not form a total order, then the policy is rejected as being potentially unsafe under some failure conditions.
-
-%
-For example, in the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation.
-This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$.
-Therefore, advertisements received at $S1$ with tag $(1,0)$ must be preferred to those received at $S1$ with tag $(0,1)$.
-%
-Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds. This leads to the following observation:
-
-\begin{lem}
-\label{lem:preference}
-$m \leq n$ in the concrete PG iff $f_{pg}(m) \leq f_{pg}(n)$ in the abstract PG.
-\end{lem}
-
-Lemma~\ref{lem:preference} tells us that inferring preferences for the abstract PG before template instantiation is equivalent to inferring preferences for an already-instantiated concrete PG.
-
 \para{mBGP}
@@
 The local preference for these imports is given by $\mathrm{pref}_i(m)$.
+We build configs using list-comprehension notation.
+For instance, $[~ l \rightarrow rc ~\vert~ l \in V, p(l,rc) ~]$ denotes the \mbgp policy $l_1 \rightarrow rc_{1},...,l_k \rightarrow rc_{k}$ where each $rc_{i}$ satisfies $p(l_i,rc_{i})$.
+We also use $\mathit{append}$ to denote sequence concatenation.%
 
@@
 These variants differ in the number of tiers and the connectivity pattern between roles.
-For each, we use a tiered abstraction similar to that in our example (\S\ref{sec:overview}) and parameterize over the number of pods, which can be scaled to allow expansion.
-We report precision of both analyzing reachability and computing the number of disjoint paths, and we report if \sysname is precise for all pairs of abstract nodes or only some of them.
+For each, we use a tiered abstraction similar to that in our example (\S\ref{sec:overview}) and parameterize over the number of pods, which can be scaled for expansion.
+We report precision of both analyzing reachability and disjoint paths, and we report if \sysname is precise for all pairs of abstract nodes or only some of them.
 We record a check when the analysis is precise and a \Conserv{} when the analysis is conservative.
-%"All pairs" precision implies "some pairs" precision, but not the other way around.
 
@@
   \caption{Abstract Synthesis Time by Phase. \label{fig:abstract-breakdown}}
-  \vspace{-1em}
+  \vspace{-.4em}
 \end{figure}

### 2017-03-14 paper/abstraction/appendix.tex
refactoring appendix

@@
 
-\newcommand{\Con}{\text{con}}
-\newcommand{\Pfx}{\mathit{pfx}}%
+\newcommand{\Con}{\mathrm{con}}
+\newcommand{\Pfx}{\mathrm{pfx}}%
+\newcommand{\CompilePred}{\ensuremath{\mathrm{compile}_\mathrm{pred}}}
+\newcommand{\CompilePg}{\ensuremath{\mathrm{compile}_\mathrm{PG}}}
+\newcommand{\CompileMbgp}{\ensuremath{\mathrm{compile}_\mathrm{mBGP}}}
+\newcommand{\Compile}{\ensuremath{\mathrm{compile}}}
+\newcommand{\Append}{\ensuremath{\mathrm{append}}}
+\newcommand{\Pref}{\ensuremath{\mathrm{pref}}}
 
@@
   \[ \begin{array}{l}
-     \text{compile}_\text{mBGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
+     \CompileMbgp( [x_1, \dots, x_k], G ) = \\
      ~~~~~ [~ l \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~ l \in internal(G.V), \\
-     ~~~~~~~~~ rc = \mathit{append}_i~  \\
-     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \}, \\
+     ~~~~~~~~~~~~ l \in internal(G.V), \\
+     ~~~~~~~~~~~~ rc = \Append_i (\CompilePred( x_i, G )) ~]  \\
+     \\
+     \CompilePred( (t,PG,pref), G ) = \\
+     ~~~~~~~~~~~~~~~ [~ t \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
      ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
      \\
-     \text{compile}( p_1, \dots, p_k, G) = \\
-     ~~~~~~ \text{compile}_\text{mBGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
+
+     \Compile( p_1, \dots, p_k, G) = \\
+     ~~~~~~ \text{compile}_\text{mBGP}([\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G)], G) \\
   \end{array} \]%
@@
 
-  \caption{\sysname syntax and expansions.}
+  \caption{\sysname syntax, expansions and concretization, as well as mBGP syntax and concretization.}
   \label{fig:syntax}
@@
 
-\section{Definitions}
+\section{Preliminaries}
 
 For reference, the full \sysname syntax as well as expansions from constraints into regular expressions are shown in Figure~\ref{fig:syntax}.
-The language includes constraints of the form $\CD{\Agg(pfx, \ensuremath{r_1 \rightarrow r_2})}$ that say that aggregation for summary prefix $\CD{pfx}$ will occur from any single location matching $\CD{\ensuremath{r_1}}$ to any location matching $\CD{\ensuremath{r_2}}$.
-For simplicity, we prove the substitution property for \sysname for the fragment without aggregation.
-mBGP syntax and compilation, as described in the paper, as well as concretization functions ($con$) are shown in Figure~\ref{fig:concretization}.
-
-\subsection{Compilation}
-
-We assume a particular router $l$ appears at most once in any mBGP specification.
-We build configs using list-comprehension notation. For instance,
-$[~ l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc) ~]$ denotes the mBGP policy
-%
-\[ \begin{array}{c}
-  l_1 \rightarrow rc_{1},... \\
-  ...           \\
-  l_k \rightarrow rc_{k},... \\
-\end{array} \]
-
-where $l_1, ..., l_k$ are the nodes in the topology
-and each $rc_{i}$ satisfies $p(l_i,rc_{i})$. We also use the $\mathit{append}$ operator to denote sequence concatenation.%
-
-\subsection{Concretization}
-
-Concretization for a \sysname policy takes as input, the policy and a context
+mBGP syntax and compilation, as described in the paper, as well as concretization functions ($\Con$) are shown in Figure~\ref{fig:syntax}.
+
+\subsection{Definition of Compilation}
+
+We present the definition of compilation slighty differently here by factoring a separate $\CompilePred$ function, to make the proof clearer.
+This is a simple rewriting of the compilation function defined in the body of the paper.
+
+\subsection{Definition of Concretization}
+
+Definitions for concretization are shown in Figure~\ref{fig:syntax}. Concretization for a \sysname policy takes as input, the policy and a context
 $\Gamma : Var \rightarrow 2^{Prefix \times V}$,
-which maps from a template prefix to a set of pairs of a concrete prefix and a concrete location that "owns" the prefix.
+which maps from a template prefix to a set of pairs of a concrete prefix and a concrete location that ``owns" the prefix.
 %
@@
 Finally, to concretize a set of neighbors, we again use $f^{-1}$ to find the set of concrete neighbors under the inverse homomorphism, but then restrict it to those that are actually connected in the underlying concrete topology with $G.E$.
-
-\subsection{Abstraction}
-
-A network topology is a graph $G$ = ($V, E$), where $V$ is a set of vertices and $E \colon V \times V$ a set of directed edges.
-A role-based abstraction is a graph homomorphism from $G$ to an abstract graph $G^A$ = ($V^A$,$E^A$).
-A graph homorphism $f : G \rightarrow G^A$ is a function that maps each node in the concrete graph to a node in the abstract graph such that, whenever $(u,v) \in E$, then $(f(u),f(v)) \in E^A$.
-We write $f^{-1}(v)$ to denote the set of concrete nodes mapping to the abstract node $v$.
-Given a path as a sequence of locations $p = l_1, \dots, l_k$ we define $f(p) = f(l_1), \dots, f(l_k)$.
 
@@
 A superscript $G^A$ refers to the abstract version (in this case of the topology), while the non-superscripted value refers to the concrete version.
+Given a path as a sequence of locations $p = l_1, \dots, l_k$ we often apply the graph homomorphism $f$ to the path by writing: $f(p) = f(l_1), \dots, f(l_k)$.
+
+\section{Proof Overview}
+
+The goal of the proof is to show that the concretization and compilation functions commute:
+%
+$$\Con(\Compile(pol,G^A),\Gamma,f,G) = \Compile(\Con(pol,\Gamma,f), G)$$ 
+%
+The proof proceeds in the following fashion.
+First, we establish several facts about the relationship of the concrete and abstract product graphs given the definition for building the product graph.
+Assumming ...
+%
+$$t = \$x \implies pfx \in \Gamma(x)$$
+$$\CompilePg(t \Path r_1 \Prefer \ldots \Prefer r_n, G) = (t, PG, \Pref)$$
+$$\CompilePg(pfx \Path r_1 \Prefer \ldots \Prefer r_n, G^A) = (pfx, PG^A, \Pref^A)$$
+%
+Then several relationships hold between $PG$ and $PG^A$ as well as between $\Pref$ and $\Pref^A$.
+Using these facts, we then establish that concretization and compilation commute for an individual constraint p:
+%
+$$\Con(\Compile(p, G^A), \Gamma, f, G) = \Compile(\Con(p,\Gamma,f), G)$$
+%
+This proof proceeds by cases on the constraint p. Finally, this theorem is lifted to policies $pol = p_1, \ldots, p_n$ using the previous proof to obtain the final theorem.
+
+%
+%$$t = \$x \implies pfx \in \Gamma(x)$$
+%$$\CompilePred((t,PG,\Pref), G) = t \rightarrow xs $$
+%$$\CompilePred((pfx,PG^A,\Pref^A), G^A) = pfx \rightarrow ys$$
+%$$xs = ys$$
 
@@
 The goal of this section is to prove that the concretization and compilation functions commute: 
-$$con(compile(pol,G^A),\Gamma,f,G) = compile(con(pol,\Gamma,f), G)$$ 
+$$\Con(\Compile(pol,G^A),\Gamma,f,G) = \Compile(\Con(pol,\Gamma,f), G)$$ 
 That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values on after compilation is complete.

### 2017-03-14 paper/abstraction/appendix.tex
cleaning up appendix

@@
 \newcommand{\Pref}{\ensuremath{\mathrm{pref}}}
+\newcommand{\Topo}{\ensuremath{\mathrm{topo}}}
+\newcommand{\EndR}{\ensuremath{\mathrm{end}}}
 
@@
 We use capital letters for abstract topology/product graph nodes and we use lower case letters for concrete topology nodes.
-By default, product graph nodes with different subscripts refer to nodes that share the same topology location (\IE, $n_1 \approx n_2$).
+By default, product graph nodes with different subscripts refer to nodes that share the same topology location (\IE, $\Topo(n_1) = \Topo(n_2)$).
 A superscript $G^A$ refers to the abstract version (in this case of the topology), while the non-superscripted value refers to the concrete version.
-Given a path as a sequence of locations $p = l_1, \dots, l_k$ we often apply the graph homomorphism $f$ to the path by writing: $f(p) = f(l_1), \dots, f(l_k)$.
-
-\section{Proof Overview}
-
-The goal of the proof is to show that the concretization and compilation functions commute:
-%
+Given a path as a sequence of locations $path = l_1, \dots, l_k$ we often apply the graph homomorphism $f$ to the path by writing: $f(path) = f(l_1), \dots, f(l_k)$.
+
+\newpage
+
+\section{Proof Sketch}
+\vspace{1em}
+
+The goal of the proof is to show that the concretization and compilation functions commute. In particular, we are interested in establishing the following theorem:
+
+\begin{thm}
+  for all \sysname policies pol, contexts $\Gamma$, and topologies G and $G^A$ related by the homomorphism $f$, 
   $$\Con(\Compile(pol,G^A),\Gamma,f,G) = \Compile(\Con(pol,\Gamma,f), G)$$
-%
-The proof proceeds in the following fashion.
-First, we establish several facts about the relationship of the concrete and abstract product graphs given the definition for building the product graph.
-Assumming ...
-%
-$$t = \$x \implies pfx \in \Gamma(x)$$
-$$\CompilePg(t \Path r_1 \Prefer \ldots \Prefer r_n, G) = (t, PG, \Pref)$$
-$$\CompilePg(pfx \Path r_1 \Prefer \ldots \Prefer r_n, G^A) = (pfx, PG^A, \Pref^A)$$
-%
-Then several relationships hold between $PG$ and $PG^A$ as well as between $\Pref$ and $\Pref^A$.
-Using these facts, we then establish that concretization and compilation commute for an individual constraint p:
+\end{thm}
+
+The proof proceeds in the following steps.
+
+\para{Product Graphs (Step 1)} First, we establish several facts about the relationship of the concrete and abstract product graphs given the definition for building the product graph.
+We start by assuming that both an abstract constraint and its concretized form are compiled to product graphs and preference functions:
+%
+\[
+\begin{array}{lll}
+  \CompilePg(t_1 \Path~ \Con(r_1,\Gamma,f) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n,\Gamma,f), G) &=& (t_1, PG, \Pref) \\
+  \CompilePg(t_2 \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, G^A) &=& (t_2, PG^A, \Pref^A) \\
+\end{array}
+\]
+%
+Using this assumption, we show that several relationships hold between $PG$ and $PG^A$ as well as between $\Pref$ and $\Pref^A$.
+
+\para{Substitution of Constraints (Step 2)} The next step is to use the relationships established in step 1 to show that concretization and compilation commute for an individual constraint \sysname p:
 %
@@
 %
-This proof proceeds by cases on the constraint p. Finally, this theorem is lifted to policies $pol = p_1, \ldots, p_n$ using the previous proof to obtain the final theorem.
-
-%
-%$$t = \$x \implies pfx \in \Gamma(x)$$
-%$$\CompilePred((t,PG,\Pref), G) = t \rightarrow xs $$
-%$$\CompilePred((pfx,PG^A,\Pref^A), G^A) = pfx \rightarrow ys$$
-%$$xs = ys$$
-
-\section{Substitution Theorem}
-
-The goal of this section is to prove that the concretization and compilation functions commute: 
+This proof proceeds by cases on the constraint p.
+
+\para{Substitution of Policies (Step 3)} Finally, this theorem is lifted to \sysname policies $pol = p_1, \ldots, p_n$ using the previous proof for individual constraints to obtain the final theorem:
+%
 $$\Con(\Compile(pol,G^A),\Gamma,f,G) = \Compile(\Con(pol,\Gamma,f), G)$$
-That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values on after compilation is complete.
-Note that the theorem states that the resulting mBGP policies are actually syntactically equivalent and not semantically equivalent.
-First we need a few helper theorems about compilation.
-
-\subsection{Automata}
+
+\newpage
+
+\section{Substitution Proof}
+
+\subsection{Product Graphs (Step 1)}
+In this section, we will establish several relationships between the product graph and preference functions for abstract and concretized \sysname policies.
+First we relate the languages denoted by regular expressions under concretization.
+Then we lift this observation to automata, and finally to product graphs.
 
@@
 
-We compile regular expressions to automata.
+%We compile regular expressions to automata.
 As a side condition, we ensure that there are no transitions from some state $q$ to the initial state: $\sigma(q,x) = q_0$.
@@
 \begin{lem}
-  For any $\Gamma$, $f$, and $r$, path $p \in \Lang(con(r,\Gamma,f)) \iff f(p) \in \Lang(r)$.
+  For any context $\Gamma$, homomorphism $f$, and regular expression $r$, 
+  path $p \in \Lang(con(r,\Gamma,f)) \iff f(p) \in \Lang(r)$.
 \end{lem}
@@
 
-\begin{lem}
-  Consider the PG created from compiling the constraint $p = (t ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$ with state machine $M^A_i$ for each $r_i$.
-We know that, for each $(pfx ~\Path~ r'_1 ~\Prefer~,\dots, ~\Prefer~ r'_k) \in con(p,\Gamma,f)$ where $r'_i$ is of the form $r \cap \text{end}(L)$ we can constuct state machine $M_i$ for $r'_i$ over the same states in the following way:
+\vspace{2em}
+For the proof, we assume regular expressions are translated to finite automata in a particular way as defined below
+
+\begin{defn}
+Given a regular expression $r$ over abstract locations, homomorphism $f$, a nonempty set of locations $L$, and a finite state machine $M^A = (\Sigma,Q^A,q_0,\sigma^A,F^A)$, we create a concrete state machine $M = (\Sigma, Q, q_0, \sigma, F)$ for the concretized policy $con(r,\Gamma, f) \cap \EndR(L)$ in the following way:
 
@@
     \end{array} \]
-
-  then $M_i$ matches $p$ $\iff$ $p \in \Lang(r_i')$
-
-  \vspace{1em}
-  \begin{proof} by cases on $t$
-
-    \vspace{1em}
-
-    \textbf{Case} $(\$x ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$
-
-    \[ \begin{array}{lcl}
-      con(p) &=& pfx_1 ~\Path~ con(r_1,\Gamma,f) \cap \text{end}(l_1), ~\Prefer~ \dots ~\Prefer~ con(r_k,\Gamma,f) \cap \text{end}(l_1)  \\
-             & & \dots, \\
-             & & pfx_n ~\Path~ con(r_1,\Gamma,f) \cap \text{end}(l_n), ~\Prefer~ \dots ~\Prefer~ con(r_k,\Gamma,f) \cap \text{end}(l_n)
-    \end{array} \]
-
-    Case ($\Rightarrow$)
-
-    Assume $M_i$ matches $p$.
-Then this means that $M^A_i$ matches $f(p)$.
+\end{defn}
+
+Next, we show that the construction is correct. That is, the machine recognizes exactly the language $con(r,\Gamma, f) \cap \EndR(L)$.
+
+\begin{lem}
+  for any path $p$, $M$ matches $p$ $\iff$ $p \in \Lang(con(r,\Gamma, f) \cap \EndR(L))$
+  %\vspace{1em}
+  \begin{proof} 
+    $ $
+    \vspace{1em}
+
+    \textbf{Case} ($\Rightarrow$)
+
+    Assume $M$ matches $p$.
+Then this means that $M^A$ matches $f(p)$.
 If we have a trace of string of the form $ p = x_1 \cdot \dots \cdot x_n$, then $f(p) = f(x_1) \cdot \dots \cdot f(x_n)$.
-For each transition $\sigma(q,l) = q'$ in the concrete automaton, we have transition $\sigma(q,f(l)) = q'$ in the abstract automaton, and they have the same final states, so this trace is accepting for $M^A_i$.
-Because $M^A_i$ matches $f(p)$, this means that $f(p) \in \Lang(r_i)$.
-From our above lemma, this means that $p \in \Lang(con(r_i,\Gamma,f))$.
-We also know that, since $L = \{ l_i \}$, the first transition $\sigma(q_0,l_i)$ is the only transition allowed from the initial state for $M_i$.
-So this means that $p \in \Lang(\text{end}(l_i))$.
-Since we know that $p \in \Lang(con(r_i,\Gamma,f))$ and $p \in \Lang(\text{end}(l_i))$, we know that $p \in \Lang(con(r_i,\Gamma,f) \cap \text{end}(l_i))$ and thus $p \in \Lang(r'_i)$.
-
-    \vspace{1em}
-    Case ($\Leftarrow$)
-
-    Assume $p \in \Lang(r'_i)$.
-This means that $p \in \Lang(con(r_i) \cap \text{end}(l_i))$.
-In turn, this means that $p \in \Lang(con(r_i))$ and $p \in \Lang(\text{end}(l_i))$.
-From the above lemma, we know that $f(p) \in \Lang(r_i)$, which means that $M^A_i$ matches $f(p)$.
-    %
-    Consider any string of the form $p = l_i \cdot x_2 \cdot \dots \cdot x_n$ such that $p \in \Lang(con(r_i) \cap \text{end}(l_i))$. Clearly there is a transition defined for $\sigma(q_0,l_i) = q_1$.
-    %
-    This means that $M^A_i$ matches $f(l_i) \cdot f(x_2) \cdot \dots \cdot f(x_n)$
-    %
-    For each transition $\sigma^A(q,f(x_i)) = q'$, we have $\sigma(q,x_i) = q'$ in $M_i$.
-    %
-    Thus the string $l_i \cdot x_2 \cdot \dots \cdot x_n$ is accepted along the same path of automaton states.
-
-  \vspace{1em}
-
-  \textbf{Case} $(pfx ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$
-
-    \[ \begin{array}{lcl}
-      con(p,\Gamma,f) &=& pfx_1 ~\Path~ con(r_1,\Gamma,f) \cap \text{end}(\Sigma^*), ~\Prefer~ \dots ~\Prefer~ con(r_k,\Gamma,f) \cap \text{end}(\Sigma^*) \\
-    \end{array} \]
-
-    First we observe that: $M^A_i$ matches $f(p)$ $\iff$ $M_i$ matches $p$.
-    %
-    Suppose $M^A_i$ matches $f(p) = A_1, \dots, A_k$, then there exists a trace through $M^A_i$ of the form:%
-    %
-    $q_0, q_1, \dots, q_{k+1}$
-    %
-    where $\sigma^A_i(q_i, A_i) = q_{i+1}$ and $q_{k+1} \in F^A$. We must show that $M_i$ matches $p = a_1, \dots, a_k$. %
-    %
-    From the construction of the automaton, we know that $\sigma_i(q_i, a_i) = q_{i+1}$ and $q_{k+1} \in F \iff q_{k+1} \in F^A_i$.
-Therefore, the trace $q_0, q_1, \dots, q_{k+1}$ is accepted by $M_i$.
-    %
-    The same proof is symmetric for the other direction. It follows that:
-
-    \[ \begin{array}{lll}
-      M ~\text{matches}~ p &\iff& M^A ~\text{matches}~ f(p) \\
-                         &\iff& f(p) \in \Lang(r) \\
-                         &\iff& p \in \Lang(con(r,\Gamma,f)) \\
-    \end{array} \]%
-
+For each transition $\sigma(q,l) = q'$ in the concrete automaton, we have transition $\sigma(q,f(l)) = q'$ in the abstract automaton, and they have the same final states, so this trace is accepting for $M^A$.
+Because $M^A$ matches $f(p)$, this means that $f(p) \in \Lang(r)$.
+From Lemma 1, this means that $p \in \Lang(con(r,\Gamma,f))$.
+We also know that, since there is only a transition from the initial state $\sigma(q_0,l)$ defined for $l \in L$ by construction, it means that $p \in \Lang(\text{end}(L))$.
+Since we know that $p \in \Lang(con(r_i,\Gamma,f))$ and $p \in \Lang(\text{end}(L))$, we know that $p \in \Lang(con(r,\Gamma,f) \cap \text{end}(l))$ and thus $p \in \Lang(con(r,\Gamma, f) \cap \EndR(L))$.
+
+    \vspace{1em}
+    \textbf{Case} ($\Leftarrow$)
+
+    Assume $p \in \Lang(con(r,\Gamma, f) \cap \EndR(L))$.
+This means that $p \in \Lang(con(r,\Gamma,f))$ and $p \in \Lang(\text{end}(L))$.
+Lemma 1, we know that $f(p) \in \Lang(r)$, which means that $M^A$ matches $f(p)$.
+    %
+    Consider any string of the form $p = l \cdot x_2 \cdot \dots \cdot x_n$ such that $p \in \Lang(con(r,\Gamma,f) \cap \text{end}(L))$.
+Clearly $l \in L$ and there is a transition defined for $\sigma(q_0,l) = q_1$.
+    %
+    This means that $M^A$ matches $f(l) \cdot f(x_2) \cdot \dots \cdot f(x_n)$.
+    %
+    For each transition $\sigma^A(q,f(x_i)) = q'$, we have $\sigma(q,x_i) = q'$ in $M$.
+    %
+    Thus the string $l \cdot x_2 \cdot \dots \cdot x_n$ is accepted along the same path of automaton states.
   \end{proof}
@@
 
-\vspace{1em}
-\subsection{Product Graph}
+\begin{lem} $M$ and $M^A$ have the same set of states. That is, $Q = Q^A$.
+    $ $
+    \vspace{1em}
+    \begin{proof}
+      This follows trivially from the construction of $M$.
+    \end{proof}
+\end{lem}
+
+\vspace{3em}
+For the remainder of this section, we will consider propositions assuming the following: 
+%
+\[
+\begin{array}{lll}
+  \CompilePg(t_1 \Path~ \Con(r_1,\Gamma,f) \cap \EndR(L) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n,\Gamma,f) \cap \EndR(L), G) &=& (t_1, PG, \Pref) \\
+  \CompilePg(t_2 \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, G^A) &=& (t_2, PG^A, \Pref^A) \\
+\end{array}
+\]
+%
+where either $L = \Sigma$, or $L = \{ l \}$ with
+
+\vspace{1em}
 

### 2017-03-14 paper/abstraction/appendix.tex
more edits

@@
 \newcommand{\EndR}{\ensuremath{\mathrm{end}}}
+\newcommand{\Rank}{\ensuremath{\mathrm{rank}}}
 
@@
 Then we lift this observation to automata, and finally to product graphs.
+We use these connections to left the notion of homomorphism to the product graphs and to relate the inferred BGP local preferences for abstract and concrete devices.
 
@@
 
-%\begin{defn}
-%If $r$ complies to state machine $M^A$, then we compile the policy $con(r)$ in the following way:%
-
-%  \[ \begin{array}{ll}
-%    1. & \sigma^A(q,f(l)) = q' \iff \sigma(q,l) = q' \\
-%    2. & q \in F^A \iff q \in F \\
-%  \end{array} \]%
-
-%That is, we construct a new automata over the same states and final states, but with a different transition function $\sigma$.
-This ensures that there is a bisimulation between the two state machines.%
-
-%\end{defn}%
-%
-
-%\begin{lem}
-%  $M^A$ matches $f(p)$ $\iff$ $M$ matches $p$.
-%\end{lem}%
-
-%\begin{proof}
-%  Suppose $M^A$ matches $f(p) = A_1, \dots, A_k$, then there exists a trace through $M^A$ of the form:%
-
-%  $$q_0, q_1, \dots, q_{k+1}$$%
-
-%  where $\sigma^A(q_i, A_i) = q_{i+1}$ and $q_{k+1} \in F^A$. We must show that $M$ matches $p = a_1, \dots, a_k$. %
-
-%  From the construction of the automaton, we know that $\sigma(q_i, a_i) = q_{i+1}$ and $q_{k+1} \in F \iff q_{k+1} \in F^A$. Therefore, the trace $q_0, q_1, \dots, q_{k+1}$ is accepted by $M$. 
-%  %
-%  The same proof is symmetric for the other direction.
-%\end{proof}%
-%
-
-%\begin{lem}
-%  $M$ matches $p$ $\iff$ $p \in \Lang(con(r))$
-%  \begin{proof}
-%    \[ \begin{array}{lllr}
-%      M ~\text{matches}~ p &\iff& M^A ~\text{matches}~ f(p) & \textit{previous lemma} \\
-%                         &\iff& f(p) \in \Lang(r) & \textit{automaton construction} \\
-%                         &\iff& p \in \Lang(con(r)) & \textit{first lemma} \\
-%    \end{array} \]%
-
-%  \end{proof}
-%\end{lem}
-
 \vspace{2em}
-For the proof, we assume regular expressions are translated to finite automata in a particular way as defined below
+For the proof, we assume an invariant that when regular expressions are translated to finite automata, there is no transition back to the initial state $q_0$.
+This is easily done by introducing a separate copy of $q_0$ that allows transitions.
+The reason is to distinguish if a state corresponds to a router originating a route.
+We also compile automata in a particular way as defined below
 
@@
 \vspace{3em}
-For the remainder of this section, we will consider propositions assuming the following: 
+For the remainder of this section, we will prove a collection of lemmas assuming the following: 
 %
@@
 %
-where either $L = \Sigma$, or $L = \{ l \}$ with
-
-\vspace{1em}
-
-\begin{defn}
-  Because compilation guarantees that the automata states are the same under the concretization function, we can lift the graph homomorphism $f$ to a new homomorphism $f_{pg}$ over the product graph in the following way:
+We will also assume that $PG = (G',start,rank)$ and $PG^A = (G'^A,start^A,rank^A)$ and that either $L = \Sigma$, or $L = \{ l \}$.
+
+\vspace{3em}
+
+\begin{lem}
+  We can lift the homomorphism $f$ to a new homomorphism $f_{pg}$ over the product graphs in the following way:
   \[ \begin{array}{rcl}
-    f_{pg}( s ) & = & s^A  \\
+    f_{pg}( start ) & = & start^A  \\
     f_{pg}( (l,q_1,\ldots,q_n) ) & = & (f(l),q_1,\ldots,q_n) \\
   \end{array} \]
-\end{defn}
-
-\vspace{1em}
+
+  We prove that $f_{pg}: G' \rightarrow G'^A$ is a valid homomorphism
+  \begin{proof}
+    From Lemma 4, we know that $(f(l),q_1,\ldots,q_n)$ is a valid node in $PG^A$ since each automata
+    shares the same states. Assume there is an edge in $PG$ from $x=(l,q_1,\ldots,q_n)$
+    to $y=(l',q_1',\ldots,q_n')$. We know that $f(x) = (f(l),q_1,\ldots,q_n)$ and $f(y) = (f(l'),q_1',\ldots,q_n')$.
+    From the construction of PG, we know that $\sigma_i(q_k, l) = q_k'$.
+However, from the construction of the abstract automata, we also know that $\sigma_i(q_k, l) = q_k' \iff \sigma^A_i(q_k, f(l)) = q_k'$.
+Therefore, we can conclude that $\sigma^A_i(q_k, f(l)) = q_k'$.
+However, from the definition of $PG^A$, this means that there must be an edge in $PG^A$ for ($f(x),f(y)$).
+  \end{proof}
+\end{lem}
+
 \begin{lem}
-  If $f_{pg}(n) = N$, then $P(n) = P^A(N)$.
+  If $f_{pg}(n) = N$, then the product graph preference of these nodes is equal: $\Rank(n) = \Rank^A(N)$.
 
   \begin{proof}
-    Assume $n = (a,q_1,\dots,q_k)$. We know that $f_{pg}(n) = (f(a),q_1,\dots,q_k)$. 
-    We also know that $q_i \in F_i \iff q_i \in F^A_i$. 
-    By the definition of the preference function $P$, then $P(n) = P^A(N)$.
+    Assume $n = (l,q_1,\dots,q_k)$. We know that $f_{pg}(n) = (f(l),q_1,\dots,q_k)$. 
+    We also know that $q_i \in F \iff q_i \in F^A$. 
+    By the definition of the ranking function $\Rank$, then 
+    $\Rank(n) = \{ i ~\vert~ q_i \in F \} = \{ i ~\vert~ q_i \in F^A \} = \Rank^A(N)$.
   \end{proof}
@@
 
-\vspace{1em}
 \begin{lem}
-  If, for abstract product graph $PG$, if we have the following:
+  For every state $N = (L, q_1, \dots, q_n)$ in $PG^A$, there exists a state $n = (l,q_1, \ldots, q_n)$ in $PG$
+  such that $f_{pg}(n) = N$.
+
+  \begin{proof}
+    By assumption, we assumed that $f$ is surjective.
+That is, every location $L$ in the original abstract topology $G^A$ is mapped to by at least one location $l$ in the concrete topology $G$: $f(l) = L$.
+  \end{proof}
+
+  \todo{re evaluate this}
+
+  \todo{make explicit the fact that we can't anycast}
+
+  \todo{tie back to existing lemmas}
+
+\end{lem}
+
+\vspace{1em}
+
+Next, we show that whenever there is a transition in $PG^A$, there is a corresponding step in the concrete product graph $PG$.
+This will allows to show that, if the preference inference succeeds for the abstract product graph, then it will also succeed for the concrete product graph while inferring the same preferences.
+
+\vspace{1em}
+
+\begin{lem}
+  If, for $PG$ and $PG^A$ we have the following:
 
@@
     1. & (a,b) ~\text{is an edge in the concrete topology} \\
-    2. & \tilde{m} = a \\
+    2. & \Topo(m) = a \\
     3. & f_{pg}(m) = M \\
     4. & (M,N) ~ \text{is an edge in the product graph}~ PG^A \\
-    5. & \tilde{N} = f(b) \\
-  \end{array} \]
-
-  then there exists a node $n$ in the concrete product graph $PG$ where:
+    5. & \Topo(N) = f(b) \\
+  \end{array} \]
+
+  then there exists a node $n$ in $PG$ where:
 
   \[ \begin{array}{ll}
-    1. & \tilde{n} = b \\
+    1. & \Topo(n) = b \\
     2. & f_{pg}(n) = N \\
@@
   \begin{proof}
-
-    suppose that $m = (a, q_1, \dots, q_k)$.
-Then we know that $M = (f(a), q_1, \dots, q_k)$.
-Also suppose there is some $b$ such that $N = (f(b), s_1, \dots, s_k)$ since $f^{-1}(N) \neq \emptyset$.
-This means that, since $(a,b)$ is an edge in the concrete topology, $(f(a),f(b))$ is an edge in the abstract topology.
-Also we know that $\tilde{N} = f(b)$.
-
+    $ $
+    \vspace{1em}
+
+    \noindent
+    Since $\Topo(m) = a$, suppose that $m = (a, q_1, \dots, q_k)$.
+We know that $f_{pg}(m) = M = (f(a), q_1, \dots, q_k)$.
+By assumption $N = (f(b), s_1, \dots, s_k)$.
 Let us take the node $n = (b, s_1, \dots, s_k)$.
 
+    \vspace{.8em}
     \begin{easylist}
-      & Clearly $\tilde{n} = b$
+      & Clearly $\Topo(n) = b$
       & Clearly $f_{pg}(n) = (f(b), s_1, \dots, s_k) = N$
-      & For each regular expression $\sigma^A(q_i, f(b)) = s_i$.
-This means that for each regular expression, $\sigma(q_i, b) = s_i$ if $q_i \neq q_{0_i}$.
-We know that $q_i \neq q_{0_i}$ due to the side condition for automaton construction.
-It follows that $(m,n)$ is an edge in the product graph by definition.
+      & Since $(M,N)$ is an edge in $PG^A$, we know that, for each automata transition function: $\sigma^A(q_i, f(b)) = s_i$.
+From the automata construction, this means that for each regular expression, $\sigma(q_i, b) = s_i$ if $q_i \neq q_{0_i}$.
+We know that $q_i \neq q_{0_i}$ due to the side condition for automaton construction that ensures no transitions to the initial state.
+It follows that $(m,n)$ is an edge in the product graph since $(a,b)$ is a valid topology edge by assumption, and $\sigma(q_i, b) = s_i$.
     \end{easylist}

### 2017-03-14 paper/abstraction/appendix.tex
more edits to appendix

@@
 
+\vspace{.5em}
 \begin{lem} $M$ and $M^A$ have the same set of states. That is, $Q = Q^A$.
@@
     \begin{proof}
-      This follows trivially from the construction of $M$.
+      This follows trivially from the construction of $M$. States in $M$ are copied over from states in $M^A$.
     \end{proof}
@@
 
-  We prove that $f_{pg}: G' \rightarrow G'^A$ is a valid homomorphism
+  Now we prove that $f_{pg}: G' \rightarrow G'^A$ is a valid homomorphism
   \begin{proof}
@@
 
-\begin{lem}
-  For every state $N = (L, q_1, \dots, q_n)$ in $PG^A$, there exists a state $n = (l,q_1, \ldots, q_n)$ in $PG$
-  such that $f_{pg}(n) = N$.
-
-  \begin{proof}
-    By assumption, we assumed that $f$ is surjective.
+%\begin{lem}
+%  For every state $N = (L, q_1, \dots, q_n)$ in $PG^A$, there exists a state $n = (l,q_1, \ldots, q_n)$ in $PG$
+%  such that $f_{pg}(n) = N$.%
+
+%  \begin{proof}
+%    By assumption, we assumed that $f$ is surjective.
 That is, every location $L$ in the original abstract topology $G^A$ is mapped to by at least one location $l$ in the concrete topology $G$: $f(l) = L$.
-  \end{proof}
+%  \end{proof}
+%\end{lem}
 
@@
 \todo{tie back to existing lemmas}
-
-\end{lem}
 
@@
 
+\newcommand{\trans}[3]{\ensuremath{#1 \overset{#3}{\rightarrow} #2}}
+
 \begin{lem}
-  $m \leq m'$ in the concrete product graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph under the lifted graph homomorphism $f_{pg}$.
-
+  For any transition $\trans{m}{m'}{l}$ in $PG$, there is a corresponding transition $\trans{f(m)}{f(m')}{f(l)}$ in $PG^A$.
   \begin{proof}
-    $(\Leftarrow)$
-
-    Suppose we have a simulation relation from the subgraphs rooted at nodes $M$ and $M'$ with $M' \geq_{rank} M$ in the abstract product graph.
-Assume that $\tilde{M} = f(a)$ and $\tilde{N} = f(b)$.
-For each neighbor $N'$, if we can make a move from $M'$:
-
-    $$M' \overset{\tilde{N'}}{\rightarrow} N'$$
-
-    then we also make a similar move for $M$ for some $N$ where $N \approx N'$ and $N' \geq_{rank} N$:
-
-    $$M \overset{\tilde{N}}{\rightarrow} N$$
-
+    if $m' = (l, q_1, \ldots, q_n)$, then $f(m') = (f(l), q_1, \ldots, q_n)$.
+Since there is the edge $(m,m')$ in $PG$, then there is the edge $(f(m),f(m'))$ in $PG^A$.
+Finally, because $\Topo(f(m')) = f(l)$, there must be a transition $\trans{f(m)}{f(m')}{f(l)}$.
+  \end{proof}
+\end{lem}
+
+% n --> m'
+% m' --> n
+
+\vspace{.4em}
+\begin{lem}
+  In the concrete product graph, $m \leq m' \iff f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph.
+  \begin{proof}
+    $ $
+
+    \vspace{1em}
+    We show that $\leq$ forms a simulation relation for the subgraph reachable from $m$ and $m'$ in $PG$ iff $\leq$ forms a simulation relation for the subgraph reachable from $f(m)$ and $f(m')$ for $PG^A$.
+This involves showing that $m \geq_{rank} m' \iff f(m) \geq_{rank} f(m')$, and that
+    for every transition $\trans{m}{n}{l}$ in $PG$ there is a transition $\trans{m'}{n'}{l}$ iff for every transition $\trans{f(m)}{f(n)}{f(l)}$ in $PG^A$ there is a transition $\trans{f(m')}{f(n')}{f(l)}$.
+
+    \vspace{1em}
+    \textbf{Case} $(\Rightarrow)$
+
+    Consider the subgraph of $PG$ reachable from $m$ and $m'$. From $m \leq m'$ and the definition of ($\leq$), we know that $m' \geq_{rank} m$.
+
+    %
+    From Lemma 6, and $m' \geq_{rank} m$ we know that $f_{pg}(m') \geq_{rank} f_{pg}(m)$. 
+    From Lemma 8, there is a transition $\trans{f(n)}{f(n')}{f(l)}$.
+
+    \vspace{1.2em}
+    \textbf{Case} $(\Leftarrow)$
+
+    Let $M = f(m)$ and let $M' = f(m')$.
+    Suppose that $M \leq M'$, which means that with $M' \geq_{rank} M$ in the abstract product graph.
+It also means that, for each neighbor $N'$, if we have the transition: $\trans{M'}{N'}{L}$ then we also have a transition: $\trans{M}{N}{L}$ where $N' \geq_{rank} N$.
 We must show that the same relation holds for $m$ and $m'$.
 
-    Now assume $m'$ has a neighbor $n'$ where $\tilde{m} = a$ and $\tilde{n} = b$.
-Then clearly $(a,b)$ is a valid topology edge since it is a transition in the product graph.
-We now apply the previous lemma with the following facts:
+    \vspace{1em}
+    Assume that $\Topo(M) = f(a)$ and $\Topo(N) = f(b)$.
+\todo{This can be done because $f$ is surjective}.
+Also assume that $m'$ has a neighbor $n'$.
+We know that $\Topo(m) = a$ and $\Topo(m') = b$.
+Clearly $(a,b)$ is a valid concrete topology edge since it is a transition in the product graph between $m$ and $m'$.
+We now apply Lemma 7 with the following facts:
 
     \[ \begin{array}{ll}
-      1. & (a,b) ~\text{is a topology edge} \\
-      2. & \tilde{m} = a \\
+      1. & (a,b) ~\text{is a concrete topology edge} \\
+      2. & \Topo(m) = a \\
       3. & f_{pg}(m) = M \\
       4. & (M,N) ~\text{is an edge in}~ PG^A \\
-      5. & \tilde{N} = f(b) \\
-    \end{array} \]
-
-    This lets us conclude that there exists a node $n'$ such that:
+      5. & \Topo(N) = f(b) \\
+    \end{array} \]
+
+    Lemma 7 lets us conclude that there exists a node $n'$ such that:
 
     \[ \begin{array}{ll}
-      1. & \tilde{n} = b \\
+      1. & \Topo(n) = b \\
       2. & f_{pg}(n) = N \\
       3. & (m,n) ~\text{is an edge in}~ PG \\
-      4. & P(n) = P(N) \\
-    \end{array} \]
-
-    Thus if we have $m' \overset{b}{\rightarrow} n'$, then we also have $m \overset{b}{\rightarrow} n$.
-The previous lemma can also be used to show that $P(n') = P(N')$ in a symmetric fashion, so we are guaranteed that $n' \geq_{rank} n$ from the fact that $N' \geq_{rank} N$.
+      4. & \Rank(n) = \Rank(N) \\
+    \end{array} \]
+
+    Thus if there is transition $\trans{m'}{n'}{b}$, then there is also a transition $\trans{m}{n}{b}$. Lemma 6 together with the assumption $N' \geq N$ shows that $n' \geq{rank} n$.
 
@@
 
-  \begin{proof}
-    $(\Rightarrow)$
-
-    This is the simpler case. We assume we have $m' \overset{b}{\rightarrow} n'$ implies $m \overset{b}{\rightarrow} n$.
-    Simply take $N = f_{pg}(n)$ and $N' = f_{pg}(n')$.
-If we know that $M' \overset{b}{\rightarrow} N'$ then we already know that $M \overset{b}{\rightarrow} N$ from the homomorphism.
-All that's required is to show that $N' \geq_{rank} N$.
-This follows trivially from the fact that $P(n) = P(N)$ and $P(n') = P(N')$.
-  \end{proof}
-
 \end{lem}
 
-\vspace{1em}
+\vspace{3em}
+
+The previous lemma tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
+We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.
+
 \begin{defn}
-  Assign $ord(m) = ord^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
-  Clearly $ord(m) \leq ord(m') \iff m \leq m'$ and $ord(f_{pg}(m)) \leq ord(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
+  Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
+  Clearly $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
 \end{defn}
 
-\vspace{1em}
-\begin{defn}
-  The previous theorem tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
-  We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.
-\end{defn}
-
-\vspace{1em}
-\subsection{Substitution}
+\vspace{3em}
+\subsection{Constraint Substitution (Part 2)}
 

### 2017-03-15 paper/abstraction/appendix.tex
checkpoint

@@
      pol     &::=& p_1, \dots, p_n & \textit{policies} \\
-     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
+     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
      pfx     &::=& d.d.d.d/[d..d] & \textit{prefix} \\
@@
          &\BNFALT& r^* & \textit{iteration} \\
-     cc     &::=& agg(pfx, r_1 \rightarrow r_2)  & \textit{control constraints} \\
   \end{array} \]%
@@
 %\begin{lem}
-%  For every state $N = (L, q_1, \dots, q_n)$ in $PG^A$, there exists a state $n = (l,q_1, \ldots, q_n)$ in $PG$
-%  such that $f_{pg}(n) = N$.%
-
+%  For every state $N = (L, q_1, \dots, q_n)$ in $PG^A$ for which there is no edge $(start^A, N)$, there exists a state $n = (l,q_1, \ldots, q_n)$ in $PG$
+%  such that $f_{pg}(n) = N$.
 %  \begin{proof}
-%    By assumption, we assumed that $f$ is surjective.
+%    By assumption, we know that that $f$ is surjective.
 That is, every location $L$ in the original abstract topology $G^A$ is mapped to by at least one location $l$ in the concrete topology $G$: $f(l) = L$.
+%
+
+%    Since there exists an $l$ such that $f(l) = L$, there must be the concrete node $(l, q_1, \ldots, q_n)$ in $PG$.%
+%
+
+%    %If $N$ is a node in $PG^A$ that is is not connected to the $start^A$ node, then no automata state is the initial state $q_i \neq q_{0_i}$.
+This means that that N must have at least one inbound edge that is not $start^A$, otherwise the node would not exist.
+Without loss of generality, assume there is an edge $(M,N)$ for $M = (L', s_1, \ldots, s_n)$.
 %  \end{proof}
@@
 
+In this section, we aim to prove that concretization and compilation commute for individual \sysname constraints.
+Since a policy is simply an ordered sequence of constraints, it is then straightfoward to show that compilation and concretization commute for entire policies.
+In particular, we are interested in showing:
+%
+$$\Con(\Compile(p, G^A), \Gamma, f, G) = \Compile(\Con(p,\Gamma,f), G)$$
+%
+The proof goes by case analysis on the test $t$ in the constraint $p$, and makes heavy use of the lemmas about the product graphs from the previous section.
+We use one helper lemma here that relates sets of neighbors:
+
+\todo{re evaluate this. I believe we need the proof of an inverse here}
 \begin{lem}
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
+     ~~~~~~~~~ [~ pfx \rightarrow [~ ma~\vert~ \\
      ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
      ~~~~~~~~~~~~~~~~~~ pin = \mathit{adjIn}(PG^A,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \} \}), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(BS,q_N) ~\vert~ BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \}, BS \neq \emptyset  \}, \\
      ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \mathit{adjOut}(PG^A,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
   \end{array} \]%
@@
   \[ \begin{array}{l}
-     ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_M) \in PG, \\
+     ~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG, \\
      ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in I, bs=\{ b ~\vert~ (b,q_N) \in pin\} \}), \\
+     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{ b ~\vert~ (b,q_n) \in pin\}, bs \neq \emptyset \}), \\
      ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathit{adjOut}(PG,m) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
+     ~~~~~~~~~~~~~~~~~~ ma = ord^A(f_{pg}(m)) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
   \end{array} \]%
@@
   \begin{proof}
-    For each $M$ there exists at least one $m$ such that $f_{pg}(m) = M$.
-Note that $f_{pg}$ overapproximates the connectivity of the product graph, by virtue of being a graph homomorphism.
-For each concrete node $n$ such that $n = (b,q_n) \in adjIn(PG,m)$ we know that if $f_{pg}(n) = N$ where $N = (f(b),q_N)$, then $N \in adjIn(PG^A,M)$ and $q_n = q_N$ from the homomorphism.
-Thus by taking $f^{-1}(B) = f^{-1}(f(b))$, for each such $f(b)$ for node $N$ that shares the same state $q_N$, we get a superset of the locations from the concrete graph.
-However, by restricting those locations to only those that appear in the topology $(b,\ell)$, we get exactly the set that appears in the concrete product graph.
-    This is because we know $q_N \rightarrow q_M$ from the abstract product graph is a valid transition, which means that $q_n \rightarrow q_m$ is a valid concrete product graph transition, and if there is a topology edge $(b,\ell)$, then there must be a product graph edge $(n,m)$.
-Therefore:
+    $ $
+    \vspace{.4em}
+
+    Suppose for node $M$, there exists a node $m=(l,q_m)$ such that $f_{pg}(m) = M$. 
+    We observe the following superset relation:
+    %
+    $$\{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG,m)\} \subseteq \{ b ~\vert~ (b,l) \in G.E \}$$
+    %
+    This is trivially true from the definition of the product graph. Any product graph edge will correspond to a topology edge. The following inequality will also hold:
+    %
+    $$\{b ~\vert~ b \in f^{-1}(B),~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \} \supseteq \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\}$$
+    %
+    Since whenever $(b,q_N) \in adjIn(PG,m)$ it must be the case that $(B,q_N) \in adjIn(PG^A, f_{pg}(m))$ by the homomorphism, and because $f^{-1}(B) \supseteq \{ b \}$.
+By combining these observations, we can conclude the following:
+    %
     $$\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \}$$
@@
     $$\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\}$$
-    This also holds for the case with adjOut.
-Further, note that because we are looking at a particular location $l$, there can only be at most one such $m = (l,q_N)$ such that $f_{pg}(m) = M = (f(l), q_N)$.
-If there is no such $m$ where $f_{pg}(m) = M$, then the above expression will produce the empty set after filtering with the topology.
-Going over each $M$ then is equivalent to going over each $m$ so long as we throw away imports $\mathit{in}$ that are empty.
+    %
+    The same reasoning can be applied to adjOut as well. 
+    Further, note that because we are looking at a particular location $l$, there can only be at most one such $m = (l,q_N)$ such that $f_{pg}(m) = M = (f(l), q_N)$ since the automata are deterministic.
+    %
+    This means that $M \leftarrow (l,q_M) \in PG^A$ can be replaced with $m \leftarrow (l,q_m) \in PG$ since for each $M$ we will either have some $m$ such that $f_{pg}(m) = M$ and the above equivalence holds, or else there is no such $M$, in which case the set is filtered by the condition: $BS \neq \emptyset$.
 
@@
 
+\begin{thm}
+  For all \sysname constraints $p$, contexts $\Gamma$, topologies $G$ and $G^A$ related by homomorphism $f : G \rightarrow G^A$:
+  $$\Con(\Compile(p,G^A),\Gamma,f,G) = \Compile(\Con(p,\Gamma,f),G)$$
+
+  \begin{proof} From the grammar, we know that $p = (t \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n)$.
+The proof proceeds by cases on $t$.
+In each case, we expand the definition of $\Compile$ and $\Con$ until they no longer appear in the term.
+We then appeal to graph properties of $PG$ and $PG^A$ to rewrite the terms into equivalent forms.
+
+  \vspace{.4em}
+  \textbf{Case} ($t = pfx$)
+  \vspace{.4em}
+
+    For the right side:
+
+    \[
+    \begin{array}{llll}
+      & & \Compile(\Con(p,\Gamma,f),G) \\
+      &=& \Compile(\Con(pfx \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, \Gamma,f), G) 
+            & \text{Substitution} \\
+      &=& \Compile(pfx \Path~ \Con(r_1,\Gamma,f) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n, \Gamma,f), G) 
+            & \text{Definition of con} \\
+      &=& \Compile(pfx \Path~ \Con(r_1,\Gamma,f) \cap \EndR(\Sigma) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n, \Gamma,f) \cap \EndR(\Sigma), G) 
+            & \text{Regex Equivalence}\\
+      &=& \CompileMbgp([\CompilePg(pfx \Path~ \Con(r_1,\Gamma,f) \cap \EndR(\Sigma) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n, \Gamma,f) \cap \EndR(\Sigma),G)]) 
+            & \text{Definition of compile} \\
+
+      &=& \CompileMbgp([(pfx, PG, \Pref)]) 
+            & \text{Assumption} \\
+
+    \end{array}
+    \]
+
+    Similarly, for the left side:
+
+        \[
+    \begin{array}{llll}
+      & & \Con(\Compile(p,G^A),\Gamma,f,G) \\
+      &=& \Con(\Compile(pfx \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A),\Gamma,f,G)
+            & \text{Substitution} \\
+      &=& \Con(\CompileMbgp([\CompilePg(pfx \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A)]),\Gamma,f,G)
+            & \text{Definition of Compile} \\
+      &=& \Con(\CompileMbgp([(pfx,PG^A,\Pref^A)]),\Gamma,f,G)
+            & \text{Assumption}\\
+    \end{array}
+    \]
+
+    Both sides of the equality are now in a form where we can apply the lemmas from the previous section.
+    This allows us to relate $PG$ and $PG^A$ as well as $\Pref$ and $\Pref^A$.
+    Continuing to expand the right side by substituting the definition of $\CompileMbgp$ we get:
+
+  \[ \begin{array}{l}
+     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ l \in internal(G.V), ~rc =  \\
+     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~]\\
+  \end{array} \]%
+
+  Next we further expand on the left side for the abstract topology to show it is equivalent:
+
+  \[ \begin{array}{l}
+     ~~~~~ \Con([~ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
+     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] ~], \Gamma, f, G) \\
+  \end{array} \]%
+
+  We apply the definition of $\Con$ to push it inside the list:
+
+    \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow \Con(rc, \ell, \Gamma, f, G) ~\vert~ \\
+     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
+     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] ~] \\
+  \end{array} \]%
+
+  We now apply the definition of $\Con$ to push it further inside:
+
+      \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
+     ~~~~~~~~~~~~~~~ \Con([~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma, f, G) ~] \\
+  \end{array} \]%
+
+  Once again, we apply the definition of $\Con$
+
+      \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
+     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), true, \ell, \Gamma, f, G) ~] ~] ~] \\
+    \end{array} \]%
+
+    Next, we rewrite the sets $in$ and $out$ according to $\Con$:
+
+      \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
+     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (\Con(in,\ell,\Gamma,f,G),q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \Con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \ell,\Gamma,f,G), \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), true, \ell, \Gamma, f, G) ~] ~] ~] \\
+  \end{array} \]%
+
+  Rewrite $\Con$ in the set $in$:
+
+    \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
+     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\Con(\{B ~\vert~ (B,q_N) \in pin \}, \ell, \Gamma, f, G), BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \Con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \ell,\Gamma,f,G), \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), true, \ell, \Gamma, f, G) ~] ~] ~] \\
+  \end{array} \]%
+
+  Apply the definition of $\Con$ on the inner set of $in$ and $out$:
+
+    \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
+     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{b ~\vert~ b \in f^{-1}(B), (b,\ell)\in G.E, (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ c \in f^{-1}(C), (c,\ell)\in G.E, (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), true, \ell, \Gamma, f, G) ~] ~] ~] \\
+  \end{array} \]%
+
+  From Lemma 10, this is equivalent to the following:
+
+    \[ \begin{array}{l}
+     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ l \in internal(G.V), ~rc =  \\
+     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(f_{pg}(m)) : (in,q_) \rightarrow (out,q_m) ~] ~] ~]\\
+  \end{array} \]%
+
+  From Definition 2, we know that the $\Pref(m) = \Pref(f_{pg}(m))$:
+
+    \[ \begin{array}{l}
+     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ l \in internal(G.V), ~rc =  \\
+     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~]\\
+  \end{array} \]%
+
+  This is exactly the result we obtained from expanding the right hand side of the equality.
+
+  \vspace{.4em}
+  \textbf{Case} ($t = \$x$)
+  \vspace{.4em}
+
+    The case for $t = \$x$ follows a similar line of reasoning. We start by evaluating the right-hand side:
+
+    \[
+    \begin{array}{llll}
+      & & \Compile(\Con(p,\Gamma,f),G) \\
+      &=& \Compile(\Con(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, \Gamma,f), G) 
+            & \text{Substitution} \\
+      &=& \Compile([pfx \Path~ \Con(r_1,\Gamma,f) \cap \EndR(l) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n, \Gamma,f) \cap \EndR(l) ~\vert~ (pfx,l) \in \Gamma(x)], G) 
+            & \text{Definition of con} \\
+      &=& \CompileMbgp([\CompilePg(pfx \Path~ \Con(r_1,\Gamma,f) \cap \EndR(l) ~\Prefer~ \\
+      & & ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \ldots ~\Prefer~ \\ 
+      & & ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \Con(r_n, \Gamma,f) \cap \EndR(l),G) ~\vert~ (pfx,l) \in \Gamma(x)]) 
+            & \text{Definition of compile} \\
+
+      &=& \CompileMbgp([(pfx_1, PG_1, \Pref_1), \ldots, (pfx_k, PG_k, \Pref_k)]) 
+            & \text{Assumption} \\
+
+    \end{array}
+    \]
+
+    Expanding further, this becomes:
+
+      \[ \begin{array}{l}
+     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ l \in internal(G.V), ~rc = append_i \\
+     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~]\\
+  \end{array} \]%
+
+    As before, we now show that the right hand side is equivalent by applying the definitions of $\Con$ and $\Compile$:
+
+        \[
+    \begin{array}{llll}
+      & & \Con(\Compile(p,G^A),\Gamma,f,G) \\
+      &=& \Con(\Compile(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A),\Gamma,f,G)
+            & \text{Substitution} \\
+      &=& \Con(\CompileMbgp([\CompilePg(\$x \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n,G^A)]),\Gamma,f,G)
+            & \text{Definition of Compile} \\
+      &=& \Con(\CompileMbgp([(pfx,PG^A,\Pref^A)]),\Gamma,f,G)
+            & \text{Assumption}\\
+    \end{array}
+    \]
+
+  Next we further expand on the left side for the abstract topology to show it is equivalent:
+
+  \[ \begin{array}{l}
+     ~~~~~ \Con([~ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
+     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] ~], \Gamma, f, G) \\
+  \end{array} \]%
+
+  \end{proof}
+
+\end{thm}
+
+\vspace{5em}
+\todo{---------------- OLD STUFF -------------------}
 \begin{thm}

### 2017-03-15 paper/abstraction/appendix.tex
refactoring proof

@@
   \vspace{.4em}
+  \noindent
   \textbf{Case} ($t = \$x$)
@@
 
+    \noindent
     The case for $t = \$x$ follows a similar line of reasoning. We start by evaluating the right-hand side:
@@
 
+    \noindent
     Expanding further, this becomes:
@@
 
+    \noindent
     As before, we now show that the right hand side is equivalent by applying the definitions of $\Con$ and $\Compile$:
@@
             & \text{Definition of Compile} \\
-      &=& \Con(\CompileMbgp([(pfx,PG^A,\Pref^A)]),\Gamma,f,G)
+      &=& \Con(\CompileMbgp([(\$x,PG^A,\Pref^A)]),\Gamma,f,G)
             & \text{Assumption}\\
@@
 
+  \noindent
+  Note that $PG_i$ and $PG^A$, as well as $\Pref$ and $\Pref^A$ are related by the lemmas from the previous section.
 Next we further expand on the left side for the abstract topology to show it is equivalent:
@@
      ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc =  \\
-     ~~~~~~~~~~~~~~~ [~ pfx \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~ [~ \$x \rightarrow [~ ma ~\vert~ \\
      ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
@@
 
-  \end{proof}
-
-\end{thm}
-
-\vspace{5em}
-\todo{---------------- OLD STUFF -------------------}
-\begin{thm}
-  For any context $\Gamma$, concrete topology $G$, abstract topology $G^A$, homomorphism $f : G \rightarrow G^A$:
-
-  $$con(compile(pol,G^A),\Gamma,f,G) = compile(con(pol,\Gamma,f),G)$$
-
-  \begin{proof} \text{ }
-
-    Suppose that $pol = p_1, \dots, p_n$. Each $p_i$ has the form $(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik})$. Then by evaulating:
-
-    \[ \begin{array}{lcl}
-      con(pol,\Gamma,f) & = & con(p_1,\dots,p_n,\Gamma,f) \\
-                        & = & con(p_1,\Gamma,f), \dots, con(p_n,\Gamma,f) \\
-                        & = & con(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k},\Gamma,f), \\
-                        &   & \dots, \\
-                        &   & con(t_n ~\Path~ r_{n1} ~\Prefer~,\dots, ~\Prefer~ r_{nk},\Gamma,f) \\
-    \end{array} \]
-
-    For each test $t_i$, if $t_i = pfx$, then we get
-
-    \[ \begin{array}{ll}
-          & con({pfx}_{i1} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik},\Gamma,f) \\
-        = & {pfx}_{i1} ~\Path~ con(r_{i1},\Gamma,f) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik},\Gamma,f) \\
-    \end{array} \]
-
-    For each test $t_i$, if $t_i = \$x$, then we get
-
-    \[ \begin{array}{lcl}
-        con(\$x_{i} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik},\Gamma,f) 
-            & = & {pfx}_{i1} ~\Path~ con(r_{i1},\Gamma,f) \cap \text{end}(l_{i1}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik},\Gamma,f) \cap \text{end}(l_{i1}), \\
-            &   & \dots, \\ 
-            &   & {pfx}_{ij} ~\Path~ con(r_{i1},\Gamma,f) \cap \text{end}(l_{ij}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik},\Gamma,f) \cap \text{end}(l_{ij}), \\
-            &   & \\
-            &   & \text{for each } (pfx_{ij}, l_{ij}) \in \Gamma(x) \\
-    \end{array} \]
-
-    Next we compute $compile(con(pol,\Gamma,f), G)$:
-
-    \[ \begin{array}{ll}
-        & compile(con(pol,\Gamma,f), G)  \\
-                          & \\
-                         =& compile_{mBGP}( \\
-                          &  ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k},G ), \\
-                          &  ~~~~ \dots, \\
-                          &  ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk},G ), \\
-                          &  ~~~~ \dots, \\
-                          &  ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k},G ), \\
-                          &  ~~~~ \dots, \\
-                          &  ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk},G ) \\
-                          &  ) \\
-    \end{array} \]
-
-    \vspace{.5em}
-    This results in a series of prefixes, product graphs, and orderings of the form: $(pfx_{ij}, PG_{ij}, ord_{ij})$.
-
-    \vspace{1em}
-    Similarly, we can compute $compile(pol, G^A)$:
-
-    \[ \begin{array}{ll}
-        & compile(pol,G^A)  \\
-                      & \\
-                     =& compile_{mBGP}( \\
-                      & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k}, G^A ), \\
-                      & ~~~~ \dots, \\
-                      & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik}, G^A ), \\
-                      & ) \\
-    \end{array} \]
-
-    This results in a series of prefixes, product graphs, and orderings of the form $(t_i, PG^A_i, ord^A_i)$.
-
-    We know the follwing:
-
-    \begin{itemize}
-      \item each $PG^A_i$ and $PG_{ij}$ are related by $f_{pg}$
-      \vspace{-.2em}
-      \item each $ord^A_i$ and $ord_{ij}$ have the property that $ord^A(f_{pg}(m)) = ord_{ij}(m)$
-    \end{itemize}
-
-  \[ \begin{array}{l}
-     con(\textbf{compile}_\textbf{mBGP}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) ), \Gamma,f,G) \\
-  \end{array} \]%
-
-Unfold definition of $\text{compile}_\text{mBGP}$
-
-  \[ \begin{array}{l}
-     ~~~~~ con([~ l \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~ l \in internal(G^A.V), \\
-     ~~~~~~~~~ rc = \mathit{append}_i~  \\
-     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma,f,G) \\
-  \end{array} \]%
-
-  Apply the definition of $con$
-
-  \[ \begin{array}{l}
-     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~ \ell \in f^{-1}(l), \\
-     ~~~~~~~~~ l \in internal(G^A.V), \\
-     ~~~~~~~~~ rc = \mathit{append}_i~  \\
-     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_n) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
-  \end{array} \]%
-
-  Rewrite $con$ on $rc$
-
-  \[ \begin{array}{l}
-     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~ \ell \in f^{-1}(l), \\
-     ~~~~~~~~~ l \in internal(G^A.V), \\
-     ~~~~~~~~~ rc = con(\mathit{append}_i~  \\
-     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
-  \end{array} \]%
-
-  Apply definition of $con$
-
-  \[ \begin{array}{l}
-     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~ \ell \in f^{-1}(l), \\
-     ~~~~~~~~~ l \in internal(G^A.V), \\
-     ~~~~~~~~~ rc = \mathit{append}_i~  \\
-     ~~~~~~~~~~~~~~~ con([~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
-  \end{array} \]%
-
-  \vspace{1em}
-  \textbf{Case 1}: Assume $t_i = pfx_{i1}$. Look at:
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ con([~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
-  \end{array} \]%
-
-  Apply definition of $con$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1, \dots, ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
-  \end{array} \]%
-
-  Apply definition of $con$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1,\text{true},\ell,\Gamma,f,G), \dots, con(ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
-  \end{array} \]%
-
-  Apply definition of $con$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\text{true},\ell,\Gamma,f,G) ~] \\
-  \end{array} \]%
-
-  Apply definition of $con$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M),\ell,\Gamma,f,G) ~] \\
-  \end{array} \]%
-
-  Rewrite on $in$ and $out$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (con(in,\ell,\Gamma,f,G),q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
-  \end{array} \]%
-
-  Rewrite $con$ on $in$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=con(\{B ~\vert~ (B,q_N) \in pin \},\ell,\Gamma,f,G) \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
-  \end{array} \]%
-
-  Apply definition of $con$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{c~\vert~ c \in f^{-1}(C),~ (c,\ell) \in G.E,~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
-  \end{array} \]%
-
-  From the relation between concrete ($PG$) and abstract ($PG^A$) product graphs given by the previous lemma
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_M) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{i1},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}), \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
-  \end{array} \]%
-
-  Since $ord^A_i(f_{pg}(m)) = ord_{i1}(m)$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_M) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{i1},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, bs=\{ b ~\vert~ (b,q_N) \in ping \} \}), \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_N) \rightarrow (out,q_M) ~] \\
-  \end{array} \]%
-
-  Since product graphs have equivalent states
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{i1},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}), \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
-  \end{array} \]%
-
-  \vspace{1em}
-  \textbf{Case 2}: Assume $t_i = \$x$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ con([~ \$x \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
-  \end{array} \]%
-
-  Apply the definition of $con$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{ij} \rightarrow con(ma_1, \dots, ma_k,\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
-  \end{array} \]%
-
-  Apply definition $con$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{ij} \rightarrow con(ma_1,\ell,\Gamma,f,G), \dots, \\ 
-     ~~~~~~~~~~~~~~~~~~~~~~~~~~ con(ma_k,\ell,\Gamma,f,G) ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
-  \end{array} \]%
-
-  Rewrite $con$ on $ma_h$.
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\ 
-     ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),l_{ij},\ell,\Gamma,f,G) ~] \\
-  \end{array} \]%
-
-  Apply definition of $con$
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\ 
-     ~~~~~~~~~~~~~~~~~~ (\Pfx_{ij},l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = \textbf{if}~ in=\{ G.s \} \text{ and } l_{ij} \neq \ell ~\textbf{then}~ \bullet \\ 
-     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else}~ ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M) \} \\
-  \end{array} \]%
-
-  \textbf{Observation}: 
-  By filtering the cases where $in = \{ \mathit{start} \}$ and $l_{ij} \neq \ell$ we get the same thing as before after applying the definition of $con$ for each $(pfx_{ij}, l_{ij}) \in \Gamma(x)$.
-
- \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{ij},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}), \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
-  \end{array} \]%
-
+  Apply the definition of $\Con$:
+
+  We apply the definition of $\Con$ to push it inside the list:
+
+  \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow \Con(rc, \ell, \Gamma, f, G) ~\vert~ \\
+     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = \\
+     ~~~~~~~~~~~~~~~ [~ \$x \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] ~] \\
+  \end{array} \]%
+
+  We now apply the definition of $\Con$ to push it further inside:
+
+  \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = \\
+     ~~~~~~~~~~~~~~~ \Con([~ \$x \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma, f, G) ~] \\
+  \end{array} \]%
+
+  Once again, we apply the definition of $\Con$
+
+  \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
+     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x),
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), \Gamma, f, G) ~] ~] ~] \\
+  \end{array} \]%
+
+  Once again, we apply the definition of $\Con$
+
+  \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
+     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \textbf{if } in = \{ G.start \} \textbf{ then } \bullet \\
+     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
+  \end{array} \]%
+
+  \todo{magic happens here}
+
+    \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
+     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \textbf{if } in = \{ G.start \} \textbf{ then } \bullet \\
+     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
+  \end{array} \]%
+
+  After filtering the cases where $in = \{ start \}$ and $l' \neq \ell$, we have the same situation as the previous case. 
   This works because each $PG_{ij}$ was constructed from $con(r_{ijk}) \cap end(l_{ij})$.
@@
 
-  \vspace{1em}
-  \textbf{Merging Cases}:
-
-  In the first case, we got a result of the form:
-
-  \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{i1}, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{i1},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}), \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{i1},m) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{i1}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
-  \end{array} \]%
-
-  In the second case, we got a result of the form:
-
- \[ \begin{array}{l}
-     ~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~ (pfx_{ij}, l_{ij}) \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{ij},m), \\
-     ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{ b ~\vert~ (b,q_n) \in ping \} \}), \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \}, \\
-     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] \\
-  \end{array} \]%
-
-  Putting these together, we get the following:
-
     \[ \begin{array}{l}
      ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~ \ell \in f^{-1}(l), \\
-     ~~~~~~~~~ l \in internal(G^A.V), \\
-     ~~~~~~~~~ rc = \mathit{append}_{ij}~  \\
-     ~~~~~~~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{ij},m), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
-  \end{array} \]%
-
-  Finally, we observe that this is equivalent to the following:
-
-  \[ \begin{array}{l}
-     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~ l \in internal(G.V), \\
-     ~~~~~~~~~ rc = \mathit{append}_{ij}~  \\
-     ~~~~~~~~~~~~~~~ [~ \Pfx_{ij} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_{ij}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_{ij},m), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_{ij},m) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_{ij}(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
-  \end{array} \]%
-
-  This is exactly the definition of compilation for the concretized policy
-
-  \[ \begin{array}{l}
-     = \textbf{compile}_\textbf{mBGP}( (pfx_{11},PG_{11},ord_{11}), \dots, (pfx_{ij},PG_{ij},ord_{ij}) ) \\
+     ~~~~~~~~~~~~ l \in internal(G.V), ~rc = append_i \\
+     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
+     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,m) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m)  ~] ~] ~]\\
   \end{array} \]%

### 2017-03-15 paper/abstraction/appendix.tex
more refactoring

@@
 
-\todo{re evaluate this}
-
-\todo{make explicit the fact that we can't anycast}
-
-\todo{tie back to existing lemmas}
-
 \vspace{1em}
@@
     Assume that $\Topo(M) = f(a)$ and $\Topo(N) = f(b)$.
-\todo{This can be done because $f$ is surjective}.
 Also assume that $m'$ has a neighbor $n'$.
@@
   Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
-  Clearly $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
+  Clearly from Lemma 9, $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
 \end{defn}
@@
 
-\todo{re evaluate this. I believe we need the proof of an inverse here}
 \begin{lem}
@@
      ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, \_) \in \Gamma(x), \\
      ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
@@
      ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~]\\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~]\\
   \end{array} \]%
@@
 
-  Apply the definition of $\Con$:
-
+  \noindent
   We apply the definition of $\Con$ to push it inside the list:
@@
 
+  \noindent
   We now apply the definition of $\Con$ to push it further inside:
@@
 
+  \noindent
   Once again, we apply the definition of $\Con$
@@
      ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma = \textbf{if } in = \{ G.start \} \textbf{ then } \bullet \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \textbf{if } in = \{ G.start \} \text{ and } l'=\ell \textbf{ then } \bullet \\
      ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
@@
 
-  \todo{magic happens here}
-
-    \[ \begin{array}{l}
-     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~~~~ \ell \in f^{-1}(l), \\
-     ~~~~~~~~~~~~ l \in internal(G^A.V), ~rc = append_i \\
-     ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
-     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A,M), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ BS=\{B ~\vert~ (B,q_N) \in pin \}, BS \neq \emptyset \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma = \textbf{if } in = \{ G.start \} \textbf{ then } \bullet \\
-     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
-  \end{array} \]%
-
   After filtering the cases where $in = \{ start \}$ and $l' \neq \ell$, we have the same situation as the previous case. 
-  This works because each $PG_{ij}$ was constructed from $con(r_{ijk}) \cap end(l_{ij})$.
-This means that the only state in $PG_{ij}$ connected to the start node ($\mathit{start}$) is a node for $l_{ij}$.
-This was ensured by the fact that the transition function for each regular expression $\sigma_{ijk}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{ij} \}$ from the construction of the automata.
+  This works because each $PG_{i}$ was constructed from $con(r_{i}, \ell, \Gamma, f, G) \cap end(l_{i})$.
+This means that the only state in $PG_{i}$ connected to the start node ($\mathit{start}$) is a node for $l_{i}$.
+This was ensured by the fact that the transition function for each regular expression $\sigma_{i}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{i} \}$ from the construction of the automata.
 
@@
      ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,m) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref(m) : (in,q_n) \rightarrow (out,q_m)  ~] ~] ~]\\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref_i(m) : (in,q_n) \rightarrow (out,q_m)  ~] ~] ~]\\
   \end{array} \]%
@@
 
+\vspace{2em}
+\begin{thm}
+  For all \sysname policies $pol$, contexts $\Gamma$, topologies $G$ and $G^A$ related by homomorphism $f : G \rightarrow G^A$:
+  $$\Con(\Compile(pol,G^A),\Gamma,f,G) = \Compile(\Con(pol,\Gamma,f),G)$$
+
+  \begin{proof} 
+    $ $
+
+    \vspace{.5em}
+    \noindent
+    Given a policy $pol = p_1, \ldots, p_n$ we apply Theorem 11 after rewriting the policy. For the left side:
+    \[
+    \begin{array}{llll}
+      & & \Con(\Compile(pol,G^A),\Gamma,f,G) \\
+      &=& \Con(\Compile(p_1, \ldots, p_n, G^A),\Gamma,f,G) & \text{Substitution} \\
+      &=& \Con(\CompileMbgp([\CompilePg(p_1), \ldots, \CompilePg(p_n)]),\Gamma,f,G)
+            & \text{Definition of Compile} \\
+      &=& \Con(\CompileMbgp([(t_1,PG^A_1,\Pref^A_1), \ldots, (t_n,PG^A_n,\Pref^A_n)]),\Gamma,f,G)
+            & \text{Assumption}\\
+    \end{array}
+    \]
+
+    \vspace{.5em}
+    \noindent
+    For the right side of the equation:
+    \[
+    \begin{array}{llll}
+      & & \Compile(\Con(pol,\Gamma,f),G) \\
+      &=& \Compile(\Con(p1,\dots,p_n, \Gamma,f), G) 
+            & \text{Substitution} \\
+      &=& \Compile(\Con(p1, \Gamma, f),\dots, \Con(p_n, \Gamma,f), G) 
+            & \text{Definition of con} \\
+      &=& \CompileMbgp([\CompilePg(\Con(p1, \Gamma, f),G), \ldots, \CompilePg(\Con(p_n, \Gamma, f),G)]) 
+            & \text{Definition of compile} \\
+
+      &=& \CompileMbgp([(t'_1, PG_1, \Pref_1), \ldots, (t'_n, PG_n, \Pref_n)])
+            & \text{Assumption} \\
+
+    \end{array}
+    \]
+
+    \noindent
+    First, we observe that, for each $p_i$, Theorem 11 and $\CompilePg$ give us that, for each $i$:
+    \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), \\ 
+     ~~~~~~~~~~~~ rc = [\CompilePred((t_i, PG^A_i, \Pref^A_i))] ~~] \\
+    \end{array} \]%
+
+    \noindent
+    Is equivalent to:
+
+    \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ l \in internal(G.V), \\ 
+     ~~~~~~~~~~~~ rc = [\CompilePred((t'_i, PG_i, \Pref_i))] ~~] \\
+    \end{array} \]%
+
+    \noindent
+    By applying the definition of $\CompileMbgp$, we need to show:
+
+    \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ l \in internal(G^A.V), \\ 
+     ~~~~~~~~~~~~ rc = append_{i \in \{1..n\}}(\CompilePred((t_i, PG^A_i, \Pref^A_i))) ~] \\
+    \end{array} \]%
+
+    \[ \begin{array}{l}
+     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ l \in internal(G.V), \\ 
+     ~~~~~~~~~~~~ rc = append_{i \in \{1..n\}}(\CompilePred((t'_i, PG_i, \Pref_i))) ~] \\
+    \end{array} \]%
+
+    \noindent
+    Clearly this follows by the definition of list $\mathrm{append}$
+
+  \end{proof}
+
+\end{thm}
+
 \end{document}

### 2017-03-15 paper/abstraction/appendix.tex
more edits to appendix

@@
          &\BNFALT& pfx & \textit{prefix test} \\
+     l   & & & \textit{topology location} \\
      r       &::=& l & \textit{location} \\
@@
   \[ \begin{array}{rclr}
+     l    &   & & \textit{topology location} \\
      d    &   & & \textit{integer} \\
@@
      \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
-     \Con(l, \Gamma, f)              &=& \Sigma_i ~ f_i^{-1}(l) \\
+     \Con(l, \Gamma, f)              &=& \Sigma ~ f^{-1}(l) \\
      \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
@@
 
-For reference, the full \sysname syntax as well as expansions from constraints into regular expressions are shown in Figure~\ref{fig:syntax}.
-mBGP syntax and compilation, as described in the paper, as well as concretization functions ($\Con$) are shown in Figure~\ref{fig:syntax}.
+For reference, the full \sysname syntax, expansions from constraints into regular expressions, mBGP syntax and compilation, as described in the paper, as well as concretization functions ($\Con$) are shown in Figure~\ref{fig:syntax}.
 
@@
 
-We present the definition of compilation slighty differently here by factoring a separate $\CompilePred$ function, to make the proof clearer.
-This is a simple rewriting of the compilation function defined in the body of the paper.
+We present the definition of compilation slighty differently here by factoring out a separate $\CompilePred$ function, to make the proof slightly cleaner.
+This is a very simple rewriting of the compilation function defined in the body of the paper where $\CompilePred$ is presented inline.
 
@@
 %
-For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$.
+For each regular expression $r$, the abstract location is replaced with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$.
 For each template variable, we replace it with a new entry for each of its corresponding concrete prefixes under the supplied mapping $\Gamma$.
@@
 
-We also define concretization over the mBGP policy in a similar manner.
-We replace each abstract router configuration $l \rightarrow rc$ a new entry for each concrete location $\ell \in f^{-1}(l)$.
+Concretization is defined for mBGP policies in a similar manner.
+Each abstract router configuration $l \rightarrow rc$ is replaced with a new entry for each concrete location $\ell \in f^{-1}(l)$.
 The concrete location $\ell$ is passed as a parameter to $con$ to remember the current router.
 %
-To concretize a prefix policy with a template ($\$x \rightarrow pc$) we replace it with a sequence of policies, one for each prefix in context ($(pfx,l) \in \Gamma(x)$).
+To concretize a prefix policy with a template ($\$x \rightarrow pc$), the template is replaced with a sequence of policies, one for each prefix in context ($(pfx,l) \in \Gamma(x)$).
 Match action statements where the set of import neighbors is the singleton set containing the product graph start node $\{ start \}$ and we are not currently at looking at the router configuration for the location specified in the context $l$, then we drop the match action.
 This is denoted with the $\bullet$ symbol.
-Finally, to concretize a set of neighbors, we again use $f^{-1}$ to find the set of concrete neighbors under the inverse homomorphism, but then restrict it to those that are actually connected in the underlying concrete topology with $G.E$.
+Finally, to concretize a set of neighbors, $f^{-1}$ is used to find the set of concrete neighbors under the inverse homomorphism, but then it is restricted to those that are actually connected in the underlying concrete topology with $G.E$.
 
@@
   \text{Product Graph} & PG, PG^A \\
-  \text{Automata} & M, M^A \\
 \end{array} \]
 
-We use capital letters for abstract topology/product graph nodes and we use lower case letters for concrete topology nodes.
-By default, product graph nodes with different subscripts refer to nodes that share the same topology location (\IE, $\Topo(n_1) = \Topo(n_2)$).
+Capital letters are used for abstract topology/product graph nodes and lower case letters for concrete topology nodes.
 A superscript $G^A$ refers to the abstract version (in this case of the topology), while the non-superscripted value refers to the concrete version.
@@
 
-The goal of the proof is to show that the concretization and compilation functions commute. In particular, we are interested in establishing the following theorem:
+The goal of the proof is to show that the concretization and compilation functions commute.
+One can concretize an abstract policy and then compile the concrete result, or compile an abstract policy and the concretize the abstract result and know that the results are the same.
+In particular, we are interested in establishing the following theorem:
 
@@
 
+\noindent
 The proof proceeds in the following steps.
@@
 \begin{array}{lll}
-  \CompilePg(t_1 \Path~ \Con(r_1,\Gamma,f) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n,\Gamma,f), G) &=& (t_1, PG, \Pref) \\
+  \CompilePg(t_1 \Path~ \Con(r_1,\Gamma,f) \cap \EndR(L) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n,\Gamma,f) \cap \EndR(L), G) &=& (t_1, PG, \Pref) \\
   \CompilePg(t_2 \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, G^A) &=& (t_2, PG^A, \Pref^A) \\
@@
 %
-Using this assumption, we show that several relationships hold between $PG$ and $PG^A$ as well as between $\Pref$ and $\Pref^A$.
-
-\para{Substitution of Constraints (Step 2)} The next step is to use the relationships established in step 1 to show that concretization and compilation commute for an individual constraint \sysname p:
+$L$ can be thought of as a set of locations that ``own" the prefix.
+Using these assumptions, we show that several relationships hold between $PG$ and $PG^A$ as well as between $\Pref$ and $\Pref^A$.
+In particular, we show that there is a homomorphism $f_{pg}$ from $PG$ to $PG^A$, and then using this fact, we demonstrate that the inferred local preference functions $\Pref$ and $\Pref^A$ have the property that for all nodes $m$,  $\Pref(m) = \Pref^A(f_{pg}(m))$.
+
+\para{Substitution of Constraints (Step 2)} 
+The next step is to use the relationships between $PG$ and $PG^A$ established in step 1 to show that concretization and compilation commute for an individual \sysname constraint p:
 %
@@
 %
-This proof proceeds by cases on the constraint p.
-
-\para{Substitution of Policies (Step 3)} Finally, this theorem is lifted to \sysname policies $pol = p_1, \ldots, p_n$ using the previous proof for individual constraints to obtain the final theorem:
+Constraints are of the form: $t \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n$.
+The proof proceeds by case analysis on the predicate $t$.
+The proof is long, but mainly involves repeatedly applying the definition of concretization and compilation until all abstract sets of locations are written in terms of concrete sets of locations.
+The proofs from step 1 are then used to show that these sets are equivalent.
+
+\para{Substitution of Policies (Step 3)} Finally, this theorem is lifted to \sysname policies $pol = p_1, \ldots, p_n$ using the proof from part 2 for individual constraints to obtain the final theorem:
 %
 $$\Con(\Compile(pol,G^A),\Gamma,f,G) = \Compile(\Con(pol,\Gamma,f), G)$$ 
+%
+The proof is obtained from a simple unfolding of the definition of compilation and concretization.
 
@@
 In this section, we will establish several relationships between the product graph and preference functions for abstract and concretized \sysname policies.
-First we relate the languages denoted by regular expressions under concretization.
+To do so, we first relate the languages denoted by regular expressions under concretization.
 Then we lift this observation to automata, and finally to product graphs.
-We use these connections to left the notion of homomorphism to the product graphs and to relate the inferred BGP local preferences for abstract and concrete devices.
+We use these connections to construct a homomorphism for the product graphs and to relate the inferred BGP local preferences for abstract and concrete devices.
 
@@
 
-\vspace{2em}
-For the proof, we assume an invariant that when regular expressions are translated to finite automata, there is no transition back to the initial state $q_0$.
-This is easily done by introducing a separate copy of $q_0$ that allows transitions.
-The reason is to distinguish if a state corresponds to a router originating a route.
+\vspace{1em}
+For the proof, we need to make sure that automata are constructed in a particular way to ensure a product graph homomorphism will exist.
+We assume an invariant that when regular expressions are translated to finite automata, there is no transition back to the initial state $q_0$.
+This can be done easily by introducing a second copy of $q_0$ that allows transitions.
+The reason is to distinguish if a state corresponds to a router ``owning" a prefix.
 We also compile automata in a particular way as defined below
@@
 \begin{defn}
-Given a regular expression $r$ over abstract locations, homomorphism $f$, a nonempty set of locations $L$, and a finite state machine $M^A = (\Sigma,Q^A,q_0,\sigma^A,F^A)$, we create a concrete state machine $M = (\Sigma, Q, q_0, \sigma, F)$ for the concretized policy $con(r,\Gamma, f) \cap \EndR(L)$ in the following way:
+Given a regular expression $r$ over abstract locations, homomorphism $f$, a nonempty set of locations $L$, and a finite state machine $M^A = (\Sigma,Q^A,q_0,\sigma^A,F^A)$, we construct a concrete state machine $M = (\Sigma, Q, q_0, \sigma, F)$ for the concretized policy $con(r,\Gamma, f) \cap \EndR(L)$ in the following way:
 
@@
       1. & \sigma(q_0,l) = q' \iff \sigma^A(q,f(l)) = q' & \textbf{for each}~~ l \in L \\
-      2. & \sigma(q,l) = q' \iff \sigma^A(q,f(l)) = q' & \textbf{for each}~~ l \in \Sigma \\
+      2. & \sigma(q,l) = q' \iff \sigma^A(q,f(l)) = q' & \textbf{for each}~~ l \in \Sigma - L \\
       3. & q \in F \iff q \in F^A & \\
@@
 
-    \textbf{Case} ($\Rightarrow$)
+    \emph{Case} ($\Rightarrow$)
 
@@
     \vspace{1em}
-    \textbf{Case} ($\Leftarrow$)
+    \emph{Case} ($\Leftarrow$)
 
@@
     \begin{proof}
-      This follows trivially from the construction of $M$. States in $M$ are copied over from states in $M^A$.
+      This follows from the construction of $M$. States in $M$ are copied over from states in $M^A$.
     \end{proof}
@@
 
-\vspace{3em}
+\vspace{1em}
+\para{Note:}
 For the remainder of this section, we will prove a collection of lemmas assuming the following: 
@@
 We will also assume that $PG = (G',start,rank)$ and $PG^A = (G'^A,start^A,rank^A)$ and that either $L = \Sigma$, or $L = \{ l \}$.
-
-\vspace{3em}
+\vspace{2em}
 
 \begin{lem}
-  We can lift the homomorphism $f$ to a new homomorphism $f_{pg}$ over the product graphs in the following way:
+  The homomorphism $f$ is lifted to a new homomorphism $f_{pg}$ over the product graphs in the following way:
   \[ \begin{array}{rcl}
@@
   \begin{proof}
-    From Lemma 4, we know that $(f(l),q_1,\ldots,q_n)$ is a valid node in $PG^A$ since each automata
-    shares the same states. Assume there is an edge in $PG$ from $x=(l,q_1,\ldots,q_n)$
+    From Lemma 4, $(f(l),q_1,\ldots,q_n)$ is a valid node in $PG^A$ since both automata share the same states. 
+    %
+    Assume there is an edge in $PG$ from $x=(l,q_1,\ldots,q_n)$
     to $y=(l',q_1',\ldots,q_n')$. We know that $f(x) = (f(l),q_1,\ldots,q_n)$ and $f(y) = (f(l'),q_1',\ldots,q_n')$.
+    %
     From the construction of PG, we know that $\sigma_i(q_k, l) = q_k'$. 
-However, from the construction of the abstract automata, we also know that $\sigma_i(q_k, l) = q_k' \iff \sigma^A_i(q_k, f(l)) = q_k'$.
+    Also from the construction of the abstract automata, we also know that $\sigma_i(q_k, l) = q_k' \iff \sigma^A_i(q_k, f(l)) = q_k'$.
 Therefore, we can conclude that $\sigma^A_i(q_k, f(l)) = q_k'$.
@@
   \[ \begin{array}{ll}
-    1. & (a,b) ~\text{is an edge in the concrete topology} \\
+    1. & (a,b) ~\text{is an edge in the concrete topology G} \\
     2. & \Topo(m) = a \\
     3. & f_{pg}(m) = M \\
-    4. & (M,N) ~ \text{is an edge in the product graph}~ PG^A \\
+    4. & (M,N) ~ \text{is an edge in}~ PG^A \\
     5. & \Topo(N) = f(b) \\
@@
 \begin{lem}
-  For any transition $\trans{m}{m'}{l}$ in $PG$, there is a corresponding transition $\trans{f(m)}{f(m')}{f(l)}$ in $PG^A$.
+  For any labelled transition $\trans{m}{m'}{l}$ in $PG$, there is a corresponding transition $\trans{f(m)}{f(m')}{f(l)}$ in $PG^A$.
   \begin{proof}
     if $m' = (l, q_1, \ldots, q_n)$, then $f(m') = (f(l), q_1, \ldots, q_n)$.
-Since there is the edge $(m,m')$ in $PG$, then there is the edge $(f(m),f(m'))$ in $PG^A$.
-Finally, because $\Topo(f(m')) = f(l)$, there must be a transition $\trans{f(m)}{f(m')}{f(l)}$.
+Since there is the edge $(m,m')$ in $PG$, then there is the edge $(f(m),f(m'))$ in $PG^A$ by the homomorphism.
+Because $\Topo(f(m')) = f(l)$, there must be a transition $\trans{f(m)}{f(m')}{f(l)}$.
   \end{proof}
@@
 \begin{lem}
-  In the concrete product graph, $m \leq m' \iff f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph.
+  In the concrete product graph $PG$, $m \leq m' \iff f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph $PG^A$.
   \begin{proof}

### 2017-03-15 paper/abstraction/appendix.tex
more clarifying edits

@@
 
-% n --> m'
-% m' --> n
-
 \vspace{.4em}
@@
     \vspace{1em}
+    \noindent
     We show that $\leq$ forms a simulation relation for the subgraph reachable from $m$ and $m'$ in $PG$ iff $\leq$ forms a simulation relation for the subgraph reachable from $f(m)$ and $f(m')$ for $PG^A$.
@@
     \vspace{1em}
-    \textbf{Case} $(\Rightarrow)$
-
+    \noindent
+    \emph{Case} $(\Rightarrow)$
+
+    \vspace{.4em}
     Consider the subgraph of $PG$ reachable from $m$ and $m'$. From $m \leq m'$ and the definition of ($\leq$), we know that $m' \geq_{rank} m$.
 
-    %
+    \noindent
     From Lemma 6, and $m' \geq_{rank} m$ we know that $f_{pg}(m') \geq_{rank} f_{pg}(m)$. 
@@
     \vspace{1.2em}
-    \textbf{Case} $(\Leftarrow)$
-
+    \noindent
+    \emph{Case} $(\Leftarrow)$
+
+    \vspace{.4em}
     Let $M = f(m)$ and let $M' = f(m')$.
@@
 We must show that the same relation holds for $m$ and $m'$.
-
-    \vspace{1em}
+    %
     Assume that $\Topo(M) = f(a)$ and $\Topo(N) = f(b)$.
@@
 
-    Lemma 7 lets us conclude that there exists a node $n'$ such that:
+    \noindent
+    Lemma 7 lets us conclude that there exists a node $n$ such that:
 
@@
       2. & f_{pg}(n) = N \\
-      3. & (m,n) ~\text{is an edge in}~ PG \\
+      3. & (m,n) ~\text{is a concrete edge in}~ PG \\
       4. & \Rank(n) = \Rank(N) \\
@@
 
-    Thus if there is transition $\trans{m'}{n'}{b}$, then there is also a transition $\trans{m}{n}{b}$. Lemma 6 together with the assumption $N' \geq N$ shows that $n' \geq{rank} n$.
+    \noindent
+    Thus if there is transition $\trans{m'}{n'}{b}$, then there is also a transition $\trans{m}{n}{b}$. 
+    Lemma 6 together with the assumption $N' \geq_{rank} N$ and the fact that $\Rank(n) = \Rank(N)$ lets us conclude that $n' \geq_{rank} n$.
 
@@
 
-\vspace{3em}
-
-The previous lemma tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
-We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.
-
+\vspace{1em}
+Lemma 9 tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
+We use this fact to define the local preference function ($\Pref : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $\Pref(m) = \Pref(f(m))$ for all product graph nodes $m$.
+
+\vspace{1em}
 \begin{defn}
-  Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
-  Clearly from Lemma 9, $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
+  Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers starting from 0 according to the total ordering for $\leq$.
+  From Lemma 9, we know that $\Pref$ and $\Pref^A$ preserve the total ordering since: $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$.
 \end{defn}
@@
 
-  For concrete ($PG$) and abstract ($PG^A$) product graphs related by $f_{pg}$
+  For concrete ($PG$) and abstract ($PG^A$) product graphs related by $f_{pg}$, if $f(\ell) = \Topo(M)$, then
 
@@
      ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
-     ~~~~~~~~~~~~~~~~~~ pin = \mathit{adjIn}(PG^A,M), \\
+     ~~~~~~~~~~~~~~~~~~ pin = \mathrm{adjIn}(PG^A,M), \\
      ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(BS,q_N) ~\vert~ BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \}, BS \neq \emptyset  \}, \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \mathit{adjOut}(PG^A,M) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \mathrm{adjOut}(PG^A,M) \}, \\
      ~~~~~~~~~~~~~~~~~~ ma = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
@@
      ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG, \\
-     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
+     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \mathrm{adjIn}(PG,m), \\
      ~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{ b ~\vert~ (b,q_n) \in pin\}, bs \neq \emptyset \}), \\
-     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathit{adjOut}(PG,m) \}, \\
+     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathrm{adjOut}(PG,m) \}, \\
      ~~~~~~~~~~~~~~~~~~ ma = ord^A(f_{pg}(m)) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
@@
     Suppose for node $M$, there exists a node $m=(l,q_m)$ such that $f_{pg}(m) = M$. 
-    We observe the following superset relation:
-    %
-    $$\{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG,m)\} \subseteq \{ b ~\vert~ (b,l) \in G.E \}$$
-    %
-    This is trivially true from the definition of the product graph. Any product graph edge will correspond to a topology edge. The following inequality will also hold:
-    %
-    $$\{b ~\vert~ b \in f^{-1}(B),~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \} \supseteq \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\}$$
-    %
-    Since whenever $(b,q_N) \in adjIn(PG,m)$ it must be the case that $(B,q_N) \in adjIn(PG^A, f_{pg}(m))$ by the homomorphism, and because $f^{-1}(B) \supseteq \{ b \}$.
+    We want to show the following:
+    %
+    %$$\{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG,m)\} \subseteq \{ b ~\vert~ (b,l) \in G.E \}$$
+    %
+    %This is trivially true from the definition of the product graph. Any product graph edge will correspond to a topology edge. The following inequality will also hold:
+    %
+    %$$ \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\} \subseteq \{b ~\vert~ b \in f^{-1}(B),~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \}$$
+    %
+    %Since whenever $(b,q_N) \in adjIn(PG,m)$ it must be the case that $(B,q_N) \in adjIn(PG^A, f_{pg}(m))$ by the homomorphism, and because $f^{-1}(B) \supseteq \{ b \}$.
 By combining these observations, we can conclude the following:
     %
-    $$\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \}$$
+    $$\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \mathrm{adjIn}(PG^A,f_{pg}(m)) \}$$
     is equivalent to
-    $$\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\}$$
-    %
+    $$\{ b ~\vert~ (b,q_N) \in \mathrm{adjIn}(PG,m)\}$$
+    %
+    Suppose that an element $x \in \{ b ~\vert~ (b,q_N) \in \mathrm{adjIn}(PG,m)\}$.
+Then $(b,q_N) \in \mathrm{adjIn}(PG,m)$ and there is an edge $(b,\ell)$ in the topology between $b$ and $\Topo(m)$.
+From the homomorphism, this means $(f(b),q_N) \in \mathrm{adjIn}(PG^A,f(m))$.
+It follows that $x \in \{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \mathrm{adjIn}(PG^A,f_{pg}(m)) \}$.
+
+    \vspace{1em}
+    \noindent
+    Now suppose the other direction.
+There is an element $x \in \{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \mathrm{adjIn}(PG^A,f_{pg}(m)) \}$.
+We know that $f(x) = B$, and that there is a topology edge between $b$ and $\ell$.
+Lemma 7 together with the fact that $f(\ell) = \Topo(m)$ lets us conclude that there is an edge in the concrete $PG$ between $(b,q_N)$ and $m$.
+It follows then that $x \in \{ b ~\vert~ (b,q_N) \in \mathrm{adjIn}(PG,m)\}$.
+
+    \vspace{1em}
+    \noindent
     The same reasoning can be applied to adjOut as well.
@@
   \vspace{.4em}
+  \noindent
   \textbf{Case} ($t = pfx$)
@@
 
+    \vspace{1em}
+    \noindent
+    \textbf{(Right-hand side)}
+
   \[ \begin{array}{l}
@@
   Next we further expand on the left side for the abstract topology to show it is equivalent:
+
+    \vspace{1em}
+    \noindent
+    \textbf{(Left-hand side)}
 
@@
      ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \Con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \ell,\Gamma,f,G), \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma = \Con(\Pref^A(M) : (in,q_N) \rightarrow (out,q_M), true, \ell, \Gamma, f, G) ~] ~] ~] \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \Pref^A(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] ~] \\
   \end{array} \]%
@@
 
-  From Lemma 10, this is equivalent to the following:
+  Applying Lemma 10 with the fact that $f(\ell) = l = \Topo(M)$ this is equivalent to the following:
 
@@
 
+    \vspace{1em}
+    \noindent
+    \textbf{(Right-hand side)}
+    %
     \[
@@
     \noindent
-    As before, we now show that the right hand side is equivalent by applying the definitions of $\Con$ and $\Compile$:
-
+    As before, we now show that the left hand side is equivalent by applying the definitions of $\Con$ and $\Compile$:
+
+    \vspace{1em}
+    \noindent
+    \textbf{(Left-hand side)}
+    %
     \[
@@
      ~~~~~~~~~~~~~~~ [~ pfx_i \rightarrow [~ ma ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x),
+     ~~~~~~~~~~~~~~~~~~~~~ (pfx_i, l') \in \Gamma(x), \\
      ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
@@
 
-  After filtering the cases where $in = \{ start \}$ and $l' \neq \ell$, we have the same situation as the previous case. 
-  This works because each $PG_{i}$ was constructed from $con(r_{i}, \ell, \Gamma, f, G) \cap end(l_{i})$.
+  After filtering the cases where $in = \{ G.start \}$ and $l' \neq \ell$, we have the same situation as the previous case. 
+  However, we know that each $PG_{i}$ was constructed from $con(r_{i}, \ell, \Gamma, f, G) \cap end(l_{i})$.
 This means that the only state in $PG_{i}$ connected to the start node ($\mathit{start}$) is a node for $l_{i}$.
 This was ensured by the fact that the transition function for each regular expression $\sigma_{i}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{i} \}$ from the construction of the automata.
+We apply Lemma 10 with the fact that $f(\ell) = \Topo(M)$:
 
@@
     \noindent
+    The proof simply uses Theorem 11 after rewriting the policy according to $\Con$ and $\Compile$.
     Given a policy $pol = p_1, \ldots, p_n$ we apply Theorem 11 after rewriting the policy. For the left side:
@@
       &=& \Con(\Compile(p_1, \ldots, p_n, G^A),\Gamma,f,G) & \text{Substitution} \\
-      &=& \Con(\CompileMbgp([\CompilePg(p_1), \ldots, \CompilePg(p_n)]),\Gamma,f,G)
+      &=& \Con(\CompileMbgp([\CompilePg(p_1, G^A), \ldots, \CompilePg(p_n, G^A)]),\Gamma,f,G)
             & \text{Definition of Compile} \\
@@
 
+    \vspace{1em}
+    \noindent
+    \textbf{(Given)}
+
     \noindent
     First, we observe that, for each $p_i$, Theorem 11 and $\CompilePg$ give us that, for each $i$:
-    \[ \begin{array}{l}
-     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~~~~ l \in internal(G^A.V), \\ 
-     ~~~~~~~~~~~~ rc = [\CompilePred((t_i, PG^A_i, \Pref^A_i))] ~~] \\
-    \end{array} \]%
-
-    \noindent
-    Is equivalent to:
-
-    \[ \begin{array}{l}
-     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+
+    \[
+    \begin{array}{lll}
+    &   \Con([~ l \rightarrow rc ~\vert~ l \in internal(G^A.V), rc = 
+        [\CompilePred((t_i, PG^A_i, \Pref^A_i))] ~~], \Gamma,f,G)     & \text{Left side} \\
+    = & [~ l \rightarrow rc ~\vert~ l \in internal(G.V), rc = 
+        [\Con(\CompilePred((t_i, PG^A_i, \Pref^A_i)), \Gamma,f,G)] ~~] & \text{Definition of con} \\
+    = & [~ l \rightarrow rc ~\vert~ l \in internal(G.V), rc = [\CompilePred((t'_i, PG_i, \Pref_i))] ~~]
+        & \text{Right side} \\
+    \end{array}
+    \]
+
+    \vspace{1em}
+    \noindent
+    \textbf{(To Show)}
+
+    \vspace{.4em}
+    \noindent
+    By applying the definition of $\CompileMbgp$, we start with the left hand side:
+
+    \[ \begin{array}{l}
+     ~~~~~ \Con([~ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~~~~~ l \in internal(G^A.V), \\ 
+     ~~~~~~~~~~~~~~~~ rc = append_{i \in \{1..n\}}(\CompilePred((t_i, PG^A_i, \Pref^A_i))) ~], \Gamma,f,G) \\
+    \end{array} \]%
+
+    \noindent
+    By applying the definition of $\Con$ to the left-hand side, we get:
+
+    \[ \begin{array}{l}
+     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
      ~~~~~~~~~~~~ l \in internal(G.V), \\ 
-     ~~~~~~~~~~~~ rc = [\CompilePred((t'_i, PG_i, \Pref_i))] ~~] \\
-    \end{array} \]%
-
-    \noindent
-    By applying the definition of $\CompileMbgp$, we need to show:
-
-    \[ \begin{array}{l}
-     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
-     ~~~~~~~~~~~~ l \in internal(G^A.V), \\ 
-     ~~~~~~~~~~~~ rc = append_{i \in \{1..n\}}(\CompilePred((t_i, PG^A_i, \Pref^A_i))) ~] \\
-    \end{array} \]%
-
-    \[ \begin{array}{l}
-     ~~~~~ [~ \ell \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ rc = \Con(append_{i \in \{1..n\}}(\CompilePred((t_i, PG^A_i, \Pref^A_i))), \Gamma,f,G)  ~]\\
+    \end{array} \]%
+
+    \noindent
+    Applying the definition of $\Con$ one more time:
+
+    \[ \begin{array}{l}
+     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
+     ~~~~~~~~~~~~ l \in internal(G.V), \\ 
+     ~~~~~~~~~~~~ rc = append_{i \in \{1..n\}}\Con((\CompilePred((t_i, PG^A_i, \Pref^A_i)), \Gamma,f,G) ) ~]\\
+    \end{array} \]%
+
+    \[ \begin{array}{l}
+     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
      ~~~~~~~~~~~~ l \in internal(G.V), \\ 
@@
     \noindent
-    Clearly this follows by the definition of list $\mathrm{append}$
+    Clearly this follows by the definition of list $\mathrm{append}$ and the given equality from Theorem 11.
 

### 2017-03-15 paper/abstraction/paper.tex
more typo fixes and edits to paper

@@
 
-At a higher level, what is happening is that each inference rule is attempting to learn the maximum possible fault tolerance information possible as a function of the symbolic inputs, and $\nu$Z~\cite{z3opt} will minimize this maximum by accounting for all possible topologies that meet the abstraction.
+At a higher level, what is happening is that each inference rule is attempting to learn the maximum fault tolerance information possible as a function of the symbolic inputs, and $\nu$Z~\cite{z3opt} will minimize this maximum by accounting for all possible topologies that meet the abstraction.
 Facts learned with $j=0$ or $k=0$ are discarded.
@@
 If S1 uses a path advertised from neighbor N2, then it will add the tag $(0,1)$ instead.
-Similarly, router A1 appears in two separate PG nodes.
-It will allow advertisements from S1 if they either have the $(1,0)$ tag or the $(0,1)$ tag attached.
+Similarly, router A1 appears in two PG nodes.
+It will allow advertisements from that have the $(1,0)$ or $(0,1)$ tag attached.
 In either case, it will not modify the tag before exporting the route to its neighbors.
@@
      ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
-     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
+     pc   &::=& ma_1, \dots, ma_k & \textit{predicate config} \\
      rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
@@
 
-The idea then is to search for such a device-local preference function for each router that totally orders advertisements from different neighbors (possibly with different tags).
+The idea is to search for such a device-local preference function for each router that totally orders advertisements from different neighbors (possibly with different tags).
 For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, S1 should prefer a message it hears from N1 over N2.
@@
 We write $m \leq n$ if the subgraph reachable from $m$ and $n$ respectively form a simulation relation with respect to $\geq_{rank}$.
+More specifically, we say that $m \leq n$ if $n \geq_{rank} m$ and for every transition $n\overset{l}{\rightarrow}n'$ from PG node $n$ there exists a transition $m\overset{l}{\rightarrow}m'$ from $m$ and $m' \leq n'$.
 \end{defn}
 
-More specifically, we say that $m \leq n$ if $m \geq_{rank} n$ and for every transition $n\overset{l}{\rightarrow}n'$ from PG node $n$ there exists a transition $m\overset{l}{\rightarrow}m'$ from $m$ and $m' \leq n'$.
-%
 If $m \leq n$, then advertisements received for node $m$ can safely be preferred over those received for node $n$ after accounting for the network-wide impact of the choice.
-For example in Figure~\ref{fig:example-compilation}, S1 can receive advertisements in two different contexts ($(S1,1,0)$ and $(S1,0,1)$) and must choose between messages received in these different contexts.
-Advertisements are preferred in state $(S1,1,0)$ because it results in a better path for S1 ($(S1,0,1) \geq_{rank} (S1,1,0)$) and downstream routers such as A1 will also obtain paths no worse than if S1 had choosen $(S1,1,0)$ instead.
+For example in Figure~\ref{fig:example-compilation}, S1 can receive advertisements in two different contexts $(S1,1,0)$ and $(S1,0,1)$ and must choose between messages received in these different contexts.
+Advertisements are preferred in state $(S1,1,0)$ because they result in a better path for S1 ($(S1,0,1) \geq_{rank} (S1,1,0)$) and downstream routers such as A1 will also obtain paths no worse than if S1 had choosen $(S1,1,0)$.
 The policy is guaranteed to be safe from failures because if a link fails in the topology, then $m \leq n$ will still hold since any transition that becomes unusable for $m$ also becomes unusable for $n$.
@@
 For each router, its corresponding PG nodes are then sorted according the the $\leq$ operator.
-If the operator defines a total order on PG nodes, then the compiler can simply prefer advertisements from peers of node $m$ over those of $n$ whenever $n \leq m$.
+If the operator defines a total order on PG nodes, then the compiler can simply prefer advertisements from peers of node $m$ over those of $n$ whenever $m \leq n$.
 However, if $\leq$ does not form a total order, then the policy is rejected as being potentially unsafe under some failure conditions.
@@
 It allows imports from these neighbors before exporting to the outbound neighbors of $m$.
-The local preference for these imports is given by $\mathrm{pref}_i(m)$.
-We build configs using list-comprehension notation.
+The local preference for these imports is given by $\mathrm{pref}_i(m)$, which represents an integer based on the total ordering of $(\leq)$.
+We build configurations using list-comprehension notation.
 For instance, $[~ l \rightarrow rc ~\vert~ l \in V, p(l,rc) ~]$ denotes the \mbgp policy $l_1 \rightarrow rc_{1},...,l_k \rightarrow rc_{k}$ where each $rc_{i}$ satisfies $p(l_i,rc_{i})$.
-We also use $\mathit{append}$ to denote sequence concatenation.%
+We use $\mathrm{append}$ to denote sequence concatenation.%
 
@@
 The similar structure between the spine template and concrete configurations is not a coincidence.
-We formalize this observation by defining a two concretization function ($con$), one for \sysname policies and another for \mbgp policies.
+We formalize this observation by defining two concretization functions ($con$), one for \sysname policies and another for \mbgp policies.
 %
 Concretization takes a context $\Gamma : \mathit{Var} \rightarrow 2^{\mathit{Prefix} \times V}$ that maps each template variable to a set of pairs of a concrete prefix and topology location where the prefix is owned.
-
-Both concretization functions traverse the policy and substitute each instance of a topology loction $l$ in the template policy with the set of all concrete locations that map to $l$, given by the inverse homomorphism $f^{-1}(l) = \{l' ~\vert~ f(l') = l \}$.
-Additionally, whenver a pair $(pfx,l) \in \Gamma(x)$, then a new entry is added to the concretized policy where $pfx$ replaces $\$\mathrm{x}$ and adds the constraint that traffic ends at $l$ ($\CD{\End(l)}$).
-%
-For example, the spine template in Figure~\ref{fig:bgp-configs}, is obtained by substituting $\{ A1,A2 \}$ for $AG$ and $\{ A3,A4 \}$ for $AL$ and by also replacing the entry for {\small \$GP} with entries for {\small GP1} and {\small GP2} given by the context (\EG, a database).
+%
+Both concretization functions traverse the policy and substitute instances of a topology location $l$ in the template policy with the set of all concrete locations that map to $l$, given by the inverse homomorphism $f^{-1}(l) = \{l' ~\vert~ f(l') = l \}$.
+Additionally, whenever a pair $(pfx,l) \in \Gamma(x)$, then a new entry is added to the concretized policy where $pfx$ replaces $\$\mathrm{x}$ and adds the constraint that traffic ends at $l$ ($\CD{\End(l)}$).
+%
+For example, the spine template in Figure~\ref{fig:bgp-configs}, is obtained by substituting $\{ A1,A2 \}$ for $AG$ and $\{ A3,A4 \}$ for $AL$ and by also replacing the entry for {\small \$GP} with entries for {\small GP1} and {\small GP2} given by the context.
 

### 2017-03-15 paper/abstraction/appendix.tex
more edits
edits

@@
 %
-For each regular expression $r$, the abstract location is replaced with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$.
+For each regular expression $r$, the abstract location is replaced with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}(l) = \{ l' ~\vert~ f(l') = l \}$.
 For each template variable, we replace it with a new entry for each of its corresponding concrete prefixes under the supplied mapping $\Gamma$.
@@
 The goal of the proof is to show that the concretization and compilation functions commute.
-One can concretize an abstract policy and then compile the concrete result, or compile an abstract policy and the concretize the abstract result and know that the results are the same.
-In particular, we are interested in establishing the following theorem:
+One can concretize an abstract policy and then compile the concrete result, or compile an abstract policy and the concretize the abstract result and know that the configurations will be the same.
+More specifically, we are interested in establishing the following theorem:
 
@@
 %
-$L$ can be thought of as a set of locations that ``own" the prefix.
-Using these assumptions, we show that several relationships hold between $PG$ and $PG^A$ as well as between $\Pref$ and $\Pref^A$.
-In particular, we show that there is a homomorphism $f_{pg}$ from $PG$ to $PG^A$, and then using this fact, we demonstrate that the inferred local preference functions $\Pref$ and $\Pref^A$ have the property that for all nodes $m$,  $\Pref(m) = \Pref^A(f_{pg}(m))$.
+where $L$ can be thought of as a set of destination locations (possibly $\Sigma$) for the prefix.
+Using these assumptions, we show that several relationships hold between $PG$ and $PG^A$ as well as between the inferred preference functions $\Pref$ and $\Pref^A$.
+In particular, we show that there is a homomorphism $f_{pg}$ from $PG$ to $PG^A$, and then using this fact, we demonstrate that the inferred local preference functions $\Pref$ and $\Pref^A$ have the property that for all nodes $m$ in $PG$,  $\Pref(m) = \Pref^A(f_{pg}(m))$.
 
@@
 %
-The proof is obtained from a simple unfolding of the definition of compilation and concretization.
+The proof is obtained by unfolding of the definition of compilation and concretization and applying the previous theorem.
 
@@
     p \in f^{-1}(l) &\iff& f(p) = l \\
-    \text{by homomorphism} & & \\
+    \text{by the homomorphism} & & \\
   \end{array} \]
@@
        f(p) \in \Lang(r_1) \vee f(p) \in \Lang(r_2) \\
-    \text{by cases + IH} & & \\
+    \text{by cases and the IH} & & \\
   \end{array} \]
@@
     p \in \Sigma^* - \Lang(con(r,\Gamma,f)) &\iff& f(p) \in \Sigma^* - \Lang(r) \\
-    \text{by IH} & & \\
+    \text{by the IH} & & \\
   \end{array} \]
@@
 \begin{defn}
-Given a regular expression $r$ over abstract locations, homomorphism $f$, a nonempty set of locations $L$, and a finite state machine $M^A = (\Sigma,Q^A,q_0,\sigma^A,F^A)$, we construct a concrete state machine $M = (\Sigma, Q, q_0, \sigma, F)$ for the concretized policy $con(r,\Gamma, f) \cap \EndR(L)$ in the following way:
+Given a regular expression $r$ over abstract locations, homomorphism $f$, a nonempty set of locations $L$, and a finite state machine $M^A = (\Sigma,Q,q_0,\sigma^A,F^A)$, we construct a concrete state machine $M = (\Sigma, Q, q_0, \sigma, F)$ for the concretized policy $con(r,\Gamma, f) \cap \EndR(L)$ in the following way:
 
@@
 
+    \noindent
+    From the definition of list $\mathrm{append}$ and the given equality from Theorem 11 shown above, we obtain the right hand side.
+
     \[ \begin{array}{l}
@@
 
-    \noindent
-    Clearly this follows by the definition of list $\mathrm{append}$ and the given equality from Theorem 11.
-
   \end{proof}

### 2017-03-15 paper/abstraction/appendix.tex
more edits

@@
 \begin{defn}
-Given a regular expression $r$ over abstract locations, homomorphism $f$, a nonempty set of locations $L$, and a finite state machine $M^A = (\Sigma,Q,q_0,\sigma^A,F^A)$, we construct a concrete state machine $M = (\Sigma, Q, q_0, \sigma, F)$ for the concretized policy $con(r,\Gamma, f) \cap \EndR(L)$ in the following way:
+Given a regular expression $r$ over abstract locations, homomorphism $f$, a nonempty set of locations $L$, and a finite state machine $M^A = (\Sigma,Q^A,q_0,\sigma^A,F^A)$, we construct a concrete state machine $M = (\Sigma, Q, q_0, \sigma, F)$ for the concretized policy $con(r,\Gamma, f) \cap \EndR(L)$ in the following way:
 
@@
 \begin{lem}
-  The homomorphism $f$ is lifted to a new homomorphism $f_{pg}$ over the product graphs in the following way:
+  For any node $n = (l,q_1,\ldots,q_k)$ in $PG$ there exists a node $f(n) = (f(l),q_1,\ldots,q_k)$ in $PG^A$.
+  \begin{proof}
+    Consider a path of length k in $PG$ to node $n$.
+The proof proceeds by induction on the path length $k$, if $n$ is connected to $start$, then $q_i = q_{0_i}$.
+Since there are no transitions back to the initial state, there must be a node $f(n) = (f(l), q_{0_1}, \ldots, q_{0_1})$ or else there is a contradiction for Lemma 1.
+For the inductive case, if $n$ is the kth hop along the path, then it has an inbound edge from neighbor $k-1$.
+Call this neighbor $m$.
+Then $(m,n)$ is an edge in $PG$, there is a node $f(m)$ with the same states.
+From the graph homomorphism, we know that $(f(m),f(n))$ must be an edge in $PG^A$ and since $f(m)$ has the same states as $m$, by the construction of the automata, $f(n)$ will have the same states as $n$.
+  \end{proof}
+\end{lem}
+
+\begin{lem}
+  The homomorphism $f$ can be lifted to a new homomorphism $f_{pg}$ over the product graphs in the following way:
   \[ \begin{array}{rcl}
@@
   \begin{proof}
-    From Lemma 4, $(f(l),q_1,\ldots,q_n)$ is a valid node in $PG^A$ since both automata share the same states. 
+    From Lemma 5, $(f(l),q_1,\ldots,q_n)$ is a valid node in $PG^A$. 
     %
@@
   \begin{proof}
-    Assume $n = (l,q_1,\dots,q_k)$. We know that $f_{pg}(n) = (f(l),q_1,\dots,q_k)$. 
+    Assume $n = (l,q_1,\dots,q_k)$. From Lemma 6, we know $f_{pg}(n) = (f(l),q_1,\dots,q_k)$. 
     We also know that $q_i \in F \iff q_i \in F^A$. 
@@
     \noindent
-    From Lemma 6, and $m' \geq_{rank} m$ we know that $f_{pg}(m') \geq_{rank} f_{pg}(m)$. 
-    From Lemma 8, there is a transition $\trans{f(n)}{f(n')}{f(l)}$.
+    From Lemma 7, and $m' \geq_{rank} m$ we know that $f_{pg}(m') \geq_{rank} f_{pg}(m)$. 
+    From Lemma 9, there is a transition $\trans{f(n)}{f(n')}{f(l)}$.
 
@@
     Thus if there is transition $\trans{m'}{n'}{b}$, then there is also a transition $\trans{m}{n}{b}$. 
-    Lemma 6 together with the assumption $N' \geq_{rank} N$ and the fact that $\Rank(n) = \Rank(N)$ lets us conclude that $n' \geq_{rank} n$.
+    Lemma 7 together with the assumption $N' \geq_{rank} N$ and the fact that $\Rank(n) = \Rank(N)$ lets us conclude that $n' \geq_{rank} n$.
 
@@
 \vspace{1em}
-Lemma 9 tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
+Lemma 10 tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
 We use this fact to define the local preference function ($\Pref : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $\Pref(m) = \Pref(f(m))$ for all product graph nodes $m$.
@@
   Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers starting from 0 according to the total ordering for $\leq$.
-  From Lemma 9, we know that $\Pref$ and $\Pref^A$ preserve the total ordering since: $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$.
+  From Lemma 10, we know that $\Pref$ and $\Pref^A$ preserve the total ordering since: $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$.
 \end{defn}

### 2017-03-15 paper/abstraction/appendix.tex
more edits

@@
   \begin{proof} 
-    $ $
-
-    \vspace{1em}
-    \noindent
     We show that $\leq$ forms a simulation relation for the subgraph reachable from $m$ and $m'$ in $PG$ iff $\leq$ forms a simulation relation for the subgraph reachable from $f(m)$ and $f(m')$ for $PG^A$.
@@
 
-    \vspace{1em}
+    \vspace{1.4em}
     \noindent
@@
 Clearly $(a,b)$ is a valid concrete topology edge since it is a transition in the product graph between $m$ and $m'$.
-We now apply Lemma 7 with the following facts:
+We now apply Lemma 8 with the following facts:
 
@@
 \end{lem}
-
-\vspace{1em}
+%
+%
+\para{Note:}
 Lemma 10 tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
 We use this fact to define the local preference function ($\Pref : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $\Pref(m) = \Pref(f(m))$ for all product graph nodes $m$.
-
-\vspace{1em}
+We do this to normalize policies so they refer to the exact same BGP local preferences.
+This is useful because we are proving syntactic equivalence of commutativity rather than semantic equivalence.
+%
 \begin{defn}
@@
 Since a policy is simply an ordered sequence of constraints, it is then straightfoward to show that compilation and concretization commute for entire policies.
-In particular, we are interested in showing:
+In particular, we are interested in showing that for all constraints $p$, contexts $\Gamma$, and graph homomorphisms $f: G \rightarrow G^A$ between $G$ and $G^A$:
 %
@@
 The proof goes by case analysis on the test $t$ in the constraint $p$, and makes heavy use of the lemmas about the product graphs from the previous section.
-We use one helper lemma here that relates sets of neighbors:
+We first use one helper lemma here that relates sets of neighbors in the concrete and abstract product graphs under the inverse homomorphism $f^{-1}$:
 

### 2017-03-15 paper/abstraction/appendix.tex
more edits

@@
     \noindent
-    Lemma 7 lets us conclude that there exists a node $n$ such that:
+    Lemma 8 lets us conclude that there exists a node $n$ such that:
 
@@
 %
-\begin{defn}
-  Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers starting from 0 according to the total ordering for $\leq$.
+
+\vspace{1em}
+\begin{lem}
+  For all node $m$, $\Pref(m) = \Pref^A(f_{pg}(m))$.
+  \begin{proof}
+    $\Pref$ and $\Pref^A$ assign values to PG nodes for each topology location as increasing integers starting from 0 according to the total ordering for $\leq$.
     From Lemma 10, we know that $\Pref$ and $\Pref^A$ preserve the total ordering since: $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$.
-\end{defn}
-
-\vspace{3em}
+Also, because there can only be a single product graph node for a particular location and set of states (since automata are determinized), and from Lemma 5 we know that for each $m$ there exists a node $f(m)$ with the same states it must be the case that $\Pref(m) = \Pref^A(f_{pg}(m))$
+  \end{proof}
+\end{lem}
+
+\vspace{2em}
 \subsection{Constraint Substitution (Part 2)}
@@
 
-  Applying Lemma 10 with the fact that $f(\ell) = l = \Topo(M)$ this is equivalent to the following:
+  Applying Lemma 12 with the fact that $f(\ell) = l = \Topo(M)$ this is equivalent to the following:
 
@@
 
-  \vspace{.4em}
+  \vspace{2em}
   \noindent
@@
      ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A,M) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma = \textbf{if } in = \{ G.start \} \text{ and } l'=\ell \textbf{ then } \bullet \\
-     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
-  \end{array} \]%
-
-  After filtering the cases where $in = \{ G.start \}$ and $l' \neq \ell$, we have the same situation as the previous case. 
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \text{if } in = \{ G.start \} \text{ and } l'=\ell \text{ then } \bullet \\
+     ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \text{else } \Pref^A(M) : (\Con(in, \ell, \Gamma, f, G),q_N) \rightarrow (\Con(out, \ell, \Gamma, f, G), q_M) ~] ~] ~]\\
+  \end{array} \]%
+
+  After filtering the cases where $in = \{ G.start \}$ and $l' = \ell$, we have the same situation as the previous case. 
   However, we know that each $PG_{i}$ was constructed from $con(r_{i}, \ell, \Gamma, f, G) \cap end(l_{i})$.
@@
 This was ensured by the fact that the transition function for each regular expression $\sigma_{i}(q_0,l) = q$ is defined only for locations $l \in L$ where $L = \{ l_{i} \}$ from the construction of the automata.
-We apply Lemma 10 with the fact that $f(\ell) = \Topo(M)$:
+We apply Lemma 12 with the fact that $f(\ell) = \Topo(M)$:
 
@@
 \vspace{2em}
+\subsection{Substitution of Policies (Step 3)}
+
+The final step is now to show the commutativity property for entire \sysname policies.
+
 \begin{thm}
@@
     \noindent
-    The proof simply uses Theorem 11 after rewriting the policy according to $\Con$ and $\Compile$.
-    Given a policy $pol = p_1, \ldots, p_n$ we apply Theorem 11 after rewriting the policy. For the left side:
+    The proof simply uses Theorem 13 after rewriting the policy according to $\Con$ and $\Compile$.
+    Given a policy $pol = p_1, \ldots, p_n$, we compute the left-hand side:
     \[

### 2017-03-15 paper/abstraction/appendix.tex
minor edits

@@
     p \in \Lang(con(l,\Gamma,f)) &\iff& f(p) \in \Lang(l) \\
-    p \in \Lang(\Sigma_i ~ f_i^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
-    p \in \bigcup_i f_i^{-1}(l) &\iff& f(p) \in \Lang(l) \\
+    p \in \Lang(\Sigma ~ f^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
+    p \in \bigcup f^{-1}(l) &\iff& f(p) \in \Lang(l) \\
     p \in f^{-1}(l) &\iff& f(p) \in \{ l \} \\
@@
 Therefore, we can conclude that $\sigma^A_i(q_k, f(l)) = q_k'$.
-However, from the definition of $PG^A$, this means that there must be an edge in $PG^A$ for ($f(x),f(y)$).
+From the definition of $PG^A$, this means that there must be an edge in $PG^A$ for ($f(x),f(y)$).
   \end{proof}
@@
 \begin{lem}
-  For all node $m$, $\Pref(m) = \Pref^A(f_{pg}(m))$.
+  For all nodes $m$, $\Pref(m) = \Pref^A(f_{pg}(m))$.
   \begin{proof}
@@
 We know that $f(x) = B$, and that there is a topology edge between $b$ and $\ell$.
-Lemma 7 together with the fact that $f(\ell) = \Topo(m)$ lets us conclude that there is an edge in the concrete $PG$ between $(b,q_N)$ and $m$.
+Lemma 8 together with the fact that $f(\ell) = \Topo(m)$ lets us conclude that there is an edge in $PG$ between $(b,q_N)$ and $m$.
 It follows then that $x \in \{ b ~\vert~ (b,q_N) \in \mathrm{adjIn}(PG,m)\}$.

### 2017-03-15 paper/abstraction/paper.tex
more edits
edits

@@
 \newtheorem{lem}[thm]{Lemma}
+
+\newcommand{\Appendix}{technical appendix\xspace}
 
@@
 \item Implementation and evaluation of a \sysname compiler that generates
-provably-correct BGP templates and is much faster
+BGP templates and is much faster
 than compilers based on concrete topologies.
@@
 We introduce a simple, vendor-independent BGP configuration language called \mbgp and describe a compilation function that uses the inferred preference ordering to generate concrete configurations from a concrete topology, or templates from an abstract topology.
-Templates can then be soundly instantiated for a concrete network by replacing instances of abstract neighbors with the union of all concrete neighbors under the inverse homomorphism, and by replacing prefix template variables with separate entries for each concrete prefix provided by a context.
+Given a concrete network, templates can be instantiated by replacing instances of abstract neighbors with the union of all concrete neighbors under the inverse homomorphism, and by replacing prefix template variables with separate entries for each concrete prefix provided by a context.
+ We call this process of transforming templates into configurations \emph{concretization}.
 We prove that concretization and compilation commute.
-By modifying compilation slightly we can further ensure that every configuration depends only on its immediate neighbors.
+Moreover, by modifying compilation slightly we can further ensure that every configuration depends only on its immediate neighbors.
 This guarantees that any change made to the concrete topology will result in a minimal number of changes to the configurations.
-
+%
 We now look at each of these steps in turn.
@@
 
-The BGP routing protocol standard allows for the use of \emph{community tags}, 32-bit integer tags that can be arbitrarily attached to, or removed from routing advertisements. 
+The BGP routing protocol standard allows for the use of \emph{community tags}---32-bit integer tags that can be arbitrarily attached to, or removed from, routing advertisements. 
 Community tags serve as a simple form of \emph{history}, and operators routinely use such tags to implement policy.
-For example, operators might record where an advertisment enters the network using community tags and then conditionally block the export of the advertisment later to other peers to prevent becoming a transit point.
-
-The idea for template generation is to use community tags to record the state of the automata from the Product Graph in every BGP announcement and update these tags whenever messages are passed between routers.
-Such a tagging mechanism is used to ensure that BGP only considers paths that are allowed by the \sysname policy (\IE, paths in the PG).
-Routers will allow advertisments that correspond to an edge in the PG and block any advertisments that do not.
+For example, operators might tag advertisements at certain entry points and then block the export of tagged
+advertisements to prevent their network from becoming a transit point.
+
+Template generation uses community tags to record the state of the automata from the Product Graph in every BGP announcement and updates these tags whenever messages are passed between routers.
+This mechanism ensures that BGP only considers paths that are allowed by the \sysname policy (\IE, paths in the PG).
+Routers will allow advertisments that correspond to an edge in the PG and will block any advertisments that do not.
 
@@
 Similarly, router A1 appears in two PG nodes.
-It will allow advertisements from that have the $(1,0)$ or $(0,1)$ tag attached.
+It will admit advertisements that have the $(1,0)$ or $(0,1)$ tag attached (and drop all other advertisements).
 In either case, it will not modify the tag before exporting the route to its neighbors.
@@
 
-Tagging and filtering according to the PG with community values in BGP forces the protocol to only consider paths to the destination that are allowed by the policy.
+Tagging and filtering according to the PG restricts the possible paths to those that are allowed by the policy.
 However, finding \emph{some} path to the destination is not enough.
 We must ensure that each router uses its \emph{best} available path to the destination according to the policy.
-Further, this must continue to hold as additional elements of the network fail.
+Further, each router must continue to use its best available path as elements of the network fail.
 In the example from Figure~\ref{fig:example-compilation}, the policy was $\True ~\Path~ \CD{\Exit(N1\Prefer N2)}$, which indicates that paths through N1 should be used whenever possible, and paths through N2 should only be used as a backup.
-If router S1 allows advertisements from both N1 and N2 but does not prefer one advertisement over another, it might end up choosing to use a path through N2 even though a more preferred path through N1 exists and is available\footnote{ties between equally preferred paths can be broken nondeterministically}.
+If router S1 allows advertisements from both N1 and N2, but does not prefer one advertisement over another, it might end up choosing to use a path through N2 even though a more preferred path through N1 exists and is available\footnote{Ties between equally preferred paths can be broken nondeterministically.}.
 On the other hand, if the S1-N1 link fails, then the best available path is through N2.
 
-To enforce correct network-wide preferences, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routers learned from another neighbor.
-The challenge is to find a collection of device-local preferences that correctly enforce the network-wide preferences from the policy for all failures.
+To enforce correct network-wide preferences, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routes learned from another neighbor.
+The challenge is to find a collection of device-local preferences that correctly enforce the policy's network-wide preferences in the face of any set of failures.
 
@@
 \Propane introduced a conservative search strategy for determining route preferences that works well in practice.
-To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:
+To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:\footnote{Recall that $\Pref(m)$ is a set of priorities --- the priorities of the
+automata whose final states include $m$.  
+For instance, if $\Pref(m)$ is \{1,3\} then
+automata 1 and automata 3 have $m$ as a final state.  Moreover, recall that
+the policy expressed by automata $i$ is preferred to the policy expressed
+by automata $j$ if $i < j$.}
 
@@
 Lemma~\ref{lem:preference} tells us that inferring preferences for the abstract PG before template instantiation is equivalent to inferring preferences for an already-instantiated concrete PG.
+A proof appears in the \Appendix.
 
@@
 An \mbgp policy consists of a sequence of router configurations (one for each internal topology location $l$).
-A router configuration is an ordered sequence of a predicate describing the traffic, and a predicate configuration.
+A router configuration is an ordered sequence of pairs, where is pair contains
+a predicate describing the traffic, and a predicate configuration.
 A predicate is either a template variable $\$\mathrm{x}$ or a prefix.
@@
 \vspace{-.6em}
-Full definitions of concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix.
+Full definitions of concretization as well as the proof of Theorem~\ref{thm:concretization} are included in the \Appendix.
 
@@
 However, in the spine configurations, the match on the global prefix template variable {\small \$GP} must be expanded when concretizing the template to include the new prefixes added by the ToR.
-Unfortunately, this small change to the topology results in a change to every single spine configuration.
+Hence, this small change to the topology results in a change to every single spine configuration.
 
@@
 Figure~\ref{fig:bgp-configs} (right) shows the spine and ToR templates after this transformation.
+Routers in the TG role will originate ($\{ \mathrm{start} \}$) global prefixes and tag them with a unique tag, while routers in the spine role match the tag.
 

### 2017-03-15 paper/abstraction/appendix.tex
edits

@@
     $\Pref$ and $\Pref^A$ assign values to PG nodes for each topology location as increasing integers starting from 0 according to the total ordering for $\leq$.
-    From Lemma 10, we know that $\Pref$ and $\Pref^A$ preserve the total ordering since: $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$.
+    We know that $\Pref$ and $\Pref^A$ preserve the total ordering since: by construction $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$, and from Lemma 10 we know that $m \leq m' \iff f_{pg}(m) \leq f_{pg}(m')$ .
 Also, because there can only be a single product graph node for a particular location and set of states (since automata are determinized), and from Lemma 5 we know that for each $m$ there exists a node $f(m)$ with the same states it must be the case that $\Pref(m) = \Pref^A(f_{pg}(m))$

### 2017-03-15 paper/abstraction/paper.tex
added more information in shepherd letter

@@
 
-At a higher level, what is happening is that each inference rule is attempting to learn the maximum fault tolerance information possible as a function of the symbolic inputs, and $\nu$Z~\cite{z3opt} will minimize this maximum by accounting for all possible topologies that meet the abstraction.
+At a higher level, what is happening is that each inference rule is attempting to learn the maximum fault tolerance information possible as a function of the symbolic inputs.
+The $\nu$Z~\cite{z3opt} solver will then minimize this maximum by accounting for all possible topologies that meet the abstraction.
 Facts learned with $j=0$ or $k=0$ are discarded.
@@
 
-Although the disjoint path analysis takes place over the PG, each application of the inference rules from Figure~\ref{fig:inference-rules} depends on the topology locations, but not the automata states.
+Although the disjoint path analysis takes place over the PG, each application of the inference rules from Figure~\ref{fig:inference-rules} depends on the topology locations, but not the automata states, and can be reused accross multiple PG nodes with the same topology location.
 Therefore, we lazily apply the rules and cache the satisfiability and minimization calls to $\nu$Z after their first use.
@@
 Specifically, it underestimates ToR-to-spine paths; it fails to account for some circuitous paths that traverse another spine because it could not disambiguate two concrete spines that map to the same abstract role.
+%
+For instance, for the fat tree topology~\cite{fattree}, it only finds 1 path between any ToR and any Spine when there should always be at least two.
+However, in this case the analysis computes the correct worst case connectivity between any source ToR and any other destination aggregation or ToR router.
+A similar pattern occurs with other tree-based topologies.
+%
 %For all fat tree variants, the analysis correctly computes the number of ToR to ToR disjoint paths, but can lose precision between ToR to spine routers due to valley paths.
 For a valley-free routing policy, the analysis is precise for ToR to spine connectivity.
-For both recursive topologies, the analysis can accurately determine reachability but is conservative in determining disjoint paths.
+For both recursive topologies, the analysis can only accurately determine reachability.
 %For the BCube topology, it is able to to determine the correct number of disjoint paths between some pairs of nodes, but not all.

### 2017-03-18 paper/abstraction/paper.tex
edits to abstract, intro, acks, header

@@
 
-\authorinfo{Ryan Beckett$^*$\and Ratul Mahajan$^\dagger$\and Todd Millstein$^\S$\and Jitendra Padhye$^\dagger$\and David Walker$^*$}
-{Princeton University$^*$, Microsoft Research$^\dagger$, University of California Los Angeles$^\S$}
-{\{rbeckett,dpw\}@cs.princeton.edu, \{ratul,padhye\}@microsoft.com, todd@cs.ucla.edu}
+\authorinfo{Ryan Beckett$^*$\and Ratul Mahajan$^{\dagger\ddagger}$\and Todd Millstein$^{\dagger\S}$\and Jitendra Padhye$^\ddagger$\and David Walker$^*$}
+{Princeton University$^*$ \hspace{0.2in} Intentionet$^\dagger$ \hspace{0.2in}  Microsoft$^\ddagger$ \hspace{0.2in}  University of California Los Angeles$^\S$}
+%{\{rbeckett,dpw\}@cs.princeton.edu, \{ratul,padhye\}@microsoft.com, todd@cs.ucla.edu}
 
@@
 We develop \sysname, a system to synthesize provably-correct
-BGP configurations for large, evolving networks from high-level
-specifications of topology, routing policy, and fault-tolerance
+BGP (border gateway protocol) configurations for large, evolving networks from high-level
+specifications of topology, routing policy, and fault-tolerance.
 requirements. \sysname is based on new abstractions for capturing
@@
 Unfortunately, templates use the same low-level constructs as ordinary router configurations (\EG,
-add a tag to this particular announcement; remove a tag from that announcement).  In both templatized
+adding or removing tags from particular announcements).  In both templatized
 and non-templatized configurations, ensuring that a collection of low-level, local configurations
@@
 concrete parameters
-and then test it using various scenarios.  In general, like in any complex software system, such testing is 
-bound to be incomplete.
+and then test it under various scenarios.  In general, like in any complex software system, such testing is inherently incomplete.
 %Thus, operators validate templates by testing some concrete instantiations using
 %simulation or verification tools~\cite{feamster+:rcc, batfish, era, arc, bagpipe}.
-Moreover, even if network operators were to instantiate their templates using their initial network 
-configuration and to verify key properties using a tool such as Bagpipe~\cite{bagpipe}, the guarantees
-provided would not hold as large networks evolve frequently over time.  In particular,
-devices and links are sometimes taken offline for maintenance and sometimes added to expand
-capacity.  Unfortunately, templates that
+
+Moreover, even if network operators were to instantiate their templates using the initial network 
+topology and verify key properties using tools such as Bagpipe~\cite{bagpipe}, the guarantees
+would not hold as the network topology evolves. Evolution of the topology is a frequent event for large networks, as  devices and links are taken offline for maintenance and  added to expand
+capacity.  
+Templates that
 work for the current topology may or may not work for future
-topologies. Problems that occur may cause operators to make small, non-uniform changes to particular router configurations,
-which defeats the purpose of a template system.  An even worse situation occurs when
-operators feel obligated to update many devices to extend or change their network.  
-Such network-wide configuration changes entail a great deal of risk and may be highly
-disruptive in production networks with live traffic.
+topologies. Ensuing problems may cause operators to make non-uniform changes to particular routers' configurations,
+which defeats the purpose of a template system.  An even worse situation is when
+operators have to update many devices to evolve their network.  
+Such network-wide configuration changes entail a great deal of risk and can be highly
+disruptive to live traffic.
 %Ideally, network engineers would like some guarantees about the future, namely that 
@@
 reluctant to use such systems. While they think of their network abstractly, in
-terms of roles, synthesis systems operate over concrete topologies.  
+terms of roles, current synthesis systems operate over concrete topologies.  
 Even if two devices play the same role, operators cannot specify policy in terms of
-this role and even if specifications for the two devices are similar,
+this role; and even if specifications for the two devices are similar,
 there is no guarantee that the systems will generate (syntactically) similar
@@
 will have to consider hundreds of device configurations instead of just a handful of
-role configurations. Finally, current synthesis systems are brittle in the face of network
-evolution: Any change in network topology requires re-execution of the engine,
-from scratch, on the new topology.  The result may be a completely different
-set of configurations.  No administrator of a large network is
-able to shut down a production network, upgrade policy on all devices and 
+role configurations. Current synthesis systems are also brittle in the face of network
+evolution. Any change in network topology requires re-execution of the engine,
+from scratch, on the new topology, and the result may be a completely different
+set of configurations.  No operator is
+able to shut down a large, production network, upgrade policy on all devices and 
 then restart their network.
 
-To address the challenge of configuration synthesis in the presence of abstract roles, we present \sysname. 
+To address the challenge of configuration synthesis in the presence of abstract roles, we develop \sysname. 
 %BGP, unlike link state protocols
@@
 at least two aggregation routers (to tolerate the failure of a link to an
-aggregation router). Other inputs to \sysname include the routing policy of the
-network and its fault-tolerance requirements (\EG, the number of simultaneous link failures
-to tolerate). For high-level specification of routing policy, we borrow notation from the original
-\Propane system~\cite{propane}.  However, while \Propane policies refer to concrete devices,
+aggregation router). \sysname takes two additional inputs. 
+The first is a  high-level specification of routing policy, for which we borrow notation from the original
+\Propane system~\cite{propane}.  While \Propane policies refer to concrete devices,
 \sysname policies refer to abstract roles.
+The final input to \sysname is the fault-tolerance requirements of the network, such as the number of simultaneous link failures it can tolerate without loss of connectivity for any traffic flow.
 
 Based on these inputs, \sysname generates one template per role. 
-These templates specify routing policy using the Border Gateway Protocol (BGP).
-BGP is a useful target for synthesis, as it is the standard protocol
-for interdomain routing and it is also commonly used
-within data centers due to its scalability.  However, it is far from the only control
-plane protocol; synthesis of configurations for other protocols such as OSPF is beyond the 
-scope of this paper.
-
-During synthesis, our compiler performs an analysis over abstract topologies to determine
-the fault tolerance properties of the specified policy.  This analysis determines a worst-case 
-lower bound on the number of link failures require to disconnect one abstract location from another 
-given the constraints specified by the abstract topology. Any concrete instance of the abstract topology will adhere to the given fault tolerance property.
+These templates specify routing policy using BGP (border gateway protocol). 
+BGP is the standard protocol for interdomain routing and is also commonly used within data centers because of its scalability and support for rich policies.\footnote{However, BGP is not the only routing protocol used in existing networks.
+In the future, we will extend our work to  other protocols such as OSPF.}
+%
+Our templates are correct by design and evolution friendly. 
+When the network evolves from
+one concrete topology to another, both of which comply with the abstract
+topology, only the configurations of devices that acquire or lose a neighbor need to change. 
+This guarantee is the best that any system can give as neighbor relationships are explicitly 
+configured in devices.  We achieve it in part by leveraging BGP features that allow arbitrary tags on routing announcements and expressing policy using such tags (instead of router identifiers). 
+%These features makes it possible to change network topologies without reflecting those changes in the configurations of distant routers.  
+%Other control plane protocols that do not provide such tagging mechanisms or that implement link-state protocols as opposed to path-vector protocols would not be able to avail themselves of these techniques.
+%No other device in the network is impacted.
+
+During synthesis, our compiler analyzes abstract topologies to determine
+the fault tolerance properties of the specified routing policy.  This analysis yields a lower  
+bound on the number of link failures require to disconnect one abstract location from another. 
+%given the connectivity constraints of the abstract topology. 
+{\em Any} concrete instance of the abstract topology will adhere to the given fault tolerance property.
+
 %% first analysis determines whether a user policy can be implemented correctly using BGP in
@@
 
-\sysname provides two other benefits. First, its templates are evolution friendly. 
-When the network migrates from
-one concrete topology to another, both of which comply with the abstract
-topology, only the configurations of devices that acquire or lose a neighbor need to change. 
-This guarantee is the best that any system can give as neighbor relationships are explicitly 
-configured in devices.  We achieve this guarantee in part by relying on the ability of BGP
-to tag announcements with abstract values.  These abstract values make it possible to change
-the source of an announcement without the target being aware of a change happening.  Other control
-plane protocols that do not provide such tagging mechanisms or that implement link-state protocols as opposed to
-path-vector protocols would not be able to avail themselves of these techniques.
-%No other device in the network is impacted.
-
-Second, \sysname can scale substantially better than its nearest competitor, the original \Propane system, 
+%\sysname provides two other benefits. First, its templates are evolution friendly. 
+%When the network migrates from
+%one concrete topology to another, both of which comply with the abstract
+%topology, only the configurations of devices that acquire or lose a neighbor need to change. 
+%This guarantee is the best that any system can give as neighbor relationships are explicitly 
+%configured in devices.  We achieve this guarantee in part by relying on the ability of BGP
+%to tag announcements with abstract values.  These abstract values make it possible to change
+%the source of an announcement without the target being aware of a change happening.  Other control
+%plane protocols that do not provide such tagging mechanisms or that implement link-state protocols as opposed to
+%path-vector protocols would not be able to avail themselves of these techniques.
+%%No other device in the network is impacted.
+
+We use \sysname for a range of real-world topologies and routing policies.
+We find that it can effectively encode the topologies and their evolution, and the fault tolerance bounds that it computes are often precise.
+We also find that \sysname scales substantially better than its nearest competitor, the original \Propane system, 
 which operates over concrete topologies. As the number of devices in a
@@
 Consequently, \sysname can be two orders of magnitude
-faster than \Propane, taking less than 10 seconds to synthesize templates for large structured networks.
-
-\vspace{1em}
+faster than \Propane, taking less than 10 seconds to synthesize templates for large  networks.
+
+\vspace{0.5em}
 \noindent
@@
 
+We demonstrate the difficulty of configuring networks today using the data center example in Figure~\ref{fig:example}.
+The boxes denote routers.
+Using terminology for fat tree networks~\cite{fattree}, S[1--2] are spine routers, A[1--8] are aggregation routers,\footnote{This term is not related to BGP route aggregation.} and T[1--8] are top-of-rack (ToR) routers.
+The spine routers connect to the Internet through neighbors N[1--2].
+%The aggregation routers bridge the spine to the ToR routers.
+The ToR routers attach to a set of servers (``a rack'') that host services with address prefixes P[1--8].
+
+%% We assume that each router is running an instance of the \emph{Border Gateway Protocol} (BGP),
+%% as is common in large data centers. In this protocol, adjacent routers use BGP to exchange messages
+%% with one another concerning the availability of routes to destinations.  A BGP \emph{configuration}
+%% (one for each router) dictates which offered routes a router will select and how to propagate chosen routes to its
+%% neighbours.\footnote{If this submission is accepted and more space is available in the final version,
+%% we will give a detailed explanation of BGP for the PLDI audience.  Henceforth, we assume knowledge of basic BGP
+%% mechanics.}
+
+%Assume that all nodes are running the border gateway protocol (BGP), as is common in large data centers~\cite{x}. \todo{more detail on BGP?}
+
 \begin{figure}[t!]
@@
 \end{figure}
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=2.5in]{figures/example2}
-  \vspace{-.8em}
-  \caption{A modified version of the example in Figure~\ref{fig:example}.}
-  \label{fig:example2}
-  \vspace{-.8em}
-\end{figure}
-
-We demonstrate the difficulty of configuring networks today using the data center example in Figure~\ref{fig:example}.
-The boxes denote routers.
-Using terminology for fat tree networks~\cite{fattree}, S[1--2] are spine routers, A[1--8] are aggregation routers,\footnote{This term is not related to BGP route aggregation.} and T[1--8] are top-of-rack (ToR) routers.
-The spine routers connect to the Internet through neighbors N[1--2].
-%The aggregation routers bridge the spine to the ToR routers.
-The ToR routers attach to a set of servers (``a rack'') that host services with address prefixes P[1--8].
-
-%% We assume that each router is running an instance of the \emph{Border Gateway Protocol} (BGP),
-%% as is common in large data centers. In this protocol, adjacent routers use BGP to exchange messages
-%% with one another concerning the availability of routes to destinations.  A BGP \emph{configuration}
-%% (one for each router) dictates which offered routes a router will select and how to propagate chosen routes to its
-%% neighbours.\footnote{If this submission is accepted and more space is available in the final version,
-%% we will give a detailed explanation of BGP for the PLDI audience.  Henceforth, we assume knowledge of basic BGP
-%% mechanics.}
-
-%Assume that all nodes are running the border gateway protocol (BGP), as is common in large data centers~\cite{x}. \todo{more detail on BGP?}
 
@@
 %Unfotunately, currently, there is no way to predict which variations will behave correctly for a given set of templates.
+
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=2.5in]{figures/example2}
+  \vspace{-.8em}
+  \caption{A modified version of the network in Figure~\ref{fig:example}.}
+  \label{fig:example2}
+  \vspace{-.8em}
+\end{figure}
 
@@
 \para{Acknowledgments}
-We thank the PLDI reviewers for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 as well as Cisco award 677002.
+We thank the many network engineers, especially George Chen and Lihua Yuan, who helped us understand the importance of working with abstract topologies and synthesizing templates. 
+We also thank the PLDI reviewers for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 as well as Cisco award 677002.
 

### 2017-03-18 paper/abstraction/paper.tex
minor fix to intro

@@
 %
-Our templates are correct by design and evolution friendly. 
-When the network evolves from
-one concrete topology to another, both of which comply with the abstract
-topology, only the configurations of devices that acquire or lose a neighbor need to change. 
+Our templates are correct for {\em any} concrete topology that complies with the abstract topology. They are also evolution friendly. 
+When the network evolves from one compliant concrete topology to another, only the configurations of devices that acquire or lose a neighbor need to change. 
 This guarantee is the best that any system can give as neighbor relationships are explicitly 
@@
 %given the connectivity constraints of the abstract topology. 
-{\em Any} concrete instance of the abstract topology will adhere to the given fault tolerance property.
+Any concrete instance of the abstract topology will adhere to the given fault tolerance property.
 

### 2017-03-19 paper/abstraction/paper.tex
edits to 7

@@
 
-In this work, we focus on synthesizing configurations for a network that runs the Border Gateway Protocol (BGP), the standard for routing across independent organizations and inside large data centers.
+In this work, we focus on synthesizing configurations for a network that runs BGP, the standard for routing across independent organizations and inside large data centers.
 It scales effectively and allows operators to define flexible policies.
@@
 
-All route announcements carry an {\em AS path}, the sequence of BGP speakers (called Autonomous Systems) that will be traversed to reach the destination.
+All route announcements carry an {\em AS path}, the sequence of BGP networks, called autonomous systems (ASes), that will be traversed to reach the destination.
 %When BGP is used inside a data center, each router tends to be its own AS.
@@
 
-To simplify network configuration, operators are adopting a template-based approach~\cite{hatch,thwack}. Instead of authoring a configuration per router, operators author a template per role.
+To simplify them, operators are adopting a template-based approach~\cite{hatch,thwack}. Instead of authoring a configuration per router, operators author a template per role.
 %
@@
 As described earlier (\S\ref{sec:introduction}), templates are hard to author and hard to validate.
-Worse, templates that work for one topology may not work for seemingly-inconsequential variations (which may arise after the network evolves).
-Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}: it has the same five roles, connected in a similar hierarchy.
-One might think that the same templates (with different database entries) can be used for both cases.
+Worse, templates that work for one topology may not work for seemingly-inconsequential variations which may arise after the network evolves.
+Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}; it has the same five roles, connected in a similar hierarchy.
+One might think that the same templates, with different database entries, can be used for both cases.
 However, if the templates are configured to disallow ``valley" paths (per policy (5) above), they will work for Figure~\ref{fig:example} but silently violate the fault tolerance policy $(8)$ when used for Figure~\ref{fig:example2}.
 Specifically, in Figure~\ref{fig:example2}, an aggregation-based black hole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]).
-No such black hole will occur in Figure~\ref{fig:example} after a single link failure because spine routers have two links to each pod.
+Such a black hole will not occur in Figure~\ref{fig:example} because spine routers have two links to each pod.
 
@@
 
-Today, if operators discover their old templates no longer work, changing a template will
-cause a change to all devices that use it---an unacceptable disruption in many cases.
-When that happens, operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the change.
-Such patches reintroduce the complexity and errors that templates were meant to prevent.
+When operators discover that an old template no longer works, they may consider changing it, which may cause a change to all devices that use it---an unacceptable disruption in many cases.
+As a result, operators may abandon the template entirely and revert to hand-crafting configuration patches to accommodate the change.
+Such patches reintroduce the complexity and the risk of errors that templates were meant to prevent.
 
@@
 \sysname takes as input the network's abstract topology and its policy.
-The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous link failures the network can withstand without losing connectivity.
+The policy consists of the routing policy that describes how traffic should flow and the fault-tolerance policy that describes how many simultaneous link failures the network should withstand without losing connectivity.
 
@@
 
-The BGP routing protocol standard allows for the use of \emph{community tags}---32-bit integer tags that can be arbitrarily attached to, or removed from, routing advertisements. 
+The BGP routing protocol allows \emph{community tags}---32-bit integer tags that can be arbitrarily attached to, or removed from, routing advertisements. 
 Community tags serve as a simple form of \emph{history}, and operators routinely use such tags to implement policy.
@@
 
-Tagging and filtering according to the PG restricts the possible paths to those that are allowed by the policy.
+Tagging and filtering based on the PG restricts the possible paths to those that are allowed by the policy.
 However, finding \emph{some} path to the destination is not enough.
-We must ensure that each router uses its \emph{best} available path to the destination according to the policy.
+We must ensure that each router uses its \emph{best} available path according to the policy.
 Further, each router must continue to use its best available path as elements of the network fail.
@@
 
-To enforce correct network-wide preferences, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routes learned from another neighbor.
+To enforce correct path preferences, we use the BGP local-preference attribute, which allows routers to prefer certain routes (e.g., those from a particular neighbor or with a tag) over other routes.
 The challenge is to find a collection of device-local preferences that correctly enforce the policy's network-wide preferences in the face of any set of failures.
@@
 \Propane introduced a conservative search strategy for determining route preferences that works well in practice.
-To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:\footnote{Recall that $\Pref(m)$ is a set of priorities --- the priorities of the
+To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:\footnote{Recall that $\Pref(m)$ is a set of priorities---those of the
 automata whose final states include $m$.  
 For instance, if $\Pref(m)$ is \{1,3\} then
-automata 1 and automata 3 have $m$ as a final state.  Moreover, recall that
+automata 1 and 3 have $m$ as a final state.  Moreover, recall that
 the policy expressed by automata $i$ is preferred to the policy expressed
@@
 %
-For example, in the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation.
+For example, in Figure~\ref{fig:example-compilation} the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation.
 This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$.

### 2017-03-23 paper/abstraction/paper.tex
stuff

@@
 $(4)$ services in Pods[3--4] should not be externally accessible;
-$(5)$ traffic paths should be valley-free, \IE, not go down then back up.
+$(5)$ traffic paths should be valley-free (\EG, a path through S1 should
+not go down through Ai and then back up through S2, for instance, 
+creating an up-down-up path);
 $(6)$ prefer neighbor N1 over N2, \IE, when both neighbors announce a prefix, send traffic through N1;
@@
 
-For example, in Figure~\ref{fig:example3}, the first two constraints: $e1 = AG$ and $e2 = TG$ say that, within any pod P, the number of outgoing edges from a node in the $TG$ role to a node in the $AG$ role equals the number of nodes in the $AG$ role.
-Similarly, the number of outgoing edges from a node in the $AG$ role to a node in the $TG$ role equals the number of nodes in the $TG$ role.
-These constraints capture the fact that, within any pod, the global aggregators and ToRs are in a full mesh.
-Furthermore, the constraints $AG = AL$ and $AG \leq S$ ensure that, within pods P and Q, the $AG$ and $TG$ roles have the same number of routers, which is less than or equal to the number of routers in the spine role $S$.
+For example, in Figure~\ref{fig:example3}, the first constraint ($e1 = AG$) 
+%and
+states that, within any pod P, the number of outgoing edges from a node in the 
+$TG$ role (\IE, $e1$) to a node in the $AG$ role equals the number of nodes in the 
+$AG$ role. Similarly, the constraint ($e2 = TG$) states that the number of 
+outgoing edges from a node in the $AG$ role (\IE, $e2$) to a node in the $TG$ role 
+equals the number of nodes in the $TG$ role. Together these constraints capture 
+the fact that, within any pod, the global aggregators and ToRs are in 
+a full mesh. Furthermore, the constraints $AG = AL$ and $AG \leq S$ ensure 
+that, within pods P and Q, the $AG$ and $AL$ roles \dpw{This originally said $AG$ and $TG$ but I changed it.} have the same number of 
+routers, which is less than or equal to the number of routers in the spine 
+role $S$.
 %
@@
 %
-The Local policy adds the $\CD{\Always(\In)}$ constraint for each local prefix described by the template variable $\CD{\$LP}$.
+The \CD{Local} policy adds the $\CD{\Always(\In)}$ constraint for each local prefix described by the template variable $\CD{\$LP}$.
 This constraint ensures that traffic follows a path that matches an internal role (\IE, in the data center) at each hop of the path.
@@
 %
-The PG for a graph $G=(V,E)$ is a tuple ($G'$, $start$, \Pref) where $G' = (V',E')$ has
+The PG for a graph (\IE, a topology) $G=(V,E)$ is a tuple ($G'$, $start$, \Pref) where $G' = (V',E')$ has
 vertices $V' \colon V \times Q_1 \times \dots \times Q_j$,
@@
 Finally, we write $\Topo{m} = l$ to extract the topology location from a PG node, when $m = (l, q_{m_1}, \dots, q_{m_k}) \in V'$.
-For the remainder of the paper, we use the term location to refer to both a router in the case of a concrete topology/PG, or a role in the case of an abstract topology/PG.
+For the remainder of the paper, we use the term \emph{location} to refer to a router in the case of a concrete topology/PG, or a role in the case of an abstract topology/PG.
 

### 2017-04-13 paper/abstraction/paper.tex
minor edits

@@
 concrete instantiation of the given abstract topology. \sysname
-also guarantees that minimal changes to existing device configurations
+also guarantees that only incremental changes to existing device configurations
 are required when the network evolves to add or remove devices and
@@
 the fault tolerance properties of the specified routing policy.  This analysis yields a lower  
-bound on the number of link failures require to disconnect one abstract location from another. 
+bound on the number of link failures required to disconnect one abstract location from another. 
 %given the connectivity constraints of the abstract topology. 
@@
 
-For each router, its corresponding PG nodes are then sorted according the the $\leq$ operator.
+For each router, its corresponding PG nodes are then sorted according to the $\leq$ operator.
 If the operator defines a total order on PG nodes, then the compiler can simply prefer advertisements from peers of node $m$ over those of $n$ whenever $m \leq n$.

### 2017-04-14 paper/abstraction/paper.tex
add copyright space

@@
-\documentclass[numbers, 10pt, preprint]{sigplanconf}
-%\documentclass[10pt]{sigalternate052015}
-
+\documentclass[numbers, 10pt]{sigplanconf}
+
+%% packages
 \usepackage{amsmath}
@@
 \usepackage{pifont}
-\newcommand{\cmark}{\ding{51}}
-\newcommand{\xmark}{\ding{55}}
-
+
+%% todo comments
 \definecolor{princetonorange}{RGB}{255,143,0}
 \definecolor{tmlblue}{RGB}{0,58,120}  % tmlblue == Toronto Maple Leafs Blue!
-
 \newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
@@
 
+%% abbreviations
 \newcommand{\EG}{\emph{e.g.}}
@@
 
+%% formatting
 \newcommand{\sysname}{{\text{}\small \sf Propane/AT}\xspace}
 \newcommand{\sysnamesec}{{\sf Propane/AT}\xspace}
-
 \newcommand{\Propane}{{\text{}\small \sf Propane}\xspace}
 \newcommand{\mbgp}{{\small \sf mBGP}\xspace}
-
 \newcommand{\para}[1]{\paragraph*{\textbf{#1}}}
 
+%% math
 \newcommand{\set}[1]{\ensuremath{\{ #1 \} }}
@@
 
+%% language
 \newcommand{\CD}[1]{\texttt{\small #1}}
 \newcommand{\KW}[1]{\texttt{\small\bfseries{#1}}}
-
 \newcommand{\True}{\CD{true}}
@@
 \newcommand{\Union}{\ensuremath{\cup}}
-
 \newcommand{\Exit}{\KW{exit}}
@@
 \newcommand{\chdr}[2]{\textbf{#1} {#2} \\ \centering}%
-
 \newcommand{\Topo}[1]{\ensuremath{{\mathrm{topo}}(#1)}}
@@
 
+%% evaluation
 \newcommand{\Conserv}{\cal{C}}
-
+\newcommand{\cmark}{\ding{51}}
+\newcommand{\xmark}{\ding{55}}
+
+%% theorems / appendix
 \newtheorem{thm}{Theorem}[section]
@@
 \newtheorem{lem}[thm]{Lemma}
-
 \newcommand{\Appendix}{technical appendix\xspace}
@@
 
-%\CopyrightYear{2016}
-%\setcopyright{acmcopyright}
-%\conferenceinfo{SIGCOMM '16,}{August 22-26, 2016, Florianopolis , Brazil}
-%\isbn{978-1-4503-4193-6/16/08}\acmPrice{\$15.00}
-%\doi{http://dx.doi.org/10.1145/2934872.2934909}
-
+%% set paper size
 \special{papersize=8.5in,11in}
@@
 
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country}
-\copyrightyear{20yy}
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
-\copyrightdoi{nnnnnnn.nnnnnnn}
-
-%\titlebanner{DRAFT -- do not distribute}        % These are ignored unless
-%\preprintfooter{submission for PLDI 2017}   % 'preprint' option specified.
+%% conference information
+%\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country}
+%\copyrightyear{20yy}
+%\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
+%\copyrightdoi{nnnnnnn.nnnnnnn}
+\toappear{}
+
+%% publication rights
+%\setcopyright{acmcopyright}
+%\setcopyright{acmlicensed}  % default
+%\setcopyright{rightsretained}
 
@@
 %
-%  **Keywords**
-%
-%
-%=====================================================
+%  **Keywords and Descriptions**
+%
+%
+%=====================================================
+
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10003033.10003083.10003098</concept_id>
+<concept_desc>Networks~Network manageability</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10003033.10003099.10003104</concept_id>
+<concept_desc>Networks~Network management</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10011006.10011050.10011017</concept_id>
+<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+\ccsdesc[300]{Networks~Network manageability}
+\ccsdesc[300]{Networks~Network management}
+\ccsdesc[300]{Software and its engineering~Domain specific languages}%
+
+%\printccsdesc
+
+\keywords{Propane/AT; Domain-specific Language; BGP; Fault Tolerance; Compilation; Network Management}
 
@@
 It proceeds by compiling constraints $p_i$ in the original \sysname policy to a tuple of: the predicate $t_i$, the product graph $PG_i$, and the preference function $pref_i$.
-These tuples are passed the the $\mathrm{compile}_\mathrm{mBGP}$ function, along with the network topology $G$.
+These tuples are passed to the $\mathrm{compile}_\mathrm{mBGP}$ function, along with the network topology $G$.
 For each internal router in the topology $l$, and each predicate $t_i$ in the \sysname policy, compilation goes through each node $m$ for $l$ in $PG_i$, and groups the inbound neighbors of $m$ by tag ($q_n$) into sets ($in$).
@@
 
-\para{Data center}
-
-Routers in the data center network run BGP using unique AS numbers and connect to multiple external neighbors.
+\para{Topologies}
+
+Routers in the data centers run BGP using unique AS numbers and connect to multiple external neighbors.
 The routers aggregate some prefix blocks when announcing them to external neighbors, and keep some prefixes internal.
 The data center prefers that traffic leave through certain neighbors over others and should not transit traffic between neighbors.
-The policy also says that the data center routers not use external neighbors to reach ``private" destinations  (i.e., those in the part of the IP address space reserved for private use).
-
+The policy also prevents routers from using external neighbors to reach ``private" destinations  (i.e., those in the IP address space reserved for private use).
+%
 We use a fat tree~\cite{fattree} and scale it by increasing the number of pods. The abstract topology uses one abstract node for each tier with additional nodes for local and global ToRs.
 
-\para{Backbone}
+%\para{Backbone}
 
@@
 Similar to the datacenter, it blocks private destinations from neighbors, drops transit traffic between certain neighbors but not others, and aggregates internal prefixes at the border of the network.
-
+%
 We scale the backbone network from 10 to 240 routers.

### 2017-04-14 paper/abstraction/paper.tex
acks
space cuts

@@
 
-\sysname is implemented in around 9500 lines of F\# code.
-The compiler accepts both concrete and abstract topologies and will generate evolution-friendly configurations for Cisco and Quagga~\cite{quagga} routers by default.
+%\sysname is implemented in around 9500 lines of F\# code. 
+The \sysname compiler generates configurations for Cisco and Quagga~\cite{quagga} routers.
 The fault-tolerance analysis uses $\nu$Z~\cite{z3opt} to both test validity and minimize variables subject to the topology constraints.
@@
 We evaluate \sysname by applying it on policies for backbone and data center networks. 
-We aim to evaluate the expressiveness of our abstractions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.
+%We aim to evaluate the expressiveness of our abstractions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.
 
@@
 
-Our work is related to three threads of prior work.
-
-\para{Network synthesis} Many recent systems focus on allowing operators to specify their policies at a high level.
+%Our work is related to three threads of prior work.
+
+\para{Network synthesis} Many recent systems focus on allowing operators to specify their policies at a high level of abstraction.
 These can be classified into two classes.
-The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell routers how to forward packets~\cite{foster:merlin,fattire,netgen}.
+The first class targets networks based on SDN (software-defined networking) and generates dataplane rules~\cite{foster:merlin,fattire,netgen}.
 The second class, to which our work belongs, targets conventional networks and generates control-plane router configurations~\cite{synet-synthesis,narain+:configassure,propane}.
@@
 
-While not the focus of this paper, \sysname can enable operators to pick the right design for their networks, more quickly and with stronger guarantees.
+%While not the focus of this paper, \sysname can enable operators to pick the right design for their networks, more quickly and with stronger guarantees.
 Today, when picking a design, operators analyze its multiple concrete instantiations because available analysis tools work with concrete topologies~\cite{condor}.
@@
 We thank the many network engineers, especially George Chen and Lihua Yuan, who helped us understand the importance of working with abstract topologies and synthesizing templates. 
-We also thank the PLDI reviewers for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 as well as Cisco award 677002.
+We also thank the PLDI reviewers, and especially our shepherd Alexandra Silva for comments on the paper.
+This work is supported in part by the National Science Foundation award CNS-1161595 as well as Cisco award 677002.
 

### 2017-04-14 paper/abstraction/paper.tex
space edits

@@
 
-We evaluate \sysname by applying it on policies for backbone and data center networks. 
+%We evaluate \sysname on backbone and data center networks. 
 %We aim to evaluate the expressiveness of our abstractions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.
@@
 \subsection{Expressiveness and precision}
-
 \begin{figure}[t!]
   \begin{center}
+\small
       \begin{tabular}{| l | c| c | c | c | c | }
@@
 
-The top part of Figure~\ref{fig:analysis-precision} shows the results for common real-world settings: tree-based topologies coupled with valley-free routing.
+The top part of Figure~\ref{fig:analysis-precision} shows the results for common data center networks: tree-based topologies coupled with valley-free routing.
 We consider four variants of tree topologies: a standard fat tree~\cite{fattree}, the Facebook fat tree~\cite{facebook-fattree}, the F10 fault-tolerant fat tree~\cite{f10-fattree}, and VL2~\cite{vl2-fattree}.
@@
 
-Our results are encouraging for these realistic settings.
+Our results are encouraging for these settings.
 Our abstractions are perfectly expressive for all tree-based topologies---we did not have to fix any aspect of their structure---and the analysis is precise in all cases.
@@
 
-To stress our abstractions and analysis, we consider additional topologies from the literature.
+%To stress our abstractions and analysis, we consider additional topologies from the literature.
 

### 2017-04-14 paper/abstraction/paper.tex
tinker acks

@@
 \para{Acknowledgments}
-We thank the many network engineers, especially George Chen and Lihua Yuan, who helped us understand the importance of working with abstract topologies and synthesizing templates. 
+We thank the many network engineers, especially George Chen and Lihua Yuan, who pointed out the importance of working with abstract topologies. 
 We also thank the PLDI reviewers, and especially our shepherd Alexandra Silva for comments on the paper.

### 2017-04-14 paper/abstraction/paper.tex
tinker acks
added copyright
edits
fix typo in abstract

@@
 %\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}  % default
+\setcopyright{acmlicensed}  % default
 %\setcopyright{rightsretained}
@@
 BGP (border gateway protocol) configurations for large, evolving networks from high-level
-specifications of topology, routing policy, and fault-tolerance.
+specifications of topology, routing policy, and fault-tolerance
 requirements. \sysname is based on new abstractions for capturing
@@
 \ccsdesc[300]{Software and its engineering~Domain specific languages}%
-
-%\printccsdesc
 
@@
 We also thank the PLDI reviewers, and especially our shepherd Alexandra Silva for comments on the paper.
-This work is supported in part by the National Science Foundation award CNS-1161595 as well as Cisco award 677002.
+This work is supported in part by the National Science Foundation award CNS-1161595 and Cisco award 677002.
 

### 2017-04-14 paper/abstraction/paper.tex
fix weird overflow issue

@@
 Our results are encouraging for these settings.
-Our abstractions are perfectly expressive for all tree-based topologies---we did not have to fix any aspect of their structure---and the analysis is precise in all cases.
+Our abstractions are perfectly expressive for tree-based topologies---we did not have to fix any aspect of their structure---and the analysis is precise in all cases.
 

### 2017-04-15 paper/abstraction/paper.tex
a bunch of grammar and spelling fixes

@@
 Unfortunately, templates use the same low-level constructs as ordinary router configurations (\EG,
-adding or removing tags from particular announcements).  In both templatized
+adding or removing tags from announcements).  In both templatized
 and non-templatized configurations, ensuring that a collection of low-level, local configurations
-achieves some important global, network-wide policy, such as a guarantee of connectivity in the face of 
+achieves some important network-wide policy, such as a guarantee of connectivity in the face of 
 failures, is extremely challenging.
@@
 %
-In order to validate  their templates, operators will typically first instantiate a template with appropriate
+To validate their templates, operators will typically first instantiate a template with appropriate
 concrete parameters
@@
 work for the current topology may or may not work for future
-topologies. Ensuing problems may cause operators to make non-uniform changes to particular routers' configurations,
+topologies. Ensuing problems may cause operators to make non-uniform changes to routers' configurations,
 which defeats the purpose of a template system.  An even worse situation is when
-operators have to update many devices to evolve their network.  
+operators must update many devices to evolve their network.  
 Such network-wide configuration changes entail a great deal of risk and can be highly
@@
 from scratch, on the new topology, and the result may be a completely different
-set of configurations.  No operator is
-able to shut down a large, production network, upgrade policy on all devices and 
+set of configurations.  No operator can shut down a large, production network, upgrade policy on all devices and 
 then restart their network.
@@
 When announcing destinations to certain neighbors, a BGP router may perform {\em route aggregation}, \IE, announce a single prefix that covers multiple prefixes (\EG, announce 10.1.0.0/16 instead of 10.1.[1--255].0/24).
-The covering prefix is announced as long as the router has a valid route for {\em any} of the covered prefixes.
+The covering prefix is announced if the router has a valid route for {\em any} of the covered prefixes.
 Aggregation helps reduce the memory consumption of routers, but it can lead to traffic black holes~\cite{route-aggregation}.
@@
 a full mesh. Furthermore, the constraints $AG = AL$ and $AG \leq S$ ensure 
-that, within pods P and Q, the $AG$ and $AL$ roles \dpw{This originally said $AG$ and $TG$ but I changed it.} have the same number of 
+that, within pods P and Q, the $AG$ and $AL$ roles have the same number of 
 routers, which is less than or equal to the number of routers in the spine 
@@
 
-Next we can capture constraint (4) that traffic for local prefixes must stay within in the data center:
+Next, we can capture constraint (4) that traffic for local prefixes must stay within in the data center:
 %
@@
 The second part of the rule uses a similar idea to reason about the overlap between roles $m$ and $o$ with respect to role $n$.
-This rule is particularly useful for data center topologies where routers in one tier of the data center often have a particular striping pattern with another tier.
+This rule is particularly useful for data center topologies where routers in one tier of the data center often have a uniform striping pattern with another tier.
 
@@
 
-The algorithm was able to infer that there is at least 1 disjoint path to any spine router, and at least 2 disjoint paths to any TL router.
+The algorithm could infer that there is at least 1 disjoint path to any spine router, and at least 2 disjoint paths to any TL router.
 In this case, the analysis is precise.
@@
 This mechanism ensures that BGP only considers paths that are allowed by the \sysname policy (\IE, paths in the PG).
-Routers will allow advertisments that correspond to an edge in the PG and will block any advertisments that do not.
+Routers will allow advertisements that correspond to an edge in the PG and will block any advertisements that do not.
 
@@
 If $m \leq n$, then advertisements received for node $m$ can safely be preferred over those received for node $n$ after accounting for the network-wide impact of the choice.
-For example in Figure~\ref{fig:example-compilation}, S1 can receive advertisements in two different contexts $(S1,1,0)$ and $(S1,0,1)$ and must choose between messages received in these different contexts.
-Advertisements are preferred in state $(S1,1,0)$ because they result in a better path for S1 ($(S1,0,1) \geq_{rank} (S1,1,0)$) and downstream routers such as A1 will also obtain paths no worse than if S1 had choosen $(S1,1,0)$.
+For example, in Figure~\ref{fig:example-compilation}, S1 can receive advertisements in two different contexts $(S1,1,0)$ and $(S1,0,1)$ and must choose between messages received in these different contexts.
+Advertisements are preferred in state $(S1,1,0)$ because they result in a better path for S1 ($(S1,0,1) \geq_{rank} (S1,1,0)$) and downstream routers such as A1 will also obtain paths no worse than if S1 had chosen $(S1,1,0)$.
 The policy is guaranteed to be safe from failures because if a link fails in the topology, then $m \leq n$ will still hold since any transition that becomes unusable for $m$ also becomes unusable for $n$.
@@
 The match for N1 is preferred since it has a higher BGP local-preference attribute (110).
-If an advertisement from N1 is choosen, the spine attaches the community tag $(1,0)$ before sending the route to all its peers ($*$).
+If an advertisement from N1 is chosen, the spine attaches the community tag $(1,0)$ before sending the route to all its peers ($*$).
 If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
 %
-The template configuration matches any global prefix {\small \$GP} from any internal peer and re-advertises the route to all of its peers.
-For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers.
-The concrete configurations for S1 and S2 obtained from compilation for the concerete PG from Figure~\ref{fig:example-compilation} have a similar structure for each local and global prefix where local routes are reflected downward, while global routes are advertised to all peers.
+The template configuration matches any global prefix {\small \$GP} from any internal peer and re-advertises the route to all its peers.
+For any local prefix, it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers.
+The concrete configurations for S1 and S2 obtained from compilation for the concrete PG from Figure~\ref{fig:example-compilation} have a similar structure for each local and global prefix where local routes are reflected downward, while global routes are advertised to all peers.
 
@@
 
-Although the disjoint path analysis takes place over the PG, each application of the inference rules from Figure~\ref{fig:inference-rules} depends on the topology locations, but not the automata states, and can be reused accross multiple PG nodes with the same topology location.
+Although the disjoint path analysis takes place over the PG, each application of the inference rules from Figure~\ref{fig:inference-rules} depends on the topology locations, but not the automata states, and can be reused across multiple PG nodes with the same topology location.
 Therefore, we lazily apply the rules and cache the satisfiability and minimization calls to $\nu$Z after their first use.
@@
 The backbone policy classifies neighbors into several categories based on commercial relationship~\cite{gao-rexford} and prefers paths through them in order.
-Similar to the datacenter, it blocks private destinations from neighbors, drops transit traffic between certain neighbors but not others, and aggregates internal prefixes at the border of the network.
+Like the data center, it blocks private destinations from neighbors, drops transit traffic between certain neighbors but not others, and aggregates internal prefixes at the border of the network.
 %

### 2017-04-15 paper/abstraction/paper.tex
remove some old comments and change graph positions to look better

@@
 %\setcopyright{acmcopyright}
-\setcopyright{acmlicensed}  % default
+\setcopyright{acmlicensed}
 %\setcopyright{rightsretained}
@@
 \title{Network Configuration Synthesis with Abstract Topologies \vspace{1cm}}
-
-%\author{Paper \#324, 14 pages}
-
-%\authorinfo{Ryan Beckett}{Princeton University}{rbeckett@cs.princeton.edu}
-%\authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
-%\authorinfo{Todd Millstein}{UCLA}{todd@cs.ucla.edu}
-%\authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
-%\authorinfo{David Walker}{Princeton University}{dpw@cs.princeton.edu}
-
-%\numberofauthors{1}
 
@@
 
-% Hence, one approach to improving network reliability is to develop better
-% languages for network configuration.  Such languages should be defined at a
-% higher level of abstraction than existing configuration languages and provide
-% support built-in support for verification of important properties, thereby
-% avoiding entire classes of configuration errors automatically.
-
-%An important class of networks are the large \emph{structured networks}
-%commonly deployed in industrial data centers.
-
 Computer networks run many critical services, and every second of downtime is
@@
 
-%It is no wonder that a major
-%network outage, such as the one that grounded all United Air flights
-%in July 2015~\cite{x}, makes international news every few months.
-
 Given the challenges of generating and validating network configurations, one
@@
 To address the challenge of configuration synthesis in the presence of abstract roles, we develop \sysname. 
-%BGP, unlike link state protocols
-%such as OSPF, is also particularly
-%useful in our setting because it contains features that help us localize the effects of changes.
 \sysname
@@
 configured in devices.  We achieve it in part by leveraging BGP features that allow arbitrary tags on routing announcements and expressing policy using such tags (instead of router identifiers).
-%These features makes it possible to change network topologies without reflecting those changes in the configurations of distant routers.  
-%Other control plane protocols that do not provide such tagging mechanisms or that implement link-state protocols as opposed to path-vector protocols would not be able to avail themselves of these techniques.
-%No other device in the network is impacted.
 
@@
 bound on the number of link failures required to disconnect one abstract location from another. 
-%given the connectivity constraints of the abstract topology. 
 Any concrete instance of the abstract topology will adhere to the given fault tolerance property.
@@
 abstract topologies.
-%one which guarantees correct compilation and one which determines fault tolerance
-%properties of network policy.
-%Both algorithms provide guarantees for any
-%concrete network satisfying the abstract connectivity invariants.
-%\item Design of a template generation strategy that supports network
-%evolution.
 \item Implementation and evaluation of a \sysname compiler that generates
@@
 \end{itemize}
-
-%% Indeed, over the last several years, many researchers have begun to
-%% develop such languages~\cite{frenetic,pyretic,pane,nettle,netkat}.
-%% However, the bulk of this research has targeted software-defined
-%% networks (SDN), a new networking technology that has emerged over the last
-%% decade.  Unfortunately, the vast majority of today's networks
-%% continue to use traditional networking techology---upgrading to SDN is
-%% expensive and technically challenging.
-
-%% In a traditional network, every router runs an independent instance of
-%% a distributed protocol that
-%% exchange messages about available routes to destination addresses.
-%% Each router is configured independently, but the overall behavior
-%% of the network---the paths from one server to another, for instance---depend
-%% upon the
 
@@
 All route announcements carry an {\em AS path}, the sequence of BGP networks, called autonomous systems (ASes), that will be traversed to reach the destination.
-%When BGP is used inside a data center, each router tends to be its own AS.
 Optionally, they may also include one or more {\em communities}, which are arbitrary tags whose semantics are agreed upon out of band.
@@
 
+\begin{figure}[t!]
+  \centering
+  \includegraphics[width=2.5in]{figures/example2}
+  \vspace{-.8em}
+  \caption{A modified version of the network in Figure~\ref{fig:example}.}
+  \label{fig:example2}
+  \vspace{-.8em}
+\end{figure}
+
 The intended policy for this network is:
@@
 A {\em role} is a specific function that is served by one or more routers.
-%\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor configuration languages.}
-%
 For example, the network in Figure~\ref{fig:example} might have five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
@@
 Such a black hole will not occur in Figure~\ref{fig:example} because spine routers have two links to each pod.
-
-%Unfotunately, currently, there is no way to predict which variations will behave correctly for a given set of templates.
-
-\begin{figure}[t!]
-  \centering
-  \includegraphics[width=2.5in]{figures/example2}
-  \vspace{-.8em}
-  \caption{A modified version of the network in Figure~\ref{fig:example}.}
-  \label{fig:example2}
-  \vspace{-.8em}
-\end{figure}
 
@@
 
-%\subsection{Inputs}
-
 \sysname takes as input the network's abstract topology and its policy.
@@
 
-%Ideally, we would like to find a suitable topology abstraction that can describe both of the data centers from figures~\ref{fig:example} and~\ref{fig:example2} as well as any reasonable generalization of these data centers.
-\sysname provides several abstraction mechanisms to achieve this goal.
-
-%We introduce our topology abstractions using the networks from \S\ref{sec:motivation}.
 Our topology abstractions consist of several concepts.
@@
 On its own, this abstraction loses a lot of information about the concrete network's structure, making it difficult to reason precisely about fault-tolerance.
-%which would hinder a useful analysis of its fault-tolerance.
 For example, with this abstraction any spine router may or may not connect to any aggregator router.
@@
 This allows operators to define complex networks in which some (e.g., legacy) parts of the network cannot evolve while others can.
-%It also means that our compiler subsumes those that operate only over concrete topologies.
 
@@
 policy cannot be met.
-%\ryan{Possibly cut here}
-%More specifically,
-%for each abstract role in the network, our analysis will learn facts about the
-%number of disjoint paths to routers in that role.  For example,
-%the fact $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
-%in the $S$ (Spine) role, there are 6 disjoint paths to the group---3
-%for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
-%\emph{some} group of 2 nodes has the property as opposed to all.
-%More generally, there is one quantifier ($A$ for all groups
-%and $S$ for exists a group).  When nodes are nested within pods,
-%there is one quantifier for each level of the hierarchy, so
-%$S_P S_{TG} (i,j)$ means that for some pod from the $P$ group of pods
-%and for some nodes in the $TG$ role within that pod, there exists a
-%group of $i$ nodes with $j$ paths to each node in the group.
-
-%\ryan{Possibly cut here}
-%As an example, suppose we want to compute the number of of disjoint paths between any global ToR and spine router in Figure~\ref{fig:example3}.
-%The analysis begins with the fact
-%$S_P S_{TG} (1,1)$---there is some group of
-%nodes of size 1 in the $TG$ role in some pod $P$ such that any initial
-%node in the $TG$ role has 1 disjoint path to it (and all such paths are
-%edge-disjoint). Since the abstract topology specifies that each node in
-%the $TG$ role is in
-%a full mesh with nodes in the $AG$ role within any given pod, we
-%infer the fact $S_P A_{AG}(e1,1)$. This says that
-%any group of nodes of size e1 in the $AG$ role is reachable with at
-%least 1 path to each such node from any initial node in
-%the $TG$ role.
-%
-%After one more step, the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node
-%In fact, due the valley-free routing constraint, a single path is
-%the worst-case fault-tolerance level for the concrete network from
-%Figure~\ref{fig:example2}.
 
@@
 The following sections detail each of the three phases.
-
-%
-%The constraint prevents traffic from over taking a path that traverses
-%either [Agg->Tor->Agg] or [Spn->Agg->Spn]. The final policy remains the same as before,
-%by combining each of these policies together.
-%
-%
 
@@
 
-%For example, the combining the Routing and Local constraints in the data center policy from \S\ref{sec:overview} would result in the following \sysname policy:
-%
-%\begin{code}
-%\$PG  \Path \End(TG),
-%\$PL  \Path \End(TL) \ensuremath{\cap} \Always(\In),
-%\True \Path \Exit(Peer1) \Prefer \Exit(Peer2)
-%\end{code}
-%\noindent%
-%
-
-%After converting the routing policy to the regular expression based language,
 We are now ready to generate the PG.
 Intuitively, the PG captures topology and routing constraints by ``intersecting" the finite automata associated with the policy regular expressions with the graph structure of the topology.
-%The PG compactly encodes all paths that protocol messages should be passed along through the network in order to guarantee that the BGP-speaking devices find policy-compliant paths dynamically.
-%
-%Although \sysname policies describe the routes that traffic should take through the network, network protocols (including BGP) typically disseminate router information in the opposite direction.
-For example, a router Y will tell its neighbor X that it has a route to the destination meaning that X can send traffic through Y.
-For this reason, we start by compiling
-%
 Because there can be a separate routing policy for each predicate $t$ in the policy, we construct one PG for each predicate.
@@
 Figure~\ref{fig:example-compilation} shows the PG for the data center policy that applies to all external traffic ($\CD{\True \Path \Exit(N1~\Prefer~N2)}$).
-%
-%\begin{code}
-%\True \Path \Exit(\sf{Peer1}) \Prefer \Exit(\sf{Peer2})
-%\end{code}
-%\noindent%
 %
@@
 As shown in \S\ref{sec:generation}, our generation strategy commutes with template instantiation, meaning that we obtain the same results if we instantiate the abstraction early, or if we defer the instantiation until after template generation.
-%
-%Lemma~\ref{lem:homomorphism} provides intuition as to why our strategy for generating templates is correct.
-%Abstract product graphs are related to concrete product graphs via a graph homomorphism, just as abstract topologies are related to concrete topologies via a graph homomorphism.
 
@@
 \label{sec:analysis}
-
-%In practice, operators would often like to reason about a variety of properties for, not only their current network topology, but also future versions of it.
-%% The Product Graph provides a convenient representation to capture the joint impact of both topology and routing policy.
-In this section we present an analysis that operates over the abstract Product Graph to find a lower bound on the number of disjoint paths between pairs of concrete nodes.
-Answering questions about the number of disjoint paths between nodes allows operators to reason about many useful network properties such as reachability (\IE, is there at least one path) and fault tolerance (\EG, how many failures will disconnect certain routers).
-
-%\subsection{Abstract k-disjoint paths}
-%\label{sec:property-checking}
 
@@
 
-%The problem for \sysname is harder because it must verify that all possible concrete instantiations of an abstract topology satisfy the fault-tolerance policy, which requires a fundamentally different approach.
-
-%
 We frame satisfying the fault-tolerance requirements as an analysis problem over the structure of the PG.
@@
 
-%
 For each node in the abstract PG,
@@
 and for some/all groups of nodes in the role $X_n$ of size $j$,
-%, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds. The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers,
 there are $k$ paths to each such that all $j*k$ paths are edge-disjoint.
@@
 The box shows the conditions that must be valid, given the abstraction constraints, for the rule to apply.
-%Validity ensures that the condition holds for all concrete instantiations of the topology.
 
@@
 We conservatively use $1$ for the number of disjoint paths to each node in role $n$, since when $n$ is very large, all reachable nodes in role $m$ might only have a single edge to completely different nodes in $n$.
-%However, because we do not know for certain that all $j$ nodes in role $m$ have outgoing edges to the same nodes at the top, we conservatively use $1$ for the number of disjoint paths to each node on top.
-%For example, if $n$ is very large, then each node in role $m$ may have only a single edge to each reachable node in role $n$.
 
@@
 
-%The rule \infrule{I-out2} follows a similar line of reasoning.
-It says that if any group of size $j$ with $k$ disjoint paths to each is reachable in the bottom role, and there is at least one incoming edge for each concrete node in the top role, then there are $min(j,e_2)$ disjoint paths to any single concrete node in the top role.
-This is because we can choose the $j$ nodes on the bottom for which we want to find disjoint paths, and then use each of the $e_2$ disjoint incoming edges for the particular node at the top connecting it to the bottom.
-
 The two rules \infrule{I-mesh1} and \infrule{I-mesh2} handle the case where there is a full mesh between the two roles.
@@
 To each node in role $n$, from a node in role $m$, we can construct at least the minimum of $X$ and $k$ disjoint paths.
-
-%The rule \infrule{I-mincut} can be thought of as an assertion about the fault tolerance between nodes in two roles.
-The rule applies to an edge that has been annotated with a $mincut(X)$ statement, which means that there are at least $X$ disjoint paths between any node in role $m$ and any node in role $n$.
 
@@
 Facts learned with $j=0$ or $k=0$ are discarded.
-
-%The algorithm associates with each inference, the set of abstract locations used to derive the inference, \IE, an overapproximation of set of concrete locations used for the edge-disjoint paths.
-When applying an inference rule between an invariant at role $m$, with a set of abstract locations $C$, to learn an invariant at role $n$, we associate the new invariant with the set $C \cup \{ n \}$.
-%
-%When, at a single PG node there is an inference $L_{X_1} \dots L_{X_{n-1}}$ A$_m(j,k)$ with location set $C$ and inference $L_{X_1} \dots L_{X_{n-1}}$ L$_m(j',k')$ with location set $D$, where $C \cap D = \emptyset$, we add a new inference with location set $C \cup D$:
-%
-%$$L_{X_1} \dots L_{X_{n-1}} L_m(\min(j, j'), k + k')$$
-%
-%\noindent
-%The idea is that, because non-overlapping abstract paths can never contain overlapping concrete paths, due to the graph homomorphism property, we can merge inferences about these disjoint paths in the abstraction.
 
@@
 There exists a concrete network, namely the data center from Figure~\ref{fig:example2}, where a single failure can disconnect a global ToR from a spine router due to the valley-free constraint.
-%The bound on the fault tolerance between ToR and spine routers can also be used to determine that an aggregation-induced black hole may arise at the data center boundary after a single failure in some concrete instantiation.
 
@@
 We now look at each of these steps in turn.
+
+\newcommand{\Con}{\text{con}}
+\newcommand{\Pfx}{\mathit{pfx}}%
+
+\vspace{2em}
+\begin{figure*}[t!]\small%
+
+  %\vspace{1em}%
+  \begin{minipage}[t]{.47\linewidth}
+  \hdr{mBGP Syntax}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{rclr}
+     d    &\in& \textit{Integers} & \\
+     c    &\in& \textit{Communities} & \\
+     l    &\in& \textit{Topology Locations} & \\
+     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
+     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
+     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
+     pc   &::=& ma_1, \dots, ma_k & \textit{predicate config} \\
+     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
+     mbgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{mbgp policy} \\%
+  \end{array} \]%%
+
+  \end{minipage}
+  %
+  %
+  \begin{minipage}[t]{.49\linewidth}
+  \hdr{Compilation to mBGP}{}
+  \vspace*{-1\baselineskip}
+  %
+  \[ \begin{array}{l}
+     \mathrm{compile}_\mathrm{mBGP}( [(t_1,PG_1,pref_1), \dots, (t_k,PG_k,pref_k)], G ) = \\
+     ~~~~~ [~ l \rightarrow rc ~\vert~ l \in \mathrm{internal}(G.V), ~rc = \mathrm{append}_i~  \\
+     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow [~ ma ~\vert~ \\
+     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
+     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \mathrm{adjIn}(PG_i,m), \\
+     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathrm{adjOut}(PG_i,m) \}, \\
+     ~~~~~~~~~~~~~~~~~~~~~ ma = \mathrm{pref}_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~] \\
+     \\
+     \mathrm{compile}( p_1, \dots, p_k, G) = \\
+     ~~~~~~ \mathrm{compile}_\mathrm{mBGP}([\mathrm{compile}_\mathrm{PG}(p_1,G), \dots, \mathrm{compile}_\mathrm{PG}(p_k,G)], G) \\
+  \end{array} \]%
+  \end{minipage}%
+
+  \vspace{1em}
+  \hrulefill%
+  \vspace{-.8em}
+  \caption{mBGP syntax (left), and compilation from product graphs (right).}
+  \label{fig:concretization}
+  \vspace{-.4em}
+\end{figure*}%
 
@@
 
-\newcommand{\Con}{\text{con}}
-\newcommand{\Pfx}{\mathit{pfx}}%
-
-\vspace{2em}
-\begin{figure*}[t!]\small%
-
-  %\hrulefill%
-
-  %\vspace{1em}%
-  \begin{minipage}[t]{.47\linewidth}
-  \hdr{mBGP Syntax}{}
-  \vspace*{-1\baselineskip}
-  %
-  \[ \begin{array}{rclr}
-     d    &\in& \textit{Integers} & \\
-     c    &\in& \textit{Communities} & \\
-     l    &\in& \textit{Topology Locations} & \\
-     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
-     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
-     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
-     pc   &::=& ma_1, \dots, ma_k & \textit{predicate config} \\
-     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
-     mbgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{mbgp policy} \\%
-  \end{array} \]%%
-
-  \end{minipage}
-  %
-  %
-  \begin{minipage}[t]{.49\linewidth}
-  \hdr{Compilation to mBGP}{}
-  \vspace*{-1\baselineskip}
-  %
-  \[ \begin{array}{l}
-     \mathrm{compile}_\mathrm{mBGP}( [(t_1,PG_1,pref_1), \dots, (t_k,PG_k,pref_k)], G ) = \\
-     ~~~~~ [~ l \rightarrow rc ~\vert~ l \in \mathrm{internal}(G.V), ~rc = \mathrm{append}_i~  \\
-     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow [~ ma ~\vert~ \\
-     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
-     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \mathrm{adjIn}(PG_i,m), \\
-     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathrm{adjOut}(PG_i,m) \}, \\
-     ~~~~~~~~~~~~~~~~~~~~~ ma = \mathrm{pref}_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~] \\
-     \\
-     \mathrm{compile}( p_1, \dots, p_k, G) = \\
-     ~~~~~~ \mathrm{compile}_\mathrm{mBGP}([\mathrm{compile}_\mathrm{PG}(p_1,G), \dots, \mathrm{compile}_\mathrm{PG}(p_k,G)], G) \\
-  \end{array} \]%
-  \end{minipage}%
-
-  \vspace{1em}
-  \hrulefill%
-  \vspace{-.8em}
-  \caption{mBGP syntax (left), and compilation from product graphs (right).}
-  \label{fig:concretization}
-  \vspace{-.4em}
-\end{figure*}%
-
 \para{Preference Search}
@@
 
-%
 For example, in Figure~\ref{fig:example-compilation} the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation.
@@
 Therefore, advertisements received at $S1$ with tag $(1,0)$ must be preferred to those received at $S1$ with tag $(0,1)$.
-%
 Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds. This leads to the following observation:
@@
 Finally, during template instantiation the tags are left unmodified.
-%Therefore, we can prevent modifications to the spine routers' configurations by associating a new unique community tag for template variable {\small \$GP} and then replacing each match on {\small \$GP} with a test on the new community tag.
-The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can match against it.
 Figure~\ref{fig:bgp-configs} (right) shows the spine and ToR templates after this transformation.
@@
       VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
-%      \end{tabular}
-%  \end{center}
-%  \vspace{-.6em}
-%  \caption{Expressiveness and analysis precision for fat tree topologies with valley-free routing policy.}
-%  \label{fig:analysis-precision2}
-%\end{figure}
-%
-%\begin{figure}[t!]
-%  \begin{center}
-%      \begin{tabular}{| l | c | c | c | c | c | }
-%      \hline
-%      \textbf{Topology} & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
-%      & & Some & All & Some & All \\
-%      & & Pairs & Pairs & Pairs & Pairs \\ \hline
 
@@
 
-%For each topology in Figure~\ref{fig:analysis-precision} we define a suitable abstraction.
-Since many topologies have tunable parameters (\EG, the recursion depth $k$ for the DCell topology), we list all such parameters that are fixed for the abstraction.
-For all topologies (Figure~\ref{fig:analysis-precision}), we implement a shortest path routing policy.
-Additionally, for clos-style topologies, we implement a valley-free routing policy (Figure~\ref{fig:analysis-precision2}) for comparison.
-In each case, we record the precision of the analysis in terms of whether or not it is able to accurately prove reachability and/or the correct number of disjoint paths between some or all pairs of nodes from a fixed source.
-
-%\para{Fat Tree Topologies}
-%
-%The fat tree topology is a widely used data center topology.
-We look at the precision of our analysis on four fat tree variants used in practice: a standard fat tree~\cite{fattree}, the Facebook fat tree~\cite{facebook-fattree}, the F10 fault tolerant fat tree~\cite{f10-fattree}, and the VL2 topology~\cite{vl2-fattree}.
-For each fat tree variant, we use a tiered abstraction similar to that in our previous example.
-Each fat tree topology is parameterized over the number of pods $k$, which can be scaled up in the abstraction to allow for expansion.
-
 \begin{figure}[t!]
@@
 The HyperX~\cite{hyperx} topology generalizes the hypercube and butterfly topologies and includes parameters $L$ for the lattice dimension of the network, and $S_i$ for the node multiplicity of each dimension $i$.
-%$K_i$ for the bandwidth of links for each dimension,
-%and $T$ for the number of terminal nodes (servers) connected to each router.
 For a fixed number of dimensions $L$, we abstract each full mesh of $S_L$ nodes into its own abstract node.
@@
 Figure~\ref{fig:example-abstractions} shows an example for $L=2$.
-%For all hypercube variants, the fault-tolerance analysis is precise.
 
@@
 A similar pattern occurs with other tree-based topologies.
-%
-%For all fat tree variants, the analysis correctly computes the number of ToR to ToR disjoint paths, but can lose precision between ToR to spine routers due to valley paths.
-For a valley-free routing policy, the analysis is precise for ToR to spine connectivity.
 For both recursive topologies, the analysis can only accurately determine reachability.
-%For the BCube topology, it is able to to determine the correct number of disjoint paths between some pairs of nodes, but not all.
-For all hypercube topologies, \sysname's fault-tolerance analysis is precise.
-
-%\para{Random Network Topologies}
-%
-%Random networks such as Scafida and Jellyfish have seen a great deal of interest in academia.
-These topologies were designed with an eye towards incremental expansion and are based on probabilistic arguments of bisection bandwidth in random regular graphs.
-However, because the topologies are created randomly, there are no hard guarantees on the connectivity between different routers.
-We can trivially represent these networks using a \emph{one big router} abstraction for the entire network.
 
@@
 
-%\para{Backbone}
-
 The backbone policy classifies neighbors into several categories based on commercial relationship~\cite{gao-rexford} and prefers paths through them in order.
@@
 \label{sec:related}
-
-%Our work is related to three threads of prior work.
 

### 2017-04-15 paper/abstraction/paper.tex
more spelling fixes from aspell

@@
 Specifically, in Figure~\ref{fig:example2}, an aggregation-based black hole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]).
-Such a black hole will not occur in Figure~\ref{fig:example} because spine routers have two links to each pod.
+Such a black hole will not occur in Fn Figure~\ref{fig:example} because spine routers have two links to each pod.
 
@@
 we introduce additional concepts. The first is topology hierarchy, captured by P and Q, which indicate that nodes in the ToR and aggregator roles are grouped into pods.
-The second is node and edge \emph{multiplicity}. Each edge (and node) is labelled
+The second is node and edge \emph{multiplicity}. Each edge (and node) is labeled
 with a symbolic variable (\EG, $e1$) that denotes a constraint on the number of edges (and nodes) that may appear in any valid concrete network.
@@
 %\begin{defn}
-The PG can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge.
+The PG can be viewed as a labeled transition system by pushing the location from each directed edge's target node onto the edge.
 That is, $m\overset{l}{\rightarrow}n$ if there is an edge $(m,n)$ in the PG and $\Topo{n} = l$.

### 2017-05-15 paper/abstraction/paper.tex

@@
 which operates over concrete topologies. As the number of devices in a
-network grows, the number of distinct roles will often stay constant~\cite{surgery}.
+network grows, the number of distinct roles will often stay constant.
 Consequently, \sysname can be two orders of magnitude
@@
 \para{Network verification}
-A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery,coalgebraic}.
+A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,batfish,bagpipe,arc,era,coalgebraic}.
 Our focus, in contrast, is on a correct-by-construction approach.

### 2017-05-15 paper/propane/SOSR/sosr.tex

@@
 Request permissions from Permissions@acm.org.}
-
-%\conferenceinfo{SOSR'17,}{April 3--4, 2017, Santa Clara, CA.} 
-%\copyrightetc{\copyright~2017 ACM. ISBN \the\acmcopyr}
-%\crdata{xxx.\\
-%DOI: http://dx.doi.org/10.1145/XXX.XXXXXXX}
-%% Update the XXX's to the DOI assigned by ACM rightsreview forms
-%\clubpenalty=10000 
-%\widowpenalty = 10000
 
@@
 
-\category{C.2.3}{Computer-Communication Networks}{Network Operations}
-\category{D.2.2}{Software Engineering}{Design Tools and Techniques}
+%\category{C.2.3}{Computer-Communication Networks}{Network Operations}
+%\category{D.2.2}{Software Engineering}{Design Tools and Techniques}
 
@@
 <concept_desc>Networks~Network manageability</concept_desc>
-<concept_significance>500</concept_significance>
+<concept_significance>300</concept_significance>
 </concept>
@@
 <concept_desc>Networks~Network management</concept_desc>
-<concept_significance>500</concept_significance>
+<concept_significance>300</concept_significance>
 </concept>
@@
 <concept_desc>Software and its engineering~Domain specific languages</concept_desc>
-<concept_significance>500</concept_significance>
+<concept_significance>300</concept_significance>
 </concept>
@@
 
-\ccsdesc[500]{Networks~Network manageability}
-\ccsdesc[500]{Networks~Network management}
+\ccsdesc[300]{Networks~Network manageability}
+\ccsdesc[300]{Networks~Network management}
 \ccsdesc[300]{Networks~Network control algorithms}
-\ccsdesc[500]{Software and its engineering~Domain specific languages}
+\ccsdesc[300]{Software and its engineering~Domain specific languages}
+
+\printccsdesc
 

### 2017-05-29 paper/abstraction/paper.tex
remove printing from command line

@@
 \usepackage{amsthm}
+\usepackage[labelfont=bf]{caption}
 \usepackage{subcaption}
@@
 \usepackage{pifont}
+
+\setlength{\bibsep}{1.8pt}
 
@@
 \authorinfo{Ryan Beckett$^*$\and Ratul Mahajan$^{\dagger\ddagger}$\and Todd Millstein$^{\dagger\S}$\and Jitendra Padhye$^\ddagger$\and David Walker$^*$}
-{Princeton University$^*$ \hspace{0.2in} Intentionet$^\dagger$ \hspace{0.2in}  Microsoft$^\ddagger$ \hspace{0.2in}  University of California Los Angeles$^\S$}
+{Princeton University, USA$^*$ \hspace{0.2in} Intentionet, USA$^\dagger$ \hspace{0.2in}  Microsoft, USA$^\ddagger$ \hspace{0.2in}  UCLA, USA$^\S$}
 %{\{rbeckett,dpw\}@cs.princeton.edu, \{ratul,padhye\}@microsoft.com, todd@cs.ucla.edu}
@@
 
-\textbf{Abstract---}
+\begin{abstract}
 We develop \sysname, a system to synthesize provably-correct
@@
 faster than systems that operate on concrete topologies.
+\end{abstract}
 
@@
 
-\section{Propane/AT overview}
+\section{Propane/AT Overview}
 \label{sec:overview}
@@
 
-\para{Abstract topology}
+\para{Abstract Topology}
 Abstract topologies in \sysname define structural and role-based invariants that compactly describe all concrete networks that can emerge as the network evolves.
@@
 
-\para{Routing policy} Routing policies in \sysname consist of an ordered sequence of $i)$ a predicate that matches a class of traffic; and $ii)$ paths that the traffic should take through the network, ranked per their relative preference.
+\para{Routing Policy} Routing policies in \sysname consist of an ordered sequence of $i)$ a predicate that matches a class of traffic; and $ii)$ paths that the traffic should take through the network, ranked per their relative preference.
 \sysname borrows syntax from \Propane~\cite{propane}, but instead of concrete predicates and paths, uses abstract predicates and paths.
@@
 
-\para{Fault-tolerance policy} This policy specifies how many link failures the network should be able to withstand before traffic experiences connectivity loss.
+\para{Fault-Tolerance Policy} This policy specifies how many link failures the network should be able to withstand before traffic experiences connectivity loss.
 Operators can specify different tolerance levels for different pairs of abstract nodes.
@@
 
-\section{Fault-tolerance Analysis}
+\section{Fault-Tolerance Analysis}
 \label{sec:analysis}
@@
 
-\subsection{Inference rules}
+\subsection{Inference Rules}
 
@@
 
-\subsection{Inference algorithm}
+\subsection{Inference Algorithm}
 
@@
 
-\subsection{Expressiveness and precision}
+\subsection{Expressiveness and Precision}
 \begin{figure}[t!]
@@
 \para{Results}
-The bottom part of Figure~\ref{fig:analysis-precision} shows the results for all types of topologies coupled with shortest-path routing.
-(Valley-free routing is not meaningful for non-tree-based topologies.) For all tree-based topologies, the analysis is precise for determining reachability, but for three of them, it does not compute a tight bound for disjoint paths for all router pairs.
+The bottom part of Figure~\ref{fig:analysis-precision} shows the results for all types of topologies with shortest-path routing.
+(Valley-free routing is not meaningful for non-tree-based topologies.) For all tree-based topologies, the analysis is precise for reachability, but for three of them, it does not compute a tight bound for disjoint paths for all router pairs.
 Specifically, it underestimates ToR-to-spine paths; it fails to account for some circuitous paths that traverse another spine because it could not disambiguate two concrete spines that map to the same abstract role.
@@
 A similar pattern occurs with other tree-based topologies.
+%
 For both recursive topologies, the analysis can only accurately determine reachability.
@@
 The backbone policy classifies neighbors into several categories based on commercial relationship~\cite{gao-rexford} and prefers paths through them in order.
-Like the data center, it blocks private destinations from neighbors, drops transit traffic between certain neighbors but not others, and aggregates internal prefixes at the border of the network.
+Like the data center, it blocks private destinations from neighbors, drops transit traffic between certain pairs of neighbors, and aggregates internal prefixes at the network border.
 %
 We scale the backbone network from 10 to 240 routers.
-To abstract it, we split it into two parts: border routers that connect to external neighbors and an internal core.
+We split it into two parts: border routers that connect to external neighbors and an internal core.
 We use one abstract node for the border routers and one for the network core with mincut annotations both within the core and between the core and border roles.
@@
 For the networks we studied above, we made a range of changes, including adding and removing routers and pods and changing prefixes that routers originate.
-In each case, we found the guarantee to hold; for prefix changes, only the originator's configuration changed.
+In each case, we found the guarantee to hold.
 In contrast, all router configurations were modified with \Propane because it heavily uses prefix lists which are sensitive to such changes.
-While \Propane may be made friendlier to network evolution (e.g., prefix lists are unnecessary at aggregation routers), its fundamental limitation will remain because it does not understand roles and the network's structure that \sysname leverages.
+While \Propane may be made friendlier to network evolution,
+%(e.g., prefix lists are unnecessary at aggregation routers), 
+its fundamental limitation will remain because it does not understand roles and the network's structure that \sysname leverages.
 
@@
 
-\para{Network synthesis} Many recent systems focus on allowing operators to specify their policies at a high level of abstraction.
+\para{Network Synthesis} Many recent systems allow operators to specify their policies at a high level of abstraction.
 These can be classified into two classes.
@@
 
-\para{Topology design} Network topology design, especially for data centers, is another active research area, with researchers exploring designs with different properties~\cite{fattree,facebook-fattree,f10-fattree,vl2-fattree,bcube,dcell,hyperx,butterfly}.
+\para{Topology Design} Network topology design, especially for data centers, is another active research area, with researchers exploring designs with different properties~\cite{fattree,facebook-fattree,f10-fattree,vl2-fattree,bcube,dcell,hyperx,butterfly}.
 We do not develop new designs but develop abstractions that can capture these designs (and their evolution).
@@
 
-\para{Network verification}
+\para{Network Verification}
 A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,batfish,bagpipe,arc,era,coalgebraic}.
@@
 
-\para{Acknowledgments}
-We thank the many network engineers, especially George Chen and Lihua Yuan, who pointed out the importance of working with abstract topologies. 
+\acks
+We thank George Chen and Lihua Yuan, who pointed out the importance of working with abstract topologies.
 We also thank the PLDI reviewers, and especially our shepherd Alexandra Silva for comments on the paper.
